### 2018-12-03 README.Rmd
First commit

---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fishcom

The goal of fishcom is to ...

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

### 2018-12-04 README.Rmd
Generate Readme + add notes

@@
 
-The goal of fishcom is to ...
+The goal of fishcom is to get all the informations concerning the ECOSTAB postdoc
+project in one place including reproducible code, notes, eventually data and
+manuscript.
 
-## Example
+## How to
 
-This is a basic example which shows you how to solve a common problem:
-
-```{r example}
-## basic example code
-```
+My notes are available in the introductory vignette
+[intro.html](https://github.com/alaindanet/fishcom/blob/master/vignettes/intro.html)

### 2018-12-05 README.Rmd
Add description of link construction
Put the "How to" informations for Colin & Maud

--- 2018-12-03 README.Rmd
@@
 
-The goal of fishcom is to ...
+[![Build Status](https://travis-ci.org/alaindanet/fishcom.svg?branch=master)](https://travis-ci.org/alaindanet/fishcom)
 
-## Example
+The goal of fishcom is to get all the informations concerning the ECOSTAB postdoc
+project in one place including reproducible code, notes, eventually data and
+manuscripts.
 
-This is a basic example which shows you how to solve a common problem:
+## How to
 
-```{r example}
-## basic example code
+### Get the repository
+
+You can clone the repository with [git](https://git-scm.com/) by pasting in your terminal:
+
 ```
+git clone https://github.com/alaindanet/fishcom.git dir_name_to_be_created
+```
+OR
+
+just download the repository: [alaindanet/fishcom](https://github.com/alaindanet/fishcom/archive/master.zip)
+
+### Open it in Rstudio
+
+If you have [Rstudio](https://www.rstudio.com/) installed on your computer, just open `fishcom.Rproj` with
+Rstudio.
+
+## Information
+
+My notes are available in the introductory vignette `vignettes/intro.html`

### 2018-12-11 R/plot_methods.R
Explore dataset quality

@@ -1,0 +1,22 @@
+theme_alain <- function(){
+
+  hrbrthemes::theme_ipsum_rc() +
+  theme(#Whipe
+    text = element_text(family = "Helvetica", hjust = .5),
+    axis.title = element_text(family = "Helvetica", hjust = .5, face = "bold", size = 10),
+    plot.title = NULL,
+    axis.title.x = NULL,
+    axis.title.y = NULL,
+    axis.text.x = NULL,
+    axis.text.y = NULL,
+    strip.text = NULL) +
+  theme(#Set up
+    plot.title = element_text(family = "Helvetica", hjust = .5, face = "bold", size = 10),
+    axis.title.y = element_text(angle = 90, face = "bold"),
+    axis.title.x = element_text(face = "bold"),
+    axis.text = element_text(size = 8),
+    strip.text = element_text(size = 8),
+    plot.margin = unit(c(.5, .5, .5, .5), "cm")
+    )
+
+}

### 2018-12-12 R/plot_methods.R
Add sampling effort analysis

@@ -1,3 +1,8 @@
+#' Personal plot theme
+#'
+#' @details This theme was design from the theme developped in the hrbrthemes
+#' package: https://github.com/hrbrmstr/hrbrthemes 
+#' @return a ggplot theme
 theme_alain <- function(){
 
   hrbrthemes::theme_ipsum_rc() +
@@ -18,5 +23,4 @@ theme_alain <- function(){
     strip.text = element_text(size = 8),
     plot.margin = unit(c(.5, .5, .5, .5), "cm")
     )
-
 }

### 2018-12-13 data-raw/clean_fish_op_data.R
Cleaning done and validated with Bonnafé work

@@ -61,8 +61,9 @@ columns_meaning <- read_delim("../bonnafe_work/data/raw_data/Codes_colonne.txt",
 library('data.table')
 fish_op <- fread("../bonnafe_work/data/raw_data/NEW_DATA.txt")
 colnames(fish_op) <- str_to_lower(colnames(fish_op))
-write_csv(fish_op[species != c("SAT", "LPP", "LPR")],
+write_csv(fish_op[!(fish_op$species %in% c("SAT", "LPP", "LPR"))],
   "global_fish_op.csv")
+rm(fish_op)
 
 ## Contains only the minimum information: code of the capture, species, body
 ## length 
@@ -138,3 +139,24 @@ environmental_data %<>%
 
 devtools::use_data(environmental_data, overwrite = TRUE)
 rm(environmental_data)
+
+############################################################
+#  Check that data_clean of Guillem is the same than mine  #
+############################################################
+
+
+##Let's check how many fishing operation there is in data_clean of bonnafé and
+##compare them to what we have
+data(environmental_data)
+opcod_to_compare <- environmental_data %>%
+  distinct(opcod)
+library(data.table)
+opcod_willem <- fread("../bonnafe_work/data/raw_data/data_clean.txt",
+  select = c("OPCOD")) %>%
+  as.tibble() %>%
+  rename("opcod" = "OPCOD") %>%
+  distinct(opcod)
+##It's ok:
+all_equal(opcod_willem, opcod_to_compare)
+
+# Cleaning done! +1 for the reproducibility!

### 2018-12-13 data-raw/quantile_generation.R

@@ -6,25 +6,12 @@ library('tidyverse')
 library('magrittr')
 devtools::load_all()
 
-###############
-#  Load data  #
-###############
-diet_shift <- read_delim("ontogenic_diet_shift_fish.csv",
-  delim = ";", locale = locale(decimal_mark = "."))
-pred_win <- read_delim("fish_fish_predation_window.csv",
-  delim = ";", locale = locale(decimal_mark = "."))
+
+#########################
+#  Cleaned data reload  #
+#########################
 data(fish_length)
 
-###########################
-#  Pre-data manipulation  #
-###########################
-colnames(pred_win) <- str_replace_all(colnames(pred_win),
-  c("par_" = "", "1" = "alpha", "2" = "beta", "_code" = ""))
-devtools::use_data(pred_win)
-
-colnames(diet_shift) <- str_replace_all(colnames(diet_shift),
-  c("species" = "species_name", "species_name_code" = "species"))
-devtools::use_data(diet_shift)
 
 #########################
 #  Quantile estimation  #
@@ -46,8 +33,15 @@ quant_willem %<>% arrange(species)
 quant_to_compare <- spread(quartile, quartile, size) %>%
   select(species, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
   arrange(species)
+## Not the same number of species:
 all_equal(quant_willem, quant_to_compare)
+## Indeed, we removed the migratory species as in bonnafé script: cleanData.r
+all_equal(filter(quant_willem, !(species %in% c("SAT", "LPP", "LPR"))),
+  quant_to_compare)
+## Looks ok! 
 
-filter(quant_willem, row_number() %in% c(43, 33, 32))
-filter(quant_to_compare, row_number() %in% c(43, 33, 32))
-## Some fish have disappeared ? Because my ranges are always thiner
+##########
+#  Save  #
+##########
+fish_size_quantile <- quant_to_compare
+devtools::use_data(fish_size_quantile)

### 2018-12-19 tests/testthat/test-metaweb_build.R
Piscivory and theoretical prey size are ok

@@ -3,25 +3,6 @@ context("metaweb_build")
 library('tidyverse')
 library('magrittr')
 
-data(fish_length_toy)
-data(fish_diet_shift)
-data(resource_diet_shift)
-data(pred_win)
-#############
-#  Metaweb  #
-#############
-test_that("Metabuild returns a correct matrix",{
-  fish_diet_shift %<>% filter(species %in% fish_length_toy$species)
-
-  metaweb <- build_metaweb(fish_length_toy, species, length, pred_win, fish_diet_shift, resource_diet_shift)
-
-  expect_is(metaweb, "matrix")
-
-  matrix_to_rep <- read_csv2("../../bonnafe_work/data/bib_data/output/AccMat_quant_9_PWvar_partOverlap.csv") %>% as.matrix
-
-  expect_identical(metaweb, matrix_to_rep)
-
-})
 
 #######################
 #  Size distribution  #
@@ -97,8 +78,8 @@ test_that("We get a correct prey size dataframe", {
   expect_is(th_prey_size, "data.frame")
   expected_prey_size <- classes_species %>%
     mutate(
-    min = 0.03 * ( (lower + upper) / 2),
-    max = 0.45 * ( (lower + upper) / 2)
+    min_prey = 0.03 * ( (lower + upper) / 2),
+    max_prey = 0.45 * ( (lower + upper) / 2)
     ) %>% select(-lower, -upper)
 
   expect_identical(th_prey_size, expected_prey_size)
@@ -108,11 +89,51 @@ test_that("We get a correct prey size dataframe", {
 #######################
 #  Compute piscivory  #
 #######################
-
 fake_onto_diet_shift <- tibble(
     species = rep(c("Pikachu", "Salameche"), each = 2),
     life_stage = rep(c(1, 2), each = 2),
-    min = c(0, 5, 0, 105),
-    max = c(5, Inf, 105, Inf)
+    min = c(0, 3, 0, 102),
+    max = c(3, Inf, 102, Inf),
+    pisc = rep(c(0, 1), times = 2)
     )
 
+test_that("piscivory is well computed", {
+   piscivory_table <- compute_piscivory(classes_species, fake_onto_diet_shift, species = species, lower = min, upper = max, fish = pisc)
+   expected_table <- th_prey_size %>%
+     mutate(pisc_index = c(rep(0, 3), rep(1, 6), rep(0, 8), 1)) %>%
[…]

### 2018-12-20 R/metaweb_build.R
Produce metaweb

@@ -35,7 +35,6 @@ build_metaweb <- function(data, species, size, pred_win, fish_diet_shift, low_bo
   size <- rlang::enquo(size)
   low_bound <- rlang::enquo(low_bound)
   upper_bound <- rlang::enquo(upper_bound)
-  life_stage <- rlang::enquo(life_stage)
   fish <- rlang::enquo(fish)
 
   # TODO: Check concordance of column names between datasets
@@ -54,8 +53,11 @@ build_metaweb <- function(data, species, size, pred_win, fish_diet_shift, low_bo
   rownames(fish_fish_int) <- colnames(fish_fish_int)  <- fish_class_names
   # Build the Fish-Resource matrix
   resource_list <- dplyr::select(resource_diet_shift, !!species) %>% unlist
+  names(resource_list) <- NULL
   nb_resource <- length(resource_list)
-  fish_resource_int <- matrix(rep(0, nb_resource * nb_class), ncol = nb_class)
+  fish_resource_int <- matrix(rep(0, nb_resource * nb_class * nb_species), ncol = nb_class * nb_species)
+  rownames(fish_resource_int) <- resource_list
+  colnames(fish_resource_int) <- fish_class_names 
   #Fill the Fish-Fish matrix
   ## Compute the th_prey size min & max + mid-point
   th_prey_size <- compute_prey_size(size_class, pred_win, !!species, !!beta_min, !!beta_max, pred_win_method = pred_win_method)
@@ -75,7 +77,6 @@ build_metaweb <- function(data, species, size, pred_win, fish_diet_shift, low_bo
     pred_data <- dplyr::filter(trophic_data, sp_class == pred_classes[j]) %>%
       unlist
 
-    cat(j, pred_classes[j], "\n", sep = ", ")
     if (pred_data["pisc_index"] != 0) {
 
       min_prey   <- as.numeric(pred_data["min_prey"])
@@ -101,19 +102,41 @@ build_metaweb <- function(data, species, size, pred_win, fish_diet_shift, low_bo
       dplyr::select(- !!fish)
     pred_diet_class_match <- pred_diet %>%
       filter(
-	(min_pred < !!low_bound & !!low_bound < max_pred) |# min stage in size class
-	(min_pred < !!upper_bound & !!upper_bound < max_pred) |# max stage in size class
-	(min_pred < !!low_bound & !!upper_bound < max_pred) |#stage class strictly in size class
[…]

### 2018-12-20 tests/testthat/test-metaweb_build.R

@@ -95,12 +95,10 @@ fake_onto_diet_shift <- tibble(
     min = c(0, 3, 0, 102),
     max = c(3, Inf, 102, Inf),
     light = c(0, 0, 0, 0),
-    det = c(1, 0, 0, 0),
     Chetiflor = c(0, 1, 1, 0),
     Paras = c(0, 0, 1, 1),
     pisc = rep(c(0, 1), times = 2)
     )
-
 test_that("piscivory is well computed", {
    piscivory_table <- compute_piscivory(classes_species, fake_onto_diet_shift, species = species, low_bound = min, upper_bound = max, fish = pisc)
    expected_table <- th_prey_size %>%
@@ -119,8 +117,8 @@ fake_resource_shift <- tibble(
     min = c(0, 0),
     max = c(0, 0),
     light = c(1, 0),
-    Chetiflor = c(0,0),
-    Paras = c(1, 0),
+    Chetiflor = c(0, 1),
+    Paras = c(0, 0),
     pisc = c(0, 0)
     )
 test_that("Metabuild returns a correct matrix",{
@@ -130,7 +128,6 @@ test_that("Metabuild returns a correct matrix",{
   expect_is(metaweb, "matrix")
 
     })
-
 test_that("metaweb works on a true dataset", {
   ## TRUE dataset
   data(fish_length_toy)

### 2019-01-07 R/metaweb_build.R
Fix metaweb build: handle NAs and check variable definition

@@ -44,9 +44,9 @@ build_metaweb <- function(data, species, size, pred_win, fish_diet_shift, low_bo
   size_class <- compute_classes(data, group_var = !!species, var = !!size, class_method = class_method, na.rm = na.rm)
 
   # Build the Fish-Fish matrix
-  species_list <- unique(select(data, !!species)) %>% unlist
+  species_list <- unique(select(size_class, !!species)) %>% unlist
   nb_species <- length(species_list)
-  fish_fish_int <- matrix(rep(0, (nb_species * nb_class) ^ 2),ncol = nb_species * nb_class)
+  fish_fish_int <- matrix(rep(0, (nb_species * nb_class) ^ 2), ncol = nb_species * nb_class)
   ## Name it
   fish_class_names <- rep(species_list, each = nb_class) %>%
     paste(., seq(1, nb_class), sep = "_")
@@ -57,7 +57,8 @@ build_metaweb <- function(data, species, size, pred_win, fish_diet_shift, low_bo
   nb_resource <- length(resource_list)
   fish_resource_int <- matrix(rep(0, nb_resource * nb_class * nb_species), ncol = nb_class * nb_species)
   rownames(fish_resource_int) <- resource_list
-  colnames(fish_resource_int) <- fish_class_names 
+  colnames(fish_resource_int) <- fish_class_names
+
   #Fill the Fish-Fish matrix
   ## Compute the th_prey size min & max + mid-point
   th_prey_size <- compute_prey_size(size_class, pred_win, !!species, !!beta_min, !!beta_max, pred_win_method = pred_win_method)
@@ -103,34 +104,34 @@ build_metaweb <- function(data, species, size, pred_win, fish_diet_shift, low_bo
     pred_diet_class_match <- pred_diet %>%
       filter(
 	# min stage in size class: ]min_pred;max_pred]
-	(min_pred < !!low_bound | !!low_bound <= max_pred) |
+	(min_pred < !!low_bound & !!low_bound <= max_pred) |
 	  # max stage in size class:]min_pred;max_pred]
-	(min_pred < !!upper_bound | !!upper_bound <= max_pred) |
-	(!!low_bound < min_pred & max_pred <= !!upper_bound) | #stage class strictly in size class:]min_pred;max_pred]
-	(!!low_bound > min_pred & max_pred >= !!upper_bound)#size class strictly in stage class:]low_bound;upper_bound]
[…]

### 2019-01-07 data-raw/clean_fish_op_data.R

@@ -13,7 +13,6 @@ library(magrittr)
 ## Sample dataset
 fish_op <- read_csv("../data-raw/fishing_operation_test.csv")
 
-
 ############################
 #  User friendly variable  #
 ############################

### 2019-01-08 tests/metaweb_test.R
quantile can handle list in split_in_classes + enrich build_metaweb output

@@ -1,0 +1,283 @@
+################################################################################
+#              Compare my metaweb with the one of Bonnafe et al.               #
+################################################################################
+
+library(tidyverse)
+library('magrittr')
+library(data.table)
+##############################
+#  Comparision of raw files  #
+##############################
+
+# Bonnafe:
+
+
+## set working directory
+setwd(getwd())
+
+## load data and species list
+# bib_data
+ff <- read.table("../bonnafe_work/data/bib_data/F-F.csv",sep=";",header=T)
+odsF <- as.matrix(read.table("../bonnafe_work/data/bib_data/ODSF.csv",sep=";",header=T))
+odsR <- as.matrix(read.table("../bonnafe_work/data/bib_data/ODSR.csv",sep=";",header=T))
+### The same, see clean_pred_ods_data.R
+
+## raw_data
+fish_length <- fread("../bonnafe_work/data/raw_data/data_clean.txt",
+  select = c("Species", "Length")) %>%
+  as.tibble()
+colnames(fish_length) <- str_to_lower(colnames(fish_length))
+#fish_length <- read.table("../bonnafe_work/data/raw_data/data_clean.txt", sep="\t", header=T)
+#data(fish_length)
+size_quantiles <- read.table("../bonnafe_work/data/bib_data/size_quantiles.csv",sep=";",header=T)
+### The same, see clean_fish_op_data.R
+
+## global variables
+# species
+speciesVect <- as.vector(unique(ff[,"species_code"]))
+# resources
+resourceList <- odsR[,"species_code"]
+
+## replace max in ODS table by maximum observed size in raw data
+odsF[odsF[,"size_max"]=="max","size_max"] <- size_quantiles[pmatch(paste(odsF[odsF[,"size_max"]=="max","species_code"]),size_quantiles[,"X"]),"X100."]
+#odsF[odsF[,"size_max"]=="max","size_max"] <- Inf
+
+#####################################
+## MATRIX CONSTRUCTION (OPTION 14) ##
+#####################################
+
+## quantile method + (xmax+xmin)/2 + (ymin+ymax)/2
[…]

### 2019-01-10 tests/metaweb_test.R
Add replace_min_by_one option to match Willem specification (for testing purpuse only)

@@ -215,16 +215,19 @@ dim(ff_fr_rf_rr_matrix)[1]==dim(ff_fr_rf_rr_matrix)[2]
 
 ## write the matrix 
 write.table(ff_fr_rf_rr_matrix,paste("./output/AccMat_","quant_",nSizeClasses,"_PWvar_partOverlap",".csv",sep=""),sep=";",row.names=FALSE,col.names=TRUE)
-matrix_to_rep <- read_csv2("../bonnafe_work/data/bib_data/output/AccMat_quant_9_PWvar_partOverlap.csv") %>% as.matrix
+matrix_to_rep <- read_csv2("../bonnafe_work/data/bib_data/output/AccMat_quant_9_PWvar_partOverlap-alain.csv") %>% as.matrix
 new_mat  <- sapply(ff_fr_rf_rr_matrix, as.numeric)
 names(new_mat) <- NULL 
 all.equal(new_mat, as.numeric(matrix_to_rep))
 
-#TEST
+###############################################################
+#  Test differences between my metaweb and the one of Willem  #
+###############################################################
+
 # Mat generated with modification in Fish resources rules
-mat_alain <- read_csv2(paste("./output/AccMat_","quant_9_PWvar_partOverlap",".csv",sep=""))
+mat_alain <- read_csv2(paste("./output/AccMat_","quant_9_PWvar_partOverlap","-alain.csv",sep=""))
 col_to_rm <- str_detect(colnames(mat_alain), "OBL")
-mat_alain_2 <- mat_alain[- which(col_to_rm) , - which(col_to_rm)] %>% as.matrix(.)
+mat_alain_2 <- mat_alain[- which(col_to_rm), - which(col_to_rm)] %>% as.matrix(.)
 ## Generate my metaweb:
 data(fish_length)
 data(fish_diet_shift)
@@ -233,7 +236,8 @@ data(pred_win)
 metaweb <- build_metaweb(fish_length, species, length, pred_win,
   fish_diet_shift, size_min, size_max, fish,
   resource_diet_shift, class_method = "quantile",
-  nb_class = 9, pred_win_method = "midpoint", na.rm = TRUE)
+  nb_class = 9, pred_win_method = "midpoint", na.rm = TRUE, replace_min_by_one = FALSE)
+filter(metaweb$size_class, species == "BRO")
 colnames(metaweb$metaweb)
[…]

### 2019-01-21 data-raw/clean_fish_op_data.R
cleaning dummys variable values
for sampled surfaces and the number of passage

@@ -79,8 +79,8 @@ operation_data %<>%
   mutate(
     method = str_replace_all(method,
       c("partielle sur be" = "partial_over_be",
-	"partielle sur be" = "partial_over_to",
 	"Point grand mil"  = "point_big_mil",
+	"partielle sur to"  = "partial_over_to",
 	"autres"           = "other")),
     strategy = str_replace_all(strategy,
       c("A pied"        = "on_foot",
@@ -91,6 +91,19 @@ operation_data %<>%
 )
 # One data by species and fishing operation 
 operation_data %<>% distinct(opcod, species, .keep_all = TRUE)
+
+# Remove spurious data:
+## nbpass is irrevelant for method != complete
+operation_data %<>% mutate(
+  nbpass = replace(nbpass, method != "complete", NA),
+  surf = ifelse(surf == 0, NA, surf)# if sampled area is 0, there is a problem
+)
+#RQ pour pêches partielles par ambiance et par point, par défaut on a supprimé
+#toutes les valeurs qui pouvaient avoir été indiquées de façon à ce que la
+#cellule apparaisse vide- ; pour les autres (berge, autre) on a laissé les
+#valeurs même si elles sont contradictoire avec la méthode
+
+
 devtools::use_data(operation_data, overwrite = TRUE)
 rm(operation_data)
 

### 2019-01-24 data-raw/generate_analysis_dataset.R
Generate dataset for temporal analysis

@@ -1,0 +1,112 @@
+################################################################################
+#                    Generate the dataset for the analysis                     #
+################################################################################
+
+library(tidyverse)
+library(magrittr)
+library(cowplot)
+library(ggpmisc)
+library(sf)
+library(rgdal)
+library(lubridate)
+devtools::load_all()
+theme_set(theme_alain())
+
+
+data(operation_data)
+op <- dplyr::select(operation_data, opcod:year, count)
+rm(operation_data)
+
+# Summary of op 
+op_stat <- op %>%
+  group_by(opcod, station, year, month) %>%
+  summarise(
+    nb_ind = sum(count),
+    nb_sp  = n()
+    )
+
+# Add details about the op 
+data(operation_data)
+op_method <- operation_data %>%
+  distinct(opcod, .keep_all = TRUE) %>%
+  select(opcod, nbpass:strategy)
+op <- left_join(op_stat, op_method, by = "opcod")
+
+#plot rep of methods
+qplot(times, data = low_int, fill = method) +
+  labs(x = "Time of monthly repeated sampling")
+
+op %<>% filter(
+  !(method == "complete" & nbpass == 1), #Rm complete that has only 1 passage
+  method != "other"#Rm other method
+)
+
+# Numbering the sampling events by station
+op_hist <- op %>%
+  group_by(station) %>%
+  summarise(freq = n()) %>%
+  arrange(desc(freq)) %>%
+  mutate(station = fct_inorder(as.factor(station)))
+# good station IDs
+good_station <- op_hist %>%
+  dplyr::filter(freq >= 10)
+good_station_id <- good_station %>%
+  dplyr::select(station) %>%
+  unlist(., use.names = FALSE)
+length(good_station_id)
+
+
+# For temporal analysis, we keep station followed more than 10 times
+op <- filter(op, station %in% good_station_id)
+
+# Get the time between each sampling event  
+int_op <- op %>%
+  ungroup() %>%
+  unite(year_month, year, month, sep = "-") %>%
+  mutate(times = ymd(paste0(year_month, "-01"))) %>%
+  select(-year_month) %>%
+  group_by(station) %>%
+  arrange(times) %>%
+  mutate(
+    point = seq(1, length(station)),
+    sample_sep = c(NA, times[-1] - times[-length(station)])
+  )
+
+low_int <- filter(int_op, sample_sep < 60) %>%
[…]

### 2019-02-01 data-raw/prepare_maps.R
Fixed station coordinates projection

@@ -6,6 +6,11 @@ library(tidyverse)
 library(magrittr)
 library(sf)
 library(rmapshaper)
+devtools::load_all()
+
+#######################
+#  France and region  #
+#######################
 
 region <- read_sf("france_region_shp/regions-20180101.shp") %>%
   dplyr::filter(surf_km2 > 10000, nom != "Guyane")
@@ -19,9 +24,37 @@ plot(simplepolys[, "nom"])
 region_polygon <- select(simplepolys, nom)
 devtools::use_data(region_polygon, overwrite = TRUE)
 
+#############
+#  Station  #
+#############
+
+# Change projection:
+#https://www.rdocumentation.org/packages/sf/versions/0.7-2/topics/st_transform
+station <- read_delim("fishing_station_localisation_wsg84.csv",
+  delim = ";", locale = locale("fr", decimal_mark = "."),
+  col_types = cols(ST_CODECSP = col_character()))
+# Lambert II
+xy_station <- dplyr::select(station, ST_ABCISSE, ST_ORDONNEE, ST_LOCALISATION, ST_ID)
+## Get Lambert II code
+library(rgdal)
+EPSG <- make_EPSG()
+EPSG[grep("Lambert zone II", EPSG$note), 1:2]
+## Define CRS
+station <- sf::st_as_sf(station, coords = c("ST_ABCISSE", "ST_ORDONNEE"), crs = 27572)
+
+# Get the same projection than region polygon 
+data(region_polygon)
+station <- st_transform(station, st_crs(region_polygon))
+st_geometry
+plot(st_geometry(region_polygon))
+plot(station, add = TRUE, pch = 20, col = "red")
+## Save station
+st_write(station, "station_wgs84.shp")
+
 ## To continue with
 #- cours_eau_shp
 #- obstacles
-#- station
-# Change projection:
-#https://www.rdocumentation.org/packages/sf/versions/0.7-2/topics/st_transform
+# Match points to lines:
+#https://github.com/r-spatial/sf/issues/790
+#https://www.gis-blog.com/nearest-neighbour-search-for-spatial-points-in-r/
+#

### 2019-02-13 analysis/01_compute_metrics.R
Fixed color definition for species

@@ -33,11 +33,16 @@ toc()
 network_analysis %<>%
   mutate(
     connectance = map_dbl(metrics, "C"),
-    richness = map_dbl(metrics, "N")
+    richness = map_dbl(metrics, "N"),
+    compartiment = map_dbl(metrics, "Cbar"),
+    troph_level = future_map(network, NetIndices::TrophInd),
+    troph_level2 = map(troph_level, "TL"),
+    troph_length = map_dbl(troph_level2, max)
   )
 
+network_analysis[1,]$troph_level2[[1]]
 network_metrics <- network_analysis %<>%
-  dplyr::select(opcod, connectance, richness)
+  dplyr::select(opcod, connectance, richness, compartiment, troph_length)
 
 devtools::use_data(network_metrics, overwrite = TRUE)
 rm(list = ls())

### 2019-02-19 README.Rmd
Description of datasets (from raw to analysis)

@@
 My notes are available in the introductory vignette `vignettes/intro.html`
+
+## Structure of the project repository
+
+### Raw data
+
+Raw datas are spreadsheets (xls, csv, etc...) shapefiles and others cartographic
+data and reports (of the AFB, ONEMA, etc). The raw datas come together with `R`
+scripts which describe cleaning procedures. The cleaning procedures end by
+saving datasets used for data analysis.
+
+It is located in `data-raw`.
+
+### Data for analysis
+
+The clean datasets live in `data` directory and stored in `rda` compressed format.
+Once the package is loaded, they can be call as easily as `load(objet_name)`.
+
+```{r}
+devtools::load_all()
+data(metaweb_analysis)
+names(metaweb_analysis)
+```
+The cleaned and filtered objects used for data analysis are named with the suffix `_analysis`.
+
+### Analysis of data
+
+The analysis of data lives in the directory named `analysis`.
+
+This folder contains scripts in which various metrics are computed for two
+different aspects that have been more or less arbitrary separated.
+
+#### Community data
+
+The community data lives in the `community_analysis` and contains the following
+data:
+
+- species abondances
+- species biomass
+- species richness
+
+The following metrics are summarised by station in `community_metrics`:
+
+- mean and cv of species richness
+- mean and cv of species biomass 
+- temporal beta-diversity
+
+#### Network data
+
+The network data lives in the `network_analysis` and contains the following
+metrics:
+
+- connectance
+- number of nodes
+- modularity and modules 
+- nestedness 
+- trophic length
+
+The following metrics are summarised by station:
+
+- mean and cv of all the above indices

### 2019-02-26 analysis/01_compute_community_metrics.R
Clean + compute biomass by trophic level

@@ -132,7 +132,7 @@ com %<>%
 betadiv <- com %>%
   mutate(
     betadiv = map_dbl(com, function(com){
-      vegdist(com, method = "bray", binary = FALSE) %>% mean
+      vegan::vegdist(com, method = "bray", binary = FALSE) %>% mean
     })
   )
 
@@ -145,6 +145,5 @@ com <- left_join(community_metrics, op_analysis, by = c("opcod")) %>%
     funs(avg = mean, cv = sd(.) / mean(.)))
 
 com <- left_join(com, select(betadiv, station, betadiv), by = "station")
-
 temporal_community_metrics <- com
 devtools::use_data(temporal_community_metrics, overwrite = TRUE)

### 2019-02-26 data-raw/04_prepare_maps.R

@@ -45,7 +45,6 @@ station <- sf::st_as_sf(station, coords = c("ST_ABCISSE", "ST_ORDONNEE"), crs = 
 # Get the same projection than region polygon 
 data(region_polygon)
 station <- st_transform(station, st_crs(region_polygon))
-st_geometry
 plot(st_geometry(region_polygon))
 plot(station, add = TRUE, pch = 20, col = "red")
 ## Save station

### 2019-02-26 analysis/02_compute_network_metrics.R
Try to add betalink diversity

@@ -7,6 +7,9 @@
 library(tidyverse)
 library(magrittr)
 library(igraph)
+library(furrr)
+options(mc.cores = 3)
+library(tictoc)
 devtools::load_all()
 
 #########################################
@@ -84,9 +87,6 @@ devtools::use_data(network_analysis, overwrite = TRUE)
 #####################
 
 library(NetIndices)
-library(furrr)
-options(mc.cores = 3)
-library(tictoc)
 
 data(network_analysis)
 
@@ -132,6 +132,41 @@ network_metrics <- network_analysis %>%
 devtools::use_data(network_metrics, overwrite = TRUE)
 rm(list = ls())
 
+#####################################
+#  Compute further network_indices  #
+#####################################
+# Compute betalink, motif distribution
+library(betalink)
+data(network_analysis)
+data(op_analysis)
+
+net <- left_join(network_analysis, select(op_analysis, opcod, station, year)) %>%
+  ungroup()
+
+## Get network as matrices
+net %<>%
+  mutate(
+    network = map2(network, station, function(x, y) {
+      message(sprintf('Station %s', y))
+      igraph::graph_from_data_frame(x, directed = TRUE)
+}
+))
+## betalink:
+plan(multiprocess)
+net %<>%
+  group_by(station) %>%
+  nest() %>%
+  mutate(betal = map2(data, station,
+      function (data, station) {
+      message(sprintf("Station %s", station))
+      network_betadiversity(data$network)
+      }
+      )
+  )
+
+# Motif
+
+
 ######################################
 #  Temporal network characteristics  #
 ######################################
@@ -141,13 +176,14 @@ data(op_analysis)
 op_analysis %<>%
   select(opcod, station, year)
 to_be_summarized <- c("nestedness", "connectance", "nbnode", "compartiment",
-  "mean_troph_level", "max_troph_level", "modularity") com <-
+  "mean_troph_level", "max_troph_level", "modularity")
+com <-
     left_join(network_metrics, op_analysis, by = "opcod") %>%
   group_by(station) %>%
   rename(mean_troph_level = troph_level_avg,
     max_troph_level = troph_length) %>%
   summarise_at(to_be_summarized,
-    funs(avg = mean, cv = sd(.) / mean(.)))
+    funs(avg = mean, cv = sd(.) / mean(.), med = median))
 
 temporal_network_metrics <- com
 devtools::use_data(temporal_network_metrics, overwrite = TRUE)

### 2019-02-27 analysis/01_compute_community_metrics.R
Standardized connectance

@@ -83,9 +83,9 @@ com <- community_analysis %>%
 community_metrics <- com
 devtools::use_data(community_metrics, overwrite = TRUE)
 
-############################################
-#  Compute temporal community description  #
-############################################
+############################
+#  Compute beta-diversity  #
+############################
 data(community_analysis)
 data(op_analysis)
 
@@ -98,7 +98,7 @@ test <- op_analysis %>%
   ungroup %>%
   select(nb) %>%
   unlist 
-which(test >1)
+which(test > 1)
 
 op_analysis %<>%
   select(opcod, station, year)
@@ -136,8 +136,14 @@ betadiv <- com %>%
     })
   )
 
+
+############################################
+#  Compute temporal community description  #
+############################################
 # Compute mean and cv of richness
 data(community_metrics)
+data(op_analysis)
+
 com <- left_join(community_metrics, op_analysis, by = c("opcod")) %>%
   group_by(station) %>%
   select(station, richness, nind, biomass) %>%

### 2019-02-28 R/plot_methods.R
Update plots and Imports

@@ -154,6 +154,7 @@ xylabs <- function (...) {
     biomass_cv = paste("CV of biomass"),
     biomass_stab = paste("Stability of Biomass"),
     biomass_avg = paste("Average biomass (g)"),
+    network_med = paste("Median of network metrics"),
     nbnode = paste("Number of nodes"),
     richness = paste("Species richness"),
     richness_cv = paste("CV of richness"),
@@ -175,7 +176,11 @@ xylabs <- function (...) {
     )
 }
 
-mylabel <- function(...) {
+###############
+#  Labellers  #
+###############
+
+mylabel <- function() {
   ggplot2::as_labeller(c(
     connectance = "Connectance",
     richness = "Number of nodes",
@@ -187,5 +192,29 @@ mylabel <- function(...) {
     richness_cv = "CV",
     richness_avg = "Average",
     betadiv = expression(bold(paste(beta, "-diversity", sep = "")))
-    ), ...)
+    ))
+}
+
+#' Troph group labeller
+#' Returns a labeller for ggplot2
+#' @param troph_class a object created by get_size_class function
+#' @return a labeller for ggplot2
+troph_group_labeller <- function (troph_class = NULL, round_lvl = 2) {
+
+  if (is.null(troph_class)) {
+    data(trophic_class)
+    troph_class <- trophic_class
+  }
+  troph_class %<>%
+    dplyr::mutate(
+      lower = paste("[", round(lower, round_lvl), sep = ""),
+      upper = paste(round(upper, round_lvl), "]", sep = "")
+      ) %>%
+  tidyr::unite(bounds, lower, upper, sep = ";") %>%
+  dplyr::rename(troph_group = class_id)
+
+  bounds <- troph_class$bounds
+  names(bounds) <- troph_class$troph_group
+  as_labeller(bounds)
+
 }

### 2019-02-28 analysis/02_compute_network_metrics.R

@@ -35,7 +35,7 @@ data(op_analysis)
 st_timing <- op_analysis %>%
   dplyr::select(opcod, station, year, month) %>%
   unite(year_month, year, month, sep = "-") %>%
-  mutate(times = ymd(paste0(year_month, "-01"))) %>%
+  mutate(times = lubridate::ymd(paste0(year_month, "-01"))) %>%
   dplyr::select(-year_month)
 rm(op_analysis)
 
@@ -79,11 +79,14 @@ summary(trophic_level)
 ## Split trophic level in three classes:
 trophic_class <- split_in_classes(trophic_level$troph_level, class_method = "percentile",
   nb_class = 3, round_limits = FALSE)
+devtools::use_data(trophic_class, overwrite = TRUE)
+
 ## Assign trophic group to each node  
 trophic_level %<>%
   mutate(
     troph_group = get_size_class(trophic_level, NULL, troph_level, trophic_class)
   )
+
 ## Assign to each network its trophic group:
 network_analysis %<>%
   mutate(

### 2019-03-01 analysis/00_get_network.R
Add check in temporal_network_metrics reconstruction + plot troph level vs richness

@@ -54,9 +54,14 @@ length_analysis %<>%
 rm(op_analysis)
 ##
 data(metaweb_analysis)
-filter(classes, is.na(class_id))
-qplot(x = length, data = filter(classes, species == "TRF"), geom = "histogram")
-filter(classes, species == "TRF") %>% map(., summary)
+## Check if NA in the metaweb:
+if (any(is.na(metaweb_analysis$size_class))) {
+  stop("NA in class id, something went wrong")
+}
+
+qplot(x = length, data = filter(length_analysis, species == "TRF"), geom = "histogram")
+filter(length_analysis, species == "TRF") %>% map(., summary)
+filter(length_analysis, species == "TRF", is.na(length))
 filter(metaweb_analysis$size_class, species == "TRF")
 network_analysis <- build_local_network(
   data = length_analysis,
@@ -67,4 +72,8 @@ network_analysis <- build_local_network(
   classes = NULL,
   out_format = "igraph"
 )
+network_analysis %>% unnest(data) %>%
+  filter(is.na(class_id))
+
+
 devtools::use_data(network_analysis, overwrite = TRUE)

### 2019-03-01 analysis/03_compute_temporal_network_properties.R

@@ -57,18 +57,23 @@ check_obs <- net %>%
   summarise(nobs = n()) %>%
   mutate(enough_obs = ifelse(nobs >= 5, TRUE, FALSE))
 
+filter(biomass_variation, is.na(troph_group))
 ## Let's put values to NA when there is not enough observations:
 biomass_variation %<>%
   left_join(., check_obs, by = c("station", "troph_group")) %>%
   mutate_at(vars(biomass_avg:nbnode_stab), funs(if_else(enough_obs, ., NA_real_))) %>%
-  select_at(vars(matches("biomass|node_avg|station|troph_group")))
+  select_at(vars(matches("biomass|richness_avg|station|troph_group")))
 
 ## Merge with temporal_network_metrics
 biomass_variation %<>%
   group_by(station) %>%
   nest(.key = "troph_group")
-data(temporal_network_metrics)
 
+data(temporal_network_metrics)
+## Check if troph_group already exist:
+if ("troph_group" %in% colnames(temporal_network_metrics)) {
+  temporal_network_metrics %<>% select(-matches("troph_group"))
+}
 temporal_network_metrics <-
   left_join(temporal_network_metrics, biomass_variation, by = "station")
 

### 2019-03-11 R/plot_methods.R
Updates on talks

@@ -77,14 +77,18 @@ plot_temporal_network <- function(net, meta = NULL, dead = NULL, lay = NULL, ...
 	set_layout_graph, glay = lay, color_scale = set_color_species(lay))
     )
     ## Get legend
-    species_colour_legend <- get_legend(net_graph[1,]$net_graph[[1]])
+    species_colour_legend <- get_legend(
+      net_graph[1, ]$net_graph[[1]] +
+	labs(colour = "Species") +
+	guides(fill = guide_legend(nrow = 2, byrow = TRUE))
+    )
     ## Remove legend in the other plots
     net_graph %<>%
       mutate(
 	net_graph = map(net_graph, function (x) {
 	  x + theme(
 	    legend.position = "none",
-	    plot.margin = unit(c(0, 0, 0, 0), "cm")
+	    plot.margin     = unit(c(0, 0, 0, 0), "cm")
 	  )
 	})
       )
@@ -128,7 +132,12 @@ set_layout_graph <- function (net, glay, title = NULL, biomass = NULL, color_sca
       if (!is.null(title)) {
 	p <- p + labs(title = title)
       }
-      p <- p + theme_graph(foreground = 'steelblue', fg_text_colour = 'white', base_family="sans")
+      p <- p + theme_graph(
+	foreground     = "steelblue",
+	fg_text_colour = "white",
+	base_family    = "sans",
+	background     = NA
+      )
 	#theme(legend.position="none")
       if (!is.null(color_scale)) {
 	p <- p + 
@@ -210,8 +219,12 @@ mylabel <- function() {
     nbnode = "Number of nodes",
     richness_cv = "CV",
     richness_avg = "Average",
-    betadiv = expression(bold(paste(beta, "-diversity", sep = "")))
-    ))
+    richness_med = "Median richness",
+    betadiv = "Beta-diversity"
+    #betadiv = expression(bold(paste(beta, "-diversity", sep = "")))
+    #see https://stackoverflow.com/questions/35524202/as-labeller-with-expression-in-ggplot2-facet-wrap?rq=1
+      )
+    )
 }
 
 #' Troph group labeller

### 2019-03-20 data-raw/04_prepare_maps.R
Load DCE data

@@ -120,3 +120,23 @@ plot(mnt)
 # Match points to lines:
 #https://github.com/r-spatial/sf/issues/790
 #https://www.gis-blog.com/nearest-neighbour-search-for-spatial-points-in-r/
+
+##############
+#  DCE data  #
+##############
+
+# Localisation des Masses d'eau
+dce <- read_sf("./DCE/2016/SurfaceWaterBodyLine_FR_20170410/SurfaceWaterBodyLine_FR_20170410.gml")
+colnames(dce)
+arrange(dce, thematicIdIdentifier)
+plot(dce["nameLanguage"])
+
+# Load data 
+## Caracterisation of the streams
+file_rapportage <- "./DCE/2016/rapportage_2016.xlsx"
+excel_sheets(file_rapportage)
+carac <- read_excel(file_rapportage, sheet = "ESU_Caract") %>%
+  filter(surfaceWaterBodyCategory == "RW")
+colnames(carac)
+arrange(carac, surfaceWaterBodyCode)
+## surfaceWaterBodyCode corresponds to thematicIdIdentifier

### 2019-03-27 R/building_dataset.R
Start create dataset from ASPE database

@@ -1,0 +1,81 @@
+#' Generate fish from fishing lot (AFB) 
+#'
+#'
+#' @param id int id of the lot  
+#' @param type character type of the lot (N, G, S/L, I)
+#' @param min_size dbl minimum size of the lot 
+#' @param max_size dbl maximum size of the lot 
+#' @param nb int effectif of the lot 
+#' @param ind_measure data.frame individual measurement of the fish 
+#' @param seed int for set.seed
+#'
+#' @details From fishing lot, we build generate the fish size individual
+#'
+#' @export
+gen_fish_from_lot <- function (
+  id = NULL, type = NULL,  min_size = NULL, max_size = NULL, nb = NULL,
+  ind_measure = NULL, ind_id = NULL, ind_size = NULL, verbose = FALSE, ...) {
+
+  if (verbose) {
+    cat(sprintf("Lot number %s \n", id))
+  }
+
+  # Promise:
+  ind_id <- rlang::enquo(ind_id)
+  id <- rlang::enquo(id)
+  ind_size <- rlang::enquo(ind_size)
+
+  # Build by lot
+  if (type == "G") {
+    if (any(is.na(c(min_size, max_size)))) {
+      warning_msg <- paste(
+	"NA in lot of type G number ",id,", lot put as NA\n", sep = ""
+      )
+      warning(warning_msg)
+      lot <- NA
+    } else if (min_size <= max_size) {
+      warning_msg <- paste(
+	"min_size <= max_size in lot of type G number ",id,", lot put as NA\n",
+	sep = "")
+      warning(warning_msg)
+      lot <- NA
+    } else {
+    avg <- (min_size + max_size) / 2
+    sdt <- (max_size - min_size) * 1 / 4
+
+    lot <- truncdist::rtrunc(n = nb, spec = "norm", a = min_size, b = max_size,
+      mean = avg, sd = sdt)
+    stopifnot(length(lot) == nb)
+    }
+  } else if (type == "S/L") {
+    #Get size:
+    size <- ind_measure %>% dplyr::filter(!!ind_id == !!id) %>%
+      dplyr::select(!!ind_size) %>%
+      unlist(., use.names = FALSE)
+    #Distribution parameters:
+    avg <- mean(size)
+    sdt <- sd(size)
+
+    # Sample inside the 90% of the distribution probability:
+    p05 <- quantile(size, 0.05)
+    p95 <- quantile(size, 0.95)
[…]

### 2019-03-27 run/00_dependancies.sh
Add pandoc to dependancies

@@ -1,9 +1,21 @@
 #!/bin/bash
 
-R -e "if (!'littler' %in% installed.packages()[, 'Package']) \
-{install.packages(c('littler'), repos = 'https://cran.rstudio.com')} else \
-{cat('littler is already installed')}"
-
+# Littler cannot be installed on the cluster :(
+#R -e "if (!'littler' %in% installed.packages()[, 'Package']) \
+#{install.packages(c('littler'), repos = 'https://cran.rstudio.com')} else \
+#{cat('littler is already installed')}"
 wait
-
 echo "Littler installed!"
+
+# Pandoc (necessary to compile Rmarkdown)
+pkgs='pandoc'
+DLDIR="$HOME/downloads/"
+PANDOCURL="https://github.com/jgm/pandoc/releases/download/2.7.1/pandoc-2.7.1-linux.tar.gz"
+PANDOCTAR="$DLDIR/pandoc-2.7.1-linux.tar.gz"
+if ! dpkg -s $pkgs >/dev/null 2>&1; then
+    echo "Pandoc is not installed"
+    wget -P $DLDIR $PANDOCURL
+    tar xvzf $PANDOCTAR --strip-components 1 -C $HOME/.local/ 
+    echo "Pandoc is installed!"
+    
+fi

### 2019-03-28 analysis/misc/parallel_setup.R
Set up fish lot analysis to the cluster

@@ -3,14 +3,15 @@
 ####################
 
 
-library(future)
-
-nb_cores <- availableCores()
+nb_cores <- future::availableCores()
 cl <- parallel::makeCluster(nb_cores)
 #Crap hack to determine if in local or on the PBS cluster:
-if (dir.exists("~/Documents")) {
-  plan(multisession)
+node_name <- Sys.info()["nodename"]
+if (node_name == "Andy") {
+  future::plan(multisession)
+} else if (node_name %in% c("mesu0", "migale")) {
+  future::plan(cluster, workers = cl)
 } else {
-  plan(cluster, workers = cl)
+  warning("Unknow location: parallel session have not been set up")
 }
 

### 2019-03-29 run/job_mesu_cluster.sh
update mesu job

@@ -1,8 +1,8 @@
 #!/bin/bash
 #Request 20 CPU cores on one node (typical for MeSU-alpha)
 #PBS -q alpha 
-#PBS -l select=1:ncpus=20
-#PBS -l walltime=10:00:00
+#PBS -l select=1:ncpus=90
+#PBS -l walltime=240:00:00
 #PBS -N temporal_networks
  
 #The command below allows"module" to properly initialize a bash / sh shell in

### 2019-04-01 tests/testthat/test-dataset_build.R
Increase fish lot building speed by 10

@@ -244,6 +244,6 @@ test_that("multiplication works", {
   expect_is(output, "data.frame")
   output %>%
     dplyr::select(lop_id, lop_pre_id, species, fish) %>%
-    unnest(fish)
+    tidyr::unnest(fish)
 
 })

### 2019-04-15 data-raw/03_generate_analysis_dataset.R
Add opcod to fish_length

@@ -12,10 +12,11 @@ library(lubridate)
 devtools::load_all()
 theme_set(theme_alain())
 
+mypath <- rprojroot::find_package_root_file
+mydir <- mypath("data-raw", "fishing_op_build")
 
-data(operation_data)
-op <- dplyr::select(operation_data, opcod:year, count)
-rm(operation_data)
+myload(op, dir = mypath("data-raw"))
+op
 
 # Summary of op 
 op_stat <- op %>%

### 2019-04-16 data-raw/03_generate_analysis_dataset.R
New datasets have been generated

@@ -16,26 +16,15 @@ mypath <- rprojroot::find_package_root_file
 mydir <- mypath("data-raw", "fishing_op_build")
 
 myload(op, dir = mypath("data-raw"))
-op
 
-# Summary of op 
-op_stat <- op %>%
-  group_by(opcod, station, year, month) %>%
-  summarise(
-    nb_ind = sum(count),
-    nb_sp  = n()
-    )
+#op_sp_ind Summary of op 
+myload(op_sp_ind, dir = mypath("data"))
+op_sp_ind
 
-# Add details about the op 
-data(operation_data)
-op_method <- operation_data %>%
-  distinct(opcod, .keep_all = TRUE) %>%
-  select(opcod, nbpass:strategy)
-op <- left_join(op_stat, op_method, by = "opcod")
+op %<>% left_join(op_sp_ind, by = "opcod")
 
 op %<>% filter(
-  nbpass == 2, #Rm complete that has only 1 passage
-  method == "complete"#Rm other method
+  protocol == "complete"#Rm other method
 )
 
 ######################################
@@ -45,60 +34,45 @@ op %<>% filter(
 # Get the time between each sampling event
 int_op <- op %>%
   ungroup() %>%
-  unite(year_month, year, month, sep = "-") %>%
-  mutate(times = ymd(paste0(year_month, "-01"))) %>%
-  select(-year_month) %>%
   group_by(station) %>%
-  arrange(times) %>%
-  mutate(
-    point = seq(1, length(station)),
-    sample_sep = c(NA, times[-1] - times[-length(station)])
-  )
-
-## double_station 
-low_int <- filter(int_op, sample_sep < 60) %>%
-  ungroup() %>%
-  arrange(station)
-filter(int_op, station == 1474)
-
-## filter double sampling, surely doubled 
-keep_most_complete_sampling <- function (station) {
-  ##Any double fishing within two month (1day - 60days):
-  dbl_op <- filter(station, sample_sep < 60)
-  if (nrow(dbl_op) == 0) {
-    return(station)
-  }
-  pmap_dfr(dbl_op, function (point, tot, ...) {
-    # Avoid argument equal var name:
-    x <- point;rm(point)
-    # The targeted op have likely less species
-    to_compare <- filter(tot, point %in% c(x, x - 1))
-    kept_station <- arrange(to_compare, desc(nb_sp), desc(nb_ind)) %>%
-      slice(1)
-    bind_rows(
[…]

### 2019-04-17 data-raw/01_clean_fish_op_data.R
Fix op_env

@@ -139,26 +139,6 @@ load(mypath("data-raw", "fishing_op_build", "op_env.rda"))
 op_env
 colnames(op_env)
 
-op_env %>%
-  filter(
-  amplitude_thermique_air_station <= 0 |
-  temperature_air_station <= 0 |
-  precipitation_bassin_versant <= 0 |
-  pente_ligne_eau < 0
-  )
-# Convert columns in english
-col_replacement <- c(
-"pente_ligne_eau" = "slope",
-"section_mouillee" = "width",
-"durete_totale" = "water_hardness",
-"temp_max_moyenne_eau" = "water_avg_30d_max_temp",
-"temp_air_bassin_versant" = "air_avg_temp_basin",
-"precipitation_bassin_versant" = "avg_rainfall_basin",
-"amplitude_thermique_air_station" = "air_thermal_amplitude",
-"temperature_air_station" = "air_avg_temp",
-"commentaire" = "comment"
-)
-colnames(op_env) %<>% str_replace_all(., col_replacement)
 
 mysave(op_env, dir = mypath("data-raw"))
 

### 2019-04-18 data-raw/03_generate_analysis_dataset.R
Fix new dataset network building

@@ -103,8 +103,34 @@ HERE:
 #devtools::use_data(env_analysis, overwrite = TRUE)
 #rm(environmental_data, env_analysis)
 
-data(fish_length)
-length_analysis <- filter(fish_length, opcod %in% good_opcod_id)
+#######################
+#  Clean fish length  #
+#######################
+
+myload(fish_length, dir = mypath("data"))
+
+# Select good op
+fish_length %<>% filter(opcod %in% good_opcod_id)
+summary(fish_length)
+
+# Remove accidental species
+nb_ind_sp <- fish_length %>%
+  group_by(species) %>%
+  summarise(nind = n())
+low_nb_ind <- filter(nb_ind_sp, nind <= 100)
+fish_length %<>% filter(!species %in% low_nb_ind$species)
+
+# Remove crazy length
+filter(fish_length, length > 1000)
+## TRF distri 
+filter(fish_length, species == "TRF") %>%
+  summary()
+# Remove it
+fish_length %<>%
+  filter(!length > 10000) # Also drop NA 
+
+length_analysis <- fish_length
+
 devtools::use_data(length_analysis, overwrite = TRUE)
 rm(fish_length, length_analysis)
 

### 2019-04-19 R/metaweb_build.R
Fix mistake in data loading for network metrics computation

@@ -443,3 +443,26 @@ split_in_classes <- function (to_class, class_method = "quantile",
       upper = classified[-1]
 	)
   }
+
+#' Sanatize fish length for metaweb
+#'
+#'
+sanatize_metaweb <- function(data = NULL, species = NULL, fish_diet_shift = NULL, ...) {
+
+  #Capture var:
+  species <- rlang::enquo(species)
+  sp_chr <- rlang::quo_name(species)
+  
+  data_sp <- unique(data[[sp_chr]])
+  onto_sp <- unique(fish_diet_shift[[sp_chr]])
+
+  sp_missing <- data_sp[!data_sp %in% onto_sp]
+  if (length(sp_missing) != 0) {
+    msg <- paste0("The following species are absent: ", cat(sp_missing))
+    message(msg)
+    #TODO: filter data
+    
+  }
+
+
+}

### 2019-04-19 analysis/03_compute_temporal_network_properties.R

@@ -22,8 +22,7 @@ op_analysis %<>%
   dplyr::select(opcod, station, year)
 to_be_summarized <- c("nestedness", "connectance", "connectance_corrected", "nbnode",
   "mean_troph_level", "max_troph_level", "modularity")
-com <-
-    left_join(network_metrics, op_analysis, by = "opcod") %>%
+com <- left_join(network_metrics, op_analysis, by = "opcod") %>%
   group_by(station) %>%
   rename(mean_troph_level = troph_level_avg,
     max_troph_level = troph_length) %>%

### 2019-04-25 analysis/04_temporal_habitat_data.R
Add habitat data

@@ -1,0 +1,97 @@
+####################################
+#  Build temporal habitat dataset  #
+####################################
+
+myload(env_analysis, dir = data_common)
+colnames(env_analysis)
+
+col_hydro <- c("opcod", "station", "slope", "width_river", "width",
+  "avg_depth_station", "avg_daily_flow", "isolation_up", "isolation_down",
+  "chanelled_station")
+hydro <- env_analysis %>%
+  select(col_hydro)
+
+###############
+#  Isolation  #
+###############
+## The different modality of isolation
+hydro %>%
+  select(isolation_down, isolation_up) %>%
+  summarise_all(list(test = ~list(unique(.)))) %>%
+  unnest()
+
+## Number of times by station where isolation has been reported:
+isolation <- hydro %>%
+  select(station, isolation_down, isolation_up) %>%
+  mutate_at(vars(matches("isolation")), list(~ifelse(. == "no", "no", "yes"))) %>%
+  group_by(station) %>%
+  summarise_all(list(~paste(ifelse(any(. == "yes"), "yes", "no"))))
+
+##########
+#  Flow  #
+##########
+
+# Ok, we have no quantitative flow data
+sum(is.na(hydro$avg_daily_flow)) / nrow(hydro)
+sum(hydro$avg_daily_flow == 0, na.rm = TRUE) / nrow(hydro)
+
+flow_col <- c("instream_flow", "artificial_flow_variation", "replenishment_flow")
+flow <- env_analysis %>%
+  select(station, flow_col) %>%
+  group_by(station) %>%
+  summarise_all(list(~paste(ifelse(any(. == "yes"), "yes", "no"))))
+
+#############################
+#  Morphology of the river  #
+#############################
+
+sum(is.na(hydro$slope)) / nrow(hydro)
+sum(hydro$slope == 0, na.rm = TRUE) / nrow(hydro)
+# We have no slope
+
+river_morpho <- hydro %>%
+  select(station, slope, width_river, avg_depth_station) %>%
+  group_by(station) %>%
+  summarise_all(list(mean = ~mean(., na.rm = TRUE), cv = ~sd(., na.rm = TRUE)/ mean(., na.rm = TRUE)))
+
+hydro %>%
+  select(chanelled_station) %>%
+  summarise_all(list(test = ~list(unique(.)))) %>%
+  unnest()
+
+# NA if unknown 
+channel <- hydro %>%
+  select(station, chanelled_station) %>%
+  rename(channelled = chanelled_station) %>%
[…]

### 2019-04-25 data-raw/03_generate_analysis_dataset.R

@@ -104,6 +104,7 @@ good_opcod_id <- select(ungroup(op_analysis), opcod) %>% unlist
 myload(op_env, dir = mypath("data-raw"))
 myload(op_desc, dir = mypath("data-raw"))
 myload(op_analysis, dir = mypath("data"))
+myload(op_hab, dir = mypath("data-raw"))
 good_opcod_id <- select(ungroup(op_analysis), opcod) %>% unlist
 
 op_desc %<>%
@@ -113,12 +114,18 @@ op_env %<>%
   filter(opcod %in% good_opcod_id) %>%
   left_join(select(op_analysis, opcod, station)) %>%
   left_join(op_desc)
-
 summary(op_env)
 
 env_analysis <- op_env
 devtools::use_data(env_analysis, overwrite = TRUE)
 rm(env_analysis, op_env, op_desc)
+
+op_hab %<>%
+  filter(opcod %in% good_opcod_id)
+
+hab_analysis <- op_hab
+devtools::use_data(hab_analysis, overwrite = TRUE)
+rm(hab_analysis, op_hab)
 
 #######################
 #  Clean fish length  #

### 2019-04-30 analysis/04_temporal_habitat_data.R
Plot stability and link to usage and river carasteristics

@@ -23,6 +23,7 @@ hydro %>%
   unnest()
 
 ## Number of times by station where isolation has been reported:
+### But what is exactly isolation?
 isolation <- hydro %>%
   select(station, isolation_down, isolation_up) %>%
   mutate_at(vars(matches("isolation")), list(~ifelse(. == "no", "no", "yes"))) %>%
@@ -40,8 +41,9 @@ sum(hydro$avg_daily_flow == 0, na.rm = TRUE) / nrow(hydro)
 flow_col <- c("instream_flow", "artificial_flow_variation", "replenishment_flow")
 flow <- env_analysis %>%
   select(station, flow_col) %>%
+  mutate_all(list(~replace(., . %in% c("NA"), NA))) %>%
   group_by(station) %>%
-  summarise_all(list(~paste(ifelse(any(. == "yes"), "yes", "no"))))
+  summarise_all(list(~sum(. == "yes", na.rm = TRUE) / length(na.omit(.))))
 
 #############################
 #  Morphology of the river  #
@@ -52,7 +54,7 @@ sum(hydro$slope == 0, na.rm = TRUE) / nrow(hydro)
 # We have no slope
 
 river_morpho <- hydro %>%
-  select(station, slope, width_river, avg_depth_station) %>%
+  select(station, width_river, avg_depth_station) %>%
   group_by(station) %>%
   summarise_all(list(mean = ~mean(., na.rm = TRUE), cv = ~sd(., na.rm = TRUE)/ mean(., na.rm = TRUE)))
 
@@ -65,9 +67,9 @@ hydro %>%
 channel <- hydro %>%
   select(station, chanelled_station) %>%
   rename(channelled = chanelled_station) %>%
-  mutate(channelled = replace(channelled, channelled == "unknown", NA)) %>%
+  mutate(channelled = replace(channelled, channelled %in% c("NA", "unknown"), NA)) %>%
   group_by(station) %>%
-  summarise_all(list(~paste(ifelse(any(. == "yes"), "yes", "no"))))
+  summarise_all(list(~sum(. == "yes", na.rm = TRUE) / length(na.omit(.))))
 
 ###########
 #  Usage  #
@@ -79,8 +81,9 @@ col_usage <- c("resettlement", "resettlement_observations",
 usage <- env_analysis %>%
   select(station, col_usage) %>%
   select(-resettlement_observations) %>%
[…]

### 2019-05-22 R/geo_methods.R
Start function to match point to closest lines

@@ -1,0 +1,31 @@
+#' Match points to lines
+#' 
+match_pt_line <- function(point = NULL, line = NULL, start_buffer = 0, inc_buffer = .1) {
+
+  stopifnot(!is.null(point) | !is.null(line))
+  # Start a list of length of the point list  
+  line_id <- integer(nrow(point))
+
+  # Begin with the buffer:
+  pt_buffer <- st_buffer(point, dist = start_buffer)
+  intersect_line <- st_intersects(pt_buffer, line)
+  mask_single <- map_lgl(intersect_line,
+    function(x) ifelse(length(x) == 1, TRUE, FALSE))
+  message(paste0(sum(mask_single), " pts have matches with one line."))
+  # Fill list with those that have one match
+  line_id[mask_single] <-
+    sapply(intersect_line[mask_single], function(x) x[1])
+
+  # For multiple matches, get the closer
+  mask_multi <- map_lgl(intersect_line,
+    function(x) ifelse(length(x) > 1, TRUE, FALSE))
+  if (any(mask_multi)) {
+    message(paste0(sum(mask_multi), " pts have matches with multi."))
+    point[mask_multi]
+  st_distance()
+     
+  }
+  # Fill list with the closer:
+  # Increase buffer size
+  line_id
+}

### 2019-05-29 tests/testthat/test-match_pt_line.R
Map quality and flow data on rht

@@ -23,7 +23,7 @@ st_cast(.,"LINESTRING")
 pol <- st_sf(id = 1:4, st_sfc(pol))
 plot(st_geometry(pts))
 plot(st_geometry(pol), add = T)
-pts_buffer <- st_buffer(pts, .1)
+pts_buffer <- st_buffer(pts, .2)
 plot(st_geometry(pts_buffer), add = TRUE)
 
 test_that("match works", {

### 2019-06-10 R/geo_methods.R
Update Makefile + update analysis

@@ -116,7 +116,7 @@ compute_glmssn <- function(data = NULL, var = NULL,
 
   # temporary hack:
   if (is.null(formula)) {
-    formula <-  avg_flow ~ avSloA
+    formula <-  as.formula(paste0(var_chr," ~ 1"))
   }
   if (is.null(corModel)) {
     corModel <- c("LinearSill.tailup", "Mariah.taildown",

### 2019-06-10 R/plot_methods.R

@@ -372,12 +372,15 @@ xylabs <- function (...) {
 mylabel <- function() {
   ggplot2::as_labeller(c(
     connectance = "Connectance",
+    connectance_corrected_med = "Median connectance",
     richness = "Number of nodes",
     max_troph_level = "Highest trophic level",
     mean_troph_level = "Average trophic level",
+    mean_troph_level_med = "Median average trophic level",
     modularity = "Modularity",
     nestedness = "Nestedness",
     nbnode = "Number of nodes",
+    nbnode_med = "Median number of nodes",
     richness_cv = "richness CV",
     richness_avg = "Average richness",
     richness_med = "Median richness",

### 2019-06-10 analysis/03_compute_temporal_network_properties.R

@@ -95,7 +95,8 @@ myload(network_analysis, dir = dest_dir)
 myload(op_analysis, dir = data_common)
 
 net <- left_join(network_analysis, dplyr::select(op_analysis, opcod, station, year)) %>%
-  ungroup()
+  ungroup() %>%
+  filter(!is.na(station))
 
 source('../analysis/misc/parallel_setup.R')
 ## Get network as matrices
@@ -107,11 +108,11 @@ net %<>%
 }
 ))
 ## betalink:
-net %>%
+net %<>%
   select(network, station) %>%
   group_by(station) %>%
   nest() %>%
-  mutate(betalink = furrr::future_map2(data, station,
+  mutate(betalink = map2(data, station,
       function (x, y) {
       message(sprintf("Station %s", y))
       betalink::network_betadiversity(x$network)

### 2019-06-10 data-raw/05_interpolate_environmental_data.R

@@ -17,235 +17,151 @@ library(sf)
 library(rgeos)
 library(openSTARS)
 mypath <- rprojroot::find_package_root_file
+Sys.setenv(LANG = "en")
 mydir <- mypath("data-raw")
 source(mypath("R", "misc.R"))
 source(mypath("R", "geo_methods.R"))
 source(mypath("R", "plot_methods.R"))
 
-#########################
-#  Test with one basin  #
-#########################
+##############
+#  Get data  #
+##############
 
 # Load fish and environmental station
 myload(rht, dir = mypath("data-raw"))
 rht %<>% st_transform(crs = 2154)
 myload(station_analysis, dir = mypath("data"))
-station_analysis %<>% st_transform(crs = 2154)
+station <- station_analysis %>%
+  st_transform(crs = 2154) %>%
+  select(id, drain_id)
 myload(donuts_analysis, dir = mypath("data"))
-donuts_analysis %<>% st_transform(crs = 2154)
-
-# Get attribute of the rht: 
-attr_rht <- read_delim(
-  mypath("data-raw", "RHT", "Attributs_RHT_fev2011_Phi_qclass2.txt"),
-  delim = "\t"
-)
-unique(attr_rht$region_csp)
-## Add to rht the region:
-rht %<>%
-  rename(id_drain = ID_DRAIN) %>%
-  left_join(dplyr::select(attr_rht, id_drain, region_csp), by = "id_drain")
-
-# Select donuts, fish station and rht that are in Seine basin:
-rht_sein <- rht %>%
-  filter(region_csp == "Sein")
-donuts_sein <- donuts_analysis %>%
-  mutate(id = as.character(id)) %>%
-  filter(drain_id %in% rht_sein$id_drain)
-station_sein <- station_analysis %>%
-  filter(drain_id %in% rht_sein$id_drain)
-
-debug(prepare_pulse_interpolation)
-flow_pulse_complete <- prepare_pulse_interpolation(data = flow_data,
-  date = meas_date, var = value, donuts = donuts_sein, id = id)
-filter(flow_pulse_complete, !is.na(low_pulse))
-flow_pulse_complete %<>%
-  mutate(low_pulse = as.numeric(low_pulse),
-    high_pulse = as.numeric(high_pulse)
-  )
-summary(flow_pulse_complete)
-
-binSp$ssn.object@data %>%
-  as_tibble()
-mf04p
[…]

### 2019-07-09 data-raw/ssn_interpolation/04_basin_interpolation.R
Check quality variable

@@ -16,7 +16,7 @@ options(mc.cores = 5)
 mclapply(basin, function (x) {
   interpolate_basin(ssn_dir = mypath("data-raw", "ssn_interpolation"),
     basin_name = x, quality_data = quality_data,
-    var = c("TN", "TP", "CONDUCTY", "SO4", "temp", "PHY_CHLA", "D_OXY"),
+    var = c("pH"),
     complete = TRUE
   )
 })

### 2019-07-09 data-raw/ssn_interpolation/05_result_exploration.R

@@ -13,7 +13,7 @@ source(mypath("R", "plot_methods.R"))
 
 # Load fish and environmental station
 
-res <- sapply(c("ouest", "nord", "sud", "est"), function (basin) {
+res <- lapply(c("ouest", "nord", "sud", "est"), function (basin) {
   myload(quality_prediction, dir = mypath("data-raw", "ssn_interpolation", basin))
   quality_prediction
 })
@@ -24,12 +24,11 @@ cross_val <- quality %>%
   mutate(cross_v = map(cross_v, enframe)) %>%
   unnest()
 
-filter(cross_val, is.na(year))
-for nord, look at data
 # Prediction:
-press <- quality %>%
+prediction <- quality %>%
   select(-cross_v) %>%
-  unnest(prediction) %>%
+  unnest(prediction)
+press <- prediction %>%
   group_by(id, var_code) %>%
   summarise(press = mean(avg_data))
 
@@ -38,3 +37,4 @@ ggplot(press, aes(x = press) ) +
   facet_wrap(~ var_code)
 
 mysave(press, dir = mypath("data-raw", "ssn_interpolation"), overwrite = TRUE)
+

### 2019-07-15 analysis/01_compute_community_metrics.R
Cleaning and compute biomass correlation between trophic level

@@ -8,12 +8,14 @@ library(magrittr)
 library(lubridate)
 library(furrr)
 library(vegan)
-devtools::load_all()
+mypath <- rprojroot::find_package_root_file
+source(mypath("R", "misc.R"))
+#devtools::load_all()
 
 # Cores
 cat("Working directory:\n")
 cat(getwd(), "\n")
-source('../analysis/misc/parallel_setup.R')
+source(mypath("analysis", "misc","parallel_setup.R"))
 
 #####################
 #  Compute biomass  #
@@ -81,7 +83,7 @@ mysave(community_analysis, dir = data_common, overwrite = TRUE)
 #  Compute community metrics  #
 ###############################
 # Summary information by fishing operation such as richness, biomass
-data(community_analysis)
+myload(community_analysis, dir = mypath("data"))
 
 com <- community_analysis %>%
   group_by(opcod) %>%
@@ -97,8 +99,7 @@ mysave(community_metrics, dir = data_common, overwrite = TRUE)
 ############################
 #  Compute beta-diversity  #
 ############################
-data(community_analysis)
-data(op_analysis)
+myload(community_analysis, op_analysis, dir = mypath("data"))
 
 # Compute beta-diversity 
 com <- left_join(ungroup(community_analysis),
@@ -161,8 +162,7 @@ betadiv <- com %>%
 #  Compute temporal community description  #
 ############################################
 # Compute mean and cv of richness
-data(community_metrics)
-data(op_analysis)
+myload(community_metrics, op_analysis, dir = mypath("data"))
 
 com <- left_join(community_metrics, op_analysis, by = c("opcod")) %>%
   group_by(station) %>%

### 2019-07-15 analysis/03_compute_temporal_network_properties.R

@@ -39,7 +39,7 @@ cat("---------------------------------------------\n")
 cat("Temporal network biomass by trophic group\n")
 cat("---------------------------------------------\n")
 
-myload(op_analysis, metaweb_analysis, dir = data_common)
+myload(op_analysis, metaweb_analysis, network_analysis, dir = data_common)
 myload(network_metrics, dir = dest_dir)
 
 op <- op_analysis %>% dplyr::select(opcod, station, year)
@@ -131,3 +131,37 @@ mysave(temporal_network_metrics, dir = dest_dir, overwrite = TRUE)
 cat("-----------------------------------\n")
 cat("End of temporal metrics computation\n")
 cat("-----------------------------------\n")
+
+################################################################
+#  Compute temporal correlation between biomass trophic level  #
+################################################################
+cat("----------------------------------------------------------\n")
+cat("Compute temporal correlation between biomass trophic level\n")
+cat("----------------------------------------------------------\n")
+myload(op_analysis, metaweb_analysis, network_analysis, dir = data_common)
+myload(network_metrics, dir = dest_dir)
+
+op <- op_analysis %>% dplyr::select(opcod, station, year)
+net <- left_join(network_metrics, op, by = "opcod") %>%
+  ungroup()
+rm(op_analysis, network_analysis)
+troph_group_biomass <- net %>%
+  unnest(composition) %>%
+  group_by(station, troph_group, year) %>%
+  summarise(biomass = mean(biomass)) %>%
+  ungroup() %>%
+  spread(troph_group, biomass) 
+
+cor_troph_group <- troph_group_biomass %>%
+  rename(low = `2`, high = `3`) %>%
+  select(station, year, low, high) %>%
+  group_by(station) %>%
+  arrange(year) %>%
+  summarise(n_obs = n(),
+    cor_troph = cor(low, high, use = "pairwise.complete.obs",method = "spearman"))
+mysave(cor_troph_group, dir = mypath("data"))
+
+cat("-----------------------------------\n")
+cat("End of temporal metrics computation\n")
+cat("-----------------------------------\n")
+

### 2019-07-17 analysis/03_compute_temporal_network_properties.R
Setup socket interpolation + setup synchrony computation + vignettes

@@ -138,28 +138,96 @@ cat("-----------------------------------\n")
 cat("----------------------------------------------------------\n")
 cat("Compute temporal correlation between biomass trophic level\n")
 cat("----------------------------------------------------------\n")
-myload(op_analysis, metaweb_analysis, network_analysis, dir = data_common)
+myload(op_analysis, network_analysis, dir = data_common)
 myload(network_metrics, dir = dest_dir)
 
-op <- op_analysis %>% dplyr::select(opcod, station, year)
+op <- op_analysis %>% dplyr::select(opcod, station, date)
 net <- left_join(network_metrics, op, by = "opcod") %>%
-  ungroup()
+  ungroup() %>%
+  filter(!is.na(station))
 rm(op_analysis, network_analysis)
 troph_group_biomass <- net %>%
   unnest(composition) %>%
-  group_by(station, troph_group, year) %>%
+  group_by(station, troph_group, date) %>%
   summarise(biomass = mean(biomass)) %>%
   ungroup() %>%
-  spread(troph_group, biomass) 
+  mutate(troph_group = ifelse(troph_group == 2, "low", "high"))
+  #spread(troph_group, biomass) %>%
 
-cor_troph_group <- troph_group_biomass %>%
-  rename(low = `2`, high = `3`) %>%
-  select(station, year, low, high) %>%
+complete_com <- troph_group_biomass %>%
   group_by(station) %>%
-  arrange(year) %>%
-  summarise(n_obs = n(),
-    cor_troph = cor(low, high, use = "pairwise.complete.obs",method = "spearman"))
-mysave(cor_troph_group, dir = mypath("data"))
+  summarise(
+    troph_group = list(unique(troph_group)),
+    date = list(unique(date))) %>%
+  mutate(comb = map2(troph_group, date, function(sp, date){
+    test <- expand.grid(troph_group = sp, date = date)
+    return(test)
+    })
+    ) %>%
+  unnest(comb)
+# Join and put biomass to 0 when no observed:
+complete_com %<>% left_join(troph_group_biomass, by = c("station", "troph_group", "date")) %>%
+  mutate(biomass = ifelse(is.na(biomass), 0, biomass))
+
+test <- complete_com %>%
+  group_by(station, troph_group, date) %>%
+  summarise(nobs = n())
+filter(test, nobs > 1)
[…]

### 2019-07-17 data-raw/03_generate_analysis_dataset.R

@@ -14,6 +14,7 @@ mypath <- rprojroot::find_package_root_file
 mydir <- mypath("data-raw", "fishing_op_build")
 source(mypath("R", "plot_methods.R"))
 source(mypath("R", "misc.R"))
+source(mypath("R", "building_dataset.R"))
 theme_set(theme_alain())
 
 
@@ -21,9 +22,20 @@ myload(op, dir = mypath("data-raw"))
 
 #op_sp_ind Summary of op 
 myload(op_sp_ind, dir = mypath("data"))
-op_sp_ind
+test_unique_op <- op_sp_ind %>%
+  group_by(opcod) %>%
+  summarise(nobs = n()) %>%
+  filter(nobs > 1)
+stopifnot(nrow(test_unique_op) == 0)
+
 
 op %<>% left_join(op_sp_ind, by = "opcod")
+test_unique_st_date  <- op %>%
+  group_by(station, date) %>%
+  summarise(nobs = n()) %>%
+  filter(nobs > 1) %>%
+  arrange(station)
+message(cat(test_unique_st_date$station), " stations have several op by date\n", "To be cleaned")
 
 ##############################################
 #  Distribution of fishing operation timing  #
@@ -55,7 +67,6 @@ low_int <- filter(int_op, sample_sep < 60) %>%
   ungroup() %>%
   arrange(station)
 filter(int_op, station == 657)
-
 ## filter double sampling, surely doubled 
 clean_dbl <- group_by(int_op, station) %>%
   nest() %>%
@@ -77,8 +88,12 @@ qplot(sample_sep, data = filter(clean_dbl, sample_sep < 2000)) +
     y = "Frequency") +
   xlim(c(0, 2000))
 filter(clean_dbl, sample_sep < 160)
-filter(clean_dbl, station == 709)
-filter(clean_dbl, station == 657)
+test_dbl_op  <- clean_dbl %>%
+  group_by(station, date) %>%
+  summarise(nobs = n()) %>%
+  filter(nobs > 1) %>%
+  arrange(station)
+stopifnot(nrow(test_dbl_op) == 0)
 
 # Numbering the sampling events by station
 op_hist <- clean_dbl %>%
@@ -111,9 +126,14 @@ qplot(sdt, data = op_test_station) +
 
 
 # For temporal analysis, we keep station followed more than 10 times
-op <- filter(op, station %in% good_station_id)
[…]

### 2019-07-17 data-raw/naiades_ssn/01_cut_dataset.R

@@ -31,6 +31,13 @@ if (!dir.exists(saving_dir)) {
   dir.create(saving_dir)
 }
 
+# Filter data according to the station selected in 00_basin_ssn.R
+myload(station_to_keep, dir = mypath("data-raw", "naiades_ssn"))
+length(unique(yearly_avg_polluants$id))
+length(unique(station_to_keep$id))
+yearly_avg_polluants %<>%
+  filter(id %in% station_to_keep$id)
+
 yearly_avg_polluants %>%
   group_by(parameter) %>%
   nest() %>%

### 2019-07-22 analysis/01_compute_community_metrics.R
Correct cv_com

@@ -186,6 +186,7 @@ mysave(temporal_community_metrics, dir = data_common, overwrite = TRUE)
 #  Compute population synchrony  #
 ##################################
 # Following Thibault & Collonny (2013). Ecolet
+source(mypath("R", "synchrony.R"))
 
 myload(community_analysis, op_analysis, dir = mypath("data"))
 
@@ -222,32 +223,22 @@ complete_com %<>%
 complete_com %<>%
   mutate(
     com_mat = purrr::map(data, function(x) spread(x, species, biomass)),
-    com_mat = purrr::map(com_mat, function(x) select(x, -date))
+    com_mat = purrr::map(com_mat, function(x) select(x, -date)),
+    com_mat = purrr::map(com_mat, as.matrix)
   )
 synchrony <- complete_com %>%
   mutate(
     avg_sp = purrr::map(com_mat, colMeans),
     cov_mat = purrr::map(com_mat, cov),
     var_sp = purrr::map(cov_mat, diag),
-    synchrony = purrr::map_dbl(cov_mat, function(x) {
-      com_var <- sum(x)
-      var_intra_sp <- sum(sqrt(diag(x)))
-      phi <- com_var / var_intra_sp^2 
-      return(phi)
-    }),
-  cv_sp = purrr::map2_dbl(avg_sp, var_sp, function(biomass, variance) {
-    #Check that the species are in the same order in the vector:
-    stopifnot(names(biomass) == names(variance))
-
-    rel_biomass <- biomass / sum(biomass)
-    rel_sdt <- sqrt(variance) / biomass
-
-    cv_avg <- sum(rel_biomass * rel_sdt)
-    return(cv_avg)
-    }),
-  cv_com = synchrony * cv_sp
+    synchrony = purrr::map_dbl(cov_mat, compute_synchrony),
+    cv_sp = purrr::map2_dbl(avg_sp, var_sp, compute_avg_cv_sp),
+    cv_com = compute_cv_com(synchrony = synchrony, cv_sp = cv_sp),
+    cv_classic = purrr::map2_dbl(cov_mat, com_mat, function(variance, biomass) {
+      sqrt(sum(variance)) / mean(rowSums(biomass))
+    })
   )
 
 synchrony %<>%
-  select(station, synchrony, cv_sp, cv_com)
+  select(station, synchrony, cv_sp, cv_com, cv_classic)
 mysave(synchrony, dir = mypath("data"), overwrite = TRUE)

### 2019-07-23 run/03_make_interpolation.R
script to interpolate polluants

@@ -1,0 +1,45 @@
+#!/usr/bin/env Rscript
+# Args should be to specify the type of cluster you are on or at home in order
+# to find the cpus
+# See: ?availableCores
+args <- commandArgs(trailingOnly=TRUE)
+if (!is.null(args) & length(args) == 2) {
+  options(future.availableCores.methods = args[1])
+  message("The first argument has been passed to the
+    future.availableCores.methods option.
+    On the cluster, it should be 'PBS'.")
+  options("network.type" = args[2])
+  message("The second argument has been passed to the
+    network.type option. It should be species for species network.
+    Other values create size class network.")
+  
+} else if (!is.null(args) & length(args) == 1) {
+  options(future.availableCores.methods = args[1])
+  message("The first argument has been passed to the
+    future.availableCores.methods option.
+    On the cluster, it should be 'PBS'.")
+}
+options(echo = TRUE)
+
+# Path to save network analysis:
+mypath <- rprojroot::find_package_root_file
+
+source(mypath("R", "misc.R"))
+source(mypath("R", "geo_methods.R"))
+
+
+# Make moving windows on raw data:
+source(mypath("data-raw", "polluants", "03_moving_windows.R")
+
+# Make press interpolation: 
+interp_scripts <- c(
+  "00_basin_ssn.R",
+  "00bis_save_ssn.R",
+  "01_cut_dataset.R",
+  "02_basin_interpolation.R",
+  "03_inspect_results.R"
+      )
+paths <- paste0(mypath("data-raw", "polluants/"), interp_scripts)
+for (i in seq_along(interp_scripts)) {
+  source(paths[i])
+}

### 2019-08-09 data-raw/03_generate_analysis_dataset.R
Keep partial fish operation

@@ -13,6 +13,7 @@ library(lubridate)
 mypath <- rprojroot::find_package_root_file
 mydir <- mypath("data-raw", "fishing_op_build")
 source(mypath("R", "plot_methods.R"))
+source(mypath("R", "building_dataset.R"))
 source(mypath("R", "misc.R"))
 theme_set(theme_alain())
 
@@ -116,11 +117,10 @@ op %<>%
   mutate(year = year(date))
 
 op_analysis_complete_partial <- op
-devtools::use_data(op_analysis_complete_partial, overwrite = TRUE)
 
 op %<>% filter( protocol == "complete")
 op_analysis <- op
-devtools::use_data(op_analysis, overwrite = TRUE)
+mysave(op_analysis, op_analysis_complete_partial, dir = mypath("data"), overwrite = TRUE)
 
 good_opcod_id <- select(ungroup(op_analysis), opcod) %>% unlist
 
@@ -157,6 +157,23 @@ filter(op_analysis, station == 203)
 op_analysis %<>% filter(opcod %in% filter(test_too_different, out == FALSE)$opcod)
 
 mysave(op_analysis, dir = mypath("data"), overwrite = TRUE)
+
+#####################
+#  Partial fishing  #
+#####################
+
+myload(op_analysis_complete_partial, dir = mypath("data"))
+myload(op_desc, dir = mypath("data-raw"))
+op_desc %<>%
+  rename(opcod = ope_id) %>%
+  filter(opcod %in% unique(op_analysis_complete_partial$opcod))
+op_partial <- op_analysis_complete_partial %>%
+  filter(protocol != "complete") %>%
+  left_join(select(op_desc, opcod, length_sourced)) %>%
+  arrange(station)
+
+## To launch again build fish lot on the clusteq
+
 
 ########################
 #  Environmental data  #

### 2019-08-21 R/building_dataset.R
Partial protocol has been successfully imported

@@ -330,10 +330,58 @@ check_lot <- function (
   status 
 }
 
+
+#' Remove fishing operation that are too close in time 
+#'
+#' @param op data.frame generated by the vignette `aspe_database.Rmd`
+#' @param sep_threshold int. Number of days minimum between two operations
+#' @param nb_sampling int. Minimum number of the operation for a station to be
+#' kept in the dataset
+#'
+#' @details sep_threshold and nb_sampling are set to 270 and 10 by default
+#' respectively.
+#'
+#' @export
+rm_dbl_fishing_op <- function (op = NULL, sep_threshold = 270, nb_sampling = 10) {
+
+  # Set consecutive days between operation by station 
+  int_op <- op %>%
+   dplyr::group_by(station) %>%
+   dplyr::arrange(date) %>%
+   dplyr::mutate(
+      point = seq(1, length(station)),
+      sample_sep = c(NA, date[-1] - date[-length(station)])
+      ) %>%
+   dplyr::arrange(station)
+
+  # Keep the most complete sampling for each op
+  clean_dbl <- int_op %>%
+    dplyr::group_by(station) %>%
+    tidyr::nest() %>%
+    dplyr::mutate(data = 
+      purrr::map(data, ~keep_most_complete_sampling(
+	  station = .x, threshold = sep_threshold))) %>%
+    tidyr::unnest()
+  #
+  # Numbering the sampling events by station
+  op_hist <- clean_dbl %>%
+    dplyr::group_by(station) %>%
+    dplyr::summarise(freq = dplyr::n())
+
+  good_station <- op_hist %>%
+    dplyr::filter(freq >= nb_sampling)
+  
+
+  op %<>% 
+    dplyr::filter(station %in% good_station$station, opcod %in% clean_dbl$opcod) %>%
+    dplyr::mutate(year = lubridate::year(date))
+
+  return(op)
+}
+
 ##################################
 #  Filter double fish operation  #
 ##################################
-
 
 del_dbl_op <- function (point, tot, ...) {
   # The targeted op have likely less species
@@ -343,7 +391,8 @@ del_dbl_op <- function (point, tot, ...) {
     slice(1)
   kept_station
 }
-keep_most_complete_sampling <- function (station, threshold = 270) {
+keep_most_complete_sampling <- function (station = NULL, threshold = 270) {
+
   ##Any double fishing within two month
[…]

### 2019-08-21 data-raw/03_generate_analysis_dataset.R

@@ -4,18 +4,11 @@
 
 library(tidyverse)
 library(magrittr)
-library(cowplot)
-library(ggpmisc)
-library(sf)
-library(rgdal)
 library(lubridate)
-#devtools::load_all()
 mypath <- rprojroot::find_package_root_file
 mydir <- mypath("data-raw", "fishing_op_build")
-source(mypath("R", "plot_methods.R"))
 source(mypath("R", "building_dataset.R"))
 source(mypath("R", "misc.R"))
-theme_set(theme_alain())
 
 
 myload(op, dir = mypath("data-raw"))
@@ -23,122 +16,43 @@ myload(op, dir = mypath("data-raw"))
 #op_sp_ind Summary of op 
 myload(op_sp_ind, dir = mypath("data"))
 op_sp_ind
-
 op %<>% left_join(op_sp_ind, by = "opcod")
 
-##############################################
-#  Distribution of fishing operation timing  #
-##############################################
-
-
-qplot(month, data = mutate(op, month = month(date))) +
-  labs(x = "Date",
-    y = "Frequency")
-
-
-######################################
-#  Remove doubled fishing operation  #
-######################################
-
-# Get the time between each sampling event
-int_op <- op %>%
-  ungroup() %>%
-  group_by(station) %>%
-  arrange(date) %>%
-  mutate(
-    point = seq(1, length(station)),
-    sample_sep = c(NA, date[-1] - date[-length(station)])
-  ) %>%
-  arrange(station)
-
-## double_station 
-low_int <- filter(int_op, sample_sep < 60) %>%
-  ungroup() %>%
-  arrange(station)
-filter(int_op, station == 657)
-
-## filter double sampling, surely doubled 
-clean_dbl <- group_by(int_op, station) %>%
-  nest() %>%
-  mutate(data = map(data, keep_most_complete_sampling)) %>%
-  unnest()
-
-
-# Check new time separation between 2 consecutive ops  
-clean_dbl %<>%
-  group_by(station) %>%
-  arrange(date) %>%
-  mutate(
-    point = seq(1, length(station)),
-    sample_sep = c(NA, date[-1] - date[-length(station)])
-  ) %>%
-  arrange(station)
-qplot(sample_sep, data = filter(clean_dbl, sample_sep < 2000)) +
-  labs(x = "Number of days between two fishing operation",
-    y = "Frequency") +
[…]

### 2019-09-17 analysis/02_compute_network_metrics.R
Add model by basin

@@ -266,6 +266,7 @@ network_analysis %<>%
 
 network_metrics <- network_analysis %>%
   dplyr::select(-metrics, -troph_level)
+
 mysave(network_metrics, dir = dest_dir, overwrite = TRUE)
 
 ##############################
@@ -382,6 +383,34 @@ net_diet %<>%
 
 network_metrics %<>%
   left_join(net_diet, by = "opcod")
+
+
+####################################
+#  Compute weighted trophic level  #
+####################################
+
+weighted_mean_trophic_lvl <- network_metrics %>%
+  select(opcod, composition) %>%
+  unnest(composition) %>%
+  group_by(opcod) %>%
+  summarise(w_trph_lvl_avg = sum(troph_level * biomass) / sum(biomass))
+network_metrics %<>%
+  left_join(weighted_mean_trophic_lvl, by = "opcod")
+
+# Disantengle weighted avg trophic richness and number of species 
+#formula <- y ~ x + I(x^2)
+#qplot(log(nbnode), w_trph_lvl_avg, data =  network_metrics, geom = "point") +
+  #geom_smooth(method = 'lm', formula = formula) +
+  #stat_poly_eq(
+    #formula = formula,
+    #eq.with.lhs = "italic(hat(y))~`=`~",
+    #aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    #parse = TRUE) +
+  #xylabs(x = "nbnode", y = "Avg trophic level")
+
+#mod <- lm(w_trph_lvl_avg ~ I(nbnode^2) , network_metrics)
+#par(mfrow = c(2,2))
+#plot(mod)
 
 mysave(network_metrics, dir = dest_dir, overwrite = TRUE)
 

### 2019-09-19 report/02-methods.Rmd
Start a book to collect results, methods, etc

# Methods

We describe our methods in this chapter.

## Data collection

## Network building

### Metaweb

```{r metaweb, fig.cap = "Metaweb representation (9 classes by fish species)"}
library(igraph)
library(NetIndices)
myload(metaweb_analysis, dir = data_common)
meta <- metaweb_analysis; rm(metaweb_analysis)

g <- igraph::graph_from_adjacency_matrix(meta$metaweb, mode = "directed")

# Define layout
lay <- layout.fruchterman.reingold(g)
# Compute trophic level
dead_material <- c("det", "biof")
lay[, 2] <- TrophInd(meta$metaweb, Dead = dead_material)$TL
# Plot
par(mar=rep(5, 4))
plot.igraph(g,layout=lay,vertex.label=NA,vertex.size=2,edge.arrow.size=.5,edge.width=.5)
```

### Local networks

OMG, that is bautiful!

```{r local-net, fig.cap = "An exemple of a local network"}
myload(network_analysis, dir = mypath("data", "species"))
myload(op_analysis, dir = data_common)
net <- network_analysis %>%
  dplyr::select(opcod, network) %>%
  unnest() %>%
  left_join(., dplyr::select(op_analysis, opcod, station, date))

net_ex <- filter(net, station == unique(net$station) %>% sample(., 1))

net_list <- net_ex %>%
  dplyr::select(date, from, to) %>%
  arrange(date) %>%
  group_by(date) %>%
  nest(.key = "network")

size_analysis <- network_analysis %>%
  dplyr::select(opcod, composition) %>%
  filter(opcod %in% net_ex$opcod) %>%
  unnest() %>%
  left_join(select(net_ex, date, opcod) %>% distinct(opcod, date)) %>%
  dplyr::select(date, biomass, species) %>%
  arrange(date) %>%
  group_by(date) %>%
  nest() %>%
  mutate(biomass = map(data, function(x){
      val <- x$biomass
      names(val) <- x$species 
      val
  }))

net_list %<>%
  left_join(dplyr::select(size_analysis, date, biomass))
#Node position:
node <- net_list$network %>% unlist(., use.names = FALSE) %>% unique
test <- graph_from_adjacency_matrix(meta$metaweb) %>% as_data_frame %>%
  mutate_all(list(~str_extract_all(., "[a-zA-Z]+", simplify = TRUE))) %>%
  distinct(from, to)
node_position <- create_layout(graph_from_data_frame(test), layout = "kk")$x
names(node_position) <- create_layout(graph_from_data_frame(test), layout = "kk")$name
#color:
color <- set_color_species(node_list = node, species_list = NULL,
  resource_list = NULL,
  col_resource = NULL)

## Graph -------------------------
plot_temporal_network(
  data = net_list,
  net_var = network,
  date = date,
  x = node_position,
  y = net_list[["y"]],
  size = net_list[["biomass"]]
)

```

This is super cool to see! =)

## Environmental data

### Habitat

### Pressure

## Analysis

### Network

### Pressure

### 2019-09-19 report/03-results.Rmd
Start a book to collect results, methods, etc

# Results

## Network description

```{r net-cor-med, fig.cap = "Correlation between network indices (median over the temporal series). "}
# Get network metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)

cor_avg <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("med"))) %>%
  cor()
#knitr::kable(cor_avg)
as.data.frame(round(cor_avg,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r net-cor-cv, fig.cap="Correlation between network indices (CV over the temporal series). "}
cor_cv <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("cv"))) %>%
  cor()
as.data.frame(round(cor_cv,2)) %>%
  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r}
library(ade4)
library(factoextra)

net_ind <- temporal_network_metrics %>%
  left_join(select(temporal_community_metrics, station, richness_med)) %>%
  select_at(vars(dplyr::matches("med")))

res.pca <- dudi.pca(na.omit(net_ind),
  scannf = FALSE,   # Hide scree plot
  nf = 5            # Number of components kept in the results
)
eig_plot <- fviz_eig(res.pca)
```

```{r}
pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
  fviz_pca_var(res.pca,
    axes = axes,
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
})

temp_plot <- plot_grid(plotlist = pca_plot)
plot_grid(temp_plot, eig_plot)
```

### Look at some network temporal series

Let's look at network that have particular network properties.

```{r}
myload(network_analysis, dir = mypath("data", "species"))
myload(op_analysis, metaweb_analysis, dir = data_common)
meta <- metaweb_analysis; rm(metaweb_analysis)

net <- network_analysis %>%
  dplyr::select(opcod, network) %>%
  unnest() %>%
  left_join(., dplyr::select(op_analysis, opcod, station, date)) 
```

```{r}
station_high_low_modularity <- temporal_network_metrics %>%
  arrange(desc(modularity_med)) %>%
  slice(c(1, n())) %>%
  select(station) %>%
  unlist
names(station_high_low_modularity) <- c("high", "low") 
```

```{r tmp-net-h-mod, fig.cap = "Station with the highest modularity (median)."}
# High modularity
net_ex <- filter(net, station == station_high_low_modularity["high"])

my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
  = network_analysis)
```
```{r tmp-net-l-mod, fig.cap = "Station with the lowest modularity (median)."}
# Low modularity
net_ex <- filter(net, station == station_high_low_modularity["low"])
my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
  = network_analysis)
```

```{r}
station_high_low_nestedness <- temporal_network_metrics %>%
  arrange(desc(nestedness_med)) %>%
  slice(c(1, n())) %>%
  select(station) %>%
  unlist
names(station_high_low_nestedness) <- c("high", "low") 
```
```{r tmp-net-h-nest, fig.cap = "Station with the highest nestedness (median)."}
# high nestedness
net_ex <- filter(net, station == station_high_low_nestedness["high"])
my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
  = network_analysis)
```

```{r tmp-net-l-nest, fig.cap = "Station with the lowest nestedness (median)."}
# low nestedness
net_ex <- filter(net, station == station_high_low_nestedness["low"])
my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
  = network_analysis)
```

## Productivity

## Stability of biomass

### Some temporal series of biomass

```{r}
myload(community_metrics, dir = data_common)
community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
station_high_low_stab <- temporal_community_metrics %>%
  arrange(desc(biomass_stab)) %>%
  slice(c(1:5, (n() - 4):(n() - 0))) %>%
  select(station) %>%
  unlist
names(station_high_low_stab) <- rep(c("high", "low"), each = 5) 
```

```{r tmp-stab, fig.dim = c(10, 7), fig.cap = "The five lowest and highest biomass stability"}
temporal_biomass <- community_metrics %>%
  filter(station %in% station_high_low_stab) %>%
  mutate(stab_status = ifelse(
      station %in% station_high_low_stab[names(station_high_low_stab) == "low"],
      "low", "high")) %>%
  group_by(stab_status, station) %>%
  nest() %>%
  group_by(stab_status) %>%
  mutate(id_stab = seq_along(station)) %>%
  unnest()
ggplot(temporal_biomass, aes(y = biomass, x = date)) +
  geom_line() +
  geom_point() +
  facet_grid(id_stab ~ stab_status, scales = "free_y") +
  labs(y = "Biomass (g)", x = "Date")
```

### Map stability

```{r}
myload(station_analysis, region_polygon, dir = data_common)
stab <- temporal_community_metrics %>% 
  select(station, biomass_stab)
station_stab <- left_join(station_analysis, rename(stab, id = station)) %>%
  filter(!is.na(biomass_stab))
ggplot(data = region_polygon) +
    geom_sf() +
    geom_sf(data = station_stab, aes(color = log(biomass_stab)), size = 4) +
    scale_color_gradient(low = "red", high = "green")
```

### Link biomass stability with community structure

```{r stab-div-mult, fig.dim = c(10, 7), fig.cap = "Link between the stability of biomass and diversity"}
biomass_com <- temporal_community_metrics %>%
  left_join(select(synchrony, station, synchrony, cv_sp)) %>%
  select(biomass_stab, synchrony, cv_sp, richness_cv, richness_med, betadiv) %>%
  gather(diversity, div_value, richness_med, richness_cv, betadiv) %>%
  gather(stability, stab_value, biomass_stab, synchrony, cv_sp)

formula <- y ~ x #needed for stat_poly_eq
qplot(div_value, stab_value, data =  biomass_com, geom = "point") +
  facet_grid(stability ~ diversity, labeller = mylabel(), scales = "free") +
  geom_smooth(method = 'lm') +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  labs(x = "Diversity", y = "Stability component")
```

```{r stab-net, fig.cap = "Link between biomass stability and network structure (median)"}
# plot
avg_network <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("med|station")))
biomass_stab_station <- temporal_community_metrics %>%
  select(station, biomass_stab)
stab_biomass_net_avg <- left_join(avg_network, biomass_stab_station) %>%
  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
  mutate(metrics = str_replace(metrics, "_med", "")) %>%
  filter(metrics != "nbnode")

# TODO: think about not facetting (list of plots ?)
# Facet label:
formula <- y ~ x #needed for stat_poly_eq
p <- ggplot(stab_biomass_net_avg, aes(y = biomass_stab, x = values)) +
  geom_point() +
  facet_wrap(~ metrics, labeller = mylabel(), scales = "free_x") +
  geom_smooth(method = 'lm') +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  labs(
    x = "Median of the network indices",
    y = "Biomass stability"
  )
p
```

```{r stab-comp, fig.cap = "Link between biomass stability by trophic group and total species richness (median)"}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
net_troph_group <- temporal_network_metrics %>% 
  unnest(troph_group) %>%
  mutate(troph_group = as.factor(troph_group))
net_troph_group %<>%
  select_at(vars(dplyr::matches("_med|stab|station|troph_group"))) %>%
  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
  mutate(metrics = str_replace(metrics, "_med", ""))
p <- ggplot(net_troph_group, aes(y = biomass_stab, x = values, color = troph_group)) +
  geom_point() +
  ggplot2::scale_fill_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    ) +
  facet_wrap(~metrics, labeller = mylabel(), scales = "free_x") +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    x = "network_med",
    y = "biomass_stab"
  )
p
```

The Figure \@ref(fig:stab-comp) showed that medium trophic level part of the
network had a positive stability-diversity relationship with while high
trophic level had a negative one.  
Furthermore, we see that high trophic level compartment had a highest stability
than the medium compartment. In the same vein, the latter pattern is confirmed when looking at the richness by compartment instead of the total richness (Figure \@ref(fig:stab-comp2)).

```{r stab-comp2, fig.dim = c(10, 7), fig.cap = "Link between biomass stability and species richness by trophic group (median)"}
net_troph_group <- temporal_network_metrics %>% 
  select(station, troph_group) %>%
  unnest() %>%
  filter(!is.na(troph_group)) %>%
  mutate(troph_group = as.factor(troph_group))
plot_stab_richness_troph_group <-
  ggplot(net_troph_group, aes(y = log(biomass_stab), x = richness_avg)) +
  geom_point() +
  facet_grid(cols = vars(troph_group)) +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    x = "richness_avg",
    y = "biomass_stab"
  )
plot_stab_richness_troph_group
```

One hypothesis to explain this opposite pattern might be a disequilibrium
between the two compartment. We can imagine that each compartment can
destabilize each other according to the part of the total biomass of total
species richness that there are in each of them. The figure
\@ref(fig:stab-comp-ratio) showed that the biomass stability of the medium
compartment decreased with the increase of biomass and species number ratio in
the high compartment and we observed the reverse for the high trophic
compartment.

We are looking forward to fully understand why we observed this inverse
relationship.

```{r stab-comp-ratio, fig.cap = "Biomass stability and ratio of biomass and species number (top and bottom panel resp.) in the high trophic level"}
ratio_sp <- net_troph_group %>%
  select(station, troph_group, richness_avg) %>%
  spread(troph_group, richness_avg) %>%
  mutate(sp_h_m = `3` / (`3` + `2`)) %>%
  select(station, sp_h_m)

ratio_bm <- net_troph_group %>%
  select(station, troph_group, biomass_avg) %>%
  spread(troph_group, biomass_avg) %>%
  mutate(bm_h_m = `3` / (`3` + `2`)) %>%
  select(station, bm_h_m)

net_troph_group <- temporal_network_metrics %>%
  left_join(ratio_sp, by = "station") %>%
  left_join(ratio_bm, by = "station") %>%
  select(station, troph_group, sp_h_m, bm_h_m) %>%
  unnest() %>%
  filter(!is.na(troph_group), troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  gather(ratio_troph, value, sp_h_m, bm_h_m)

plot_stab_richness_troph_group <-
  ggplot(net_troph_group, aes(y = log(biomass_stab), x = value)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(ratio_troph), labeller =
    troph_group_labeller()) +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    y = "biomass_stab"
  ) + 
    xlab("Ratio of biomass and species nb in high troph compartment compare to total")
plot_stab_richness_troph_group
```

## Pressure

## SEM

### All

### By basin

### 2019-09-19 R/plot_methods.R

@@ -373,18 +373,24 @@ mylabel <- function() {
   ggplot2::as_labeller(c(
     connectance = "Connectance",
     connectance_corrected_med = "Median connectance",
+    connectance_corrected = "Connectance (corrected)",
     richness = "Number of nodes",
     max_troph_level = "Highest trophic level",
     mean_troph_level = "Average trophic level",
     mean_troph_level_med = "Median average trophic level",
+    mean_troph_level_corrected_med = "Median average trophic level",
     modularity = "Modularity",
+    modularity_corrected = "Modularity corrected",
     nestedness = "Nestedness",
     nbnode = "Number of nodes",
     nbnode_med = "Median number of nodes",
     richness_cv = "richness CV",
     richness_avg = "Average richness",
     richness_med = "Median richness",
-    betadiv = "Beta-diversity"
+    betadiv = "Beta-diversity",
+    synchrony = "Synchrony",
+    cv_sp = "Avg species CV",
+    biomass_stab = "Biomass stability (1/CV)"
     #betadiv = expression(bold(paste(beta, "-diversity", sep = "")))
     #see https://stackoverflow.com/questions/35524202/as-labeller-with-expression-in-ggplot2-facet-wrap?rq=1
       )

### 2019-11-12 report/05-stability.Rmd
Add synchrony method for trophic species + plot method for species biomass dynamic

--- 2019-09-19 report/03-results.Rmd
@@
-# Results
-
-## Network description
-
-```{r net-cor-med, fig.cap = "Correlation between network indices (median over the temporal series). "}
-# Get network metrics
-myload(temporal_network_metrics, dir = dest_dir)
-myload(temporal_community_metrics, synchrony, dir = data_common)
-
-cor_avg <- temporal_network_metrics %>%
-  select_at(vars(dplyr::matches("med"))) %>%
-  cor()
-#knitr::kable(cor_avg)
-as.data.frame(round(cor_avg,2)) %>%
-  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
-	  "black")))) %>%
-  mutate(variable = colnames(.)) %>%
-  select(variable, everything()) %>%
-  kable(format = "html", escape = F)
-```
-
-```{r net-cor-cv, fig.cap="Correlation between network indices (CV over the temporal series). "}
-cor_cv <- temporal_network_metrics %>%
-  select_at(vars(dplyr::matches("cv"))) %>%
-  cor()
-as.data.frame(round(cor_cv,2)) %>%
-  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
-	  "black")))) %>%
-  mutate(variable = colnames(.)) %>%
-  select(variable, everything()) %>%
-  kable(format = "html", escape = F)
-```
+## Stability of biomass
 
 ```{r}
-library(ade4)
-library(factoextra)
-
-net_ind <- temporal_network_metrics %>%
-  left_join(select(temporal_community_metrics, station, richness_med)) %>%
-  select_at(vars(dplyr::matches("med")))
-
-res.pca <- dudi.pca(na.omit(net_ind),
-  scannf = FALSE,   # Hide scree plot
-  nf = 5            # Number of components kept in the results
-)
-eig_plot <- fviz_eig(res.pca)
+myload(temporal_network_metrics, dir = mypath("data", "cl~/Documents/post-these/mnhn/fishcom/report/index.Rmdasses"))
+temporal_network_metrics_classes <- temporal_network_metrics
+myload(temporal_network_metrics, dir = dest_dir)
+myload(temporal_community_metrics, synchrony, op_analysis, dir = data_common)
 ```
-
-```{r}
-pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
-  fviz_pca_var(res.pca,
-    axes = axes,
-    col.var = "contrib", # Color by contributions to the PC
-    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-    repel = TRUE     # Avoid text overlapping
-  )
-})
-
-temp_plot <- plot_grid(plotlist = pca_plot)
-plot_grid(temp_plot, eig_plot)
-```
-
-### Look at some network temporal series
-
-Let's look at network that have particular network properties.
-
-```{r}
-myload(network_analysis, dir = mypath("data", "species"))
-myload(op_analysis, metaweb_analysis, dir = data_common)
-meta <- metaweb_analysis; rm(metaweb_analysis)
-
-net <- network_analysis %>%
-  dplyr::select(opcod, network) %>%
-  unnest() %>%
-  left_join(., dplyr::select(op_analysis, opcod, station, date)) 
-```
-
-```{r}
-station_high_low_modularity <- temporal_network_metrics %>%
-  arrange(desc(modularity_med)) %>%
-  slice(c(1, n())) %>%
-  select(station) %>%
-  unlist
-names(station_high_low_modularity) <- c("high", "low") 
-```
-
-```{r tmp-net-h-mod, fig.cap = "Station with the highest modularity (median)."}
-# High modularity
-net_ex <- filter(net, station == station_high_low_modularity["high"])
-
-my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
-  = network_analysis)
-```
-```{r tmp-net-l-mod, fig.cap = "Station with the lowest modularity (median)."}
-# Low modularity
-net_ex <- filter(net, station == station_high_low_modularity["low"])
-my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
-  = network_analysis)
-```
-
-```{r}
-station_high_low_nestedness <- temporal_network_metrics %>%
-  arrange(desc(nestedness_med)) %>%
-  slice(c(1, n())) %>%
-  select(station) %>%
-  unlist
-names(station_high_low_nestedness) <- c("high", "low") 
-```
-```{r tmp-net-h-nest, fig.cap = "Station with the highest nestedness (median)."}
-# high nestedness
-net_ex <- filter(net, station == station_high_low_nestedness["high"])
-my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
-  = network_analysis)
-```
-
-```{r tmp-net-l-nest, fig.cap = "Station with the lowest nestedness (median)."}
-# low nestedness
-net_ex <- filter(net, station == station_high_low_nestedness["low"])
-my_crap_temporal_network(net = net_ex, metaweb = meta$metaweb, network_data
-  = network_analysis)
-```
-
-## Productivity
-
-## Stability of biomass
 
@@
   labs(y = "Biomass (g)", x = "Date")
+```
+
+```{r}
+myload(network_analysis, dir = mypath("data", "classes"))
+test <- select(network_analysis, opcod, composition) %>%
+  unnest(composition)
+test2 <- get_sync_cv_mat(com_analysis = test, op_analysis = op_analysis)
+
+# TODO: Plot for the five stations the most and the less stable:
+plot_dyn_sp_biomass(sync = test2, station = 122, .log = TRUE)
+plot_dyn_sp_biomass(sync = test2, station = 21877, .log = TRUE)
+```
+
+```{r}
+high_div_station <- temporal_community_metrics %>%
+  arrange(desc(richness_med)) %>%
+  slice(1: 5) %>%
+  select(station) %>%
+  unlist
+```
+
+```{r tmp-richest, fig.dim = c(10, 7), fig.cap = "The five highest rich community."}
+label_stab <- filter(temporal_community_metrics,
+  station %in% high_div_station) %>%
+mutate(
+  x_pos = ymd_hms("2005-01-01T15:00:00"),
+  x_pos = as.Date(x_pos),
+  y_pos = 50000,
+  text = paste0("Stability: ", round(biomass_stab,2)),
+)
+ggplot(filter(community_metrics, station %in% high_div_station),
+  aes(y = biomass, x = date)) +
+  geom_line() +
+  geom_point() +
+  geom_text(data = label_stab, aes(x = x_pos, y = y_pos, label =
+      text), size = 6) +
+  facet_wrap( ~ station) + 
+  labs(y = "Biomass (g)", x = "Date")
+```
+
+```{r}
+myload(network_analysis, network_metrics, dir = dest_dir)
+high_div_troph_group <- network_metrics %>%
+  select(opcod, troph_group) %>%
+  unnest() %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  left_join(select(op_analysis, opcod, station, date)) %>%
+  filter(station %in% high_div_station)
+```
+
+```{r, fig.dim = c(10, 7)}
+ggplot(high_div_troph_group,
+  aes(y = nbnode, x = date, color = troph_group)) +
+  geom_line() +
+  geom_point() +
+  geom_text(data = label_stab,
+    x = ymd_hms("2015-01-01T15:00:00"),
+    y = 3, aes(label =
+      text), size = 6, inherit.aes = FALSE) +
+  facet_wrap( ~ station) + 
+  labs(title = "The five richest station",
+  y = "Fish species richness", x = "Date")
+```
+
+```{r}
+highest_div_grp_3_station <- temporal_network_metrics_classes %>%
+  select(station, troph_group) %>%
+  unnest(troph_group) %>%
+  filter(troph_group == 3) %>%
+  arrange(desc(richness_avg)) %>%
+  slice(1:12) %>%
+  select(station) %>%
+  unlist()
+high_div_troph_group_3 <- network_metrics %>%
+  select(opcod, troph_group) %>%
+  unnest() %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  left_join(select(op_analysis, opcod, station, date)) %>%
+  filter(station %in% highest_div_grp_3_station)
+```
+
+```{r, fig.dim = c(10, 7)}
+ggplot(high_div_troph_group_3,
+  aes(y = biomass, x = date, color = troph_group)) +
+  geom_line() +
+  geom_point() +
+  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
+    x = ymd_hms("2015-01-01T15:00:00"),
+    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
+    size = 6, inherit.aes = FALSE) +
+  facet_wrap( ~ station) + 
+  labs(title = "The twelve richest station of superior predator",
+  y = "Fish species richness", x = "Date")
 ```
@@
 ```{r stab-comp, fig.cap = "Link between biomass stability by trophic group and total species richness (median)"}
-myload(temporal_network_metrics, dir = mypath("data", "classes"))
-net_troph_group <- temporal_network_metrics %>% 
+net_troph_group <- temporal_network_metrics_classes %>% 
   unnest(troph_group) %>%
@@
 Furthermore, we see that high trophic level compartment had a highest stability
-than the medium compartment. In the same vein, the latter pattern is confirmed when looking at the richness by compartment instead of the total richness (Figure \@ref(fig:stab-comp2)).
+than the medium compartment. In the same vein, the latter pattern is confirmed
+when looking at the richness by compartment instead of the total richness
+(Figure \@ref(fig:stab-comp2)).
 
-```{r stab-comp2, fig.dim = c(10, 7), fig.cap = "Link between biomass stability and species richness by trophic group (median)"}
-net_troph_group <- temporal_network_metrics %>% 
+```{r stab-comp2, fig.dim = c(10, 7), fig.cap = "Link between biomass stability and species richness by trophic group (median). (Classes network)"}
+net_troph_group <- temporal_network_metrics_classes %>% 
   select(station, troph_group) %>%
@@
 the high compartment and we observed the reverse for the high trophic
-compartment.
+compartment. It indicates that a trophic compartment is more stable when their
+relative biomass increases.
 
@@
 
-```{r stab-comp-ratio, fig.cap = "Biomass stability and ratio of biomass and species number (top and bottom panel resp.) in the high trophic level"}
+```{r stab-comp-ratio, fig.cap = "Biomass stability and ratio of biomass and species number (top and bottom panel resp.) in the high trophic level (classes network) for the medium and high trophic group (resp.
+left and right panels)."}
 ratio_sp <- net_troph_group %>%
@@
 
-net_troph_group <- temporal_network_metrics %>%
+net_troph_group <- temporal_network_metrics_classes %>%
   left_join(ratio_sp, by = "station") %>%
@@
 ```
-
-## Pressure
-
-## SEM
-
-### All
-
-### By basin

### 2019-11-12 R/plot_methods.R

@@ -92,7 +92,8 @@ net_list %<>%
 #Node position:
 node <- net_list$network %>% unlist(., use.names = FALSE) %>% unique
 try(
-test <- graph_from_adjacency_matrix(metaweb) %>% as_data_frame %>%
+test <- graph_from_adjacency_matrix(metaweb) %>% 
+  igraph::as_data_frame(.) %>%
   mutate_all(list(~str_extract_all(., "[a-zA-Z]+", simplify = TRUE))) %>%
   distinct(from, to)
 )
@@ -365,6 +366,44 @@ xylabs <- function (...) {
     )
 }
 
+#' Plot dynamic of biomass by station
+#'
+#' @param sync data.frame e.g. synchrony dataset, output from get_sync_cv_mat()
+#' @param station id of station
+#' @param .log logical transform biomass in log (e.g. log10())
+plot_dyn_sp_biomass <- function (sync = NULL, station = NULL, .log = FALSE) {
+
+  sync <- sync[sync$station == station, ] 
+
+  .data <- sync$data[[1]]
+
+  main_title <- paste0("Stab = ", round(1/(sync$cv_com), 2),", ", "Sync = ",
+    round(sync$synchrony, 2),", ", "CVsp = ", round(sync$cv_sp, 2))
+  
+  p <- .data %>%
+    mutate(label = if_else(date == max(date), as.character(species), NA_character_)) %>%
+  ggplot(aes(x = date, y = biomass, colour = species)) + 
+  geom_line(aes(linetype = as.factor(troph_group))) + 
+  labs(y = "Biomass (g)", x = "Sampling date",
+  title = main_title, subtitle = paste0("Station: ", station)) +
+  ggrepel::geom_label_repel(aes(label = label),
+                  nudge_x = 1,
+                  na.rm = TRUE)
+
+  #p <- ggplot(.data,
+    #aes(x = date, y = biomass, color = species)) +
+    #geom_line(aes(linetype = as.factor(troph_group))) +
+    #labs(y = "Biomass (g)", x = "Sampling date",
+      #title = main_title, subtitle = paste0("Station: ", station)
+    #)
+
+    if (.log) {
+      p <- p + scale_y_log10() 
+    }
+
+  return(p)
+}
+
 ###############
 #  Labellers  #
 ###############
@@ -374,11 +413,15 @@ mylabel <- function() {
     connectance = "Connectance",
     connectance_corrected_med = "Median connectance",
[…]

### 2019-11-13 report/02-methods.Rmd
Update report

@@
 node <- net_list$network %>% unlist(., use.names = FALSE) %>% unique
-test <- graph_from_adjacency_matrix(meta$metaweb) %>% as_data_frame %>%
+test <- graph_from_adjacency_matrix(meta$metaweb) %>%
+  igraph::as_data_frame(.) %>%
   mutate_all(list(~str_extract_all(., "[a-zA-Z]+", simplify = TRUE))) %>%
@@
 
+```{r}
+myload(temporal_station_desc, temporal_press_polluants, dir = data_common)
+myload(hab_analysis, geo_station, dir = data_common)
+
+habitat <- hab_analysis %>%
+  mutate_all(list(as.factor)) %>%
+  select(-opcod, -station, -aqua_vg)
+
+lvl <- c("null", "weak", "medium", "high")
+lvl_sinuosite <- c("straight", "sinuous", "very_sinuous", "meandering")
+lvl_shade <- c("clear", "quite_clear", "quite_covered", "covered")
+
+habitat_station <- hab_analysis %>%
+  select(-opcod, -aqua_vg, - shade, - sinuosite) %>%
+  mutate_if(is.character, list(~factor(., levels = lvl, ordered = TRUE))) %>%
+  left_join(select(hab_analysis, station, shade, sinuosite)) %>%
+  mutate(
+    shade = factor(shade, levels = lvl_shade, ordered = TRUE),
+    sinuosite = factor(sinuosite, levels = lvl_sinuosite, ordered = TRUE)) %>%
+  group_by(station) %>%
+  summarise_all(list(med = ~median(as.numeric(.), na.rm = TRUE))) %>%
+  left_join(select(temporal_station_desc, station, width_river_mean, avg_depth_station_mean))
+
+# Add alt, lat, etc...
+habitat_station %<>% 
+  left_join(geo_station, by = "station") %>%
+  select(-region_csp)
+# Add temp and flow
+flow_temp <- temporal_press_polluants %>%
+  filter(category %in% c("flow", "temperature", "DBO", "herbicides",
+      "fungicides", "insecticides", "nitrates", "phosphore")) %>%
+  rename(station = id) %>%
+  select(station, category, press_med) %>%
+  spread(category, press_med)
+
+habitat_station %<>%
+  left_join(flow_temp, by = "station")
+```
+
+```{r pca-hab, fig.dim = c(10, 7), fig.cap = "PCA over habitat description"}
+library(ade4)
+library(factoextra)
+pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_station), -station)), scannf = FALSE, nf = 2, center = TRUE, scale = TRUE)
+
+eig_plot <- fviz_eig(pca_hab)
+pca_plot <- fviz_pca_var(pca_hab,
+    axes = c(1, 2),
+    col.var = "contrib", # Color by contributions to the PC
+    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+    repel = TRUE     # Avoid text overlapping
+  )
+
+ggdraw(pca_plot) + 
+  draw_plot(eig_plot, x = .7, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
+```
+
+The PCA (Fig. \@ref(fig:pca-hab)) showed unsurprisingly that order of strahler, the
+depth, width of the river and distance to source and avg flow are closely
+linked. Altitude, slope and the amount of rocky shelter are also closely linked.
+Station of larger latitude had also higher DBO and phosphorus, higher annual
+mean temperature and more vegetation.  The first axis of the PCA (ordinate)
+discriminated station located far from the source (which are large, deep, with a
+big annual flow and high strahler order) from the shady station, which are
+sinuous, with a variety of habitat such as under bank and logjam.
+The second axis (abscissa) discriminated station in altitude with high slope,
+composed of rocky habitat from the ones that had higher average annual
+temperature located in the south, with more enrichment (DBO, nitrates,
+phosphorus) and that are more vegetated.
+
 ### Pressure
+
+#### Press category
+
+```{r press-units, fig.cap = "All the parameters collected together with their units"}
+# Put units to present all the parameters
+myload(polluant_units, dir = mypath("data-raw", "polluants", "naiades_data"))
+kable(polluant_units) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "400px")
+```
+
+```{r press-cat, fig.cap = "Molecules of pressure by category together with their toxicity if relevant or available"}
+myload(press_cat, dir = mypath("data-raw", "polluants"))
+kable(arrange(press_cat, category)) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "400px")
+```
+
+#### Press trough time
+
+```{r press-time, fig.cap = "Average press category over the station through time. The pesticides are expressed in Toxic Unit (TU)."}
+myload(press_metrics, dir = mypath("data"))
+ggplot(press_metrics, aes(y = press, x = year)) +
+  stat_summary(fun.y = "mean", geom = "line") +
+  stat_summary(geom="ribbon", fun.data=mean_cl_normal, colour=NA,alpha=0.1)+
+  facet_wrap(~category, scales = "free_y")
+```
+
+Most of the pressure decreased through time expect notably the nitrates and the
+temperature (Fig. \@ref(fig:press-time)). **Be careful, there are certainly a
+biais in temperature increase because the number of station that have been
+sampled. It would be nice to look at the tendency by station.**
 

### 2019-11-13 report/03-results.Rmd
Update report

@@
 # Get network metrics
+myload(temporal_network_metrics, dir = mypath("data", "classes"))
+temporal_network_metrics_classes <- temporal_network_metrics
 myload(temporal_network_metrics, dir = dest_dir)
@@
 
-temp_plot <- plot_grid(plotlist = pca_plot)
-plot_grid(temp_plot, eig_plot)
+plot_grid(eig_plot, pca_plot[[1]], pca_plot[[2]], pca_plot[[3]], labels =
+  "AUTO")
 ```
@@
 ```
-
-## Productivity
-
-## Stability of biomass
-
-### Some temporal series of biomass
-
-```{r}
-myload(community_metrics, dir = data_common)
-community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
-station_high_low_stab <- temporal_community_metrics %>%
-  arrange(desc(biomass_stab)) %>%
-  slice(c(1:5, (n() - 4):(n() - 0))) %>%
-  select(station) %>%
-  unlist
-names(station_high_low_stab) <- rep(c("high", "low"), each = 5) 
-```
-
-```{r tmp-stab, fig.dim = c(10, 7), fig.cap = "The five lowest and highest biomass stability"}
-temporal_biomass <- community_metrics %>%
-  filter(station %in% station_high_low_stab) %>%
-  mutate(stab_status = ifelse(
-      station %in% station_high_low_stab[names(station_high_low_stab) == "low"],
-      "low", "high")) %>%
-  group_by(stab_status, station) %>%
-  nest() %>%
-  group_by(stab_status) %>%
-  mutate(id_stab = seq_along(station)) %>%
-  unnest()
-ggplot(temporal_biomass, aes(y = biomass, x = date)) +
-  geom_line() +
-  geom_point() +
-  facet_grid(id_stab ~ stab_status, scales = "free_y") +
-  labs(y = "Biomass (g)", x = "Date")
-```
-
-### Map stability
-
-```{r}
-myload(station_analysis, region_polygon, dir = data_common)
-stab <- temporal_community_metrics %>% 
-  select(station, biomass_stab)
-station_stab <- left_join(station_analysis, rename(stab, id = station)) %>%
-  filter(!is.na(biomass_stab))
-ggplot(data = region_polygon) +
-    geom_sf() +
-    geom_sf(data = station_stab, aes(color = log(biomass_stab)), size = 4) +
-    scale_color_gradient(low = "red", high = "green")
-```
-
-### Link biomass stability with community structure
-
-```{r stab-div-mult, fig.dim = c(10, 7), fig.cap = "Link between the stability of biomass and diversity"}
-biomass_com <- temporal_community_metrics %>%
-  left_join(select(synchrony, station, synchrony, cv_sp)) %>%
-  select(biomass_stab, synchrony, cv_sp, richness_cv, richness_med, betadiv) %>%
-  gather(diversity, div_value, richness_med, richness_cv, betadiv) %>%
-  gather(stability, stab_value, biomass_stab, synchrony, cv_sp)
-
-formula <- y ~ x #needed for stat_poly_eq
-qplot(div_value, stab_value, data =  biomass_com, geom = "point") +
-  facet_grid(stability ~ diversity, labeller = mylabel(), scales = "free") +
-  geom_smooth(method = 'lm') +
-  stat_poly_eq(
-    formula = formula,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  labs(x = "Diversity", y = "Stability component")
-```
-
-```{r stab-net, fig.cap = "Link between biomass stability and network structure (median)"}
-# plot
-avg_network <- temporal_network_metrics %>%
-  select_at(vars(dplyr::matches("med|station")))
-biomass_stab_station <- temporal_community_metrics %>%
-  select(station, biomass_stab)
-stab_biomass_net_avg <- left_join(avg_network, biomass_stab_station) %>%
-  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
-  mutate(metrics = str_replace(metrics, "_med", "")) %>%
-  filter(metrics != "nbnode")
-
-# TODO: think about not facetting (list of plots ?)
-# Facet label:
-formula <- y ~ x #needed for stat_poly_eq
-p <- ggplot(stab_biomass_net_avg, aes(y = biomass_stab, x = values)) +
-  geom_point() +
-  facet_wrap(~ metrics, labeller = mylabel(), scales = "free_x") +
-  geom_smooth(method = 'lm') +
-  stat_poly_eq(
-    formula = formula,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  labs(
-    x = "Median of the network indices",
-    y = "Biomass stability"
-  )
-p
-```
-
-```{r stab-comp, fig.cap = "Link between biomass stability by trophic group and total species richness (median)"}
-myload(temporal_network_metrics, dir = mypath("data", "classes"))
-net_troph_group <- temporal_network_metrics %>% 
-  unnest(troph_group) %>%
-  mutate(troph_group = as.factor(troph_group))
-net_troph_group %<>%
-  select_at(vars(dplyr::matches("_med|stab|station|troph_group"))) %>%
-  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
-  mutate(metrics = str_replace(metrics, "_med", ""))
-p <- ggplot(net_troph_group, aes(y = biomass_stab, x = values, color = troph_group)) +
-  geom_point() +
-  ggplot2::scale_fill_manual(
-    labels = troph_group_labeller(),
-    values = c("blue", "green", "red"),
-    name = "Trophic level"
-    ) +
-  facet_wrap(~metrics, labeller = mylabel(), scales = "free_x") +
-  geom_smooth(method = 'lm')+
-  stat_poly_eq(
-    formula = formula,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  xylabs(
-    x = "network_med",
-    y = "biomass_stab"
-  )
-p
-```
-
-The Figure \@ref(fig:stab-comp) showed that medium trophic level part of the
-network had a positive stability-diversity relationship with while high
-trophic level had a negative one.  
-Furthermore, we see that high trophic level compartment had a highest stability
-than the medium compartment. In the same vein, the latter pattern is confirmed when looking at the richness by compartment instead of the total richness (Figure \@ref(fig:stab-comp2)).
-
-```{r stab-comp2, fig.dim = c(10, 7), fig.cap = "Link between biomass stability and species richness by trophic group (median)"}
-net_troph_group <- temporal_network_metrics %>% 
-  select(station, troph_group) %>%
-  unnest() %>%
-  filter(!is.na(troph_group)) %>%
-  mutate(troph_group = as.factor(troph_group))
-plot_stab_richness_troph_group <-
-  ggplot(net_troph_group, aes(y = log(biomass_stab), x = richness_avg)) +
-  geom_point() +
-  facet_grid(cols = vars(troph_group)) +
-  geom_smooth(method = 'lm')+
-  stat_poly_eq(
-    formula = formula,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  xylabs(
-    x = "richness_avg",
-    y = "biomass_stab"
-  )
-plot_stab_richness_troph_group
-```
-
-One hypothesis to explain this opposite pattern might be a disequilibrium
-between the two compartment. We can imagine that each compartment can
-destabilize each other according to the part of the total biomass of total
-species richness that there are in each of them. The figure
-\@ref(fig:stab-comp-ratio) showed that the biomass stability of the medium
-compartment decreased with the increase of biomass and species number ratio in
-the high compartment and we observed the reverse for the high trophic
-compartment.
-
-We are looking forward to fully understand why we observed this inverse
-relationship.
-
-```{r stab-comp-ratio, fig.cap = "Biomass stability and ratio of biomass and species number (top and bottom panel resp.) in the high trophic level"}
-ratio_sp <- net_troph_group %>%
-  select(station, troph_group, richness_avg) %>%
-  spread(troph_group, richness_avg) %>%
-  mutate(sp_h_m = `3` / (`3` + `2`)) %>%
-  select(station, sp_h_m)
-
-ratio_bm <- net_troph_group %>%
-  select(station, troph_group, biomass_avg) %>%
-  spread(troph_group, biomass_avg) %>%
-  mutate(bm_h_m = `3` / (`3` + `2`)) %>%
-  select(station, bm_h_m)
-
-net_troph_group <- temporal_network_metrics %>%
-  left_join(ratio_sp, by = "station") %>%
-  left_join(ratio_bm, by = "station") %>%
-  select(station, troph_group, sp_h_m, bm_h_m) %>%
-  unnest() %>%
-  filter(!is.na(troph_group), troph_group != 1) %>%
-  mutate(troph_group = as.factor(troph_group)) %>%
-  gather(ratio_troph, value, sp_h_m, bm_h_m)
-
-plot_stab_richness_troph_group <-
-  ggplot(net_troph_group, aes(y = log(biomass_stab), x = value)) +
-  geom_point() +
-  facet_grid(cols = vars(troph_group), rows = vars(ratio_troph), labeller =
-    troph_group_labeller()) +
-  geom_smooth(method = 'lm')+
-  stat_poly_eq(
-    formula = formula,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  xylabs(
-    y = "biomass_stab"
-  ) + 
-    xlab("Ratio of biomass and species nb in high troph compartment compare to total")
-plot_stab_richness_troph_group
-```
-
-## Pressure
-
-## SEM
-
-### All
-
-### By basin

### 2019-11-13 report/04-productivity.Rmd
Update report

## Productivity

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)
```

```{r prod-dist, fig.cap = "Median community biomass by station"}
biomass_prod_station <- temporal_community_metrics %>%
  select(station, biomass_med, richness_med) %>%
  rename(biomass = biomass_med)

plot_biomass_dist <- ggplot(biomass_prod_station, aes(x = biomass)) +
  geom_histogram() +
  labs(
    x = "Median of biomass (g)",
    y = "# of stations"
  )
plot_biomass_dist
```

There is no bistability in biomass distribution.

```{r prod-net, fig.cap = "Median biomass versus their median network metrics by station."}
avg_network <- temporal_network_metrics %>%
  select_at(vars(dplyr::matches("med|station")))
#colnames(temporal_network_metrics)
biomass_prod_station <- temporal_community_metrics %>%
  select(station, biomass_med, richness_med) %>%
  rename(biomass = biomass_med)
prod_biomass_net_avg <- left_join(avg_network, biomass_prod_station) %>%
  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
  mutate(metrics = str_replace(metrics, "_med", "")) %>%
  filter(metrics != "nbnode")

net_troph_group <- temporal_network_metrics_classes %>% 
  select(station, troph_group) %>%
  unnest() %>%
  filter(!is.na(troph_group)) %>%
  mutate(troph_group = as.factor(troph_group))
# TODO: think about not facetting (list of plots ?)
# Facet label:
formula <- y ~ x #needed for stat_poly_eq
plot_stab_biomass_net_avg <- ggplot(prod_biomass_net_avg, aes(y = biomass, x = values)) +
  geom_point() +
  facet_wrap(~metrics, labeller = mylabel(), scales = "free_x") +
  geom_smooth(method = 'lm') +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  labs(
    x = "Median of the network indices",
    y = "Average Biomass"
  )
plot_stab_biomass_net_avg
```

### By trophic level

```{r, fig.cap="Biomass production and stability by trophic level", fig.dim = c(10, 7)}
plot_prod_richness_troph_group <-
  ggplot(net_troph_group, aes(y = biomass_avg, x = richness_avg)) +
  geom_point() +
  facet_grid(cols = vars(troph_group)) +
  geom_smooth(method = 'lm')+
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  xylabs(
    x = "richness_avg",
    y = "biomass_avg"
  )
plot_prod_richness_troph_group
```

### 2019-11-13 report/05-stability.Rmd
Update report

@@
 ```{r}
-myload(temporal_network_metrics, dir = mypath("data", "cl~/Documents/post-these/mnhn/fishcom/report/index.Rmdasses"))
+myload(temporal_network_metrics, dir = mypath("data", "classes"))
 temporal_network_metrics_classes <- temporal_network_metrics
@@
 ### Some temporal series of biomass
+
+#### Total biomass
 
@@
 
+```{r more-stab-troph, fig.dim = c(10, 21), fig.cap = "The four station with the highest biomass stability. Dashed and solid lines represent respectively trophic species in the group 2 and 3."}
+
+myload(network_analysis, dir = mypath("data", "classes"))
+myload(trophic_level, trophic_class, dir = mypath("data"))
+source(mypath("R", "synchrony.R"))
+source(mypath("R", "local_network_build.R"))
+# Get biomass by sp node:
+net_sp_troph <- select(network_analysis, opcod, composition) %>%
+  unnest(composition)
+# Get synchrony and cv sp:
+sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis) %>%
+  arrange(cv_com)
+# Get trophic lvl by node
+trophic_level %<>%
+  rename(species = sp_class) %>%
+  mutate( troph_group = get_size_class(trophic_level, NULL, troph_level,
+      trophic_class))
+
+plot_stab <- purrr::map(station_high_low_stab, function (x) {
+  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
+  p + theme(legend.position="none") 
+})
+plot_grid(plotlist = plot_stab, ncol = 2)
+```
+
+```{r less-stab-troph, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
+plot_grid(plotlist = plot_stab[7:8], ncol = 2)
+```
+
+```{r mid-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium biomass stability. See caption of Figure for details."}
+# Middle station 
+plot_stab <- purrr::map(sync_sp_troph$station[209:212], function (x) {
+  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
+  p + theme(legend.position="none") 
+})
+plot_grid(plotlist = plot_stab[1:4], ncol = 2)
+```
+
+```{r 75-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
+# Third quater
+plot_stab <- purrr::map(sync_sp_troph$station[300:304], function (x) {
+  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
+  p + theme(legend.position="none") 
+})
+plot_grid(plotlist = plot_stab[1:4], ncol = 2)
+```
+
+```{r 25-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
+# Third quater
+plot_stab <- purrr::map(sync_sp_troph$station[104:107], function (x) {
+  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
+  p + theme(legend.position="none") 
+})
+plot_grid(plotlist = plot_stab[1:10], ncol = 2)
+```
+
+### CV sp
+
+```{r abun-sp, fig.cap = "Species most abundant by trophic group."}
+# Sp the most abundant by group
+bm_sp_troph_grp <- net_sp_troph %>%
+  filter(!is.na(troph_group) & troph_group != 1) %>%
+  group_by(troph_group, sp_class) %>%
+  summarise(biomass = mean(biomass)) %>%
+  arrange(desc(biomass)) %>%
+  slice(1:20)
+
+p_bm <- map(c(2, 3), .f = function(x) {
+  mylim <- sapply(c(min, max),
+    FUN = function(x) x(bm_sp_troph_grp$biomass))
+
+  .data <- bm_sp_troph_grp %>%
+    filter(troph_group == x)
+  if (x == 2) {
+    tmp_title <- paste("Medium trophic group (2)")
+  } else {
+    tmp_title <- paste("High trophic group (3)")
+  }
+
+  ggplot(data = .data, aes(x = sp_class, y = biomass)) +
+    geom_point() +
+    labs(x = "Trophic species", y = "Biomass (g)", title = tmp_title) +
+    ylim(mylim[1], mylim[2])
+
+})
+plot_grid(plotlist = p_bm, ncol = 2)
+```
+
 ```{r}
-myload(network_analysis, dir = mypath("data", "classes"))
-test <- select(network_analysis, opcod, composition) %>%
-  unnest(composition)
-test2 <- get_sync_cv_mat(com_analysis = test, op_analysis = op_analysis)
+# I need:
+# - by species:
+#   - CV
+#   - Biomass 
+# - by Trophic group:
+#   - Species richness 
+#   - CV
+#   - biomass
 
-# TODO: Plot for the five stations the most and the less stable:
-plot_dyn_sp_biomass(sync = test2, station = 122, .log = TRUE)
-plot_dyn_sp_biomass(sync = test2, station = 21877, .log = TRUE)
+# Species
+
+## Variance by sp and station:
+var_sp <- sync_sp_troph %>%
+  select(station, var_sp) %>%
+  mutate(var_sp = map(var_sp, ~enframe(.x))) %>%
+  unnest(var_sp) %>%
+  rename(species = name, var_sp = value)
+## Average biomass by sp and station:
+avg_sp <- sync_sp_troph %>%
+  select(station, avg_sp) %>%
+  mutate(avg_sp = map(avg_sp, ~enframe(.x))) %>%
+  unnest(avg_sp) %>%
+  rename(species = name, avg_sp = value)
+## CV and biomass by sp and station  
+cv_bm_sp <- left_join(avg_sp, var_sp, by = c("station", "species")) %>%
+  mutate(cv = sqrt(var_sp) / avg_sp, var_sp = NULL) %>%
+  rename(bm = avg_sp)
+
+# By trophic group:
+
+## CV, biomass and div (ALREADY DONE!)
+cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
+  select(station, troph_group) %>%
+  unnest(troph_group) %>%
+  filter(!is.na(troph_group) & troph_group != 1) %>%
+  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
+  mutate(troph_group = as.factor(troph_group))
+```
+
+#### CV sp VS CV group
+
+```{r}
+cv_sp_grp <- left_join(select(cv_bm_sp, -bm),
+  select(cv_bm_div_troph_grp, -biomass_stab), by = "station")
+
+ang9 <- cv_sp_grp %>%
+  filter(species == "ANG_9")
+
 ```
@@
   ggplot(net_troph_group, aes(y = log(biomass_stab), x = value)) +
-  geom_point() +
+  geom_point(aes(color = richness_avg)) +
   facet_grid(cols = vars(troph_group), rows = vars(ratio_troph), labeller =
@@
 plot_stab_richness_troph_group
+
 ```

### 2019-11-13 report/06-pressure.Rmd
Update report

## Pressure

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony,
temporal_press_polluants, press_metrics, op_analysis,
  dir = data_common)
```

```{r}
var_values <-  temporal_press_polluants %>%
  select(id, category, press) %>%
  spread(category, press) %>% 
  ungroup()

m <- cor(na.omit(select(var_values, -id)))

as.data.frame(round(m, 2)) %>%
  mutate_all(list(~cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r press-pca, fig.cap = "PCA of the different press category."}
res.pca <- dudi.pca(na.omit(select(ungroup(var_values), -id)),
  scannf = FALSE,   # Hide scree plot
  nf = 5            # Number of components kept in the results
)

eig_plot <- fviz_eig(res.pca)

pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
  fviz_pca_var(res.pca,
    axes = axes,
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
})

plot_grid(eig_plot, pca_plot[[1]], pca_plot[[2]], pca_plot[[3]], labels = "AUTO")
```

The PCA performed poorly (Fig. \@ref(fig:press-pca)A), the two first axis explaining
less than 40% of the variance. However, the first axis showed that the DBO,
phosphorus, nitrates, temperature and herbicides co-vary strongly (Fig.
\@ref(fig:press-pca)B), DBO and phosphorus being the more strongly related.
Interestingly, insecticides concentration was orthogonal with DBO (meaning no
correlation?) (Fig. \@ref(fig:press-pca)C and D). Fungicides and herbicides seems to
covary positively whereas insecticides seemed to covary negatively with the
formers (Fig. \@ref(fig:press-pca)B and C). We also found that the percentage of
dissolved was negatively linked with temperature and DBO (Fig.
\@ref(fig:press-pca)C and D), which makes sense.

### Effects on stability

```{r}
cat_to_rm <- c("mes", "disolved_oxygen",
  "flow", "industry")
temporal_press_polluants %<>%
  filter(!category %in% c(
      "matieres azotees", "other", "matieres phosphorees", "matieres
      organiques"))
```

```{r}
biomass_com <- temporal_community_metrics %>%
  select(station, biomass_stab, richness_med, betadiv)
biomass_com %<>%
  left_join(rename(temporal_press_polluants, station = id), by = "station")
biomass_com %<>% na.omit()

pca_press_data <- biomass_com %>%
  select(station, richness_med, category, press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, press)
```

```{r, fig.dim = c(4, 4)}
res.pca <- dudi.pca(na.omit(select(pca_press_data, -station)),
  scannf = FALSE,   # Hide scree plot
  nf = 5            # Number of components kept in the results
)

eig_plot <- fviz_eig(res.pca)
```

```{r pca-press2, fig.dim = c(10, 7), fig.cap = "PCA with the candidate pressure"}
pca_plot <- lapply(list(c(1,2), c(1, 3), c(1, 4), c(3, 2), c(4, 2), c(4, 3)), function (axes) {
  fviz_pca_var(res.pca,
    axes = axes,
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
})
plot_grid(eig_plot, pca_plot[[1]], pca_plot[[2]], pca_plot[[3]], pca_plot[[4]],
  pca_plot[[5]], labels = "AUTO")
```

## SEM

```{r}
mod <- lm(betadiv ~ log(richness_med), data = temporal_community_metrics)
temporal_community_metrics$betadiv_corrected <- resid(mod)
```

```{r}
biomass_com <- temporal_community_metrics %>%
  select(station, biomass_stab, richness_med, betadiv, simpson_med, pielou_med,
  betadiv_corrected)
biomass_com %<>%
  left_join(rename(temporal_press_polluants, station = id), by = "station")
biomass_com %<>% na.omit()
biomass_com %<>% 
  select(-cv_press, -press) %>%
  spread(category, press_med) %>%
  left_join(synchrony)
net_com <- temporal_network_metrics %>%
  select(station, connectance_corrected_med, modularity_corrected_med,
    mean_troph_level_corrected_med, w_trph_lvl_avg_med)

dsem <- biomass_com  %>%
  mutate(log_rich = log10(richness_med)) %>%
  left_join(net_com, by = "station") %>%
  na.omit()
```

### All

```{r}
library(lavaan)
options(width = 100)
lav_data <- dsem %>%
  mutate(log_cv_sp = log10(cv_sp),
    log_biomass_stab = log10(biomass_stab)
  )
lav_formula <- " 
  synchrony ~ log_rich + pielou_med + temperature + connectance_corrected_med + w_trph_lvl_avg_med + betadiv_corrected
  log_cv_sp ~ log_rich + pielou_med + temperature + connectance_corrected_med + w_trph_lvl_avg_med + betadiv_corrected
  log_biomass_stab ~ log_rich + pielou_med + connectance_corrected_med + w_trph_lvl_avg_med + betadiv_corrected
  log_rich ~ temperature + DBO + fungicides + herbicides + insecticides
  betadiv_corrected ~ temperature + DBO + fungicides + herbicides + insecticides
  connectance_corrected_med ~ temperature + DBO + fungicides + herbicides + insecticides
  pielou_med ~ temperature + DBO + fungicides + herbicides + insecticides
  w_trph_lvl_avg_med ~ temperature + DBO + fungicides + herbicides + insecticides
  DBO ~ nitrates + phosphore + fungicides + herbicides + insecticides
  "
lav_mod <- sem(lav_formula, lav_data)
summary(lav_mod, standardized = TRUE)
```

```{r, fig.dim = c(10, 7)}
ggsem <- function(fit, layout = "sugiyama") {

  # Extract standardized parameters
  params <- lavaan::standardizedSolution(fit)

  # Edge properties
  param_edges <- params %>% 
    filter(op %in% c("=~", "~", "~~"), lhs != rhs, pvalue < .05) %>%
    transmute(to = lhs,
              from = rhs,
              val = est.std,
              type = dplyr::case_when(
                op == "=~" ~ "loading",
                op == "~"  ~ "regression",
                op == "~~" ~ "correlation",
                TRUE ~ NA_character_))

  # Identify latent variables for nodes
  latent_nodes <- param_edges %>% 
    filter(type == "loading") %>% 
    distinct(to) %>% 
    transmute(metric = to, latent = TRUE)

  # Node properties
  param_nodes <- params %>% 
    filter(lhs == rhs) %>% 
    transmute(metric = lhs, e = est.std) %>% 
    left_join(latent_nodes) %>% 
    mutate(latent = if_else(is.na(latent), FALSE, latent))

  # Complete Graph Object
  param_graph <- tidygraph::tbl_graph(param_nodes, param_edges)

  # Plot
  ggraph(param_graph, layout = layout) +
    # Latent factor Nodes
    geom_node_point(aes(alpha = as.numeric(latent)),
                                     shape = 16, size = 5) +
    geom_node_point(aes(alpha = as.numeric(latent)),
                                     shape = 16, size = 4, color = "white") +
    # Observed Nodes
    geom_node_point(aes(alpha = as.numeric(!latent)),
                                     shape = 15, size = 5) +
    geom_node_point(aes(alpha = as.numeric(!latent)),
                                     shape = 15, size = 4, color = "white") +
    # Regression Paths (and text)
    geom_edge_link(aes(color = val, label = round(val, 2),
                       alpha = as.numeric(type == "regression")),
                   linetype = 1, angle_calc = "along", vjust = -.5,
                   arrow = arrow(20, unit(.3, "cm"), type = "closed")) +
    # Factor Loadings (no text)
    geom_edge_link(aes(color = val, alpha = as.numeric(type == "loading")),
                   linetype = 3, angle_calc = "along",
                   arrow = arrow(20, unit(.3, "cm"), ends = "first", type = "closed")) +
    # Correlation Paths (no text)
    geom_edge_link(aes(color = val, alpha = as.numeric(type == "correlation")),
                   linetype = 2, angle_calc = "along",
                   arrow = arrow(20, unit(.3, "cm"), type = "closed", ends = "both")) +
    # Node names
    geom_node_text(aes(label = metric),
                   nudge_y = .25, hjust = "inward") +
    # Node residual error
    geom_node_text(aes(label = sprintf("%.2f", e)),
                   nudge_y = -.1, size = 3) +
    # Scales and themes
    scale_alpha(guide = FALSE, range = c(0, 1)) +
    scale_edge_alpha(guide = FALSE, range = c(0, 1)) +
    scale_edge_colour_gradient2(guide = FALSE, low = "red", mid = "darkgray", high = "green") +
    scale_edge_linetype(guide = FALSE) +
    scale_size(guide = FALSE) +
    theme_graph()
}
ggsem(lav_mod)

```

### By basin

```{r}

myload(the_8_hydrologic_basin, station_analysis, dir = data_common)

station_analysis %<>%
  st_transform(crs = 2154)
the_8_hydrologic_basin %<>%
  mutate(NomDistric = ifelse(CdBassinDC == "B2", "SAMBRE", NomDistric))

station_basin <- st_intersects(station_analysis, the_8_hydrologic_basin)
station_analysis$basin <- purrr::map_chr(station_basin, function(x){
  if (length(x) == 0) {
   return(NA) 
  }
  the_8_hydrologic_basin[["NomDistric"]][x]
})
# Filter NA
station_analysis %<>%
  filter(!is.na(basin)) %>%
  mutate(station = id) %>%
  select(station, basin)
st_geometry(station_analysis) <- NULL

# How many station by basin:
nb_st_basin <- station_analysis %>%
  group_by(basin) %>%
  summarise(nobs = n())
```

```{r}
lav_data %<>%
  left_join(station_analysis, by = "station")

lav_data_test <- filter(lav_data, basin %in% nb_st_basin[nb_st_basin$nobs > 61, ]$basin)

# Since the group 1 and 3 are two small, I cut two basin 
unique(lav_data$basin)
lav_mod_basin <- sem(lav_formula, lav_data_test, group = "basin")
summary(lav_mod_basin, standardized = TRUE)
```

```{r, fig.dim = c(14, 10)}
lav_basin_list <- lav_data_test %>%
  group_by(basin) %>%
  nest() %>%
  mutate(lav_mod = map(data, function(.data){ sem(lav_formula, .data)}),
      plot_lav = map(lav_mod, function(lav){ ggsem(lav)})
      )
plot_grid(plotlist = lav_basin_list$plot_lav)
```

### Model with only community structure and stability

```{r, fig.dim = c(14, 10)}
lav_formula_str_stab <- " 
  synchrony ~ log_rich + pielou_med + connectance_corrected_med + w_trph_lvl_avg_med + betadiv_corrected
  log_cv_sp ~ log_rich + pielou_med + connectance_corrected_med + w_trph_lvl_avg_med + betadiv_corrected
  log_biomass_stab ~ log_rich + pielou_med + connectance_corrected_med + w_trph_lvl_avg_med + betadiv_corrected
  "

lav_basin_str_stab_list <- lav_data %>%
  group_by(basin) %>%
  nest() %>%
  mutate(lav_mod = map(data, function(.data){
      out <- tryCatch(
	{sem(lav_formula_str_stab, .data)},
	error = function(cond) {return(NA)},
	warning = function(cond) {return(NA)}
      )
      return(out)
		       }),
      plot_lav = map(lav_mod, function(lav){
      out <- tryCatch(
	{ggsem(lav)},
	error = function(cond) {return(NA)},
	warning = function(cond) {return(NA)}
      )
      return(out)
})
      )

lav_basin_str_stab_list %<>%
  mutate(class_plot = map_lgl(plot_lav, is.logical))%>%
  filter(!class_plot)
plot_grid(plotlist = lav_basin_str_stab_list$plot_lav)
```

### 2019-11-13 report/07-time_series.Rmd
Update report

##  Biomass temporal dynamics

```{r load dataset, include = FALSE}
library(jmotif)
myload(community_metrics, op_analysis, dir = mypath("data"))
community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
```

```{r}
ts_biomass  <- community_metrics %>%
  select(station, date, biomass) %>%
  mutate(station = as.character(station)) %>%
  group_by(station) %>%
  arrange(date) %>%
  nest()

ts_biomass %<>%
  mutate(
    zts = map(data, function(x) znorm(x$biomass, threshold = 0.01)),
    paa = map(zts, ~paa(., 3)),
    sax = map_chr(paa, ~series_to_string(., 3))
  )
```

```{r}
pattern_dist <- ts_biomass %>%
  group_by(sax) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
ggplot(ts_biomass, aes(x = sax)) +
  geom_histogram(stat = "count")

filter(pattern_dist, count > 10)
```

```{r}
test <- ts_biomass %>%
  filter(sax %in% c("cba", "bbb", "cab", "abc", "acb", "bca", "bac", "cbb")) %>%
  group_by(sax) %>%
  sample_n(10) %>%
  mutate(
    paa2 = map2(data, zts, function (x, zts) {
      cbind(x[,1], zts)
  }),
    id_sta = as.character(seq(1,n()))

  ) %>%
  unnest(paa2)

ggplot(test, aes(x = date, y = zts)) +
  geom_line(aes(color = id_sta)) +
  facet_wrap(~ sax)

```

```{r}
myload(polluant_units, dir = mypath("data-raw", "polluants", "naiades_data"))

myload(press_metrics, dir = mypath("data"))
press_year <- press_metrics %>%
  filter(category %in% c("fungicides", "herbicides", "insecticides", "DBO", "temperature"))

biomass <- community_metrics %>%
  mutate(
    year = lubridate::year(date),
    category = "biomass",
    press = biomass 
    ) %>%
  select(station, year, category, press)
press_biomass <- press_year %>%
  bind_rows(rename(biomass, id = station)) %>%
  na.omit()
```

```{r}
samp_station <- sample(unique(press_biomass$id), 10)
temp <- press_biomass %>%
  mutate(id = as.character(id)) %>%
  filter(id %in% samp_station)

ggplot(temp, aes(y = press, x = year)) +
  facet_wrap(~category, scales = "free_y") +
  geom_line(aes(color = id))

```

### 2019-11-13 report/before_chapter.R

@@ -10,7 +10,7 @@ knitr::opts_chunk$set(
   fig.show = "hold",
   echo = FALSE,
   message = FALSE,
-  warnings = FALSE
+  warning = FALSE
 )
 
 library(MASS)

### 2019-11-15 report/05-stability.Rmd
Add fine analysis of the CV

@@
 ```{r less-stab-troph, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
-plot_grid(plotlist = plot_stab[7:8], ncol = 2)
+plot_grid(plotlist = plot_stab[7:10], ncol = 2)
 ```
@@
 
-```{r 25-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
+```{r 25-stab-troph, fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
 # Third quater
@@
 
-```{r abun-sp, fig.cap = "Species most abundant by trophic group."}
+```{r abun-sp, fig.dim = c(10, 7), fig.cap = "Species most abundant by trophic group."}
 # Sp the most abundant by group
@@
   filter(!is.na(troph_group) & troph_group != 1) %>%
+  group_by(troph_group, sp_class, opcod) %>%
+  mutate(rel_biomass = biomass / sum(biomass)) %>%
   group_by(troph_group, sp_class) %>%
-  summarise(biomass = mean(biomass)) %>%
-  arrange(desc(biomass)) %>%
+  summarise(sum_rel_bm = sum(rel_biomass), biomass = mean(biomass)) %>%
+  arrange(desc(sum_rel_bm)) %>%
   slice(1:20)
@@
 
+#### Diversity is not all
+
+```{r}
+library(ade4)
+library(factoextra)
+myload(habitat_pressure, dir = mypath("report"))
+```
+
+```{r}
+div_troph_grp <- cv_bm_div_troph_grp %>%
+  select(station, troph_group, cv_st) %>%
+  spread(key = troph_group, cv_st) %>%
+  rename(mid_cv = `2`, high_cv = `3`)
+
+hab_press_div <- left_join(habitat_pressure,
+  temporal_community_metrics[, c("station", "richness_med", "biomass_avg","biomass_stab")],
+  by = "station") %>%
+left_join(div_troph_grp, by = "station")
+pca_hab <- dudi.pca(as.data.frame(select(na.omit(hab_press_div), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)
+
+eig_plot <- fviz_eig(pca_hab)
+pca_plot <- fviz_pca_var(pca_hab,
+    axes = c(1, 2),
+    col.var = "contrib", # Color by contributions to the PC
+    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+    repel = TRUE     # Avoid text overlapping
+  )
+
+ggdraw(pca_plot) + 
+  draw_plot(eig_plot, x = .9, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
+```
+
+```{r}
+m <- cor(as.matrix(select(na.omit(hab_press_div), -station)), method =
+  "spearman")
+corrplot::corrplot(m, order="hclust")
+```
+
+```{r, eval = FALSE}
+mod <- lm(high_cv ~ temperature + richness_med:temperature + DBO + lat + insecticides + herbicides + insecticides, hab_press_div)
+car::vif(mod)
+
+mod <- lm(mid_cv ~ richness_med + DBO + lat + temperature + insecticides + herbicides + insecticides, hab_press_div)
+car::vif(mod)
+```
+
+#### Assembly rules: richness and biomass distribution
+
+One missing part was the fact that we do not know the assembly rules of the
+trophic group.
+
+```{r}
+cv_bm_div_troph_grp %>%
+  ggplot(aes(y = cv_st, x = div_st)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group))
+```
+
+```{r}
+sync_com_troph <- net_sp_troph %>%
+    rename(species = sp_class) %>%
+    filter(troph_group != 1) %>%
+    mutate(troph_group = as.factor(troph_group)) %>%
+    group_by(troph_group) %>%
+    nest() %>%
+    mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
+    unnest(sync) %>%
+    mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
+    select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev) %>%
+    left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
+```
+
+```{r sd-avg-div}
+form <- y ~ x
+form2 <- y ~ Vmax * x / (Km + x)
+form3 <- y ~  a + exp(b * x) 
+fit <- stat_poly_eq(
+  formula = form2,
+  eq.with.lhs = "italic(hat(y))~`=`~",
+  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+  parse = TRUE)
+
+ymax <- max(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
+ymin <- min(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
+p_bm <- cv_bm_div_troph_grp %>%
+  ggplot(aes(y = bm_st, x = div_st)) +
+  geom_point() +
+  geom_smooth(method = 'nls', formula = form3,
+   method.args = list(start = c(a = 0, b = 3)), se = F) +
+  #fit +
+  facet_grid(cols = vars(troph_group)) +
+  #scale_y_log10(limits = c(ymin, ymax)) +
+  labs(y = "Average biomass (g).", x = "Species richness")
+
+p_sd <- sync_com_troph %>%
+  ggplot(aes(x = div_st, y = sdt.dev)) +
+  geom_point() +
+  geom_smooth(method = 'lm') +
+  fit +
+  facet_grid(cols = vars(troph_group)) +
+  scale_y_log10(limits = c(ymin, ymax)) +
+  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")
+
+plot_grid(p_sd, p_bm, ncol = 1)
+```
+It seems that the relationship between the standard deviation and the number of
+species saturates for 10 species in medium trophic group while it saturates at 7
+for the high trophic group (Figure \@ref(fig:sd-avg-div)).
+
+To get opposite stability-diversity relationships in the different trophic
+group, it supposes that for medium trophic group, the avg biomass increases
+faster than the biomass standard deviation with increasing species richness. And
+the reverse for the high trophic group, i.e. that the standard deviation
+increases faster than the average biomass.
+
+A question: What are the determinant of the relationship beween avg/standard
+deviation and the number of species?
+
+Part of the solution
+
+```{r}
+formula <- y ~ x #needed for stat_poly_eq
+sync_com_troph %>%
+  ggplot(aes(x = bm_st, y = sdt.dev)) +
+  geom_point() +
+  geom_smooth(method = 'lm') +
+  stat_poly_eq(
+    formula = formula,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  facet_grid(cols = vars(troph_group)) +
+  scale_y_log10() +
+  scale_x_log10() +
+  labs(y = "Standard deviation of biomass temporal data (g).", x = "Average
+      biomass (g)")
+```
+
+```{r}
+
+```
+
 #### CV sp VS CV group
 
-```{r}
+There was a positive relationship between the species CV of the most abundant
+species in the high trophic group and the CV of the same high trophic group
+(Figure \@ref(fig:cv-sp-grp3), right panel). Interestingly, this relationship
+is less clear (however clearly present for some species) for the most abundant
+species in the medium trophic group (Figure \@ref(fig:cv-sp-grp2), right panel).
+
+```{r cv-sp-grp3, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the CV of the different trophic groups"}
 cv_sp_grp <- left_join(select(cv_bm_sp, -bm),
@@
 
-ang9 <- cv_sp_grp %>%
-  filter(species == "ANG_9")
+sp_grp3 <- bm_sp_troph_grp %>%
+  filter(troph_group == 3) %>%
+  arrange(desc(biomass))
+
+cv_sp_grp %>%
+  filter(species %in% sp_grp3$sp_class[1:10]) %>%
+  ggplot(aes(x = cv_st, y = cv)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller())) +
+  labs(x = "CV of the trophic group", y = "CV of the species")
+```
+
+```{r cv-sp-grp2, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the CV of the different trophic groups"}
+sp_grp2 <- bm_sp_troph_grp %>%
+  filter(troph_group == 2) %>%
+  arrange(desc(biomass))
+
+cv_sp_grp %>%
+  filter(species %in% sp_grp2$sp_class[1:10]) %>%
+  ggplot(aes(x = cv_st, y = cv)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group), rows = vars(species), labeller =
+    labeller(troph_group = troph_group_labeller())) +
+  labs(x = "CV of the trophic group", y = "CV of the species")
+```
+
+#### CVsp versus Biomass by trophic group
+
+```{r cv-sp-bm-grp3, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the biomass of the different trophic groups"}
+cv_sp_grp %>%
+  filter(species %in% sp_grp3$sp_class[1:10]) %>%
+  ggplot(aes(x = bm_st, y = cv)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller()),
+    scales = "free_x") +
+  labs(x = "Biomass of the trophic group (g)", y = "CV of the species")
 
 ```
+
+```{r cv-sp-bm-grp2, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the biomass of the different trophic groups"}
+cv_sp_grp %>%
+  filter(species %in% sp_grp2$sp_class[1:10]) %>%
+  ggplot(aes(x = bm_st, y = cv)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller()),
+    scales = "free_x") +
+  labs(x = "Biomass of the trophic group (g)", y = "CV of the species")
+```
+
+#### CVsp versus diversity by trophic group
+
+```{r cv-sp-div-grp3, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the species richness in the different trophic groups."}
+cv_sp_grp %>%
+  filter(species %in% sp_grp3$sp_class[1:10]) %>%
+  ggplot(aes(x = div_st, y = cv)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller())) +
+  labs(x = "Species richness of the trophic group", y = "CV of the species")
+```
+
+```{r cv-sp-div-grp2, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the species richness in the different trophic groups."}
+cv_sp_grp %>%
+  filter(species %in% sp_grp2$sp_class[1:10]) %>%
+  ggplot(aes(x = div_st, y = cv)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller())) +
+  labs(x = "Species richness of the trophic group", y = "CV of the species")
+```
+
+#### Temporal dynamics in high diversity community
 
@@
   labs(title = "The twelve richest station of superior predator",
-  y = "Fish species richness", x = "Date")
+  y = "Biomass of trophic group (g)", x = "Date")
+```
+
+```{r}
+ggplot(high_div_troph_group_3,
+  aes(y = biomass, x = date, color = troph_group)) +
+  geom_line() +
+  geom_point() +
+  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
+    x = ymd_hms("2015-01-01T15:00:00"),
+    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
+    size = 6, inherit.aes = FALSE) +
+  facet_wrap( ~ station) + 
+  labs(title = "The twelve richest station of superior predator",
+  y = "Biomass of trophic group (g)", x = "Date")
 ```
@@
 
-```{r}
+```{r map-stab, fig.cap = "Repartition of average biomass and biomass stability (logged)."}
 myload(station_analysis, region_polygon, dir = data_common)
 stab <- temporal_community_metrics %>% 
-  select(station, biomass_stab)
+  select(station, biomass_stab, biomass_avg)
 station_stab <- left_join(station_analysis, rename(stab, id = station)) %>%
   filter(!is.na(biomass_stab))
+map_stab <- ggplot(data = region_polygon) +
+    geom_sf() +
+    geom_sf(data = station_stab, aes(color = log(biomass_stab)), size = 4) +
+    scale_color_gradient(low = "red", high = "green") +
+    labs(title = "Biomass stability")
+
+map_bm <- ggplot(data = region_polygon) +
+    geom_sf() +
+    geom_sf(data = station_stab, aes(color = log(biomass_avg)), size = 4) +
+    scale_color_gradient(low = "red", high = "green") +
+    labs(title = "Average biomass (g)")
+
+plot_grid(map_stab, map_bm, ncol = 2)
+```
+
+Biomass stability was lower in south-west of France (Figure
+\@ref{fig:map-stab}, left panel). Average fish biomass was lower in moutain
+region (Pyrénées, Alps, Massif Central; Figure \@ref{fig:map-stab}, right
+panel), generally close to the source.
+
+```{r map-st, fig.dim = c(7, 15), fig.cap = "Repartition of the average biomass, biomass stability and species diversity by trophic group, respectively medium and high for the left and right panel.
+All the metrics were logged."}
+tmp <- rename(cv_bm_div_troph_grp, id = station)
+station_troph_div <- left_join(station_analysis, tmp, by = "id")
+
+map_st_metrics <- purrr::map(c("bm_st", "div_st", "biomass_stab"), function (metric) {
+  station_troph_div[[metric]] <- log10(station_troph_div[[metric]])
   ggplot(data = region_polygon) +
     geom_sf() +
-    geom_sf(data = station_stab, aes(color = log(biomass_stab)), size = 4) +
+    geom_sf(data = station_troph_div, aes_(color = as.name(metric)), size = 4) +
+    facet_grid(cols = vars(troph_group)) +
     scale_color_gradient(low = "red", high = "green")
+
+  })
+plot_grid(plotlist = map_st_metrics, ncol = 1)
 ```
+
+The biomass in both trophic groups were lower in moutain area (Figure
+\@ref(map-st)), the same was true for species diversity. For stability, it is
+difficult to see a pattern.
 

### 2019-11-20 report/02-methods.Rmd
Compute species contribution to the CV, CV_sp and synchrony

@@
   left_join(flow_temp, by = "station")
+habitat_pressure <- habitat_station
+mysave(habitat_pressure, dir = mypath("report"), overwrite = TRUE)
 ```
@@
 
+### Stability
+
+#### Species contribution
+
+The species contribution to CV and synchrony have been computed, to identify
+which species are driving the relationship between CV and species richness.
+
+Species contribution to a metric can be computed as follow:
+
+$$
+C_k = CV_{-k} - CV
+$$
+
 ### Pressure

### 2019-11-20 report/05-stability.Rmd
Compute species contribution to the CV, CV_sp and synchrony

@@
 myload(temporal_network_metrics, dir = dest_dir)
-myload(temporal_community_metrics, synchrony, op_analysis, dir = data_common)
+myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
+myload(network_analysis, dir = mypath("data", "classes"))
+myload(trophic_level, trophic_class, dir = mypath("data"))
+source(mypath("R", "synchrony.R"))
+source(mypath("R", "local_network_build.R"))
+```
+```{r}
+temporal_network_metrics_classes %>%
+  select(station, troph_group) %>%
+  unnest(troph_group) %>%
+  filter(troph_group != 1) %>%
+  mutate(troph_group = as.factor(troph_group)) 
+%>%
+  select(station, troph_group, biomass_cv, richness_avg, nbnode_med) %>%
+  gather(richness_type, div, richness_avg, nbnode_med) %>%
+  ggplot(aes(x = div, y = biomass_cv, color = troph_group)) +
+  facet_grid(cols = vars(richness_type), scales = "free_x") +
+  geom_point() +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  ggplot2::scale_color_manual(
+    labels = troph_group_labeller(),
+    values = c("blue", "green", "red"),
+    name = "Trophic level"
+    )
+```
+
+The stability of biomass is determined by the standard deviation and the average
+biomass of the community.
+
+### Decompose stability
+
+One missing part was the fact that we do not know the assembly rules of the
+trophic group.
+
+```{r}
+cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
+  select(station, troph_group) %>%
+  unnest(troph_group) %>%
+  filter(!is.na(troph_group) & troph_group != 1) %>%
+  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
+  mutate(troph_group = as.factor(troph_group))
+
+cv_bm_div_troph_grp %>%
+  ggplot(aes(y = cv_st, x = div_st)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group))
+```
+
+```{r}
+sync_com_troph <- network_analysis %>%
+  select(opcod, composition) %>%
+  unnest(composition) %>%
+  rename(species = sp_class) %>%
+  filter(troph_group != 1) %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  group_by(troph_group) %>%
+  nest() %>%
+  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
+  unnest(sync) %>%
+  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
+  mutate(
+    contrib = purrr::pmap(
+      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
+      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
+    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
+    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
+      ) %>% 
+  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
+    troph_sp_nb_avg, troph_sp_nb_med) %>%
+  left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
+```
+
+```{r}
+sync_com_troph %>%
+  filter(troph_group != 1) %>%
+  select(station, troph_group, cv_com, troph_sp_nb_med) %>%
+  ggplot(aes(x = troph_sp_nb_med, y = 1/cv_com, color = troph_group)) +
+  geom_point() +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  ggplot2::scale_color_manual(
+    labels = troph_group_labeller(),
+    values = c("blue", "green", "red"),
+    name = "Trophic level"
+    )
+```
+
+```{r sd-avg-div}
+fit <- stat_poly_eq(
+  formula = y ~x,
+  eq.with.lhs = "italic(hat(y))~`=`~",
+  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+  parse = TRUE)
+
+ymax <- max(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
+ymin <- min(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
+p_bm <- cv_bm_div_troph_grp %>%
+  ggplot(aes(y = bm_st, x = div_st)) +
+  geom_point() +
+  geom_smooth(method = 'loess', se = F) +
+  #fit +
+  facet_grid(cols = vars(troph_group)) +
+  scale_y_log10(limits = c(ymin, ymax)) +
+  labs(y = "Average biomass (g).", x = "Species richness")
+
+p_sd <- sync_com_troph %>%
+  ggplot(aes(x = div_st, y = sdt.dev)) +
+  geom_point() +
+  geom_smooth(method = 'loess', se = FALSE) +
+  facet_grid(cols = vars(troph_group)) +
+  scale_y_log10(limits = c(ymin, ymax)) +
+  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")
+
+plot_grid(p_sd, p_bm, ncol = 1)
+```
+It seems that the relationship between the standard deviation and the number of
+species saturates for 10 species in medium trophic group while it saturates at 7
+for the high trophic group (Figure \@ref(fig:sd-avg-div)).
+
+To get opposite stability-diversity relationships in the different trophic
+group, it supposes that for medium trophic group, the avg biomass increases
+faster than the biomass standard deviation with increasing species richness. And
+the reverse for the high trophic group, i.e. that the standard deviation
+increases faster than the average biomass.
+
+A question: What are the determinant of the relationship beween avg/standard
+deviation and the number of species?
+
+Part of the solution
+
+```{r}
+formula <- y ~ x #needed for stat_poly_eq
+sync_com_troph %>%
+  ggplot(aes(x = bm_st, y = sdt.dev)) +
+  geom_point() +
+  geom_smooth(method = 'lm') +
+  stat_poly_eq(
+    formula = formula,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  facet_grid(cols = vars(troph_group)) +
+  scale_y_log10() +
+  scale_x_log10() +
+  labs(y = "Standard deviation of biomass temporal data (g).", x = "Average
+      biomass (g)")
+```
+
+```{r, fig.dim = c(7, 14)}
+sync_com_troph %>%
+  select(troph_group:cv_com, div_st) %>%
+  gather(comp, stab, synchrony:cv_com) %>%
+  ggplot(aes(x = div_st, y = stab)) +
+  geom_smooth(method = "loess", se = FALSE) +
+  labs(x = "Trophic species diversity", y = "Stability component") +
+  geom_point() +
+  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
+```
+
+```{r, fig.dim = c(10, 7)}
+synchrony %>%
+  left_join(select(temporal_community_metrics, station, richness_med), by =
+    "station") %>%
+  gather(comp, stab, synchrony:cv_com) %>%
+  ggplot(aes(x = richness_med, y = stab)) +
+  geom_smooth(method = "loess", se = FALSE) +
+  labs(x = "Species diversity", y = "Stability component") +
+  geom_point() +
+  facet_grid(rows = vars(comp), scales = "free_y")
+```
+
+#### Contribution
+
+```{r}
+sync_com_troph %>%
+  unnest(contrib) %>%
+  group_by(troph_group, species) %>%
+  summarise(
+    sum_cbt_cv_com = sum(abs(cbt_cv_com)),
+    sum_cbt_cv_sp = sum(abs(cbt_cv_sp)),
+    sum_cbt_sync = sum(abs(cbt_sync))
+    ) %>%
+  arrange(desc(sum_cbt_cv_com)) %>%
+  slice(1:10) %>%
+  gather(comp, contrib, sum_cbt_cv_com:sum_cbt_sync) %>%
+  ggplot(aes(y = contrib, x = species)) +
+  geom_point() +
+  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
+```
+
+```{r var-cbt, fig.dim = c(10, 7)}
+var_cbt <- sync_com_troph %>%
+  unnest(contrib) %>%
+  group_by(troph_group, station) %>%
+  summarise(
+    var_cbt_cv_com = var(cbt_cv_com),
+    var_cbt_cv_sp = var(cbt_cv_sp),
+    var_cbt_sync = var(cbt_sync)
+    ) %>%
+  gather(comp, contrib, var_cbt_cv_com:var_cbt_sync) %>%
+  left_join(select(cv_bm_div_troph_grp, station, troph_group, div_st),
+    by = c("station", "troph_group"))
+
+  var_cbt %<>%
+    nest() %>%
+    mutate(plot = map2(data, troph_group, function(.data, m_title){
+	.data %>%
+	ggplot(aes(y = contrib, x = div_st)) +
+	  geom_point() +
+	  scale_x_log10() +
+	  facet_wrap(facets = ~comp, scales = "free_y") +
+	  labs(title = paste0(m_title))
+}
+    )
+    )
+
+plot_grid(plotlist = var_cbt$plot, ncol = 2)
 ```
@@
 
-```{r}
-myload(community_metrics, dir = data_common)
+```{r, fig.dim = c(10, 7)}
 community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
@@
 
-myload(network_analysis, dir = mypath("data", "classes"))
-myload(trophic_level, trophic_class, dir = mypath("data"))
-source(mypath("R", "synchrony.R"))
-source(mypath("R", "local_network_build.R"))
 # Get biomass by sp node:
@@
 ## CV, biomass and div (ALREADY DONE!)
-cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
-  select(station, troph_group) %>%
-  unnest(troph_group) %>%
-  filter(!is.na(troph_group) & troph_group != 1) %>%
-  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
-  mutate(troph_group = as.factor(troph_group))
 ```
@@
 car::vif(mod)
-```
-
-#### Assembly rules: richness and biomass distribution
-
-One missing part was the fact that we do not know the assembly rules of the
-trophic group.
-
-```{r}
-cv_bm_div_troph_grp %>%
-  ggplot(aes(y = cv_st, x = div_st)) +
-  geom_point() +
-  facet_grid(cols = vars(troph_group))
-```
-
-```{r}
-sync_com_troph <- net_sp_troph %>%
-    rename(species = sp_class) %>%
-    filter(troph_group != 1) %>%
-    mutate(troph_group = as.factor(troph_group)) %>%
-    group_by(troph_group) %>%
-    nest() %>%
-    mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
-    unnest(sync) %>%
-    mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
-    select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev) %>%
-    left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
-```
-
-```{r sd-avg-div}
-form <- y ~ x
-form2 <- y ~ Vmax * x / (Km + x)
-form3 <- y ~  a + exp(b * x) 
-fit <- stat_poly_eq(
-  formula = form2,
-  eq.with.lhs = "italic(hat(y))~`=`~",
-  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-  parse = TRUE)
-
-ymax <- max(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
-ymin <- min(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
-p_bm <- cv_bm_div_troph_grp %>%
-  ggplot(aes(y = bm_st, x = div_st)) +
-  geom_point() +
-  geom_smooth(method = 'nls', formula = form3,
-   method.args = list(start = c(a = 0, b = 3)), se = F) +
-  #fit +
-  facet_grid(cols = vars(troph_group)) +
-  #scale_y_log10(limits = c(ymin, ymax)) +
-  labs(y = "Average biomass (g).", x = "Species richness")
-
-p_sd <- sync_com_troph %>%
-  ggplot(aes(x = div_st, y = sdt.dev)) +
-  geom_point() +
-  geom_smooth(method = 'lm') +
-  fit +
-  facet_grid(cols = vars(troph_group)) +
-  scale_y_log10(limits = c(ymin, ymax)) +
-  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")
-
-plot_grid(p_sd, p_bm, ncol = 1)
-```
-It seems that the relationship between the standard deviation and the number of
-species saturates for 10 species in medium trophic group while it saturates at 7
-for the high trophic group (Figure \@ref(fig:sd-avg-div)).
-
-To get opposite stability-diversity relationships in the different trophic
-group, it supposes that for medium trophic group, the avg biomass increases
-faster than the biomass standard deviation with increasing species richness. And
-the reverse for the high trophic group, i.e. that the standard deviation
-increases faster than the average biomass.
-
-A question: What are the determinant of the relationship beween avg/standard
-deviation and the number of species?
-
-Part of the solution
-
-```{r}
-formula <- y ~ x #needed for stat_poly_eq
-sync_com_troph %>%
-  ggplot(aes(x = bm_st, y = sdt.dev)) +
-  geom_point() +
-  geom_smooth(method = 'lm') +
-  stat_poly_eq(
-    formula = formula,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  facet_grid(cols = vars(troph_group)) +
-  scale_y_log10() +
-  scale_x_log10() +
-  labs(y = "Standard deviation of biomass temporal data (g).", x = "Average
-      biomass (g)")
-```
-
-```{r}
-
 ```

### 2019-11-21 report/02-methods.Rmd
Test stab div in different context: basin, consistence of biomass trajectories

@@
 
+### Community
+
+Community composition were analyzed thanks to [NMDS](https://jonlefcheck.net/2012/10/24/nmds-tutorial-in-r/).
+
+```{r}
+myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
+myload(community_analysis, dir = data_common)
+myload(network_analysis, dir = mypath("data", "classes"))
+myload(habitat_pressure, dir = mypath("report"))
+```
+
+```{r}
+com <- ungroup(community_analysis) %>%
+  select(opcod, species, biomass) %>%
+  spread(species, biomass) %>%
+  left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
+  mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
+  select(-opcod) %>%
+  group_by(station) %>%
+  summarise_all(list(median))
+
+com_mat <- as.matrix(com[, names(com) != "station"]) 
+```
+
+```{r}
+library(vegan)
+
+nmds <- metaMDS(com_mat, k=3, trymax = 100)
+
+stressplot(nmds)
+plot(nmds)
+ordiplot(nmds,type="n")
+orditorp(nmds,display="species",col="gray",air=0.01)
+```
+
+```{r}
+# Add habitat
+match_st <- match(habitat_pressure$station, com$station)
+habitat <- habitat_pressure[order(match_st), ]
+match_st_com <- match(temporal_community_metrics$station, com$station)
+com_metrics <- temporal_community_metrics[order(match_st_com), ]
+
+ordisurf(nmds,habitat$alt,main="",col="forestgreen")
+```
+
+```{r}
+
+hab_var <- c("temperature", "alt", "lat", "flow", "width_river_mean", "DBO")
+par(mfrow = c(2,3))
+for (i in seq_along(hab_var)) {
+  ordisurf(nmds, habitat[[hab_var[i]]], main = hab_var[i], col = "brown")
+}
+
+```
+
+```{r}
+com_var <- c("richness_med", "biomass_stab", "biomass_med")
+par(mfrow = c(2,2))
+for (i in seq_along(com_var)) {
+  ordisurf(nmds, com_metrics[[com_var[i]]], main = com_var[i], col =
+    "forestgreen")
+}
+```
+
+```{r basin-st}
+station_analysis <- get_basin_station(sf_obj = TRUE)
+plot(station_analysis[,"basin"])
+# How many station by basin:
+nb_st_basin <- station_analysis %>%
+  group_by(basin) %>%
+  summarise(nobs = n())
+```
+
+```{r basin-com}
+match_st_basin <- match(station_analysis$station, com$station)
+st_basin <- station_analysis[order(match_st_basin), ]
+
+ordiplot(nmds,type="n")
+orditorp(nmds,display="species",col="red",air=0.01)
+ordihull(nmds, groups = st_basin[["basin"]], draw="polygon",col="grey90",label=F)
+```
+
 ### Network
@@
 $$
-C_k = CV_{-k} - CV
+C_{k} = CV_{-k} - CV
 $$
@@
 ### Pressure
+
+### Time series classification
+
+```{r load dataset, include = FALSE}
+library(jmotif)
+myload(community_metrics, op_analysis, dir = mypath("data"))
+community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
+```
+
+```{r}
+ts_biomass  <- community_metrics %>%
+  select(station, date, biomass) %>%
+  mutate(station = as.character(station)) %>%
+  group_by(station) %>%
+  arrange(date) %>%
+  nest()
+
+ts_biomass %<>%
+  mutate(
+    zts = map(data, function(x) znorm(x$biomass, threshold = 0.01)),
+    paa = map(zts, ~paa(., 3)),
+    sax = map_chr(paa, ~series_to_string(., 3))
+  )
+
+biomass_ts_sax <- ts_biomass 
+mysave(biomass_ts_sax, dir = mypath("data"), overwrite = TRUE)
+```
+
+```{r}
+pattern_dist <- ts_biomass %>%
+  group_by(sax) %>%
+  summarise(count = n()) %>%
+  arrange(desc(count))
+ggplot(ts_biomass, aes(x = sax)) +
+  geom_histogram(stat = "count")
+```
+
+```{r}
+test <- ts_biomass %>%
+  filter(sax %in% c("cba", "bbb", "cab", "abc", "acb", "bca", "bac", "cbb")) %>%
+  group_by(sax) %>%
+  sample_n(10) %>%
+  mutate(
+    paa2 = map2(data, zts, function (x, zts) {
+      cbind(x[,1], zts)
+  }),
+    id_sta = as.character(seq(1,n()))
+
+  ) %>%
+  unnest(paa2)
+
+ggplot(test, aes(x = date, y = zts)) +
+  geom_line(aes(color = id_sta)) +
+  facet_wrap(~ sax)
+
+```
+
+```{r}
+myload(polluant_units, dir = mypath("data-raw", "polluants", "naiades_data"))
+
+myload(press_metrics, dir = mypath("data"))
+press_year <- press_metrics %>%
+  filter(category %in% c("fungicides", "herbicides", "insecticides", "DBO", "temperature"))
+
+biomass <- community_metrics %>%
+  mutate(
+    year = lubridate::year(date),
+    category = "biomass",
+    press = biomass 
+    ) %>%
+  select(station, year, category, press)
+press_biomass <- press_year %>%
+  bind_rows(rename(biomass, id = station)) %>%
+  na.omit()
+```
+
+```{r}
+samp_station <- sample(unique(press_biomass$id), 10)
+temp <- press_biomass %>%
+  mutate(id = as.character(id)) %>%
+  filter(id %in% samp_station)
+
+ggplot(temp, aes(y = press, x = year)) +
+  facet_wrap(~category, scales = "free_y") +
+  geom_line(aes(color = id))
+
+```

### 2019-11-21 report/05-stability.Rmd
Test stab div in different context: basin, consistence of biomass trajectories

@@
 source(mypath("R", "synchrony.R"))
+source(mypath("R", "geo_methods.R"))
 source(mypath("R", "local_network_build.R"))
@@
 ```{r}
-temporal_network_metrics_classes %>%
+st_basin <- get_basin_station() 
+myload(region_polygon, dir = mypath("data"))
+stab_div_basin <- temporal_network_metrics_classes %>%
   select(station, troph_group) %>%
@@
   filter(troph_group != 1) %>%
-  mutate(troph_group = as.factor(troph_group)) 
-%>%
-  select(station, troph_group, biomass_cv, richness_avg, nbnode_med) %>%
-  gather(richness_type, div, richness_avg, nbnode_med) %>%
-  ggplot(aes(x = div, y = biomass_cv, color = troph_group)) +
-  facet_grid(cols = vars(richness_type), scales = "free_x") +
+  mutate(troph_group = as.factor(troph_group)) %>%
+  select(station, troph_group, biomass_stab, richness_avg) %>%
+  left_join(st_basin, by = "station") %>%
+  filter(!is.na(basin))
+
+# By basin
+p_stab_div_basin <- ggplot(stab_div_basin,
+  aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
+  facet_wrap(~basin, ncol = 4) +
   geom_point() +
@@
   )
+# Total
+p_stab_div_tot <-  ggplot(stab_div_basin,
+  aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
+  geom_point() +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  ggplot2::scale_color_manual(
+    labels = troph_group_labeller(),
+    values = c("blue", "green", "red"),
+    name = "Trophic level"
+  )
+
+plot_grid(p_stab_div_basin, p_stab_div_tot, nrow = 2)
+
+```
+
+```{r}
+myload(biomass_ts_sax, dir = mypath("data"))
+p_bbb_stab_div <- stab_div_basin %>%
+  mutate(station = as.character(station)) %>%
+  left_join(biomass_ts_sax[, c("station", "sax")], by = "station") %>%
+  filter(sax == "bbb") %>%
+  ggplot(aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
+  geom_point() +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  ggplot2::scale_color_manual(
+    labels = troph_group_labeller(),
+    values = c("blue", "green", "red"),
+    name = "Trophic level"
+  )
+
+station_map <- get_basin_station(sf_obj = TRUE) %>%
+  mutate(station = as.character(station)) %>%
+  left_join(biomass_ts_sax[, c("station", "sax")], by = "station") %>%
+  mutate(type = ifelse(sax == "bbb", "stable", "unstable")) %>%
+  select(type)
+
+p_bbb_map <- ggplot(region_polygon) +
+  geom_sf() +
+  geom_sf(data = station_map, aes(color = type))
+#plot(station_map, pch = 16)
+
+plot_grid(p_bbb_stab_div, p_bbb_map, ncol = 2)
+```
+
+```{r temp-grp}
+myload(habitat_pressure, dir = mypath("report"))
+
 ```
@@
 ### Decompose stability
-
-One missing part was the fact that we do not know the assembly rules of the
-trophic group.
 
@@
 
-cv_bm_div_troph_grp %>%
-  ggplot(aes(y = cv_st, x = div_st)) +
-  geom_point() +
-  facet_grid(cols = vars(troph_group))
 ```

### 2019-11-21 R/geo_methods.R

@@ -594,3 +594,36 @@ fill_data_ssn <- function(ssn = NULL, data = NULL, var = NULL,
 
   return(ssn)
 }
+
+#' Get hydrographic basin name for each station  
+#'
+#' @param sf_obj logical should return a spatial object
+#'
+get_basin_station <- function (sf_obj = FALSE) {
+
+  myload(the_8_hydrologic_basin, station_analysis, dir = data_common)
+
+  station_analysis %<>%
+    st_transform(crs = 2154)
+  the_8_hydrologic_basin %<>%
+    mutate(NomDistric = ifelse(CdBassinDC == "B2", "SAMBRE", NomDistric))
+
+  station_basin <- st_intersects(station_analysis, the_8_hydrologic_basin)
+  station_analysis$basin <- purrr::map_chr(station_basin, function(x){
+    if (length(x) == 0) {
+      return(NA) 
+    }
+    the_8_hydrologic_basin[["NomDistric"]][x]
+    })
+  station_analysis %<>%
+    #filter(!is.na(basin)) %>%
+    mutate(station = id) %>%
+    select(station, basin)
+
+  if (!sf_obj) {
+    st_geometry(station_analysis) <- NULL
+  }
+
+  return(station_analysis)
+
+}

### 2019-11-25 report/02-methods.Rmd
Test stab div relationship by spliting dataset in two

@@
 
+### Relationship between environmental variables
+
 ```{r pca-hab, fig.dim = c(10, 7), fig.cap = "PCA over habitat description"}
@@
 phosphorus) and that are more vegetated.
+
+#### Distribution of environmental variables
+
+```{r dist-env, fig.cap = "Histogram of the station average environmental values through time."}
+
+habitat_pressure %>%
+  select(station, width_river_mean:temperature) %>%
+  gather(env_var, value, width_river_mean:temperature) %>%
+  ggplot(aes(x = value)) +
+  geom_histogram() +
+  facet_wrap(facets = ~ env_var, ncol = 3, scales = "free")
+```
+
+The figure \@ref[fig:dist-env] shows that, taking the environmental values one
+by one, there was no apparent bimodality for habitat description such as
+altitude, slope, distance from source, strahler order, river width and depth, flow, temperature.
+However, variables such as latitude, insecticides, fungicides, herbicides
+displayed bimodality. Those bimodalities will be helpful to test relationship
+between stability and diversity for different subset of the dataset and so, test
+the robustness of the relationship.
 

### 2019-11-25 report/05-stability.Rmd
Test stab div relationship by spliting dataset in two

@@
 
-```{r temp-grp}
+```{r}
 myload(habitat_pressure, dir = mypath("report"))
+```
+
+```{r bimod-stab-div, fig.cap = "Relationship between stability and diversity by spliting dataset in two according to an environmental variable.
+The threshold for the dataset split is the median of the environmental variable."}
+plot_bin_stab_div <- function (env = NULL) {
+
+  habitat_pressure$env_bin <- ifelse(
+    habitat_pressure[[env]] < median(habitat_pressure[[env]], na.rm = TRUE),
+    "inf", "sup")
+  habitat_pressure <- na.omit(habitat_pressure[, c("station", "env_bin")])
+  habitat_pressure %>%
+    left_join(stab_div_basin, by = "station") %>%
+    ggplot(aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
+    geom_point() +
+    facet_grid(cols = vars(env_bin)) +
+    stat_poly_eq(
+      formula = y ~ x,
+      eq.with.lhs = "italic(hat(y))~`=`~",
+      aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+      parse = TRUE) +
+    geom_smooth(method = "lm", formula = y ~ x) +
+    ggplot2::scale_color_manual(
+      labels = troph_group_labeller(),
+      values = c("blue", "green", "red"),
+      name = "Trophic level"
+    ) +
+  labs(title = env, x = "Average species richness", y = "Biomass stability")
+}
+
+#width_river_mean avg_depth_station_mean
+env <- c("width_river_mean", "avg_depth_station_mean", "lat", "long",
+  "temperature", "flow", "d_source", "DBO")
+mult_plot_stab_div_bin <- map(env, ~plot_bin_stab_div(env = .x))
+plot_bin_stab_div(env = "width_river_mean")
+
+plot_grid(plotlist = mult_plot_stab_div_bin)
 

### 2019-11-26 report/02-methods.Rmd
Test w/wht ANG + statistical averaging

@@
 
-habitat_pressure %>%
+dist_env <- habitat_pressure %>%
   select(station, width_river_mean:temperature) %>%
-  gather(env_var, value, width_river_mean:temperature) %>%
+  gather(env_var, value, width_river_mean:temperature) 
+med_dist_env <- dist_env %>%
+  group_by(env_var) %>%
+  summarise(value = median(value, na.rm = TRUE))
+
+dist_env %>%
   ggplot(aes(x = value)) +
   geom_histogram() +
+  geom_vline(data = med_dist_env, aes(xintercept = value), color = "red", size =
+    2) +
   facet_wrap(facets = ~ env_var, ncol = 3, scales = "free")
+
 ```

### 2019-11-26 report/05-stability.Rmd
Test w/wht ANG + statistical averaging

@@
 ```
+
 ```{r}
@@
 plot_grid(p_stab_div_basin, p_stab_div_tot, nrow = 2)
-
 ```
@@
 plot_grid(plotlist = mult_plot_stab_div_bin)
+```
 
+The relationship between stability and species diversity (Figure
+\@ref(fig:bimod-stab-div)) seemed to work only in station far from the source
+(which are deeper, hotter, wider, fig. \@ref(fig:pca-hab))). It should be the
+place where the ANG is the most present. The ANG were effectively more abundant
+in the latter station (Figure: \@ref(fig:ang-map-bio)).
+
+```{r ang-map-bio}
+ang_bm <- network_analysis %>%
+  left_join(select(op_analysis, opcod, station), by = "opcod") %>%
+  unnest(composition) %>%
+  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
+  filter(species == "ANG") %>%
+  group_by(station) %>%
+  summarise(biomass = mean(biomass))
+
+mult_plot_ang_env <- map(env, function(x) {
+
+  habitat_pressure$env <- habitat_pressure[[x]]
+
+  ang_bm %>%
+    left_join(habitat_pressure[, c("station", "env")], by = "station") %>%
+    ggplot(aes(x = env, y = biomass)) +
+    geom_point() +
+    stat_poly_eq(
+      formula = y ~ x,
+      eq.with.lhs = "italic(hat(y))~`=`~",
+      aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+      parse = TRUE) +
+    geom_smooth(method = "loess", formula = y ~ x) +
+    scale_y_log10() +
+    labs(x = x, y = "Average biomass of ANG (g)")
+
+  })
+plot_grid(plotlist = mult_plot_ang_env)
 ```
@@
 biomass of the community.
-
-### Decompose stability
 
@@
   mutate(troph_group = as.factor(troph_group))
-
 ```
@@
 ```{r}
-sync_com_troph <- network_analysis %>%
+sync_com_troph_without_ang <- network_analysis %>%
   select(opcod, composition) %>%
@@
   rename(species = sp_class) %>%
-  filter(troph_group != 1) %>%
+  mutate(ang_logic = ifelse(!is.na(str_match(species, "ANG")[,1] == "ANG"),
+      TRUE, FALSE)) %>%
+  filter(troph_group != 1, ang_logic != TRUE) %>%
   mutate(troph_group = as.factor(troph_group)) %>%
@@
     troph_sp_nb_avg, troph_sp_nb_med) %>%
-  left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
+  left_join(stab_div_basin, by = c("station", "troph_group"))
 ```
 
-```{r}
-sync_com_troph %>%
+```{r stab-ang}
+sync_com_troph_without_ang %>%
+  mutate(stab_without_ang = 1/cv_com) %>%
+  rename(stab_with_ang = biomass_stab) %>%
   filter(troph_group != 1) %>%
-  select(station, troph_group, cv_com, troph_sp_nb_med) %>%
-  ggplot(aes(x = troph_sp_nb_med, y = 1/cv_com, color = troph_group)) +
+  select(station, troph_group, richness_avg, stab_with_ang, stab_without_ang) %>% 
+  gather(stab_type, stab, stab_with_ang, stab_without_ang) %>%
+  ggplot(aes(x = richness_avg, y = stab, color = troph_group)) +
   geom_point() +
+  facet_grid(cols = vars(stab_type)) +
   stat_poly_eq(
@@
     )
+```
+
+### Decompose stability
+
+```{r}
+sync_com_troph <- network_analysis %>%
+  select(opcod, composition) %>%
+  unnest(composition) %>%
+  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
+  select(-sp_class) %>%
+  filter(troph_group != 1) %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  group_by(opcod, troph_group, species) %>%
+  summarise(
+    troph_level = sum(troph_level * biomass /sum(biomass)),
+    biomass = sum(biomass)
+  ) %>%
+  group_by(troph_group) %>%
+  nest() %>%
+  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
+  unnest(sync) %>%
+  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
+  mutate(
+    contrib = purrr::pmap(
+      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
+      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
+    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
+    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
+      ) %>% 
+  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
+    troph_sp_nb_avg, troph_sp_nb_med) %>%
+  left_join(select(temporal_community_metrics, station, richness_avg,
+      biomass_avg), by = "station") %>%
+  rename(bm_st = biomass_avg, div_st = richness_avg)
 ```
@@
 
-```{r}
+```{r cbt-top, fig.cap = "Contribution of species to the different facets of stability. Positive contribution values mean that the species contributes negatively to the metric."}
+top_contrib_sp <- sync_com_troph %>%
+  unnest(contrib) %>%
+  group_by(station, troph_group) %>%
+  mutate(cbt_cv_com_n = cbt_cv_com / sd(cbt_cv_com)) %>%
+  group_by(troph_group, species) %>%
+  summarise(
+    avg_cbt_cv_com_n = mean(cbt_cv_com_n),
+    avg_cbt_cv_com = mean(cbt_cv_com),
+    avg_cbt_cv_sp = mean(cbt_cv_sp),
+    avg_cbt_sync = mean(cbt_sync),
+    avg_abs_cbt_cv_com = mean(abs(cbt_cv_com))
+    ) %>%
+  arrange(desc(abs(avg_cbt_cv_com_n))) %>%
+  slice(1:10)
+
+p_top_contrib_sp <- map(c(2, 3), function(x){
+
+  mask <- top_contrib_sp$troph_group == x 
+  top_sp <- unique(top_contrib_sp[mask,]$species)
+
   sync_com_troph %>%
     unnest(contrib) %>%
-  group_by(troph_group, species) %>%
-  summarise(
-    sum_cbt_cv_com = sum(abs(cbt_cv_com)),
-    sum_cbt_cv_sp = sum(abs(cbt_cv_sp)),
-    sum_cbt_sync = sum(abs(cbt_sync))
-    ) %>%
-  arrange(desc(sum_cbt_cv_com)) %>%
-  slice(1:10) %>%
-  gather(comp, contrib, sum_cbt_cv_com:sum_cbt_sync) %>%
+    group_by(station, troph_group) %>%
+    mutate(cbt_cv_com_n = cbt_cv_com / sd(cbt_cv_com)) %>%
+    filter(species %in% top_sp, troph_group == x) %>%
+    gather(comp, contrib, cbt_cv_com_n, cbt_cv_com:cbt_sync) %>%
     ggplot(aes(y = contrib, x = species)) +
-  geom_point() +
-  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
+    geom_violin() +
+    facet_grid(rows = vars(comp), scales = "free_y") +
+    labs(title = x)
+    })
+plot_grid(plotlist = p_top_contrib_sp)
 ```
+
+The figure \@ref(fig:cbt-top), left panel) shows that for the trophic group 2, LOF, GOU and
+VAI were the species that contributes the most to the the CV of the community
+and to its components (CVsp and synchrony). For the 3 trophic group (Figure
+\@ref(fig:cbt-top), right panel), the ANG and CHE contribute the most to
+stability and its facets. Interestingly, the contribution of the species to
+the community CV were quite asymetric toward positive values, meaning that
+species tend to stabilize more than destabilize communities.
 
@@
 	  scale_x_log10() +
-	  facet_wrap(facets = ~comp, scales = "free_y") +
+	  facet_grid(rows = vars(comp), scales = "free_y") +
 	  labs(title = paste0(m_title))
@@
 plot_grid(plotlist = var_cbt$plot, ncol = 2)
+```
+
+#### Statistical averaging
+
+```{r}
+pielou <- network_analysis %>%
+  select(opcod, composition) %>%
+  unnest(composition) %>%
+  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
+  select(-sp_class) %>%
+  filter(troph_group != 1) %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  group_by(opcod, troph_group, species) %>%
+  summarise(
+    troph_level = sum(troph_level * biomass /sum(biomass)),
+    biomass = sum(biomass)
+  ) %>%
+  group_by(troph_group, opcod) %>%
+  mutate(rel_bm = biomass / sum(biomass)) %>%
+  summarise(
+    richness = n(),
+    shannon = diversity(biomass, index = "shannon"),
+    pielou = shannon / log(n())
+  )
+
+pielou %>%
+  left_join(select(op_analysis, station, opcod), by = "opcod") %>%
+  group_by(station, troph_group) %>%
+  summarise(richness_avg = mean(richness), pielou_med = median(pielou)) %>%
+  ggplot(aes(x = richness_avg, y = pielou_med)) +
+  geom_point() +
+  facet_grid(~troph_group)
+
 ```
@@
   rename(species = sp_class) %>%
-  mutate( troph_group = get_size_class(trophic_level, NULL, troph_level,
+  mutate(troph_group = get_size_class(trophic_level, NULL, troph_level,
       trophic_class))

### 2019-11-26 R/plot_methods.R

@@ -378,8 +378,9 @@ plot_dyn_sp_biomass <- function (sync = NULL, station = NULL, trophic_level = NU
   sync <- sync[sync$station == station, ] 
 
   .data <- sync$com_mat_date[[1]] %>%
-    gather(key = species, value = biomass, -date) %>%
-    left_join(trophic_level, by = "species")
+    gather(key = species, value = biomass, -date) 
+  #%>%
+    #left_join(trophic_level, by = "species")
 
   main_title <- paste0("Stab = ", round(1/(sync$cv_com), 2),", ", "Sync = ",
     round(sync$synchrony, 2),", ", "CVsp = ", round(sync$cv_sp, 2))

### 2019-11-30 report/02-methods.Rmd
structure project 1 and 2

@@
 ## Data collection
+
+### Fish length
+
+```{r, fig.cap = "Distribution of fish length. Red, green and black respectively locate the median, the mean and the 200mm threshold."}
+myload(length_analysis, dir = mypath("data"))
+length_analysis %>%
+  ggplot(aes(x = length)) +
+  geom_histogram() +
+  geom_vline(xintercept = median(length_analysis$length, na.rm = TRUE), color = "red") +
+  geom_vline(xintercept = mean(length_analysis$length, na.rm = TRUE), color = "green") +
+  geom_vline(xintercept = 200, color = "black")
+```
 
@@
   summarise_all(list(med = ~median(as.numeric(.), na.rm = TRUE))) %>%
-  left_join(select(temporal_station_desc, station, width_river_mean, avg_depth_station_mean))
+  left_join(select(temporal_station_desc, station, width_river_mean, avg_depth_station_mean, width_river_cv, avg_depth_station_cv))
 
@@
       "fungicides", "insecticides", "nitrates", "phosphore")) %>%
-  rename(station = id) %>%
+  rename(station = id) 
+flow_temp_med <- flow_temp %>%
+  mutate(category = str_c(category, "_med")) %>%
   select(station, category, press_med) %>%
   spread(category, press_med)
+flow_temp_cv <- flow_temp %>%
+  mutate(category = str_c(category, "_cv")) %>%
+  select(station, category, cv_press) %>%
+  spread(category, cv_press)
 
 habitat_station %<>%
-  left_join(flow_temp, by = "station")
+  left_join(left_join(flow_temp_med, flow_temp_cv, by = "station"), by = "station")
 habitat_pressure <- habitat_station
@@
 
-```{r pca-hab, fig.dim = c(10, 7), fig.cap = "PCA over habitat description"}
+```{r pca-hab, fig.dim = c(7, 21), fig.cap = "PCA over habitat description"}
 library(ade4)
 library(factoextra)
-pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_station), -station)), scannf = FALSE, nf = 2, center = TRUE, scale = TRUE)
+pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_station), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)
 
@@
   )
+pca_plot12 <- ggdraw(pca_plot) +
+  draw_plot(eig_plot, x = .7, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
 
-ggdraw(pca_plot) + 
-  draw_plot(eig_plot, x = .7, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
+pca_plot13 <- fviz_pca_var(pca_hab,
+    axes = c(1, 3),
+    col.var = "contrib", # Color by contributions to the PC
+    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+    repel = TRUE     # Avoid text overlapping
+  )
+
+pca_plot23 <- fviz_pca_var(pca_hab,
+    axes = c(2, 3),
+    col.var = "contrib", # Color by contributions to the PC
+    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+    repel = TRUE     # Avoid text overlapping
+  )
+plot_grid(pca_plot12, pca_plot13, pca_plot23, ncol = 1)
 ```
@@
 
+```{r}
+dev.off()
+m <- cor(as.matrix(select(na.omit(habitat_station), -station)), method = "spearman")
+corrplot::corrplot(m, order="hclust", type = "upper", diag = FALSE)
+```
+
 #### Distribution of environmental variables
@@
 dist_env <- habitat_pressure %>%
-  select(station, width_river_mean:temperature) %>%
-  gather(env_var, value, width_river_mean:temperature) 
+  select(station, width_river_mean:temperature_cv) %>%
+  gather(env_var, value, width_river_mean:temperature_cv) 
 med_dist_env <- dist_env %>%
@@
 the robustness of the relationship.
+
+```{r split-rivers, fig.dim = c(7, 12)}
+hab_type <- habitat_pressure %>%
+  mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
+  wide_bin = ifelse(width_river_mean > median(width_river_mean), TRUE, FALSE),
+  hab_type = map2_chr(high_bin, wide_bin, function(high, wide){
+    if (high) {
+      if (wide) {
+	"high_wide"
+      } else {
+	"high_narrow"
+      }
+    } else {
+      if (wide) {
+	"low_wide"
+      } else {
+	"low_narrow"
+      }
+    }
+
+      })
+  ) %>%
+mutate(hab_type = map_chr(high_bin, ~ifelse(.x, "high", "low"))) %>%
+select(station, hab_type)
+
+hab_type_pca <- hab_type[hab_type$station %in% na.omit(habitat_station)$station, ]
+match_st <- match(hab_type_pca$station, na.omit(habitat_station)$station)
+hab_type_pca <- hab_type_pca[order(match_st), ]
+
+pca_cat_river <- fviz_pca_ind(pca_hab, label="none", habillage=hab_type_pca$hab_type,
+  , ellipse.type = "convex",
+             addEllipses=TRUE, ellipse.level=0.95)
+plot_grid(pca_plot, pca_cat_river, ncol = 1)
+mysave(hab_type, dir = mypath("report"), overwrite = TRUE)
+```
 
@@
 
-```{r}
+```{r, echo = FALSE}
 library(vegan)
@@
 com_metrics <- temporal_community_metrics[order(match_st_com), ]
-
-ordisurf(nmds,habitat$alt,main="",col="forestgreen")
 ```
 
-```{r}
-
-hab_var <- c("temperature", "alt", "lat", "flow", "width_river_mean", "DBO")
-par(mfrow = c(2,3))
+```{r, fig.dim = c(7, 14)}
+hab_var <- c("temperature_med", "temperature_cv", "alt", "lat", "flow_med", "flow_cv", "width_river_mean", "width_river_cv", "DBO_med", "DBO_cv")
+par(mfrow = c(5,2))
 for (i in seq_along(hab_var)) {
@@
 }
-
 ```
@@
 ```{r basin-com}
+dev.off()
 match_st_basin <- match(station_analysis$station, com$station)
-st_basin <- station_analysis[order(match_st_basin), ]
+st_basin <- station_analysis[order(match_st_basin), ] %>%
+  mutate(basin = ifelse(is.na(basin), "INCONNU", basin))
 
@@
 orditorp(nmds,display="species",col="red",air=0.01)
-ordihull(nmds, groups = st_basin[["basin"]], draw="polygon",col="grey90",label=F)
+# See https://www.davidzeleny.net/anadat-r/doku.php/en:ordiagrams_examples
+u_basin  <- unique(st_basin[["basin"]])
+for (i in seq_along(u_basin)) {
+  ordihull(nmds, groups = st_basin[["basin"]],
+ show.group = u_basin[i], col = i, draw = 'polygon', label = T)
+}
+```
+
+```{r}
+match_st <- match(hab_type$station, com$station)
+hab_type <- hab_type[order(match_st), ]
+ordiplot(nmds,type="points", choices = c(1, 2))
+orditorp(nmds,display="species",col="red",air=0.01)
+u_hab  <- unique(hab_type[["hab_type"]])
+for (i in seq_along(u_hab)) {
+  ordihull(nmds, groups = hab_type[["hab_type"]], alpha = .1,
+ show.group = u_hab[i], col = i, draw = 'polygon', label = T)
+}
+```
+
+```{r}
+st_basin <- get_basin_station() 
+myload(region_polygon, dir = mypath("data"))
+myload(temporal_network_metrics, dir = mypath("data", "classes"))
+temporal_network_metrics_classes <- temporal_network_metrics
+stab_div_basin <- temporal_network_metrics_classes %>%
+  select(station, troph_group) %>%
+  unnest(troph_group) %>%
+  filter(troph_group != 1) %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  select(station, troph_group, biomass_stab, richness_avg) %>%
+  left_join(st_basin, by = "station") %>%
+  filter(!is.na(basin))
+stab_div_basin %>%
+  left_join(hab_type, by = "station") %>%
+  left_join(habitat_pressure[,c("station", "temperature_med", "DBO_med")],
+    by = "station") %>%
+  gather(variable, value, temperature_med, DBO_med) %>%
+  ggplot(aes(x = richness_avg, y = value)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group), rows = vars(variable), scales = "free_y") +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  ggplot2::scale_color_manual(
+    labels = troph_group_labeller(),
+    values = c("blue", "green", "red"),
+    name = "Trophic level"
+    ) +
+  #scale_y_log10() +
+  scale_x_log10() +
+  labs(title = "Stability - Div by habitat type",
+    x = "Average species richness (log10)", y = "Biomass stability (log10)")
 ```
@@
 $$
-C_{k} = CV_{-k} - CV
+C_{k} = X - X_{-k}
 $$
+
+It means that a negative $C_k$ correspond to a negative contribution of the
+species $k$ to $X$.
 
@@
 
-```{r load dataset, include = FALSE}
+```{r load dataset}
 library(jmotif)
 myload(community_metrics, op_analysis, dir = mypath("data"))
-community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
+community_metrics  <-   
+  left_join(community_metrics, op_analysis[, c("opcod", "station", "date")], by = "opcod")
 ```

### 2019-11-30 report/05-stability.Rmd
structure project 1 and 2

--- 2019-11-21 report/05-stability.Rmd
@@
 myload(network_analysis, dir = mypath("data", "classes"))
-myload(trophic_level, trophic_class, dir = mypath("data"))
+myload( trophic_level, trophic_class, dir = mypath("data"))
+myload(hab_type, dir = mypath("report"))
 source(mypath("R", "synchrony.R"))
@@
 source(mypath("R", "local_network_build.R"))
-```
+stab_div_troph <- temporal_network_metrics_classes %>%
+  select(station, troph_group) %>%
+  unnest(troph_group) %>%
+  filter(troph_group != 1) %>%
+  mutate(troph_group = as.factor(troph_group)) 
+```
+
+```{r}
+synchrony %>%
+  left_join(hab_type, by = "station") %>%
+  left_join(select(temporal_community_metrics, station, richness_med), by = "station") %>%
+  ggplot(aes(x = richness_med, y = 1/cv_com)) +
+  geom_point() +
+  geom_smooth(method = "auto") +
+  facet_grid(cols = vars(hab_type))
+```
+
+```{r}
+synchrony %>%
+  left_join(hab_type, by = "station") %>%
+  left_join(select(temporal_community_metrics, station, richness_med), by = "station") %>%
+  ggplot(aes(x = richness_med, y = 1/cv_com)) +
+  geom_point() +
+  geom_smooth(method = "auto")
+```
+
 ```{r}
@@
 plot_grid(p_stab_div_basin, p_stab_div_tot, nrow = 2)
-
-```
-
-```{r}
+```
+
+```{r, fig.dim = c(8, 7)}
 myload(biomass_ts_sax, dir = mypath("data"))
@@
 
-plot_grid(p_bbb_stab_div, p_bbb_map, ncol = 2)
-```
-
-```{r temp-grp}
+plot_grid(p_bbb_stab_div, p_bbb_map, ncol = 1)
+```
+
+```{r}
 myload(habitat_pressure, dir = mypath("report"))
-
+```
+
+```{r bimod-stab-div, fig.dim = c(7, 16), fig.cap = "Relationship between stability and diversity by spliting dataset in two according to an environmental variable.
+The threshold for the dataset split is the median of the environmental variable."}
+plot_bin_stab_div <- function (env = NULL) {
+
+  habitat_pressure$env_bin <- ifelse(
+    habitat_pressure[[env]] < median(habitat_pressure[[env]], na.rm = TRUE),
+    "inf", "sup")
+  habitat_pressure <- na.omit(habitat_pressure[, c("station", "env_bin")])
+  habitat_pressure %>%
+    left_join(stab_div_basin, by = "station") %>%
+    ggplot(aes(x = richness_avg, y = biomass_stab, color = troph_group)) +
+    geom_point() +
+    facet_grid(cols = vars(env_bin)) +
+    stat_poly_eq(
+      formula = y ~ x,
+      eq.with.lhs = "italic(hat(y))~`=`~",
+      aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+      parse = TRUE) +
+    geom_smooth(method = "lm", formula = y ~ x) +
+    ggplot2::scale_color_manual(
+      labels = troph_group_labeller(),
+      values = c("blue", "green", "red"),
+      name = "Trophic level"
+    ) +
+  labs(title = env, x = "Average species richness", y = "Biomass stability") +
+  theme(legend.position = "none")
+}
+
+#width_river_mean avg_depth_station_mean
+env <- c("width_river_mean", "avg_depth_station_mean", "lat",
+  "temperature_med", "flow_med", "d_source", "DBO_med", "nitrates_med")
+mult_plot_stab_div_bin <- map(env, ~plot_bin_stab_div(env = .x))
+
+plot_grid(plotlist = mult_plot_stab_div_bin, ncol = 2)
+```
+
+The relationship between stability and species diversity (Figure
+\@ref(fig:bimod-stab-div)) seemed to work only in station far from the source
+(which are deeper, hotter, wider, fig. \@ref(fig:pca-hab))). It should be the
+place where the ANG is the most present. The ANG were effectively more abundant
+in the latter station (Figure: \@ref(fig:ang-map-bio)).
+
+```{r ang-map-bio, include = FALSE}
+ang_bm <- network_analysis %>%
+  left_join(select(op_analysis, opcod, station), by = "opcod") %>%
+  unnest(composition) %>%
+  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
+  filter(species == "ANG") %>%
+  group_by(station) %>%
+  summarise(cv_biomass = sd(biomass) / mean(biomass),
+    biomass = mean(biomass))
+
+mult_plot_ang_env <- map(env, function(x) {
+
+  habitat_pressure$env <- habitat_pressure[[x]]
+
+  ang_bm %>%
+    left_join(habitat_pressure[, c("station", "env")], by = "station") %>%
+    ggplot(aes(x = env, y = biomass)) +
+    geom_point() +
+    stat_poly_eq(
+      formula = y ~ x,
+      eq.with.lhs = "italic(hat(y))~`=`~",
+      aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+      parse = TRUE) +
+    geom_smooth(method = "loess", formula = y ~ x) +
+    scale_y_log10() +
+    labs(x = x, y = "Average biomass of ANG (g)")
+
+  })
+plot_grid(plotlist = mult_plot_ang_env)
+```
+
+```{r, fig.dim = c(10, 5)}
+myload(hab_type, dir = mypath("report"))
+stab_div_basin %>%
+  left_join(hab_type, by = "station") %>%
+  ggplot(aes(y = biomass_stab, x = richness_avg, color = troph_group)) +
+  geom_point() +
+  facet_grid(cols = vars(hab_type)) +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  ggplot2::scale_color_manual(
+    labels = troph_group_labeller(),
+    values = c("blue", "green", "red"),
+    name = "Trophic level"
+    ) +
+  scale_y_log10() +
+  scale_x_log10() +
+  labs(title = "Stability - Div by habitat type",
+    x = "Average species richness (log10)", y = "Biomass stability (log10)")
+```
+
+```{r}
+model_enrich_temp <- stab_div_basin %>%
+  left_join(hab_type, by = "station") %>%
+  left_join(habitat_pressure[,c("station", "temperature_med", "temperature_cv", "DBO_med", "DBO_cv")],
+    by = "station") %>%
+  na.omit() %>%
+  group_by(troph_group, hab_type) %>%
+  mutate(
+    log_rich = log10(richness_avg),
+    temp_res = resid(lm(temperature_med ~ log_rich)),
+    dbo_res = resid(lm(DBO_med ~ log_rich)),
+  ) %>%
+  nest() %>%
+  mutate(
+    corel = map(data, function(x) {
+      div_temp <- cor(x = x$richness_avg, y = x$temp_res, method = c("spearman"))
+      div_dbo <- cor(x = x$richness_avg, y = x$dbo_res, method = c("spearman"))
+      data.frame(div_temp = div_temp, div_dbo = div_dbo)
+      }
+     ),
+    model = map(data, ~lm(log10(biomass_stab) ~
+	log_rich  + log_rich:temp_res + log_rich:dbo_res + log_rich:temp_res:dbo_res, data = .x)),
+    colinearity = map(model, ~enframe(car::vif(.x))),
+    coefs = map(model, ~tidy(.x)),
+    sumup = map(model, ~glance(.x))
+  )
+
+unnest(model_enrich_temp, coefs) %>%
+  mutate_at(vars(estimate, std.error, statistic), ~round(., 2)) %>%
+  rename(est = estimate, error = std.error,
+    stat = statistic, grp = troph_group) %>%
+  kable %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "400px")
+```
+
+```{r}
+unnest(model_enrich_temp, colinearity)
+
+```
+
+```{r}
+stab_div_troph %>%
+  select(station, troph_group, biomass_avg) %>%
+  spread(troph_group, biomass_avg) %>%
+  mutate(bm_h_m = `3` / (`3` + `2`)) %>%
+  left_join(hab_type, by = "station") %>%
+  ggplot(aes(x = hab_type, y = bm_h_m)) +
+  geom_boxplot() +
+  labs(x = "Type of river", y = "Proportion of biomass in the high trophic group")
+```
+
+```{r}
+div_troph_col <- stab_div_troph %>%
+  select(station, troph_group, richness_avg) %>%
+  spread(troph_group, richness_avg)
+
+stab_div_troph %>%
+  select(station, troph_group, biomass_stab) %>%
+  left_join(hab_type, by = "station") %>% 
+  left_join(div_troph_col, by = "station") %>%
+  ggplot(aes(x = `2`, y = `3`)) +
+  geom_point(aes(size = log10(biomass_stab), color = log10(biomass_stab))) +
+  facet_grid(cols = vars(troph_group), rows = vars(hab_type))
+```
+
+```{r}
+#TODO: Update cor_troph_group 
+myload(cor_troph_group, dir = mypath("data"))
+cor_troph_group %>%
+  left_join(hab_type, by = "station") %>%
+  filter(!is.na(hab_type)) %>%
+  ggplot(aes(x = hab_type, y = cor_troph)) +
+  geom_boxplot() 
+```
+
+TODO: may be that the altitude station misses the really big fishes that
+stabilizes the communities. Look at dist of biomass (biomass avg by station and the shape of biomass dist).
+
+```{r}
+myload(network_metrics, dir = mypath("data", "classes"))
+avg_troph_lvl <- network_metrics %>%
+  select(opcod, composition) %>%
+  unnest(composition) %>%
+  filter(troph_group != 1) %>%
+  arrange(opcod, troph_group) %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  group_by(opcod, troph_group) %>%
+  mutate(w_troph_lvl = troph_level * biomass / sum(biomass)) %>%
+  summarise(avg_t_lvl = sum(w_troph_lvl))%>%
+  left_join(select(op_analysis, opcod, station), by = "opcod") %>%
+  group_by(station, troph_group) %>%
+  summarise(avg_t_lvl = mean(avg_t_lvl))
+
+avg_troph_lvl %>%
+  left_join(select(stab_div_troph, station, troph_group, richness_avg), by = c("station", "troph_group")) %>%
+  left_join(hab_type, by = "station") %>%
+  ggplot(aes(x = richness_avg, y = avg_t_lvl)) +
+  geom_point() +
+  facet_grid(hab_type~troph_group) +
+  stat_poly_eq(
+    label.x = "right",
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x)
 ```
@@
   mutate(troph_group = as.factor(troph_group))
-
-```
-
-```{r}
-sync_com_troph <- network_analysis %>%
+```
+
+```{r}
+cbt_sync_troph_without_ang <- network_analysis %>%
   select(opcod, composition) %>%
@@
     troph_sp_nb_avg, troph_sp_nb_med) %>%
-  left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
-```
-
-```{r}
-sync_com_troph %>%
+  left_join(stab_div_basin, by = c("station", "troph_group"))
+```
+
+```{r stab-ang, fig.dim = c(10, 7)}
+cbt_sync_troph_without_ang %>%
+  mutate(stab_without_ang = 1/cv_com) %>%
+  rename(stab_with_ang = biomass_stab) %>%
   filter(troph_group != 1) %>%
-  select(station, troph_group, cv_com, troph_sp_nb_med) %>%
-  ggplot(aes(x = troph_sp_nb_med, y = 1/cv_com, color = troph_group)) +
-  geom_point() +
+  select(station, troph_group, richness_avg, stab_with_ang, stab_without_ang) %>% 
+  gather(stab_type, stab, stab_with_ang, stab_without_ang) %>%
+  ggplot(aes(x = richness_avg, y = stab, color = troph_group)) +
+  geom_point() +
+  facet_grid(cols = vars(stab_type)) +
   stat_poly_eq(
@@
 
+### Decompose stability
+
+```{r}
+sync_troph <- network_analysis %>%
+  select(opcod, composition) %>%
+  unnest(composition) %>%
+  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
+  select(-sp_class) %>%
+  filter(troph_group != 1) %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  group_by(opcod, troph_group, species) %>%
+  summarise(
+    troph_level = sum(troph_level * biomass /sum(biomass)),
+    biomass = sum(biomass)
+  ) %>%
+  group_by(troph_group) %>%
+  nest() %>%
+  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>% 
+  unnest(sync)
+
+cbt_sync_troph <- sync_troph %>%
+  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
+  mutate(
+    contrib = purrr::pmap(
+      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
+      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
+    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
+    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
+      ) %>% 
+  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
+    troph_sp_nb_avg, troph_sp_nb_med) %>%
+  left_join(select(temporal_community_metrics, station, richness_avg,
+      biomass_avg), by = "station") %>%
+  rename(bm_st = biomass_avg, div_st = troph_sp_nb_avg)
+```
+
 ```{r sd-avg-div}
 fit <- stat_poly_eq(
-  formula = y ~x,
+  formula = y ~ x,
   eq.with.lhs = "italic(hat(y))~`=`~",
@@
 
-ymax <- max(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
-ymin <- min(cv_bm_div_troph_grp$bm_st, sync_com_troph$sdt.dev)
+ymax <- max(cv_bm_div_troph_grp$bm_st, cbt_sync_troph$sdt.dev)
+ymin <- min(cv_bm_div_troph_grp$bm_st, cbt_sync_troph$sdt.dev)
 p_bm <- cv_bm_div_troph_grp %>%
@@
   geom_point() +
-  geom_smooth(method = 'loess', se = F) +
-  #fit +
+  geom_smooth(method = 'lm', se = F) +
+  fit +
   facet_grid(cols = vars(troph_group)) +
   scale_y_log10(limits = c(ymin, ymax)) +
+  scale_x_log10() +
   labs(y = "Average biomass (g).", x = "Species richness")
 
-p_sd <- sync_com_troph %>%
+p_sd <- cbt_sync_troph %>%
   ggplot(aes(x = div_st, y = sdt.dev)) +
   geom_point() +
-  geom_smooth(method = 'loess', se = FALSE) +
+  geom_smooth(method = 'lm', se = FALSE) +
+  fit +
   facet_grid(cols = vars(troph_group)) +
   scale_y_log10(limits = c(ymin, ymax)) +
+  scale_x_log10() +
   labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")
@@
 
-Part of the solution
+```{r}
+ymax <- max(cv_bm_div_troph_grp$bm_st, cbt_sync_troph$sdt.dev)
+ymin <- min(cv_bm_div_troph_grp$bm_st, cbt_sync_troph$sdt.dev)
+p_bm <- cv_bm_div_troph_grp %>%
+  left_join(hab_type, by = "station") %>%
+  ggplot(aes(y = bm_st, x = div_st)) +
+  geom_point() +
+  geom_smooth(method = 'lm', se = F) +
+  fit +
+  facet_grid(cols = vars(troph_group), rows = vars(hab_type)) +
+  scale_y_log10(limits = c(ymin, ymax)) +
+  scale_x_log10() +
+  labs(y = "Average biomass (g).", x = "Species richness")
+
+p_sd <- cbt_sync_troph %>%
+  left_join(hab_type, by = "station") %>%
+  ggplot(aes(x = div_st, y = sdt.dev)) +
+  geom_point() +
+  geom_smooth(method = 'lm', se = FALSE) +
+  fit +
+  facet_grid(cols = vars(troph_group), rows = vars(hab_type)) +
+  scale_y_log10(limits = c(ymin, ymax)) +
+  scale_x_log10() +
+  labs(y = "Standard deviation of biomass temporal data (g).", x = "Species richness")
+
+plot_grid(p_sd, p_bm, ncol = 1)
+```
 
@@
 formula <- y ~ x #needed for stat_poly_eq
-sync_com_troph %>%
+cbt_sync_troph %>%
   ggplot(aes(x = bm_st, y = sdt.dev)) +
@@
 
-```{r, fig.dim = c(7, 14)}
-sync_com_troph %>%
-  select(troph_group:cv_com, div_st) %>%
+```{r, fig.dim = c(10, 10)}
+u_hab <- unique(hab_type$hab_type)
+p_test <- map(u_hab, function(x){
+cbt_sync_troph %>%
+  select(troph_group:cv_com) %>%
+  left_join(stab_div_basin, by = c("station", "troph_group")) %>%
+  left_join(hab_type, by = "station") %>%
+  filter(hab_type == x) %>%
   gather(comp, stab, synchrony:cv_com) %>%
-  ggplot(aes(x = div_st, y = stab)) +
-  geom_smooth(method = "loess", se = FALSE) +
-  labs(x = "Trophic species diversity", y = "Stability component") +
+  ggplot(aes(x = richness_avg, y = stab)) +
+  geom_smooth(method = "lm", se = FALSE) +
+  stat_poly_eq(
+    label.x = "right",
+    formula = formula,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  labs(title = x, x = "Average species richness", y = "Stability component") +
+  scale_x_log10() +
+  scale_y_log10() +
   geom_point() +
   facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
-```
-
-```{r, fig.dim = c(10, 7)}
+
+      })
+plot_grid(plotlist = p_test)
+```
+
+```{r, fig.dim = c(10, 7), include = FALSE}
 synchrony %>%
@@
   ggplot(aes(x = richness_med, y = stab)) +
-  geom_smooth(method = "loess", se = FALSE) +
+  geom_smooth(method = "lm", se = FALSE) +
   labs(x = "Species diversity", y = "Stability component") +
   geom_point() +
+  scale_x_log10() +
+  scale_y_log10() +
   facet_grid(rows = vars(comp), scales = "free_y")
@@
 
-```{r}
-sync_com_troph %>%
+```{r cbt-top, fig.cap = "Contribution of species to the different facets of stability. Positive contribution values mean that the species contributes negatively to the metric."}
+top_contrib_sp <- cbt_sync_troph %>%
   unnest(contrib) %>%
+  group_by(station, troph_group) %>%
+  mutate(cbt_cv_com_n = cbt_cv_com / sd(cbt_cv_com)) %>%
   group_by(troph_group, species) %>%
   summarise(
-    sum_cbt_cv_com = sum(abs(cbt_cv_com)),
-    sum_cbt_cv_sp = sum(abs(cbt_cv_sp)),
-    sum_cbt_sync = sum(abs(cbt_sync))
+    avg_cbt_cv_com_n = mean(cbt_cv_com_n),
+    avg_cbt_cv_com = mean(cbt_cv_com),
+    avg_cbt_cv_sp = mean(cbt_cv_sp),
+    avg_cbt_sync = mean(cbt_sync),
+    avg_abs_cbt_cv_com = mean(abs(cbt_cv_com))
     ) %>%
-  arrange(desc(sum_cbt_cv_com)) %>%
-  slice(1:10) %>%
-  gather(comp, contrib, sum_cbt_cv_com:sum_cbt_sync) %>%
+  arrange(desc(abs(avg_cbt_cv_com_n))) %>%
+  slice(1:10)
+
+p_top_contrib_sp <- map(c(2, 3), function(x){
+
+  mask <- top_contrib_sp$troph_group == x 
+  top_sp <- unique(top_contrib_sp[mask,]$species)
+
+  cbt_sync_troph %>%
+    unnest(contrib) %>%
+    group_by(station, troph_group) %>%
+    mutate(cbt_cv_com_n = cbt_cv_com / sd(cbt_cv_com)) %>%
+    filter(species %in% top_sp, troph_group == x) %>%
+    gather(comp, contrib, cbt_cv_com_n, cbt_cv_com:cbt_sync) %>%
     ggplot(aes(y = contrib, x = species)) +
-  geom_point() +
-  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
-```
+    geom_violin() +
+    facet_grid(rows = vars(comp), scales = "free_y") +
+    labs(title = x)
+    })
+plot_grid(plotlist = p_top_contrib_sp)
+```
+
+The figure \@ref(fig:cbt-top), left panel) shows that for the trophic group 2,
+TRF, LOF and GOU were the species that contributes the most to the the CV of the
+community and to its components (CVsp and synchrony). For the 3 trophic group
+(Figure \@ref(fig:cbt-top), right panel), the TRF, ANG and CHE contribute the
+most to stability and its facets. Interestingly, the contribution of the species
+to the community CV were quite asymetric toward negative values, meaning that
+species which contributes the most tend to stabilize more than destabilize
+communities. The reason was that the variance of contribution decreases with
+species diversity (Figure \@ref(fig:var-cbt)), meaning that each species
+contributes less and less. Two reasons might explain that: (1) the biomass
+distribution of communities became more even with the increase of species
+number, (2) the population stability converges.  Apparently the eveness of
+biomass distribution does not change with species diversity (figure
+\@ref(fig:even-sdcv-div), A). And the standard deviation of species CV decreases
+with species richness (figure
+\@ref(fig:even-sdcv-div), A).
 
 ```{r var-cbt, fig.dim = c(10, 7)}
-var_cbt <- sync_com_troph %>%
+var_cbt <- cbt_sync_troph %>%
   unnest(contrib) %>%
@@
   gather(comp, contrib, var_cbt_cv_com:var_cbt_sync) %>%
-  left_join(select(cv_bm_div_troph_grp, station, troph_group, div_st),
+  left_join(select(stab_div_basin, station, troph_group, richness_avg),
     by = c("station", "troph_group"))
@@
 	.data %>%
-	ggplot(aes(y = contrib, x = div_st)) +
+	ggplot(aes(y = contrib, x = richness_avg)) +
 	  geom_point() +
 	  scale_x_log10() +
-	  facet_wrap(facets = ~comp, scales = "free_y") +
+	  facet_grid(rows = vars(comp), scales = "free_y") +
 	  labs(title = paste0(m_title))
@@
     )
-
 plot_grid(plotlist = var_cbt$plot, ncol = 2)
+```
+
+#### Statistical averaging
+
+```{r eveness-div}
+pielou <- network_analysis %>%
+  select(opcod, composition) %>%
+  unnest(composition) %>%
+  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
+  select(-sp_class) %>%
+  filter(troph_group != 1) %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  group_by(opcod, troph_group, species) %>%
+  summarise(
+    troph_level = sum(troph_level * biomass /sum(biomass)),
+    biomass = sum(biomass)
+  ) %>%
+  group_by(troph_group, opcod) %>%
+  mutate(rel_bm = biomass / sum(biomass)) %>%
+  summarise(
+    richness = n(),
+    shannon = vegan::diversity(biomass, index = "shannon"),
+    pielou = shannon / log(n())
+  )
+
+p_pielou <- pielou %>%
+  left_join(select(op_analysis, station, opcod), by = "opcod") %>%
+  group_by(station, troph_group) %>%
+  summarise(richness_avg = mean(richness), pielou_med = median(pielou)) %>%
+  left_join(hab_type, by = c("station")) %>%
+  ggplot(aes(x = richness_avg, y = pielou_med, color = hab_type)) +
+  #scale_x_log10() +
+  geom_point() +
+  facet_grid(~troph_group) +
+  stat_poly_eq(
+    label.x = "right",
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "loess", formula = y ~ x, se = FALSE) +
+  labs(x = "Avg species richness", y = "Avagerage evenness of biomass")
+
+p_pielou
+```
+
+```{r even-sdcv-div}
+var_sp <- sync_troph %>%
+  mutate(var_sp = map(var_sp, enframe)) %>%
+  unnest(var_sp) %>%
+  rename(species = name, var_bm = value) %>% 
+  select(station, troph_group, species, var_bm)
+avg_sp <- sync_troph %>%
+  mutate(avg_sp = map(avg_sp, enframe)) %>%
+  unnest(avg_sp) %>%
+  rename(species = name, avg_bm = value) %>% 
+  group_by(station, troph_group) %>%
+  mutate(rel_bm = avg_bm / sum(avg_bm)) %>%
+  ungroup() %>%
+  select(station, troph_group, species, avg_bm, rel_bm)
+cv_bm_sp <- left_join(avg_sp, var_sp, by = c("station", "troph_group", "species")) %>%
+  mutate(cv = sqrt(var_bm) / avg_bm, var_bm = NULL) %>%
+  rename(bm = avg_bm)
+
+p_cv_sp_div <- map(unique(hab_type$hab_type), function(hab) {
+
+var_sp %>%
+  left_join(avg_sp, by = c("station", "troph_group", "species")) %>%
+  left_join(hab_type, by = c("station")) %>%
+  group_by(hab_type) %>%
+  filter(rel_bm < .10, hab_type == hab) %>%
+  ungroup() %>%
+  mutate(cv_sp = sqrt(var_bm) / avg_bm,
+    cv_sp_p = cv_sp * rel_bm) %>%
+  gather(type, cv_sp, cv_sp, cv_sp_p) %>%
+  left_join(select(stab_div_basin, station, troph_group, basin, richness_avg), by = c("station", "troph_group")) %>%
+  ggplot(aes(x = richness_avg, y = cv_sp, color = species)) +
+  geom_point() +
+  #scale_y_log10() +
+  facet_grid(cols = vars(troph_group), rows = vars(type), scales = "free_y") +
+  geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
+  labs(x = "Average species richness", y = "Average species CV", title = hab) +
+  theme(legend.position = "none")
+    })
+
+plot_grid(plotlist = p_cv_sp_div, nrow = 2)
+```
+
+```{r}
+cv_sp_div_troph <- var_sp %>%
+  left_join(avg_sp, by = c("station", "troph_group", "species")) %>%
+  left_join(stab_div_basin[, c("station", "troph_group", "richness_avg")], by = c("station", "troph_group")) %>%
+  mutate(
+    cv_sp = sqrt(var_bm) / avg_bm,
+    cv_sp_p = cv_sp * rel_bm
+  )
+
+m <- cv_sp_div_troph %>%
+  gather(type, cv, rel_bm, cv_sp, cv_sp_p) %>%
+  left_join(hab_type, by = c("station")) %>%
+  group_by(troph_group, species, type, hab_type) %>%
+  nest() %>%
+  mutate(
+    model = map(data, ~lm(cv ~ richness_avg, data = .x)),
+    coeff = map(model, tidy)
+  )
+
+coefs <- m %>%
+  unnest(coeff)
+
+p_list <- map(unique(coefs$type), function (x) {
+  filter(coefs, type == x, term == "richness_avg") %>%
+  ggplot(aes(x = estimate)) +
+  geom_histogram() +
+  facet_grid(cols = vars(hab_type), rows = vars(troph_group), scales = "free_x") + 
+  geom_vline(xintercept = 0, color = "grey") +
+  #geom_vline(xintercept = mean(estimate), color = "red") +
+  labs(title = x)
+  })
+
+plot_grid(plotlist = p_list, labels = "AUTO")
+```
+
+```{r}
+coefs %>%
+  filter(term == "richness_avg", type == "rel_bm") %>%
+  arrange((estimate))
+
+```
+
+```{r}
+cv_sp_div_troph %>%
+  group_by(station, troph_group) %>%
+  summarise(avg_cv = mean(cv_sp), richness_avg = unique(richness_avg)) %>%
+  left_join(hab_type, by = "station") %>%
+  ggplot(aes(x = richness_avg, y = avg_cv)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group), rows = vars(hab_type)) +
+  geom_smooth(method = 'lm') +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE)
+```
+
+```{r}
+cv_sp_div_troph %>%
+  left_join(hab_type, by = "station") %>%
+  ggplot(aes(x = richness_avg, y = cv_sp_p)) +
+  geom_point() +
+  facet_grid(cols = vars(troph_group), rows = vars(hab_type))
 ```
@@
 # Get synchrony and cv sp:
-sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis) %>%
-  arrange(cv_com)
+sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis)
 # Get trophic lvl by node
@@
 
-```{r less-stab-troph, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
+```{r less-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
 plot_grid(plotlist = plot_stab[7:10], ncol = 2)
@@
 
-```{r mid-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium biomass stability. See caption of Figure for details."}
+```{r mid-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium biomass stability. See caption of Figure for details."}
 # Middle station 
@@
 
-```{r 75-stab-troph, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
+```{r 75-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
 # Third quater
@@
 
-```{r 25-stab-troph, fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
+```{r 25-stab-troph, eval = FALSE, fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
 # Third quater
@@
 
-```{r cv-sp-grp3, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the CV of the different trophic groups"}
-cv_sp_grp <- left_join(select(cv_bm_sp, -bm),
-  select(cv_bm_div_troph_grp, -biomass_stab), by = "station")
-
-sp_grp3 <- bm_sp_troph_grp %>%
+```{r cv-sp-grp3, eval = FALSE, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the CV of the different trophic groups"}
+cv_sp_grp <- left_join(
+  select(cv_bm_sp, -bm),
+  select(cv_bm_div_troph_grp, -biomass_stab), by = c("station"))
+
+sp_grp3 <- cv_sp_grp %>%
   filter(troph_group == 3) %>%
@@
 
+u_troph <- unique(cv_sp_grp$troph_group) 
+p_cv_abun_sp <- map(u_troph, function(x) {
 cv_sp_grp %>%
   filter(species %in% sp_grp3$sp_class[1:10]) %>%
+  filter(troph_group == u_troph) %>%
   ggplot(aes(x = cv_st, y = cv)) +
   geom_point() +
-  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller())) +
-  labs(x = "CV of the trophic group", y = "CV of the species")
-```
-
-```{r cv-sp-grp2, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the CV of the different trophic groups"}
+  facet_grid(rows = vars(species)) +
+  labs(x = "CV of the trophic group", y = "CV of the species", title = u_troph)
+  })
+plot_grid(plotlist = p_cv_abun_sp)
+```
+
+```{r cv-sp-grp2, eval = FALSE, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the CV of the different trophic groups"}
 sp_grp2 <- bm_sp_troph_grp %>%
@@
 
-```{r cv-sp-bm-grp3, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the biomass of the different trophic groups"}
+```{r cv-sp-bm-grp3, eval = FALSE, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the biomass of the different trophic groups"}
 cv_sp_grp %>%
@@
 
-```{r cv-sp-bm-grp2, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the biomass of the different trophic groups"}
+```{r cv-sp-bm-grp2, eval = FALSE, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the biomass of the different trophic groups"}
 cv_sp_grp %>%
@@
 
-```{r cv-sp-div-grp3, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the species richness in the different trophic groups."}
+```{r cv-sp-div-grp3, eval = FALSE, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the species richness in the different trophic groups."}
+
 cv_sp_grp %>%
@@
 
-```{r cv-sp-div-grp2, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the species richness in the different trophic groups."}
+```{r cv-sp-div-grp2, eval = FALSE, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the medium trophic group versus the species richness in the different trophic groups."}
 cv_sp_grp %>%
@@
 plot_stab_richness_troph_group
-
-```
+```
+
+## P1: Habitat and trophic group determine the shape of the stability-diversity relationship
+
+What are the contributions of environment and trophic level on the shape of the stability-diversity relationship?
+
+### Statistical Model
+
+1. Stability total vs div + habitat 
+2. Stability by trophic group vs diversity:trophic group:habitat
+   - Random effects: catchement & # sampling years
+   - Include composition in the analyses as [@sandau_including_2014]
+3. SEM:
+   - Paths:
+     - Total Stability
+     - Stability at trophic level 2 & trophic level 3
+     - Diversity at trophic level 2 & trophic level 3
+     - Altitude or PCA coordinates 
+   - Groups: habitat 
+   - Replicate for productivity
+4. Test for different datasets
+
+```{r}
+
+```
+
+## P2: Evt and network structure conjointly drives fonctioning and stability of fish communities
+
+What are the contributions of the the environment and the structure of
+the network on the functioning and the stability of the trophic network
+
+```{r}
+
+```
+
+```{r}
+mod <- lm(betadiv_bin ~ log(richness_med), data = temporal_community_metrics)
+temporal_community_metrics$beta_bin_c <- resid(mod)
+```
+
+```{r}
+biomass_sem <- temporal_community_metrics %>%
+  select(station, biomass_stab, biomass_med, richness_med, pielou_med,
+  beta_bin_c) %>%
+  left_join(select(synchrony, station, synchrony, cv_sp), by = "station") %>%
+  rename(sync = synchrony,
+    piel = pielou_med,
+    prod = biomass_med 
+  )
+habitat_sem <- habitat_pressure %>% 
+  select(station, alt, width_river_mean) %>%
+  rename(width = width_river_mean)
+net_sem <- temporal_network_metrics %>%
+  select(station, connectance_corrected_med, w_trph_lvl_avg_med) %>%
+  rename(c_c = connectance_corrected_med,
+    t_lvl = w_trph_lvl_avg_med)
+
+dsem <- biomass_sem  %>%
+  mutate(log_rich = log10(richness_med)) %>%
+  left_join(net_sem, by = "station") %>%
+  left_join(habitat_sem, by = "station") %>%
+  left_join(st_basin, by = "station") %>%
+  na.omit()
+
+lav_data <- dsem %>%
+  mutate(
+    log_sync = log10(sync), 
+    log_cv_sp = log10(cv_sp),
+    log_stab = log10(biomass_stab)
+  )
+```
+
+```{r}
+library(lavaan)
+options(width = 100)
+
+#log_stab ~ log_sync + log_cv_sp
+lav_formula <- " 
+  log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c
+  log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c
+  log_rich ~ alt + width 
+  piel ~ alt + width
+  c_c ~ alt + width
+  t_lvl ~ alt + width
+  beta_bin_c ~ alt + width
+  log_cv_sp ~~ log_sync
+  "
+lav_mod <- sem(lav_formula, lav_data)
+standardizedsolution(lav_mod) %>%
+  kable() %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "400px")
+```
+
+```{r, fig.dim = c(10, 7), fig.cap = "Lavaan SEM"}
+debug(ggsem)
+ggsem(lav_mod)
+```
+
+```{r}
+library(lme4)
+library(nlme)
+library(piecewiseSEM)
+```
+
+```{r, fig.cap = "The basic SEM"}
+corsem <- psem(
+  lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
+  lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
+  lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
+  lme(piel ~ alt + width, random = ~ 1 | basin, data = lav_data),
+  lme(c_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
+  lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = lav_data),
+  lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
+  lm(log_stab ~ log_cv_sp + log_sync, data = lav_data)
+)
+output <- summary(corsem, .progressBar = F)
+output$coefficients %>%
+  kable() %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "400px")
+source(mypath("R", "plot_methods.R"))
+ggpiecewisesem(output)
+```
+
+```{r, fig.cap = "Biomass"}
+prod_sem <- psem(
+  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
+  lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
+  lme(piel ~ alt + width, random = ~ 1 | basin, data = lav_data),
+  lme(c_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
+  lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = lav_data),
+  lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = lav_data)
+)
+sumup_prod <- summary(prod_sem, .progressBar = F)
+sumup_prod$coefficients %>%
+  kable() %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "400px")
+```

### 2019-11-30 R/plot_methods.R

@@ -378,9 +378,8 @@ plot_dyn_sp_biomass <- function (sync = NULL, station = NULL, trophic_level = NU
   sync <- sync[sync$station == station, ] 
 
   .data <- sync$com_mat_date[[1]] %>%
-    gather(key = species, value = biomass, -date) 
-  #%>%
-    #left_join(trophic_level, by = "species")
+    gather(key = species, value = biomass, -date) %>%
+    left_join(trophic_level, by = "species")
 
   main_title <- paste0("Stab = ", round(1/(sync$cv_com), 2),", ", "Sync = ",
     round(sync$synchrony, 2),", ", "CVsp = ", round(sync$cv_sp, 2))
@@ -462,4 +461,151 @@ troph_group_labeller <- function (troph_class = NULL, round_lvl = 2) {
   names(bounds) <- troph_class$troph_group
   as_labeller(bounds)
 
+}
+
+
+###############
+#  plot SEMs  #
+###############
+ggsem <- function(fit, layout = "sugiyama") {
+
+  # Extract standardized parameters
+  params <- lavaan::standardizedSolution(fit)
+
+  # Edge properties
+  param_edges <- params %>% 
+    filter(op %in% c("=~", "~", "~~"), lhs != rhs, pvalue < .05) %>%
+    transmute(to = lhs,
+              from = rhs,
+              val = est.std,
+              type = dplyr::case_when(
+                op == "=~" ~ "loading",
+                op == "~"  ~ "regression",
+                op == "~~" ~ "correlation",
+                TRUE ~ NA_character_))
+
+  # Identify latent variables for nodes
+  latent_nodes <- param_edges %>% 
+    filter(type == "loading") %>% 
+    distinct(to) %>% 
+    transmute(metric = to, latent = TRUE)
+
+  # Node properties
+  param_nodes <- params %>% 
+    filter(lhs == rhs) %>% 
+    transmute(metric = lhs, e = est.std) %>% 
+    left_join(latent_nodes) %>% 
+    mutate(latent = if_else(is.na(latent), FALSE, latent))
+
+  # Complete Graph Object
+  param_graph <- tidygraph::tbl_graph(param_nodes, param_edges)
+
+  # Plot
+  ggraph(param_graph, layout = layout) +
+    # Latent factor Nodes
+    geom_node_point(aes(alpha = as.numeric(latent)),
+                                     shape = 16, size = 5) +
+    geom_node_point(aes(alpha = as.numeric(latent)),
[…]

### 2019-11-30 R/synchrony.R

@@ -106,7 +106,7 @@ get_sync_cv_mat <- function(com_analysis = NULL, op_analysis = NULL, presence_th
 })
     )
 
-  # To get biomass ans troph information:
+  # To get biomass and troph information:
   if (troph) {
     synchrony$data <- troph_data$data
   }
@@ -134,15 +134,16 @@ compute_sp_contrib <- function (
   stopifnot(is.matrix(mat))
 
   if (ncol(mat) < 2) {
-   data.frame(
-     species = NA,
-     cv_com = NA,
-     cv_sp = NA,
-     sync = NA, 
-     cbt_cv_com = NA,
-     cbt_cv_sp = NA, 
-     cbt_sync = NA
-   ) 
+   return(
+     data.frame(species = NA,
+       cv_com = NA,
+       cv_sp = NA,
+       sync = NA, 
+       cbt_cv_com = NA,
+       cbt_cv_sp = NA, 
+       cbt_sync = NA
+     ) 
+     )
   }
 
   sp <- colnames(mat)
@@ -164,9 +165,9 @@ compute_sp_contrib <- function (
   # Compute contribution
   contrib <- leave_one_out %>%
     mutate(
-      cbt_cv_com = cv_com_sp - cv_com_tot,
-      cbt_cv_sp = cv_sp_sp - cv_sp_tot,
-      cbt_sync = sync_sp - sync_tot
+      cbt_cv_com = cv_com_tot - cv_com_sp,
+      cbt_cv_sp = cv_sp_tot - cv_sp_sp,
+      cbt_sync = sync_tot - sync_sp
     )
   contrib
 }

### 2019-11-30 report/before_chapter.R

@@ -4,10 +4,10 @@ data_common <- mypath("data")
 dest_dir <- mypath("data", "species")
 
 knitr::opts_chunk$set(
-  cache = TRUE,
+  cache = FALSE,
   collapse = TRUE,
   comment = "#>",
-  fig.dim = c(10, 10),
+  fig.dim = c(7, 7),
   fig.show = "hold",
   echo = FALSE,
   message = FALSE,
@@ -24,6 +24,7 @@ library(sf)
 library(ggraph)
 library(lubridate)
 library(pander)
+library(broom)
 source(mypath("R", "misc.R"))
 source(mypath("R", "plot_methods.R"))
 source(mypath("R", "geo_methods.R"))

### 2019-12-12 report/before_chapter.R
Add sub station dataset without holes in monitoring

@@ -4,7 +4,7 @@ data_common <- mypath("data")
 dest_dir <- mypath("data", "species")
 
 knitr::opts_chunk$set(
-  cache = FALSE,
+  cache = TRUE,
   collapse = TRUE,
   comment = "#>",
   fig.dim = c(7, 7),

### 2019-12-13 report/02-methods.Rmd
Fix op cleaning

@@
   left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
+  filter(!is.na(station)) %>%
   mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
@@
 com_mat <- as.matrix(com[, names(com) != "station"])
+rownames(com_mat)  <- com$station
+
+order_st <- match(temporal_community_metrics$station, com$station) 
+tps_com_met <- temporal_community_metrics[order(order_st),]
+
 ```
@@
 nmds <- metaMDS(com_mat, k=3, trymax = 100)
-
 stressplot(nmds)
 plot(nmds)
+mysave(nmds, dir = mypath("report"), overwrite = TRUE)
+
+bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
 ordiplot(nmds,type="n")
 orditorp(nmds,display="species",col="gray",air=0.01)
+orditorp(nmds, display="sites",
+  col= bluefunc(5)[findInterval(tps_com_met$richness_avg, seq(2,6))],
+  # cex = scale(tps_com_met$biomass_med, center = FALSE),
+  air=0.01, pch = "+")
 ```

### 2019-12-13 report/05-stability.Rmd
Add sub station dataset without holes in monitoring
Fix op cleaning

@@
 4. Test for different datasets
+   - factorise calcultation of temporal metrics
 
@@
     t_lvl = w_trph_lvl_avg_med)
+composition_axis <- nmds$points %>%
+  as_tibble %>%
+  mutate(station = as.integer(dimnames(nmds$points)[[1]]))
 
@@
   left_join(st_basin, by = "station") %>%
+  left_join(composition_axis, by = "station") %>%
   na.omit()
@@
 
-```{r}
+```{r, eval = FALSE}
 library(lavaan)
@@
 
-```{r, fig.dim = c(10, 7), fig.cap = "Lavaan SEM"}
-debug(ggsem)
+```{r, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Lavaan SEM"}
 ggsem(lav_mod)
 ```
+
+### Piecewiese SEM
 
@@
 ```
+
+#### Stability
 
@@
   scroll_box(width = "100%", height = "400px")
+
 source(mypath("R", "plot_methods.R"))
@@
 
+```{r}
+compute_psem <- function(.data) {
+  corsem <- psem(
+    lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = .data),
+    lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = .data),
+    lme(log_rich ~ alt + width, random = ~ 1 | basin, data = .data),
+    lme(MDS2 ~ alt + width, random = ~ 1 | basin, data = .data),
+    lme(piel ~ alt + width, random = ~ 1 | basin, data = .data),
+    lme(c_c ~ alt + width, random = ~ 1 | basin, data = .data),
+    lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = .data),
+    lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = .data),
+    lm(log_stab ~ log_cv_sp + log_sync, data = .data)
+  )
+  output <- summary(corsem, .progressBar = F)
+
+  output
+}
+test <- compute_psem(lav_data)
+ggpiecewisesem(test)
+```
+
+```{r sensitivity, eval = FALSE}
+myload(op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
+
+# Compute stability, network metrics, etc with the new datasets
+
+# Compute SEMs
+map(list(), compute_psem)
+
+# Plot
+
+```
+
+```{r}
+lav_data %>%
+  ggplot(aes(x = log_rich, y = MDS1)) +
+  geom_point() +
+  labs(x = "Log of species richness", y = "Axis of composition")
+
+```
+
+#### Productivity
+
 ```{r, fig.cap = "Biomass"}
 prod_sem <- psem(
-  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
+  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = lav_data),
+  lme(MDS2 ~ alt + width, random = ~ 1 | basin, data = lav_data),
   lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
@@
 ```
+
+```{r}
+ggpiecewisesem(sumup_prod)
+```
+
+```{r colin_prod}
+car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = lav_data))
+```

### 2019-12-16 report/02-methods.Rmd
Group PCA by relevant part + add temp & DBO to SEM

@@
 
+#### Separate Med and CV pressure
+
+```{r pca-med-cv, fig.cap="PCA with Avg or CV variables"}
+hab_med <- habitat_pressure %>%
+  select_at(vars(matches("med|mean")))
+hab_cv <- habitat_pressure %>%
+  select_at(vars(matches("_cv"))) %>%
+  select(-width_river_cv, -avg_depth_station_cv, -nitrates_cv, -phosphore_cv)
+
+plot_pca <- function (.data, title = NULL) {
+
+  if (is.null(title)){
+  title <- paste0("PCA - ",
+      ifelse(any(!is.na(str_match(names(.data), "_cv"))), "CV",
+      "Median"))
+  }
+
+  pca_hab <- dudi.pca(as.data.frame(na.omit(.data)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE) 
+  eig_plot <- fviz_eig(pca_hab)
+  pca_plot <- fviz_pca_var(pca_hab,
+    axes = c(1, 2),
+    col.var = "contrib", # Color by contributions to the PC
+    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+    title = title,
+    repel = TRUE # Avoid text overlapping
+  )
+  pca_plot12 <- ggdraw(pca_plot) +
+    draw_plot(eig_plot, x = .7, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
+  pca_plot12
+  }
+plot_pca_med_cv <- map(list(hab_med, hab_cv), plot_pca)
+plot_grid(plotlist = plot_pca_med_cv, labels = "AUTO")
+```
+
+#### Separate according to physical habitat, climate, enrichment
+
+```{r pca-evt}
+phys_var <- c( "width_river_mean", "avg_depth_station_mean",
+   "slope", "alt", "d_source", "strahler")
+#"width_river_cv", "avg_depth_station_cv", "under_bank_med", "hole_pit_med",
+#"long", "lat","logjam_stumps_med", "edge_vg_med",
+#"rock_shelter_med", "aqua_vg_shelter_med", "shade_med", "sinuosite_med",
+climate_var <- c("flow_med", "temperature_med", "flow_cv", "temperature_cv") 
+pressure_var <- c( "fungicides_cv", "herbicides_cv",
+  "insecticides_cv",  "fungicides_med",
+  "herbicides_med", "insecticides_med")
+#, "nitrates_med", "phosphore_med","nitrates_cv", "phosphore_cv","DBO_med", "DBO_cv"
+hab_physical <- habitat_pressure[, names(habitat_pressure) %in% phys_var]
+hab_climate <- habitat_pressure[, names(habitat_pressure) %in% climate_var]
+hab_pressure <- habitat_pressure[, names(habitat_pressure) %in% pressure_var]
+
+p_pca_clim_phy_press <- map2(
+  list(hab_physical, hab_climate, hab_pressure),
+  c("Physical", "Climate", "Pressure"),
+  plot_pca)
+plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
+```
+
 #### Distribution of environmental variables
@@
 orditorp(nmds, display="sites",
-  col= bluefunc(5)[findInterval(tps_com_met$richness_avg, seq(2,6))],
-  # cex = scale(tps_com_met$biomass_med, center = FALSE),
-  air=0.01, pch = "+")
+  col= bluefunc(15)[findInterval(tps_com_met$richness_avg, seq(1,15))],
+   cex = findInterval(log10(tps_com_met$biomass_med), seq(1, 4, 1))/2,
+  air=0.01, pch = "+", labels = "+")
+
 ```

### 2019-12-16 report/05-stability.Rmd
Group PCA by relevant part + add temp & DBO to SEM

@@
 ```{r}
+myload(nmds, dir = mypath("report"))
 
@@
 habitat_sem <- habitat_pressure %>% 
-  select(station, alt, width_river_mean) %>%
+  select(station, lat, alt, width_river_mean, DBO_med, DBO_cv, flow_med, flow_cv,
+    temperature_med, temperature_cv) %>%
   rename(width = width_river_mean)
@@
   left_join(st_basin, by = "station") %>%
-  left_join(composition_axis, by = "station") %>%
+  #left_join(composition_axis, by = "station") %>%
   na.omit()
@@
 lav_mod <- sem(lav_formula, lav_data)
+
 standardizedsolution(lav_mod) %>%
@@
 ```{r, fig.cap = "The basic SEM"}
-  corsem <- psem(
-    lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
-    lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data),
-    lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
-    lme(piel ~ alt + width, random = ~ 1 | basin, data = lav_data),
-    lme(c_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
-    lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = lav_data),
-    lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
-    lm(log_stab ~ log_cv_sp + log_sync, data = lav_data)
-  )
-output <- summary(corsem, .progressBar = F)
+build_stab_sem <- function (evt = NULL, com = NULL, stab_comp = NULL, stab = NULL,  .data = NULL) {
+
+  rs <- map(list(evt = evt, com = com, stab_comp = stab_comp), ~paste(.x, collapse = " + "))
+  stab_eq <- paste(stab, rs[["stab_comp"]], sep = " ~ ")
+  stab_comp_eq <- map_chr(stab_comp, ~ paste(.x, rs[["com"]], sep = " ~ "))
+  com_eq <- map_chr(com, ~paste(.x, rs[["evt"]], sep = " ~ "))
+
+  formulas <- map(c(stab_eq, stab_comp_eq, com_eq), as.formula)
+
+  output <- vector("list", length = length(formulas))
+
+  output[[1]] <- lm(as.formula(stab_eq), data = .data)
+
+  lmer_models <- map(formulas[2:length(formulas)],~lme(fixed = .x, random = ~ 1 | basin, data = .data))
+  lmer_models_c <- map2(lmer_models, formulas[2:length(formulas)],
+    function (.model, .formula){
+      .model$call$fixed <- as.call((.formula))
+      return(.model)
+  })
+
+  output[2:length(output)] <- lmer_models_c
+  return(output)
+
+}
+
+#undebug(build_stab_sem)
+corsem <- build_stab_sem(
+  evt = c("alt", "width", "DBO_med", "temperature_med"),
+  com = c("log_rich", "piel", "c_c", "t_lvl", "beta_bin_c"),
+  stab_comp = c("log_sync", "log_cv_sp"),
+  stab = c("log_stab"),
+  .data = lav_data)
+
+output <- summary(as.psem(corsem), .progressBar = F)
 output$coefficients %>%
@@
 ```
+```{r}
+
+car::vif(lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c, random = ~ 1 | basin, data = lav_data))
+car::vif(lme(log_sync ~ alt + width + temperature_med + DBO_med + flow_med, random = ~ 1 | basin, data = lav_data))
+```
 
@@
   corsem <- psem(
-    lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = .data),
-    lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = .data),
-    lme(log_rich ~ alt + width, random = ~ 1 | basin, data = .data),
-    lme(MDS2 ~ alt + width, random = ~ 1 | basin, data = .data),
-    lme(piel ~ alt + width, random = ~ 1 | basin, data = .data),
-    lme(c_c ~ alt + width, random = ~ 1 | basin, data = .data),
-    lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = .data),
-    lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = .data),
+    lme(temperature_med ~ alt, random = ~ 1 | basin, data = .data),
+    lme(log_rich ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
+    lme(piel ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
+    lme(c_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
+    lme(t_lvl ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
+    lme(beta_bin_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
+    lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c,
+      random = ~ 1 | basin, data = .data),
+    lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl +
+    beta_bin_c, random = ~ 1 | basin, data = .data),
     lm(log_stab ~ log_cv_sp + log_sync, data = .data)
@@
 ```
+
+- Main results:
+  - Richness destabilizes communities 
+  - Turnover destabilizes communities, latter increased by enrichment
+  - Trophic level decreased CV but increase species synchrony!:
+  - Connectance!
 

### 2019-12-17 report/05-stability.Rmd
Minor modification to the SEM

@@
   - Turnover destabilizes communities, latter increased by enrichment
-  - Trophic level decreased CV but increase species synchrony!:
+  - Trophic level decreased CV but increase species synchrony!
   - Connectance!
@@
 
-```{r}
-lav_data %>%
-  ggplot(aes(x = log_rich, y = MDS1)) +
-  geom_point() +
-  labs(x = "Log of species richness", y = "Axis of composition")
-
-```
-
 #### Productivity
@@
 prod_sem <- psem(
-  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = lav_data),
-  lme(MDS2 ~ alt + width, random = ~ 1 | basin, data = lav_data),
-  lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
-  lme(piel ~ alt + width, random = ~ 1 | basin, data = lav_data),
-  lme(c_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
-  lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = lav_data),
-  lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = lav_data)
+  lme(temperature_med ~ alt, random = ~ 1 | basin, data = lav_data),
+  lme(log_rich ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
+  lme(piel ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
+  lme(c_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
+  lme(t_lvl ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
+  lme(beta_bin_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
+  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + DBO_med + temperature_med, random = ~ 1 | basin, data = lav_data)
 )
@@
 ```{r colin_prod}
-car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = lav_data))
-```
+car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data))
+```

### 2019-12-19 R/press_methods.R
All temporal network and community summary operations are turn into functions

@@ -2,7 +2,6 @@
 #                               Manipulate press                               #
 ################################################################################
 
-
 gather_press_to_category <- function(press = NULL, polluant_units = NULL, var_to_sum = NULL, group_var = NULL, ld_weighting = TRUE) {
 
   # Polluants avg by those categories and weighted by their ld_50:

### 2019-12-19 analysis/03_compute_temporal_network_properties.R

@@ -38,7 +38,6 @@ cat("---------------------------------------------\n")
 
 myload(op_analysis, metaweb_analysis, dir = data_common)
 myload(network_metrics, network_analysis, dir = dest_dir)
-debug(summarise_bm_troph_over_time)
 biomass_variation <- summarise_bm_troph_over_time(
   op = op_analysis,
   network = network_analysis 

### 2019-12-19 report/before_chapter.R

@@ -28,4 +28,7 @@ library(broom)
 source(mypath("R", "misc.R"))
 source(mypath("R", "plot_methods.R"))
 source(mypath("R", "geo_methods.R"))
+source(mypath("R", "synchrony.R"))
+source(mypath("R", "community_methods.R"))
+source(mypath("R", "community_analysis.R"))
 theme_set(theme_alain())

### 2019-12-20 report/02-methods.Rmd
Compute sensibility

@@
   select(-region_csp)
+
 # Add temp and flow

### 2019-12-20 report/05-stability.Rmd
Compute sensibility

@@
 myload( trophic_level, trophic_class, dir = mypath("data"))
-myload(hab_type, dir = mypath("report"))
+myload(hab_type, habitat_pressure, dir = mypath("report"))
 source(mypath("R", "synchrony.R"))
@@
 ```{r}
-myload(nmds, dir = mypath("report"))
 
@@
 ```{r}
-
-```
-
-```{r}
-mod <- lm(betadiv_bin ~ log(richness_med), data = temporal_community_metrics)
-temporal_community_metrics$beta_bin_c <- resid(mod)
-```
-
-```{r}
-biomass_sem <- temporal_community_metrics %>%
-  select(station, biomass_stab, biomass_med, richness_med, pielou_med,
-  beta_bin_c) %>%
-  left_join(select(synchrony, station, synchrony, cv_sp), by = "station") %>%
-  rename(sync = synchrony,
-    piel = pielou_med,
-    prod = biomass_med 
-  )
-habitat_sem <- habitat_pressure %>% 
-  select(station, lat, alt, width_river_mean, DBO_med, DBO_cv, flow_med, flow_cv,
-    temperature_med, temperature_cv) %>%
-  rename(width = width_river_mean)
-net_sem <- temporal_network_metrics %>%
-  select(station, connectance_corrected_med, w_trph_lvl_avg_med) %>%
-  rename(c_c = connectance_corrected_med,
-    t_lvl = w_trph_lvl_avg_med)
-composition_axis <- nmds$points %>%
-  as_tibble %>%
-  mutate(station = as.integer(dimnames(nmds$points)[[1]]))
-
-dsem <- biomass_sem  %>%
-  mutate(log_rich = log10(richness_med)) %>%
-  left_join(net_sem, by = "station") %>%
-  left_join(habitat_sem, by = "station") %>%
-  left_join(st_basin, by = "station") %>%
-  #left_join(composition_axis, by = "station") %>%
-  na.omit()
-
-lav_data <- dsem %>%
-  mutate(
-    log_sync = log10(sync), 
-    log_cv_sp = log10(cv_sp),
-    log_stab = log10(biomass_stab)
-  )
-```
-
-```{r, eval = FALSE}
-library(lavaan)
-options(width = 100)
-
-#log_stab ~ log_sync + log_cv_sp
-lav_formula <- "
-  log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c
-  log_cv_sp ~ log_rich + piel + c_c + t_lvl + beta_bin_c
-  log_rich ~ alt + width 
-  piel ~ alt + width
-  c_c ~ alt + width
-  t_lvl ~ alt + width
-  beta_bin_c ~ alt + width
-  log_cv_sp ~~ log_sync
-  "
-lav_mod <- sem(lav_formula, lav_data)
-
-standardizedsolution(lav_mod) %>%
-  kable() %>%
-  kable_styling() %>%
-  scroll_box(width = "100%", height = "400px")
-```
-
-```{r, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Lavaan SEM"}
-ggsem(lav_mod)
+myload(nmds, dir = mypath("report"))
+lav_data <- compute_sem_dataset(
+  com = temporal_community_metrics,
+  network = temporal_network_metrics, 
+  hab_press = habitat_pressure, 
+  sync = synchrony,
+  nmds = nmds,
+  basin = st_basin 
+  )
 ```
@@
 
-```{r, fig.cap = "The basic SEM"}
+```{r, eval = FALSE, fig.cap = "The basic SEM"}
 build_stab_sem <- function (evt = NULL, com = NULL, stab_comp = NULL, stab = NULL,  .data = NULL) {
@@
 ```
-```{r}
+```{r, eval = FALSE}
 
@@
 ```{r}
-compute_psem <- function(.data) {
-  corsem <- psem(
-    lme(temperature_med ~ alt, random = ~ 1 | basin, data = .data),
-    lme(log_rich ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
-    lme(piel ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
-    lme(c_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
-    lme(t_lvl ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
-    lme(beta_bin_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = .data),
-    lme(log_sync ~ log_rich + piel + alt + c_c + t_lvl + beta_bin_c,
-      random = ~ 1 | basin, data = .data),
-    lme(log_cv_sp ~ log_rich + piel + c_c + t_lvl +
-    beta_bin_c, random = ~ 1 | basin, data = .data),
-    lm(log_stab ~ log_cv_sp + log_sync, data = .data)
-  )
-  output <- summary(corsem, .progressBar = F)
-
-  output
-}
-test <- compute_psem(lav_data)
-ggpiecewisesem(test)
+library(nlme)
+library(piecewiseSEM)
+
+st_basin <- get_basin_station()
+myload(nmds, dir = mypath("report"))
+
+# Compute stability, network metrics, etc with the new datasets
+com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))
+
+# Compute sem dataset 
+sem_data <- compute_sem_dataset(
+  com = com_data[["tps_com"]],
+  network = com_data[["tps_net"]], 
+  hab_press = habitat_pressure, 
+  sync = com_data[["sync"]],
+  nmds = nmds,
+  basin = st_basin 
+  )
+
+# Compute SEMs
+sem <- compute_stab_sem(.data = sem_data,
+  random_effect = as.formula("~1|basin"))
+
+```
+
+```{r}
+ggpiecewisesem(sem)
 ```
@@
 ```{r sensitivity, eval = FALSE}
-myload(op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
-
-# Compute stability, network metrics, etc with the new datasets
-
-# Compute SEMs
-map(list(), compute_psem)
-
-# Plot
-
+myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
+
+sem_l_data <- map(list(full = op_analysis, wo_holes = op_analysis_wo_holes, ov = op_analysis_ov),
+  ~build_dataset_get_sem_coefficient(
+    .op = .x,
+    dest_dir = mypath("data", "species"))
+)
+
+sem_results <- map(sem_l_data,
+  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
+  enframe() %>%
+  rename(dataset = name) %>%
+  unnest(value)
+
+# Reformat
+colnames(sem_results) <- str_to_lower(colnames(sem_results))
+sem_results %>%
+  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
+  ggplot(aes(x = r_p, y = std.estimate)) +
+  geom_point(aes(color = dataset)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
 ```

### 2019-12-20 R/statistical_analysis.R

@@ -1,0 +1,129 @@
+
+#' Compute statistical analysis
+#'
+#'
+#'
+#'
+#'
+compute_sem_dataset <- function (
+  com = NULL,
+  network = NULL, 
+  hab_press = NULL,
+  sync = NULL,
+  nmds = NULL,
+  basin = NULL
+  ) {
+  # Check:
+  #stopifnot(
+    #any(
+      ##map_lgl(list("com", "network", "hab_press", "sync", "nmds"), ~missing(get(.x)))
+      #missing(nmds),
+      #missing(com),
+      #missing(network),
+      #missing(hab_press),
+      #missing(sync)
+      #)
+  #)
+
+  # Community -----------------------------------------------------------------
+
+  # Detrend turnover from richness
+  mod <- lm(betadiv_bin ~ log(richness_med), data = com)
+  com$beta_bin_c <- resid(mod)
+
+  # Add synchrony
+  sync %<>% dplyr::select(station, synchrony, cv_sp)
+  biomass_sem <- com %>%
+    dplyr::select(station, biomass_stab, biomass_med, richness_med, pielou_med,
+      beta_bin_c) %>%
+    dplyr::left_join(sync, by = "station") %>%
+    dplyr::rename(sync = synchrony,
+      piel = pielou_med,
+      prod = biomass_med 
+    )
+
+  # Composition
+  composition_axis <- nmds$points %>%
+    as_tibble %>%
+    mutate(station = as.integer(dimnames(nmds$points)[[1]]))
+
+  # Habitat -----------------------------------------------------------------
+  habitat_sem <- hab_press %>% 
+    select(station, lat, alt, width_river_mean, DBO_med, DBO_cv, flow_med, flow_cv,
+      temperature_med, temperature_cv) %>%
+  rename(width = width_river_mean)
+
+  # Network -----------------------------------------------------------------
+  net_sem <- network %>%
+    dplyr::select(station, connectance_corrected_med, w_trph_lvl_avg_med) %>%
+    dplyr::rename(c_c = connectance_corrected_med,
+      t_lvl = w_trph_lvl_avg_med)
+
+  # Merge and return --------------------------------------------------------
+  dsem <- biomass_sem  %>%
+    dplyr::left_join(net_sem, by = "station") %>%
+    dplyr::left_join(habitat_sem, by = "station") %>%
[…]

### 2020-01-07 report/02-methods.Rmd
SEM with 8 pca axis: 2 * (median/cv) * (press/evt)

@@
 habitat_station %<>%
-  left_join(left_join(flow_temp_med, flow_temp_cv, by = "station"), by = "station")
+  left_join(left_join(flow_temp_med, flow_temp_cv, by = "station"), by = "station") %>%
+  filter(station %in% op_analysis$station)
 habitat_pressure <- habitat_station
-mysave(habitat_pressure, dir = mypath("report"), overwrite = TRUE)
 ```
@@
 
+####
+
+```{r pca-evt-press-med-cv}
+evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
+  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler")
+evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
+  "avg_depth_station_cv")
+
+press_var_cv <- c("fungicides_cv", "herbicides_cv", "insecticides_cv", "DBO_cv")
+press_var_med <- c("fungicides_med", "herbicides_med",
+  "insecticides_med","DBO_med")
+
+#, "nitrates_med", "phosphore_med","nitrates_cv", "phosphore_cv", "DBO_cv"
+hab_evt <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean,
+  evt_var_cv)]
+hab_press <- habitat_pressure[, names(habitat_pressure) %in% c(press_var_med,
+  press_var_cv)]
+
+p_pca_clim_phy_press <- map2(
+  list(hab_evt, hab_press),
+  c("EVT", "Pressure"),
+  plot_pca)
+plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
+```
+
+####
+
+```{r}
+hab_mean <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean , press_var_med)]
+hab_cv <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_cv, press_var_cv)]
+
+p_pca_clim_phy_press <- map2(
+  list(hab_mean, hab_cv),
+  c("Med", "Cv"),
+  plot_pca)
+plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
+```
+
+####
+
+```{r}
+pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean, evt_var_cv, press_var_med, press_var_cv, "station")] %>% 
+  na.omit
+hab_evt_mean <- pca_pressure[, names(pca_pressure) %in% evt_var_mean]
+hab_evt_cv <- pca_pressure[, names(pca_pressure) %in% evt_var_cv]
+hab_press_mean <- pca_pressure[, names(pca_pressure) %in% press_var_med]
+hab_press_cv <- pca_pressure[, names(pca_pressure) %in% press_var_cv]
+
+p_pca_clim_phy_press <- map2(
+  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
+  c("Med evt", "Cv evt", "Med press", "Cv press"),
+  plot_pca)
+plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
+```
+
+```{r}
+pca_clim_phy_press <- map(
+  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
+  function(.data) dudi.pca(as.data.frame(na.omit(.data)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE))
+
+names(pca_clim_phy_press) <- c("med_evt", "cv_evt", "med_press", "cv_press")
+```
+
+#### Rotate PCA axis
+
+```{r}
+pca_rotated <- map2( 
+  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
+  c("Med evt", "Cv evt", "Med press", "Cv press"),
+  function(.data, title) {
+    .data %<>% na.omit
+    pca <- dudi.pca(as.data.frame(.data), scannf = FALSE, nf = 2, center = TRUE, scale = TRUE)
+    pca_rotated <- psych::principal(.data, rotate="varimax", nfactors=2,
+      scores=TRUE)
+
+    return(list(normal = pca, rotated = pca_rotated))
+
+  })
+names(pca_rotated) <- c("med_evt", "cv_evt", "med_press", "cv_press")
+
+test <- vector(mode = "list", length = 4)
+for (i in seq_along(names(pca_rotated))) {
+
+  s.corcircle(
+    pca_rotated[[i]]$rotated$loadings[1:nrow(pca_rotated[[i]]$rotated$loadings),], xax = 1,
+    yax = 2)
+  rotated_plot <- recordPlot()
+
+   pca_plot <- fviz_pca_var(pca_rotated[[i]]$normal,
+      axes = c(1, 2),
+      col.var = "contrib", # Color by contributions to the PC
+      gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+      repel = TRUE # Avoid text overlapping
+    )
+
+  test[[i]] <- plot_grid(rotated_plot, pca_plot)
+  rm(rotated_plot)
+
+}
+plot_grid(plotlist=test)
+mysave(pca_rotated, dir = mypath("report"), overwrite = TRUE)
+```
+
+```{r add pca axis to habitat pressure}
+
+test <- map(pca_rotated, function(.pca) .pca$rotated$scores)
+axis_names <- paste0(rep(names(pca_rotated), each = 2), c("1", "2"))
+test2 <- do.call(cbind, test)
+colnames(test2) <- axis_names
+rotated_axis_st <- cbind(pca_pressure[, "station"], test2)
+
+habitat_pressure %<>%
+  left_join(rotated_axis_st, by = "station")
+
+mysave(habitat_pressure, dir = mypath("report"), overwrite = TRUE)
+```
+
 #### Distribution of environmental variables
@@
 ```{r dist-env, fig.cap = "Histogram of the station average environmental values through time."}
-
 dist_env <- habitat_pressure %>%
@@
 hab_type <- habitat_pressure %>%
+  filter(station %in% op_analysis$station) %>%
   mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
@@
 
-```{r}
-com <- ungroup(community_analysis) %>%
-  select(opcod, species, biomass) %>%
-  spread(species, biomass) %>%
-  left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
-  filter(!is.na(station)) %>%
-  mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
-  select(-opcod) %>%
-  group_by(station) %>%
-  summarise_all(list(median))
-
-com_mat <- as.matrix(com[, names(com) != "station"])
-rownames(com_mat)  <- com$station
-
-order_st <- match(temporal_community_metrics$station, com$station) 
-tps_com_met <- temporal_community_metrics[order(order_st),]
-
-```
-
 ```{r, echo = FALSE}
@@
 
-nmds <- metaMDS(com_mat, k=3, trymax = 100)
+myload(nmds, com_mat, dir = mypath("report"))
+
 stressplot(nmds)
 plot(nmds)
-mysave(nmds, dir = mypath("report"), overwrite = TRUE)
+
+order_st <- match(temporal_community_metrics$station, com_mat$station) 
+tps_com_met <- temporal_community_metrics[order(order_st),]
 
@@
   air=0.01, pch = "+", labels = "+")
-
 ```
@@
 # Add habitat
-match_st <- match(habitat_pressure$station, com$station)
-habitat <- habitat_pressure[order(match_st), ]
-match_st_com <- match(temporal_community_metrics$station, com$station)
+habitat_press  <- filter(habitat_pressure, station %in% com_mat$station)
+match_st <- match(habitat_press$station, com_mat$station)
+habitat <- habitat_press[order(match_st), ]
+match_st_com <- match(temporal_community_metrics$station, com_mat$station)
 com_metrics <- temporal_community_metrics[order(match_st_com), ]
@@
 ```{r basin-st}
-station_analysis <- get_basin_station(sf_obj = TRUE)
+station_analysis <- get_basin_station(sf_obj = TRUE) %>%
+  filter(station %in% com_mat$station)
+
 plot(station_analysis[,"basin"])
@@
 dev.off()
-match_st_basin <- match(station_analysis$station, com$station)
-st_basin <- station_analysis[order(match_st_basin), ] %>%
+match_st_basin <- match(station_analysis$station, com_mat$station)
+st_basin <- 
+  station_analysis[order(match_st_basin), ] %>%
   mutate(basin = ifelse(is.na(basin), "INCONNU", basin))
@@
 ```{r}
-match_st <- match(hab_type$station, com$station)
+match_st <- match(hab_type$station, com_mat$station)
 hab_type <- hab_type[order(match_st), ]

### 2020-01-07 report/03-results.Rmd
Test w/wht ANG + statistical averaging
SEM with 8 pca axis: 2 * (median/cv) * (press/evt)

@@
   select_at(vars(dplyr::matches("med"))) %>%
-  cor()
+  na.omit %>%
+  cor(., method = "spearman")
 #knitr::kable(cor_avg)
@@
   select_at(vars(dplyr::matches("cv"))) %>%
-  cor()
+  na.omit %>%
+  cor(., method = "spearman")
+
 as.data.frame(round(cor_cv,2)) %>%

### 2020-01-07 report/05-stability.Rmd
SEM with 8 pca axis: 2 * (median/cv) * (press/evt)

@@
   sync = synchrony,
-  nmds = nmds,
+  nmds = NULL,
   basin = st_basin 
@@
   sync = com_data[["sync"]],
-  nmds = nmds,
+  nmds = NULL,
   basin = st_basin 

### 2020-01-07 R/community_analysis.R

@@ -81,14 +81,19 @@ summarise_com_over_time <- function (
   op = NULL,
   com = NULL
 ) {
-  com %<>%
+
+    if ("station" %in% names(com)) {
+     com$station <- NULL
+    }
+
+  output <- com %>%
     dplyr::left_join(op, by = c("opcod")) %>%
     dplyr::filter(!(is.na(station) | is.na(opcod))) %>%
     dplyr::select(station, richness, nind, biomass, pielou, simpson) %>%
     dplyr::group_by(station) %>%
     dplyr::summarise_at(c("richness", "nind", "biomass", "pielou", "simpson"),
       list(avg = mean, cv =~ sd(.) / mean(.), med = median, stab = ~mean(.) / sd(.)))
-  return(com)
+  return(output)
 }
 
 #' Compute temporal beta-diversity
@@ -157,7 +162,9 @@ compute_com_synchrony <- function (.op = NULL, com = NULL) {
 
   return(synchrony)
 } 
-
+#'
+#'
+#'
 compute_community_temporal_analysis <- function(.op = NULL, dest_dir = NULL) {
 
   output <- vector("list", length = 4)
@@ -211,3 +218,35 @@ compute_community_temporal_analysis <- function(.op = NULL, dest_dir = NULL) {
   return(output)
 
 }
+
+
+#' Compute community matrix 
+#'
+#' 
+#' @param com community_analysis
+#'
+#'
+compute_com_mat <- function (.op = NULL, com = NULL) {
+
+  com <- community_analysis %>%
+    dplyr::select(opcod, species, biomass) %>%
+    dplyr::left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
+    dplyr::filter(!is.na(station)) %>%
+    dplyr::group_by(station) %>%
+    tidyr::nest() %>%
+    mutate(data = map(data, function (.data) {
+	.data %<>%
+	  tidyr::spread(species, biomass) %>%
+	  dplyr::select(-opcod) %>%
+	  dplyr::mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
+	  dplyr::summarise_all(list(median))
+	return(.data)
+    }))
+  
+  com %<>%
+    tidyr::unnest(data) %>%
+    dplyr::mutate_all(list(~ ifelse(is.na(.), 0, .)))
+
+  return(com)
+
+} 

### 2020-01-07 analysis/01_compute_community_metrics.R

@@ -172,3 +172,15 @@ myload(community_analysis, op_analysis, dir = mypath("data"))
 synchrony <- compute_com_synchrony(.op = op_analysis, com = community_analysis)
 
 mysave(synchrony, dir = mypath("data"), overwrite = TRUE)
+
+##################
+#  Compute nmds  #
+##################
+source(mypath("R", "community_analysis.R"))
+
+com_mat <- compute_com_mat(.op = op_analysis, com = ungroup(community_analysis))
+com <- select(com_mat, -station)
+com <- round(com[, colSums(com != 0) > 0])
+
+nmds <- vegan::metaMDS(com, k=3, trymax = 200)
+mysave(nmds, com_mat, dir = mypath("report"), overwrite = TRUE)

### 2020-01-08 report/02-methods.Rmd
Simplify SEM (only evt) + function to rm sp from community_analysis

@@
   function(.data) dudi.pca(as.data.frame(na.omit(.data)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE))
-
 names(pca_clim_phy_press) <- c("med_evt", "cv_evt", "med_press", "cv_press")
@@
 
-```{r}
-pca_rotated <- map2( 
-  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
-  c("Med evt", "Cv evt", "Med press", "Cv press"),
-  function(.data, title) {
-    .data %<>% na.omit
-    pca <- dudi.pca(as.data.frame(.data), scannf = FALSE, nf = 2, center = TRUE, scale = TRUE)
-    pca_rotated <- psych::principal(.data, rotate="varimax", nfactors=2,
-      scores=TRUE)
-
-    return(list(normal = pca, rotated = pca_rotated))
-
-  })
-names(pca_rotated) <- c("med_evt", "cv_evt", "med_press", "cv_press")
-
-test <- vector(mode = "list", length = 4)
-for (i in seq_along(names(pca_rotated))) {
-
-  s.corcircle(
-    pca_rotated[[i]]$rotated$loadings[1:nrow(pca_rotated[[i]]$rotated$loadings),], xax = 1,
-    yax = 2)
-  rotated_plot <- recordPlot()
-
-   pca_plot <- fviz_pca_var(pca_rotated[[i]]$normal,
-      axes = c(1, 2),
-      col.var = "contrib", # Color by contributions to the PC
-      gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-      repel = TRUE # Avoid text overlapping
+```{r, fig.show = "hide"}
+pca_rotated <- compute_rotated_pca(
+  data_list = list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
+  titles = c("med_evt", "cv_evt", "med_press", "cv_press")
 )
 
-  test[[i]] <- plot_grid(rotated_plot, pca_plot)
-  rm(rotated_plot)
+test <- plot_rotated_pca(pca_rotated)
 
-}
+mysave(pca_rotated, dir = mypath("report"), overwrite = TRUE)
+```
+
+```{r pca_rotated_plot}
 plot_grid(plotlist=test)
-mysave(pca_rotated, dir = mypath("report"), overwrite = TRUE)
+```
+
+#### Rotate PCA axis 2
+
+```{r pca-data, fig.show = "hide"}
+evt_var_mean_ok <-  c(evt_var_mean, "DBO_med")
+evt_var_cv_ok <-  c(evt_var_cv, "DBO_cv")
+pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean_ok, evt_var_cv_ok, "station")] %>% 
+  na.omit
+
+pca_list <- map(list(evt_var_mean_ok, evt_var_cv_ok), function (.var) {
+  pca_pressure[, names(pca_pressure) %in% .var]
+})
+names(pca_list) <- c("evt_med", "evt_cv")
+
+pca_rotated <- compute_rotated_pca(
+  data_list = pca_list,
+  titles = names(pca_list)  
+)
+
+pca_rotated_plot <- plot_rotated_pca(pca_rotated = pca_rotated)
+```
+
+```{r pca_env_ok}
+plot_grid(plotlist = pca_rotated_plot, ncol = 1)
 ```
@@
 
+#### Species occurence
+
+```{r}
+myload(community_analysis, dir = data_common)
+
+com <- community_analysis %>%
+  dplyr::select(opcod, species, biomass) %>%
+  dplyr::left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
+  dplyr::filter(!is.na(station)) %>%
+  dplyr::group_by(station) %>%
+  tidyr::nest() %>%
+  mutate(data = map(data, function (.data) {
+      .data %<>%
+	tidyr::spread(species, biomass) %>%
+	dplyr::select(-opcod) %>%
+	dplyr::mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
+	dplyr::summarise_all(list(~ sum(. != 0) / n()))
+      return(.data)
+      }
+    )
+  )
+occurence_sp_st <- com %>%
+  unnest() 
+%>%
+  dplyr::mutate_if(is.double, list(~ ifelse(is.na(.), 0, .)))
+
+med_occ <- occurence_sp_st %>%
+  dplyr::summarise_if(is.double, list(~median(., na.rm = TRUE))) %>%
+  gather(sp, med_occ, everything())
+
+med_occ %>%
+  ggplot(aes(x = med_occ)) +
+  geom_histogram()
+
+```
+
+```{r}
+sp_per <- med_occ[med_occ$med_occ < .30,]$sp
+
+threshold_occ <- c(.10, .30, .50, .80)
+com_wo_per  <- map(threshold_occ, ~ rm_sp_from_com(com = community_analysis, sp_to_rm =
+    med_occ[med_occ$med_occ < .x,]$sp))
+names(com_wo_per) <- threshold_occ
+
+com_data <- list(total = community_analysis)
+com_data <- c(com_data, com_wo_per)
+
+res_sync_per <- map2(com_data, names(com_data), function (.data, .names) {
+
+  sync <- compute_com_synchrony(
+    .op = op_analysis,
+    com = .data)
+  sync$type <- .names 
+  sync$biomass_stab <- 1 / sync$cv_com
+  return(sync)
+
+})
+
+test <- do.call(rbind, res_sync_per)
+
+test %>%
+  ggplot(aes(x = richness_med, y = biomass_stab)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  facet_grid(cols = vars(type))
+
+```
+
 ### Network

### 2020-01-08 report/05-stability.Rmd
Simplify SEM (only evt) + function to rm sp from community_analysis

@@
 
-```{r}
-
-```
-
 ## P2: Evt and network structure conjointly drives fonctioning and stability of fish communities
@@
 
-```{r}
+```{r, fig.dim = c(10, 7), echo = FALSE, fig.cap = "SEM for stability"}
 library(nlme)
@@
 
-```
-
-```{r}
 ggpiecewisesem(sem)
@@
   - Richness destabilizes communities 
-  - Turnover destabilizes communities, latter increased by enrichment
+  - 
   - Trophic level decreased CV but increase species synchrony!
@@
 
-```{r sensitivity, eval = FALSE}
+```{r sensitivity, fig.dim = c(14, 7), fig.cap = "Sensivity analysis with different dataset"}
 myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
-
 sem_l_data <- map(list(full = op_analysis, wo_holes = op_analysis_wo_holes, ov = op_analysis_ov),
@@
 
-```{r, fig.cap = "Biomass"}
-prod_sem <- psem(
-  lme(temperature_med ~ alt, random = ~ 1 | basin, data = lav_data),
-  lme(log_rich ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
-  lme(piel ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
-  lme(c_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
-  lme(t_lvl ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
-  lme(beta_bin_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
-  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + DBO_med + temperature_med, random = ~ 1 | basin, data = lav_data)
-)
-sumup_prod <- summary(prod_sem, .progressBar = F)
-sumup_prod$coefficients %>%
+```{r, fig.cap = "Coefficients of the SEM of biomass"}
+
+prod_sem <- compute_prod_sem(.data = sem_data)
+
+prod_sem$coefficients %>%
   kable() %>%
@@
 ```{r}
-ggpiecewisesem(sumup_prod)
-```
-
-```{r colin_prod}
-car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data))
-```
+ggpiecewisesem(prod_sem)
+```
+
+```{r colin_prod, fig.cap = "Colinearity check for total biomass"}
+car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + evt_med1 + evt_med2 + evt_cv1 + evt_cv2, random = ~ 1 | basin, data = sem_data)) %>%
+  enframe %>%
+  kable
+```

### 2020-01-10 report/02-methods.Rmd
Peripherical species testing

@@
 
-```{r}
+```{r sp-occ}
 myload(community_analysis, dir = data_common)
@@
   unnest()
-%>%
-  dplyr::mutate_if(is.double, list(~ ifelse(is.na(.), 0, .)))
 
@@
 
-```{r}
+###### Species peripherical globally
+
+```{r stab-sp-occ, fig.dim = c(10, 7), fig.cap = "Relationship between biomass stability and species richness without peripherical species."}
 sp_per <- med_occ[med_occ$med_occ < .30,]$sp
@@
 ```
+
+```{r}
+test %>%
+  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
+  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
+  ggplot(aes(x = log10(richness_med), y = value)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  facet_grid(cols = vars(type), rows = vars(stab))
+
+```
+
+###### Species peripherical by station
+
+```{r}
+
+threshold_occ <- c(0, .10, .30, .60, .90)
+
+res_sync_occ_st <- map_dfr(threshold_occ, function (.threshold) {
+
+  # List of sp to rm
+  sp_to_rm <- occurence_sp_st %>%
+    gather(sp, occ, -station) %>%
+    group_by(station) %>%
+    filter(occ < .threshold) %>%
+    summarise(sp2 = list(unique(sp)))
+
+  # Rm species by station
+  truncated_com <- community_analysis %>%
+    left_join(select(op_analysis, opcod, station), by = "opcod") %>%
+    filter(!is.na(station)) %>%
+    group_by(station) %>%
+    nest() %>%
+    left_join(sp_to_rm, by = "station") %>%
+    mutate(
+      output = map2(data, sp2, function (.data, sp_vec) {
+	rm_sp_from_com(com = .data, sp_to_rm = sp_vec)
+  })
+      ) %>%
+  unnest(output) %>%
+  select(-station)
+
+  sync <- compute_com_synchrony(
+    .op = op_analysis,
+    com = truncated_com)
+
+  sync$type <- .threshold 
+  sync$biomass_stab <- 1 / sync$cv_com
+
+  return(sync)
+    })
+
+res_sync_occ_st %>%
+  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
+  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
+  ggplot(aes(x = richness_med, y = value)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  facet_grid(cols = vars(type), rows = vars(stab))
+```
+
+Removing the peripherical species nor at the global scale neither at the station
+scale do not affect the stability-diversity relationship.
 

### 2020-01-10 manuscript/bef_stability/manuscript.Rmd
Begin manuscript

---
title: Species richness destabilizes trophic communities in freshwater ecosystems
author: Alain Danet, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today 
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

```{r}
mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.dim = c(7, 7),
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(magrittr)
library(cowplot)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
theme_set(theme_alain())
```

# Abstract

# Introduction

# Methods

## Community

```{r}
myload(
  temporal_community_metrics,
  dir = mypath("data")
)

myload( temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
rm(temporal_network_metrics)

stab_troph <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  select(station, troph_group, biomass_stab, richness_avg)
```

## Habitat and environment

```{r}
myload(
  hab_analysis,
  temporal_station_desc,
  temporal_press_polluants,
  geo_station,
  dir = mypath("data")
)
habitat_pressure <- build_habitat_pressure_dataset(
  .habitat_analysis = hab_analysis,
  .tmp_press = temporal_press_polluants,
  .tmp_st_desc = temporal_station_desc,
  .geo_st = geo_station 
)
```

```{r, fig.show = "hide"}
evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler")
evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
  "avg_depth_station_cv")
evt_var_mean_ok <-  c(evt_var_mean, "DBO_med")
evt_var_cv_ok <-  c(evt_var_cv, "DBO_cv")
pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean_ok, evt_var_cv_ok, "station")] %>%
  na.omit

pca_list <- map(list(evt_var_mean_ok, evt_var_cv_ok), function (.var) {
  pca_pressure[, names(pca_pressure) %in% .var]
})
names(pca_list) <- c("evt_med", "evt_cv")

pca_rotated <- compute_rotated_pca(
  data_list = pca_list,
  titles = names(pca_list)  
)

pca_rotated_plot <- plot_rotated_pca(pca_rotated = pca_rotated)
names(pca_rotated_plot)
```

## Statistical analysis

### SEM

```{r}
library(nlme)
library(piecewiseSEM)

st_basin <- get_basin_station()
myload(nmds, habitat_pressure, dir = mypath("report"))

# Compute stability, network metrics, etc with ;he new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )

# Compute SEMs
stab_sem <- compute_stab_sem(.data = sem_data,
  random_effect = as.formula("~1|basin"))

bm_sem <- compute_prod_sem(.data = sem_data,
  random_effect = as.formula("~1|basin"))

library(ggraph)
p_stab_sem <- ggpiecewisesem(stab_sem)
p_bm_sem <- ggpiecewisesem(stab_sem)
```

# Results

## Diversity has a destabilizing effect on community

```{r s-div, fig.dim = c(7,3)}
# Plot left  
p_stab_div <- temporal_community_metrics %>%
  ggplot(aes(x = richness_med, y = biomass_stab))+
  geom_smooth(method = "lm") +
  geom_point() +
  labs(x = "Median species richness", y = "Biomass stability")

# Right plot
p_stab_div_troph <- stab_div_troph %>%
  ggplot(aes(x = richness_avg, y = biomass_stab)) +
  geom_point(aes(color = troph_group)) +
  geom_smooth(method = "lm") +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  labs(x = "Average species richness", y = "Biomass stability")

plot_grid(p_stab_div, p_stab_div_troph, ncol = 2, rel_widths = c(.4, .6))
```

## Drivers of total biomass and stability

```{r sem, fig.dim = c(10,6)}
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple
plot_grid(
  plot_grid(pca_rotated_plot$evt_med$rotated,
  pca_rotated_plot$evt_cv$rotated),
  p_stab_sem,
  p_bm_sem, labels = "AUTO"
)
```

- Habitat:
  - Median:
    - Axis1 (river width, dist source, strahler)
    - Axis2 (DBO, slope)
  - CV: 
    - Axis1 (temperature cv, flow cv)
    - Axis2 (width)

- Community structure: 
  - Richness decreases synchrony but increases CV
  - Trophic level increases synchrony but decreases CV
  - Betadiv increases CV

- Stability component:
  - CV is the main driver of stability

# Discussion

# References

### 2020-01-10 report/02-methods.Rmd
Begin manuscript

@@
 
-habitat <- hab_analysis %>%
-  mutate_all(list(as.factor)) %>%
-  select(-opcod, -station, -aqua_vg)
-
-lvl <- c("null", "weak", "medium", "high")
-lvl_sinuosite <- c("straight", "sinuous", "very_sinuous", "meandering")
-lvl_shade <- c("clear", "quite_clear", "quite_covered", "covered")
-
-habitat_station <- hab_analysis %>%
-  select(-opcod, -aqua_vg, - shade, - sinuosite) %>%
-  mutate_if(is.character, list(~factor(., levels = lvl, ordered = TRUE))) %>%
-  left_join(select(hab_analysis, station, shade, sinuosite)) %>%
-  mutate(
-    shade = factor(shade, levels = lvl_shade, ordered = TRUE),
-    sinuosite = factor(sinuosite, levels = lvl_sinuosite, ordered = TRUE)) %>%
-  group_by(station) %>%
-  summarise_all(list(med = ~median(as.numeric(.), na.rm = TRUE))) %>%
-  left_join(select(temporal_station_desc, station, width_river_mean, avg_depth_station_mean, width_river_cv, avg_depth_station_cv))
-
-# Add alt, lat, etc...
-habitat_station %<>% 
-  left_join(geo_station, by = "station") %>%
-  select(-region_csp)
-
-# Add temp and flow
-flow_temp <- temporal_press_polluants %>%
-  filter(category %in% c("flow", "temperature", "DBO", "herbicides",
-      "fungicides", "insecticides", "nitrates", "phosphore")) %>%
-  rename(station = id) 
-flow_temp_med <- flow_temp %>%
-  mutate(category = str_c(category, "_med")) %>%
-  select(station, category, press_med) %>%
-  spread(category, press_med)
-flow_temp_cv <- flow_temp %>%
-  mutate(category = str_c(category, "_cv")) %>%
-  select(station, category, cv_press) %>%
-  spread(category, cv_press)
-
-habitat_station %<>%
-  left_join(left_join(flow_temp_med, flow_temp_cv, by = "station"), by = "station") %>%
-  filter(station %in% op_analysis$station)
-habitat_pressure <- habitat_station
+habitat_pressure <- build_habitat_pressure_dataset(
+  .habitat_analysis = hab_analysis,
+  .tmp_press = temporal_press_polluants,
+  .tmp_st_desc = temporal_station_desc,
+  .geo_st = geo_station 
+)
 ```
@@
 ```{r pca_rotated_plot}
-plot_grid(plotlist=test)
+plot_grid(plotlist = test)
 ```

### 2020-01-10 R/geo_methods.R

@@ -604,11 +604,11 @@ get_basin_station <- function (sf_obj = FALSE) {
   myload(the_8_hydrologic_basin, station_analysis, dir = data_common)
 
   station_analysis %<>%
-    st_transform(crs = 2154)
+    sf::st_transform(crs = 2154)
   the_8_hydrologic_basin %<>%
-    mutate(NomDistric = ifelse(CdBassinDC == "B2", "SAMBRE", NomDistric))
+    dplyr::mutate(NomDistric = ifelse(CdBassinDC == "B2", "SAMBRE", NomDistric))
 
-  station_basin <- st_intersects(station_analysis, the_8_hydrologic_basin)
+  station_basin <- sf::st_intersects(station_analysis, the_8_hydrologic_basin)
   station_analysis$basin <- purrr::map_chr(station_basin, function(x){
     if (length(x) == 0) {
       return(NA) 
@@ -617,11 +617,11 @@ get_basin_station <- function (sf_obj = FALSE) {
     })
   station_analysis %<>%
     #filter(!is.na(basin)) %>%
-    mutate(station = id) %>%
-    select(station, basin)
+    dplyr::mutate(station = id) %>%
+    dplyr::select(station, basin)
 
   if (!sf_obj) {
-    st_geometry(station_analysis) <- NULL
+    sf::st_geometry(station_analysis) <- NULL
   }
 
   return(station_analysis)

### 2020-01-10 R/press_methods.R

@@ -208,3 +208,70 @@ compute_temporal_habitat <- function (.op = NULL ) {
 
 
 }
+
+#' Built the habitat and press dataset 
+#'
+#' @param .habitat_analysis data.frame 
+#' @param .tmp_press data.frame
+#' @param .tmp_st_desc data.frame
+#' @param .geo_st data.frame
+#'
+build_habitat_pressure_dataset <- function (
+  .habitat_analysis = NULL,
+  .tmp_press = NULL,
+  .tmp_st_desc = NULL,
+  .geo_st = NULL
+    ) {
+
+  # Transform the qualitative data from character to ordered factor
+  habitat <- .habitat_analysis %>%
+    mutate_all(list(as.factor)) %>%
+    select(-opcod, -station, -aqua_vg)
+
+  lvl <- c("null", "weak", "medium", "high")
+  lvl_sinuosite <- c("straight", "sinuous", "very_sinuous", "meandering")
+  lvl_shade <- c("clear", "quite_clear", "quite_covered", "covered")
+
+  habitat_station <- .habitat_analysis %>%
+    select(-opcod, -aqua_vg, - shade, - sinuosite) %>%
+    mutate_if(is.character, list(~factor(., levels = lvl, ordered = TRUE))) %>%
+    left_join(select(hab_analysis, station, shade, sinuosite)) %>%
+    mutate(
+      shade = factor(shade, levels = lvl_shade, ordered = TRUE),
+      sinuosite = factor(sinuosite, levels = lvl_sinuosite, ordered = TRUE)
+    )
+
+  # Compute avg over the studied period 
+  habitat_station %<>%
+    group_by(station) %>%
+    summarise_all(list(med = ~median(as.numeric(.), na.rm = TRUE)))
+
+
+  # Add alt, lat, etc...
+  habitat_station %<>% 
+    left_join(.geo_st, by = "station") %>%
+    select(-region_csp) %>%
+    left_join(select(.tmp_st_desc, station, width_river_mean,
+	avg_depth_station_mean, width_river_cv, avg_depth_station_cv))
+
+  # Add temp and flow
+  flow_temp <- .tmp_press %>%
+    filter(category %in% c("flow", "temperature", "DBO", "herbicides",
+	"fungicides", "insecticides", "nitrates", "phosphore")) %>%
+  rename(station = id)
+
+  # Get Med and cv for press
+  flow_temp_med <- flow_temp %>%
+    mutate(category = str_c(category, "_med")) %>%
[…]

### 2020-01-10 R/statistical_analysis.R

@@ -177,23 +177,24 @@ compute_rotated_pca <- function(data_list = NULL, titles = NULL) {
 #'
 plot_rotated_pca <- function (pca_rotated = NULL) {
 
-  test <- vector(mode = "list", length = 4)
+  test <- vector(mode = "list", length = length(names(pca_rotated)))
+  names(test) <- names(pca_rotated)
   for (i in seq_along(names(pca_rotated))) {
 
-    s.corcircle(
+    ade4::s.corcircle(
       pca_rotated[[i]]$rotated$loadings[1:nrow(pca_rotated[[i]]$rotated$loadings),], xax = 1,
       yax = 2)
-    rotated_plot <- recordPlot()
+    rotated_plot <- grDevices::recordPlot()
 
-    pca_plot <- fviz_pca_var(pca_rotated[[i]]$normal,
+    pca_plot <- factoextra::fviz_pca_var(pca_rotated[[i]]$normal,
       axes = c(1, 2),
       col.var = "contrib", # Color by contributions to the PC
       gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
       repel = TRUE # Avoid text overlapping
     )
 
-    test[[i]] <- plot_grid(rotated_plot, pca_plot)
-    rm(rotated_plot)
+    test[[i]]$rotated <- rotated_plot
+    test[[i]]$normal <- pca_plot
 
   }
   return(test)

### 2020-01-13 manuscript/bef_stability/manuscript.Rmd
Add total richness and research questions

@@
 knitr::opts_chunk$set(
-  cache = FALSE,
+  cache = TRUE,
   collapse = TRUE,
@@
 source(mypath("R", "statistical_analysis.R"))
+source(mypath("R", "press_methods.R"))
+source(mypath("R", "geo_methods.R"))
+source(mypath("R", "synchrony.R"))
+
 theme_set(theme_alain())
@@
 # Introduction
+
+- Research questions:
+  - What are the effects of the community structure on total biomass and stability ? 
+    1. What are the effects of species richness on total biomass and stability ?
+      - effect of species richness
+      - effect of trophic group
+    2. What are the effects of the community structure on total biomass and stability ?
+      - What is the relative effect of the environment relative to the community
+	structure ?
+      - What is the effect of the community structure on the different
+	parts of the stability + total biomass?
+	- Effect of horizontal and vertical diversity
 
@@
 
-### SEM
-
-```{r}
+```{r get-data}
 library(nlme)
@@
 myload(nmds, habitat_pressure, dir = mypath("report"))
+myload(op_analysis, dir = mypath("data"))
 
@@
   )
+```
+
+### Relationship between stability and species richness
+
+```{r}
+stab_div_mod <- lme(data = sem_data,
+  fixed = biomass_stab ~ richness_med,
+  random = ~ 1 | basin/(alt + width)
+)
+rsquared(stab_div_mod, method = "nagelkerke")
+
+```
+
+### SEM
+
+```{r}
 
@@
 
-## Diversity has a destabilizing effect on community
+## Species richness has a destabilizing effect on community
 

### 2020-01-13 report/02-methods.Rmd
Add total richness and research questions

@@
 library(factoextra)
-pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_station), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)
+pca_hab <- dudi.pca(as.data.frame(select(na.omit(habitat_pressure), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)
 
@@
 dev.off()
-m <- cor(as.matrix(select(na.omit(habitat_station), -station)), method = "spearman")
+m <- cor(as.matrix(select(na.omit(habitat_pressure), -station)), method = "spearman")
 corrplot::corrplot(m, order="hclust", type = "upper", diag = FALSE)
@@
 ```{r split-rivers, fig.dim = c(7, 12)}
-hab_type <- habitat_pressure %>%
-  filter(station %in% op_analysis$station) %>%
+hab_type <- na.omit(habitat_pressure) %>%
   mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
@@
 
-hab_type_pca <- hab_type[hab_type$station %in% na.omit(habitat_station)$station, ]
-match_st <- match(hab_type_pca$station, na.omit(habitat_station)$station)
+hab_type_pca <- hab_type[hab_type$station %in% na.omit(habitat_pressure)$station, ]
+match_st <- match(hab_type_pca$station, na.omit(habitat_pressure)$station)
 hab_type_pca <- hab_type_pca[order(match_st), ]
@@
 
-```{r}
+```{r, fig.dim = c(10, 7)}
 
@@
 res_sync_occ_st %>%
-  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
-  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
-  ggplot(aes(x = richness_med, y = value)) +
+  select(richness_tot, richness_med, biomass_stab, type) %>%
+  gather(rich_type, richness, richness_med, richness_tot) %>%
+  ggplot(aes(x = richness, y = biomass_stab)) +
   geom_point() +
@@
   geom_smooth(method = "lm", formula = y ~ x) +
-  facet_grid(cols = vars(type), rows = vars(stab))
+  facet_grid(cols = vars(type), rows = vars(rich_type))
 ```

### 2020-01-13 report/05-stability.Rmd
Add total richness and research questions

@@
   left_join(hab_type, by = "station") %>%
-  left_join(select(temporal_community_metrics, station, richness_med), by = "station") %>%
   ggplot(aes(x = richness_med, y = 1/cv_com)) +
@@
 synchrony %>%
-  left_join(hab_type, by = "station") %>%
-  left_join(select(temporal_community_metrics, station, richness_med), by = "station") %>%
-  ggplot(aes(x = richness_med, y = 1/cv_com)) +
-  geom_point() +
-  geom_smooth(method = "auto")
+  gather(rich_type, richness, richness_tot, richness_med) %>%
+  ggplot(aes(x = log10(richness), y = log10(1/cv_com))) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(cols = vars(rich_type))
 ```

### 2020-01-14 report/02-methods.Rmd
Pielou et betadiv en biomass instead of individual number

@@
 ## Network building
+
+- A metaweb was built:
+  - less computational intensive
+
+When you do a metaweb, you kind of consider that you have one type of community
+in terms of species interaction:
+  - Trophic lvl is defined at the metaweb lvl, different from the realized
+    metaweb
 
@@
 
+#### Description of horizontal Community structure
+
+- Pielou computed on biomass:
+  - pielou does not depend on total biomass (same value if computed on raw
+    biomass or relattive biomass)
+
+- Binary betadiversity computed on biomass:
+  - betadiversity-bin is the same if computed on biomass or individual number 
+  - betadiversity-bin computed on biomass is correlated at .72 with the one
+    computed with individual numbers.
+
+- Species richness
+
 ### Network

### 2020-01-15 manuscript/bef_stability/manuscript.Rmd
One PCA + compute clean statistical model

@@
 library(magrittr)
+library(ggeffects)
 library(cowplot)
@@
 ```{r}
-myload(
-  temporal_community_metrics,
-  dir = mypath("data")
-)
+myload(temporal_community_metrics, dir = mypath("data"))
 
-myload( temporal_network_metrics, dir = mypath("data", "classes"))
+myload(temporal_network_metrics, dir = mypath("data", "classes"))
 temporal_network_metrics_classes <- temporal_network_metrics
-rm(temporal_network_metrics)
+myload(temporal_network_metrics, dir = mypath("data", "species"))
 
-stab_troph <- temporal_network_metrics_classes %>%
-  select(station, troph_group) %>%
+stab_div_troph <- temporal_network_metrics %>%
+  dplyr::select(station, troph_group) %>%
   unnest(troph_group) %>%
@@
   mutate(troph_group = as.factor(troph_group)) %>%
-  select(station, troph_group, biomass_stab, richness_avg)
+  dplyr::select(station, troph_group, biomass_stab, richness_med)
 ```
@@
 evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
-  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler")
+  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler", "DBO_med")
 evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
-  "avg_depth_station_cv")
-evt_var_mean_ok <-  c(evt_var_mean, "DBO_med")
-evt_var_cv_ok <-  c(evt_var_cv, "DBO_cv")
-pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean_ok, evt_var_cv_ok, "station")] %>%
+  "avg_depth_station_cv", "DBO_cv")
+pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean, evt_var_cv, "station")] %>%
   na.omit
 
-pca_list <- map(list(evt_var_mean_ok, evt_var_cv_ok), function (.var) {
-  pca_pressure[, names(pca_pressure) %in% .var]
-})
-names(pca_list) <- c("evt_med", "evt_cv")
-
 pca_rotated <- compute_rotated_pca(
-  data_list = pca_list,
-  titles = names(pca_list)  
+  .data = pca_pressure[, !names(pca_pressure) %in% "station"],
+  naxis = 5 
 )
 
-pca_rotated_plot <- plot_rotated_pca(pca_rotated = pca_rotated)
-names(pca_rotated_plot)
 ```
@@
 
-```{r}
+$$
+S_i = \beta_0 + \beta_Rx_{Ri} + \epsilon_{ij}
+$$
+
+```{r mod-div-total}
+ctrl <- lmeControl(opt='optim')
 stab_div_mod <- lme(data = sem_data,
-  fixed = biomass_stab ~ richness_med,
-  random = ~ 1 | basin/(alt + width)
+  fixed = log_stab ~ log_rich,
+  random = ~ 1 + log_rich | basin,
+  control = ctrl 
 )
-rsquared(stab_div_mod, method = "nagelkerke")
+#stab_div_colin <- car::vif(stab_div_mod)
+stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke")
+```
+
+```{r predict}
+pred <- ggpredict(stab_div_mod, terms = c("log_rich"), type = "fe")
+stab_div_pred <- pred %>%
+  as_tibble() %>%
+  rename(
+    log_stab = predicted,
+    log_rich = x,
+    basin = group
+  )
 
@@
 p_stab_sem <- ggpiecewisesem(stab_sem)
-p_bm_sem <- ggpiecewisesem(stab_sem)
+p_bm_sem <- ggpiecewisesem(bm_sem)
 ```
@@
 
-```{r s-div, fig.dim = c(7,3)}
+```{r s-div, fig.dim = c(10,5)}
+label_rsq <- "paste(
+  \"Conditional italic(R) ^ 2 == \", round(stab_div_sum$Conditional, 2),
+  \", Marginal italic(R) ^ 2 == \", round(stab_div_sum$Marginal, 2))"
 # Plot left  
-p_stab_div <- temporal_community_metrics %>%
-  ggplot(aes(x = richness_med, y = biomass_stab))+
-  geom_smooth(method = "lm") +
+p_stab_div <- sem_data %>%
+  ggplot(aes(x = log_rich, y = log_stab))+
   geom_point() +
-  labs(x = "Median species richness", y = "Biomass stability")
+  #scale_x_log10() + scale_y_log10() +
+  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
+  geom_line(data = stab_div_pred) +
+  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
+  = "grey20", alpha = .5) +
+  annotate("text", x = 1.0, y = .8, label = paste(
+  " Marg. R^2 = ", round(stab_div_sum$Marginal, 2),
+  ", Cond. R^2 = ", round(stab_div_sum$Conditional, 2)
+  )
+    )
 
@@
 p_stab_div_troph <- stab_div_troph %>%
-  ggplot(aes(x = richness_avg, y = biomass_stab)) +
-  geom_point(aes(color = troph_group)) +
-  geom_smooth(method = "lm") +
+  ggplot(aes(x = richness_med, y = biomass_stab, color = troph_group)) +
+  geom_point() +
+  geom_smooth(method = "lm" ) +
   ggplot2::scale_color_manual(
@@
   ) +
+  scale_x_log10() + scale_y_log10() +
   labs(x = "Average species richness", y = "Biomass stability")
@@
 
-```{r sem, fig.dim = c(10,6)}
-#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
-#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple
-plot_grid(
-  plot_grid(pca_rotated_plot$evt_med$rotated,
-  pca_rotated_plot$evt_cv$rotated),
-  p_stab_sem,
-  p_bm_sem, labels = "AUTO"
+```{r, fig.show = "hide"}
+axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
+p_l_rot <- map(axis_pair, 
+  function (axis)
+    pca_rotated_plot <- plot_rotated_pca(
+      pca_rotated = pca_rotated,
+      axis = axis 
+    )
 )
@@
 
-- Habitat:
-  - Median:
-    - Axis1 (river width, dist source, strahler)
-    - Axis2 (DBO, slope)
-  - CV: 
-    - Axis1 (temperature cv, flow cv)
-    - Axis2 (width)
+```{r sem-plot, fig.dim = c(10,10)}
+#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
+#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple
+to_plot <- c(1, 6, 7)
+plot_grid(
+  plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
+      ncol = length(to_plot), labels = LETTERS[1]),
+  plot_grid(p_stab_sem, p_bm_sem, labels = LETTERS[2:3]),
+  ncol = 1,
+  rel_heights = c(.4, .6)
+)
+```
+
+- Habitat: (+ / -)
+  - RC 1: width & depth & flow med, d source, strahler 	/
+  - RC 2: T°C med 					/ slope, alt 
+  - RC 3: 						/ flow CV, DBO med
+  - RC 4: river width med, depth med 			/
+  - RC 5: DBO CV 					/
 

### 2020-01-15 report/02-methods.Rmd
One PCA + compute clean statistical model

@@
 
-#### Separate Med and CV pressure
-
-```{r pca-med-cv, fig.cap="PCA with Avg or CV variables"}
-hab_med <- habitat_pressure %>%
-  select_at(vars(matches("med|mean")))
-hab_cv <- habitat_pressure %>%
-  select_at(vars(matches("_cv"))) %>%
-  select(-width_river_cv, -avg_depth_station_cv, -nitrates_cv, -phosphore_cv)
-
-plot_pca <- function (.data, title = NULL) {
-
-  if (is.null(title)){
-  title <- paste0("PCA - ",
-      ifelse(any(!is.na(str_match(names(.data), "_cv"))), "CV",
-      "Median"))
-  }
-
-  pca_hab <- dudi.pca(as.data.frame(na.omit(.data)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE) 
-  eig_plot <- fviz_eig(pca_hab)
-  pca_plot <- fviz_pca_var(pca_hab,
-    axes = c(1, 2),
-    col.var = "contrib", # Color by contributions to the PC
-    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-    title = title,
-    repel = TRUE # Avoid text overlapping
-  )
-  pca_plot12 <- ggdraw(pca_plot) +
-    draw_plot(eig_plot, x = .7, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
-  pca_plot12
-  }
-plot_pca_med_cv <- map(list(hab_med, hab_cv), plot_pca)
-plot_grid(plotlist = plot_pca_med_cv, labels = "AUTO")
-```
-
-#### Separate according to physical habitat, climate, enrichment
-
-```{r pca-evt}
-phys_var <- c( "width_river_mean", "avg_depth_station_mean",
-   "slope", "alt", "d_source", "strahler")
-#"width_river_cv", "avg_depth_station_cv", "under_bank_med", "hole_pit_med",
-#"long", "lat","logjam_stumps_med", "edge_vg_med",
-#"rock_shelter_med", "aqua_vg_shelter_med", "shade_med", "sinuosite_med",
-climate_var <- c("flow_med", "temperature_med", "flow_cv", "temperature_cv") 
-pressure_var <- c( "fungicides_cv", "herbicides_cv",
-  "insecticides_cv",  "fungicides_med",
-  "herbicides_med", "insecticides_med")
-#, "nitrates_med", "phosphore_med","nitrates_cv", "phosphore_cv","DBO_med", "DBO_cv"
-hab_physical <- habitat_pressure[, names(habitat_pressure) %in% phys_var]
-hab_climate <- habitat_pressure[, names(habitat_pressure) %in% climate_var]
-hab_pressure <- habitat_pressure[, names(habitat_pressure) %in% pressure_var]
-
-p_pca_clim_phy_press <- map2(
-  list(hab_physical, hab_climate, hab_pressure),
-  c("Physical", "Climate", "Pressure"),
-  plot_pca)
-plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
-```
-
-####
-
-```{r pca-evt-press-med-cv}
-evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
-  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler")
-evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
-  "avg_depth_station_cv")
-
-press_var_cv <- c("fungicides_cv", "herbicides_cv", "insecticides_cv", "DBO_cv")
-press_var_med <- c("fungicides_med", "herbicides_med",
-  "insecticides_med","DBO_med")
-
-#, "nitrates_med", "phosphore_med","nitrates_cv", "phosphore_cv", "DBO_cv"
-hab_evt <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean,
-  evt_var_cv)]
-hab_press <- habitat_pressure[, names(habitat_pressure) %in% c(press_var_med,
-  press_var_cv)]
-
-p_pca_clim_phy_press <- map2(
-  list(hab_evt, hab_press),
-  c("EVT", "Pressure"),
-  plot_pca)
-plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
-```
-
-####
+#### 1 rotated PCA
 
 ```{r}
-hab_mean <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean , press_var_med)]
-hab_cv <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_cv, press_var_cv)]
+evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
+  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler", "DBO_med")
+evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
+  "avg_depth_station_cv", "DBO_cv")
+pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean, evt_var_cv, "station")] %>%
+  na.omit
 
-p_pca_clim_phy_press <- map2(
-  list(hab_mean, hab_cv),
-  c("Med", "Cv"),
-  plot_pca)
-plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
-```
-
-####
-
-```{r}
-pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean, evt_var_cv, press_var_med, press_var_cv, "station")] %>% 
-  na.omit
-hab_evt_mean <- pca_pressure[, names(pca_pressure) %in% evt_var_mean]
-hab_evt_cv <- pca_pressure[, names(pca_pressure) %in% evt_var_cv]
-hab_press_mean <- pca_pressure[, names(pca_pressure) %in% press_var_med]
-hab_press_cv <- pca_pressure[, names(pca_pressure) %in% press_var_cv]
-
-p_pca_clim_phy_press <- map2(
-  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
-  c("Med evt", "Cv evt", "Med press", "Cv press"),
-  plot_pca)
-plot_grid(plotlist = p_pca_clim_phy_press, labels = "AUTO")
-```
-
-```{r}
-pca_clim_phy_press <- map(
-  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
-  function(.data) dudi.pca(as.data.frame(na.omit(.data)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE))
-names(pca_clim_phy_press) <- c("med_evt", "cv_evt", "med_press", "cv_press")
-```
-
-#### Rotate PCA axis
-
-```{r, fig.show = "hide"}
 pca_rotated <- compute_rotated_pca(
-  data_list = list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
-  titles = c("med_evt", "cv_evt", "med_press", "cv_press")
+  .data = pca_pressure[, !names(pca_pressure) %in% "station"],
+  naxis = 5 
 )
 
-test <- plot_rotated_pca(pca_rotated)
-
-mysave(pca_rotated, dir = mypath("report"), overwrite = TRUE)
-```
-
-```{r pca_rotated_plot}
-plot_grid(plotlist = test)
-```
-
-#### Rotate PCA axis 2
-
-```{r pca-data, fig.show = "hide"}
-evt_var_mean_ok <-  c(evt_var_mean, "DBO_med")
-evt_var_cv_ok <-  c(evt_var_cv, "DBO_cv")
-pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean_ok, evt_var_cv_ok, "station")] %>% 
-  na.omit
-
-pca_list <- map(list(evt_var_mean_ok, evt_var_cv_ok), function (.var) {
-  pca_pressure[, names(pca_pressure) %in% .var]
-})
-names(pca_list) <- c("evt_med", "evt_cv")
-
-pca_rotated <- compute_rotated_pca(
-  data_list = pca_list,
-  titles = names(pca_list)  
+axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
+p_l_rot <- map(axis_pair, 
+  function (axis)
+    pca_rotated_plot <- plot_rotated_pca(
+      pca_rotated = pca_rotated,
+      axis = axis 
     )
-
-pca_rotated_plot <- plot_rotated_pca(pca_rotated = pca_rotated)
-```
-
-```{r pca_env_ok}
-plot_grid(plotlist = pca_rotated_plot, ncol = 1)
+)
+to_plot <- c(1, 6, 7)
+plot_grid(plotlist = c(
+    map(p_l_rot[to_plot], ~.x$rotated),
+    map(p_l_rot[to_plot], ~.x$normal)
+    ), ncol = length(to_plot))
 ```
@@
 
-test <- map(pca_rotated, function(.pca) .pca$rotated$scores)
-axis_names <- paste0(rep(names(pca_rotated), each = 2), c("1", "2"))
-test2 <- do.call(cbind, test)
-colnames(test2) <- axis_names
-rotated_axis_st <- cbind(pca_pressure[, "station"], test2)
+test <- pca_rotated$rotated$scores
+rotated_axis_st <- cbind(pca_pressure[, "station"], test)
 

### 2020-01-15 R/press_methods.R

@@ -225,18 +225,18 @@ build_habitat_pressure_dataset <- function (
 
   # Transform the qualitative data from character to ordered factor
   habitat <- .habitat_analysis %>%
-    mutate_all(list(as.factor)) %>%
-    select(-opcod, -station, -aqua_vg)
+    dplyr::mutate_all(list(as.factor)) %>%
+    dplyr::select(-opcod, -station, -aqua_vg)
 
   lvl <- c("null", "weak", "medium", "high")
   lvl_sinuosite <- c("straight", "sinuous", "very_sinuous", "meandering")
   lvl_shade <- c("clear", "quite_clear", "quite_covered", "covered")
 
   habitat_station <- .habitat_analysis %>%
-    select(-opcod, -aqua_vg, - shade, - sinuosite) %>%
-    mutate_if(is.character, list(~factor(., levels = lvl, ordered = TRUE))) %>%
-    left_join(select(hab_analysis, station, shade, sinuosite)) %>%
-    mutate(
+    dplyr::select(-opcod, -aqua_vg, - shade, - sinuosite) %>%
+    dplyr::mutate_if(is.character, list(~factor(., levels = lvl, ordered = TRUE))) %>%
+    dplyr::left_join(dplyr::select(hab_analysis, station, shade, sinuosite)) %>%
+    dplyr::mutate(
       shade = factor(shade, levels = lvl_shade, ordered = TRUE),
       sinuosite = factor(sinuosite, levels = lvl_sinuosite, ordered = TRUE)
     )
@@ -244,34 +244,34 @@ build_habitat_pressure_dataset <- function (
   # Compute avg over the studied period 
   habitat_station %<>%
     group_by(station) %>%
-    summarise_all(list(med = ~median(as.numeric(.), na.rm = TRUE)))
+    dplyr::summarise_all(list(med = ~median(as.numeric(.), na.rm = TRUE)))
 
 
   # Add alt, lat, etc...
   habitat_station %<>% 
-    left_join(.geo_st, by = "station") %>%
-    select(-region_csp) %>%
-    left_join(select(.tmp_st_desc, station, width_river_mean,
+    dplyr::left_join(.geo_st, by = "station") %>%
+    dplyr::select(-region_csp) %>%
+    dplyr::left_join(dplyr::select(.tmp_st_desc, station, width_river_mean,
 	avg_depth_station_mean, width_river_cv, avg_depth_station_cv))
 
   # Add temp and flow
   flow_temp <- .tmp_press %>%
[…]

### 2020-01-16 manuscript/bef_stability/manuscript.Rmd
Add predict and Rsq for figure one

@@
 myload(temporal_community_metrics, dir = mypath("data"))
+st_basin <- get_basin_station(sf_obj = FALSE)
 
@@
   filter(troph_group != 1) %>%
-  mutate(troph_group = as.factor(troph_group)) %>%
-  dplyr::select(station, troph_group, biomass_stab, richness_med)
+  mutate(troph_group = as.factor(troph_group),
+    log_rich = log10(richness_med),
+    log_stab = log10(biomass_stab)) %>%
+  dplyr::select(station, troph_group, biomass_stab, richness_med, log_rich, log_stab) %>%
+  dplyr::left_join(st_basin, by = "station")
 ```
@@
 
-st_basin <- get_basin_station()
 myload(nmds, habitat_pressure, dir = mypath("report"))
@@
 
+with $i$ being the station $i$.
+
 ```{r mod-div-total}
@@
 )
-#stab_div_colin <- car::vif(stab_div_mod)
-stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke")
-```
+#stab_div_colin <- car::vif(stab_div_mod) not use if one response
+stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
 
-```{r predict}
 pred <- ggpredict(stab_div_mod, terms = c("log_rich"), type = "fe")
@@
     basin = group
+  )
+```
+
+```{r mod-div-troph}
+stab_troph_mod <- lme(data = na.omit(stab_div_troph),
+  fixed = log_stab ~ log_rich * troph_group,
+  random = ~ 1 + log_rich * troph_group | basin,
+  control = ctrl 
+)
+
+#stab_div_colin <- car::vif(stab_troph_mod) not use if one response
+stab_troph_sum <- piecewiseSEM::rsquared(stab_troph_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
+
+pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
+stab_troph_pred <- pred_troph_mod %>%
+  as_tibble() %>%
+  rename(
+    log_stab = predicted,
+    log_rich = x,
+    troph_group = group
   )
@@
 ```{r s-div, fig.dim = c(10,5)}
-label_rsq <- "paste(
-  \"Conditional italic(R) ^ 2 == \", round(stab_div_sum$Conditional, 2),
-  \", Marginal italic(R) ^ 2 == \", round(stab_div_sum$Marginal, 2))"
 # Plot left  
@@
   = "grey20", alpha = .5) +
-  annotate("text", x = 1.0, y = .8, label = paste(
-  " Marg. R^2 = ", round(stab_div_sum$Marginal, 2),
-  ", Cond. R^2 = ", round(stab_div_sum$Conditional, 2)
-  )
-    )
+  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
+    parse = TRUE)
 
@@
 p_stab_div_troph <- stab_div_troph %>%
-  ggplot(aes(x = richness_med, y = biomass_stab, color = troph_group)) +
+  ggplot(aes(x = log_rich, y = log_stab, color = troph_group)) +
   geom_point() +
-  geom_smooth(method = "lm" ) +
   ggplot2::scale_color_manual(
@@
   ) +
-  scale_x_log10() + scale_y_log10() +
-  labs(x = "Average species richness", y = "Biomass stability")
+  geom_line(data = stab_troph_pred) +
+  geom_ribbon(data = stab_troph_pred,
+    aes(ymin = conf.low, ymax = conf.high),
+    alpha = .5) +
+  annotate("text", x = 0.8, y = .8, label = make_label_rsq(rsq = stab_troph_sum),
+    parse = TRUE) +
+  #scale_x_log10() + scale_y_log10() +
+  labs(x = "Median species richness", y = "Biomass stability")
 

### 2020-01-20 manuscript/bef_stability/manuscript.Rmd
Improve plots + latex path analysis

--- 2020-01-15 manuscript/bef_stability/manuscript.Rmd
@@
 knitr::opts_chunk$set(
-  cache = TRUE,
+  cache = FALSE,
   collapse = TRUE,
@@
   filter(troph_group != 1) %>%
-  mutate(troph_group = as.factor(troph_group)) %>%
-  dplyr::select(station, troph_group, biomass_stab, richness_med)
+  mutate(troph_group = as.factor(troph_group),
+    log_rich = log10(richness_med),
+    log_bm = log10(biomass_med),
+    log_stab = log10(biomass_stab)) %>%
+  dplyr::select(station, troph_group, biomass_stab, richness_med, log_rich, log_stab, log_bm, biomass_med) %>%
+  dplyr::left_join(st_basin, by = "station")
 ```
@@
 $$
-S_i = \beta_0 + \beta_Rx_{Ri} + \epsilon_{ij}
+\Log_{10}(S_i) = \beta_0 + \beta_R\Log_{10}(x_{Ri}) + \epsilon_{ij}
 $$
 
+$$
+S_i = 10^(\beta_0 + \beta_R\Log_{10}(x_{Ri}) + \epsilon_{ij})
+$$
+
+$$
+S_i = 10^(\beta_0) \times 10^(\beta_R\Log(x_{Ri})) * 10^(\epsilon_{ij})
+$$
+
+with $i$ being the station $i$.
+
 ```{r mod-div-total}
+library(lme4)
 ctrl <- lmeControl(opt='optim')
-stab_div_mod <- lme(data = sem_data,
-  fixed = log_stab ~ log_rich,
-  random = ~ 1 + log_rich | basin,
-  control = ctrl 
+ctrl_lmer <- lmerControl(optCtrl = list(method = 'optim'))
+stab_div_mod <- lmer(data = sem_data,
+  #control = ctrl_lmer,
+  formula = log_stab ~ log_rich + (1 | basin)
 )
-#stab_div_colin <- car::vif(stab_div_mod)
-stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke")
-```
+stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
+#stab_div_colin <- car::vif(stab_div_mod) not use if one response
+stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
 
-```{r predict}
 pred <- ggpredict(stab_div_mod, terms = c("log_rich"), type = "fe")
@@
 
+#
+bm_div_mod <- lme(data = sem_data,
+  fixed = log_bm ~ log_rich,
+  random = ~ 1 + log_rich | basin,
+  control = ctrl 
+)
+bm_div_sum <- piecewiseSEM::rsquared(bm_div_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
+
+pred <- ggpredict(bm_div_mod, terms = c("log_rich"), type = "fe")
+#plot(pred, add.data = TRUE)
+bm_div_pred <- pred %>%
+  as_tibble() %>%
+  rename(
+    log_bm = predicted,
+    log_rich = x,
+    basin = group
+  )
+```
+
+```{r mod-div-troph}
+stab_troph_mod <- lme(data = na.omit(stab_div_troph),
+  fixed = log_stab ~ log_rich + troph_group + log_rich:troph_group,
+  random = ~ 1 | basin,
+  control = ctrl
+)
+
+stab_troph_colin <- car::vif(stab_troph_mod)
+stab_troph_sum <- piecewiseSEM::rsquared(stab_troph_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
+
+pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
+plot(pred_troph_mod, add.data = TRUE)
+stab_troph_pred <- pred_troph_mod %>%
+  as_tibble() %>%
+  rename(
+    log_stab = predicted,
+    log_rich = x,
+    troph_group = group
+  )
+
+# Productivity and troph group
+
+bm_troph_mod <- lme(data = na.omit(stab_div_troph),
+  fixed = log_bm ~ log_rich * troph_group,
+  random = ~ 1 + log_rich * troph_group | basin,
+  control = ctrl 
+)
+
+bm_troph_sum <- piecewiseSEM::rsquared(bm_troph_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
+
+pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
+#plot(pred_troph_mod, add.data = TRUE)
+bm_troph_pred <- pred_troph_mod %>%
+  as_tibble() %>%
+  rename(
+    log_bm = predicted,
+    log_rich = x,
+    troph_group = group
+  )
 ```
@@
 
-```{r s-div, fig.dim = c(10,5)}
-label_rsq <- "paste(
-  \"Conditional italic(R) ^ 2 == \", round(stab_div_sum$Conditional, 2),
-  \", Marginal italic(R) ^ 2 == \", round(stab_div_sum$Marginal, 2))"
+```{r p-s-div}
+lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
+lim_log_rich <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich")
+filter(stab_div_troph, log_rich < 0)
 # Plot left  
@@
   geom_point() +
-  #scale_x_log10() + scale_y_log10() +
+  ylim(lim_log_stab) +
+  xlim(lim_log_rich) +
   labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
@@
   geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
-  = "grey20", alpha = .5) +
-  annotate("text", x = 1.0, y = .8, label = paste(
-  " Marg. R^2 = ", round(stab_div_sum$Marginal, 2),
-  ", Cond. R^2 = ", round(stab_div_sum$Conditional, 2)
-  )
-    )
+  = "grey20", alpha = .2) +
+  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
+    parse = TRUE)
 
@@
   ) +
-  scale_x_log10() + scale_y_log10() +
-  labs(x = "Average species richness", y = "Biomass stability")
+  ylim(lim_log_stab) +
+  xlim(lim_log_rich) +
+  geom_line(data = stab_troph_pred) +
+  geom_ribbon(data = stab_troph_pred,
+    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
+    alpha = .2) +
+  annotate("text", x = 0.8, y = .8, label = make_label_rsq(rsq = stab_troph_sum),
+    parse = TRUE) +
+  #scale_x_log10() + scale_y_log10() +
+  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)")
 
-plot_grid(p_stab_div, p_stab_div_troph, ncol = 2, rel_widths = c(.4, .6))
+p_stab <- plot_grid(p_stab_div, p_stab_div_troph, ncol = 2, rel_widths = c(.4, .6))
 ```
+
+```{r p-p-div}
+lim_log_bm <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_bm")
+
+p_bm_div <- sem_data %>%
+  ggplot(aes(x = log_rich, y = log_bm))+
+  geom_point() +
+  ylim(lim_log_bm) +
+  xlim(lim_log_rich) +
+  labs(x = "Median species richness (Log 10)", y = " Total biomass(Log 10)") +
+  geom_line(data = bm_div_pred) +
+  geom_ribbon(data = bm_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
+  = "grey20", alpha = .2) +
+  annotate("text", x = 1.0, y = 5, label = make_label_rsq(rsq = bm_div_sum),
+    parse = TRUE)
+
+p_bm_div_troph <- stab_div_troph %>%
+  ggplot(aes(x = log_rich, y = log_bm, color = troph_group)) +
+  geom_point() +
+  ylim(lim_log_bm) +
+  xlim(lim_log_rich) +
+  ggplot2::scale_color_manual(
+    labels = troph_group_labeller(),
+    values = c("blue", "green", "red"),
+    name = "Trophic group"
+  ) +
+  geom_line(data = bm_troph_pred) +
+  geom_ribbon(data = bm_troph_pred,
+    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
+    alpha = .2) +
+  annotate("text", x = 0.8, y = 5, label = make_label_rsq(rsq = bm_troph_sum),
+    parse = TRUE) +
+  #scale_x_log10() + scale_y_log10() +
+  labs(x = "Median species richness (Log 10)", y = "Total biomass (Log 10)")
+
+p_bm <- plot_grid(p_bm_div, p_bm_div_troph, ncol = 2, rel_widths = c(.4, .6))
+```
+
+```{r psbm, fig.dim = c(10,5)}
+plot_grid(p_stab, p_bm, ncol = 1)
+```
+
+- Stability:
+  - decreases with richness
+  - is higher for higher trophic group
+  - increases and decreases with richness for the lower and higher trophic group
+    respectively
+
+- richness on stab:
+  - globally negative
+  -
 
@@
 
+- Stability:
+  - Stability component:
+    - CV is the main driver of stability:
   - Community structure: 
@@
     - Betadiv increases CV
+  - Habitat/Env:
+    - very weak to no direct effect on stability
+      - direct: CV_sp dec with increasing RC3, cad enrichment and flow_cv decrease.  
+    - indirectly affect stability by modulating community structure
 
-- Stability component:
-  - CV is the main driver of stability
+- Total biomass:
+  - Community structure:
+    - Richness increased total biomass / had the bigger effect
+    - Even community deceased total biomass
+    - Species turnover decreased total biomass  
+    - Connectance increased biomass
+  - Habitat/Env:
+    - very weak to no direct effect on total biomass 
+    - Effect of environment is thus mediated by the community structure
+
+- Main outcome
+
+- Latex:
+  - csv:
+    - https://tex.stackexchange.com/questions/178904/use-datatool-to-read-a-row-from-a-csv-file-then-use-the-variables-in-the-docume
+    - https://tex.stackexchange.com/questions/40901/datatool-getting-a-specific-value-given-the-value-of-another-column
+  - path:
 

### 2020-01-20 report/sem_tex/bm_sem.tex
Improve plots + latex path analysis

\documentclass{article}
\def\xcolorversion{2.00}
\def\xkeyvalversion{1.8}

\usepackage[version=0.96]{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri}
\usepackage[latin1]{inputenc}
\usepackage{verbatim}

\begin{document}

\begin{comment}
:Title: A Petri-net for Hagen
:Slug: nodetutorial
:Tags: Manual, Petri net, Graphs

This example is from the tutorial: A Petri-net for Hagen.

| Author: Till Tantau
| Source: The PGF/TikZ manual

\end{comment}

\begin{tikzpicture}[node distance=4cm,->,>=stealth',bend angle=45,auto]

  \tikzstyle{place}=[circle,thick,draw=blue!75,fill=blue!20,minimum
  size=6mm,text centered, inner sep=2pt, text width = 2cm]
  \tikzstyle{red place}=[place,draw=red!75,fill=red!20]
  \tikzstyle{transition}=[rectangle,thick,draw=black!75,
  			  fill=black!20,minimum size=4mm]

  \tikzstyle{every label}=[red]

    % Evt 
    \node [place] (rc3)  {RC3};
    \node [place] (rc2) [left of=rc3] {RC2};
    \node [place] (rc1) [left of=rc2] {RC1};
    \node [place] (rc4) [right of=rc3] {RC4};
    \node [place] (rc5) [right of=rc4] {RC5};

   %Community structure 
    \node [place] (rich) [below of=rc3] {Species richness};
    \node [place] (piel) [left of=rich] {Pielou};
    \node [place] (beta)  [left of=piel] {$\beta$-diversity};
    \node [place] (troph) [right of=rich] {Trophic level};
    \node [place] (c)  [right of=troph] {Connectance};

    %bmility
    \node [place] (bm)  [below of=rich] {Total biomass};

    \path 
	(rc3) edge node[anchor=south,above]{$SC_n=0$} (piel)
	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (rich)
	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (beta)
	(rc3) edge (troph)
	(rc3) edge (c)
	(rc3) edge (bm)

	(rc2) edge (piel)
	(rc2) edge (rich)
	(rc2) edge (beta)
	(rc2) edge (troph)
	(rc2) edge (c)
	(rc2) edge (bm)

	(rc1) edge (piel)
	(rc1) edge (rich)
	(rc1) edge (beta)
	(rc1) edge (troph)
	(rc1) edge (c)
	(rc1) edge (bm)

	(rc4) edge (piel)
	(rc4) edge (rich)
	(rc4) edge (beta)
	(rc4) edge (troph)
	(rc4) edge (c)
	(rc4) edge (bm)

	(rc5) edge (piel)
	(rc5) edge (rich)
	(rc5) edge (beta)
	(rc5) edge (troph)
	(rc5) edge (c)
	(rc5) edge (bm)
	;

    \path 
	(piel)  edge (bm)
	(rich)  edge (bm)
	(beta)  edge (bm)
	(troph) edge (bm)
	(c) edge (bm)
	(bm) edge (bm)
	;

\end{tikzpicture}

\end{document}

### 2020-01-20 report/sem_tex/stab_sem.tex
Improve plots + latex path analysis

--- 2020-01-20 report/sem_tex/bm_sem.tex
@@
 
-    %bmility
-    \node [place] (bm)  [below of=rich] {Total biomass};
+    %Stability
+    \node [place] (cv) [below left of=rich] {$CV_{sp}$};
+    \node [place] (sync) [below right of=rich] {Synchrony};
+    \node [place] (stab)  [below left of=sync] {Biomass stability};
 
@@
 	(rc3) edge (c)
-	(rc3) edge (bm)
+	(rc3) edge (sync)
+	(rc3) edge (cv)
 
@@
 	(rc2) edge (c)
-	(rc2) edge (bm)
+	(rc2) edge (sync)
+	(rc2) edge (cv)
 
@@
 	(rc1) edge (c)
-	(rc1) edge (bm)
+	(rc1) edge (sync)
+	(rc1) edge (cv)
 
@@
 	(rc4) edge (c)
-	(rc4) edge (bm)
+	(rc4) edge (sync)
+	(rc4) edge (cv)
 
@@
 	(rc5) edge (c)
-	(rc5) edge (bm)
+	(rc5) edge (sync)
+	(rc5) edge (cv)
 	;
@@
     \path 
-	(piel)  edge (bm)
-	(rich)  edge (bm)
-	(beta)  edge (bm)
-	(troph) edge (bm)
-	(c) edge (bm)
-	(bm) edge (bm)
+	(piel)  edge (sync)
+	(piel)  edge (cv)
+	(rich)  edge (sync)
+	(rich)  edge (cv)
+	(beta)  edge (sync)
+	(beta)  edge (cv)
+	(troph) edge (sync)
+	(troph) edge (cv)
+	(c) edge (sync)
+	(c) edge (cv)
+	(cv) edge (stab)
+	(sync) edge (stab)
 	;

### 2020-01-20 report/sem_tex/theoric_sem.tex
Improve plots + latex path analysis

--- 2020-01-20 report/sem_tex/bm_sem.tex
@@
 
-\begin{tikzpicture}[node distance=4cm,->,>=stealth',bend angle=45,auto]
+\begin{tikzpicture}[node distance=3.3cm,>=stealth',bend angle=45,auto]
 
@@
 
-    % Evt 
-    \node [place] (rc3)  {RC3};
-    \node [place] (rc2) [left of=rc3] {RC2};
-    \node [place] (rc1) [left of=rc2] {RC1};
-    \node [place] (rc4) [right of=rc3] {RC4};
-    \node [place] (rc5) [right of=rc4] {RC5};
+  \begin{scope}
+    % First net
+    \node [place] (evt) {Environment};
+    \node [place] (com) [below of=evt] {Community structure}
+      edge [pre]                            (evt);
+    \node [place] (stab)  [below of=com] {Biomass\\\
+	stability}
+      edge [pre]                            (com)
+      edge [pre, bend left]                            (evt);
 
-   %Community structure 
-    \node [place] (rich) [below of=rc3] {Species richness};
-    \node [place] (piel) [left of=rich] {Pielou};
-    \node [place] (beta)  [left of=piel] {$\beta$-diversity};
-    \node [place] (troph) [right of=rich] {Trophic level};
-    \node [place] (c)  [right of=troph] {Connectance};
+  \end{scope}
 
-    %bmility
-    \node [place] (bm)  [below of=rich] {Total biomass};
+  \begin{scope}[xshift=6cm]
+    % Second net
+    \node [place] (evt1) {Environment};
+    \node [place] (com1) [below of=evt1] {Community structure}
+      edge [pre]                            (evt1);
+    \node [place] (bm)  [below of=com1] {Total biomass}
+      edge [pre]                            (com1)
+      edge [pre, bend right]                (evt1);
+  \end{scope}
 
-    \path 
-	(rc3) edge node[anchor=south,above]{$SC_n=0$} (piel)
-	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (rich)
-	(rc3) edge node[anchor=south,above]{$SC_n\neq 0$} (beta)
-	(rc3) edge (troph)
-	(rc3) edge (c)
-	(rc3) edge (bm)
-
-	(rc2) edge (piel)
-	(rc2) edge (rich)
-	(rc2) edge (beta)
-	(rc2) edge (troph)
-	(rc2) edge (c)
-	(rc2) edge (bm)
-
-	(rc1) edge (piel)
-	(rc1) edge (rich)
-	(rc1) edge (beta)
-	(rc1) edge (troph)
-	(rc1) edge (c)
-	(rc1) edge (bm)
-
-	(rc4) edge (piel)
-	(rc4) edge (rich)
-	(rc4) edge (beta)
-	(rc4) edge (troph)
-	(rc4) edge (c)
-	(rc4) edge (bm)
-
-	(rc5) edge (piel)
-	(rc5) edge (rich)
-	(rc5) edge (beta)
-	(rc5) edge (troph)
-	(rc5) edge (c)
-	(rc5) edge (bm)
-	;
-
-    \path 
-	(piel)  edge (bm)
-	(rich)  edge (bm)
-	(beta)  edge (bm)
-	(troph) edge (bm)
-	(c) edge (bm)
-	(bm) edge (bm)
-	;
-
+  \begin{pgfonlayer}{background}
+    \filldraw [line width=2cm,join=round,black!10]
+      (evt.north  -| stab.east)  rectangle (stab.south  -| stab.west)
+      (evt1.north -| bm.east) rectangle (bm.south -| bm.west);
+  \end{pgfonlayer}
 \end{tikzpicture}

### 2020-01-20 R/statistical_analysis.R

@@ -39,7 +39,7 @@ compute_sem_dataset <- function (
     dplyr::left_join(sync, by = "station") %>%
     dplyr::rename(sync = synchrony,
       piel = pielou_med,
-      prod = biomass_med 
+      prod = biomass_med
     )
 
   # Composition
@@ -72,7 +72,8 @@ compute_sem_dataset <- function (
       log_rich = log10(richness_med),
       log_sync = log10(sync), 
       log_cv_sp = log10(cv_sp),
-      log_stab = log10(biomass_stab)
+      log_stab = log10(biomass_stab),
+      log_bm = log10(prod)
     )
   return(dsem)
 

### 2020-01-21 manuscript/bef_stability/manuscript.Rmd
Add dataset description: *_network_* and *_community_*

@@
 
-```{r}
+```{r, echo = FALSE}
 mypath <- rprojroot::find_package_root_file
@@
 
-```{r get-data}
+```{r get-data, cache = TRUE}
 library(nlme)
@@
 
-```{r mod-div-troph}
+```{r mod-div-troph, fig.show = "hide"}
 stab_troph_mod <- lme(data = na.omit(stab_div_troph),
@@
 lim_log_rich <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich")
-filter(stab_div_troph, log_rich < 0)
 # Plot left  

### 2020-01-21 report/02-methods.Rmd
Add dataset description: *_network_* and *_community_*

@@
 We describe our methods in this chapter.
+
+## Describe datasets
+
+### Community and network datas
+
+- \*\_analysis (data in general by species and fishing operation):
+  - community_analysis:
+    - by species and by fishing operation:
+      - number of individuals
+      - mean length   
+      - sum of biomass
+  - network_analysis:
+    - by fishing operation:
+      - data:
+	-length, class and species of each individual
+      - network:
+	- feeding link between species in the igraph::graph_from_data_frame()
+	  format
+	- from to: the "from" is eaten by "to", i.e. the biomass goes "from" "to"
+      - composition (by opcod and by species):
+	- troph_level: trophic level of the species
+	- biomass: species biomass
+	- troph_group: high (group 3) or low predator (group 2)
+
+- \*\_metrics (metrics by fishing operation):
+  - community_metrics:
+    - richness: species richness
+    - nind: number of individuals
+    - biomass: sum of biomass
+    - sp_vector: named vector of species biomass (name corresponding to species)
+    - rel_bm: named vector of relative species biomass (name corresponding to species)
+    - pielou: pielou index on biomass distribution of species
+    - simpson: simpson index on biomass distribution of species
+  - network_metrics:
+    - from data to troph_group: see network_analysis
+    - nestedness: network index
+    - modul_guimera: guimera modularity index
+    - diet_overlap: matrix of diet overlap between species pair 
+    - avg_diet_overlap: mean diet overlap between species pair
+    - connectance: network index 
+    - nbnode: nb of nodes in the network (i.e. species or species classes plus
+      resources as detrivor, zooplankton, phytoplankton)
+    - compartiment: compartimentation index of the network 
+    - troph_level_avg: mean trophic level of the network  
+    - troph_length: trophic length of the network
+    - modularity: modeularity of the network
+    - connectance_corrected: residuals of the relationship between connectance
+      and nbnode
+    - modularity_corrected: cf above
+    - troph_level_avg_corrected: cf above 
+    - mean_troph_level_corrected: cf above
+    - w_trph_lvl_avg: mean trophic level of the network WEIGHTED by biomass
+
+- temporal\_\*\_metrics (metrics summarised by station):
+  - temporal_community_metrics (cf community_metrics for the index):
+    - \*\_avg: mean of the index  
+    - \*\_cv: cv of the index
+    - \*\_med: median of the index 
+    - \*\_stab: stab of the index (i.e. 1/cv)
+    - betadiv\_\*: $\beta$-diversity 
+      - betadiv: mean dissimilarity between year for species composition
+      - \*\_bin: binary species composition (0 or 1)
+      - \*\_diag: dissimilarity between year to year (diagonal of the
+	dissimilarity matrix)
+  - temporal_network_metrics (cf network_metrics for the index):
+    - same principle than for temporal_community_metrics
+    - troph_group
+
+### Station data
+
+- op_analysis:
+  - protocol_type: type of fishing (complete or partial)
+  - opcod: id of the fishing operation
+  - date: date (YYYY-MM-DD) of the fishing operation
+  - station: id of the station
+  - protocol: protocole name (complete, partial_by_point, partial_over_bank)
+  - surface: surface sampled
+  - nb_sp: number of the species sampled for the fishing operation
+  - nb_ind: number of the individuals sampled for the fishing operation
+  - year: year at which the fishing operation was done  
+  - length_sourced: length of river fished
 
@@
 
-```{r}
+```{r, eval = FALSE}
 match_st <- match(hab_type$station, com_mat$station)
@@
 ts_biomass <- community_metrics %>%
-  select(station, date, biomass) %>%
+  dplyr::select(station, date, biomass) %>%
   mutate(station = as.character(station)) %>%

### 2020-01-22 report/02-methods.Rmd
Cleaning report

@@
 
-```{r, fig.cap = "Distribution of fish length. Red, green and black respectively locate the median, the mean and the 200mm threshold."}
+```{r, fig.dim = c(4, 4), fig.cap = "Distribution of fish length. Red, green and black respectively locate the median, the mean and the 200mm threshold."}
 myload(length_analysis, dir = mypath("data"))
@@
 
+### Network caracteristics
+
+```{r}
+myload(temporal_network_metrics, dir = mypath("data", "classes"))
+temporal_network_metrics_classes <- temporal_network_metrics
+myload(temporal_network_metrics, dir = dest_dir)
+myload(temporal_community_metrics, synchrony, dir = data_common)
+```
+
+```{r net-cor-med, fig.cap = "Correlation between network indices (median over the temporal series). "}
+# Get network metrics
+
+cor_avg <- temporal_network_metrics %>%
+  select_at(vars(dplyr::matches("med"))) %>%
+  na.omit %>%
+  cor(., method = "spearman")
+#knitr::kable(cor_avg)
+as.data.frame(round(cor_avg,2)) %>%
+  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
+	  "black")))) %>%
+  mutate(variable = colnames(.)) %>%
+  select(variable, everything()) %>%
+  kable(format = "html", escape = F) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "400px")
+```
+
+```{r net-cor-cv, fig.cap="Correlation between network indices (CV over the temporal series). "}
+cor_cv <- temporal_network_metrics %>%
+  select_at(vars(dplyr::matches("cv"))) %>%
+  na.omit %>%
+  cor(., method = "spearman")
+
+as.data.frame(round(cor_cv,2)) %>%
+  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
+	  "black")))) %>%
+  mutate(variable = colnames(.)) %>%
+  select(variable, everything()) %>%
+  kable(format = "html", escape = F) %>%
+  kable_styling() %>%
+  scroll_box(width = "100%", height = "400px")
+
+```
+
+```{r}
+library(ade4)
+library(factoextra)
+
+net_ind <- temporal_network_metrics %>%
+  left_join(select(temporal_community_metrics, station, richness_med)) %>%
+  select_at(vars(dplyr::matches("med")))
+
+res.pca <- dudi.pca(na.omit(net_ind),
+  scannf = FALSE,   # Hide scree plot
+  nf = 5            # Number of components kept in the results
+)
+eig_plot <- fviz_eig(res.pca)
+```
+
+```{r}
+pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
+  fviz_pca_var(res.pca,
+    axes = axes,
+    col.var = "contrib", # Color by contributions to the PC
+    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+    repel = TRUE     # Avoid text overlapping
+  )
+})
+
+plot_grid(eig_plot, pca_plot[[1]], pca_plot[[2]], pca_plot[[3]], labels =
+  "AUTO")
+```
+
 ## Environmental data
@@
 
-```{r pca-hab, fig.dim = c(7, 21), fig.cap = "PCA over habitat description"}
+```{r, fig.cap = "Spearman correlation between environmental variables."}
+m <- cor(as.matrix(select(na.omit(habitat_pressure), -station)), method = "spearman")
+corrplot::corrplot(m, order="hclust", type = "upper", diag = FALSE)
+```
+
+```{r pca-hab, fig.dim = c(10, 7), fig.cap = "PCA over habitat description"}
 library(ade4)
@@
   )
-plot_grid(pca_plot12, pca_plot13, pca_plot23, ncol = 1)
+plot_grid(pca_plot12, pca_plot13, pca_plot23, ncol = 3)
 ```
@@
 
-```{r}
-dev.off()
-m <- cor(as.matrix(select(na.omit(habitat_pressure), -station)), method = "spearman")
-corrplot::corrplot(m, order="hclust", type = "upper", diag = FALSE)
-```
-
-#### 1 rotated PCA
-
-```{r}
+```{r, fig.show = "hide"}
 evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
@@
 )
+```
+
+```{r}
 to_plot <- c(1, 6, 7)
@@
     map(p_l_rot[to_plot], ~.x$normal)
-    ), ncol = length(to_plot))
+    ), ncol = length(to_plot), rel_height = c(.4, .6))
 ```
@@
 
-mysave(habitat_pressure, dir = mypath("report"), overwrite = TRUE)
+mysave(habitat_pressure, pca_pressure, dir = mypath("report"), overwrite = TRUE)
 ```
@@
 
-```{r split-rivers, fig.dim = c(7, 12)}
-hab_type <- na.omit(habitat_pressure) %>%
+```{r split-rivers, fig.dim = c(4, 4)}
+hab_type <- habitat_pressure %>%
   mutate(high_bin = ifelse(alt > median(alt), TRUE, FALSE),
@@
 
-hab_type_pca <- hab_type[hab_type$station %in% na.omit(habitat_pressure)$station, ]
-match_st <- match(hab_type_pca$station, na.omit(habitat_pressure)$station)
-hab_type_pca <- hab_type_pca[order(match_st), ]
-
-pca_cat_river <- fviz_pca_ind(pca_hab, label="none", habillage=hab_type_pca$hab_type,
-  , ellipse.type = "convex",
-             addEllipses=TRUE, ellipse.level=0.95)
-plot_grid(pca_plot, pca_cat_river, ncol = 1)
+#plot_grid(pca_cat_river, ncol = 1)
 mysave(hab_type, dir = mypath("report"), overwrite = TRUE)
@@
 
-```{r, echo = FALSE}
+```{r, fig.dim = c(7, 5), fig.cap = "NMDS on species composition."}
 library(vegan)
@@
 
-stressplot(nmds)
-plot(nmds)
-
 order_st <- match(temporal_community_metrics$station, com_mat$station) 
@@
 
+par(mfrow = c(1, 2))
+stressplot(nmds)
+title("Stress plot")
 bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
@@
   air=0.01, pch = "+", labels = "+")
+title("Color = species richness; Size of points = biomass")
 ```
@@
 
-plot(station_analysis[,"basin"])
 # How many station by basin:
@@
 
-```{r basin-com}
-dev.off()
+```{r basin-com, fig.dim = c(7, 4), fig.cap = "Species composition by group (95% ellipse)"}
 match_st_basin <- match(station_analysis$station, com_mat$station)
@@
 
+par(mfrow = c(1,2))
+
 ordiplot(nmds,type="n")
 orditorp(nmds,display="species",col="red",air=0.01)
+title("Composition by basin")
 # See https://www.davidzeleny.net/anadat-r/doku.php/en:ordiagrams_examples
@@
 for (i in seq_along(u_basin)) {
-  ordihull(nmds, groups = st_basin[["basin"]],
+  ordiellipse(nmds, groups = st_basin[["basin"]],
  show.group = u_basin[i], col = i, draw = 'polygon', label = T)
 }
-```
 
-```{r, eval = FALSE}
-match_st <- match(hab_type$station, com_mat$station)
-hab_type <- hab_type[order(match_st), ]
+tmp_hab_type <- filter(hab_type, station %in% com_mat$station)
+match_st <- match(tmp_hab_type$station, com_mat$station)
+tmp_hab_type <- tmp_hab_type[order(match_st), ]
 ordiplot(nmds,type="points", choices = c(1, 2))
 orditorp(nmds,display="species",col="red",air=0.01)
-u_hab  <- unique(hab_type[["hab_type"]])
+title("Composition by Low / High altitude")
+u_hab  <- unique(tmp_hab_type[["hab_type"]])
 for (i in seq_along(u_hab)) {
-  ordihull(nmds, groups = hab_type[["hab_type"]], alpha = .1,
+  ordiellipse(nmds, groups = tmp_hab_type[["hab_type"]], alpha = .3,
  show.group = u_hab[i], col = i, draw = 'polygon', label = T)
@@
 
-```{r}
-st_basin <- get_basin_station() 
-myload(region_polygon, dir = mypath("data"))
-myload(temporal_network_metrics, dir = mypath("data", "classes"))
-temporal_network_metrics_classes <- temporal_network_metrics
-stab_div_basin <- temporal_network_metrics_classes %>%
-  select(station, troph_group) %>%
-  unnest(troph_group) %>%
-  filter(troph_group != 1) %>%
-  mutate(troph_group = as.factor(troph_group)) %>%
-  select(station, troph_group, biomass_stab, richness_avg) %>%
-  left_join(st_basin, by = "station") %>%
-  filter(!is.na(basin))
-stab_div_basin %>%
-  left_join(hab_type, by = "station") %>%
-  left_join(habitat_pressure[,c("station", "temperature_med", "DBO_med")],
-    by = "station") %>%
-  gather(variable, value, temperature_med, DBO_med) %>%
-  ggplot(aes(x = richness_avg, y = value)) +
-  geom_point() +
-  facet_grid(cols = vars(troph_group), rows = vars(variable), scales = "free_y") +
-  stat_poly_eq(
-    formula = y ~ x,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  geom_smooth(method = "lm", formula = y ~ x) +
-  ggplot2::scale_color_manual(
-    labels = troph_group_labeller(),
-    values = c("blue", "green", "red"),
-    name = "Trophic level"
-    ) +
-  #scale_y_log10() +
-  scale_x_log10() +
-  labs(title = "Stability - Div by habitat type",
-    x = "Average species richness (log10)", y = "Biomass stability (log10)")
-```
-
-#### Species occurence
+#### Species occurrence
 
@@
   )
+
+# Local med occurence
 occurence_sp_st <- com %>%
@@
 
-med_occ <- occurence_sp_st %>%
+global_med_occ <- occurence_sp_st %>%
   dplyr::summarise_if(is.double, list(~median(., na.rm = TRUE))) %>%
@@
 
-med_occ %>%
+p_global_med_occ <- global_med_occ %>%
   ggplot(aes(x = med_occ)) +
-  geom_histogram()
+  geom_histogram() +
+  labs(x = "Median occurrence of species in station")
 
+mysave(occurence_sp_st, dir = mypath("report"), overwrite = TRUE)
 ```
-
-###### Species peripherical globally
-
-```{r stab-sp-occ, fig.dim = c(10, 7), fig.cap = "Relationship between biomass stability and species richness without peripherical species."}
-sp_per <- med_occ[med_occ$med_occ < .30,]$sp
-
-threshold_occ <- c(.10, .30, .50, .80)
-com_wo_per  <- map(threshold_occ, ~ rm_sp_from_com(com = community_analysis, sp_to_rm =
-    med_occ[med_occ$med_occ < .x,]$sp))
-names(com_wo_per) <- threshold_occ
-
-com_data <- list(total = community_analysis)
-com_data <- c(com_data, com_wo_per)
-
-res_sync_per <- map2(com_data, names(com_data), function (.data, .names) {
-
-  sync <- compute_com_synchrony(
-    .op = op_analysis,
-    com = .data)
-  sync$type <- .names 
-  sync$biomass_stab <- 1 / sync$cv_com
-  return(sync)
-
-})
-
-test <- do.call(rbind, res_sync_per)
-
-test %>%
-  ggplot(aes(x = richness_med, y = biomass_stab)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  stat_poly_eq(
-    formula = y ~ x,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  geom_smooth(method = "lm", formula = y ~ x) +
-  facet_grid(cols = vars(type))
-
-```
-
-```{r}
-test %>%
-  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
-  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
-  ggplot(aes(x = log10(richness_med), y = value)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  stat_poly_eq(
-    formula = y ~ x,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  geom_smooth(method = "lm", formula = y ~ x) +
-  facet_grid(cols = vars(type), rows = vars(stab))
-
-```
-
-###### Species peripherical by station
-
-```{r, fig.dim = c(10, 7)}
-
-threshold_occ <- c(0, .10, .30, .60, .90)
-
-res_sync_occ_st <- map_dfr(threshold_occ, function (.threshold) {
-
-  # List of sp to rm
-  sp_to_rm <- occurence_sp_st %>%
-    gather(sp, occ, -station) %>%
-    group_by(station) %>%
-    filter(occ < .threshold) %>%
-    summarise(sp2 = list(unique(sp)))
-
-  # Rm species by station
-  truncated_com <- community_analysis %>%
-    left_join(select(op_analysis, opcod, station), by = "opcod") %>%
-    filter(!is.na(station)) %>%
-    group_by(station) %>%
-    nest() %>%
-    left_join(sp_to_rm, by = "station") %>%
-    mutate(
-      output = map2(data, sp2, function (.data, sp_vec) {
-	rm_sp_from_com(com = .data, sp_to_rm = sp_vec)
-  })
-      ) %>%
-  unnest(output) %>%
-  select(-station)
-
-  sync <- compute_com_synchrony(
-    .op = op_analysis,
-    com = truncated_com)
-
-  sync$type <- .threshold 
-  sync$biomass_stab <- 1 / sync$cv_com
-
-  return(sync)
-    })
-
-res_sync_occ_st %>%
-  select(richness_tot, richness_med, biomass_stab, type) %>%
-  gather(rich_type, richness, richness_med, richness_tot) %>%
-  ggplot(aes(x = richness, y = biomass_stab)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  stat_poly_eq(
-    formula = y ~ x,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  geom_smooth(method = "lm", formula = y ~ x) +
-  facet_grid(cols = vars(type), rows = vars(rich_type))
-```
-
-Removing the peripherical species nor at the global scale neither at the station
-scale do not affect the stability-diversity relationship.
 

### 2020-01-22 report/03-results.Rmd
Cleaning report

--- 2019-11-13 report/03-results.Rmd
@@
 
-```{r net-cor-med, fig.cap = "Correlation between network indices (median over the temporal series). "}
-# Get network metrics
+```{r}
 myload(temporal_network_metrics, dir = mypath("data", "classes"))
@@
 myload(temporal_community_metrics, synchrony, dir = data_common)
-
-cor_avg <- temporal_network_metrics %>%
-  select_at(vars(dplyr::matches("med"))) %>%
-  cor()
-#knitr::kable(cor_avg)
-as.data.frame(round(cor_avg,2)) %>%
-  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
-	  "black")))) %>%
-  mutate(variable = colnames(.)) %>%
-  select(variable, everything()) %>%
-  kable(format = "html", escape = F)
-```
-
-```{r net-cor-cv, fig.cap="Correlation between network indices (CV over the temporal series). "}
-cor_cv <- temporal_network_metrics %>%
-  select_at(vars(dplyr::matches("cv"))) %>%
-  cor()
-as.data.frame(round(cor_cv,2)) %>%
-  mutate_all(funs(cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
-	  "black")))) %>%
-  mutate(variable = colnames(.)) %>%
-  select(variable, everything()) %>%
-  kable(format = "html", escape = F)
-```
-
-```{r}
-library(ade4)
-library(factoextra)
-
-net_ind <- temporal_network_metrics %>%
-  left_join(select(temporal_community_metrics, station, richness_med)) %>%
-  select_at(vars(dplyr::matches("med")))
-
-res.pca <- dudi.pca(na.omit(net_ind),
-  scannf = FALSE,   # Hide scree plot
-  nf = 5            # Number of components kept in the results
-)
-eig_plot <- fviz_eig(res.pca)
-```
-
-```{r}
-pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
-  fviz_pca_var(res.pca,
-    axes = axes,
-    col.var = "contrib", # Color by contributions to the PC
-    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-    repel = TRUE     # Avoid text overlapping
-  )
-})
-
-plot_grid(eig_plot, pca_plot[[1]], pca_plot[[2]], pca_plot[[3]], labels =
-  "AUTO")
 ```
@@
 ```
+
+### Community description
+
+#### Temporal dynamics
+
+```{r}
+myload(community_metrics, dir = data_common)
+```
+
+```{r, fig.dim = c(10, 7)}
+community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
+station_high_low_stab <- temporal_community_metrics %>%
+  arrange(desc(biomass_stab)) %>%
+  slice(c(1:5, (n() - 4):(n() - 0))) %>%
+  select(station) %>%
+  unlist
+names(station_high_low_stab) <- rep(c("high", "low"), each = 5) 
+```
+
+```{r tmp-stab, fig.dim = c(10, 7), fig.cap = "The five lowest and highest biomass stability"}
+temporal_biomass <- community_metrics %>%
+  filter(station %in% station_high_low_stab) %>%
+  mutate(stab_status = ifelse(
+      station %in% station_high_low_stab[names(station_high_low_stab) == "low"],
+      "low", "high")) %>%
+  group_by(stab_status, station) %>%
+  nest() %>%
+  group_by(stab_status) %>%
+  mutate(id_stab = seq_along(station)) %>%
+  unnest()
+ggplot(temporal_biomass, aes(y = biomass, x = date)) +
+  geom_line() +
+  geom_point() +
+  facet_grid(id_stab ~ stab_status, scales = "free_y") +
+  labs(y = "Biomass (g)", x = "Date")
+```
+
+```{r more-stab-troph, fig.dim = c(10, 21), fig.cap = "The four station with the highest biomass stability. Dashed and solid lines represent respectively trophic species in the group 2 and 3."}
+
+# Get biomass by sp node:
+net_sp_troph <- select(network_analysis, opcod, composition) %>%
+  unnest(composition)
+# Get synchrony and cv sp:
+sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis)
+# Get trophic lvl by node
+trophic_level %<>%
+  rename(species = sp_class) %>%
+  mutate(troph_group = get_size_class(trophic_level, NULL, troph_level,
+      trophic_class))
+
+plot_stab <- purrr::map(station_high_low_stab, function (x) {
+  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
+  p + theme(legend.position="none") 
+})
+plot_grid(plotlist = plot_stab, ncol = 2)
+```
+
+```{r less-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
+plot_grid(plotlist = plot_stab[7:10], ncol = 2)
+```
+
+```{r mid-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium biomass stability. See caption of Figure for details."}
+# Middle station 
+plot_stab <- purrr::map(sync_sp_troph$station[209:212], function (x) {
+  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
+  p + theme(legend.position="none") 
+})
+plot_grid(plotlist = plot_stab[1:4], ncol = 2)
+```
+
+```{r 75-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
+# Third quater
+plot_stab <- purrr::map(sync_sp_troph$station[300:304], function (x) {
+  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
+  p + theme(legend.position="none") 
+})
+plot_grid(plotlist = plot_stab[1:4], ncol = 2)
+```
+
+```{r 25-stab-troph, eval = FALSE, fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
+# Third quater
+plot_stab <- purrr::map(sync_sp_troph$station[104:107], function (x) {
+  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
+  p + theme(legend.position="none") 
+})
+plot_grid(plotlist = plot_stab[1:10], ncol = 2)
+```
+
+```{r}
+high_div_station <- temporal_community_metrics %>%
+  arrange(desc(richness_med)) %>%
+  slice(1: 5) %>%
+  select(station) %>%
+  unlist
+```
+
+```{r tmp-richest, fig.dim = c(10, 7), fig.cap = "The five highest rich community."}
+label_stab <- filter(temporal_community_metrics,
+  station %in% high_div_station) %>%
+mutate(
+  x_pos = ymd_hms("2005-01-01T15:00:00"),
+  x_pos = as.Date(x_pos),
+  y_pos = 50000,
+  text = paste0("Stability: ", round(biomass_stab,2)),
+)
+ggplot(filter(community_metrics, station %in% high_div_station),
+  aes(y = biomass, x = date)) +
+  geom_line() +
+  geom_point() +
+  geom_text(data = label_stab, aes(x = x_pos, y = y_pos, label =
+      text), size = 6) +
+  facet_wrap( ~ station) + 
+  labs(y = "Biomass (g)", x = "Date")
+```
+
+```{r}
+myload(network_analysis, network_metrics, dir = dest_dir)
+high_div_troph_group <- network_metrics %>%
+  select(opcod, troph_group) %>%
+  unnest() %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  left_join(select(op_analysis, opcod, station, date)) %>%
+  filter(station %in% high_div_station)
+```
+
+```{r, fig.dim = c(10, 7)}
+ggplot(high_div_troph_group,
+  aes(y = nbnode, x = date, color = troph_group)) +
+  geom_line() +
+  geom_point() +
+  geom_text(data = label_stab,
+    x = ymd_hms("2015-01-01T15:00:00"),
+    y = 3, aes(label =
+      text), size = 6, inherit.aes = FALSE) +
+  facet_wrap( ~ station) + 
+  labs(title = "The five richest station",
+  y = "Fish species richness", x = "Date")
+```
+
+```{r}
+highest_div_grp_3_station <- temporal_network_metrics_classes %>%
+  select(station, troph_group) %>%
+  unnest(troph_group) %>%
+  filter(troph_group == 3) %>%
+  arrange(desc(richness_avg)) %>%
+  slice(1:12) %>%
+  select(station) %>%
+  unlist()
+high_div_troph_group_3 <- network_metrics %>%
+  select(opcod, troph_group) %>%
+  unnest() %>%
+  mutate(troph_group = as.factor(troph_group)) %>%
+  left_join(select(op_analysis, opcod, station, date)) %>%
+  filter(station %in% highest_div_grp_3_station)
+```
+
+```{r, fig.dim = c(10, 7)}
+ggplot(high_div_troph_group_3,
+  aes(y = biomass, x = date, color = troph_group)) +
+  geom_line() +
+  geom_point() +
+  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
+    x = ymd_hms("2015-01-01T15:00:00"),
+    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
+    size = 6, inherit.aes = FALSE) +
+  facet_wrap( ~ station) + 
+  labs(title = "The twelve richest station of superior predator",
+  y = "Biomass of trophic group (g)", x = "Date")
+```
+
+```{r}
+ggplot(high_div_troph_group_3,
+  aes(y = biomass, x = date, color = troph_group)) +
+  geom_line() +
+  geom_point() +
+  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
+    x = ymd_hms("2015-01-01T15:00:00"),
+    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
+    size = 6, inherit.aes = FALSE) +
+  facet_wrap( ~ station) + 
+  labs(title = "The twelve richest station of superior predator",
+  y = "Biomass of trophic group (g)", x = "Date")
+```

### 2020-01-22 report/05-stability.Rmd
Cleaning report

@@
   mutate(troph_group = as.factor(troph_group)) 
+```
+
+### Link biomass stability with community structure
+
+```{r stab-div-mult, fig.dim = c(10, 7), fig.cap = "Link between the stability of biomass and diversity"}
+biomass_com <- temporal_community_metrics %>%
+  left_join(select(synchrony, station, synchrony, cv_sp)) %>%
+  select(biomass_stab, synchrony, cv_sp, richness_cv, richness_med, betadiv) %>%
+  gather(diversity, div_value, richness_med, richness_cv, betadiv) %>%
+  gather(stability, stab_value, biomass_stab, synchrony, cv_sp)
+
+formula <- y ~ x #needed for stat_poly_eq
+qplot(div_value, stab_value, data =  biomass_com, geom = "point") +
+  facet_grid(stability ~ diversity, labeller = mylabel(), scales = "free") +
+  geom_smooth(method = 'lm') +
+  stat_poly_eq(
+    formula = formula,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  labs(x = "Diversity", y = "Stability component")
+```
+
+```{r stab-net, fig.cap = "Link between biomass stability and network structure (median)"}
+# plot
+avg_network <- temporal_network_metrics %>%
+  select_at(vars(dplyr::matches("med|station")))
+biomass_stab_station <- temporal_community_metrics %>%
+  select(station, biomass_stab)
+stab_biomass_net_avg <- left_join(avg_network, biomass_stab_station) %>%
+  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
+  mutate(metrics = str_replace(metrics, "_med", "")) %>%
+  filter(metrics != "nbnode")
+
+# TODO: think about not facetting (list of plots ?)
+# Facet label:
+formula <- y ~ x #needed for stat_poly_eq
+p <- ggplot(stab_biomass_net_avg, aes(y = biomass_stab, x = values)) +
+  geom_point() +
+  facet_wrap(~ metrics, labeller = mylabel(), scales = "free_x") +
+  geom_smooth(method = 'lm') +
+  stat_poly_eq(
+    formula = formula,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  labs(
+    x = "Median of the network indices",
+    y = "Biomass stability"
+  )
+p
 ```
@@
 synchrony %>%
-  left_join(select(temporal_community_metrics, station, richness_med), by =
+  left_join(select(temporal_community_metrics, station), by =
     "station") %>%
@@
 
-### Some temporal series of biomass
-
-#### Total biomass
-
-```{r, fig.dim = c(10, 7)}
-community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
-station_high_low_stab <- temporal_community_metrics %>%
-  arrange(desc(biomass_stab)) %>%
-  slice(c(1:5, (n() - 4):(n() - 0))) %>%
-  select(station) %>%
-  unlist
-names(station_high_low_stab) <- rep(c("high", "low"), each = 5) 
-```
-
-```{r tmp-stab, fig.dim = c(10, 7), fig.cap = "The five lowest and highest biomass stability"}
-temporal_biomass <- community_metrics %>%
-  filter(station %in% station_high_low_stab) %>%
-  mutate(stab_status = ifelse(
-      station %in% station_high_low_stab[names(station_high_low_stab) == "low"],
-      "low", "high")) %>%
-  group_by(stab_status, station) %>%
+### Separate core and peripherical species
+
+#### Species peripherical globally
+
+```{r}
+myload(occurence_sp_st, dir = mypath("report"))
+myload(community_analysis, dir = data_common)
+
+global_med_occ <- occurence_sp_st %>%
+  dplyr::summarise_if(is.double, list(~median(., na.rm = TRUE))) %>%
+  gather(sp, med_occ, everything())
+
+```
+
+Removing the peripherical species nor at the global scale neither at the station
+scale do not affect the stability-diversity relationship.
+
+```{r stab-sp-occ, fig.dim = c(10, 7), fig.cap = "Relationship between biomass stability and species richness without peripherical species."}
+
+threshold_occ <- c(0, .10, .30, .60, .90)
+com_wo_per  <- map(threshold_occ, 
+  ~rm_sp_from_com(com = community_analysis, sp_to_rm =
+    global_med_occ[global_med_occ$med_occ < .x,]$sp))
+names(com_wo_per) <- threshold_occ
+
+res_sync_per <- map2_dfr(com_wo_per, names(com_wo_per), function (.data, .names) {
+
+  sync <- compute_com_synchrony(
+    .op = op_analysis,
+    com = .data)
+  sync$type <- .names 
+  sync$biomass_stab <- 1 / sync$cv_com
+  return(sync)
+
+})
+
+p_sync_global_per <- res_sync_per %>%
+  ggplot(aes(x = richness_med, y = biomass_stab)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  facet_grid(cols = vars(type))
+
+p_sync_global_per
+```
+
+```{r, fig.show = "hide"}
+res_sync_per %>%
+  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
+  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
+  ggplot(aes(x = richness_med, y = value)) +
+  geom_point() +
+  geom_smooth(method = "auto") +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  facet_grid(cols = vars(type), rows = vars(stab), scales = "free_y")
+
+```
+
+#### Species peripherical by station
+
+```{r stab-occ-st, fig.dim = c(10, 7), fig.cap = "Relationship between biomass stability and species richness without peripherical species."}
+
+res_sync_occ_st <- map_dfr(c(threshold_occ, .99), function (.threshold) {
+  # List of sp to rm
+  sp_to_rm <- occurence_sp_st %>%
+    gather(sp, occ, -station) %>%
+    group_by(station) %>%
+    filter(occ < .threshold) %>%
+    summarise(sp2 = list(unique(sp)))
+
+  # Rm species by station
+  truncated_com <- community_analysis %>%
+    left_join(select(op_analysis, opcod, station), by = "opcod") %>%
+    filter(!is.na(station)) %>%
+    group_by(station) %>%
     nest() %>%
-  group_by(stab_status) %>%
-  mutate(id_stab = seq_along(station)) %>%
-  unnest()
-ggplot(temporal_biomass, aes(y = biomass, x = date)) +
-  geom_line() +
-  geom_point() +
-  facet_grid(id_stab ~ stab_status, scales = "free_y") +
-  labs(y = "Biomass (g)", x = "Date")
-```
-
-```{r more-stab-troph, fig.dim = c(10, 21), fig.cap = "The four station with the highest biomass stability. Dashed and solid lines represent respectively trophic species in the group 2 and 3."}
-
-# Get biomass by sp node:
-net_sp_troph <- select(network_analysis, opcod, composition) %>%
-  unnest(composition)
-# Get synchrony and cv sp:
-sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis)
-# Get trophic lvl by node
-trophic_level %<>%
-  rename(species = sp_class) %>%
-  mutate(troph_group = get_size_class(trophic_level, NULL, troph_level,
-      trophic_class))
-
-plot_stab <- purrr::map(station_high_low_stab, function (x) {
-  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
-  p + theme(legend.position="none") 
+    left_join(sp_to_rm, by = "station") %>%
+    mutate(
+      output = map2(data, sp2, function (.data, sp_vec) {
+	rm_sp_from_com(com = .data, sp_to_rm = sp_vec)
   })
-plot_grid(plotlist = plot_stab, ncol = 2)
-```
-
-```{r less-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
-plot_grid(plotlist = plot_stab[7:10], ncol = 2)
-```
-
-```{r mid-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium biomass stability. See caption of Figure for details."}
-# Middle station 
-plot_stab <- purrr::map(sync_sp_troph$station[209:212], function (x) {
-  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
-  p + theme(legend.position="none") 
+      ) %>%
+  unnest(output) %>%
+  select(-station)
+
+  sync <- compute_com_synchrony(
+    .op = op_analysis,
+    com = truncated_com)
+
+  sync$type <- .threshold 
+  sync$biomass_stab <- 1 / sync$cv_com
+
+  return(sync)
     })
-plot_grid(plotlist = plot_stab[1:4], ncol = 2)
-```
-
-```{r 75-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
-# Third quater
-plot_stab <- purrr::map(sync_sp_troph$station[300:304], function (x) {
-  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
-  p + theme(legend.position="none") 
-})
-plot_grid(plotlist = plot_stab[1:4], ncol = 2)
-```
-
-```{r 25-stab-troph, eval = FALSE, fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
-# Third quater
-plot_stab <- purrr::map(sync_sp_troph$station[104:107], function (x) {
-  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
-  p + theme(legend.position="none") 
-})
-plot_grid(plotlist = plot_stab[1:10], ncol = 2)
-```
+
+p_sync_local_per <-  res_sync_occ_st %>%
+  select(richness_tot, richness_med, biomass_stab, type) %>%
+  gather(rich_type, richness, richness_med, richness_tot) %>%
+  ggplot(aes(x = richness, y = biomass_stab)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  facet_grid(cols = vars(type), rows = vars(rich_type))
+p_sync_local_per
+```
+
+The removal of peripheral species does not change the relationship between stability and species richness meaning that this relation is due to species present most of the time.
 
@@
 library(factoextra)
-myload(habitat_pressure, dir = mypath("report"))
+myload(habitat_pressure, pca_pressure, dir = mypath("report"))
 ```
@@
 left_join(div_troph_grp, by = "station")
-pca_hab <- dudi.pca(as.data.frame(select(na.omit(hab_press_div), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)
-
-eig_plot <- fviz_eig(pca_hab)
-pca_plot <- fviz_pca_var(pca_hab,
-    axes = c(1, 2),
-    col.var = "contrib", # Color by contributions to the PC
-    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-    repel = TRUE     # Avoid text overlapping
-  )
-
-ggdraw(pca_plot) + 
-  draw_plot(eig_plot, x = .9, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
-```
-
-```{r}
-m <- cor(as.matrix(select(na.omit(hab_press_div), -station)), method =
-  "spearman")
-corrplot::corrplot(m, order="hclust")
-```
-
-```{r, eval = FALSE}
-mod <- lm(high_cv ~ temperature + richness_med:temperature + DBO + lat + insecticides + herbicides + insecticides, hab_press_div)
-car::vif(mod)
-
-mod <- lm(mid_cv ~ richness_med + DBO + lat + temperature + insecticides + herbicides + insecticides, hab_press_div)
-car::vif(mod)
+pca_hab <- dudi.pca(as.data.frame(select(pca_pressure, -station)), scannf = FALSE, nf = 5, center = TRUE, scale = TRUE)
+
+supp_var <- pca_pressure %>%
+  select(station) %>%
+  left_join(select(temporal_community_metrics, station, biomass_stab,
+      richness_med), by = "station")
+#check
+stopifnot(all(pca_pressure$station == supp_var$station))
+
+pca_stab <- fviz_pca_biplot(
+  pca_hab, geom = "point",
+  col.ind = (supp_var$biomass_stab),
+  pointsize = 2,
+  gradient.cols = "RdYlBu",
+) %>% 
+ggpubr::ggpar(title = "Biomass stability")
+
+pca_rich <- fviz_pca_biplot(
+  pca_hab, geom = "point",
+  col.ind = supp_var$richness_med,
+  gradient.cols = "RdYlBu",
+  pointsize = 2,
+) %>% 
+ggpubr::ggpar(title = "Species richness")
+plot_grid(pca_stab, pca_rich)
 ```
@@
   labs(x = "Biomass of the trophic group (g)", y = "CV of the species")
-
 ```
@@
   labs(x = "Species richness of the trophic group", y = "CV of the species")
-```
-
-#### Temporal dynamics in high diversity community
-
-```{r}
-high_div_station <- temporal_community_metrics %>%
-  arrange(desc(richness_med)) %>%
-  slice(1: 5) %>%
-  select(station) %>%
-  unlist
-```
-
-```{r tmp-richest, fig.dim = c(10, 7), fig.cap = "The five highest rich community."}
-label_stab <- filter(temporal_community_metrics,
-  station %in% high_div_station) %>%
-mutate(
-  x_pos = ymd_hms("2005-01-01T15:00:00"),
-  x_pos = as.Date(x_pos),
-  y_pos = 50000,
-  text = paste0("Stability: ", round(biomass_stab,2)),
-)
-ggplot(filter(community_metrics, station %in% high_div_station),
-  aes(y = biomass, x = date)) +
-  geom_line() +
-  geom_point() +
-  geom_text(data = label_stab, aes(x = x_pos, y = y_pos, label =
-      text), size = 6) +
-  facet_wrap( ~ station) + 
-  labs(y = "Biomass (g)", x = "Date")
-```
-
-```{r}
-myload(network_analysis, network_metrics, dir = dest_dir)
-high_div_troph_group <- network_metrics %>%
-  select(opcod, troph_group) %>%
-  unnest() %>%
-  mutate(troph_group = as.factor(troph_group)) %>%
-  left_join(select(op_analysis, opcod, station, date)) %>%
-  filter(station %in% high_div_station)
-```
-
-```{r, fig.dim = c(10, 7)}
-ggplot(high_div_troph_group,
-  aes(y = nbnode, x = date, color = troph_group)) +
-  geom_line() +
-  geom_point() +
-  geom_text(data = label_stab,
-    x = ymd_hms("2015-01-01T15:00:00"),
-    y = 3, aes(label =
-      text), size = 6, inherit.aes = FALSE) +
-  facet_wrap( ~ station) + 
-  labs(title = "The five richest station",
-  y = "Fish species richness", x = "Date")
-```
-
-```{r}
-highest_div_grp_3_station <- temporal_network_metrics_classes %>%
-  select(station, troph_group) %>%
-  unnest(troph_group) %>%
-  filter(troph_group == 3) %>%
-  arrange(desc(richness_avg)) %>%
-  slice(1:12) %>%
-  select(station) %>%
-  unlist()
-high_div_troph_group_3 <- network_metrics %>%
-  select(opcod, troph_group) %>%
-  unnest() %>%
-  mutate(troph_group = as.factor(troph_group)) %>%
-  left_join(select(op_analysis, opcod, station, date)) %>%
-  filter(station %in% highest_div_grp_3_station)
-```
-
-```{r, fig.dim = c(10, 7)}
-ggplot(high_div_troph_group_3,
-  aes(y = biomass, x = date, color = troph_group)) +
-  geom_line() +
-  geom_point() +
-  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
-    x = ymd_hms("2015-01-01T15:00:00"),
-    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
-    size = 6, inherit.aes = FALSE) +
-  facet_wrap( ~ station) + 
-  labs(title = "The twelve richest station of superior predator",
-  y = "Biomass of trophic group (g)", x = "Date")
-```
-
-```{r}
-ggplot(high_div_troph_group_3,
-  aes(y = biomass, x = date, color = troph_group)) +
-  geom_line() +
-  geom_point() +
-  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
-    x = ymd_hms("2015-01-01T15:00:00"),
-    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
-    size = 6, inherit.aes = FALSE) +
-  facet_wrap( ~ station) + 
-  labs(title = "The twelve richest station of superior predator",
-  y = "Biomass of trophic group (g)", x = "Date")
 ```
@@
 difficult to see a pattern.
-
-### Link biomass stability with community structure
-
-```{r stab-div-mult, fig.dim = c(10, 7), fig.cap = "Link between the stability of biomass and diversity"}
-biomass_com <- temporal_community_metrics %>%
-  left_join(select(synchrony, station, synchrony, cv_sp)) %>%
-  select(biomass_stab, synchrony, cv_sp, richness_cv, richness_med, betadiv) %>%
-  gather(diversity, div_value, richness_med, richness_cv, betadiv) %>%
-  gather(stability, stab_value, biomass_stab, synchrony, cv_sp)
-
-formula <- y ~ x #needed for stat_poly_eq
-qplot(div_value, stab_value, data =  biomass_com, geom = "point") +
-  facet_grid(stability ~ diversity, labeller = mylabel(), scales = "free") +
-  geom_smooth(method = 'lm') +
-  stat_poly_eq(
-    formula = formula,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  labs(x = "Diversity", y = "Stability component")
-```
-
-```{r stab-net, fig.cap = "Link between biomass stability and network structure (median)"}
-# plot
-avg_network <- temporal_network_metrics %>%
-  select_at(vars(dplyr::matches("med|station")))
-biomass_stab_station <- temporal_community_metrics %>%
-  select(station, biomass_stab)
-stab_biomass_net_avg <- left_join(avg_network, biomass_stab_station) %>%
-  gather(metrics, values, colnames(select_at(., vars((dplyr::matches("med")))))) %>%
-  mutate(metrics = str_replace(metrics, "_med", "")) %>%
-  filter(metrics != "nbnode")
-
-# TODO: think about not facetting (list of plots ?)
-# Facet label:
-formula <- y ~ x #needed for stat_poly_eq
-p <- ggplot(stab_biomass_net_avg, aes(y = biomass_stab, x = values)) +
-  geom_point() +
-  facet_wrap(~ metrics, labeller = mylabel(), scales = "free_x") +
-  geom_smooth(method = 'lm') +
-  stat_poly_eq(
-    formula = formula,
-    eq.with.lhs = "italic(hat(y))~`=`~",
-    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
-    parse = TRUE) +
-  labs(
-    x = "Median of the network indices",
-    y = "Biomass stability"
-  )
-p
-```
 
@@
 ```{r colin_prod, fig.cap = "Colinearity check for total biomass"}
-car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + evt_med1 + evt_med2 + evt_cv1 + evt_cv2, random = ~ 1 | basin, data = sem_data)) %>%
+car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + RC1 + RC2 + RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data)) %>%
   enframe %>%

### 2020-01-31 manuscript/bef_stability/manuscript.Rmd
Switch to lm4 + bootstrap

@@
   message = FALSE,
-  warning = FALSE
+  warning = FALSE,
+  results = FALSE
 )
@@
 
-stab_div_troph <- temporal_network_metrics %>%
+stab_div_troph <- temporal_network_metrics_classes %>%
   dplyr::select(station, troph_group) %>%
@@
   )
+
 ```
@@
 ctrl <- lmeControl(opt='optim')
-ctrl_lmer <- lmerControl(optCtrl = list(method = 'optim'))
-stab_div_mod <- lmer(data = sem_data,
-  #control = ctrl_lmer,
+ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
+#If we want that the model converges with basin as random slope,
+# we have to remove basin with low data
+sem_data %>% group_by(basin) %>% summarise(n())
+stab_div_mod <- lmer(
+  data = sem_data,
+  control = ctrl_lmer,
   formula = log_stab ~ log_rich + (1 | basin)
 )
+
 stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
@@
 #
-bm_div_mod <- lme(data = sem_data,
-  fixed = log_bm ~ log_rich,
-  random = ~ 1 + log_rich | basin,
-  control = ctrl 
+bm_div_mod <- lmer(data = sem_data,
+  formula = log_bm ~ log_rich + (1 | basin)
 )
@@
 ```{r mod-div-troph, fig.show = "hide"}
-stab_troph_mod <- lme(data = na.omit(stab_div_troph),
-  fixed = log_stab ~ log_rich + troph_group + log_rich:troph_group,
-  random = ~ 1 | basin,
-  control = ctrl
+stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
+  formula = log_stab ~ log_rich + troph_group + log_rich:troph_group + (1 | basin)
+  #control = ctrl
 )
+mySumm2 <- function(.) {
+  c(beta=fixef(.),sigma=sigma(.), sig01=sqrt(unlist(VarCorr(.))))
+}
+stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
+#plot(test,index=2)
+stab_troph_ci <- confint(test)
 
@@
 p_bm_sem <- ggpiecewisesem(bm_sem)
+```
+
+```{r get-sem-coeff}
+coef_stab_sem <- coef(stab_sem) %>%
+  group_by(Response) %>%
+  nest() %>%
+  mutate(sum_c = map_dbl(data, ~ sum(.x$Std.Estimate)))
+
+#cor_mat <- cor(sem_data[, !names(sem_data) %in% c("station", "basin")])
 ```
@@
 
-- Main outcome
+- Main outcome:
+
+The effect of richness on biomass stability follows a power law with a negative
+coefficient, meaning that it's a decelerating function.
 
@@
 
+# Appendix
+
+```{r}
+mod_list <- list(bm_div_mod, bm_troph_mod, stab_div_mod, stab_troph_mod)
+plot_res <- map(mod_list, ~ plot(.x))
+plot_grid(plotlist = plot_res)
+```
+
 # References

### 2020-01-31 report/02-methods.Rmd
Try to cover some issues with sampling effort

@@
   "AUTO")
+```
+
+## Fishing methods
+
+```{r}
+myload(env_analysis, biomass_ts_sax, dir = data_common)
+```
+
+```{r}
+census <- op_analysis %>%
+  left_join(select(env_analysis, station, opcod, width_river))
+
+census %>%
+  ggplot(aes(y = length_sourced, x = width_river, color = protocol_type)) +
+  scale_x_log10() +
+  scale_y_log10() +
+  geom_point()
+```
+
+```{r}
+census %>%
+  group_by(station) %>%
+  arrange(year) %>%
+  nest()
+bm_census <-  biomass_ts_sax %>%
+  unnest(data) %>%
+  left_join(mutate(census, station = as.character(station)),
+    by = c("station", "date"))
+```
+
+```{r}
+# Test how sampled effort is linked to biomass
+mod_bm_census <- bm_census %>%
+  group_by(station, protocol_type) %>%
+  #mutate(biomass = scale(biomass)) %>%
+  nest() %>%
+  filter(!is.na(station)) %>%
+  mutate(
+    mod_w_l = map(data, ~lm(length_sourced ~ width_river, data = .x)),
+    data_w_l = map(mod_w_l, broom::augment),
+    data_resid = map2(data, data_w_l,
+      function(raw, augmented) {
+	raw$resid_length <- augmented[[".resid"]]
+        return(raw)
+      }),
+    model = map(data_resid, ~lm(biomass ~ resid_length, data = .x)),
+    coeff = map(model, broom::tidy),
+    summary = map(model, broom::glance)
+  )
+
+mod_bm_census %>%
+  unnest(coeff) %>%
+  #rename(interp = `(Intercept)`, slope = length_sourced) %>%
+  filter(! term %in% "(Intercept)") %>%
+  mutate(effect_size = estimate / std.error) %>%
+  #select(station, term, estimate) %>%
+  #spread(term, estimate) %>%
+  ggplot(aes(x = estimate)) +
+  geom_histogram() +
+  geom_vline(aes(xintercept = mean(estimate)))
+
+```
+
+```{r}
+
+mod_bm_census %>%
+  unnest(coeff) %>%
+  filter(! term %in% "(Intercept)")
+
+residuals(mod_bm_census$model[[9]])
+mod_bm_census$model[[9]]
+mod_bm_census$data[[9]]
 ```

### 2020-01-31 report/03-results.Rmd
Try to cover some issues with sampling effort

@@
 myload(temporal_community_metrics, synchrony, dir = data_common)
+source(mypath("R", "local_network_build.R"))
 ```
@@
 ```{r more-stab-troph, fig.dim = c(10, 21), fig.cap = "The four station with the highest biomass stability. Dashed and solid lines represent respectively trophic species in the group 2 and 3."}
-
+myload(trophic_level, trophic_class, dir = mypath("data"))
 # Get biomass by sp node:

### 2020-01-31 report/05-stability.Rmd
Try to cover some issues with sampling effort

@@
 myload(network_analysis, dir = mypath("data", "classes"))
-myload( trophic_level, trophic_class, dir = mypath("data"))
+myload(trophic_level, trophic_class, dir = mypath("data"))
 myload(hab_type, habitat_pressure, dir = mypath("report"))
@@
 
+### Stability by habitat type
+
 ```{r}
@@
 \@ref(fig:bimod-stab-div)) seemed to work only in station far from the source
-(which are deeper, hotter, wider, fig. \@ref(fig:pca-hab))). It should be the
-place where the ANG is the most present. The ANG were effectively more abundant
-in the latter station (Figure: \@ref(fig:ang-map-bio)).
+(which are deeper, hotter, wider, fig. \@ref(fig:pca-hab))). May be there are
+difference in richness distribution.
+
+```{r}
+plot_bin_rich_div <- function (env = NULL) {
+
+  habitat_pressure$env_bin <- ifelse(
+    habitat_pressure[[env]] < median(habitat_pressure[[env]], na.rm = TRUE),
+    "inf", "sup")
+  habitat_pressure <- na.omit(habitat_pressure[, c("station", "env_bin")])
+  habitat_pressure %>%
+    left_join(stab_div_basin, by = "station") %>%
+    ggplot(aes(x = richness_avg, color = troph_group)) +
+    geom_histogram() +
+    facet_grid(cols = vars(env_bin)) +
+    ggplot2::scale_color_manual(
+      labels = troph_group_labeller(),
+      values = c("blue", "green", "red"),
+      name = "Trophic level"
+    ) +
+  labs(title = env, x = "Average species richness", y = "Frequency") +
+  theme(legend.position = "none")
+}
+
+mult_plot_rich_div_bin <- map(env, ~plot_bin_rich_div(env = .x))
+plot_grid(plotlist = mult_plot_rich_div_bin, ncol = 2)
+```
 
@@
 
+```{r, fig.cap = "histogram of species occurence by station"}
+hist(as.matrix(occurence_sp_st[, !names(occurence_sp_st) %in% "station"])) 
+```
+
+```{r, fig.dim = c(14, 14), fig.cap = "Histogram of species evaluation"}
+occurence_sp_st[, !names(occurence_sp_st) %in% "station"] %>%
+  gather(species, occurence) %>%
+  ggplot(aes(x = occurence)) +
+  geom_histogram() +
+  geom_vline(data = rename(global_med_occ, species = sp, occurence = med_occ),
+    aes(xintercept = occurence), color = "red") +
+  facet_wrap(~species, scales = "free_y")
+```
+
 ```{r stab-occ-st, fig.dim = c(10, 7), fig.cap = "Relationship between biomass stability and species richness without peripherical species."}
@@
 
+#### Remove most abundant species
+
+```{r}
+threshold_occ <- c(.50, .80, .90, 1)
+com_wo_core  <- map(threshold_occ, 
+  ~rm_sp_from_com(com = ungroup(community_analysis), sp_to_rm =
+    global_med_occ[global_med_occ$med_occ > .x,]$sp))
+names(com_wo_core) <- threshold_occ
+
+res_sync_core <- map2_dfr(com_wo_core, names(com_wo_core), function (.data, .names) {
+
+  sync <- compute_com_synchrony(
+    .op = op_analysis,
+    com = .data, presence_threshold = NA)
+  sync$type <- .names 
+  sync$biomass_stab <- 1 / sync$cv_com
+  return(sync)
+
+})
+
+p_sync_global_core <- res_sync_core %>%
+  ggplot(aes(x = richness_med, y = biomass_stab)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  stat_poly_eq(
+    formula = y ~ x,
+    eq.with.lhs = "italic(hat(y))~`=`~",
+    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+    parse = TRUE) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  facet_grid(cols = vars(type))
+
+p_sync_global_core
+
+```
+
+#### Remove low richness
+
+```{r}
+sync_rm <- map_dfr(seq(0, 10, 1),
+  function (x)
+    filter(synchrony, !richness_tot < x) %>%
+      mutate(min_rich = x) 
+)
+sync_rm_res <- sync_rm %>%
+  mutate(
+    log_rich = log10(richness_med),
+    log_stab = log10(1/cv_com)) %>%
+  group_by(min_rich) %>%
+  nest() %>%
+  mutate(
+    model = map(data, ~ lm(log_stab ~ log_rich, .x)),
+    coeff = map(model, broom::tidy),
+    plot = map2(.x = data, .y = min_rich,
+      ~ .x %>%
+	ggplot(aes(x = richness_med, y = 1/cv_com)) +
+	geom_point() +
+	geom_smooth(method = "lm") +
+	stat_poly_eq(
+	  formula = y ~ x,
+	  eq.with.lhs = "italic(hat(y))~`=`~",
+	  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
+	  parse = TRUE) +
+	labs(title = .y)
+      )
+  )
+plot_grid(plotlist = sync_rm_res$plot)
+```
+
+```{r}
+sync_rm_res %>%
+  unnest(coeff) %>%
+  rename(est = estimate, se = std.error) %>%
+  filter(term == "log_rich") %>%
+  ggplot(aes(y = est, x = min_rich)) +
+  geom_point() +
+  geom_errorbar(aes(ymin = est - 2 * se, ymax = est + 2 * se)) +
+  geom_hline(yintercept = 0) +
+  labs(y = "Slope of linear relationship between Biomass stability and median species richness ()")
+```
+
+In fact, the removal of low species station has an notable effect if the
+richness cut was done on median richness. However, if total richness is
+considered, the removal has far less effect.
+
 ### CV sp
@@
 ```{r abun-sp, fig.dim = c(10, 7), fig.cap = "Species most abundant by trophic group."}
+net_sp_troph <- select(network_analysis, opcod, composition) %>%
+  unnest(composition)
+# Get synchrony and cv sp:
+sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis)
 # Sp the most abundant by group
@@
 myload(nmds, dir = mypath("report"))
+myload(network_metrics, dir = mypath("data", "species"))
 
@@
 com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))
-
 # Compute sem dataset 

### 2020-02-04 manuscript/bef_stability/manuscript.Rmd
Add coefficient table + new richness sem

@@
 library(cowplot)
+library(kableExtra)
 source(mypath("R", "misc.R"))
@@
   )
-
 ```
@@
 $$
-S_i = 10^(\beta_0) \times 10^(\beta_R\Log(x_{Ri})) * 10^(\epsilon_{ij})
+S_i = 10^(\beta_0) \times 10^(\beta_R\Log(x_{Ri})) \times 10^(\epsilon_{ij})
+$$
+
+$$
+S_i = 10^(\beta_{0}) \times x_{Ri}10^(\beta_{R}) \times 10^(\epsilon_{ij})
 $$
@@
 ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
-#If we want that the model converges with basin as random slope,
-# we have to remove basin with low data
-sem_data %>% group_by(basin) %>% summarise(n())
 stab_div_mod <- lmer(
@@
 )
-
 stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
@@
     basin = group
+  )
+stab_div_pred %<>%
+  mutate(
+    stab = 10^log_stab, # FALSE
+    rich = 10^log_rich,
+    cl10 =  10^conf.low,
+    ch10 =  10^conf.high
   )
@@
 stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
-#plot(test,index=2)
-stab_troph_ci <- confint(test)
+stab_troph_ci <- confint(stab_troph_boot)
 
@@
 pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
-plot(pred_troph_mod, add.data = TRUE)
+#plot(pred_troph_mod, add.data = TRUE)
 stab_troph_pred <- pred_troph_mod %>%
@@
 
-bm_troph_mod <- lme(data = na.omit(stab_div_troph),
-  fixed = log_bm ~ log_rich * troph_group,
-  random = ~ 1 + log_rich * troph_group | basin,
-  control = ctrl 
+bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
+  #fixed = log_bm ~ log_rich * troph_group,
+  formula = log_bm ~ log_rich + troph_group + log_rich:troph_group + (1 | basin)
+  #random = ~ 1 + log_rich * troph_group | basin,
+  #control = ctrl 
 )
+bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
+bm_troph_ci <- confint(bm_troph_boot)
 
@@
 ```{r}
-
 # Compute SEMs
 stab_sem <- compute_stab_sem(.data = sem_data,
+  random_effect = as.formula("~1|basin"))
+stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
   random_effect = as.formula("~1|basin"))
@@
 p_bm_sem <- ggpiecewisesem(bm_sem)
+p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
 ```
@@
 # Plot left
+
 p_stab_div <- sem_data %>%
@@
   xlim(lim_log_rich) +
+  #scale_y_log10() +
+  #scale_x_log10() +
   labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
-  geom_line(data = stab_div_pred) +
   geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
@@
 
+## Model summary and diagnostics
+
+### Biomass and stability models
+
+```{r tab-coeff-bm, fig.cap = "Coefficient"}
+# Replacement rules for term
+rp_est <- c(
+  "(Intercept)" =     "intercept",
+  "sd\\_\\(intercept\\)\\.basin" = "sd intercept basin",
+  "log_rich" =     "Median richness (log base 10)",
+  "troph_group3" =     "high trophic group",
+  "log_rich:troph_group3" =     "Median richness (log10) : high trophic group",
+  "sig01.basin" =     "sd intercept basin",
+  "sd_Observation.Residual" =     "residuals",
+  "sigma" = "residuals"
+)
+# Replacement rules for group
+rp_group <- c(
+  "fixed" = "Fixed",
+  "basin" = "Random"
+)
+
+```
+
+```{r}
+test <- map2_dfr(list(bm_troph_ci, stab_troph_ci), list(bm_troph_mod, stab_troph_mod),
+  clean_summary_mod, term_rp = rp_est, group_rp = rp_group)
+
+kable(test) %>%
+  pack_rows("Biomass", 1, 6) %>%
+  pack_rows("Stab", 7, 12)
+```
+
+### SEM
+
+```{r tab-coeff-stab}
+
+```
+
+## Model residuals
+
+### Biomass and stability models
+
 ```{r}
@@
 
+### SEM linear relationship
+
+```{r}
+```
+
+## Relationship at the absolute scale, i.e. not the logarythme scale
+
+```{r}
+ggplot(sem_data, aes(x = richness_med, y = biomass_stab)) +
+  geom_point()
+test <- tibble(
+  richness_med = seq(1,20, length.out = 100),
+  biomass_stab =
+    10^(fixef(stab_div_mod)[1])*richness_med^fixef(stab_div_mod)[2]
+)  
+```
+
 # References

### 2020-02-04 report/05-stability.Rmd
Add coefficient table + new richness sem

@@
 source(mypath("R", "local_network_build.R"))
+select <- dplyr::select
 stab_div_troph <- temporal_network_metrics_classes %>%
@@
   spread(troph_group, biomass_avg) %>%
-  mutate(bm_h_m = `3` / (`3` + `2`)) %>%
+  mutate(bm_h_m = `3` / (`2` + `3`)) %>%
   select(station, bm_h_m)
+
+ratio_bm %>%
+  left_join(select(temporal_community_metrics, station, biomass_stab)) %>%
+  ggplot(aes(x = bm_h_m, y = biomass_stab)) +
+  geom_point() +
+  scale_x_log10()
 

### 2020-02-04 R/statistical_analysis.R

@@ -35,11 +35,12 @@ compute_sem_dataset <- function (
   sync %<>% dplyr::select(station, synchrony, cv_sp)
   biomass_sem <- com %>%
     dplyr::select(station, biomass_stab, biomass_med, richness_med, pielou_med,
-      beta_bin_c) %>%
+      betadiv_bin, beta_bin_c) %>%
     dplyr::left_join(sync, by = "station") %>%
     dplyr::rename(sync = synchrony,
       piel = pielou_med,
-      prod = biomass_med
+      prod = biomass_med,
+      beta_bin = betadiv_bin
     )
 
   # Composition
@@ -49,14 +50,14 @@ compute_sem_dataset <- function (
 
   # Habitat -----------------------------------------------------------------
   habitat_sem <- hab_press %>% 
-    dplyr::select(station, lat, alt, width_river_mean, DBO_med, DBO_cv, flow_med, flow_cv,
-      temperature_med, temperature_cv, RC1, RC2, RC3, RC4, RC5) %>%
-    dplyr::rename(width = width_river_mean)
+    dplyr::select(station, RC1, RC2, RC3, RC4, RC5)
 
   # Network -----------------------------------------------------------------
   net_sem <- network %>%
-    dplyr::select(station, connectance_corrected_med, w_trph_lvl_avg_med) %>%
-    dplyr::rename(c_c = connectance_corrected_med,
+    dplyr::select(station, connectance_med, connectance_corrected_med, w_trph_lvl_avg_med) %>%
+    dplyr::rename(
+      c = connectance_med,
+      c_c = connectance_corrected_med,
       t_lvl = w_trph_lvl_avg_med)
 
   # Merge and return --------------------------------------------------------
@@ -83,6 +84,23 @@ compute_sem_dataset <- function (
 #'
 #' @param .data data.frame
 #'
+compute_stab_sem_rich <- function(.data, random_effect = "~ 1 | basin") {
+  corsem <- piecewiseSEM::psem(
+    nlme::lme(log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5,  random = ~ 1 | basin, data = .data),
+    nlme::lme(piel ~ RC1 + RC2 + RC3 + RC4 + RC5, random = ~ 1 | basin, data = .data),
[…]

### 2020-02-05 manuscript/bef_stability/manuscript.Rmd
Add numbers for the linear models

@@
 
-```{r get-data, cache = TRUE}
+```{r get-data, cache = FALSE}
 library(nlme)
@@
 stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
+stab_div_boot <- bootMer(stab_div_mod, mySumm2, nsim = 100)
+stab_div_ci <- confint(stab_div_boot)
 #stab_div_colin <- car::vif(stab_div_mod) not use if one response
@@
 )
+bm_div_boot <- bootMer(bm_div_mod, mySumm2, nsim = 100)
+bm_div_ci <- confint(bm_div_boot)
 bm_div_sum <- piecewiseSEM::rsquared(bm_div_mod, method = "nagelkerke") %>%
@@
   )
+
+# get coeff
+coef_div <- map(list(stab = stab_div_mod, bm = bm_div_mod), fixed.effects)
 ```
@@
 )
-mySumm2 <- function(.) {
-  c(beta=fixef(.),sigma=sigma(.), sig01=sqrt(unlist(VarCorr(.))))
-}
 stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
@@
   )
+
+# get coeff
+coef_troph <- map(list(stab = stab_troph_mod, bm = bm_troph_mod), fixed.effects)
 ```
@@
   labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
+  geom_line(data = stab_div_pred) +
   geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
@@
 plot_grid(p_stab, p_bm, ncol = 1)
+
+print_coef <- function (vec){
+  round(abs(vec)*100)
+}
+print_ci <- function(.df){
+  .df <- round(.df, 3)*100
+
+  paste0("[", .df[["2.5 %"]],";",.df[["97.5 %"]] ,"]")
+}
+
+```
+
+```{r print-coef-stab}
+# Coefficients
+s_co_i <- print_coef(coef_div$stab["(Intercept)"])
+s_co_r <- print_coef(coef_div$stab["log_rich"])
+s_co_t <- print_coef(coef_troph$stab["troph_group3"])
+s_co_r_t2 <- print_coef(coef_troph$stab["log_rich"])
+s_co_r_t3 <- print_coef(coef_troph$stab["log_rich"]+coef_troph$stab["log_rich:troph_group3"])
+
+s_ci_r <- print_ci(stab_div_ci["beta.log_rich",])
+s_ci_t <- print_ci(stab_troph_ci["beta.troph_group3",])
+s_ci_r_t2 <- print_ci(stab_troph_ci["beta.log_rich",])
+s_ci_r_t3 <- print_ci(coef_troph$stab["log_rich"] + stab_troph_ci["beta.log_rich:troph_group3",])
+```
+
+```{r print-coef-bm}
+# Coefficients
+b_co_i <- print_coef(coef_div$bm["(Intercept)"])
+b_co_r <- print_coef(coef_div$bm["log_rich"])
+b_co_t <- print_coef(coef_troph$bm["troph_group3"])
+b_co_r_t2 <- print_coef(coef_troph$bm["log_rich"])
+b_co_r_t3 <- print_coef(coef_troph$bm["log_rich"]+coef_troph$bm["log_rich:troph_group3"])
+
+b_ci_r <- print_ci(bm_div_ci["beta.log_rich",])
+b_ci_t <- print_ci(bm_troph_ci["beta.troph_group3",])
+b_ci_r_t2 <- print_ci(bm_troph_ci["beta.log_rich",])
+b_ci_r_t3 <- print_ci(coef_troph$bm["log_rich"] + bm_troph_ci["beta.log_rich:troph_group3",])
 ```
@@
 - Stability:
-  - decreases with richness
-  - is higher for higher trophic group
-  - increases and decreases with richness for the lower and higher trophic group
-    respectively
+  - decreases globally with median species richness (MSR)
+    - An increase of 1% of MSR decreased biomass stability by
+      `r s_co_r`% (`r s_ci_r`)
+  - was `r s_co_t`% (`r s_ci_t`) higher for higher trophic group
+  - increased by `r s_co_r_t2`% (`r s_ci_r_t2`) and decreased by `r s_co_r_t3`
+    (`r s_ci_r_t3`) with 1% increase in MSR for the lower and higher trophic
+    group respectively
 
-- richness on stab:
-  - globally negative
-  -
+- Biomass:
+  - increases with MSR 
+    - An increase of 1% of MSR increased total biomass by
+      `r b_co_r` % `r b_ci_r`
+  - was `r b_co_t`% `r b_ci_t` higher for higher trophic group
+  - increased by `r b_co_r_t2`% `r b_ci_r_t2` and decreased by `r b_co_r_t3`
+    (`r b_ci_r_t3`) with 1% increase in MSR for the lower and higher trophic
+    group respectively
 
@@
   - path: 
+- Reporting:
+  - equations: https://stats.stackexchange.com/questions/169115/reporting-the-actual-formula-equation-of-an-lme-model-with-factors-used-in-r
+  - log-log results:
+    - https://dev.to/rokaandy/logarithmic-transformation-in-linear-regression-models-why-when-3a7c
+    - https://stats.stackexchange.com/questions/18480/interpretation-of-log-transformed-predictor-and-or-response
 
@@
 ```{r}
-test <- map2_dfr(list(bm_troph_ci, stab_troph_ci), list(bm_troph_mod, stab_troph_mod),
+coeff_troph <- map2_dfr(list(bm_troph_ci, stab_troph_ci), list(bm_troph_mod, stab_troph_mod),
   clean_summary_mod, term_rp = rp_est, group_rp = rp_group)
 
-kable(test) %>%
+kable(coeff_troph) %>%
   pack_rows("Biomass", 1, 6) %>%
@@
 
-```{r}
+```{r, eval = FALSE}
+compute_stab_sem_rich(.data = sem_data, get_sem =TRUE)
+
+mod_list <-  
+  list(
+    nlme::lme(log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
+    nlme::lme(piel ~ RC1 + RC2 + RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(ct ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(t_lvl ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich, random = ~ 1 | basin, data = sem_data),
+    #nlme::lme( ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(log_sync ~ log_rich + piel + ct + t_lvl + RC1 + RC2 + RC3 + RC4 + RC5,
+      random = ~ 1 | basin, data = sem_data),
+    nlme::lme(log_cv_sp ~ log_rich + piel + ct + t_lvl
+      + RC1 + RC2 + RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data),
+    lm(log_stab ~ log_cv_sp + log_sync, data = sem_data)
+  )
+names(mod_list) <- c("richness", "pielou", "connectance", "weighted_mean_trophic_lvl", "synchrony", "cv_sp", "stability") 
+colin_stab_sem <- map(mod_list, car::vif)
+
+tibble(
+  vif = colin_stab_sem,
+  mod = names(mod_list)
+) 
+test <- cbind(colin_stab_sem)
+
+formulas <- list(
+  "log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5",
+  "piel ~ RC1 + RC2 + RC3 + RC4 + RC5"
+)
+test <- map(formulas, function(x, y, random_effect) {
+  lmer(as.formula(x), random= as.formula(random_effect), data = y)
+
+}, y =sem_data, random_effect = "~ 1 |basin")
+
 ```

### 2020-02-06 manuscript/bef_stability/manuscript.Rmd
residual plot sem

@@
 
-```{r, eval = FALSE}
-compute_stab_sem_rich(.data = sem_data, get_sem =TRUE)
+```{r colin-sem, fig.cap = "Variance Inflation factor for each individual model of stability sem"}
+#compute_stab_sem_rich(.data = sem_data, get_sem =TRUE)
 
@@
 
-tibble(
-  vif = colin_stab_sem,
-  mod = names(mod_list)
-) 
-test <- cbind(colin_stab_sem)
+tmp <- map(colin_stab_sem, enframe)
 
-formulas <- list(
-  "log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5",
-  "piel ~ RC1 + RC2 + RC3 + RC4 + RC5"
-)
-test <- map(formulas, function(x, y, random_effect) {
-  lmer(as.formula(x), random= as.formula(random_effect), data = y)
+# colinearity table
+colin_sem <- tibble(vif = tmp, mod = names(mod_list)) %>%
+  unnest(vif) %>%
+  spread(name, value)
 
-}, y =sem_data, random_effect = "~ 1 |basin")
+#formulas <- list(
+  #"log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5",
+  #"piel ~ RC1 + RC2 + RC3 + RC4 + RC5"
+#)
+#test <- map(formulas, function(x, y, random_effect) {
+  #lmer(as.formula(x), random= as.formula(random_effect), data = y)
 
+#}, y =sem_data, random_effect = "~ 1 |basin")
+
+kable(colin_sem)
+```
+
+```{r}
+plot_residuals <- function (x, y = "Diagnostic") {
+  plot.lme(x)
+  #title(main = y, xlab = "Fitted values", y = "Residuals")
+}
+plot.lme(mod_list[[7]])
+p_resid_stab_sem <- map2(mod_list, names(mod_list) , plot_residuals)
+plot_grid(plotlist = p_resid_stab_sem)
 ```

### 2020-02-13 manuscript/bef_stability/manuscript.Rmd
Test several SEM

--- 2020-02-04 manuscript/bef_stability/manuscript.Rmd
@@
     math: katex
+bibliography: references.bib
 ---
@@
 
+## Fish data
+
+- OFB
+  - French long term protocol
+  - standardized
+
+- Electric fishing:
+  - stuned fish
+  - identification of the fishes
+  - fish counted  
+  - length of the fishes in mm by lot (4):
+    - I: big fishes measured individually
+    - S/L: fishes are grouped by species and by size 
+      - 30 random fishes were measured in each lot
+      - simulate the size of all the fishes of the lot:
+	- normal distribution truncated at 95% (?)
+	- mean and sd calculted from the sample of the lot 
+    - G: little fishes are grouped by species
+      - min and max size by lot 
+      - simulate the size of all the fishes of the lot:
+	- normal distribution truncated at 95% (?)
+	- mean computed as ???  
+	- se computed as ??? 
+    - N:
+
+- Protocols type:
+  - complete
+    - shallow river
+  - partial:
+    - deep and large river
+    - partial over bank
+    - partial by point
+    - fusion of the two Protocols when "by point" all the point were done
+      over bank
+
+- Fishing operations and station
+  - kept one protocol type by station
+  - kept one sampling operation per year (of the season the most sampled in the
+    time series)
+  - remove operations which sampling effort (length of river) superior to average
+    plus or minus 30% of sd (by station)
+  - kept station that had 10 or more samplings, i.e. followed 10 years or more
+
+- Biomass:
+  - infered by allometric law 
+  - approximated by $B = 0.01 \times (l^3.03)$
+
+## Network building
+
+- Diet data: 
+  - 7? species over 57 had a piscivorous stage
+  - 3? species had a strict piscivorous stage
+  - ontogenic diet shift based on size
+
+- 7 Resource nodes:
+  - based on diet database
+
 ## Community
@@
 myload(temporal_community_metrics, dir = mypath("data"))
+myload(synchrony, dir = mypath("data"))
 st_basin <- get_basin_station(sf_obj = FALSE)
@@
     log_rich = log10(richness_med),
+    log_rich_tot = log10(richness_tot),
     log_bm = log10(biomass_med),
     log_stab = log10(biomass_stab)) %>%
-  dplyr::select(station, troph_group, biomass_stab, richness_med, log_rich, log_stab, log_bm, biomass_med) %>%
+  dplyr::select(station, troph_group, biomass_stab, richness_med, richness_tot, log_rich, log_rich_tot, log_stab, log_bm, biomass_med, richness_tot) %>%
   dplyr::left_join(st_basin, by = "station")
@@
   control = ctrl_lmer,
-  formula = log_stab ~ log_rich + (1 | basin)
+  formula = log_stab ~ log_rich_tot + (1 | basin)
 )
 stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
+stab_div_boot <- bootMer(stab_div_mod, mySumm2, nsim = 100)
+stab_div_ci <- confint(stab_div_boot)
 #stab_div_colin <- car::vif(stab_div_mod) not use if one response
@@
 
-pred <- ggpredict(stab_div_mod, terms = c("log_rich"), type = "fe")
+pred <- ggpredict(stab_div_mod, terms = c("log_rich_tot"), type = "fe")
 stab_div_pred <- pred %>%
@@
     log_stab = predicted,
-    log_rich = x,
+    log_rich_tot = x,
     basin = group
@@
     stab = 10^log_stab, # FALSE
-    rich = 10^log_rich,
+    rich = 10^log_rich_tot,
     cl10 =  10^conf.low,
@@
 bm_div_mod <- lmer(data = sem_data,
-  formula = log_bm ~ log_rich + (1 | basin)
+  formula = log_bm ~ log_rich_tot + (1 | basin)
 )
+bm_div_boot <- bootMer(bm_div_mod, mySumm2, nsim = 100)
+bm_div_ci <- confint(bm_div_boot)
 bm_div_sum <- piecewiseSEM::rsquared(bm_div_mod, method = "nagelkerke") %>%
@@
 
-pred <- ggpredict(bm_div_mod, terms = c("log_rich"), type = "fe")
+pred <- ggpredict(bm_div_mod, terms = c("log_rich_tot"), type = "fe")
 #plot(pred, add.data = TRUE)
@@
     log_bm = predicted,
-    log_rich = x,
+    log_rich_tot = x,
     basin = group
   )
+
+# get coeff
+coef_div <- map(list(stab = stab_div_mod, bm = bm_div_mod), fixed.effects)
 ```
@@
 stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
-  formula = log_stab ~ log_rich + troph_group + log_rich:troph_group + (1 | basin)
+  formula = log_stab ~ log_rich_tot + troph_group + log_rich_tot:troph_group + (1 | basin)
   #control = ctrl
 )
-mySumm2 <- function(.) {
-  c(beta=fixef(.),sigma=sigma(.), sig01=sqrt(unlist(VarCorr(.))))
-}
 stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
@@
 
-pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
+pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot", "troph_group"), type = "fe")
 #plot(pred_troph_mod, add.data = TRUE)
@@
     log_stab = predicted,
-    log_rich = x,
+    log_rich_tot = x,
     troph_group = group
@@
 bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
-  #fixed = log_bm ~ log_rich * troph_group,
-  formula = log_bm ~ log_rich + troph_group + log_rich:troph_group + (1 | basin)
-  #random = ~ 1 + log_rich * troph_group | basin,
+  #fixed = log_bm ~ log_rich_tot * troph_group,
+  formula = log_bm ~ log_rich_tot + troph_group + log_rich_tot:troph_group + (1 | basin)
+  #random = ~ 1 + log_rich_tot * troph_group | basin,
   #control = ctrl 
@@
 
-pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich", "troph_group"), type = "fe")
+pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot", "troph_group"), type = "fe")
 #plot(pred_troph_mod, add.data = TRUE)
@@
     log_bm = predicted,
-    log_rich = x,
+    log_rich_tot = x,
     troph_group = group
   )
+
+# get coeff
+coef_troph <- map(list(stab = stab_troph_mod, bm = bm_troph_mod), fixed.effects)
 ```
@@
 
+We computed Structural Equation Modeling (SEM) to unravel mechanisms underlying link
+between environment, community structure and both biomass stability and total
+biomass. Why SEM?
+
+SEM enables to reason in terms of causal relationship between components. The
+goal was to understand the mechanisms behind the negative relationship biomass
+stability and species richness and the positive relationship between total
+biomass and species richness.
+
+We built a metamodel to set up the nodes and the links between the different
+compartment of the SEM. Basically, we wanted to test the links between
+environmental conditions, community structure and stability. Theory in ecology 
+predicts that community structure influences stability. In turn, environment 
+influences community structure but also directly stability.
+
+To characterize environment, we retained five axis of PCA on habitat and
+climatic variables which represent different types of forcing (constant and
+variability). The two first axis (RC1 and RC2) were mainly linked the physical
+structure and position of the river and the altitutinal gradient (+temperature).
+The third axis (RC3) was linked to enrichment (Organic Biological Demand) and CV
+of annual flow. The fourth and fifth (RC4 and RC5) axis were associated to
+environmental variability, respectively to CV of width and depth of the river
+and CV of enrichment.
+
+- Community structure:
+  - species richness:
+  - avg trophic level:
+  - connectance:
+  - beta diversity:
+
+- Stability:
+  - 2 components synchrony and $CV_{sp}$
+
+The stream physical structure (RC1 axis) and its altitutinal position (RC2 axis)
+was linked to species richness [REF].
+
 ```{r}
 # Compute SEMs
+stab_sem_rich_beta <- compute_stab_sem_rich_beta(.data = sem_data,
+  random_effect = as.formula("~1|basin"))
+stab_sem_meta <- compute_stab_sem_meta(.data = sem_data,
+  random_effect = as.formula("~1|basin"))
 stab_sem <- compute_stab_sem(.data = sem_data,
-  random_effect = as.formula("~1|basin"))
-stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
   random_effect = as.formula("~1|basin"))
@@
   random_effect = as.formula("~1|basin"))
+bm_sem_rich_beta <- compute_prod_sem_rich_beta(.data = sem_data,
+  random_effect = as.formula("~1|basin"))
 
 library(ggraph)
+p_stab_sem_rich_beta <- ggpiecewisesem(stab_sem_rich_beta)
+p_stab_sem_meta <- ggpiecewisesem(stab_sem_meta, p_val_thd = 1)
 p_stab_sem <- ggpiecewisesem(stab_sem)
+p_bm_sem_rich_beta <- ggpiecewisesem(bm_sem_rich_beta)
 p_bm_sem <- ggpiecewisesem(bm_sem)
-p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
+plot_grid(
+  p_stab_sem,
+  p_stab_sem_rich_beta,
+  p_bm_sem,
+  p_bm_sem_rich_beta
+)
 ```
@@
 ```{r get-sem-coeff}
-coef_stab_sem <- coef(stab_sem) %>%
+coef_stab_sem_sum <- coef(stab_sem) %>%
   group_by(Response) %>%
@@
   mutate(sum_c = map_dbl(data, ~ sum(.x$Std.Estimate)))
+
+coef_stab_sem <- coef(stab_sem_rich_beta) %>%
+  select(- 9) %>%
+  filter(P.Value < 0.05)
 
@@
 
+```{r}
+richness_lab <- "Total richness (Log 10)"
+stab_lab <- "Biomass stability (Log 10)"
+bm_lab <- "Total biomass (Log 10)"
+```
+
 ```{r p-s-div}
 lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
-lim_log_rich <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich")
+lim_log_rich_tot <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich_tot")
 # Plot left
@@
 p_stab_div <- sem_data %>%
-  ggplot(aes(x = log_rich, y = log_stab))+
+  ggplot(aes(x = log_rich_tot, y = log_stab))+
   geom_point() +
   ylim(lim_log_stab) +
-  xlim(lim_log_rich) +
+  xlim(lim_log_rich_tot) +
   #scale_y_log10() +
   #scale_x_log10() +
-  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)") +
+  labs(x = richness_lab, y = stab_lab) +
+  geom_line(data = stab_div_pred) +
   geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
@@
 p_stab_div_troph <- stab_div_troph %>%
-  ggplot(aes(x = log_rich, y = log_stab, color = troph_group)) +
+  ggplot(aes(x = log_rich_tot, y = log_stab, color = troph_group)) +
   geom_point() +
@@
   ylim(lim_log_stab) +
-  xlim(lim_log_rich) +
+  xlim(lim_log_rich_tot) +
   geom_line(data = stab_troph_pred) +
@@
   #scale_x_log10() + scale_y_log10() +
-  labs(x = "Median species richness (Log 10)", y = " Biomass stability (Log 10)")
+  labs(x = richness_lab, y = stab_lab)
 
@@
 p_bm_div <- sem_data %>%
-  ggplot(aes(x = log_rich, y = log_bm))+
+  ggplot(aes(x = log_rich_tot, y = log_bm))+
   geom_point() +
   ylim(lim_log_bm) +
-  xlim(lim_log_rich) +
-  labs(x = "Median species richness (Log 10)", y = " Total biomass(Log 10)") +
+  xlim(lim_log_rich_tot) +
+  labs(x = richness_lab, y = bm_lab) +
   geom_line(data = bm_div_pred) +
@@
   = "grey20", alpha = .2) +
-  annotate("text", x = 1.0, y = 5, label = make_label_rsq(rsq = bm_div_sum),
+  annotate("text", x = .8, y = 1.5, label = make_label_rsq(rsq = bm_div_sum),
     parse = TRUE)
@@
 p_bm_div_troph <- stab_div_troph %>%
-  ggplot(aes(x = log_rich, y = log_bm, color = troph_group)) +
+  ggplot(aes(x = log_rich_tot, y = log_bm, color = troph_group)) +
   geom_point() +
   ylim(lim_log_bm) +
-  xlim(lim_log_rich) +
+  xlim(lim_log_rich_tot) +
   ggplot2::scale_color_manual(
@@
     alpha = .2) +
-  annotate("text", x = 0.8, y = 5, label = make_label_rsq(rsq = bm_troph_sum),
+  annotate("text", x = 0.8, y = 1.5, label = make_label_rsq(rsq = bm_troph_sum),
     parse = TRUE) +
   #scale_x_log10() + scale_y_log10() +
-  labs(x = "Median species richness (Log 10)", y = "Total biomass (Log 10)")
+  labs(x = richness_lab, y = bm_lab)
 
@@
 plot_grid(p_stab, p_bm, ncol = 1)
+
+print_coef <- function (vec){
+  round(abs(vec)*100)
+}
+print_ci <- function(.df){
+  .df <- round(.df, 3)*100
+
+  paste0("[", .df[["2.5 %"]],";",.df[["97.5 %"]] ,"]")
+}
+```
+
+```{r print-coef-stab}
+# Coefficients
+s_co_i <- print_coef(coef_div$stab["(Intercept)"])
+s_co_r <- print_coef(coef_div$stab["log_rich_tot"])
+s_co_t <- print_coef(coef_troph$stab["troph_group3"])
+s_co_r_t2 <- print_coef(coef_troph$stab["log_rich_tot"])
+s_co_r_t3 <- print_coef(coef_troph$stab["log_rich_tot"]+coef_troph$stab["log_rich_tot:troph_group3"])
+
+s_ci_r <- print_ci(stab_div_ci["beta.log_rich_tot",])
+s_ci_t <- print_ci(stab_troph_ci["beta.troph_group3",])
+s_ci_r_t2 <- print_ci(stab_troph_ci["beta.log_rich_tot",])
+s_ci_r_t3 <- print_ci(coef_troph$stab["log_rich_tot"] + stab_troph_ci["beta.log_rich_tot:troph_group3",])
+```
+
+```{r print-coef-bm}
+# Coefficients
+b_co_i <- print_coef(coef_div$bm["(Intercept)"])
+b_co_r <- print_coef(coef_div$bm["log_rich_tot"])
+b_co_t <- print_coef(coef_troph$bm["troph_group3"])
+b_co_r_t2 <- print_coef(coef_troph$bm["log_rich_tot"])
+b_co_r_t3 <- print_coef(coef_troph$bm["log_rich_tot"]+coef_troph$bm["log_rich_tot:troph_group3"])
+
+b_ci_r <- print_ci(bm_div_ci["beta.log_rich_tot",])
+b_ci_t <- print_ci(bm_troph_ci["beta.troph_group3",])
+b_ci_r_t2 <- print_ci(bm_troph_ci["beta.log_rich_tot",])
+b_ci_r_t3 <- print_ci(coef_troph$bm["log_rich_tot"] + bm_troph_ci["beta.log_rich_tot:troph_group3",])
 ```
@@
 - Stability:
-  - decreases with richness
-  - is higher for higher trophic group
-  - increases and decreases with richness for the lower and higher trophic group
-    respectively
+  - decreases globally with total species richness (TSR)
+    - An increase of 1% of TSR decreased biomass stability by
+      `r s_co_r`% (`r s_ci_r`)
+  - was `r s_co_t`% (`r s_ci_t`) higher for higher trophic group
+  - increased by `r s_co_r_t2`% (`r s_ci_r_t2`) and decreased by `r s_co_r_t3`
+    (`r s_ci_r_t3`) with 1% increase in TSR for the lower and higher trophic
+    group respectively
 
-- richness on stab:
-  - globally negative
-  -
+- Biomass:
+  - increases with TSR 
+    - An increase of 1% of TSR increased total biomass by
+      `r b_co_r` % `r b_ci_r`
+  - was `r b_co_t`% `r b_ci_t` higher for higher trophic group
+  - increased by `r b_co_r_t2`% `r b_ci_r_t2` and decreased by `r b_co_r_t3`
+    (`r b_ci_r_t3`) with 1% increase in TSR for the lower and higher trophic
+    group respectively
 
@@
       ncol = length(to_plot), labels = LETTERS[1]),
-  plot_grid(p_stab_sem, p_bm_sem, labels = LETTERS[2:3]),
+  plot_grid(p_stab_sem_rich_beta, p_bm_sem_rich_beta, labels = LETTERS[2:3]),
   ncol = 1,
@@
   - Community structure: 
-    - Richness decreases synchrony but increases CV
-    - Trophic level increases synchrony but decreases CV
+    - Species richness had no direct effects on CV but on synchrony!  
+    - Evenness of biomass dist increased CV but decreased synchrony
+    - Trophic level decreased CV
     - Betadiv increases CV
   - Habitat/Env:
-    - very weak to no direct effect on stability
+    - few direct effect on stability
       - direct: CV_sp dec with increasing RC3, cad enrichment and flow_cv decrease.  
-    - indirectly affect stability by modulating community structure
+      - direct: CV_sp inc with increasing RC2, cad temperature_med.  
+    - indirectly affect stability by modulating community structure,
+      particularly richness
 
@@
 - Main outcome:
+  - Biomass but stability increased with richness
+  - Higher trophic group was more stable that lower one
+    - Opposite relationship stability/richness
+  - Stability was mainly driven by species richness
 
@@
 
+```{r s-colin-sem, fig.cap = "Variance Inflation factor for each individual model of stability sem"}
+#compute_stab_sem_rich(.data = sem_data, get_sem =TRUE)
+
+mod_stab_list <-
+  list(
+    nlme::lme(log_rich_tot ~ RC1 + RC2 + RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
+    nlme::lme(piel ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(ct ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(t_lvl ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(beta_bin ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(log_sync ~ log_rich_tot + piel + ct + t_lvl + RC1 + RC2 + RC3 + RC4 + RC5,
+      random = ~ 1 | basin, data = sem_data),
+    nlme::lme(log_cv_sp ~ log_rich_tot + piel + ct + t_lvl
+      + RC1 + RC2 + RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data),
+    lm(log_stab ~ log_cv_sp + log_sync, data = sem_data)
+  )
+names(mod_stab_list) <- c("richness", "pielou", "connectance", "weighted_mean_trophic_lvl", "beta", "synchrony", "cv_sp", "stability") 
+colin_stab_sem <- map(mod_stab_list, car::vif)
+
+tmp <- map(colin_stab_sem, enframe)
+
+# colinearity table
+colin_stab_sem <- tibble(vif = tmp, mod = names(mod_stab_list)) %>%
+  unnest(vif) %>%
+  spread(name, value)
+
+#formulas <- list(
+  #"log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5",
+  #"piel ~ RC1 + RC2 + RC3 + RC4 + RC5"
+#)
+#test <- map(formulas, function(x, y, random_effect) {
+  #lmer(as.formula(x), random= as.formula(random_effect), data = y)
+
+#}, y =sem_data, random_effect = "~ 1 |basin")
+
+kable(colin_stab_sem)
+```
+
 ```{r}
+plot_residuals <- function (x, y = "Diagnostic") {
+  plot.lme(x, main = y, xlab = "Fitted values", ylab = "Residuals")
+}
+p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
+plot_grid(plotlist = p_resid_stab_sem)
+```
+
+```{r, eval = FALSE}
+mod_tlvl <- nlme::lme(t_lvl ~ scale(RC1) + scale(RC2) + scale(RC3) + scale(RC4) + scale(RC5) + log_rich_tot, random = ~ 1 | basin, data = sem_data)
+plot(mod_tlvl)
+sem_data %>%
+  ggplot(aes(x = log10(richness_tot), y = t_lvl)) +
+  geom_point()+
+  geom_smooth(method = "lm")
+
+sem_data %>%
+  ggplot(aes(x = RC1, y = t_lvl)) +
+  geom_point()+
+  geom_smooth(method = "lm")
+plot(nlme::lme(t_lvl ~ I(log10(RC1 + abs(min(RC1)))) + log_rich_tot, random = ~ 1 | basin, data = sem_data))
+nlme::lme(t_lvl ~ log_rich_tot, random = ~ 1 | basin, data = sem_data)
+semd_test <- sem_data %>%
+  mutate(RC1b = RC1 + abs(min(RC1)))
+ricker.mixed.fit <- nls(
+  t_lvl ~ (Vm*(RC1 + b) / (K + (RC1 + b)) + d),
+ #fixed = Vm + K + b + d ~ 1,
+ #random = Vm + K + b + d ~ 1|basin,
+ start= c(Vm=1, K = 0.1, b = .5, d = 2.5),
+ data = semd_test,
+ control = lmeControl(maxIter = 1e8, msMaxIter = 1e8) 
+)
+summary(ricker.mixed.fit)
+x <- seq(min(sem_data$RC1), max(sem_data$RC1), length.out = 100)
+sem_data$test_pred <- predict(ricker.mixed.fit)
+
+semd_test %>%
+  ggplot(aes(x = RC1b, y = t_lvl)) +
+  geom_point() +
+  geom_line(aes(y = test_pred))
+  geom_smooth(method = "lm")
+cor(semd_test$piel, semd_test$t_lvl, method = c("spearman"))
 ```

### 2020-02-14 manuscript/bef_stability/manuscript.Rmd
Begin to explain SEM hypothesis

@@
 We built a metamodel to set up the nodes and the links between the different
-compartment of the SEM. Basically, we wanted to test the links between
+compartment of the SEM. Basically, we tested the links between
 environmental conditions, community structure and stability. Theory in ecology 
@@
 
+#### Variables
+
 To characterize environment, we retained five axis of PCA on habitat and
 climatic variables which represent different types of forcing (constant and
-variability). The two first axis (RC1 and RC2) were mainly linked the physical
+variability). The two first axis (RC1 and RC2) were linked to the physical
 structure and position of the river and the altitutinal gradient (+temperature).
@@
 
-- Community structure:
-  - species richness:
-  - avg trophic level:
-  - connectance:
-  - beta diversity:
+The community structure was characterized by total species richness (TSR),
+species turnover (ST), median average weighted trophic level (TLvl) and median connectance.
+Total species richness was the number of unique fish species that were observed
+at a given station over the whole sampling. Species turnover was computed as average
+dissimilarity between the different community composition through time. The
+dissimilarity was calculated on species presence/absence with the Bray-Curtis
+method implemented in the `vegan` R package (`vegdist` function). Both median
+connectance and Tlvl were just computed as the median over the temporal period.
+For the details of the computation of the trophic networks, see Network
+inference part.
 
-- Stability:
-  - 2 components synchrony and $CV_{sp}$
+The biomass stability was decomposed in synchrony and weighted average CV
+components according to @thibaut_understanding_2013.
 
-The stream physical structure (RC1 axis) and its altitutinal position (RC2 axis)
-was linked to species richness [REF].
+#### Causal relationships
+
+---
+# Environment to community attributes and stability  
+---
+We linked environmental variables both to community structure and stability
+components. Rooted in assembly theory, environment filters species that can
+establish in a community and thus affect community structure. (+ add specific
+hypothesis about physical and climate). (1) We hypothesized that enrichment
+(characterized by DBO) and mean annual temperature will increase ST
+[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
+decrease biomass stability directly without going by community structure. First,
+instability of habitat and environmental factors may in turn drive biomass
+instability [@hansen_climate_2013]. Secondly, average environmental conditions
+such as enrichment can increase directly CV by increasing species biomass
+fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
+to decrease stability through starvation resulting from high metabolic activity
+[@tabi_warming_2019].
+
+---
+# Species richness to community attributes 
+---
+The reveal the mechanisms behind the relationship between species richness and
+biomass stability, causal links were set from species richness to other
+community attributes. (4) We hypothesized that TSR increased ST because
+increasing species richness because of assembly processes. Species rich
+community are more resistant to invasion and thus produces more ST
+[@tilman_niche_2004; @shurin_how_2007].
 
@@
 
+- Stability versus several studies:
+  - [@zhang_scale_nodate]: productivity stability range from [0.4 to 1.4] for
+    diversity range [10 to 30]
+  - [@tilman_biodiversity_2006] on abundances:
+    - stability range: 2 to 12
+    - diversity range: 1 to 16
+
 # Appendix

### 2020-02-19 manuscript/bef_stability/manuscript.Rmd
Add computation of cv over basin + DiagrammeR

@@
 The biomass stability was decomposed in synchrony and weighted average CV
-components according to @thibaut_understanding_2013.
+components according to @thibaut_understanding_2013:
+
+$$
+CV_{com} = \overline{CV_{sp}} \times \sqrt{\phi}
+$$
+
+with $CV_{com}$ being the Coefficient of Variation of the community,
+$\overline{CV_{sp}}$ the average coefficient of variation of population
+pondered by biomass. $\phi$ is the synchrony, which is the ratio the total
+community variance ($\sigma^2_{x_T}$) and the sum of population variance
+($\sigma_{x_i}$) [@loreau_species_2008]:
+
+$$
+\phi = \frac{\sigma^2_{x_T}}{\sum_i{\sigma_{x_i}}}
+$$
 
@@
 ---
-The reveal the mechanisms behind the relationship between species richness and
+To reveal the mechanisms behind the relationship between species richness and
 biomass stability, causal links were set from species richness to other
@@
 increasing species richness because of assembly processes. Species rich
-community are more resistant to invasion and thus produces more ST
-[@tilman_niche_2004; @shurin_how_2007].
+communities are more resistant to invasion and thus increase ST
+[@tilman_niche_2004; @shurin_how_2007]. (5) We hypothesized also that TSR
+decreased connectance following results from @thebault_stability_2010;
+@winemiller_must_1989. But theoretically, some ecological networks can show the
+inverse relationship [@winemiller_must_1989]. (6) We hypothesized also that TSR
+will modulate average weighted trophic level because of food web assembly
+processes. If *TSR increased and that new species are placed at random in the
+network, we expected a positive relationship between Tlvl and TSR because
+individuals of the higher trophic level have a higher body mass [to think
+again]*. Finally, we set up causal relationships from community attributes to
+stability components.
+
+---
+#  Community attributes to stability
+---
+We hypothesized that (7) TSR decreased synchrony between species by portfolio
+effects [REF] and increased $\overline{CV_{sp}}$ [@tilman_biodiversity_2006] *to
+complete*. We hypothesized that (8) ST increased $\overline{CV_{sp}}$ and that it
+decreased synchrony. (9a) We expected that Tlvl had a positive or negative
+relationship with synchrony, bottom-up effects should result in positive whereas
+top-down in negative relationship. We expected a (9b) negative relationship
+between Tlvl and $\overline{CV_{sp}}$ if predators stabilised population
+fluctuations or if the increasing part of biomass in the predators decreased
+$\overline{CV_{sp}}$ because of their higher body mass (if mean increase faster than
+variance). (10a) Connectance was expected to decrease or increase $\overline{CV_{sp}}$
+and (10b) synchrony because of top down effects or bottom up effects.
 
@@
 stab_sem_rich_beta <- compute_stab_sem_rich_beta(.data = sem_data,
+  random_effect = as.formula("~1|basin"))
+stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
   random_effect = as.formula("~1|basin"))
@@
   random_effect = as.formula("~1|basin"))
+bm_sem_rich <- compute_prod_sem_rich(.data = sem_data,
+  random_effect = as.formula("~1|basin"))
 bm_sem_rich_beta <- compute_prod_sem_rich_beta(.data = sem_data,
@@
 library(ggraph)
+p_stab_sem <- ggpiecewisesem(stab_sem)
 p_stab_sem_rich_beta <- ggpiecewisesem(stab_sem_rich_beta)
-p_stab_sem_meta <- ggpiecewisesem(stab_sem_meta, p_val_thd = 1)
-p_stab_sem <- ggpiecewisesem(stab_sem)
-p_bm_sem_rich_beta <- ggpiecewisesem(bm_sem_rich_beta)
+p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
+
+library(DiagrammeR)
+graph <- build_diag_from_sem(stab_sem_rich, p_val_thd = 0.05)
+
 p_bm_sem <- ggpiecewisesem(bm_sem)
-plot_grid(
-  p_stab_sem,
-  p_stab_sem_rich_beta,
-  p_bm_sem,
-  p_bm_sem_rich_beta
-)
+p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
 ```
@@
 
-p_stab <- plot_grid(p_stab_div, p_stab_div_troph, ncol = 2, rel_widths = c(.4, .6))
+p_stab <- plot_grid(p_stab_div, p_stab_div_troph,
+  ncol = 2, rel_widths = c(.4, .6),
+  labels = c("A", "B") 
+)
 ```
@@
 
-p_bm <- plot_grid(p_bm_div, p_bm_div_troph, ncol = 2, rel_widths = c(.4, .6))
+p_bm <- plot_grid(p_bm_div, p_bm_div_troph, ncol = 2, rel_widths = c(.4, .6),
+  labels = c("C", "D"))
 ```
@@
 
-- Stability:
-  - decreases globally with total species richness (TSR)
-    - An increase of 1% of TSR decreased biomass stability by
-      `r s_co_r`% (`r s_ci_r`)
-  - was `r s_co_t`% (`r s_ci_t`) higher for higher trophic group
-  - increased by `r s_co_r_t2`% (`r s_ci_r_t2`) and decreased by `r s_co_r_t3`
-    (`r s_ci_r_t3`) with 1% increase in TSR for the lower and higher trophic
-    group respectively
-
-- Biomass:
-  - increases with TSR 
-    - An increase of 1% of TSR increased total biomass by
-      `r b_co_r` % `r b_ci_r`
-  - was `r b_co_t`% `r b_ci_t` higher for higher trophic group
-  - increased by `r b_co_r_t2`% `r b_ci_r_t2` and decreased by `r b_co_r_t3`
-    (`r b_ci_r_t3`) with 1% increase in TSR for the lower and higher trophic
-    group respectively
+---
+# Total biomass versus TSR
+---
+TSR increased total biomass (`r b_co_r`% `r b_ci_r` by 1% TSR increase). Total
+biomass was `r b_co_t`% `r b_ci_t` higher in the high than in the low trophic group. However,
+the increase of total biomass with the increase of TSR was lower in the high
+than the low trophic group (`r b_co_r_t3`% `r b_ci_r_t3` and `r b_co_r_t2`%
+`rb_ci_r_t2` respectively,  by 1% TSR increase).
+---
+# Stability versus TSR
+---
+However, biomass stability decreased with TSR (`r s_co_r`% `r s_ci_r` by 1%
+TSR increase). Biomass stability was overall `r s_co_t`% `r s_ci_t` higher for the high
+than the low trophic group. But biomass stability decreased by `r s_co_r_t3`% by
+1% increase in TSR in the high trophic group and increased by `r s_co_r_t2`% `r s_ci_r_t2`
+in the low trophic group.
 
@@
       ncol = length(to_plot), labels = LETTERS[1]),
-  plot_grid(p_stab_sem_rich_beta, p_bm_sem_rich_beta, labels = LETTERS[2:3]),
+  plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[2:3]),
   ncol = 1,
@@
 coefficient, meaning that it's a decelerating function.
+
+- R diagramm:
+  - https://rstudio-pubs-static.s3.amazonaws.com/78926_5aa94ae32fae49f3a384ce885744ef4a.html
 
@@
 
-### SEM linear relationship
+### SEM linear relationships
+
+```{r hist-sem-data}
+sem_data %>%
+  select(prod, log_rich_tot, log_sync, log_stab, log_cv_sp, RC1, RC2, RC3, RC4,
+    RC5, t_lvl, ct, log_bm) %>%
+  gather(variable, value) %>%
+  ggplot(aes(x = value)) +
+  geom_histogram() +
+  facet_wrap(~variable, scales = "free")
+
+```
 
@@
   list(
-    nlme::lme(log_rich_tot ~ RC1 + RC2 + RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
-    nlme::lme(piel ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(ct ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(t_lvl ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(beta_bin ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(log_sync ~ log_rich_tot + piel + ct + t_lvl + RC1 + RC2 + RC3 + RC4 + RC5,
+    nlme::lme(log_rich_tot ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
+    #nlme::lme(piel ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(ct ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    #nlme::lme(beta_bin ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(log_sync ~ log_rich_tot + ct + t_lvl + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,
       random = ~ 1 | basin, data = sem_data),
-    nlme::lme(log_cv_sp ~ log_rich_tot + piel + ct + t_lvl
-      + RC1 + RC2 + RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(log_cv_sp ~ log_rich_tot  + ct + t_lvl
+      + RC1 + log_RC2 + log_RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data),
     lm(log_stab ~ log_cv_sp + log_sync, data = sem_data)
   )
-names(mod_stab_list) <- c("richness", "pielou", "connectance", "weighted_mean_trophic_lvl", "beta", "synchrony", "cv_sp", "stability") 
+names(mod_stab_list) <- c("richness", "connectance", "weighted_mean_trophic_lvl", "synchrony", "cv_sp", "stability") 
 colin_stab_sem <- map(mod_stab_list, car::vif)
@@
   spread(name, value)
-
-#formulas <- list(
-  #"log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5",
-  #"piel ~ RC1 + RC2 + RC3 + RC4 + RC5"
-#)
-#test <- map(formulas, function(x, y, random_effect) {
-  #lmer(as.formula(x), random= as.formula(random_effect), data = y)
-
-#}, y =sem_data, random_effect = "~ 1 |basin")
 
@@
   geom_smooth(method = "lm")
-
+plot(x = log10(sem_data$RC1 + abs(min(sem_data$RC1))), y = sem_data$t_lvl)
 sem_data %>%
-  ggplot(aes(x = RC1, y = t_lvl)) +
+  ggplot(aes(x = log10(RC1), y = t_lvl)) +
   geom_point()+
@@
 
+```{r, eval = FALSE}
+library(glmmTMB)
+# Gaussian
+mod_log_rich <- glmmTMB(
+  log_rich_tot ~ log_RC1 + log_RC2 + log_RC3
+  + RC4 + RC5 + (1 | basin), family = gaussian, data = sem_data)
+summary(mod_log_rich)
+plot(y = resid(mod_log_rich), x = fitted(mod_log_rich))
+
+# Poisson 
+mod_log_rich_poi <- glmmTMB(
+  richness_tot ~ log_RC1 + log_RC2 + log_RC3
+  + RC4 + RC5 + (1 | basin), family = poisson, data = sem_data)
+summary(mod_log_rich_poi)
+plot(y = resid(mod_log_rich_poi), x = fitted(mod_log_rich_poi))
+
+# Truncate 
+mod_log_rich_nbinom <- glmmTMB(
+  richness_tot ~ log_RC1 + log_RC2 + log_RC3
+  + RC4 + RC5 + (1 | basin), family = nbinom1, data = sem_data)
+summary(mod_log_rich_nbinom)
+plot(y = resid(mod_log_rich_nbinom), x = fitted(mod_log_rich_nbinom))
+```
+
+#### Total biomass
+
+```{r}
+
+mod_bm_list <-
+  list(
+    nlme::lme(log_rich_tot ~ RC1 + RC2 + RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
+    #nlme::lme(piel ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(ct ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(t_lvl ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    #nlme::lme(beta_bin ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(log_bm ~ log_rich_tot + ct + t_lvl + RC1 + RC2 + RC3 + RC4 + RC5,
+      random = ~ 1 | basin, data = sem_data)
+  )
+names(mod_bm_list) <- c("richness", "connectance", "weighted_mean_trophic_lvl", "total_biomass") 
+colin_bm_sem <- map(mod_bm_list, car::vif)
+
+tmp <- map(colin_bm_sem, enframe)
+
+# colinearity table
+colin_bm_sem <- tibble(vif = tmp, mod = names(mod_bm_list)) %>%
+  unnest(vif) %>%
+  spread(name, value)
+
+kable(colin_bm_sem)
+```
+
 ## Relationship at the absolute scale, i.e. not the logarythme scale

### 2020-02-19 R/statistical_analysis.R

@@ -32,7 +32,7 @@ compute_sem_dataset <- function (
   com$beta_bin_c <- resid(mod)
 
   # Add synchrony
-  sync %<>% dplyr::select(station, synchrony, cv_sp)
+  sync %<>% dplyr::select(station, synchrony, cv_sp, richness_tot)
   biomass_sem <- com %>%
     dplyr::select(station, biomass_stab, biomass_med, richness_med, pielou_med,
       betadiv_bin, beta_bin_c) %>%
@@ -51,6 +51,7 @@ compute_sem_dataset <- function (
   # Habitat -----------------------------------------------------------------
   habitat_sem <- hab_press %>% 
     dplyr::select(station, RC1, RC2, RC3, RC4, RC5)
+
 
   # Network -----------------------------------------------------------------
   net_sem <- network %>%
@@ -71,10 +72,14 @@ compute_sem_dataset <- function (
   dsem %<>%
     dplyr::mutate(
       log_rich = log10(richness_med),
+      log_rich_tot = log10(richness_tot),
       log_sync = log10(sync), 
       log_cv_sp = log10(cv_sp),
       log_stab = log10(biomass_stab),
-      log_bm = log10(prod)
+      log_bm = log10(prod),
+      log_RC1 = log10(RC1 + abs(min(RC1)) + 1),
+      log_RC2 = log10(RC2 + abs(min(RC2)) + 1),
+      log_RC3 = log10(RC3 + abs(min(RC3)) + 1)
     )
   return(dsem)
 
@@ -87,15 +92,15 @@ compute_sem_dataset <- function (
 compute_stab_sem_rich <- function(.data, random_effect = "~ 1 | basin", get_sem = FALSE) {
 
   mod_list <- list(
-    nlme::lme(log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5,  random = ~ 1 | basin, data = .data),
-    nlme::lme(piel ~ RC1 + RC2 + RC3 + RC4 + RC5, random = ~ 1 | basin, data = .data),
-    nlme::lme(ct ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich, random = ~ 1 | basin, data = .data),
[…]

### 2020-02-19 report/05-stability.Rmd
Add SEM with bbb and TSR
bbb = stable station
TSR: total species richness

@@
 # Compute SEMs
-sem <- compute_stab_sem(.data = sem_data,
+sem <- compute_stab_sem_rich_beta(.data = sem_data,
   random_effect = as.formula("~1|basin"))
@@
 
-- Main results:
-  - Richness destabilizes communities 
-  - 
-  - Trophic level decreased CV but increase species synchrony!
-  - Connectance!
-
-```{r sensitivity, fig.dim = c(14, 7), fig.cap = "Sensivity analysis with different dataset"}
+```{r sensitivity, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
 myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
-sem_l_data <- map(list(full = op_analysis, wo_holes = op_analysis_wo_holes, ov = op_analysis_ov),
+myload(biomass_ts_sax, dir = mypath("data"))
+op_analysis_bbb <- filter(op_analysis, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+
+#library(future)
+#plan(multiprocess)
+sem_sensivity_data <- list(full = op_analysis, wo_holes = op_analysis_wo_holes, bbb = op_analysis_bbb)
+sem_l_data <- furrr::future_map(sem_sensivity_data,
   ~build_dataset_get_sem_coefficient(
     .op = .x,
+    sem_fun = compute_stab_sem_rich_beta,
     dest_dir = mypath("data", "species"))
@@
 
+```{r, fig.dim = c(10, 5)}
+p_sensitivity_stab_sem <- map(sem_l_data, ggpiecewisesem)
+p_sensitivity_stab_sem %<>% map2(., names(sem_sensivity_data),  ~ .x + labs(title = .y))
+plot_grid(plotlist = p_sensitivity_stab_sem)
+```
+```{r}
+p_op_analysis_protocol_bbb <- op_analysis_bbb %>%
+  group_by(station) %>%
+  slice(1) %>%
+  ggplot(aes(x = protocol_type)) + 
+  geom_histogram(stat ="count") +
+  labs(title = "Station bbb")
+
+p_op_analysis_protocol <- op_analysis %>%
+  group_by(station) %>%
+  slice(1) %>%
+  ggplot(aes(x = protocol_type)) + 
+  geom_histogram(stat ="count") +
+  labs(title = "All stations")
+plot_grid(p_op_analysis_protocol_bbb, p_op_analysis_protocol, ncol = 2)
+```
+
+```{r, eval = FALSE}
+bootstrap_bbb <- map(seq(1,10),
+  function(x) {
+
+    sampled_st <- map(c(complete = "complete", partial = "partial"), function (y) {
+      st_id <- unique(op_analysis_bbb[op_analysis_bbb$protocol_type == y,
+	]$station)
+      sample(x = st_id, size = 20, replace = FALSE)
+    })
+
+    op_analysis_bbb %>%
+      filter(station %in% unlist(sampled_st))
+  }
+)
+names(bootstrap_bbb) <- letters[1:10]
+
+bootstrap_sem <- map(c(bootstrap_bbb, list(full = op_analysis)),
+  ~build_dataset_get_sem_coefficient(
+    .op = .x,
+    sem_fun = compute_stab_sem_rich_beta,
+    dest_dir = mypath("data", "species"))
+)
+
+sem_results <- map(bootstrap_sem,
+  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
+  enframe() %>%
+  rename(dataset = name) %>%
+  unnest(value)
+
+# Reformat
+colnames(sem_results) <- str_to_lower(colnames(sem_results))
+sem_results %>%
+  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
+  ggplot(aes(x = r_p, y = std.estimate)) +
+  geom_point(aes(color = dataset)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+
+#### CV by basin
+
+```{r}
+st_basin %<>%
+  mutate(basin = str_replace_all(basin, "RHIN|MEUSE", "RHIN MEUSE"))
+sync_basin <- compute_synchrony_over_basin(com = community_analysis, basin = st_basin, .op = op_analysis)
+sync_basin %>%
+  filter(!is.na(basin)) %>%
+  filter(!basin %in% c("ESCAUT SOMME", "MEUSE", "RHIN")) %>%
+  ggplot(aes(x = richness_tot, y = 1/ cv_com, label = basin)) +
+  geom_point() +
+  geom_text(hjust = 0, nudge_x = 0.05) +
+  labs(
+    x = "Total richness", y = "Biomass stability",
+    title = "Basin scale",
+    caption = "Average biomass by species by year and by basin was taken to
+    compute CV."
+  )
+```
+
 #### Productivity
@@
 
-prod_sem <- compute_prod_sem(.data = sem_data)
+prod_sem <- compute_prod_sem_rich_beta(.data = sem_data)
 

### 2020-02-24 manuscript/bef_stability/manuscript.Rmd
compute total effect on BM sem + little updates

@@
 # Compute stability, network metrics, etc with ;he new datasets
-com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))
+com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "classes"))
 
@@
 # Compute SEMs
-stab_sem_rich_beta <- compute_stab_sem_rich_beta(.data = sem_data,
-  random_effect = as.formula("~1|basin"))
 stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
   random_effect = as.formula("~1|basin"))
-stab_sem_meta <- compute_stab_sem_meta(.data = sem_data,
-  random_effect = as.formula("~1|basin"))
-stab_sem <- compute_stab_sem(.data = sem_data,
-  random_effect = as.formula("~1|basin"))
 
-bm_sem <- compute_prod_sem(.data = sem_data,
-  random_effect = as.formula("~1|basin"))
 bm_sem_rich <- compute_prod_sem_rich(.data = sem_data,
-  random_effect = as.formula("~1|basin"))
-bm_sem_rich_beta <- compute_prod_sem_rich_beta(.data = sem_data,
   random_effect = as.formula("~1|basin"))
@@
 library(ggraph)
-p_stab_sem <- ggpiecewisesem(stab_sem)
-p_stab_sem_rich_beta <- ggpiecewisesem(stab_sem_rich_beta)
 p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
@@
 
-p_bm_sem <- ggpiecewisesem(bm_sem)
 p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
@@
 ```{r get-sem-coeff}
-coef_stab_sem_sum <- coef(stab_sem) %>%
-  group_by(Response) %>%
-  nest() %>%
-  mutate(sum_c = map_dbl(data, ~ sum(.x$Std.Estimate)))
+total_effect_stab_sem <- compute_stab_sem_indirect(sem = stab_sem_rich,
+  p_val_thl = 0.05)
 
-coef_stab_sem <- coef(stab_sem_rich_beta) %>%
+total_effect_bm_sem <- compute_bm_sem_indirect(sem = bm_sem_rich,
+  p_val_thl = 0.05)
+
+coef_stab_sem <- coef(stab_sem_rich) %>%
   select(- 9) %>%
@@
 
-#cor_mat <- cor(sem_data[, !names(sem_data) %in% c("station", "basin")])
+coef_bm_sem <- coef(stab_bm_rich) %>%
+  select(- 9) %>%
+  filter(P.Value < 0.05)
 ```
@@
 
-## Species richness has a destabilizing effect on community
+## Contradictory responses of species richness on total biomass and biomass stability
 
@@
   xlim(lim_log_rich_tot) +
-  #scale_y_log10() +
-  #scale_x_log10() +
   labs(x = richness_lab, y = stab_lab) +

### 2020-02-24 R/community_analysis.R

@@ -31,8 +31,8 @@ summarise_network_over_time <- function (op = NULL, network = NULL,
   com <- op %>%
     dplyr::left_join(network, by = "opcod") %>%
     dplyr::group_by(station) %>%
-    dplyr::rename(mean_troph_level = troph_level_avg,
-      max_troph_level = troph_length) %>%
+    #dplyr::rename(mean_troph_level = troph_level_avg,
+      #max_troph_level = troph_length) %>%
     dplyr::summarise_at(metrics,
       list(cv = ~sd(.) / mean(.), med = median, stab = ~mean(.) / sd(.)))
 

### 2020-02-24 R/plot_methods.R

@@ -626,7 +626,7 @@ build_diag_from_sem <- function (fit = NULL, p_val_thd = NULL) {
   node_set %<>%
     mutate(
       type = map_chr(nodes, function (x) {
-	if (any(paste0("RC", seq(1,5)) %in% x)) {
+	if (any(c(paste0("RC", seq(1,5)), paste0("log_RC", seq(1,5))) %in% x)) {
 	  type <- "evt" 
 	} else if (x == "log_rich_tot") {
 	  type <- "rich"

### 2020-02-24 report/08-infer-interactions.Rmd
Test PLNmodels

## Infer species association

The goal is to infer species associations thanks to `PLNmodels` R package.

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(network_analysis, dir = mypath("data", "classes"))
myload(community_analysis, dir = data_common)
```

```{r get-fish-network-abun}
fish_abun <- network_analysis %>%
  unnest(composition) %>%
  select(opcod, sp_class, nind) %>%
  filter(!is.na(opcod))
```

```{r get-opcod-covariate}
myload(habitat_pressure, dir = mypath("report"))
myload(press_metrics, flow_temp_metrics, dir = data_common)
myload(env_analysis, geo_station, dir = data_common)
myload(op_analysis, dir = data_common)

# DBO:
press <- press_metrics %>%
  filter(category %in% c("DBO")) %>%
  rename(station = id) %>%
  spread(category, press)
# temperature and flow 
flow_temp <- flow_temp_metrics %>%
  ungroup() %>%
  rename(station = id) %>%
  spread(category, press)
# River desc:
env <- env_analysis %>%
  select(opcod, width_river, avg_depth_station)
# Alt, d_source
position <- geo_station %>%
  select(station, alt, d_source)

# Collect data:
## Fish operation:
op <- op_analysis %>%
  select(opcod, station, year, surface, length_sourced) %>%
  left_join(env, by = c("opcod"))

## covariate table:
covariates <- press %>% 
  left_join(flow_temp, by = c("station", "year")) %>%
  left_join(position, by = c("station")) %>%
  left_join(
    select(op, opcod, station, year, width_river, avg_depth_station), by = c("station", "year")) %>%
  select(-station, -year) %>%
  filter(!is.na(opcod))

```

```{r}

# Sanitize opcod:
map_dbl(list(fish_abun, covariates), ~length(unique(.x$opcod))) 
fish_ok <- fish_abun %>%
  filter(opcod %in% unique(covariates$opcod)) %>%
  arrange(opcod)
cov_mat <- covariates %>%
  filter(opcod %in% unique(fish_abun$opcod)) %>%
  arrange(opcod) %>%
  as.matrix
rownames(cov_mat) <- cov_mat[, "opcod"] 
cov_mat  <- cov_mat[, !colnames(cov_mat) %in% "opcod"]

# remove opcod and build abundance matrix
mat_abun <- fish_abun %>%
  spread(sp_class, nind)%>%
  #select(-opcod) %>%
  as.matrix
rownames(mat_abun) <- mat_abun[, "opcod"] 
mat_abun <- mat_abun[, !colnames(mat_abun) %in% "opcod"]

```

```{r}
library(PLNmodels)
fish <- prepare_data(
  counts = mat_abun, 
  covariates = cov_mat)
network_models <- PLNnetwork(Abundance ~ 1 + offset(log(Offset)), data = fish)
plot(network_models, "diagnostic")
plot(network_models)
network_models
model_StARS <- getBestModel(network_models, "StARS")

my_graph <- plot(model_StARS, plot = FALSE)
plot(model_StARS)
plot(model_StARS, type = "support", output = "corrplot")
```

```{r}
data(trichoptera)
trichoptera <- prepare_data(trichoptera$Abundance, trichoptera$Covariate)
network_models <- PLNnetwork(Abundance ~ 1 + offset(log(Offset)), data = trichoptera)
plot(network_models)
model_StARS <- getBestModel(network_models, "StARS")
my_graph <- plot(model_StARS, plot = FALSE)
plot(model_StARS)
```

### 2020-02-25 manuscript/bef_stability/manuscript.Rmd
Sensivity analysis + cba + improve total effect computation

@@
 myload(nmds, habitat_pressure, dir = mypath("report"))
-myload(op_analysis, dir = mypath("data"))
+myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
+myload(biomass_ts_sax, dir = mypath("data"))
+op_analysis_bbb <- filter(op_analysis, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
 
 # Compute stability, network metrics, etc with ;he new datasets
-com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "classes"))
-
+com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb, dest_dir = mypath("data", "classes"))
 # Compute sem dataset 
@@
 
-coef_bm_sem <- coef(stab_bm_rich) %>%
+coef_bm_sem <- coef(bm_sem_rich) %>%
   select(- 9) %>%

### 2020-02-25 report/05-stability.Rmd
Sensivity analysis + cba + improve total effect computation

@@
   gather(sp, med_occ, everything())
-
 ```
@@
 
+#### Sensivity to dataset
+
 ```{r sensitivity, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
@@
   biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
-
+op_analysis_cba <- filter(op_analysis, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "cba",]$station)
+op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
 #library(future)
 #plan(multiprocess)
-sem_sensivity_data <- list(full = op_analysis, wo_holes = op_analysis_wo_holes, bbb = op_analysis_bbb)
-sem_l_data <- furrr::future_map(sem_sensivity_data,
+#undebug(build_dataset_get_sem_coefficient)
+#undebug(compute_community_temporal_analysis)
+#undebug(summarise_network_over_time)
+myload(network_metrics, dir = mypath("data", "classes"))
+sem_sensivity_data <- list(full = op_analysis, cba = op_analysis_cba, bbb = op_analysis_bbb)
+sem_stab_l_data <- furrr::future_map(sem_sensivity_data,
+  ~build_dataset_get_sem_coefficient(
+    .op = .x,
+    sem_fun = compute_stab_sem_rich,
+    dest_dir = mypath("data", "classes"))
+)
+
+# Nb station by dataset 
+nb_station <- map_int(sem_sensivity_data, ~length(unique(.x$station)))
+
+sem_stab_results <- map(sem_stab_l_data,
+  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
+  enframe() %>%
+  rename(dataset = name) %>%
+  unnest(value)
+
+# Reformat
+colnames(sem_stab_results) <- str_to_lower(colnames(sem_stab_results))
+sem_stab_results %>%
+  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
+  ggplot(aes(x = r_p, y = std.estimate)) +
+  geom_point(aes(color = dataset)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+
+```{r, fig.dim = c(10, 5)}
+p_sensitivity_stab_sem <- map(sem_stab_l_data, ggpiecewisesem)
+p_sensitivity_stab_sem %<>% map2(., names(sem_sensivity_data),  ~ .x + labs(title = .y))
+plot_grid(plotlist = p_sensitivity_stab_sem)
+```
+
+```{r}
+sem_bm_l_data <- furrr::future_map(sem_sensivity_data,
+  ~build_dataset_get_sem_coefficient(
+    .op = .x,
+    sem_fun = compute_prod_sem_rich,
+    dest_dir = mypath("data", "classes"))
+)
+sem_bm_results <- map(sem_bm_l_data,
+  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
+  enframe() %>%
+  rename(dataset = name) %>%
+  unnest(value)
+
+# Reformat
+colnames(sem_bm_results) <- str_to_lower(colnames(sem_bm_results))
+sem_bm_results %>%
+  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
+  ggplot(aes(x = r_p, y = std.estimate)) +
+  geom_point(aes(color = dataset)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+
+```{r}
+p_sensitivity_bm_sem <- map(sem_bm_l_data, ggpiecewisesem)
+p_sensitivity_bm_sem %<>% map2(., names(sem_sensivity_data),  ~ .x + labs(title = .y))
+plot_grid(plotlist = p_sensitivity_bm_sem)
+```
+
+```{r}
+p_op_analysis_protocol_bbb <- op_analysis_bbb %>%
+  group_by(station) %>%
+  slice(1) %>%
+  ggplot(aes(x = protocol_type)) + 
+  geom_histogram(stat ="count") +
+  labs(title = "Station bbb")
+
+p_op_analysis_protocol <- op_analysis %>%
+  group_by(station) %>%
+  slice(1) %>%
+  ggplot(aes(x = protocol_type)) + 
+  geom_histogram(stat ="count") +
+  labs(title = "All stations")
+plot_grid(p_op_analysis_protocol_bbb, p_op_analysis_protocol, ncol = 2)
+```
+
+```{r, eval = FALSE}
+bootstrap_bbb <- map(seq(1,10),
+  function(x) {
+
+    sampled_st <- map(c(complete = "complete", partial = "partial"), function (y) {
+      st_id <- unique(op_analysis_bbb[op_analysis_bbb$protocol_type == y,
+	]$station)
+      sample(x = st_id, size = 20, replace = FALSE)
+    })
+
+    op_analysis_bbb %>%
+      filter(station %in% unlist(sampled_st))
+  }
+)
+names(bootstrap_bbb) <- letters[1:10]
+
+bootstrap_sem <- map(c(bootstrap_bbb, list(full = op_analysis)),
   ~build_dataset_get_sem_coefficient(
@@
 
-sem_results <- map(sem_l_data,
+sem_results <- map(bootstrap_sem,
   ~.x$coefficients[-ncol(.x$coefficients)]) %>%
@@
 
-```{r, fig.dim = c(10, 5)}
-p_sensitivity_stab_sem <- map(sem_l_data, ggpiecewisesem)
-p_sensitivity_stab_sem %<>% map2(., names(sem_sensivity_data),  ~ .x + labs(title = .y))
-plot_grid(plotlist = p_sensitivity_stab_sem)
-```
-```{r}
-p_op_analysis_protocol_bbb <- op_analysis_bbb %>%
+```{r sampling-span-stab}
+span_sampling <- op_analysis %>%
   group_by(station) %>%
-  slice(1) %>%
-  ggplot(aes(x = protocol_type)) + 
-  geom_histogram(stat ="count") +
-  labs(title = "Station bbb")
-
-p_op_analysis_protocol <- op_analysis %>%
-  group_by(station) %>%
-  slice(1) %>%
-  ggplot(aes(x = protocol_type)) + 
-  geom_histogram(stat ="count") +
-  labs(title = "All stations")
-plot_grid(p_op_analysis_protocol_bbb, p_op_analysis_protocol, ncol = 2)
-```
-
-```{r, eval = FALSE}
-bootstrap_bbb <- map(seq(1,10),
-  function(x) {
-
-    sampled_st <- map(c(complete = "complete", partial = "partial"), function (y) {
-      st_id <- unique(op_analysis_bbb[op_analysis_bbb$protocol_type == y,
-	]$station)
-      sample(x = st_id, size = 20, replace = FALSE)
-    })
-
-    op_analysis_bbb %>%
-      filter(station %in% unlist(sampled_st))
-  }
-)
-names(bootstrap_bbb) <- letters[1:10]
-
-bootstrap_sem <- map(c(bootstrap_bbb, list(full = op_analysis)),
-  ~build_dataset_get_sem_coefficient(
-    .op = .x,
-    sem_fun = compute_stab_sem_rich_beta,
-    dest_dir = mypath("data", "species"))
-)
-
-sem_results <- map(bootstrap_sem,
-  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
-  enframe() %>%
-  rename(dataset = name) %>%
-  unnest(value)
-
-# Reformat
-colnames(sem_results) <- str_to_lower(colnames(sem_results))
-sem_results %>%
-  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
-  ggplot(aes(x = r_p, y = std.estimate)) +
-  geom_point(aes(color = dataset)) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+  summarise(span = max(year) - min(year) + 1)
+
+sem_data %>%
+  left_join(span_sampling, by = "station") %>%
+  ggplot(aes(x = span, y = biomass_stab)) +
+  geom_point()
 ```

### 2020-02-26 manuscript/bef_stability/manuscript.Rmd
DiagrammeR plot ok + safer class/species metrics computation

@@
 # Compute stability, network metrics, etc with ;he new datasets
-com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb, dest_dir = mypath("data", "classes"))
+com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb, dest_dir = mypath("data", "species"))
 # Compute sem dataset 
@@
 p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
+p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
 
 library(DiagrammeR)
-graph <- build_diag_from_sem(stab_sem_rich, p_val_thd = 0.05)
 
-p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
+p_format <- "png"
+p_width <- 500
+p_height <- 500
+
+stab_sem_path <- mypath("manuscript", "bef_stability",
+  paste0("stab_sem.", p_format))
+stab_bm_path <- mypath("manuscript", "bef_stability",
+  paste0("bm_sem.", p_format))
+
+graph_stab_sem <- build_diag_from_sem(stab_sem_rich, p_val_thd = 0.05)
+render_graph(graph_stab_sem)
+export_graph(graph = graph_stab_sem, file_type = p_format,
+  file_name = stab_sem_path,
+  height = p_height,
+  width = p_width
+)
+#source(mypath("R", "plot_methods.R")) 
+graph_bm_sem <- build_diag_from_sem(bm_sem_rich, p_val_thd = 0.05)
+render_graph(graph_bm_sem)
+export_graph(graph = graph_bm_sem, file_type = p_format,
+  file_name = stab_bm_path,
+  #file_name = "stab_sem.svg",
+  height = p_height,
+  width = p_width 
+)
+
+library(magick)
+img_stab_sem <- mypath("manuscript", "bef_stability", "stab_sem.svg") %>%
+  image_read_svg(width = 1300, height = 1000)
+p_stab_sem_rich <- ggdraw() +
+  draw_image(img_stab_sem)
+img_bm_sem <- mypath("manuscript", "bef_stability", "bm_sem.svg") %>%
+  image_read_svg(width = 1000, height = 700)
+p_bm_sem_rich <- ggdraw() +
+  draw_image(img_bm_sem)
+
 ```
@@
 to_plot <- c(1, 6, 7)
+
 plot_grid(

### 2020-02-26 analysis/02_compute_network_metrics.R

@@ -116,11 +116,11 @@ trophic_level %<>%
 ## Assign to each network its trophic group:
 source('../analysis/misc/parallel_setup.R')
 
-#if (!is.null(options("network.type")) & options("network.type") == "species") {
-  #var_chr <- "species"
-#} else {
+if (!is.null(options("network.type")) & options("network.type") == "species") {
+  var_chr <- "species"
+} else {
   var_chr <- "sp_class"
-#}
+}
 network_analysis %<>%
   mutate(
   composition = furrr::future_map(composition, function (compo, troph_group, var2join){

### 2020-03-04 manuscript/bef_stability/manuscript.Rmd
Inverse PCA axis

--- 2020-02-24 manuscript/bef_stability/manuscript.Rmd
@@
 # Introduction
+
+Cf blutghen for CVsp as portfolio and statistical averaging of species.
+Synchrony as insurance hypothesis facing environmental variations.
 
@@
 ```{r}
-myload(temporal_community_metrics, dir = mypath("data"))
-myload(synchrony, dir = mypath("data"))
+myload(nmds, habitat_pressure, dir = mypath("report"))
 st_basin <- get_basin_station(sf_obj = FALSE)
+myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
+myload(biomass_ts_sax, dir = mypath("data"))
+op_analysis_bbb <- filter(op_analysis, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
 
-myload(temporal_network_metrics, dir = mypath("data", "classes"))
-temporal_network_metrics_classes <- temporal_network_metrics
-myload(temporal_network_metrics, dir = mypath("data", "species"))
+# Compute stability, network metrics, etc with ;he new datasets
+com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb)
+# Compute sem dataset 
+sem_data <- compute_sem_dataset(
+  com = com_data[["tps_com"]],
+  network = com_data[["tps_net"]],
+  hab_press = habitat_pressure,
+  sync = com_data[["sync"]],
+  nmds = NULL,
+  basin = st_basin
+  )
 
-stab_div_troph <- temporal_network_metrics_classes %>%
-  dplyr::select(station, troph_group) %>%
-  unnest(troph_group) %>%
+stab_div_troph <- com_data$tps_bm_troph %>%
   filter(troph_group != 1) %>%
@@
 )
-habitat_pressure <- build_habitat_pressure_dataset(
+habitat_press <- build_habitat_pressure_dataset(
   .habitat_analysis = hab_analysis,
@@
   "avg_depth_station_cv", "DBO_cv")
-pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean, evt_var_cv, "station")] %>%
+pca_pressure <- habitat_press[, names(habitat_press) %in% c(evt_var_mean, evt_var_cv, "station")] %>%
   na.omit
@@
 library(piecewiseSEM)
-
-myload(nmds, habitat_pressure, dir = mypath("report"))
-myload(op_analysis, dir = mypath("data"))
-
-# Compute stability, network metrics, etc with ;he new datasets
-com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "classes"))
-
-# Compute sem dataset 
-sem_data <- compute_sem_dataset(
-  com = com_data[["tps_com"]],
-  network = com_data[["tps_net"]],
-  hab_press = habitat_pressure,
-  sync = com_data[["sync"]],
-  nmds = NULL,
-  basin = st_basin
-  )
 ```
@@
 p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
+p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
 
 library(DiagrammeR)
-graph <- build_diag_from_sem(stab_sem_rich, p_val_thd = 0.05)
 
-p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
+p_format <- "png"
+p_width <- 700
+p_height <- 700
+
+stab_sem_path <- mypath("manuscript", "bef_stability",
+  paste0("stab_sem.", p_format))
+bm_sem_path <- mypath("manuscript", "bef_stability",
+  paste0("bm_sem.", p_format))
+
+graph_stab_sem <- build_diag_from_sem(stab_sem_rich, p_val_thd = 0.05)
+render_graph(graph_stab_sem)
+export_graph(graph = graph_stab_sem, file_type = p_format,
+  file_name = stab_sem_path,
+  height = p_height - p_height*20/100,
+  width = p_width
+)
+#source(mypath("R", "plot_methods.R")) 
+graph_bm_sem <- build_diag_from_sem(bm_sem_rich, p_val_thd = 0.05)
+render_graph(graph_bm_sem)
+export_graph(graph = graph_bm_sem, file_type = p_format,
+  file_name = bm_sem_path,
+  #file_name = "stab_sem.svg",
+  height = p_height,
+  width = p_width 
+)
+
+library(magick)
+library(rsvg)
+img_stab_sem <- stab_sem_path %>%
+  image_read()
+p_stab_sem_rich <- ggdraw() +
+  draw_image(img_stab_sem)
+img_bm_sem <- bm_sem_path %>%
+  image_read()
+p_bm_sem_rich <- ggdraw() +
+  draw_image(img_bm_sem)
+
 ```
@@
 
-coef_bm_sem <- coef(stab_bm_rich) %>%
+coef_bm_sem <- coef(bm_sem_rich) %>%
   select(- 9) %>%
   filter(P.Value < 0.05)
+```
+
+```{r stab-network}
+sem_data %>%
+  select(sync, cv_sp, ct, t_lvl) %>%
+  gather(network, metrics, ct, t_lvl) %>%
+  gather(stab_comp, value, sync, cv_sp) %>%
+  ggplot(aes(y = value, x = metrics)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(stab_comp ~ network, scales = "free_x")
+
+stab_ct_mod <- lmer(data = sem_data,
+  #fixed = log_bm ~ log_rich_tot * troph_group,
+  formula = log_stab ~ ct + (1 | basin)
+  #random = ~ 1 + log_rich_tot * troph_group | basin,
+  #control = ctrl 
+)
+stab_ct_boot <- bootMer(stab_ct_mod, mySumm2, nsim = 100)
+stab_ct_ci <- confint(stab_ct_boot)
+
+stab_ct_sum <- piecewiseSEM::rsquared(stab_ct_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
+
+pred_stab_ct_mod <- ggpredict(stab_ct_mod, terms = c("ct"), type = "fe")
+#plot(pred_troph_mod, add.data = TRUE)
+stab_ct_pred <- pred_stab_ct_mod %>%
+  as_tibble() %>%
+  rename(
+    log_bm = predicted,
+    log_rich_tot = x,
+    troph_group = group
+  )
+
+# get coeff
+coef_stab_ct <- map(list(stab = stab_ct_mod), fixed.effects)
+
+stab_tlvl_mod <- lmer(data = sem_data,
+  #fixed = log_bm ~ log_rich_tot * troph_group,
+  formula = log_stab ~ t_lvl + (1 | basin)
+  #random = ~ 1 + log_rich_tot * troph_group | basin,
+  #control = ctrl 
+)
+stab_tlvl_boot <- bootMer(stab_tlvl_mod, mySumm2, nsim = 100)
+stab_tlvl_ci <- confint(stab_tlvl_boot)
+
+stab_tlvl_sum <- piecewiseSEM::rsquared(stab_tlvl_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
+
+pred_stab_tlvl_mod <- ggpredict(stab_tlvl_mod, terms = c("t_lvl"), type = "fe")
+#plot(pred_troph_mod, add.data = TRUE)
+stab_tlvl_pred <- pred_stab_tlvl_mod %>%
+  as_tibble() %>%
+  rename(
+    log_bm = predicted,
+    log_rich_tot = x,
+    troph_group = group
+  )
+
+# get coeff
+coef_stab_tlvl <- map(list(stab = stab_tlvl_mod), fixed.effects)
+
 ```
@@
       ncol = length(to_plot), labels = LETTERS[1]),
-  plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[2:3]),
+  plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[2:3], rel_widths = c(.6, .4)),
   ncol = 1,
@@
 
-- Habitat: (+ / -)
-  - RC 1: width & depth & flow med, d source, strahler 	/
-  - RC 2: T°C med 					/ slope, alt 
-  - RC 3: 						/ flow CV, DBO med
-  - RC 4: river width med, depth med 			/
-  - RC 5: DBO CV 					/
+```{r}
+total_effect_bm_sem
+total_effect_stab_sem
+```
 
-- Stability:
-  - Stability component:
-    - CV is the main driver of stability:
-  - Community structure: 
-    - Species richness had no direct effects on CV but on synchrony!  
-    - Evenness of biomass dist increased CV but decreased synchrony
-    - Trophic level decreased CV
-    - Betadiv increases CV
-  - Habitat/Env:
-    - few direct effect on stability
-      - direct: CV_sp dec with increasing RC3, cad enrichment and flow_cv decrease.  
-      - direct: CV_sp inc with increasing RC2, cad temperature_med.  
-    - indirectly affect stability by modulating community structure,
-      particularly richness
+---
+# Total biomass
+---
+We found that the primary drivers of total biomass were the total species
+richness (TSR) and the average trophic level (Tlvl) ($r_\delta = 0.35$ and
+$r_\delta = 0.40$ resp.) whereas connectance had no significant effect  (Fig.
+\@ref{fig:sem-plot} C). The stream size had a direct positive effect on total
+biomass ($r_\delta = 0.22$) whereas CV of flow and avg DBO increased total
+biomass ($r_\delta = - 0.2$). Avg temperature, CV of river size and CV of DBO
+had no direct effects on total biomass.
 
-- Total biomass:
-  - Community structure:
-    - Richness increased total biomass / had the bigger effect
-    - Even community deceased total biomass
-    - Species turnover decreased total biomass  
-    - Connectance increased biomass
-  - Habitat/Env:
-    - very weak to no direct effect on total biomass 
-    - Effect of environment is thus mediated by the community structure
+TSR had also a indirect positive effect on total biomass through Tlvl ($r_\delta
+= 0.21$), that is, TSR had a total positive effect of $0.56$ on total biomass.
+The stream size had a total effect on total biomass as strong as TSR ($r_\delta
+= 0.54$), indirectly through Tlvl ($r_\delta = 0.10$) and TSR ($r_\delta = 0.22$).
+The avg temperature of the river had an indirect positive effect on total biomass
+($r_\delta = 0.48$), through Tlvl ($r_\delta = 0.11$) and TSR ($r_\delta = 0.33$).
+Avg DBO, CV DBO and CV of river size had no or weak indirect effect on total
+biomass.
+
+---
+# Biomass stability
+---
+\overline{CV_{sp}} ($r_\delta = -1.26$) decreased biomass stability more than
+synchrony ($r_\delta = -0.55$, Figure \@ref{fig:sem-plot}). TSR had a strong
+positive effect on \overline{CV_{sp}} and a strong negative effect on synchrony
+whereas Tlvl and connectance had no significant effects on either
+\overline{CV_{sp}} nor synchrony. The avg river size had a small positive direct
+effect on synchrony ($r_\delta = 0.19$). The other environmental variables had
+no significant direct effects on \overline{CV_{sp}} nor synchrony.
+
+Indirectly through synchrony and \overline{CV_{sp}}, TSR had a total negative
+effect on biomass stability ($r_\delta = -0.26$). Avg river size and avg
+temperature had also a total effect which was negative on biomass stability
+(resp. $r_\delta = -0.24$ and $r_\delta = -0.16$), going through richness 
+(resp. $r_\delta = -0.10$ and $r_\delta = -0.16$).
 
@@
 
-The effect of richness on biomass stability follows a power law with a negative
-coefficient, meaning that it's a decelerating function.
+# Discussion
 
-- R diagramm:
-  - https://rstudio-pubs-static.s3.amazonaws.com/78926_5aa94ae32fae49f3a384ce885744ef4a.html
+We tested for the first time the determinants of temporal biomass stability in a
+foodweb with an empirical dataset at such high temporal and spatial scales.
 
-- Latex:
-  - csv:
-    - https://tex.stackexchange.com/questions/178904/use-datatool-to-read-a-row-from-a-csv-file-then-use-the-variables-in-the-docume
-    - https://tex.stackexchange.com/questions/40901/datatool-getting-a-specific-value-given-the-value-of-another-column
-  - path: 
-- Reporting:
-  - equations: https://stats.stackexchange.com/questions/169115/reporting-the-actual-formula-equation-of-an-lme-model-with-factors-used-in-r
-  - log-log results:
-    - https://dev.to/rokaandy/logarithmic-transformation-in-linear-regression-models-why-when-3a7c
-    - https://stats.stackexchange.com/questions/18480/interpretation-of-log-transformed-predictor-and-or-response
+Surprisingly, we found a negative relationship biomass stability and species
+richness whereas there was a positive one between total biomass and species
+richness. Those relationships followed a power law, meaning that they represent
+respectively accelerating and decelerating functions. Overall, it contrasts
+with studies in grasslands [@tilman_biodiversity_2006, @zhang_scale_nodate],
+mesocosms [@pennekamp_biodiversity_2018] or other animals
+[@olivier_independent_nodate] where positive relationships are typically found
+between biomass stability and species richness. Even @franssen_annual_2011 found
+that species rich communities are more stable than species poor in streams.
 
-# Discussion
+@grace_integrative_2016 found that biomass negatively linked to species richness
+in grasslands, notably because of light competition. In freshwater ecosystems,
+where resources are based on trophic relationship, TOCOMPLETE.
+
+The total biomass of high and low trophic group trophic groups responded both
+positively to species richness but not biomass stability TOREPHRASE. There is a
+paradox where the high trophic group is overall more stable than the low but
+species richness had a destabilizing effect on the former whereas a stabilizing
+on the latter. @shanafelt_david_w._stability_nodate showed in a theoretical
+study in trophic chains, the top trophic level is the more stable TOEXPLORE.
+The comparison between our study and theoretical studies stays limited because
+fishes in our system have a large diet and consume food item of several trophic
+level while theoretical studies consider system in which one species of one
+trophic level feeds only on the trophic level directly inferior
+[@shanafelt_david_w._stability_nodate] ADD REF.
+
+---
+# Effect of synchrony and cv_sp  
+---
+It was unexpected that the average population CV had a stronger negative effect
+on biomass stability than synchrony [@bluthgen_land_2016;
+@olivier_independent_nodate] *cf ref in bluthgen*. We see two hypothesis that
+can raise this effect. First, the opportunity for diet differentiation can be
+low in streams compare to other organisms. Bird species are for example quite
+specialized in seed, flying or soil arthropods or mammals which gives
+opportunities for independent dynamics. Plants also can achieve independent
+dynamics either spatial segregation, niche differentiation. Because fish
+species even piscivorous one are quite opportunistic in
+their foraging. Secondly, in trophic network, amplitude of species biomass
+involved in trophic interactions could covary positively TOTHINKABOUT.
+
+---
+# Effect of trophic level and connectance are richness effects:
+---
+Our path analysis reveled that, although species richness has a strong effect on
+connectance and the average trophic level, network structure had itself little
+to no effect either on synchrony nor average population stability. This result
+contradicts precedent theoretical studies on the relationship
+between stability and network structure [@angelis_stability_1975, @may_will_1972], although
+they considered different stability metrics (i.e. local stability of equilibrium
+point). The reason might be that in our inferred network, network structure is
+strongly constraints by assembly processes. Indeed, connectance decreased with
+increasing species richness [@thebault_stability_2010], because a small fraction
+of links are realized because of food diet constraints. In theoretical studies,
+connectance can be tuned from 0 (no links) to 1 (all possible links are
+present). SAMEFORTLVL
+Finally, the biomass stability of freshwater ecosystems can be derived by
+species richness because, through trophic structure constraints, species
+richness determine largely network structure.
 
@@
 
+```{r save-plot}
+
+save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div.pdf",
+  p_stab_div,
+  base_height = 3,
+  bg = "transparent",
+  ncol = 1)
+
+save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div_troph.pdf",
+  p_stab_div_troph + theme(legend.position = "bottom"),
+  base_height = 3,
+  bg = "transparent",
+  ncol = 1)
+
+```
+
 # References

### 2020-03-04 report/06-pressure.Rmd
Inverse PCA axis

@@
   dir = data_common)
+
+myload(yearly_press_interp, dir = mypath())
 ```

### 2020-03-04 report/08-infer-interactions.Rmd
Inverse PCA axis

@@
   arrange(opcod) %>%
-  as.matrix
+  as.data.frame
+
 rownames(cov_mat) <- cov_mat[, "opcod"] 
@@
 mat_abun <- fish_abun %>%
-  spread(sp_class, nind)%>%
-  #select(-opcod) %>%
-  as.matrix
+  spread(sp_class, nind) %>%
+  as.data.frame
+
 rownames(mat_abun) <- mat_abun[, "opcod"] 
@@
 
+save_dir <- mypath("report", "stephane")
+if (!dir.exists(save_dir)) {
+  dir.create(save_dir)
+}
+mysave(mat_abun, cov_mat, dir = save_dir)
 ```

### 2020-03-04 R/statistical_analysis.R

@@ -78,7 +78,7 @@ compute_sem_dataset <- function (
       log_bm = log10(prod),
       log_RC1 = log10(RC1 + abs(min(RC1)) + 1),
       log_RC2 = log10(RC2 + abs(min(RC2)) + 1),
-      log_RC3 = log10(RC3 + abs(min(RC3)) + 1)
+      log_RC3 = log10((RC3)*(-1) + abs(min((RC3)*(-1))) + 1)
     )
   return(dsem)
 

### 2020-03-10 manuscript/bef_stability/manuscript.Rmd
New stab indirect effect computation, to be tested rigourously
Add introduction bullet points + indirect effect of bm + mv fig 1 to 2

@@
 output:
-  prettydoc::html_pretty:
-    theme: cayman
-    highlight: github
-    math: katex
+  pdf_document:
+      fig_caption: true
 bibliography: references.bib
@@
 source(mypath("R", "statistical_analysis.R"))
+source(mypath("R", "total_sem_effect.R"))
 source(mypath("R", "press_methods.R"))
@@
 Synchrony as insurance hypothesis facing environmental variations.
+
+- Diversity - stability and diversity - biomass / productivity
+  - well studied: both experimentally, empirically and theoretically
+  - mecanisms:
+    - stability: insurance (asynchrony),
+    - diversity: overyielding (complementarity)
+  - key papers: [@tilman_biodiversity_2006, @loreau_species_2008,
+    @thibaut_understanding_2013, @may_will_1972]
+  - BUT: less vertical diversity, trophic communities
+
+- Vertical diversity and stability/biomass
+  - well studied: theoretically and (experimentally, less)
+  - mecanisms:
+    - stability: top-down and bottom-up effect
+    - biomass: top-down and bottom-up effects (pyramids of biomass)
+  - key papers:[@barbier_pyramids_2019, @shanafelt_david_w._stability_nodate]
+  - BUT: local stability, little systems
+
+- Environment can drive stability and biomass:
+  - forcing: environmental forcing on communities 
+  - can lead to misleading effect: @grace_integrative_2016
+
+- Big scope assessment:
+  - inconsistency between theoretical and empirical stability
+    - theoretical: no cv_sp nor synchrony
+  - No studies on stability-richness in empirical trophic communities
+    - no effect of trophic structure
+
+- Goal: Assess relation biomass/stability-diversity in empirical trophic communities
+  - introduce effect of trophic structure and environment
+  - merge gap between theoretical and empirical studies
+
+- What we have done:
+  - big empirical dataset
+  - rebuilding empirical network
+  - assess relationship between environment, community structure and stability
 
@@
     time series)
-  - remove operations which sampling effort (length of river) superior to average
+  - remove operations which sampling effort (length of river sampled) superior to average
     plus or minus 30% of sd (by station)
   - kept station that had 10 or more samplings, i.e. followed 10 years or more
-
-- Biomass:
-  - infered by allometric law 
-  - approximated by $B = 0.01 \times (l^3.03)$
 
@@
   - based on diet database
+  - no information about their biomass
+
+- Size class:
+  - quantile: 9 size class per species
+
+- Interaction:
+  - Fish-resources and resources: based on diet data 
+  - Fish-fish:
+    1. diet data: is piscivorous?
+    2. allometric relationship: predation range from .03 to .45 of body size
 
 ## Community
+
+- Biomass:
+  - infered by allometric law 
+  - approximated by $B = 0.01 \times (l^3.03)$
 
@@
 
+- Collected during fishing operation:   
+  - River size (width and depth)
+  - Altitude and slope
+  - distance to source
+- Independant dataset from naiades: 
+  - flow, temperature, DBO
+    1. moving window average
+    2. annual average 
+    3. interpolation along rivers (OpenStars + SSN package)
+
 ```{r}
@@
 )
-
 ```
@@
 $$
-\Log_{10}(S_i) = \beta_0 + \beta_R\Log_{10}(x_{Ri}) + \epsilon_{ij}
-$$
-
-$$
-S_i = 10^(\beta_0 + \beta_R\Log_{10}(x_{Ri}) + \epsilon_{ij})
-$$
-
-$$
-S_i = 10^(\beta_0) \times 10^(\beta_R\Log(x_{Ri})) \times 10^(\epsilon_{ij})
-$$
-
-$$
-S_i = 10^(\beta_{0}) \times x_{Ri}10^(\beta_{R}) \times 10^(\epsilon_{ij})
+\begin{align}
+
+\log_{10}S_i &= \beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}\\
+
+S_i &= 10^{\beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}}\\
+
+S_i &= 10^{\beta_0} \times 10^{\beta_R\log_{10}x_{Ri}} \times
+10^{\epsilon_{ij}}\\
+
+S_i &= 10^{\beta_{0}} \times x_{Ri}10^{\beta_{R}} \times 10^{\epsilon_{ij}}
+
+\end{align}
 $$
@@
 
-SEM enables to reason in terms of causal relationship between components. The
-goal was to understand the mechanisms behind the negative relationship biomass
+SEM enables to reason in terms of causal relationship between components. We
+aimed to understand the mechanisms behind the negative relationship biomass
 stability and species richness and the positive relationship between total
@@
 We built a metamodel to set up the nodes and the links between the different
-compartment of the SEM. Basically, we tested the links between
-environmental conditions, community structure and stability. Theory in ecology 
-predicts that community structure influences stability. In turn, environment 
-influences community structure but also directly stability.
+compartment of the SEM. Basically, we tested the links between environmental
+conditions, community structure and stability. Theory in ecology predicts that
+community structure influences stability. In turn, environment influences
+community structure but also directly stability.
 
@@
 
-The community structure was characterized by total species richness (TSR),
-species turnover (ST), median average weighted trophic level (TLvl) and median connectance.
+The community structure was characterized by total species richness,
+median average weighted trophic level and median connectance.
 Total species richness was the number of unique fish species that were observed
-at a given station over the whole sampling. Species turnover was computed as average
-dissimilarity between the different community composition through time. The
-dissimilarity was calculated on species presence/absence with the Bray-Curtis
-method implemented in the `vegan` R package (`vegdist` function). Both median
-connectance and Tlvl were just computed as the median over the temporal period.
-For the details of the computation of the trophic networks, see Network
-inference part.
+at a given station over the whole sampling. Both median
+connectance and average trophic level were just computed as the median over the
+temporal period. For the details of the computation of the trophic networks,
+see Network inference part.
 
@@
 hypothesis about physical and climate). (1) We hypothesized that enrichment
-(characterized by DBO) and mean annual temperature will increase ST
+(characterized by DBO) and mean annual temperature will increase species turnover
 [@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
@@
 biomass stability, causal links were set from species richness to other
-community attributes. (4) We hypothesized that TSR increased ST because
-increasing species richness because of assembly processes. Species rich
-communities are more resistant to invasion and thus increase ST
-[@tilman_niche_2004; @shurin_how_2007]. (5) We hypothesized also that TSR
+community attributes. (5) We hypothesized also that species richness
 decreased connectance following results from @thebault_stability_2010;
 @winemiller_must_1989. But theoretically, some ecological networks can show the
-inverse relationship [@winemiller_must_1989]. (6) We hypothesized also that TSR
+inverse relationship [@winemiller_must_1989]. (6) We hypothesized also that species richness
 will modulate average weighted trophic level because of food web assembly
-processes. If *TSR increased and that new species are placed at random in the
-network, we expected a positive relationship between Tlvl and TSR because
-individuals of the higher trophic level have a higher body mass [to think
-again]*. Finally, we set up causal relationships from community attributes to
-stability components.
+processes. If *species richness increased and that new species are placed at
+random in the network, we expected a positive relationship between average
+trophic level and species richness because individuals of the higher trophic
+level have a higher body mass [to think again]*. Finally, we set up causal
+relationships from community attributes to stability components.
 
@@
 ---
-We hypothesized that (7) TSR decreased synchrony between species by portfolio
-effects [REF] and increased $\overline{CV_{sp}}$ [@tilman_biodiversity_2006] *to
-complete*. We hypothesized that (8) ST increased $\overline{CV_{sp}}$ and that it
-decreased synchrony. (9a) We expected that Tlvl had a positive or negative
-relationship with synchrony, bottom-up effects should result in positive whereas
-top-down in negative relationship. We expected a (9b) negative relationship
-between Tlvl and $\overline{CV_{sp}}$ if predators stabilised population
+We hypothesized that (7) species richness decreased synchrony between species
+[REF] and increased $\overline{CV_{sp}}$ [@tilman_biodiversity_2006] *to
+complete*. (8a) We expected that average trophic level had a positive or
+negative relationship with synchrony, bottom-up effects should result in
+positive whereas top-down in negative relationship. We expected a (8b) negative
+relationship between average trophic level and $\overline{CV_{sp}}$ if predators
+stabilised population
 fluctuations or if the increasing part of biomass in the predators decreased
 $\overline{CV_{sp}}$ because of their higher body mass (if mean increase faster than
-variance). (10a) Connectance was expected to decrease or increase $\overline{CV_{sp}}$
-and (10b) synchrony because of top down effects or bottom up effects.
+variance). (9a) Connectance was expected to decrease or increase $\overline{CV_{sp}}$
+and (9b) synchrony because of top down effects or bottom up effects.
 
@@
 ```{r get-sem-coeff}
-total_effect_stab_sem <- compute_stab_sem_indirect(sem = stab_sem_rich,
-  p_val_thl = 0.05)
-
-total_effect_bm_sem <- compute_bm_sem_indirect(sem = bm_sem_rich,
-  p_val_thl = 0.05)
-
 coef_stab_sem <- coef(stab_sem_rich) %>%
@@
 coef_stab_tlvl <- map(list(stab = stab_tlvl_mod), fixed.effects)
-
 ```
@@
 
-## Contradictory responses of species richness on total biomass and biomass stability
+## Drivers of total biomass and stability
+
+```{r sem-plot, fig.dim = c(10,10), fig.cap = "SEM"}
+#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
+#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple
+
+plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[1:2], rel_widths = c(.55, .45))
+```
+
+```{r get-bm-sem-single-effect}
+bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)
+get_clean_sem_coef <- function(sem = NULL, resp = NULL, pred = NULL) {
+  out <- sem[sem$Response == resp & sem$Predictor == pred, ]$Std.Estimate
+  out <- ifelse(length(out) == 0, 0, out)
+  round(out, 2)
+}
+
+rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_rich_tot")
+tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "t_lvl")
+RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_RC1")
+```
+
+```{r get-bm-tot-effect-env}
+bm_all_params <- get_coefficient_piecewisesem(sem = bm_sem_rich, p_val_thl = NULL)
+
+# effect of env on bm 
+env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05)
+# env on com 
+env_on_t_lvl <- get_env_on_com(fit = bm_all_params,
+  p_val_thl = 0.05,
+  com = "t_lvl")
+env_on_ct <- get_env_on_com(fit = bm_all_params,
+  p_val_thl = 0.05,
+  com = "ct")
+env_on_richness <- get_env_on_rich(fit = bm_all_params,
+  p_val_thl = 0.05)
+```
+
+```{r get-sem-tot-effect-rich}
+rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
+  p_val_thl = 0.05)
+rich_on_sync <- get_rich_on_bm_comp(fit = bm_all_params,
+  p_val_thl = 0.05,
+  bm_comp = "log_sync")
+rich_on_cv_sp <- get_rich_on_bm_comp(fit = bm_all_params,
+  p_val_thl = 0.05,
+  bm_comp = "log_cv_sp")
+```
+
+---
+# Total biomass
+---
+
+Species richness and the average trophic level were the main direct drivers of
+total biomass ($r_\delta = `r rich_on_bm`$ and $r_\delta = `r tlvl_on_bm`$ resp.) whereas
+connectance had no significant effect (Fig. \@ref(fig:sem-plot) C). The stream
+size had a direct positive effect on total biomass ($r_\delta = `r RC1_on_bm`$) whereas
+avg temperature, avg DBO, CV of river size and CV of DBO had no direct effects
+on total biomass.
+
+Species richness had also a indirect positive effect on total biomass through
+average trophic level, species richness had a total positive effect of $`r rich_on_bm`$
+on total biomass. The stream size had a total effect on total biomass as strong
+as species richness ($r_\delta =`r env_on_bm["log_RC1"]`$), indirectly through average trophic level
+and species richness. The avg temperature of the river had an indirect positive
+effect on total biomass ($r_\delta = `r env_on_bm["log_RC2"]`$), through
+average trophic level and species richness as well. Avg DBO, CV DBO and CV of
+river size had no or weak indirect effect on total biomass
+(resp. $r_\delta =`r env_on_bm["log_RC3"]`$, $r_\delta =`r env_on_bm["log_RC5"]`$, $r_\delta =`r env_on_bm["log_RC4"]`$).
+
+```{r get-sem-single-effect}
+stab_sem_coef <- filter(coef_stab_sem, P.Value < 0.05)
+get_clean_sem_coef <- function(sem = NULL, resp = NULL, pred = NULL) {
+  out <- sem[sem$Response == resp & sem$Predictor == pred, ]$Std.Estimate
+  out <- ifelse(length(out) == 0, 0, out)
+  round(out, 2)
+}
+
+sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_sync")
+cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_cv_sp")
+RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
+```
+
+```{r get-sem-tot-effect-env}
+all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
+# effect of env on stab
+
+env_on_stab <- get_env_on_stab(fit = all_params, p_val_thl = 0.05)
+# effect of env on sync and cv_sp
+env_on_sync <- get_env_on_stab_comp(fit = all_params,
+  p_val_thl = 0.05,
+  stab_comp = "log_sync")
+env_on_cv_sp <- get_env_on_stab_comp(fit = all_params,
+  p_val_thl = 0.05,
+  stab_comp = "log_cv_sp")
+# env on com 
+env_on_t_lvl <- get_env_on_com(fit = all_params,
+  p_val_thl = 0.05,
+  com = "t_lvl")
+env_on_ct <- get_env_on_com(fit = all_params,
+  p_val_thl = 0.05,
+  com = "ct")
+env_on_richness <- get_env_on_rich(fit = all_params,
+  p_val_thl = 0.05)
+```
+
+```{r get-sem-tot-effect-rich}
+rich_on_stab <- get_rich_on_stab(fit = all_params,
+  p_val_thl = 0.05)
+rich_on_sync <- get_rich_on_stab_comp(fit = all_params,
+  p_val_thl = 0.05,
+  stab_comp = "log_sync")
+rich_on_cv_sp <- get_rich_on_stab_comp(fit = all_params,
+  p_val_thl = 0.05,
+  stab_comp = "log_cv_sp")
+```
+
+---
+# Biomass stability
+---
+
+\overline{CV_{sp}} ($r_\delta = `r cv_sp_on_stab`$) decreased biomass stability more than
+synchrony ($r_\delta = `r sync_on_stab`$, Figure \@ref(fig:sem-plot)). Species richness had a strong
+positive effect on \overline{CV_{sp}} and a strong negative effect on synchrony
+whereas average trophic level and connectance had no significant effects on either
+\overline{CV_{sp}} nor synchrony. The avg river size had a small positive direct
+effect on synchrony ($r_\delta = `r RC1_on_sync`$). The other environmental variables had
+no significant direct effects on either \overline{CV_{sp}} nor synchrony.
+
+Indirectly through synchrony and \overline{CV_{sp}}, species richness had a total negative
+effect on biomass stability ($r_\delta = `r rich_on_stab`$). Avg river size and avg
+temperature had also a total effect which was negative on biomass stability
+(resp. $r_\delta = `r env_on_stab["log_RC1"]`$ and $r_\delta = `r env_on_stab["log_RC2"]`$),
+going through richness (resp. $r_\delta = `r env_on_richness["log_RC1"]`$ and
+$r_\delta = `r env_on_richness["log_RC2"]`$).
+
+- Main outcome:
+  - Biomass but stability increased with richness
+  - Higher trophic group was more stable that lower one
+    - Opposite relationship stability/richness
+  - Stability was mainly driven by species richness
+
+## Species richness increases total biomass but decreases biomass stability
 
@@
 bm_lab <- "Total biomass (Log 10)"
-```
-
-```{r p-s-div}
+
+stab_div_caption <- paste0("Relationship between biomass stability (log 10) (top panel) or total biomass (log 10) (bottom panel) versus total species richness.") 
+```
+
+```{r p-s-div, fig.cap = stab_div_caption}
 lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
@@
 ---
-# Total biomass versus TSR
----
-TSR increased total biomass (`r b_co_r`% `r b_ci_r` by 1% TSR increase). Total
-biomass was `r b_co_t`% `r b_ci_t` higher in the high than in the low trophic group. However,
-the increase of total biomass with the increase of TSR was lower in the high
-than the low trophic group (`r b_co_r_t3`% `r b_ci_r_t3` and `r b_co_r_t2`%
-`rb_ci_r_t2` respectively,  by 1% TSR increase).
----
-# Stability versus TSR
----
-However, biomass stability decreased with TSR (`r s_co_r`% `r s_ci_r` by 1%
-TSR increase). Biomass stability was overall `r s_co_t`% `r s_ci_t` higher for the high
+# Total biomass versus species richness
+---
+species richness increased total biomass (`r b_co_r`% `r b_ci_r` by 1% species richness increase). Total
+biomass was `r b_co_t`% `r b_ci_t` higher in the high than in the low trophic
+group. However, the increase of total biomass with the increase of species
+richness was lower in the high than the low trophic group (`r b_co_r_t3`% `r
+b_ci_r_t3` and `r b_co_r_t2`% `r b_ci_r_t2` respectively,  by 1% species
+richness increase).
+
+---
+# Stability versus species richness
+---
+
+However, biomass stability decreased with species richness (`r s_co_r`% `r s_ci_r` by 1%
+species richness increase). Biomass stability was overall `r s_co_t`% `r s_ci_t` higher for the high
 than the low trophic group. But biomass stability decreased by `r s_co_r_t3`% by
-1% increase in TSR in the high trophic group and increased by `r s_co_r_t2`% `r s_ci_r_t2`
+1% increase in species richness in the high trophic group and increased by `r s_co_r_t2`% `r s_ci_r_t2`
 in the low trophic group.
 
-## Drivers of total biomass and stability
-
-```{r, fig.show = "hide"}
-axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
-p_l_rot <- map(axis_pair, 
-  function (axis)
-    pca_rotated_plot <- plot_rotated_pca(
-      pca_rotated = pca_rotated,
-      axis = axis 
-    )
-)
-```
-
-```{r sem-plot, fig.dim = c(10,10)}
-#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
-#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple
-to_plot <- c(1, 6, 7)
-
-plot_grid(
-  plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
-      ncol = length(to_plot), labels = LETTERS[1]),
-  plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[2:3], rel_widths = c(.6, .4)),
-  ncol = 1,
-  rel_heights = c(.4, .6)
-)
-```
-
-```{r}
-total_effect_bm_sem
-total_effect_stab_sem
-```
-
----
-# Total biomass
----
-We found that the primary drivers of total biomass were the total species
-richness (TSR) and the average trophic level (Tlvl) ($r_\delta = 0.35$ and
-$r_\delta = 0.40$ resp.) whereas connectance had no significant effect  (Fig.
-\@ref{fig:sem-plot} C). The stream size had a direct positive effect on total
-biomass ($r_\delta = 0.22$) whereas CV of flow and avg DBO increased total
-biomass ($r_\delta = - 0.2$). Avg temperature, CV of river size and CV of DBO
-had no direct effects on total biomass.
-
-TSR had also a indirect positive effect on total biomass through Tlvl ($r_\delta
-= 0.21$), that is, TSR had a total positive effect of $0.56$ on total biomass.
-The stream size had a total effect on total biomass as strong as TSR ($r_\delta
-= 0.54$), indirectly through Tlvl ($r_\delta = 0.10$) and TSR ($r_\delta = 0.22$).
-The avg temperature of the river had an indirect positive effect on total biomass
-($r_\delta = 0.48$), through Tlvl ($r_\delta = 0.11$) and TSR ($r_\delta = 0.33$).
-Avg DBO, CV DBO and CV of river size had no or weak indirect effect on total
-biomass.
-
----
-# Biomass stability
----
-\overline{CV_{sp}} ($r_\delta = -1.26$) decreased biomass stability more than
-synchrony ($r_\delta = -0.55$, Figure \@ref{fig:sem-plot}). TSR had a strong
-positive effect on \overline{CV_{sp}} and a strong negative effect on synchrony
-whereas Tlvl and connectance had no significant effects on either
-\overline{CV_{sp}} nor synchrony. The avg river size had a small positive direct
-effect on synchrony ($r_\delta = 0.19$). The other environmental variables had
-no significant direct effects on \overline{CV_{sp}} nor synchrony.
-
-Indirectly through synchrony and \overline{CV_{sp}}, TSR had a total negative
-effect on biomass stability ($r_\delta = -0.26$). Avg river size and avg
-temperature had also a total effect which was negative on biomass stability
-(resp. $r_\delta = -0.24$ and $r_\delta = -0.16$), going through richness 
-(resp. $r_\delta = -0.10$ and $r_\delta = -0.16$).
-
-- Main outcome:
-  - Biomass but stability increased with richness
-  - Higher trophic group was more stable that lower one
-    - Opposite relationship stability/richness
-  - Stability was mainly driven by species richness
-
 # Discussion
 
-We tested for the first time the determinants of temporal biomass stability in a
-foodweb with an empirical dataset at such high temporal and spatial scales.
+For the first time, we assessed the determinants of total biomass and temporal
+biomass stability in empirical trophic communities at such high temporal and
+spatial scales. We showed that species richness increased total biomass but 
+decreased biomass stability. In particular, species richness decreased
+synchrony and increased species CV ($\LaTeX$). Surprisingly, the avg trophic
+level and connectance had no effects on either synchrony nor species CV.
+Finally, we showed that high trophic group was more stable than low trophic
+group but that high trophic was responsible for the negative stability-diversity
+relationship.
 
@@
 
+The total effect of river size on biomass stability was as negative as species richness,
+indicating that big rivers had a high negative effect on stability.
+
 ---
@@
 ---
+
 It was unexpected that the average population CV had a stronger negative effect
@@
 ---
-Our path analysis reveled that, although species richness has a strong effect on
+
+Our path analysis revealed that, although species richness has a strong effect on
 connectance and the average trophic level, network structure had itself little
@@
 strongly constraints by assembly processes. Indeed, connectance decreased with
-increasing species richness [@thebault_stability_2010], because a small fraction
-of links are realized because of food diet constraints. In theoretical studies,
-connectance can be tuned from 0 (no links) to 1 (all possible links are
-present). SAMEFORTLVL
+increasing species richness [@winemiller_must_1989, @thebault_stability_2010],
+because a small fraction of links are realized because of food diet constraints.
+In theoretical studies, connectance can be tuned from 0 (no links) to 1 (all
+possible links are present) [@angelis_stability_1975]. SAMEFORTLVL
 Finally, the biomass stability of freshwater ecosystems can be derived by
@@
 # Appendix
+
+## PCA of environmental variables
+
+```{r, fig.show = "hide"}
+axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
+p_l_rot <- map(axis_pair, 
+  function (axis)
+    pca_rotated_plot <- plot_rotated_pca(
+      pca_rotated = pca_rotated,
+      axis = axis 
+    )
+)
+```
+
+```{r}
+prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
+  map_dbl(., ~round(.x * 100))
+
+tot_var_expl_pca <- round(sum(pca_rotated$rotated$Vaccounted["Proportion Var", ]) * 100)
+
+pca_caption <- paste0(
+  "Rotated axis of PCA on environmental variables. The five components
+  explained,", tot_var_expl_pca, "% of the variance (",
+  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
+  "(A) Axis 1 was positively related to the river size, axis 2 was related to
+  average temperature and negatively related to the river slope and altitude.
+  (B) Axis 3 was negatively related to the CV of flow and average enrichment.
+  Axis 4 was related to the CV of river size. Finally, axis 5 was related to the
+  CV of enrichment.")
+```
+
+```{r pca-rotated, fig.cap = pca_caption}
+to_plot <- c(1, 6, 7)
+plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
+  ncol = length(to_plot), labels = LETTERS[1:3])
+```
 

### 2020-03-11 report/05-stability.Rmd
Recompute biomass correlation between trophic group + plot results
No link between stability and strength of bottom-up effect

@@
 
+## Temporal correlation between troph group biomass
+
 ```{r}
 #TODO: Update cor_troph_group 
-myload(cor_troph_group, dir = mypath("data"))
-cor_troph_group %>%
-  left_join(hab_type, by = "station") %>%
-  filter(!is.na(hab_type)) %>%
-  ggplot(aes(x = hab_type, y = cor_troph)) +
-  geom_boxplot() 
+myload(cor_troph, dir = mypath("data"))
+cor_troph %>%
+  left_join(stab_div_troph, by = "station") %>%
+  ggplot(aes(y = log10(1/ biomass_cv), x = cor_troph, color = troph_group)) +
+  geom_point()
+
+cor_troph %>%
+  left_join(stab_div_troph, by = "station") %>%
+  ggplot(aes(y = cor_troph, x = log10(richness_tot), color = troph_group)) +
+  geom_point()
 ```

### 2020-03-11 manuscript/bef_stability/manuscript.Rmd
First version of the discussion completed

@@
 
-```{r get-sem-tot-effect-rich}
+```{r get-bm-tot-effect-rich}
 rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
   p_val_thl = 0.05)
-rich_on_sync <- get_rich_on_bm_comp(fit = bm_all_params,
-  p_val_thl = 0.05,
-  bm_comp = "log_sync")
-rich_on_cv_sp <- get_rich_on_bm_comp(fit = bm_all_params,
-  p_val_thl = 0.05,
-  bm_comp = "log_cv_sp")
 ```
@@
 
+---
+# Chapeau
+---
+
 For the first time, we assessed the determinants of total biomass and temporal
@@
 Finally, we showed that high trophic group was more stable than low trophic
-group but that high trophic was responsible for the negative stability-diversity
-relationship.
+group but that high trophic group was responsible for the negative
+stability-diversity relationship.
+
+---
+# Negative relationship between stability and richness 
+---
 
@@
 [@olivier_independent_nodate] where positive relationships are typically found
-between biomass stability and species richness. Even @franssen_annual_2011 found
-that species rich communities are more stable than species poor in streams.
-
-@grace_integrative_2016 found that biomass negatively linked to species richness
-in grasslands, notably because of light competition. In freshwater ecosystems,
-where resources are based on trophic relationship, TOCOMPLETE.
+between biomass stability (computed as CV) and species richness. In streams as
+well, @franssen_annual_2011 found that species richness increased biomass
+stability. However other studies found a opposite relationship
+[@yang_effects_2011] or a marginal one [@declerc_species_2006].
+
+---
+# Total biomass
+---
+
+We found that species richness increased total biomass as found in salt
+marshes, forests [@wu_relationship_2014,@shuaifeng_positive_2018]. But opposite
+relation has been found in richness in grasslands [@grace_integrative_2016],
+notably because of light competition. Precedent researches in plant communities
+showed that the total biomass was primary driven by environmental drivers. In
+contrast, we found that the species richness was one of the main driver of the
+total biomass, together with the stream size and increasing avg temperature
+(with decreasing altitude). The big effect of species richness is 
+partly explained by its effect on food web assembly and so, avg trophic level
+(`r round(.2/0.54 * 100)` % of richness effect on total biomass). The direct
+positive effect of species richness on total biomass might be due to resource use
+complementarity [@cardinale_species_2002] [add more direct REF]. It was however
+unexpected that connectance had no effect on total biomass, because we could
+imagine that connectance could also improve resource use, but this might be
+true only under the assumption that all species have the same assimilation
+efficiency.
+
+We found that contrary to stream size, the effect of altitude of the river and
+its avg temperature on total biomass was only indirect through community
+structure (avg trophic level and connectance).
+
+---
+# Effect of environment on community structure
+---
+
+The total effect of river size on biomass stability was as negative as species
+richness, indicating that big rivers had a high negative effect on stability (TO MOVE).
+We found a mix of both expected and unexpected results on the effects on
+environment on community structure. First, we expected that bigger and low
+altitude streams had higher species richness because they might receive more
+confluents streams and so more species through immigration.
+Stream size increased both connectance and avg trophic level with the same
+magnitude. An increase in mean trophic position of piscivorous species in
+bigger rivers could explain this relation [@post_ecosystem_2000]. In our
+network reconstruction, the fish-fish interactions are more resolved than
+fish-resource interactions, which might explain positive effect of stream size
+on connectance. @petchey_predicting_2010 predicted that temperature should
+increase connectance but we did not find any relationship but temperature (and
+low altitude) increased avg trophic level (**Bullshit**). 
+CV of enrichment decreased both connectance and avg trophic level, while avg
+enrichment (and CV of flow) increased both. The latter might by explained by
+the fact that enrichment can benefit to top trophic level
+[@hulot_functional_2000]. One explanation for the former is that enrichment
+variation might destabilize top predators (REF or Bullshit again).
+
+---
+# Effect of synchrony and cv_sp  
+---
+
+Species richness decreased synchrony and increased \overline{CV_{sp}}. Species
+richness can reduce synchrony through decrease of population size, thus raising
+the role of demographic stochasticity [@loreau_species_2008] but also in the
+case where species have different responses to environmental variation
+[@loreau_species_2008]. While the effect of species richness on synchrony is
+well understood, its effect on \overline{CV_{sp}} is more complex.
+Indeed, studies reported positive [@tilman_biodiversity_2006, ], neutral  [@jiang_different_2009, @olivier_independent_nodate] or negative relationships [@franssen_annual_2011, @olivier_independent_nodate].
+Positive relationship between
+
+In turn, we found that synchrony and \overline{CV_{sp}} both decreased biomass
+stability, as predicted by the formulation of stability based on the CV
+[@thibaut_understanding_2013].
+However, it was unexpected that the average population \overline{CV_{sp}} had
+a stronger negative effect on biomass stability than synchrony
+[@bluthgen_land_2016; @olivier_independent_nodate]. We can advance two
+hypothesis that can raise this effect. First, the opportunity for diet
+differentiation can be low in streams compare to other organisms. Bird species
+are for example quite specialized in seed, flying or soil arthropods or mammals
+which gives opportunities for independent dynamics. Plants also can achieve
+independent dynamics either spatial segregation or niche differentiation. Because
+fish species even piscivorous one are quite opportunistic in their foraging.
+Secondly, in trophic communities, species directly affect each other through
+feeding interactions, and so could raise synchrony between species
+[@raimondo_interspecific_2004] more than in systems where interactions happen
+more in the form of competitive exploitation.
+
+---
+# Effect of trophic level and connectance are richness effects:
+---
+
+Our path analysis revealed that, although species richness has a strong effect on
+connectance and the average trophic level, network structure  itself had little
+to no effect either on synchrony nor average population stability. This result
+contradicts precedent theoretical studies on the relationship
+between stability and network structure [@angelis_stability_1975,
+@may_will_1972], although they considered different stability metrics (i.e.
+local stability of equilibrium point). The reason might be that in our inferred
+network, network structure is strongly constraints by assembly processes.
+Indeed, connectance generally decreased with increasing species richness
+[@winemiller_must_1989, @thebault_stability_2010], because a small fraction of
+links are realized because of food diet constraints. In theoretical studies,
+connectance can be tuned from 0 (no links) to 1 (all possible links are
+present) [@angelis_stability_1975]. The link between the average trophic level
+and species richness has been less studied. However, we can suppose that
+because species richness increase total biomass, species richness also increase
+both the biomass of prey available for piscivorous fishes and the biomass of
+piscivorous species which in turn, increase the avg trophic level of the
+community. In sum, the biomass stability of freshwater ecosystems can be
+derived by species richness because, through trophic structure constraints,
+species richness determine largely network structure.
+
+---
+# Trophic group
+---
 
 The total biomass of high and low trophic group trophic groups responded both
-positively to species richness but not biomass stability TOREPHRASE. There is a
+positively to species richness but not biomass stability. There is a
 paradox where the high trophic group is overall more stable than the low but
@@
 [@shanafelt_david_w._stability_nodate] ADD REF.
-
-The total effect of river size on biomass stability was as negative as species richness,
-indicating that big rivers had a high negative effect on stability.
-
----
-# Effect of synchrony and cv_sp  
----
-
-It was unexpected that the average population CV had a stronger negative effect
-on biomass stability than synchrony [@bluthgen_land_2016;
-@olivier_independent_nodate] *cf ref in bluthgen*. We see two hypothesis that
-can raise this effect. First, the opportunity for diet differentiation can be
-low in streams compare to other organisms. Bird species are for example quite
-specialized in seed, flying or soil arthropods or mammals which gives
-opportunities for independent dynamics. Plants also can achieve independent
-dynamics either spatial segregation, niche differentiation. Because fish
-species even piscivorous one are quite opportunistic in
-their foraging. Secondly, in trophic network, amplitude of species biomass
-involved in trophic interactions could covary positively TOTHINKABOUT.
-
----
-# Effect of trophic level and connectance are richness effects:
----
-
-Our path analysis revealed that, although species richness has a strong effect on
-connectance and the average trophic level, network structure had itself little
-to no effect either on synchrony nor average population stability. This result
-contradicts precedent theoretical studies on the relationship
-between stability and network structure [@angelis_stability_1975, @may_will_1972], although
-they considered different stability metrics (i.e. local stability of equilibrium
-point). The reason might be that in our inferred network, network structure is
-strongly constraints by assembly processes. Indeed, connectance decreased with
-increasing species richness [@winemiller_must_1989, @thebault_stability_2010],
-because a small fraction of links are realized because of food diet constraints.
-In theoretical studies, connectance can be tuned from 0 (no links) to 1 (all
-possible links are present) [@angelis_stability_1975]. SAMEFORTLVL
-Finally, the biomass stability of freshwater ecosystems can be derived by
-species richness because, through trophic structure constraints, species
-richness determine largely network structure.
-
-- Stability versus several studies:
-  - [@zhang_scale_nodate]: productivity stability range from [0.4 to 1.4] for
-    diversity range [10 to 30]
-  - [@tilman_biodiversity_2006] on abundances:
-    - stability range: 2 to 12
-    - diversity range: 1 to 16
 

### 2020-03-11 manuscript/bef_stability/manuscript.Rmd
Fix Latex compilation problem

@@
 
-$$
-\begin{align}
-
+$$\begin{aligned}
 \log_{10}S_i &= \beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}\\
-
 S_i &= 10^{\beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}}\\
-
-S_i &= 10^{\beta_0} \times 10^{\beta_R\log_{10}x_{Ri}} \times
-10^{\epsilon_{ij}}\\
-
+S_i &= 10^{\beta_0} \times 10^{\beta_R\log_{10}x_{Ri}} \times10^{\epsilon_{ij}}\\
 S_i &= 10^{\beta_{0}} \times x_{Ri}10^{\beta_{R}} \times 10^{\epsilon_{ij}}
-
-\end{align}
-$$
+\end{aligned}$$
 
@@
 
-\overline{CV_{sp}} ($r_\delta = `r cv_sp_on_stab`$) decreased biomass stability more than
+$\overline{CV_{sp}}$ ($r_\delta = `r cv_sp_on_stab`$) decreased biomass stability more than
 synchrony ($r_\delta = `r sync_on_stab`$, Figure \@ref(fig:sem-plot)). Species richness had a strong
-positive effect on \overline{CV_{sp}} and a strong negative effect on synchrony
+positive effect on $\overline{CV_{sp}}$ and a strong negative effect on synchrony
 whereas average trophic level and connectance had no significant effects on either
-\overline{CV_{sp}} nor synchrony. The avg river size had a small positive direct
+$\overline{CV_{sp}}$ nor synchrony. The avg river size had a small positive direct
 effect on synchrony ($r_\delta = `r RC1_on_sync`$). The other environmental variables had
-no significant direct effects on either \overline{CV_{sp}} nor synchrony.
-
-Indirectly through synchrony and \overline{CV_{sp}}, species richness had a total negative
+no significant direct effects on either $\overline{CV_{sp}}$ nor synchrony.
+
+Indirectly through synchrony and $\overline{CV_{sp}}$, species richness had a total negative
 effect on biomass stability ($r_\delta = `r rich_on_stab`$). Avg river size and avg
@@
 decreased biomass stability. In particular, species richness decreased
-synchrony and increased species CV ($\LaTeX$). Surprisingly, the avg trophic
+synchrony and increased species CV (\LaTeX). Surprisingly, the avg trophic
 level and connectance had no effects on either synchrony nor species CV.
@@
 
-Species richness decreased synchrony and increased \overline{CV_{sp}}. Species
+Species richness decreased synchrony and increased $\overline{CV_{sp}}$. Species
 richness can reduce synchrony through decrease of population size, thus raising
@@
 [@loreau_species_2008]. While the effect of species richness on synchrony is
-well understood, its effect on \overline{CV_{sp}} is more complex.
+well understood, its effect on $\overline{CV_{sp}}$ is more complex.
 Indeed, studies reported positive [@tilman_biodiversity_2006, ], neutral  [@jiang_different_2009, @olivier_independent_nodate] or negative relationships [@franssen_annual_2011, @olivier_independent_nodate].
@@
 
-In turn, we found that synchrony and \overline{CV_{sp}} both decreased biomass
+In turn, we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
 stability, as predicted by the formulation of stability based on the CV
 [@thibaut_understanding_2013].
-However, it was unexpected that the average population \overline{CV_{sp}} had
+However, it was unexpected that the average population $\overline{CV_{sp}}$ had
 a stronger negative effect on biomass stability than synchrony

### 2020-03-16 report/04-productivity.Rmd
Compute total biomass and richness by sampled area

@@
 myload(temporal_network_metrics, dir = dest_dir)
+myload(community_metrics, dir = data_common)
 myload(temporal_community_metrics, synchrony, dir = data_common)
@@
 biomass_prod_station <- temporal_community_metrics %>%
-  select(station, biomass_med, richness_med) %>%
+  select(station, biomass_med, bm_std_med, richness_med, rich_std_med) %>%
   rename(biomass = biomass_med)
@@
 plot_biomass_dist
+
+plot_biomass_std_dist <- ggplot(biomass_prod_station, aes(x = bm_std_med)) +
+  geom_histogram() +
+  labs(
+    x = "Median of standardized biomass (g/m2)",
+    y = "# of stations"
+  )
+plot_biomass_std_dist
 ```
@@
 
+### Biomass richness
+
+```{r}
+# Raw biomass
+raw_bm_rich <- biomass_prod_station %>% 
+  select(station, biomass, richness_med) %>%
+  rename(richness = richness_med) %>%
+  mutate(type = "raw")
+std_bm_rich <- biomass_prod_station %>% 
+  select(station, bm_std_med, rich_std_med) %>%
+  rename(richness = rich_std_med, biomass = bm_std_med) %>%
+  mutate(type = "std")
+
+p_bm_rich_raw_std <- map(list(raw_bm_rich, std_bm_rich), function (x) {
+
+  if (unique(x$type) == "raw") {
+    x_lab <- paste0("Median richness")
+    y_lab <- paste0("Median biomass (g)")
+  } else {
+    x_lab <- paste0("Median standardized richness (m2^-1)")
+    y_lab <- paste0("Median standardized biomass (g/m2)")
+  }
+
+  x %>%
+  ggplot(aes(x = log10(richness), y = log10(biomass))) +
+  geom_point() +
+  labs(x = x_lab, y = y_lab)
+  })
+plot_grid(plotlist = p_bm_rich_raw_std)
+```
+
 ### By trophic level

### 2020-03-16 R/community_analysis.R

@@ -128,12 +128,14 @@ summarise_com_over_time <- function (
      com$station <- NULL
     }
 
+var_to_summarise <- c("richness", "rich_std", "nind", "nind_std", "biomass", "bm_std", "pielou", "simpson")
+
   output <- com %>%
     dplyr::left_join(op, by = c("opcod")) %>%
     dplyr::filter(!(is.na(station) | is.na(opcod))) %>%
-    dplyr::select(station, richness, nind, biomass, pielou, simpson) %>%
+    dplyr::select_at(c("station", var_to_summarise)) %>%
     dplyr::group_by(station) %>%
-    dplyr::summarise_at(c("richness", "nind", "biomass", "pielou", "simpson"),
+    dplyr::summarise_at(var_to_summarise,
       list(avg = mean, cv =~ sd(.) / mean(.), med = median, stab = ~mean(.) / sd(.)))
   return(output)
 }
@@ -218,8 +220,14 @@ compute_com_synchrony <- function (.op = NULL, com = NULL, ...) {
       richness_tot = map_dbl(com_mat, ~ncol(.x))
     )
 
+  # Total number of of species by unit of surface: 
+  sum_surface <- .op %>%
+    dplyr::group_by(station) %>%
+    dplyr::summarise(sum_surface = sum(surface))
   synchrony %<>%
-    dplyr::select(station, richness_med, synchrony, cv_sp, cv_com, cv_classic, contrib, richness_tot)
+    dplyr::left_join(sum_surface, by = "station") %>%
+    dplyr::mutate(rich_tot_std = richness_tot / sum_surface) %>%
+    dplyr::select(station, richness_med,  synchrony, cv_sp, cv_com, cv_classic, contrib, richness_tot, rich_tot_std)
 
   return(synchrony)
 } 

### 2020-03-16 R/statistical_analysis.R

@@ -32,14 +32,15 @@ compute_sem_dataset <- function (
   com$beta_bin_c <- resid(mod)
 
   # Add synchrony
-  sync %<>% dplyr::select(station, synchrony, cv_sp, richness_tot)
+  sync %<>% dplyr::select(station, synchrony, cv_sp, richness_tot, rich_tot_std)
   biomass_sem <- com %>%
-    dplyr::select(station, biomass_stab, biomass_med, richness_med, pielou_med,
+    dplyr::select(station, biomass_stab, biomass_med, bm_std_med, richness_med, rich_std_med, pielou_med,
       betadiv_bin, beta_bin_c) %>%
     dplyr::left_join(sync, by = "station") %>%
     dplyr::rename(sync = synchrony,
       piel = pielou_med,
       prod = biomass_med,
+      prod_std = bm_std_med,
       beta_bin = betadiv_bin
     )
 
@@ -76,6 +77,7 @@ compute_sem_dataset <- function (
       log_cv_sp = log10(cv_sp),
       log_stab = log10(biomass_stab),
       log_bm = log10(prod),
+      log_bm_std = log10(prod_std),
       log_RC1 = log10(RC1 + abs(min(RC1)) + 1),
       log_RC2 = log10(RC2 + abs(min(RC2)) + 1),
       log_RC3 = log10((RC3)*(-1) + abs(min((RC3)*(-1))) + 1)
@@ -213,7 +215,7 @@ compute_prod_sem_rich <- function(.data, random_effect = "~ 1 | basin") {
     nlme::lme(ct ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = .data),
     nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = .data),
     #nlme::lme(beta_bin_c ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5, random = ~ 1 | basin, data = .data),
-    nlme::lme(log_bm ~ log_rich_tot + ct + t_lvl + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,
+    nlme::lme(log_bm_std ~ log_rich_tot + ct + t_lvl + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,
       random = ~ 1 | basin, data = .data)
   )
   output <- summary(corsem, .progressBar = F)

### 2020-03-16 analysis/01_compute_community_metrics.R

@@ -54,7 +54,7 @@ mysave(weight_analysis, dir = data_common, overwrite = TRUE)
 # Get station and  
 myload(length_analysis, op_analysis, dir = data_common)
 op_analysis %<>%
-  select(opcod, station, date)
+  select(opcod, station, date, surface)
 
 com_analysis <- length_analysis %>%
   group_by(opcod, species) %>%
@@ -93,8 +93,15 @@ com <- community_analysis %>%
   summarise(
     richness = n(),
     nind = sum(nind),
-    biomass = sum(biomass)
-  )
+    biomass = sum(biomass),
+    #bm_std = sum(biomass)/surface
+  ) %>%
+  left_join(select(op_analysis, opcod, surface), by = "opcod") %>%
+  mutate(
+    rich_std = richness / surface, 
+    nind_std = nind / surface,
+    bm_std = biomass / surface
+  ) 
 
 ######################
 #  Compute evenness  #

### 2020-03-18 manuscript/bef_stability/manuscript.Rmd
Standardized biomass and richness + introduction done

@@
   pdf_document:
-    fig_caption: true
+    fig_caption: yes
+fontsize: 12pt
+header-includes:
+   - \usepackage{setspace}
+   - \doublespacing
+geometry: margin=2cm
 bibliography: references.bib
@@
 
-Cf blutghen for CVsp as portfolio and statistical averaging of species.
-Synchrony as insurance hypothesis facing environmental variations.
-
-- Diversity - stability and diversity - biomass / productivity
-  - well studied: both experimentally, empirically and theoretically
-  - mecanisms:
-    - stability: insurance (asynchrony),
-    - diversity: overyielding (complementarity)
-  - key papers: [@tilman_biodiversity_2006, @loreau_species_2008,
-    @thibaut_understanding_2013, @may_will_1972]
-  - BUT: less vertical diversity, trophic communities
-
-- Vertical diversity and stability/biomass
-  - well studied: theoretically and (experimentally, less)
-  - mecanisms:
-    - stability: top-down and bottom-up effect
-    - biomass: top-down and bottom-up effects (pyramids of biomass)
-  - key papers:[@barbier_pyramids_2019, @shanafelt_david_w._stability_nodate]
-  - BUT: local stability, little systems
-
-- Environment can drive stability and biomass:
-  - forcing: environmental forcing on communities 
-  - can lead to misleading effect: @grace_integrative_2016
-
-- Big scope assessment:
-  - inconsistency between theoretical and empirical stability
-    - theoretical: no cv_sp nor synchrony
-  - No studies on stability-richness in empirical trophic communities
-    - no effect of trophic structure
-
-- Goal: Assess relation biomass/stability-diversity in empirical trophic communities
-  - introduce effect of trophic structure and environment
-  - merge gap between theoretical and empirical studies
-
-- What we have done:
-  - big empirical dataset
-  - rebuilding empirical network
-  - assess relationship between environment, community structure and stability
-
-- Research questions:
-  - What are the effects of the community structure on total biomass and stability ? 
-    1. What are the effects of species richness on total biomass and stability ?
-      - effect of species richness
-      - effect of trophic group
-    2. What are the effects of the community structure on total biomass and stability ?
-      - What is the relative effect of the environment relative to the community
-	structure ?
-      - What is the effect of the community structure on the different
-	parts of the stability + total biomass?
-	- Effect of horizontal and vertical diversity
+Determining the shape of the relationship between species diversity and ecosystem
+functioning has been a central research topic in ecology [@may_will_1972,
+@hector_plant_1999, @loreau_biodiversity_2001, @hooper_effects_2005,
+@duffy_why_2009, @isbell_forest_quantifying_2018]. Current biodiversity losses
+in all ecosystems challenge scientists to understand how ecosystems will be
+affected in turn. Studies in Bioversity-Ecosystem Functioning (BEF) usually
+quantify species diversity as species richness (i.e number of species) while
+ecosystem functioning is quantified as total biomass, productivity (biomass
+produced by unit of time) or stability which is quantified in more diverse ways
+such as the variability of species abundance, the resilience to perturbation, or
+resistance to perturbation [@donohue_navigating_2016].
+
+---
+#- Diversity - stability and diversity - biomass / productivity
+  #- well studied: both experimentally, empirically and theoretically
+  #- mecanisms:
+    #- stability: insurance (asynchrony),
+    #- diversity: overyielding (complementarity)
+  #- key papers: [@tilman_biodiversity_2006, @loreau_species_2008,
+    #@thibaut_understanding_2013, @may_will_1972]
+  #- BUT: less vertical diversity, trophic communities
+---
+
+Species richness has been reported to increase productivity in grasslands
+[@grace_integrative_2016], but complex links between between species richness,
+environment, productivity and total biomass showed that species richness
+decrease total biomass [@grace_integrative_2016] contrary to previous
+assessment [@hector_plant_1999, @tilman_biodiversity_2014] because of
+competition for light between plants [@grace_integrative_2016]. Complementarity
+between species in resource exploitation [@cardinale_species_2002] leading to
+overyielding (CHECK) has been proposed to explain positive relationship between
+productivity
+and species richness, while species richness effect can also rise from the
+statistical probability to end up with a highly productive species . The
+relationship between species richness and stability is even more complex
+partly because of the inherent multidimensionality of stability
+[@donohue_dimensionality_2013, @donohue_navigating_2016] and because of the
+different metrics of stability privileged in theoretical (stability of local
+equilibrium, robustness to primary extinction) and empirical work (variability
+of abundance or biomass through time). @may_will_1972 stimulated a lot of
+debate and fecund research, showing that species richness, probability of
+interacting and average interaction strength destabilizes communities in which
+species interact randomly. Empirically, consistent works showed that species
+richness increased community stability in grasslands [@tilman_biodiversity_2006],
+mesocosms [@pennekamp_biodiversity_2018] and vertebrates
+[@olivier_independent_nodate, @franssen_annual_2011]. Two components can
+explain variation of community stability, (1) individual species stability and (2)
+the species synchrony [@loreau_species_2008, @thibaut_understanding_2013].
+Positive [@tilman_biodiversity_2006], neutral [@jiang_different_2009, @olivier_independent_nodate]
+and negative [@franssen_annual_2011, @olivier_independent_nodate] relationships
+between species stability and species richness have been found.
+On the other side, studies consistently found that species richness decreased
+synchrony between species [@loreau_species_2008, @thibaut_understanding_2013,
+@bluthgen_land_2016; @olivier_independent_nodate]. However, as far as we know,
+less studies have reported empirical assessment of stability-richness
+relationship in trophic network [but see @thebault_stability_2010].
+
+Conversely, an extensive literature exists on the effects of network structure
+on stability in mutualistic and trophic networks [@angelis_stability_1975, @stouffer_,
+@thebault_stability_2010, @barbier_pyramids_2019,
+@shanafelt_david_w._stability_nodate, add ref]. Particularly, in trophic
+networks, most studies are theoretical and consider asymptotic stability to
+small perturbation. Studies showed that compartimentalization [@stouffer_] can
+increase persistence, while nestedness can either increase [@bascompte,
+@thebault_stability_2010] or decrease persistence [@thebault_stability_2010].
+Connectance can decrease [@thebault_stability_2010] or increase
+[@angelis_stability_1975] resilience of trophic network depending on the
+functioning of networks [@angelis_stability_1975].
+
+---
+#- Vertical diversity and stability/biomass
+  #- well studied: theoretically and (experimentally, less)
+  #- mecanisms:
+    #- stability: top-down and bottom-up effect
+    #- biomass: top-down and bottom-up effects (pyramids of biomass)
+  #- key papers:[@barbier_pyramids_2019, @shanafelt_david_w._stability_nodate]
+  #- BUT: local stability, little systems 
+---
+
+Trophic network are assembled both vertically and horizontally. Studies showed
+that the vertical position in the trophic network as well as the strength of
+top-down and bottom-up regulation determine biomass and stability at
+equilibrium  [@shanafelt_david_w._stability_nodate, @barbier_pyramids_2019].
+However studies on stability-diversity have focused on either vertical
+diversity or horizontal but rarely both. @zhao_horizontal_2019 have shown that
+horizontal and vertical diversity respectively increase and decrease stability
+in plankton communities.
+
+---
+#- Big scope assessment:
+  #- inconsistency between theoretical and empirical stability
+    #- theoretical: no cv_sp nor synchrony
+  #- No studies on stability-richness in empirical trophic communities
+    #- no effect of trophic structure
+---
+
+A large inconsistency remains between theoretical and empirical assessment of
+stability-diversity in trophic communities. Theoretical studies have
+ignored temporal variability and the relative contribution of synchrony and
+species variability while empirical studies about temporal variability in natural 
+communities have ignored trophic communities and the effect of trophic structure.
+
+---
+#- Goal: Assess relation biomass/stability-diversity in empirical trophic communities
+  #- introduce effect of trophic structure and environment
+  #- merge gap between theoretical and empirical studies
+---
+
+---
+#- What we have done:
+  #- big empirical dataset
+  #- rebuilding empirical network
+  #- assess relationship between environment, community structure and stability
+---
+
+Our goal was to assess stability-diversity in natural trophic community with the
+effect of the trophic structure. We combined together the effect of vertical
+and horizontal diversity and thus aimed to bridge the gap between theoretical
+and empirical studies. We used an standardized monitoring of freshwater fish
+communities in french streams. More than three hundreds sites were followed
+more than 10 years on the 1995-2018 period. We inferred four thousands potential
+interaction networks corresponding to each sampling event, based on size
+relationships and knowledge about their ontogenic diet shift.
+
+---
+#- Research questions:
+  #- What are the effects of the community structure on total biomass and stability ? 
+    #1. What are the effects of species richness on total biomass and stability ?
+      #- effect of species richness
+      #- effect of trophic group
+    #2. What are the effects of the community structure on total biomass and stability ?
+      #- What is the relative effect of the environment relative to the community
+	#structure ?
+      #- What is the effect of the community structure on the different
+	#parts of the stability + total biomass?
+	#- Effect of horizontal and vertical diversity
+---
+
+We investigated the effects of the community structure on total biomass and on
+synchrony and species variability, which in turn determine community
+variability. We have also included the effect of environmental drivers which
+can directly affect community variability or indirectly via community structure.
+Finally, we assessed the effect of horizontal diversity on trophic group
+biomass and variability.
+
+---
+#- Environment can drive stability and biomass:
+  #- forcing: environmental forcing on communities 
+  #- can lead to misleading effect: @grace_integrative_2016
+---
 
@@
 # Compute stability, network metrics, etc with ;he new datasets
+#debug(summarise_network_over_time)
+##myload(network_metrics, dir = mypath("data", "classes"))
+#network_metrics %>%
+  #left_join(op_analysis, by = "opcod") %>%
+  #select(opcod, station, composition) %>%
+  #unnest(composition) %>%
+  #group_by(station, troph_group) %>%
+  #summarise(richness_tot = length(unique(species)))
 com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb)
@@
   hab_press = habitat_pressure,
-  sync = com_data[["sync"]],
+  sync = com_data[["sync_std"]],
   nmds = NULL,
@@
     log_rich = log10(richness_med),
+    log_rich_std = log10(rich_std_med),
     log_rich_tot = log10(richness_tot),
+    log_rich_tot_std = log10(rich_tot_std),
     log_bm = log10(biomass_med),
-    log_stab = log10(biomass_stab)) %>%
-  dplyr::select(station, troph_group, biomass_stab, richness_med, richness_tot, log_rich, log_rich_tot, log_stab, log_bm, biomass_med, richness_tot) %>%
+    log_bm_std = log10(bm_std_med),
+    log_stab = log10(biomass_stab),
+    log_stab_std = log10(bm_std_stab)
+    ) %>%
+  dplyr::select(station, troph_group, biomass_stab, richness_med, richness_tot, log_rich, log_rich_std, log_rich_tot, log_rich_tot_std, log_stab, log_stab_std, log_bm, log_bm_std, biomass_med, bm_std_med, richness_tot, rich_tot_std) %>%
   dplyr::left_join(st_basin, by = "station")
@@
 
-```{r get-data, cache = FALSE}
-library(nlme)
-library(piecewiseSEM)
-```
-
 ### Relationship between stability and species richness
@@
 
-```{r mod-div-total}
+```{r get-data, cache = FALSE}
+library(nlme)
+library(piecewiseSEM)
 library(lme4)
@@
 ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
+```
+
+```{r mod-div-total}
 stab_div_mod <- lmer(
@@
   control = ctrl_lmer,
-  formula = log_stab ~ log_rich_tot + (1 | basin)
+  formula = log_stab_std ~ log_rich_tot_std + (1 | basin)
 )
@@
 
-pred <- ggpredict(stab_div_mod, terms = c("log_rich_tot"), type = "fe")
+pred <- ggpredict(stab_div_mod, terms = c("log_rich_tot_std"), type = "fe")
 stab_div_pred <- pred %>%
@@
   rename(
-    log_stab = predicted,
-    log_rich_tot = x,
+    log_stab_std = predicted,
+    log_rich_tot_std = x,
     basin = group
@@
   mutate(
-    stab = 10^log_stab, # FALSE
-    rich = 10^log_rich_tot,
+    stab = 10^log_stab_std, # FALSE
+    rich = 10^log_rich_tot_std,
     cl10 =  10^conf.low,
@@
 bm_div_mod <- lmer(data = sem_data,
-  formula = log_bm ~ log_rich_tot + (1 | basin)
+  formula = log_bm_std ~ log_rich_tot_std + (1 | basin)
 )
@@
 
-pred <- ggpredict(bm_div_mod, terms = c("log_rich_tot"), type = "fe")
+pred <- ggpredict(bm_div_mod, terms = c("log_rich_tot_std"), type = "fe")
 #plot(pred, add.data = TRUE)
@@
   rename(
-    log_bm = predicted,
-    log_rich_tot = x,
+    log_bm_std = predicted,
+    log_rich_tot_std = x,
     basin = group
@@
 ```{r mod-div-troph, fig.show = "hide"}
-stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
-  formula = log_stab ~ log_rich_tot + troph_group + log_rich_tot:troph_group + (1 | basin)
+stab_troph_mod <- lmer(data = stab_div_troph,
+  formula = log_stab_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
   #control = ctrl
 )
-stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
+stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 200)
 stab_troph_ci <- confint(stab_troph_boot)
@@
 
-pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot", "troph_group"), type = "fe")
+pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
 #plot(pred_troph_mod, add.data = TRUE)
@@
   rename(
-    log_stab = predicted,
-    log_rich_tot = x,
+    log_stab_std = predicted,
+    log_rich_tot_std = x,
     troph_group = group
@@
   #fixed = log_bm ~ log_rich_tot * troph_group,
-  formula = log_bm ~ log_rich_tot + troph_group + log_rich_tot:troph_group + (1 | basin)
+  formula = log_bm_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
   #random = ~ 1 + log_rich_tot * troph_group | basin,
@@
 
-pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot", "troph_group"), type = "fe")
+pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
 #plot(pred_troph_mod, add.data = TRUE)
@@
   rename(
-    log_bm = predicted,
-    log_rich_tot = x,
+    log_bm_std = predicted,
+    log_rich_tot_std = x,
     troph_group = group
@@
 
-```{r stab-network}
+```{r stab-network, fig.show = "hide"}
 sem_data %>%
@@
   #fixed = log_bm ~ log_rich_tot * troph_group,
-  formula = log_stab ~ ct + (1 | basin)
+  formula = log_stab_std ~ ct + (1 | basin)
   #random = ~ 1 + log_rich_tot * troph_group | basin,
@@
   rename(
-    log_bm = predicted,
-    log_rich_tot = x,
+    log_stab_std = predicted,
+    log_rich_tot_std = x,
     troph_group = group
@@
   #fixed = log_bm ~ log_rich_tot * troph_group,
-  formula = log_stab ~ t_lvl + (1 | basin)
+  formula = log_stab_std ~ t_lvl + (1 | basin)
   #random = ~ 1 + log_rich_tot * troph_group | basin,
@@
 
-rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_rich_tot")
-tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "t_lvl")
-RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_RC1")
+rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_rich_tot_std")
+tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
+RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC1")
 ```
@@
 # effect of env on bm 
-env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05)
+env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05,
+  type = "std")
 # env on com 
-env_on_t_lvl <- get_env_on_com(fit = bm_all_params,
-  p_val_thl = 0.05,
-  com = "t_lvl")
+env_on_t_lvl <- get_env_on_com(fit = bm_all_params, p_val_thl = 0.05,
+  com = "t_lvl", type = "std")
 env_on_ct <- get_env_on_com(fit = bm_all_params,
-  p_val_thl = 0.05,
-  com = "ct")
+  p_val_thl = 0.05, com = "ct", type = "std")
 env_on_richness <- get_env_on_rich(fit = bm_all_params,
-  p_val_thl = 0.05)
+  p_val_thl = 0.05, type = "std")
 ```
@@
 ```{r get-bm-tot-effect-rich}
-rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
-  p_val_thl = 0.05)
+tot_rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
+  p_val_thl = 0.05, type = "std")
 ```
@@
 
-sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_sync")
-cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_cv_sp")
+sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_sync")
+cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_cv_sp")
 RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
@@
 
-env_on_stab <- get_env_on_stab(fit = all_params, p_val_thl = 0.05)
+env_on_stab <- get_env_on_stab(fit = all_params, p_val_thl = 0.05,
+  type = "std")
 # effect of env on sync and cv_sp
@@
   p_val_thl = 0.05,
-  stab_comp = "log_sync")
+  stab_comp = "log_sync", type = "std")
 env_on_cv_sp <- get_env_on_stab_comp(fit = all_params,
   p_val_thl = 0.05,
-  stab_comp = "log_cv_sp")
+  stab_comp = "log_cv_sp", type = "std")
 # env on com 
@@
   p_val_thl = 0.05,
-  com = "t_lvl")
+  com = "t_lvl", type = "std")
 env_on_ct <- get_env_on_com(fit = all_params,
   p_val_thl = 0.05,
-  com = "ct")
+  com = "ct", type = "std")
 env_on_richness <- get_env_on_rich(fit = all_params,
-  p_val_thl = 0.05)
+  p_val_thl = 0.05, type = "std")
 ```
@@
 rich_on_stab <- get_rich_on_stab(fit = all_params,
-  p_val_thl = 0.05)
+  p_val_thl = 0.05, type = "std")
 rich_on_sync <- get_rich_on_stab_comp(fit = all_params,
   p_val_thl = 0.05,
-  stab_comp = "log_sync")
+  stab_comp = "log_sync", type = "std")
 rich_on_cv_sp <- get_rich_on_stab_comp(fit = all_params,
   p_val_thl = 0.05,
-  stab_comp = "log_cv_sp")
+  stab_comp = "log_cv_sp", type = "std")
 ```
@@
 ```{r}
-richness_lab <- "Total richness (Log 10)"
+richness_lab <- "Total richness (m2^-1) (Log 10)"
 stab_lab <- "Biomass stability (Log 10)"
-bm_lab <- "Total biomass (Log 10)"
+bm_lab <- "Total biomass (g/m2) (Log 10)"
 
@@
 ```{r p-s-div, fig.cap = stab_div_caption}
-lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
-lim_log_rich_tot <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich_tot")
+lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab_std")
+lim_log_rich_tot <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich_tot_std")
 # Plot left
@@
 p_stab_div <- sem_data %>%
-  ggplot(aes(x = log_rich_tot, y = log_stab))+
+  ggplot(aes(x = log_rich_tot_std, y = log_stab_std))+
   geom_point() +
@@
 p_stab_div_troph <- stab_div_troph %>%
-  ggplot(aes(x = log_rich_tot, y = log_stab, color = troph_group)) +
+  ggplot(aes(x = log_rich_tot_std, y = log_stab_std, color = troph_group)) +
   geom_point() +
@@
 ```{r p-p-div}
-lim_log_bm <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_bm")
+lim_log_bm <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_bm_std")
 
 p_bm_div <- sem_data %>%
-  ggplot(aes(x = log_rich_tot, y = log_bm))+
+  ggplot(aes(x = log_rich_tot_std, y = log_bm_std))+
   geom_point() +
@@
 p_bm_div_troph <- stab_div_troph %>%
-  ggplot(aes(x = log_rich_tot, y = log_bm, color = troph_group)) +
+  ggplot(aes(x = log_rich_tot_std, y = log_bm_std, color = troph_group)) +
   geom_point() +
@@
 s_co_i <- print_coef(coef_div$stab["(Intercept)"])
-s_co_r <- print_coef(coef_div$stab["log_rich_tot"])
+s_co_r <- print_coef(coef_div$stab["log_rich_tot_std"])
 s_co_t <- print_coef(coef_troph$stab["troph_group3"])
-s_co_r_t2 <- print_coef(coef_troph$stab["log_rich_tot"])
-s_co_r_t3 <- print_coef(coef_troph$stab["log_rich_tot"]+coef_troph$stab["log_rich_tot:troph_group3"])
-
-s_ci_r <- print_ci(stab_div_ci["beta.log_rich_tot",])
+s_co_r_t2 <- print_coef(coef_troph$stab["log_rich_tot_std"])
+s_co_r_t3 <- print_coef(coef_troph$stab["log_rich_tot_std"]+coef_troph$stab["log_rich_tot_std:troph_group3"])
+
+s_ci_r <- print_ci(stab_div_ci["beta.log_rich_tot_std",])
 s_ci_t <- print_ci(stab_troph_ci["beta.troph_group3",])
-s_ci_r_t2 <- print_ci(stab_troph_ci["beta.log_rich_tot",])
-s_ci_r_t3 <- print_ci(coef_troph$stab["log_rich_tot"] + stab_troph_ci["beta.log_rich_tot:troph_group3",])
+s_ci_r_t2 <- print_ci(stab_troph_ci["beta.log_rich_tot_std",])
+s_ci_r_t3 <- print_ci(coef_troph$stab["log_rich_tot_std"] + stab_troph_ci["beta.log_rich_tot_std:troph_group3",])
 ```
@@
 b_co_i <- print_coef(coef_div$bm["(Intercept)"])
-b_co_r <- print_coef(coef_div$bm["log_rich_tot"])
+b_co_r <- print_coef(coef_div$bm["log_rich_tot_std"])
 b_co_t <- print_coef(coef_troph$bm["troph_group3"])
-b_co_r_t2 <- print_coef(coef_troph$bm["log_rich_tot"])
-b_co_r_t3 <- print_coef(coef_troph$bm["log_rich_tot"]+coef_troph$bm["log_rich_tot:troph_group3"])
-
-b_ci_r <- print_ci(bm_div_ci["beta.log_rich_tot",])
+b_co_r_t2 <- print_coef(coef_troph$bm["log_rich_tot_std"])
+b_co_r_t3 <- print_coef(coef_troph$bm["log_rich_tot_std"]+coef_troph$bm["log_rich_tot_std:troph_group3"])
+
+b_ci_r <- print_ci(bm_div_ci["beta.log_rich_tot_std",])
 b_ci_t <- print_ci(bm_troph_ci["beta.troph_group3",])
-b_ci_r_t2 <- print_ci(bm_troph_ci["beta.log_rich_tot",])
-b_ci_r_t3 <- print_ci(coef_troph$bm["log_rich_tot"] + bm_troph_ci["beta.log_rich_tot:troph_group3",])
+b_ci_r_t2 <- print_ci(bm_troph_ci["beta.log_rich_tot_std",])
+b_ci_r_t3 <- print_ci(coef_troph$bm["log_rich_tot_std"] + bm_troph_ci["beta.log_rich_tot_std:troph_group3",])
 ```
@@
 well understood, its effect on $\overline{CV_{sp}}$ is more complex.
-Indeed, studies reported positive [@tilman_biodiversity_2006, ], neutral  [@jiang_different_2009, @olivier_independent_nodate] or negative relationships [@franssen_annual_2011, @olivier_independent_nodate].
-Positive relationship between
 
@@
 stability, as predicted by the formulation of stability based on the CV
-[@thibaut_understanding_2013].
-However, it was unexpected that the average population $\overline{CV_{sp}}$ had
-a stronger negative effect on biomass stability than synchrony
-[@bluthgen_land_2016; @olivier_independent_nodate]. We can advance two
-hypothesis that can raise this effect. First, the opportunity for diet
-differentiation can be low in streams compare to other organisms. Bird species
+[@thibaut_understanding_2013]. However, it was unexpected that the average
+population $\overline{CV_{sp}}$ had a stronger negative effect on biomass
+stability than synchrony [@bluthgen_land_2016; @olivier_independent_nodate]. We
+can advance two hypothesis that can raise this effect. First, the opportunity
+for diet differentiation can be low in streams compare to other organisms. Bird
+species
 are for example quite specialized in seed, flying or soil arthropods or mammals

### 2020-03-19 manuscript/bef_stability/manuscript.Rmd
Add methods

@@
    - \doublespacing
+   - \usepackage{lineno}
+   - \linenumbers
 geometry: margin=2cm
@@
 overyielding (CHECK) has been proposed to explain positive relationship between
-productivity
-and species richness, while species richness effect can also rise from the
-statistical probability to end up with a highly productive species . The
-relationship between species richness and stability is even more complex
+productivity and species richness, while species richness effect can also rise
+from the statistical probability to end up with a highly productive species
+. The relationship between species richness and stability is even more complex
 partly because of the inherent multidimensionality of stability
@@
 species interact randomly. Empirically, consistent works showed that species
-richness increased community stability in grasslands [@tilman_biodiversity_2006],
-mesocosms [@pennekamp_biodiversity_2018] and vertebrates
-[@olivier_independent_nodate, @franssen_annual_2011]. Two components can
-explain variation of community stability, (1) individual species stability and (2)
-the species synchrony [@loreau_species_2008, @thibaut_understanding_2013].
-Positive [@tilman_biodiversity_2006], neutral [@jiang_different_2009, @olivier_independent_nodate]
-and negative [@franssen_annual_2011, @olivier_independent_nodate] relationships
-between species stability and species richness have been found.
-On the other side, studies consistently found that species richness decreased
-synchrony between species [@loreau_species_2008, @thibaut_understanding_2013,
+richness increased community stability in grasslands
+[@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018] and
+vertebrates [@olivier_independent_nodate, @franssen_annual_2011]. Two
+components can explain variation of community stability, (1) individual species
+stability and (2) the species synchrony [@loreau_species_2008,
+@thibaut_understanding_2013]. Positive [@tilman_biodiversity_2006], neutral
+[@jiang_different_2009, @olivier_independent_nodate] and negative
+[@franssen_annual_2011, @olivier_independent_nodate] relationships between
+species stability and species richness have been found. On the other side,
+studies consistently found that species richness decreased synchrony between
+species [@loreau_species_2008, @thibaut_understanding_2013,
 @bluthgen_land_2016; @olivier_independent_nodate]. However, as far as we know,
@@
 
-- OFB
-  - French long term protocol
-  - standardized
-
-- Electric fishing:
-  - stuned fish
-  - identification of the fishes
-  - fish counted  
-  - length of the fishes in mm by lot (4):
-    - I: big fishes measured individually
-    - S/L: fishes are grouped by species and by size 
-      - 30 random fishes were measured in each lot
-      - simulate the size of all the fishes of the lot:
-	- normal distribution truncated at 95% (?)
-	- mean and sd calculted from the sample of the lot 
-    - G: little fishes are grouped by species
-      - min and max size by lot 
-      - simulate the size of all the fishes of the lot:
-	- normal distribution truncated at 95% (?)
-	- mean computed as ???  
-	- se computed as ??? 
-    - N:
-
-- Protocols type:
-  - complete
-    - shallow river
-  - partial:
-    - deep and large river
-    - partial over bank
-    - partial by point
-    - fusion of the two Protocols when "by point" all the point were done
-      over bank
-
-- Fishing operations and station
-  - kept one protocol type by station
-  - kept one sampling operation per year (of the season the most sampled in the
-    time series)
-  - remove operations which sampling effort (length of river sampled) superior to average
-    plus or minus 30% of sd (by station)
-  - kept station that had 10 or more samplings, i.e. followed 10 years or more
+---
+#- OFB
+  #- French long term protocol
+  #- standardized
+#- Electric fishing:
+  #- stuned fish
+  #- identification of the fishes
+  #- fish counted  
+  #- length of the fishes in mm by lot (4):
+    #- I: big fishes measured individually
+    #- S/L: fishes are grouped by species and by size 
+      #- 30 random fishes were measured in each lot
+      #- simulate the size of all the fishes of the lot:
+	#- normal distribution truncated at 95% (?)
+	#- mean and sd calculted from the sample of the lot 
+    #- G: little fishes are grouped by species
+      #- min and max size by lot 
+      #- simulate the size of all the fishes of the lot:
+	#- normal distribution truncated at 95% (?)
+	#- mean computed as ???  
+	#- se computed as ??? 
+    #- N:
+#- Protocols type:
+  #- complete
+    #- shallow river
+  #- partial:
+    #- deep and large river
+    #- partial over bank
+    #- partial by point
+    #- fusion of the two Protocols when "by point" all the point were done
+      #over bank
+---
+
+Fish communities were monitored across streams of France on the period
+1995-2018 by a French governmental agency (OFB, previously AFB and ONEMA). We
+kept only standardized protocols: complete and partial methods for respectively
+little and big streams (detailed in Supplementary methods).  The sampling was
+performed by electric fishing. All the stunned fish species were identified and
+the individuals counted. Fish were classified in batch according to species and
+size class. Depending on the size class, individual fishes were measured or
+only a subsample. The size of individual fishes in subsampled batches were
+inferred under normality distribution assumption (detailed in Supplementary
+material).
 
@@
 
-- Diet data: 
-  - 7? species over 57 had a piscivorous stage
-  - 3? species had a strict piscivorous stage
-  - ontogenic diet shift based on size
-
-- 7 Resource nodes:
-  - based on diet database
-  - no information about their biomass
-
-- Size class:
-  - quantile: 9 size class per species
-
-- Interaction:
-  - Fish-resources and resources: based on diet data 
-  - Fish-fish:
-    1. diet data: is piscivorous?
-    2. allometric relationship: predation range from .03 to .45 of body size
+```{r}
+myload(metaweb_analysis, dir= mypath("data"))
+meta <- metaweb_analysis
+#metaweb_analysis$resource
+#meta$metaweb[meta$resource, meta$resource]
+
+```
+
+---
+#- Diet data: 
+  #- 7? species over 57 had a piscivorous stage
+  #- 3? species had a strict piscivorous stage
+  #- ontogenic diet shift based on size
+#- 7 Resource nodes:
+  #- based on diet database
+  #- no information about their biomass
+#- Size class:
+  #- quantile: 9 size class per species
+---
+
+---
+#- Interaction:
+  #- Fish-resources and resources: based on diet data 
+  #- Fish-fish:
+    #1. diet data: is piscivorous?
+    #2. allometric relationship: predation range from .03 to .45 of body size
+---
+
+Network inference was performed in two steps: determine trophic species,  build
+a metaweb, subtract the metaweb according to the trophic species present in
+community. Diet information were obtained from database and literature. Over
+the 57 fish species, only seven had a piscivorous life stage and only three had
+as strict piscivorous life stage. Fish species were largely omnivorous. Because
+species have ontogenic diet shift, we created nine size classes by species, one
+size class of one species constituting one trophic species. The bounds between
+size classes were equidistant (percentile method). The metaweb described the
+potential trophic interactions between the $`r 57*9`$ ($57\times9$) trophic species. 
+We had seven resource nodes which were present in the diet of the trophic
+species namely detritus, biofilm, phytoplankton, zooplankton, macrophages,
+phytobenthos and zoobenthos. A trophic species belonged to a life stage if the
+median of its size range fell in the range of the life stage. In turn, this
+trophic species has feeding interactions with the resource nodes of its life stage.
+Interactions between resource nodes are determined by literature. For example,
+phytobenthos fed on detritus, while zooplankton fed on zooplankton and
+phytoplankton. Fish-fish trophic interactions were determined by allometric
+relationships as in many studies [@brose_predator_2019, @poisot_structure_2016,
+@schneider_body_2012]. For a given trophic species, we first determined if its
+size class end up in a life stage containing piscivorous diet. If it did, we
+determined the prey size range of the trophic species from 3% to 45% of the
+median of its size range. A feeding interaction was set for each trophic species
+whose median of its size class fell into the prey range of the predator trophic
+species. To sum up, the metaweb was obtained with allometric feeding
+interactions (1) between trophic species, (2) between trophic species and
+resource nodes and (3) between resource nodes.
+
+The local networks (i.e. one network for each fish community sampling) was
+obtained by determining the trophic species of each fish individual in the
+community and interactions were set according to the metaweb. All the resource
+nodes were assumed to be present in each local network. Finally, the
+structure of the local networks varied according the presence of the trophic
+species. The inferred interactions represent potential interactions (i.e.
+not measured interactions) and are binary (i.e. presence or absence of feeding
+interactions).
+
+We computed the connectance ($C = L/N^2$, L and N being resp. the number of
+links and of nodes) and the average trophic level of each network, the average
+trophic level was weighted the biomass of each node (excluding resource nodes
+for which we had no biomass) ($\overline{T} = \sum_i^N{B_i * T_i} \times
+\sum_i^N{b_i}^{-1}$, $T_i$ and $B_i$ being resp. the trophic level and the
+biomass of the node $i$). In order to have connectance at the species level
+(i.e. not a trophic species level), we merge the trophic species of the network
+by species and thereby aggregating the link by species.
 
@@
 
-- Biomass:
-  - infered by allometric law 
-  - approximated by $B = 0.01 \times (l^3.03)$
+---
+#- Biomass:
+  #- infered by allometric law 
+  #- approximated by $B = 0.01 \times (l^3.03)$
+---
+
+The body mass of each fish was approximated from their body size with an
+allometric law ($B = 0.01 \times (l^3.03)$, $B$ being the body mass in grams and $l$ the
+body size in millimeters). We have worked with body mass instead of abundances to avoid to sum
+abundances of fishes that had really different sizes and so body masses. Body
+mass are more meaningful in terms of ecosystem description. The biomass of each
+trophic species (and species) was divided by the surface sampled (measured in
+square meters) during the sampling event. The total biomass in a given
+community are so expressed in $gm^{-2}$.
 
@@
 
-- Collected during fishing operation:   
-  - River size (width and depth)
-  - Altitude and slope
-  - distance to source
-- Independant dataset from naiades: 
-  - flow, temperature, DBO
-    1. moving window average
-    2. annual average 
-    3. interpolation along rivers (OpenStars + SSN package)
+---
+#- Collected during fishing operation:
+  #- River size (width and depth)
+  #- Altitude and slope
+  #- distance to source
+#- Independant dataset from naiades: 
+  #- flow, temperature, DBO
+    #1. moving window average
+    #2. annual average 
+    #3. interpolation along rivers (OpenStars + SSN package)
+---
+
+Habitat description were obtained from fish sampling data. We kept variables
+describing the ecosystem size namely the stream width and depth, the ecosystem
+position (altitude and slope). Physico-chemical variables were obtained from
+naiades (http://www.naiades.eaufrance.fr/)[http://www.naiades.eaufrance.fr/].
+We chose flow and temperature as physical variables to describe streams as flow
+impose swimming constraints which filter fish species that can establish [REF].
+Water temperature is linked to physiological constraints namely thermal
+tolerance and oxygen concentration tolerance [REF] since the level of water
+saturation in oxygen is inversely linked to water temperature. We chose
+Biochemical Oxygen Demand (BOD) for a proxy of enrichment in the ecosystem [REF
+mccann]. BOD is also inversely linked to oxygen concentration in water.
+The time resolution was heterogeneous according to the variable considered
+(hourly, daily and monthly for temperature, flow and BOD). For each recording
+station, we applied a moving window averaging (more details in supplementary
+material) to get rid of seasonal effects and took the annual mean (i.e. one
+value by year and by station. As the environmental recording stations were not
+located at the same place than the fish stations, we interpolated data with
+spatial statistical network model [@isaak_applications_2014] implemented in the 
+`SSN` R package [@hoef_ssn:_2014]. The interpolation procedure is detailed
+in supplementary material. For each fish station, environmental variables were
+matched with the year of fish sampling (except for water temperature for which the 
+record began in 2006). Then, the average temperature, flow, BDO, river width
+and depth were computed as well as coefficient of variation ($CV = \sigma
+\mu^{-1}$). As habitat and environmental variables are often colinear,
+a principal component analysis (PCA) was performed on the scaled variables. The
+PCA explained % of the variance. An axis rotation was performed to maximize the
+representation of the variables by the principal components
+(Fig. \@ref{fig:pca-rotated}). We kept five axis, representing respectively the
+(1) river size (river width & depth), (2) the altitude, slope and decreasing
+average temperature, (3) average enrichment (BDO) and CV of flow, (4) river
+size CV (CV of river width and depth) and (5) CV of enrichment (CV of BDO).
+Additionally, we logged the axis one, two and three to normalize their
+distribution and we reversed the third axis to get increasing average
+temperature with increasing values of the axis.
 
@@
 ```
+
+---
+#- Fishing operations and station
+  #- kept one protocol type by station
+  #- kept one sampling operation per year (of the season the most sampled in the
+    #time series)
+  #- remove operations which sampling effort (length of river sampled) superior to average
+    #plus or minus 30% of sd (by station)
+  #- kept station that had 10 or more samplings, i.e. followed 10 years or more
+---
+
+Only one protocol
+type was kept by station. We kept only one sampling event by year to homogenize
+the dataset [numbers: month of sampling, number of days bw samplings] (detailed
+in Supplementary material).
 

### 2020-03-25 manuscript/bef_stability/manuscript.Rmd
Improve SEM plot and the other Figures

@@
   pdf_document:
-    fig_caption: yes
+    fig_caption: true 
+    keep_tex: true
 fontsize: 12pt
@@
 Determining the shape of the relationship between species diversity and ecosystem
-functioning has been a central research topic in ecology [@may_will_1972,
-@hector_plant_1999, @loreau_biodiversity_2001, @hooper_effects_2005,
-@duffy_why_2009, @isbell_forest_quantifying_2018]. Current biodiversity losses
+functioning has been a central research topic in ecology
+[@may_will_1972, @hector_plant_1999, @loreau_biodiversity_2001, @hooper_effects_2005, @duffy_why_2009, @isbell_forest_quantifying_2018].
+Current biodiversity losses
 in all ecosystems challenge scientists to understand how ecosystems will be
@@
 components can explain variation of community stability, (1) individual species
-stability and (2) the species synchrony [@loreau_species_2008,
-@thibaut_understanding_2013]. Positive [@tilman_biodiversity_2006], neutral
+stability and (2) the species synchrony [@loreau_species_2008, @thibaut_understanding_2013].
+Positive [@tilman_biodiversity_2006], neutral
 [@jiang_different_2009, @olivier_independent_nodate] and negative
@@
 studies consistently found that species richness decreased synchrony between
-species [@loreau_species_2008, @thibaut_understanding_2013,
-@bluthgen_land_2016; @olivier_independent_nodate]. However, as far as we know,
+species [@loreau_species_2008, @thibaut_understanding_2013, @bluthgen_land_2016; @olivier_independent_nodate]. However, as far as we know,
 less studies have reported empirical assessment of stability-richness
@@
 Conversely, an extensive literature exists on the effects of network structure
-on stability in mutualistic and trophic networks [@angelis_stability_1975, @stouffer_,
-@thebault_stability_2010, @barbier_pyramids_2019,
-@shanafelt_david_w._stability_nodate, add ref]. Particularly, in trophic
+on stability in mutualistic and trophic networks
+[@angelis_stability_1975, @stouffer_, @thebault_stability_2010, @barbier_pyramids_2019, @shanafelt_david_w._stability_nodate, add ref].
+Particularly, in trophic
 networks, most studies are theoretical and consider asymptotic stability to
 small perturbation. Studies showed that compartimentalization [@stouffer_] can
-increase persistence, while nestedness can either increase [@bascompte,
-@thebault_stability_2010] or decrease persistence [@thebault_stability_2010].
+increase persistence, while nestedness can either increase
+[@bascompte, @thebault_stability_2010] or decrease persistence
+[@thebault_stability_2010].
 Connectance can decrease [@thebault_stability_2010] or increase
@@
 phytoplankton. Fish-fish trophic interactions were determined by allometric
-relationships as in many studies [@brose_predator_2019, @poisot_structure_2016,
-@schneider_body_2012]. For a given trophic species, we first determined if its
+relationships as in many studies [@brose_predator_2019, @poisot_structure_2016, @schneider_body_2012].
+For a given trophic species, we first determined if its
 size class end up in a life stage containing piscivorous diet. If it did, we
@@
 trophic level was weighted the biomass of each node (excluding resource nodes
-for which we had no biomass) ($\overline{T} = \sum_i^N{B_i * T_i} \times
-\sum_i^N{b_i}^{-1}$, $T_i$ and $B_i$ being resp. the trophic level and the
+for which we had no biomass) ($\overline{T} = \sum_i^N{B_iT_i \times
+\sum_i^N{B_i}^{-1}}$, $T_i$ and $B_i$ being resp. the trophic level and the
 biomass of the node $i$). In order to have connectance at the species level
@@
 p_format <- "png"
-p_width <- 700
-p_height <- 700
+p_width <- 700*2
+p_height <- 900*2
 
@@
 
-graph_stab_sem <- build_diag_from_sem(stab_sem_rich, p_val_thd = 0.05)
+graph_stab_sem <- build_diag_from_sem(
+  stab_sem_rich, 
+  p_val_thd = 0.05,
+  env_x_pos_range = c(from = 0, to = 7.5),
+  env_y_pos = 0,
+  env_y_sep = 1.5,
+  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2")  
+)
+graph_stab_sem %<>%
+  add_global_graph_attrs(
+    attr = "splines",
+    value = "ortho", #spline
+    attr_type = "graph")
 render_graph(graph_stab_sem)
@@
   file_name = stab_sem_path,
-  height = p_height - p_height*20/100,
+  height = p_height - p_height*30/100,
   width = p_width
@@
 #source(mypath("R", "plot_methods.R")) 
-graph_bm_sem <- build_diag_from_sem(bm_sem_rich, p_val_thd = 0.05)
+graph_bm_sem <- build_diag_from_sem(
+  bm_sem_rich, 
+  p_val_thd = 0.05,
+  env_x_pos_range = c(from = 0, to = 7.5),
+  env_y_pos = 0,
+  env_y_sep = 1.5,
+  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2")  
+)
+graph_bm_sem %<>%
+  add_global_graph_attrs(
+    attr = "splines",
+    value = "ortho", #spline
+    attr_type = "graph")
 render_graph(graph_bm_sem)
@@
   file_name = bm_sem_path,
-  #file_name = "stab_sem.svg",
-  height = p_height,
+  height = p_height - p_height*45/100,
   width = p_width 
@@
   draw_image(img_bm_sem)
-
 ```
@@
 
-```{r sem-plot, fig.dim = c(10,10), fig.cap = "SEM"}
+```{r}
+sem_caption <- paste0(
+  "Results of the Structural Equation Models for (A) the determinants of biomass stability and (B) total biomass.
+Red and green represent respectively negative and positive path coefficients.
+The path coefficients are standardized coeffients.
+For convenience, only significant paths (i.e, *P < 0.05*) are shown."
+
+)
+```
+
+```{r sem-plot, fig.dim = c(10,10), fig.cap = sem_caption}
 #https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
@@
 
-plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[1:2], rel_widths = c(.55, .45))
+plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[1:2], rel_widths = c(.50, .5))
 ```
@@
 
-Species richness and the average trophic level were the main direct drivers of
-total biomass ($r_\delta = `r rich_on_bm`$ and $r_\delta = `r tlvl_on_bm`$ resp.) whereas
-connectance had no significant effect (Fig. \@ref(fig:sem-plot) C). The stream
-size had a direct positive effect on total biomass ($r_\delta = `r RC1_on_bm`$) whereas
-avg temperature, avg DBO, CV of river size and CV of DBO had no direct effects
-on total biomass.
-
-Species richness had also a indirect positive effect on total biomass through
-average trophic level, species richness had a total positive effect of $`r rich_on_bm`$
-on total biomass. The stream size had a total effect on total biomass as strong
+The average trophic level was the only direct driver of
+total biomass ($r_\delta = `r tlvl_on_bm`$) whereas
+connectance and species richness had no significant effects (Fig.
+\@ref(fig:sem-plot) C). Environmental variables  no direct effects on total
+biomass.
+
+Species richness had a indirect positive effect on total biomass through
+average trophic level ($`r 0.38*.51`$). The stream size had a total effect on total biomass as strong
 as species richness ($r_\delta =`r env_on_bm["log_RC1"]`$), indirectly through average trophic level
@@
 river size had no or weak indirect effect on total biomass
-(resp. $r_\delta =`r env_on_bm["log_RC3"]`$, $r_\delta =`r env_on_bm["log_RC5"]`$, $r_\delta =`r env_on_bm["log_RC4"]`$).
+(resp. $r_\delta =`r env_on_bm["log_RC3"]`$, $r_\delta =`r env_on_bm["RC5"]`$, $r_\delta =`r env_on_bm["RC4"]`$).
 
@@
 whereas average trophic level and connectance had no significant effects on either
-$\overline{CV_{sp}}$ nor synchrony. The avg river size had a small positive direct
-effect on synchrony ($r_\delta = `r RC1_on_sync`$). The other environmental variables had
+$\overline{CV_{sp}}$ nor synchrony. The environmental variables had
 no significant direct effects on either $\overline{CV_{sp}}$ nor synchrony.
@@
 Indirectly through synchrony and $\overline{CV_{sp}}$, species richness had a total negative
-effect on biomass stability ($r_\delta = `r rich_on_stab`$). Avg river size and avg
-temperature had also a total effect which was negative on biomass stability
-(resp. $r_\delta = `r env_on_stab["log_RC1"]`$ and $r_\delta = `r env_on_stab["log_RC2"]`$),
-going through richness (resp. $r_\delta = `r env_on_richness["log_RC1"]`$ and
-$r_\delta = `r env_on_richness["log_RC2"]`$).
+effect on biomass stability ($r_\delta = `r rich_on_stab`$). Avg river size and
+avg temperature had also a total effect which was negative on biomass stability
+(resp. $r_\delta = `r env_on_stab["log_RC1"]`$ and $r_\delta = `r
+env_on_stab["log_RC2"]`$), going through richness (resp. $r_\delta = `r
+env_on_richness["log_RC1"]`$ and $r_\delta = `r env_on_richness["log_RC2"]`$).
 
@@
 ```{r}
-richness_lab <- "Total richness (m2^-1) (Log 10)"
+richness_lab <- expression(bold(paste("Total richness (", m^"-2", ") (Log 10)")))
 stab_lab <- "Biomass stability (Log 10)"
-bm_lab <- "Total biomass (g/m2) (Log 10)"
+bm_lab <- expression(bold(paste("Total biomass (", g.m^"-2", ") (Log 10)")))
 
@@
   = "grey20", alpha = .2) +
-  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
+  annotate("text", x = -2.75, y = .75, label = make_label_rsq(rsq = stab_div_sum),
     parse = TRUE)
@@
     alpha = .2) +
-  annotate("text", x = 0.8, y = .8, label = make_label_rsq(rsq = stab_troph_sum),
+  annotate("text", x = -2.75, y = .75, label = make_label_rsq(rsq = stab_troph_sum),
     parse = TRUE) +
@@
 
-p_stab <- plot_grid(p_stab_div, p_stab_div_troph,
+troph_legend <- get_legend(
+  p_stab_div_troph + 
+    guides(color = guide_legend(nrow = 1)) +
+    theme(legend.position = "bottom")
+)
+
+p_stab <- plot_grid(
+  p_stab_div,
+  p_stab_div_troph + theme(legend.position = "none"),
   ncol = 2, rel_widths = c(.4, .6),
@@
   = "grey20", alpha = .2) +
-  annotate("text", x = .8, y = 1.5, label = make_label_rsq(rsq = bm_div_sum),
+  annotate("text", x = -2.75, y = -1.0, label = make_label_rsq(rsq = bm_div_sum),
     parse = TRUE)
@@
     alpha = .2) +
-  annotate("text", x = 0.8, y = 1.5, label = make_label_rsq(rsq = bm_troph_sum),
+  annotate("text", x = -2.75, y = -1.0, label = make_label_rsq(rsq = bm_troph_sum),
     parse = TRUE) +
-  #scale_x_log10() + scale_y_log10() +
   labs(x = richness_lab, y = bm_lab)
 
-p_bm <- plot_grid(p_bm_div, p_bm_div_troph, ncol = 2, rel_widths = c(.4, .6),
-  labels = c("C", "D"))
-```
-
-```{r psbm, fig.dim = c(10,5)}
-plot_grid(p_stab, p_bm, ncol = 1)
+p_bm <- plot_grid(
+  p_bm_div,
+  p_bm_div_troph + theme(legend.position = "none"),
+  ncol = 2,
+  rel_widths = c(.4, .6),
+  labels = c("C", "D")
+)
+```
+```{r}
+troph_caption <- paste0(
+  "The effect of species richness on biomass stability
+  (upper panel) and total biomass (bottom panel) for the whole community (left
+    panel) and the community splited by trophic group (right panel)."
+)
+
+```
+
+```{r psbm, fig.dim = c(10,5), fig.cap = troph_cap}
+plot_grid(
+  p_stab,
+  p_bm,
+  troph_legend,
+  ncol = 1,
+  rel_heights = c(1, 1, .1)
+)
 
@@
 
+**Truc chelou sur l'effet du niveau trophique sur la biomasse et la stabilité,
+to check again the computation. Plots look good but the model coefficients does
+not go in the same direction**
+
 ---
@@
 ---
-species richness increased total biomass (`r b_co_r`% `r b_ci_r` by 1% species richness increase). Total
-biomass was `r b_co_t`% `r b_ci_t` higher in the high than in the low trophic
+Species richness increased total biomass (`r b_co_r`% `r b_ci_r` by 1% species
+richness increase). Total biomass was `r b_co_t`% `r b_ci_t` higher in the high
+than in the low trophic
 group. However, the increase of total biomass with the increase of species
@@
 showed that the total biomass was primary driven by environmental drivers. In
-contrast, we found that the species richness was one of the main driver of the
+contrast, we found that the average trophic level was one of the main driver of the
 total biomass, together with the stream size and increasing avg temperature
-(with decreasing altitude). The big effect of species richness is 
-partly explained by its effect on food web assembly and so, avg trophic level
-(`r round(.2/0.54 * 100)` % of richness effect on total biomass). The direct
-positive effect of species richness on total biomass might be due to resource use
-complementarity [@cardinale_species_2002] [add more direct REF]. It was however
-unexpected that connectance had no effect on total biomass, because we could
-imagine that connectance could also improve resource use, but this might be
-true only under the assumption that all species have the same assimilation
-efficiency.
-
-We found that contrary to stream size, the effect of altitude of the river and
-its avg temperature on total biomass was only indirect through community
-structure (avg trophic level and connectance).
+(with decreasing altitude). The effect of species richness is 
+goes through its effect on food web assembly and so, avg trophic level.
+The indirect positive effect of species richness on total biomass might be due to
+resource use complementarity [@cardinale_species_2002].
+It was however unexpected that connectance had no effect on total biomass,
+because we could imagine that connectance could also improve resource use, but
+this might be true only under the assumption that all species have the same
+assimilation efficiency.
+We found that the effect of stream size, altitude of the river and its avg
+temperature on total biomass was only indirect through community structure
+(species richness and average trophic level).
 
@@
 
-The total effect of river size on biomass stability was as negative as species
-richness, indicating that big rivers had a high negative effect on stability (TO MOVE).
-We found a mix of both expected and unexpected results on the effects on
-environment on community structure. First, we expected that bigger and low
-altitude streams had higher species richness because they might receive more
+The total effect of river size on biomass stability was negative as avg
+temperature (and low altitude), indicating that big rivers in plains had a high
+negative effect on stability (TO MOVE). We found a mix of both expected and
+unexpected results on the effects on environment on community structure. First,
+we expected that bigger and low altitude streams had higher species richness
+because they might receive more
 confluents streams and so more species through immigration.
-Stream size increased both connectance and avg trophic level with the same
-magnitude. An increase in mean trophic position of piscivorous species in
-bigger rivers could explain this relation [@post_ecosystem_2000]. In our
-network reconstruction, the fish-fish interactions are more resolved than
-fish-resource interactions, which might explain positive effect of stream size
-on connectance. @petchey_predicting_2010 predicted that temperature should
-increase connectance but we did not find any relationship but temperature (and
+Stream size increased avg trophic level. An increase in mean trophic position
+of piscivorous species in bigger rivers could explain this relation
+[@post_ecosystem_2000]. In our network reconstruction, the fish-fish
+interactions are more resolved than fish-resource interactions.
+@petchey_predicting_2010 predicted that temperature should increase connectance
+but we did not find any relationship but temperature (and
 low altitude) increased avg trophic level (**Bullshit**). 
 CV of enrichment decreased both connectance and avg trophic level, while avg
-enrichment (and CV of flow) increased both. The latter might by explained by
+enrichment (and CV of flow) increased avg trophic level. The latter might by explained by
 the fact that enrichment can benefit to top trophic level
@@
 for diet differentiation can be low in streams compare to other organisms. Bird
-species
-are for example quite specialized in seed, flying or soil arthropods or mammals
-which gives opportunities for independent dynamics. Plants also can achieve
-independent dynamics either spatial segregation or niche differentiation. Because
-fish species even piscivorous one are quite opportunistic in their foraging.
+species are for example quite specialized in seed size, flying or soil arthropods or
+mammals which gives opportunities for independent dynamics. Plants also can
+achieve independent dynamics either spatial segregation or niche
+differentiation. Because fish species even piscivorous one are quite
+opportunistic in their foraging.
 Secondly, in trophic communities, species directly affect each other through

### 2020-04-01 manuscript/bef_stability/manuscript.Rmd
Add table indir + modify troph group effect

@@
 
+##### BEF
 Determining the shape of the relationship between species diversity and ecosystem
@@
 
----
-#- Diversity - stability and diversity - biomass / productivity
-  #- well studied: both experimentally, empirically and theoretically
-  #- mecanisms:
-    #- stability: insurance (asynchrony),
-    #- diversity: overyielding (complementarity)
-  #- key papers: [@tilman_biodiversity_2006, @loreau_species_2008,
-    #@thibaut_understanding_2013, @may_will_1972]
-  #- BUT: less vertical diversity, trophic communities
----
-
 Species richness has been reported to increase productivity in grasslands
@@
 decrease total biomass [@grace_integrative_2016] contrary to previous
-assessment [@hector_plant_1999, @tilman_biodiversity_2014] because of
-competition for light between plants [@grace_integrative_2016]. Complementarity
+assessment [@hector_plant_1999, @tilman_biodiversity_2014]. Complementarity
 between species in resource exploitation [@cardinale_species_2002] leading to
@@
   #summarise(richness_tot = length(unique(species)))
-com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb)
+com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
+ type_network_metrics = "classes" 
+)
 # Compute sem dataset 
@@
 ```{r get-data, cache = FALSE}
-library(nlme)
 library(piecewiseSEM)
 library(lme4)
-ctrl <- lmeControl(opt='optim')
+library(nlme)
+
+#ctrl <- lmeControl(opt='optim')
 ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
@@
 # get coeff
-coef_div <- map(list(stab = stab_div_mod, bm = bm_div_mod), fixed.effects)
+coef_div <- map(list(stab = stab_div_mod, bm = bm_div_mod), fixef)
 ```
@@
 ```{r mod-div-troph, fig.show = "hide"}
-stab_troph_mod <- lmer(data = stab_div_troph,
+stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
   formula = log_stab_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
@@
 )
-stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 200)
+
+stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
+  formula = log_stab_std ~  troph_group + (1 | basin)
+  #control = ctrl
+)
+
+stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
 stab_troph_ci <- confint(stab_troph_boot)
 
-stab_troph_colin <- car::vif(stab_troph_mod)
+#stab_troph_colin <- car::vif(stab_troph_mod)
 stab_troph_sum <- piecewiseSEM::rsquared(stab_troph_mod, method = "nagelkerke") %>%
@@
 
-pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
-#plot(pred_troph_mod, add.data = TRUE)
-stab_troph_pred <- pred_troph_mod %>%
-  as_tibble() %>%
-  rename(
-    log_stab_std = predicted,
-    log_rich_tot_std = x,
-    troph_group = group
-  )
-
-# Productivity and troph group
-
-bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
-  #fixed = log_bm ~ log_rich_tot * troph_group,
-  formula = log_bm_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
-  #random = ~ 1 + log_rich_tot * troph_group | basin,
-  #control = ctrl 
-)
-bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
-bm_troph_ci <- confint(bm_troph_boot)
-
-bm_troph_sum <- piecewiseSEM::rsquared(bm_troph_mod, method = "nagelkerke") %>%
-  mutate_at(vars(Conditional, Marginal), ~round(., 2))
-
-pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
-#plot(pred_troph_mod, add.data = TRUE)
-bm_troph_pred <- pred_troph_mod %>%
-  as_tibble() %>%
-  rename(
-    log_bm_std = predicted,
-    log_rich_tot_std = x,
-    troph_group = group
-  )
-
-# get coeff
-coef_troph <- map(list(stab = stab_troph_mod, bm = bm_troph_mod), fixed.effects)
+#pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
+##plot(pred_troph_mod, add.data = TRUE)
+#stab_troph_pred <- pred_troph_mod %>%
+  #as_tibble() %>%
+  #rename(
+    #log_stab_std = predicted,
+    #log_rich_tot_std = x,
+    #troph_group = group
+  #)
+
+## Productivity and troph group
+
+#bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
+  ##fixed = log_bm ~ log_rich_tot * troph_group,
+  #formula = log_bm_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
+  ##random = ~ 1 + log_rich_tot * troph_group | basin,
+  ##control = ctrl 
+#)
+#bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
+#bm_troph_ci <- confint(bm_troph_boot)
+
+#bm_troph_sum <- piecewiseSEM::rsquared(bm_troph_mod, method = "nagelkerke") %>%
+  #mutate_at(vars(Conditional, Marginal), ~round(., 2))
+
+#pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
+##plot(pred_troph_mod, add.data = TRUE)
+#bm_troph_pred <- pred_troph_mod %>%
+  #as_tibble() %>%
+  #rename(
+    #log_bm_std = predicted,
+    #log_rich_tot_std = x,
+    #troph_group = group
+  #)
+
+## get coeff
+#coef_troph <- map(list(stab = stab_troph_mod, bm = bm_troph_mod), fixed.effects)
+```
+```{r stab-div-troph}
+stab_div_by_troph <- compute_stat_troph_rich(
+  .data = stab_div_troph,
+  resp = "log_stab_std"
+)
+
+bm_div_by_troph <- compute_stat_troph_rich(
+  .data = stab_div_troph,
+  resp = "log_bm_std"
+)
+troph_perm_test <- map(c(stab = "log_stab_std", bm = "log_bm_std"),
+  ~test_troph(.data = stab_div_troph, var = .x)
+  )
+troph_perm_test$bm$obs
+troph_perm_test$stab$obs
+troph_perm_test$bm$p_val
+troph_perm_test$stab$p_val
+
 ```
@@
 
-library(ggraph)
-p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
-p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
-
 library(DiagrammeR)
-
-p_format <- "png"
-p_width <- 700*2
-p_height <- 900*2
-
-stab_sem_path <- mypath("manuscript", "bef_stability",
-  paste0("stab_sem.", p_format))
-bm_sem_path <- mypath("manuscript", "bef_stability",
-  paste0("bm_sem.", p_format))
-
-graph_stab_sem <- build_diag_from_sem(
-  stab_sem_rich, 
-  p_val_thd = 0.05,
+p_stab_sem_rich <- export_diagram(
+  fit = stab_sem_rich,
+  file_path = mypath("manuscript", "bef_stability", "stab_sem"),
+  format = "png",
+  width = 700*2,
+  height = 900*2  - 900*2*30/100,
+  arrows = "ortho",
+  val_thd = 0.05,
   env_x_pos_range = c(from = 0, to = 7.5),
@@
 )
-graph_stab_sem %<>%
-  add_global_graph_attrs(
-    attr = "splines",
-    value = "ortho", #spline
-    attr_type = "graph")
-render_graph(graph_stab_sem)
-export_graph(graph = graph_stab_sem, file_type = p_format,
-  file_name = stab_sem_path,
-  height = p_height - p_height*30/100,
-  width = p_width
-)
-#source(mypath("R", "plot_methods.R")) 
-graph_bm_sem <- build_diag_from_sem(
-  bm_sem_rich, 
-  p_val_thd = 0.05,
+
+p_bm_sem_rich <- export_diagram(
+  fit = bm_sem_rich,
+  file_path = mypath("manuscript", "bef_stability", "bm_sem"),
+  format = "png",
+  width = 700*2,
+  height = 900*2  - 900*2*45/100,
+  arrows = "ortho",
+  val_thd = 0.05,
   env_x_pos_range = c(from = 0, to = 7.5),
@@
 )
-graph_bm_sem %<>%
-  add_global_graph_attrs(
-    attr = "splines",
-    value = "ortho", #spline
-    attr_type = "graph")
-render_graph(graph_bm_sem)
-export_graph(graph = graph_bm_sem, file_type = p_format,
-  file_name = bm_sem_path,
-  height = p_height - p_height*45/100,
-  width = p_width 
-)
-
-library(magick)
-library(rsvg)
-img_stab_sem <- stab_sem_path %>%
-  image_read()
-p_stab_sem_rich <- ggdraw() +
-  draw_image(img_stab_sem)
-img_bm_sem <- bm_sem_path %>%
-  image_read()
-p_bm_sem_rich <- ggdraw() +
-  draw_image(img_bm_sem)
 ```
@@
 bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)
-get_clean_sem_coef <- function(sem = NULL, resp = NULL, pred = NULL) {
-  out <- sem[sem$Response == resp & sem$Predictor == pred, ]$Std.Estimate
-  out <- ifelse(length(out) == 0, 0, out)
-  round(out, 2)
-}
 
@@
   type = "std")
-# env on com 
-env_on_t_lvl <- get_env_on_com(fit = bm_all_params, p_val_thl = 0.05,
-  com = "t_lvl", type = "std")
-env_on_ct <- get_env_on_com(fit = bm_all_params,
-  p_val_thl = 0.05, com = "ct", type = "std")
-env_on_richness <- get_env_on_rich(fit = bm_all_params,
+# rich on bm 
+rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
   p_val_thl = 0.05, type = "std")
-```
-
-```{r get-bm-tot-effect-rich}
-tot_rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
-  p_val_thl = 0.05, type = "std")
+
+tmp_bm_indir_table <- map(list(env_on_bm, rich_on_bm),
+  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
+  ) %>%
+bind_rows()
 ```
@@
 ```{r get-sem-tot-effect-env}
-all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
-# effect of env on stab
-
-env_on_stab <- get_env_on_stab(fit = all_params, p_val_thl = 0.05,
-  type = "std")
+source(mypath("R", "total_sem_effect.R"))
+stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
 # effect of env on sync and cv_sp
-env_on_sync <- get_env_on_stab_comp(fit = all_params,
+env_on_sync <- get_env_on_stab_comp(fit = stab_all_params,
   p_val_thl = 0.05,
   stab_comp = "log_sync", type = "std")
-env_on_cv_sp <- get_env_on_stab_comp(fit = all_params,
+env_on_cv_sp <- get_env_on_stab_comp(fit = stab_all_params,
   p_val_thl = 0.05,
   stab_comp = "log_cv_sp", type = "std")
-# env on com 
-env_on_t_lvl <- get_env_on_com(fit = all_params,
+# env on stab via network 
+env_on_t_lvl <- get_env_on_com(fit = stab_all_params,
   p_val_thl = 0.05,
   com = "t_lvl", type = "std")
-env_on_ct <- get_env_on_com(fit = all_params,
+env_on_ct <- get_env_on_com(fit = stab_all_params,
   p_val_thl = 0.05,
   com = "ct", type = "std")
-env_on_richness <- get_env_on_rich(fit = all_params,
+env_on_richness <- get_env_on_rich(fit = stab_all_params,
   p_val_thl = 0.05, type = "std")
@@
 ```{r get-sem-tot-effect-rich}
-rich_on_stab <- get_rich_on_stab(fit = all_params,
-  p_val_thl = 0.05, type = "std")
-rich_on_sync <- get_rich_on_stab_comp(fit = all_params,
+rich_on_sync <- get_rich_on_stab_comp(fit = stab_all_params,
   p_val_thl = 0.05,
   stab_comp = "log_sync", type = "std")
-rich_on_cv_sp <- get_rich_on_stab_comp(fit = all_params,
+rich_on_cv_sp <- get_rich_on_stab_comp(fit = stab_all_params,
   p_val_thl = 0.05,
   stab_comp = "log_cv_sp", type = "std")
+```
+
+```{r}
+# effect of env on stab
+env_on_stab <- get_env_on_stab(fit = stab_all_params, p_val_thl = 0.05,
+  type = "std")
+rich_on_stab <- get_rich_on_stab(fit = stab_all_params,
+  p_val_thl = 0.05, type = "std")
+com_on_stab <- get_com_on_stab(fit = stab_all_params,
+  p_val_thl = 0.05, type = "std")
+
+tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, com_on_stab),
+  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
+
+  ) %>%
+bind_rows()
+
 ```
@@
 # Right plot
-p_stab_div_troph <- stab_div_troph %>%
-  ggplot(aes(x = log_rich_tot_std, y = log_stab_std, color = troph_group)) +
-  geom_point() +
-  ggplot2::scale_color_manual(
-    labels = troph_group_labeller(),
-    values = c("blue", "green", "red"),
-    name = "Trophic group"
-  ) +
-  ylim(lim_log_stab) +
-  xlim(lim_log_rich_tot) +
-  geom_line(data = stab_troph_pred) +
-  geom_ribbon(data = stab_troph_pred,
-    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
-    alpha = .2) +
-  annotate("text", x = -2.75, y = .75, label = make_label_rsq(rsq = stab_troph_sum),
-    parse = TRUE) +
-  #scale_x_log10() + scale_y_log10() +
-  labs(x = richness_lab, y = stab_lab)
+p_stab_div_troph <- make_troph_plot(
+  .data = stab_div_by_troph,
+  resp  = "log_stab_std",
+  x_lim = lim_log_rich_tot,
+  y_lim = lim_log_stab,
+  lab_xy = c(x = richness_lab, y = stab_lab),
+  rsq_xy = c(x = -2.75, y = .75) 
+  )
 
@@
 
-p_bm_div_troph <- stab_div_troph %>%
-  ggplot(aes(x = log_rich_tot_std, y = log_bm_std, color = troph_group)) +
-  geom_point() +
-  ylim(lim_log_bm) +
-  xlim(lim_log_rich_tot) +
-  ggplot2::scale_color_manual(
-    labels = troph_group_labeller(),
-    values = c("blue", "green", "red"),
-    name = "Trophic group"
-  ) +
-  geom_line(data = bm_troph_pred) +
-  geom_ribbon(data = bm_troph_pred,
-    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
-    alpha = .2) +
-  annotate("text", x = -2.75, y = -1.0, label = make_label_rsq(rsq = bm_troph_sum),
-    parse = TRUE) +
-  labs(x = richness_lab, y = bm_lab)
+p_bm_div_troph <- make_troph_plot(
+  .data = bm_div_by_troph,
+  resp  = "log_bm_std",
+  x_lim = lim_log_rich_tot,
+  y_lim = lim_log_bm,
+  lab_xy = c(x = richness_lab, y = bm_lab),
+  rsq_xy = c(x = -2.75, y = -1.0) 
+  )
 
@@
 
-print_coef <- function (vec){
-  round(abs(vec)*100)
-}
-print_ci <- function(.df){
-  .df <- round(.df, 3)*100
-
-  paste0("[", .df[["2.5 %"]],";",.df[["97.5 %"]] ,"]")
-}
 ```
@@
 ```{r print-coef-stab}
+
 # Coefficients
@@
 
-```{r tab-coeff-stab}
-
+#### Indirect effect
+
+```{r indir-tab, fig.cap = "Indirect effect from SEM"}
+kable(tmp_stab_indir_table)
+kable(tmp_bm_indir_table)
 ```

### 2020-04-01 report/03-results.Rmd
Add table indir + modify troph group effect

@@
 ```
+
+## Network properties
+
+### class connectance versus species connectance
+
+```{r}
+cl_ct <- temporal_network_metrics_classes %>%
+  select(station, connectance_med, nbnode_med) %>%
+  rename(cl_ct_med = connectance_med, cl_node_med = nbnode_med)
+myload(temporal_network_metrics, dir = mypath("data", "species"))
+sp_ct <- temporal_network_metrics %>%
+  select(station, connectance_med, nbnode_med) %>%
+  rename(sp_ct_med = connectance_med, sp_node_med = nbnode_med)
+
+myload(network_metrics, dir = mypath("data", "classes"))
+cl_network_metrics <- network_metrics
+myload(network_metrics, dir = mypath("data", "species"))
+sp_network_metrics <- network_metrics
+sp_net <- sp_network_metrics %>%
+  select(opcod, connectance, nbnode) %>%
+  rename(sp_ct = connectance, sp_node = nbnode)
+cl_net <- cl_network_metrics %>%
+  select(opcod, connectance, nbnode) %>%
+  rename(cl_ct = connectance, cl_node = nbnode)
+
+net_comp <- sp_net %>% 
+  left_join(cl_net, by = "opcod")
+```
+
+```{r}
+net_comp %>%
+  pivot_longer(
+        cols = ends_with("ct"),
+        names_to = "type",
+        names_prefix = "_ct",
+        values_to = "ct",
+        values_drop_na = TRUE
+  ) %>%
+  ggplot(aes(x = ct, fill = type)) +
+  geom_histogram(position = "identity", alpha = .2) +
+  xlab("Connectance")
+```
+
+### Weighted average trophic level: class vs species network
+
+```{r}
+sp_net <- sp_network_metrics %>%
+  select(opcod, w_trph_lvl_avg, nbnode) %>%
+  rename(cl_tlvl = w_trph_lvl_avg, cl_node = nbnode)
+cl_net <- cl_network_metrics %>%
+  select(opcod, w_trph_lvl_avg, nbnode) %>%
+  rename(sp_tlvl = w_trph_lvl_avg, sp_node = nbnode)
+
+net_comp <- sp_net %>% 
+  left_join(cl_net, by = "opcod")
+```
+
+```{r}
+net_comp %>%
+  pivot_longer(
+        cols = ends_with("tlvl"),
+        names_to = "type",
+        names_prefix = "_tlvl",
+        values_to = "tlvl",
+        values_drop_na = TRUE
+  ) %>%
+  ggplot(aes(x = tlvl, fill = type)) +
+  geom_histogram(position = "identity", alpha = .2) +
+  xlab("Connetlvlance")
+```

### 2020-04-01 report/05-stability.Rmd
Add table indir + modify troph group effect

@@
 
-```{r}
-myload(nmds, dir = mypath("report"))
-lav_data <- compute_sem_dataset(
-  com = temporal_community_metrics,
-  network = temporal_network_metrics, 
-  hab_press = habitat_pressure, 
-  sync = synchrony,
-  nmds = NULL,
-  basin = st_basin 
-  )
-```
-
 ### Piecewiese SEM
@@
 #### Stability
+
+```{r, fig.dim = c(10, 7), echo = FALSE, fig.cap = "SEM for stability"}
+library(nlme)
+library(piecewiseSEM)
+
+st_basin <- get_basin_station()
+myload(nmds, dir = mypath("report"))
+myload(network_metrics, dir = mypath("data", "species"))
+sp_network_metrics <- network_metrics
+rm(network_metrics)
+myload(network_metrics, dir = mypath("data", "classes"))
+cl_network_metrics <- network_metrics
+rm(network_metrics)
+
+myload(biomass_ts_sax, dir = mypath("data"))
+op_analysis_bbb <- filter(op_analysis, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+
+# Compute stability, network metrics, etc with the new datasets
+source(mypath("R", "community_analysis.R"))
+#debug(compute_community_temporal_analysis)
+com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb)
+class_tps_net <- summarise_network_over_time(op = op_analysis_bbb,
+class_network = cl_network_metrics,
+species_network = sp_network_metrics,
+metrics = c("connectance", "w_trph_lvl_avg"),
+type_metrics = "classes")
+
+# Compute sem dataset 
+sem_data <- map(list(sp = com_data[["tps_net"]], cl = class_tps_net),
+~compute_sem_dataset(
+  com = com_data[["tps_com"]],
+  network = .x, 
+  hab_press = habitat_pressure, 
+  sync = com_data[["sync"]],
+  nmds = NULL,
+  basin = st_basin 
+  )
+)
+
+# Compute SEMs
+sem <- map(sem_data, ~compute_stab_sem_rich(.data = .x))
+
+library(DiagrammeR)
+sem_graph <- map2(
+  sem,
+  paste0(mypath("manuscript", "bef_stability"), "/", c("species", "class"), "_stab_sem"),
+  function(x, path) {
+
+  export_diagram(
+    fit = x,
+    file_path = path,
+    format = "png",
+    width = 700*2,
+    height = 900*2  - 900*2*30/100,
+    arrows = "ortho",
+    val_thd = 0.05,
+    env_x_pos_range = c(from = 0, to = 7.5),
+    env_y_pos = 0,
+    env_y_sep = 1.5,
+    order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2")
+  )
+
+}
+)
+```
 
@@
   stab = c("log_stab"),
-  .data = lav_data)
+  .data = sem_data)
 
@@
 car::vif(lme(log_sync ~ alt + width + temperature_med + DBO_med + flow_med, random = ~ 1 | basin, data = lav_data))
-```
-
-```{r, fig.dim = c(10, 7), echo = FALSE, fig.cap = "SEM for stability"}
-library(nlme)
-library(piecewiseSEM)
-
-st_basin <- get_basin_station()
-myload(nmds, dir = mypath("report"))
-myload(network_metrics, dir = mypath("data", "species"))
-
-# Compute stability, network metrics, etc with the new datasets
-com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))
-# Compute sem dataset 
-sem_data <- compute_sem_dataset(
-  com = com_data[["tps_com"]],
-  network = com_data[["tps_net"]], 
-  hab_press = habitat_pressure, 
-  sync = com_data[["sync"]],
-  nmds = NULL,
-  basin = st_basin 
-  )
-
-# Compute SEMs
-sem <- compute_stab_sem_rich_beta(.data = sem_data,
-  random_effect = as.formula("~1|basin"))
-
-ggpiecewisesem(sem)
 ```

### 2020-04-01 R/total_sem_effect.R

@@ -97,9 +97,15 @@ get_env_on_stab <- function (fit = NULL, p_val_thl = NULL, type = "std") {
    stab_var <- paste0(stab_var, "_", type)
   }
 
-  via_cv_sp_sync <- get_indirect_effect(fit = fit, p_val_thl = 0.05,
+  via_cv_sp <- get_indirect_effect(fit = fit, p_val_thl = 0.05,
     x = c(paste0("log_RC", seq(1,3)), paste0("RC", c(4,5))),
-    zz = c("log_sync", "log_cv_sp"),
+    zz = c("log_cv_sp"),
+    zzz = c(stab_var) 
+  )
+  
+  via_sync <- get_indirect_effect(fit = fit, p_val_thl = 0.05,
+    x = c(paste0("log_RC", seq(1,3)), paste0("RC", c(4,5))),
+    zz = c("log_sync"),
     zzz = c(stab_var) 
   )
   # effect of env through richness 
@@ -125,10 +131,16 @@ get_env_on_stab <- function (fit = NULL, p_val_thl = NULL, type = "std") {
     zz = c("log_sync", "log_cv_sp"),
     zzz = c(stab_var)
   )
-  to_sum <- list(via_cv_sp_sync = via_cv_sp_sync, via_richness = via_richness,
-    via_com = via_com, via_richness_com = via_richness_com)
 
-  from_indir_to_tot(to_sum = to_sum)
+  to_sum <- list(
+    via_cv_sp = via_cv_sp,
+    via_sync = via_sync,
+    via_richness = via_richness,
+    via_com = via_com,
+    via_richness_com = via_richness_com
+  )
+
+  return(get_indir_common_output(.data = to_sum))
 }
 
 #' Get env effect on sync cv_sp 
@@ -158,7 +170,8 @@ get_env_on_stab_comp <- function (fit = NULL, p_val_thl = NULL,
     zz = stab_comp
   )
   to_sum <- list(direct = direct, via_richness = via_richness, via_com = via_com)
-  from_indir_to_tot(to_sum = to_sum)
+
+  return(get_indir_common_output(.data = to_sum))
 }
 
 #' get env on com 
@@ -181,7 +194,7 @@ get_env_on_com <- function (fit = NULL, p_val_thl = NULL, com = NULL, type = "st
   )
   to_sum <- list(direct = direct, via_richness = via_richness)
 
-  from_indir_to_tot(to_sum = to_sum)
+  return(get_indir_common_output(.data = to_sum))
 }
 #' Get env on richness
[…]

### 2020-04-01 analysis/02_compute_network_metrics.R

@@ -405,19 +405,24 @@ network_metrics %<>%
 ####################################
 #  Compute weighted trophic level  #
 ####################################
+myload(network_metrics, dir = mypath("data", "classes"))
+myload(op_analysis, dir = mypath("data"))
 
-obs_troph_level <- network_metrics %>%
-  select(opcod, obs_troph_level) %>% 
-  mutate(obs_troph_level = map(obs_troph_level, enframe)) %>%
-  unnest(obs_troph_level) %>%
-  rename(obs_troph_level = value, !!var_chr := name)
+weighted_mean_trophic_lvl <- 
+  compute_weighted_avg_trophic_level(.net = network_metrics)
 
-weighted_mean_trophic_lvl <- network_metrics %>%
-  select(opcod, composition) %>%
-  unnest(composition) %>%
-  left_join(obs_troph_level, by = c("opcod", var_chr)) %>%
-  group_by(opcod) %>%
-  summarise(w_trph_lvl_avg = sum(obs_troph_level * biomass) / sum(biomass))
+weighted_mean_trophic_lvl <- 
+  compute_weighted_avg_trophic_level(
+    .net = network_metrics, bm_var = "bm_std",
+    .op = op_analysis
+  )
+
+if ("w_trph_lvl_avg" %in% names(network_metrics)) {
+
+  network_metrics %<>%
+    select(-w_trph_lvl_avg)
+}
+
 network_metrics %<>%
   left_join(weighted_mean_trophic_lvl, by = "opcod")
 
@@ -468,7 +473,8 @@ network_metrics %>%
   select(opcod, troph_group) %>%
   unnest(troph_group)
 
-mysave(network_metrics, network_analysis, dir = mypath("data", "classes"), overwrite = TRUE)
+mysave(network_metrics, network_analysis,
+  dir = mypath("data", "classes"), overwrite = TRUE)
 
 ################################
 #  Compute motif distribution  #

### 2020-04-01 manuscript/bef_stability/manuscript.Rmd
Update Introduction + Biomass, protocol and variability methods

@@
 ---
-title: Species richness destabilizes trophic communities in freshwater ecosystems
+title:"""
+  Complex mecanisms linking biomass stability and total biomass with
+species richness and network structure in stream ecosystems 
+"""
 author: Alain Danet, Maud Mouchet, Elisa Thébault and Colin Fontaine
@@
 
-##### BEF
+#### Importance of BEF assessment
+
 Determining the shape of the relationship between species diversity and ecosystem
@@
 
-Species richness has been reported to increase productivity in grasslands
-[@grace_integrative_2016], but complex links between between species richness,
-environment, productivity and total biomass showed that species richness
-decrease total biomass [@grace_integrative_2016] contrary to previous
-assessment [@hector_plant_1999, @tilman_biodiversity_2014]. Complementarity
-between species in resource exploitation [@cardinale_species_2002] leading to
-overyielding (CHECK) has been proposed to explain positive relationship between
-productivity and species richness, while species richness effect can also rise
-from the statistical probability to end up with a highly productive species
-. The relationship between species richness and stability is even more complex
+#### Shape of BEF: total biomass
+
+Species richness has been reported to increase productivity
+[@tilman_productivity_1996, @grace_integrative_2016] through complementarity
+between species in resource exploitation and selection effects
+[@loreau_partioning_2001, @cardinale_species_2002, @fargione_from_2007].
+Empirical assessment of the effect of species richness on total biomass showed negative
+[@grace_integrative_2016] and positive relationships [@hector_plant_1999,
+@tilman_biodiversity_2014]. @grace_integrative_2016 showed that the results
+depend on the refinement of the mecanisms involved in the analysis.
+
+#### Shape of BEF: stability
+
+The relationship between species richness and stability is even more complex
 partly because of the inherent multidimensionality of stability
@@
 equilibrium, robustness to primary extinction) and empirical work (variability
-of abundance or biomass through time). @may_will_1972 stimulated a lot of
-debate and fecund research, showing that species richness, probability of
-interacting and average interaction strength destabilizes communities in which
-species interact randomly. Empirically, consistent works showed that species
-richness increased community stability in grasslands
+of abundance or biomass through time). Empirical studies showed consistently
+that species richness decreased community variability in grasslands
 [@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018] and
 vertebrates [@olivier_independent_nodate, @franssen_annual_2011]. Two
-components can explain variation of community stability, (1) individual species
-stability and (2) the species synchrony [@loreau_species_2008, @thibaut_understanding_2013].
+mecanisms are involved into community variability, (1) species
+variability and (2) the species synchrony [@loreau_species_2008, @thibaut_understanding_2013].
 Positive [@tilman_biodiversity_2006], neutral
@@
 [@franssen_annual_2011, @olivier_independent_nodate] relationships between
-species stability and species richness have been found. On the other side,
+species variability and species richness have been found. On the other side,
 studies consistently found that species richness decreased synchrony between
-species [@loreau_species_2008, @thibaut_understanding_2013, @bluthgen_land_2016; @olivier_independent_nodate]. However, as far as we know,
-less studies have reported empirical assessment of stability-richness
-relationship in trophic network [but see @thebault_stability_2010].
-
-Conversely, an extensive literature exists on the effects of network structure
-on stability in mutualistic and trophic networks
-[@angelis_stability_1975, @stouffer_, @thebault_stability_2010, @barbier_pyramids_2019, @shanafelt_david_w._stability_nodate, add ref].
-Particularly, in trophic
-networks, most studies are theoretical and consider asymptotic stability to
-small perturbation. Studies showed that compartimentalization [@stouffer_] can
-increase persistence, while nestedness can either increase
-[@bascompte, @thebault_stability_2010] or decrease persistence
-[@thebault_stability_2010].
-Connectance can decrease [@thebault_stability_2010] or increase
-[@angelis_stability_1975] resilience of trophic network depending on the
-functioning of networks [@angelis_stability_1975].
-
----
-#- Vertical diversity and stability/biomass
-  #- well studied: theoretically and (experimentally, less)
-  #- mecanisms:
-    #- stability: top-down and bottom-up effect
-    #- biomass: top-down and bottom-up effects (pyramids of biomass)
-  #- key papers:[@barbier_pyramids_2019, @shanafelt_david_w._stability_nodate]
-  #- BUT: local stability, little systems 
----
-
-Trophic network are assembled both vertically and horizontally. Studies showed
-that the vertical position in the trophic network as well as the strength of
-top-down and bottom-up regulation determine biomass and stability at
-equilibrium  [@shanafelt_david_w._stability_nodate, @barbier_pyramids_2019].
-However studies on stability-diversity have focused on either vertical
-diversity or horizontal but rarely both. @zhao_horizontal_2019 have shown that
-horizontal and vertical diversity respectively increase and decrease stability
-in plankton communities.
-
----
-#- Big scope assessment:
-  #- inconsistency between theoretical and empirical stability
-    #- theoretical: no cv_sp nor synchrony
-  #- No studies on stability-richness in empirical trophic communities
-    #- no effect of trophic structure
----
-
-A large inconsistency remains between theoretical and empirical assessment of
-stability-diversity in trophic communities. Theoretical studies have
-ignored temporal variability and the relative contribution of synchrony and
-species variability while empirical studies about temporal variability in natural 
-communities have ignored trophic communities and the effect of trophic structure.
-
----
-#- Goal: Assess relation biomass/stability-diversity in empirical trophic communities
-  #- introduce effect of trophic structure and environment
-  #- merge gap between theoretical and empirical studies
----
-
----
-#- What we have done:
-  #- big empirical dataset
-  #- rebuilding empirical network
-  #- assess relationship between environment, community structure and stability
----
-
-Our goal was to assess stability-diversity in natural trophic community with the
-effect of the trophic structure. We combined together the effect of vertical
-and horizontal diversity and thus aimed to bridge the gap between theoretical
-and empirical studies. We used an standardized monitoring of freshwater fish
+species
+[@loreau_species_2008, @thibaut_understanding_2013, @bluthgen_land_2016, @olivier_independent_nodate].
+Beyond species richness, species interactions, which modifies species
+abondance and biomass and make species dynamics interdependant, have been
+largely ignored in empirical assessment.
+
+#### BEF: Theoretical ecology
+
+Conversely, theoretical ecology display an extensive literature about the
+effects of network structure on stability 
+[@may_will_1972, @angelis_stability_1975, @stouffer_compartmentalization_2011, @thebault_stability_2010, @barbier_pyramids_2019, @shanafelt_david_w._stability_nodate].
+Theoretical ecology generally uses stability definitions related to community
+equilibrium and its stability to small perturbations.
+Connectance (i.e. proportion of realized links in a network) can decrease
+[@angelis_stability_1975, @thebault_stability_2010] or increase resilience of
+trophic network depending on the functioning of networks
+[@angelis_stability_1975].
+The number of trophic levels, the vertical position in the trophic network as
+well as the strength of their biomass regulation (i.e. top-down and bottom-up)
+can determine biomass and stability at equilibrium
+[@hurd_stability_1971, @shanafelt_david_w._stability_nodate, @zhao_horizontal_2019, @barbier_pyramids_2019].
+
+A large inconsistency remains between theoretical and empirical assessments of
+the relationship between community structure and ecosystem properties.
+Theoretical studies have ignored temporal variability and then the relative
+contribution of synchrony and species variability on community variability while
+empirical studies about temporal variability and total biomass in natural
+communities have ignored the contribution of network structure.
+
+Our goal was to assess the mecanisms determining temporal variability and total
+biomass in natural communities while integrating both species richness and
+network structure. We combined together the effect of vertical
+and horizontal diversity and thus aimed to bridge the current gap between theoretical
+and empirical studies. We used an standardized monitoring of fish
 communities in french streams. More than three hundreds sites were followed
 more than 10 years on the 1995-2018 period. We inferred four thousands potential
-interaction networks corresponding to each sampling event, based on size
-relationships and knowledge about their ontogenic diet shift.
+interaction networks corresponding to each sampling event, based on trait
+matching.
 
@@
 
-We investigated the effects of the community structure on total biomass and on
-synchrony and species variability, which in turn determine community
-variability. We have also included the effect of environmental drivers which
-can directly affect community variability or indirectly via community structure.
-Finally, we assessed the effect of horizontal diversity on trophic group
-biomass and variability.
+We investigated the effects of the community structure on total biomass and
+community variability, which in turn determine community variability. We have
+also included the effect of environmental drivers [@grace_integrative_2016]
+which can directly affect community variability or indirectly via community
+structure.
 
@@
   #- forcing: environmental forcing on communities 
-  #- can lead to misleading effect: @grace_integrative_2016
+  #- can lead to misleading effect: 
 ---
@@
 
-## Fish data
+## Community variability
 
@@
 
+#### Protocol
+
 Fish communities were monitored across streams of France on the period
@@
 kept only standardized protocols: complete and partial methods for respectively
-little and big streams (detailed in Supplementary methods).  The sampling was
-performed by electric fishing. All the stunned fish species were identified and
-the individuals counted. Fish were classified in batch according to species and
-size class. Depending on the size class, individual fishes were measured or
-only a subsample. The size of individual fishes in subsampled batches were
-inferred under normality distribution assumption (detailed in Supplementary
-material).
+little and big streams (detailed in Supplementary methods). In the complete
+protocol, the sampling takes place over the whole width of the river and is done
+by foot whereas in the partial protocol, the sampling is done over the bank only
+and by boat. The sampling took place either in late spring and/or Autumn.
+Heterogeneity in the sampling time may introduce variability that is not related
+to ecological processes such as the presence of juveniles. In order to reduce
+heterogeneity in sampling time, we select only one sampling per year if there
+was two in a given year. Most of the fish sampling occurred in September
+(Median: mid-August) and within station the median standard deviation of the
+sampling month was inferior to one (0.7). Additionally, we removed sampling
+events, in a given station, which the length of the stream sampled was outside
+the median length sampled more or less 30%. The number of sampling events is
+critical in order to estimate a meaningful variability of the community. We kept
+only station that have been followed ten years or more (i.e 10 sampling events
+or more), which sums to 403 stations.
+
+The sampling itself was performed by electric fishing. All the stunned fish
+species were identified and the individuals counted.
+
+##### Biomass
+
+To characterize communities variability, abundance or biomass are generally
+used. When the body size and therefore body mass vary by several orders of
+magnitude, one downside of abundance is that we mix individual that have
+potentially really different meaning in terms of ecosystem properties such as
+biomass. We therefore estimated the body mass of fish individuals according to
+their body size. During sampling, the fishes were classified in batch according
+to species and size class. Depending on the batches, the body size of all
+individuals were measured or only a subsample. Only the body size big fishes was
+measured individually. The body size of individual fishes in subsampled batches
+was inferred under normality distribution assumption (detailed in Supplementary
+material). The body mass of individual fishes were then estimated with an
+allometric law ($B_i = 0.01 \times l_i^3.03$, $B$ being the body mass in grams,
+$l$ the body size in millimeters and $i$ the individual).
+
+The species and community biomass were then computed for each sampling event.
+As sampling effort varied across protocol type and sampling event, biomass
+was reported to the surface sampled (in $m^{2}$). Community and species biomass
+were then expressed in $gm^{-2}$.
+
+Total biomass was characterized as the median total biomass over time. Community
+stability was defined as the inverse of biomass variability. Variability was
+computed as Coefficient of Variation (CV) of the biomass ($CV_i = \sigma_i \mu_i^{-1}$,
+with $\sigma_i$ and $\mu_i$ being respectively the standard deviation and the
+average of the biomass of the station $i$). Then, biomass stability was equal to
+$CV^{-1} = \mu \sigma^{-1}$.
+
+The CV of community biomass can represent very different dynamics such as
+decreasing, stable or increasing. However, the concept of community variability
+refered to variability around an equilibrium, which is rarely observed or
+difficult to characterize in natural communities. 
+We However used SAX (Symbolic Aggregate Approximation) method to caracterize
+rougly biomass dynamics over time (details in Supplementary information). We
+finally kept only the stations which the biomass had no trends, remaining 99
+stations.
+
+To characterize the mecanisms driving biomass stability, we decomposed
+the community CV in synchrony and weighted average species CV
+components according to @thibaut_understanding_2013:
+
+$$
+CV_{com} = \overline{CV_{sp}} \times \sqrt{\phi}
+$$
+
+with $CV_{com}$ being the Coefficient of Variation of the community,
+$\overline{CV_{sp}}$ the average coefficient of variation of population
+pondered by biomass. $\phi$ is the synchrony, which is the ratio the total
+community variance ($\sigma^2_{x_T}$) and the sum of population variance
+($\sigma_{x_i}$) [@loreau_species_2008]:
+
+$$
+\phi = \frac{\sigma^2_{x_T}}{\sum_i{\sigma_{x_i}}}
+$$
+
+Species richness was computed as the total species richness over time in a given
+station. To normalize by sampling effort, we reported total species richness to
+the sum of surface sampled over the time period, it was expressed in number of
+species by square meter.
 
@@
 #meta$metaweb[meta$resource, meta$resource]
-
 ```
@@
 phytoplankton. Fish-fish trophic interactions were determined by allometric
-relationships as in many studies [@brose_predator_2019, @poisot_structure_2016, @schneider_body_2012].
+relationships as in many studies
+[@brose_predator_2019, @poisot_structure_2016, @schneider_body_2012].
 For a given trophic species, we first determined if its
@@
 ---
-
-The body mass of each fish was approximated from their body size with an
-allometric law ($B = 0.01 \times (l^3.03)$, $B$ being the body mass in grams and $l$ the
-body size in millimeters). We have worked with body mass instead of abundances to avoid to sum
-abundances of fishes that had really different sizes and so body masses. Body
-mass are more meaningful in terms of ecosystem description. The biomass of each
-trophic species (and species) was divided by the surface sampled (measured in
-square meters) during the sampling event. The total biomass in a given
-community are so expressed in $gm^{-2}$.
 
@@
 
-The biomass stability was decomposed in synchrony and weighted average CV
-components according to @thibaut_understanding_2013:
-
-$$
-CV_{com} = \overline{CV_{sp}} \times \sqrt{\phi}
-$$
-
-with $CV_{com}$ being the Coefficient of Variation of the community,
-$\overline{CV_{sp}}$ the average coefficient of variation of population
-pondered by biomass. $\phi$ is the synchrony, which is the ratio the total
-community variance ($\sigma^2_{x_T}$) and the sum of population variance
-($\sigma_{x_i}$) [@loreau_species_2008]:
-
-$$
-\phi = \frac{\sigma^2_{x_T}}{\sum_i{\sigma_{x_i}}}
-$$
-
 #### Causal relationships

### 2020-04-27 manuscript/bef_stability/appendix.Rmd
Update manuscript + appendix

---
title: Appendix of Complex mecanisms linking biomass stability and total biomass with species richness and network structure in stream ecosystems 
author: Alain Danet, Maud Mouchet, Elisa Thebault and Colin Fontaine
date: \today 
output:
  pdf_document:
    fig_caption: true 
    keep_tex: true
fontsize: 12pt
header-includes:
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{float}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
---

```{r, echo = FALSE}
mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.dim = c(7, 7),
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "total_sem_effect.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

theme_set(theme_alain())
```

```{r}
# Load manuscript results
load(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
```

# Sampling protocols

## Fishing

### Protocol

```{r}

```

The fish community sampling took place in a variety of stream size, shape and
depth. This diversity constraints the type of protocol that can take place.
For the small streams (depth < 0.7m across the entire width), the complete protocol
is used. It consists in placing anodes every X meter across the width of the
river. **Add the precise procedure?**
The fishermen made from one to three row of fishing. We kept only the first row
for analysis.
For deeper and wider streams, the sampling was partial over the bank and the
channel and performed by boat and by foot (along the bank). We kept only
sampling done over the bank because channel sampling was not always done.
Two types of partial protocols takes place: partial over bank and partial by
points. The former is continuous while the latter is discrete. Furthermore, in
partial by point protocol the channel can be sampled as well. We kept only the
partial by point fish sampling which all the sampling point were done over the
bank to homogenize the sampling. Then, we merged partial over bank and partial
over point protocols. Some sampling stations had mix characteristics in which mix of
partial and complete protocols were applied depending of the depth of the river
at the time of sampling. Those stations were removed from the analysis.

### Batches definition and body size measurement 
During the electric fishing, and before that fish body size are measured, they
are regrouped by batches. Each batches contains one species but there can be
several batches by species. Body size assessment are different according to the
batches. There are four types of batches: N, I, S/L and G. The batches N and
I contains the biggest individuals, there are normally less numerous and then
the body size of the individuals of those batches is recorded. The batches S/L
contains fishes of intermediate sizes. Inside each S/L batches, the operator
tries to make batches as homogeneous as possible in body size. Then, the body
size of a subsample of X individuals are recorded. The G batches contain
individuals of low body size, with care that body size is as homogenous as
possible in the batches. Then body size of the shortest and the longest
individuals are recorded.

## Body size inference

```{r}
myload(fish_length, lot_id_opcod, dir = mypath("data-raw", "fishing_op_build"))

fish_length %<>%
  left_join(lot_id_opcod) %>%
  rename(length = fish) %>%
  select(opcod, species, length)
length_sem_analysis <- fish_length %>% 
  filter(opcod %in% op_analysis_bbb$opcod)
na_length <- sum(is.na(length_sem_analysis$length))
```

The instructions for body size inference were guided by the recommendations of
the OFB agency, which has defined the sampling protocols, supervised the data
collection and performed analysis for multiple purpose including stream
management.

```{r}
body_size_caption <- paste0(
  "Body size inference of the fishes. ",
  "(1) Sampled fishes were attributed to batch type according to their size and
  the number of individuals. A batch contains one species only. (2) In the batch
  type N and I, the body size of all the individuals was recorded. In the
  batches, S/L, the body size of a subsample of the individuals was recorded.
  Finally, only the body size of the littlest and of the tallest individual was
  recorded. ",
  "Then, (3) we inferred the body size distribution in the S/L and G batches by
  assuming that it followed a normal distribution. The mean and the standard
  deviation were estimated with the measured subsample."
) 
```

```{r p-body-size, fig.cap=body_size_caption}
knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "length_inference.pdf"))
```

With the information contained in the batch record, we inferred the body size of
the fishes in the community. No inference were needed for the N and I batches
because the body size of the individuals were recorded. The body size ($l$) of the
fishes in the S/L and G were inferred under the assumption that its distribution
followed a normal law ($l ~ N(\mu , \sigma)$).
For a S/L batch, the mean $\mu$ and the standard deviation $\sigma$ were simply
the average and the standard deviation of the body size of the subsample
recorded. For a G batch, the average was approximated by 
$\hat{\mu} = (l_{min} + l_{max}) 2^{-1}$ and the standard deviation by
$\hat{\sigma} = (l_{min} + l_{max}) 4^{-1}$. Together with the estimations of
the mean and the standard deviation, the number of individuals in a batch and
assumption of a normal distribution, we simulated the body size distribution in
S/L and G batches. To avoid simulation of unrealistic body size, we used a
truncated normal distribution bounded at [0.05; .95] for the density of
probability of the S/L batches, and bounded at [$l_{min}$; $l_{max}$] for the G
batches. Body size distribution were generated using the R function
`truncdist::rtrunc`.

We removed batches that did not satisfied the following conditions. First, we
removed batches which the total number of individuals was not recorded. In lot
"G", we removed batches were  $l_{min} \geq l_{max}$ or if at least one of the
measurement was missing. Additionally, G batches were removed when number of
individuals fell below five, as G batches normally contained more individuals.
In the S/L lot, we removed batches were the number of individuals in the
recorded individuals fell below 10. In sum, those sanity check allowed to
exclude potentially problematic batches. Finally, in the dataset used in the
analysis, `r na_length` individuals had missing length over 
`r nrow(fish_length)` individuals.

## Community data

```{r}
source(mypath("R", "cleaning_methods.R"))
removed_ind <- filter(length_sem_analysis, species %in% sp_to_remove())
removed_sp <- unique(removed_ind$species)
```

We removed rare fish species, species from lake, crayfish species, and migratory
species. In total, we removed `r nrow(removed_ind)` over 
`r nrow(length_sem_analysis)` individuals and `r length(removed_sp)`.

During fish sampling, some species are identified based on morphotype but they
belong to the same species based on fecundation criteria (CHECK with Eric).
We merged those morphotype species into one species. There was
`r length(unique(names(sp_to_replace())))` to merge which belonged to 
`r length(unique(sp_to_replace()))` species.

## Network inference

```{r}
myload(metaweb_analysis, dir = mypath("data"))
species_in_metaweb <- metaweb_analysis$species

length_sem_analysis %<>%
  filter(!species %in% sp_to_remove()) %>%
  mutate(
    species = str_replace_all(species, sp_to_replace())
  )

removed_ind_metaweb <- length_sem_analysis %>%
  filter(!species %in% species_in_metaweb)
removed_sp_metaweb <- unique(removed_ind_metaweb$species)
```

The metaweb building was based on trait matching, so it necessitates to have
information about their diet. `r length(removed_sp_metaweb)` species were
removed because information about their diet was missing. It represented  
`r nrow(removed_ind_metaweb)` individuals over `r nrow(length_sem_analysis)` 
individuals.

** I question myself if I should move the network inference figure here and
just let the temporal network in the main text. May be even add the temporal
biomass plot (species/trophic species) in the main text**

## Environmental variables

The procedure to obtain altitude, slope, width depth of the streams are fully
explained in main text. Because those measurements were collected during the
fishing protocol, they were easier to manage in the analysis. Then, we detailled
in the following sections how water temperature, flow and BOD were obtained.

### Preparation

Water temperature, flow and BOD (Biogical Oxygen Demand) were obtained from the
[naiades database](http://www.naiades.eaufrance.fr/).
Water temperature, flow and BOD were respectively collected at a hourly, daily
and monthly frequency. Water temperature and flow are recorded by automated
sendors while BOD is collected manually because it necessitates analysis in a
laboratory. BOD data collection is coordinated by the Agence de l'eau which
realized the analysis itself or order it to a company.
It is crucial to make clear that those variables are collected at different
places than the fish samplings.

- Number of station
- Space repartition

```{r}
myload(fourier, dir = mypath("data-raw", "polluants"))
# Where is DBO?
```

For BOD, we removed measurements that were expressed in uncommon units.

The first goal was to harmonize the different variables and scale it to the
timescale of fish sampling, we took annual average of each variables. To reduce 
daily or seasonal effects, we first applied average data with the moving
window of one year. For temperature, the moving was performed on daily average
temperature. Then we took the annual average of each year and each variable.

Several characteristics of the streams make the interpolation more complicated
than along terrestrial surface. Interpolations in terrestrial areas are roughly
based on euclidian distance. Euclidian distance is more complicated to consider
in streams because it had the follow the path of the streams. Futhermore,
two streams can be close by but not connected and the value of their variables
could be not related or a only a few. For those reason, we used stream spatial
network methods to interpolate temperature, flow and BOD.

We reconstructed the stream network and the connection between sites with the
`openSTARS` R package. The reconstruction was done with a raster of digital
elevation model at a resolution of 250 meters [(IGN)](https://wxs.ign.fr/jvam1hsjm11u8voorw81v2xb/telechargement/prepackage/BDALTI-75M_PACK_FXX_2018-01-24%24BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15/file/BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15.7z)
and a theoretical hydrologic network [put a link](test) [@pella_reseau_2012].

The procedure was done by hydrographic basin because of convergence problem
when the interpolation was done at the France scale. We had to make a tradeoff
between the number of data (to keep enough high to perform the interpolation)
and the level of dataset splitting. We then merge some hydrographic basin to end
up with four region of interpolation: West, East, South and North. (XXX ADD 
basins merged)

Then we modeled each variable as dependant only on the covariation between sites
and taking in account stream network. To model the autocovariance between sites,
we used the linear-sill and mariah functions for taildown and tailup
autocovariance, according to their performance of prediction. The interpolations
were done with the `SSN` R package 
[@isaak_applications_2014, @hoef_ssn_2014].

### Performance and post check

```{r eval = FALSE}
myload(cv_press_interp_mv_avg,
  dir = mypath("data-raw", "polluants"))
myload(cv_temp_press_interp_mv_avg,
  dir = mypath("data-raw", "naiades_temperatures"))
myload(cv_flow_press_interp_mv_avg,
  dir = mypath("data-raw", "flow"))
dbo_cv <- cv_press_interp_mv_avg %>%
  filter(parameter == "dbo5")

cv_dbo_temp_flow <- map2_dfr(
  list(dbo = dbo_cv, temp = cv_temp_press_interp_mv_avg, flow = cv_flow_press_interp_mv_avg),
  c("BOD", "Temperature", "Flow"),
  function(x, y) {
    x %>%
      group_by(basin, year) %>%
      summarise_if(is.numeric, list(avg = ~mean(., na.rm = TRUE))) %>%
      mutate(Variable = y) %>%
      select(Variable, basin, year, everything()) %>%
      ungroup
  })

cv_dbo_temp_flow %>%
  mutate_if(is.double, ~signif(., 2)) %>%
  kable(
    align = "c",
    format = "latex",
    booktabs = T,
    caption = paste0("Results of the cross-validation for the interpolation of
      BOD, temperature and flow. Average over 4 interpolations are shown.") 
      ) %>%
    collapse_rows(columns = c(1, 2), valign = "top") %>%
    kable_styling(latex_options =c("striped", "scale_down"))
```

```{r}
cv_bias_caption <- paste0(
  "Bias of the interpolation from Leave-One-Out Cross Validation (LOOCV). "
)
```

```{r cv-biais, fig.cap = cv_bias_caption}
cv_dbo_temp_flow %>%
  rename(Bias = bias_avg) %>%
  ggplot(aes(x = Bias)) +
  geom_histogram() +
  facet_wrap(~Variable, scales = "free_x")
```

The performance of the interpolation was evaluated with leave one out
cross-validation (already implemented in the SSN package). The value of the
interpolated variable of each station was predicted after removing it from the
dataset. ADD SUMMARIES ABOUT CV.

With the model, we then simply predicted variable values at the location of the
fish stations.

When predicted values were below the minimum value or above the maximum value
recorded in the dataset for flow, (temperature?) and BOD, we replaced the
predicted value by respectively the minimum and the maximum value found in the
dataset. We ran the interpolation four times and we kept the predicted value
which had the least standard deviation.

# Analysis

## Time series classication

The CV of biomass over can cover multiple dynamics, including increases,
stable, decreases and a mix of them. Theoretically, however, the CV computed to
quantify stability is often represented with the assumption that the overall
dynamic of the biomass varies around an equilibrium. In order to approach this
condition, we kept only the stations that have met this criteria. To qualify the
biomass trajectories over time, we used the symbolic aggregated approximation
method (SAX) which is commonly used in time series analysis and implemented in
the `jmotif` R package. This method classifies time series rather than
quantifies trends and so is generic enough to encompass the diversity of time
series shapes. The classification necessitates three steps. First, the time
series are normalized (i.e. substracting the mean and divide by the standard
deviation). The second step is to reduce the dimensionality of the time series
by Piecewise Aggregation Approximation (PAA) method. Each time series is divived
in $N$ frames of equal size that allows to the reduce the dimensionality of the
time series. For each frame, we simply kept the mean value of the time series.
The last step is to qualify each frame into string. Because values of
normalized time series typically follows a normal distribution ($N(0,1)$), a
breakpoints can be computed by dividing the area under the normal distribution
in equal parts. The algoritm attributes a alphabetic letter to each part from
the lowest to the highest ($a$, $b$, $c$, ...). We set three breakpoints, so
$a$, $b$ and $c$. Finally, the trajectory of each time series is classified as
a combination of $a$, $b$, $c$ letters. $abc$ and $cba$ time series represent
respectively monoton increasing and decreasing trajectories. For data analysis,
we kept only the $bbb$ which represent time series that showed no temporal
tendancies (with respect to our methodology).

## PCA of environmental variables

```{r, fig.show = "hide"}
axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
p_l_rot <- map(axis_pair, 
  function (axis)
    pca_rotated_plot <- plot_rotated_pca(
      pca_rotated = pca_rotated,
      axis = axis 
    )
)
```

```{r}
prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
  map_dbl(., ~round(.x * 100))

tot_var_expl_pca <- round(sum(pca_rotated$rotated$Vaccounted["Proportion Var", ]) * 100)

pca_caption <- paste0(
  "Rotated axis of PCA on environmental variables. The five components
  explained,", tot_var_expl_pca, "% of the variance (",
  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
  "(A) Axis 1 was positively related to the river size, axis 2 was related to
  average temperature and negatively related to the river slope and altitude.
  (B) Axis 3 was negatively related to the CV of flow and average enrichment.
  Axis 4 was related to the CV of river size. Finally, axis 5 was related to the
  CV of enrichment.")
```

```{r pca-rotated, fig.cap = pca_caption}
to_plot <- c(1, 6, 7)
plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
  ncol = length(to_plot), labels = LETTERS[1:3])
```

```{r}
print_prop_var_pca <- prop_var_expl_pca[order(names(prop_var_expl_pca))]
```

The five axis of the rotated PCA explained respectively
`r paste0(prop_var_expl_pca, "%", collapse = ", ")` of the variance.
Please see the main text for the interpretation of the axis.

## Model summary and diagnostics

####  SEM indirect and total effect

```{r}
caption_indir_stab_sem <- paste0(
  "Indirect and total effect of variables on biomass stability from the
  structural equation model. Indirect effects are computed by multiplying the
  path coefficients from the variable predictor to the response variable, here
  biomass stability. Indirect effects are considered as one step from the target
  variable. For exemple, the indirect effect of species richness on
  biomass stability via its effect on CVsp is $-0.61$. To compute indirect
  effect, only the significant direct effects were taken into account. ",
  "Network structure being the indirect effect that went through both avg trophic
  level and connectance and Species richness_Network structure being the
  indirect effect that went through (i) species richness and from (ii) species
  richness to network structure."

)

caption_indir_bm_sem <- paste0(
  "Indirect and total effect of variables on total biomass from the
  structural equation model. See the table (X) for details about computation and
  meaning."

)
```

```{r indir-tab, fig.cap = "Indirect effect from SEM"}
format_table <- function (x = tmp_stab_indir_table) {
  x <- x[, c("variable", names(x)[!names(x) %in% "variable"])]

  rm_n <- str_remove_all(get_sem_var_name_replacement(), pattern = "\n")
  names(rm_n) <- names(get_sem_var_name_replacement()) 
  x$variable <- str_replace_all(x$variable, rm_n)

  colnames(x) %<>% str_remove_all(., pattern = "via_")

  col_replacement <- c(
    variable = "Variable",
    cv_sp = "CVsp",
    sync = "Synchrony",
    richness = "Species richness",
    com = "Network structure",
    richness_com = "Sp. richness and network str.",
    total = "Total effect"
  )
  colnames(x) %<>% str_replace_all(., col_replacement)

  x
}

kable(format_table(tmp_stab_indir_table),
  "latex",
  booktabs = T,
  caption = caption_indir_stab_sem 
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))

```

```{r}

kable(format_table(tmp_bm_indir_table),
  "latex",
  booktabs = T,
  caption = caption_indir_bm_sem
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))
```

### Model linear Relationship

```{r}
hist_var_caption <- paste0(
  "Distribution of the variables used in the Structural Equation Modeling."
)
```

```{r hist-sem-data, fig.cap = hist_var_caption}
sem_data %>%
  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, log_RC3, RC4,
    RC5, t_lvl, ct, log_bm) %>%
  gather(variable, value) %>%
  mutate(variable = str_replace_all(variable, get_sem_var_name_replacement())) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~variable, scales = "free")
```

### Colinearity tables

```{r s-colin-sem, fig.cap = "Variance Inflation factor for each individual model of stability sem"}

mod_stab_list <-
  list(
    nlme::lme(log_rich_tot_std ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
    nlme::lme(ct ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
    nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
    nlme::lme(log_sync ~ log_rich_tot_std + ct + t_lvl + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,
      random = ~ 1 | basin, data = sem_data),
    nlme::lme(log_cv_sp ~ log_rich_tot_std  + ct + t_lvl
      + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data),
    lm(log_stab_std ~ log_cv_sp + log_sync, data = sem_data),
    nlme::lme(log_bm_std ~ log_rich_tot_std  + ct + t_lvl
      + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data)
  )
names(mod_stab_list) <- c(
  "Species richness",
  "Connectance",
  "Avg trophic level",
  "Synchrony",
  "CVsp",
  "Biomass stability",
  "Total biomass"
)

colin_stab_sem <- map(mod_stab_list, car::vif)

tmp <- map(colin_stab_sem, enframe)

# colinearity table
colin_stab_sem <- tibble(vif = tmp, mod = names(mod_stab_list)) %>%
  unnest(vif) %>%
  mutate(
    value = round(value, 1),
    name = str_replace_all(name, get_sem_var_name_replacement())
    ) %>%
  spread(name, value)

kable(colin_stab_sem,
  format = "latex",
  booktabs = T,
  caption = caption_indir_bm_sem
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

```{r}
caption_mod_res <- paste0(
  "Residuals versus fitted values of the linear models used in the structural
  equation modelings."
) 
```

```{r mod-res, fig.cap = caption_mod_res}
library(nlme)
plot_residuals <- function (x, y = "Diagnostic") {
  plot.lme(x, main = y, xlab = "Fitted values", ylab = "Residuals")
}
p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
plot_grid(plotlist = p_resid_stab_sem)
```

### Biomass and stability models

```{r}
format_coef_table <- function (sem = NULL) {

  params <- sem$coefficients
  colnames(params)[length(colnames(params))] <- "Stars"

  replace_wo_n <- str_replace_all(get_sem_var_name_replacement(), "\n", "")
  names(replace_wo_n) <- names(get_sem_var_name_replacement())

  params %<>%
    mutate_at(c("Response", "Predictor"),
      ~str_replace_all(., replace_wo_n))

  params
}

```

```{r}
est_stab_sem_caption <- paste0(
  "Estimate of the effects for the biomass stability structural equation
  modeling."

)

kable(format_coef_table(stab_sem_rich),
  format = "latex",
  booktabs = T,
  caption = est_stab_sem_caption
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

```{r}

est_bm_sem_caption <- paste0(
  "Estimate of the effects for the total biomass structural equation
  modeling."
)

kable(format_coef_table(bm_sem_rich),
  format = "latex",
  booktabs = T,
  caption = est_bm_sem_caption
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

```{r rsq-model}
rm_n <- str_remove_all(get_sem_var_name_replacement(), pattern = "\n")
names(rm_n) <- names(get_sem_var_name_replacement()) 
rsq_table <- map_dfr(mod_stab_list, piecewiseSEM::rsquared, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2)) %>%
  mutate(Response = str_replace_all(Response, rm_n)) %>%
  dplyr::select(Response, Marginal, Conditional, R.squared)
rsq_table_caption <- paste0(
  "R squared of the linear models used in the structural equation modeling."
)
kable(format_coef_table(bm_sem_rich),
  format = "latex",
  booktabs = T,
  caption = est_bm_sem_caption
  ) %>%
kable_styling(latex_options = c("striped"))
```

```{r tab-coeff-bm, fig.cap = "Coefficient"}

# Replacement rules for term
rp_est <- c(
  "(Intercept)" =     "intercept",
  "sd\\_\\(intercept\\)\\.basin" = "sd intercept basin",
  "log_rich" =     "Median richness (log base 10)",
  "troph_group3" =     "high trophic group",
  "log_rich:troph_group3" =     "Median richness (log10) : high trophic group",
  "sig01.basin" =     "sd intercept basin",
  "sd_Observation.Residual" =     "residuals",
  "sigma" = "residuals"
)
# Replacement rules for group
rp_group <- c(
  "fixed" = "Fixed",
  "basin" = "Random"
)

```

```{r}
mask_drop_lm <- names(mod_stab_list) %in% "Biomass stability"
random_coeff_sem <- map(mod_stab_list[!mask_drop_lm], random.effects)

format_random <- function (x, y) {
  tibble(
    Variable = y, 
    `Hydrographic basin` = rownames(x),
    Intercept = x[[1]]
  )
}
formated_random_effects <- do.call(rbind, map2(random_coeff_sem, names(random_coeff_sem), format_random))

caption_random_effect <- paste0(
  "Estimated random effect of hydrographic basin on the intercept of the linear
  models performed in structural equation modeling."

)

kable(formated_random_effects,
  format = "latex",
  booktabs = T,
  caption = caption_random_effect
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

```{r}
knitr::opts_chunk$set(eval = FALSE)
```

```{r}
coeff_troph <- map2_dfr(list(bm_troph_ci, stab_troph_ci), list(bm_troph_mod, stab_troph_mod),
  clean_summary_mod, term_rp = rp_est, group_rp = rp_group)

kable(coeff_troph) %>%
  pack_rows("Biomass", 1, 6) %>%
  pack_rows("Stab", 7, 12)
```

## Relationship at the absolute scale, i.e. not the logarythme scale

```{r}
ggplot(sem_data, aes(x = richness_med, y = biomass_stab)) +
  geom_point()
test <- tibble(
  richness_med = seq(1,20, length.out = 100),
  biomass_stab =
    10^(fixef(stab_div_mod)[1])*richness_med^fixef(stab_div_mod)[2]
)  
```

```{r save-plot, eval = FALSE}

save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div.pdf",
  p_stab_div,
  base_height = 3,
  bg = "transparent",
  ncol = 1)

save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div_troph.pdf",
  p_stab_div_troph + theme(legend.position = "bottom"),
  base_height = 3,
  bg = "transparent",
  ncol = 1)

```

### Ecological modeling fun

```{r, eval = FALSE}
mod_tlvl <- nlme::lme(t_lvl ~ scale(RC1) + scale(RC2) + scale(RC3) + scale(RC4) + scale(RC5) + log_rich_tot, random = ~ 1 | basin, data = sem_data)
plot(mod_tlvl)
sem_data %>%
  ggplot(aes(x = log10(richness_tot), y = t_lvl)) +
  geom_point()+
  geom_smooth(method = "lm")
plot(x = log10(sem_data$RC1 + abs(min(sem_data$RC1))), y = sem_data$t_lvl)
sem_data %>%
  ggplot(aes(x = log10(RC1), y = t_lvl)) +
  geom_point()+
  geom_smooth(method = "lm")
plot(nlme::lme(t_lvl ~ I(log10(RC1 + abs(min(RC1)))) + log_rich_tot, random = ~ 1 | basin, data = sem_data))
nlme::lme(t_lvl ~ log_rich_tot, random = ~ 1 | basin, data = sem_data)
semd_test <- sem_data %>%
  mutate(RC1b = RC1 + abs(min(RC1)))
ricker.mixed.fit <- nls(
  t_lvl ~ (Vm*(RC1 + b) / (K + (RC1 + b)) + d),
 #fixed = Vm + K + b + d ~ 1,
 #random = Vm + K + b + d ~ 1|basin,
 start= c(Vm=1, K = 0.1, b = .5, d = 2.5),
 data = semd_test,
 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8) 
)
summary(ricker.mixed.fit)
x <- seq(min(sem_data$RC1), max(sem_data$RC1), length.out = 100)
sem_data$test_pred <- predict(ricker.mixed.fit)

semd_test %>%
  ggplot(aes(x = RC1b, y = t_lvl)) +
  geom_point() +
  geom_line(aes(y = test_pred))
  geom_smooth(method = "lm")
cor(semd_test$piel, semd_test$t_lvl, method = c("spearman"))
```

```{r, eval = FALSE}
library(glmmTMB)
# Gaussian
mod_log_rich <- glmmTMB(
  log_rich_tot ~ log_RC1 + log_RC2 + log_RC3
  + RC4 + RC5 + (1 | basin), family = gaussian, data = sem_data)
summary(mod_log_rich)
plot(y = resid(mod_log_rich), x = fitted(mod_log_rich))

# Poisson 
mod_log_rich_poi <- glmmTMB(
  richness_tot ~ log_RC1 + log_RC2 + log_RC3
  + RC4 + RC5 + (1 | basin), family = poisson, data = sem_data)
summary(mod_log_rich_poi)
plot(y = resid(mod_log_rich_poi), x = fitted(mod_log_rich_poi))

# Truncate 
mod_log_rich_nbinom <- glmmTMB(
  richness_tot ~ log_RC1 + log_RC2 + log_RC3
  + RC4 + RC5 + (1 | basin), family = nbinom1, data = sem_data)
summary(mod_log_rich_nbinom)
plot(y = resid(mod_log_rich_nbinom), x = fitted(mod_log_rich_nbinom))
```

### 2020-04-27 manuscript/bef_stability/manuscript.Rmd
Update manuscript + appendix

@@
 ---
-title:"""
-  Complex mecanisms linking biomass stability and total biomass with
-species richness and network structure in stream ecosystems 
-"""
-author: Alain Danet, Maud Mouchet, Elisa Thébault and Colin Fontaine
+title: Complex mecanisms linking biomass stability and total biomass with species richness and network structure in stream ecosystems 
+author: Alain Danet, Maud Mouchet, Elisa Thebault and Colin Fontaine
 date: \today 
 output:
-  pdf_document:
+  bookdown::pdf_document2:
     fig_caption: true 
@@
   fig.dim = c(7, 7),
+  fig.fullwidth = TRUE,
   fig.show = "hold",
@@
 between species in resource exploitation and selection effects
-[@loreau_partioning_2001, @cardinale_species_2002, @fargione_from_2007].
+[@loreau_partitioning_2001, @cardinale_species_2002, @fargione_selection_2007].
 Empirical assessment of the effect of species richness on total biomass showed negative
-[@grace_integrative_2016] and positive relationships [@hector_plant_1999,
-@tilman_biodiversity_2014]. @grace_integrative_2016 showed that the results
-depend on the refinement of the mecanisms involved in the analysis.
+[@grace_integrative_2016] and positive relationships
+[@hector_plant_1999, @tilman_biodiversity_2014]. @grace_integrative_2016 showed
+that the results depend on the refinement of the mecanisms involved in the
+analysis.
 
@@
 
----
-#- Research questions:
-  #- What are the effects of the community structure on total biomass and stability ? 
-    #1. What are the effects of species richness on total biomass and stability ?
-      #- effect of species richness
-      #- effect of trophic group
-    #2. What are the effects of the community structure on total biomass and stability ?
-      #- What is the relative effect of the environment relative to the community
-	#structure ?
-      #- What is the effect of the community structure on the different
-	#parts of the stability + total biomass?
-	#- Effect of horizontal and vertical diversity
----
-
 We investigated the effects of the community structure on total biomass and
@@
 
----
-#- Environment can drive stability and biomass:
-  #- forcing: environmental forcing on communities 
-  #- can lead to misleading effect: 
----
-
 # Methods
 
+```{r}
+matmet_cap <- paste0(
+  "Mat&met figure"
+)
+```
+
+```{r matmet, fig.cap = matmet_cap}
+myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))
+p_st <- p_st +
+  theme(legend.position = "none")
+# Network inference
+net_method_path <- mypath("manuscript/bef_stability/figs",
+  "network_inference.pdf")
+net_method <- net_method_path %>%
+  magick::image_read()
+p_net_method <- cowplot::ggdraw() +
+  cowplot::draw_image(net_method)
+
+top <- plot_grid(p_st, p_net_method, ncol = 2, rel_widths = c(.8, 1), labels =
+  "AUTO")
+p_method <- plot_grid(top, temporal_network, nrow = 2, rel_heights = c(1, .3),
+  labels = c("", "C"))
+p_method
+```
+
 ## Community variability
-
----
-#- OFB
-  #- French long term protocol
-  #- standardized
-#- Electric fishing:
-  #- stuned fish
-  #- identification of the fishes
-  #- fish counted  
-  #- length of the fishes in mm by lot (4):
-    #- I: big fishes measured individually
-    #- S/L: fishes are grouped by species and by size 
-      #- 30 random fishes were measured in each lot
-      #- simulate the size of all the fishes of the lot:
-	#- normal distribution truncated at 95% (?)
-	#- mean and sd calculted from the sample of the lot 
-    #- G: little fishes are grouped by species
-      #- min and max size by lot 
-      #- simulate the size of all the fishes of the lot:
-	#- normal distribution truncated at 95% (?)
-	#- mean computed as ???  
-	#- se computed as ??? 
-    #- N:
-#- Protocols type:
-  #- complete
-    #- shallow river
-  #- partial:
-    #- deep and large river
-    #- partial over bank
-    #- partial by point
-    #- fusion of the two Protocols when "by point" all the point were done
-      #over bank
----
 
@@
 Species richness was computed as the total species richness over time in a given
-station. To normalize by sampling effort, we reported total species richness to
+station. To normalize by sampling effort, we reported species richness to
 the sum of surface sampled over the time period, it was expressed in number of
@@
 
----
-#- Diet data: 
-  #- 7? species over 57 had a piscivorous stage
-  #- 3? species had a strict piscivorous stage
-  #- ontogenic diet shift based on size
-#- 7 Resource nodes:
-  #- based on diet database
-  #- no information about their biomass
-#- Size class:
-  #- quantile: 9 size class per species
----
-
----
-#- Interaction:
-  #- Fish-resources and resources: based on diet data 
-  #- Fish-fish:
-    #1. diet data: is piscivorous?
-    #2. allometric relationship: predation range from .03 to .45 of body size
----
-
-Network inference was performed in two steps: determine trophic species,  build
-a metaweb, subtract the metaweb according to the trophic species present in
-community. Diet information were obtained from database and literature. Over
-the 57 fish species, only seven had a piscivorous life stage and only three had
-as strict piscivorous life stage. Fish species were largely omnivorous. Because
-species have ontogenic diet shift, we created nine size classes by species, one
-size class of one species constituting one trophic species. The bounds between
-size classes were equidistant (percentile method). The metaweb described the
-potential trophic interactions between the $`r 57*9`$ ($57\times9$) trophic species. 
-We had seven resource nodes which were present in the diet of the trophic
-species namely detritus, biofilm, phytoplankton, zooplankton, macrophages,
-phytobenthos and zoobenthos. A trophic species belonged to a life stage if the
-median of its size range fell in the range of the life stage. In turn, this
-trophic species has feeding interactions with the resource nodes of its life stage.
-Interactions between resource nodes are determined by literature. For example,
-phytobenthos fed on detritus, while zooplankton fed on zooplankton and
-phytoplankton. Fish-fish trophic interactions were determined by allometric
-relationships as in many studies
+To obtain the network structure of the communities, we needed to infer
+ecological interactions between the components of the communities and thus build
+the ecological network. As the interactions were not measured, we used trait
+matching method to infer the presence or absence of an interaction. This method is
+widely used to infer trophic interactions
+[@brose_predator_2019, @poisot_structure_2016, @schneider_body_2012]. Indeed,
+the existence of an trophic interaction between two species have been reported
+to be largely dependant on their body size ratio [cascade model, @cohen_stochastic_1985, @warren_invertebrate_1987, @brose_predator_2019].
+
+Additionally to body size, we used food diet data to infer trophic
+interactions. The diet of stream fishes, as many organisms, shifts over lifespan.
+For example, alvins feeds on plankton while adults may feed on algae or fishes.
+As we got body size of each fish individuals (cf Biomass inference methods and
+supplementary material), we are able to define trophic interactions beyond
+species level. We thus divided each fish species into nine body size classes,
+each class having the same body size range (percentile method). Each body size
+class constituting a trophic species. We then infered trophic interactions
+between the trophic species. At this stage, it is important to make clear that
+we infered potential trophic interactions and not actual measured interactions.
+We determined network structure in two steps: (1) build a metaweb decribing the
+trophic interactions between all the possible trophic species, then (2)
+determine network of a given community by subtracting the metaweb according to
+the trophic species present in a given community.
+
+### Metaweb
+
+#### Ontogenic diet
+
+Diet information were obtained from database and literature [REF edeline?]. The
+diet information contained from two to three life stages by species, the life
+stages being defined by the body size of the fishes. Over the 57 fish species,
+only seven had a piscivorous life stage and only three had as strict piscivorous
+life stage. Fish species were largely omnivorous.
+
+#### Define trophic interactions
+
+The metaweb described the potential trophic interactions between the $`r 57*9`$
+($57\times9$) trophic species. We had seven resource nodes which were present
+in the diet of the trophic species namely detritus, biofilm, phytoplankton,
+zooplankton, macrophages, phytobenthos and zoobenthos.
+
+A trophic species belonged to a life stage if the median of its body size range
+fell in the range of the life stage. In turn, this trophic species has feeding
+interactions with the resource nodes of its life stage. Interactions between
+resource nodes were determined by literature. For example, phytobenthos fed on
+detritus, while zooplankton fed on zooplankton and phytoplankton. Fish-fish
+trophic interactions between a predator and a prey were determined by body size
+ratio as in many studies
 [@brose_predator_2019, @poisot_structure_2016, @schneider_body_2012].
-For a given trophic species, we first determined if its
-size class end up in a life stage containing piscivorous diet. If it did, we
-determined the prey size range of the trophic species from 3% to 45% of the
-median of its size range. A feeding interaction was set for each trophic species
-whose median of its size class fell into the prey range of the predator trophic
-species. To sum up, the metaweb was obtained with allometric feeding
-interactions (1) between trophic species, (2) between trophic species and
-resource nodes and (3) between resource nodes.
-
-The local networks (i.e. one network for each fish community sampling) was
-obtained by determining the trophic species of each fish individual in the
-community and interactions were set according to the metaweb. All the resource
-nodes were assumed to be present in each local network. Finally, the
-structure of the local networks varied according the presence of the trophic
-species. The inferred interactions represent potential interactions (i.e.
-not measured interactions) and are binary (i.e. presence or absence of feeding
-interactions).
-
-We computed the connectance ($C = L/N^2$, L and N being resp. the number of
-links and of nodes) and the average trophic level of each network, the average
-trophic level was weighted the biomass of each node (excluding resource nodes
-for which we had no biomass) ($\overline{T} = \sum_i^N{B_iT_i \times
-\sum_i^N{B_i}^{-1}}$, $T_i$ and $B_i$ being resp. the trophic level and the
-biomass of the node $i$). In order to have connectance at the species level
-(i.e. not a trophic species level), we merge the trophic species of the network
-by species and thereby aggregating the link by species.
-
-## Community
-
----
-#- Biomass:
-  #- infered by allometric law 
-  #- approximated by $B = 0.01 \times (l^3.03)$
----
+For a given trophic species, we first determined if its size class end up in a
+life stage containing piscivorous diet, i.e. if there was an overlap between
+them. We were more liberal for piscivory determination to not miss potential
+fish-fish trophic interactions which were the main interactions in our
+community. If the trophic species was piscivorous, we determined its prey size range
+from 3% to 45% of the median of its size range. A trophic interaction was set
+for each trophic species whose median of its size class fell into the prey range
+of the predator trophic species. To sum up, the metaweb was obtained with
+allometric feeding interactions (1) between trophic species, (2) between trophic
+species and resource nodes and (3) between resource nodes.
+
+#### Obtain network of a community
+
+The trophic network of a community (i.e. one network for each fish community
+sampling) was obtained by determining the trophic species of each fish
+individual in the community and interactions were set according to the metaweb.
+All the resource nodes were assumed to be present in each local network.
+Finally, the structure of the local networks varied according the presence of
+the trophic species. The inferred interactions represent potential interactions
+(i.e.  not measured interactions) and are binary (i.e. presence or absence of
+feeding interactions).
+
+#### Network structure
+
+In each network, we computed two network metrics that have been commonly used to
+characterize network structure. Connectance which describes the number of
+interactions compared to the number of possible links,
+ computed as ($C = L / N^2$, L and N being resp. the number of
+links and of nodes). We then computed the average trophic level, the
+average trophic level was weighted by the biomass of each trophic species
+(excluding resource nodes for which we had no biomass) ($\overline{T} =
+\sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, $T_i$ and $B_i$ being resp. the
+trophic level and the biomass of the node $i$).
+
+To sum up, we infered binary trophic networks at the scale of trophic species
+(i.e. body size classes by species) to take in account ontogenic diet shifts and
+that fish-fish trophic interaction depends on body size ratio. On the other
+side, the community metrics were defined at the species level, (i.e. species
+richness, average species CV and synchrony).
 
@@
 # Compute stability, network metrics, etc with ;he new datasets
-#debug(summarise_network_over_time)
 ##myload(network_metrics, dir = mypath("data", "classes"))
@@
 
+```
+
+```{r, eval = FALSE}
 stab_div_troph <- com_data$tps_bm_troph %>%
@@
 
----
-#- Collected during fishing operation:
-  #- River size (width and depth)
-  #- Altitude and slope
-  #- distance to source
-#- Independant dataset from naiades: 
-  #- flow, temperature, DBO
-    #1. moving window average
-    #2. annual average 
-    #3. interpolation along rivers (OpenStars + SSN package)
----
-
-Habitat description were obtained from fish sampling data. We kept variables
-describing the ecosystem size namely the stream width and depth, the ecosystem
-position (altitude and slope). Physico-chemical variables were obtained from
-naiades (http://www.naiades.eaufrance.fr/)[http://www.naiades.eaufrance.fr/].
-We chose flow and temperature as physical variables to describe streams as flow
-impose swimming constraints which filter fish species that can establish [REF].
-Water temperature is linked to physiological constraints namely thermal
-tolerance and oxygen concentration tolerance [REF] since the level of water
-saturation in oxygen is inversely linked to water temperature. We chose
-Biochemical Oxygen Demand (BOD) for a proxy of enrichment in the ecosystem [REF
-mccann]. BOD is also inversely linked to oxygen concentration in water.
-The time resolution was heterogeneous according to the variable considered
-(hourly, daily and monthly for temperature, flow and BOD). For each recording
-station, we applied a moving window averaging (more details in supplementary
-material) to get rid of seasonal effects and took the annual mean (i.e. one
-value by year and by station. As the environmental recording stations were not
-located at the same place than the fish stations, we interpolated data with
-spatial statistical network model [@isaak_applications_2014] implemented in the 
-`SSN` R package [@hoef_ssn:_2014]. The interpolation procedure is detailed
-in supplementary material. For each fish station, environmental variables were
-matched with the year of fish sampling (except for water temperature for which the 
-record began in 2006). Then, the average temperature, flow, BDO, river width
-and depth were computed as well as coefficient of variation ($CV = \sigma
-\mu^{-1}$). As habitat and environmental variables are often colinear,
-a principal component analysis (PCA) was performed on the scaled variables. The
-PCA explained % of the variance. An axis rotation was performed to maximize the
-representation of the variables by the principal components
-(Fig. \@ref{fig:pca-rotated}). We kept five axis, representing respectively the
-(1) river size (river width & depth), (2) the altitude, slope and decreasing
-average temperature, (3) average enrichment (BDO) and CV of flow, (4) river
-size CV (CV of river width and depth) and (5) CV of enrichment (CV of BDO).
-Additionally, we logged the axis one, two and three to normalize their
-distribution and we reversed the third axis to get increasing average
-temperature with increasing values of the axis.
-
 ```{r}
@@
 )
-```
+
+prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
+  map_dbl(., ~round(.x * 100))
+
+tot_var_expl_pca <- round(sum(pca_rotated$rotated$Vaccounted["Proportion Var", ]) * 100) 
+```
+
+Habitat description were obtained from fish sampling data. We kept variables
+describing the ecosystem size namely the stream width, depth and the ecosystem
+position (altitude and slope). Physico-chemical variables were obtained from
+naiades web portal [http://www.naiades.eaufrance.fr/](http://www.naiades.eaufrance.fr/).
+We chose flow and temperature as physical variables to describe streams as flow
+impose swimming constraints which filters fish species that can establish
+[@rolls_scaling_2018, @tonkin_flow_2018, @gutierrez-canovas_contrasting_2013].
+Water temperature is linked to physiological constraints namely thermal
+tolerance and oxygen concentration tolerance [REF] since the level of water
+saturation in oxygen is inversely linked to water temperature. We took 
+Biochemical Oxygen Demand (BOD) for a proxy of enrichment in the ecosystem [REF].
+BOD is also inversely linked to oxygen concentration in water.
+The time resolution was heterogeneous according to the variable considered
+(hourly, daily and monthly for temperature, flow and BOD resp.). For each recording
+station, we applied a moving window averaging (more details in supplementary
+material) to get rid of seasonal effects and took the annual mean (i.e. one
+value by year and by station. As the environmental recording stations were not
+located at the same place than the fish stations, we interpolated environmental
+data with spatial statistical network model [@isaak_applications_2014]
+implemented in the `SSN` R package [@hoef_ssn:_2014]. The interpolation
+procedure is detailed in supplementary material. For each fish station,
+environmental variables were matched with the year of fish sampling (except for
+water temperature for which the record began in 2006). Then, the average
+temperature, flow, BOD, river width and depth were computed as well as
+coefficient of variation ($CV = \sigma \mu^{-1}$). As habitat and environmental
+variables are often colinear, a principal component analysis (PCA) was performed
+on the scaled variables. The PCA explained `r tot_var_expl_pca`% of the
+variance. An axis rotation was performed to maximize the representation of the
+variables by the principal components (Fig. \@ref(fig:pca-rotated)). We kept
+five axis, representing respectively the (1) river size (river width & depth),
+(2) the altitude, slope and decreasing average temperature, (3) average
+enrichment (BOD) and CV of flow, (4) river size CV (CV of river width and depth)
+and (5) CV of enrichment (CV of BOD). Additionally, we logged the axis one, two
+and three to normalize their distribution and we reversed the third axis to get
+increasing average temperature with increasing values of the axis.
 
 ## Statistical analysis
-
-### Relationship between stability and species richness
-
-$$\begin{aligned}
-\log_{10}S_i &= \beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}\\
-S_i &= 10^{\beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}}\\
-S_i &= 10^{\beta_0} \times 10^{\beta_R\log_{10}x_{Ri}} \times10^{\epsilon_{ij}}\\
-S_i &= 10^{\beta_{0}} \times x_{Ri}10^{\beta_{R}} \times 10^{\epsilon_{ij}}
-\end{aligned}$$
-
-with $i$ being the station $i$.
 
@@
 
-```{r mod-div-total}
+```{r mod-div-total, eval = FALSE}
 stab_div_mod <- lmer(
@@
 
-```{r mod-div-troph, fig.show = "hide"}
+```{r mod-div-troph, fig.show = "hide", eval = FALSE}
 stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
@@
 ```
-```{r stab-div-troph}
+```{r stab-div-troph, eval = FALSE}
 stab_div_by_troph <- compute_stat_troph_rich(
@@
 troph_perm_test$stab$p_val
-
 ```
@@
 
-We computed Structural Equation Modeling (SEM) to unravel mechanisms underlying link
-between environment, community structure and both biomass stability and total
-biomass. Why SEM?
-
-SEM enables to reason in terms of causal relationship between components. We
-aimed to understand the mechanisms behind the negative relationship biomass
-stability and species richness and the positive relationship between total
-biomass and species richness.
-
-We built a metamodel to set up the nodes and the links between the different
-compartment of the SEM. Basically, we tested the links between environmental
-conditions, community structure and stability. Theory in ecology predicts that
-community structure influences stability. In turn, environment influences
-community structure but also directly stability.
+We seeked to disantangle the unravel the links between
+environment and community structure on both biomass stability and total biomass.
+To investigate complex relationships, direct and indirect, between variables,
+Structural Equation Modeling (SEM) is one promising way  
+[@grace_structural_2008, @grace_causal_2014, @lefcheck_piecewisesem_2016,
+@grace_integrative_2016]. SEM makes possible to set causal relationships between
+variables. This step can be critical, as the estimated parameters can be
+determined by both the choice of the variables and the links between them.
+Therefore, the set of variables and links shoud be supported by theory and
+litterature.
+
+We built a metamodel (set of variables and links between them). Basically, we
+tested the links between environmental conditions, community structure and
+ecosystem properties namely biomass stability on total biomass. Theory in
+ecology predicts that community structure influences stability. In turn,
+environment influences community structure but also directly stability.
 
@@
 structure and position of the river and the altitutinal gradient (+temperature).
-The third axis (RC3) was linked to enrichment (Organic Biological Demand) and CV
-of annual flow. The fourth and fifth (RC4 and RC5) axis were associated to
+The third axis (RC3) was linked to enrichment (Biological Demand in Oxygen) and
+CV of annual flow. The fourth and fifth (RC4 and RC5) axis were associated to
 environmental variability, respectively to CV of width and depth of the river
@@
 
-The community structure was characterized by total species richness,
-median average weighted trophic level and median connectance.
-Total species richness was the number of unique fish species that were observed
-at a given station over the whole sampling. Both median
-connectance and average trophic level were just computed as the median over the
-temporal period. For the details of the computation of the trophic networks,
-see Network inference part.
+The community structure was characterized by total species richness, median
+average weighted trophic level and median connectance. Total species richness
+was the number of unique fish species that were observed at a given station over
+the whole sampling. Both median connectance and average trophic level were just
+computed as the median over the time series. For the details of the
+computation of the trophic networks, see Network inference part.
 
@@
 
----
-# Environment to community attributes and stability  
----
 We linked environmental variables both to community structure and stability
@@
 biomass stability, causal links were set from species richness to other
-community attributes. (5) We hypothesized also that species richness
-decreased connectance following results from @thebault_stability_2010;
-@winemiller_must_1989. But theoretically, some ecological networks can show the
-inverse relationship [@winemiller_must_1989]. (6) We hypothesized also that species richness
-will modulate average weighted trophic level because of food web assembly
-processes. If *species richness increased and that new species are placed at
-random in the network, we expected a positive relationship between average
-trophic level and species richness because individuals of the higher trophic
-level have a higher body mass [to think again]*. Finally, we set up causal
-relationships from community attributes to stability components.
+community attributes. In particular, species richness decreased connectance
+following results from @thebault_stability_2010; @winemiller_must_1989. But
+theoretically, some ecological networks can show the inverse relationship
+[@winemiller_must_1989]. (6) We hypothesized also that species richness will
+modulate average weighted trophic level because of food web assembly processes.
+A community with more fish species can support higher trophic level. Finally, we
+set up causal relationships from community attributes to stability components.
 
@@
 We hypothesized that (7) species richness decreased synchrony between species
-[REF] and increased $\overline{CV_{sp}}$ [@tilman_biodiversity_2006] *to
-complete*. (8a) We expected that average trophic level had a positive or
-negative relationship with synchrony, bottom-up effects should result in
-positive whereas top-down in negative relationship. We expected a (8b) negative
-relationship between average trophic level and $\overline{CV_{sp}}$ if predators
-stabilised population
-fluctuations or if the increasing part of biomass in the predators decreased
-$\overline{CV_{sp}}$ because of their higher body mass (if mean increase faster than
-variance). (9a) Connectance was expected to decrease or increase $\overline{CV_{sp}}$
-and (9b) synchrony because of top down effects or bottom up effects.
+[@loreau_species_2008] and increased $\overline{CV_{sp}}$
+[@tilman_biodiversity_2006]. (8a) We expected that average trophic level had a
+positive or negative relationship with synchrony, bottom-up effects should
+result in positive whereas top-down in negative relationships. We expected a (8b)
+negative relationship between average trophic level and $\overline{CV_{sp}}$ if
+predators stabilised prey fluctuations or if the increasing part of
+biomass in the predators decreased $\overline{CV_{sp}}$ because of their higher
+body mass (if mean increase faster than variance). (9a) Connectance was expected
+to decrease or increase $\overline{CV_{sp}}$ and (9b) synchrony because of top
+down effects or bottom up effects.
 
@@
 library(DiagrammeR)
+meta_stab_sem_rich <- export_diagram(
+  fit = stab_sem_rich,
+  file_path = mypath("manuscript", "bef_stability", "meta_stab_sem"),
+  format = "png",
+  width = 700*2,
+  height = 900*2  - 900*2*30/100,
+  arrows = "ortho",
+  val_thd = 0.05,
+  env_x_pos_range = c(from = 0, to = 7.5),
+  env_y_pos = 0,
+  env_y_sep = 1.5,
+  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2"),
+  metamodel = TRUE
+)
 p_stab_sem_rich <- export_diagram(
@@
 
+meta_bm_sem_rich <- export_diagram(
+  fit = bm_sem_rich,
+  file_path = mypath("manuscript", "bef_stability", "meta_bm_sem"),
+  format = "png",
+  width = 700*2,
+  height = 900*2  - 900*2*45/100,
+  arrows = "ortho",
+  val_thd = 0.05,
+  env_x_pos_range = c(from = 0, to = 7.5),
+  env_y_pos = 0,
+  env_y_sep = 1.5,
+  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2"),
+  metamodel = TRUE
+)
 p_bm_sem_rich <- export_diagram(
@@
 
----
-#- Fishing operations and station
-  #- kept one protocol type by station
-  #- kept one sampling operation per year (of the season the most sampled in the
-    #time series)
-  #- remove operations which sampling effort (length of river sampled) superior to average
-    #plus or minus 30% of sd (by station)
-  #- kept station that had 10 or more samplings, i.e. followed 10 years or more
----
-
-Only one protocol
-type was kept by station. We kept only one sampling event by year to homogenize
-the dataset [numbers: month of sampling, number of days bw samplings] (detailed
-in Supplementary material).
-
 # Results
-
-## Drivers of total biomass and stability
 
@@
 sem_caption <- paste0(
-  "Results of the Structural Equation Models for (A) the determinants of biomass stability and (B) total biomass.
-Red and green represent respectively negative and positive path coefficients.
-The path coefficients are standardized coeffients.
-For convenience, only significant paths (i.e, *P < 0.05*) are shown."
-
-)
-```
-
-```{r sem-plot, fig.dim = c(10,10), fig.cap = sem_caption}
+  "Metamodel of the Structural Equation Models for (A) biomass stability and
+  (B) total biomass. ",
+  "Results of the Structural Equation Models for (C) the
+  determinants of biomass stability and (D) total biomass. Red and green
+  represent respectively negative and positive path coefficients. The path
+  coefficients are standardized coeffients. For convenience, only significant
+  paths (i.e, *P < 0.05*) are shown."
+
+)
+```
+
+```{r sem-plot, fig.cap = sem_caption}
 #https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
@@
 
-plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[1:2], rel_widths = c(.50, .5))
+plot_grid(
+  meta_stab_sem_rich, meta_bm_sem_rich,
+  p_stab_sem_rich, p_bm_sem_rich,
+  labels = LETTERS[1:4], nrow = 2,
+  rel_widths = c(1, .8)
+)
 ```
@@
 RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC1")
+RC2_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC2")
 ```
@@
 
+## Drivers of total biomass
+
 ---
@@
 
-The average trophic level was the only direct driver of
-total biomass ($r_\delta = `r tlvl_on_bm`$) whereas
-connectance and species richness had no significant effects (Fig.
-\@ref(fig:sem-plot) C). Environmental variables  no direct effects on total
-biomass.
-
-Species richness had a indirect positive effect on total biomass through
-average trophic level ($`r 0.38*.51`$). The stream size had a total effect on total biomass as strong
-as species richness ($r_\delta =`r env_on_bm["log_RC1"]`$), indirectly through average trophic level
-and species richness. The avg temperature of the river had an indirect positive
-effect on total biomass ($r_\delta = `r env_on_bm["log_RC2"]`$), through
-average trophic level and species richness as well. Avg DBO, CV DBO and CV of
-river size had no or weak indirect effect on total biomass
-(resp. $r_\delta =`r env_on_bm["log_RC3"]`$, $r_\delta =`r env_on_bm["RC5"]`$, $r_\delta =`r env_on_bm["RC4"]`$).
+#### Direct effect
+Species richness and average trophic level had a significant positive direct
+effects on total biomass (resp. $r_\delta = `r rich_on_bm$direct`$ and $r_\delta
+= `r tlvl_on_bm`$) whereas connectance had no significant direct effects (Fig.
+\@ref(fig:sem-plot) B). CV of enrichment had a direct negative effect on total
+while the other environmental variables had no significant direct
+effect.
+
+##### Indirect effect
+Avg river size, avg temperature and avg enrichment had however indirect positive
+effects on total biomass through species richness or/and average trophic level
+(Table XX & Fig.  \@ref(fig:sem-plot) B). Those indirect effects went
+independently by species richness and avg trophic level because species richness
+had no significant effect on avg trophic level.
 
@@
 ```{r get-sem-tot-effect-env}
-source(mypath("R", "total_sem_effect.R"))
 stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
@@
   ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
-
   ) %>%
@@
 
-```
-
----
-# Biomass stability
----
-
-$\overline{CV_{sp}}$ ($r_\delta = `r cv_sp_on_stab`$) decreased biomass stability more than
-synchrony ($r_\delta = `r sync_on_stab`$, Figure \@ref(fig:sem-plot)). Species richness had a strong
-positive effect on $\overline{CV_{sp}}$ and a strong negative effect on synchrony
-whereas average trophic level and connectance had no significant effects on either
-$\overline{CV_{sp}}$ nor synchrony. The environmental variables had
-no significant direct effects on either $\overline{CV_{sp}}$ nor synchrony.
-
-Indirectly through synchrony and $\overline{CV_{sp}}$, species richness had a total negative
-effect on biomass stability ($r_\delta = `r rich_on_stab`$). Avg river size and
-avg temperature had also a total effect which was negative on biomass stability
-(resp. $r_\delta = `r env_on_stab["log_RC1"]`$ and $r_\delta = `r
-env_on_stab["log_RC2"]`$), going through richness (resp. $r_\delta = `r
-env_on_richness["log_RC1"]`$ and $r_\delta = `r env_on_richness["log_RC2"]`$).
-
-- Main outcome:
-  - Biomass but stability increased with richness
-  - Higher trophic group was more stable that lower one
-    - Opposite relationship stability/richness
-  - Stability was mainly driven by species richness
-
-## Species richness increases total biomass but decreases biomass stability
-
-```{r}
-richness_lab <- expression(bold(paste("Total richness (", m^"-2", ") (Log 10)")))
-stab_lab <- "Biomass stability (Log 10)"
-bm_lab <- expression(bold(paste("Total biomass (", g.m^"-2", ") (Log 10)")))
-
-stab_div_caption <- paste0("Relationship between biomass stability (log 10) (top panel) or total biomass (log 10) (bottom panel) versus total species richness.") 
-```
-
-```{r p-s-div, fig.cap = stab_div_caption}
-lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab_std")
-lim_log_rich_tot <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich_tot_std")
-# Plot left
-
-p_stab_div <- sem_data %>%
-  ggplot(aes(x = log_rich_tot_std, y = log_stab_std))+
-  geom_point() +
-  ylim(lim_log_stab) +
-  xlim(lim_log_rich_tot) +
-  labs(x = richness_lab, y = stab_lab) +
-  geom_line(data = stab_div_pred) +
-  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
-  = "grey20", alpha = .2) +
-  annotate("text", x = -2.75, y = .75, label = make_label_rsq(rsq = stab_div_sum),
-    parse = TRUE)
-
-# Right plot
-p_stab_div_troph <- make_troph_plot(
-  .data = stab_div_by_troph,
-  resp  = "log_stab_std",
-  x_lim = lim_log_rich_tot,
-  y_lim = lim_log_stab,
-  lab_xy = c(x = richness_lab, y = stab_lab),
-  rsq_xy = c(x = -2.75, y = .75) 
-  )
-
-troph_legend <- get_legend(
-  p_stab_div_troph + 
-    guides(color = guide_legend(nrow = 1)) +
-    theme(legend.position = "bottom")
-)
-
-p_stab <- plot_grid(
-  p_stab_div,
-  p_stab_div_troph + theme(legend.position = "none"),
-  ncol = 2, rel_widths = c(.4, .6),
-  labels = c("A", "B") 
-)
-```
-
-```{r p-p-div}
-lim_log_bm <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_bm_std")
-
-p_bm_div <- sem_data %>%
-  ggplot(aes(x = log_rich_tot_std, y = log_bm_std))+
-  geom_point() +
-  ylim(lim_log_bm) +
-  xlim(lim_log_rich_tot) +
-  labs(x = richness_lab, y = bm_lab) +
-  geom_line(data = bm_div_pred) +
-  geom_ribbon(data = bm_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
-  = "grey20", alpha = .2) +
-  annotate("text", x = -2.75, y = -1.0, label = make_label_rsq(rsq = bm_div_sum),
-    parse = TRUE)
-
-p_bm_div_troph <- make_troph_plot(
-  .data = bm_div_by_troph,
-  resp  = "log_bm_std",
-  x_lim = lim_log_rich_tot,
-  y_lim = lim_log_bm,
-  lab_xy = c(x = richness_lab, y = bm_lab),
-  rsq_xy = c(x = -2.75, y = -1.0) 
-  )
-
-p_bm <- plot_grid(
-  p_bm_div,
-  p_bm_div_troph + theme(legend.position = "none"),
-  ncol = 2,
-  rel_widths = c(.4, .6),
-  labels = c("C", "D")
-)
-```
-
-```{r}
-troph_caption <- paste0(
-  "The effect of species richness on biomass stability
-  (upper panel) and total biomass (bottom panel) for the whole community (left
-    panel) and the community splited by trophic group (right panel)."
-)
-```
-
-```{r psbm, fig.dim = c(10,5), fig.cap = troph_cap}
-plot_grid(
-  p_stab,
-  p_bm,
-  troph_legend,
-  ncol = 1,
-  rel_heights = c(1, 1, .1)
-)
-
-```
-
-```{r print-coef-stab}
-
-# Coefficients
-s_co_i <- print_coef(coef_div$stab["(Intercept)"])
-s_co_r <- print_coef(coef_div$stab["log_rich_tot_std"])
-s_co_t <- print_coef(coef_troph$stab["troph_group3"])
-s_co_r_t2 <- print_coef(coef_troph$stab["log_rich_tot_std"])
-s_co_r_t3 <- print_coef(coef_troph$stab["log_rich_tot_std"]+coef_troph$stab["log_rich_tot_std:troph_group3"])
-
-s_ci_r <- print_ci(stab_div_ci["beta.log_rich_tot_std",])
-s_ci_t <- print_ci(stab_troph_ci["beta.troph_group3",])
-s_ci_r_t2 <- print_ci(stab_troph_ci["beta.log_rich_tot_std",])
-s_ci_r_t3 <- print_ci(coef_troph$stab["log_rich_tot_std"] + stab_troph_ci["beta.log_rich_tot_std:troph_group3",])
-```
-
-```{r print-coef-bm}
-# Coefficients
-b_co_i <- print_coef(coef_div$bm["(Intercept)"])
-b_co_r <- print_coef(coef_div$bm["log_rich_tot_std"])
-b_co_t <- print_coef(coef_troph$bm["troph_group3"])
-b_co_r_t2 <- print_coef(coef_troph$bm["log_rich_tot_std"])
-b_co_r_t3 <- print_coef(coef_troph$bm["log_rich_tot_std"]+coef_troph$bm["log_rich_tot_std:troph_group3"])
-
-b_ci_r <- print_ci(bm_div_ci["beta.log_rich_tot_std",])
-b_ci_t <- print_ci(bm_troph_ci["beta.troph_group3",])
-b_ci_r_t2 <- print_ci(bm_troph_ci["beta.log_rich_tot_std",])
-b_ci_r_t3 <- print_ci(coef_troph$bm["log_rich_tot_std"] + bm_troph_ci["beta.log_rich_tot_std:troph_group3",])
-```
-
-**Truc chelou sur l'effet du niveau trophique sur la biomasse et la stabilité,
-to check again the computation. Plots look good but the model coefficients does
-not go in the same direction**
-
----
-# Total biomass versus species richness
----
-Species richness increased total biomass (`r b_co_r`% `r b_ci_r` by 1% species
-richness increase). Total biomass was `r b_co_t`% `r b_ci_t` higher in the high
-than in the low trophic
-group. However, the increase of total biomass with the increase of species
-richness was lower in the high than the low trophic group (`r b_co_r_t3`% `r
-b_ci_r_t3` and `r b_co_r_t2`% `r b_ci_r_t2` respectively,  by 1% species
-richness increase).
-
----
-# Stability versus species richness
----
-
-However, biomass stability decreased with species richness (`r s_co_r`% `r s_ci_r` by 1%
-species richness increase). Biomass stability was overall `r s_co_t`% `r s_ci_t` higher for the high
-than the low trophic group. But biomass stability decreased by `r s_co_r_t3`% by
-1% increase in species richness in the high trophic group and increased by `r s_co_r_t2`% `r s_ci_r_t2`
-in the low trophic group.
+options(knitr.table.format = "latex")
+kable(tmp_stab_indir_table, "latex", booktabs = T, align = "c") 
+kable(tmp_bm_indir_table, "latex", booktabs = T, align = "c")
+
+#kable(rbind(
+  #mutate(tmp_stab_indir_table, type = "stab"),
+  #mutate(tmp_bm_indir_table, type = "bm")
+  #), "latex", booktabs = T, align = "c") %>%
+  #column_spec(1, bold=T) %>%
+  #collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
+```
+
+## Biomass stability
+
+#### Direct effects 
+$\overline{CV_{sp}}$ ($r_\delta = `r cv_sp_on_stab`$) decreased biomass
+stability more than synchrony ($r_\delta = `r sync_on_stab`$, Figure
+\@ref(fig:sem-plot)). Species richness had a strong opposite direct effect on
+$\overline{CV_{sp}}$ and synchrony, positive on $\overline{CV_{sp}}$ ($r_\delta
+= `r cv_sp_on_stab`$) and  negative on synchrony. Average trophic level had a
+negative direct effect on $\overline{CV_{sp}}$ and connectance had no
+significant direct effect on either $\overline{CV_{sp}}$ nor synchrony. Avg
+enrichment had a direct positive effect on $\overline{CV_{sp}}$. The other
+environmental variables had no significant direct effects on either
+$\overline{CV_{sp}}$ nor synchrony.
+
+#### Indirect effects
+Indirectly through synchrony ($r_\delta = `r rich_on_stab$via_sync`$) and
+$\overline{CV_{sp}}$ ($r_\delta = `r rich_on_stab$via_cv_sp`$), species richness
+had a total negative effect on biomass stability
+($r_\delta = `r rich_on_stab$total`$). Avg trophic level had a positive indirect
+effect on
+biomass stability through $\overline{CV_{sp}}$
+($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$).
+
+Avg temperature had an indirect negative effect on biomass stability through
+$\overline{CV_{sp}}$ ($r_\delta = `r env_on_stab$via_cv_sp["log_RC2"]`$) and
+through species richness ($r_\delta = `r env_on_stab$via_richness["log_RC2"]`$)
+but weakly positive through avg trophic level ($r_\delta = `r env_on_stab$via_com["log_RC2"]`$).
+In sum, avg temperature had a the highest total negative effect  
+on biomass stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$).
 
@@
 
-For the first time, we assessed the determinants of total biomass and temporal
-biomass stability in empirical trophic communities at such high temporal and
-spatial scales. We showed that species richness increased total biomass but 
-decreased biomass stability. In particular, species richness decreased
-synchrony and increased species CV (\LaTeX). Surprisingly, the avg trophic
-level and connectance had no effects on either synchrony nor species CV.
-Finally, we showed that high trophic group was more stable than low trophic
-group but that high trophic group was responsible for the negative
-stability-diversity relationship.
-
----
-# Negative relationship between stability and richness 
----
-
-Surprisingly, we found a negative relationship biomass stability and species
+#### Hat
+
+With the aim to find out the determinants of total biomass and temporal
+biomass variability in trophic communities, we analysis a standardized dataset
+at France scale going on from 1995 to 2018. We infer network structure with
+trait matching method and used SEM to disantangle direct and indirect effects of
+environment, community and network structure on both total biomass and biomass
+stability. We fund that species richness increased total biomass but 
+decreased biomass stability. Suprisingly, we found that $\overline{CV_{sp}}$ had
+an negative effect twice higher than synchrony on biomass stability.
+Furthermore, we found that the effects of species richness on stability and
+biomass were independent from the effects of network structure.
+
+#### Richness on stability and biomass
+
+We found a negative relationship biomass stability and species
 richness whereas there was a positive one between total biomass and species
-richness. Those relationships followed a power law, meaning that they represent
-respectively accelerating and decelerating functions. Overall, it contrasts
-with studies in grasslands [@tilman_biodiversity_2006, @zhang_scale_nodate],
-mesocosms [@pennekamp_biodiversity_2018] or other animals
-[@olivier_independent_nodate] where positive relationships are typically found
-between biomass stability (computed as CV) and species richness. In streams as
-well, @franssen_annual_2011 found that species richness increased biomass
-stability. However other studies found a opposite relationship
-[@yang_effects_2011] or a marginal one [@declerc_species_2006].
-
----
-# Total biomass
----
-
-We found that species richness increased total biomass as found in salt
-marshes, forests [@wu_relationship_2014,@shuaifeng_positive_2018]. But opposite
-relation has been found in richness in grasslands [@grace_integrative_2016],
-notably because of light competition. Precedent researches in plant communities
-showed that the total biomass was primary driven by environmental drivers. In
-contrast, we found that the average trophic level was one of the main driver of the
-total biomass, together with the stream size and increasing avg temperature
-(with decreasing altitude). The effect of species richness is 
-goes through its effect on food web assembly and so, avg trophic level.
-The indirect positive effect of species richness on total biomass might be due to
-resource use complementarity [@cardinale_species_2002].
-It was however unexpected that connectance had no effect on total biomass,
-because we could imagine that connectance could also improve resource use, but
-this might be true only under the assumption that all species have the same
-assimilation efficiency.
-We found that the effect of stream size, altitude of the river and its avg
-temperature on total biomass was only indirect through community structure
-(species richness and average trophic level).
-
----
-# Effect of environment on community structure
----
-
-The total effect of river size on biomass stability was negative as avg
-temperature (and low altitude), indicating that big rivers in plains had a high
-negative effect on stability (TO MOVE). We found a mix of both expected and
-unexpected results on the effects on environment on community structure. First,
-we expected that bigger and low altitude streams had higher species richness
-because they might receive more
-confluents streams and so more species through immigration.
-Stream size increased avg trophic level. An increase in mean trophic position
-of piscivorous species in bigger rivers could explain this relation
-[@post_ecosystem_2000]. In our network reconstruction, the fish-fish
-interactions are more resolved than fish-resource interactions.
-@petchey_predicting_2010 predicted that temperature should increase connectance
-but we did not find any relationship but temperature (and
-low altitude) increased avg trophic level (**Bullshit**). 
-CV of enrichment decreased both connectance and avg trophic level, while avg
-enrichment (and CV of flow) increased avg trophic level. The latter might by explained by
-the fact that enrichment can benefit to top trophic level
-[@hulot_functional_2000]. One explanation for the former is that enrichment
-variation might destabilize top predators (REF or Bullshit again).
-
----
-# Effect of synchrony and cv_sp  
----
-
+richness. Overall, it contrasts with studies in grasslands
+[@tilman_biodiversity_2006, @zhang_scale_nodate], mesocosms
+[@pennekamp_biodiversity_2018] or other animals [@olivier_independent_nodate]
+where positive relationships are typically found between biomass stability
+and species richness. In streams as well, @franssen_annual_2011
+found that species richness increased biomass stability. However other studies
+found a opposite relationship [@yang_effects_2011] or a marginal one
+[@declerck_species_2006]. We found that species richness increased total biomass
+as found in salt marshes, forests
+[@wu_relationship_2015,@li_relationship_2018]. The positive effect
+of species richness on total biomass might be due to resource use
+complementarity [@cardinale_species_2002]. But opposite relation has been found
+in richness in grasslands
+[@grace_integrative_2016].
+
+#### connectance on stability and biomass
+Our path analysis revealed that, although species richness has a strong effect on
+connectance, connectance itself had little to no effect either on stability nor
+total biomass. This result contradicts precedent theoretical studies on the
+relationship between stability and network structure [@angelis_stability_1975,
+@may_will_1972], although they considered different stability metrics (i.e.
+local stability of equilibrium point). The reason might be that in our inferred
+network, network structure is strongly constraints by assembly processes.
+Indeed, connectance generally decreased with increasing species richness
+[@winemiller_must_1989, @thebault_stability_2010]. It is an effect important to
+consider the link between connectance and ecosystem properties, as this direct
+relationship can be misleading if species richness is not taken into account.
+
+##### Trophic level on stability and biomass 
+We also found that richness had no effect on average trophic level but average
+trophic level was positively linked to total biomass and biomass stability.
+It means that the effects of richness and avg trophic level are
+independent. Then, it underlied the importance to consider facets of community
+structure related to biological interactions. The positive relation between
+average trophic level and biomass is straitforward. As feeding interactions were
+partly determined by body size and that body mass increase with body size, we
+expected that the more the average biomass is located at higher trophic level,
+the more the total biomass increase. Average trophic level had a positive effect
+on biomass stability by its negative effect on average species CV (i.e. positive
+effect on average species stability). It means that species at higher trophic
+level are more stable than the species at lower trophic levels. But, the
+relations between trophic position and stability more complex
+[@shanafelt_david_w._stability_nodate], even more if we take in account the
+repartition of the biomass across trophic level [@barbier_pyramids_2019].
+Further investigation are needed to understand the interplay between trophic
+level number, their biomass repartition and stability.
+
+##### Environment on biomass and stability
+
+Precedent researches in plant communities showed that the total biomass was
+primary driven by environmental drivers [@grace_integrative_2016]. We found that
+environmental drivers in general did not directly affect either total biomass
+nor synchrony and CVsp except avg temperature and CV of enrichment which were
+respectively positively linked to CVsp and negatively linked to total biomass.
+It indicates that the effect of environment primary drive community structure
+which in turn affect total biomass and biomass stability. Our results also
+showed that avg temperature had the biggest effect on biomass stability while Cv
+of enrichment had the second biggest impact on total biomass.
+
+#### Synchrony and CVsp 
 Species richness decreased synchrony and increased $\overline{CV_{sp}}$. Species
@@
 well understood, its effect on $\overline{CV_{sp}}$ is more complex. 
-
 In turn, we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
@@
 differentiation. Because fish species even piscivorous one are quite
-opportunistic in their foraging.
-Secondly, in trophic communities, species directly affect each other through
-feeding interactions, and so could raise synchrony between species
-[@raimondo_interspecific_2004] more than in systems where interactions happen
-more in the form of competitive exploitation.
-
----
-# Effect of trophic level and connectance are richness effects:
----
-
-Our path analysis revealed that, although species richness has a strong effect on
-connectance and the average trophic level, network structure  itself had little
-to no effect either on synchrony nor average population stability. This result
-contradicts precedent theoretical studies on the relationship
-between stability and network structure [@angelis_stability_1975,
-@may_will_1972], although they considered different stability metrics (i.e.
-local stability of equilibrium point). The reason might be that in our inferred
-network, network structure is strongly constraints by assembly processes.
-Indeed, connectance generally decreased with increasing species richness
-[@winemiller_must_1989, @thebault_stability_2010], because a small fraction of
-links are realized because of food diet constraints. In theoretical studies,
-connectance can be tuned from 0 (no links) to 1 (all possible links are
-present) [@angelis_stability_1975]. The link between the average trophic level
-and species richness has been less studied. However, we can suppose that
-because species richness increase total biomass, species richness also increase
-both the biomass of prey available for piscivorous fishes and the biomass of
-piscivorous species which in turn, increase the avg trophic level of the
-community. In sum, the biomass stability of freshwater ecosystems can be
-derived by species richness because, through trophic structure constraints,
-species richness determine largely network structure.
-
----
-# Trophic group
----
-
-The total biomass of high and low trophic group trophic groups responded both
-positively to species richness but not biomass stability. There is a
-paradox where the high trophic group is overall more stable than the low but
-species richness had a destabilizing effect on the former whereas a stabilizing
-on the latter. @shanafelt_david_w._stability_nodate showed in a theoretical
-study in trophic chains, the top trophic level is the more stable TOEXPLORE.
-The comparison between our study and theoretical studies stays limited because
-fishes in our system have a large diet and consume food item of several trophic
-level while theoretical studies consider system in which one species of one
-trophic level feeds only on the trophic level directly inferior
-[@shanafelt_david_w._stability_nodate] ADD REF.
-
-# Appendix
-
-## PCA of environmental variables
-
-```{r, fig.show = "hide"}
-axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
-p_l_rot <- map(axis_pair, 
-  function (axis)
-    pca_rotated_plot <- plot_rotated_pca(
-      pca_rotated = pca_rotated,
-      axis = axis 
-    )
-)
-```
+opportunistic in their foraging.  Secondly, in trophic communities, species
+directly affect each other through feeding interactions, and so could raise
+synchrony between species [@raimondo_interspecific_2004] more than in systems
+where interactions happen more in the form of competitive exploitation.
+
+#### Ending paragraph
+This work aims to facilitate the rapprochement between theoretical ecology and
+empirical ecology. While theoretical ecology has focused on the effects of
+network structure on stability and biomass distribution, empirical ecology
+ignored network structure. Furthermore, both fields have largely used different
+stability metrics. We tried to move forward by including network structure in
+the explanation of both total biomass and biomass stability. We showed that
+species richness and network structure can have independent effects on ecosystem
+properties. It opens a promising way for the understanding on how species
+interactions, of different types, can affect both synchrony and CVsp in
+different ecosystems. The reconstruction of ecological network with trait
+matching methods can be a first approach to document such relationship, however
+it will not compensate for close evaluation of measured interaction strength.
+We also believe that SEM methods are particularly helpful to assess complex
+relationship between environment, community structure and ecosystem properties
+in empirical data which necessitate to move from simple bivariate relationships
+[@grace_integrative_2016]. We believe that the integration of network structure
+and species interaction in general will improve our understanding of the
+mechanisms which determines ecosystem properties.
 
 ```{r}
-prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
-  map_dbl(., ~round(.x * 100))
-
-tot_var_expl_pca <- round(sum(pca_rotated$rotated$Vaccounted["Proportion Var", ]) * 100)
-
-pca_caption <- paste0(
-  "Rotated axis of PCA on environmental variables. The five components
-  explained,", tot_var_expl_pca, "% of the variance (",
-  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
-  "(A) Axis 1 was positively related to the river size, axis 2 was related to
-  average temperature and negatively related to the river slope and altitude.
-  (B) Axis 3 was negatively related to the CV of flow and average enrichment.
-  Axis 4 was related to the CV of river size. Finally, axis 5 was related to the
-  CV of enrichment.")
-```
-
-```{r pca-rotated, fig.cap = pca_caption}
-to_plot <- c(1, 6, 7)
-plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
-  ncol = length(to_plot), labels = LETTERS[1:3])
-```
-
-## Model summary and diagnostics
-
-### Biomass and stability models
-
-```{r tab-coeff-bm, fig.cap = "Coefficient"}
-# Replacement rules for term
-rp_est <- c(
-  "(Intercept)" =     "intercept",
-  "sd\\_\\(intercept\\)\\.basin" = "sd intercept basin",
-  "log_rich" =     "Median richness (log base 10)",
-  "troph_group3" =     "high trophic group",
-  "log_rich:troph_group3" =     "Median richness (log10) : high trophic group",
-  "sig01.basin" =     "sd intercept basin",
-  "sd_Observation.Residual" =     "residuals",
-  "sigma" = "residuals"
-)
-# Replacement rules for group
-rp_group <- c(
-  "fixed" = "Fixed",
-  "basin" = "Random"
-)
-
-```
-
-```{r}
-coeff_troph <- map2_dfr(list(bm_troph_ci, stab_troph_ci), list(bm_troph_mod, stab_troph_mod),
-  clean_summary_mod, term_rp = rp_est, group_rp = rp_group)
-
-kable(coeff_troph) %>%
-  pack_rows("Biomass", 1, 6) %>%
-  pack_rows("Stab", 7, 12)
-```
-
-### SEM
-
-#### Indirect effect
-
-```{r indir-tab, fig.cap = "Indirect effect from SEM"}
-kable(tmp_stab_indir_table)
-kable(tmp_bm_indir_table)
-```
-
-## Model residuals
-
-### Biomass and stability models
-
-```{r}
-mod_list <- list(bm_div_mod, bm_troph_mod, stab_div_mod, stab_troph_mod)
-plot_res <- map(mod_list, ~ plot(.x))
-plot_grid(plotlist = plot_res)
-```
-
-### SEM linear relationships
-
-```{r hist-sem-data}
-sem_data %>%
-  select(prod, log_rich_tot, log_sync, log_stab, log_cv_sp, RC1, RC2, RC3, RC4,
-    RC5, t_lvl, ct, log_bm) %>%
-  gather(variable, value) %>%
-  ggplot(aes(x = value)) +
-  geom_histogram() +
-  facet_wrap(~variable, scales = "free")
-
-```
-
-```{r s-colin-sem, fig.cap = "Variance Inflation factor for each individual model of stability sem"}
-#compute_stab_sem_rich(.data = sem_data, get_sem =TRUE)
-
-mod_stab_list <-
-  list(
-    nlme::lme(log_rich_tot ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
-    #nlme::lme(piel ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(ct ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    #nlme::lme(beta_bin ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(log_sync ~ log_rich_tot + ct + t_lvl + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,
-      random = ~ 1 | basin, data = sem_data),
-    nlme::lme(log_cv_sp ~ log_rich_tot  + ct + t_lvl
-      + RC1 + log_RC2 + log_RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data),
-    lm(log_stab ~ log_cv_sp + log_sync, data = sem_data)
-  )
-names(mod_stab_list) <- c("richness", "connectance", "weighted_mean_trophic_lvl", "synchrony", "cv_sp", "stability") 
-colin_stab_sem <- map(mod_stab_list, car::vif)
-
-tmp <- map(colin_stab_sem, enframe)
-
-# colinearity table
-colin_stab_sem <- tibble(vif = tmp, mod = names(mod_stab_list)) %>%
-  unnest(vif) %>%
-  spread(name, value)
-
-kable(colin_stab_sem)
-```
-
-```{r}
-plot_residuals <- function (x, y = "Diagnostic") {
-  plot.lme(x, main = y, xlab = "Fitted values", ylab = "Residuals")
-}
-p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
-plot_grid(plotlist = p_resid_stab_sem)
-```
-
-```{r, eval = FALSE}
-mod_tlvl <- nlme::lme(t_lvl ~ scale(RC1) + scale(RC2) + scale(RC3) + scale(RC4) + scale(RC5) + log_rich_tot, random = ~ 1 | basin, data = sem_data)
-plot(mod_tlvl)
-sem_data %>%
-  ggplot(aes(x = log10(richness_tot), y = t_lvl)) +
-  geom_point()+
-  geom_smooth(method = "lm")
-plot(x = log10(sem_data$RC1 + abs(min(sem_data$RC1))), y = sem_data$t_lvl)
-sem_data %>%
-  ggplot(aes(x = log10(RC1), y = t_lvl)) +
-  geom_point()+
-  geom_smooth(method = "lm")
-plot(nlme::lme(t_lvl ~ I(log10(RC1 + abs(min(RC1)))) + log_rich_tot, random = ~ 1 | basin, data = sem_data))
-nlme::lme(t_lvl ~ log_rich_tot, random = ~ 1 | basin, data = sem_data)
-semd_test <- sem_data %>%
-  mutate(RC1b = RC1 + abs(min(RC1)))
-ricker.mixed.fit <- nls(
-  t_lvl ~ (Vm*(RC1 + b) / (K + (RC1 + b)) + d),
- #fixed = Vm + K + b + d ~ 1,
- #random = Vm + K + b + d ~ 1|basin,
- start= c(Vm=1, K = 0.1, b = .5, d = 2.5),
- data = semd_test,
- control = lmeControl(maxIter = 1e8, msMaxIter = 1e8) 
-)
-summary(ricker.mixed.fit)
-x <- seq(min(sem_data$RC1), max(sem_data$RC1), length.out = 100)
-sem_data$test_pred <- predict(ricker.mixed.fit)
-
-semd_test %>%
-  ggplot(aes(x = RC1b, y = t_lvl)) +
-  geom_point() +
-  geom_line(aes(y = test_pred))
-  geom_smooth(method = "lm")
-cor(semd_test$piel, semd_test$t_lvl, method = c("spearman"))
-```
-
-```{r, eval = FALSE}
-library(glmmTMB)
-# Gaussian
-mod_log_rich <- glmmTMB(
-  log_rich_tot ~ log_RC1 + log_RC2 + log_RC3
-  + RC4 + RC5 + (1 | basin), family = gaussian, data = sem_data)
-summary(mod_log_rich)
-plot(y = resid(mod_log_rich), x = fitted(mod_log_rich))
-
-# Poisson 
-mod_log_rich_poi <- glmmTMB(
-  richness_tot ~ log_RC1 + log_RC2 + log_RC3
-  + RC4 + RC5 + (1 | basin), family = poisson, data = sem_data)
-summary(mod_log_rich_poi)
-plot(y = resid(mod_log_rich_poi), x = fitted(mod_log_rich_poi))
-
-# Truncate 
-mod_log_rich_nbinom <- glmmTMB(
-  richness_tot ~ log_RC1 + log_RC2 + log_RC3
-  + RC4 + RC5 + (1 | basin), family = nbinom1, data = sem_data)
-summary(mod_log_rich_nbinom)
-plot(y = resid(mod_log_rich_nbinom), x = fitted(mod_log_rich_nbinom))
-```
-
-#### Total biomass
-
-```{r}
-
-mod_bm_list <-
-  list(
-    nlme::lme(log_rich_tot ~ RC1 + RC2 + RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
-    #nlme::lme(piel ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(ct ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(t_lvl ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    #nlme::lme(beta_bin ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(log_bm ~ log_rich_tot + ct + t_lvl + RC1 + RC2 + RC3 + RC4 + RC5,
-      random = ~ 1 | basin, data = sem_data)
-  )
-names(mod_bm_list) <- c("richness", "connectance", "weighted_mean_trophic_lvl", "total_biomass") 
-colin_bm_sem <- map(mod_bm_list, car::vif)
-
-tmp <- map(colin_bm_sem, enframe)
-
-# colinearity table
-colin_bm_sem <- tibble(vif = tmp, mod = names(mod_bm_list)) %>%
-  unnest(vif) %>%
-  spread(name, value)
-
-kable(colin_bm_sem)
-```
-
-## Relationship at the absolute scale, i.e. not the logarythme scale
-
-```{r}
-ggplot(sem_data, aes(x = richness_med, y = biomass_stab)) +
-  geom_point()
-test <- tibble(
-  richness_med = seq(1,20, length.out = 100),
-  biomass_stab =
-    10^(fixef(stab_div_mod)[1])*richness_med^fixef(stab_div_mod)[2]
-)  
-```
-
-```{r save-plot}
-
-save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div.pdf",
-  p_stab_div,
-  base_height = 3,
-  bg = "transparent",
-  ncol = 1)
-
-save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div_troph.pdf",
-  p_stab_div_troph + theme(legend.position = "bottom"),
-  base_height = 3,
-  bg = "transparent",
-  ncol = 1)
-
+save.image(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
 ```

### 2020-04-27 temporal_network.R

@@ -1,0 +1,71 @@
+library(tidyverse)
+library(magrittr)
+library(cowplot)
+mypath <- rprojroot::find_package_root_file
+source(mypath("R", "misc.R"))
+source(mypath("R", "plot_methods.R"))
+
+myload(network_analysis, dir = mypath("data", "classes"))
+myload(op_analysis, metaweb_analysis, dir = mypath("data"))
+meta <- metaweb_analysis; rm(metaweb_analysis)
+
+st_sp_node <- network_analysis %>%
+  select(opcod, composition) %>%
+  left_join(dplyr::select(op_analysis, opcod, station, date), by = "opcod") %>%
+  unnest(cols = c(composition)) %>%
+  group_by(station) %>%
+  summarise(
+    nbnode = length(unique(sp_class)),
+    nbsp = length(unique(str_extract(sp_class, "[A-Z]+")))
+  ) %>%
+  arrange(nbsp)
+
+
+net <- network_analysis %>%
+  dplyr::select(opcod, network) %>%
+  unnest(cols = c(network)) %>%
+
+station_to_get <- function (rich = NULL)  {
+  tmp <- filter(st_sp_node, nbsp == rich)
+  choice <- sample(tmp$station, 1)
+  cat(choice, "\n")
+  return(choice)
+}
+choice <- station_to_get(6)
+
+net_ex <- filter(net, station == 11329) %>% #choice
+  mutate(date = lubridate::year(date)) %>%
+  filter(date %in% seq(2000, 2004))
+
+p <- my_crap_temporal_network(
+  net = net_ex,
+  metaweb = meta$metaweb,
+  network_data = network_analysis,
+  nrow_sp_legend = 1,
+)
+p
+save_plot(filename = mypath("manuscript", "bef_stability", "figs", "temporal_network.pdf"),
+  p)
+temporal_network <- p
+mysave(temporal_network, dir = mypath("manuscript/bef_stability/figs"), overwrite = TRUE)
+
+######
+# metaweb   #
+######
+
+metaweb <- meta$metaweb
+
+
+llay <- ggraph::create_layout(metaweb, layout = "kk")
+node_pos <- NetIndices::TrophInd(metaweb, Dead = NULL)$TL - 1
+llay$y <- node_pos
+llay$species <- get_species(llay$name)
+
+p <- ggraph::ggraph(llay) +
[…]

### 2020-04-27 truta.R

@@ -1,0 +1,57 @@
+##############################
+#  truta example for figure  #
+##############################
+
+library(tidyverse)
+library(magrittr)
+library(cowplot)
+theme_set(theme_cowplot())
+
+mypath <- rprojroot::find_package_root_file
+source(mypath("R", "plot_methods.R"))
+source(mypath("R", "misc.R"))
+source(mypath("R", "geo_methods.R"))
+
+myload(length_analysis, dir = mypath("data"))
+
+truta_length <- length_analysis %>%  
+  filter(species == "TRF")
+
+summary(truta_length)
+
+p_truta_length <- truta_length %>%
+  ggplot(aes(x = length)) +
+  geom_histogram(binwidth = 10)
+
+myload(metaweb_analysis, dir = mypath("data"))
+names(metaweb_analysis)
+
+truta_size_class <- metaweb_analysis$size_class %>%
+  filter(species == "TRF")
+size_class_segment <- c(0, truta_size_class$upper) 
+
+size_class_segment_df <- data.frame(y = -1000, length = size_class_segment)
+
+p <- p_truta_length + 
+  scale_shape_identity() +
+  geom_point(
+    data = size_class_segment_df,
+    aes(y = y, x = length, shape = 124, size = 5)) +
+  geom_line(data = size_class_segment_df, aes(y = y, x = length, size = 1)) +
+  labs(x = "Body size (mm)", y = "Frequency") +
+  theme(legend.position = "none")
+
+save_plot(
+  filename = mypath("manuscript", "bef_stability", "figs", "truta_body_size.pdf"),
+  plot = p#,
+  #base_height = ,
+  #base_width = 
+)
+
+# Fish ontogenic size
+myload(diet_shift, dir = mypath("data"))
+truta_diet_shift <- diet_shift %>% 
+  filter(species == "TRF")
+
+truta_diet_shift %>%
+  select(light:fish)

### 2020-05-10 manuscript/bef_stability/appendix.Rmd
Commit before text review

@@
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, message = FALSE, collapse = FALSE}
 mypath <- rprojroot::find_package_root_file
@@
 
+knitr::opts_chunk$set(
+  cache = FALSE,
+  collapse = TRUE,
+  comment = "#>",
+  #fig.dim = c(7, 7),
+  fig.fullwidth = TRUE,
+  fig.show = "hold",
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  results = FALSE
+)
 knitr::opts_chunk$set(
@@
 
-```{r}
-caption_indir_stab_sem <- paste0(
-  "Indirect and total effect of variables on biomass stability from the
-  structural equation model. Indirect effects are computed by multiplying the
-  path coefficients from the variable predictor to the response variable, here
-  biomass stability. Indirect effects are considered as one step from the target
-  variable. For exemple, the indirect effect of species richness on
-  biomass stability via its effect on CVsp is $-0.61$. To compute indirect
-  effect, only the significant direct effects were taken into account. ",
-  "Network structure being the indirect effect that went through both avg trophic
-  level and connectance and Species richness_Network structure being the
-  indirect effect that went through (i) species richness and from (ii) species
-  richness to network structure."
-
-)
-
-caption_indir_bm_sem <- paste0(
-  "Indirect and total effect of variables on total biomass from the
-  structural equation model. See the table (X) for details about computation and
-  meaning."
-
-)
-```
-
-```{r indir-tab, fig.cap = "Indirect effect from SEM"}
-format_table <- function (x = tmp_stab_indir_table) {
-  x <- x[, c("variable", names(x)[!names(x) %in% "variable"])]
-
-  rm_n <- str_remove_all(get_sem_var_name_replacement(), pattern = "\n")
-  names(rm_n) <- names(get_sem_var_name_replacement()) 
-  x$variable <- str_replace_all(x$variable, rm_n)
-
-  colnames(x) %<>% str_remove_all(., pattern = "via_")
-
-  col_replacement <- c(
-    variable = "Variable",
-    cv_sp = "CVsp",
-    sync = "Synchrony",
-    richness = "Species richness",
-    com = "Network structure",
-    richness_com = "Sp. richness and network str.",
-    total = "Total effect"
-  )
-  colnames(x) %<>% str_replace_all(., col_replacement)
-
-  x
-}
-
-kable(format_table(tmp_stab_indir_table),
-  "latex",
-  booktabs = T,
-  caption = caption_indir_stab_sem 
-  ) %>%
-kable_styling(latex_options =c("striped", "scale_down"))
-
-```
-
-```{r}
-
-kable(format_table(tmp_bm_indir_table),
-  "latex",
-  booktabs = T,
-  caption = caption_indir_bm_sem
-  ) %>%
-kable_styling(latex_options =c("striped", "scale_down"))
-```
-
 ### Model linear Relationship

### 2020-05-10 manuscript/bef_stability/manuscript.Rmd
Commit before text review

@@
   comment = "#>",
-  fig.dim = c(7, 7),
+  #fig.dim = c(7, 7),
   fig.fullwidth = TRUE,
@@
 
-#### Importance of BEF assessment
-
-Determining the shape of the relationship between species diversity and ecosystem
-functioning has been a central research topic in ecology
-[@may_will_1972, @hector_plant_1999, @loreau_biodiversity_2001, @hooper_effects_2005, @duffy_why_2009, @isbell_forest_quantifying_2018].
-Current biodiversity losses
-in all ecosystems challenge scientists to understand how ecosystems will be
-affected in turn. Studies in Bioversity-Ecosystem Functioning (BEF) usually
-quantify species diversity as species richness (i.e number of species) while
-ecosystem functioning is quantified as total biomass, productivity (biomass
-produced by unit of time) or stability which is quantified in more diverse ways
-such as the variability of species abundance, the resilience to perturbation, or
-resistance to perturbation [@donohue_navigating_2016].
+#### Biodiversity and ecosystem functioning
+
+Biodiversity is essential to determine and maintain ecosytem properties.
+Current biodiversity losses question the ability of how ecosystems will be
+affected in turn.
+
+The relationship between biodiversity and ecosystem functioning has been a
+central research topic in ecology [@may_will_1972; @hector_plant_1999;
+@loreau_biodiversity_2001; @hooper_effects_2005; @duffy_why_2009;
+@isbell_forest_quantifying_2018].
+
+Studies in
+Bioversity-Ecosystem
+Functioning (BEF) usually quantify species diversity as species richness (i.e
+number of species) while ecosystem functioning is quantified as total biomass,
+productivity (biomass produced by unit of time) or stability which is quantified
+in more diverse ways such as the variability of species abundance, the
+resilience to perturbation, or resistance to perturbation
+[@donohue_navigating_2016].
 
@@
 Species richness has been reported to increase productivity
-[@tilman_productivity_1996, @grace_integrative_2016] through complementarity
+[@tilman_productivity_1996; @grace_integrative_2016] through complementarity
 between species in resource exploitation and selection effects
-[@loreau_partitioning_2001, @cardinale_species_2002, @fargione_selection_2007].
-Empirical assessment of the effect of species richness on total biomass showed negative
-[@grace_integrative_2016] and positive relationships
-[@hector_plant_1999, @tilman_biodiversity_2014]. @grace_integrative_2016 showed
+[@loreau_partitioning_2001; @cardinale_species_2002; @fargione_selection_2007].
+Empirical assessment of the effect of species richness on total biomass showed
+negative [@grace_integrative_2016] and positive relationships
+[@hector_plant_1999; @tilman_biodiversity_2014]. @grace_integrative_2016 showed
 that the results depend on the refinement of the mecanisms involved in the
@@
 partly because of the inherent multidimensionality of stability
-[@donohue_dimensionality_2013, @donohue_navigating_2016] and because of the
+[@donohue_dimensionality_2013; @donohue_navigating_2016] and because of the
 different metrics of stability privileged in theoretical (stability of local
@@
 [@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018] and
-vertebrates [@olivier_independent_nodate, @franssen_annual_2011]. Two
-mecanisms are involved into community variability, (1) species
-variability and (2) the species synchrony [@loreau_species_2008, @thibaut_understanding_2013].
-Positive [@tilman_biodiversity_2006], neutral
-[@jiang_different_2009, @olivier_independent_nodate] and negative
-[@franssen_annual_2011, @olivier_independent_nodate] relationships between
-species variability and species richness have been found. On the other side,
-studies consistently found that species richness decreased synchrony between
-species
-[@loreau_species_2008, @thibaut_understanding_2013, @bluthgen_land_2016, @olivier_independent_nodate].
-Beyond species richness, species interactions, which modifies species
-abondance and biomass and make species dynamics interdependant, have been
-largely ignored in empirical assessment.
+vertebrates [@olivier_independent_nodate; @franssen_annual_2011]. Two mecanisms
+are involved into community variability, (1) species variability and (2) the
+species synchrony [@loreau_species_2008; @thibaut_understanding_2013].  Positive
+[@tilman_biodiversity_2006], neutral [@jiang_different_2009;
+@olivier_independent_nodate] and negative [@franssen_annual_2011;
+@olivier_independent_nodate] relationships between species variability and
+species richness have been found. On the other side, studies consistently found
+that species richness decreased synchrony between species [@loreau_species_2008;
+@thibaut_understanding_2013; @bluthgen_land_2016; @olivier_independent_nodate].
+Beyond species richness, species interactions, which modifies species abondance
+and biomass and make species dynamics interdependant, have been largely ignored
+in empirical assessment.
 
@@
 Conversely, theoretical ecology display an extensive literature about the
-effects of network structure on stability 
-[@may_will_1972, @angelis_stability_1975, @stouffer_compartmentalization_2011, @thebault_stability_2010, @barbier_pyramids_2019, @shanafelt_david_w._stability_nodate].
-Theoretical ecology generally uses stability definitions related to community
-equilibrium and its stability to small perturbations.
-Connectance (i.e. proportion of realized links in a network) can decrease
-[@angelis_stability_1975, @thebault_stability_2010] or increase resilience of
-trophic network depending on the functioning of networks
-[@angelis_stability_1975].
-The number of trophic levels, the vertical position in the trophic network as
-well as the strength of their biomass regulation (i.e. top-down and bottom-up)
-can determine biomass and stability at equilibrium
-[@hurd_stability_1971, @shanafelt_david_w._stability_nodate, @zhao_horizontal_2019, @barbier_pyramids_2019].
+effects of network structure on stability [@may_will_1972;
+@angelis_stability_1975; @stouffer_compartmentalization_2011;
+@thebault_stability_2010; @barbier_pyramids_2019;
+@shanafelt_david_w._stability_nodate].  Theoretical ecology generally uses
+stability definitions related to community equilibrium and its stability to
+small perturbations.  Connectance (i.e. proportion of realized links in a
+network) can decrease [@angelis_stability_1975; @thebault_stability_2010] or
+increase resilience of trophic network depending on the functioning of networks
+[@angelis_stability_1975].  The number of trophic levels, the vertical position
+in the trophic network as well as the strength of their biomass regulation (i.e.
+top-down and bottom-up) can determine biomass and stability at equilibrium
+[@hurd_stability_1971; @shanafelt_david_w._stability_nodate;
+@zhao_horizontal_2019; @barbier_pyramids_2019].
 
@@
 biomass in natural communities while integrating both species richness and
-network structure. We combined together the effect of vertical
-and horizontal diversity and thus aimed to bridge the current gap between theoretical
-and empirical studies. We used an standardized monitoring of fish
-communities in french streams. More than three hundreds sites were followed
-more than 10 years on the 1995-2018 period. We inferred four thousands potential
-interaction networks corresponding to each sampling event, based on trait
-matching.
+network structure. We combined together the effect of vertical and horizontal
+diversity and thus aimed to bridge the current gap between theoretical and
+empirical studies. We used an standardized monitoring of fish communities in
+french streams. More than three hundreds sites were followed more than 10 years
+on the 1995-2018 period. We inferred four thousands potential interaction
+networks corresponding to each sampling event, based on trait matching.
 
@@
 
+- Q1: diversity-stability, diversity-biomass in aquatic systems
+- Q2: Effect of horizontal and vertical diversity on total biomass and stablity
+- Q3:
+
 # Methods
@@
 matmet_cap <- paste0(
-  "Mat&met figure"
+  "(A) Conceptual model of the hypothesized relationships between environment,
+  species richness, network metrics and total biomass / biomass stability. ",
+  "Solid and dashed arrows represent respectively direct and indirect effects.
+  ",
+  "The blue, green and blue/green dashed arrows being respectively indirect
+  effects going through species richness, network metrics and through both
+  species richness and network metrics.",
+  "(B) Observation sites (black dots) were located across France and monitored
+  on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
+  "Inner borders draw the limits of the hydrographic basins. ",
+  "(C) The metaweb. Each trophic species (N = 412) is represented by a node and
+  each color represent a species (S = ). Resource nodes (7) were drawn in grey. ",
+  "(D) Subset over network variation through time."
 )
@@
 myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))
-p_st <- p_st +
-  theme(legend.position = "none")
+
 # Network inference
 net_method_path <- mypath("manuscript/bef_stability/figs",
-  "network_inference.pdf")
-net_method <- net_method_path %>%
-  magick::image_read()
+  "hypothesis.pdf")
+metaweb_path <- mypath("manuscript/bef_stability/figs",
+  "metaweb.png")
+library(magick)
+
 p_net_method <- cowplot::ggdraw() +
-  cowplot::draw_image(net_method)
-
-top <- plot_grid(p_st, p_net_method, ncol = 2, rel_widths = c(.8, 1), labels =
+  cowplot::draw_image(magick::image_read_pdf(net_method_path))
+p_metaweb <- cowplot::ggdraw() +
+  cowplot::draw_image(magick::image_read(metaweb_path))
+
+top <- plot_grid(p_net_method, p_st, ncol = 2, rel_widths = c(1, 1), labels =
   "AUTO")
-p_method <- plot_grid(top, temporal_network, nrow = 2, rel_heights = c(1, .3),
+bottom <- plot_grid(p_metaweb, temporal_network, ncol = 2,
+  rel_widths = c(1, 1), labels = c("C", "D"))
+
+p_method <- plot_grid(top, bottom, nrow = 2, rel_heights = c(1, 1),
   labels = c("", "C"))
+save_plot(
+  filename = mypath("manuscript/bef_stability/figs",
+    "method_fig.pdf"),
+  p_method, nrow = 2, ncol =2,
+  base_width = 7/2.54,
+  base_asp = 0.3
+)
 p_method
@@
 widely used to infer trophic interactions
-[@brose_predator_2019, @poisot_structure_2016, @schneider_body_2012]. Indeed,
+[@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012]. Indeed;
 the existence of an trophic interaction between two species have been reported
-to be largely dependant on their body size ratio [cascade model, @cohen_stochastic_1985, @warren_invertebrate_1987, @brose_predator_2019].
+to be largely dependant on their body size ratio
+[cascade model; @cohen_stochastic_1985; @warren_invertebrate_1987; @brose_predator_2019].
 
@@
 ratio as in many studies
-[@brose_predator_2019, @poisot_structure_2016, @schneider_body_2012].
+[@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012].
 For a given trophic species, we first determined if its size class end up in a
@@
 impose swimming constraints which filters fish species that can establish
-[@rolls_scaling_2018, @tonkin_flow_2018, @gutierrez-canovas_contrasting_2013].
+[@rolls_scaling_2018; @tonkin_flow_2018; @gutierrez-canovas_contrasting_2013].
 Water temperature is linked to physiological constraints namely thermal
@@
 Structural Equation Modeling (SEM) is one promising way  
-[@grace_structural_2008, @grace_causal_2014, @lefcheck_piecewisesem_2016,
+[@grace_structural_2008; @grace_causal_2014; @lefcheck_piecewisesem_2016;
 @grace_integrative_2016]. SEM makes possible to set causal relationships between
@@
 ```
+```{r}
+caption_indir_stab_sem <- paste0(
+  "Indirect and total effect of variables on biomass stability from the
+  structural equation model. Indirect effects are computed by multiplying the
+  path coefficients from the variable predictor to the response variable, here
+  biomass stability. Indirect effects are considered as one step from the target
+  variable. For exemple, the indirect effect of species richness on
+  biomass stability via its effect on CVsp is $-0.61$. To compute indirect
+  effect, only the significant direct effects were taken into account. ",
+  "Network structure being the indirect effect that went through both avg trophic
+  level and connectance and Species richness_Network structure being the
+  indirect effect that went through (i) species richness and from (ii) species
+  richness to network structure."
+
+)
+
+caption_indir_bm_sem <- paste0(
+  "Indirect and total effect of variables on total biomass from the
+  structural equation model. See the table (X) for details about computation and
+  meaning."
+
+)
+```
+
+```{r indir-bm, fig.cap = "Indirect effect from SEM"}
+format_table <- function (x = tmp_stab_indir_table) {
+  x <- x[, c("variable", names(x)[!names(x) %in% "variable"])]
+
+  rm_n <- str_remove_all(get_sem_var_name_replacement(), pattern = "\n")
+  names(rm_n) <- names(get_sem_var_name_replacement()) 
+  x$variable <- str_replace_all(x$variable, rm_n)
+
+  colnames(x) %<>% str_remove_all(., pattern = "via_")
+
+  col_replacement <- c(
+    variable = "Variable",
+    cv_sp = "CVsp",
+    sync = "Synchrony",
+    richness = "Horizontal diversity",
+    com = "Vertical diversity",
+    richness_com = "Horizontal & vertical diversity",
+    total = "Total effect"
+  )
+  colnames(x) %<>% str_replace_all(., col_replacement)
+
+  x
+}
+
+kable(format_table(tmp_bm_indir_table),
+  "latex",
+  booktabs = T,
+  caption = caption_indir_bm_sem
+  ) %>%
+kable_styling(latex_options =c("striped", "scale_down"))
+
+```
+
+```{r}
+stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
+# effect of env on stab
+env_on_stab <- get_env_on_stab(fit = stab_all_params, p_val_thl = 0.05,
+  type = "std")
+rich_on_stab <- get_rich_on_stab(fit = stab_all_params,
+  p_val_thl = 0.05, type = "std")
+com_on_stab <- get_com_on_stab(fit = stab_all_params,
+  p_val_thl = 0.05, type = "std")
+
+tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, com_on_stab),
+  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
+  ) %>%
+bind_rows()
+```
+
+```{r indir-stab}
+kable(format_table(tmp_stab_indir_table),
+  "latex",
+  booktabs = T,
+  caption = caption_indir_stab_sem 
+  ) %>%
+kable_styling(latex_options =c("striped", "scale_down"))
+```
 
@@
 ```{r get-sem-tot-effect-env}
-stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
 # effect of env on sync and cv_sp
@@
 
-```{r}
-# effect of env on stab
-env_on_stab <- get_env_on_stab(fit = stab_all_params, p_val_thl = 0.05,
-  type = "std")
-rich_on_stab <- get_rich_on_stab(fit = stab_all_params,
-  p_val_thl = 0.05, type = "std")
-com_on_stab <- get_com_on_stab(fit = stab_all_params,
-  p_val_thl = 0.05, type = "std")
-
-tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, com_on_stab),
-  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
-  ) %>%
-bind_rows()
-
-options(knitr.table.format = "latex")
-kable(tmp_stab_indir_table, "latex", booktabs = T, align = "c") 
-kable(tmp_bm_indir_table, "latex", booktabs = T, align = "c")
-
-#kable(rbind(
-  #mutate(tmp_stab_indir_table, type = "stab"),
-  #mutate(tmp_bm_indir_table, type = "bm")
-  #), "latex", booktabs = T, align = "c") %>%
-  #column_spec(1, bold=T) %>%
-  #collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
-```
-
 ## Biomass stability
@@
 richness. Overall, it contrasts with studies in grasslands
-[@tilman_biodiversity_2006, @zhang_scale_nodate], mesocosms
+[@tilman_biodiversity_2006; @zhang_scale_nodate]; mesocosms
 [@pennekamp_biodiversity_2018] or other animals [@olivier_independent_nodate]
@@
 as found in salt marshes, forests
-[@wu_relationship_2015,@li_relationship_2018]. The positive effect
+[@wu_relationship_2015;@li_relationship_2018]. The positive effect
 of species richness on total biomass might be due to resource use
@@
 total biomass. This result contradicts precedent theoretical studies on the
-relationship between stability and network structure [@angelis_stability_1975,
+relationship between stability and network structure [@angelis_stability_1975;
 @may_will_1972], although they considered different stability metrics (i.e.
@@
 Indeed, connectance generally decreased with increasing species richness
-[@winemiller_must_1989, @thebault_stability_2010]. It is an effect important to
+[@winemiller_must_1989; @thebault_stability_2010]. It is an effect important to
 consider the link between connectance and ecosystem properties, as this direct

### 2020-05-10 data-raw/polluants/03_moving_windows.R

@@ -55,7 +55,9 @@ monthly_avg_polluants %<>%
     parameter = str_replace_all(parameter, replace_rules)
     )
 # Yearly avg
-mysave(monthly_avg_polluants, dir = mypath("data-raw", "polluants"), overwrite = TRUE)
+mysave(monthly_avg_polluants,
+  dir = mypath("data-raw", "polluants"),
+  overwrite = TRUE)
 
 yearly_avg_polluants <- monthly_avg_polluants %>%
   mutate(year = year(year_month)) %>%

### 2020-05-11 manuscript/bef_stability/manuscript.Rmd
Introduction done

@@
 
-#### Biodiversity and ecosystem functioning
+#### Biodiversity and ecosystem properties
 
@@
 Current biodiversity losses question the ability of how ecosystems will be
-affected in turn.
-
-The relationship between biodiversity and ecosystem functioning has been a
-central research topic in ecology [@may_will_1972; @hector_plant_1999;
+affected in turn. Since 1970s, ecology aims to uncover the complex relationships
+between biodiversity and ecosystem properties [@may_will_1972; @hector_plant_1999;
 @loreau_biodiversity_2001; @hooper_effects_2005; @duffy_why_2009;
-@isbell_forest_quantifying_2018].
+@isbell_forest_quantifying_2018]. Because biodiversity largely determines in
+turn both quantity and distribution of biomass or energy across ecosystems, it
+has a tremendous effects on the properties exhibited by an ecosystem, such as
+its size (total biomass) [REF], its production (production of biomass by units of
+time) [REF] and the temporal stability of its biomass [REF].
+
+#### Horizontal and vertical diversity are two ways to look at biodiversity
+
+Biodiversity can be quantified in numerous ways, as the number of species, i.e.
+species richness [REF] and in number of functional groups, i.e species are
+gathered on what they do [REF]. Those metrics can be gathered into "horizontal
+diversity", describing the list of components present in a community. An
+orthogonal view, based on trophic chains, described species on what they eat. It 
+can be defined as interactions or biomass/energy fluxes between species and how
+they are distributed among species. The latter can be quantified as the number
+of interaction between species or the number of trophic level. This orthogonal
+view of seeing biodiversity, can be gathered into "vertical diversity".  
+Horizontal and vertical diversity are two views of quantifying biodiversity that
+are, however, not independent from each other [@zhao_horizontal_2019]. The add
+or removal of one species can have different effects depending on its vertical
+position in the trophic chain [REF duffy 2007]. Hence, it is crucial to
+study their interplay to increase our understanding of ecosystem dynamics.
+
+#### horizontal and vertical diversity increase total biomass by common and different mechanisms
+
+Horizontal and vertical diversity has been shown to promote higher biomass
+production in a variety of ecosystems. Horizontal diversity, as species richness, has been
+reported to increase productivity through complementarity between species in
+resource exploitation and selection effects in plant communities
+[@tilman_productivity_1996; @cardinale_resource_2001; @grace_integrative_2016].
+Regarding total biomass, empirical assessment have
+shown generally positive relationships with species richness in plant
+communities [@hector_plant_1999; @tilman_biodiversity_2014, but see
+@grace_integrative_2016], as in mesocosms [@pennekamp_biodiversity_2018].
+Theoretical models have also confirmed that an increase in horizontal diversity should
+translate into increase in plant biomass  through
+resource complementarity [@loreau_biodiversity_1998] and selection effects [@tilman_plant_1997]. The
+addition of trophic levels, notably consumer on plants generally breaks the
+positive relationship between plant biomass and plant diversity as a significant
+amount of biomass is transfered to consumers. It has been shown both in
+experiments [REF] and theoretical models [@thebault_food-web_2003]. Futhermore,
+at higher trophic level, the resource complementary of consumers can increase as
+the number of consumer species increase [@thebault_food-web_2003]. However, the
+joint effects of horizontal and vertical diversity on total biomass has been
+rarely tested. It is not clear whether horizontal and vertical diversity just
+change the distribution of biomass across trophic level or it increases the
+total amount of  biomass.
+
+One reason might be the focus on plant communities, which are relatively easy to
+manipulate and have an important role on determining the quantity and quality of
+biomass for the other compartments of ecosystems [REF]. One trophic level is
+often considered, and so the comp
 
@@
 
-#### Shape of BEF: total biomass
-
-Species richness has been reported to increase productivity
-[@tilman_productivity_1996; @grace_integrative_2016] through complementarity
-between species in resource exploitation and selection effects
-[@loreau_partitioning_2001; @cardinale_species_2002; @fargione_selection_2007].
-Empirical assessment of the effect of species richness on total biomass showed
-negative [@grace_integrative_2016] and positive relationships
-[@hector_plant_1999; @tilman_biodiversity_2014]. @grace_integrative_2016 showed
-that the results depend on the refinement of the mecanisms involved in the
-analysis.
-
-#### Shape of BEF: stability
-
-The relationship between species richness and stability is even more complex
-partly because of the inherent multidimensionality of stability
-[@donohue_dimensionality_2013; @donohue_navigating_2016] and because of the
-different metrics of stability privileged in theoretical (stability of local
-equilibrium, robustness to primary extinction) and empirical work (variability
-of abundance or biomass through time). Empirical studies showed consistently
-that species richness decreased community variability in grasslands
-[@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018] and
-vertebrates [@olivier_independent_nodate; @franssen_annual_2011]. Two mecanisms
-are involved into community variability, (1) species variability and (2) the
-species synchrony [@loreau_species_2008; @thibaut_understanding_2013].  Positive
-[@tilman_biodiversity_2006], neutral [@jiang_different_2009;
-@olivier_independent_nodate] and negative [@franssen_annual_2011;
-@olivier_independent_nodate] relationships between species variability and
-species richness have been found. On the other side, studies consistently found
-that species richness decreased synchrony between species [@loreau_species_2008;
-@thibaut_understanding_2013; @bluthgen_land_2016; @olivier_independent_nodate].
-Beyond species richness, species interactions, which modifies species abondance
-and biomass and make species dynamics interdependant, have been largely ignored
-in empirical assessment.
-
-#### BEF: Theoretical ecology
-
-Conversely, theoretical ecology display an extensive literature about the
-effects of network structure on stability [@may_will_1972;
-@angelis_stability_1975; @stouffer_compartmentalization_2011;
-@thebault_stability_2010; @barbier_pyramids_2019;
-@shanafelt_david_w._stability_nodate].  Theoretical ecology generally uses
+#### Horizontal and vertical diversity stability
+
+Horizontal and vertical diversity also affects the stability of ecosytem
+properties. Experimental studies showed consistently that species richness
+increase temporal biomass stability in grasslands [@tilman_biodiversity_2006],
+mesocosms [@pennekamp_biodiversity_2018]. While in natural communities,
+same relation has been found for temporal biomass stability in stream fish communities 
+[@franssen_annual_2011] and temporal abundance stability of birds and butterfies
+[@olivier_independent_nodate, but not bats]. Two mecanisms are involved into
+temporal stability of communities, (1) synchrony and (2) variability
+[@loreau_species_2008; @thibaut_understanding_2013]. Synchrony mesures the
+covariation of species through time. Very low synchrony indicates compensatory
+temporal variation between species and so increased temporal stability. studies
+consistently found that species richness decreased synchrony between species
+[@loreau_species_2008; @thibaut_understanding_2013; @bluthgen_land_2016;
+@olivier_independent_nodate]. (*Should I add more details about the
+mecanisms?*). The average temporal variability of species is measured as a
+average coefficient of variation of species, weighted by species
+abundance/biomass. Higher species temporal variabiliy thus results in lower
+temporal stability. Positive [@tilman_biodiversity_2006], neutral
+[@jiang_different_2009; @olivier_independent_nodate] and negative
+[@franssen_annual_2011; @olivier_independent_nodate] relationships between
+species variability and species richness have been found. Hence, synchrony
+has been found to be the main driver of temporal
+stability [@tilman_biodiversity_2006; @olivier_independent_nodate] and
+responsible for the positive relationship between horizontal diversity and
+temporal stability of biomass and abundance.
+
+Vertical diversity, represented by network structure, has been central to the
+the literature of diversity-stability debate and largely explored by theoretical
+ecology [@may_will_1972; @angelis_stability_1975;
+@stouffer_compartmentalization_2011; @thebault_stability_2010;
+@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate]. Because species
+interactions make species dynamics interdependant, they have a tremendous role
+on stability notably through its effects on the propagation of perturbation.
+However, it is important to note that theoretical ecology generally uses
 stability definitions related to community equilibrium and its stability to
-small perturbations.  Connectance (i.e. proportion of realized links in a
-network) can decrease [@angelis_stability_1975; @thebault_stability_2010] or
-increase resilience of trophic network depending on the functioning of networks
-[@angelis_stability_1975].  The number of trophic levels, the vertical position
-in the trophic network as well as the strength of their biomass regulation (i.e.
-top-down and bottom-up) can determine biomass and stability at equilibrium
-[@hurd_stability_1971; @shanafelt_david_w._stability_nodate;
-@zhao_horizontal_2019; @barbier_pyramids_2019].
-
-A large inconsistency remains between theoretical and empirical assessments of
-the relationship between community structure and ecosystem properties.
-Theoretical studies have ignored temporal variability and then the relative
-contribution of synchrony and species variability on community variability while
-empirical studies about temporal variability and total biomass in natural
-communities have ignored the contribution of network structure.
-
-Our goal was to assess the mecanisms determining temporal variability and total
-biomass in natural communities while integrating both species richness and
-network structure. We combined together the effect of vertical and horizontal
-diversity and thus aimed to bridge the current gap between theoretical and
-empirical studies. We used an standardized monitoring of fish communities in
-french streams. More than three hundreds sites were followed more than 10 years
-on the 1995-2018 period. We inferred four thousands potential interaction
-networks corresponding to each sampling event, based on trait matching.
-
-We investigated the effects of the community structure on total biomass and
-community variability, which in turn determine community variability. We have
-also included the effect of environmental drivers [@grace_integrative_2016]
-which can directly affect community variability or indirectly via community
-structure.
+small perturbations [@may_will_1972; @angelis_stability_1975;
+@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate] or to the number
+of secondary extinctions of perturbation [@duffy_why_2009]. Those stability 
+metrics harly relates to empirical temporal stability [see
+@arnoldi_resilience_2016]. However, the work of @thebault_trophic_2005 shows
+that asynchrony consistenly increase temporal stability and the positive
+relationship between temporal stability and species richness. However asynchrony
+can also increase species variability through interspecic competition, which
+amplifies species fluctuations. Furthermore species interactions, considered as 
+as competition strength and niche breath of consumers can results in negative or
+positive temporal stability-species richness relationships
+[@thebault_trophic_2005]. Vertical diversity, as network structure, can have
+strong effects on temporal stability. However, there are few assesments of the
+effects of horizontal and diversity on temporal stability in natural
+communities.
+
+#### Stream fish communities is a good model to study effects of horizontal & vertical diversity
+
+Stream fish communities constitutes good model to study the joint effects of
+horizontal & vertical diversity on total biomass and the temporal stability of
+biomass. Despite that fish trophic interactions are not recorded in nature, a
+consequent body of litterature supports that they can be infered through body
+size and diet informations [@gravel_inferring_2013; @jennings_weak_2001;
+@brose_predator_2019]. Most of the biomass-diversity and
+stability-diversity relationships have been assessed in terrestrial ecosytems
+while there is a evident need to test such relationships in a variety of
+ecosystem types. Stream ecosystems are caracterized by the flowing water and
+depends for the large part from the input of terrestrial ecosystems
+. Furthermore, the biotic activity in stream ecosystems
+determines for a large part the water quality [@cummins_structure_1974] and thus  
+are crucial to maintain **human selfish goals (I can do better than that)**.
+
+#### Environment plays a big role in structuring communities
+
+Environment also largely structure communities and is important to take in
+account when considering natural communities. Environment directly affects
+organism performance, and subsequently, abundance of species and in turn
+determines total biomass [Add general ref; @grace_integrative_2016] and temporal
+stability [@de-boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
+@oliver_heterogeneous_2010; @fried-peterson_drivers_2020]. Hydrology of streams
+constraints the composition of fish communities [REF toulouse à balle], and is
+also related to fish population temporal stability [@franssen_annual_2011].
+However it is not clear which is the relative strength of direct and indirect
+effects of environment on total biomass and its temporal stability (Figure
+\@ref(fig:matmet) A).
+
+#### SEM is perfect and our metamodel too
+
+To reveal the direct and indirect effects of environment, horizontal & vertical
+diversity on both total biomass and its temporal stability, we used Structural
+Equation Modeling (SEM). It is one promising way to go beyond bivarite
+relationships and to investigate complex relationships, direct and indirect,
+between variables  [@grace_structural_2008; @grace_causal_2014;
+@lefcheck_piecewisesem_2016; @grace_integrative_2016]. SEM makes possible to set
+causal relationships between variables. This step can be critical, as the
+estimated parameters can be determined by both the choice of the variables and
+the links between them.  Therefore, the set of variables and links shoud be
+supported by theory and litterature. We built a metamodel (set of variables and
+links between them). Basically, we tested the links between environmental
+conditions, horizontal & vertical diversity and both total biomass and its temporal
+stability (Figure \@ref(fig:matmet) A). We considered that environment can
+directly affect horizontal and vertical diversity, as well as total biomass and
+its temporal stability. Horizontal diversity, measured as species richness
+directly affects vertical diversity, total biomass and
+its temporal stability. Food web structure was shown to be constrained by
+species richness. In turn vertical diversity affects total biomass and
+its temporal stability (Figure \@ref(fig:matmet) A). Two other questions can
+only be answered when considering both direct & indirect relationships. (1) What
+is the magnitude of environmental effects on total biomass and
+its temporal stability compared to horizontal and vertical diversity? (2) Which
+is the pathway of environment, horizontal & vertical diversity on total biomass
+and its temporal stability ? (2a) For environment, is it mainly (i) direct,
+indirect (ii) through horizontal diversity, (iii) through horizontal & vertical
+diversity or (iv) indirect through only vertical diversity? (2b) For horizontal
+diversity, is it mainly (i) direct, or (ii) indirect through vertical diversity?
+Finally for temporal stability, how do environement, horizontal & vertical
+diversity affect synchrony & species stability ?
+
+We used an standardized monitoring of fish communities in french streams. 99
+sites were followed more than 10 years on the 1995-2018 period. We inferred
+(**XXX**) potential interaction networks corresponding to each sampling event,
+based on trait matching. Horizontal diversity was measured as species richness
+while vertical diversity was as connectance and average trophic level.
+Environment was characterized by the stream size, temperature, flow,
+enrichment, altitude and their stability (expect for altitude). Finally total
+biomass was measured as median total biomass over the sampling period while its
+temporal stability was quantified as the inverse of the CV.
+
+Mid point used in niche model to characterize feeding links [@dunne__2006]
 
@@
 - Q2: Effect of horizontal and vertical diversity on total biomass and stablity
-- Q3:
+- Q3: Relative contribution of environment and community structure to biomass
+  and stability
 
@@
 
-We seeked to disantangle the unravel the links between
-environment and community structure on both biomass stability and total biomass.
-To investigate complex relationships, direct and indirect, between variables,
-Structural Equation Modeling (SEM) is one promising way  
-[@grace_structural_2008; @grace_causal_2014; @lefcheck_piecewisesem_2016;
-@grace_integrative_2016]. SEM makes possible to set causal relationships between
-variables. This step can be critical, as the estimated parameters can be
-determined by both the choice of the variables and the links between them.
-Therefore, the set of variables and links shoud be supported by theory and
-litterature.
-
-We built a metamodel (set of variables and links between them). Basically, we
-tested the links between environmental conditions, community structure and
-ecosystem properties namely biomass stability on total biomass. Theory in
-ecology predicts that community structure influences stability. In turn,
-environment influences community structure but also directly stability.
-
 #### Variables

### 2020-05-26 manuscript/bef_stability/appendix.Rmd
Fix PCA plot

@@
 ---
-title: Appendix of Complex mecanisms linking biomass stability and total biomass with species richness and network structure in stream ecosystems 
+title: Appendix
 author: Alain Danet, Maud Mouchet, Elisa Thebault and Colin Fontaine
@@
 ```{r, echo = FALSE, message = FALSE, collapse = FALSE}
+
 mypath <- rprojroot::find_package_root_file
@@
 dest_dir <- mypath("data", "species")
+
+load(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
 
@@
   warning = FALSE,
-  results = FALSE
-)
-knitr::opts_chunk$set(
-  cache = FALSE,
-  collapse = TRUE,
-  comment = "#>",
-  fig.dim = c(7, 7),
-  fig.show = "hold",
-  echo = FALSE,
-  message = FALSE,
-  warning = FALSE
+  results = TRUE 
 )
@@
 library(kableExtra)
+library(sf)
 source(mypath("R", "misc.R"))
@@
 # Load manuscript results
-load(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
 ```
@@
 ```{r}
-
 ```
@@
 The fish community sampling took place in a variety of stream size, shape and
-depth. This diversity constraints the type of protocol that can take place.
-For the small streams (depth < 0.7m across the entire width), the complete protocol
+depth. This diversity constraints the type of protocol that can take place.  For
+the small streams (depth < 0.7m across the entire width), the complete protocol
 is used. It consists in placing anodes every X meter across the width of the
-river. **Add the precise procedure?**
-The fishermen made from one to three row of fishing. We kept only the first row
-for analysis.
-For deeper and wider streams, the sampling was partial over the bank and the
-channel and performed by boat and by foot (along the bank). We kept only
-sampling done over the bank because channel sampling was not always done.
-Two types of partial protocols takes place: partial over bank and partial by
-points. The former is continuous while the latter is discrete. Furthermore, in
-partial by point protocol the channel can be sampled as well. We kept only the
-partial by point fish sampling which all the sampling point were done over the
-bank to homogenize the sampling. Then, we merged partial over bank and partial
-over point protocols. Some sampling stations had mix characteristics in which mix of
+river (**Add the precise procedure?**). The fishermen made from one to three row
+of fishing. We kept only the first row for analysis to homogenize the sampling
+effort. For deeper and wider streams, the sampling was partial over the bank and
+the channel and performed by boat and by foot (along the bank). We kept only
+sampling done over the bank because channel sampling was not always done.  Two
+types of partial protocols takes place: partial over bank and partial by points.
+The former is continuous while the latter is discrete. Furthermore, in partial
+by point protocol the channel can be sampled as well. We kept only the partial
+by point fish sampling which all the sampling point were done over the bank to
+homogenize the sampling.  Then, we merged partial over bank and partial over
+point protocols. Some sampling stations had mix characteristics in which mix of
 partial and complete protocols were applied depending of the depth of the river
@@
 
+Heterogeneity in the sampling period may introduce variability that is not related
+to ecological processes such as the presence of juveniles. In order to reduce
+heterogeneity in sampling time, only one sampling per year was retained if there
+was two in a given year, the one with with the most species and then individual
+collected. Finally, most of the fish sampling occurred in September (Median:
+mid-August) and the median standard deviation of the sampling month was inferior
+to one (0.7) within station. Additionally, we removed sampling events, in a
+given station, which the sampled length along the stream was outside the median
+length sampled more or less 30%. Finally, we standardadized the biomass record
+and species richness by the sampled surface to get rid of sampling effort
+effects.
+
 ### Batches definition and body size measurement
+
 During the electric fishing, and before that fish body size are measured, they
@@
   select(opcod, species, length)
+
 length_sem_analysis <- fish_length %>% 
   filter(opcod %in% op_analysis_bbb$opcod)
+rm(fish_length, lot_id_opcod)
+nrow_fish_length <- nrow(length_sem_analysis)
 na_length <- sum(is.na(length_sem_analysis$length))
@@
 analysis, `r na_length` individuals had missing length over 
-`r nrow(fish_length)` individuals.
+`r nrow_fish_length` individuals.
 
@@
 
-## Network inference
+### Metaweb
+
+#### Ontogenic diet
+
+Diet information were obtained from fishbase.org and literature [REF willem?]. The
+diet information contained from two to three life stages by species, the life
+stages being defined by the body size of the fishes. Over the 57 fish species,
+only seven had a piscivorous life stage and only three had as strict piscivorous
+life stage. Fish species were largely omnivorous.
+
+#### Define trophic interactions
+
+```{r}
+trophic_building_caption <- paste0(
+  "Trophic species"
+) 
+```
+
+```{r p-net-inf, fig.cap=trophic_building_caption}
+knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "network_inference.pdf"))
+```
 
@@
 
+The metaweb described the potential trophic interactions between the
+($`r ncol(metaweb_analysis$metaweb) - length(metaweb_analysis$resource)`$) trophic species.
+We had seven resource nodes which were present in the diet of the trophic
+species namely detritus, biofilm, phytoplankton, zooplankton, macrophages,
+phytobenthos and zoobenthos.
+
 The metaweb building was based on trait matching, so it necessitates to have
@@
 
-** I question myself if I should move the network inference figure here and
-just let the temporal network in the main text. May be even add the temporal
-biomass plot (species/trophic species) in the main text**
+A trophic species belonged to a life stage if the median of its body size range
+fell in the range of the life stage. In turn, this trophic species has feeding
+interactions with the resource nodes of its life stage. Interactions between
+resource nodes were determined by literature. For example, phytobenthos fed on
+detritus, while zooplankton fed on zooplankton and phytoplankton. Fish-fish
+trophic interactions between a predator and a prey were determined by body size
+ratio as in many studies [@brose_predator_2019; @poisot_structure_2016;
+@schneider_body_2012].  For a given trophic species, we first determined if its
+size class end up in a life stage containing piscivorous diet, i.e. if there was
+an overlap between them. We were more liberal for piscivory determination to not
+miss potential fish-fish trophic interactions which were the main interactions
+in our community. If the trophic species was piscivorous, we determined its prey
+size range from 3% to 45% of the median of its size range. A trophic interaction
+was set for each trophic species whose median of its size class fell into the
+prey range of the predator trophic species. To sum up, the metaweb was obtained
+with allometric feeding interactions (1) between trophic species, (2) between
+trophic species and resource nodes and (3) between resource nodes.
+
+#### Obtain network of a community
+
+The trophic network of a community (i.e. one network for each fish community
+sampling) was obtained by determining the trophic species of each fish
+individual in the community and interactions were set according to the metaweb.
+All the resource nodes were assumed to be present in each local network.
+Finally, the structure of the local networks varied according the presence of
+the trophic species. The inferred interactions represent potential interactions
+(i.e. not measured interactions) and are binary (i.e. presence or absence of
+feeding interactions).
 
@@
 
-```{r}
+```{r, fig.height = 20/2.54}
 myload(fourier, dir = mypath("data-raw", "polluants"))
-# Where is DBO?
+myload(flow_temp_metrics, dir = mypath("data"))
+sf_pressure <- station_analysis %>% 
+  select(id) %>%
+  left_join(rename(pca_pressure, id = station)) %>%
+  na.omit()
+
+p <- ggplot() +
+  geom_sf(data = the_8_hydrologic_basin)
+
+var_to_plot <- colnames(sf_pressure)[
+  !colnames(sf_pressure) %in% c("id", "geometry")]
+var_replacement <- c(
+  "slope" = "Slope",
+  "alt" = "Altitude",
+  "d_source" = "Distance from source",
+  "strahler" = "Strahler order",
+  "width_river_mean" = "Average stream width",
+  "avg_depth_station_mean" = "Average stream depth",
+  "width_river_cv" = "CV of stream width",
+  "avg_depth_station_cv" = "CV of stream depth",
+  "DBO_med" = "Average BOD",
+  "flow_med" = "Average flow",
+  "temperature_med" = "Average temperature",
+  "DBO_cv" = "CV of BOD",
+  "flow_cv" = "CV of flow",
+  "temperature_cv" = "CV of temperature"
+)
+
+map_pressure <- map(var_to_plot,
+~p +
+  geom_sf(data = sf_pressure, aes_string(color = .x)) +
+  labs(title = str_replace_all(.x, var_replacement)) +
+  theme(legend.title = element_blank(),
+    axis.text = element_blank(),
+    axis.ticks = element_blank()
+  )
+)
+
+plot_grid(plotlist = map_pressure, ncol = 2)
+
 ```
 
-For BOD, we removed measurements that were expressed in uncommon units.
-
-The first goal was to harmonize the different variables and scale it to the
-timescale of fish sampling, we took annual average of each variables. To reduce 
-daily or seasonal effects, we first applied average data with the moving
-window of one year. For temperature, the moving was performed on daily average
-temperature. Then we took the annual average of each year and each variable.
+The time resolution was heterogeneous according to the variable considered
+(hourly, daily and monthly for temperature, flow and BOD resp.). For each recording
+station, we applied a moving window averaging (more details in supplementary
+material) to get rid of seasonal effects. For temperature, the moving was performed on daily
+average temperature. Then we took the annual average of each year and each
+variable (i.e. one value by year and by station).
 
@@
 we used the linear-sill and mariah functions for taildown and tailup
-autocovariance, according to their performance of prediction. The interpolations
+autocovariance, according to their prediction performance. The interpolations
 were done with the `SSN` R package 
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE}
 myload(cv_press_interp_mv_avg,
@@
     x %>%
-      group_by(basin, year) %>%
-      summarise_if(is.numeric, list(avg = ~mean(., na.rm = TRUE))) %>%
+      select(basin, year, bias, std.bias, RMSPE, std.MSPE) %>%
+      group_by(basin) %>%
+      summarise_if(is.numeric, list(avg = ~mean(., na.rm = TRUE), sd = ~sd(., na.rm = TRUE))) %>%
       mutate(Variable = y) %>%
-      select(Variable, basin, year, everything()) %>%
+      select(Variable, basin, everything()) %>%
       ungroup
@@
 
-```{r, fig.show = "hide"}
-axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
-p_l_rot <- map(axis_pair, 
-  function (axis)
-    pca_rotated_plot <- plot_rotated_pca(
-      pca_rotated = pca_rotated,
-      axis = axis 
+```{r eig-plot}
+rotated_eigen_values <- 
+  tibble(
+    name = paste0("RC", seq(1,14)),
+    type = c(rep("Kept", 5), rep("No kept", 9)),
+    value = pca_rotated$rotated$values
   )
+eigen_rotated_plot <-
+  ggplot(rotated_eigen_values,
+    aes(x = reorder(name, -value) , y = value)) +
+  geom_col(aes(fill = type)) +
+  scale_fill_discrete(name = "Status") +
+  labs(x = "Rotated component", y = "Eigen values")
+```
+
+```{r contrib-pca}
+#https://stats.stackexchange.com/a/143949
+caption_contrib_pca <- paste0(
+  "Loadings of variable to rotated components of the PCA.
+  Loadings are the coefficients which determine the components of the PCA as
+  linear combinations of the variables.
+  "
 )
+
+loadings_pca <- matrix(
+  as.matrix(round(pca_rotated$rotated$Structure, 2)),
+  nrow = 14,
+  dimnames = dimnames(pca_rotated$rotated$Structure)
+  ) %>%
+  as_tibble %>%
+  mutate(
+    Variable = str_replace_all(
+      dimnames(pca_rotated$rotated$Structure)[[1]],
+      pca_var_replacement)
+  ) %>%
+  select(Variable, RC1, RC2, RC3, RC4, RC5)
+
+kable(
+  x = loadings_pca,
+  format = "latex",
+  booktabs = T,
+  label = "contrib-pca",
+  caption = caption_contrib_pca
+  ) %>%
+kable_styling(latex_options = c("striped", "scale_down"))
+```
+
+```{r}
+corr_pca_caption <- paste0(
+  "Spearman correlation between environmental variables used in the PCA.
+  The variables have been scaled before to compute the correlation."
+)
+
+pca_var_correlation <- pca_pressure %>%
+  select(-station) %>%
+  #mutate_all(scale) %>%
+  as.matrix() %>%
+  cor(., method = "spearman")
+
+pca_var_correlation %<>% round(., 2)
+dimnames(pca_var_correlation) %<>%
+  map(., ~str_replace_all(.x, get_pca_var_name_replacement()))
+
+kable(
+  x = pca_var_correlation,
+  format = "latex",
+  booktabs = T,
+  label = "corr-pca",
+  caption = corr_pca_caption
+  ) %>%
+kable_styling(latex_options = c("striped", "scale_down"))
 ```
@@
   average temperature and negatively related to the river slope and altitude.
-  (B) Axis 3 was negatively related to the CV of flow and average enrichment.
-  Axis 4 was related to the CV of river size. Finally, axis 5 was related to the
-  CV of enrichment.")
+  (B) Axis 3 was negatively related to the CV of stream size.
+  Axis 4 was related to the CV of enrichment.
+  Finally, axis 5 was related to the CV of flow and average enrichment.")
 ```
 
-```{r pca-rotated, fig.cap = pca_caption}
-to_plot <- c(1, 6, 7)
-plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
-  ncol = length(to_plot), labels = LETTERS[1:3])
+```{r pca-rotated, fig.cap = pca_caption, fig.asp = 1}
+p1 <- my_pca_plot(xaxis = "RC1", yaxis = "RC2", ctb_thld = .4)
+p2 <- my_pca_plot(xaxis = "RC3", yaxis = "RC4", ctb_thld = .4)
+p3 <- my_pca_plot(xaxis = "RC4", yaxis = "RC5", ctb_thld = .4)
+
+pca_plot <- plot_grid(p1, p2, p3, eigen_rotated_plot, nrow = 2)
+save_plot(
+  filename = mypath("manuscript", "bef_stability", "figs", "pca_plot.pdf"),
+  pca_plot,
+  nrow = 2, ncol = 2,
+  base_height = 6/2.54, base_asp = 1, base_width = NULL 
+  )
+pca_plot
 ```
@@
 
+```{r }
+rc2 <- tibble(
+  station = pca_pressure$station,
+  alt = pca_pressure$alt,
+  temperature_med = pca_pressure$temperature_med,
+  value = pca_rotated$rotated$scores[,"RC2"]
+)
+
+rc2_sf <- station_analysis %>%
+  select(station = id) %>%
+  filter(station %in% rc2$station) %>%
+  left_join(rc2, by = "station")
+
+caption_rc2_map <- paste0(
+  "Map of the station values for the second axis of the rotated PCA."
+)
+```
+
+```{r rc2-map, fig.cap = caption_rc2_map}
+p +
+  geom_sf(data = rc2_sf, aes(color = log(value + abs(min(value)) + 1 ))) +
+  labs(title = "RC2 (Log)") +
+  theme(legend.title = element_blank())
+```
+
+```{r pca-two-axis, eval = FALSE}
+two_axis <- compute_rotated_pca(.data = pca_pressure, naxis = 2)
+two_axis$rotated$Vaccounted
+
+cor(two_axis$rotated$score[,c("RC1", "RC2")],
+  pca_rotated$rotated$score[,c("RC1", "RC2")])
+```
+
 ## Model summary and diagnostics
 
-####  SEM indirect and total effect
+### Data transformation
 
-### Model linear Relationship
+Additionally, we logged the axis one, two and three to normalize their
+distribution and we reversed the third axis to get increasing average
+temperature with increasing values of the axis and so decreasing values of
+altitude.
+
+```{r}
+sem_variable_table <- tibble(
+  variable = c(paste0("PCA axis", seq(1, 5)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
+  unit = c(rep("unitless", 5), "# by square meter", rep("unitless", 4), "gram by square meter"
+    ),
+  transformation = c(rep("Log base 10", 3), rep("No", 2), "Log base 10", rep("No", 2), rep("Log base 10", 3)),
+  interpretation = c(rep("", 11)) 
+) %>%
+kable(
+  format = "latex",
+  booktabs = T,
+  caption = "Variable description and transformation"
+  ) %>%
+kable_styling(latex_options = c("striped", "scale_down"))
+```
+
+### SEM hypothesis
+
+We linked environmental variables both to community structure and stability
+components. Rooted in assembly theory, environment filters species that can
+establish in a community and thus affect community structure. (+ add specific
+hypothesis about physical and climate). (1) We hypothesized that enrichment
+(characterized by DBO) and mean annual temperature will increase species turnover
+[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
+decrease biomass stability directly without going by community structure. First,
+instability of habitat and environmental factors may in turn drive biomass
+instability [@hansen_climate_2013]. Secondly, average environmental conditions
+such as enrichment can increase directly CV by increasing species biomass
+fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
+to decrease stability through starvation resulting from high metabolic activity
+[@tabi_warming_2019].
+
+---
+# Species richness to community attributes 
+---
+To reveal the mechanisms behind the relationship between species richness and
+biomass stability, causal links were set from species richness to other
+community attributes. In particular, species richness decreased connectance
+following results from @thebault_stability_2010; @winemiller_must_1989. But
+theoretically, some ecological networks can show the inverse relationship
+[@winemiller_must_1989]. (6) We hypothesized also that species richness will
+modulate average weighted trophic level because of food web assembly processes.
+A community with more fish species can support higher trophic level. Finally, we
+set up causal relationships from community attributes to stability components.
+
+---
+#  Community attributes to stability
+---
+We hypothesized that (7) species richness decreased synchrony between species
+[@loreau_species_2008] and increased $\overline{CV_{sp}}$
+[@tilman_biodiversity_2006]. (8a) We expected that average trophic level had a
+positive or negative relationship with synchrony, bottom-up effects should
+result in positive whereas top-down in negative relationships. We expected a (8b)
+negative relationship between average trophic level and $\overline{CV_{sp}}$ if
+predators stabilised prey fluctuations or if the increasing part of
+biomass in the predators decreased $\overline{CV_{sp}}$ because of their higher
+body mass (if mean increase faster than variance). (9a) Connectance was expected
+to decrease or increase $\overline{CV_{sp}}$ and (9b) synchrony because of top
+down effects or bottom up effects.
+
+## Model linear Relationship
+
+### Variables
 
@@
 hist_var_caption <- paste0(
-  "Distribution of the variables used in the Structural Equation Modeling."
+  "Distribution of the variables (before transformation) used in the Structural Equation Modeling."
 )
 ```
-
 ```{r hist-sem-data, fig.cap = hist_var_caption}
@@
   booktabs = T,
-  caption = caption_indir_bm_sem
+  caption = "Variance Inflation Factor for the linear models used in structural
+  equation modeling"
   ) %>%
@@
 ```{r}
-
 est_bm_sem_caption <- paste0(
@@
 ```{r tab-coeff-bm, fig.cap = "Coefficient"}
-
 # Replacement rules for term
@@
 kable_styling(latex_options = c("striped", "scale_down"))
+```
+
+### Robustness to different dataset selection
+
+```{r sensitivity, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset", cache = TRUE}
+library(furrr)
+
+myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
+myload(biomass_ts_sax, dir = mypath("data"))
+op_analysis_bbb <- filter(op_analysis, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+
+#myload(network_metrics, dir = mypath("data", "classes"))
+sem_sensivity_data <- list(full = op_analysis, bbb = op_analysis_bbb,
+  without_holes = op_analysis_wo_holes, bbb_without_holes = op_analysis_wo_holes_bbb)
+
+sem_stab_l_data <- furrr::future_map(sem_sensivity_data,
+
+  ~build_dataset_get_sem_coefficient(
+    .op = .x,
+    sem_fun = compute_stab_sem_rich
+)
+  )
+
+nb_station <- map_int(sem_sensivity_data, ~length(unique(.x$station)))
+
+sem_stab_results <- map(sem_stab_l_data,
+  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
+  enframe() %>%
+  rename(dataset = name) %>%
+  unnest(value)
+
+# Reformat
+colnames(sem_stab_results) <- str_to_lower(colnames(sem_stab_results))
+sem_stab_results %>%
+  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
+  ggplot(aes(x = r_p, y = std.estimate)) +
+  geom_point(aes(color = dataset)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+
+```{r sem-sens-bm, cache = TRUE, fig.cap = "Sensivity analysis for Biomass"}
+sem_bm_l_data <- furrr::future_map(sem_sensivity_data,
+  ~build_dataset_get_sem_coefficient(
+    .op = .x,
+    sem_fun = compute_prod_sem_rich)
+)
+sem_bm_results <- map(sem_bm_l_data,
+  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
+  enframe() %>%
+  rename(dataset = name) %>%
+  unnest(value)
+
+# Reformat
+colnames(sem_bm_results) <- str_to_lower(colnames(sem_bm_results))
+sem_bm_results %>%
+  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
+  ggplot(aes(x = r_p, y = std.estimate)) +
+  geom_point(aes(color = dataset)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
 ```

### 2020-05-26 manuscript/bef_stability/manuscript.Rmd
Fix PCA plot

--- 2020-05-10 manuscript/bef_stability/manuscript.Rmd
@@
 ---
-title: Complex mecanisms linking biomass stability and total biomass with species richness and network structure in stream ecosystems 
+title: Horizontal and vertical diversity drive total biomass and its temporal stability in fish communities
 author: Alain Danet, Maud Mouchet, Elisa Thebault and Colin Fontaine
@@
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, results = FALSE}
 mypath <- rprojroot::find_package_root_file
@@
 
+```{r}
+knitr::opts_chunk$set(
+  results = TRUE 
+)
+```
+
 # Abstract
@@
 
-#### Biodiversity and ecosystem functioning
-
-Biodiversity is essential to determine and maintain ecosytem properties.
-Current biodiversity losses question the ability of how ecosystems will be
-affected in turn.
-
-The relationship between biodiversity and ecosystem functioning has been a
-central research topic in ecology [@may_will_1972; @hector_plant_1999;
-@loreau_biodiversity_2001; @hooper_effects_2005; @duffy_why_2009;
-@isbell_forest_quantifying_2018].
-
-Studies in
-Bioversity-Ecosystem
-Functioning (BEF) usually quantify species diversity as species richness (i.e
-number of species) while ecosystem functioning is quantified as total biomass,
-productivity (biomass produced by unit of time) or stability which is quantified
-in more diverse ways such as the variability of species abundance, the
-resilience to perturbation, or resistance to perturbation
-[@donohue_navigating_2016].
-
-#### Shape of BEF: total biomass
-
-Species richness has been reported to increase productivity
-[@tilman_productivity_1996; @grace_integrative_2016] through complementarity
-between species in resource exploitation and selection effects
-[@loreau_partitioning_2001; @cardinale_species_2002; @fargione_selection_2007].
-Empirical assessment of the effect of species richness on total biomass showed
-negative [@grace_integrative_2016] and positive relationships
-[@hector_plant_1999; @tilman_biodiversity_2014]. @grace_integrative_2016 showed
-that the results depend on the refinement of the mecanisms involved in the
-analysis.
-
-#### Shape of BEF: stability
-
-The relationship between species richness and stability is even more complex
-partly because of the inherent multidimensionality of stability
-[@donohue_dimensionality_2013; @donohue_navigating_2016] and because of the
-different metrics of stability privileged in theoretical (stability of local
-equilibrium, robustness to primary extinction) and empirical work (variability
-of abundance or biomass through time). Empirical studies showed consistently
-that species richness decreased community variability in grasslands
-[@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018] and
-vertebrates [@olivier_independent_nodate; @franssen_annual_2011]. Two mecanisms
-are involved into community variability, (1) species variability and (2) the
-species synchrony [@loreau_species_2008; @thibaut_understanding_2013].  Positive
-[@tilman_biodiversity_2006], neutral [@jiang_different_2009;
-@olivier_independent_nodate] and negative [@franssen_annual_2011;
-@olivier_independent_nodate] relationships between species variability and
-species richness have been found. On the other side, studies consistently found
-that species richness decreased synchrony between species [@loreau_species_2008;
-@thibaut_understanding_2013; @bluthgen_land_2016; @olivier_independent_nodate].
-Beyond species richness, species interactions, which modifies species abondance
-and biomass and make species dynamics interdependant, have been largely ignored
-in empirical assessment.
-
-#### BEF: Theoretical ecology
-
-Conversely, theoretical ecology display an extensive literature about the
-effects of network structure on stability [@may_will_1972;
-@angelis_stability_1975; @stouffer_compartmentalization_2011;
-@thebault_stability_2010; @barbier_pyramids_2019;
-@shanafelt_david_w._stability_nodate].  Theoretical ecology generally uses
+#### Biodiversity and ecosystem properties
+
+Biodiversity is essential to determine and maintain ecosystem properties
+[@duffy_why_2009].  Current biodiversity losses and global changes question the
+way in which ecosystems will be affected in turn [@bellard_impacts_2012]. Since
+1970s and the @may_will_1972 seminal paper, ecology aims to uncover the complex
+relationships between biodiversity and ecosystem properties [@hector_plant_1999;
+@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
+@duffy_why_2009; @isbell_forest_quantifying_2018]. Because biodiversity largely
+determines both quantity and distribution of biomass or energy across
+ecosystems, it has a tremendous effects on the properties exhibited by an
+ecosystem, such as its total biomass [@hector_plant_1999;
+@tilman_biodiversity_2014; @grace_integrative_2016;
+@pennekamp_biodiversity_2018]], its biomass production
+[@tilman_productivity_1996; @cardinale_species_2002; @grace_integrative_2016]
+and the temporal stability of its biomass [@thebault_trophic_2005;
+@thebault_relationship_2006; @tilman_biodiversity_2006;
+@olivier_independent_nodate].
+
+#### Horizontal and vertical diversity are two ways to look at biodiversity
+
+Biodiversity can be quantified in numerous ways, as the number of species, i.e.
+species richness and in number of functional groups, i.e species are
+gathered on what they do. Those metrics can be gathered into "horizontal
+diversity", describing the list of components present in a community, i.e. here
+species and functional groups. An
+orthogonal view, based on trophic chains, described species on what they eat. It 
+can be defined as interactions (or biomass/energy fluxes) between species and how
+they are distributed among communities. It can be quantified as the number
+of interaction between species or the number of trophic level. This orthogonal
+view of seeing biodiversity, can be gathered into "vertical diversity".  
+Horizontal and vertical diversity are two views of quantifying biodiversity that
+are, however, not independent from each other [@duffy_functional_2007; @zhao_horizontal_2019]. The add
+or removal of one species can have different effects depending on its vertical
+position in the trophic chain [@duffy_functional_2007]. Hence, it is crucial to
+study their interplay to improve our understanding of ecosystem dynamics. 
+(*This paragraph is surely too simplistic*)
+
+#### horizontal and vertical diversity increase total biomass by common and different mechanisms
+
+Horizontal and vertical diversity has been shown to promote higher biomass
+production in a variety of ecosystems. Horizontal diversity, as species richness, has been
+reported to increase productivity through complementarity between species in
+resource exploitation and selection effects in plant communities
+[@tilman_productivity_1996; @cardinale_species_2002; @grace_integrative_2016].
+Regarding total biomass, empirical assessment have
+shown generally positive relationships with species richness in plant
+communities [@hector_plant_1999; @tilman_biodiversity_2014, but see
+@grace_integrative_2016], as in mesocosms [@pennekamp_biodiversity_2018].
+Theoretical models have also confirmed that an increase in horizontal diversity should
+translate into increase in plant biomass through resource complementarity
+[@loreau_biodiversity_1998] and selection effects [@tilman_plant_1997]. The
+addition of trophic levels, notably consumer on plants generally breaks the
+positive relationship between plant biomass and plant diversity as a significant
+amount of biomass is transfered to consumers [@thebault_food-web_2003]. It has been shown both in
+experiments [REF] and theoretical models [@thebault_food-web_2003].
+@thebault_relationship_2006 have shown with a theoretical model that total biomass should increase with
+the increase species diversity at two trophic level. However, the joint effects
+of horizontal and vertical diversity on total biomass has been
+rarely tested, especially in natural communities. It is not clear whether
+horizontal and vertical diversity just change the distribution of biomass across
+trophic level or it increases the total amount of  biomass (*It misses a lot of
+references here*).
+
+#### Horizontal and vertical diversity versus temporal stability
+
+Horizontal and vertical diversity also affects the stability of ecosystem
+properties. Experimental studies showed consistently that species richness
+increase temporal stability of biomass in grasslands
+[@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018]. While in
+natural communities, same relation has been found for temporal biomass stability
+in stream fish communities [@franssen_annual_2011] and temporal abundance
+stability of birds and butterflies [@olivier_independent_nodate, but not bats].
+Two mechanisms are involved into temporal stability of communities, (1)
+synchrony and (2) species variability [@loreau_species_2008;
+@thibaut_understanding_2013]. Synchrony measures the temporal covariation of
+species. Very low synchrony indicates compensatory temporal variation between
+species and so increased temporal stability. Species richness has been generally
+found to decrease synchrony between species [@loreau_species_2008;
+@thibaut_understanding_2013; @bluthgen_land_2016; @olivier_independent_nodate,
+but @declerck_species_2006]. The average temporal variability of species is
+measured as a average coefficient of variation of species, weighted by species
+abundance/biomass. Higher species temporal variabiliy thus results in lower
+temporal stability. Positive [@tilman_biodiversity_2006], neutral
+[@jiang_different_2009; @olivier_independent_nodate] and negative
+[@franssen_annual_2011; @olivier_independent_nodate] relationships between
+species variability and species richness have been found. This different
+patterns can be dependent on species mean variance relationships and on the
+relationship between evenness and species richness
+[@thibaut_understanding_2013].  Synchrony has been found to be the main driver
+of temporal stability [@tilman_biodiversity_2006; @olivier_independent_nodate]
+and responsible for the positive relationship between horizontal diversity and
+temporal stability of biomass and abundance. (*Should I add more details about
+the mecanisms?*)
+
+Vertical diversity, represented by network structure, has been central to the
+literature of diversity-stability debate and largely explored by theoretical
+ecology [@may_will_1972; @angelis_stability_1975;
+@stouffer_compartmentalization_2011; @thebault_stability_2010;
+@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate]. Because species
+interactions make species dynamics interdependant, they have a tremendous role
+on stability notably through its effects on the propagation of perturbations.
+However, it is important to note that theoretical ecology generally uses
 stability definitions related to community equilibrium and its stability to
-small perturbations.  Connectance (i.e. proportion of realized links in a
-network) can decrease [@angelis_stability_1975; @thebault_stability_2010] or
-increase resilience of trophic network depending on the functioning of networks
-[@angelis_stability_1975].  The number of trophic levels, the vertical position
-in the trophic network as well as the strength of their biomass regulation (i.e.
-top-down and bottom-up) can determine biomass and stability at equilibrium
-[@hurd_stability_1971; @shanafelt_david_w._stability_nodate;
-@zhao_horizontal_2019; @barbier_pyramids_2019].
-
-A large inconsistency remains between theoretical and empirical assessments of
-the relationship between community structure and ecosystem properties.
-Theoretical studies have ignored temporal variability and then the relative
-contribution of synchrony and species variability on community variability while
-empirical studies about temporal variability and total biomass in natural
-communities have ignored the contribution of network structure.
-
-Our goal was to assess the mecanisms determining temporal variability and total
-biomass in natural communities while integrating both species richness and
-network structure. We combined together the effect of vertical and horizontal
-diversity and thus aimed to bridge the current gap between theoretical and
-empirical studies. We used an standardized monitoring of fish communities in
-french streams. More than three hundreds sites were followed more than 10 years
-on the 1995-2018 period. We inferred four thousands potential interaction
-networks corresponding to each sampling event, based on trait matching.
-
-We investigated the effects of the community structure on total biomass and
-community variability, which in turn determine community variability. We have
-also included the effect of environmental drivers [@grace_integrative_2016]
-which can directly affect community variability or indirectly via community
-structure.
-
-- Q1: diversity-stability, diversity-biomass in aquatic systems
+small independent perturbations [@may_will_1972; @angelis_stability_1975;
+@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate] or to the number
+of secondary extinctions after species removal [@duffy_why_2009]. Those
+stability metrics hardly relates to empirical temporal stability [@arnoldi_resilience_2016].
+However, @thebault_trophic_2005 shows for a bi-trophic community
+that asynchrony consistently increase temporal stability and a positive
+relationship between temporal stability and species richness. However asynchrony
+can also increase species variability through interspecific competition, which
+amplifies species biomass fluctuations [@thebault_trophic_2005]. Furthermore
+species interactions, considered as competition strength and niche breath of
+consumers can results in negative or positive temporal stability-species
+richness relationships
+[@thebault_trophic_2005] depending on the food web configuration. Vertical
+diversity, as network structure, can have strong effects on temporal stability.
+However, there are few assesments of the effects of horizontal and diversity on
+temporal stability in natural communities.
+
+**Justify that horizontal and vertical diversity are linked**
+Because horizontal & vertical diversity are not indedepent, they should be
+analyzed jointly. For example, connectance generally covaries negatively with
+species richness [@dunne_network_2006; @thebault_stability_2010; but see
+@winemiller_must_1989]. This is also true for other metrics [@dunne_network_2006;
+@delmas_analyzing_2018]. **TO DEVELOP, MOVE or RM**
+
+#### Stream fish communities is a good model to study effects of horizontal & vertical diversity
+
+Stream fish community constitutes a good model to study the joint effects of
+horizontal & vertical diversity on total biomass and its temporal stability.
+Despite that fish trophic interactions are difficult to assess in nature, a consequent
+body of literature supports that they can be inferred through body size and diet
+informations [@gravel_inferring_2013; @jennings_weak_2001;
+@brose_predator_2019]. Most of the biomass-diversity and stability-diversity
+relationships have been assessed in terrestrial ecosystems while there is a
+evident need to test such relationships in a variety of ecosystem types. Stream
+ecosystems are characterized by the flowing water and depends for a large part
+from the input of terrestrial ecosystems. Furthermore, the biotic activity in
+stream ecosystems determines for a large part the water quality
+[@cummins_structure_1974] and thus are crucial to maintain **human selfish
+goals (can do better than that)**.
+
+#### Environment plays a big role in structuring communities
+
+Environment also largely structure communities and is important to take in
+account when considering natural communities. Environment directly affects
+organism performance, and subsequently, abundance of species and in turn
+determines total biomass [Add general ref; @grace_integrative_2016] and temporal
+stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
+@oliver_heterogeneous_2010; @friedpetersen_drivers_2020]. Hydrology of streams
+constraints the composition of fish communities [REF toulouse à balle], and is
+also related to fish population temporal stability [@franssen_annual_2011].
+However it is not clear which is the relative strength of direct and indirect
+effects of environment on total biomass and its temporal stability (Figure
+\@ref(fig:matmet) A).
+
+#### Research questions
+
+The joint effects of horizontal & vertical diversity on total biomass and its
+temporal stability remains yet poorly documented, especially in natural
+communities. In this study, we questionned (1) whether the relationships between
+horizontal diversity and total biomass/temporal stability are positive or
+negative in aquatic ecosystems (Figure \@ref(fig:matmet) A). Then, as indicated
+by theoretical studies, (2) what are the effects of vertical diversity on total
+biomass and its temporal stability? Considering both direct & indirect effects,
+(3) What is the magnitude of environmental effects on total biomass and its
+temporal stability compare to horizontal and vertical diversity? (4) Which are
+the pathways of the effects of environment, horizontal & vertical diversity on total
+biomass and its temporal stability ? (4a) For environment, is it mainly (i)
+direct, indirect (ii) through horizontal diversity, (iii) through horizontal &
+vertical diversity or (iv) indirect through only vertical diversity? (4b) For
+horizontal diversity, is it mainly (i) direct, or (ii) indirect through vertical
+diversity?  Finally for temporal stability, (4c) how do environment, horizontal
+& vertical diversity affect synchrony & species stability ?
+
+#### SEM is a convenient approach to investigate direct and indirect path
+
+To reveal the direct and indirect effects of environment, horizontal & vertical
+diversity on both total biomass and its temporal stability, we built and
+analyzed Structural Equation Models (SEM). It is one promising way to go beyond
+bivariate relationships and to investigate complex relationships, direct and
+indirect, between variables [@grace_structural_2008; @grace_causal_2014;
+@lefcheck_piecewisesem_2016; @grace_integrative_2016]. SEM makes possible to set
+causal relationships between variables. This step can be critical, as the
+estimated parameters can be determined by both the choice of the variables and
+the links between them. Therefore, the set of variables and links should be
+supported by theory and literature. We built a metamodel which present the set
+of variables and the links between them (Figure \@ref(fig:matmet) A,
+\@ref(fig:sem-plot) A & B). Basically, we tested the links between environmental
+conditions, horizontal & vertical diversity and both total biomass and its
+temporal stability (Figure \@ref(fig:matmet) A). We considered that environment
+can directly affect horizontal and vertical diversity, as well as total biomass
+and its temporal stability. Horizontal diversity, measured as species richness
+directly affects vertical diversity, total biomass and its temporal stability.
+Food web structure was shown to be constrained by species richness. In turn,
+vertical diversity affects total biomass and its temporal stability (Figure
+\@ref(fig:matmet) A).
+
+We used an standardized monitoring of fish communities in french streams. 99
+sites were followed more than 10 years on the 1995-2018 period. We inferred
+(**XXX**) potential interaction networks, based on body size and food diet.
+Horizontal diversity was quantified as species richness while vertical diversity
+was as connectance and average trophic level. Environment was characterized by
+the stream size, altitude, slope, and the temperature, flow, enrichment and
+their temporal variability (expect for altitude and slope). Finally total
+biomass was measured as median total biomass over the sampling period while its
+temporal stability was quantified as the inverse of the CV.
+
+- Q1:  horizontal diversity-biomass horizontal diversity-stability in aquatic systems
+- Q2:  in aquatic systems
 - Q2: Effect of horizontal and vertical diversity on total biomass and stablity
-- Q3:
+- Q3: Relative contribution of environment and community structure to biomass
+  and stability
 
@@
 
-## Community variability
-
 #### Protocol
 
-Fish communities were monitored across streams of France on the period
-1995-2018 by a French governmental agency (OFB, previously AFB and ONEMA). We
-kept only standardized protocols: complete and partial methods for respectively
-little and big streams (detailed in Supplementary methods). In the complete
-protocol, the sampling takes place over the whole width of the river and is done
-by foot whereas in the partial protocol, the sampling is done over the bank only
-and by boat. The sampling took place either in late spring and/or Autumn.
-Heterogeneity in the sampling time may introduce variability that is not related
-to ecological processes such as the presence of juveniles. In order to reduce
-heterogeneity in sampling time, we select only one sampling per year if there
-was two in a given year. Most of the fish sampling occurred in September
-(Median: mid-August) and within station the median standard deviation of the
-sampling month was inferior to one (0.7). Additionally, we removed sampling
-events, in a given station, which the length of the stream sampled was outside
-the median length sampled more or less 30%. The number of sampling events is
-critical in order to estimate a meaningful variability of the community. We kept
-only station that have been followed ten years or more (i.e 10 sampling events
-or more), which sums to 403 stations.
-
-The sampling itself was performed by electric fishing. All the stunned fish
-species were identified and the individuals counted.
-
-##### Biomass
+Fish communities were monitored across streams of France on the period 1995-2018
+by a French governmental agency (Office Français de la Biodiversité), using
+electric fishing. Two different standardized protocols were used for little and
+big streams (detailed in Supplementary methods). For streams shallower than (XX
+m), the sampling takes place over the whole width of the streams and is done by
+foot whereas in streams deeper than (XX m), the sampling is done over the bank
+only and by foot or by boat. The sampling took place either in late spring and/or Autumn
+and temperal series were checked to reduce sampling heterogeneity within
+stations (detailed in Supplementary methods). Each station have been followed
+ten years or more (i.e 10 sampling events or more). The temporal stability of
+biomass, computed as inverse of the CV, can cover very different dynamics such
+as decreasing, stable or increasing. However, the concept of community
+variability referred to variability around an equilibrium, which is rarely
+observed or difficult to characterize in natural communities. We finally kept
+only the 99 stations (Figure \@ref(fig:matmet) B) which had no trends in
+biomass (method detailed in Supplementary methods). However, the results
+were robust to the relaxation of this hypothesis (Supplementary results).
+
+##### Total biomass and its temporal stability
 
@@
 biomass. We therefore estimated the body mass of fish individuals according to
-their body size. During sampling, the fishes were classified in batch according
-to species and size class. Depending on the batches, the body size of all
-individuals were measured or only a subsample. Only the body size big fishes was
-measured individually. The body size of individual fishes in subsampled batches
-was inferred under normality distribution assumption (detailed in Supplementary
-material). The body mass of individual fishes were then estimated with an
-allometric law ($B_i = 0.01 \times l_i^3.03$, $B$ being the body mass in grams,
-$l$ the body size in millimeters and $i$ the individual).
+their body size. The body mass of individual fishes were then estimated with an
+allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$ being the body mass in grams,
+$l$ the body size in millimeters and $i$ the individual)
+[@lleonart_removing_2000; @froese_cube_2006].
 
 The species and community biomass were then computed for each sampling event.
-As sampling effort varied across protocol type and sampling event, biomass
-was reported to the surface sampled (in $m^{2}$). Community and species biomass
-were then expressed in $gm^{-2}$.
-
-Total biomass was characterized as the median total biomass over time. Community
-stability was defined as the inverse of biomass variability. Variability was
-computed as Coefficient of Variation (CV) of the biomass ($CV_i = \sigma_i \mu_i^{-1}$,
-with $\sigma_i$ and $\mu_i$ being respectively the standard deviation and the
-average of the biomass of the station $i$). Then, biomass stability was equal to
-$CV^{-1} = \mu \sigma^{-1}$.
-
-The CV of community biomass can represent very different dynamics such as
-decreasing, stable or increasing. However, the concept of community variability
-refered to variability around an equilibrium, which is rarely observed or
-difficult to characterize in natural communities. 
-We However used SAX (Symbolic Aggregate Approximation) method to caracterize
-rougly biomass dynamics over time (details in Supplementary information). We
-finally kept only the stations which the biomass had no trends, remaining 99
-stations.
-
-To characterize the mecanisms driving biomass stability, we decomposed
+As sampling effort, reported as the surface sampled during the sampling event,
+varied across protocol type and sampling event, biomass was reported to the
+surface sampled (in $m^{2}$). Community and species biomass were then expressed
+in $gm^{-2}$.
+
+Total biomass was characterized as the median total biomass over time. Temporal
+biomass stability was defined as the inverse of biomass variability. Variability
+was computed as Coefficient of Variation (CV) of the biomass ($CV_i = \sigma_i
+\mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being respectively the standard
+deviation and the temporal average of the biomass of the station $i$). Then, temporal
+stability was equal to $CV^{-1} = \mu \sigma^{-1}$.
+
+To characterize the mecanisms driving temporal stability, we decomposed
 the community CV in synchrony and weighted average species CV
@@
 community variance ($\sigma^2_{x_T}$) and the sum of population variance
-($\sigma_{x_i}$) [@loreau_species_2008]:
+($\sigma_{x_i}$) [@loreau_species_2008].
+
+$$
+\overline{CV_{sp}} = \sum_i{\frac{B_i {CV}_i}{\sum_i{B_i}}}
+$$
 
@@
 
+## Hozizontal & vertical diversity
+
+### Horizontal diversity
+
+####  Species richness
+
 Species richness was computed as the total species richness over time in a given
-station. To normalize by sampling effort, we reported species richness to
-the sum of surface sampled over the time period, it was expressed in number of
+station. To normalize by sampling effort, we reported species richness to the
+sum of surface sampled over the time period, it was expressed in number of
 species by square meter.
 
-## Network building
+### Vertical diversity
+
+#### Trophic network inference
 
@@
 
-To obtain the network structure of the communities, we needed to infer
-ecological interactions between the components of the communities and thus build
-the ecological network. As the interactions were not measured, we used trait
-matching method to infer the presence or absence of an interaction. This method is
-widely used to infer trophic interactions
-[@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012]. Indeed;
-the existence of an trophic interaction between two species have been reported
-to be largely dependant on their body size ratio
-[cascade model; @cohen_stochastic_1985; @warren_invertebrate_1987; @brose_predator_2019].
-
-Additionally to body size, we used food diet data to infer trophic
-interactions. The diet of stream fishes, as many organisms, shifts over lifespan.
-For example, alvins feeds on plankton while adults may feed on algae or fishes.
-As we got body size of each fish individuals (cf Biomass inference methods and
-supplementary material), we are able to define trophic interactions beyond
-species level. We thus divided each fish species into nine body size classes,
-each class having the same body size range (percentile method). Each body size
-class constituting a trophic species. We then infered trophic interactions
-between the trophic species. At this stage, it is important to make clear that
-we infered potential trophic interactions and not actual measured interactions.
-We determined network structure in two steps: (1) build a metaweb decribing the
-trophic interactions between all the possible trophic species, then (2)
-determine network of a given community by subtracting the metaweb according to
-the trophic species present in a given community.
-
-### Metaweb
-
-#### Ontogenic diet
-
-Diet information were obtained from database and literature [REF edeline?]. The
-diet information contained from two to three life stages by species, the life
-stages being defined by the body size of the fishes. Over the 57 fish species,
-only seven had a piscivorous life stage and only three had as strict piscivorous
-life stage. Fish species were largely omnivorous.
-
-#### Define trophic interactions
-
-The metaweb described the potential trophic interactions between the $`r 57*9`$
-($57\times9$) trophic species. We had seven resource nodes which were present
-in the diet of the trophic species namely detritus, biofilm, phytoplankton,
-zooplankton, macrophages, phytobenthos and zoobenthos.
-
-A trophic species belonged to a life stage if the median of its body size range
-fell in the range of the life stage. In turn, this trophic species has feeding
-interactions with the resource nodes of its life stage. Interactions between
-resource nodes were determined by literature. For example, phytobenthos fed on
-detritus, while zooplankton fed on zooplankton and phytoplankton. Fish-fish
-trophic interactions between a predator and a prey were determined by body size
-ratio as in many studies
-[@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012].
-For a given trophic species, we first determined if its size class end up in a
-life stage containing piscivorous diet, i.e. if there was an overlap between
-them. We were more liberal for piscivory determination to not miss potential
-fish-fish trophic interactions which were the main interactions in our
-community. If the trophic species was piscivorous, we determined its prey size range
-from 3% to 45% of the median of its size range. A trophic interaction was set
-for each trophic species whose median of its size class fell into the prey range
-of the predator trophic species. To sum up, the metaweb was obtained with
-allometric feeding interactions (1) between trophic species, (2) between trophic
-species and resource nodes and (3) between resource nodes.
-
-#### Obtain network of a community
-
-The trophic network of a community (i.e. one network for each fish community
-sampling) was obtained by determining the trophic species of each fish
-individual in the community and interactions were set according to the metaweb.
-All the resource nodes were assumed to be present in each local network.
-Finally, the structure of the local networks varied according the presence of
-the trophic species. The inferred interactions represent potential interactions
-(i.e. not measured interactions) and are binary (i.e. presence or absence of
-feeding interactions).
-
-#### Network structure
+Trophic interaction network was inferred from body size and ontogenic diet.
+Body size is a reasonable approximation widely used to infer trophic
+interactions [@gravel_inferring_2013; @brose_predator_2019;
+@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
+over lifespan. For example, alvins feed on plankton while adults may feed on
+algae or fishes. Accordingly,  each fish species was divided in nine body size
+classes. Each body size class constituting a trophic species. A high congruence
+has been found at trophic species scale between inferred interactions and
+measured trophic interactions, but not at the species
+scale [@jennings_weak_2001]. We then inferred trophic interactions between the trophic species (Figure
+\@ref(fig:matmet) C).  We determined network structure in two steps: (1) build a
+metaweb describing the trophic interactions between all trophic
+species (Figure \@ref(fig:matmet) C), then (2) determine network of a given
+community by subtracting the metaweb according to the trophic species present in
+a given community (Figure \@ref(fig:matmet) D). We added to each network seven
+resource nodes present in food diet database: detritus, biofilm, phytoplankton,
+zooplankton, macrophages, phytobenthos and zoobenthos (grey nodes in Figure
+\@ref(fig:matmet) C & D). The trophic network inference procedure is detailed in
+supplementary informations.
+
+#### Trophic network structure
 
@@
 characterize network structure. Connectance which describes the number of
-interactions compared to the number of possible links,
- computed as ($C = L / N^2$, L and N being resp. the number of
-links and of nodes). We then computed the average trophic level, the
-average trophic level was weighted by the biomass of each trophic species
-(excluding resource nodes for which we had no biomass) ($\overline{T} =
-\sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, $T_i$ and $B_i$ being resp. the
-trophic level and the biomass of the node $i$).
-
-To sum up, we infered binary trophic networks at the scale of trophic species
+interactions compared to the number of possible links, computed as ($C = L /
+N^2$, L and N being
+resp. the number of links and of trophic species plus resource nodes). We then
+computed the average trophic level, the average trophic level was weighted by
+the biomass of each trophic species (excluding resource nodes for which we had
+no biomass) ($\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, $T_i$
+and $B_i$ being resp. the trophic level and the biomass of the node $i$).
+
+In resume, we infered binary trophic networks at the scale of trophic species
 (i.e. body size classes by species) to take in account ontogenic diet shifts and
@@
 
-## Habitat and environment
+## Environment
 
@@
 
-Habitat description were obtained from fish sampling data. We kept variables
-describing the ecosystem size namely the stream width, depth and the ecosystem
-position (altitude and slope). Physico-chemical variables were obtained from
+Habitat description, obtained from fish sampling data, describing the ecosystem
+size namely the stream width, depth and position (altitude and
+slope). Physico-chemical variables were obtained from
 naiades web portal [http://www.naiades.eaufrance.fr/](http://www.naiades.eaufrance.fr/).
-We chose flow and temperature as physical variables to describe streams as flow
+We chose flow and temperature to describe streams as flow
 impose swimming constraints which filters fish species that can establish
@@
 Biochemical Oxygen Demand (BOD) for a proxy of enrichment in the ecosystem [REF].
-BOD is also inversely linked to oxygen concentration in water.
-The time resolution was heterogeneous according to the variable considered
-(hourly, daily and monthly for temperature, flow and BOD resp.). For each recording
-station, we applied a moving window averaging (more details in supplementary
-material) to get rid of seasonal effects and took the annual mean (i.e. one
-value by year and by station. As the environmental recording stations were not
-located at the same place than the fish stations, we interpolated environmental
-data with spatial statistical network model [@isaak_applications_2014]
-implemented in the `SSN` R package [@hoef_ssn:_2014]. The interpolation
-procedure is detailed in supplementary material. For each fish station,
-environmental variables were matched with the year of fish sampling (except for
-water temperature for which the record began in 2006). Then, the average
-temperature, flow, BOD, river width and depth were computed as well as
-coefficient of variation ($CV = \sigma \mu^{-1}$). As habitat and environmental
-variables are often colinear, a principal component analysis (PCA) was performed
-on the scaled variables. The PCA explained `r tot_var_expl_pca`% of the
-variance. An axis rotation was performed to maximize the representation of the
-variables by the principal components (Fig. \@ref(fig:pca-rotated)). We kept
-five axis, representing respectively the (1) river size (river width & depth),
-(2) the altitude, slope and decreasing average temperature, (3) average
-enrichment (BOD) and CV of flow, (4) river size CV (CV of river width and depth)
-and (5) CV of enrichment (CV of BOD). Additionally, we logged the axis one, two
-and three to normalize their distribution and we reversed the third axis to get
-increasing average temperature with increasing values of the axis.
+BOD is also inversely linked to oxygen concentration in water and so, BOD is
+also linked to physiological stress of fishes. As physico-chemical variables
+were not recorded at the same place than fish communities, they were
+interpolated with spatial stream networks [@isaak_applications_2014;
+@hoef_ssn:_2014]. The interpolation procedure is detailed in supplementary
+methods.
+
+For each fish station, environmental variables were matched with the year of
+fish sampling (except for water temperature for which the record began in 2006).
+Then, the average temperature, flow, BOD, river width and depth were computed as
+well as coefficient of variation ($CV = \sigma \mu^{-1}$). As habitat and
+environmental variables are often collinear, a principal component analysis (PCA)
+was performed on the scaled variables. The PCA explained `r tot_var_expl_pca`%
+of the variance. An axis rotation was performed to maximize the representation
+of the variables by the principal components (Fig. \@ref(fig:pca-rotated)).
+Five principal components were used in the analysis, representing respectively
+the (1) river size (river width & depth), (2) altitude, slope and decreasing
+average temperature, (3) average enrichment (BOD) and CV of flow, (4) river size
+CV (CV of river width and depth) and (5) CV of enrichment (CV of BOD). Further
+informations about data transformation and filtering are detailed in
+supplementary information.
 
 ## Statistical analysis
+
+#### Summarise SEM statistical framework
+
+Structural Equation Modeling are able to assess multivariate relationships,
+directs and indirects between variables.  The metamodel describes how variables
+are interrelated (Figure \@ref(fig:matmet) A). We built separated structural
+equation model for total biomass and its temporal variability (Figure
+\@ref(fig:sem-plot) A & B). Structural equation modeling was set up according to the
+hypothesis described in introduction and detailed in supplementary information.
+Structural equation models were based on Gaussian linear models, some variables
+were logged to fulfill model assumptions (see residual plots and data
+transformation in supplementary
+informations). To account for heterogeneity of hydrographic basin, we set it as random effect on the intercept. Moreover, statistical model were checked for the presence of
+multicollinearity (Supplementary information). The slopes reported in the main
+text are standardized in order to compare their magnitude ($r_\delta = \beta
+\frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope, $\sigma_x$
+and $\sigma_y$ being respectively the standard deviation of the predictive
+variable $x$ and of the response variable $y$). In the main text, only the
+slopes which had $P$ value inferior to $0.05$ were reported (but see Table SXX).
+Linear models and SEMs were computed with respectively the `nlme` and
+`piecewieseSEM` R packages. The code used for the analysis are accessible on
+github.
+
+The structural equation models used for total biomass and its temporal stability
+contains respectively 4 and 6 response variables, 35 and 26 direct paths.
+
+#### Computation of indirect effects
+
+The indirect effects of variables on total biomass and its temporal stability
+was computed by multiplying slopes along the path. As an example, if we consider
+$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times r_{BC}$.
+Only significant direct slopes were entered in the calculation of
+indirect effects. Finally total effects were computed as the sum of direct and
+indirect effects.
 
@@
 
-### SEM
-
-We seeked to disantangle the unravel the links between
-environment and community structure on both biomass stability and total biomass.
-To investigate complex relationships, direct and indirect, between variables,
-Structural Equation Modeling (SEM) is one promising way  
-[@grace_structural_2008; @grace_causal_2014; @lefcheck_piecewisesem_2016;
-@grace_integrative_2016]. SEM makes possible to set causal relationships between
-variables. This step can be critical, as the estimated parameters can be
-determined by both the choice of the variables and the links between them.
-Therefore, the set of variables and links shoud be supported by theory and
-litterature.
-
-We built a metamodel (set of variables and links between them). Basically, we
-tested the links between environmental conditions, community structure and
-ecosystem properties namely biomass stability on total biomass. Theory in
-ecology predicts that community structure influences stability. In turn,
-environment influences community structure but also directly stability.
-
-#### Variables
-
-To characterize environment, we retained five axis of PCA on habitat and
-climatic variables which represent different types of forcing (constant and
-variability). The two first axis (RC1 and RC2) were linked to the physical
-structure and position of the river and the altitutinal gradient (+temperature).
-The third axis (RC3) was linked to enrichment (Biological Demand in Oxygen) and
-CV of annual flow. The fourth and fifth (RC4 and RC5) axis were associated to
-environmental variability, respectively to CV of width and depth of the river
-and CV of enrichment.
-
-The community structure was characterized by total species richness, median
-average weighted trophic level and median connectance. Total species richness
-was the number of unique fish species that were observed at a given station over
-the whole sampling. Both median connectance and average trophic level were just
-computed as the median over the time series. For the details of the
-computation of the trophic networks, see Network inference part.
-
-#### Causal relationships
-
-We linked environmental variables both to community structure and stability
-components. Rooted in assembly theory, environment filters species that can
-establish in a community and thus affect community structure. (+ add specific
-hypothesis about physical and climate). (1) We hypothesized that enrichment
-(characterized by DBO) and mean annual temperature will increase species turnover
-[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
-decrease biomass stability directly without going by community structure. First,
-instability of habitat and environmental factors may in turn drive biomass
-instability [@hansen_climate_2013]. Secondly, average environmental conditions
-such as enrichment can increase directly CV by increasing species biomass
-fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
-to decrease stability through starvation resulting from high metabolic activity
-[@tabi_warming_2019].
-
----
-# Species richness to community attributes 
----
-To reveal the mechanisms behind the relationship between species richness and
-biomass stability, causal links were set from species richness to other
-community attributes. In particular, species richness decreased connectance
-following results from @thebault_stability_2010; @winemiller_must_1989. But
-theoretically, some ecological networks can show the inverse relationship
-[@winemiller_must_1989]. (6) We hypothesized also that species richness will
-modulate average weighted trophic level because of food web assembly processes.
-A community with more fish species can support higher trophic level. Finally, we
-set up causal relationships from community attributes to stability components.
-
----
-#  Community attributes to stability
----
-We hypothesized that (7) species richness decreased synchrony between species
-[@loreau_species_2008] and increased $\overline{CV_{sp}}$
-[@tilman_biodiversity_2006]. (8a) We expected that average trophic level had a
-positive or negative relationship with synchrony, bottom-up effects should
-result in positive whereas top-down in negative relationships. We expected a (8b)
-negative relationship between average trophic level and $\overline{CV_{sp}}$ if
-predators stabilised prey fluctuations or if the increasing part of
-biomass in the predators decreased $\overline{CV_{sp}}$ because of their higher
-body mass (if mean increase faster than variance). (9a) Connectance was expected
-to decrease or increase $\overline{CV_{sp}}$ and (9b) synchrony because of top
-down effects or bottom up effects.
-
 ```{r}
@@
   random_effect = as.formula("~1|basin"))
+
+def_env_x_pos <- c(from = 0, to = 6)
 
@@
   val_thd = 0.05,
-  env_x_pos_range = c(from = 0, to = 7.5),
+  env_x_pos_range = def_env_x_pos,
   env_y_pos = 0,
@@
 
-```{r sem-plot, fig.cap = sem_caption}
+```{r sem-plot, fig.height = 7, fig.cap = sem_caption}
 #https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
@@
   labels = LETTERS[1:4], nrow = 2,
-  rel_widths = c(1, .8)
+  rel_widths = c(1, 1)
 )
@@
   variable. For exemple, the indirect effect of species richness on
-  biomass stability via its effect on CVsp is $-0.61$. To compute indirect
+  biomass stability via its effect on CVsp is -0.61. To compute indirect
   effect, only the significant direct effects were taken into account. ",
@@
   richness to network structure."
-
 )
@@
   "Indirect and total effect of variables on total biomass from the
-  structural equation model. See the table (X) for details about computation and
+  structural equation model. See the table 1 for details about computation and
   meaning."
@@
 )
-```
-
-```{r indir-bm, fig.cap = "Indirect effect from SEM"}
-format_table <- function (x = tmp_stab_indir_table) {
-  x <- x[, c("variable", names(x)[!names(x) %in% "variable"])]
-
-  rm_n <- str_remove_all(get_sem_var_name_replacement(), pattern = "\n")
-  names(rm_n) <- names(get_sem_var_name_replacement()) 
-  x$variable <- str_replace_all(x$variable, rm_n)
-
-  colnames(x) %<>% str_remove_all(., pattern = "via_")
-
-  col_replacement <- c(
-    variable = "Variable",
-    cv_sp = "CVsp",
-    sync = "Synchrony",
-    richness = "Horizontal diversity",
-    com = "Vertical diversity",
-    richness_com = "Horizontal & vertical diversity",
-    total = "Total effect"
-  )
-  colnames(x) %<>% str_replace_all(., col_replacement)
-
-  x
-}
-
-kable(format_table(tmp_bm_indir_table),
-  "latex",
-  booktabs = T,
-  caption = caption_indir_bm_sem
-  ) %>%
-kable_styling(latex_options =c("striped", "scale_down"))
-
 ```
@@
 ```{r indir-stab}
+format_table <- function (x = tmp_stab_indir_table) {
+  x <- x[, c("variable", names(x)[!names(x) %in% "variable"])]
+
+  rm_n <- str_remove_all(get_sem_var_name_replacement(), pattern = "\n")
+  names(rm_n) <- names(get_sem_var_name_replacement()) 
+  x$variable <- str_replace_all(x$variable, rm_n)
+
+  colnames(x) %<>% str_remove_all(., pattern = "via_")
+
+  col_replacement <- c(
+    variable = "Variable",
+    cv_sp = "CVsp",
+    sync = "Synchrony",
+    richness = "Horizontal diversity",
+    com = "Vertical diversity",
+    richness_com = "Horizontal & vertical diversity",
+    total = "Total effect"
+  )
+  colnames(x) %<>% str_replace_all(., col_replacement)
+
+  x
+}
+
 kable(format_table(tmp_stab_indir_table),
-  "latex",
+  format = "latex",
   booktabs = T,
+  label = paste0("indir-stab"),
   caption = caption_indir_stab_sem 
@@
 
-## Drivers of total biomass
-
----
-# Total biomass
----
-
-#### Direct effect
-Species richness and average trophic level had a significant positive direct
-effects on total biomass (resp. $r_\delta = `r rich_on_bm$direct`$ and $r_\delta
-= `r tlvl_on_bm`$) whereas connectance had no significant direct effects (Fig.
-\@ref(fig:sem-plot) B). CV of enrichment had a direct negative effect on total
-while the other environmental variables had no significant direct
-effect.
-
-##### Indirect effect
-Avg river size, avg temperature and avg enrichment had however indirect positive
-effects on total biomass through species richness or/and average trophic level
-(Table XX & Fig.  \@ref(fig:sem-plot) B). Those indirect effects went
-independently by species richness and avg trophic level because species richness
-had no significant effect on avg trophic level.
+```{r indir-bm}
+
+kable(format_table(tmp_bm_indir_table),
+  format = "latex",
+  booktabs = T,
+  label = paste0("indir-bm"),
+  caption = caption_indir_bm_sem
+  ) %>%
+kable_styling(latex_options =c("striped", "scale_down"))
+```
 
@@
 
-## Biomass stability
-
-#### Direct effects 
-$\overline{CV_{sp}}$ ($r_\delta = `r cv_sp_on_stab`$) decreased biomass
-stability more than synchrony ($r_\delta = `r sync_on_stab`$, Figure
-\@ref(fig:sem-plot)). Species richness had a strong opposite direct effect on
-$\overline{CV_{sp}}$ and synchrony, positive on $\overline{CV_{sp}}$ ($r_\delta
-= `r cv_sp_on_stab`$) and  negative on synchrony. Average trophic level had a
-negative direct effect on $\overline{CV_{sp}}$ and connectance had no
-significant direct effect on either $\overline{CV_{sp}}$ nor synchrony. Avg
-enrichment had a direct positive effect on $\overline{CV_{sp}}$. The other
-environmental variables had no significant direct effects on either
-$\overline{CV_{sp}}$ nor synchrony.
-
-#### Indirect effects
-Indirectly through synchrony ($r_\delta = `r rich_on_stab$via_sync`$) and
-$\overline{CV_{sp}}$ ($r_\delta = `r rich_on_stab$via_cv_sp`$), species richness
-had a total negative effect on biomass stability
-($r_\delta = `r rich_on_stab$total`$). Avg trophic level had a positive indirect
-effect on
-biomass stability through $\overline{CV_{sp}}$
-($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$).
-
-Avg temperature had an indirect negative effect on biomass stability through
-$\overline{CV_{sp}}$ ($r_\delta = `r env_on_stab$via_cv_sp["log_RC2"]`$) and
-through species richness ($r_\delta = `r env_on_stab$via_richness["log_RC2"]`$)
-but weakly positive through avg trophic level ($r_\delta = `r env_on_stab$via_com["log_RC2"]`$).
-In sum, avg temperature had a the highest total negative effect  
-on biomass stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$).
+Overall, the structural equation models explained a large part of the variation
+of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
+.45$, $.47$, $.49$ and $.38$) but not of average trophic level ($R^2 =
+.18$, Figure \@ref(fig:sem-plot) C and D).
+
+## Horizontal diversity increased total biomass but decreased its temporal stability
+
+Species richness had a significant positive direct effect on total biomass
+$r_\delta = `r rich_on_bm$direct`$ (Figure \@ref(fig:sem-plot) D, Table
+\@ref(tab:indir-bm)). However, species richness had a total negative effect
+on biomass stability ($r_\delta = `r rich_on_stab$total`$, Table
+\@ref(tab:indir-stab)). Species richness had a positive effect on stability
+through synchrony ($r_\delta = `r rich_on_stab$via_sync`$) but a negative  one
+through $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
+\@ref(tab:indir-stab)). Futhermore, species richness had a strong opposite
+direct effect on $\overline{CV_{sp}}$ and synchrony, positive on
+$\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$) and negative on synchrony
+($r_\delta = `r rich_on_sync$direct`$).  Finally, it was surprising that the negative
+effect of $\overline{CV_{sp}}$ on temporal stability was twice higher than the
+negative effect of synchrony (resp. $r_\delta = `r cv_sp_on_stab`$ and $r_\delta
+= `r sync_on_stab`$, Figure \@ref(fig:sem-plot) C).
+
+## Vertical diversity increased total biomass and its temporal stability
+
+Average trophic level had a positive effect on total biomass ($r_\delta
+= `r tlvl_on_bm`$) but connectance had no significant effect (Figure
+\@ref(fig:sem-plot) D). Average trophic level had a total positive effect on
+temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$, Table
+\@ref(tab:indir-stab)) by decreasing $\overline{CV_{sp}}$ ($r_\delta = -0.26$,
+Figure \@ref(fig:sem-plot) C). Again, connectance had no significant effect on
+temporal stability (Figure \@ref(fig:sem-plot) C, Table SXX).
+
+## Horizontal and vertical diversity had opposite and independant effect on total biomass and its temporal stability
+
+We described above that species richess had respectively a positive and a negative 
+on total biomass and its temporal stability whereas average trophic level had a
+positive effect on both (Table \@ref(tab:indir-bm) and \@ref(tab:indir-stab)).
+The total effect of average trophic level on total biomass was of the same
+magnitude than the one of species richness (resp. $0.30$ and $0.36$, Table
+\@ref(tab:indir-bm)). It was also true for temporal stability (resp. $0.34$ and
+$-0.24$, Table \@ref(tab:indir-stab)). Average trophic level was
+independent of species richness because species richness had no significant
+effect on average trophic level. However species richness had a strong negative
+effect on connectance ($r_\delta = -0.64$, Figure \@ref(fig:sem-plot) C and D).
+But, in turn, connectance had no significant effect on either total biomass nor
+its temporal stability.
+
+## Environment had an high effect on total biomass and its temporal stability
+
+The CV of enrichment had a direct negative effect on total biomass ($r_\delta =
+-0.24$, Figure \@ref(fig:sem-plot) D). The other environmental variables had no
+significant direct effects on total biomass (Table SXX). Avg temperature and
+altitude respectively increased and decreased total biomass ($r_\delta = 0.30$,
+Table \@ref(tab:indir-bm)), mainly through species richness ($r_\delta = 0.21$,
+Table \@ref(tab:indir-bm)). Average stream size had a positive effect on total
+biomass ($r_\delta = 0.18$, Table \@ref(tab:indir-bm)), equally through species
+richness and average trophic level ($r_\delta = 0.09$, Table
+\@ref(tab:indir-bm)). Average temperature and altitude effects on total biomass
+were of the same magnitude than the effects on species richness and average
+trophic level.
+
+Average temperature and altitude had a negative and a positive effect on
+temporal stability ($r_\delta = -.43$, Table \@ref(tab:indir-stab)) mainly
+through a direct positive effect on $\overline{CV_{sp}}$ ($r_\delta = -.40$,
+Table \@ref(tab:indir-stab)). Interesting, average temperature (and reverse of
+altitude, *chiant cette variable composite*) had also a negative effect on
+temporal stability through species richness but a positive one through average
+trophic level (resp. $r_\delta = -.14$ and $r_\delta = .10$, Table
+\@ref(tab:indir-stab)). This was also true for average river size but effects
+were weak. Finally, the effect of average temperature on temporal stability had
+a magnitude higher than species richness and average trophic level (Table
+\@ref(tab:indir-stab)).
 
@@
 
-With the aim to find out the determinants of total biomass and temporal
-biomass variability in trophic communities, we analysis a standardized dataset
-at France scale going on from 1995 to 2018. We infer network structure with
-trait matching method and used SEM to disantangle direct and indirect effects of
-environment, community and network structure on both total biomass and biomass
-stability. We fund that species richness increased total biomass but 
-decreased biomass stability. Suprisingly, we found that $\overline{CV_{sp}}$ had
-an negative effect twice higher than synchrony on biomass stability.
-Furthermore, we found that the effects of species richness on stability and
-biomass were independent from the effects of network structure.
-
-#### Richness on stability and biomass
-
-We found a negative relationship biomass stability and species
-richness whereas there was a positive one between total biomass and species
-richness. Overall, it contrasts with studies in grasslands
-[@tilman_biodiversity_2006; @zhang_scale_nodate]; mesocosms
-[@pennekamp_biodiversity_2018] or other animals [@olivier_independent_nodate]
-where positive relationships are typically found between biomass stability
-and species richness. In streams as well, @franssen_annual_2011
-found that species richness increased biomass stability. However other studies
-found a opposite relationship [@yang_effects_2011] or a marginal one
-[@declerck_species_2006]. We found that species richness increased total biomass
-as found in salt marshes, forests
-[@wu_relationship_2015;@li_relationship_2018]. The positive effect
-of species richness on total biomass might be due to resource use
-complementarity [@cardinale_species_2002]. But opposite relation has been found
-in richness in grasslands
-[@grace_integrative_2016].
-
-#### connectance on stability and biomass
-Our path analysis revealed that, although species richness has a strong effect on
-connectance, connectance itself had little to no effect either on stability nor
-total biomass. This result contradicts precedent theoretical studies on the
-relationship between stability and network structure [@angelis_stability_1975;
-@may_will_1972], although they considered different stability metrics (i.e.
-local stability of equilibrium point). The reason might be that in our inferred
-network, network structure is strongly constraints by assembly processes.
-Indeed, connectance generally decreased with increasing species richness
-[@winemiller_must_1989; @thebault_stability_2010]. It is an effect important to
-consider the link between connectance and ecosystem properties, as this direct
-relationship can be misleading if species richness is not taken into account.
-
-##### Trophic level on stability and biomass 
-We also found that richness had no effect on average trophic level but average
-trophic level was positively linked to total biomass and biomass stability.
-It means that the effects of richness and avg trophic level are
-independent. Then, it underlied the importance to consider facets of community
-structure related to biological interactions. The positive relation between
-average trophic level and biomass is straitforward. As feeding interactions were
-partly determined by body size and that body mass increase with body size, we
-expected that the more the average biomass is located at higher trophic level,
-the more the total biomass increase. Average trophic level had a positive effect
-on biomass stability by its negative effect on average species CV (i.e. positive
-effect on average species stability). It means that species at higher trophic
-level are more stable than the species at lower trophic levels. But, the
-relations between trophic position and stability more complex
-[@shanafelt_david_w._stability_nodate], even more if we take in account the
-repartition of the biomass across trophic level [@barbier_pyramids_2019].
-Further investigation are needed to understand the interplay between trophic
-level number, their biomass repartition and stability.
-
-##### Environment on biomass and stability
-
-Precedent researches in plant communities showed that the total biomass was
-primary driven by environmental drivers [@grace_integrative_2016]. We found that
-environmental drivers in general did not directly affect either total biomass
-nor synchrony and CVsp except avg temperature and CV of enrichment which were
-respectively positively linked to CVsp and negatively linked to total biomass.
-It indicates that the effect of environment primary drive community structure
-which in turn affect total biomass and biomass stability. Our results also
-showed that avg temperature had the biggest effect on biomass stability while Cv
-of enrichment had the second biggest impact on total biomass.
-
-#### Synchrony and CVsp 
-Species richness decreased synchrony and increased $\overline{CV_{sp}}$. Species
-richness can reduce synchrony through decrease of population size, thus raising
-the role of demographic stochasticity [@loreau_species_2008] but also in the
-case where species have different responses to environmental variation
-[@loreau_species_2008]. While the effect of species richness on synchrony is
-well understood, its effect on $\overline{CV_{sp}}$ is more complex. 
-In turn, we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
+With the aim to find out the determinants of total biomass and its temporal
+stability in fish trophic communities, we analyzed a standardized dataset at
+France scale going on from 1995 to 2018. We infer network structure with
+together body size and food diet method and used SEM to disantangle direct and
+indirect effects of environment, horizontal and vertical diversity on both total
+biomass and biomass stability. We found that species richness and average
+trophic level positively covariated with total biomass. However, species
+richness negatively covariated with temporal stability whereas average trophic
+level covariated positively. Futhermore, we found that the effect of species
+richness and average trophic level on total biomass and its temporal stability
+were independant. Finally, we found the magnitude of the effects of average
+temperature and altitude was equal or superior to the effects of species
+richness and average trophic level.
+
+## Horizontal diversity increased total biomass but decreased its temporal stability
+
+We found that species richness increased total biomass as found in salt marshes,
+forests [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
+@li_relationship_2018]. The positive effect of species richness on total biomass
+might be due to resource use complementarity [@cardinale_species_2002]. But
+opposite relation has been found in richness in grasslands presumably because of
+light competition [@grace_integrative_2016].  In accordance with theoretical
+models, resource use complementarity [@loreau_biodiversity_1998;
+@thebault_relationship_2006] might also be at work in fish trophic communities.
+
+Surprisingly found a negative relationship between temporal stability and
+species richness. Overall, it contrasts with studies experimental studies in
+grasslands [@tilman_biodiversity_2006]; mesocosms [@pennekamp_biodiversity_2018]
+and even in natural communities [@olivier_independent_nodate] where positive
+relationships are typically found between temporal stability and species
+richness. In streams as well, @franssen_annual_2011 found that species richness
+increased temporal stability. However other studies found a opposite relationship
+in natural grassland [@yang_effects_2011] or a marginal one
+[@declerck_species_2006] in natural forests. Further investigations are needed
+to identify the mechanisms behind those contrasting patterns,
+
+- add [@yang_effects_2011]
+
+ Species richness decreased synchrony
+and increased $\overline{CV_{sp}}$. Species richness can reduce synchrony
+through decrease of population size, thus raising the role of demographic
+stochasticity [@loreau_species_2008] but also in the case where species have
+different responses to environmental variation [@loreau_species_2008]. While the
+effect of species richness on synchrony is well understood, its effect on
+$\overline{CV_{sp}}$ is more complex [see @thibaut_understanding_2013].
+
+Suprisingly, we found that $\overline{CV_{sp}}$ had an negative effect twice
+higher than synchrony on biomass stability.In turn,
+we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
 stability, as predicted by the formulation of stability based on the CV
@@
 can advance two hypothesis that can raise this effect. First, the opportunity
-for diet differentiation can be low in streams compare to other organisms. Bird
-species are for example quite specialized in seed size, flying or soil arthropods or
-mammals which gives opportunities for independent dynamics. Plants also can
-achieve independent dynamics either spatial segregation or niche
-differentiation. Because fish species even piscivorous one are quite
-opportunistic in their foraging.  Secondly, in trophic communities, species
-directly affect each other through feeding interactions, and so could raise
-synchrony between species [@raimondo_interspecific_2004] more than in systems
-where interactions happen more in the form of competitive exploitation.
-
-#### Ending paragraph
-This work aims to facilitate the rapprochement between theoretical ecology and
-empirical ecology. While theoretical ecology has focused on the effects of
-network structure on stability and biomass distribution, empirical ecology
-ignored network structure. Furthermore, both fields have largely used different
-stability metrics. We tried to move forward by including network structure in
-the explanation of both total biomass and biomass stability. We showed that
-species richness and network structure can have independent effects on ecosystem
-properties. It opens a promising way for the understanding on how species
-interactions, of different types, can affect both synchrony and CVsp in
-different ecosystems. The reconstruction of ecological network with trait
-matching methods can be a first approach to document such relationship, however
-it will not compensate for close evaluation of measured interaction strength.
-We also believe that SEM methods are particularly helpful to assess complex
-relationship between environment, community structure and ecosystem properties
-in empirical data which necessitate to move from simple bivariate relationships
+for diet differentiation can be low in streams compare to other organisms.
+Secondly, in trophic communities, species directly affect each other through
+feeding interactions, and so could raise synchrony between species
+[@raimondo_interspecific_2004] more than in systems where interactions happen
+more in the form of competitive exploitation.
+
+- But @thebault_relationship_2006 with the same mecanisms on vertical and
+  horizontal diversity
+
+## Vertical diversity increased total biomass and its temporal stability
+
+The average trophic level was positively linked to total biomass. This result is
+straightforward. As feeding interactions were partly determined by body size and
+that body mass increase with body size, it is expected that the more the average
+biomass is located at higher trophic level, the more the total biomass increase.
+In contrast, connectance had no effect on total biomass. One might have expected
+that an increase in connectance should translate in higher resource transfer
+efficiency between prey and predators and so results in higher total biomass. A
+reason for such an absence of an effect might be the absence of an interaction
+strength knowledge/estimation. A consequence can be that connectance contains
+few too informations. [ADD @thebault_relationship_2006].
+
+Average trophic level had a positive effect on biomass stability by its negative
+effect on CVsp (i.e. positive effect on average species stability). It means
+that species at higher trophic level are more stable than the species at lower
+trophic levels. @shanafelt_david_w._stability_nodate and @barbier_pyramids_2019
+found the same pattern with pure trophic chain models. They have shown that
+strong top-down control can generate the pattern that we observed but it is not
+clear if this theoretical prediction holds when considering omnivorous species
+(i.e not a pure food chain) and if other mechanisms can generate the same
+pattern.  For example, species mean-variance relationship could also generate
+this pattern. Moreover, the ontogenic nature of our networks can also be an
+important mechanism at play.  Over its life span, a given fish will change of
+diet and thus move upward in the trophic chain. The dynamic of a given species
+composed of several trophic species can thus be a mix of the dynamics of several
+trophic levels, plus the oscillatory dynamics of the cohorts
+[@townsend_population_1989; @medvinsky_modelling_2015]. Then, there is a clear
+need for a better understanding of how the dynamics of pure food chain models
+would be affected by inclusion of omnivory and ontogeny.
+
+We found that connectance had no effect on temporal stability. This result
+contradicts precedent theoretical studies on the relationship between stability
+and network structure [@angelis_stability_1975; @may_will_1972;
+@thebault_stability_2010], although they considered different stability metrics
+(i.e. local stability of equilibrium point). Once again, it is possible that
+that connectance from our networks contains too few information.
+Furthermore, a crucial missing ingredient to go further is the interaction
+strength. Indeed, @may_will_1972 has theoretically demonstrated the
+fondamental interplay between connectance, species richness and average
+interaction strength (*Add ref and develop a bit*).
+
+## Horizontal and vertical diversity had common, opposite and independant effects on total biomass and its temporal stability
+
+We found that species richness had a positive and a negative effect on
+respectively total biomass and its temporal stability whereas average trophic
+level had a positive effect on both. It confirms that more investigation is needed to
+understand the mechanisms leading to common and opposite effects of
+horizontal and vertical diversity.  @thibaut_understanding_2013 have
+theoretically shown that a highly positive relationship between species variance
+and mean together with a positive relationship between mean species abundance
+(i.e. dominance) and species richness should drive to a negative temporal
+stability - species richness relationship. @thebault_relationship_2006 have
+also shown in a bi-trophic foodweb that a positive temporal stability-species
+richness appears in case of a plant species is highly dominant through low
+comsumption by consumers but in the same time highly variable because of low
+competitive ability. Then, common mecanisms might be at play for both horizontal
+and vertical diversity while having same or opposite effects on total biomass
+and its temporal stability.
+
+We found that connectance covaries negatively with species richness
+[@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010],
+connectance had itself no effects on both total biomass and its temporal
+stability. On the other side, we found species richness was not related to
+average trophic level but average trophic level covariated positively with total
+biomass and its temporal stability. It indicates that the effects of horizontal
+and vertical diversity had independant pathways and the
+importance to consider both horizontal and vertical diversity.
+
+## Environment had an high effect on total biomass and its temporal stability
+
+- add [@yang_effects_2011]
+
+Precedent researches in plant communities showed that the total biomass was
+primary driven by environmental drivers [@grace_integrative_2016]. We found that
+environmental drivers in general did not directly affect total biomass, but CV
+of enrichment was negatively linked to total biomass. Hence, average temperature
+(& inverse altitude) and average stream size had indirect effects on total
+biomass. The former had positive effect on total biomass mainly through species
+richness while the latter had a positive effect equally through species richness
+and average trophic level. It is not straightforward to explain why the effect
+average temperature and altitude was going through horizontal diversity and why
+average stream size is going through both horizontal and vertical diversity.
+(*Add more biological interpretations about total effect? Until now, what I have
+in mind is a bit bullshit and those explanations are not the heart of the paper.
+What do you think?*). 
+Overall it indicates that environment affects primarily community
+structure and then affects total biomass. Furthermore, one can notice that
+average temperature had a positive effect on total of the same magnitude than
+horizontal & vertical diversity. It underlines that environment should not be
+ignored in natural communities studies and that its effects can be mainly
+indirect and in this case, path analysis should more relevant than bivariate
+relationships [@grace_causal_2014; @grace_integrative_2016].
+
+Average temperature (& inverse of altitude) had a negative effect on temporal
+stability, mainly by an direct positive CVsp. Two mecanisms might explain this
+pattern: (i) temperature is negatively linked to concentration of dissolved
+oxygen and so might be linked to respiration stress, (ii) temperature might lead be
+to higher metabolic activity and so higher variability [@taby_warming_2019]. Interestingly, average
+temperature (& inverse of altitude) had also a negative effect on temporal
+stability through species richness but a positive one through average trophic
+level. Then, the effect of temperature on temporal stability might be more
+complex than previously thought and call for further investigations.
+Furthermore, average temperature and altitude had a stronger effect on temporal
+stability than horizontal and vertical diversity. Considering big effects of
+temperature on both total biomass and its temporal stability might suggest the
+crucial role of climate change on stream ecosystems. (*Not convinced: may be to
+discuss together*)
+
+# Conclusion and perspectives
+
+We aimed to assess the effect of horizontal & vertical diversity on empirical
+trophic communities. While theoretical ecology has focused on the effects of
+network structure on stability, empirical ecology has focused on species richess
+and ingnored network structure. Furthermore, both fields have largely used
+different stability metrics. We showed that horizontal and vertical diversity
+can have independent and sometimes opposite effects on total biomass and its
+temporal stability. It opens a promising way for the understanding on how
+species interactions, of different types, can affect both synchrony and CVsp in
+different ecosystems. The reconstruction of ecological networks based on trait
+can be a first approach to document such relationships, however it will not
+compensate for close evaluation of measured interaction strength. We also
+believe that SEM methods are particularly helpful to assess complex relationship
+between environment, community structure and ecosystem properties in empirical
+data which necessitate to move from simple bivariate relationships
 [@grace_integrative_2016]. We believe that the integration of network structure
 and species interaction in general will improve our understanding of the
-mechanisms which determines ecosystem properties.
+mechanisms which determines ecosystem properties. (*c'est pas top mais à
+discuter*)
 

### 2020-05-28 manuscript/bef_stability/appendix.Rmd
Fix result PCA with two axis

@@
     name = paste0("RC", seq(1,14)),
-    type = c(rep("Kept", 5), rep("No kept", 9)),
+    type = c(rep("Kept", 2), rep("No kept", 14 - 2)),
     value = pca_rotated$rotated$values
@@
       dimnames(pca_rotated$rotated$Structure)[[1]],
-      pca_var_replacement)
-  ) %>%
-  select(Variable, RC1, RC2, RC3, RC4, RC5)
-
+      get_pca_var_name_replacement())
+  ) %>%
+  select(Variable, RC1, RC2)
 kable(
@@
 p1 <- my_pca_plot(xaxis = "RC1", yaxis = "RC2", ctb_thld = .4)
-p2 <- my_pca_plot(xaxis = "RC3", yaxis = "RC4", ctb_thld = .4)
-p3 <- my_pca_plot(xaxis = "RC4", yaxis = "RC5", ctb_thld = .4)
-
-pca_plot <- plot_grid(p1, p2, p3, eigen_rotated_plot, nrow = 2)
+#p2 <- my_pca_plot(xaxis = "RC3", yaxis = "RC4", ctb_thld = .4)
+#p3 <- my_pca_plot(xaxis = "RC4", yaxis = "RC5", ctb_thld = .4)
+
+pca_plot <- plot_grid(p1, eigen_rotated_plot, nrow = 1)
 save_plot(
@@
   pca_plot,
-  nrow = 2, ncol = 2,
+  nrow = 1, ncol = 2,
   base_height = 6/2.54, base_asp = 1, base_width = NULL 
@@
 ```
+
+```{r stab-network, eval = FALSE}
+sem_data %>%
+  select(sync, cv_sp, ct, t_lvl) %>%
+  gather(network, metrics, ct, t_lvl) %>%
+  gather(stab_comp, value, sync, cv_sp) %>%
+  ggplot(aes(y = value, x = metrics)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_grid(stab_comp ~ network, scales = "free_x")
+
+stab_ct_mod <- lmer(data = sem_data,
+  #fixed = log_bm ~ log_rich_tot * troph_group,
+  formula = log_stab_std ~ ct + (1 | basin)
+  #random = ~ 1 + log_rich_tot * troph_group | basin,
+  #control = ctrl 
+)
+stab_ct_boot <- bootMer(stab_ct_mod, mySumm2, nsim = 100)
+stab_ct_ci <- confint(stab_ct_boot)
+
+stab_ct_sum <- piecewiseSEM::rsquared(stab_ct_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
+
+pred_stab_ct_mod <- ggpredict(stab_ct_mod, terms = c("ct"), type = "fe")
+#plot(pred_troph_mod, add.data = TRUE)
+stab_ct_pred <- pred_stab_ct_mod %>%
+  as_tibble() %>%
+  rename(
+    log_stab_std = predicted,
+    log_rich_tot_std = x,
+    troph_group = group
+  )
+
+# get coeff
+coef_stab_ct <- map(list(stab = stab_ct_mod), fixed.effects)
+
+stab_tlvl_mod <- lmer(data = sem_data,
+  #fixed = log_bm ~ log_rich_tot * troph_group,
+  formula = log_stab_std ~ t_lvl + (1 | basin)
+  #random = ~ 1 + log_rich_tot * troph_group | basin,
+  #control = ctrl 
+)
+stab_tlvl_boot <- bootMer(stab_tlvl_mod, mySumm2, nsim = 100)
+stab_tlvl_ci <- confint(stab_tlvl_boot)
+
+stab_tlvl_sum <- piecewiseSEM::rsquared(stab_tlvl_mod, method = "nagelkerke") %>%
+  mutate_at(vars(Conditional, Marginal), ~round(., 2))
+
+pred_stab_tlvl_mod <- ggpredict(stab_tlvl_mod, terms = c("t_lvl"), type = "fe")
+#plot(pred_troph_mod, add.data = TRUE)
+stab_tlvl_pred <- pred_stab_tlvl_mod %>%
+  as_tibble() %>%
+  rename(
+    log_stab_std = predicted,
+    log_rich_tot_std = x,
+    troph_group = group
+  )
+
+# get coeff
+coef_stab_tlvl <- map(list(stab = stab_tlvl_mod), fixed.effects)
+```

### 2020-05-28 manuscript/bef_stability/manuscript.Rmd
Fix result PCA with two axis

@@
 
-```{r, echo = FALSE, results = FALSE}
+```{r, echo = FALSE, results = FALSE, message = FALSE}
 mypath <- rprojroot::find_package_root_file
@@
 
-```{r}
+```{r, results = FALSE}
 knitr::opts_chunk$set(
@@
 
-Biodiversity is essential to determine and maintain ecosystem properties
+Biodiversity is a key to determine ecosystem properties
 [@duffy_why_2009]. Current biodiversity losses and global changes question the
 way in which ecosystems will be affected in turn [@bellard_impacts_2012]. Since
-1970s and the @may_will_1972 seminal paper, ecology aims to uncover the complex
-relationships between biodiversity and ecosystem properties [@hector_plant_1999;
+the seminal of paper of @may_will_1972, the relationships between
+biodiversity and ecosystem properties have received a lot of attention [@hector_plant_1999;
 @loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
 @duffy_why_2009; @isbell_forest_quantifying_2018]. Because biodiversity largely
-determines both quantity and distribution of biomass or energy across
-ecosystems, it has a tremendous effects on the properties exhibited by an
+determines both the quantity and the distribution of matter and energy across
+ecosystems, it has a tremendous effect on the properties exhibited by an
 ecosystem, such as its total biomass [@hector_plant_1999;
@@
 Biodiversity can be quantified in numerous ways, as the number of species, i.e.
-species richness and in number of functional groups, i.e species are
-gathered on what they do. Those metrics can be gathered into "horizontal
-diversity", describing the list of components present in a community, i.e. here
-species and functional groups. An
-orthogonal view, based on trophic chains, described species on what they eat. It 
-can be defined as interactions (or biomass/energy fluxes) between species and how
-they are distributed among communities. It can be quantified as the number
-of interaction between species or the number of trophic level. This orthogonal
-view of seeing biodiversity, can be gathered into "vertical diversity".  
-Horizontal and vertical diversity are two views of quantifying biodiversity that
-are, however, not independent from each other [@duffy_functional_2007; @zhao_horizontal_2019]. The add
-or removal of one species can have different effects depending on its vertical
-position in the trophic chain [@duffy_functional_2007]. Hence, it is crucial to
-study their interplay to improve our understanding of ecosystem dynamics. 
+species richness and in number of functional groups, i.e. species are
+gathered on what they do [@tilman_biodiversity_2014]. Those metrics can be
+gathered into "horizontal diversity", describing the list of components present
+in a community, i.e. here species and functional groups. An orthogonal
+perspective, based on trophic chains, described species on what they eat. It can
+be defined as interactions (or biomass/energy fluxes) between species and how
+they are distributed among communities. It can be quantified as the number of
+interaction between species or the number of trophic level. This orthogonal view
+of seeing biodiversity, can be gathered into "vertical diversity". Horizontal
+and vertical diversity are, however, not independent from each other
+[@duffy_functional_2007; @zhao_horizontal_2019]. The add or removal of one
+species can have different effects depending on its vertical position in the
+trophic chain [@duffy_functional_2007]. Hence, it is crucial to study their
+interplay to improve our understanding of ecosystem dynamics. 
 (*This paragraph is surely too simplistic*)
@@
 Horizontal and vertical diversity has been shown to promote higher biomass
-production in a variety of ecosystems. Horizontal diversity, as species richness, has been
-reported to increase productivity through complementarity between species in
-resource exploitation and selection effects in plant communities
-[@tilman_productivity_1996; @cardinale_species_2002; @grace_integrative_2016].
-Regarding total biomass, empirical assessment have
+production in a variety of ecosystems. Horizontal diversity, as species
+richness, has been reported to increase productivity through complementarity
+between species in resource exploitation and selection effects in plant
+communities [@tilman_productivity_1996; @cardinale_species_2002;
+@grace_integrative_2016].  Regarding total biomass, empirical assessment have
 shown generally positive relationships with species richness in plant
@@
 @grace_integrative_2016], as in mesocosms [@pennekamp_biodiversity_2018].
-Theoretical models have also confirmed that an increase in horizontal diversity should
-translate into increase in plant biomass through resource complementarity
+Theoretical models have also confirmed that an increase in horizontal diversity
+should translate into increase in plant biomass through resource complementarity
 [@loreau_biodiversity_1998] and selection effects [@tilman_plant_1997]. The
@@
 positive relationship between plant biomass and plant diversity as a significant
-amount of biomass is transfered to consumers [@thebault_food-web_2003]. It has been shown both in
-experiments [REF] and theoretical models [@thebault_food-web_2003].
-@thebault_relationship_2006 have shown with a theoretical model that total biomass should increase with
-the increase species diversity at two trophic level. However, the joint effects
-of horizontal and vertical diversity on total biomass has been
-rarely tested, especially in natural communities. It is not clear whether
-horizontal and vertical diversity just change the distribution of biomass across
-trophic level or it increases the total amount of  biomass (*It misses a lot of
-references here*).
+amount of biomass is transfered to consumers [@thebault_food-web_2003]. It has
+been shown both in experiments [REF] and theoretical models
+[@thebault_food-web_2003].  @thebault_relationship_2006 have shown with a
+theoretical model that total biomass should increase with the increase species
+diversity at two trophic level. However, the joint effects of horizontal and
+vertical diversity on total biomass has been rarely tested, especially in
+natural communities. It is not clear whether horizontal and vertical diversity
+just change the distribution of biomass across trophic level or it increases the
+total amount of  biomass (*It misses a lot of references here*).
 
@@
 @oliver_heterogeneous_2010; @friedpetersen_drivers_2020]. Hydrology of streams
-constraints the composition of fish communities [REF toulouse à balle], and is
-also related to fish population temporal stability [@franssen_annual_2011].
+constraints the composition of fish communities [REF toulouse à balle], and has
+already been related to fish population temporal stability [@franssen_annual_2011].
 However it is not clear which is the relative strength of direct and indirect
@@
 was as connectance and average trophic level. Environment was characterized by
-the stream size, altitude, slope, and the temperature, flow, enrichment and
-their temporal variability (expect for altitude and slope). Finally total
+the stream size, altitude, slope, and the temperature, flow and enrichment. Finally total
 biomass was measured as median total biomass over the sampling period while its
@@
 ```{r}
-myload(nmds, habitat_pressure, dir = mypath("report"))
+# Basin
 st_basin <- get_basin_station(sf_obj = FALSE)
+
+# Select fishing operation 
 myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
@@
 
-# Compute stability, network metrics, etc with ;he new datasets
-##myload(network_metrics, dir = mypath("data", "classes"))
-#network_metrics %>%
-  #left_join(op_analysis, by = "opcod") %>%
-  #select(opcod, station, composition) %>%
-  #unnest(composition) %>%
-  #group_by(station, troph_group) %>%
-  #summarise(richness_tot = length(unique(species)))
+```
+
+```{r, fig.show = "hide"}
+myload(
+  hab_analysis,
+  temporal_station_desc,
+  temporal_press_polluants,
+  geo_station,
+  dir = mypath("data")
+)
+habitat_press <- build_habitat_pressure_dataset(
+  .habitat_analysis = hab_analysis,
+  .tmp_press = temporal_press_polluants,
+  .tmp_st_desc = temporal_station_desc,
+  .geo_st = geo_station 
+)
+
+# Make PCA 
+habitat_press %<>% na.omit()
+mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())
+
+pca_rotated <- compute_rotated_pca(
+  .data = habitat_press[, mask],
+  naxis = 2
+)
+habitat_pressure <- 
+  cbind(habitat_press[, c("station", "temperature_med", "alt")], pca_rotated$rotated$score) %>%
+  as_tibble
+ggplot(habitat_pressure, aes(x = RC2, y = temperature_med)) +
+  geom_point()
+
+ggplot(
+  pivot_longer(habitat_pressure, cols = c("RC1", "RC2"),
+    names_to = "variable", values_to = "value"
+  )
+  , aes(x = value)) +
+geom_histogram() +
+facet_grid(cols = vars(variable))
+
+```
+
+```{r}
+prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
+  map_dbl(., ~round(.x * 100))
+tot_var_expl_pca <- sum(prop_var_expl_pca) 
+```
+
+```{r, message = FALSE, results = FALSE}
+# Com
 com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
@@
 
-```{r, eval = FALSE}
-stab_div_troph <- com_data$tps_bm_troph %>%
-  filter(troph_group != 1) %>%
-  mutate(troph_group = as.factor(troph_group),
-    log_rich = log10(richness_med),
-    log_rich_std = log10(rich_std_med),
-    log_rich_tot = log10(richness_tot),
-    log_rich_tot_std = log10(rich_tot_std),
-    log_bm = log10(biomass_med),
-    log_bm_std = log10(bm_std_med),
-    log_stab = log10(biomass_stab),
-    log_stab_std = log10(bm_std_stab)
-    ) %>%
-  dplyr::select(station, troph_group, biomass_stab, richness_med, richness_tot, log_rich, log_rich_std, log_rich_tot, log_rich_tot_std, log_stab, log_stab_std, log_bm, log_bm_std, biomass_med, bm_std_med, richness_tot, rich_tot_std) %>%
-  dplyr::left_join(st_basin, by = "station")
-```
-
 ## Environment
-
-```{r}
-myload(
-  hab_analysis,
-  temporal_station_desc,
-  temporal_press_polluants,
-  geo_station,
-  dir = mypath("data")
-)
-habitat_press <- build_habitat_pressure_dataset(
-  .habitat_analysis = hab_analysis,
-  .tmp_press = temporal_press_polluants,
-  .tmp_st_desc = temporal_station_desc,
-  .geo_st = geo_station 
-)
-```
-
-```{r, fig.show = "hide"}
-evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
-  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler", "DBO_med")
-evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
-  "avg_depth_station_cv", "DBO_cv")
-pca_pressure <- habitat_press[, names(habitat_press) %in% c(evt_var_mean, evt_var_cv, "station")] %>%
-  na.omit
-
-pca_rotated <- compute_rotated_pca(
-  .data = pca_pressure[, !names(pca_pressure) %in% "station"],
-  naxis = 5 
-)
-
-prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
-  map_dbl(., ~round(.x * 100))
-
-tot_var_expl_pca <- round(sum(pca_rotated$rotated$Vaccounted["Proportion Var", ]) * 100) 
-```
 
@@
 environmental variables are often collinear, a principal component analysis (PCA)
-was performed on the scaled variables. The PCA explained `r tot_var_expl_pca`%
-of the variance. An axis rotation was performed to maximize the representation
+was performed on the scaled variables. We kept in the analysis the two first
+principal components based on eigen values distribution (Fig. SXX).
+The PCA explained `r tot_var_expl_pca`%
+of the variance. An varimax axis rotation was performed to maximize the representation
 of the variables by the principal components (Fig. \@ref(fig:pca-rotated)).
@@
 slopes which had $P$ value inferior to $0.05$ were reported (but see Table SXX).
-Linear models and SEMs were computed with respectively the `nlme` and
-`piecewieseSEM` R packages. The code used for the analysis are accessible on
-github.
 
@@
 
+Environmental variables were interpolated with the `openStars` and `SSN`
+packages. Linear models and SEMs were computed with respectively the `nlme` and
+`piecewieseSEM` R packages. The code used for the analysis and the Rmarkdown
+used to generate this document are accessible on github.
+
 ```{r get-data, cache = FALSE}
@@
 
-```{r mod-div-total, eval = FALSE}
-stab_div_mod <- lmer(
-  data = sem_data,
-  control = ctrl_lmer,
-  formula = log_stab_std ~ log_rich_tot_std + (1 | basin)
-)
-stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
-stab_div_boot <- bootMer(stab_div_mod, mySumm2, nsim = 100)
-stab_div_ci <- confint(stab_div_boot)
-#stab_div_colin <- car::vif(stab_div_mod) not use if one response
-stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke") %>%
-  mutate_at(vars(Conditional, Marginal), ~round(., 2))
-
-pred <- ggpredict(stab_div_mod, terms = c("log_rich_tot_std"), type = "fe")
-stab_div_pred <- pred %>%
-  as_tibble() %>%
-  rename(
-    log_stab_std = predicted,
-    log_rich_tot_std = x,
-    basin = group
-  )
-stab_div_pred %<>%
-  mutate(
-    stab = 10^log_stab_std, # FALSE
-    rich = 10^log_rich_tot_std,
-    cl10 =  10^conf.low,
-    ch10 =  10^conf.high
-  )
-
-#
-bm_div_mod <- lmer(data = sem_data,
-  formula = log_bm_std ~ log_rich_tot_std + (1 | basin)
-)
-bm_div_boot <- bootMer(bm_div_mod, mySumm2, nsim = 100)
-bm_div_ci <- confint(bm_div_boot)
-bm_div_sum <- piecewiseSEM::rsquared(bm_div_mod, method = "nagelkerke") %>%
-  mutate_at(vars(Conditional, Marginal), ~round(., 2))
-
-pred <- ggpredict(bm_div_mod, terms = c("log_rich_tot_std"), type = "fe")
-#plot(pred, add.data = TRUE)
-bm_div_pred <- pred %>%
-  as_tibble() %>%
-  rename(
-    log_bm_std = predicted,
-    log_rich_tot_std = x,
-    basin = group
-  )
-
-# get coeff
-coef_div <- map(list(stab = stab_div_mod, bm = bm_div_mod), fixef)
-```
-
-```{r mod-div-troph, fig.show = "hide", eval = FALSE}
-stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
-  formula = log_stab_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
-  #control = ctrl
-)
-
-stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
-  formula = log_stab_std ~  troph_group + (1 | basin)
-  #control = ctrl
-)
-
-stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
-stab_troph_ci <- confint(stab_troph_boot)
-
-#stab_troph_colin <- car::vif(stab_troph_mod)
-stab_troph_sum <- piecewiseSEM::rsquared(stab_troph_mod, method = "nagelkerke") %>%
-  mutate_at(vars(Conditional, Marginal), ~round(., 2))
-
-#pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
-##plot(pred_troph_mod, add.data = TRUE)
-#stab_troph_pred <- pred_troph_mod %>%
-  #as_tibble() %>%
-  #rename(
-    #log_stab_std = predicted,
-    #log_rich_tot_std = x,
-    #troph_group = group
-  #)
-
-## Productivity and troph group
-
-#bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
-  ##fixed = log_bm ~ log_rich_tot * troph_group,
-  #formula = log_bm_std ~ log_rich_tot_std + troph_group + log_rich_tot_std:troph_group + (1 | basin)
-  ##random = ~ 1 + log_rich_tot * troph_group | basin,
-  ##control = ctrl 
-#)
-#bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
-#bm_troph_ci <- confint(bm_troph_boot)
-
-#bm_troph_sum <- piecewiseSEM::rsquared(bm_troph_mod, method = "nagelkerke") %>%
-  #mutate_at(vars(Conditional, Marginal), ~round(., 2))
-
-#pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot_std", "troph_group"), type = "fe")
-##plot(pred_troph_mod, add.data = TRUE)
-#bm_troph_pred <- pred_troph_mod %>%
-  #as_tibble() %>%
-  #rename(
-    #log_bm_std = predicted,
-    #log_rich_tot_std = x,
-    #troph_group = group
-  #)
-
-## get coeff
-#coef_troph <- map(list(stab = stab_troph_mod, bm = bm_troph_mod), fixed.effects)
-```
-```{r stab-div-troph, eval = FALSE}
-stab_div_by_troph <- compute_stat_troph_rich(
-  .data = stab_div_troph,
-  resp = "log_stab_std"
-)
-
-bm_div_by_troph <- compute_stat_troph_rich(
-  .data = stab_div_troph,
-  resp = "log_bm_std"
-)
-troph_perm_test <- map(c(stab = "log_stab_std", bm = "log_bm_std"),
-  ~test_troph(.data = stab_div_troph, var = .x)
-  )
-troph_perm_test$bm$obs
-troph_perm_test$stab$obs
-troph_perm_test$bm$p_val
-troph_perm_test$stab$p_val
-```
-
 ```{r}
@@
 
-def_env_x_pos <- c(from = 0, to = 6)
+def_env_x_pos <- c(from = 0, to = 3)
+asp <- 1.6
 
@@
   width = 700*2,
-  height = 900*2  - 900*2*30/100,
+  height = 700*2 * asp,
   arrows = "ortho",
@@
   env_y_sep = 1.5,
-  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2"),
+  order_env_node = c("log_RC1", "log_RC2"),
   metamodel = TRUE
@@
   env_y_sep = 1.5,
-  order_env_node = c("RC4", "log_RC3", "RC5", "log_RC1", "log_RC2")
+  order_env_node = c("log_RC1", "log_RC2")
 )
@@
   width = 700*2,
-  height = 900*2  - 900*2*45/100,
+  height = 700*2 * asp,
   arrows = "ortho",
@@
   filter(P.Value < 0.05)
-```
-
-```{r stab-network, fig.show = "hide"}
-sem_data %>%
-  select(sync, cv_sp, ct, t_lvl) %>%
-  gather(network, metrics, ct, t_lvl) %>%
-  gather(stab_comp, value, sync, cv_sp) %>%
-  ggplot(aes(y = value, x = metrics)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_grid(stab_comp ~ network, scales = "free_x")
-
-stab_ct_mod <- lmer(data = sem_data,
-  #fixed = log_bm ~ log_rich_tot * troph_group,
-  formula = log_stab_std ~ ct + (1 | basin)
-  #random = ~ 1 + log_rich_tot * troph_group | basin,
-  #control = ctrl 
-)
-stab_ct_boot <- bootMer(stab_ct_mod, mySumm2, nsim = 100)
-stab_ct_ci <- confint(stab_ct_boot)
-
-stab_ct_sum <- piecewiseSEM::rsquared(stab_ct_mod, method = "nagelkerke") %>%
-  mutate_at(vars(Conditional, Marginal), ~round(., 2))
-
-pred_stab_ct_mod <- ggpredict(stab_ct_mod, terms = c("ct"), type = "fe")
-#plot(pred_troph_mod, add.data = TRUE)
-stab_ct_pred <- pred_stab_ct_mod %>%
-  as_tibble() %>%
-  rename(
-    log_stab_std = predicted,
-    log_rich_tot_std = x,
-    troph_group = group
-  )
-
-# get coeff
-coef_stab_ct <- map(list(stab = stab_ct_mod), fixed.effects)
-
-stab_tlvl_mod <- lmer(data = sem_data,
-  #fixed = log_bm ~ log_rich_tot * troph_group,
-  formula = log_stab_std ~ t_lvl + (1 | basin)
-  #random = ~ 1 + log_rich_tot * troph_group | basin,
-  #control = ctrl 
-)
-stab_tlvl_boot <- bootMer(stab_tlvl_mod, mySumm2, nsim = 100)
-stab_tlvl_ci <- confint(stab_tlvl_boot)
-
-stab_tlvl_sum <- piecewiseSEM::rsquared(stab_tlvl_mod, method = "nagelkerke") %>%
-  mutate_at(vars(Conditional, Marginal), ~round(., 2))
-
-pred_stab_tlvl_mod <- ggpredict(stab_tlvl_mod, terms = c("t_lvl"), type = "fe")
-#plot(pred_troph_mod, add.data = TRUE)
-stab_tlvl_pred <- pred_stab_tlvl_mod %>%
-  as_tibble() %>%
-  rename(
-    log_stab_std = predicted,
-    log_rich_tot_std = x,
-    troph_group = group
-  )
-
-# get coeff
-coef_stab_tlvl <- map(list(stab = stab_tlvl_mod), fixed.effects)
 ```
@@
 rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_rich_tot_std")
+rich_on_tlvl <- get_clean_sem_coef(sem = bm_sem_coef, resp = "t_lvl", pred = "log_rich_tot_std")
 tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
@@
   meaning." 
-
 )
@@
 ```{r indir-stab}
-format_table <- function (x = tmp_stab_indir_table) {
-  x <- x[, c("variable", names(x)[!names(x) %in% "variable"])]
-
-  rm_n <- str_remove_all(get_sem_var_name_replacement(), pattern = "\n")
-  names(rm_n) <- names(get_sem_var_name_replacement()) 
-  x$variable <- str_replace_all(x$variable, rm_n)
-
-  colnames(x) %<>% str_remove_all(., pattern = "via_")
-
-  col_replacement <- c(
-    variable = "Variable",
-    cv_sp = "CVsp",
-    sync = "Synchrony",
-    richness = "Horizontal diversity",
-    com = "Vertical diversity",
-    richness_com = "Horizontal & vertical diversity",
-    total = "Total effect"
-  )
-  colnames(x) %<>% str_replace_all(., col_replacement)
-
-  x
-}
-
 kable(format_table(tmp_stab_indir_table),
@@
 ```{r indir-bm}
-
 kable(format_table(tmp_bm_indir_table),
@@
 stab_sem_coef <- filter(coef_stab_sem, P.Value < 0.05)
-get_clean_sem_coef <- function(sem = NULL, resp = NULL, pred = NULL) {
-  out <- sem[sem$Response == resp & sem$Predictor == pred, ]$Std.Estimate
-  out <- ifelse(length(out) == 0, 0, out)
-  round(out, 2)
-}
 
@@
 RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
+tlvl_on_cv_sp <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_cv_sp", pred = "t_lvl")
 ```
@@
 
+Overall, the structural equation models explained a large part of the variation
+of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
+.45$, $.47$, $.49$ and $.38$) but not of average trophic level ($R^2 =
+.18$, Figure \@ref(fig:sem-plot) C and D).
+
+## Horizontal diversity increased total biomass but decreased its temporal stability
+
 ```{r get-sem-tot-effect-rich}
@@
 ```
-
-Overall, the structural equation models explained a large part of the variation
-of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
-.45$, $.47$, $.49$ and $.38$) but not of average trophic level ($R^2 =
-.18$, Figure \@ref(fig:sem-plot) C and D).
-
-## Horizontal diversity increased total biomass but decreased its temporal stability
 
@@
 temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$, Table
-\@ref(tab:indir-stab)) by decreasing $\overline{CV_{sp}}$ ($r_\delta = -0.26$,
+\@ref(tab:indir-stab)) by decreasing $\overline{CV_{sp}}$
+($r_\delta = `r tlvl_on_cv_sp`$,
 Figure \@ref(fig:sem-plot) C). Again, connectance had no significant effect on
@@
 The total effect of average trophic level on total biomass was of the same
-magnitude than the one of species richness (resp. $0.30$ and $0.36$, Table
-\@ref(tab:indir-bm)). It was also true for temporal stability (resp. $0.34$ and
-$-0.24$, Table \@ref(tab:indir-stab)). Average trophic level was
-independent of species richness because species richness had no significant
-effect on average trophic level. However species richness had a strong negative
-effect on connectance ($r_\delta = -0.64$, Figure \@ref(fig:sem-plot) C and D).
-But, in turn, connectance had no significant effect on either total biomass nor
+magnitude than the one of species richness (resp. $`r tlvl_on_bm`$ and
+$`r rich_on_bm$total`$, Table
+\@ref(tab:indir-bm)). It was also true for temporal stability (resp.
+$`r com_on_stab$total["t_lvl"]`$ and
+$`r rich_on_stab$total`$, Table \@ref(tab:indir-stab)). Average trophic level was
+dependent of species richness because species richness had a significant
+negative effect on average trophic level ($r_\delta = `r rich_on_tlvl`$). 
+Species richness had also a strong negative effect on connectance ($r_\delta =
+`r rich_on_stab$total`$, Figure \@ref(fig:sem-plot) C and D).  But, in turn,
+connectance had no significant effect on either total biomass nor
 its temporal stability.
@@
 
-The CV of enrichment had a direct negative effect on total biomass ($r_\delta =
--0.24$, Figure \@ref(fig:sem-plot) D). The other environmental variables had no
-significant direct effects on total biomass (Table SXX). Avg temperature and
-altitude respectively increased and decreased total biomass ($r_\delta = 0.30$,
-Table \@ref(tab:indir-bm)), mainly through species richness ($r_\delta = 0.21$,
-Table \@ref(tab:indir-bm)). Average stream size had a positive effect on total
-biomass ($r_\delta = 0.18$, Table \@ref(tab:indir-bm)), equally through species
-richness and average trophic level ($r_\delta = 0.09$, Table
-\@ref(tab:indir-bm)). Average temperature and altitude effects on total biomass
-were of the same magnitude than the effects on species richness and average
-trophic level.
+The environmental variables had no significant direct effects on total biomass
+(Table SXX), but indirect (Table \@ref(tab:indir-bm)). Average temperature and
+altitude respectively increased and decreased total biomass ($r_\delta =
+`r env_on_bm$direct["log_RC2"]`$, Table \@ref(tab:indir-bm)), mainly through
+species richness ($r_\delta = `r env_on_bm$via_richness["log_RC2"]`$, Table
+\@ref(tab:indir-bm)).  Average stream size had a positive effect on total
+biomass ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-bm)),
+equally through species richness and average trophic level 
+($r_\delta = `r env_on_bm$via_richness["log_RC1"]`$ and
+$`r env_on_bm$via_com["log_RC1"]`$ resp., Table \@ref(tab:indir-bm)). Average
+temperature and altitude effects on total biomass were of the same magnitude
+than the effects on species richness and average trophic level.
 
 Average temperature and altitude had a negative and a positive effect on
-temporal stability ($r_\delta = -.43$, Table \@ref(tab:indir-stab)) mainly
-through a direct positive effect on $\overline{CV_{sp}}$ ($r_\delta = -.40$,
-Table \@ref(tab:indir-stab)). Interesting, average temperature (and reverse of
+temporal stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-stab)) mainly
+through a direct positive effect on $\overline{CV_{sp}}$
+($r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-stab)).
+Interesting, average temperature (and reverse of
 altitude, *chiant cette variable composite*) had also a negative effect on
 temporal stability through species richness but a positive one through average
-trophic level (resp. $r_\delta = -.14$ and $r_\delta = .10$, Table
-\@ref(tab:indir-stab)). This was also true for average river size but effects
-were weak. Finally, the effect of average temperature on temporal stability had
-a magnitude higher than species richness and average trophic level (Table
-\@ref(tab:indir-stab)).
+trophic level (resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
+$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-stab)).
+This was also true for average river size but effects were weak. Finally, the
+effect of average temperature on temporal stability had a magnitude higher than
+species richness and average trophic level (Table \@ref(tab:indir-stab)).
 
@@
 
-## Horizontal and vertical diversity had common, opposite and independant effects on total biomass and its temporal stability
+## Horizontal and vertical diversity had common, opposite and dependant effects on total biomass and its temporal stability
 
@@
 connectance had itself no effects on both total biomass and its temporal
-stability. On the other side, we found species richness was not related to
-average trophic level but average trophic level covariated positively with total
-biomass and its temporal stability. It indicates that the effects of horizontal
-and vertical diversity had independant pathways and the
-importance to consider both horizontal and vertical diversity.
+stability. On the other side, we found species richness was negatively related
+to average trophic level and average trophic level covariated positively with
+total biomass and its temporal stability. Hence, horizontal diversity had a
+direct positive and negative effect respectively on total biomass and its
+stability but a negative and positive effect through vertical diversity. It
+indicates the importance to consider both horizontal, vertical diversity and
+their dependance.
 
@@
 Precedent researches in plant communities showed that the total biomass was
-primary driven by environmental drivers [@grace_integrative_2016]. We found that
-environmental drivers in general did not directly affect total biomass, but CV
-of enrichment was negatively linked to total biomass. Hence, average temperature
-(& inverse altitude) and average stream size had indirect effects on total
-biomass. The former had positive effect on total biomass mainly through species
-richness while the latter had a positive effect equally through species richness
-and average trophic level. It is not straightforward to explain why the effect
-average temperature and altitude was going through horizontal diversity and why
-average stream size is going through both horizontal and vertical diversity.
-(*Add more biological interpretations about total effect? Until now, what I have
-in mind is a bit bullshit and those explanations are not the heart of the paper.
-What do you think?*). 
-Overall it indicates that environment affects primarily community
-structure and then affects total biomass. Furthermore, one can notice that
-average temperature had a positive effect on total of the same magnitude than
-horizontal & vertical diversity. It underlines that environment should not be
-ignored in natural communities studies and that its effects can be mainly
-indirect and in this case, path analysis should more relevant than bivariate
-relationships [@grace_causal_2014; @grace_integrative_2016].
+primary driven by environmental drivers [@grace_integrative_2016]. We did not
+find direct but indirect effects of environmental drivers on total biomass. The
+average temperature (& inverse altitude) was positively linked to total biomass
+mainly through species richness while the average stream size had a positive
+link equally through species richness and average trophic level. It is not
+straightforward to explain why the effect average temperature and altitude was
+going through horizontal diversity and why average stream size is going through
+both horizontal and vertical diversity.  (*Add more biological interpretations
+about total effect? Until now, what I have in mind is a bit bullshit and those
+explanations are not the heart of the paper.  What do you think?*).  Overall it
+indicates that environment affects primarily community structure and then
+affects total biomass. Furthermore, one can notice that average temperature had
+a positive effect on total of the same magnitude than horizontal & vertical
+diversity. It underlines that environment should not be ignored in natural
+communities studies and that its effects can be mainly indirect and in this
+case, path analysis should more relevant than bivariate relationships
+[@grace_causal_2014; @grace_integrative_2016].
 
@@
 pattern: (i) temperature is negatively linked to concentration of dissolved
-oxygen and so might be linked to respiration stress, (ii) temperature might lead be
-to higher metabolic activity and so higher variability [@taby_warming_2019]. Interestingly, average
-temperature (& inverse of altitude) had also a negative effect on temporal
-stability through species richness but a positive one through average trophic
-level. Then, the effect of temperature on temporal stability might be more
-complex than previously thought and call for further investigations.
-Furthermore, average temperature and altitude had a stronger effect on temporal
-stability than horizontal and vertical diversity. Considering big effects of
-temperature on both total biomass and its temporal stability might suggest the
-crucial role of climate change on stream ecosystems. (*Not convinced: may be to
-discuss together*)
+oxygen and so might be linked to respiration stress, (ii) temperature might lead
+be to higher metabolic activity and so higher variability [@taby_warming_2019].
+Interestingly, average temperature (& inverse of altitude) had also a negative
+effect on temporal stability through species richness but a positive one through
+average trophic level. Then, the effect of temperature on temporal stability
+might be more complex than previously thought and call for further
+investigations. Furthermore, average temperature and altitude had a stronger
+effect on temporal stability than horizontal and vertical diversity. Considering
+big effects of temperature on both total biomass and its temporal stability
+might suggest the crucial role of climate change on stream ecosystems. (*Not
+convinced: may be to discuss together*)
 

### 2020-05-29 manuscript/bef_stability/manuscript.Rmd
Stuck to vertical diversity on total biomass

@@
 
-Biodiversity is a key to determine ecosystem properties
-[@duffy_why_2009]. Current biodiversity losses and global changes question the
-way in which ecosystems will be affected in turn [@bellard_impacts_2012]. Since
-the seminal of paper of @may_will_1972, the relationships between
-biodiversity and ecosystem properties have received a lot of attention [@hector_plant_1999;
-@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
-@duffy_why_2009; @isbell_forest_quantifying_2018]. Because biodiversity largely
-determines both the quantity and the distribution of matter and energy across
-ecosystems, it has a tremendous effect on the properties exhibited by an
-ecosystem, such as its total biomass [@hector_plant_1999;
-@tilman_biodiversity_2014; @grace_integrative_2016;
-@pennekamp_biodiversity_2018]], its biomass production
+Current biodiversity losses and global changes affect ecosystems in complex and
+unpredictable ways [@bellard_impacts_2012]. Since the seminal of paper of
+@may_will_1972, the relationships between biodiversity and ecosystem properties
+have received a lot of attention [@hector_plant_1999; @loreau_biodiversity_2001;
+@hooper_effects_2005; @dunne_network_2006; @duffy_why_2009;
+@isbell_forest_quantifying_2018]. Biodiversity largely determines both the
+amount and the distribution of matter and energy fluxes within ecosystems, and
+has hence a tremendous effect on ecosystem properties [@duffy_why_2009], such as
+its total biomass [@hector_plant_1999; @tilman_biodiversity_2014;
+@grace_integrative_2016; @pennekamp_biodiversity_2018]], biomass production
 [@tilman_productivity_1996; @cardinale_species_2002; @grace_integrative_2016]
-and the temporal stability of its biomass [@thebault_trophic_2005;
+and the biomass temporal stability [@thebault_trophic_2005;
 @thebault_relationship_2006; @tilman_biodiversity_2006;
@@
 
-Biodiversity can be quantified in numerous ways, as the number of species, i.e.
-species richness and in number of functional groups, i.e. species are
-gathered on what they do [@tilman_biodiversity_2014]. Those metrics can be
-gathered into "horizontal diversity", describing the list of components present
-in a community, i.e. here species and functional groups. An orthogonal
-perspective, based on trophic chains, described species on what they eat. It can
-be defined as interactions (or biomass/energy fluxes) between species and how
-they are distributed among communities. It can be quantified as the number of
-interaction between species or the number of trophic level. This orthogonal view
-of seeing biodiversity, can be gathered into "vertical diversity". Horizontal
-and vertical diversity are, however, not independent from each other
+Biodiversity can be quantified in numerous ways: either as the number of species
+(i.e.  species richness) and in number of functional groups, which are usually
+defined based on the trophic ecology of species, namely the way they acquire
+food [@allan_stream_2007]. Those metrics can be organized into (i) "horizontal
+diversity", which captures the overall diversity of components (i.e. species)
+present in a community, and (ii) "vertical diversity" which captures diversity
+of components across functional groups, such as the amount trophic categories,
+often termed guilds or levels [@allan_stream_2007; @loreau_population_2010;
+@zhao_horizontal_2019; @wang_biodiversity_2017]. Vertical diversity has been
+primarily quantified as food chain length [@loreau_population_2010;
+@zhao_horizontal_2019; @wang_biodiversity_2017] but it can also be characterized
+by the food web structure [@wang_biodiversity_2017] such as connectance and
+average trophic level. Horizontal and vertical diversity are, however, not
+independent from each other. Connectance is known to covary negatively with
+species richness [@winemiller_must_1989; @dunne_network_2006;
+@thebault_stability_2010].
+
+**Horizontal and vertical diversity are, however, not independent from each other
 [@duffy_functional_2007; @zhao_horizontal_2019]. The add or removal of one
-species can have different effects depending on its vertical position in the
+species (i.e. ) can have different effects depending on its vertical position in the
 trophic chain [@duffy_functional_2007]. Hence, it is crucial to study their
-interplay to improve our understanding of ecosystem dynamics. 
-(*This paragraph is surely too simplistic*)
+interplay to improve our understanding of ecosystem dynamics.**
 
@@
 
-Horizontal and vertical diversity has been shown to promote higher biomass
-production in a variety of ecosystems. Horizontal diversity, as species
-richness, has been reported to increase productivity through complementarity
-between species in resource exploitation and selection effects in plant
-communities [@tilman_productivity_1996; @cardinale_species_2002;
-@grace_integrative_2016].  Regarding total biomass, empirical assessment have
-shown generally positive relationships with species richness in plant
-communities [@hector_plant_1999; @tilman_biodiversity_2014, but see
-@grace_integrative_2016], as in mesocosms [@pennekamp_biodiversity_2018].
-Theoretical models have also confirmed that an increase in horizontal diversity
-should translate into increase in plant biomass through resource complementarity
-[@loreau_biodiversity_1998] and selection effects [@tilman_plant_1997]. The
-addition of trophic levels, notably consumer on plants generally breaks the
-positive relationship between plant biomass and plant diversity as a significant
-amount of biomass is transfered to consumers [@thebault_food-web_2003]. It has
-been shown both in experiments [REF] and theoretical models
-[@thebault_food-web_2003].  @thebault_relationship_2006 have shown with a
-theoretical model that total biomass should increase with the increase species
-diversity at two trophic level. However, the joint effects of horizontal and
-vertical diversity on total biomass has been rarely tested, especially in
-natural communities. It is not clear whether horizontal and vertical diversity
-just change the distribution of biomass across trophic level or it increases the
+Horizontal diversity has been shown to promote higher biomass production in a
+variety of ecosystems. Horizontal diversity, as species richness, has been
+reported to increase primary productivity [@cardinale_species_2002,
+@tilman_productivity_1996; @grace_integrative_2016]. Two mechanisms have been
+proposed to rise this effect [@loreau_partitioning_2001]. The complementarity in
+resource use, rising through niche differentiation and interspecific
+facilitation, increase the total amount of resource used
+[@loreau_biodiversity_1998; @cardinale_species_2002; @loreau_partitioning_2001].
+Positive select effect arise when species richness leads to an higher dominance
+of the most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
+As for total biomass, empirical studies have generally demonstrated positive
+relationships with species richness in plant communities [@hector_plant_1999;
+@tilman_biodiversity_2014; but see @grace_integrative_2016] and mesocosms
+[@pennekamp_biodiversity_2018]. When adding the vertical diversity, e.g.
+consumers species, @gamfelt_species_2005 and @thebault_relationship_2006 have found that total
+biomass increased with increasing species diversity at two trophic levels.
+But this positive relation seems to strongly depend on the niche differentiation of
+the consumer species, i.e. their resource complementarity,
+@thebault_relationship_2006. Hence, the total biomass-species richness
+relationship seems to be supported by the same mechanisms within consumers and
+within plants. (also duffy_ecosystem_2005)
+
+The effect of the vertical diversity itself does not seem to affect total
+biomass. But seek food chain length, connectance
+
+You should connect average trophic level to biomass repartition (good when lots
+of omnivory and no trophic chain)
+
+- Effect of food web structure on total biomass are relatively absent
+
+However, increasing consumer species richness
+results in higher consumer biomass to the detriment of primary producer biomass
+[@gamfelt_species_2005; @thebault_relationship_2006].
+
+- Horizontal div at different trophic levels (v & h )
+- Vertical div:
+
+The food web structure, vertical diversity, also modulates total biomass and
+productivity [@thebault_food-web_2003; @thebault_trophic_2005;
+@ogorman_multiple_2012; @dossena_warming_2012; @schneider_animal_2016;
+@gamfelt_species_2005]. Both in theoretical and experimental study,
+
+The addition of trophic levels, consumer usually
+breaks the positive relationship between plant biomass and plant diversity as a
+significant amount of biomass is transfered to consumers
+[@thebault_food-web_2003].
+
+It has been shown both in experiments
+[@ogorman_multiple_2012; @dossena_warming_2012]
+and theoretical models [@thebault_food-web_2003; @schneider_animal_2016;
+@wang_biodiversity_2017].
+
+Theoretical models @thebault_relationship_2006
+have shown with a theoretical model that total biomass should increase with the
+increase species diversity at two trophic level *+[]*. However, the joint effects of horizontal and vertical
+diversity on total biomass has been rarely tested, especially in natural
+communities. It is not clear whether horizontal and vertical diversity just
+change the distribution of biomass across trophic level or it increases the
 total amount of  biomass (*It misses a lot of references here*).

### 2020-06-03 manuscript/bef_stability/manuscript.Rmd
Review until data protocol

@@
 species richness [@winemiller_must_1989; @dunne_network_2006;
-@thebault_stability_2010].
-
-**Horizontal and vertical diversity are, however, not independent from each other
-[@duffy_functional_2007; @zhao_horizontal_2019]. The add or removal of one
-species (i.e. ) can have different effects depending on its vertical position in the
-trophic chain [@duffy_functional_2007]. Hence, it is crucial to study their
-interplay to improve our understanding of ecosystem dynamics.**
+@thebault_stability_2010]. Species diversity also result in modification of
+biomass distribution across the food web [@thebault_relationship_2006;
+@duffy_ecosystem_2005; @duffy_functional_2007; @schneider_animal_2016].
+Hence, it is crucial to study if horizontal and vertical diversity have synergic
+or antagonistic effects and how their interplay modulates ecosystem properties.
 
@@
 relationship seems to be supported by the same mechanisms within consumers and
-within plants. (also duffy_ecosystem_2005)
-
-The effect of the vertical diversity itself does not seem to affect total
-biomass. But seek food chain length, connectance
-
-You should connect average trophic level to biomass repartition (good when lots
-of omnivory and no trophic chain)
-
-- Effect of food web structure on total biomass are relatively absent
-
-However, increasing consumer species richness
-results in higher consumer biomass to the detriment of primary producer biomass
-[@gamfelt_species_2005; @thebault_relationship_2006].
-
-- Horizontal div at different trophic levels (v & h )
-- Vertical div:
-
-The food web structure, vertical diversity, also modulates total biomass and
-productivity [@thebault_food-web_2003; @thebault_trophic_2005;
-@ogorman_multiple_2012; @dossena_warming_2012; @schneider_animal_2016;
-@gamfelt_species_2005]. Both in theoretical and experimental study,
-
-The addition of trophic levels, consumer usually
-breaks the positive relationship between plant biomass and plant diversity as a
-significant amount of biomass is transfered to consumers
-[@thebault_food-web_2003].
-
-It has been shown both in experiments
-[@ogorman_multiple_2012; @dossena_warming_2012]
-and theoretical models [@thebault_food-web_2003; @schneider_animal_2016;
-@wang_biodiversity_2017].
-
-Theoretical models @thebault_relationship_2006
-have shown with a theoretical model that total biomass should increase with the
-increase species diversity at two trophic level *+[]*. However, the joint effects of horizontal and vertical
-diversity on total biomass has been rarely tested, especially in natural
-communities. It is not clear whether horizontal and vertical diversity just
-change the distribution of biomass across trophic level or it increases the
-total amount of  biomass (*It misses a lot of references here*).
+within plants. @schneider_animal_2016 also showed in a allometric food web model
+that species richness should increase total animal biomass.
+Vertical diversity also affect total biomass. Theoretical studies showed that food
+web properties, such as interaction distribution and strength, affect the
+vertical distribution of biomass [@thebault_relationship_2006;
+@schneider_animal_2016; @barbier_pyramids_2019], i.e. average trophic level.
+More precisely, an increase of animal diversity results in
+higher animal biomass as more biomass is transfered from plant to animals
+[@schneider_animal_2016; @thebault_food-web_2003]. However, the role of vertical
+diversity on the total biomass remains unclear in
+natural communities.
 
@@
 properties. Experimental studies showed consistently that species richness
-increase temporal stability of biomass in grasslands
-[@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018]. While in
-natural communities, same relation has been found for temporal biomass stability
-in stream fish communities [@franssen_annual_2011] and temporal abundance
-stability of birds and butterflies [@olivier_independent_nodate, but not bats].
-Two mechanisms are involved into temporal stability of communities, (1)
-synchrony and (2) species variability [@loreau_species_2008;
-@thibaut_understanding_2013]. Synchrony measures the temporal covariation of
-species. Very low synchrony indicates compensatory temporal variation between
-species and so increased temporal stability. Species richness has been generally
-found to decrease synchrony between species [@loreau_species_2008;
-@thibaut_understanding_2013; @bluthgen_land_2016; @olivier_independent_nodate,
-but @declerck_species_2006]. The average temporal variability of species is
-measured as a average coefficient of variation of species, weighted by species
-abundance/biomass. Higher species temporal variabiliy thus results in lower
-temporal stability. Positive [@tilman_biodiversity_2006], neutral
-[@jiang_different_2009; @olivier_independent_nodate] and negative
-[@franssen_annual_2011; @olivier_independent_nodate] relationships between
-species variability and species richness have been found. This different
-patterns can be dependent on species mean variance relationships and on the
-relationship between evenness and species richness
-[@thibaut_understanding_2013].  Synchrony has been found to be the main driver
-of temporal stability [@tilman_biodiversity_2006; @olivier_independent_nodate]
-and responsible for the positive relationship between horizontal diversity and
-temporal stability of biomass and abundance. (*Should I add more details about
-the mecanisms?*)
-
-Vertical diversity, represented by network structure, has been central to the
-literature of diversity-stability debate and largely explored by theoretical
-ecology [@may_will_1972; @angelis_stability_1975;
+increases the temporal stability of biomass in grasslands
+[@tilman_biodiversity_2006], and mesocosms [@pennekamp_biodiversity_2018]. The
+same relation was found in natural settings for temporal biomass stability in
+stream fish communities [@franssen_annual_2011] and temporal abundance stability
+of birds and butterflies [@olivier_independent_nodate, but not bats].  Two
+mechanisms may govern the temporal stability of communities, (1) species
+synchrony and (2) variability [@loreau_species_2008;
+@thibaut_understanding_2013]. Species synchrony measures the temporal
+covariation of species where low synchrony indicates that species temporal
+variation compensate each other at the community level, thereby increasing
+temporal stability. Species richness was found to decrease
+synchrony between species [@loreau_species_2008; @thibaut_understanding_2013;
+@bluthgen_land_2016; @olivier_independent_nodate, but @declerck_species_2006].
+The species variability is measured as a average coefficient
+of variation of abundance/biomass, weighted by species abundance/biomass. Higher species
+temporal variability should thus result in lower temporal stability. Positive
+[@tilman_biodiversity_2006], neutral [@jiang_different_2009;
+@olivier_independent_nodate] and negative [@franssen_annual_2011;
+@olivier_independent_nodate] relationships between species variability and
+species richness have been found. This conflicting patterns are dependent on
+various mechanisms [see @thibaut_understanding_2013]. Species synchrony has been found to be
+the main driver of temporal stability [@tilman_biodiversity_2006;
+@olivier_independent_nodate] and responsible for the positive relationship
+between horizontal diversity and temporal stability of biomass and abundance.
+
+Vertical diversity, captured by network structure, has been at the heart of the
+diversity-stability debate and largely explored by theoretical ecology
+[@may_will_1972; @angelis_stability_1975; @dunne_network_2006;
 @stouffer_compartmentalization_2011; @thebault_stability_2010;
-@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate]. Because species
-interactions make species dynamics interdependant, they have a tremendous role
-on stability notably through its effects on the propagation of perturbations.
-However, it is important to note that theoretical ecology generally uses
-stability definitions related to community equilibrium and its stability to
+@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate]. As species
+interactions introduce inter-dependencies in species dynamics, they have a
+substantial impact on stability. In particular, the strength of predation and
+degree of omnivory in food webs have been shown to favor stability
+[@neutel__2007]. Furthermore, competition strength and niche breath of
+consumers, can lead to negative or positive temporal stability-species richness
+relationships [@thebault_trophic_2005] depending on the food web configuration
+[@neutel__2007].  However, it is important to note that theoretical ecology
+generally defines stability based on community equilibrium and its stability to
 small independent perturbations [@may_will_1972; @angelis_stability_1975;
-@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate] or to the number
-of secondary extinctions after species removal [@duffy_why_2009]. Those
-stability metrics hardly relates to empirical temporal stability [@arnoldi_resilience_2016].
-However, @thebault_trophic_2005 shows for a bi-trophic community
-that asynchrony consistently increase temporal stability and a positive
-relationship between temporal stability and species richness. However asynchrony
-can also increase species variability through interspecific competition, which
-amplifies species biomass fluctuations [@thebault_trophic_2005]. Furthermore
-species interactions, considered as competition strength and niche breath of
-consumers can results in negative or positive temporal stability-species
-richness relationships
-[@thebault_trophic_2005] depending on the food web configuration. Vertical
-diversity, as network structure, can have strong effects on temporal stability.
-However, there are few assesments of the effects of horizontal and diversity on
-temporal stability in natural communities.
-
-**Justify that horizontal and vertical diversity are linked**
-Because horizontal & vertical diversity are not indedepent, they should be
-analyzed jointly. For example, connectance generally covaries negatively with
-species richness [@dunne_network_2006; @thebault_stability_2010; but see
-@winemiller_must_1989]. This is also true for other metrics [@dunne_network_2006;
-@delmas_analyzing_2018]. **TO DEVELOP, MOVE or RM**
+@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate] or to the amount
+of secondary extinctions following species removal [@duffy_why_2009]. In
+practice, these stability metrics hardly relate to empirical temporal stability
+[@arnoldi_resilience_2016].
+
+#### Problematic
+
+Overall, the evidence suggests that both a higher horizontal and vertical
+diversity should lead to a greater total biomass and stability in communities.
+The effects of horizontal and vertical diversity are potentially conflicting and
+interacting, as they rely on inter-dependent mechanisms, in such a way that
+they need to be addressed jointly. Yet, there is no direct empirical evidence to
+date for an interaction between effects of horizontal and vertical diversity on
+total biomass and stability in natural communities.
+
+#### Environment can mitigate community structure and ecosystem properties
+
+The environment affects organism performance directly, and thereby, species
+abundances and total biomass [Add general ref; @grace_integrative_2016] and
+temporal stability [@de_boeck_patterns_2017; @hansen_climate_2013;
+@bluthgen_land_2016; @oliver_heterogeneous_2010; @friedpetersen_drivers_2020].
+For instance, the hydrology of streams determines the composition of fish
+communities, and is also related to fish population temporal stability
+[@franssen_annual_2011].  Temperature has potentially conflicting effects on
+horizontal and vertical diversity, as higher temperature favour primary
+production and fluxes of biomass [@dossena__2012; @ogorman__2012], thus
+potentially supporting more species and trophic levels [@arim__2007;
+@stegen__2012], but selects against larger body sized individuals
+[@dossena__2012; @edeline__2013; @hattab__2016], and thereby should reduce
+trophic diversity [@hattab__2016]. It is thus unclear whether these temperature
+effects translate indirectly into changes in total standing biomass and
+stability in natural food webs. The relative strength of direct and indirect
+effects of environment on total biomass and its temporal stability remains an
+open question.
+
+- TODO Add on ecosystem size (cf elisa)
+
+#### Research questions
+
+Overall, the joint effects of horizontal and vertical diversity on total biomass
+and its temporal stability remains poorly documented, especially in natural
+communities. In this study, we identified (1) the effects of horizontal
+diversity and (2) vertical diversity on total biomass and temporal stability
+(Figure \@ref(fig:matmet) A).  Considering both direct & indirect effects, (3)
+we quantify if the magnitude of environmental effects on total biomass and its
+temporal stability and compare them to that of horizontal and vertical
+diversities.  (4) We identify the pathway for the effects of environment,
+horizontal and vertical diversities on total biomass and its temporal stability.
+(4a) Whether environmental effects operate mainly (i) directly, indirectly (ii)
+through horizontal diversity, (iii) through horizontal and vertical diversities
+or (iv) indirectly through vertical diversity only? (4b) Whether effects of
+horizontal diversity arise (i) directly, or (ii) indirectly through vertical
+diversity? Finally, (4c) whether environmental variables, horizontal and
+vertical diversities affect species synchrony and species variability ?
+
+We used the ONEMA dataset consisting in standardized sampling of fish
+communities in french streams [@edeline__2013]. 99 sites were sampled for more
+than 10 years spanning on the 1995-2018 period. We inferred
+(**XXX**) potential interaction networks, based on body size and food diet.
+Horizontal diversity was quantified as species richness while vertical diversity
+was as connectance and average trophic level. Environment was characterized by
+the stream size, altitude, slope, and the temperature, flow and enrichment. Finally total
+biomass was measured as median total biomass over the sampling period while its
+temporal stability was quantified as the inverse of the CV.
+
+We show that TODO
+
+# Methods
+
+```{r}
+matmet_cap <- paste0(
+  "(A) Conceptual model of the hypothesized relationships between environment,
+  species richness, network metrics and total biomass / biomass stability. ",
+  "Solid and dashed arrows represent respectively direct and indirect effects.
+  ",
+  "The blue, green and blue/green dashed arrows being respectively indirect
+  effects going through species richness, network metrics and through both
+  species richness and network metrics.",
+  "(B) Observation sites (black dots) were located across France and monitored
+  on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
+  "Inner borders draw the limits of the hydrographic basins. ",
+  "(C) The metaweb. Each trophic species (N = 412) is represented by a node and
+  each color represent a species (S = ). Resource nodes (7) were drawn in grey. ",
+  "(D) Subset over network variation through time."
+)
+```
+
+```{r matmet, fig.cap = matmet_cap}
+myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))
+
+# Network inference
+net_method_path <- mypath("manuscript/bef_stability/figs",
+  "hypothesis.pdf")
+metaweb_path <- mypath("manuscript/bef_stability/figs",
+  "metaweb.png")
+library(magick)
+
+p_net_method <- cowplot::ggdraw() +
+  cowplot::draw_image(magick::image_read_pdf(net_method_path))
+p_metaweb <- cowplot::ggdraw() +
+  cowplot::draw_image(magick::image_read(metaweb_path))
+
+top <- plot_grid(p_net_method, p_st, ncol = 2, rel_widths = c(1, 1), labels =
+  "AUTO")
+bottom <- plot_grid(p_metaweb, temporal_network, ncol = 2,
+  rel_widths = c(1, 1), labels = c("C", "D"))
+
+p_method <- plot_grid(top, bottom, nrow = 2, rel_heights = c(1, 1),
+  labels = c("", "C"))
+save_plot(
+  filename = mypath("manuscript/bef_stability/figs",
+    "method_fig.pdf"),
+  p_method, nrow = 2, ncol =2,
+  base_width = 7/2.54,
+  base_asp = 0.3
+)
+p_method
+```
 
@@
 
-#### Environment plays a big role in structuring communities
-
-Environment also largely structure communities and is important to take in
-account when considering natural communities. Environment directly affects
-organism performance, and subsequently, abundance of species and in turn
-determines total biomass [Add general ref; @grace_integrative_2016] and temporal
-stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
-@oliver_heterogeneous_2010; @friedpetersen_drivers_2020]. Hydrology of streams
-constraints the composition of fish communities [REF toulouse à balle], and has
-already been related to fish population temporal stability [@franssen_annual_2011].
-However it is not clear which is the relative strength of direct and indirect
-effects of environment on total biomass and its temporal stability (Figure
-\@ref(fig:matmet) A).
-
-#### Research questions
-
-The joint effects of horizontal & vertical diversity on total biomass and its
-temporal stability remains yet poorly documented, especially in natural
-communities. In this study, we questionned (1) whether the relationships between
-horizontal diversity and total biomass/temporal stability are positive or
-negative in aquatic ecosystems (Figure \@ref(fig:matmet) A). Then, as indicated
-by theoretical studies, (2) what are the effects of vertical diversity on total
-biomass and its temporal stability? Considering both direct & indirect effects,
-(3) What is the magnitude of environmental effects on total biomass and its
-temporal stability compare to horizontal and vertical diversity? (4) Which are
-the pathways of the effects of environment, horizontal & vertical diversity on total
-biomass and its temporal stability ? (4a) For environment, is it mainly (i)
-direct, indirect (ii) through horizontal diversity, (iii) through horizontal &
-vertical diversity or (iv) indirect through only vertical diversity? (4b) For
-horizontal diversity, is it mainly (i) direct, or (ii) indirect through vertical
-diversity?  Finally for temporal stability, (4c) how do environment, horizontal
-& vertical diversity affect synchrony & species stability ?
+## Data collection
+
+#### Protocol
+
+Fish communities were monitored across stream sections in France on the period 1995-2018
+by the French Office French Office of Water and Aquatic Ecosystems (ONEMA) using
+electric fishing, resulting in over XX individual fish sampled [see
+@edeline__2013]. Two different standardized protocols were used for little and
+big streams (detailed in Supplementary methods). For streams shallower than (XX
+m), the sampling takes place over the whole width of the streams and is done by
+foot whereas in streams deeper than (XX m), the sampling was done over the bank
+only and by foot or by boat. The sampling took place either in late spring and/or Autumn
+and temporal series were checked to reduce sampling heterogeneity within
+stations (detailed in Supplementary methods). Each station have been followed
+ten years or more. The temporal stability of biomass, computed as inverse of the
+CV, can cover very different dynamics such as decreasing, stable or increasing.
+However, the concept of community variability referred to variability around an
+equilibrium, which is rarely observed or difficult to characterize in natural
+communities. We finally kept only the 99 stations (Figure \@ref(fig:matmet) B)
+which had no trends in biomass (method detailed in Supplementary methods).
+However, the results were robust to the relaxation of this hypothesis
+(Supplementary results).
+
+##### Total biomass and its temporal stability
+
+To characterize communities variability, abundance or biomass are generally
+used. When the body size and therefore body mass vary by several orders of
+magnitude, one downside of abundance is that we mix individual that have
+potentially really different meaning in terms of ecosystem properties such as
+biomass. We therefore estimated the body mass of fish individuals according to
+their body size. The body mass of individual fishes were then estimated with an
+allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$ being the body mass in grams,
+$l$ the body size in millimeters and $i$ the individual)
+[@lleonart_removing_2000; @froese_cube_2006].
+
+The species and community biomass were then computed for each sampling event.
+As sampling effort, reported as the surface sampled during the sampling event,
+varied across protocol type and sampling event, biomass was reported to the
+surface sampled (in $m^{2}$). Community and species biomass were then expressed
+in $gm^{-2}$.
+
+Total biomass was characterized as the median total biomass over time. Temporal
+biomass stability was defined as the inverse of biomass variability. Variability
+was computed as Coefficient of Variation (CV) of the biomass ($CV_i = \sigma_i
+\mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being respectively the standard
+deviation and the temporal average of the biomass of the station $i$). Then, temporal
+stability was equal to $CV^{-1} = \mu \sigma^{-1}$.
+
+To characterize the mecanisms driving temporal stability, we decomposed
+the community CV in synchrony and weighted average species CV
+components according to @thibaut_understanding_2013:
+
+$$
+CV_{com} = \overline{CV_{sp}} \times \sqrt{\phi}
+$$
+
+with $CV_{com}$ being the Coefficient of Variation of the community,
+$\overline{CV_{sp}}$ the average coefficient of variation of population
+pondered by biomass. $\phi$ is the synchrony, which is the ratio the total
+community variance ($\sigma^2_{x_T}$) and the sum of population variance
+($\sigma_{x_i}$) [@loreau_species_2008].
+
+$$
+\overline{CV_{sp}} = \sum_i{\frac{B_i {CV}_i}{\sum_i{B_i}}}
+$$
+
+$$
+\phi = \frac{\sigma^2_{x_T}}{\sum_i{\sigma_{x_i}}}
+$$
+
+## Hozizontal & vertical diversity
+
+### Horizontal diversity
+
+####  Species richness
+
+Species richness was computed as the total species richness over time in a given
+station. To normalize by sampling effort, we reported species richness to the
+sum of surface sampled over the time period, it was expressed in number of
+species by square meter.
+
+### Vertical diversity
+
+#### Trophic network inference
+
+```{r}
+myload(metaweb_analysis, dir= mypath("data"))
+meta <- metaweb_analysis
+#metaweb_analysis$resource
+#meta$metaweb[meta$resource, meta$resource]
+```
+
+Trophic interaction network was inferred from body size and ontogenic diet.
+Body size is a reasonable approximation widely used to infer trophic
+interactions [@gravel_inferring_2013; @brose_predator_2019;
+@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
+over lifespan. For example, alvins feed on plankton while adults may feed on
+algae or fishes. Accordingly,  each fish species was divided in nine body size
+classes. Each body size class constituting a trophic species. A high congruence
+has been found at trophic species scale between inferred interactions and
+measured trophic interactions, but not at the species
+scale [@jennings_weak_2001]. We then inferred trophic interactions between the trophic species (Figure
+\@ref(fig:matmet) C).  We determined network structure in two steps: (1) build a
+metaweb describing the trophic interactions between all trophic
+species (Figure \@ref(fig:matmet) C), then (2) determine network of a given
+community by subtracting the metaweb according to the trophic species present in
+a given community (Figure \@ref(fig:matmet) D). We added to each network seven
+resource nodes present in food diet database: detritus, biofilm, phytoplankton,
+zooplankton, macrophages, phytobenthos and zoobenthos (grey nodes in Figure
+\@ref(fig:matmet) C & D). The trophic network inference procedure is detailed in
+supplementary informations.
+
+#### Trophic network structure
+
+In each network, we computed two network metrics that have been commonly used to
+characterize network structure. Connectance which describes the number of
+interactions compared to the number of possible links, computed as ($C = L /
+N^2$, L and N being
+resp. the number of links and of trophic species plus resource nodes). We then
+computed the average trophic level, the average trophic level was weighted by
+the biomass of each trophic species (excluding resource nodes for which we had
+no biomass) ($\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, $T_i$
+and $B_i$ being resp. the trophic level and the biomass of the node $i$).
+
+In resume, we infered binary trophic networks at the scale of trophic species
+(i.e. body size classes by species) to take in account ontogenic diet shifts and
+that fish-fish trophic interaction depends on body size ratio. On the other
+side, the community metrics were defined at the species level, (i.e. species
+richness, average species CV and synchrony).
+
+```{r}
+# Basin
+st_basin <- get_basin_station(sf_obj = FALSE)
+
+# Select fishing operation 
+myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
+myload(biomass_ts_sax, dir = mypath("data"))
+op_analysis_bbb <- filter(op_analysis, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+
+```
+
+```{r, fig.show = "hide"}
+myload(
+  hab_analysis,
+  temporal_station_desc,
+  temporal_press_polluants,
+  geo_station,
+  dir = mypath("data")
+)
+habitat_press <- build_habitat_pressure_dataset(
+  .habitat_analysis = hab_analysis,
+  .tmp_press = temporal_press_polluants,
+  .tmp_st_desc = temporal_station_desc,
+  .geo_st = geo_station 
+)
+
+# Make PCA 
+habitat_press %<>% na.omit()
+mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())
+
+pca_rotated <- compute_rotated_pca(
+  .data = habitat_press[, mask],
+  naxis = 2
+)
+habitat_pressure <- 
+  cbind(habitat_press[, c("station", "temperature_med", "alt")], pca_rotated$rotated$score) %>%
+  as_tibble
+ggplot(habitat_pressure, aes(x = RC2, y = temperature_med)) +
+  geom_point()
+
+ggplot(
+  pivot_longer(habitat_pressure, cols = c("RC1", "RC2"),
+    names_to = "variable", values_to = "value"
+  )
+  , aes(x = value)) +
+geom_histogram() +
+facet_grid(cols = vars(variable))
+
+```
+
+```{r}
+prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
+  map_dbl(., ~round(.x * 100))
+tot_var_expl_pca <- sum(prop_var_expl_pca) 
+```
+
+```{r, message = FALSE, results = FALSE}
+# Com
+com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
+ type_network_metrics = "classes"
+)
+# Compute sem dataset
+sem_data <- compute_sem_dataset(
+  com = com_data[["tps_com"]],
+  network = com_data[["tps_net"]],
+  hab_press = habitat_pressure,
+  sync = com_data[["sync_std"]],
+  nmds = NULL,
+  basin = st_basin
+  )
+
+```
+
+## Environment
+
+Habitat description, obtained from fish sampling data, describing the ecosystem
+size namely the stream width, depth and position (altitude and
+slope). Physico-chemical variables were obtained from
+naiades web portal [http://www.naiades.eaufrance.fr/](http://www.naiades.eaufrance.fr/).
+We chose flow and temperature to describe streams as flow
+impose swimming constraints which filters fish species that can establish
+[@rolls_scaling_2018; @tonkin_flow_2018; @gutierrez-canovas_contrasting_2013].
+Water temperature is linked to physiological constraints namely thermal
+tolerance and oxygen concentration tolerance [REF] since the level of water
+saturation in oxygen is inversely linked to water temperature. We took 
+Biochemical Oxygen Demand (BOD) for a proxy of enrichment in the ecosystem [REF].
+BOD is also inversely linked to oxygen concentration in water and so, BOD is
+also linked to physiological stress of fishes. As physico-chemical variables
+were not recorded at the same place than fish communities, they were
+interpolated with spatial stream networks [@isaak_applications_2014;
+@hoef_ssn:_2014]. The interpolation procedure is detailed in supplementary
+methods.
+
+For each fish station, environmental variables were matched with the year of
+fish sampling (except for water temperature for which the record began in 2006).
+Then, the average temperature, flow, BOD, river width and depth were computed as
+well as coefficient of variation ($CV = \sigma \mu^{-1}$). As habitat and
+environmental variables are often collinear, a principal component analysis (PCA)
+was performed on the scaled variables. We kept in the analysis the two first
+principal components based on eigen values distribution (Fig. SXX).
+The PCA explained `r tot_var_expl_pca`%
+of the variance. An varimax axis rotation was performed to maximize the representation
+of the variables by the principal components (Fig. \@ref(fig:pca-rotated)).
+Five principal components were used in the analysis, representing respectively
+the (1) river size (river width & depth), (2) altitude, slope and decreasing
+average temperature, (3) average enrichment (BOD) and CV of flow, (4) river size
+CV (CV of river width and depth) and (5) CV of enrichment (CV of BOD). Further
+informations about data transformation and filtering are detailed in
+supplementary information.
+
+## Statistical analysis
 
@@
 
-We used an standardized monitoring of fish communities in french streams. 99
-sites were followed more than 10 years on the 1995-2018 period. We inferred
-(**XXX**) potential interaction networks, based on body size and food diet.
-Horizontal diversity was quantified as species richness while vertical diversity
-was as connectance and average trophic level. Environment was characterized by
-the stream size, altitude, slope, and the temperature, flow and enrichment. Finally total
-biomass was measured as median total biomass over the sampling period while its
-temporal stability was quantified as the inverse of the CV.
-
-- Q1:  horizontal diversity-biomass horizontal diversity-stability in aquatic systems
-- Q2:  in aquatic systems
-- Q2: Effect of horizontal and vertical diversity on total biomass and stablity
-- Q3: Relative contribution of environment and community structure to biomass
-  and stability
-
-# Methods
-
-```{r}
-matmet_cap <- paste0(
-  "(A) Conceptual model of the hypothesized relationships between environment,
-  species richness, network metrics and total biomass / biomass stability. ",
-  "Solid and dashed arrows represent respectively direct and indirect effects.
-  ",
-  "The blue, green and blue/green dashed arrows being respectively indirect
-  effects going through species richness, network metrics and through both
-  species richness and network metrics.",
-  "(B) Observation sites (black dots) were located across France and monitored
-  on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
-  "Inner borders draw the limits of the hydrographic basins. ",
-  "(C) The metaweb. Each trophic species (N = 412) is represented by a node and
-  each color represent a species (S = ). Resource nodes (7) were drawn in grey. ",
-  "(D) Subset over network variation through time."
-)
-```
-
-```{r matmet, fig.cap = matmet_cap}
-myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))
-
-# Network inference
-net_method_path <- mypath("manuscript/bef_stability/figs",
-  "hypothesis.pdf")
-metaweb_path <- mypath("manuscript/bef_stability/figs",
-  "metaweb.png")
-library(magick)
-
-p_net_method <- cowplot::ggdraw() +
-  cowplot::draw_image(magick::image_read_pdf(net_method_path))
-p_metaweb <- cowplot::ggdraw() +
-  cowplot::draw_image(magick::image_read(metaweb_path))
-
-top <- plot_grid(p_net_method, p_st, ncol = 2, rel_widths = c(1, 1), labels =
-  "AUTO")
-bottom <- plot_grid(p_metaweb, temporal_network, ncol = 2,
-  rel_widths = c(1, 1), labels = c("C", "D"))
-
-p_method <- plot_grid(top, bottom, nrow = 2, rel_heights = c(1, 1),
-  labels = c("", "C"))
-save_plot(
-  filename = mypath("manuscript/bef_stability/figs",
-    "method_fig.pdf"),
-  p_method, nrow = 2, ncol =2,
-  base_width = 7/2.54,
-  base_asp = 0.3
-)
-p_method
-```
-
-#### Protocol
-
-Fish communities were monitored across streams of France on the period 1995-2018
-by a French governmental agency (Office Français de la Biodiversité), using
-electric fishing. Two different standardized protocols were used for little and
-big streams (detailed in Supplementary methods). For streams shallower than (XX
-m), the sampling takes place over the whole width of the streams and is done by
-foot whereas in streams deeper than (XX m), the sampling is done over the bank
-only and by foot or by boat. The sampling took place either in late spring and/or Autumn
-and temperal series were checked to reduce sampling heterogeneity within
-stations (detailed in Supplementary methods). Each station have been followed
-ten years or more (i.e 10 sampling events or more). The temporal stability of
-biomass, computed as inverse of the CV, can cover very different dynamics such
-as decreasing, stable or increasing. However, the concept of community
-variability referred to variability around an equilibrium, which is rarely
-observed or difficult to characterize in natural communities. We finally kept
-only the 99 stations (Figure \@ref(fig:matmet) B) which had no trends in
-biomass (method detailed in Supplementary methods). However, the results
-were robust to the relaxation of this hypothesis (Supplementary results).
-
-##### Total biomass and its temporal stability
-
-To characterize communities variability, abundance or biomass are generally
-used. When the body size and therefore body mass vary by several orders of
-magnitude, one downside of abundance is that we mix individual that have
-potentially really different meaning in terms of ecosystem properties such as
-biomass. We therefore estimated the body mass of fish individuals according to
-their body size. The body mass of individual fishes were then estimated with an
-allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$ being the body mass in grams,
-$l$ the body size in millimeters and $i$ the individual)
-[@lleonart_removing_2000; @froese_cube_2006].
-
-The species and community biomass were then computed for each sampling event.
-As sampling effort, reported as the surface sampled during the sampling event,
-varied across protocol type and sampling event, biomass was reported to the
-surface sampled (in $m^{2}$). Community and species biomass were then expressed
-in $gm^{-2}$.
-
-Total biomass was characterized as the median total biomass over time. Temporal
-biomass stability was defined as the inverse of biomass variability. Variability
-was computed as Coefficient of Variation (CV) of the biomass ($CV_i = \sigma_i
-\mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being respectively the standard
-deviation and the temporal average of the biomass of the station $i$). Then, temporal
-stability was equal to $CV^{-1} = \mu \sigma^{-1}$.
-
-To characterize the mecanisms driving temporal stability, we decomposed
-the community CV in synchrony and weighted average species CV
-components according to @thibaut_understanding_2013:
-
-$$
-CV_{com} = \overline{CV_{sp}} \times \sqrt{\phi}
-$$
-
-with $CV_{com}$ being the Coefficient of Variation of the community,
-$\overline{CV_{sp}}$ the average coefficient of variation of population
-pondered by biomass. $\phi$ is the synchrony, which is the ratio the total
-community variance ($\sigma^2_{x_T}$) and the sum of population variance
-($\sigma_{x_i}$) [@loreau_species_2008].
-
-$$
-\overline{CV_{sp}} = \sum_i{\frac{B_i {CV}_i}{\sum_i{B_i}}}
-$$
-
-$$
-\phi = \frac{\sigma^2_{x_T}}{\sum_i{\sigma_{x_i}}}
-$$
-
-## Hozizontal & vertical diversity
-
-### Horizontal diversity
-
-####  Species richness
-
-Species richness was computed as the total species richness over time in a given
-station. To normalize by sampling effort, we reported species richness to the
-sum of surface sampled over the time period, it was expressed in number of
-species by square meter.
-
-### Vertical diversity
-
-#### Trophic network inference
-
-```{r}
-myload(metaweb_analysis, dir= mypath("data"))
-meta <- metaweb_analysis
-#metaweb_analysis$resource
-#meta$metaweb[meta$resource, meta$resource]
-```
-
-Trophic interaction network was inferred from body size and ontogenic diet.
-Body size is a reasonable approximation widely used to infer trophic
-interactions [@gravel_inferring_2013; @brose_predator_2019;
-@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
-over lifespan. For example, alvins feed on plankton while adults may feed on
-algae or fishes. Accordingly,  each fish species was divided in nine body size
-classes. Each body size class constituting a trophic species. A high congruence
-has been found at trophic species scale between inferred interactions and
-measured trophic interactions, but not at the species
-scale [@jennings_weak_2001]. We then inferred trophic interactions between the trophic species (Figure
-\@ref(fig:matmet) C).  We determined network structure in two steps: (1) build a
-metaweb describing the trophic interactions between all trophic
-species (Figure \@ref(fig:matmet) C), then (2) determine network of a given
-community by subtracting the metaweb according to the trophic species present in
-a given community (Figure \@ref(fig:matmet) D). We added to each network seven
-resource nodes present in food diet database: detritus, biofilm, phytoplankton,
-zooplankton, macrophages, phytobenthos and zoobenthos (grey nodes in Figure
-\@ref(fig:matmet) C & D). The trophic network inference procedure is detailed in
-supplementary informations.
-
-#### Trophic network structure
-
-In each network, we computed two network metrics that have been commonly used to
-characterize network structure. Connectance which describes the number of
-interactions compared to the number of possible links, computed as ($C = L /
-N^2$, L and N being
-resp. the number of links and of trophic species plus resource nodes). We then
-computed the average trophic level, the average trophic level was weighted by
-the biomass of each trophic species (excluding resource nodes for which we had
-no biomass) ($\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, $T_i$
-and $B_i$ being resp. the trophic level and the biomass of the node $i$).
-
-In resume, we infered binary trophic networks at the scale of trophic species
-(i.e. body size classes by species) to take in account ontogenic diet shifts and
-that fish-fish trophic interaction depends on body size ratio. On the other
-side, the community metrics were defined at the species level, (i.e. species
-richness, average species CV and synchrony).
-
-```{r}
-# Basin
-st_basin <- get_basin_station(sf_obj = FALSE)
-
-# Select fishing operation 
-myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
-myload(biomass_ts_sax, dir = mypath("data"))
-op_analysis_bbb <- filter(op_analysis, station %in%
-  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
-op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
-  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
-
-```
-
-```{r, fig.show = "hide"}
-myload(
-  hab_analysis,
-  temporal_station_desc,
-  temporal_press_polluants,
-  geo_station,
-  dir = mypath("data")
-)
-habitat_press <- build_habitat_pressure_dataset(
-  .habitat_analysis = hab_analysis,
-  .tmp_press = temporal_press_polluants,
-  .tmp_st_desc = temporal_station_desc,
-  .geo_st = geo_station 
-)
-
-# Make PCA 
-habitat_press %<>% na.omit()
-mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())
-
-pca_rotated <- compute_rotated_pca(
-  .data = habitat_press[, mask],
-  naxis = 2
-)
-habitat_pressure <- 
-  cbind(habitat_press[, c("station", "temperature_med", "alt")], pca_rotated$rotated$score) %>%
-  as_tibble
-ggplot(habitat_pressure, aes(x = RC2, y = temperature_med)) +
-  geom_point()
-
-ggplot(
-  pivot_longer(habitat_pressure, cols = c("RC1", "RC2"),
-    names_to = "variable", values_to = "value"
-  )
-  , aes(x = value)) +
-geom_histogram() +
-facet_grid(cols = vars(variable))
-
-```
-
-```{r}
-prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
-  map_dbl(., ~round(.x * 100))
-tot_var_expl_pca <- sum(prop_var_expl_pca) 
-```
-
-```{r, message = FALSE, results = FALSE}
-# Com
-com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
- type_network_metrics = "classes"
-)
-# Compute sem dataset
-sem_data <- compute_sem_dataset(
-  com = com_data[["tps_com"]],
-  network = com_data[["tps_net"]],
-  hab_press = habitat_pressure,
-  sync = com_data[["sync_std"]],
-  nmds = NULL,
-  basin = st_basin
-  )
-
-```
-
-## Environment
-
-Habitat description, obtained from fish sampling data, describing the ecosystem
-size namely the stream width, depth and position (altitude and
-slope). Physico-chemical variables were obtained from
-naiades web portal [http://www.naiades.eaufrance.fr/](http://www.naiades.eaufrance.fr/).
-We chose flow and temperature to describe streams as flow
-impose swimming constraints which filters fish species that can establish
-[@rolls_scaling_2018; @tonkin_flow_2018; @gutierrez-canovas_contrasting_2013].
-Water temperature is linked to physiological constraints namely thermal
-tolerance and oxygen concentration tolerance [REF] since the level of water
-saturation in oxygen is inversely linked to water temperature. We took 
-Biochemical Oxygen Demand (BOD) for a proxy of enrichment in the ecosystem [REF].
-BOD is also inversely linked to oxygen concentration in water and so, BOD is
-also linked to physiological stress of fishes. As physico-chemical variables
-were not recorded at the same place than fish communities, they were
-interpolated with spatial stream networks [@isaak_applications_2014;
-@hoef_ssn:_2014]. The interpolation procedure is detailed in supplementary
-methods.
-
-For each fish station, environmental variables were matched with the year of
-fish sampling (except for water temperature for which the record began in 2006).
-Then, the average temperature, flow, BOD, river width and depth were computed as
-well as coefficient of variation ($CV = \sigma \mu^{-1}$). As habitat and
-environmental variables are often collinear, a principal component analysis (PCA)
-was performed on the scaled variables. We kept in the analysis the two first
-principal components based on eigen values distribution (Fig. SXX).
-The PCA explained `r tot_var_expl_pca`%
-of the variance. An varimax axis rotation was performed to maximize the representation
-of the variables by the principal components (Fig. \@ref(fig:pca-rotated)).
-Five principal components were used in the analysis, representing respectively
-the (1) river size (river width & depth), (2) altitude, slope and decreasing
-average temperature, (3) average enrichment (BOD) and CV of flow, (4) river size
-CV (CV of river width and depth) and (5) CV of enrichment (CV of BOD). Further
-informations about data transformation and filtering are detailed in
-supplementary information.
-
-## Statistical analysis
-
 #### Summarise SEM statistical framework
@@
 biomass is located at higher trophic level, the more the total biomass increase.
+*Look at Digel et al. 2011, Riede et al. 2011*
+
 In contrast, connectance had no effect on total biomass. One might have expected

### 2020-06-24 manuscript/bef_stability/appendix.Rmd
Version sent to coauthors

@@
 ```{r, fig.height = 20/2.54}
+pca_pressure <- habitat_press
 myload(fourier, dir = mypath("data-raw", "polluants"))
@@
 sem_data %>%
-  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, log_RC3, RC4,
-    RC5, t_lvl, ct, log_bm) %>%
+  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct, log_bm) %>%
   gather(variable, value) %>%
@@
   list(
-    nlme::lme(log_rich_tot_std ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
-    nlme::lme(ct ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(log_sync ~ log_rich_tot_std + ct + t_lvl + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,
+    nlme::lme(log_rich_tot_std ~ log_RC1 + log_RC2,  random = ~ 1 | basin, data = sem_data),
+    nlme::lme(ct ~ log_RC1 + log_RC2 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
+    nlme::lme(log_sync ~ log_rich_tot_std + ct + t_lvl + log_RC1 + log_RC2,
       random = ~ 1 | basin, data = sem_data),
     nlme::lme(log_cv_sp ~ log_rich_tot_std  + ct + t_lvl
-      + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data),
+      + log_RC1 + log_RC2, random = ~ 1 | basin, data = sem_data),
     lm(log_stab_std ~ log_cv_sp + log_sync, data = sem_data),
     nlme::lme(log_bm_std ~ log_rich_tot_std  + ct + t_lvl
-      + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data)
+      + log_RC1 + log_RC2, random = ~ 1 | basin, data = sem_data)
   )

### 2020-06-24 manuscript/bef_stability/manuscript.Rmd
Version sent to coauthors

@@
 ---
-title: Horizontal and vertical diversity drive total biomass and its temporal stability in fish communities
-author: Alain Danet, Maud Mouchet, Elisa Thebault and Colin Fontaine
+title: Horizontal and vertical diversity jointly drive total biomass and its temporal stability in fish communities
+author: Alain Danet, Maud Mouchet, (Willem Bonnaffe ici?), Elisa Thebault and Colin Fontaine
 date: \today 
@@
   bookdown::pdf_document2:
+    toc: false 
     fig_caption: true 
@@
 
+- Author affiliation:
+  - Alain Danet:
+  - Maud Mouchet:
+  - Willem Bonnaffe:
+  - Elisa Thebault: 
+  - Colin Fontaine:
+
+- Author contributions: AD, CF, MM and ET designed the study. WB designed the
+  network inference method and collected the food diet data. AD performed the
+  data analysis and wrote the first draft of the manuscript. All authors
+  contributed substantially to revisions.
+
+- Data accessibility statement: the ONEMA database is available upon request to 
+  eddy.cosson@afbiodiversite.fr and thierry.point@afbiodiversite.fr. The code
+  used for the analysis and to generate the manuscript is available on github:
+  (alaindanet/fishcom.git)
+
+- Article type: Letters
+
+- Number of words:
+  - Abstract: 194
+  - Main text: XXXX
+
+- Number of references: XXX
+- Number of figures: 2
+- Number of tables: 2
+- Number of text boxes: 0
+
+- Coresponding author:
+  - Alain Danet
+  - UMR 7204 CESCO, BP 61; 45, rue Buffon, 75005 Paris, France
+  - alain.danet@mnhn.fr 
+  - +331XXXXXXXX
+
 # Abstract
+
+The effect of horizontal  and vertical diversity on ecosystem properties has
+been central to ecology. It has been at the basis of the predictions of the
+effect species richness and  network structure on total biomass, productivity
+and stability. However, they have mainly been studied separately.  We used a
+dataset of standardized fish sampling in French stream running from 1995 to
+2018. We inferred trophic interactions thanks to recorded body size and diet
+literature. We then investigate the direct and indirect effects of stream
+size and temperature, horizontal and vertical diversity on total biomass and
+its temporal stability. We found that horizontal and vertical diversity had
+a positive relationship with total biomass while they had respectively a
+negative and positive effect on temporal stability. We also found that
+horizontal and vertical diversity are not independent and that environment
+had an tremendous effect on total biomass and its temporal stability notably
+through its effect on horizontal and vertical diversity. We conclude that our
+study highlights that the effects horizontal and vertical diversity should not
+treated separately and that it opens exciting perspectives on how environment,
+horizontal and vertical can jointly determine total biomass in natural
+communities.
+
+(194/150 words)
 
@@
 its total biomass [@hector_plant_1999; @tilman_biodiversity_2014;
-@grace_integrative_2016; @pennekamp_biodiversity_2018]], biomass production
+@grace_integrative_2016; @pennekamp_biodiversity_2018], biomass production
 [@tilman_productivity_1996; @cardinale_species_2002; @grace_integrative_2016]
@@
 of components across functional groups, such as the amount trophic categories,
-often termed guilds or levels [@allan_stream_2007; @loreau_population_2010;
-@zhao_horizontal_2019; @wang_biodiversity_2017]. Vertical diversity has been
-primarily quantified as food chain length [@loreau_population_2010;
-@zhao_horizontal_2019; @wang_biodiversity_2017] but it can also be characterized
-by the food web structure [@wang_biodiversity_2017] such as connectance and
+often termed guilds or levels [@allan_stream_2007; @loreau_populations_2010;
+@zhao_horizontal_2019; @wang_biodiversity_2016]. Vertical diversity has been
+primarily quantified as food chain length [@loreau_populations_2010;
+@zhao_horizontal_2019; @wang_biodiversity_2016] but it can also be characterized
+by the food web structure [@wang_biodiversity_2016] such as connectance and
 average trophic level. Horizontal and vertical diversity are, however, not
@@
 [@pennekamp_biodiversity_2018]. When adding the vertical diversity, e.g.
-consumers species, @gamfelt_species_2005 and @thebault_relationship_2006 have found that total
+consumers species, @gamfeldt_species_2005 and @thebault_relationship_2006 have found that total
 biomass increased with increasing species diversity at two trophic levels.
@@
 synchrony between species [@loreau_species_2008; @thibaut_understanding_2013;
-@bluthgen_land_2016; @olivier_independent_nodate, but @declerck_species_2006].
+@bluthgen_land_2016; @olivier_independent_nodate; but @declerck_species_2006].
 The species variability is measured as a average coefficient
@@
 degree of omnivory in food webs have been shown to favor stability
-[@neutel__2007]. Furthermore, competition strength and niche breath of
+[@neutel_reconciling_2007]. Furthermore, competition strength and niche breath of
 consumers, can lead to negative or positive temporal stability-species richness
 relationships [@thebault_trophic_2005] depending on the food web configuration
-[@neutel__2007].  However, it is important to note that theoretical ecology
+[@neutel_reconciling_2007].  However, it is important to note that theoretical ecology
 generally defines stability based on community equilibrium and its stability to
@@
 The environment affects organism performance directly, and thereby, species
-abundances and total biomass [Add general ref; @grace_integrative_2016] and
+abundances and total biomass [@grace_integrative_2016] and
 temporal stability [@de_boeck_patterns_2017; @hansen_climate_2013;
@@
 communities, and is also related to fish population temporal stability
-[@franssen_annual_2011].  Temperature has potentially conflicting effects on
-horizontal and vertical diversity, as higher temperature favour primary
-production and fluxes of biomass [@dossena__2012; @ogorman__2012], thus
-potentially supporting more species and trophic levels [@arim__2007;
-@stegen__2012], but selects against larger body sized individuals
-[@dossena__2012; @edeline__2013; @hattab__2016], and thereby should reduce
-trophic diversity [@hattab__2016]. It is thus unclear whether these temperature
-effects translate indirectly into changes in total standing biomass and
-stability in natural food webs. The relative strength of direct and indirect
-effects of environment on total biomass and its temporal stability remains an
-open question.
-
-- TODO Add on ecosystem size (cf elisa)
+[@franssen_annual_2011]. Ecosystem size can also increase habitat heterogeneity
+and so the number of different resource available, which in turn might increase
+resource complementary between species and increase total biomass
+[@post_ecosystem_2000; @doi_resource_2009]. Temperature has potentially
+conflicting effects on horizontal and vertical diversity, as higher temperature
+favour primary production and fluxes of biomass [@dossena_warming_2012;
+@ogorman_chapter_2012], thus potentially supporting more species and trophic
+levels [@arim_relationship_2007; @stegen_evolving_2012], but selects against
+larger body sized individuals [@dossena_warming_2012; @edeline_ecological_2013;
+@hattab_forecasting_2016], and thereby should reduce trophic diversity
+[@hattab_forecasting_2016]. It is thus unclear whether these temperature effects
+translate indirectly into changes in total standing biomass and stability in
+natural food webs. The relative strength of direct and indirect effects of
+environment on total biomass and its temporal stability remains an open
+question.
 
@@
 We used the ONEMA dataset consisting in standardized sampling of fish
-communities in french streams [@edeline__2013]. 99 sites were sampled for more
+communities in french streams [@edeline_ecological_2013]. 99 sites were sampled for more
 than 10 years spanning on the 1995-2018 period. We inferred
-(**XXX**) potential interaction networks, based on body size and food diet.
+1496 interaction networks, based on body size and food diet.
 Horizontal diversity was quantified as species richness while vertical diversity
@@
 temporal stability was quantified as the inverse of the CV.
+
+#### Stream fish communities is a good model to study effects of horizontal & vertical diversity
+
+Stream fish community constitutes a good model to study the joint effects of
+horizontal & vertical diversity on total biomass and its temporal stability.
+Despite that fish trophic interactions are difficult to assess in nature, a consequent
+body of literature supports that they can be inferred through body size and diet
+informations [@gravel_inferring_2013; @jennings_weak_2001;
+@brose_predator_2019]. Most of the biomass-diversity and stability-diversity
+relationships have been assessed in terrestrial ecosystems while there is a
+evident need to test such relationships in a variety of ecosystem types. Stream
+ecosystems are characterized by the flowing water and depends for a large part
+from the input of terrestrial ecosystems. Furthermore, the biotic activity in
+stream ecosystems determines for a large part the water quality
+[@cummins_structure_1974] and thus are crucial to maintain stream ecosystem
+properties.
 
@@
 
-#### Stream fish communities is a good model to study effects of horizontal & vertical diversity
-
-Stream fish community constitutes a good model to study the joint effects of
-horizontal & vertical diversity on total biomass and its temporal stability.
-Despite that fish trophic interactions are difficult to assess in nature, a consequent
-body of literature supports that they can be inferred through body size and diet
-informations [@gravel_inferring_2013; @jennings_weak_2001;
-@brose_predator_2019]. Most of the biomass-diversity and stability-diversity
-relationships have been assessed in terrestrial ecosystems while there is a
-evident need to test such relationships in a variety of ecosystem types. Stream
-ecosystems are characterized by the flowing water and depends for a large part
-from the input of terrestrial ecosystems. Furthermore, the biotic activity in
-stream ecosystems determines for a large part the water quality
-[@cummins_structure_1974] and thus are crucial to maintain **human selfish
-goals (can do better than that)**.
-
 ## Data collection
@@
 electric fishing, resulting in over XX individual fish sampled [see
-@edeline__2013]. Two different standardized protocols were used for little and
+@edeline_ecological_2013]. Two different standardized protocols were used for little and
 big streams (detailed in Supplementary methods). For streams shallower than (XX
@@
 used. When the body size and therefore body mass vary by several orders of
-magnitude, one downside of abundance is that we mix individual that have
-potentially really different meaning in terms of ecosystem properties such as
-biomass. We therefore estimated the body mass of fish individuals according to
-their body size. The body mass of individual fishes were then estimated with an
-allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$ being the body mass in grams,
-$l$ the body size in millimeters and $i$ the individual)
-[@lleonart_removing_2000; @froese_cube_2006].
-
-The species and community biomass were then computed for each sampling event.
-As sampling effort, reported as the surface sampled during the sampling event,
-varied across protocol type and sampling event, biomass was reported to the
-surface sampled (in $m^{2}$). Community and species biomass were then expressed
+magnitude inside a community, one downside of using abundance is that we mix
+individuals that have potentially really different contributions in terms of ecosystem
+properties such as total biomass and biomass repartition. We estimated
+the body mass following an allometric law ($B_i = 0.01 \times
+l_i^{3.03}$, $B$ being the body mass in grams, $l$ the body size in millimeters
+and $i$ the individual) [@lleonart_removing_2000; @froese_cube_2006].
+
+The species and total biomass were then computed for each sampling event.
+As the sampling effort, reported as the surface sampled during the sampling event,
+varied across protocol type and sampling event, biomass was divided by the
+surface sampled (in $m^{2}$). So that, community and species biomass were expressed
 in $gm^{-2}$.
 
-Total biomass was characterized as the median total biomass over time. Temporal
-biomass stability was defined as the inverse of biomass variability. Variability
-was computed as Coefficient of Variation (CV) of the biomass ($CV_i = \sigma_i
-\mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being respectively the standard
-deviation and the temporal average of the biomass of the station $i$). Then, temporal
-stability was equal to $CV^{-1} = \mu \sigma^{-1}$.
-
-To characterize the mecanisms driving temporal stability, we decomposed
-the community CV in synchrony and weighted average species CV
+In the analysis, the total biomass of a given station was characterized as the
+median of the total biomass over time. Temporal biomass stability was defined as
+the inverse of biomass variability. Variability was computed as Coefficient of
+Variation (CV) of the biomass over time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and
+$\mu_i$ being respectively the standard deviation and the temporal average of
+the biomass of the station $i$). Then, temporal stability was equal to $CV^{-1}
+= \mu \sigma^{-1}$.
+
+To characterize the mechanisms driving temporal stability of communities, we
+decomposed the community CV in synchrony and weighted average species CV
 components according to @thibaut_understanding_2013:
@@
 $$
-CV_{com} = \overline{CV_{sp}} \times \sqrt{\phi}
+CV_{com, i} = \overline{CV_{sp, i}} \times \sqrt{\phi_i}
 $$
 
-with $CV_{com}$ being the Coefficient of Variation of the community,
-$\overline{CV_{sp}}$ the average coefficient of variation of population
-pondered by biomass. $\phi$ is the synchrony, which is the ratio the total
-community variance ($\sigma^2_{x_T}$) and the sum of population variance
-($\sigma_{x_i}$) [@loreau_species_2008].
+with $CV_{com, i}$ being the Coefficient of Variation of the community in the
+station $i$, $\overline{CV_{sp, i}}$ the average coefficient of variation of
+population in the station $i$ pondered by the biomass of each population.
+Synchrony of the station $i$, $\phi_i$, is the ratio between the variance of
+total biomass over time ($\sigma^2_{x_T}$) and the sum of the variance of
+population biomass over time ($\sigma_{x_k}$) [@loreau_species_2008]. $i$ being
+the station $i$ and $k$ the species $k$.
 
 $$
-\overline{CV_{sp}} = \sum_i{\frac{B_i {CV}_i}{\sum_i{B_i}}}
+\overline{CV_{sp, i}} = \sum_k{\frac{B_k {CV}_i}{\sum_k{B_k}}}
 $$
@@
 $$
-\phi = \frac{\sigma^2_{x_T}}{\sum_i{\sigma_{x_i}}}
+\phi_i = \frac{\sigma^2_{x_T}}{(\sum_k{\sqrt{\sigma^2_{x_k}}})^2}
 $$
 
-## Hozizontal & vertical diversity
+## Horizontal & vertical diversity
 
@@
 
-Species richness was computed as the total species richness over time in a given
-station. To normalize by sampling effort, we reported species richness to the
-sum of surface sampled over the time period, it was expressed in number of
-species by square meter.
+Species richness was computed as the total number of species present over time in a given
+station. As for biomass, we controlled species richness for sampling effort by
+dividing the total number of species by the total surface sampled in the given
+station. Species richness was then expressed in number of species by square meter sampled.
 
@@
 myload(metaweb_analysis, dir= mypath("data"))
+myload(trophic_class, dir= mypath("data", "classes"))
 meta <- metaweb_analysis
@@
 
-In each network, we computed two network metrics that have been commonly used to
-characterize network structure. Connectance which describes the number of
-interactions compared to the number of possible links, computed as ($C = L /
-N^2$, L and N being
-resp. the number of links and of trophic species plus resource nodes). We then
-computed the average trophic level, the average trophic level was weighted by
-the biomass of each trophic species (excluding resource nodes for which we had
-no biomass) ($\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, $T_i$
-and $B_i$ being resp. the trophic level and the biomass of the node $i$).
-
-In resume, we infered binary trophic networks at the scale of trophic species
-(i.e. body size classes by species) to take in account ontogenic diet shifts and
-that fish-fish trophic interaction depends on body size ratio. On the other
-side, the community metrics were defined at the species level, (i.e. species
-richness, average species CV and synchrony).
+For each trophic network, corresponding to a particular community at a given
+time and location, we computed two of the most communly used network metrics to
+characterize network structure, namely the connectance and average trophic
+level. Connectance describes the number of interactions compared to the number
+of possible links, computed as ($C = L / N^2$, L and N being resp. the number of
+links and of trophic species plus resource nodes). The average trophic level was
+computed as the mean trophic level of the nodes that the predator nodes consumes
+to which is added one, obtained recursively by setting the trophic level of
+basal nodes to 1, and was further weighted by the biomass of each trophic
+species (excluding resource nodes for which we had no biomass information)
+($\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, $T_i$ and $B_i$
+being resp. the trophic level and the biomass of the node $i$). In resume, we
+infered trophic networks at the scale of trophic species (i.e. nodes being body
+size classes) to take in account ontogenic diet shifts and that fish-fish
+trophic interaction depends on body size ratio between prey and predator. On the
+other side, the community metrics were defined at the species level, (i.e.
+species richness, average species CV and synchrony).
 
@@
 of the variables by the principal components (Fig. \@ref(fig:pca-rotated)).
-Five principal components were used in the analysis, representing respectively
+The two first principal components were used in the analysis, representing respectively
 the (1) river size (river width & depth), (2) altitude, slope and decreasing
-average temperature, (3) average enrichment (BOD) and CV of flow, (4) river size
-CV (CV of river width and depth) and (5) CV of enrichment (CV of BOD). Further
-informations about data transformation and filtering are detailed in
-supplementary information.
+average temperature. Further informations about data transformation and
+filtering are detailed in supplementary information.
 
@@
 
-#### SEM is a convenient approach to investigate direct and indirect path
-
-To reveal the direct and indirect effects of environment, horizontal & vertical
-diversity on both total biomass and its temporal stability, we built and
-analyzed Structural Equation Models (SEM). It is one promising way to go beyond
+#### Summarise SEM statistical framework
+
+Structural Equation Modeling are able to assess multivariate relationships,
+directs and indirects between variables. It is one promising way to go beyond
 bivariate relationships and to investigate complex relationships, direct and
@@
 vertical diversity affects total biomass and its temporal stability (Figure
-\@ref(fig:matmet) A).
-
-#### Summarise SEM statistical framework
-
-Structural Equation Modeling are able to assess multivariate relationships,
-directs and indirects between variables.  The metamodel describes how variables
-are interrelated (Figure \@ref(fig:matmet) A). We built separated structural
-equation model for total biomass and its temporal variability (Figure
-\@ref(fig:sem-plot) A & B). Structural equation modeling was set up according to the
-hypothesis described in introduction and detailed in supplementary information.
+\@ref(fig:matmet) A). The metamodel describes how variables are interrelated
+(Figure \@ref(fig:matmet) A). We built separated structural equation model for
+total biomass and its temporal variability (Figure \@ref(fig:sem-plot) A & B).
+
 Structural equation models were based on Gaussian linear models, some variables
 were logged to fulfill model assumptions (see residual plots and data
-transformation in supplementary
-informations). To account for heterogeneity of hydrographic basin, we set it as random effect on the intercept. Moreover, statistical model were checked for the presence of
-multicollinearity (Supplementary information). The slopes reported in the main
+transformation in supplementary informations). To account for heterogeneity of
+hydrographic basin, we set it as random effect on the intercept. Moreover, each
+statistical model was checked for the presence of multicollinearity
+(Supplementary information). The slopes reported in the main
 text are standardized in order to compare their magnitude ($r_\delta = \beta
@@
 slopes which had $P$ value inferior to $0.05$ were reported (but see Table SXX).
-
 The structural equation models used for total biomass and its temporal stability
 contains respectively 4 and 6 response variables, 35 and 26 direct paths.
-
-#### Computation of indirect effects
-
 The indirect effects of variables on total biomass and its temporal stability
@@
 bind_rows()
-```
-
-```{r indir-stab}
-kable(format_table(tmp_stab_indir_table),
-  format = "latex",
-  booktabs = T,
-  label = paste0("indir-stab"),
-  caption = caption_indir_stab_sem 
-  ) %>%
-kable_styling(latex_options =c("striped", "scale_down"))
 ```
@@
 
+```{r indir-stab}
+kable(format_table(tmp_stab_indir_table),
+  format = "latex",
+  booktabs = T,
+  label = paste0("indir-stab"),
+  caption = caption_indir_stab_sem 
+  ) %>%
+kable_styling(latex_options =c("striped", "scale_down"))
+```
+
 Overall, the structural equation models explained a large part of the variation
@@
 $r_\delta = `r rich_on_bm$direct`$ (Figure \@ref(fig:sem-plot) D, Table
-\@ref(tab:indir-bm)). However, species richness had a total negative effect
+\@ref(tab:indir-bm)). However, species richness had a negative total effect
 on biomass stability ($r_\delta = `r rich_on_stab$total`$, Table
-\@ref(tab:indir-stab)). Species richness had a positive effect on stability
-through synchrony ($r_\delta = `r rich_on_stab$via_sync`$) but a negative  one
-through $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
-\@ref(tab:indir-stab)). Futhermore, species richness had a strong opposite
-direct effect on $\overline{CV_{sp}}$ and synchrony, positive on
-$\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$) and negative on synchrony
-($r_\delta = `r rich_on_sync$direct`$).  Finally, it was surprising that the negative
+\@ref(tab:indir-stab)). On the one hand, species richness had a direct negative effect on synchrony
+($r_\delta = `r rich_on_sync$direct`$), thereby increasing stability ($r_\delta
+= `r rich_on_stab$via_sync`$). On the other hand, species richness had a
+positive direct effect on $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$),
+thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
+\@ref(tab:indir-stab)). Finally, it was surprising that the negative
 effect of $\overline{CV_{sp}}$ on temporal stability was twice higher than the
@@
 
-Average trophic level had a positive effect on total biomass ($r_\delta
-= `r tlvl_on_bm`$) but connectance had no significant effect (Figure
-\@ref(fig:sem-plot) D). Average trophic level had a total positive effect on
-temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$, Table
-\@ref(tab:indir-stab)) by decreasing $\overline{CV_{sp}}$
-($r_\delta = `r tlvl_on_cv_sp`$,
-Figure \@ref(fig:sem-plot) C). Again, connectance had no significant effect on
-temporal stability (Figure \@ref(fig:sem-plot) C, Table SXX).
+Average trophic level had a direct positive effect on total biomass ($r_\delta
+= `r tlvl_on_bm`$) but connectance had no direct nor indirect significant effect (Figure
+\@ref(fig:sem-plot) D) on total biomass. However, the average trophic level had
+a direct negative effect on $\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
+Figure \@ref(fig:sem-plot) C) and thereby had a total positive
+effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
+Table \@ref(tab:indir-stab)). The average trophic level had no significant
+effect on synchrony and connectance had no significant direct, nor indirect
+effect on temporal stability (Figure \@ref(fig:sem-plot) C, Table SXX).
 
@@
 ($r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-stab)).
-Interesting, average temperature (and reverse of
-altitude, *chiant cette variable composite*) had also a negative effect on
-temporal stability through species richness but a positive one through average
-trophic level (resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
+Interestingly, average temperature (and opposite of altitude) had also a negative
+effect on temporal stability through species richness but a positive one through
+average trophic level 
+(resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
 $r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-stab)).
 This was also true for average river size but effects were weak. Finally, the
-effect of average temperature on temporal stability had a magnitude higher than
-species richness and average trophic level (Table \@ref(tab:indir-stab)).
+effect of average temperature on temporal stability was of higher magnitude than
+the effects of species richness and average trophic level (Table
+\@ref(tab:indir-stab)).
 
@@
 
-With the aim to find out the determinants of total biomass and its temporal
-stability in fish trophic communities, we analyzed a standardized dataset at
-France scale going on from 1995 to 2018. We infer network structure with
-together body size and food diet method and used SEM to disantangle direct and
-indirect effects of environment, horizontal and vertical diversity on both total
-biomass and biomass stability. We found that species richness and average
-trophic level positively covariated with total biomass. However, species
-richness negatively covariated with temporal stability whereas average trophic
-level covariated positively. Futhermore, we found that the effect of species
-richness and average trophic level on total biomass and its temporal stability
-were independant. Finally, we found the magnitude of the effects of average
-temperature and altitude was equal or superior to the effects of species
-richness and average trophic level.
+Our aim was to clarify respective importance and nature of direct and indirect
+effects of environmental drivers, horizontal and vertical diversity, captured by
+species richness and trophic network structure (connectance and average trophic
+level), on total biomass and its temporal stability in aquatic foodwebs. To do
+this we quantified interactive effects of habitat properties, species richness,
+and trophic structure, on the biomass and stability of fish communities, from
+the ONEMA fish dataset, containing over X million individual fish samples,
+across 99 locations France spanning the period 1995 to 2018. We infered trophic
+interactions networks based on body size-dependency in food diet from the
+literature and prey/predator body size ratio for piscivory. We used SEM to
+disantangle direct and indirect effects of environmental drivers, horizontal and
+vertical diversity on both total biomass and biomass stability. We found that
+species richness and average trophic level had a positive effect on total
+biomass. In contrast, species richness had a negative effect on temporal
+stability whereas average trophic level covaried positively.  Futhermore, we
+found that the effect of species richness and average trophic level on total
+biomass and its temporal stability were not independant as species richness had
+a positive effect on average trophic level.  Finally, we found that the
+magnitude of the effects of average temperature and altitude was equal or
+superior to the effects of species richness and average trophic level. Overall,
+our study is unique by its level of integration, from environmental effects to
+total biomass and stability, going through horizontal and vertical diversity,
+and the fist direct assessment of a possible interaction between effects of
+horizontal and vertical diversity.
 
@@
 We found that species richness increased total biomass as found in salt marshes,
+grasslands and
 forests [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
 @li_relationship_2018]. The positive effect of species richness on total biomass
-might be due to resource use complementarity [@cardinale_species_2002]. But
-opposite relation has been found in richness in grasslands presumably because of
-light competition [@grace_integrative_2016].  In accordance with theoretical
-models, resource use complementarity [@loreau_biodiversity_1998;
-@thebault_relationship_2006] might also be at work in fish trophic communities.
+might be due to resource use complementarity, which is held by niche
+differentiation and interspecific facilitation [@loreau_biodiversity_1998;
+@loreau_partitioning_2001; @cardinale_species_2002] or might be due to positive
+select effect which takes place through the dominance of the
+most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
+Previous research seems to indicate that resource complementarity might be the
+main driver in fish communities [@carey_determining_2011].
 
 Surprisingly found a negative relationship between temporal stability and
-species richness. Overall, it contrasts with studies experimental studies in
+species richness. Overall, it contrasts with experimental studies in
 grasslands [@tilman_biodiversity_2006]; mesocosms [@pennekamp_biodiversity_2018]
@@
 [@declerck_species_2006] in natural forests. Further investigations are needed
-to identify the mechanisms behind those contrasting patterns,
-
-- add [@yang_effects_2011]
-
- Species richness decreased synchrony
-and increased $\overline{CV_{sp}}$. Species richness can reduce synchrony
-through decrease of population size, thus raising the role of demographic
-stochasticity [@loreau_species_2008] but also in the case where species have
-different responses to environmental variation [@loreau_species_2008]. While the
-effect of species richness on synchrony is well understood, its effect on
-$\overline{CV_{sp}}$ is more complex [see @thibaut_understanding_2013].
-
-Suprisingly, we found that $\overline{CV_{sp}}$ had an negative effect twice
-higher than synchrony on biomass stability.In turn,
-we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
+to identify the mechanisms behind those contrasting patterns.
+
+Species richness decreased synchrony and increased $\overline{CV_{sp}}$. Species
+richness can reduce synchrony through decrease of population size, thus raising
+the role of demographic stochasticity [@loreau_species_2008] but also in the
+case where species have different responses to environmental variation
+[@loreau_species_2008]. While the effect of species richness on synchrony is
+well understood, its effect on $\overline{CV_{sp}}$ is more complex [see
+@thibaut_understanding_2013]. However a negative effect of species richness of
+both population ($\overline{CV_{sp}}$) and community stability can arise the
+biomass distribution across population is strongly uneven and that the biomass
+variance of population increases much faster than its mean
+[@thibaut_understanding_2013].
+
+In turn, we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
 stability, as predicted by the formulation of stability based on the CV
@@
 that body mass increase with body size, it is expected that the more the average
-biomass is located at higher trophic level, the more the total biomass increase.
-*Look at Digel et al. 2011, Riede et al. 2011*
-
+biomass is located at higher trophic level, the more the total biomass
+increase. A mechanism, suggested by experimental and theoretical work, can
+be that a higher trophic level is the result of a stronger top-down effect,
+meaning higher predation rates and biomass fluxes to higher trophic levels
+[@thebault_relationship_2006; @kratina_warming_2012], hence leading to an
+increase in total biomass with vertical diversity. Furthermore,
+@wang_biodiversity_2016 have shown that total nutrient uptake might increases
+with the length of trophic chain and so results in higher total biomass. 
 In contrast, connectance had no effect on total biomass. One might have expected
 that an increase in connectance should translate in higher resource transfer
-efficiency between prey and predators and so results in higher total biomass. A
-reason for such an absence of an effect might be the absence of an interaction
-strength knowledge/estimation. A consequence can be that connectance contains
-few too informations. [ADD @thebault_relationship_2006].
+efficiency between prey and predators and so results in higher total biomass in
+the fish compartment. A reason for such an absence of an effect might be the
+little resolution that we have about interactions in non fish compartment (Fig.
+\@ref(fig:methods) C, D). A consequence can be that our connectance measurement
+contains few too informations.
 
@@
 found the same pattern with pure trophic chain models. They have shown that
-strong top-down control can generate the pattern that we observed but it is not
+strong top-down control can generate this pattern but it is not
 clear if this theoretical prediction holds when considering omnivorous species
-(i.e not a pure food chain) and if other mechanisms can generate the same
-pattern.  For example, species mean-variance relationship could also generate
-this pattern. Moreover, the ontogenic nature of our networks can also be an
-important mechanism at play.  Over its life span, a given fish will change of
-diet and thus move upward in the trophic chain. The dynamic of a given species
-composed of several trophic species can thus be a mix of the dynamics of several
-trophic levels, plus the oscillatory dynamics of the cohorts
-[@townsend_population_1989; @medvinsky_modelling_2015]. Then, there is a clear
-need for a better understanding of how the dynamics of pure food chain models
-would be affected by inclusion of omnivory and ontogeny.
+(i.e not a pure food chain) [@wang_biodiversity_2016] and if other mechanisms
+can generate the same pattern [@thibaut_understanding_2013].
+Another explanation is that the fishes at higher trophic levels are not more
+stable themselves, but rather allow for stronger top-down control and resource
+complementarity and thus reduce biomass fluctuations [@rooney_structural_2006;
+@neutel_reconciling_2007]. However, the ontogenic nature of the trophic
+networks complicate the interpretation from the network to population
+perspective. Over its life span, a given fish will change of diet and thus move
+upward in the trophic chain. The dynamic of a given species composed
+of several trophic species can thus be a mix of the dynamics of several trophic
+levels, plus the oscillatory dynamics of the cohorts [@townsend_population_1989;
+@medvinsky_modelling_2015]. Then, there is a clear need for a better
+understanding of how the dynamics of pure food chain models would be affected by
+inclusion of omnivory and ontogeny.
 
@@
 and network structure [@angelis_stability_1975; @may_will_1972;
-@thebault_stability_2010], although they considered different stability metrics
-(i.e. local stability of equilibrium point). Once again, it is possible that
-that connectance from our networks contains too few information.
-Furthermore, a crucial missing ingredient to go further is the interaction
-strength. Indeed, @may_will_1972 has theoretically demonstrated the
-fondamental interplay between connectance, species richness and average
-interaction strength (*Add ref and develop a bit*).
-
-## Horizontal and vertical diversity had common, opposite and dependant effects on total biomass and its temporal stability
+@thebault_stability_2010], although they considered different stability concepts
+and metrics [@arnoldi_resilience_2016]. Once again, it is possible that
+that connectance from our networks contains too few information. Furthermore, a
+crucial missing ingredient to go further is the interaction strength. Indeed,
+@may_will_1972 has demonstrated theoretically the fundamental interplay between
+connectance, species richness and average interaction strength
+[@angelis_stability_1975; @dunne_network_2006].An alternative explanation can be
+that connectance increases inhomogeneously in the food web, for instance a
+higher connectance in lower trophic levels will not have the stabilising effects
+conferred by higher predation and omnivory in higher trophic levels. Further
+investigations on this effect is needed.
+
+## Horizontal and vertical diversity had common, opposite and dependent effects on total biomass and its temporal stability
 
@@
 respectively total biomass and its temporal stability whereas average trophic
-level had a positive effect on both. It confirms that more investigation is needed to
-understand the mechanisms leading to common and opposite effects of
-horizontal and vertical diversity. @thibaut_understanding_2013 have
-theoretically shown that a highly positive relationship between species variance
-and mean together with a positive relationship between mean species abundance
-(i.e. dominance) and species richness should drive to a negative temporal
-stability - species richness relationship. @thebault_relationship_2006 have
-also shown in a bi-trophic foodweb that a positive temporal stability-species
-richness appears in case of a plant species is highly dominant through low
-comsumption by consumers but in the same time highly variable because of low
-competitive ability. Then, common mecanisms might be at play for both horizontal
-and vertical diversity while having same or opposite effects on total biomass
-and its temporal stability.
-
-We found that connectance covaries negatively with species richness
-[@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010],
-connectance had itself no effects on both total biomass and its temporal
-stability. On the other side, we found species richness was negatively related
-to average trophic level and average trophic level covariated positively with
-total biomass and its temporal stability. Hence, horizontal diversity had a
-direct positive and negative effect respectively on total biomass and its
-stability but a negative and positive effect through vertical diversity. It
-indicates the importance to consider both horizontal, vertical diversity and
-their dependance.
+level had a positive effect on both. It confirms that more investigation is
+needed to understand the mechanisms leading to common and opposite effects of
+horizontal and vertical diversity. We found that connectance covaries
+negatively with species richness [@winemiller_must_1989; @dunne_network_2006;
+@thebault_stability_2010], connectance had itself no effects on both total
+biomass and its temporal stability. On the other side, we found species richness
+was negatively related to average trophic level and average trophic level
+covariated positively with total biomass and its temporal stability. Hence,
+horizontal diversity had a direct positive and negative effect respectively on
+total biomass and its stability but a negative and positive effect through
+vertical diversity.  Theoretical work have shown that species richness can be
+linked to allocation of biomass toward higher trophic level
+[@thebault_relationship_2006; @schneider_animal_2016; @wang_biodiversity_2016].
+It indicates the importance to consider both horizontal, vertical diversity and
+their dependence. Moreover, it calls for further investigations on how species
+diversity variation translates in network structure.
+
+@thibaut_understanding_2013 have theoretically shown that a highly positive
+relationship between species variance and mean together with a positive
+relationship between mean species abundance (i.e. dominance) and species
+richness should drive to a negative temporal stability-species richness
+relationship. @thebault_relationship_2006 have also shown in a bi-trophic
+foodweb that a negative temporal stability-species richness appears in case of a
+plant species is highly dominant through low consumption by consumers but in the
+same time highly variable because of low competitive ability. Then, common
+mechanisms might be at play for both horizontal and vertical diversity while
+having same or opposite effects on total biomass and its temporal stability.
+Overall our results confirm that more investigation is needed to understand the
+mechanisms leading to common and opposite effects of horizontal and vertical
+diversity.
 
@@
 
-- add [@yang_effects_2011]
-
-Precedent researches in plant communities showed that the total biomass was
-primary driven by environmental drivers [@grace_integrative_2016]. We did not
-find direct but indirect effects of environmental drivers on total biomass. The
-average temperature (& inverse altitude) was positively linked to total biomass
-mainly through species richness while the average stream size had a positive
-link equally through species richness and average trophic level. It is not
-straightforward to explain why the effect average temperature and altitude was
-going through horizontal diversity and why average stream size is going through
-both horizontal and vertical diversity.  (*Add more biological interpretations
-about total effect? Until now, what I have in mind is a bit bullshit and those
-explanations are not the heart of the paper.  What do you think?*).  Overall it
-indicates that environment affects primarily community structure and then
-affects total biomass. Furthermore, one can notice that average temperature had
-a positive effect on total of the same magnitude than horizontal & vertical
-diversity. It underlines that environment should not be ignored in natural
-communities studies and that its effects can be mainly indirect and in this
-case, path analysis should more relevant than bivariate relationships
+We find that environmental drivers overall affect total biomass indirectly,
+through changes in vertical and horizontal diversity. This contrasts with
+research in plant communities that showed that total biomass was primarily
+driven by environmental factors [@grace_integrative_2016], and in particular by
+warming, which has contrasted effects on biomass in aquatic communities
+[@yvondurocher_warming_2011; @dossena_warming_2012]. Average temperature,
+inverse altitude, and average stream size had indirect positive effects on total
+biomass, through a positive direct effect on species richness. These effects are
+well known in freshwater communities and are explained by a gain in species
+along thermal gradients, from smaller and colder streams, which support small
+food webs dominated by salmonids [@ogorman_chapter_2012; @emmrich_geographical_2014],
+to wider and warmer sections of river networks, which contain larger food webs
+dominated by mesotrophic preators such as percids [@allan_stream_2007;
+@emmrich_geographical_2014]. Further in line with this pattern, we find that average stream
+size had a positive effect on total biomass through
+a positive effect on average trophic level, consistent with the fact that food
+webs in wider streams, with a greater amount of running waters, are also larger,
+and hence support more species and biomass [@allan_stream_2007]. Greater ecosystem
+size might be linked to a greater diversity of resources through habitat
+heterogeneity, on so higher species richness and total biomass by surface unit,
+through resource complementarity. Greater diversity of resources might also
+allow to maintain higher biomass in high trophic level [@post_ecosystem_2000;
+@doi_resource_2009]. Overall, our results indicate that environmental effects on
+total biomass operate primarily through changes in community structure.
+Furthermore, the positive effect of temperature on total biomass was of the
+magnitude of effects of horizontal and vertical diversity, and thereby of
+changes in community structure. This adds to the mounting body of work reporting
+important effects of temperature on the structure and biomass of aquatic system
+[e.g. @dossena_warming_2012; @edeline_ecological_2013;
+@emmrich_geographical_2014; @hattab_forecasting_2016].
+
+Interestingly, stream flow and size, inverse altitude, and temperature had
+indirect effects on stability through two conflicting pathways, either
+stabilising, involving vertical diversity, or destabilising, involving
+horizontal diversity. The first pathway consists in a positive effect of
+temperature and stream properties on average trophic level, in line with the idea
+that wider streams and warmer conditions are favourable to mesotrophic predators
+[@allan_stream_2007; @emmrich_geographical_2014], which in turn stabilises
+biomass fluctuations, possibly due to increased top-down regulation (as
+discussed above). The second pathway consists in a positive effect of
+temperature and stream properties (width, flow, inverse altitude) on species
+richness, which itself has a destabilising effect (see discussion on horizontal
+diversity). This result is interesting in that though both pathways had not been
+evidenced to be at jointly play, as far as we know. Furthermore, it is unclear
+as to which pathway is dominating, and under which circumstance, opening an
+interesting avenue for further investigations. Overall our study highlights
+that environmental factors should not be ignored in natural communities studies
+and that its effects can be mainly indirect and in this case, path analysis
+should more relevant than bivariate relationships
 [@grace_causal_2014; @grace_integrative_2016].
-
-Average temperature (& inverse of altitude) had a negative effect on temporal
-stability, mainly by an direct positive CVsp. Two mecanisms might explain this
-pattern: (i) temperature is negatively linked to concentration of dissolved
-oxygen and so might be linked to respiration stress, (ii) temperature might lead
-be to higher metabolic activity and so higher variability [@taby_warming_2019].
-Interestingly, average temperature (& inverse of altitude) had also a negative
-effect on temporal stability through species richness but a positive one through
-average trophic level. Then, the effect of temperature on temporal stability
-might be more complex than previously thought and call for further
-investigations. Furthermore, average temperature and altitude had a stronger
-effect on temporal stability than horizontal and vertical diversity. Considering
-big effects of temperature on both total biomass and its temporal stability
-might suggest the crucial role of climate change on stream ecosystems. (*Not
-convinced: may be to discuss together*)
 
@@
 trophic communities. While theoretical ecology has focused on the effects of
-network structure on stability, empirical ecology has focused on species richess
-and ingnored network structure. Furthermore, both fields have largely used
+network structure on stability, empirical ecology has focused on species richness
+and ignored network structure. Furthermore, both fields have largely used
 different stability metrics. We showed that horizontal and vertical diversity
@@
 [@grace_integrative_2016]. We believe that the integration of network structure
-and species interaction in general will improve our understanding of the
-mechanisms which determines ecosystem properties. (*c'est pas top mais à
-discuter*)
+and species interaction will improve our understanding of the mechanisms driving
+ecosystem properties.
 

### 2020-07-03 manuscript/bef_stability/manuscript.Rmd
Finish review results, start discussion

@@
 ---
-title: Horizontal and vertical diversity jointly drive total biomass and its temporal stability in fish communities
+title: Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
 author: Alain Danet, Maud Mouchet, (Willem Bonnaffe ici?), Elisa Thebault and Colin Fontaine
@@
 
-The effect of horizontal  and vertical diversity on ecosystem properties has
+The effect of species richness and network structure on ecosystem properties has
 been central to ecology. It has been at the basis of the predictions of the
 effect species richness and  network structure on total biomass, productivity
-and stability. However, they have mainly been studied separately.  We used a
-dataset of standardized fish sampling in French stream running from 1995 to
+and stability. However, empirical data are lacking on the link between network
+structure and ecosystem properties. We used a dataset of standardized fish
+sampling in French stream running from 1995 to
 2018. We inferred trophic interactions thanks to recorded body size and diet
 literature. We then investigate the direct and indirect effects of stream
-size and temperature, horizontal and vertical diversity on total biomass and
-its temporal stability. We found that horizontal and vertical diversity had
+size and temperature, species richness and network structure on total biomass and
+its temporal stability. We found that species richness and network structure had
 a positive relationship with total biomass while they had respectively a
 negative and positive effect on temporal stability. We also found that
-horizontal and vertical diversity are not independent and that environment
+species richness and network structure are not independent and that environment
 had an tremendous effect on total biomass and its temporal stability notably
-through its effect on horizontal and vertical diversity. We conclude that our
-study highlights that the effects horizontal and vertical diversity should not
-treated separately and that it opens exciting perspectives on how environment,
-horizontal and vertical can jointly determine total biomass in natural
+through its effect on species richness and network structure. We conclude that our
+study highlights that the effects of species richness and network structure should be 
+assessed conjointly and that it opens exciting perspectives on how environment,
+species richness and network structure can jointly determine total biomass in natural
 communities.
 
-(194/150 words)
+(210/150 words)
 
@@
 
-Current biodiversity losses and global changes affect ecosystems in complex and
-unpredictable ways [@bellard_impacts_2012]. Since the seminal of paper of
-@may_will_1972, the relationships between biodiversity and ecosystem properties
-have received a lot of attention [@hector_plant_1999; @loreau_biodiversity_2001;
-@hooper_effects_2005; @dunne_network_2006; @duffy_why_2009;
-@isbell_forest_quantifying_2018]. Biodiversity largely determines both the
-amount and the distribution of matter and energy fluxes within ecosystems, and
-has hence a tremendous effect on ecosystem properties [@duffy_why_2009], such as
-its total biomass [@hector_plant_1999; @tilman_biodiversity_2014;
-@grace_integrative_2016; @pennekamp_biodiversity_2018], biomass production
-[@tilman_productivity_1996; @cardinale_species_2002; @grace_integrative_2016]
-and the biomass temporal stability [@thebault_trophic_2005;
-@thebault_relationship_2006; @tilman_biodiversity_2006;
-@olivier_independent_nodate].
-
-#### Horizontal and vertical diversity are two ways to look at biodiversity
-
-Biodiversity can be quantified in numerous ways: either as the number of species
-(i.e.  species richness) and in number of functional groups, which are usually
-defined based on the trophic ecology of species, namely the way they acquire
-food [@allan_stream_2007]. Those metrics can be organized into (i) "horizontal
-diversity", which captures the overall diversity of components (i.e. species)
-present in a community, and (ii) "vertical diversity" which captures diversity
-of components across functional groups, such as the amount trophic categories,
-often termed guilds or levels [@allan_stream_2007; @loreau_populations_2010;
-@zhao_horizontal_2019; @wang_biodiversity_2016]. Vertical diversity has been
-primarily quantified as food chain length [@loreau_populations_2010;
-@zhao_horizontal_2019; @wang_biodiversity_2016] but it can also be characterized
-by the food web structure [@wang_biodiversity_2016] such as connectance and
-average trophic level. Horizontal and vertical diversity are, however, not
-independent from each other. Connectance is known to covary negatively with
-species richness [@winemiller_must_1989; @dunne_network_2006;
-@thebault_stability_2010]. Species diversity also result in modification of
-biomass distribution across the food web [@thebault_relationship_2006;
-@duffy_ecosystem_2005; @duffy_functional_2007; @schneider_animal_2016].
-Hence, it is crucial to study if horizontal and vertical diversity have synergic
-or antagonistic effects and how their interplay modulates ecosystem properties.
-
-#### horizontal and vertical diversity increase total biomass by common and different mechanisms
-
-Horizontal diversity has been shown to promote higher biomass production in a
-variety of ecosystems. Horizontal diversity, as species richness, has been
-reported to increase primary productivity [@cardinale_species_2002,
-@tilman_productivity_1996; @grace_integrative_2016]. Two mechanisms have been
-proposed to rise this effect [@loreau_partitioning_2001]. The complementarity in
+Current biodiversity losses and global changes has the potential to affect
+ecosystems in complex ways [@bellard_impacts_2012]. Biodiversity has a
+tremendous effect on ecosystem properties because it largely determines both the
+amount and the distribution of matter and energy fluxes
+within ecosystems [@duffy_why_2009]. Biodiversity thus affects biomass
+production [@tilman_productivity_1996; @cardinale_species_2002;
+@grace_integrative_2016], biomass repartition [@thebault_relationship_2006] and
+biomass stability [@thebault_trophic_2005; @thebault_relationship_2006;
+@tilman_biodiversity_2006]. The relationship between biodiversity and
+ecosystem properties is a central topic in ecology [@hector_plant_1999;
+@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
+@duffy_why_2009; @isbell_forest_quantifying_2018] and its documentation is thus
+crucial to better anticipate the impacts of global changes.
+
+#### Species richness increases total biomass
+
+Species richness promotes higher biomass production in a variety of ecosystems
+and organisms. Indeed species richness generally increases primary productivity
+and total biomass in experimental plant communities [@tilman_productivity_1996;
+@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
+@grace_integrative_2016], but also in briophyte communities
+[@mulder_physical_2001], stream feeders [@cardinale_species_2002] and aquatic
+bacterial consumers [@pennekamp_biodiversity_2018]. Theoretical models also
+predict this pattern in plant communities [@tilman_plant_1997;
+@loreau_partitioning_2001] and food webs [@schneider_animal_2016]. Resource use
+complementarity and selection effects have been proposed to elucidate the
+positive effect of species richness on productivity. The complementarity in
 resource use, rising through niche differentiation and interspecific
@@
 [@loreau_biodiversity_1998; @cardinale_species_2002; @loreau_partitioning_2001].
-Positive select effect arise when species richness leads to an higher dominance
+A positive selection effect arises when species richness leads to an higher dominance
 of the most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
-As for total biomass, empirical studies have generally demonstrated positive
-relationships with species richness in plant communities [@hector_plant_1999;
-@tilman_biodiversity_2014; but see @grace_integrative_2016] and mesocosms
-[@pennekamp_biodiversity_2018]. When adding the vertical diversity, e.g.
-consumers species, @gamfeldt_species_2005 and @thebault_relationship_2006 have found that total
-biomass increased with increasing species diversity at two trophic levels.
-But this positive relation seems to strongly depend on the niche differentiation of
-the consumer species, i.e. their resource complementarity,
-@thebault_relationship_2006. Hence, the total biomass-species richness
-relationship seems to be supported by the same mechanisms within consumers and
-within plants. @schneider_animal_2016 also showed in a allometric food web model
-that species richness should increase total animal biomass.
-Vertical diversity also affect total biomass. Theoretical studies showed that food
-web properties, such as interaction distribution and strength, affect the
-vertical distribution of biomass [@thebault_relationship_2006;
-@schneider_animal_2016; @barbier_pyramids_2019], i.e. average trophic level.
-More precisely, an increase of animal diversity results in
-higher animal biomass as more biomass is transfered from plant to animals
-[@schneider_animal_2016; @thebault_food-web_2003]. However, the role of vertical
-diversity on the total biomass remains unclear in
-natural communities.
-
-#### Horizontal and vertical diversity versus temporal stability
-
-Horizontal and vertical diversity also affects the stability of ecosystem
-properties. Experimental studies showed consistently that species richness
-increases the temporal stability of biomass in grasslands
-[@tilman_biodiversity_2006], and mesocosms [@pennekamp_biodiversity_2018]. The
-same relation was found in natural settings for temporal biomass stability in
-stream fish communities [@franssen_annual_2011] and temporal abundance stability
-of birds and butterflies [@olivier_independent_nodate, but not bats].  Two
-mechanisms may govern the temporal stability of communities, (1) species
-synchrony and (2) variability [@loreau_species_2008;
-@thibaut_understanding_2013]. Species synchrony measures the temporal
-covariation of species where low synchrony indicates that species temporal
-variation compensate each other at the community level, thereby increasing
-temporal stability. Species richness was found to decrease
-synchrony between species [@loreau_species_2008; @thibaut_understanding_2013;
-@bluthgen_land_2016; @olivier_independent_nodate; but @declerck_species_2006].
-The species variability is measured as a average coefficient
-of variation of abundance/biomass, weighted by species abundance/biomass. Higher species
-temporal variability should thus result in lower temporal stability. Positive
-[@tilman_biodiversity_2006], neutral [@jiang_different_2009;
-@olivier_independent_nodate] and negative [@franssen_annual_2011;
-@olivier_independent_nodate] relationships between species variability and
-species richness have been found. This conflicting patterns are dependent on
-various mechanisms [see @thibaut_understanding_2013]. Species synchrony has been found to be
-the main driver of temporal stability [@tilman_biodiversity_2006;
-@olivier_independent_nodate] and responsible for the positive relationship
-between horizontal diversity and temporal stability of biomass and abundance.
-
-Vertical diversity, captured by network structure, has been at the heart of the
-diversity-stability debate and largely explored by theoretical ecology
-[@may_will_1972; @angelis_stability_1975; @dunne_network_2006;
-@stouffer_compartmentalization_2011; @thebault_stability_2010;
-@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate]. As species
-interactions introduce inter-dependencies in species dynamics, they have a
-substantial impact on stability. In particular, the strength of predation and
-degree of omnivory in food webs have been shown to favor stability
-[@neutel_reconciling_2007]. Furthermore, competition strength and niche breath of
-consumers, can lead to negative or positive temporal stability-species richness
-relationships [@thebault_trophic_2005] depending on the food web configuration
-[@neutel_reconciling_2007].  However, it is important to note that theoretical ecology
-generally defines stability based on community equilibrium and its stability to
-small independent perturbations [@may_will_1972; @angelis_stability_1975;
-@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate] or to the amount
-of secondary extinctions following species removal [@duffy_why_2009]. In
-practice, these stability metrics hardly relate to empirical temporal stability
-[@arnoldi_resilience_2016].
+In contrast, both positive [@wu_relationship_2014; @li_relationship_2018],
+negative or no effects [@szwagrzyk_above-ground_2007; @jacob_productivity_2010;
+@seidel_relationship_2013] of species richness on total biomass have been found
+in natural forest. Some authors suggest that the lack of resource
+complementarity or environmental harshness might be responsible for an absence or a
+negative effect of species richness [@loreau_partitioning_2001; @he_global_2013;
+@wu_relationship_2014]. Overall, under what conditions and through what
+mechanisms we should observe positive relationships between biomass and species
+richness in natural settings is still an open question.
+
+Many studies showed that species richness also increases temporal stability,
+i.e. variation through time, often quantified using CV. Such positive
+relationships between species richness and temporal stability have been reported
+in experimental grasslands and aquatic bacterial systems
+[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018]. Theoretical works
+have clarified which mechanisms generate this positive relationship between
+species richness and temporal stability [@loreau_species_2008;
+@thibaut_understanding_2013]. Two mechanisms may govern the temporal stability
+of communities, (1) species synchrony and (2) species variability. Species
+synchrony quantify to what extent the fluctuations of abundances or biomasses
+through time are correlated among species. A low synchrony in species
+fluctuations, i.e.  asynchrony, is synonymous of compensatory dynamic, where the
+decrease in abundance of a species is compensated by the increase of an other.
+Asynchrony is generally the main mechanism whereby species richness has a
+stabilizing effect on temporal stability [@tilman_biodiversity_2006;
+@olivier_independent_nodate].  ^[Colin asked for a word about $cv_{sp}$ and
+stability but my opinion is that it is not necessary and that the depth of mecanisms are
+currently fairly explained for the introduction]. Such positive relationships
+between speciesrichness and temporal are also observed in natural settings, such
+as stream fish communities [@franssen_annual_2011], bird and butterfly
+communities [@olivier_independent_nodate].
+
+#### Multitrophic communities
+
+One has to notice that most of the empirical and experimental evidence of the
+positive effect of richness on biomass production and stablity through time
+comes from studies focusing on one trophic level, generally primary producers or
+primary consumers. Natural ecosystems generally include
+more than one or two trophic levels and it is not certain that what holds
+on one trophic level hold also in multitrophic communities.
+Theoretical studies showed that food web properties, such as interaction
+distribution and strength, affect the distribution of biomass among adjacent
+trophic levels, [@thebault_relationship_2006; @schneider_animal_2016;
+@barbier_pyramids_2019]. A
+large body of theoretical studies links the propagation of perturbations to the
+foodweb structure [@may_will_1972; @angelis_stability_1975; @dunne_network_2006;
+@neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011],
+or trophic chain [@shanafelt_david_w._stability_nodate; @wang_biodiversity_2016;
+@barbier_pyramids_2019]. To date, we have few evidence on the relationship
+between network structure and total biomass and its temporal stability in
+empirical multitrophic communities.
 
@@
 
-Overall, the evidence suggests that both a higher horizontal and vertical
-diversity should lead to a greater total biomass and stability in communities.
-The effects of horizontal and vertical diversity are potentially conflicting and
-interacting, as they rely on inter-dependent mechanisms, in such a way that
-they need to be addressed jointly. Yet, there is no direct empirical evidence to
-date for an interaction between effects of horizontal and vertical diversity on
-total biomass and stability in natural communities.
+Overall, the evidence suggests that both species richness and network structure
+should modulate total biomass and stability of communities. The effects of
+species richness and network structure are potentially conflicting or
+synergistic in such a way that they need to be addressed jointly. Yet, there is
+no direct empirical evidence to date for the combined effects of species
+richness and network structure on total biomass and stability in natural
+communities.
 
@@
 
-The environment affects organism performance directly, and thereby, species
-abundances and total biomass [@grace_integrative_2016] and
-temporal stability [@de_boeck_patterns_2017; @hansen_climate_2013;
-@bluthgen_land_2016; @oliver_heterogeneous_2010; @friedpetersen_drivers_2020].
-For instance, the hydrology of streams determines the composition of fish
-communities, and is also related to fish population temporal stability
-[@franssen_annual_2011]. Ecosystem size can also increase habitat heterogeneity
-and so the number of different resource available, which in turn might increase
-resource complementary between species and increase total biomass
-[@post_ecosystem_2000; @doi_resource_2009]. Temperature has potentially
-conflicting effects on horizontal and vertical diversity, as higher temperature
-favour primary production and fluxes of biomass [@dossena_warming_2012;
-@ogorman_chapter_2012], thus potentially supporting more species and trophic
-levels [@arim_relationship_2007; @stegen_evolving_2012], but selects against
-larger body sized individuals [@dossena_warming_2012; @edeline_ecological_2013;
-@hattab_forecasting_2016], and thereby should reduce trophic diversity
-[@hattab_forecasting_2016]. It is thus unclear whether these temperature effects
-translate indirectly into changes in total standing biomass and stability in
-natural food webs. The relative strength of direct and indirect effects of
-environment on total biomass and its temporal stability remains an open
-question.
-
-#### Research questions
-
-Overall, the joint effects of horizontal and vertical diversity on total biomass
-and its temporal stability remains poorly documented, especially in natural
-communities. In this study, we identified (1) the effects of horizontal
-diversity and (2) vertical diversity on total biomass and temporal stability
-(Figure \@ref(fig:matmet) A).  Considering both direct & indirect effects, (3)
-we quantify if the magnitude of environmental effects on total biomass and its
-temporal stability and compare them to that of horizontal and vertical
-diversities.  (4) We identify the pathway for the effects of environment,
-horizontal and vertical diversities on total biomass and its temporal stability.
-(4a) Whether environmental effects operate mainly (i) directly, indirectly (ii)
-through horizontal diversity, (iii) through horizontal and vertical diversities
-or (iv) indirectly through vertical diversity only? (4b) Whether effects of
-horizontal diversity arise (i) directly, or (ii) indirectly through vertical
-diversity? Finally, (4c) whether environmental variables, horizontal and
-vertical diversities affect species synchrony and species variability ?
+When assessing the relationship between community structure and ecosystem
+properties in natural communities, it is crucial 
+to consider environmental factors [@loreau_biodiversity_2001;
+@he_global_2013; @grace_integrative_2016]. Environment affects organism
+performance directly, and thereby, species abundances, total biomass
+[@grace_integrative_2016] and temporal stability [@de_boeck_patterns_2017;
+@hansen_climate_2013; @bluthgen_land_2016; @oliver_heterogeneous_2010; @franssen_annual_2011;
+@friedpetersen_drivers_2020]. For example, greater ecosystem size might increase
+the number of available resources and thus total biomass [@post_ecosystem_2000;
+@doi_resource_2009]. @li_relationship_2018 have notably shown that climate
+moisture has a positive direct effect on total biomass, but also indirect
+through a positive effect on species richness. Taking in consideration
+environment also allow for an overall comparison of the strength of the
+the effects of environment and community structure on total biomass and its
+stability.
+
+#### Stream fish communities is a good model to study effects of horizontal & vertical diversity
+
+Stream fish community constitutes a good model to study the effects of
+network structure on total biomass and its temporal stability. Despite that
+fish trophic interactions are difficult to measure in nature, a consequent body
+of literature supports that they can be inferred through body size and diet
+informations [@gravel_inferring_2013; @jennings_weak_2001;
+@brose_predator_2019]. Especially in stream communities, including fishes,
+@brose_predator_2019 found that the prediction of predator prey trophic
+interactions based on body size ratio was far better in stream ecosystems than
+in other aquatic and te ecosystems. Furthermore, the biotic activity in stream
+ecosystems determines for a large part the water quality
+[@cummins_structure_1974] and thus are crucial to maintain stream ecosystem
+properties. Lastly, most of the diversity-biomass and diversity-stability
+relationships, have been assessed in terrestrial ecosystems
+while there is a evident need to test such relationships in a variety of
+ecosystem types.
 
 We used the ONEMA dataset consisting in standardized sampling of fish
-communities in french streams [@edeline_ecological_2013]. 99 sites were sampled for more
-than 10 years spanning on the 1995-2018 period. We inferred
-1496 interaction networks, based on body size and food diet.
-Horizontal diversity was quantified as species richness while vertical diversity
-was as connectance and average trophic level. Environment was characterized by
-the stream size, altitude, slope, and the temperature, flow and enrichment. Finally total
-biomass was measured as median total biomass over the sampling period while its
-temporal stability was quantified as the inverse of the CV.
-
-#### Stream fish communities is a good model to study effects of horizontal & vertical diversity
-
-Stream fish community constitutes a good model to study the joint effects of
-horizontal & vertical diversity on total biomass and its temporal stability.
-Despite that fish trophic interactions are difficult to assess in nature, a consequent
-body of literature supports that they can be inferred through body size and diet
-informations [@gravel_inferring_2013; @jennings_weak_2001;
-@brose_predator_2019]. Most of the biomass-diversity and stability-diversity
-relationships have been assessed in terrestrial ecosystems while there is a
-evident need to test such relationships in a variety of ecosystem types. Stream
-ecosystems are characterized by the flowing water and depends for a large part
-from the input of terrestrial ecosystems. Furthermore, the biotic activity in
-stream ecosystems determines for a large part the water quality
-[@cummins_structure_1974] and thus are crucial to maintain stream ecosystem
-properties.
-
-We show that TODO
+communities in French streams [@edeline_ecological_2013]. 99 sites were sampled
+for more than 10 years spanning on the 1995-2018 period. We inferred
+1496 interaction networks, based on body size and food diet.  The network
+structure was summarized by connectance and mean trophic level. Environment
+was characterized by the stream size, altitude, slope, and the temperature, flow
+and enrichment. Finally total biomass was measured as median total biomass over
+the sampling period while its temporal stability was quantified as the inverse
+of the CV.
+
+We found a positive relationship between total biomass and species richness and
+network structure  while total biomass and species richness had respectively a
+negative and positive effect on temporal stability. We also showed a link
+between species richness and network structure. We found that the environment had
+a strong effect on total biomass and its temporal stability in particular by 
+its effect on species richness and network structure. We then discuss the
+possible mechanisms at play to explain those results and their implications on
+our knowledge of the effect of network structure on ecosystem properties.
 
@@
 
-Fish communities were monitored across stream sections in France on the period 1995-2018
-by the French Office French Office of Water and Aquatic Ecosystems (ONEMA) using
-electric fishing, resulting in over XX individual fish sampled [see
-@edeline_ecological_2013]. Two different standardized protocols were used for little and
-big streams (detailed in Supplementary methods). For streams shallower than (XX
-m), the sampling takes place over the whole width of the streams and is done by
-foot whereas in streams deeper than (XX m), the sampling was done over the bank
-only and by foot or by boat. The sampling took place either in late spring and/or Autumn
-and temporal series were checked to reduce sampling heterogeneity within
-stations (detailed in Supplementary methods). Each station have been followed
-ten years or more. The temporal stability of biomass, computed as inverse of the
-CV, can cover very different dynamics such as decreasing, stable or increasing.
-However, the concept of community variability referred to variability around an
-equilibrium, which is rarely observed or difficult to characterize in natural
-communities. We finally kept only the 99 stations (Figure \@ref(fig:matmet) B)
-which had no trends in biomass (method detailed in Supplementary methods).
-However, the results were robust to the relaxation of this hypothesis
-(Supplementary results).
-
-##### Total biomass and its temporal stability
-
-To characterize communities variability, abundance or biomass are generally
-used. When the body size and therefore body mass vary by several orders of
-magnitude inside a community, one downside of using abundance is that we mix
-individuals that have potentially really different contributions in terms of ecosystem
-properties such as total biomass and biomass repartition. We estimated
-the body mass following an allometric law ($B_i = 0.01 \times
-l_i^{3.03}$, $B$ being the body mass in grams, $l$ the body size in millimeters
-and $i$ the individual) [@lleonart_removing_2000; @froese_cube_2006].
-
-The species and total biomass were then computed for each sampling event.
-As the sampling effort, reported as the surface sampled during the sampling event,
-varied across protocol type and sampling event, biomass was divided by the
-surface sampled (in $m^{2}$). So that, community and species biomass were expressed
-in $gm^{-2}$.
-
-In the analysis, the total biomass of a given station was characterized as the
-median of the total biomass over time. Temporal biomass stability was defined as
-the inverse of biomass variability. Variability was computed as Coefficient of
-Variation (CV) of the biomass over time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and
-$\mu_i$ being respectively the standard deviation and the temporal average of
-the biomass of the station $i$). Then, temporal stability was equal to $CV^{-1}
-= \mu \sigma^{-1}$.
-
-To characterize the mechanisms driving temporal stability of communities, we
-decomposed the community CV in synchrony and weighted average species CV
-components according to @thibaut_understanding_2013:
+Fish communities were monitored across stream sections in France on the period
+1995-2018 by the French Office of Water and Aquatic Ecosystems
+(ONEMA) using electric fishing. Two different standardized protocols were used
+for little and big streams (detailed in Supplementary methods). For streams
+shallower than (XX m), the sampling takes place over the whole width of the
+streams and is done by foot whereas in streams deeper than (XX m), the sampling
+was done over the bank by foot or by boat. The sampling season spans from 
+late spring to Autumn. During sampling, all the fishes caught were
+identified and counted. For each species, either the body size of all fish was
+measured, or a representative sample when the number of fish was high (See
+supplementary methods for details). The fishes were released at the end
+of the sampling. Additionally, the physical characteristics of the river was
+recorded during sampling as well as the sampling effort, quantified as the
+surface sampled.
+
+#### Data selection
+
+We kept only the most frequent sampling protocol in each station and kept
+stations that had been sampled ten years or more. The median sampling month was
+mid-August while the median of the standard deviation of the sampled month
+within station was $0.7$, i.e. there was low heterogeneity of the sampling month
+within stations. As the concept of community variability referred to variability
+around an equilibrium, which is rarely observed or difficult to characterize in
+natural communities, only those stations with no temporal trends in total
+biomass were selected (detailled in supplementary methods). However, the results
+were robust to the relaxation of this hypothesis (Supplementary results). We
+retained 99 stations distributed over seven hydrographic basins (Figure
+\@ref(fig:matmet) B).
+
+## Data preparation
+
+#### Biomass
+
+The body size of the unmeasured individuals was inferred under the assumption
+that species body size followed a normal distribution whose the mean and the
+standard deviation was quantified from the measured individuals of the sampling
+(See supplementary methods). The body mass of each individual was then estimated
+using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$ being the body mass
+in grams, $l$ the body size in millimeters and $i$ the individual), where the
+coefficients $0.01$ and $3.03$ comes from meta-analysis
+[@lleonart_removing_2000; @froese_cube_2006]. The species biomass
+and total biomass at each sampling was then calculated by summing individual
+body masses. To account for the sampling effort, species biomass and total
+biomass have been related to the surface sampled, i.e. $gm^{-2}$.
+In the further analysis, the total biomass of a station has been defined as the
+median of the total biomass over time.
+
+Temporal biomass stability was defined as the inverse of biomass variability.
+Variability was computed as Coefficient of Variation (CV) of the biomass over
+time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being
+respectively the standard deviation and the temporal average of the biomass of
+the station $i$). Then, temporal stability was equal to $CV^{-1} = \mu
+\sigma^{-1}$.
+
+In order to describe the mechanisms driving temporal stability of biomass, we
+decomposed the $CV$ of total biomass ($CV_{com}$) in synchrony ($\phi$) and
+weighted average species $CV$ (\overline{CV_{sp}}) components according to
+@thibaut_understanding_2013:
 
@@
 
-with $CV_{com, i}$ being the Coefficient of Variation of the community in the
+with $CV_{com, i}$ being the Coefficient of Variation of the biomass in the
 station $i$, $\overline{CV_{sp, i}}$ the average coefficient of variation of
-population in the station $i$ pondered by the biomass of each population.
+species in the station $i$ weighted by the biomass of the species, $B_{k,i}$.
 Synchrony of the station $i$, $\phi_i$, is the ratio between the variance of
-total biomass over time ($\sigma^2_{x_T}$) and the sum of the variance of
+total biomass over time ($\sigma^2_{x_{T,i}}$) and the sum of the variance of
 population biomass over time ($\sigma_{x_k}$) [@loreau_species_2008]. $i$ being
@@
 $$
-\overline{CV_{sp, i}} = \sum_k{\frac{B_k {CV}_i}{\sum_k{B_k}}}
+\overline{CV_{sp, i}} = \sum_k{\frac{B_{k,i} {CV}_{k, i}}{\sum_k{B_{k,i}}}}
 $$
@@
 $$
-\phi_i = \frac{\sigma^2_{x_T}}{(\sum_k{\sqrt{\sigma^2_{x_k}}})^2}
+\phi_i = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sqrt{\sigma^2_{x_{k,i}}}})^2}
 $$
 
-## Horizontal & vertical diversity
-
-### Horizontal diversity
-
 ####  Species richness
 
-Species richness was computed as the total number of species present over time in a given
-station. As for biomass, we controlled species richness for sampling effort by
-dividing the total number of species by the total surface sampled in the given
-station. Species richness was then expressed in number of species by square meter sampled.
-
-### Vertical diversity
+Species richness was computed as the total number of species present over time
+in a given station. As for biomass, we controlled species richness for sampling
+effort by dividing the total number of species by the total surface sampled in
+the given station. Species richness was then expressed in number of species by
+square meter sampled.
+
+### Network structure
 
@@
 
-Trophic interaction network was inferred from body size and ontogenic diet.
+Trophic interaction network was inferred from body size and ontogenic diet shift.
 Body size is a reasonable approximation widely used to infer trophic
@@
 algae or fishes. Accordingly, each fish species was divided in nine body size
-classes. Each body size class constituting a trophic species. A high congruence
-has been found at trophic species scale between inferred interactions and
-measured trophic interactions, but not at the species
-scale [@jennings_weak_2001]. We then inferred trophic interactions between the trophic species (Figure
-\@ref(fig:matmet) C).  We determined network structure in two steps: (1) build a
-metaweb describing the trophic interactions between all trophic
-species (Figure \@ref(fig:matmet) C), then (2) determine network of a given
-community by subtracting the metaweb according to the trophic species present in
-a given community (Figure \@ref(fig:matmet) D). We added to each network seven
-resource nodes present in food diet database: detritus, biofilm, phytoplankton,
-zooplankton, macrophages, phytobenthos and zoobenthos (grey nodes in Figure
-\@ref(fig:matmet) C & D). The trophic network inference procedure is detailed in
-supplementary informations.
-
-#### Trophic network structure
-
-For each trophic network, corresponding to a particular community at a given
-time and location, we computed two of the most communly used network metrics to
-characterize network structure, namely the connectance and average trophic
-level. Connectance describes the number of interactions compared to the number
-of possible links, computed as ($C = L / N^2$, L and N being resp. the number of
-links and of trophic species plus resource nodes). The average trophic level was
-computed as the mean trophic level of the nodes that the predator nodes consumes
+classes, each of which is trophic species (Figure SXX). A high congruence
+between inferred interactions and measured trophic interactions has been found
+at trophic species scale but not at the species scale [@jennings_weak_2001].
+Additionally to the fish trophic species, we added seven resource nodes present
+in ontogenic food diet database: detritus, biofilm, phytoplankton, zooplankton,
+macrophages, phytobenthos and zoobenthos (grey nodes in Figure \@ref(fig:matmet)
+C & D). The ontogenic diet database was based on informations from fishbase and
+literature. Each fish species had two or three life stages which are delimited by
+body size (Table SXX, Figure SXX).
+
+The trophic interactions of fish trophic species was determining with the median
+of its body size range, hereafter after midpoint. The midpoint of trophic
+species fall into one of the species life stage and a trophic link was set
+between the trophic species and the resources present in the life stage. If the
+trophic species is in a piscivorous life stage, the fish-fish trophic links was
+defined in two steps and based on the body size ratio between predators and
+prey. First of all, we defined the range predation window from 3% to 45% of the
+midpoint of the trophic species. Then, a trophic link was set between the
+piscivorous trophic species and every trophic species whose midpoint was
+included in the predation range (Figure SXX). Lastly, the trophic links between resources was
+set according to the food diet data.
+
+We determined the network structure in two steps: (1) build a metaweb describing the
+trophic interactions between all trophic species and the resources (Figure
+\@ref(fig:matmet) C), then (2) determine network of a given community by
+subtracting the metaweb according to the trophic species present in a given
+site and sampling event (Figure \@ref(fig:matmet) D).
+
+For each trophic network, corresponding to a particular site and sampling, we
+computed two of the most commonly used network metrics to characterize the food
+web, namely the connectance and mean trophic level. Connectance describes 
+the level of generalism in the network and is calculated as the number of actual
+interaction divided by the maximum number of interaction if all species interact
+together ($C = L / N^2$, L and N being resp. the number of
+links and of trophic species plus resource nodes). The trophic level of the
+nodes was computed of the nodes that the predator nodes consumes
 to which is added one, obtained recursively by setting the trophic level of
-basal nodes to 1, and was further weighted by the biomass of each trophic
-species (excluding resource nodes for which we had no biomass information)
-($\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, $T_i$ and $B_i$
-being resp. the trophic level and the biomass of the node $i$). In resume, we
-infered trophic networks at the scale of trophic species (i.e. nodes being body
-size classes) to take in account ontogenic diet shifts and that fish-fish
-trophic interaction depends on body size ratio between prey and predator. On the
-other side, the community metrics were defined at the species level, (i.e.
-species richness, average species CV and synchrony).
+basal nodes to 1. The mean trophic level $\overline{T}$ was computed as the mean trophic level
+weighted by the biomass of each trophic species (excluding resource nodes for
+which we had no biomass information), so
+$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and $B_i$
+being resp. the trophic level and the biomass of the node $i$.
 
@@
 
-Habitat description, obtained from fish sampling data, describing the ecosystem
-size namely the stream width, depth and position (altitude and
-slope). Physico-chemical variables were obtained from
-naiades web portal [http://www.naiades.eaufrance.fr/](http://www.naiades.eaufrance.fr/).
-We chose flow and temperature to describe streams as flow
-impose swimming constraints which filters fish species that can establish
-[@rolls_scaling_2018; @tonkin_flow_2018; @gutierrez-canovas_contrasting_2013].
-Water temperature is linked to physiological constraints namely thermal
-tolerance and oxygen concentration tolerance [REF] since the level of water
-saturation in oxygen is inversely linked to water temperature. We took 
-Biochemical Oxygen Demand (BOD) for a proxy of enrichment in the ecosystem [REF].
-BOD is also inversely linked to oxygen concentration in water and so, BOD is
-also linked to physiological stress of fishes. As physico-chemical variables
-were not recorded at the same place than fish communities, they were
-interpolated with spatial stream networks [@isaak_applications_2014;
-@hoef_ssn:_2014]. The interpolation procedure is detailed in supplementary
-methods.
-
-For each fish station, environmental variables were matched with the year of
-fish sampling (except for water temperature for which the record began in 2006).
-Then, the average temperature, flow, BOD, river width and depth were computed as
-well as coefficient of variation ($CV = \sigma \mu^{-1}$). As habitat and
-environmental variables are often collinear, a principal component analysis (PCA)
-was performed on the scaled variables. We kept in the analysis the two first
+we characterised the sampled sites by their altitude, slope, distance from
+source, stream width and depth and its strahler order, i.e. its position in the
+stream network. From the naiades database
+[http://www.naiades.eaufrance.fr/](http://www.naiades.eaufrance.fr/), we also
+got data on water temperature and flow as they affect the type of fish that can
+establish [@franssen_annual_2011; @rolls_scaling_2018; @tonkin_flow_2018;
+@gutierrez-canovas_contrasting_2013] as well as BOD (Biological Oxygen Demand)
+as a proxy for eutrophisation. As data from the naide database are not collected
+on same site as our fish sampling sites, we performed an interpolation with
+spatial stream networks [@isaak_applications_2014; @hoef_ssn:_2014]. The
+interpolation procedure is detailed in supplementary methods.
+
+We had one environmental variable value for each site and sampling event, except
+for water temperature for which the record began in 2006. Then, we computed the average over
+time and the CV over time for water temperature, flow, BOD, river width and
+depth. As habitat and environmental variables are often collinear, a principal
+component analysis (PCA)
+was performed on the 14 scaled variables. We kept in the analysis the two first
 principal components based on eigen values distribution (Fig. SXX).
-The PCA explained `r tot_var_expl_pca`%
-of the variance. An varimax axis rotation was performed to maximize the representation
-of the variables by the principal components (Fig. \@ref(fig:pca-rotated)).
+The two first principal components explained `r tot_var_expl_pca`%
+of the variance. A varimax axis rotation was performed to maximize the representation
+of the variables by the principal components (Figure SXX).
 The two first principal components were used in the analysis, representing respectively
 the (1) river size (river width & depth), (2) altitude, slope and decreasing
-average temperature. Further informations about data transformation and
-filtering are detailed in supplementary information.
+average temperature. Further description of the variables are detailed in
+supplementary information.
 
@@
 
-Structural Equation Modeling are able to assess multivariate relationships,
-directs and indirects between variables. It is one promising way to go beyond
-bivariate relationships and to investigate complex relationships, direct and
+Structural Equation Modeling are able to assess multivariate relationships
+between variables. It is one promising way to go beyond bivariate relationships
+and to investigate complex relationships, direct and
 indirect, between variables [@grace_structural_2008; @grace_causal_2014;
-@lefcheck_piecewisesem_2016; @grace_integrative_2016]. SEM makes possible to set
-causal relationships between variables. This step can be critical, as the
-estimated parameters can be determined by both the choice of the variables and
-the links between them. Therefore, the set of variables and links should be
-supported by theory and literature. We built a metamodel which present the set
-of variables and the links between them (Figure \@ref(fig:matmet) A,
-\@ref(fig:sem-plot) A & B). Basically, we tested the links between environmental
-conditions, horizontal & vertical diversity and both total biomass and its
-temporal stability (Figure \@ref(fig:matmet) A). We considered that environment
-can directly affect horizontal and vertical diversity, as well as total biomass
-and its temporal stability. Horizontal diversity, measured as species richness
-directly affects vertical diversity, total biomass and its temporal stability.
-Food web structure was shown to be constrained by species richness. In turn,
-vertical diversity affects total biomass and its temporal stability (Figure
-\@ref(fig:matmet) A). The metamodel describes how variables are interrelated
-(Figure \@ref(fig:matmet) A). We built separated structural equation model for
-total biomass and its temporal variability (Figure \@ref(fig:sem-plot) A & B).
+@lefcheck_piecewisesem_2016; @grace_integrative_2016]. We built the biomass
+model (Figure \@ref(fig:matmet) A, \@ref(fig:sem-plot) B) by considering that environment
+can directly affect species richness and network structure, as well as total
+biomass. Species richness directly affects total biomass. Food web structure
+was shown to be constrained by species richness @winemiller_must_1989;
+@dunne_network_2006; @thebault_stability_2010. In turn,
+the network structure affects total biomass (Figure
+\@ref(fig:matmet) A, \@ref(fig:sem-plot) B). We used the same model structure for
+temporal variability (Figure \@ref(fig:sem-plot) A). The structural equation
+models used for total biomass and its temporal stability contains respectively 4
+and 6 response variables, 35 and 26 direct paths.
 
@@
 were logged to fulfill model assumptions (see residual plots and data
-transformation in supplementary informations). To account for heterogeneity of
-hydrographic basin, we set it as random effect on the intercept. Moreover, each
-statistical model was checked for the presence of multicollinearity
-(Supplementary information). The slopes reported in the main
-text are standardized in order to compare their magnitude ($r_\delta = \beta
-\frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope, $\sigma_x$
-and $\sigma_y$ being respectively the standard deviation of the predictive
-variable $x$ and of the response variable $y$). In the main text, only the
-slopes which had $P$ value inferior to $0.05$ were reported (but see Table SXX).
-The structural equation models used for total biomass and its temporal stability
-contains respectively 4 and 6 response variables, 35 and 26 direct paths.
+transformation in supplementary informations, Table SXX). To account for the heterogeneity
+between the seven hydrographic basins, we set it as random effect on the
+intercept of the linear model. The absence of multicollinearity 
+was checked with Variance Inflation Factor (VIF, Table SXX). The slopes reported
+in the main text were standardized in order to compare their magnitude ($r_\delta
+= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
+$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
+predictive variable $x$ and of the response variable $y$). In the main text,
+only the slopes which had a $P$ value inferior to $0.05$ were reported (but see
+Table SXX and SXX).
+
 The indirect effects of variables on total biomass and its temporal stability
 was computed by multiplying slopes along the path. As an example, if we consider
-$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times r_{BC}$.
-Only significant direct slopes were entered in the calculation of
-indirect effects. Finally total effects were computed as the sum of direct and
-indirect effects.
+$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times
+r_{BC}$.  Only significant direct slopes were entered in the calculation of
+indirect effects. Finally total effects were computed as the sum
+of direct and indirect effects.
 
@@
 of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
-.45$, $.47$, $.49$ and $.38$) but not of average trophic level ($R^2 =
+.45$, $.47$, $.49$ and $.38$) but not of mean trophic level ($R^2 =
 .18$, Figure \@ref(fig:sem-plot) C and D).
 
-## Horizontal diversity increased total biomass but decreased its temporal stability
+## Total biomass
 
@@
 
-Species richness had a significant positive direct effect on total biomass
-$r_\delta = `r rich_on_bm$direct`$ (Figure \@ref(fig:sem-plot) D, Table
-\@ref(tab:indir-bm)). However, species richness had a negative total effect
-on biomass stability ($r_\delta = `r rich_on_stab$total`$, Table
-\@ref(tab:indir-stab)). On the one hand, species richness had a direct negative effect on synchrony
-($r_\delta = `r rich_on_sync$direct`$), thereby increasing stability ($r_\delta
-= `r rich_on_stab$via_sync`$). On the other hand, species richness had a
-positive direct effect on $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$),
-thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
-\@ref(tab:indir-stab)). Finally, it was surprising that the negative
-effect of $\overline{CV_{sp}}$ on temporal stability was twice higher than the
-negative effect of synchrony (resp. $r_\delta = `r cv_sp_on_stab`$ and $r_\delta
-= `r sync_on_stab`$, Figure \@ref(fig:sem-plot) C).
-
-## Vertical diversity increased total biomass and its temporal stability
-
-Average trophic level had a direct positive effect on total biomass ($r_\delta
-= `r tlvl_on_bm`$) but connectance had no direct nor indirect significant effect (Figure
-\@ref(fig:sem-plot) D) on total biomass. However, the average trophic level had
-a direct negative effect on $\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
-Figure \@ref(fig:sem-plot) C) and thereby had a total positive
-effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
-Table \@ref(tab:indir-stab)). The average trophic level had no significant
-effect on synchrony and connectance had no significant direct, nor indirect
-effect on temporal stability (Figure \@ref(fig:sem-plot) C, Table SXX).
-
-## Horizontal and vertical diversity had opposite and independant effect on total biomass and its temporal stability
-
-We described above that species richess had respectively a positive and a negative 
-on total biomass and its temporal stability whereas average trophic level had a
-positive effect on both (Table \@ref(tab:indir-bm) and \@ref(tab:indir-stab)).
-The total effect of average trophic level on total biomass was of the same
-magnitude than the one of species richness (resp. $`r tlvl_on_bm`$ and
-$`r rich_on_bm$total`$, Table
-\@ref(tab:indir-bm)). It was also true for temporal stability (resp.
-$`r com_on_stab$total["t_lvl"]`$ and
-$`r rich_on_stab$total`$, Table \@ref(tab:indir-stab)). Average trophic level was
-dependent of species richness because species richness had a significant
-negative effect on average trophic level ($r_\delta = `r rich_on_tlvl`$). 
-Species richness had also a strong negative effect on connectance ($r_\delta =
-`r rich_on_stab$total`$, Figure \@ref(fig:sem-plot) C and D).  But, in turn,
-connectance had no significant effect on either total biomass nor
-its temporal stability.
-
-## Environment had an high effect on total biomass and its temporal stability
+Species richness and mean trophic level had a significant positive direct effect on total biomass
+($r_\delta = `r rich_on_bm$direct`$ and $r_\delta = `r tlvl_on_bm`$ resp., Figure
+\@ref(fig:sem-plot) D, Table \@ref(tab:indir-bm)), while connectance had no
+direct nor indirect significant effect (Figure \@ref(fig:sem-plot) D) on total
+biomass. The total effect of mean trophic level on total biomass was of the same
+magnitude than the one of species richness (resp. $`r tlvl_on_bm`$ and $`r
+rich_on_bm$total`$, Table \@ref(tab:indir-bm)).
+
+Species richness had a significant negative effect on mean trophic level
+($r_\delta = `r rich_on_tlvl`$) and a strong negative effect on connectance
+($r_\delta = `r rich_on_stab$total`$, Figure \@ref(fig:sem-plot) C and D). But,
+in turn, connectance had no significant effect on total biomass.
 
@@
 biomass ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-bm)),
-equally through species richness and average trophic level 
-($r_\delta = `r env_on_bm$via_richness["log_RC1"]`$ and
-$`r env_on_bm$via_com["log_RC1"]`$ resp., Table \@ref(tab:indir-bm)). Average
-temperature and altitude effects on total biomass were of the same magnitude
-than the effects on species richness and average trophic level.
+equally through species richness and mean trophic level ($r_\delta = `r
+env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
+resp., Table \@ref(tab:indir-bm)). Average temperature and altitude effects on
+total biomass were of the same magnitude than the effects on species richness
+and mean trophic level.
+
+## Temporal stability of biomass
+
+By its effect on synchrony and $\overline{CV_{sp}}$, species richness had a
+negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
+Table \@ref(tab:indir-stab)). On the one hand, species richness had a direct
+negative effect on synchrony ($r_\delta = `r rich_on_sync$direct`$), thereby
+increasing stability ($r_\delta = `r rich_on_stab$via_sync`$). On the other
+hand, species richness had a
+positive direct effect on $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$),
+thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
+\@ref(tab:indir-stab)). Finally, it was surprising that the negative
+effect of $\overline{CV_{sp}}$ on temporal stability was twice higher than the
+negative effect of synchrony (resp. $r_\delta = `r cv_sp_on_stab`$ and $r_\delta
+= `r sync_on_stab`$, Figure \@ref(fig:sem-plot) C).
+
+The mean trophic level had a direct negative effect on
+$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
+Figure \@ref(fig:sem-plot) C) and thereby had a total positive
+effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
+Table \@ref(tab:indir-stab)). The mean trophic level had no significant
+effect on synchrony and connectance had no significant direct, nor indirect
+effect on temporal stability (Figure \@ref(fig:sem-plot) C, Table SXX).
+The total effect of mean trophic level on temporal stability of biomass was of
+the same magnitude than the one of species richness (resp.
+$`r com_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
+\@ref(tab:indir-stab)).
 
@@
 effect on temporal stability through species richness but a positive one through
-average trophic level 
+mean trophic level 
 (resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
@@
 effect of average temperature on temporal stability was of higher magnitude than
-the effects of species richness and average trophic level (Table
+the effects of species richness and mean trophic level (Table
 \@ref(tab:indir-stab)).
@@
 
-Our aim was to clarify respective importance and nature of direct and indirect
-effects of environmental drivers, horizontal and vertical diversity, captured by
-species richness and trophic network structure (connectance and average trophic
-level), on total biomass and its temporal stability in aquatic foodwebs. To do
+Our aim was to evaluate the effects of the network structure on the total
+biomass and its temporal stability in natural communities, which have been
+poorly documented. To do
 this we quantified interactive effects of habitat properties, species richness,
-and trophic structure, on the biomass and stability of fish communities, from
+and food web structure, on the biomass and stability of fish communities, from
 the ONEMA fish dataset, containing over X million individual fish samples,
-across 99 locations France spanning the period 1995 to 2018. We infered trophic
+across 99 locations France spanning the period 1995 to 2018.
+We infered trophic
 interactions networks based on body size-dependency in food diet from the
-literature and prey/predator body size ratio for piscivory. We used SEM to
+literature and prey/predator body size ratio for piscivory^[ 
+We inferred trophic networks at the scale of trophic species (i.e. nodes being
+body size classes) to take in account ontogenic diet shifts and that fish-fish
+trophic interaction depends on body size ratio between prey and predator. On the
+other side, the community metrics were defined at the species level, (i.e.
+species richness, average species CV and synchrony).
+].
+We used SEM to
 disantangle direct and indirect effects of environmental drivers, horizontal and
 vertical diversity on both total biomass and biomass stability. We found that
-species richness and average trophic level had a positive effect on total
+species richness and mean trophic level had a positive effect on total
 biomass. In contrast, species richness had a negative effect on temporal
-stability whereas average trophic level covaried positively.  Futhermore, we
-found that the effect of species richness and average trophic level on total
+stability whereas mean trophic level covaried positively.  Futhermore, we
+found that the effect of species richness and mean trophic level on total
 biomass and its temporal stability were not independant as species richness had
-a positive effect on average trophic level.  Finally, we found that the
+a positive effect on mean trophic level.  Finally, we found that the
 magnitude of the effects of average temperature and altitude was equal or
-superior to the effects of species richness and average trophic level. Overall,
+superior to the effects of species richness and mean trophic level. Overall,
 our study is unique by its level of integration, from environmental effects to
-total biomass and stability, going through horizontal and vertical diversity,
-and the fist direct assessment of a possible interaction between effects of
-horizontal and vertical diversity.
-
-## Horizontal diversity increased total biomass but decreased its temporal stability
+total biomass and stability, going through species richness and network
+structure, and the first direct assessment of a possible joint effect of
+species richness and network structure.
+
+## Species richness increased total biomass but decreased its temporal stability
+
+#### Species and total biomass
 
@@
 [@declerck_species_2006] in natural forests. Further investigations are needed
-to identify the mechanisms behind those contrasting patterns.
-
-Species richness decreased synchrony and increased $\overline{CV_{sp}}$. Species
-richness can reduce synchrony through decrease of population size, thus raising
-the role of demographic stochasticity [@loreau_species_2008] but also in the
-case where species have different responses to environmental variation
-[@loreau_species_2008]. While the effect of species richness on synchrony is
-well understood, its effect on $\overline{CV_{sp}}$ is more complex [see
-@thibaut_understanding_2013]. However a negative effect of species richness of
+to identify the mechanisms behind those contrasting patterns. A first step is to
+look at the effects of species richness on synchrony and $\overline{CV_{sp}}$,
+which constitute the two components of temporal stability quantified as CV
+[@loreau_species_2008; @thibaut_understanding_2013].
+
+The negative effect of species richness on synchrony, thereby increasing
+stability, was expected. Whereas the positive effect of species richness on
+$\overline{CV_{sp}}$, thereby decreasing stability, was more intriguing. Species
+richness can reduce synchrony through decrease of population size, thus
+raising the role of demographic stochasticity [@loreau_species_2008] but also in
+the case where species have different responses to environmental variation
+[@loreau_species_2008]. Two empirical studies found ... that mechanisms behind
+synchrony was ...
+
+However a negative effect of species richness on
 both population ($\overline{CV_{sp}}$) and community stability can arise the
@@
 
-The average trophic level was positively linked to total biomass. This result is
+The mean trophic level was positively linked to total biomass. This result is
 straightforward. As feeding interactions were partly determined by body size and
@@
 
-Average trophic level had a positive effect on biomass stability by its negative
+mean trophic level had a positive effect on biomass stability by its negative
 effect on CVsp (i.e. positive effect on average species stability). It means
@@
 biomass and its temporal stability. On the other side, we found species richness
-was negatively related to average trophic level and average trophic level
+was negatively related to mean trophic level and mean trophic level
 covariated positively with total biomass and its temporal stability. Hence,
@@
 size had a positive effect on total biomass through
-a positive effect on average trophic level, consistent with the fact that food
+a positive effect on mean trophic level, consistent with the fact that food
 webs in wider streams, with a greater amount of running waters, are also larger,
@@
 horizontal diversity. The first pathway consists in a positive effect of
-temperature and stream properties on average trophic level, in line with the idea
+temperature and stream properties on mean trophic level, in line with the idea
 that wider streams and warmer conditions are favourable to mesotrophic predators

### 2020-07-07 manuscript/bef_stability/manuscript.Rmd
Update biomass discussion

@@
 @neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011],
-or trophic chain [@shanafelt_david_w._stability_nodate; @wang_biodiversity_2016;
+or trophic chain [@shanafelt_stability_nodate; @wang_biodiversity_2016;
 @barbier_pyramids_2019]. To date, we have few evidence on the relationship
@@
 decomposed the $CV$ of total biomass ($CV_{com}$) in synchrony ($\phi$) and
-weighted average species $CV$ (\overline{CV_{sp}}) components according to
+weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
 @thibaut_understanding_2013:
@@
 biomass ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-bm)),
-equally through species richness and mean trophic level ($r_\delta = `r
-env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
+equally through species richness and mean trophic level ($r_\delta = 
+`r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
 resp., Table \@ref(tab:indir-bm)). Average temperature and altitude effects on
@@
 Average temperature and altitude had a negative and a positive effect on
-temporal stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-stab)) mainly
-through a direct positive effect on $\overline{CV_{sp}}$
+temporal stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table
+\@ref(tab:indir-stab)) mainly through a direct positive effect on
+$\overline{CV_{sp}}$
 ($r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-stab)).
@@
 
----
-# Chapeau
----
-
 #### Hat
@@
 biomass and its temporal stability in natural communities, which have been
-poorly documented. To do
-this we quantified interactive effects of habitat properties, species richness,
-and food web structure, on the biomass and stability of fish communities, from
-the ONEMA fish dataset, containing over X million individual fish samples,
-across 99 locations France spanning the period 1995 to 2018.
-We infered trophic
-interactions networks based on body size-dependency in food diet from the
-literature and prey/predator body size ratio for piscivory^[ 
-We inferred trophic networks at the scale of trophic species (i.e. nodes being
-body size classes) to take in account ontogenic diet shifts and that fish-fish
-trophic interaction depends on body size ratio between prey and predator. On the
-other side, the community metrics were defined at the species level, (i.e.
-species richness, average species CV and synchrony).
-].
-We used SEM to
-disantangle direct and indirect effects of environmental drivers, horizontal and
-vertical diversity on both total biomass and biomass stability. We found that
-species richness and mean trophic level had a positive effect on total
-biomass. In contrast, species richness had a negative effect on temporal
-stability whereas mean trophic level covaried positively.  Futhermore, we
-found that the effect of species richness and mean trophic level on total
-biomass and its temporal stability were not independant as species richness had
-a positive effect on mean trophic level.  Finally, we found that the
-magnitude of the effects of average temperature and altitude was equal or
-superior to the effects of species richness and mean trophic level. Overall,
-our study is unique by its level of integration, from environmental effects to
-total biomass and stability, going through species richness and network
-structure, and the first direct assessment of a possible joint effect of
-species richness and network structure.
+poorly documented. To do so, we quantified the effects, directs and indirects,
+of habitat properties, species richness, and food web structure, on the biomass
+and stability of fish communities, from the ONEMA fish dataset, containing over
+X million individual fish samples, across 99 locations France spanning the
+period 1995 to 2018.  We infered trophic interactions networks based on body
+size-dependency in food diet from the literature and prey/predator body size
+ratio for piscivory^[ We inferred trophic networks at the scale of trophic
+species (i.e. nodes being body size classes) to take in account ontogenic diet
+shifts and that fish-fish trophic interaction depends on body size ratio between
+prey and predator. On the other side, the community metrics were defined at the
+species level, (i.e.  species richness, average species CV and synchrony).  ].
+We built structural equation models to disantangle the direct and indirect
+effects of environmental drivers, species richness and network structure on both
+total biomass and biomass stability.  We found that species richness and mean
+trophic level had a positive effect on total biomass. In contrast, species
+richness had a negative effect on temporal stability whereas mean trophic level
+covaried positively.  Futhermore, we found that the effect of species richness
+and mean trophic level on total biomass and its temporal stability were not
+independant as species richness had a positive effect on mean trophic level.
+Finally, we found that the magnitude of the effects of average temperature and
+altitude was equal or superior to the effects of species richness and mean
+trophic level. Overall, our study is unique by its level of integration, from
+environmental effects to total biomass and stability, going through species
+richness and network structure, and the first direct assessment of a possible
+joint effect of species richness and network structure.
 
@@
 We found that species richness increased total biomass as found in salt marshes,
-grasslands and
-forests [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
-@li_relationship_2018]. The positive effect of species richness on total biomass
-might be due to resource use complementarity, which is held by niche
-differentiation and interspecific facilitation [@loreau_biodiversity_1998;
-@loreau_partitioning_2001; @cardinale_species_2002] or might be due to positive
-select effect which takes place through the dominance of the
-most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
-Previous research seems to indicate that resource complementarity might be the
-main driver in fish communities [@carey_determining_2011].
+grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
+@wu_relationship_2015; @li_relationship_2018]. The positive effect of species
+richness on total biomass might be due to resource use complementarity, which is
+held by niche differentiation and interspecific facilitation
+[@loreau_biodiversity_1998; @loreau_partitioning_2001; @cardinale_species_2002]
+or might be due to positive select effect which takes place through the
+dominance of the most productive species [@tilman_plant_1997;
+@loreau_partitioning_2001]. Previous research seems to indicate that resource
+complementarity might be the main driver in fish communities
+[@carey_determining_2011] but futher invesgations are needed to assess the
+dominance of this mecanism in aquatic communities and more generally in food
+webs.
 
@@
 [@declerck_species_2006] in natural forests. Further investigations are needed
-to identify the mechanisms behind those contrasting patterns. A first step is to
-look at the effects of species richness on synchrony and $\overline{CV_{sp}}$,
-which constitute the two components of temporal stability quantified as CV
-[@loreau_species_2008; @thibaut_understanding_2013].
-
-The negative effect of species richness on synchrony, thereby increasing
-stability, was expected. Whereas the positive effect of species richness on
-$\overline{CV_{sp}}$, thereby decreasing stability, was more intriguing. Species
-richness can reduce synchrony through decrease of population size, thus
-raising the role of demographic stochasticity [@loreau_species_2008] but also in
-the case where species have different responses to environmental variation
-[@loreau_species_2008]. Two empirical studies found ... that mechanisms behind
-synchrony was ...
-
-However a negative effect of species richness on
-both population ($\overline{CV_{sp}}$) and community stability can arise the
-biomass distribution across population is strongly uneven and that the biomass
-variance of population increases much faster than its mean
-[@thibaut_understanding_2013].
+to identify the mechanisms behind those contrasting patterns. A first step is 
+be to look at the effects of species richness on synchrony and
+$\overline{CV_{sp}}$, which constitute the two components of temporal stability
+quantified as CV [@loreau_species_2008; @thibaut_understanding_2013].
+
+We found that species richness decreases synchrony, thereby increasing
+stability. Species richness can reduce synchrony through decrease of population
+size, thus raising the role of demographic stochasticity [@loreau_species_2008]
+but also in the case where species have different responses to environmental
+variation [@loreau_species_2008]. While
+a negative effect of species richness on synchrony is generally found in
+experimental grasslands [@isbell_biodiversity_2009; @roscher_identifying_2011],
+no relation has been found in natural forests [@declerck_species_2006], but
+negative relationships have been found in natural communities of birds, bats,
+grasslands, bats and butterflies [@bluthgen_land_2016;
+@olivier_independent_nodate]. Our study thus highlights that species richness
+might also decrease synchrony in empirical trophic communities.
+
+Whereas the positive effect of species richness on $\overline{CV_{sp}}$, thereby
+decreasing stability, was more intriguing. Indeed, precedent studies found that
+constrasting results. For example, @olivier_independent_nodate reported negative, neutral and
+positive effect of species richness on $\overline{CV_{sp}}$ in respectively
+butterfly, bat and birds communities. @thibaut_understanding_2013 proposed that
+two ingredients can generate a positive effect of species richness on
+population ($\overline{CV_{sp}}$) stability: a strongly uneven biomass
+distribution across populationand that the biomass variance
+of population increases much faster than its mean.
 
@@
 more in the form of competitive exploitation.
-
-- But @thebault_relationship_2006 with the same mecanisms on vertical and
-  horizontal diversity
 
@@
 that species at higher trophic level are more stable than the species at lower
-trophic levels. @shanafelt_david_w._stability_nodate and @barbier_pyramids_2019
+trophic levels. @shanafelt_stability_nodate and @barbier_pyramids_2019
 found the same pattern with pure trophic chain models. They have shown that
@@
 diversity.
+
+In
+trophic communities,  additionnaly to the **portefolio effect**, the importance
+of trophic interactions on synchrony (mal dit).
 

### 2020-07-13 manuscript/bef_stability/manuscript.Rmd
Review discussion

@@
 and stability of fish communities, from the ONEMA fish dataset, containing over
-X million individual fish samples, across 99 locations France spanning the
-period 1995 to 2018.  We infered trophic interactions networks based on body
-size-dependency in food diet from the literature and prey/predator body size
+X million individual fish samples, across 99 locations in France from 1995 to
+2018. We infered trophic interactions networks based on body size-dependency in
+   food diet from the literature and prey/predator body size
 ratio for piscivory^[ We inferred trophic networks at the scale of trophic
@@
 [@loreau_biodiversity_1998; @loreau_partitioning_2001; @cardinale_species_2002]
-or might be due to positive select effect which takes place through the
-dominance of the most productive species [@tilman_plant_1997;
-@loreau_partitioning_2001]. Previous research seems to indicate that resource
-complementarity might be the main driver in fish communities
-[@carey_determining_2011] but futher invesgations are needed to assess the
-dominance of this mecanism in aquatic communities and more generally in food
-webs.
+or might be due to a positive selection effect [@tilman_plant_1997;
+@loreau_partitioning_2001], which leads to the dominance of the most productive
+species. Previous research seems to indicate that resource complementarity might
+be the main driver in fish communities [@carey_determining_2011].
 
 Surprisingly found a negative relationship between temporal stability and
-species richness. Overall, it contrasts with experimental studies in
-grasslands [@tilman_biodiversity_2006]; mesocosms [@pennekamp_biodiversity_2018]
-and even in natural communities [@olivier_independent_nodate] where positive
-relationships are typically found between temporal stability and species
-richness. In streams as well, @franssen_annual_2011 found that species richness
-increased temporal stability. However other studies found a opposite relationship
-in natural grassland [@yang_effects_2011] or a marginal one
-[@declerck_species_2006] in natural forests. Further investigations are needed
-to identify the mechanisms behind those contrasting patterns. A first step is 
-be to look at the effects of species richness on synchrony and
-$\overline{CV_{sp}}$, which constitute the two components of temporal stability
-quantified as CV [@loreau_species_2008; @thibaut_understanding_2013].
-
-We found that species richness decreases synchrony, thereby increasing
-stability. Species richness can reduce synchrony through decrease of population
-size, thus raising the role of demographic stochasticity [@loreau_species_2008]
-but also in the case where species have different responses to environmental
-variation [@loreau_species_2008]. While
-a negative effect of species richness on synchrony is generally found in
-experimental grasslands [@isbell_biodiversity_2009; @roscher_identifying_2011],
-no relation has been found in natural forests [@declerck_species_2006], but
-negative relationships have been found in natural communities of birds, bats,
-grasslands, bats and butterflies [@bluthgen_land_2016;
-@olivier_independent_nodate]. Our study thus highlights that species richness
-might also decrease synchrony in empirical trophic communities.
-
-Whereas the positive effect of species richness on $\overline{CV_{sp}}$, thereby
-decreasing stability, was more intriguing. Indeed, precedent studies found that
-constrasting results. For example, @olivier_independent_nodate reported negative, neutral and
-positive effect of species richness on $\overline{CV_{sp}}$ in respectively
-butterfly, bat and birds communities. @thibaut_understanding_2013 proposed that
-two ingredients can generate a positive effect of species richness on
-population ($\overline{CV_{sp}}$) stability: a strongly uneven biomass
-distribution across populationand that the biomass variance
-of population increases much faster than its mean.
-
-In turn, we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
-stability, as predicted by the formulation of stability based on the CV
-[@thibaut_understanding_2013]. However, it was unexpected that the average
-population $\overline{CV_{sp}}$ had a stronger negative effect on biomass
-stability than synchrony [@bluthgen_land_2016; @olivier_independent_nodate]. We
-can advance two hypothesis that can raise this effect. First, the opportunity
-for diet differentiation can be low in streams compare to other organisms.
-Secondly, in trophic communities, species directly affect each other through
-feeding interactions, and so could raise synchrony between species
-[@raimondo_interspecific_2004] more than in systems where interactions happen
-more in the form of competitive exploitation.
+species richness. Overall, it contrasts with experimental studies in grasslands
+[@tilman_biodiversity_2006]; mesocosms (Pennekamp et al. 2018), in 
+butterflies natural communities [@olivier_independent_nodate] or even in lotic
+fish communities [@franssen_annual_2011] where positive relationships were found
+between temporal stability and species richness. However other studies found a
+opposite relationship in natural grassland [@yang_effects_2011] or a marginal
+one in natural forests [@declerck_species_2006]. A first step to identify the
+mechanisms behind those contrasting patterns is be to look at the effects of
+species richness on synchrony and $\overline{CV_{sp}}$, which constitute the two
+components of temporal stability quantified as CV [@loreau_species_2008;
+@thibaut_understanding_2013].
+
+We found that species richness decreases
+synchrony, thereby increasing stability. Species richness can reduce synchrony
+by decreasing of population size, thus raising the role of demographic
+stochasticity on population dynamics [@loreau_species_2008] but also in the case
+where species have different responses to environmental variation
+[@loreau_species_2008]. While a negative effect of species richness on synchrony
+is generally found in experimental grasslands [@isbell_biodiversity_2009;
+@roscher_identifying_2011], no relation has been found in natural forests
+[@declerck_species_2006], but negative relationships have been found in natural
+communities of birds, bats, grasslands, bats and butterflies
+[@bluthgen_land_2016; @olivier_independent_nodate]. Our study thus highlights
+that species richness might also decrease synchrony in empirical trophic
+communities. The positive effect of species richness on $\overline{CV_{sp}}$,
+thereby decreasing stability, is more intriguing. While  positive effect of
+species richness on $\overline{CV_{sp}}$ was reported in experimental grasslands
+and natural bird communities [@tilman_biodiversity_2006;
+@olivier_independent_nodate], negative and neutral relationships have been found
+in butterfly and bat communities. @thibaut_understanding_2013 proposed that a
+strongly uneven biomass distribution across population and that the biomass
+variance of population increases much faster than its mean can generate a
+positive effect of species richness on population ($\overline{CV_{sp}}$)
+stability. It was unexpected that the average population $\overline{CV_{sp}}$ had
+a stronger negative effect on biomass stability than synchrony
+[@bluthgen_land_2016; @olivier_independent_nodate], and explain why we observe a
+negative effect of species on temporal stability of biomass. The lower
+effect of synchrony can be explained by the the presence of generalist predator
+in stream communities, which can raise synchrony between prey species which
+shares the same predator [@raimondo_interspecific_2004]. Alternatively,
+uneveness can also raise synchrony between species
+[@thibaut_understanding_2013], in line with mecanisms which can raise positive
+relationships between $\overline{CV_{sp}}$ and species richness.
 
@@
 [@thebault_relationship_2006; @kratina_warming_2012], hence leading to an
-increase in total biomass with vertical diversity. Furthermore,
+increase in total biomass with trophic length. Furthermore,
 @wang_biodiversity_2016 have shown that total nutrient uptake might increases
@@
 efficiency between prey and predators and so results in higher total biomass in
-the fish compartment. A reason for such an absence of an effect might be the
-little resolution that we have about interactions in non fish compartment (Fig.
-\@ref(fig:methods) C, D). A consequence can be that our connectance measurement
-contains few too informations.
-
-mean trophic level had a positive effect on biomass stability by its negative
-effect on CVsp (i.e. positive effect on average species stability). It means
-that species at higher trophic level are more stable than the species at lower
-trophic levels. @shanafelt_stability_nodate and @barbier_pyramids_2019
-found the same pattern with pure trophic chain models. They have shown that
-strong top-down control can generate this pattern but it is not
+the fish compartment. A reason for such an absence of an effect might be due the
+absence of information that we have about the other compartments of the
+community, i.e, the primary producers, zooplankton and zoobenthos. Further
+research are needed to assess the role of the trophic structure with a more
+complete communities.
+
+Mean trophic level had a positive effect on biomass stability by its negative
+effect on $\overline{CV_{sp}}$, thereby increasing average species stability. It
+means that species at higher trophic level are more stable than the species at
+lower trophic levels. Strong top-down control can generate this pattern in pure
+trophic chain [@barbier_pyramids_2018; @shanafelt_stability_2018] but it is not
 clear if this theoretical prediction holds when considering omnivorous species
-(i.e not a pure food chain) [@wang_biodiversity_2016] and if other mechanisms
-can generate the same pattern [@thibaut_understanding_2013].
-Another explanation is that the fishes at higher trophic levels are not more
-stable themselves, but rather allow for stronger top-down control and resource
-complementarity and thus reduce biomass fluctuations [@rooney_structural_2006;
-@neutel_reconciling_2007]. However, the ontogenic nature of the trophic
-networks complicate the interpretation from the network to population
-perspective. Over its life span, a given fish will change of diet and thus move
-upward in the trophic chain. The dynamic of a given species composed
-of several trophic species can thus be a mix of the dynamics of several trophic
-levels, plus the oscillatory dynamics of the cohorts [@townsend_population_1989;
-@medvinsky_modelling_2015]. Then, there is a clear need for a better
-understanding of how the dynamics of pure food chain models would be affected by
-inclusion of omnivory and ontogeny.
-
-We found that connectance had no effect on temporal stability. This result
-contradicts precedent theoretical studies on the relationship between stability
-and network structure [@angelis_stability_1975; @may_will_1972;
-@thebault_stability_2010], although they considered different stability concepts
-and metrics [@arnoldi_resilience_2016]. Once again, it is possible that
-that connectance from our networks contains too few information. Furthermore, a
-crucial missing ingredient to go further is the interaction strength. Indeed,
-@may_will_1972 has demonstrated theoretically the fundamental interplay between
-connectance, species richness and average interaction strength
-[@angelis_stability_1975; @dunne_network_2006].An alternative explanation can be
+[@wang_biodiversity_2016] and if other mechanisms can generate the same pattern
+[@thibaut_understanding_2013]. Another explanation is that the fishes at higher
+trophic levels are not more stable themselves, but rather allow for stronger
+top-down control and resource complementarity and thus reduce biomass
+fluctuations in lower trophic levels [@rooney_structural_2006;
+@neutel_reconciling_2007]. However, the ontogenic nature of the trophic networks
+complicate the interpretation from the network perspective to population
+fluctuations, the network structure fluctuate according to change in population
+size structure. Generally, a fish will change of diet over its life span and
+thus move upward in the trophic chain. The temporal dynamic of a given species
+composed of several trophic species can thus be a mix of the dynamics of several
+trophic levels, plus the oscillatory dynamics of the cohorts
+[@townsend_population_1989; @medvinsky_modelling_2015]. Then, there is a clear
+need for a better understanding of how the dynamics of pure food chain models
+would be affected by inclusion of omnivory and ontogeny. We found that
+connectance had no effect on temporal stability. This result previous precedent
+theoretical studies on the relationship between stability and network structure
+[@angelis_stability_1975; @may_will_1972; @thebault_stability_2010], although
+they considered different stability concepts and metrics
+[@arnoldi_resilience_2016]. Once again, it is possible that that connectance
+from our networks contains too few information. Furthermore, a crucial missing
+ingredient to go further is the interaction strength. Indeed, interaction
+strength is a crucial ingredient of stability [@may_will_1972;
+@angelis_stability_1975; @dunne_network_2006]. An alternative explanation can be
 that connectance increases inhomogeneously in the food web, for instance a
@@
 needed to understand the mechanisms leading to common and opposite effects of
-horizontal and vertical diversity. We found that connectance covaries
+species richness and network structure. We found that connectance covaries
 negatively with species richness [@winemiller_must_1989; @dunne_network_2006;
 @thebault_stability_2010], connectance had itself no effects on both total
-biomass and its temporal stability. On the other side, we found species richness
+biomass and its temporal stability. On the other side, we found that species richness
 was negatively related to mean trophic level and mean trophic level
 covariated positively with total biomass and its temporal stability. Hence,
-horizontal diversity had a direct positive and negative effect respectively on
+species richness had a direct positive and negative effect respectively on
 total biomass and its stability but a negative and positive effect through
-vertical diversity.  Theoretical work have shown that species richness can be
+mean trophic level. Theoretical work have shown that species richness can be
 linked to allocation of biomass toward higher trophic level
 [@thebault_relationship_2006; @schneider_animal_2016; @wang_biodiversity_2016].
-It indicates the importance to consider both horizontal, vertical diversity and
-their dependence. Moreover, it calls for further investigations on how species
-diversity variation translates in network structure.
-
-@thibaut_understanding_2013 have theoretically shown that a highly positive
-relationship between species variance and mean together with a positive
-relationship between mean species abundance (i.e. dominance) and species
-richness should drive to a negative temporal stability-species richness
-relationship. @thebault_relationship_2006 have also shown in a bi-trophic
-foodweb that a negative temporal stability-species richness appears in case of a
-plant species is highly dominant through low consumption by consumers but in the
-same time highly variable because of low competitive ability. Then, common
-mechanisms might be at play for both horizontal and vertical diversity while
-having same or opposite effects on total biomass and its temporal stability.
-Overall our results confirm that more investigation is needed to understand the
-mechanisms leading to common and opposite effects of horizontal and vertical
-diversity.
-
-In
-trophic communities,  additionnaly to the **portefolio effect**, the importance
-of trophic interactions on synchrony (mal dit).
+It indicates the importance to consider both species richness, network structure
+and their dependence. It calls for further investigations on how species
+diversity variation translates in network structure. Finally, common mechanisms
+might be at play in mono and multi-trophic communities such as while having same or
+opposite effects on total biomass and its temporal stability.
 
@@
 We find that environmental drivers overall affect total biomass indirectly,
-through changes in vertical and horizontal diversity. This contrasts with
-research in plant communities that showed that total biomass was primarily
-driven by environmental factors [@grace_integrative_2016], and in particular by
+through changes in network structure and species richness. This contrasts with
+research in plant communities that showed that total biomass was directly driven
+by environmental factors [@grace_integrative_2016], and in particular by
 warming, which has contrasted effects on biomass in aquatic communities
@@
 biomass, through a positive direct effect on species richness. These effects are
-well known in freshwater communities and are explained by a gain in species
+well known in biogeography and in freshwater communities and are explained by a gain in species
 along thermal gradients, from smaller and colder streams, which support small
-food webs dominated by salmonids [@ogorman_chapter_2012; @emmrich_geographical_2014],
-to wider and warmer sections of river networks, which contain larger food webs
-dominated by mesotrophic preators such as percids [@allan_stream_2007;
-@emmrich_geographical_2014]. Further in line with this pattern, we find that average stream
-size had a positive effect on total biomass through
-a positive effect on mean trophic level, consistent with the fact that food
-webs in wider streams, with a greater amount of running waters, are also larger,
-and hence support more species and biomass [@allan_stream_2007]. Greater ecosystem
-size might be linked to a greater diversity of resources through habitat
-heterogeneity, on so higher species richness and total biomass by surface unit,
-through resource complementarity. Greater diversity of resources might also
-allow to maintain higher biomass in high trophic level [@post_ecosystem_2000;
-@doi_resource_2009]. Overall, our results indicate that environmental effects on
-total biomass operate primarily through changes in community structure.
-Furthermore, the positive effect of temperature on total biomass was of the
-magnitude of effects of horizontal and vertical diversity, and thereby of
-changes in community structure. This adds to the mounting body of work reporting
-important effects of temperature on the structure and biomass of aquatic system
-[e.g. @dossena_warming_2012; @edeline_ecological_2013;
-@emmrich_geographical_2014; @hattab_forecasting_2016].
+food webs dominated by salmonids [@ogorman_chapter_2012;
+@emmrich_geographical_2014], to wider and warmer sections of stream networks,
+which contain larger food webs dominated by mesotrophic preators such as percids
+[@allan_stream_2007; @emmrich_geographical_2014]. Further in line with this
+pattern, we find that average stream size had a positive effect on total biomass
+through a positive effect on mean trophic level, consistent with the fact that
+food webs in wider streams, with a greater amount of running waters, are also
+larger, and hence support more species and biomass [@allan_stream_2007]. Greater
+ecosystem size might be linked to a greater diversity of resources through
+habitat heterogeneity, on so higher species richness and total biomass by
+surface unit, through resource complementarity. Greater diversity of resources
+might also allow to maintain higher biomass in high trophic level
+[@post_ecosystem_2000; @doi_resource_2009]. Overall, our results indicate that
+environmental effects on total biomass operate primarily through changes in
+community structure. Furthermore, the positive effect of temperature on total
+biomass was of the magnitude of effects of network structure and species
+richness. This adds to the mounting body of work reporting important effects of
+temperature on the structure and biomass of aquatic system [e.g.
+@dossena_warming_2012; @edeline_ecological_2013; @emmrich_geographical_2014;
+@hattab_forecasting_2016].
 
@@
 indirect effects on stability through two conflicting pathways, either
-stabilising, involving vertical diversity, or destabilising, involving
-horizontal diversity. The first pathway consists in a positive effect of
+stabilising, involving network structure, or destabilising, involving
+species richness. The first pathway consists in a positive effect of
 temperature and stream properties on mean trophic level, in line with the idea
@@
 temperature and stream properties (width, flow, inverse altitude) on species
-richness, which itself has a destabilising effect (see discussion on horizontal
-diversity). This result is interesting in that though both pathways had not been
-evidenced to be at jointly play, as far as we know. Furthermore, it is unclear
+richness, which itself has a destabilising effect (see discussion on species).
+This result is interesting in that though both pathways had not been evidenced
+to be jointly to play, as far as we know. Furthermore, it is unclear
 as to which pathway is dominating, and under which circumstance, opening an
@@
 
-We aimed to assess the effect of horizontal & vertical diversity on empirical
+We aimed to assess the effect of species richness & network structure on empirical
 trophic communities. While theoretical ecology has focused on the effects of
@@
 and ignored network structure. Furthermore, both fields have largely used
-different stability metrics. We showed that horizontal and vertical diversity
-can have independent and sometimes opposite effects on total biomass and its
-temporal stability. It opens a promising way for the understanding on how
-species interactions, of different types, can affect both synchrony and CVsp in
-different ecosystems. The reconstruction of ecological networks based on trait
-can be a first approach to document such relationships, however it will not
-compensate for close evaluation of measured interaction strength. We also
-believe that SEM methods are particularly helpful to assess complex relationship
-between environment, community structure and ecosystem properties in empirical
-data which necessitate to move from simple bivariate relationships
-[@grace_integrative_2016]. We believe that the integration of network structure
-and species interaction will improve our understanding of the mechanisms driving
-ecosystem properties.
+different stability metrics. We showed that species richness and network
+structure can have independent and sometimes opposite effects on total biomass
+and its temporal stability. It opens a promising way for the understanding on
+how species interactions, of different types, can affect both synchrony and $\overline{CV_{sp}}$
+in different ecosystems. However, the mecanisms leading to such patterns remains
+to be elucidated. The reconstruction of ecological networks based on body size
+and food diet litterarure can be a first approach to document such
+relationships, however it will not compensate for close evaluation of measured
+interaction strength. We also believe that SEM methods are particularly helpful
+to assess complex relationship between environment, community structure and
+ecosystem properties in empirical data which necessitate to move from simple
+bivariate relationships [@grace_integrative_2016]. We believe that the
+integration of network structure and species interaction will improve our
+understanding of the mechanisms driving ecosystem properties.
 

### 2020-07-22 manuscript/bef_stability/appendix.Rmd

@@
     keep_tex: true
+    toc: true
 fontsize: 12pt
@@
 
-```{r}
+```{r, echo = FALSE}
+package <- c("openSTARS", "SSN", "nlme", "piecewiseSEM")
+purrr::map_(package, ~ toBibtex(citation(.x)))
+
+toBibtex(citation())
+
+#print(cm, bibtex = TRUE)
 # Load manuscript results
@@
 
-# Sampling protocols
+# Data collection and preparation
 
@@
 ### Protocol
-
-```{r}
-```
 
@@
 is used. It consists in placing anodes every X meter across the width of the
-river (**Add the precise procedure?**). The fishermen made from one to three row
+river. The fishermen made from one to three row
 of fishing. We kept only the first row for analysis to homogenize the sampling
@@
 
-```{r mod-res, fig.cap = caption_mod_res}
+```{r mod-res, fig.height = 7, fig.cap = caption_mod_res}
 library(nlme)

### 2020-07-22 manuscript/bef_stability/manuscript.Rmd

@@
 been central to ecology. It has been at the basis of the predictions of the
-effect species richness and  network structure on total biomass, productivity
-and stability. However, empirical data are lacking on the link between network
-structure and ecosystem properties. We used a dataset of standardized fish
-sampling in French stream running from 1995 to
-2018. We inferred trophic interactions thanks to recorded body size and diet
-literature. We then investigate the direct and indirect effects of stream
-size and temperature, species richness and network structure on total biomass and
-its temporal stability. We found that species richness and network structure had
-a positive relationship with total biomass while they had respectively a
-negative and positive effect on temporal stability. We also found that
-species richness and network structure are not independent and that environment
-had an tremendous effect on total biomass and its temporal stability notably
-through its effect on species richness and network structure. We conclude that our
-study highlights that the effects of species richness and network structure should be 
-assessed conjointly and that it opens exciting perspectives on how environment,
-species richness and network structure can jointly determine total biomass in natural
-communities.
-
-(210/150 words)
+effects of species richness and network structure on total biomass, productivity
+and stability. However, empirical data on the link between network structure and
+ecosystem properties are lacking. We used a dataset of standardized fish
+sampling in French stream running from 1995 to 2018. We inferred trophic
+interactions thanks to recorded body size and diet literature. We then
+investigate the direct and indirect effects of stream size and temperature,
+species richness and network structure on total biomass and its temporal
+stability. We found that species richness and network structure had a positive
+relationship with total biomass while they had respectively a negative and
+positive effect on temporal stability. We also found that species richness and
+network structure are not independent and that environment had a tremendous
+effect on total biomass and its temporal stability notably through its effect on
+species richness and network structure. Our study highlights that the effects of
+species richness and network structure should be assessed conjointly and that it
+opens exciting perspectives on how environment, species richness and network
+structure can jointly determine total biomass in natural communities.
+
+(208/150 words)
 
@@
 amount and the distribution of matter and energy fluxes
-within ecosystems [@duffy_why_2009]. Biodiversity thus affects biomass
+within and among ecosystems [@duffy_why_2009]. Biodiversity thus affects biomass
 production [@tilman_productivity_1996; @cardinale_species_2002;
@@
 of the most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
-In contrast, both positive [@wu_relationship_2014; @li_relationship_2018],
-negative or no effects [@szwagrzyk_above-ground_2007; @jacob_productivity_2010;
-@seidel_relationship_2013] of species richness on total biomass have been found
-in natural forest. Some authors suggest that the lack of resource
+In contrast, positive [@wu_relationship_2015; @li_relationship_2018],
+negative or non significant effects of species richness on total biomass have been found
+in natural forests [@szwagrzyk_above-ground_2007; @jacob_productivity_2010;
+@seidel_relationship_2013]. Some authors suggest that the lack of resource
 complementarity or environmental harshness might be responsible for an absence or a
 negative effect of species richness [@loreau_partitioning_2001; @he_global_2013;
-@wu_relationship_2014]. Overall, under what conditions and through what
+@wu_relationship_2015]. Overall, under what conditions and through what
 mechanisms we should observe positive relationships between biomass and species
-richness in natural settings is still an open question.
-
-Many studies showed that species richness also increases temporal stability,
-i.e. variation through time, often quantified using CV. Such positive
+richness in natural settings remains an open question.
+
+Many studies showed that species richness also increases temporal stability of
+communities,
+i.e. variation through time, often quantified by the temporal CV. Such positive
 relationships between species richness and temporal stability have been reported
@@
 species richness and temporal stability [@loreau_species_2008;
-@thibaut_understanding_2013]. Two mechanisms may govern the temporal stability
-of communities, (1) species synchrony and (2) species variability. Species
+@thibaut_understanding_2013], (1) species synchrony and (2) species variability. Species
 synchrony quantify to what extent the fluctuations of abundances or biomasses
@@
 stabilizing effect on temporal stability [@tilman_biodiversity_2006;
-@olivier_independent_nodate].  ^[Colin asked for a word about $cv_{sp}$ and
+@olivier_urbanization_2020]. ^[Colin asked for a word about $cv_{sp}$ and
 stability but my opinion is that it is not necessary and that the depth of mecanisms are
-currently fairly explained for the introduction]. Such positive relationships
+currently fairly explained for the introduction.] Such positive relationships
 between speciesrichness and temporal are also observed in natural settings, such
 as stream fish communities [@franssen_annual_2011], bird and butterfly
-communities [@olivier_independent_nodate].
+communities [@olivier_urbanization_2020].
 
@@
 comes from studies focusing on one trophic level, generally primary producers or
-primary consumers. Natural ecosystems generally include
-more than one or two trophic levels and it is not certain that what holds
-on one trophic level hold also in multitrophic communities.
-Theoretical studies showed that food web properties, such as interaction
-distribution and strength, affect the distribution of biomass among adjacent
-trophic levels, [@thebault_relationship_2006; @schneider_animal_2016;
-@barbier_pyramids_2019]. A
+primary consumers. Natural ecosystems generally include more than one or two
+trophic levels and there is no certainty that the relationship between species
+richness and total biomass and its temporal stability for a given trophic level
+is representative of this relationship at the food web level. Theoretical
+studies showed that food web properties, such as interaction distribution and
+strength, affect the distribution of biomass among adjacent trophic levels,
+[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019]. A
 large body of theoretical studies links the propagation of perturbations to the
@@
 @neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011],
-or trophic chain [@shanafelt_stability_nodate; @wang_biodiversity_2016;
+or trophic chain [@shanafelt_stability_2018; @wang_biodiversity_2016;
 @barbier_pyramids_2019]. To date, we have few evidence on the relationship
@@
 When assessing the relationship between community structure and ecosystem
-properties in natural communities, it is crucial 
-to consider environmental factors [@loreau_biodiversity_2001;
-@he_global_2013; @grace_integrative_2016]. Environment affects organism
-performance directly, and thereby, species abundances, total biomass
-[@grace_integrative_2016] and temporal stability [@de_boeck_patterns_2017;
-@hansen_climate_2013; @bluthgen_land_2016; @oliver_heterogeneous_2010; @franssen_annual_2011;
-@friedpetersen_drivers_2020]. For example, greater ecosystem size might increase
-the number of available resources and thus total biomass [@post_ecosystem_2000;
-@doi_resource_2009]. @li_relationship_2018 have notably shown that climate
-moisture has a positive direct effect on total biomass, but also indirect
-through a positive effect on species richness. Taking in consideration
-environment also allow for an overall comparison of the strength of the
-the effects of environment and community structure on total biomass and its
-stability.
+properties in natural communities, it is crucial to consider environmental
+factors [@loreau_biodiversity_2001; @he_global_2013; @grace_integrative_2016].
+Environment affects organism performance directly, and thereby, species
+abundances, total biomass [@grace_integrative_2016] and temporal stability
+[@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
+@oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
+For example, greater ecosystem size might increase the number of available
+resources and thus total biomass [@post_ecosystem_2000; @doi_resource_2009].
+@li_relationship_2018 have notably shown that climate moisture has a positive
+direct effect on total biomass, but also indirect through a positive effect on
+species richness. Accounting for environment also allow for an overall
+comparison of the strength of the the effects of environment and community
+structure on total biomass and its stability.
 
@@
 network structure on total biomass and its temporal stability. Despite that
-fish trophic interactions are difficult to measure in nature, a consequent body
+fish trophic interactions are difficult to measure in natural conditions, a consequent body
 of literature supports that they can be inferred through body size and diet
@@
 interactions based on body size ratio was far better in stream ecosystems than
-in other aquatic and te ecosystems. Furthermore, the biotic activity in stream
+in other aquatic and terrestrial ecosystems. Furthermore, the biotic activity in stream
 ecosystems determines for a large part the water quality
@@
 structure was summarized by connectance and mean trophic level. Environment
-was characterized by the stream size, altitude, slope, and the temperature, flow
+was characterized by stream size, altitude, slope, temperature, flow
 and enrichment. Finally total biomass was measured as median total biomass over
@@
 matmet_cap <- paste0(
-  "(A) Conceptual model of the hypothesized relationships between environment,
-  species richness, network metrics and total biomass / biomass stability. ",
-  "Solid and dashed arrows represent respectively direct and indirect effects.
-  ",
-  "The blue, green and blue/green dashed arrows being respectively indirect
-  effects going through species richness, network metrics and through both
-  species richness and network metrics.",
-  "(B) Observation sites (black dots) were located across France and monitored
+  #"(A) Conceptual model of the hypothesized relationships between environment,
+  #species richness, network metrics and total biomass / biomass stability. ",
+  #"Solid and dashed arrows represent respectively direct and indirect effects.
+  #",
+  #"The blue, green and blue/green dashed arrows being respectively indirect
+  #effects going through species richness, network metrics and through both
+  #species richness and network metrics.",
+  "(A) Observation sites (black dots) were located across France and monitored
   on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
   "Inner borders draw the limits of the hydrographic basins. ",
-  "(C) The metaweb. Each trophic species (N = 412) is represented by a node and
-  each color represent a species (S = ). Resource nodes (7) were drawn in grey. ",
-  "(D) Subset over network variation through time."
-)
-```
-
-```{r matmet, fig.cap = matmet_cap}
+  "(B) The metaweb. Each trophic species (N = 412) is represented by a node and
+  each color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
+  "(C) Subset over network variation through time."
+)
+```
+
+```{r matmet, fig.cap = matmet_cap, cache = FALSE}
 myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))
@@
 
+left <- plot_grid(p_st, p_metaweb, ncol = 1, rel_widths = c(1, 1), labels =
+  c("A", "B"))
+p_test <- plot_grid(left, temporal_network, ncol = 2, labels = c("A", "C"))
+
 p_method <- plot_grid(top, bottom, nrow = 2, rel_heights = c(1, 1),
@@
     "method_fig.pdf"),
-  p_method, nrow = 2, ncol =2,
+  p_test, nrow = 2, ncol =2,
   base_width = 7/2.54,
@@
 )
-p_method
+p_test
 ```
@@
 Fish communities were monitored across stream sections in France on the period
-1995-2018 by the French Office of Water and Aquatic Ecosystems
-(ONEMA) using electric fishing. Two different standardized protocols were used
-for little and big streams (detailed in Supplementary methods). For streams
-shallower than (XX m), the sampling takes place over the whole width of the
-streams and is done by foot whereas in streams deeper than (XX m), the sampling
-was done over the bank by foot or by boat. The sampling season spans from 
-late spring to Autumn. During sampling, all the fishes caught were
-identified and counted. For each species, either the body size of all fish was
-measured, or a representative sample when the number of fish was high (See
-supplementary methods for details). The fishes were released at the end
+1995-2018 by the French Office of Water and Aquatic Ecosystems (ONEMA) using
+electric fishing. Two different standardized protocols were used for small and
+large streams (detailed in Supplementary material, part 1.1). For streams
+shallower than 0.7m across the entire width, the sampling took place over the
+whole width of the streams and was done by foot whereas in streams deeper than
+0.7m, the sampling was done over the bank by foot or by boat. The sampling
+season spanned from late spring to autumn. During sampling, all the fishes
+caught were identified and recorded. For each species, either the body size of
+all fish was measured, or a representative sample when the number of fish was
+high (Figure S1, supplementary information). The fishes were released at the end
 of the sampling. Additionally, the physical characteristics of the river was
@@
 
-We kept only the most frequent sampling protocol in each station and kept
+We kept only the most frequent of the two sampling protocols in each station and kept
 stations that had been sampled ten years or more. The median sampling month was
@@
 natural communities, only those stations with no temporal trends in total
-biomass were selected (detailled in supplementary methods). However, the results
+biomass were selected (detailed in supplementary methods). However, the results
 were robust to the relaxation of this hypothesis (Supplementary results). We
@@
 The body size of the unmeasured individuals was inferred under the assumption
-that species body size followed a normal distribution whose the mean and the
-standard deviation was quantified from the measured individuals of the sampling
-(See supplementary methods). The body mass of each individual was then estimated
+that species body size followed a normal distribution whose mean and
+standard deviation were quantified from the recorded individuals of the sampling
+(See supplementary methods, Figure S1). The body mass of each individual was then estimated
 using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$ being the body mass
 in grams, $l$ the body size in millimeters and $i$ the individual), where the
-coefficients $0.01$ and $3.03$ comes from meta-analysis
-[@lleonart_removing_2000; @froese_cube_2006]. The species biomass
+coefficients $0.01$ and $3.03$ comes from two meta-analyses
+[@lleonart_removing_2000; @froese_cube_2006]. Species biomass
 and total biomass at each sampling was then calculated by summing individual
@@
 total biomass over time ($\sigma^2_{x_{T,i}}$) and the sum of the variance of
-population biomass over time ($\sigma_{x_k}$) [@loreau_species_2008]. $i$ being
-the station $i$ and $k$ the species $k$.
+population biomass over time ($\sigma_{x_k}$), $i$ being the station $i$ and $k$
+the species $k$ [@loreau_species_2008].
 
@@
 algae or fishes. Accordingly, each fish species was divided in nine body size
-classes, each of which is trophic species (Figure SXX). A high congruence
+classes, each corresponding to a trophic species (Figure S2). A high congruence
 between inferred interactions and measured trophic interactions has been found
@@
 macrophages, phytobenthos and zoobenthos (grey nodes in Figure \@ref(fig:matmet)
-C & D). The ontogenic diet database was based on informations from fishbase and
-literature. Each fish species had two or three life stages which are delimited by
-body size (Table SXX, Figure SXX).
-
-The trophic interactions of fish trophic species was determining with the median
-of its body size range, hereafter after midpoint. The midpoint of trophic
-species fall into one of the species life stage and a trophic link was set
-between the trophic species and the resources present in the life stage. If the
-trophic species is in a piscivorous life stage, the fish-fish trophic links was
-defined in two steps and based on the body size ratio between predators and
-prey. First of all, we defined the range predation window from 3% to 45% of the
-midpoint of the trophic species. Then, a trophic link was set between the
-piscivorous trophic species and every trophic species whose midpoint was
-included in the predation range (Figure SXX). Lastly, the trophic links between resources was
-set according to the food diet data.
+C & D). The ontogenic diet database was based on fishbase and literature. Each
+fish species had two or three life stages which are delimited by body size
+(Figure S2).
+
+The trophic interactions of fish trophic species was determined with the median
+of its body size range, hereafter midpoint. The midpoint of trophic species fall
+into one of the species life stage and a trophic link was set between the
+trophic species and the resources present in the life stage. If the trophic
+species is in a piscivorous life stage, the fish-fish trophic links was defined
+in two steps and based on the body size ratio between predators and prey
+[@mittelbach_ontogeny_1998; @claessen_impact_2002]. First of all, we defined the
+range predation window from 3% to 45% of the midpoint of the trophic species.
+Then, a trophic link was set between the piscivorous trophic species and every
+trophic species whose midpoint was included in the predation range (Figure S2).
+Lastly, the trophic links between resources was set according to the food diet
+data [@allan_stream_2007; @hart_handbook_2008].
 
@@
 $\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and $B_i$
-being resp. the trophic level and the biomass of the node $i$.
+being respectively the trophic level and the biomass of the node $i$.
 
@@
 
-we characterised the sampled sites by their altitude, slope, distance from
+We characterised the sampled sites by their altitude, slope, distance from
 source, stream width and depth and its strahler order, i.e. its position in the
 stream network. From the naiades database
-[http://www.naiades.eaufrance.fr/](http://www.naiades.eaufrance.fr/), we also
-got data on water temperature and flow as they affect the type of fish that can
-establish [@franssen_annual_2011; @rolls_scaling_2018; @tonkin_flow_2018;
+[(www.naiades.eaufrance.fr)](http://www.naiades.eaufrance.fr/), we also
+got data on water temperature and flow as they affect the type of fish that 
+settling down [@franssen_annual_2011; @rolls_scaling_2018; @tonkin_flow_2018;
 @gutierrez-canovas_contrasting_2013] as well as BOD (Biological Oxygen Demand)
-as a proxy for eutrophisation. As data from the naide database are not collected
-on same site as our fish sampling sites, we performed an interpolation with
+as a proxy for eutrophisation. As data from the naiades database are not collected
+on the same site as our fish sampling sites, we performed an interpolation with
 spatial stream networks [@isaak_applications_2014; @hoef_ssn:_2014]. The
-interpolation procedure is detailed in supplementary methods.
+interpolation procedure is detailed in supplementary (part 1.2).
 
 We had one environmental variable value for each site and sampling event, except
-for water temperature for which the record began in 2006. Then, we computed the average over
-time and the CV over time for water temperature, flow, BOD, river width and
+for water temperature for which the record began in 2006. Then, the temporal
+average and CV values of for water temperature, flow, BOD, river width and
 depth. As habitat and environmental variables are often collinear, a principal
-component analysis (PCA)
-was performed on the 14 scaled variables. We kept in the analysis the two first
-principal components based on eigen values distribution (Fig. SXX).
-The two first principal components explained `r tot_var_expl_pca`%
-of the variance. A varimax axis rotation was performed to maximize the representation
-of the variables by the principal components (Figure SXX).
-The two first principal components were used in the analysis, representing respectively
-the (1) river size (river width & depth), (2) altitude, slope and decreasing
-average temperature. Further description of the variables are detailed in
-supplementary information.
+component analysis (PCA) was performed on the 14 scaled variables. We kept in
+the analysis the two first principal components based on the elbow method, on
+the eigen values distribution (Fig. S4). The two first principal components
+explained `r tot_var_expl_pca`% of the variance. A varimax axis rotation was
+performed to maximize the representation of the variables by the principal
+components (Figure S4). The two first principal components were used in the
+analysis, representing respectively the (1) river size (river width & depth),
+(2) altitude, slope and decreasing average temperature. Further description of
+the variables are detailed in supplementary information (part 1.3).
 
@@
 @lefcheck_piecewisesem_2016; @grace_integrative_2016]. We built the biomass
-model (Figure \@ref(fig:matmet) A, \@ref(fig:sem-plot) B) by considering that environment
+model by considering that environment
 can directly affect species richness and network structure, as well as total
-biomass. Species richness directly affects total biomass. Food web structure
-was shown to be constrained by species richness @winemiller_must_1989;
-@dunne_network_2006; @thebault_stability_2010. In turn,
-the network structure affects total biomass (Figure
-\@ref(fig:matmet) A, \@ref(fig:sem-plot) B). We used the same model structure for
-temporal variability (Figure \@ref(fig:sem-plot) A). The structural equation
-models used for total biomass and its temporal stability contains respectively 4
-and 6 response variables, 35 and 26 direct paths.
+biomass (Figure \@ref(fig:matmet) A, \@ref(fig:sem-plot) B). 
+Food web structure was shown to be constrained by species richness [@winemiller_must_1989;
+@dunne_network_2006; @thebault_stability_2010]. 
+We assumed that both species richness and network structure directly affect
+total biomass (Figure \@ref(fig:matmet) A, \@ref(fig:sem-plot) B). In addition,
+we assumed that species richness would indirectly affect total biomass through
+network structure [@schneider_animal_2016].
+We used the same model structure for temporal variability (Figure
+\@ref(fig:sem-plot) A). The structural equation models used for total biomass
+and its temporal stability contains respectively 4 and 6 response variables, 35
+and 26 direct paths.
 
@@
 Environmental variables were interpolated with the `openStars` and `SSN`
-packages. Linear models and SEMs were computed with respectively the `nlme` and
-`piecewieseSEM` R packages. The code used for the analysis and the Rmarkdown
-used to generate this document are accessible on github.
+R packages [@kattwinkel_openstars_2018; @hoef_ssn:_2014]. Linear models and SEMs
+were computed with respectively the `nlme` and `piecewieseSEM` R packages
+[@pinheiro_nlme_2020; @lefcheck_piecewisesem_2016]. The code used for the
+analysis and the manuscript are accessible on github. The analysis were
+performed with R version 3.6.3 [@r_core_team_r_2020].
 
@@
 ```
-```{r}
-caption_indir_stab_sem <- paste0(
-  "Indirect and total effect of variables on biomass stability from the
-  structural equation model. Indirect effects are computed by multiplying the
-  path coefficients from the variable predictor to the response variable, here
-  biomass stability. Indirect effects are considered as one step from the target
-  variable. For exemple, the indirect effect of species richness on
-  biomass stability via its effect on CVsp is -0.61. To compute indirect
-  effect, only the significant direct effects were taken into account. ",
-  "Network structure being the indirect effect that went through both avg trophic
-  level and connectance and Species richness_Network structure being the
-  indirect effect that went through (i) species richness and from (ii) species
-  richness to network structure."
-)
-
-caption_indir_bm_sem <- paste0(
-  "Indirect and total effect of variables on total biomass from the
-  structural equation model. See the table 1 for details about computation and
-  meaning." 
-)
-```
 
@@
 ```
-
-```{r indir-bm}
-kable(format_table(tmp_bm_indir_table),
-  format = "latex",
-  booktabs = T,
-  label = paste0("indir-bm"),
-  caption = caption_indir_bm_sem
-  ) %>%
-kable_styling(latex_options =c("striped", "scale_down"))
-```
-
 ```{r get-sem-single-effect}
@@
 
-```{r indir-stab}
-kable(format_table(tmp_stab_indir_table),
-  format = "latex",
-  booktabs = T,
-  label = paste0("indir-stab"),
-  caption = caption_indir_stab_sem 
-  ) %>%
-kable_styling(latex_options =c("striped", "scale_down"))
-```
-
 Overall, the structural equation models explained a large part of the variation
@@
 
-Species richness and mean trophic level had a significant positive direct effect on total biomass
-($r_\delta = `r rich_on_bm$direct`$ and $r_\delta = `r tlvl_on_bm`$ resp., Figure
-\@ref(fig:sem-plot) D, Table \@ref(tab:indir-bm)), while connectance had no
-direct nor indirect significant effect (Figure \@ref(fig:sem-plot) D) on total
-biomass. The total effect of mean trophic level on total biomass was of the same
-magnitude than the one of species richness (resp. $`r tlvl_on_bm`$ and $`r
-rich_on_bm$total`$, Table \@ref(tab:indir-bm)).
+Species richness and mean trophic level had a significant positive direct effect
+on total biomass ($r_\delta = `r rich_on_bm$direct`$ and $r_\delta = 
+`r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) D, Table \@ref(tab:indir-sem)),
+while connectance had no direct nor indirect significant effect on total biomass (Figure
+\@ref(fig:sem-plot) D). The total effect of mean trophic level
+on total biomass was of the same magnitude than the one of species richness
+(resp. $`r tlvl_on_bm`$ and $`r rich_on_bm$total`$, Table \@ref(tab:indir-sem)).
 
@@
 The environmental variables had no significant direct effects on total biomass
-(Table SXX), but indirect (Table \@ref(tab:indir-bm)). Average temperature and
+(Table SXX), but indirect (Table \@ref(tab:indir-sem)). Average temperature and
 altitude respectively increased and decreased total biomass ($r_\delta =
-`r env_on_bm$direct["log_RC2"]`$, Table \@ref(tab:indir-bm)), mainly through
+`r env_on_bm$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)), mainly through
 species richness ($r_\delta = `r env_on_bm$via_richness["log_RC2"]`$, Table
-\@ref(tab:indir-bm)). Average stream size had a positive effect on total
-biomass ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-bm)),
+\@ref(tab:indir-sem)). Average stream size had a positive effect on total
+biomass ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
 equally through species richness and mean trophic level ($r_\delta = 
 `r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
-resp., Table \@ref(tab:indir-bm)). Average temperature and altitude effects on
+resp., Table \@ref(tab:indir-sem)). Average temperature and altitude effects on
 total biomass were of the same magnitude than the effects on species richness
@@
 negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
-Table \@ref(tab:indir-stab)). On the one hand, species richness had a direct
+Table \@ref(tab:indir-sem)). On the one hand, species richness had a direct
 negative effect on synchrony ($r_\delta = `r rich_on_sync$direct`$), thereby
@@
 thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
-\@ref(tab:indir-stab)). Finally, it was surprising that the negative
+\@ref(tab:indir-sem)). Finally, it was surprising that the negative
 effect of $\overline{CV_{sp}}$ on temporal stability was twice higher than the
@@
 effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
-Table \@ref(tab:indir-stab)). The mean trophic level had no significant
+Table \@ref(tab:indir-sem)). The mean trophic level had no significant
 effect on synchrony and connectance had no significant direct, nor indirect
@@
 $`r com_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
-\@ref(tab:indir-stab)).
+\@ref(tab:indir-sem)).
 
@@
 temporal stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table
-\@ref(tab:indir-stab)) mainly through a direct positive effect on
+\@ref(tab:indir-sem)) mainly through a direct positive effect on
 $\overline{CV_{sp}}$
-($r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-stab)).
+($r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)).
 Interestingly, average temperature (and opposite of altitude) had also a negative
@@
 (resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
-$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-stab)).
+$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-sem)).
 This was also true for average river size but effects were weak. Finally, the
@@
 the effects of species richness and mean trophic level (Table
-\@ref(tab:indir-stab)).
+\@ref(tab:indir-sem)).
+
+```{r indir-stab, cache = FALSE}
+caption_sem <- paste0(
+  "Direct, indirect and total effect of environment, species richness and
+  network structure, i.e. connectance and mean trophic level on total biomass
+  and its temporal stability. Indirect effects are computed by multiplying the
+  path coefficients from the variable predictor to the response variable, here
+  biomass stability. Indirect effects are considered as one step from the target
+  variable. For exemple, the indirect effect of species richness on
+  biomass stability via its effect on CVsp is $-0.61$. To compute indirect
+  effect, only the significant direct effects were taken into account. ",
+  "Network structure being the indirect effect that went through both avg trophic
+  level and connectance and Species richness_Network structure being the
+  indirect effect that went through (i) species richness and from (ii) species
+  richness to network structure."
+)
+
+full_table <- bind_rows(
+  tmp_bm_indir_table,
+  tmp_stab_indir_table
+) %>%
+select(variable, direct, via_richness, via_richness_com, via_com, via_cv_sp, via_sync, total) %>%
+format_table()
+
+kable(full_table,
+  format = "latex",
+  booktabs = T,
+  label = paste0("indir-sem"),
+  caption = caption_sem
+  ) %>%
+kable_styling(latex_options =c("striped", "scale_down")) %>%
+pack_rows("Total biomass", 1, 3) %>%
+pack_rows("Temporal stability of biomass", 4, 8)
+```
 
@@
 poorly documented. To do so, we quantified the effects, directs and indirects,
-of habitat properties, species richness, and food web structure, on the biomass
-and stability of fish communities, from the ONEMA fish dataset, containing over
-X million individual fish samples, across 99 locations in France from 1995 to
+of habitat properties, species richness, and food web structure, on the total biomass
+and stability of fish communities, from the ONEMA fish dataset, across 99
+locations in France from 1995 to
 2018. We infered trophic interactions networks based on body size-dependency in
-   food diet from the literature and prey/predator body size
-ratio for piscivory^[ We inferred trophic networks at the scale of trophic
+food diet from the literature and prey/predator body size ratio for piscivory ^[
+We inferred trophic networks at the scale of trophic
 species (i.e. nodes being body size classes) to take in account ontogenic diet
@@
 [@tilman_biodiversity_2006]; mesocosms (Pennekamp et al. 2018), in 
-butterflies natural communities [@olivier_independent_nodate] or even in lotic
+butterflies natural communities [@olivier_urbanization_2020] or even in lotic
 fish communities [@franssen_annual_2011] where positive relationships were found
@@
 
-We found that species richness decreases
-synchrony, thereby increasing stability. Species richness can reduce synchrony
-by decreasing of population size, thus raising the role of demographic
-stochasticity on population dynamics [@loreau_species_2008] but also in the case
-where species have different responses to environmental variation
-[@loreau_species_2008]. While a negative effect of species richness on synchrony
-is generally found in experimental grasslands [@isbell_biodiversity_2009;
-@roscher_identifying_2011], no relation has been found in natural forests
-[@declerck_species_2006], but negative relationships have been found in natural
-communities of birds, bats, grasslands, bats and butterflies
-[@bluthgen_land_2016; @olivier_independent_nodate]. Our study thus highlights
-that species richness might also decrease synchrony in empirical trophic
-communities. The positive effect of species richness on $\overline{CV_{sp}}$,
-thereby decreasing stability, is more intriguing. While  positive effect of
-species richness on $\overline{CV_{sp}}$ was reported in experimental grasslands
-and natural bird communities [@tilman_biodiversity_2006;
-@olivier_independent_nodate], negative and neutral relationships have been found
+We found that species richness decreases synchrony, thereby increasing
+stability. Species richness can reduce synchrony by decreasing of population
+size, thus raising the role of demographic stochasticity on population dynamics
+[@loreau_species_2008] but also in the case where species have different
+responses to environmental variation [@loreau_species_2008]. While a negative
+effect of species richness on synchrony is generally found in experimental
+grasslands [@isbell_biodiversity_2009; @roscher_identifying_2011], no relation
+has been found in natural forests [@declerck_species_2006], but negative
+relationships have been found in natural communities of birds, bats, grasslands,
+bats and butterflies [@bluthgen_land_2016; @olivier_urbanization_2020]. Our
+study thus highlights that species richness might also decrease synchrony in
+empirical trophic communities. The positive effect of species richness on
+$\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
+positive effect of species richness on $\overline{CV_{sp}}$ was reported in
+experimental grasslands and natural bird communities [@tilman_biodiversity_2006;
+@olivier_urbanization_2020], negative and neutral relationships have been found
 in butterfly and bat communities. @thibaut_understanding_2013 proposed that a
@@
 positive effect of species richness on population ($\overline{CV_{sp}}$)
-stability. It was unexpected that the average population $\overline{CV_{sp}}$ had
-a stronger negative effect on biomass stability than synchrony
-[@bluthgen_land_2016; @olivier_independent_nodate], and explain why we observe a
-negative effect of species on temporal stability of biomass. The lower
-effect of synchrony can be explained by the the presence of generalist predator
-in stream communities, which can raise synchrony between prey species which
-shares the same predator [@raimondo_interspecific_2004]. Alternatively,
-uneveness can also raise synchrony between species
-[@thibaut_understanding_2013], in line with mecanisms which can raise positive
-relationships between $\overline{CV_{sp}}$ and species richness.
+stability. It was unexpected that the average population $\overline{CV_{sp}}$
+had a stronger negative effect on biomass stability than synchrony
+[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
+negative effect of species on temporal stability of biomass. The lower effect of
+synchrony can be explained by the the presence of generalist predator in stream
+communities, which can raise synchrony between prey species which shares the
+same predator [@raimondo_interspecific_2004]. Alternatively, uneveness can also
+raise synchrony between species [@thibaut_understanding_2013], in line with
+mechanisms which can raise positive relationships between $\overline{CV_{sp}}$
+and species richness.
 
@@
 that body mass increase with body size, it is expected that the more the average
-biomass is located at higher trophic level, the more the total biomass
-increase. A mechanism, suggested by experimental and theoretical work, can
-be that a higher trophic level is the result of a stronger top-down effect,
-meaning higher predation rates and biomass fluxes to higher trophic levels
+biomass is located at higher trophic level, the more the total biomass increase.
+A mechanism, suggested by experimental and theoretical work, can be that a
+higher trophic level is the result of a stronger top-down effect, meaning higher
+predation rates and biomass fluxes to higher trophic levels
 [@thebault_relationship_2006; @kratina_warming_2012], hence leading to an
@@
 @wang_biodiversity_2016 have shown that total nutrient uptake might increases
-with the length of trophic chain and so results in higher total biomass. 
-In contrast, connectance had no effect on total biomass. One might have expected
+with the length of trophic chain and so results in higher total biomass.  In
+contrast, connectance had no effect on total biomass. One might have expected
 that an increase in connectance should translate in higher resource transfer

### 2020-07-23 manuscript/bef_stability/manuscript.Rmd

@@
 - Number of words:
-  - Abstract: 194
+  - Abstract: 208 
   - Main text: XXXX
@@
 can directly affect species richness and network structure, as well as total
-biomass (Figure \@ref(fig:matmet) A, \@ref(fig:sem-plot) B). 
+biomass (Figure \@ref(fig:sem-plot) B). 
 Food web structure was shown to be constrained by species richness [@winemiller_must_1989;
@@
 We assumed that both species richness and network structure directly affect
-total biomass (Figure \@ref(fig:matmet) A, \@ref(fig:sem-plot) B). In addition,
+total biomass (Figure \@ref(fig:sem-plot) B). In addition,
 we assumed that species richness would indirectly affect total biomass through
@@
 richness on total biomass might be due to resource use complementarity, which is
-held by niche differentiation and interspecific facilitation
-[@loreau_biodiversity_1998; @loreau_partitioning_2001; @cardinale_species_2002]
-or might be due to a positive selection effect [@tilman_plant_1997;
-@loreau_partitioning_2001], which leads to the dominance of the most productive
-species. Previous research seems to indicate that resource complementarity might
-be the main driver in fish communities [@carey_determining_2011].
-
-Surprisingly found a negative relationship between temporal stability and
+held by niche differentiation [@loreau_biodiversity_1998;
+@loreau_partitioning_2001] or might be due to a positive selection effect
+[@tilman_plant_1997; @loreau_partitioning_2001], which leads to the dominance of
+the most productive species. The study of @carey_determining_2011 showed that
+resource complementarity might be the main driver in fish communities.
+
+Surprisingly we found a negative relationship between temporal stability and
 species richness. Overall, it contrasts with experimental studies in grasslands
@@
 study thus highlights that species richness might also decrease synchrony in
-empirical trophic communities. The positive effect of species richness on
+empirical trophic communities.
+
+The positive effect of species richness on
 $\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
@@
 positive effect of species richness on population ($\overline{CV_{sp}}$)
-stability. It was unexpected that the average population $\overline{CV_{sp}}$
+stability.
+
+It was unexpected that the average population $\overline{CV_{sp}}$
 had a stronger negative effect on biomass stability than synchrony
@@
 
-## Vertical diversity increased total biomass and its temporal stability
-
-The mean trophic level was positively linked to total biomass. This result is
-straightforward. As feeding interactions were partly determined by body size and
-that body mass increase with body size, it is expected that the more the average
+## Mean trophic level increased total biomass and its temporal stability
+
+The mean trophic level was positively linked to total biomass. As feeding
+interactions were partly determined by body size and that body mass increase
+with body size, it is expected that the more the average
 biomass is located at higher trophic level, the more the total biomass increase.
@@
 @wang_biodiversity_2016 have shown that total nutrient uptake might increases
-with the length of trophic chain and so results in higher total biomass.  In
+with the length of trophic chain and so results in higher total biomass.
+
+We found that species richness was negatively related to mean trophic level and 
+connectance [@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010]. In
 contrast, connectance had no effect on total biomass. One might have expected
@@
 fluctuations in lower trophic levels [@rooney_structural_2006;
-@neutel_reconciling_2007]. However, the ontogenic nature of the trophic networks
-complicate the interpretation from the network perspective to population
-fluctuations, the network structure fluctuate according to change in population
-size structure. Generally, a fish will change of diet over its life span and
-thus move upward in the trophic chain. The temporal dynamic of a given species
-composed of several trophic species can thus be a mix of the dynamics of several
-trophic levels, plus the oscillatory dynamics of the cohorts
-[@townsend_population_1989; @medvinsky_modelling_2015]. Then, there is a clear
-need for a better understanding of how the dynamics of pure food chain models
-would be affected by inclusion of omnivory and ontogeny. We found that
-connectance had no effect on temporal stability. This result previous precedent
-theoretical studies on the relationship between stability and network structure
-[@angelis_stability_1975; @may_will_1972; @thebault_stability_2010], although
-they considered different stability concepts and metrics
-[@arnoldi_resilience_2016]. Once again, it is possible that that connectance
-from our networks contains too few information. Furthermore, a crucial missing
-ingredient to go further is the interaction strength. Indeed, interaction
-strength is a crucial ingredient of stability [@may_will_1972;
-@angelis_stability_1975; @dunne_network_2006]. An alternative explanation can be
-that connectance increases inhomogeneously in the food web, for instance a
-higher connectance in lower trophic levels will not have the stabilising effects
-conferred by higher predation and omnivory in higher trophic levels. Further
-investigations on this effect is needed.
-
-## Horizontal and vertical diversity had common, opposite and dependent effects on total biomass and its temporal stability
-
-We found that species richness had a positive and a negative effect on
-respectively total biomass and its temporal stability whereas average trophic
-level had a positive effect on both. It confirms that more investigation is
-needed to understand the mechanisms leading to common and opposite effects of
-species richness and network structure. We found that connectance covaries
-negatively with species richness [@winemiller_must_1989; @dunne_network_2006;
-@thebault_stability_2010], connectance had itself no effects on both total
-biomass and its temporal stability. On the other side, we found that species richness
-was negatively related to mean trophic level and mean trophic level
-covariated positively with total biomass and its temporal stability. Hence,
-species richness had a direct positive and negative effect respectively on
-total biomass and its stability but a negative and positive effect through
-mean trophic level. Theoretical work have shown that species richness can be
-linked to allocation of biomass toward higher trophic level
-[@thebault_relationship_2006; @schneider_animal_2016; @wang_biodiversity_2016].
-It indicates the importance to consider both species richness, network structure
-and their dependence. It calls for further investigations on how species
-diversity variation translates in network structure. Finally, common mechanisms
-might be at play in mono and multi-trophic communities such as while having same or
-opposite effects on total biomass and its temporal stability.
+@neutel_reconciling_2007].
+
+We found that connectance had no effect on temporal
+stability. This result previous precedent theoretical studies on the
+relationship between stability and network structure [@angelis_stability_1975;
+@may_will_1972; @thebault_stability_2010], although they considered different
+stability concepts and metrics [@arnoldi_resilience_2016].  Furthermore, we did
+not information about the interaction strength. Indeed, interaction strength is
+a crucial ingredient of stability [@may_will_1972; @angelis_stability_1975;
+@dunne_network_2006]. An alternative explanation can be that connectance
+increases inhomogeneously in the food web, for instance a higher connectance in
+lower trophic levels will not have the stabilising effects conferred by higher
+predation and omnivory in higher trophic levels. Further investigations on this
+effect is needed.
 
@@
 biomass, through a positive direct effect on species richness. These effects are
-well known in biogeography and in freshwater communities and are explained by a gain in species
-along thermal gradients, from smaller and colder streams, which support small
-food webs dominated by salmonids [@ogorman_chapter_2012;
-@emmrich_geographical_2014], to wider and warmer sections of stream networks,
-which contain larger food webs dominated by mesotrophic preators such as percids
-[@allan_stream_2007; @emmrich_geographical_2014]. Further in line with this
-pattern, we find that average stream size had a positive effect on total biomass
-through a positive effect on mean trophic level, consistent with the fact that
-food webs in wider streams, with a greater amount of running waters, are also
+well known in biogeography and in freshwater communities [@allan_stream_2007; @ogorman_chapter_2012;
+@emmrich_geographical_2014].
+Further in line with this pattern, we find that average stream size had a
+positive effect on total biomass through a positive effect on mean trophic
+level, consistent with the fact that food webs in wider streams, are also
 larger, and hence support more species and biomass [@allan_stream_2007]. Greater
@@
 structure can have independent and sometimes opposite effects on total biomass
-and its temporal stability. It opens a promising way for the understanding on
+and its temporal stability. Species richness had a direct positive and negative effect
+respectively on total biomass and its stability but a negative and positive
+effect through mean trophic level. It indicates the importance to consider both
+species richness, network structure and their dependence. It calls for further
+investigations on how species diversity variation translates in network
+structure. Our work opens a promising way for the understanding on
 how species interactions, of different types, can affect both synchrony and $\overline{CV_{sp}}$

### 2020-07-27 manuscript/bef_stability/manuscript.Rmd
Review until network building

@@
 species richness and network structure on total biomass and its temporal
-stability. We found that species richness and network structure had a positive
+stability. We found that species richness and average trophic level had a positive
 relationship with total biomass while they had respectively a negative and
 positive effect on temporal stability. We also found that species richness and
-network structure are not independent and that environment had a tremendous
+average trophic level are not independent and that environment had a tremendous
 effect on total biomass and its temporal stability notably through its effect on
-species richness and network structure. Our study highlights that the effects of
-species richness and network structure should be assessed conjointly and that it
+species richness and average trophic level. Our study highlights that the effects of
+species richness and average trophic level should be assessed conjointly and that it
 opens exciting perspectives on how environment, species richness and network
@@
 Species richness promotes higher biomass production in a variety of ecosystems
-and organisms. Indeed species richness generally increases primary productivity
+and taxons. Indeed species richness generally increases primary productivity
 and total biomass in experimental plant communities [@tilman_productivity_1996;
@@
 of the most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
+
 In contrast, positive [@wu_relationship_2015; @li_relationship_2018],
@@
 stabilizing effect on temporal stability [@tilman_biodiversity_2006;
-@olivier_urbanization_2020]. ^[Colin asked for a word about $cv_{sp}$ and
-stability but my opinion is that it is not necessary and that the depth of mecanisms are
-currently fairly explained for the introduction.] Such positive relationships
-between speciesrichness and temporal are also observed in natural settings, such
-as stream fish communities [@franssen_annual_2011], bird and butterfly
-communities [@olivier_urbanization_2020].
+@olivier_urbanization_2020]. Increasing, respectively decreasing, species
+variability results in respectively a decrease and an increase of temporal
+stability [@thibaut_understanding_2013]. Positive relationships between species
+variability and species richness have been observed in experimental grasslands
+[@tilman_biodiversity_2006], thereby decreasing stability. However, positive,
+neutral and negative relationships have been found in natural settings
+[@thibaut_understanding_2013; @olivier_urbanization_2020]. ^[Colin asked for a
+word about $cv_{sp}$ and stability but my opinion is that it
+is not necessary and that the depth of mecanisms are currently fairly explained
+for the introduction.] Overall, positive relationships between species richness and
+temporal stability are also observed in natural settings, such as stream fish communities
+[@franssen_annual_2011], bird and butterfly communities
+[@olivier_urbanization_2020].
 
@@
 species richness. Accounting for environment also allow for an overall
-comparison of the strength of the the effects of environment and community
+comparison of the strength of the effects of environment and community
 structure on total biomass and its stability.
@@
 
-Stream fish community constitutes a good model to study the effects of
-network structure on total biomass and its temporal stability. Despite that
-fish trophic interactions are difficult to measure in natural conditions, a consequent body
+Because their trophic interactions can be infered, stream fish community
+constitutes a good model to study the effects of network structure on total
+biomass and its temporal stability. Despite that fish trophic
+interactions are difficult to measure in natural conditions, a consequent body
 of literature supports that they can be inferred through body size and diet
@@
 interactions based on body size ratio was far better in stream ecosystems than
-in other aquatic and terrestrial ecosystems. Furthermore, the biotic activity in stream
-ecosystems determines for a large part the water quality
+in other aquatic and terrestrial ecosystems. Furthermore, the biotic activity in
+stream ecosystems determines for a large part the water quality
 [@cummins_structure_1974] and thus are crucial to maintain stream ecosystem
 properties. Lastly, most of the diversity-biomass and diversity-stability
-relationships, have been assessed in terrestrial ecosystems
-while there is a evident need to test such relationships in a variety of
-ecosystem types.
-
-We used the ONEMA dataset consisting in standardized sampling of fish
-communities in French streams [@edeline_ecological_2013]. 99 sites were sampled
-for more than 10 years spanning on the 1995-2018 period. We inferred
-1496 interaction networks, based on body size and food diet. The network
-structure was summarized by connectance and mean trophic level. Environment
-was characterized by stream size, altitude, slope, temperature, flow
-and enrichment. Finally total biomass was measured as median total biomass over
-the sampling period while its temporal stability was quantified as the inverse
-of the CV.
-
-We found a positive relationship between total biomass and species richness and
-network structure  while total biomass and species richness had respectively a
-negative and positive effect on temporal stability. We also showed a link
-between species richness and network structure. We found that the environment had
-a strong effect on total biomass and its temporal stability in particular by 
-its effect on species richness and network structure. We then discuss the
-possible mechanisms at play to explain those results and their implications on
-our knowledge of the effect of network structure on ecosystem properties.
+relationships, have been assessed in terrestrial ecosystems while there is a
+evident need to test such relationships in a variety of ecosystem types.
+
+Our study aims to document the relationships between foodweb structure and total
+biomass and its temporal stability in natural communities. To do so, we used the
+ONEMA dataset consisting in standardized sampling of fish communities in French
+streams [@edeline_ecological_2013]. 99 sites were sampled for more than 10 years
+spanning on the 1995-2018 period. We inferred 1496 interaction networks, based
+on body size and food diet. We question whether species richness, connectance
+and average trophic level increase, decrease or are not related to total biomass
+and its temporal stability. We further question whether the species richness,
+connectance and average trophic level have antagonistic or synergistic effect on
+total biomass and its temporal stability. Finally, we question if 
+ecosystem size and average temperature increase total biomass and its temporal
+stability.
+
+---
+#We used the ONEMA dataset consisting in standardized sampling of fish
+#communities in French streams [@edeline_ecological_2013]. 99 sites were sampled
+#for more than 10 years spanning on the 1995-2018 period. We inferred 1496
+#interaction networks, based on body size and food diet. The network structure
+#was summarized by connectance and mean trophic level. Environment was
+#characterized by stream size, altitude, slope, temperature, flow and enrichment.
+#Finally total biomass was measured as median total biomass over the sampling
+#period while its temporal stability was quantified as the inverse of the CV.
+#
+#We found a positive relationship between total biomass and species richness and
+#network structure while total biomass and species richness had respectively a
+#negative and positive effect on temporal stability. We also showed a link
+#between species richness and network structure. We found that the environment had
+#a strong effect on total biomass and its temporal stability in particular by 
+#its effect on species richness and network structure. We then discuss the
+#possible mechanisms at play to explain those results and their implications on
+#our knowledge of the effect of network structure on ecosystem properties.
+---
 
@@
 recorded during sampling as well as the sampling effort, quantified as the
-surface sampled.
+surface sampled (range XXX-XXX).
 
@@
 
-We kept only the most frequent of the two sampling protocols in each station and kept
-stations that had been sampled ten years or more. The median sampling month was
+The stations where the stream was of intermediate size could be sampled
+alternatively with one of the two sampling protocols. When it was the case, we
+kept only the most frequently used sampling protocol. Finally, we kept stations
+that had been sampled ten years or more. there was low heterogeneity of the sampling month
+within stations, with the median sampled month being 
 mid-August while the median of the standard deviation of the sampled month
-within station was $0.7$, i.e. there was low heterogeneity of the sampling month
-within stations. As the concept of community variability referred to variability
+within station was $0.7$. As the concept of community variability referred to variability
 around an equilibrium, which is rarely observed or difficult to characterize in
@@
 biomass were selected (detailed in supplementary methods). However, the results
-were robust to the relaxation of this hypothesis (Supplementary results). We
-retained 99 stations distributed over seven hydrographic basins (Figure
-\@ref(fig:matmet) B).
+were robust to the relaxation of this hypothesis (Supplementary results). These
+selections resulted in 99 stations distributed over seven hydrographic basins
+(Figure \@ref(fig:matmet) A).
 
@@
 
-The body size of the unmeasured individuals was inferred under the assumption
-that species body size followed a normal distribution whose mean and
+The body size of all fish individuals was not recorded when they were too
+numerous. The body size of the unmeasured individuals was inferred under the
+assumption that species body size followed a normal distribution whose mean and
 standard deviation were quantified from the recorded individuals of the sampling
-(See supplementary methods, Figure S1). The body mass of each individual was then estimated
-using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$ being the body mass
-in grams, $l$ the body size in millimeters and $i$ the individual), where the
-coefficients $0.01$ and $3.03$ comes from two meta-analyses
-[@lleonart_removing_2000; @froese_cube_2006]. Species biomass
-and total biomass at each sampling was then calculated by summing individual
-body masses. To account for the sampling effort, species biomass and total
-biomass have been related to the surface sampled, i.e. $gm^{-2}$.
-In the further analysis, the total biomass of a station has been defined as the
-median of the total biomass over time.
+(See supplementary methods, Figure S1). The body mass of each individual was
+then estimated using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$
+being the body mass in grams, $l$ the body size in millimeters and $i$ the
+individual), where the coefficients $0.01$ and $3.03$ comes from two
+meta-analyses [@lleonart_removing_2000; @froese_cube_2006]. Species biomass and
+total biomass at each sampling event was then calculated by summing individual body
+masses. To account for the variation in sampling effort among sites, species
+biomass and total biomass have been related to the surface sampled, i.e.
+$gm^{-2}$. In the further analysis, the total biomass of a station has been
+defined as the median of the total biomass over time.
 
@@
 time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being
-respectively the standard deviation and the temporal average of the biomass of
-the station $i$). Then, temporal stability was equal to $CV^{-1} = \mu
-\sigma^{-1}$.
-
-In order to describe the mechanisms driving temporal stability of biomass, we
+respectively the standard deviation and the temporal average of the annual total
+biomass of the station $i$). Then, temporal stability was equal to $CV^{-1} =
+\mu \sigma^{-1}$.
+
+In order to describe the mechanisms driving the temporal stability of biomass, we
 decomposed the $CV$ of total biomass ($CV_{com}$) in synchrony ($\phi$) and
@@
 
-Trophic interaction network was inferred from body size and ontogenic diet shift.
-Body size is a reasonable approximation widely used to infer trophic
-interactions [@gravel_inferring_2013; @brose_predator_2019;
+Trophic interaction network was inferred from body size and ontogenic diet shift
+following previous studies [@gravel_inferring_2013; @brose_predator_2019;
 @poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
-over lifespan. For example, alvins feed on plankton while adults may feed on
-algae or fishes. Accordingly, each fish species was divided in nine body size
-classes, each corresponding to a trophic species (Figure S2). A high congruence
-between inferred interactions and measured trophic interactions has been found
-at trophic species scale but not at the species scale [@jennings_weak_2001].
+over lifespan and thereby over body size. For example, alvins feed on plankton while adults may feed on
+algae, fishes, with bigger individuals eating bigger fishes. Each
+fish species was hence divided in nine body size classes, each corresponding to a
+trophic species (Figure S2), thereby increasing the accuracy of trophic
+interactions inference [@jennings_weak_2001]. HERE
 Additionally to the fish trophic species, we added seven resource nodes present
@@
 lower trophic levels. Strong top-down control can generate this pattern in pure
-trophic chain [@barbier_pyramids_2018; @shanafelt_stability_2018] but it is not
+trophic chain [@barbier_pyramids_2019; @shanafelt_stability_2018] but it is not
 clear if this theoretical prediction holds when considering omnivorous species
@@
 biomass, through a positive direct effect on species richness. These effects are
-well known in biogeography and in freshwater communities [@allan_stream_2007; @ogorman_chapter_2012;
-@emmrich_geographical_2014].
-Further in line with this pattern, we find that average stream size had a
-positive effect on total biomass through a positive effect on mean trophic
-level, consistent with the fact that food webs in wider streams, are also
-larger, and hence support more species and biomass [@allan_stream_2007]. Greater
-ecosystem size might be linked to a greater diversity of resources through
-habitat heterogeneity, on so higher species richness and total biomass by
-surface unit, through resource complementarity. Greater diversity of resources
-might also allow to maintain higher biomass in high trophic level
-[@post_ecosystem_2000; @doi_resource_2009]. Overall, our results indicate that
-environmental effects on total biomass operate primarily through changes in
-community structure. Furthermore, the positive effect of temperature on total
-biomass was of the magnitude of effects of network structure and species
-richness. This adds to the mounting body of work reporting important effects of
-temperature on the structure and biomass of aquatic system [e.g.
-@dossena_warming_2012; @edeline_ecological_2013; @emmrich_geographical_2014;
-@hattab_forecasting_2016].
+well known in biogeography and in freshwater communities [@allan_stream_2007;
+@ogorman_chapter_2012; @emmrich_geographical_2014].  Further in line with this
+pattern, we find that average stream size had a positive effect on total biomass
+through a positive effect on mean trophic level, consistent with the fact that
+food webs in wider streams, are also larger, and hence support more species and
+biomass [@allan_stream_2007]. Greater ecosystem size might be linked to a
+greater diversity of resources through habitat heterogeneity, on so higher
+species richness and total biomass by surface unit, through resource
+complementarity. Greater diversity of resources might also allow to maintain
+higher biomass in high trophic level [@post_ecosystem_2000; @doi_resource_2009].
+Overall, our results indicate that environmental effects on total biomass
+operate primarily through changes in community structure. Furthermore, the
+positive effect of temperature on total biomass was of the magnitude of effects
+of network structure and species richness. This adds to the mounting body of
+work reporting important effects of temperature on the structure and biomass of
+aquatic system [e.g.  @dossena_warming_2012; @edeline_ecological_2013;
+@emmrich_geographical_2014; @hattab_forecasting_2016].
 

### 2020-07-27 run/02_run_analysis.R

@@ -24,6 +24,7 @@ options(echo = TRUE)
 # Path to save network analysis:
 mypath <- rprojroot::find_package_root_file
 data_common <- mypath("data")
+source(mypath("R", "misc.R"))
 # Make network of species:
 if (!is.null(options("network.type")) & options("network.type") == "species") {
   dest_dir <- mypath("data", "species")
@@ -42,7 +43,6 @@ if (!is.null(options("network.type")) & options("network.type") == "species") {
 cat("Working directory:\n")
 cat(getwd(), "\n")
 
-source(mypath("R", "misc.R"))
 
 source(mypath("analysis", "00_get_network.R"))
 cat("Got networks!\n")

### 2020-08-14 manuscript/bef_stability/manuscript.Rmd
Review discussion

@@
 
-The effect of species richness and network structure on ecosystem properties has
-been central to ecology. It has been at the basis of the predictions of the
-effects of species richness and network structure on total biomass, productivity
-and stability. However, empirical data on the link between network structure and
-ecosystem properties are lacking. We used a dataset of standardized fish
-sampling in French stream running from 1995 to 2018. We inferred trophic
-interactions thanks to recorded body size and diet literature. We then
-investigate the direct and indirect effects of stream size and temperature,
-species richness and network structure on total biomass and its temporal
-stability. We found that species richness and average trophic level had a positive
-relationship with total biomass while they had respectively a negative and
-positive effect on temporal stability. We also found that species richness and
-average trophic level are not independent and that environment had a tremendous
-effect on total biomass and its temporal stability notably through its effect on
-species richness and average trophic level. Our study highlights that the effects of
-species richness and average trophic level should be assessed conjointly and that it
-opens exciting perspectives on how environment, species richness and network
-structure can jointly determine total biomass in natural communities.
-
-(208/150 words)
+---
+#Our aim was to evaluate the effects of the network structure on the total
+#biomass and its temporal stability in natural communities, which have been
+#poorly documented. To do so, we quantified the effects, directs and indirects,
+#of habitat properties, species richness, and food web structure, on the total biomass
+#and stability of fish communities, from the ONEMA fish dataset, across 99
+#locations in France from 1995 to
+#2018. We infered trophic interactions networks based on body size-dependency in
+#food diet from the literature and prey/predator body size ratio for piscivory ^[
+#We inferred trophic networks at the scale of trophic
+#species (i.e. nodes being body size classes) to take in account ontogenic diet
+#shifts and that fish-fish trophic interaction depends on body size ratio between
+#prey and predator. On the other side, the community metrics were defined at the
+#species level, (i.e.  species richness, average species CV and synchrony).  ].
+#We built structural equation models to disantangle the direct and indirect
+#effects of environmental drivers, species richness and network structure on both
+#total biomass and biomass stability.  
+---
+
+Species richness and network structure are at the basis of the predictions of
+total biomass, productivity and stability. However, empirical data linking
+network structure and ecosystem properties are lacking. We used a dataset of
+standardized fish sampling in French streams running from 1995
+to 2018. We inferred trophic interactions thanks to recorded body size and diet
+literature. We investigated the direct and indirect effects of stream size
+and temperature, species richness and network structure on total biomass and its
+temporal stability. Species richness and average trophic level had
+a positive relationship with total biomass while they had respectively a
+negative and positive effect on temporal stability. We found a strong link
+between species richness and network structure, highlighting that their effects
+should be assessed conjointly. Overall, our study opens fruitful perspectives on
+the link between species richness, network structure and ecosystem properties.
+
+(142/150 words)
 
@@
 
+---
 #### Biodiversity and ecosystem properties 
+---
 
@@
 
+---
 #### Species richness increases total biomass
+---
 
@@
 
+---
 #### Multitrophic communities
+---
 
 One has to notice that most of the empirical and experimental evidence of the
-positive effect of richness on biomass production and stablity through time
+positive effect of richness on biomass production and stability through time
 comes from studies focusing on one trophic level, generally primary producers or
@@
 
+---
 #### Problematic
+---
 
@@
 
+---
 #### Environment can mitigate community structure and ecosystem properties 
+---
 
@@
 
+---
 #### Stream fish communities is a good model to study effects of horizontal & vertical diversity
+---
 
@@
 
-#### Protocol
-
 Fish communities were monitored across stream sections in France on the period
@@
 
-#### Data selection
-
 The stations where the stream was of intermediate size could be sampled
@@
 ## Data preparation
-
-#### Biomass
 
@@
 
-####  Species richness
-
 Species richness was computed as the total number of species present over time
@@
 square meter sampled.
-
-### Network structure
-
-#### Trophic network inference
 
@@
 ```
-
-Trophic interaction network was inferred from body size and ontogenic diet shift
-following previous studies [@gravel_inferring_2013; @brose_predator_2019;
-@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
-over lifespan and thereby over body size. For example, alvins feed on plankton while adults may feed on
-algae, fishes, with bigger individuals eating bigger fishes. Each
-fish species was hence divided in nine body size classes, each corresponding to a
-trophic species (Figure S2), thereby increasing the accuracy of trophic
-interactions inference [@jennings_weak_2001]. HERE
-Additionally to the fish trophic species, we added seven resource nodes present
-in ontogenic food diet database: detritus, biofilm, phytoplankton, zooplankton,
-macrophages, phytobenthos and zoobenthos (grey nodes in Figure \@ref(fig:matmet)
-C & D). The ontogenic diet database was based on fishbase and literature. Each
-fish species had two or three life stages which are delimited by body size
-(Figure S2).
-
-The trophic interactions of fish trophic species was determined with the median
-of its body size range, hereafter midpoint. The midpoint of trophic species fall
-into one of the species life stage and a trophic link was set between the
-trophic species and the resources present in the life stage. If the trophic
-species is in a piscivorous life stage, the fish-fish trophic links was defined
-in two steps and based on the body size ratio between predators and prey
-[@mittelbach_ontogeny_1998; @claessen_impact_2002]. First of all, we defined the
-range predation window from 3% to 45% of the midpoint of the trophic species.
-Then, a trophic link was set between the piscivorous trophic species and every
-trophic species whose midpoint was included in the predation range (Figure S2).
-Lastly, the trophic links between resources was set according to the food diet
-data [@allan_stream_2007; @hart_handbook_2008].
-
 We determined the network structure in two steps: (1) build a metaweb describing the
@@
 
-For each trophic network, corresponding to a particular site and sampling, we
-computed two of the most commonly used network metrics to characterize the food
-web, namely the connectance and mean trophic level. Connectance describes 
+Trophic interaction network was inferred from body size and ontogenic diet shift
+following previous studies [@gravel_inferring_2013; @brose_predator_2019;
+@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
+over lifespan and thereby over body size. For example, alvins feed on plankton
+while adults may feed on algae, fishes, with bigger individuals eating bigger
+fishes. Each fish species was hence divided in nine body size classes, each
+corresponding to a trophic species (Figure S2). Additionally to the fish trophic
+species, we added seven resource nodes present in the ontogenic food diet database:
+detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
+zoobenthos (grey nodes in Figure \@ref(fig:matmet) C & D). The fish trophic
+species and the resources constituted the 412 nodes of the metaweb, 45 fish
+species divided into nine body classes plus seven resource nodes. The inference
+of trophic interactions was shown to be more accurate when considering body size
+classes, i.e. trophic species, rather than species [@jennings_weak_2001].
+
+The feeding interactions of a fish node, i.e a trophic species, are determined
+by both its species identity and its body size. Then, species identity allows to
+differentiate between piscivorous and non piscivorous species, to know on which
+resources the trophic species are feeding on and to know the minimum size at
+which a piscivorous species begins to feed on fishes. The ontogenic fish diet
+database was filled according to fishbase and literature (cf Bonnaffe ref). Each
+fish species had two or three life stages which are delimited by a body size
+range (Figure S2). The life stage of a fish trophic species was determined with
+the center of its body size range, hereafter midpoint (Figure S2).
+
+For a piscivorous trophic species, i.e. a piscivorous node, the fish-fish
+trophic links was defined in two steps and based on the body size ratio between
+predators and prey. First of all, the predation window of a piscivorous node was
+defined as 3% to 45% of its midpoint [@mittelbach_ontogeny_1998;
+@claessen_impact_2002; @hart_handbook_2008]. Then, a trophic link was set
+between the piscivorous node and every node whose midpoint
+was included in the predation range (Figure S2). The fish-resource trophic
+links, for piscivorous and non piscivorous nodes, were set between the
+trophic species and the resources nodes present in their life stage.
+Lastly, the trophic links between resource nodes were set according to the food
+diet data [@allan_stream_2007; @hart_handbook_2008].
+
+For each trophic network, corresponding to a particular site and year, we
+computed two of the most commonly used network metrics to characterize food
+webs, namely the connectance and mean trophic level. Connectance describes 
 the level of generalism in the network and is calculated as the number of actual
@@
 together ($C = L / N^2$, L and N being resp. the number of
-links and of trophic species plus resource nodes). The trophic level of the
-nodes was computed of the nodes that the predator nodes consumes
-to which is added one, obtained recursively by setting the trophic level of
-basal nodes to 1. The mean trophic level $\overline{T}$ was computed as the mean trophic level
+links and of trophic species plus resource nodes). 
+The mean trophic level $\overline{T}$ was computed as the mean trophic level
 weighted by the biomass of each trophic species (excluding resource nodes for
-which we had no biomass information), so
-$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and $B_i$
-being respectively the trophic level and the biomass of the node $i$.
+which we had no biomass information), so $\overline{T} = \sum_i^N{B_iT_i \times
+\sum_i^N{B_i}^{-1}}$, with $T_i$ and $B_i$ being respectively the trophic level
+and the biomass of the node $i$. The trophic level of the nodes was computed as
+one added to the average trophic level of its food item.
 
@@
 
-We characterised the sampled sites by their altitude, slope, distance from
+We characterised the sites by their altitude, slope, distance from
 source, stream width and depth and its strahler order, i.e. its position in the
@@
 [(www.naiades.eaufrance.fr)](http://www.naiades.eaufrance.fr/), we also
-got data on water temperature and flow as they affect the type of fish that 
-settling down [@franssen_annual_2011; @rolls_scaling_2018; @tonkin_flow_2018;
-@gutierrez-canovas_contrasting_2013] as well as BOD (Biological Oxygen Demand)
-as a proxy for eutrophisation. As data from the naiades database are not collected
-on the same site as our fish sampling sites, we performed an interpolation with
-spatial stream networks [@isaak_applications_2014; @hoef_ssn:_2014]. The
-interpolation procedure is detailed in supplementary (part 1.2).
-
-We had one environmental variable value for each site and sampling event, except
-for water temperature for which the record began in 2006. Then, the temporal
+got data on water temperature and flow. As data from the naiades database are
+not collected on the same site as our fish sampling sites, we performed an
+interpolation with spatial stream networks [@isaak_applications_2014;
+@hoef_ssn:_2014]. The interpolation procedure is detailed in supplementary (part
+1.2).
+
+We had one environmental variable value for each site and year event, except
+for water temperature for which the record began in 2006. Then, we computed the
 average and CV values of for water temperature, flow, BOD, river width and
@@
 the analysis the two first principal components based on the elbow method, on
-the eigen values distribution (Fig. S4). The two first principal components
-explained `r tot_var_expl_pca`% of the variance. A varimax axis rotation was
+the eigen values distribution (Figure S4). The two first principal components
+explained `r tot_var_expl_pca`% of the variance (Figure S4). A varimax axis rotation was
 performed to maximize the representation of the variables by the principal
-components (Figure S4). The two first principal components were used in the
-analysis, representing respectively the (1) river size (river width & depth),
-(2) altitude, slope and decreasing average temperature. Further description of
-the variables are detailed in supplementary information (part 1.3).
+components [@kaiser_varimax_1958; @revelle_psych_2019]. The first axis
+represented a gradient from small to big streams, characterized by their width
+and depth, but also a gradient from stream close to far from the source. The
+second axis represented a gradient of increasing average water temperature and
+decreasing altitude and slope. Further description of the variables are provided
+in supplementary information (part 1.3).
 
 ## Statistical analysis
-
-#### Summarise SEM statistical framework
 
@@
 indirect, between variables [@grace_structural_2008; @grace_causal_2014;
-@lefcheck_piecewisesem_2016; @grace_integrative_2016]. We built the biomass
-model by considering that environment
-can directly affect species richness and network structure, as well as total
-biomass (Figure \@ref(fig:sem-plot) B). 
-Food web structure was shown to be constrained by species richness [@winemiller_must_1989;
-@dunne_network_2006; @thebault_stability_2010]. 
-We assumed that both species richness and network structure directly affect
-total biomass (Figure \@ref(fig:sem-plot) B). In addition,
-we assumed that species richness would indirectly affect total biomass through
-network structure [@schneider_animal_2016].
-We used the same model structure for temporal variability (Figure
-\@ref(fig:sem-plot) A). The structural equation models used for total biomass
-and its temporal stability contains respectively 4 and 6 response variables, 35
-and 26 direct paths.
-
-Structural equation models were based on Gaussian linear models, some variables
+@lefcheck_piecewisesem_2016; @grace_integrative_2016]. The structural equation
+model explaining the annual total biomass set that environment
+can directly affect species richness and network structure, as well as annual total
+biomass (Figure \@ref(fig:sem-plot) B). We assumed that both species richness
+and network structure directly affect total biomass (Figure \@ref(fig:sem-plot)
+B) and that species richness constrained food web structure
+[@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010].
+
+We used the same model structure for temporal stability of biomass (Figure
+\@ref(fig:sem-plot) A). Instead of the annual total biomass, we set the
+synchrony and population variability which in turn determined the temporal
+stability of biomass. The structural equation models used for annual total
+biomass and its temporal stability contains respectively 4 and 6 response
+variables, 35 and 26 direct paths.
+
+The structural equation models were based on Gaussian linear models, some variables
 were logged to fulfill model assumptions (see residual plots and data
-transformation in supplementary informations, Table SXX). To account for the heterogeneity
-between the seven hydrographic basins, we set it as random effect on the
-intercept of the linear model. The absence of multicollinearity 
-was checked with Variance Inflation Factor (VIF, Table SXX). The slopes reported
+transformation in supplementary informations, Table SXX). We set the seven
+hydrographic basins as a random effect on the intercept of the linear models to
+account for their heterogeneity. We checked for the absence of multicollinearity 
+with Variance Inflation Factor (VIF, Table SXX). The slopes reported
 in the main text were standardized in order to compare their magnitude ($r_\delta
@@
 $\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
-predictive variable $x$ and of the response variable $y$). In the main text,
-only the slopes which had a $P$ value inferior to $0.05$ were reported (but see
-Table SXX and SXX).
+predictive variable $x$ and of the response variable $y$). The paths whose
+slope had a $P$ value inferior to $0.05$ were reported in the main text, all the
+path values are presented in Table SXX and SXX).
 
@@
 ```
-
-# Results
 
@@
 
+# Results
+
 Overall, the structural equation models explained a large part of the variation
 of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
-.45$, $.47$, $.49$ and $.38$) but not of mean trophic level ($R^2 =
-.18$, Figure \@ref(fig:sem-plot) C and D).
-
-## Total biomass
+.45$, $.47$, $.49$ and $.38$) but less so for mean trophic level ($R^2 =
+.18$, Figure \@ref(fig:sem-plot) C and D). We found that species richness had a
+significant negative effect on mean trophic level ($r_\delta = 
+`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_stab$total`$, Figure
+\@ref(fig:sem-plot) C and D), meaning that the effects of species richness and
+network structure are not independant.
+
+## Species richness and average trophic level are positively correlated to total biomass
 
@@
 `r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) D, Table \@ref(tab:indir-sem)),
-while connectance had no direct nor indirect significant effect on total biomass (Figure
+while connectance had no direct significant effect on total biomass (Figure
 \@ref(fig:sem-plot) D). The total effect of mean trophic level
@@
 
-Species richness had a significant negative effect on mean trophic level
-($r_\delta = `r rich_on_tlvl`$) and a strong negative effect on connectance
-($r_\delta = `r rich_on_stab$total`$, Figure \@ref(fig:sem-plot) C and D). But,
-in turn, connectance had no significant effect on total biomass.
-
-The environmental variables had no significant direct effects on total biomass
-(Table SXX), but indirect (Table \@ref(tab:indir-sem)). Average temperature and
-altitude respectively increased and decreased total biomass ($r_\delta =
-`r env_on_bm$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)), mainly through
-species richness ($r_\delta = `r env_on_bm$via_richness["log_RC2"]`$, Table
-\@ref(tab:indir-sem)). Average stream size had a positive effect on total
-biomass ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
-equally through species richness and mean trophic level ($r_\delta = 
+The two PCA axis capturing environmental variables had no significant direct effects on total biomass
+(Table SXX), but indirect (Table \@ref(tab:indir-sem)). The first axis, PCA1,
+related to the stream size was positively linked to total biomass ($r_\delta = 
+`r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
+through species richness and mean trophic level too ($r_\delta = 
 `r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
-resp., Table \@ref(tab:indir-sem)). Average temperature and altitude effects on
-total biomass were of the same magnitude than the effects on species richness
-and mean trophic level.
-
-## Temporal stability of biomass
-
-By its effect on synchrony and $\overline{CV_{sp}}$, species richness had a
+resp., Table \@ref(tab:indir-sem)). The second axis, PCA2, related the average
+annual temperature and reversely to altitude of the sites was positively related
+to total biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
+\@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
+`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The effect
+of PCA2 on total biomass was of the same magnitude than the effects on species
+richness and mean trophic level.
+
+## Temporal stability of annual biomass
+
+By its effects on synchrony and $\overline{CV_{sp}}$, species richness had a
 negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
@@
 increasing stability ($r_\delta = `r rich_on_stab$via_sync`$). On the other
-hand, species richness had a
-positive direct effect on $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$),
+hand, species richness had a positive direct effect on $\overline{CV_{sp}}$
+($r_\delta = `r rich_on_cv_sp$direct`$),
 thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
-\@ref(tab:indir-sem)). Finally, it was surprising that the negative
-effect of $\overline{CV_{sp}}$ on temporal stability was twice higher than the
-negative effect of synchrony (resp. $r_\delta = `r cv_sp_on_stab`$ and $r_\delta
-= `r sync_on_stab`$, Figure \@ref(fig:sem-plot) C).
-
-The mean trophic level had a direct negative effect on
-$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
-Figure \@ref(fig:sem-plot) C) and thereby had a total positive
-effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
-Table \@ref(tab:indir-sem)). The mean trophic level had no significant
-effect on synchrony and connectance had no significant direct, nor indirect
-effect on temporal stability (Figure \@ref(fig:sem-plot) C, Table SXX).
+\@ref(tab:indir-sem)). The negative effect of $\overline{CV_{sp}}$ on temporal
+stability was twice higher than the negative effect of synchrony (resp.
+$r_\delta = `r cv_sp_on_stab`$ and $r_\delta = `r sync_on_stab`$, Figure
+\@ref(fig:sem-plot) C).
+
 The total effect of mean trophic level on temporal stability of biomass was of
@@
 \@ref(tab:indir-sem)).
-
-Average temperature and altitude had a negative and a positive effect on
-temporal stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table
-\@ref(tab:indir-sem)) mainly through a direct positive effect on
-$\overline{CV_{sp}}$
-($r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)).
-Interestingly, average temperature (and opposite of altitude) had also a negative
-effect on temporal stability through species richness but a positive one through
+The mean trophic level had only a direct negative effect on
+$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
+Figure \@ref(fig:sem-plot) C) and thereby had a total positive
+effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
+Table \@ref(tab:indir-sem)). Connectance had no significant direct on either
+$\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
+(Figure \@ref(fig:sem-plot) C, Table SXX).
+
+The total effect of PCA2, related to average annual temperature and reversely to
+altitude, on temporal stability was of higher magnitude than the effects of
+species richness and mean trophic level (Table
+\@ref(tab:indir-sem)).
+The PCA2 had a total negative effect on temporal stability 
+($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
+PCA2 had an indirect positive effect on temporal stability through a
+direct positive effect on $\overline{CV_{sp}}$ ($r_\delta = 
+`r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)) but also a
+negative on through species richness but a positive one through
 mean trophic level 
@@
 $r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-sem)).
-This was also true for average river size but effects were weak. Finally, the
-effect of average temperature on temporal stability was of higher magnitude than
-the effects of species richness and mean trophic level (Table
-\@ref(tab:indir-sem)).
-
-```{r indir-stab, cache = FALSE}
+This was also true for the PCA1, related to stream size, but effects were weaker
+than for PCA2.
+
+```{r indir-stab, cache = TRUE, results = TRUE}
 caption_sem <- paste0(
@@
 
-Our aim was to evaluate the effects of the network structure on the total
-biomass and its temporal stability in natural communities, which have been
-poorly documented. To do so, we quantified the effects, directs and indirects,
-of habitat properties, species richness, and food web structure, on the total biomass
-and stability of fish communities, from the ONEMA fish dataset, across 99
-locations in France from 1995 to
-2018. We infered trophic interactions networks based on body size-dependency in
-food diet from the literature and prey/predator body size ratio for piscivory ^[
-We inferred trophic networks at the scale of trophic
-species (i.e. nodes being body size classes) to take in account ontogenic diet
-shifts and that fish-fish trophic interaction depends on body size ratio between
-prey and predator. On the other side, the community metrics were defined at the
-species level, (i.e.  species richness, average species CV and synchrony).  ].
-We built structural equation models to disantangle the direct and indirect
-effects of environmental drivers, species richness and network structure on both
-total biomass and biomass stability.  We found that species richness and mean
+We found that species richness and mean
 trophic level had a positive effect on total biomass. In contrast, species
@@
 @wu_relationship_2015; @li_relationship_2018]. The positive effect of species
-richness on total biomass might be due to resource use complementarity, which is
+richness on total biomass might be due to resource use complementarity [@carey_determining_2011], which is
 held by niche differentiation [@loreau_biodiversity_1998;
-@loreau_partitioning_2001] or might be due to a positive selection effect
-[@tilman_plant_1997; @loreau_partitioning_2001], which leads to the dominance of
-the most productive species. The study of @carey_determining_2011 showed that
-resource complementarity might be the main driver in fish communities.
+@loreau_partitioning_2001] or to the higher probability to get high biomass
+species  with higher species richness [@loreau_biodiversity_2001].
 
@@
 opposite relationship in natural grassland [@yang_effects_2011] or a marginal
-one in natural forests [@declerck_species_2006]. A first step to identify the
-mechanisms behind those contrasting patterns is be to look at the effects of
-species richness on synchrony and $\overline{CV_{sp}}$, which constitute the two
-components of temporal stability quantified as CV [@loreau_species_2008;
-@thibaut_understanding_2013].
-
-We found that species richness decreases synchrony, thereby increasing
-stability. Species richness can reduce synchrony by decreasing of population
-size, thus raising the role of demographic stochasticity on population dynamics
+one in natural forests [@declerck_species_2006].
+
+A first step to identify the mechanisms behind those contrasting patterns is to
+look at the effects of species richness on synchrony and $\overline{CV_{sp}}$.
+As most studies on the topic, in experimental grasslands
+[@isbell_biodiversity_2009; @roscher_identifying_2011], in natural communities
+of birds, bats, grasslands, bats and butterflies [@bluthgen_land_2016;
+@olivier_urbanization_2020], we found that species richness decreases synchrony,
+thereby increasing stability. However, no relation has been found in
+natural forests [@declerck_species_2006]. Our study thus
+highlights that species richness might also decrease synchrony in empirical
+trophic communities. Species richness can reduce synchrony when a given
+increase in species richness leads to a decrease of population sizes, which in
+turn raises the role of demographic stochasticity on population dynamics
 [@loreau_species_2008] but also in the case where species have different
-responses to environmental variation [@loreau_species_2008]. While a negative
-effect of species richness on synchrony is generally found in experimental
-grasslands [@isbell_biodiversity_2009; @roscher_identifying_2011], no relation
-has been found in natural forests [@declerck_species_2006], but negative
-relationships have been found in natural communities of birds, bats, grasslands,
-bats and butterflies [@bluthgen_land_2016; @olivier_urbanization_2020]. Our
-study thus highlights that species richness might also decrease synchrony in
-empirical trophic communities.
+responses to environmental variation [@loreau_species_2008].
 
@@
 @olivier_urbanization_2020], negative and neutral relationships have been found
-in butterfly and bat communities. @thibaut_understanding_2013 proposed that a
-strongly uneven biomass distribution across population and that the biomass
-variance of population increases much faster than its mean can generate a
-positive effect of species richness on population ($\overline{CV_{sp}}$)
-stability.
-
-It was unexpected that the average population $\overline{CV_{sp}}$
-had a stronger negative effect on biomass stability than synchrony
-[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
-negative effect of species on temporal stability of biomass. The lower effect of
-synchrony can be explained by the the presence of generalist predator in stream
-communities, which can raise synchrony between prey species which shares the
-same predator [@raimondo_interspecific_2004]. Alternatively, uneveness can also
-raise synchrony between species [@thibaut_understanding_2013], in line with
-mechanisms which can raise positive relationships between $\overline{CV_{sp}}$
-and species richness.
+in butterfly and bat communities. However, the ecological mechanisms leading to
+such relationships in foodwebs are not known and this question deserves further
+research.
+
+---
+#@thibaut_understanding_2013 proposed that a
+#strongly uneven biomass distribution across populations and that the biomass
+#variance of population increases much faster than its mean can generate a
+#positive effect of species richness on population ($\overline{CV_{sp}}$)
+#stability.
+---
 
@@
 with body size, it is expected that the more the average
-biomass is located at higher trophic level, the more the total biomass increase.
-A mechanism, suggested by experimental and theoretical work, can be that a
+biomass is located at higher trophic level, the higher the total biomass is. 
+Experimental and theoretical work suggested that a
 higher trophic level is the result of a stronger top-down effect, meaning higher
@@
 
-We found that species richness was negatively related to mean trophic level and 
-connectance [@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010]. In
-contrast, connectance had no effect on total biomass. One might have expected
+In contrast, connectance had no effect on total biomass. One might have expected
 that an increase in connectance should translate in higher resource transfer
 efficiency between prey and predators and so results in higher total biomass in
-the fish compartment. A reason for such an absence of an effect might be due the
-absence of information that we have about the other compartments of the
-community, i.e, the primary producers, zooplankton and zoobenthos. Further
-research are needed to assess the role of the trophic structure with a more
-complete communities.
+the fish compartment. A reason for such an absence of an effect might be due our
+data lacks informations about the lower compartments of the
+community, i.e, the primary producers, zooplankton and zoobenthos.
 
@@
 effect on $\overline{CV_{sp}}$, thereby increasing average species stability. It
-means that species at higher trophic level are more stable than the species at
-lower trophic levels. Strong top-down control can generate this pattern in pure
-trophic chain [@barbier_pyramids_2019; @shanafelt_stability_2018] but it is not
-clear if this theoretical prediction holds when considering omnivorous species
-[@wang_biodiversity_2016] and if other mechanisms can generate the same pattern
-[@thibaut_understanding_2013]. Another explanation is that the fishes at higher
-trophic levels are not more stable themselves, but rather allow for stronger
-top-down control and resource complementarity and thus reduce biomass
-fluctuations in lower trophic levels [@rooney_structural_2006;
-@neutel_reconciling_2007].
-
-We found that connectance had no effect on temporal
-stability. This result previous precedent theoretical studies on the
-relationship between stability and network structure [@angelis_stability_1975;
-@may_will_1972; @thebault_stability_2010], although they considered different
-stability concepts and metrics [@arnoldi_resilience_2016].  Furthermore, we did
-not information about the interaction strength. Indeed, interaction strength is
-a crucial ingredient of stability [@may_will_1972; @angelis_stability_1975;
-@dunne_network_2006]. An alternative explanation can be that connectance
-increases inhomogeneously in the food web, for instance a higher connectance in
-lower trophic levels will not have the stabilising effects conferred by higher
-predation and omnivory in higher trophic levels. Further investigations on this
-effect is needed.
+might be because species at higher trophic level are more stable than the species at
+lower trophic levels as predicted by food chains models [@barbier_pyramids_2019;
+@shanafelt_stability_2018] but it is not sure that it holds when considering
+omnivorous species [@wang_biodiversity_2016] and if other mechanisms can
+generate the same pattern [@thibaut_understanding_2013]. An alternative
+explanation is that higher mean trophic level leads to stronger top-down control
+and resource complementarity and thus reduce biomass fluctuations in lower
+trophic levels [@rooney_structural_2006; @neutel_reconciling_2007].
+
+We found that connectance had no effect on temporal stability. This result
+contradicts previous precedent theoretical studies on the relationship between
+stability and network structure [@angelis_stability_1975; @may_will_1972;
+@thebault_stability_2010], although they considered different stability concepts
+and metrics [@arnoldi_resilience_2016]. However, our measure of connectance
+suffers limitation and further research should examine
+the effect of connectance on temporal stability in empirical foodwebs.
 
@@
 
-We find that environmental drivers overall affect total biomass indirectly,
-through changes in network structure and species richness. This contrasts with
-research in plant communities that showed that total biomass was directly driven
-by environmental factors [@grace_integrative_2016], and in particular by
-warming, which has contrasted effects on biomass in aquatic communities
-[@yvondurocher_warming_2011; @dossena_warming_2012]. Average temperature,
-inverse altitude, and average stream size had indirect positive effects on total
-biomass, through a positive direct effect on species richness. These effects are
-well known in biogeography and in freshwater communities [@allan_stream_2007;
-@ogorman_chapter_2012; @emmrich_geographical_2014].  Further in line with this
-pattern, we find that average stream size had a positive effect on total biomass
-through a positive effect on mean trophic level, consistent with the fact that
-food webs in wider streams, are also larger, and hence support more species and
-biomass [@allan_stream_2007]. Greater ecosystem size might be linked to a
-greater diversity of resources through habitat heterogeneity, on so higher
-species richness and total biomass by surface unit, through resource
-complementarity. Greater diversity of resources might also allow to maintain
+Contrasting with a previous study in experimental plant communities
+[@grace_integrative_2016] and in fish communities [@yvondurocher_warming_2011;
+@dossena_warming_2012], we found that environmental drivers overall affect total
+biomass indirectly rather than directly. In line with previous studies, we found
+that the two PCA axis, respectively related to stream size and temperature, 
+had indirect positive effects on total biomass, through a positive direct effect
+on species richness [@allan_stream_2007; @ogorman_chapter_2012;
+@emmrich_geographical_2014].
+
+Consistent with research showing that food webs in wider streams, are also
+larger, and hence support more species and biomass [@allan_stream_2007], we
+found that the PCA axis related to stream size had a positive effect on total
+biomass through a positive effect on mean trophic level. Greater ecosystem size
+might provide a greater diversity of resources through habitat heterogeneity,
+and so higher species richness and total biomass by surface unit, through
+resource complementarity. Greater diversity of resources can also maintain
 higher biomass in high trophic level [@post_ecosystem_2000; @doi_resource_2009].
-Overall, our results indicate that environmental effects on total biomass
-operate primarily through changes in community structure. Furthermore, the
-positive effect of temperature on total biomass was of the magnitude of effects
-of network structure and species richness. This adds to the mounting body of
-work reporting important effects of temperature on the structure and biomass of
-aquatic system [e.g.  @dossena_warming_2012; @edeline_ecological_2013;
-@emmrich_geographical_2014; @hattab_forecasting_2016].
-
-Interestingly, stream flow and size, inverse altitude, and temperature had
-indirect effects on stability through two conflicting pathways, either
-stabilising, involving network structure, or destabilising, involving
-species richness. The first pathway consists in a positive effect of
-temperature and stream properties on mean trophic level, in line with the idea
-that wider streams and warmer conditions are favourable to mesotrophic predators
-[@allan_stream_2007; @emmrich_geographical_2014], which in turn stabilises
-biomass fluctuations, possibly due to increased top-down regulation (as
-discussed above). The second pathway consists in a positive effect of
-temperature and stream properties (width, flow, inverse altitude) on species
-richness, which itself has a destabilising effect (see discussion on species).
-This result is interesting in that though both pathways had not been evidenced
-to be jointly to play, as far as we know. Furthermore, it is unclear
-as to which pathway is dominating, and under which circumstance, opening an
-interesting avenue for further investigations. Overall our study highlights
-that environmental factors should not be ignored in natural communities studies
-and that its effects can be mainly indirect and in this case, path analysis
-should more relevant than bivariate relationships
-[@grace_causal_2014; @grace_integrative_2016].
+Furthermore, the positive effect of the PCA axis related to temperature on total
+biomass was of the magnitude of effects of network structure and species
+richness, in line with the mounting body of work reporting important effects of
+temperature on the structure and biomass of aquatic system [e.g.
+@dossena_warming_2012; @edeline_ecological_2013; @emmrich_geographical_2014;
+@hattab_forecasting_2016].
+
+Interestingly, the two PCA axis related to environmental conditions had indirect
+effects on stability through two conflicting pathways, either stabilising, via
+network structure, or destabilising, via species richness. The first pathway
+consists in a positive effect of temperature and stream properties on mean
+trophic level, in line with the idea that wider streams and warmer conditions
+are favourable to mesotrophic predators [@allan_stream_2007;
+@emmrich_geographical_2014], which in turn stabilises biomass fluctuations,
+possibly due to increased top-down regulation. The second pathway consists in a
+positive effect of temperature and stream size on species richness, which itself
+has a destabilising effect.  This result is interesting in that though both
+pathways had not been evidenced to be jointly to play, as far as we know.
+Furthermore, it is unclear under which circumstance which pathway is dominating,
+opening an interesting avenue for further investigations.
+
+---
+## Final thoughts about empirical foodwebs
+
+#It was unexpected that the average population $\overline{CV_{sp}}$
+#had a stronger negative effect on biomass stability than synchrony
+#[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
+#negative effect of species on temporal stability of biomass. The lower effect of
+#synchrony can be explained by the  presence of generalist predators in stream
+#communities, which can raise synchrony between prey species which shares the
+#same predator [@raimondo_interspecific_2004]. Uneven population biomass within
+#communities also raise synchrony between species [@thibaut_understanding_2013].
+
+#As found in other studies, we found that species richness was negatively related
+#to mean trophic level and connectance [@winemiller_must_1989;
+#@dunne_network_2006; @thebault_stability_2010]. Species richness had thus a
+#consistent destabilising effect on temporal stability of biomass directly and
+#through average trophic level, but it has a direct positive effect on total annual
+#biomass directly but a negative one through the decrease of average trophic
+#level. It highlights the importance to consider several aspects of
+#network structure to order to improve our understanding of the drivers of
+#community structure and stability.
+---
 
@@
 
-We aimed to assess the effect of species richness & network structure on empirical
-trophic communities. While theoretical ecology has focused on the effects of
-network structure on stability, empirical ecology has focused on species richness
-and ignored network structure. Furthermore, both fields have largely used
-different stability metrics. We showed that species richness and network
-structure can have independent and sometimes opposite effects on total biomass
-and its temporal stability. Species richness had a direct positive and negative effect
-respectively on total biomass and its stability but a negative and positive
-effect through mean trophic level. It indicates the importance to consider both
-species richness, network structure and their dependence. It calls for further
-investigations on how species diversity variation translates in network
-structure. Our work opens a promising way for the understanding on
-how species interactions, of different types, can affect both synchrony and $\overline{CV_{sp}}$
-in different ecosystems. However, the mecanisms leading to such patterns remains
-to be elucidated. The reconstruction of ecological networks based on body size
-and food diet litterarure can be a first approach to document such
-relationships, however it will not compensate for close evaluation of measured
-interaction strength. We also believe that SEM methods are particularly helpful
-to assess complex relationship between environment, community structure and
-ecosystem properties in empirical data which necessitate to move from simple
-bivariate relationships [@grace_integrative_2016]. We believe that the
-integration of network structure and species interaction will improve our
-understanding of the mechanisms driving ecosystem properties.
+Our study extends the assessment of the effect of species richness on total
+annual biomass and its temporal stability in natural settings to the case of
+foodwebs, while including network structure. Species richness had a direct
+positive and negative effect respectively on total biomass and its stability but
+mean trophic level had a positive effect on both. We furthermore found that
+species richness had antagonistic effects on total biomass, through its effect
+on mean trophic level. Our study thus highlights the importance to consider both
+species richness, network structure and their dependence. However, the
+mechanisms leading to such remains to be elucidated. One limitation of our study
+is that the use of inferred networks and the lack of information about the
+foodwebs outside fishes. Our findings and interpretation could be confirmed by
+experimental and theoretical works considering foodwebs instead of pure
+foodchains. It would be promising to explore the effects of omnivory and
+ontogeny, i.e. relaxing the foodchain assumption, on the link between network
+structure and ecosystem functioning.
+
+While theoretical ecology has focused on the effects of network structure on
+stability, empirical ecology has focused on species richness and ignored network
+structure. Furthermore, both fields have largely used different stability
+metrics. Therefore, our work aims to contribute at bridging this gap between
+theoretical and empirical ecology. Finally, we found that environmental gradient
+related to temperature and ecosystem size have antagonistic effects on biomass
+temporal stability, positive through mean trophic level and negative through
+species richness. Further research is needed to find the mechanisms behind those
+pathways, that are crucial in context of global changes.
 

### 2020-08-17 manuscript/bef_stability/appendix.Rmd

@@
 package <- c("openSTARS", "SSN", "nlme", "piecewiseSEM")
-purrr::map_(package, ~ toBibtex(citation(.x)))
+purrr::map(package, ~ toBibtex(citation(.x)))
 
@@
 
-#### Obtain network of a community
-
-The trophic network of a community (i.e. one network for each fish community
+#### Local trophic network
+
+The local trophic network (i.e. one network for each fish community
 sampling) was obtained by determining the trophic species of each fish
@@
 myload(fourier, dir = mypath("data-raw", "polluants"))
-myload(flow_temp_metrics, dir = mypath("data"))
+myload(flow_temp_metrics, station_analysis, the_8_hydrologic_basin, dir = mypath("data"))
 sf_pressure <- station_analysis %>% 
@@
 which had the least standard deviation.
+
+# Species list and food diet data
+
+```{r sp-list}
+myload(species, fish_diet_shift, dir = mypath("data"))
+kable(species,
+  format = "latex",
+  booktabs = T,
+  label = paste0("indir-sem"),
+  caption = "Fish species list."
+  ) %>%
+kable_styling(latex_options =c("striped", "scale_down"))
+
+```
+
+```{r food}
+kable(fish_diet_shift,
+  format = "latex",
+  booktabs = T,
+  label = paste0("indir-sem"),
+  caption = "Ontogenic diet shift for each species"
+  ) %>%
+kable_styling(latex_options =c("striped", "scale_down"))
+
+```
 

### 2020-08-17 manuscript/bef_stability/manuscript.Rmd

@@
 title: Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
-author: Alain Danet, Maud Mouchet, (Willem Bonnaffe ici?), Elisa Thebault and Colin Fontaine
+author: Alain Danet, Maud Mouchet, Willem Bonnaffe, Elisa Thebault, Colin Fontaine
 date: \today 
@@
 - Number of words:
-  - Abstract: 208 
-  - Main text: XXXX
+  - Abstract: 142 
+  - Main text: 4929
 
@@
 - Number of figures: 2
-- Number of tables: 2
+- Number of tables: 1
 - Number of text boxes: 0
@@
   - alain.danet@mnhn.fr 
-  - +331XXXXXXXX
+  - +33140798134
 
@@
 the link between species richness, network structure and ecosystem properties.
-
-(142/150 words)
 
@@
   each color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
-  "(C) Subset over network variation through time."
-)
-```
-
-```{r matmet, fig.cap = matmet_cap, cache = FALSE}
+  "(C) Subset over network variation through time. The species names
+  corresponding to the three digit codes are found in Table SXX."
+)
+```
+
+```{r matmet, fig.cap = matmet_cap}
 myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))
@@
 
-```{r get-data, cache = FALSE}
+```{r get-data}
 library(piecewiseSEM)
@@
 
-```{r indir-stab, cache = TRUE, results = TRUE}
+```{r indir-stab, results = TRUE}
 caption_sem <- paste0(
@@
 
-#### Hat
-
 We found that species richness and mean
@@
 ## Species richness increased total biomass but decreased its temporal stability
-
-#### Species and total biomass
 

### 2020-09-15 manuscript/bef_stability/manuscript.Rmd
Review by elisa + put CV/synchrony comparison

@@
 - Number of words:
-  - Abstract: 142 
+  - Abstract: 184
   - Main text: 4929
@@
 
----
-#Our aim was to evaluate the effects of the network structure on the total
-#biomass and its temporal stability in natural communities, which have been
-#poorly documented. To do so, we quantified the effects, directs and indirects,
-#of habitat properties, species richness, and food web structure, on the total biomass
-#and stability of fish communities, from the ONEMA fish dataset, across 99
-#locations in France from 1995 to
-#2018. We infered trophic interactions networks based on body size-dependency in
-#food diet from the literature and prey/predator body size ratio for piscivory ^[
-#We inferred trophic networks at the scale of trophic
-#species (i.e. nodes being body size classes) to take in account ontogenic diet
-#shifts and that fish-fish trophic interaction depends on body size ratio between
-#prey and predator. On the other side, the community metrics were defined at the
-#species level, (i.e.  species richness, average species CV and synchrony).  ].
-#We built structural equation models to disantangle the direct and indirect
-#effects of environmental drivers, species richness and network structure on both
-#total biomass and biomass stability.  
----
-
-Species richness and network structure are at the basis of the predictions of
-total biomass, productivity and stability. However, empirical data linking
-network structure and ecosystem properties are lacking. We used a dataset of
-standardized fish sampling in French streams running from 1995
-to 2018. We inferred trophic interactions thanks to recorded body size and diet
-literature. We investigated the direct and indirect effects of stream size
-and temperature, species richness and network structure on total biomass and its
-temporal stability. Species richness and average trophic level had
-a positive relationship with total biomass while they had respectively a
-negative and positive effect on temporal stability. We found a strong link
-between species richness and network structure, highlighting that their effects
-should be assessed conjointly. Overall, our study opens fruitful perspectives on
-the link between species richness, network structure and ecosystem properties.
+Both the relations between diversity and ecosystem functioning, and between food
+web complexity and stability, have received considerable attention during the
+last decades in ecology. While the former relation remains rarely investigated
+in the context of food webs, especially in empirical studies explicitly
+considering food web structures, the latter has been mainly the focus of
+theoretical studies and empirical tests are critically missing. Here we link
+species richness, food web structure and total biomass and its stability by
+using a dataset of standardized fish sampling in French streams running from
+1995 to 2018. We inferred trophic interactions thanks to recorded body size and
+diet literature. We reveal that species richness and average trophic level had a
+positive relationship with total biomass of fish communities while they had
+respectively a negative and positive effect on its temporal stability. We
+also found that the effects of stream size and temperature on total biomass and
+stability are partly mediated by their effects on diversity and food web
+structure. Overall, our study opens fruitful perspectives on the link between
+species richness, network structure, ecosystem properties and their stability.
 
@@
 Species richness promotes higher biomass production in a variety of ecosystems
-and taxons. Indeed species richness generally increases primary productivity
-and total biomass in experimental plant communities [@tilman_productivity_1996;
+and taxons. Indeed species richness generally increases primary productivity and
+total biomass in experimental plant communities [@tilman_productivity_1996;
 @grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@@
 [@mulder_physical_2001], stream feeders [@cardinale_species_2002] and aquatic
-bacterial consumers [@pennekamp_biodiversity_2018]. Theoretical models also
-predict this pattern in plant communities [@tilman_plant_1997;
-@loreau_partitioning_2001] and food webs [@schneider_animal_2016]. Resource use
-complementarity and selection effects have been proposed to elucidate the
-positive effect of species richness on productivity. The complementarity in
-resource use, rising through niche differentiation and interspecific
-facilitation, increase the total amount of resource used
-[@loreau_biodiversity_1998; @cardinale_species_2002; @loreau_partitioning_2001].
-A positive selection effect arises when species richness leads to an higher dominance
-of the most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
-
-In contrast, positive [@wu_relationship_2015; @li_relationship_2018],
-negative or non significant effects of species richness on total biomass have been found
-in natural forests [@szwagrzyk_above-ground_2007; @jacob_productivity_2010;
-@seidel_relationship_2013]. Some authors suggest that the lack of resource
-complementarity or environmental harshness might be responsible for an absence or a
-negative effect of species richness [@loreau_partitioning_2001; @he_global_2013;
-@wu_relationship_2015]. Overall, under what conditions and through what
-mechanisms we should observe positive relationships between biomass and species
-richness in natural settings remains an open question.
+bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
+ecosystems and taxons studied, the relation between diversity and ecosystem
+functioning remains traditionally focused on single trophic levels, ignoring the
+effects of food web structure. Theoretical models have recently extended
+classical theoretical studies in plant communities [@tilman_plant_1997;
+@loreau_biodiversity_2001] to food webs [@thebault_food-web_2003;
+@poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018].
+These models show that both resource use complementarity and selection effects,
+the two main mechanisms previously highlighted in single-trophic studies, are
+also important to understand diversity effects in food webs
+[@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
+However, they also reveal new mechanisms such as positive effects of diversity
+of trophic levels, i.e. associated with higher trophic levels, on ecosystem
+functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
+web properties, such as interaction distribution and strength, affect the
+distribution of biomass among adjacent trophic levels
+[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
+Empirical studies are however missing to assess further how food web structure,
+in conjunction with species diversity, affect total biomass production and other
+ecosystem properties.
+
+---
+#### Single and multitrophic communities
+---
 
 Many studies showed that species richness also increases temporal stability of
-communities,
-i.e. variation through time, often quantified by the temporal CV. Such positive
-relationships between species richness and temporal stability have been reported
-in experimental grasslands and aquatic bacterial systems
-[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018]. Theoretical works
-have clarified which mechanisms generate this positive relationship between
-species richness and temporal stability [@loreau_species_2008;
-@thibaut_understanding_2013], (1) species synchrony and (2) species variability. Species
-synchrony quantify to what extent the fluctuations of abundances or biomasses
-through time are correlated among species. A low synchrony in species
-fluctuations, i.e.  asynchrony, is synonymous of compensatory dynamic, where the
-decrease in abundance of a species is compensated by the increase of an other.
-Asynchrony is generally the main mechanism whereby species richness has a
-stabilizing effect on temporal stability [@tilman_biodiversity_2006;
-@olivier_urbanization_2020]. Increasing, respectively decreasing, species
-variability results in respectively a decrease and an increase of temporal
-stability [@thibaut_understanding_2013]. Positive relationships between species
-variability and species richness have been observed in experimental grasslands
-[@tilman_biodiversity_2006], thereby decreasing stability. However, positive,
-neutral and negative relationships have been found in natural settings
-[@thibaut_understanding_2013; @olivier_urbanization_2020]. ^[Colin asked for a
-word about $cv_{sp}$ and stability but my opinion is that it
-is not necessary and that the depth of mecanisms are currently fairly explained
-for the introduction.] Overall, positive relationships between species richness and
-temporal stability are also observed in natural settings, such as stream fish communities
-[@franssen_annual_2011], bird and butterfly communities
-[@olivier_urbanization_2020].
-
----
-#### Multitrophic communities
----
-
-One has to notice that most of the empirical and experimental evidence of the
-positive effect of richness on biomass production and stability through time
-comes from studies focusing on one trophic level, generally primary producers or
-primary consumers. Natural ecosystems generally include more than one or two
-trophic levels and there is no certainty that the relationship between species
-richness and total biomass and its temporal stability for a given trophic level
-is representative of this relationship at the food web level. Theoretical
-studies showed that food web properties, such as interaction distribution and
-strength, affect the distribution of biomass among adjacent trophic levels,
-[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019]. A
-large body of theoretical studies links the propagation of perturbations to the
-foodweb structure [@may_will_1972; @angelis_stability_1975; @dunne_network_2006;
-@neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011],
-or trophic chain [@shanafelt_stability_2018; @wang_biodiversity_2016;
-@barbier_pyramids_2019]. To date, we have few evidence on the relationship
-between network structure and total biomass and its temporal stability in
-empirical multitrophic communities.
+communities, i.e. variation through time, often quantified by the temporal CV.
+Such positive relationships between species richness and temporal stability have
+been reported in experimental grasslands and aquatic bacterial systems
+[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018] as well as in natural
+settings, such as stream fish communities [@franssen_annual_2011], bird and
+butterfly communities [@olivier_urbanization_2020]. However, this relation has
+been mostly explored in single trophic level systems or without accounting for
+food web structure, even more so than the relation between diversity and biomass
+production. Single-level theoretical works have clarified which mechanisms
+generate this positive relationship between species richness and temporal
+stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
+synchrony and (2) species variability. Species synchrony quantify to what extent
+the fluctuations of abundances or biomasses through time are correlated among
+species. A low synchrony in species fluctuations, i.e.  asynchrony, is
+synonymous of compensatory dynamic, where the decrease in abundance of a species
+is compensated by the increase of an other.  Asynchrony is generally the main
+mechanism whereby species richness has a stabilizing effect on temporal
+stability [@tilman_biodiversity_2006; @olivier_urbanization_2020] while
+positive, neutral and negative relationships have been found in natural settings
+[@tilman_biodiversity_2006; @thibaut_understanding_2013;
+@olivier_urbanization_2020]. In addition to diversity, food web structure is
+expected to strongly affect the stability of communities and ecosystems, as
+outlined by the large body of theoretical studies on this topic [@may_will_1972;
+@dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
+@stouffer_compartmentalization_2011]. For instance, predation has cascading
+effects on species variability [@shanafelt_stability_2018] and it affects as
+well synchrony between species [@teng_dynamics_2004]. Despite a long-standing
+interest on the links between food web complexity and stability in ecology, to
+date we have very few evidence on the relationship between network structure and
+the temporal stability of species and total biomass in empirical multitrophic
+communities.
 
@@
 should modulate total biomass and stability of communities. The effects of
-species richness and network structure are potentially conflicting or
-synergistic in such a way that they need to be addressed jointly. Yet, there is
-no direct empirical evidence to date for the combined effects of species
-richness and network structure on total biomass and stability in natural
-communities.
+species richness and network structure, such as connectance and average trophic
+level, are potentially conflicting or synergistic in such a way that they need
+to be addressed jointly. Yet, there is no direct empirical evidence to date for
+the combined effects of species richness and network structure on total biomass
+and stability in natural communities.
+
+Although the relationships between diversity, total biomass and its stability in
+natural systems can be similar to those found in experimental communities [e.g.,
+@wu_relationship_2015; @li_relationship_2018], negative or non significant
+effects of species richness on total biomass have for example been found in some
+natural communities such as forests [@szwagrzyk_above-ground_2007;
+@jacob_productivity_2010; @seidel_relationship_2013]. Some authors suggest that
+the lack of resource complementarity or environmental harshness might be
+responsible for an absence or a negative effect of species richness
+[@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015]. These
+different relations might also arise from effects of the environment on both
+diversity and ecosystem functions [@loreau_biodiversity_2001].
 
@@
 When assessing the relationship between community structure and ecosystem
-properties in natural communities, it is crucial to consider environmental
-factors [@loreau_biodiversity_2001; @he_global_2013; @grace_integrative_2016].
-Environment affects organism performance directly, and thereby, species
-abundances, total biomass [@grace_integrative_2016] and temporal stability
-[@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
+properties in natural communities, it is indeed crucial to consider
+environmental factors [@loreau_biodiversity_2001; @he_global_2013;
+@grace_integrative_2016]. Environment affects organism performance directly, and
+thereby, species abundances, total biomass [@grace_integrative_2016] and temporal
+stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
 @oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
@@
 species richness. Accounting for environment also allow for an overall
-comparison of the strength of the effects of environment and community
-structure on total biomass and its stability.
+comparison of the strength of the effects of environment and community structure
+on total biomass and its stability.
 
@@
 
-Because their trophic interactions can be infered, stream fish community
+Because their trophic interactions can be inferred, stream fish community
 constitutes a good model to study the effects of network structure on total
@@
 
-Our study aims to document the relationships between foodweb structure and total
-biomass and its temporal stability in natural communities. To do so, we used the
-ONEMA dataset consisting in standardized sampling of fish communities in French
-streams [@edeline_ecological_2013]. 99 sites were sampled for more than 10 years
-spanning on the 1995-2018 period. We inferred 1496 interaction networks, based
-on body size and food diet. We question whether species richness, connectance
-and average trophic level increase, decrease or are not related to total biomass
-and its temporal stability. We further question whether the species richness,
-connectance and average trophic level have antagonistic or synergistic effect on
-total biomass and its temporal stability. Finally, we question if 
-ecosystem size and average temperature increase total biomass and its temporal
-stability.
-
----
-#We used the ONEMA dataset consisting in standardized sampling of fish
-#communities in French streams [@edeline_ecological_2013]. 99 sites were sampled
-#for more than 10 years spanning on the 1995-2018 period. We inferred 1496
-#interaction networks, based on body size and food diet. The network structure
-#was summarized by connectance and mean trophic level. Environment was
-#characterized by stream size, altitude, slope, temperature, flow and enrichment.
-#Finally total biomass was measured as median total biomass over the sampling
-#period while its temporal stability was quantified as the inverse of the CV.
-#
-#We found a positive relationship between total biomass and species richness and
-#network structure while total biomass and species richness had respectively a
-#negative and positive effect on temporal stability. We also showed a link
-#between species richness and network structure. We found that the environment had
-#a strong effect on total biomass and its temporal stability in particular by 
-#its effect on species richness and network structure. We then discuss the
-#possible mechanisms at play to explain those results and their implications on
-#our knowledge of the effect of network structure on ecosystem properties.
----
+Our study aims to document the relationships between food web structure and
+total biomass and its temporal stability in natural communities. To do so, we
+used the ONEMA dataset consisting in standardized sampling of fish communities
+in French streams [@edeline_ecological_2013]. 99 sites were sampled for more than 10
+years spanning on the 1995-2018 period. We inferred 1496 interaction networks,
+based on body size and food diet. We question whether species richness,
+connectance and average trophic level increase, decrease or are not related to
+total biomass and its temporal stability. We further question whether the
+species richness, connectance and average trophic level have antagonistic or
+synergistic effect on total biomass and its temporal stability. Finally, we
+question if ecosystem size and average temperature increase total biomass and
+its temporal stability.
 
@@
 
-## Data collection
+## Data preparation and filtering
 
@@
 
-## Data preparation
+## Variable computation
+
+### Biomass estimation
 
@@
 individual), where the coefficients $0.01$ and $3.03$ comes from two
-meta-analyses [@lleonart_removing_2000; @froese_cube_2006]. Species biomass and
-total biomass at each sampling event was then calculated by summing individual body
-masses. To account for the variation in sampling effort among sites, species
-biomass and total biomass have been related to the surface sampled, i.e.
-$gm^{-2}$. In the further analysis, the total biomass of a station has been
-defined as the median of the total biomass over time.
+meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006]. Species
+biomass and total biomass at each sampling event was then calculated by summing
+individual body masses. To account for the variation in sampling effort among
+sites, species biomass and total biomass have been related to the surface
+sampled, i.e.  $gm^{-2}$. In the further analysis, the total biomass of a
+station has been defined as the median of the total biomass over time.
+
+### Stability measures
 
@@
 
+### Species richness
+
 Species richness was computed as the total number of species present over time
@@
 square meter sampled.
+
+### Network building
 
@@
 ```
+
 We determined the network structure in two steps: (1) build a metaweb describing the
@@
 was included in the predation range (Figure S2). The fish-resource trophic
-links, for piscivorous and non piscivorous nodes, were set between the
-trophic species and the resources nodes present in their life stage.
-Lastly, the trophic links between resource nodes were set according to the food
-diet data [@allan_stream_2007; @hart_handbook_2008].
+links were set between the trophic species and the resources nodes according the
+food diet of their size class, for both the piscivorous and non piscivorous
+trophic species. Lastly, the trophic links between resource nodes were set
+according to the food diet data [@allan_stream_2007; @hart_handbook_2008].
+
+### Network structure
 
@@
 computed two of the most commonly used network metrics to characterize food
-webs, namely the connectance and mean trophic level. Connectance describes 
-the level of generalism in the network and is calculated as the number of actual
+webs, namely the connectance and mean trophic level. 
+As the networks, the networks metrics were also based on the trophic species,
+i.e. body size classes. Connectance describes the level of generalism in the
+network and is calculated as the number of actual
 interaction divided by the maximum number of interaction if all species interact
-together ($C = L / N^2$, L and N being resp. the number of
-links and of trophic species plus resource nodes). 
-The mean trophic level $\overline{T}$ was computed as the mean trophic level
-weighted by the biomass of each trophic species (excluding resource nodes for
-which we had no biomass information), so $\overline{T} = \sum_i^N{B_iT_i \times
-\sum_i^N{B_i}^{-1}}$, with $T_i$ and $B_i$ being respectively the trophic level
-and the biomass of the node $i$. The trophic level of the nodes was computed as
-one added to the average trophic level of its food item.
+together ($C = L / N^2$, L and N being resp. the number of links and of trophic
+species plus resource nodes). The mean trophic level $\overline{T}$ was computed
+as the mean trophic level weighted by the biomass of each trophic species
+(excluding resource nodes for which we had no biomass information), so
+$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and
+$B_i$ being respectively the trophic level and the biomass of the node $i$. The
+trophic level of the nodes was computed as one added to the average trophic
+level of its food item. For each site, the median of connectance and average
+trophic level over time was used in subsequent analysis.
 
@@
 facet_grid(cols = vars(variable))
+
+mysave(habitat_press, habitat_pressure, dir = mypath("data"))
 
@@
 
-## Environment
+## Environmental variables
 
@@
 \@ref(tab:indir-sem)).
-The PCA2 had a total negative effect on temporal stability 
+The PCA2 had a total negative effect on temporal stability, meaning that higher
+temperature results in lower stability
 ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
@@
 
-We found that species richness and mean
+Overall, our study is unique by its level of integration, from environmental
+effects to total biomass and stability, going through species richness and
+network structure, and the first direct assessment of a possible joint effect of
+species richness and network structure.  We found that species richness and mean
 trophic level had a positive effect on total biomass. In contrast, species
 richness had a negative effect on temporal stability whereas mean trophic level
-covaried positively. Futhermore, we found that the effect of species richness
-and mean trophic level on total biomass and its temporal stability were not
-independant as species richness had a positive effect on mean trophic level.
-Finally, we found that the magnitude of the effects of average temperature and
-altitude was equal or superior to the effects of species richness and mean
-trophic level. Overall, our study is unique by its level of integration, from
-environmental effects to total biomass and stability, going through species
-richness and network structure, and the first direct assessment of a possible
-joint effect of species richness and network structure.
+covaried positively. We also found that the effect of species richness and mean
+trophic level on total biomass and its temporal stability were not independant
+as species richness had a negative effect on mean trophic level.  Furthermore,
+we found that connectance had no significant effect on both total biomass and
+its temporal stability. Finally, we found that the magnitude of the effects of
+average temperature and altitude was equal or superior to the effects of species
+richness and mean trophic level.
 
@@
 @wu_relationship_2015; @li_relationship_2018]. The positive effect of species
-richness on total biomass might be due to resource use complementarity [@carey_determining_2011], which is
-held by niche differentiation [@loreau_biodiversity_1998;
-@loreau_partitioning_2001] or to the higher probability to get high biomass
-species  with higher species richness [@loreau_biodiversity_2001].
+richness on total biomass might be due to resource use complementarity
+[@carey_determining_2011], which is held by niche differentiation
+[@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
+probability to get high biomass species  with higher species richness
+[@loreau_biodiversity_2001].
 
@@
 @olivier_urbanization_2020], we found that species richness decreases synchrony,
-thereby increasing stability. However, no relation has been found in
-natural forests [@declerck_species_2006]. Our study thus
+thereby increasing stability [but see @declerck_species_2006]. Our study thus
 highlights that species richness might also decrease synchrony in empirical
 trophic communities. Species richness can reduce synchrony when a given
-increase in species richness leads to a decrease of population sizes, which in
-turn raises the role of demographic stochasticity on population dynamics
-[@loreau_species_2008] but also in the case where species have different
-responses to environmental variation [@loreau_species_2008].
+increase in species richness leads to a decrease of population sizes but also in
+the case where species have different responses to environmental variation
+[@loreau_species_2008].
 
@@
 @olivier_urbanization_2020], negative and neutral relationships have been found
-in butterfly and bat communities. However, the ecological mechanisms leading to
-such relationships in foodwebs are not known and this question deserves further
-research.
+in butterfly and bat communities. ** Our results contrast with a previous
+meta-analysis which concludes that species richness had a positive effect on
+population stability in multi-trophic aquatic microcosms
+[@jiang_different_2009]. In foodwebs, the relationship between temporal
+stability of populations and species richness depends on interaction strength
+and their distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
+@brose_allometric_2006], high interaction strength inducing a negative
+relationship. Overall, more research is needed to assess the links between
+species richness and the functioning of empirical foodwebs.**
 
@@
 
-## Mean trophic level increased total biomass and its temporal stability
-
-The mean trophic level was positively linked to total biomass. As feeding
-interactions were partly determined by body size and that body mass increase
-with body size, it is expected that the more the average
-biomass is located at higher trophic level, the higher the total biomass is. 
-Experimental and theoretical work suggested that a
-higher trophic level is the result of a stronger top-down effect, meaning higher
-predation rates and biomass fluxes to higher trophic levels
-[@thebault_relationship_2006; @kratina_warming_2012], hence leading to an
+## Average trophic level increased total biomass and its temporal stability
+
+The average trophic level was positively linked to total biomass.
+Experimental and theoretical work suggested that a higher trophic level is the
+result of a stronger top-down effect, meaning higher predation rates and biomass
+fluxes to higher trophic levels [@kratina_warming_2012], hence leading to an
 increase in total biomass with trophic length. Furthermore,
@@
 In contrast, connectance had no effect on total biomass. One might have expected
-that an increase in connectance should translate in higher resource transfer
-efficiency between prey and predators and so results in higher total biomass in
-the fish compartment. A reason for such an absence of an effect might be due our
-data lacks informations about the lower compartments of the
-community, i.e, the primary producers, zooplankton and zoobenthos.
+that an increase in connectance may translate in higher total nutrient uptake
+and so results in higher total biomass in the fish compartment. A reason for
+such an absence of an effect might be due our data lacks informations about the
+lower compartments of the community, i.e, the primary producers, zooplankton and
+zoobenthos.
 
@@
 @shanafelt_stability_2018] but it is not sure that it holds when considering
-omnivorous species [@wang_biodiversity_2016] and if other mechanisms can
-generate the same pattern [@thibaut_understanding_2013]. An alternative
-explanation is that higher mean trophic level leads to stronger top-down control
-and resource complementarity and thus reduce biomass fluctuations in lower
-trophic levels [@rooney_structural_2006; @neutel_reconciling_2007].
+omnivorous species [@wang_biodiversity_2016]. An alternative explanation is that
+higher mean trophic level leads to stronger top-down control and resource
+complementarity and thus reduce biomass fluctuations in lower trophic levels
+[@rooney_structural_2006].
 
@@
 stability and network structure [@angelis_stability_1975; @may_will_1972;
-@thebault_stability_2010], although they considered different stability concepts
-and metrics [@arnoldi_resilience_2016]. However, our measure of connectance
-suffers limitation and further research should examine
-the effect of connectance on temporal stability in empirical foodwebs.
+@thebault_stability_2010; but see @neutel_reconciling_2007], although they
+considered different stability concepts and metrics [@arnoldi_resilience_2016].
+However, our measure of connectance suffers limitation (discussed above) and
+further research should examine the effect of connectance on temporal stability
+in more complete empirical foodwebs.
+
+## Population stability was the main driver of temporal stability
+
+**It was unexpected that the average population variability ($\overline{CV_{sp}}$) had a
+stronger negative effect on biomass stability than synchrony
+[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
+negative effect of species richness on temporal stability of biomass. The lower
+effect of synchrony might be explained by the presence of generalist predators in
+stream communities, which can raise synchrony between prey species which shares
+the same predator [@raimondo_interspecific_2004]. In the other way, it is
+possible that, in aquatic foodwebs, the occurrence of large oscillatory dynamics
+[@mccann_reevaluating_1997] leads to a higher contribution of population
+variability rather than synchrony to community stability. How both
+strengths and the relative contribution of synchrony and population
+variaribility to overall stability vary between foodwebs and single trophic communities is
+still an open question.**
+
+---
+#Rough average synchrony in Théophile study: exp(-0.75) = .47 or exp(-0.6) = .54
+#This study: sync avg = .69
+---
 
@@
 
-Contrasting with a previous study in experimental plant communities
-[@grace_integrative_2016] and in fish communities [@yvondurocher_warming_2011;
-@dossena_warming_2012], we found that environmental drivers overall affect total
-biomass indirectly rather than directly. In line with previous studies, we found
-that the two PCA axis, respectively related to stream size and temperature, 
-had indirect positive effects on total biomass, through a positive direct effect
-on species richness [@allan_stream_2007; @ogorman_chapter_2012;
-@emmrich_geographical_2014].
+**We found that the total effect of environmental drivers on total biomass and its
+stability was indirect and of the same magnitude order than the effect of
+species richness and average trophic level, highlighting that environmental
+changes may result in signicant ecosystem responses, through alteration of
+both species richness and network structure.**
 
@@
 resource complementarity. Greater diversity of resources can also maintain
-higher biomass in high trophic level [@post_ecosystem_2000; @doi_resource_2009].
+more biomass at high trophic level [@post_ecosystem_2000; @doi_resource_2009].
 Furthermore, the positive effect of the PCA axis related to temperature on total
@@
 @dossena_warming_2012; @edeline_ecological_2013; @emmrich_geographical_2014;
-@hattab_forecasting_2016].
+@hattab_forecasting_2016]. Contrasting with a previous study in experimental
+plant communities [@grace_integrative_2016] and in fish communities
+[@yvondurocher_warming_2011; @dossena_warming_2012], we found that environmental
+drivers overall affect total biomass indirectly rather than directly.
 
@@
 
+While theoretical ecology has focused on the effects of network structure on
+stability, empirical ecology has focused on species richness and ignored network
+structure. Furthermore, both fields have largely used different stability
+metrics. Our work thus aims to contribute at bridging this gap between
+theoretical and empirical ecology.
+
 Our study extends the assessment of the effect of species richness on total
@@
 species richness, network structure and their dependence. However, the
-mechanisms leading to such remains to be elucidated. One limitation of our study
-is that the use of inferred networks and the lack of information about the
-foodwebs outside fishes. Our findings and interpretation could be confirmed by
-experimental and theoretical works considering foodwebs instead of pure
-foodchains. It would be promising to explore the effects of omnivory and
-ontogeny, i.e. relaxing the foodchain assumption, on the link between network
-structure and ecosystem functioning.
-
-While theoretical ecology has focused on the effects of network structure on
-stability, empirical ecology has focused on species richness and ignored network
-structure. Furthermore, both fields have largely used different stability
-metrics. Therefore, our work aims to contribute at bridging this gap between
-theoretical and empirical ecology. Finally, we found that environmental gradient
-related to temperature and ecosystem size have antagonistic effects on biomass
-temporal stability, positive through mean trophic level and negative through
-species richness. Further research is needed to find the mechanisms behind those
-pathways, that are crucial in context of global changes.
+mechanisms leading to such remains to be elucidated. Finally, we found that
+environmental gradient related to temperature and ecosystem size have
+antagonistic effects on biomass temporal stability, positive through mean
+trophic level and negative through species richness. Further research is needed
+to find the mechanisms behind those pathways, that are crucial in context of
+global changes.
+
+One limitation of our study is that the use of inferred networks, i.e. not
+observed interactions, and the lack of information about the foodwebs outside
+fishes. We look forward to see our findings and their interpretation tested by
+experimental and theoretical works considering foodwebs, allowing explore the
+effects of omnivory and ontogeny on the link between network structure and
+ecosystem functioning.
 

### 2020-09-15 R/plot_methods.R

@@ -477,6 +477,54 @@ plot_dyn_sp_biomass <- function (sync = NULL, station = NULL, trophic_level = NU
   return(p)
 }
 
+plot_temporal_biomass <- function (bm_data = NULL, biomass_var = NULL, com = NULL, .log = FALSE) {
+
+  #main_title <- paste0("Stab = ", round(1/(sync$cv_com), 2),", ", "Sync = ",
+    #round(sync$synchrony, 2),", ", "CVsp = ", round(sync$cv_sp, 2))
+  sym_bm_var <- rlang::sym(biomass_var)
+  # Total
+  total_biomass <- bm_data %>% 
+  group_by(date) %>%
+  summarise(!!sym_bm_var := sum(!!sym_bm_var, na.rm = FALSE))
+  
+  p <- bm_data %>%
+    mutate(label = if_else(date == max(date), as.character(species), NA_character_)) %>%
+  ggplot(aes_string(x = "date", y = biomass_var, color = "species")) + 
+  geom_line() +
+  lims(y = c(0, max(total_biomass[[biomass_var]]))) +
+  labs(
+  #title = main_title, subtitle = paste0("Station: ", station),
+    y = "Biomass (g)", x = "Sampling date"
+  ) +
+  ggrepel::geom_label_repel(aes(label = label),
+    size = 2.5, nudge_x = 1, na.rm = TRUE) 
+  
+  # Add total biomass
+  p2 <- p +
+    geom_line(data = total_biomass, aes(color = "black", size = 3)) +
+    theme(legend.position = "none")
+
+  # Add summary: richness, connectance, stab, t_lvl, sync, cv_sp 
+  label <- paste(
+    "S = ", com$bm_std_stab,
+    "sync = ", com$sync,
+    "CVsp = ", com$cv_sp,
+    "R = ", com$rich_tot_std,
+    "C = ", com$ct,
+    "Tlvl = ", com$t_lvl
+  ) 
+
+  p3 <- p2 +
+    annotate("text", x = median(total_biomass$date),
+      y = 15, label = "Some text")
+
+  if (.log) {
+    p3 <- p3 + scale_y_log10() 
+  }
+
+  return(p3)
+}
+
 ###############
 #  Labellers  #
 ###############

### 2020-09-22 manuscript/bef_stability/manuscript.Rmd
Revision according to Willem comments

@@
   - Maud Mouchet:
-  - Willem Bonnaffe:
+  - Willem Bonnaffe: Ecological and Evolutionary Dynamics Lab. Zoology Research
+    and Administration Building, 11a Mansfield Rd, Oxford OX1 3SZ, United
+    Kingdom.
   - Elisa Thebault: 
@@
 
-Both the relations between diversity and ecosystem functioning, and between food
+Both the relationship between diversity and ecosystem functioning, and that between food
 web complexity and stability, have received considerable attention during the
-last decades in ecology. While the former relation remains rarely investigated
+last decades in ecology. The former relationship remains rarely investigated
 in the context of food webs, especially in empirical studies explicitly
@@
 production [@tilman_productivity_1996; @cardinale_species_2002;
-@grace_integrative_2016], biomass repartition [@thebault_relationship_2006] and
-biomass stability [@thebault_trophic_2005; @thebault_relationship_2006;
+@grace_integrative_2016], distribution [@thebault_relationship_2006] and
+stability [@thebault_trophic_2005; @thebault_relationship_2006;
 @tilman_biodiversity_2006]. The relationship between biodiversity and
@@
 @duffy_why_2009; @isbell_forest_quantifying_2018] and its documentation is thus
-crucial to better anticipate the impacts of global changes.
+crucial to better anticipate the impacts of global change.
 
@@
 @grace_integrative_2016], but also in briophyte communities
-[@mulder_physical_2001], stream feeders [@cardinale_species_2002] and aquatic
+[@mulder_physical_2001], stream feeders, [@cardinale_species_2002] and aquatic
 bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
-ecosystems and taxons studied, the relation between diversity and ecosystem
+ecosystems and taxons studied, the relationship between diversity and ecosystem
 functioning remains traditionally focused on single trophic levels, ignoring the
@@
 [@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
-Empirical studies are however missing to assess further how food web structure,
-in conjunction with species diversity, affect total biomass production and other
+We are lacking empirical studies that assess jointly how food web structure, in
+conjunction with species diversity, affect total biomass production and other
 ecosystem properties.
@@
 
-Many studies showed that species richness also increases temporal stability of
+Many studies showed that species richness increases temporal stability of
 communities, i.e. variation through time, often quantified by the temporal CV.
@@
 settings, such as stream fish communities [@franssen_annual_2011], bird and
-butterfly communities [@olivier_urbanization_2020]. However, this relation has
+butterfly communities [@olivier_urbanization_2020]. However, this relationship has
 been mostly explored in single trophic level systems or without accounting for
-food web structure, even more so than the relation between diversity and biomass
-production. Single-level theoretical works have clarified which mechanisms
+food web structure, even more so than the relationship between diversity and biomass
+production. Several theoretical studies at considering single trophic level have clarified which mechanisms
 generate this positive relationship between species richness and temporal
 stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
-synchrony and (2) species variability. Species synchrony quantify to what extent
+synchrony and (2) species variability. Species synchrony captures to what extent
 the fluctuations of abundances or biomasses through time are correlated among
@@
 is compensated by the increase of an other.  Asynchrony is generally the main
-mechanism whereby species richness has a stabilizing effect on temporal
-stability [@tilman_biodiversity_2006; @olivier_urbanization_2020] while
-positive, neutral and negative relationships have been found in natural settings
+mechanism which species richness has a stabilizing effect on temporal
+stability [@tilman_biodiversity_2006; @olivier_urbanization_2020].Though most often positive, the relationship between species diversity and asynchrony has also been evidenced to be neutral or negative in natural settings
 [@tilman_biodiversity_2006; @thibaut_understanding_2013;
@@
 @dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
-@stouffer_compartmentalization_2011]. For instance, predation has cascading
-effects on species variability [@shanafelt_stability_2018] and it affects as
-well synchrony between species [@teng_dynamics_2004]. Despite a long-standing
-interest on the links between food web complexity and stability in ecology, to
+@stouffer_compartmentalization_2011]. In particular, predation has cascading
+effects on both species variability and synchrony [@teng_dynamics_2004; @shanafelt_stability_2018] and it affects as
+well synchrony between species. In spite a long-standing interest for the links between food web complexity and stability in ecology, to
 date we have very few evidence on the relationship between network structure and
@@
 the lack of resource complementarity or environmental harshness might be
-responsible for an absence or a negative effect of species richness
+responsible for negligible, or negative effects of species richness
 [@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015]. These
-different relations might also arise from effects of the environment on both
+different relationships might also arise from effects of the environment on both
 diversity and ecosystem functions [@loreau_biodiversity_2001].
@@
 
-When assessing the relationship between community structure and ecosystem
-properties in natural communities, it is indeed crucial to consider
-environmental factors [@loreau_biodiversity_2001; @he_global_2013;
+Environmental effects might also complicate (or obscure) the relationship
+between diversity and structure in driving stability and biomass in natural
+systems [@loreau_biodiversity_2001; @he_global_2013;
 @grace_integrative_2016]. Environment affects organism performance directly, and
@@
 @oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
-For example, greater ecosystem size might increase the number of available
+For example, larger ecosystem might increase the number of available
 resources and thus total biomass [@post_ecosystem_2000; @doi_resource_2009].
@@
 
-Because their trophic interactions can be inferred, stream fish community
-constitutes a good model to study the effects of network structure on total
+Because their trophic interactions can be inferred, stream fish communities
+constitute a good model to study the effects of network structure on total
 biomass and its temporal stability. Despite that fish trophic
-interactions are difficult to measure in natural conditions, a consequent body
+interactions are difficult to measure in natural conditions, a substantial body
 of literature supports that they can be inferred through body size and diet
@@
 interactions based on body size ratio was far better in stream ecosystems than
-in other aquatic and terrestrial ecosystems. Furthermore, the biotic activity in
-stream ecosystems determines for a large part the water quality
-[@cummins_structure_1974] and thus are crucial to maintain stream ecosystem
-properties. Lastly, most of the diversity-biomass and diversity-stability
+in other aquatic and terrestrial ecosystems. Lastly, most of the diversity-biomass and diversity-stability
 relationships, have been assessed in terrestrial ecosystems while there is a
@@
 years spanning on the 1995-2018 period. We inferred 1496 interaction networks,
-based on body size and food diet. We question whether species richness,
+based on body size and diet. We question whether species richness,
 connectance and average trophic level increase, decrease or are not related to
 total biomass and its temporal stability. We further question whether the
-species richness, connectance and average trophic level have antagonistic or
+species richness, connectance, and average trophic level have antagonistic or
 synergistic effect on total biomass and its temporal stability. Finally, we
@@
 sites, species biomass and total biomass have been related to the surface
-sampled, i.e.  $gm^{-2}$. In the further analysis, the total biomass of a
-station has been defined as the median of the total biomass over time.
+sampled, i.e.  $gm^{-2}$. In the analysis, the total biomass of a
+station has been defined as the median of the total biomass acrossall times.
 
@@
 In order to describe the mechanisms driving the temporal stability of biomass, we
-decomposed the $CV$ of total biomass ($CV_{com}$) in synchrony ($\phi$) and
+decomposed the $CV$ of total biomass ($CV_{com}$) into a synchrony ($\phi$) and
+a
 weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
@@
 
-Species richness was computed as the total number of species present over time
+Species richness was computed as the total number of species present across all times
 in a given station. As for biomass, we controlled species richness for sampling
@@
 \@ref(fig:matmet) C), then (2) determine network of a given community by
-subtracting the metaweb according to the trophic species present in a given
+extracting the metaweb according to the trophic species present at a given
 site and sampling event (Figure \@ref(fig:matmet) D).
@@
 @poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
-over lifespan and thereby over body size. For example, alvins feed on plankton
-while adults may feed on algae, fishes, with bigger individuals eating bigger
+throughout an individual's life, and thereby with body size. For example, alvins
+feed on plankton while adults may feed on algae, fishes, with bigger individuals
+eating bigger
 fishes. Each fish species was hence divided in nine body size classes, each
@@
 species and the resources constituted the 412 nodes of the metaweb, 45 fish
-species divided into nine body classes plus seven resource nodes. The inference
+species divided into nine body size classes plus seven resource nodes. The inference
 of trophic interactions was shown to be more accurate when considering body size
@@
 
-The feeding interactions of a fish node, i.e a trophic species, are determined
-by both its species identity and its body size. Then, species identity allows to
-differentiate between piscivorous and non piscivorous species, to know on which
+The feeding interactions of a fish node, i.e a trophic species, were determined
+by both its species identity and its body size. Then, species identity allowed to
+differentiate between piscivorous and non piscivorous species, to know which
 resources the trophic species are feeding on and to know the minimum size at
-which a piscivorous species begins to feed on fishes. The ontogenic fish diet
+which a piscivorous species begin to feed on fishes. The ontogenic fish diet
 database was filled according to fishbase and literature (cf Bonnaffe ref). Each
@@
 webs, namely the connectance and mean trophic level. 
-As the networks, the networks metrics were also based on the trophic species,
+The networks metrics were also based on the trophic species,
 i.e. body size classes. Connectance describes the level of generalism in the
-network and is calculated as the number of actual
-interaction divided by the maximum number of interaction if all species interact
+network and is calculated as the actual number of
+interactions divided by the maximum number of interactions if all species interact
 together ($C = L / N^2$, L and N being resp. the number of links and of trophic
@@
 
-Structural Equation Modeling are able to assess multivariate relationships
-between variables. It is one promising way to go beyond bivariate relationships
+Structural Equation Modeling enables us to assess multivariate relationships
+between variables. It is a promising way to go beyond bivariate relationships
 and to investigate complex relationships, direct and
@@
 @lefcheck_piecewisesem_2016; @grace_integrative_2016]. The structural equation
-model explaining the annual total biomass set that environment
-can directly affect species richness and network structure, as well as annual total
+model explaining the annual total biomass allowed the environment
+to affect directly species richness and network structure, as well as annual total
 biomass (Figure \@ref(fig:sem-plot) B). We assumed that both species richness
 and network structure directly affect total biomass (Figure \@ref(fig:sem-plot)
-B) and that species richness constrained food web structure
+B) and that species richness affected food web structure
 [@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010].
@@
 We used the same model structure for temporal stability of biomass (Figure
-\@ref(fig:sem-plot) A). Instead of the annual total biomass, we set the
+\@ref(fig:sem-plot) A). Instead of the annual total biomass, we modelled the
 synchrony and population variability which in turn determined the temporal
 stability of biomass. The structural equation models used for annual total
-biomass and its temporal stability contains respectively 4 and 6 response
+biomass and its temporal stability contained respectively 4 and 6 response
 variables, 35 and 26 direct paths.
@@
 
-The indirect effects of variables on total biomass and its temporal stability
-was computed by multiplying slopes along the path. As an example, if we consider
+Indirect effects on total biomass and its temporal stability
+were computed by multiplying slopes along the path. As an example, if we consider
 $A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times
@@
 `r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
-resp., Table \@ref(tab:indir-sem)). The second axis, PCA2, related the average
-annual temperature and reversely to altitude of the sites was positively related
+resp., Table \@ref(tab:indir-sem)). The second axis, PCA2, related to the average
+annual temperature and inversely to altitude of the sites was positively related
 to total biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
@@
 effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
-Table \@ref(tab:indir-sem)). Connectance had no significant direct on either
+Table \@ref(tab:indir-sem)). Connectance had no significant direct effect on either
 $\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
@@
 
-The total effect of PCA2, related to average annual temperature and reversely to
+The total effect of PCA2, related to average annual temperature and inversely to
 altitude, on temporal stability was of higher magnitude than the effects of
@@
 `r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)) but also a
-negative on through species richness but a positive one through
+negative one through species richness but a positive one through
 mean trophic level
@@
 network structure, and the first direct assessment of a possible joint effect of
-species richness and network structure.  We found that species richness and mean
+species richness and network structure on both total biomass and its temporal
+stability. We found that species richness and mean
 trophic level had a positive effect on total biomass. In contrast, species
@@
 [@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
-probability to get high biomass species  with higher species richness
+probability of getting high biomass species with higher species richness
 [@loreau_biodiversity_2001].
@@
 fish communities [@franssen_annual_2011] where positive relationships were found
-between temporal stability and species richness. However other studies found a
-opposite relationship in natural grassland [@yang_effects_2011] or a marginal
+between temporal stability and species richness. However, other studies found an
+opposite relationship in natural grassland [@yang_effects_2011] and a marginal
 one in natural forests [@declerck_species_2006].
@@
 [@isbell_biodiversity_2009; @roscher_identifying_2011], in natural communities
-of birds, bats, grasslands, bats and butterflies [@bluthgen_land_2016;
+of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
 @olivier_urbanization_2020], we found that species richness decreases synchrony,
 thereby increasing stability [but see @declerck_species_2006]. Our study thus
-highlights that species richness might also decrease synchrony in empirical
+extends the evidence that species richness decrease synchrony to the case of empirical
 trophic communities. Species richness can reduce synchrony when a given
@@
 @olivier_urbanization_2020], negative and neutral relationships have been found
-in butterfly and bat communities. ** Our results contrast with a previous
+in butterfly and bat communities. Our results contrast with a previous
 meta-analysis which concludes that species richness had a positive effect on
@@
 @brose_allometric_2006], high interaction strength inducing a negative
-relationship. Overall, more research is needed to assess the links between
-species richness and the functioning of empirical foodwebs.**
+relationship. Therefore, it is possible that our results are due to a high
+degree of omnivory in food webs, which combined with strong trophic interactions
+lead to more fluctuations in population biomass.
 
@@
 increase in total biomass with trophic length. Furthermore,
-@wang_biodiversity_2016 have shown that total nutrient uptake might increases
-with the length of trophic chain and so results in higher total biomass.
+@wang_biodiversity_2016 have shown that total nutrient uptake might increase
+with the length of trophic chains and so results in higher total biomass.
 
@@
 and so results in higher total biomass in the fish compartment. A reason for
-such an absence of an effect might be due our data lacks informations about the
+such an absence of an effect might be explained by the fact that our data lack information about the
 lower compartments of the community, i.e, the primary producers, zooplankton and
@@
 might be because species at higher trophic level are more stable than the species at
-lower trophic levels as predicted by food chains models [@barbier_pyramids_2019;
-@shanafelt_stability_2018] but it is not sure that it holds when considering
-omnivorous species [@wang_biodiversity_2016]. An alternative explanation is that
-higher mean trophic level leads to stronger top-down control and resource
-complementarity and thus reduce biomass fluctuations in lower trophic levels
+lower trophic levels as predicted by food chain models in the presence of
+strong top-down control [@barbier_pyramids_2019; @shanafelt_stability_2018] but it
+is not sure that it holds when considering omnivorous species
+[@wang_biodiversity_2016]. An alternative explanation is that higher mean
+trophic level leads to stronger top-down control and resource complementarity
+and thus reduce biomass fluctuations in lower trophic levels
 [@rooney_structural_2006].
@@
 
-**It was unexpected that the average population variability ($\overline{CV_{sp}}$) had a
-stronger negative effect on biomass stability than synchrony
-[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
-negative effect of species richness on temporal stability of biomass. The lower
-effect of synchrony might be explained by the presence of generalist predators in
-stream communities, which can raise synchrony between prey species which shares
-the same predator [@raimondo_interspecific_2004]. In the other way, it is
-possible that, in aquatic foodwebs, the occurrence of large oscillatory dynamics
+In contrast with previous studies, we found that the average population
+variability ($\overline{CV_{sp}}$) had a stronger negative effect on biomass
+stability than synchrony [@tilman_biodiversity_2006; @bluthgen_land_2016;
+@olivier_urbanization_2020]. It explains why we observe a negative effect of
+species richness on temporal stability of biomass. The lower effect of synchrony
+might be explained by the presence of generalist predators in stream
+communities, which can raise synchrony between prey species which share the
+same predator [@raimondo_interspecific_2004] and thus decreases the
+occurrence of compensatory population dynamics. Alternatively, it is possible that, in
+aquatic foodwebs, the occurrence of large oscillatory dynamics
 [@mccann_reevaluating_1997] leads to a higher contribution of population
@@
 variaribility to overall stability vary between foodwebs and single trophic communities is
-still an open question.**
+still an open question.
 
@@
 
-**We found that the total effect of environmental drivers on total biomass and its
+We found that the total effect of environmental drivers on total biomass and its
 stability was indirect and of the same magnitude order than the effect of
@@
 changes may result in signicant ecosystem responses, through alteration of
-both species richness and network structure.**
+both species richness and network structure.
 
@@
 positive effect of temperature and stream size on species richness, which itself
-has a destabilising effect. This result is interesting in that though both
+has a destabilising effect. This result is interesting in that both
 pathways had not been evidenced to be jointly to play, as far as we know.
-Furthermore, it is unclear under which circumstance which pathway is dominating,
+Furthermore, it is unclear which pathway is dominating, and under which circumstances,
 opening an interesting avenue for further investigations.
@@
 While theoretical ecology has focused on the effects of network structure on
-stability, empirical ecology has focused on species richness and ignored network
+stability, empirical ecology has focused on species richness but often did not considere network
 structure. Furthermore, both fields have largely used different stability
-metrics. Our work thus aims to contribute at bridging this gap between
+metrics. Our work is hence contributing to bridging the gap between
 theoretical and empirical ecology.
@@
 positive and negative effect respectively on total biomass and its stability but
-mean trophic level had a positive effect on both. We furthermore found that
+mean trophic level had a positive effect on both. Furthermore, we found that
 species richness had antagonistic effects on total biomass, through its effect
-on mean trophic level. Our study thus highlights the importance to consider both
-species richness, network structure and their dependence. However, the
-mechanisms leading to such remains to be elucidated. Finally, we found that
+on mean trophic level. Our study thus highlights the importance of considering both
+species richness, network structure and their dependence, though the
+mechanisms remain to be elucidated. Finally, we found that
 environmental gradient related to temperature and ecosystem size have

### 2020-10-18 manuscript/bef_stability/manuscript.Rmd
Manuscript update: colin rreview + new table and figures

@@
 
-Both the relationship between diversity and ecosystem functioning, and that between food
+Both the relationship between diversity and ecosystem functioning, and between food
 web complexity and stability, have received considerable attention during the
@@
 theoretical studies and empirical tests are critically missing. Here we link
-species richness, food web structure and total biomass and its stability by
+species richness, food web structure and annual biomass and its temporal stability
 using a dataset of standardized fish sampling in French streams running from
@@
 diet literature. We reveal that species richness and average trophic level had a
-positive relationship with total biomass of fish communities while they had
+positive relationship with annual biomass of fish communities while they had
 respectively a negative and positive effect on its temporal stability. We
-also found that the effects of stream size and temperature on total biomass and
+also found that the effects of stream size and temperature on annual biomass and
 stability are partly mediated by their effects on diversity and food web
@@
 
-Current biodiversity losses and global changes has the potential to affect
-ecosystems in complex ways [@bellard_impacts_2012]. Biodiversity has a
+Current biodiversity losses and further global change has the potential to affect
+ecosystems in complex ways [@loreau_biodiversity_2001; @tilman_biodiversity_2014]. Biodiversity has a
 tremendous effect on ecosystem properties because it largely determines both the
 amount and the distribution of matter and energy fluxes
-within and among ecosystems [@duffy_why_2009]. Biodiversity thus affects biomass
+within and among ecosystems [@loreau_meta-ecosystems:_2003]. Biodiversity thus affects biomass
 production [@tilman_productivity_1996; @cardinale_species_2002;
@@
 @loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
-@duffy_why_2009; @isbell_forest_quantifying_2018] and its documentation is thus
+@duffy_why_2009; @isbell_forest_quantifying_2018] and our understanding of it is 
 crucial to better anticipate the impacts of global change.
@@
 functioning remains traditionally focused on single trophic levels, ignoring the
-effects of food web structure. Theoretical models have recently extended
-classical theoretical studies in plant communities [@tilman_plant_1997;
-@loreau_biodiversity_2001] to food webs [@thebault_food-web_2003;
+effects of food web structure. Theoretical models have recently moved from
+single trophic [@tilman_plant_1997;
+@loreau_biodiversity_2001] to multitrophic communities [@thebault_food-web_2003;
 @poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018]. 
@@
 [@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
-However, they also reveal new mechanisms such as positive effects of diversity
-of trophic levels, i.e. associated with higher trophic levels, on ecosystem
+However, they also reveal new mechanisms such as positive effects of 
+the number of trophic levels, i.e. associated with higher trophic levels, on ecosystem
 functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
@@
 [@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
-We are lacking empirical studies that assess jointly how food web structure, in
-conjunction with species diversity, affect total biomass production and other
-ecosystem properties.
+Despite these theoretical evidences that structure affects biomass, we are
+lacking empirical studies that assess jointly how food web structure and species
+diversity affect total biomass and its production.
 
@@
 
-Many studies showed that species richness increases temporal stability of
-communities, i.e. variation through time, often quantified by the temporal CV.
-Such positive relationships between species richness and temporal stability have
-been reported in experimental grasslands and aquatic bacterial systems
+Further than biomass production, many studies showed that species richness
+increases temporal stability of communities, i.e. variation through time, often
+quantified by the temporal CV of biomass.  Such positive relationship between
+species richness and temporal stability of biomass has been reported in
+experimental grasslands and aquatic bacterial systems
 [@tilman_biodiversity_2006; @pennekamp_biodiversity_2018] as well as in natural
 settings, such as stream fish communities [@franssen_annual_2011], bird and
-butterfly communities [@olivier_urbanization_2020]. However, this relationship has
-been mostly explored in single trophic level systems or without accounting for
-food web structure, even more so than the relationship between diversity and biomass
-production. Several theoretical studies at considering single trophic level have clarified which mechanisms
-generate this positive relationship between species richness and temporal
+butterfly communities [@olivier_urbanization_2020]. However, this relationship
+has been mostly explored in single trophic level systems or without accounting
+for food web structure, even more so than the relationship between diversity and
+biomass production.
+
+Several theoretical studies considering single trophic level have
+clarified which mechanisms generate this positive relationship between species
+richness and temporal
 stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
@@
 mechanism which species richness has a stabilizing effect on temporal
-stability [@tilman_biodiversity_2006; @olivier_urbanization_2020].Though most often positive, the relationship between species diversity and asynchrony has also been evidenced to be neutral or negative in natural settings
+stability [@tilman_biodiversity_2006; @olivier_urbanization_2020]. Asynchrony is
+expected to raise with the variability of species responses to perturbations. Though most
+often positive, the relationship between species diversity and asynchrony has
+also been evidenced to be neutral or negative in natural settings
 [@tilman_biodiversity_2006; @thibaut_understanding_2013;
-@olivier_urbanization_2020]. In addition to diversity, food web structure is
-expected to strongly affect the stability of communities and ecosystems, as
-outlined by the large body of theoretical studies on this topic [@may_will_1972;
-@dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
-@stouffer_compartmentalization_2011]. In particular, predation has cascading
-effects on both species variability and synchrony [@teng_dynamics_2004; @shanafelt_stability_2018] and it affects as
-well synchrony between species. In spite a long-standing interest for the links between food web complexity and stability in ecology, to
-date we have very few evidence on the relationship between network structure and
-the temporal stability of species and total biomass in empirical multitrophic
-communities.
+@olivier_urbanization_2020; @valencia_synchrony_2020].
+
+In addition to diversity,
+food web structure is expected to strongly affect the stability of communities
+and ecosystems, as outlined by the large body of theoretical studies on this
+topic [@may_will_1972; @dunne_network_2006; @neutel_reconciling_2007;
+@duffy_why_2009; @stouffer_compartmentalization_2011]. In particular, predation
+has cascading effects on both species variability and synchrony
+[@teng_dynamics_2004; @shanafelt_stability_2018] and it also affects
+synchrony between species.
 
@@
 level, are potentially conflicting or synergistic in such a way that they need
-to be addressed jointly. Yet, there is no direct empirical evidence to date for
-the combined effects of species richness and network structure on total biomass
-and stability in natural communities.
-
-Although the relationships between diversity, total biomass and its stability in
-natural systems can be similar to those found in experimental communities [e.g.,
-@wu_relationship_2015; @li_relationship_2018], negative or non significant
-effects of species richness on total biomass have for example been found in some
+to be addressed jointly. Despite the long-standing interest for the links
+between food web complexity and stability in ecology, we still have very few
+evidence of the relationship between network structure and the temporal
+stability of multitrophic communities in natural settings.
+Although the relationships between diversity, total biomass and its stability
+found in experimental and in natural settings can be similar
+[e.g., @wu_relationship_2015; @li_relationship_2018], negative or non
+significant effects of species richness on total biomass have been found in some
 natural communities such as forests [@szwagrzyk_above-ground_2007;
@@
 responsible for negligible, or negative effects of species richness
-[@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015]. These
-different relationships might also arise from effects of the environment on both
-diversity and ecosystem functions [@loreau_biodiversity_2001].
+[@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015].
 
@@
 
-Environmental effects might also complicate (or obscure) the relationship
-between diversity and structure in driving stability and biomass in natural
-systems [@loreau_biodiversity_2001; @he_global_2013;
+When analyzing data from natural communities, the relationships among species
+richness, total biomass and species richness might also arise from effects of
+the environment on both diversity and ecosystem functions
+[@loreau_biodiversity_2001; @he_global_2013;
 @grace_integrative_2016]. Environment affects organism performance directly, and
@@
 
-Because their trophic interactions can be inferred, stream fish communities
+Because their trophic interactions are well known, stream fish communities
 constitute a good model to study the effects of network structure on total
@@
 interactions based on body size ratio was far better in stream ecosystems than
-in other aquatic and terrestrial ecosystems. Lastly, most of the diversity-biomass and diversity-stability
-relationships, have been assessed in terrestrial ecosystems while there is a
-evident need to test such relationships in a variety of ecosystem types.
-
-Our study aims to document the relationships between food web structure and
+in other aquatic and terrestrial ecosystems. Lastly, most of the
+diversity-biomass and diversity-stability relationships, have been assessed in
+terrestrial ecosystems while there is a evident need to test such relationships
+in a variety of ecosystem types.
+
+Our aim is to document the relationships among species richness, food web structure, 
 total biomass and its temporal stability in natural communities. To do so, we
 used the ONEMA dataset consisting in standardized sampling of fish communities
-in French streams [@edeline_ecological_2013]. 99 sites were sampled for more than 10
+in French streams [@edeline_ecological_2013]. We selected 99 sites that were sampled for more than 10
 years spanning on the 1995-2018 period. We inferred 1496 interaction networks,
-based on body size and diet. We question whether species richness,
-connectance and average trophic level increase, decrease or are not related to
+based on body size and diet. We question whether species richness, connectance
+and average trophic level increase, decrease or are not related to
 total biomass and its temporal stability. We further question whether the
 species richness, connectance, and average trophic level have antagonistic or
-synergistic effect on total biomass and its temporal stability. Finally, we
+mutual effect on total biomass and its temporal stability. Finally, we
 question if ecosystem size and average temperature increase total biomass and
@@
   #species richness and network metrics.",
-  "(A) Observation sites (black dots) were located across France and monitored
-  on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
-  "Inner borders draw the limits of the hydrographic basins. ",
-  "(B) The metaweb. Each trophic species (N = 412) is represented by a node and
-  each color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
-  "(C) Subset over network variation through time. The species names
-  corresponding to the three digit codes are found in Table SXX."
-)
-```
-
-```{r matmet, fig.cap = matmet_cap}
-myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))
-
-# Network inference
-net_method_path <- mypath("manuscript/bef_stability/figs",
-  "hypothesis.pdf")
-metaweb_path <- mypath("manuscript/bef_stability/figs",
-  "metaweb.png")
-library(magick)
-
-p_net_method <- cowplot::ggdraw() +
-  cowplot::draw_image(magick::image_read_pdf(net_method_path))
-p_metaweb <- cowplot::ggdraw() +
-  cowplot::draw_image(magick::image_read(metaweb_path))
-
-top <- plot_grid(p_net_method, p_st, ncol = 2, rel_widths = c(1, 1), labels =
-  "AUTO")
-bottom <- plot_grid(p_metaweb, temporal_network, ncol = 2,
-  rel_widths = c(1, 1), labels = c("C", "D"))
-
-left <- plot_grid(p_st, p_metaweb, ncol = 1, rel_widths = c(1, 1), labels =
-  c("A", "B"))
-p_test <- plot_grid(left, temporal_network, ncol = 2, labels = c("A", "C"))
-
-p_method <- plot_grid(top, bottom, nrow = 2, rel_heights = c(1, 1),
-  labels = c("", "C"))
-save_plot(
-  filename = mypath("manuscript/bef_stability/figs",
-    "method_fig.pdf"),
-  p_test, nrow = 2, ncol =2,
-  base_width = 7/2.54,
-  base_asp = 0.3
-)
-p_test
+  "Yearly temporal series of networks of two stations having respectively a low (A) and high
+  (B) temporal stability of biomass. A and B stations have respectively the
+  closest stability to the first and third quartile of the distribution of the
+  temporal stability of biomass in the dataset. Point size are proportional to
+  the biomass of the trophic species.  (C) Observation sites (black dots) were
+  located across France and monitored on the period 1995-2018. ", "Grey shades
+  highlighted elevalation variation. ", "Inner borders draw the limits of the
+  hydrographic basins. ", "(D) The metaweb. Each trophic species (N = 412) is
+  represented by a node and each color represent a species (S = 45). Resource
+  nodes (7) were drawn in grey. ", "The species names corresponding to the three
+  digit codes are found in Table SXX."
+)
+```
+
+```{r matmet, fig.cap = matmet_cap, results = "fig.show"}
+library(knitr)
+include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"))
+```
+
+```{r}
+# Basin
+st_basin <- get_basin_station(sf_obj = FALSE)
+
+# Select fishing operation 
+myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
+myload(biomass_ts_sax, dir = mypath("data"))
+op_analysis_bbb <- filter(op_analysis, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+range_surface <- map_dbl(c(min, max), ~.x(op_analysis_bbb$surface, na.rm =TRUE))
+# quantile(op_analysis_bbb$surface, na.rm =TRUE)
 ```
@@
 0.7m, the sampling was done over the bank by foot or by boat. The sampling
-season spanned from late spring to autumn. During sampling, all the fishes
-caught were identified and recorded. For each species, either the body size of
-all fish was measured, or a representative sample when the number of fish was
-high (Figure S1, supplementary information). The fishes were released at the end
-of the sampling. Additionally, the physical characteristics of the river was
-recorded during sampling as well as the sampling effort, quantified as the
-surface sampled (range XXX-XXX).
+season spanned from late spring to autumn. One sampling event correspond to a
+sampling a given year in a given sampling station. During sampling, all the
+fishes caught were identified. For each species, either the body size of all
+fish was measured, or a representative sample when the number of fish was high
+(Figure S1, supplementary information). The fishes were released at the end of
+the sampling. Additionally, the physical characteristics of the stream were 
+recorded during sampling event as well as the sampling effort, quantified as the
+surface sampled (range `r range_surface[1]`-`r range_surface[2]` square metres).
 
 The stations where the stream was of intermediate size could be sampled
-alternatively with one of the two sampling protocols. When it was the case, we
-kept only the most frequently used sampling protocol. Finally, we kept stations
-that had been sampled ten years or more. there was low heterogeneity of the sampling month
-within stations, with the median sampled month being 
+alternatively with one of the two sampling protocols. In this case, we
+kept only the most frequently used sampling protocol. Then, we selected the
+stations that had been sampled ten years or more. There was low heterogeneity of
+the sampling month within stations, with the median sampled month being
 mid-August while the median of the standard deviation of the sampled month
-within station was $0.7$. As the concept of community variability referred to variability
-around an equilibrium, which is rarely observed or difficult to characterize in
-natural communities, only those stations with no temporal trends in total
-biomass were selected (detailed in supplementary methods). However, the results
-were robust to the relaxation of this hypothesis (Supplementary results). These
-selections resulted in 99 stations distributed over seven hydrographic basins
-(Figure \@ref(fig:matmet) A).
+within station was $0.7$. As the concept of community variability referred to
+variability around an equilibrium, which is rarely observed or difficult to
+characterize in natural communities, only stations with no temporal trends
+in total biomass were selected (detailed in supplementary methods). However, the
+results were robust to the relaxation of this hypothesis (Supplementary
+results). These selection steps resulted in 99 stations distributed over seven
+hydrographic basins (Figure \@ref(fig:matmet) A).
 
@@
 (See supplementary methods, Figure S1). The body mass of each individual was
-then estimated using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$
-being the body mass in grams, $l$ the body size in millimeters and $i$ the
-individual), where the coefficients $0.01$ and $3.03$ comes from two
+then estimated using an allometric law $B_i = 0.01 \times l_i^{3.03}$, $B$
+with the body mass in grams, $l$ the body size in millimeters, $i$ the
+individual and where the coefficients $0.01$ and $3.03$ comes from two
 meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006]. Species
@@
 sampled, i.e. $gm^{-2}$. In the analysis, the total biomass of a
-station has been defined as the median of the total biomass acrossall times.
+station has been defined as the median of the total biomass across sampling
+events.
 
@@
 
-In order to describe the mechanisms driving the temporal stability of biomass, we
-decomposed the $CV$ of total biomass ($CV_{com}$) into a synchrony ($\phi$) and
-a
-weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
+We described the mechanisms driving the temporal stability of biomass, by
+decomposing the $CV$ of total biomass ($CV_{com}$) into a synchrony ($\phi$) and
+a weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
 @thibaut_understanding_2013:
@@
 
-Species richness was computed as the total number of species present across all times
+Species richness was computed as the total number of species present across
+sampling events 
 in a given station. As for biomass, we controlled species richness for sampling
 effort by dividing the total number of species by the total surface sampled in
-the given station. Species richness was then expressed in number of species by
+the given station. Species richness was then expressed in number of species per 
 square meter sampled.
 
-### Network building
+### Network inference
 
@@
 following previous studies [@gravel_inferring_2013; @brose_predator_2019;
-@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
+@poisot_structure_2016]. The diet of stream fishes, as for many organisms, shifts
 throughout an individual's life, and thereby with body size. For example, alvins
-feed on plankton while adults may feed on algae, fishes, with bigger individuals
+feed on plankton while adults may feed on algae and fishes, with bigger individuals
 eating bigger
@@
 of trophic interactions was shown to be more accurate when considering body size
-classes, i.e. trophic species, rather than species [@jennings_weak_2001].
-
-The feeding interactions of a fish node, i.e a trophic species, were determined
-by both its species identity and its body size. Then, species identity allowed to
+classes, i.e. trophic species, than species [@jennings_weak_2001].
+
+The feeding interactions of a fish node, i.e. a trophic species, were determined
+by both its species identity and its body size. Species identity allowed to
 differentiate between piscivorous and non piscivorous species, to know which
@@
 
-For a piscivorous trophic species, i.e. a piscivorous node, the fish-fish
+For a piscivorous trophic species, the fish-fish
 trophic links was defined in two steps and based on the body size ratio between
-predators and prey. First of all, the predation window of a piscivorous node was
+predators and prey. First of all, the predation window of a piscivorous trophic specie was
 defined as 3% to 45% of its midpoint [@mittelbach_ontogeny_1998;
 @claessen_impact_2002; @hart_handbook_2008]. Then, a trophic link was set
-between the piscivorous node and every node whose midpoint
-was included in the predation range (Figure S2). The fish-resource trophic
+between the piscivorous trophic species and every trophic species whose midpoint
+was included in the predation window (Figure S2). The fish-resource trophic
 links were set between the trophic species and the resources nodes according the
 food diet of their size class, for both the piscivorous and non piscivorous
-trophic species. Lastly, the trophic links between resource nodes were set
-according to the food diet data [@allan_stream_2007; @hart_handbook_2008].
+trophic species. Lastly, the trophic links among resource nodes were set
+according to the literature [@allan_stream_2007; @hart_handbook_2008].
 
@@
 computed two of the most commonly used network metrics to characterize food
-webs, namely the connectance and mean trophic level. 
-The networks metrics were also based on the trophic species,
-i.e. body size classes. Connectance describes the level of generalism in the
-network and is calculated as the actual number of
+webs, namely the connectance and mean trophic level. Connectance describes the
+level of generalism in the network and is calculated as the actual number of
 interactions divided by the maximum number of interactions if all species interact
@@
 
-```{r}
-# Basin
-st_basin <- get_basin_station(sf_obj = FALSE)
-
-# Select fishing operation 
-myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
-myload(biomass_ts_sax, dir = mypath("data"))
-op_analysis_bbb <- filter(op_analysis, station %in%
-  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
-op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
-  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
-
-```
-
 ```{r, fig.show = "hide"}
@@
 
-mysave(habitat_press, habitat_pressure, dir = mypath("data"))
+mysave(habitat_press, habitat_pressure, dir = mypath("data"), overwrite = TRUE)
 
@@
   )
-
+mysave(sem_data, dir = mypath("data"), overwrite = TRUE)
 ```
@@
 
-We had one environmental variable value for each site and year event, except
+We had one environmental variable value for each sampling event, except
 for water temperature for which the record began in 2006. Then, we computed the
@@
 
-The structural equation models were based on Gaussian linear models, some variables
+The structural equation models were based on Gaussian linear models, all variables
+except the connectance and average trophic level
 were logged to fulfill model assumptions (see residual plots and data
@@
   order_env_node = c("log_RC1", "log_RC2"),
-  metamodel = TRUE
+  metamodel = TRUE,
+  inverse_y_node_pose = TRUE
 )
@@
   env_y_sep = 1.5,
-  order_env_node = c("log_RC1", "log_RC2")
+  order_env_node = c("log_RC1", "log_RC2"),
+  inverse_y_node_pose = TRUE
 )
@@
   coefficients are standardized coeffients. For convenience, only significant
-  paths (i.e, *P < 0.05*) are shown."
+  paths (i.e, *P < 0.05*) are shown. Rsq: Ajusted R square."
 
@@
 plot_grid(
-  meta_stab_sem_rich, meta_bm_sem_rich,
-  p_stab_sem_rich, p_bm_sem_rich,
+  meta_bm_sem_rich, p_bm_sem_rich,
+  meta_stab_sem_rich, p_stab_sem_rich,
   labels = LETTERS[1:4], nrow = 2,
@@
 tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
+ct_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "ct")
 RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC1")
@@
   p_val_thl = 0.05, type = "std")
-
-tmp_bm_indir_table <- map(list(env_on_bm, rich_on_bm),
+# direct
+ct_on_bm_trick <- list(direct = c(ct = ct_on_bm), total = c(ct = ct_on_bm))
+tlvl_on_bm_trick <- list(direct = c(t_lvl = tlvl_on_bm), total = c(t_lvl = tlvl_on_bm))
+
+tmp_bm_indir_table <- map(list(env_on_bm, rich_on_bm, ct_on_bm_trick,
+    tlvl_on_bm_trick),
   ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
@@
   p_val_thl = 0.05, type = "std")
-com_on_stab <- get_com_on_stab(fit = stab_all_params,
+ct_on_stab <- get_ct_on_stab(fit = stab_all_params,
   p_val_thl = 0.05, type = "std")
-
-tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, com_on_stab),
+tlvl_on_stab <- get_tlvl_on_stab(fit = stab_all_params,
+  p_val_thl = 0.05, type = "std")
+
+tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, ct_on_stab, tlvl_on_stab),
   ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
@@
 
-Overall, the structural equation models explained a large part of the variation
+The structural equation models explained a large part of the variation
 of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
@@
 `r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_stab$total`$, Figure
-\@ref(fig:sem-plot) C and D), meaning that the effects of species richness and
-network structure are not independant.
+\@ref(fig:sem-plot) C and D), meaning that a part of the effects of species richness went 
+through network structure.
 
@@
 Species richness and mean trophic level had a significant positive direct effect
-on total biomass ($r_\delta = `r rich_on_bm$direct`$ and $r_\delta = 
-`r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) D, Table \@ref(tab:indir-sem)),
-while connectance had no direct significant effect on total biomass (Figure
-\@ref(fig:sem-plot) D). The total effect of mean trophic level
-on total biomass was of the same magnitude than the one of species richness
-(resp. $`r tlvl_on_bm`$ and $`r rich_on_bm$total`$, Table \@ref(tab:indir-sem)).
+on total biomass ($r_\delta = `r rich_on_bm$direct`$ and 
+$r_\delta = `r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) D, Table
+\@ref(tab:indir-sem)),
+while connectance had no direct effect on total biomass (Figure
+\@ref(fig:sem-plot) D).
 
 The two PCA axis capturing environmental variables had no significant direct effects on total biomass
-(Table SXX), but indirect (Table \@ref(tab:indir-sem)). The first axis, PCA1,
+, but indirect (Table \@ref(tab:indir-sem)). The first axis, PCA1,
 related to the stream size was positively linked to total biomass ($r_\delta = 
 `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
-through species richness and mean trophic level too ($r_\delta = 
-`r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
+through both species richness and mean trophic level ($r_\delta = 
+`r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_tlvl["log_RC1"]`$
 resp., Table \@ref(tab:indir-sem)). The second axis, PCA2, related to the average
@@
 negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
-Table \@ref(tab:indir-sem)). On the one hand, species richness had a direct
-negative effect on synchrony ($r_\delta = `r rich_on_sync$direct`$), thereby
+Table \@ref(tab:indir-sem)). This effect resulted from two opposite effects. On
+the one hand, species richness had a direct negative effect on synchrony
+($r_\delta = `r rich_on_sync$direct`$), thereby
 increasing stability ($r_\delta = `r rich_on_stab$via_sync`$). On the other
@@
 the same magnitude than the one of species richness (resp.
-$`r com_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
+$`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
 \@ref(tab:indir-sem)).
@@
 Figure \@ref(fig:sem-plot) C) and thereby had a total positive
-effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
+effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$,
 Table \@ref(tab:indir-sem)). Connectance had no significant direct effect on either
 $\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
-(Figure \@ref(fig:sem-plot) C, Table SXX).
+(Figure \@ref(fig:sem-plot) C, Table \@ref(tab:indir-sem)).
 
@@
 (resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
-$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-sem)).
+$r_\delta = `r env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)).
 This was also true for the PCA1, related to stream size, but effects were weaker
@@
 
-```{r indir-stab, results = TRUE}
+```{r indir-stab}
 caption_sem <- paste0(
@@
   effect, only the significant direct effects were taken into account. ",
-  "Network structure being the indirect effect that went through both avg trophic
-  level and connectance and Species richness_Network structure being the
-  indirect effect that went through (i) species richness and from (ii) species
-  richness to network structure."
+  "As an example, the indirect effect via species richness takes into account
+ the direct effect of species richness as well as the effect of species richness
+ through connectance and average trophic level. ",
+ "NA values indicate that the corresponding paths do not exist in the
+ specified Structural Equation Model (SEM)."
 )
@@
 ) %>%
-select(variable, direct, via_richness, via_richness_com, via_com, via_cv_sp, via_sync, total) %>%
-format_table()
-
-kable(full_table,
+mutate(`SEM type` = c(rep("Total annual biomass", 5), rep("Temporal Stability of annual biomass", 5))) %>%
+select(`SEM type`, variable, direct, via_richness, via_ct, via_tlvl, via_cv_sp, via_sync, total) %>%
+format_table() %>%
+select(`SEM type`, everything())
+
+library(kableExtra)
+mytable <- kable(full_table,
   format = "latex",
@@
   ) %>%
-kable_styling(latex_options =c("striped", "scale_down")) %>%
-pack_rows("Total biomass", 1, 3) %>%
-pack_rows("Temporal stability of biomass", 4, 8)
+#kable_paper() %>%
+kable_styling(latex_options =c("scale_down")) %>%
+column_spec(1:2, width = "3cm") %>%
+collapse_rows(columns = 1, valign = "top")
+write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
+```
+
+```{=latex}
+\input{table.tex}
 ```
@@
 
-Overall, our study is unique by its level of integration, from environmental
+Overall, its study is unique by its level of integration, from environmental
 effects to total biomass and stability, going through species richness and
-network structure, and the first direct assessment of a possible joint effect of
+network structure. It is the first direct assessment of a possible joint effect of
 species richness and network structure on both total biomass and its temporal
@@
 and so results in higher total biomass in the fish compartment. A reason for
-such an absence of an effect might be explained by the fact that our data lack information about the
-lower compartments of the community, i.e, the primary producers, zooplankton and
-zoobenthos.
+such an absence of an effect might be explained by the fact that our data lack
+information about the lower compartments of the community, i.e, the primary
+producers, zooplankton and zoobenthos.
 
@@
 considered different stability concepts and metrics [@arnoldi_resilience_2016].
-However, our measure of connectance suffers limitation (discussed above) and
-further research should examine the effect of connectance on temporal stability
-in more complete empirical foodwebs.
+However, our measure of connectance does not include the variability of the
+lower compartments of the foodweb and further research should examine the effect
+of connectance on temporal stability in more complete empirical foodwebs.
 
@@
 network structure, or destabilising, via species richness. The first pathway
-consists in a positive effect of temperature and stream properties on mean
+consists in a positive effect of temperature and stream size on mean
 trophic level, in line with the idea that wider streams and warmer conditions
@@
 has a destabilising effect. This result is interesting in that both
-pathways had not been evidenced to be jointly to play, as far as we know.
+pathways had not been evidenced to jointly play, as far as we know.
 Furthermore, it is unclear which pathway is dominating, and under which circumstances,

### 2020-10-22 manuscript/bef_stability/manuscript.Rmd
Add affiliations

@@
 - Author affiliation:
-  - Alain Danet:
-  - Maud Mouchet:
+  - Alain Danet: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
+    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
+    Paris, 43 rue Buffon, 75005 Paris, France
+  - Maud Mouchet: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
+    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
+    Paris, 43 rue Buffon, 75005 Paris, France
   - Willem Bonnaffe: Ecological and Evolutionary Dynamics Lab. Zoology Research
@@
     Kingdom.
-  - Elisa Thebault: 
-  - Colin Fontaine:
+  - Elisa Thebault: Sorbonne Université, CNRS, IRD, INRAE, Université Paris Est
+    Créteil, Institute of Ecology and Environmental Sciences of Paris
+    (iEES-Paris), Paris, France  
+  - Colin Fontaine: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
+    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
+    Paris, 43 rue Buffon, 75005 Paris, France
 
@@
 - Number of words:
-  - Abstract: 184
+  - Abstract: 172
   - Main text: 4929
@@
   - Alain Danet
-  - UMR 7204 CESCO, BP 61; 45, rue Buffon, 75005 Paris, France
+  - UMR 7204 CESCO, CP 135; 43, rue Buffon, 75005 Paris, France
   - alain.danet@mnhn.fr 
@@
 
-Both the relationship between diversity and ecosystem functioning, and between food
-web complexity and stability, have received considerable attention during the
-last decades in ecology. The former relationship remains rarely investigated
-in the context of food webs, especially in empirical studies explicitly
-considering food web structures, the latter has been mainly the focus of
-theoretical studies and empirical tests are critically missing. Here we link
-species richness, food web structure and annual biomass and its temporal stability
-using a dataset of standardized fish sampling in French streams running from
-1995 to 2018. We inferred trophic interactions thanks to recorded body size and
-diet literature. We reveal that species richness and average trophic level had a
-positive relationship with annual biomass of fish communities while they had
-respectively a negative and positive effect on its temporal stability. We
-also found that the effects of stream size and temperature on annual biomass and
-stability are partly mediated by their effects on diversity and food web
-structure. Overall, our study opens fruitful perspectives on the link between
-species richness, network structure, ecosystem properties and their stability.
+Both biodiversity-ecosystem functioning (BEF) and foodweb complexity-stability
+relationships have received considerable attention during the last decades.
+Still, the BEF relationship remains rarely investigated in the context of food
+webs, especially in empirical studies explicitly considering foodweb structures.
+Foodweb stability-complexity relationship has been mainly the focus of
+theoretical studies with very empirical testing. To fill this gap, we link
+species richness, foodweb structure and annual biomass and its temporal
+stability using a standardized monitoring of fish communities in French streams
+running from 1995 to 2018. We inferred trophic interactions thanks to recorded
+body size and diet literature. We reveal that species richness and average
+trophic level had a positive relationship with annual biomass of fish
+communities while they had respectively a negative and positive effect on its
+temporal stability. We also found that the effects of stream size and
+temperature on annual biomass and stability are mediated by their effects on
+diversity and foodweb structure. Overall, our study opens fruitful perspectives
+on the link between species richness, network structure, biomass and its
+stability.
 
@@
 functioning remains traditionally focused on single trophic levels, ignoring the
-effects of food web structure. Theoretical models have recently moved from
+effects of foodweb structure. Theoretical models have recently moved from
 single trophic [@tilman_plant_1997;
@@
 the two main mechanisms previously highlighted in single-trophic studies, are
-also important to understand diversity effects in food webs
+also important to understand diversity effects in foodwebs
 [@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
@@
 Despite these theoretical evidences that structure affects biomass, we are
-lacking empirical studies that assess jointly how food web structure and species
+lacking empirical studies that assess jointly how foodweb structure and species
 diversity affect total biomass and its production.
@@
 has been mostly explored in single trophic level systems or without accounting
-for food web structure, even more so than the relationship between diversity and
+for foodweb structure, even more so than the relationship between diversity and
 biomass production.
@@
 In addition to diversity,
-food web structure is expected to strongly affect the stability of communities
+foodweb structure is expected to strongly affect the stability of communities
 and ecosystems, as outlined by the large body of theoretical studies on this
@@
 to be addressed jointly. Despite the long-standing interest for the links
-between food web complexity and stability in ecology, we still have very few
+between foodweb complexity and stability in ecology, we still have very few
 evidence of the relationship between network structure and the temporal
@@
 
-Our aim is to document the relationships among species richness, food web structure, 
+Our aim is to document the relationships among species richness, foodweb structure, 
 total biomass and its temporal stability in natural communities. To do so, we
@@
 ```{r}
+myload(qt_station, dir = mypath("data"))
 matmet_cap <- paste0( 
-  #"(A) Conceptual model of the hypothesized relationships between environment,
-  #species richness, network metrics and total biomass / biomass stability. ",
-  #"Solid and dashed arrows represent respectively direct and indirect effects.
-  #",
-  #"The blue, green and blue/green dashed arrows being respectively indirect
-  #effects going through species richness, network metrics and through both
-  #species richness and network metrics.",
-  "Yearly temporal series of networks of two stations having respectively a low (A) and high
-  (B) temporal stability of biomass. A and B stations have respectively the
-  closest stability to the first and third quartile of the distribution of the
-  temporal stability of biomass in the dataset. Point size are proportional to
-  the biomass of the trophic species.  (C) Observation sites (black dots) were
-  located across France and monitored on the period 1995-2018. ", "Grey shades
-  highlighted elevalation variation. ", "Inner borders draw the limits of the
-  hydrographic basins. ", "(D) The metaweb. Each trophic species (N = 412) is
-  represented by a node and each color represent a species (S = 45). Resource
-  nodes (7) were drawn in grey. ", "The species names corresponding to the three
-  digit codes are found in Table SXX."
-)
+  "Yearly temporal series of networks of two stations having respectively a low
+  (A) and high (B) temporal stability of biomass. A and B stations have
+  respectively biomass stability the closest to the first and third quartile of
+  the distribution of the temporal stability of biomass in the dataset,
+  respectively ",
+  round(qt_station$bm_std_stab[1],2), " and ", round(qt_station$bm_std_stab[2],
+    2),
+  ". Point size are proportional to the biomass of the trophic species. (C)
+  Observation sites (black dots) were located across France and monitored on the
+  period 1995-2018. Red dots being the location of (A) and (B) sites. ",
+  "Inner borders draw the limits of the hydrographic basins. ", "(D) The metaweb
+  of the study. Each trophic species (N = 412) is represented by a node and each
+  color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
+  "The species names corresponding to the three digit codes are found in Table
+  SXX.")
+
 ```
@@
 range_surface <- map_dbl(c(min, max), ~.x(op_analysis_bbb$surface, na.rm =TRUE))
+range_surface[1] <- ceiling(range_surface[1] / 10) * 10
+range_surface[2] <- ceiling(range_surface[2] / 100) * 100
 # quantile(op_analysis_bbb$surface, na.rm =TRUE)
@@
 and network structure directly affect total biomass (Figure \@ref(fig:sem-plot)
-B) and that species richness affected food web structure
+B) and that species richness affected foodweb structure
 [@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010].
@@
   fit = stab_sem_rich,
-  file_path = mypath("manuscript", "bef_stability", "meta_stab_sem"),
-  format = "png",
+  file_path = mypath("manuscript", "bef_stability","figs", "meta_stab_sem"),
+  format = "pdf",
   width = 700*2,
@@
   fit = stab_sem_rich,
-  file_path = mypath("manuscript", "bef_stability", "stab_sem"),
-  format = "png",
+  file_path = mypath("manuscript", "bef_stability", "figs", "stab_sem"),
+  format = "pdf",
   width = 700*2,
@@
   fit = bm_sem_rich,
-  file_path = mypath("manuscript", "bef_stability", "meta_bm_sem"),
-  format = "png",
+  file_path = mypath("manuscript", "bef_stability", "figs", "meta_bm_sem"),
+  format = "pdf",
   width = 700*2,
@@
   fit = bm_sem_rich,
-  file_path = mypath("manuscript", "bef_stability", "bm_sem"),
-  format = "png",
+  file_path = mypath("manuscript", "bef_stability", "figs", "bm_sem"),
+  format = "pdf",
   width = 700*2,
@@
   "Results of the Structural Equation Models for (C) the
-  determinants of biomass stability and (D) total biomass. Red and green
+  determinants of biomass stability and (D) total biomass. Red and green arrows
   represent respectively negative and positive path coefficients. The path
-  coefficients are standardized coeffients. For convenience, only significant
-  paths (i.e, *P < 0.05*) are shown. Rsq: Ajusted R square."
-
-)
-```
-
-```{r sem-plot, fig.height = 7, fig.cap = sem_caption}
+  coefficients are standardized. For convenience, only significant
+  paths (i.e. $P < 0.05$) are shown. Rsq: Ajusted $R^2$; Avg:
+  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
+  second axis of the PCA."
+)
+```
+
+```{r sem-plot, fig.height = 6, fig.cap = sem_caption}
 #https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
@@
 caption_sem <- paste0(
-  "Direct, indirect and total effect of environment, species richness and
-  network structure, i.e. connectance and mean trophic level on total biomass
+  "Direct, indirect and total effects of environment, species richness,
+  connectance and mean trophic level on total biomass
   and its temporal stability. Indirect effects are computed by multiplying the
@@
   variable. For exemple, the indirect effect of species richness on
-  biomass stability via its effect on CVsp is $-0.61$. To compute indirect
-  effect, only the significant direct effects were taken into account. ",
-  "As an example, the indirect effect via species richness takes into account
- the direct effect of species richness as well as the effect of species richness
- through connectance and average trophic level. ",
+  biomass stability via its effect on CVsp is $-0.62$. Only the
+  significant direct effects were retained for the computation of indirect
+  effects. ", "As an example, the indirect effect via species richness takes
+  into account the direct effect of species richness as well as the effect of
+  species richness through connectance and average trophic level.",
  "NA values indicate that the corresponding paths do not exist in the
@@
 kable_styling(latex_options =c("scale_down")) %>%
+add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
 column_spec(1:2, width = "3cm") %>%
 collapse_rows(columns = 1, valign = "top")
+#str_replace(mytable, "\\\\#(.*)", "\\\\label{tab:indir-sem}")
+#str_view(mytable, "\\\\#(.*)")
 write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
@@
 effects to total biomass and stability, going through species richness and
-network structure. It is the first direct assessment of a possible joint effect of
-species richness and network structure on both total biomass and its temporal
-stability. We found that species richness and mean
-trophic level had a positive effect on total biomass. In contrast, species
-richness had a negative effect on temporal stability whereas mean trophic level
-covaried positively. We also found that the effect of species richness and mean
-trophic level on total biomass and its temporal stability were not independant
-as species richness had a negative effect on mean trophic level.  Furthermore,
-we found that connectance had no significant effect on both total biomass and
-its temporal stability. Finally, we found that the magnitude of the effects of
-average temperature and altitude was equal or superior to the effects of species
-richness and mean trophic level.
+network structure. It is the first direct assessment of a possible joint effect
+of species richness and network structure on both total biomass and its temporal
+stability. We found that species richness and mean trophic level had a positive
+effect on total biomass. In contrast, species richness had a negative effect on
+temporal stability whereas mean trophic level covaried positively. We also found
+that the effect of species richness and mean trophic level on total biomass and
+its temporal stability were not independant as species richness had a negative
+effect on mean trophic level.  Furthermore, we found that connectance had no
+significant effect on both total biomass and its temporal stability. Finally, we
+found that the magnitude of the effects of average temperature and altitude was
+equal or superior to the effects of species richness and mean trophic level.
 
@@
 
-Surprisingly we found a negative relationship between temporal stability and
+Surprisingly, we found a negative relationship between temporal stability and
 species richness. Overall, it contrasts with experimental studies in grasslands
-[@tilman_biodiversity_2006]; mesocosms (Pennekamp et al. 2018), in 
-butterflies natural communities [@olivier_urbanization_2020] or even in lotic
+[@tilman_biodiversity_2006; @valencia_synchrony_2020]; mesocosms (Pennekamp et al. 2018), in 
+natural communities of butterflies [@olivier_urbanization_2020] or even in lotic
 fish communities [@franssen_annual_2011] where positive relationships were found
@@
 
-A first step to identify the mechanisms behind those contrasting patterns is to
+The first step to identify the mechanisms behind those contrasting patterns is to
 look at the effects of species richness on synchrony and $\overline{CV_{sp}}$.
-As most studies on the topic, in experimental grasslands
-[@isbell_biodiversity_2009; @roscher_identifying_2011], in natural communities
+As most studies on experimental grasslands
+[@isbell_biodiversity_2009; @roscher_identifying_2011] and natural communities
 of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
 @olivier_urbanization_2020], we found that species richness decreases synchrony,
-thereby increasing stability [but see @declerck_species_2006]. Our study thus
-extends the evidence that species richness decrease synchrony to the case of empirical
-trophic communities. Species richness can reduce synchrony when a given
-increase in species richness leads to a decrease of population sizes but also in
-the case where species have different responses to environmental variation
-[@loreau_species_2008].
+thereby increasing stability [but see @declerck_species_2006;
+@valencia_synchrony_2020]. Our study thus extends the evidence that species
+richness decreases synchrony to the case of trophic communities in natural
+settings. Species richness can reduce synchrony when (i) a given increase in species
+richness leads to a decrease of population sizes which raises the role of
+demographic stochasticity, when (ii) species have different
+responses to environmental variation [@loreau_species_2008].
 
@@
 stability of populations and species richness depends on interaction strength
-and their distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
+and its distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
 @brose_allometric_2006], high interaction strength inducing a negative
 relationship. Therefore, it is possible that our results are due to a high
-degree of omnivory in food webs, which combined with strong trophic interactions
+degree of omnivory in foodwebs, which combined with strong trophic interactions
 lead to more fluctuations in population biomass.
@@
 In contrast, connectance had no effect on total biomass. One might have expected
-that an increase in connectance may translate in higher total nutrient uptake
+that an increase in connectance may translate in a higher total nutrient uptake
 and so results in higher total biomass in the fish compartment. A reason for
 such an absence of an effect might be explained by the fact that our data lack
-information about the lower compartments of the community, i.e, the primary
+information about the lower compartments of the community, i.e., the primary
 producers, zooplankton and zoobenthos.
@@
 effect on $\overline{CV_{sp}}$, thereby increasing average species stability. It
-might be because species at higher trophic level are more stable than the species at
-lower trophic levels as predicted by food chain models in the presence of
-strong top-down control [@barbier_pyramids_2019; @shanafelt_stability_2018] but it
-is not sure that it holds when considering omnivorous species
+might result from a higher stability of higher trophic level as predicted by
+food chain models in the presence of strong top-down control
+[@barbier_pyramids_2019; @shanafelt_stability_2018]. But it
+might not hold when considering omnivorous species
 [@wang_biodiversity_2016]. An alternative explanation is that higher mean
-trophic level leads to stronger top-down control and resource complementarity
+trophic level leads to a stronger top-down control and resource complementarity
 and thus reduce biomass fluctuations in lower trophic levels
@@
 variability ($\overline{CV_{sp}}$) had a stronger negative effect on biomass
-stability than synchrony [@tilman_biodiversity_2006; @bluthgen_land_2016;
+stability than synchrony [@tilman_biodiversity_2006;
 @olivier_urbanization_2020]. It explains why we observe a negative effect of
@@
 might be explained by the presence of generalist predators in stream
-communities, which can raise synchrony between prey species which share the
-same predator [@raimondo_interspecific_2004] and thus decreases the
-occurrence of compensatory population dynamics. Alternatively, it is possible that, in
-aquatic foodwebs, the occurrence of large oscillatory dynamics
-[@mccann_reevaluating_1997] leads to a higher contribution of population
-variability rather than synchrony to community stability. How both
-strengths and the relative contribution of synchrony and population
-variaribility to overall stability vary between foodwebs and single trophic communities is
-still an open question.
+communities, that raise synchrony between prey species that share the
+same predator and thus reduces compensatory
+population dynamics [@raimondo_interspecific_2004]. Alternatively, it is
+possible that, in aquatic foodwebs, the occurrence of large oscillatory dynamics
+ leads to a higher contribution of population
+variability rather than synchrony to community stability
+[@mccann_reevaluating_1997]. How both strengths and the relative contribution of
+synchrony and population variaribility to overall stability vary between
+foodwebs and single trophic communities is still an open question.
 
@@
 
-Consistent with research showing that food webs in wider streams, are also
-larger, and hence support more species and biomass [@allan_stream_2007], we
-found that the PCA axis related to stream size had a positive effect on total
+Consistent with research showing that foodwebs in wider streams support more
+species and biomass [@allan_stream_2007], we found that the PCA axis related to
+stream size had a positive effect on total
 biomass through a positive effect on mean trophic level. Greater ecosystem size
@@
 has a destabilising effect. This result is interesting in that both
-pathways had not been evidenced to jointly play, as far as we know.
+pathways had not been evidenced to jointly play, to the best of our knowledge.
 Furthermore, it is unclear which pathway is dominating, and under which circumstances,
@@
 While theoretical ecology has focused on the effects of network structure on
-stability, empirical ecology has focused on species richness but often did not considere network
-structure. Furthermore, both fields have largely used different stability
-metrics. Our work is hence contributing to bridging the gap between
-theoretical and empirical ecology.
+stability, empirical ecology has focused on species richness but often did not
+consider network structure. Furthermore, both fields have largely used
+different stability metrics. Our work is hence contributing to bridging the gap
+between theoretical and empirical ecology.
 
@@
 environmental gradient related to temperature and ecosystem size have
-antagonistic effects on biomass temporal stability, positive through mean
+antagonistic effects on biomass and its temporal stability, positive through mean
 trophic level and negative through species richness. Further research is needed
@@
 observed interactions, and the lack of information about the foodwebs outside
-fishes. We look forward to see our findings and their interpretation tested by
-experimental and theoretical works considering foodwebs, allowing explore the
-effects of omnivory and ontogeny on the link between network structure and
-ecosystem functioning.
+fishes. But this approach is a promising way to explore how the architecture of
+ecological networks vary along environmental gradients across time. It
+constitutes an interesting complement to the real assessment of ecological
+interactions. The use of inferred networks also allow to maximise the
+information contained from already available long term datasets.
+
+We look forward to see our findings and their interpretation tested by future
+experimental and theoretical studies, allowing to unravel the ecological
+mechanisms driving the complex relationships among environment, the structure of
+ecological networks and ecosystem properties such as productivity and temporal
+stability.
 

### 2020-10-23 manuscript/bef_stability/manuscript.Rmd
Fix figure label reference in main text

@@
   - Abstract: 172
-  - Main text: 4929
-
-- Number of references: XXX
+  - Main text: 5383
+
+- Number of references: 87 
 - Number of figures: 2
@@
 
-```{r matmet, fig.cap = matmet_cap, results = "fig.show"}
+```{r matmet, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
 library(knitr)
-include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"))
+include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"),)
 ```
@@
 trophic interactions between all trophic species and the resources (Figure
-\@ref(fig:matmet) C), then (2) determine network of a given community by
+\@ref(fig:matmet) B), then (2) determine network of a given community by
 extracting the metaweb according to the trophic species present at a given
-site and sampling event (Figure \@ref(fig:matmet) D).
+site and sampling event (Figure \@ref(fig:matmet) C and D).
 
@@
 detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
-zoobenthos (grey nodes in Figure \@ref(fig:matmet) C & D). The fish trophic
+zoobenthos (grey nodes in Figure \@ref(fig:matmet) B, C & D). The fish trophic
 species and the resources constituted the 412 nodes of the metaweb, 45 fish
@@
 which a piscivorous species begin to feed on fishes. The ontogenic fish diet
-database was filled according to fishbase and literature (cf Bonnaffe ref). Each
+database was filled according to fishbase and literature [REF WILLEM]. Each
 fish species had two or three life stages which are delimited by a body size
@@
 to affect directly species richness and network structure, as well as annual total
-biomass (Figure \@ref(fig:sem-plot) B). We assumed that both species richness
+biomass (Figure \@ref(fig:sem-plot) A). We assumed that both species richness
 and network structure directly affect total biomass (Figure \@ref(fig:sem-plot)
-B) and that species richness affected foodweb structure
+A) and that species richness affected foodweb structure
 [@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010].
@@
 We used the same model structure for temporal stability of biomass (Figure
-\@ref(fig:sem-plot) A). Instead of the annual total biomass, we modelled the
+\@ref(fig:sem-plot) C). Instead of the annual total biomass, we modelled the
 synchrony and population variability which in turn determined the temporal
@@
 sem_caption <- paste0(
-  "Metamodel of the Structural Equation Models for (A) biomass stability and
-  (B) total biomass. ",
-  "Results of the Structural Equation Models for (C) the
-  determinants of biomass stability and (D) total biomass. Red and green arrows
-  represent respectively negative and positive path coefficients. The path
-  coefficients are standardized. For convenience, only significant
+  "Metamodel of the Structural Equation Models for the (A) median of annual
+  total biomass (in grams by square meter) and (C) its temporal stability.",
+  "Results of the Structural Equation Models for
+  (B) the determinants of the median of annual total biomass and (D) its temporal stability. Red and green
+  arrows represent respectively negative and positive path coefficients. The
+  path coefficients are standardized. For convenience, only significant
   paths (i.e. $P < 0.05$) are shown. Rsq: Ajusted $R^2$; Avg:
@@
 .45$, $.47$, $.49$ and $.38$) but less so for mean trophic level ($R^2 =
-.18$, Figure \@ref(fig:sem-plot) C and D). We found that species richness had a
+.18$, Figure \@ref(fig:sem-plot) B and D). We found that species richness had a
 significant negative effect on mean trophic level ($r_\delta = 
 `r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_stab$total`$, Figure
-\@ref(fig:sem-plot) C and D), meaning that a part of the effects of species richness went 
+\@ref(fig:sem-plot) B and D), meaning that a part of the effects of species richness went 
 through network structure.
@@
 on total biomass ($r_\delta = `r rich_on_bm$direct`$ and 
-$r_\delta = `r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) D, Table
+$r_\delta = `r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) B, Table
 \@ref(tab:indir-sem)),
 while connectance had no direct effect on total biomass (Figure
-\@ref(fig:sem-plot) D).
+\@ref(fig:sem-plot) B).
 
@@
 $r_\delta = `r cv_sp_on_stab`$ and $r_\delta = `r sync_on_stab`$, Figure
-\@ref(fig:sem-plot) C).
+\@ref(fig:sem-plot) D).
 
@@
 $\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
-Figure \@ref(fig:sem-plot) C) and thereby had a total positive
+Figure \@ref(fig:sem-plot) D) and thereby had a total positive
 effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$,
@@
 $\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
-(Figure \@ref(fig:sem-plot) C, Table \@ref(tab:indir-sem)).
+(Figure \@ref(fig:sem-plot) D, Table \@ref(tab:indir-sem)).
 
@@
 The average trophic level was positively linked to total biomass.
-Experimental and theoretical work suggested that a higher trophic level is the
+Experimental and theoretical work suggested that a higher trophic level can be the
 result of a stronger top-down effect, meaning higher predation rates and biomass

### 2020-10-29 manuscript/bef_stability/appendix.Rmd
Manuscript update: colin rreview + new table and figures
Improve appendix clarity

@@
 source(mypath("R", "synchrony.R"))
+source(mypath("R", "cleaning_methods.R"))
 
@@
 package <- c("openSTARS", "SSN", "nlme", "piecewiseSEM")
-purrr::map(package, ~ toBibtex(citation(.x)))
-
-toBibtex(citation())
+#purrr::map(package, ~ toBibtex(citation(.x)))
+
+#toBibtex(citation())
 
@@
 the small streams (depth < 0.7m across the entire width), the complete protocol
-is used. It consists in placing anodes every X meter across the width of the
+is used. It consists in placing anodes every X meters across the width of the
 river. The fishermen made from one to three row
@@
 partial and complete protocols were applied depending of the depth of the river
-at the time of sampling. Those stations were removed from the analysis.
+at the time of sampling.
 
@@
 given station, which the sampled length along the stream was outside the median
-length sampled more or less 30%. Finally, we standardadized the biomass record
+length sampled more or less 30%. Finally, we standardized the biomass record
 and species richness by the sampled surface to get rid of sampling effort
@@
 size of a subsample of X individuals are recorded. The G batches contain
-individuals of low body size, with care that body size is as homogenous as
+individuals of low body size, with care that body size is as homogeneous as
 possible in the batches. Then body size of the shortest and the longest
@@
   Finally, only the body size of the littlest and of the tallest individual was
-  recorded. ",
+  recorded in the G batches. ",
   "Then, (3) we inferred the body size distribution in the S/L and G batches by
@@
 During fish sampling, some species are identified based on morphotype but they
-belong to the same species based on fecundation criteria (CHECK with Eric).
+belong to the same species based on fecundation criteria.
 We merged those morphotype species into one species. There was
@@
 explained in main text. Because those measurements were collected during the
-fishing protocol, they were easier to manage in the analysis. Then, we detailled
+fishing protocol, they were easier to manage in the analysis. Then, we detailed
 in the following sections how water temperature, flow and BOD were obtained.
@@
 
-Water temperature, flow and BOD (Biogical Oxygen Demand) were obtained from the
+Water temperature, flow and BOD (Biological Oxygen Demand) were obtained from the
 [naiades database](http://www.naiades.eaufrance.fr/).
@@
 and monthly frequency. Water temperature and flow are recorded by automated
-sendors while BOD is collected manually because it necessitates analysis in a
+sensors while BOD is collected manually because it necessitates analysis in a
 laboratory. BOD data collection is coordinated by the Agence de l'eau which
@@
 
-- Number of station
-- Space repartition
+```{r}
+pressure_cap <- paste0(
+  "Map of environmental variables obtained for the 99 sites used in the analysis."
+)
+```
 
@@
 myload(flow_temp_metrics, station_analysis, the_8_hydrologic_basin, dir = mypath("data"))
+
 sf_pressure <- station_analysis %>% 
+  filter(id %in% op_analysis_bbb$station) %>%
   select(id) %>%
@@
 
-var_to_plot <- colnames(sf_pressure)[
-  !colnames(sf_pressure) %in% c("id", "geometry")]
+var_to_plot <- colnames(pca_rotated$normal$tab)
+
 var_replacement <- c(
@@
 ~p +
-  geom_sf(data = sf_pressure, aes_string(color = .x)) +
+  geom_sf(data = sf_pressure, aes_string(color = .x), size = .5) +
+  viridis::scale_color_viridis() +
   labs(title = str_replace_all(.x, var_replacement)) +
   theme(legend.title = element_blank(),
+    text = element_text(size = 8),
     axis.text = element_blank(),
     axis.ticks = element_blank()
-  )
-)
-
-plot_grid(plotlist = map_pressure, ncol = 2)
-
+  ) +
+ guides(fill = guide_colourbar(barwidth = 0.5, barheight = 10))
+)
+
+plot_grid(plotlist = map_pressure, ncol = 3)
 ```
@@
 than along terrestrial surface. Interpolations in terrestrial areas are roughly
-based on euclidian distance. Euclidian distance is more complicated to consider
-in streams because it had the follow the path of the streams. Futhermore,
+based on euclidean distance. Euclidean distance is more complicated to consider
+in streams because it had the follow the path of the streams. Furthermore,
 two streams can be close by but not connected and the value of their variables
@@
 elevation model at a resolution of 250 meters [(IGN)](https://wxs.ign.fr/jvam1hsjm11u8voorw81v2xb/telechargement/prepackage/BDALTI-75M_PACK_FXX_2018-01-24%24BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15/file/BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15.7z)
-and a theoretical hydrologic network [put a link](test) [@pella_reseau_2012].
+and a theoretical hydrologic network [@pella_reseau_2012].
 
 The procedure was done by hydrographic basin because of convergence problem
-when the interpolation was done at the France scale. We had to make a tradeoff
+when the interpolation was done at the France scale. We had to make a trade-off
 between the number of data (to keep enough high to perform the interpolation)
@@
 
-```{r cv-biais, fig.cap = cv_bias_caption}
-cv_dbo_temp_flow %>%
-  rename(Bias = bias_avg) %>%
-  ggplot(aes(x = Bias)) +
-  geom_histogram() +
-  facet_wrap(~Variable, scales = "free_x")
-```
-
 The performance of the interpolation was evaluated with leave one out
@@
 interpolated variable of each station was predicted after removing it from the
-dataset. ADD SUMMARIES ABOUT CV.
-
-With the model, we then simply predicted variable values at the location of the
-fish stations.
+dataset.
 
 When predicted values were below the minimum value or above the maximum value
-recorded in the dataset for flow, (temperature?) and BOD, we replaced the
+recorded in the dataset for flow, temperature and BOD, we replaced the
 predicted value by respectively the minimum and the maximum value found in the
@@
   booktabs = T,
-  label = paste0("indir-sem"),
+  label = paste0("fish-sp"),
   caption = "Fish species list."
   ) %>%
-kable_styling(latex_options =c("striped", "scale_down"))
-
+kable_styling(latex_options =c("striped"))
 ```
@@
 ```{r food}
-kable(fish_diet_shift,
+kable(select(fish_diet_shift, - species_name, -remark),
   format = "latex",
   booktabs = T,
-  label = paste0("indir-sem"),
+  label = paste0("onto-diet"),
   caption = "Ontogenic diet shift for each species"
@@
 kable_styling(latex_options =c("striped", "scale_down"))
-
 ```
@@
 series shapes. The classification necessitates three steps. First, the time
-series are normalized (i.e. substracting the mean and divide by the standard
+series are normalized (i.e. Substituting the mean and divide by the standard
 deviation). The second step is to reduce the dimensionality of the time series
-by Piecewise Aggregation Approximation (PAA) method. Each time series is divived
+by Piecewise Aggregation Approximation (PAA) method. Each time series is divided
 in $N$ frames of equal size that allows to the reduce the dimensionality of the
@@
 breakpoints can be computed by dividing the area under the normal distribution
-in equal parts. The algoritm attributes a alphabetic letter to each part from
+in equal parts. The algorithm attributes a alphabetic letter to each part from
 the lowest to the highest ($a$, $b$, $c$, ...). We set three breakpoints, so
@@
 a combination of $a$, $b$, $c$ letters. $abc$ and $cba$ time series represent
-respectively monoton increasing and decreasing trajectories. For data analysis,
+respectively monotonic increasing and decreasing trajectories. For data analysis,
 we kept only the $bbb$ which represent time series that showed no temporal
-tendancies (with respect to our methodology).
+tendencies, with respect to our methodology.
 
@@
   ) %>%
-kable_styling(latex_options = c("striped", "scale_down"))
+kable_styling(latex_options = c("striped"))
 ```
@@
 
-```{r pca-rotated, fig.cap = pca_caption, fig.asp = 1}
+```{r pca-rotated, fig.cap = pca_caption}
 p1 <- my_pca_plot(xaxis = "RC1", yaxis = "RC2", ctb_thld = .4)
@@
   nrow = 1, ncol = 2,
-  base_height = 6/2.54, base_asp = 1, base_width = NULL 
+  base_height = 6/2.54, base_asp = 1.6, base_width = NULL 
   )
@@
   geom_sf(data = rc2_sf, aes(color = log(value + abs(min(value)) + 1 ))) +
+  viridis::scale_color_viridis() +
   labs(title = "RC2 (Log)") +
@@
 kable_styling(latex_options = c("striped", "scale_down"))
+sem_variable_table
 ```
@@
 hist_var_caption <- paste0(
-  "Distribution of the variables (before transformation) used in the Structural Equation Modeling."
-)
-```
+  "Distribution of the variables used in the Structural Equation Modeling. The
+  biomass stability, the CV of species (CVsp), PCA1, PCA2, species richness,
+  synchrony and total biomass were logged."
+)
+```
+
 ```{r hist-sem-data, fig.cap = hist_var_caption}
 sem_data %>%
-  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct, log_bm) %>%
+  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct) %>%
   gather(variable, value) %>%
@@
 
-```{r s-colin-sem, fig.cap = "Variance Inflation factor for each individual model of stability sem"}
-
+```{r}
+colin_sem_cap <- paste0(
+  "Variance Inflation Factor for each individual linear model of the structural
+  equation models."
+) 
+```
+
+```{r s-colin-sem, fig.cap = ""}
 mod_stab_list <-
@@
   unnest(vif) %>%
+  rename(`Response variable` = mod) %>%
   mutate(
@@
   "Residuals versus fitted values of the linear models used in the structural
-  equation modelings."
-) 
-```
-
-```{r mod-res, fig.height = 7, fig.cap = caption_mod_res}
+  equation models."
+) 
+```
+
+```{r mod-res, fig.height = 8, fig.cap = caption_mod_res}
 library(nlme)
@@
 p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
-plot_grid(plotlist = p_resid_stab_sem)
+plot_grid(plotlist = p_resid_stab_sem, ncol = 2)
 ```
@@
 est_stab_sem_caption <- paste0(
-  "Estimate of the effects for the biomass stability structural equation
-  modeling."
+  "Estimate of the effects for the temporal stability of annual biomass of the structural equation
+  model."
 
@@
 est_bm_sem_caption <- paste0(
-  "Estimate of the effects for the total biomass structural equation
-  modeling."
+  "Estimate of the effects for the structural equation
+  model of the median of annual total biomass."
 )
@@
 random_coeff_sem <- map(mod_stab_list[!mask_drop_lm], random.effects)
-
-format_random <- function (x, y) {
-  tibble(
-    Variable = y, 
-    `Hydrographic basin` = rownames(x),
-    Intercept = x[[1]]
-  )
+test <- getVarCov(mod_stab_list[!mask_drop_lm][[2]])
+
+get_intercept_variance <- function (mod) {
+  vc <- VarCorr(mod)
+  suppressWarnings(storage.mode(vc) <- "numeric")
+  enframe(vc[1,])
 }
-formated_random_effects <- do.call(rbind, map2(random_coeff_sem, names(random_coeff_sem), format_random))
+random_coeff_sem <- map(mod_stab_list[!mask_drop_lm],
+  get_intercept_variance) %>%
+  enframe(name = "variable") %>%
+  unnest(value) %>%
+  pivot_wider(names_from = "name", values_from = "value")
+get_intercept <- function (mod) {
+  mod[["coefficients"]]$fixed["(Intercept)"]
+}
+intercept_sem <- map_dbl(mod_stab_list[!mask_drop_lm],
+  get_intercept) %>%
+enframe(name = "variable", value = "Intercept")
+
+formated_random_effects <- intercept_sem %>% 
+  left_join(random_coeff_sem, by = "variable") %>%
+  rename(`Response variable` = variable)
+#format_random <- function (x, y) {
+  #tibble(
+    #Variable = y, 
+    #`Hydrographic basin` = rownames(x),
+    #Intercept = x[[1]]
+  #)
+#}
+#formated_random_effects <- do.call(rbind, map2(random_coeff_sem, names(random_coeff_sem), format_random))
 
@@
   models performed in structural equation modeling."
-
 )
@@
 
-```{r sensitivity, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset", cache = TRUE}
+```{r sensitivity, message = FALSE, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset", cache = FALSE}
 library(furrr)
@@
 
-#myload(network_metrics, dir = mypath("data", "classes"))
+myload(network_metrics, dir = mypath("data", "classes"))
 sem_sensivity_data <- list(full = op_analysis, bbb = op_analysis_bbb,
@@
 
-sem_stab_l_data <- furrr::future_map(sem_sensivity_data,
+sem_stab_l_data <- 
+  furrr::future_map(sem_sensivity_data,
 
@@
 colnames(sem_stab_results) <- str_to_lower(colnames(sem_stab_results))
-sem_stab_results %>%
-  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
-  ggplot(aes(x = r_p, y = std.estimate)) +
-  geom_point(aes(color = dataset)) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+mysave(sem_stab_results, dir = mypath("data"), overwrite = TRUE)
 ```
@@
 colnames(sem_bm_results) <- str_to_lower(colnames(sem_bm_results))
-sem_bm_results %>%
-  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
-  ggplot(aes(x = r_p, y = std.estimate)) +
-  geom_point(aes(color = dataset)) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-```
-
-```{r}
-knitr::opts_chunk$set(eval = FALSE)
-```
-
-```{r}
-coeff_troph <- map2_dfr(list(bm_troph_ci, stab_troph_ci), list(bm_troph_mod, stab_troph_mod),
-  clean_summary_mod, term_rp = rp_est, group_rp = rp_group)
-
-kable(coeff_troph) %>%
-  pack_rows("Biomass", 1, 6) %>%
-  pack_rows("Stab", 7, 12)
-```
-
-## Relationship at the absolute scale, i.e. not the logarythme scale
-
-```{r}
-ggplot(sem_data, aes(x = richness_med, y = biomass_stab)) +
-  geom_point()
-test <- tibble(
-  richness_med = seq(1,20, length.out = 100),
-  biomass_stab =
-    10^(fixef(stab_div_mod)[1])*richness_med^fixef(stab_div_mod)[2]
-)  
-```
-
-```{r save-plot, eval = FALSE}
-
-save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div.pdf",
-  p_stab_div,
-  base_height = 3,
-  bg = "transparent",
-  ncol = 1)
-
-save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div_troph.pdf",
-  p_stab_div_troph + theme(legend.position = "bottom"),
-  base_height = 3,
-  bg = "transparent",
-  ncol = 1)
-
-```
-
-### Ecological modeling fun
-
-```{r, eval = FALSE}
-mod_tlvl <- nlme::lme(t_lvl ~ scale(RC1) + scale(RC2) + scale(RC3) + scale(RC4) + scale(RC5) + log_rich_tot, random = ~ 1 | basin, data = sem_data)
-plot(mod_tlvl)
-sem_data %>%
-  ggplot(aes(x = log10(richness_tot), y = t_lvl)) +
-  geom_point()+
-  geom_smooth(method = "lm")
-plot(x = log10(sem_data$RC1 + abs(min(sem_data$RC1))), y = sem_data$t_lvl)
-sem_data %>%
-  ggplot(aes(x = log10(RC1), y = t_lvl)) +
-  geom_point()+
-  geom_smooth(method = "lm")
-plot(nlme::lme(t_lvl ~ I(log10(RC1 + abs(min(RC1)))) + log_rich_tot, random = ~ 1 | basin, data = sem_data))
-nlme::lme(t_lvl ~ log_rich_tot, random = ~ 1 | basin, data = sem_data)
-semd_test <- sem_data %>%
-  mutate(RC1b = RC1 + abs(min(RC1)))
-ricker.mixed.fit <- nls(
-  t_lvl ~ (Vm*(RC1 + b) / (K + (RC1 + b)) + d),
- #fixed = Vm + K + b + d ~ 1,
- #random = Vm + K + b + d ~ 1|basin,
- start= c(Vm=1, K = 0.1, b = .5, d = 2.5),
- data = semd_test,
- control = lmeControl(maxIter = 1e8, msMaxIter = 1e8) 
-)
-summary(ricker.mixed.fit)
-x <- seq(min(sem_data$RC1), max(sem_data$RC1), length.out = 100)
-sem_data$test_pred <- predict(ricker.mixed.fit)
-
-semd_test %>%
-  ggplot(aes(x = RC1b, y = t_lvl)) +
-  geom_point() +
-  geom_line(aes(y = test_pred))
-  geom_smooth(method = "lm")
-cor(semd_test$piel, semd_test$t_lvl, method = c("spearman"))
-```
-
-```{r, eval = FALSE}
-library(glmmTMB)
-# Gaussian
-mod_log_rich <- glmmTMB(
-  log_rich_tot ~ log_RC1 + log_RC2 + log_RC3
-  + RC4 + RC5 + (1 | basin), family = gaussian, data = sem_data)
-summary(mod_log_rich)
-plot(y = resid(mod_log_rich), x = fitted(mod_log_rich))
-
-# Poisson 
-mod_log_rich_poi <- glmmTMB(
-  richness_tot ~ log_RC1 + log_RC2 + log_RC3
-  + RC4 + RC5 + (1 | basin), family = poisson, data = sem_data)
-summary(mod_log_rich_poi)
-plot(y = resid(mod_log_rich_poi), x = fitted(mod_log_rich_poi))
-
-# Truncate 
-mod_log_rich_nbinom <- glmmTMB(
-  richness_tot ~ log_RC1 + log_RC2 + log_RC3
-  + RC4 + RC5 + (1 | basin), family = nbinom1, data = sem_data)
-summary(mod_log_rich_nbinom)
-plot(y = resid(mod_log_rich_nbinom), x = fitted(mod_log_rich_nbinom))
-```
-
-```{r stab-network, eval = FALSE}
-sem_data %>%
-  select(sync, cv_sp, ct, t_lvl) %>%
-  gather(network, metrics, ct, t_lvl) %>%
-  gather(stab_comp, value, sync, cv_sp) %>%
-  ggplot(aes(y = value, x = metrics)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  facet_grid(stab_comp ~ network, scales = "free_x")
-
-stab_ct_mod <- lmer(data = sem_data,
-  #fixed = log_bm ~ log_rich_tot * troph_group,
-  formula = log_stab_std ~ ct + (1 | basin)
-  #random = ~ 1 + log_rich_tot * troph_group | basin,
-  #control = ctrl 
-)
-stab_ct_boot <- bootMer(stab_ct_mod, mySumm2, nsim = 100)
-stab_ct_ci <- confint(stab_ct_boot)
-
-stab_ct_sum <- piecewiseSEM::rsquared(stab_ct_mod, method = "nagelkerke") %>%
-  mutate_at(vars(Conditional, Marginal), ~round(., 2))
-
-pred_stab_ct_mod <- ggpredict(stab_ct_mod, terms = c("ct"), type = "fe")
-#plot(pred_troph_mod, add.data = TRUE)
-stab_ct_pred <- pred_stab_ct_mod %>%
-  as_tibble() %>%
-  rename(
-    log_stab_std = predicted,
-    log_rich_tot_std = x,
-    troph_group = group
-  )
-
-# get coeff
-coef_stab_ct <- map(list(stab = stab_ct_mod), fixed.effects)
-
-stab_tlvl_mod <- lmer(data = sem_data,
-  #fixed = log_bm ~ log_rich_tot * troph_group,
-  formula = log_stab_std ~ t_lvl + (1 | basin)
-  #random = ~ 1 + log_rich_tot * troph_group | basin,
-  #control = ctrl 
-)
-stab_tlvl_boot <- bootMer(stab_tlvl_mod, mySumm2, nsim = 100)
-stab_tlvl_ci <- confint(stab_tlvl_boot)
-
-stab_tlvl_sum <- piecewiseSEM::rsquared(stab_tlvl_mod, method = "nagelkerke") %>%
-  mutate_at(vars(Conditional, Marginal), ~round(., 2))
-
-pred_stab_tlvl_mod <- ggpredict(stab_tlvl_mod, terms = c("t_lvl"), type = "fe")
-#plot(pred_troph_mod, add.data = TRUE)
-stab_tlvl_pred <- pred_stab_tlvl_mod %>%
-  as_tibble() %>%
-  rename(
-    log_stab_std = predicted,
-    log_rich_tot_std = x,
-    troph_group = group
-  )
-
-# get coeff
-coef_stab_tlvl <- map(list(stab = stab_tlvl_mod), fixed.effects)
-```
+mysave(sem_bm_results, dir = mypath("data"), overwrite = TRUE)
+```
+
+```{r}
+sens_cap <- paste0(
+  "Sensivity analysis of the Structural Equation models for total biomass
+  and its temporal stability."," The Constant dataset is the one kepting only the
+  sites that had not a significant temporal trend in biomass; ", "Constant/
+    without holes dataset kept only the constant sites plus the ones that had not
+  holes in their sampling period; ", "Complete is the dataset containing all the
+  site that have been followed ten years or more, as the other dataset;", "Without holes dataset is
+  the dataset containing only the sites that had no holes in the their sampling period."
+)
+```
+
+```{r, fig.height = 8, fig.cap = sens_cap}
+p_sens_bm <- plot_sensivity_analysis(.data = sem_bm_results) +
+  theme(legend.position = "none")
+
+p_sens_stab <- plot_sensivity_analysis(.data = sem_stab_results) +
+  guides(color = guide_legend(direction = "horizontal", nrow = 2))
+legend_b <- get_legend(p_sens_stab)
+p_sens_stab %<>% + theme(legend.position = "none")
+p <- plot_grid(
+  p_sens_bm, p_sens_stab, legend_b, nrow = 3,
+  rel_heights = c(1, 1, .1),
+  labels = c("Total biomass", "Biomass stability")
+)
+p
+```
+
+# References

### 2020-10-29 R/community_analysis.R

@@ -272,7 +272,7 @@ compute_com_synchrony <- function (.op = NULL, com = NULL, ...) {
 #'
 #'
 compute_community_temporal_analysis <- function(.op = NULL,
-  type_network_metrics = "species") {
+  type_network_metrics = "species", msg = FALSE) {
 
   output <- vector("list", length = 4)
   names(output) <- c("tps_net", "tps_com", "tps_bm_troph", "sync")
@@ -292,7 +292,9 @@ compute_community_temporal_analysis <- function(.op = NULL,
     type_metrics = type_network_metrics
   )
 
-  cat("Network done (1/4)\n")
+  if (msg) {
+    cat("Network done (1/4)\n")
+  }
 
   # Beta-diversity ---------------------------------------------------
   if(!exists("community_analysis")) {
@@ -300,12 +302,16 @@ compute_community_temporal_analysis <- function(.op = NULL,
   }
   betadiv <- compute_temporal_betadiv(.op = .op, com = community_analysis)
 
-  cat("Beta-diversity done (1.5/4)\n")
+  if (msg) {
+    cat("Beta-diversity done (1.5/4)\n")
+  }
 
   # Synchrony of species ---------------------------------------------
   output[["sync"]] <- compute_com_synchrony(.op = .op, com = community_analysis)
 
-  cat("Synchrony done (2/4)\n")
+  if (msg) {
+    cat("Synchrony done (2/4)\n")
+  }
   # 
   com_std <- community_analysis %>%
     dplyr::ungroup() %>%
@@ -318,7 +324,9 @@ compute_community_temporal_analysis <- function(.op = NULL,
 
   output[["sync_std"]] <- compute_com_synchrony(.op = .op, com = com_std)
 
-  cat("Synchrony standardized done (2.5/4)\n")
+  if (msg) {
+    cat("Synchrony standardized done (2.5/4)\n")
+  }
 
   # Biomass ---------------------------------------------------------- 
   if(!exists("community_metrics")) {
@@ -331,7 +339,9 @@ compute_community_temporal_analysis <- function(.op = NULL,
   output[["tps_com"]] %<>%
     dplyr::left_join(dplyr::select(betadiv, -data, -com), by = "station")
 
-  cat("Community description done (3/4)\n")
+  if (msg) {
+    cat("Community description done (3/4)\n")
+  }
 
   # Biomass by trophic group -----------------------------------------
[…]

### 2020-11-17 manuscript/bef_stability/appendixB.Rmd
Update appendix

--- 2020-10-29 manuscript/bef_stability/appendix.Rmd
@@
 ---
-title: Appendix
-author: Alain Danet, Maud Mouchet, Elisa Thebault and Colin Fontaine
+title: Appendix of Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
+author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
 date: \today 
@@
 header-includes:
+   -  \newcommand{\beginsupplement}{\setcounter{table}{2}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
    - \usepackage{booktabs}
@@
 library(sf)
+library(nlme)
 source(mypath("R", "misc.R"))
@@
 ```
+
+\beginsupplement
 
@@
 
+```{=latex}
+\pagebreak
+```
+
 ## Community data
@@
 During fish sampling, some species are identified based on morphotype but they
-belong to the same species based on fecundation criteria.
-We merged those morphotype species into one species. There was
-`r length(unique(names(sp_to_replace())))` to merge which belonged to 
-`r length(unique(sp_to_replace()))` species.
+belong to the same species based on fecundation criteria.  We merged those
+morphotype species into one species. There was `r
+length(unique(names(sp_to_replace())))` to merge which belonged to `r
+length(unique(sp_to_replace()))` species.
 
@@
 
-Diet information were obtained from fishbase.org and literature [REF willem?]. The
+Diet information were obtained from fishbase.org and literature (Appendix A, Table S2). The
 diet information contained from two to three life stages by species, the life
@@
 life stage. Fish species were largely omnivorous.
+
+```{r food, eval = FALSE}
+onto_shift_cap <- paste0(
+  "Ontogenic diet shift for each fish species.", 
+  "Species had between two and three life stages, bounded by body size (in mm).
+  A life stage of a given determine its diet. The fourth column to the last one
+  correspond to this respective resource: light, detritus, biofilm,
+  phytobenthos, macrophages, phytoplankton, zooplankton,  zoobenthos and
+  fishes."
+)
+table_onto_diet <- fish_diet_shift %>%
+  rename(`Life stage` = stage) %>%
+  mutate(
+    min = paste0("[", size_min),
+    max = paste0(size_max, "]")
+  ) %>%
+  unite("Size interval", min:max, sep = ";") %>%
+  select(species, `Life stage`, `Size interval`, light:ref_ods)
+
+kable(table_onto_diet,
+  format = "latex",
+  booktabs = T,
+  label = paste0("onto-diet"),
+  caption = onto_shift_cap
+  ) %>%
+kable_styling(latex_options =c("striped", "scale_down"))
+```
+
+```{=latex}
+%\includepdf[pages={2-7}]{figs/supplementary_ref_willem.pdf}
+```
 
@@
 
-```{r, fig.height = 20/2.54}
+```{r, fig.height = 20/2.54, fig.cap = pressure_cap}
 pca_pressure <- habitat_press
@@
   labs(title = str_replace_all(.x, var_replacement)) +
-  theme(legend.title = element_blank(),
+  theme(
+    legend.title = element_blank(),
     text = element_text(size = 8),
@@
   ) +
- guides(fill = guide_colourbar(barwidth = 0.5, barheight = 10))
+ guides(color = guide_colourbar(barwidth = 0.5, barheight = 4))
 )
@@
 The time resolution was heterogeneous according to the variable considered
-(hourly, daily and monthly for temperature, flow and BOD resp.). For each recording
-station, we applied a moving window averaging (more details in supplementary
-material) to get rid of seasonal effects. For temperature, the moving was performed on daily
-average temperature. Then we took the annual average of each year and each
-variable (i.e. one value by year and by station).
+(hourly, daily and monthly for temperature, flow and BOD resp.). For each
+recording station, we applied a moving window averaging (more details in
+supplementary material) to get rid of seasonal effects. For temperature, the
+moving was performed on daily average temperature. Then we took the annual
+average of each year and each variable (i.e. one value by year and by station).
 
@@
 based on euclidean distance. Euclidean distance is more complicated to consider
-in streams because it had the follow the path of the streams. Furthermore,
-two streams can be close by but not connected and the value of their variables
-could be not related or a only a few. For those reason, we used stream spatial
-network methods to interpolate temperature, flow and BOD.
+in streams because it had the follow the path of the streams. Furthermore, two
+streams can be close by but not connected and the value of their variables could
+be not related or a only a few. For those reason, we used stream spatial network
+methods to interpolate temperature, flow and BOD.
 
 We reconstructed the stream network and the connection between sites with the
-`openSTARS` R package. The reconstruction was done with a raster of digital
+`openSTARS` R package [@kattwinkel_preparing_2020]. The reconstruction was done with a raster of digital
 elevation model at a resolution of 250 meters [(IGN)](https://wxs.ign.fr/jvam1hsjm11u8voorw81v2xb/telechargement/prepackage/BDALTI-75M_PACK_FXX_2018-01-24%24BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15/file/BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15.7z)
@@
 were done with the `SSN` R package 
-[@isaak_applications_2014, @hoef_ssn_2014].
+[@isaak_applications_2014, @hoef_ssn:_2014].
 
@@
 
-# Species list and food diet data
-
-```{r sp-list}
-myload(species, fish_diet_shift, dir = mypath("data"))
-kable(species,
-  format = "latex",
-  booktabs = T,
-  label = paste0("fish-sp"),
-  caption = "Fish species list."
-  ) %>%
-kable_styling(latex_options =c("striped"))
-```
-
-```{r food}
-kable(select(fish_diet_shift, - species_name, -remark),
-  format = "latex",
-  booktabs = T,
-  label = paste0("onto-diet"),
-  caption = "Ontogenic diet shift for each species"
-  ) %>%
-kable_styling(latex_options =c("striped", "scale_down"))
-```
-
-# Analysis
-
-## Time series classication
+```{=latex}
+\pagebreak
+```
+
+# Data analysis
 
@@
 
-## PCA of environmental variables
-
 ```{r eig-plot}
@@
   scale_fill_discrete(name = "Status") +
-  labs(x = "Rotated component", y = "Eigen values")
+  labs(x = "Rotated component", y = "Eigen values") +
+  theme(legend.position = "none",
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank())
 ```
@@
 
-```{r}
+```{r, eval=FALSE}
 corr_pca_caption <- paste0(
@@
 
-```{r rc2-map, fig.cap = caption_rc2_map}
+```{r rc2-map, eval = FALSE, fig.cap = caption_rc2_map}
 p +
@@
 
-## Model summary and diagnostics
-
-### Data transformation
-
-Additionally, we logged the axis one, two and three to normalize their
-distribution and we reversed the third axis to get increasing average
-temperature with increasing values of the axis and so decreasing values of
-altitude.
+```{=latex}
+\pagebreak
+```
+
+# Statistical analysis
 
@@
 sem_variable_table <- tibble(
-  variable = c(paste0("PCA axis", seq(1, 5)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
-  unit = c(rep("unitless", 5), "# by square meter", rep("unitless", 4), "gram by square meter"
+  variable = c(paste0("PCA axis", seq(1, 2)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
+  unit = c(rep("unitless", 2), "# by square meter", rep("unitless", 4), "gram by square meter"
     ),
-  transformation = c(rep("Log base 10", 3), rep("No", 2), "Log base 10", rep("No", 2), rep("Log base 10", 3)),
-  interpretation = c(rep("", 11)) 
-) %>%
+  transformation = c(rep("Log base 10", 2), "Log base 10", rep("No", 2), rep("Log base 10", 3)),
+  interpretation = c("linked to stream size",
+    "linked to average temperature",
+    "Total species richness over the temporal series",
+    "Median of annual link density", "Median of annual average trophic level", "", "",
+    "Median of annual total biomass")) %>%
 kable(
@@
   ) %>%
-kable_styling(latex_options = c("striped", "scale_down"))
+kable_styling(latex_options = c("striped"))
 sem_variable_table
@@
 ---
+
 To reveal the mechanisms behind the relationship between species richness and
@@
 
-## Model linear Relationship
-
-### Variables
-
 ```{r}
@@
 ```
-
-### Colinearity tables
 
@@
 
-### Biomass and stability models
-
 ```{r}
@@
   ) %>%
+collapse_rows(columns = 1, valign = "top") %>%
 kable_styling(latex_options = c("striped", "scale_down"))
@@
 )
-kable(format_coef_table(bm_sem_rich),
-  format = "latex",
-  booktabs = T,
-  caption = est_bm_sem_caption
-  ) %>%
-kable_styling(latex_options = c("striped"))
 ```
@@
 
+# get random effect 
 get_intercept_variance <- function (mod) {
@@
   pivot_wider(names_from = "name", values_from = "value")
+#check
+#all.equal(random_coeff_sem[[2]],(random_coeff_sem[[3]])^2)
+#good
+
+# get intercept 
 get_intercept <- function (mod) {
@@
 }
-intercept_sem <- map_dbl(mod_stab_list[!mask_drop_lm],
-  get_intercept) %>%
+intercept_sem <- map_dbl(
+  mod_stab_list[!mask_drop_lm], get_intercept) %>%
   enframe(name = "variable", value = "Intercept")
@@
   rename(`Response variable` = variable)
-#format_random <- function (x, y) {
-  #tibble(
-    #Variable = y, 
-    #`Hydrographic basin` = rownames(x),
-    #Intercept = x[[1]]
-  #)
-#}
-#formated_random_effects <- do.call(rbind, map2(random_coeff_sem, names(random_coeff_sem), format_random))
-
 caption_random_effect <- paste0(
-  "Estimated random effect of hydrographic basin on the intercept of the linear
-  models performed in structural equation modeling."
+  "Estimated variance and standard deviation on the intercept due to the hydrographic basins."
 )
@@
 
-### Robustness to different dataset selection
-
-```{r sensitivity, message = FALSE, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset", cache = FALSE}
+```{r sensitivity, message = FALSE, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
 library(furrr)
@@
   furrr::future_map(sem_sensivity_data,
-
     ~build_dataset_get_sem_coefficient(
@@
 
-```{r sem-sens-bm, cache = TRUE, fig.cap = "Sensivity analysis for Biomass"}
+```{r sem-sens-bm, fig.cap = "Sensivity analysis for Biomass"}
 sem_bm_l_data <- furrr::future_map(sem_sensivity_data,
@@
 ```{r, fig.height = 8, fig.cap = sens_cap}
-p_sens_bm <- plot_sensivity_analysis(.data = sem_bm_results) +
-  theme(legend.position = "none")
-
-p_sens_stab <- plot_sensivity_analysis(.data = sem_stab_results) +
+p_sens_bm <- plot_sensivity_analysis(
+  .data = sem_bm_results,
+  inverse_label_order = TRUE) +
+  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
+
+p_sens_stab <- plot_sensivity_analysis(.data = sem_stab_results,
+  inverse_label_order = TRUE) +
   guides(color = guide_legend(direction = "horizontal", nrow = 2))
 legend_b <- get_legend(p_sens_stab)
-p_sens_stab %<>% + theme(legend.position = "none")
+p_sens_stab %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm"))
 p <- plot_grid(
@@
 
+```{=latex}
+\pagebreak
+```
+
 # References

### 2020-11-17 manuscript/bef_stability/manuscript.Rmd
Update appendix

@@
 title: Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
-author: Alain Danet, Maud Mouchet, Willem Bonnaffe, Elisa Thebault, Colin Fontaine
+author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault, Colin Fontaine
 date: \today 
@@
     Paris, 43 rue Buffon, 75005 Paris, France
-  - Willem Bonnaffe: Ecological and Evolutionary Dynamics Lab. Zoology Research
+  - Willem Bonnaffé: Ecological and Evolutionary Dynamics Lab. Zoology Research
     and Administration Building, 11a Mansfield Rd, Oxford OX1 3SZ, United
     Kingdom.
-  - Elisa Thebault: Sorbonne Université, CNRS, IRD, INRAE, Université Paris Est
+  - Elisa Thébault: Sorbonne Université, CNRS, IRD, INRAE, Université Paris Est
     Créteil, Institute of Ecology and Environmental Sciences of Paris
@@
 Foodweb stability-complexity relationship has been mainly the focus of
-theoretical studies with very empirical testing. To fill this gap, we link
-species richness, foodweb structure and annual biomass and its temporal
+theoretical studies with very little empirical testing. To fill this gap, we linked
+species richness, foodweb structure, annual biomass and its temporal
 stability using a standardized monitoring of fish communities in French streams
-running from 1995 to 2018. We inferred trophic interactions thanks to recorded
-body size and diet literature. We reveal that species richness and average
+running from 1995 to 2018. We inferred trophic interactions from
+body size recorded and diet literature. We reveal that species richness and average
 trophic level had a positive relationship with annual biomass of fish
@@
 diversity and foodweb structure. Overall, our study opens fruitful perspectives
-on the link between species richness, network structure, biomass and its
-stability.
+on the link among species richness, network structure, community biomass and its
+temporal stability.
 
@@
 @poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018]. 
-These models show that both resource use complementarity and selection effects,
+These models show that both complementarity in the use of resources and selection effects,
 the two main mechanisms previously highlighted in single-trophic studies, are
@@
 [@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
-Despite these theoretical evidences that structure affects biomass, we are
+Despite these theoretical evidence that structure affects biomass, we are
 lacking empirical studies that assess jointly how foodweb structure and species
@@
 
-Several theoretical studies considering single trophic level have
+Several theoretical studies considering a single trophic level have
 clarified which mechanisms generate this positive relationship between species
@@
 stability [@tilman_biodiversity_2006; @olivier_urbanization_2020]. Asynchrony is
-expected to raise with the variability of species responses to perturbations. Though most
+expected to increase with the variability of species responses to perturbations. Though most
 often positive, the relationship between species diversity and asynchrony has
@@
 matmet_cap <- paste0( 
+  "(A) Observation sites (black dots) were located across France and monitored
+  on the period 1995-2018. The red dots show the location of (C) and (D) sites.
+  ", " Inner borders draw the limits of the hydrographic basins. ", "(B) The
+  metaweb of the study. Each trophic species (N = 412) is represented by a node
+  and each
+  color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
+  "The species names corresponding to the three digit codes are found in Table
+  SXX." ,
   "Yearly temporal series of networks of two stations having respectively a low
-  (A) and high (B) temporal stability of biomass. A and B stations have
+  (C) and high (D) temporal stability of biomass. C and D stations have
   respectively biomass stability the closest to the first and third quartile of
   the distribution of the temporal stability of biomass in the dataset,
-  respectively ",
-  round(qt_station$bm_std_stab[1],2), " and ", round(qt_station$bm_std_stab[2],
-    2),
-  ". Point size are proportional to the biomass of the trophic species. (C)
-  Observation sites (black dots) were located across France and monitored on the
-  period 1995-2018. Red dots being the location of (A) and (B) sites. ",
-  "Inner borders draw the limits of the hydrographic basins. ", "(D) The metaweb
-  of the study. Each trophic species (N = 412) is represented by a node and each
-  color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
-  "The species names corresponding to the three digit codes are found in Table
-  SXX.")
+  respectively ", round(qt_station$bm_std_stab[1],2), " and ",
+  round(qt_station$bm_std_stab[2],
+    2), ". Point size are proportional to the biomass of the trophic species.")
 
@@
 library(knitr)
-include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"),)
+include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"))
 ```
@@
 in total biomass were selected (detailed in supplementary methods). However, the
-results were robust to the relaxation of this hypothesis (Supplementary
-results). These selection steps resulted in 99 stations distributed over seven
-hydrographic basins (Figure \@ref(fig:matmet) A).
+results were robust to the relaxation of this hypothesis (Table SXX). These
+selection steps resulted in 99 stations distributed over seven hydrographic
+basins (Figure \@ref(fig:matmet) A).
 
@@
 
-Trophic interaction network was inferred from body size and ontogenic diet shift
+The trophic interaction network was inferred from body size and ontogenic diet shift
 following previous studies [@gravel_inferring_2013; @brose_predator_2019;
@@
   Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
-  second axis of the PCA."
+  second axis of the PCA performed on environmental variables (cf methods)."
 )
@@
 
-## Species richness and average trophic level are positively correlated to total biomass
+## Species richness and average trophic level are positively correlated with total biomass
 
@@
 PCA2 had an indirect positive effect on temporal stability through a
-direct positive effect on $\overline{CV_{sp}}$ ($r_\delta = 
-`r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-sem)) but also a
-negative one through species richness but a positive one through
-mean trophic level
-(resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
-$r_\delta = `r env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)).
-This was also true for the PCA1, related to stream size, but effects were weaker
-than for PCA2.
+direct positive effect on mean trophic level ($r_\delta = `r
+env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)). However, PCA2
+had a negative effect on temporal stability through a direct positive effect on 
+$\overline{CV_{sp}}$ and species richness (resp.  $r_\delta = 
+`r env_on_cv_sp$direct["log_RC2"]`$ and $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$,
+Table \@ref(tab:indir-sem)). This was also true for the PCA1, related to stream
+size, but effects were weaker than for PCA2.
 
@@
   ) %>%
-#kable_paper() %>%
 kable_styling(latex_options =c("scale_down")) %>%
@@
 collapse_rows(columns = 1, valign = "top")
-#str_replace(mytable, "\\\\#(.*)", "\\\\label{tab:indir-sem}")
-#str_view(mytable, "\\\\#(.*)")
 write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
@@
 settings. Species richness can reduce synchrony when (i) a given increase in species
-richness leads to a decrease of population sizes which raises the role of
+richness leads to a decrease of population sizes which increases the impacts of
 demographic stochasticity, when (ii) species have different
@@
 foodwebs, while including network structure. Species richness had a direct
-positive and negative effect respectively on total biomass and its stability but
-mean trophic level had a positive effect on both. Furthermore, we found that
-species richness had antagonistic effects on total biomass, through its effect
-on mean trophic level. Our study thus highlights the importance of considering both
-species richness, network structure and their dependence, though the
-mechanisms remain to be elucidated. Finally, we found that
-environmental gradient related to temperature and ecosystem size have
-antagonistic effects on biomass and its temporal stability, positive through mean
-trophic level and negative through species richness. Further research is needed
-to find the mechanisms behind those pathways, that are crucial in context of
-global changes.
-
-One limitation of our study is that the use of inferred networks, i.e. not
+positive effect on total biomass and a negative effect on biomass stability.
+Mean trophic level had a positive effect on both total biomass and its temporal
+stability. Furthermore, we found that species richness had antagonistic effects
+on total biomass, through its effect on mean trophic level. Our study thus
+highlights the importance of considering both species richness, network
+structure and their dependence, though the mechanisms remain to be elucidated.
+Finally, we found that environmental gradient related to temperature and
+ecosystem size have antagonistic effects on biomass and its temporal stability,
+positive through mean trophic level and negative through species richness.
+Further research is needed to find the mechanisms behind those pathways, and
+crucial in the context of global change.
+
+One limitation of our study is the use of inferred networks, i.e. not
 observed interactions, and the lack of information about the foodwebs outside
@@
 
-We look forward to see our findings and their interpretation tested by future
+We look forward to seeing our findings and their interpretation tested by future
 experimental and theoretical studies, allowing to unravel the ecological

### 2020-11-17 manuscript/bef_stability/table_onto_species.Rmd
Update appendix

--- 2020-11-17 manuscript/bef_stability/appendixB.Rmd
@@
 ---
-title: Appendix of Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
+title: List of species and ontogenic diet data
 author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
@@
     keep_tex: true
-    toc: true
+    toc: false 
 fontsize: 12pt
 header-includes:
-   -  \newcommand{\beginsupplement}{\setcounter{table}{2}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
+   -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
+   - \usepackage{pdfpages}
+   - \usepackage{longtable}
    - \usepackage{booktabs}
@@
 
-load(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
+#load(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
 
@@
 
-```{r, echo = FALSE}
-package <- c("openSTARS", "SSN", "nlme", "piecewiseSEM")
-#purrr::map(package, ~ toBibtex(citation(.x)))
-
-#toBibtex(citation())
-
-#print(cm, bibtex = TRUE)
-# Load manuscript results
+```{r sp-list}
+myload(species, metaweb_analysis, fish_diet_shift, dir = mypath("data"))
+species %<>%
+  filter(code %in% metaweb_analysis$species) %>%
+  select(-max_size) %>%
+  rename(`Common name` = common_name, `Latin name` = latin_name)
+kable(species,
+  format = "latex",
+  longtable = T,
+  booktabs = T,
+  label = paste0("fish-sp"),
+  caption = "Fish species list.") %>%
+kable_styling(latex_options =c("striped", latex_options = c("repeat_header")))
 ```
-
-# Data collection and preparation
-
-## Fishing
-
-### Protocol
-
-The fish community sampling took place in a variety of stream size, shape and
-depth. This diversity constraints the type of protocol that can take place.  For
-the small streams (depth < 0.7m across the entire width), the complete protocol
-is used. It consists in placing anodes every X meters across the width of the
-river. The fishermen made from one to three row
-of fishing. We kept only the first row for analysis to homogenize the sampling
-effort. For deeper and wider streams, the sampling was partial over the bank and
-the channel and performed by boat and by foot (along the bank). We kept only
-sampling done over the bank because channel sampling was not always done. Two
-types of partial protocols takes place: partial over bank and partial by points.
-The former is continuous while the latter is discrete. Furthermore, in partial
-by point protocol the channel can be sampled as well. We kept only the partial
-by point fish sampling which all the sampling point were done over the bank to
-homogenize the sampling. Then, we merged partial over bank and partial over
-point protocols. Some sampling stations had mix characteristics in which mix of
-partial and complete protocols were applied depending of the depth of the river
-at the time of sampling.
-
-Heterogeneity in the sampling period may introduce variability that is not related
-to ecological processes such as the presence of juveniles. In order to reduce
-heterogeneity in sampling time, only one sampling per year was retained if there
-was two in a given year, the one with with the most species and then individual
-collected. Finally, most of the fish sampling occurred in September (Median:
-mid-August) and the median standard deviation of the sampling month was inferior
-to one (0.7) within station. Additionally, we removed sampling events, in a
-given station, which the sampled length along the stream was outside the median
-length sampled more or less 30%. Finally, we standardized the biomass record
-and species richness by the sampled surface to get rid of sampling effort
-effects.
-
-### Batches definition and body size measurement
-
-During the electric fishing, and before that fish body size are measured, they
-are regrouped by batches. Each batches contains one species but there can be
-several batches by species. Body size assessment are different according to the
-batches. There are four types of batches: N, I, S/L and G. The batches N and
-I contains the biggest individuals, there are normally less numerous and then
-the body size of the individuals of those batches is recorded. The batches S/L
-contains fishes of intermediate sizes. Inside each S/L batches, the operator
-tries to make batches as homogeneous as possible in body size. Then, the body
-size of a subsample of X individuals are recorded. The G batches contain
-individuals of low body size, with care that body size is as homogeneous as
-possible in the batches. Then body size of the shortest and the longest
-individuals are recorded.
-
-## Body size inference
-
-```{r}
-myload(fish_length, lot_id_opcod, dir = mypath("data-raw", "fishing_op_build"))
-
-fish_length %<>%
-  left_join(lot_id_opcod) %>%
-  rename(length = fish) %>%
-  select(opcod, species, length)
-
-length_sem_analysis <- fish_length %>% 
-  filter(opcod %in% op_analysis_bbb$opcod)
-rm(fish_length, lot_id_opcod)
-nrow_fish_length <- nrow(length_sem_analysis)
-na_length <- sum(is.na(length_sem_analysis$length))
-```
-
-The instructions for body size inference were guided by the recommendations of
-the OFB agency, which has defined the sampling protocols, supervised the data
-collection and performed analysis for multiple purpose including stream
-management.
-
-```{r}
-body_size_caption <- paste0(
-  "Body size inference of the fishes. ",
-  "(1) Sampled fishes were attributed to batch type according to their size and
-  the number of individuals. A batch contains one species only. (2) In the batch
-  type N and I, the body size of all the individuals was recorded. In the
-  batches, S/L, the body size of a subsample of the individuals was recorded.
-  Finally, only the body size of the littlest and of the tallest individual was
-  recorded in the G batches. ",
-  "Then, (3) we inferred the body size distribution in the S/L and G batches by
-  assuming that it followed a normal distribution. The mean and the standard
-  deviation were estimated with the measured subsample."
-) 
-```
-
-```{r p-body-size, fig.cap=body_size_caption}
-knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "length_inference.pdf"))
-```
-
-With the information contained in the batch record, we inferred the body size of
-the fishes in the community. No inference were needed for the N and I batches
-because the body size of the individuals were recorded. The body size ($l$) of the
-fishes in the S/L and G were inferred under the assumption that its distribution
-followed a normal law ($l ~ N(\mu , \sigma)$).
-For a S/L batch, the mean $\mu$ and the standard deviation $\sigma$ were simply
-the average and the standard deviation of the body size of the subsample
-recorded. For a G batch, the average was approximated by 
-$\hat{\mu} = (l_{min} + l_{max}) 2^{-1}$ and the standard deviation by
-$\hat{\sigma} = (l_{min} + l_{max}) 4^{-1}$. Together with the estimations of
-the mean and the standard deviation, the number of individuals in a batch and
-assumption of a normal distribution, we simulated the body size distribution in
-S/L and G batches. To avoid simulation of unrealistic body size, we used a
-truncated normal distribution bounded at [0.05; .95] for the density of
-probability of the S/L batches, and bounded at [$l_{min}$; $l_{max}$] for the G
-batches. Body size distribution were generated using the R function
-`truncdist::rtrunc`.
-
-We removed batches that did not satisfied the following conditions. First, we
-removed batches which the total number of individuals was not recorded. In lot
-"G", we removed batches were  $l_{min} \geq l_{max}$ or if at least one of the
-measurement was missing. Additionally, G batches were removed when number of
-individuals fell below five, as G batches normally contained more individuals.
-In the S/L lot, we removed batches were the number of individuals in the
-recorded individuals fell below 10. In sum, those sanity check allowed to
-exclude potentially problematic batches. Finally, in the dataset used in the
-analysis, `r na_length` individuals had missing length over 
-`r nrow_fish_length` individuals.
-
-```{=latex}
-\pagebreak
-```
-
-## Community data
-
-```{r}
-source(mypath("R", "cleaning_methods.R"))
-removed_ind <- filter(length_sem_analysis, species %in% sp_to_remove())
-removed_sp <- unique(removed_ind$species)
-```
-
-We removed rare fish species, species from lake, crayfish species, and migratory
-species. In total, we removed `r nrow(removed_ind)` over 
-`r nrow(length_sem_analysis)` individuals and `r length(removed_sp)`.
-
-During fish sampling, some species are identified based on morphotype but they
-belong to the same species based on fecundation criteria.  We merged those
-morphotype species into one species. There was `r
-length(unique(names(sp_to_replace())))` to merge which belonged to `r
-length(unique(sp_to_replace()))` species.
-
-### Metaweb
-
-#### Ontogenic diet
-
-Diet information were obtained from fishbase.org and literature (Appendix A, Table S2). The
-diet information contained from two to three life stages by species, the life
-stages being defined by the body size of the fishes. Over the 57 fish species,
-only seven had a piscivorous life stage and only three had as strict piscivorous
-life stage. Fish species were largely omnivorous.
-
-```{r food, eval = FALSE}
-onto_shift_cap <- paste0(
-  "Ontogenic diet shift for each fish species.", 
-  "Species had between two and three life stages, bounded by body size (in mm).
-  A life stage of a given determine its diet. The fourth column to the last one
-  correspond to this respective resource: light, detritus, biofilm,
-  phytobenthos, macrophages, phytoplankton, zooplankton,  zoobenthos and
-  fishes."
-)
-table_onto_diet <- fish_diet_shift %>%
-  rename(`Life stage` = stage) %>%
-  mutate(
-    min = paste0("[", size_min),
-    max = paste0(size_max, "]")
-  ) %>%
-  unite("Size interval", min:max, sep = ";") %>%
-  select(species, `Life stage`, `Size interval`, light:ref_ods)
-
-kable(table_onto_diet,
-  format = "latex",
-  booktabs = T,
-  label = paste0("onto-diet"),
-  caption = onto_shift_cap
-  ) %>%
-kable_styling(latex_options =c("striped", "scale_down"))
-```
-
-```{=latex}
-%\includepdf[pages={2-7}]{figs/supplementary_ref_willem.pdf}
-```
-
-#### Define trophic interactions
-
-```{r}
-trophic_building_caption <- paste0(
-  "Trophic species"
-) 
-```
-
-```{r p-net-inf, fig.cap=trophic_building_caption}
-knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "network_inference.pdf"))
-```
-
-```{r}
-myload(metaweb_analysis, dir = mypath("data"))
-species_in_metaweb <- metaweb_analysis$species
-
-length_sem_analysis %<>%
-  filter(!species %in% sp_to_remove()) %>%
-  mutate(
-    species = str_replace_all(species, sp_to_replace())
-  )
-
-removed_ind_metaweb <- length_sem_analysis %>%
-  filter(!species %in% species_in_metaweb)
-removed_sp_metaweb <- unique(removed_ind_metaweb$species)
-```
-
-The metaweb described the potential trophic interactions between the
-($`r ncol(metaweb_analysis$metaweb) - length(metaweb_analysis$resource)`$) trophic species.
-We had seven resource nodes which were present in the diet of the trophic
-species namely detritus, biofilm, phytoplankton, zooplankton, macrophages,
-phytobenthos and zoobenthos.
-
-The metaweb building was based on trait matching, so it necessitates to have
-information about their diet. `r length(removed_sp_metaweb)` species were
-removed because information about their diet was missing. It represented  
-`r nrow(removed_ind_metaweb)` individuals over `r nrow(length_sem_analysis)` 
-individuals.
-
-A trophic species belonged to a life stage if the median of its body size range
-fell in the range of the life stage. In turn, this trophic species has feeding
-interactions with the resource nodes of its life stage. Interactions between
-resource nodes were determined by literature. For example, phytobenthos fed on
-detritus, while zooplankton fed on zooplankton and phytoplankton. Fish-fish
-trophic interactions between a predator and a prey were determined by body size
-ratio as in many studies [@brose_predator_2019; @poisot_structure_2016;
-@schneider_body_2012].  For a given trophic species, we first determined if its
-size class end up in a life stage containing piscivorous diet, i.e. if there was
-an overlap between them. We were more liberal for piscivory determination to not
-miss potential fish-fish trophic interactions which were the main interactions
-in our community. If the trophic species was piscivorous, we determined its prey
-size range from 3% to 45% of the median of its size range. A trophic interaction
-was set for each trophic species whose median of its size class fell into the
-prey range of the predator trophic species. To sum up, the metaweb was obtained
-with allometric feeding interactions (1) between trophic species, (2) between
-trophic species and resource nodes and (3) between resource nodes.
-
-#### Local trophic network
-
-The local trophic network (i.e. one network for each fish community
-sampling) was obtained by determining the trophic species of each fish
-individual in the community and interactions were set according to the metaweb.
-All the resource nodes were assumed to be present in each local network.
-Finally, the structure of the local networks varied according the presence of
-the trophic species. The inferred interactions represent potential interactions
-(i.e. not measured interactions) and are binary (i.e. presence or absence of
-feeding interactions).
-
-## Environmental variables
-
-The procedure to obtain altitude, slope, width depth of the streams are fully
-explained in main text. Because those measurements were collected during the
-fishing protocol, they were easier to manage in the analysis. Then, we detailed
-in the following sections how water temperature, flow and BOD were obtained.
-
-### Preparation
-
-Water temperature, flow and BOD (Biological Oxygen Demand) were obtained from the
-[naiades database](http://www.naiades.eaufrance.fr/).
-Water temperature, flow and BOD were respectively collected at a hourly, daily
-and monthly frequency. Water temperature and flow are recorded by automated
-sensors while BOD is collected manually because it necessitates analysis in a
-laboratory. BOD data collection is coordinated by the Agence de l'eau which
-realized the analysis itself or order it to a company.
-It is crucial to make clear that those variables are collected at different
-places than the fish samplings.
-
-```{r}
-pressure_cap <- paste0(
-  "Map of environmental variables obtained for the 99 sites used in the analysis."
-)
-```
-
-```{r, fig.height = 20/2.54, fig.cap = pressure_cap}
-pca_pressure <- habitat_press
-myload(fourier, dir = mypath("data-raw", "polluants"))
-myload(flow_temp_metrics, station_analysis, the_8_hydrologic_basin, dir = mypath("data"))
-
-sf_pressure <- station_analysis %>% 
-  filter(id %in% op_analysis_bbb$station) %>%
-  select(id) %>%
-  left_join(rename(pca_pressure, id = station)) %>%
-  na.omit()
-
-p <- ggplot() +
-  geom_sf(data = the_8_hydrologic_basin)
-
-var_to_plot <- colnames(pca_rotated$normal$tab)
-
-var_replacement <- c(
-  "slope" = "Slope",
-  "alt" = "Altitude",
-  "d_source" = "Distance from source",
-  "strahler" = "Strahler order",
-  "width_river_mean" = "Average stream width",
-  "avg_depth_station_mean" = "Average stream depth",
-  "width_river_cv" = "CV of stream width",
-  "avg_depth_station_cv" = "CV of stream depth",
-  "DBO_med" = "Average BOD",
-  "flow_med" = "Average flow",
-  "temperature_med" = "Average temperature",
-  "DBO_cv" = "CV of BOD",
-  "flow_cv" = "CV of flow",
-  "temperature_cv" = "CV of temperature"
-)
-
-map_pressure <- map(var_to_plot,
-~p +
-  geom_sf(data = sf_pressure, aes_string(color = .x), size = .5) +
-  viridis::scale_color_viridis() +
-  labs(title = str_replace_all(.x, var_replacement)) +
-  theme(
-    legend.title = element_blank(),
-    text = element_text(size = 8),
-    axis.text = element_blank(),
-    axis.ticks = element_blank()
-  ) +
- guides(color = guide_colourbar(barwidth = 0.5, barheight = 4))
-)
-
-plot_grid(plotlist = map_pressure, ncol = 3)
-```
-
-The time resolution was heterogeneous according to the variable considered
-(hourly, daily and monthly for temperature, flow and BOD resp.). For each
-recording station, we applied a moving window averaging (more details in
-supplementary material) to get rid of seasonal effects. For temperature, the
-moving was performed on daily average temperature. Then we took the annual
-average of each year and each variable (i.e. one value by year and by station).
-
-Several characteristics of the streams make the interpolation more complicated
-than along terrestrial surface. Interpolations in terrestrial areas are roughly
-based on euclidean distance. Euclidean distance is more complicated to consider
-in streams because it had the follow the path of the streams. Furthermore, two
-streams can be close by but not connected and the value of their variables could
-be not related or a only a few. For those reason, we used stream spatial network
-methods to interpolate temperature, flow and BOD.
-
-We reconstructed the stream network and the connection between sites with the
-`openSTARS` R package [@kattwinkel_preparing_2020]. The reconstruction was done with a raster of digital
-elevation model at a resolution of 250 meters [(IGN)](https://wxs.ign.fr/jvam1hsjm11u8voorw81v2xb/telechargement/prepackage/BDALTI-75M_PACK_FXX_2018-01-24%24BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15/file/BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15.7z)
-and a theoretical hydrologic network [@pella_reseau_2012].
-
-The procedure was done by hydrographic basin because of convergence problem
-when the interpolation was done at the France scale. We had to make a trade-off
-between the number of data (to keep enough high to perform the interpolation)
-and the level of dataset splitting. We then merge some hydrographic basin to end
-up with four region of interpolation: West, East, South and North. (XXX ADD 
-basins merged)
-
-Then we modeled each variable as dependant only on the covariation between sites
-and taking in account stream network. To model the autocovariance between sites,
-we used the linear-sill and mariah functions for taildown and tailup
-autocovariance, according to their prediction performance. The interpolations
-were done with the `SSN` R package 
-[@isaak_applications_2014, @hoef_ssn:_2014].
-
-### Performance and post check
-
-```{r eval = TRUE}
-myload(cv_press_interp_mv_avg,
-  dir = mypath("data-raw", "polluants"))
-myload(cv_temp_press_interp_mv_avg,
-  dir = mypath("data-raw", "naiades_temperatures"))
-myload(cv_flow_press_interp_mv_avg,
-  dir = mypath("data-raw", "flow"))
-dbo_cv <- cv_press_interp_mv_avg %>%
-  filter(parameter == "dbo5")
-
-cv_dbo_temp_flow <- map2_dfr(
-  list(dbo = dbo_cv, temp = cv_temp_press_interp_mv_avg, flow = cv_flow_press_interp_mv_avg),
-  c("BOD", "Temperature", "Flow"),
-  function(x, y) {
-    x %>%
-      select(basin, year, bias, std.bias, RMSPE, std.MSPE) %>%
-      group_by(basin) %>%
-      summarise_if(is.numeric, list(avg = ~mean(., na.rm = TRUE), sd = ~sd(., na.rm = TRUE))) %>%
-      mutate(Variable = y) %>%
-      select(Variable, basin, everything()) %>%
-      ungroup
-  })
-
-cv_dbo_temp_flow %>%
-  mutate_if(is.double, ~signif(., 2)) %>%
-  kable(
-    align = "c",
-    format = "latex",
-    booktabs = T,
-    caption = paste0("Results of the cross-validation for the interpolation of
-      BOD, temperature and flow. Average over 4 interpolations are shown.") 
-      ) %>%
-    collapse_rows(columns = c(1, 2), valign = "top") %>%
-    kable_styling(latex_options =c("striped", "scale_down"))
-```
-
-```{r}
-cv_bias_caption <- paste0(
-  "Bias of the interpolation from Leave-One-Out Cross Validation (LOOCV). "
-)
-```
-
-The performance of the interpolation was evaluated with leave one out
-cross-validation (already implemented in the SSN package). The value of the
-interpolated variable of each station was predicted after removing it from the
-dataset.
-
-When predicted values were below the minimum value or above the maximum value
-recorded in the dataset for flow, temperature and BOD, we replaced the
-predicted value by respectively the minimum and the maximum value found in the
-dataset. We ran the interpolation four times and we kept the predicted value
-which had the least standard deviation.
-
-```{=latex}
-\pagebreak
-```
-
-# Data analysis
-
-The CV of biomass over can cover multiple dynamics, including increases,
-stable, decreases and a mix of them. Theoretically, however, the CV computed to
-quantify stability is often represented with the assumption that the overall
-dynamic of the biomass varies around an equilibrium. In order to approach this
-condition, we kept only the stations that have met this criteria. To qualify the
-biomass trajectories over time, we used the symbolic aggregated approximation
-method (SAX) which is commonly used in time series analysis and implemented in
-the `jmotif` R package. This method classifies time series rather than
-quantifies trends and so is generic enough to encompass the diversity of time
-series shapes. The classification necessitates three steps. First, the time
-series are normalized (i.e. Substituting the mean and divide by the standard
-deviation). The second step is to reduce the dimensionality of the time series
-by Piecewise Aggregation Approximation (PAA) method. Each time series is divided
-in $N$ frames of equal size that allows to the reduce the dimensionality of the
-time series. For each frame, we simply kept the mean value of the time series.
-The last step is to qualify each frame into string. Because values of
-normalized time series typically follows a normal distribution ($N(0,1)$), a
-breakpoints can be computed by dividing the area under the normal distribution
-in equal parts. The algorithm attributes a alphabetic letter to each part from
-the lowest to the highest ($a$, $b$, $c$, ...). We set three breakpoints, so
-$a$, $b$ and $c$. Finally, the trajectory of each time series is classified as
-a combination of $a$, $b$, $c$ letters. $abc$ and $cba$ time series represent
-respectively monotonic increasing and decreasing trajectories. For data analysis,
-we kept only the $bbb$ which represent time series that showed no temporal
-tendencies, with respect to our methodology.
-
-```{r eig-plot}
-rotated_eigen_values <- 
-  tibble(
-    name = paste0("RC", seq(1,14)),
-    type = c(rep("Kept", 2), rep("No kept", 14 - 2)),
-    value = pca_rotated$rotated$values
-  )
-eigen_rotated_plot <-
-  ggplot(rotated_eigen_values,
-    aes(x = reorder(name, -value) , y = value)) +
-  geom_col(aes(fill = type)) +
-  scale_fill_discrete(name = "Status") +
-  labs(x = "Rotated component", y = "Eigen values") +
-  theme(legend.position = "none",
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank())
-```
-
-```{r contrib-pca}
-#https://stats.stackexchange.com/a/143949
-caption_contrib_pca <- paste0(
-  "Loadings of variable to rotated components of the PCA.
-  Loadings are the coefficients which determine the components of the PCA as
-  linear combinations of the variables.
-  "
-)
-
-loadings_pca <- matrix(
-  as.matrix(round(pca_rotated$rotated$Structure, 2)),
-  nrow = 14,
-  dimnames = dimnames(pca_rotated$rotated$Structure)
-  ) %>%
-  as_tibble %>%
-  mutate(
-    Variable = str_replace_all(
-      dimnames(pca_rotated$rotated$Structure)[[1]],
-      get_pca_var_name_replacement())
-  ) %>%
-  select(Variable, RC1, RC2)
-kable(
-  x = loadings_pca,
-  format = "latex",
-  booktabs = T,
-  label = "contrib-pca",
-  caption = caption_contrib_pca
-  ) %>%
-kable_styling(latex_options = c("striped"))
-```
-
-```{r, eval=FALSE}
-corr_pca_caption <- paste0(
-  "Spearman correlation between environmental variables used in the PCA.
-  The variables have been scaled before to compute the correlation."
-)
-
-pca_var_correlation <- pca_pressure %>%
-  select(-station) %>%
-  #mutate_all(scale) %>%
-  as.matrix() %>%
-  cor(., method = "spearman")
-
-pca_var_correlation %<>% round(., 2)
-dimnames(pca_var_correlation) %<>%
-  map(., ~str_replace_all(.x, get_pca_var_name_replacement()))
-
-kable(
-  x = pca_var_correlation,
-  format = "latex",
-  booktabs = T,
-  label = "corr-pca",
-  caption = corr_pca_caption
-  ) %>%
-kable_styling(latex_options = c("striped", "scale_down"))
-```
-
-```{r}
-prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
-  map_dbl(., ~round(.x * 100))
-
-tot_var_expl_pca <- round(sum(pca_rotated$rotated$Vaccounted["Proportion Var", ]) * 100)
-
-pca_caption <- paste0(
-  "Rotated axis of PCA on environmental variables. The five components
-  explained,", tot_var_expl_pca, "% of the variance (",
-  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
-  "(A) Axis 1 was positively related to the river size, axis 2 was related to
-  average temperature and negatively related to the river slope and altitude.
-  (B) Axis 3 was negatively related to the CV of stream size.
-  Axis 4 was related to the CV of enrichment.
-  Finally, axis 5 was related to the CV of flow and average enrichment.")
-```
-
-```{r pca-rotated, fig.cap = pca_caption}
-p1 <- my_pca_plot(xaxis = "RC1", yaxis = "RC2", ctb_thld = .4)
-#p2 <- my_pca_plot(xaxis = "RC3", yaxis = "RC4", ctb_thld = .4)
-#p3 <- my_pca_plot(xaxis = "RC4", yaxis = "RC5", ctb_thld = .4)
-
-pca_plot <- plot_grid(p1, eigen_rotated_plot, nrow = 1)
-save_plot(
-  filename = mypath("manuscript", "bef_stability", "figs", "pca_plot.pdf"),
-  pca_plot,
-  nrow = 1, ncol = 2,
-  base_height = 6/2.54, base_asp = 1.6, base_width = NULL 
-  )
-pca_plot
-```
-
-```{r}
-print_prop_var_pca <- prop_var_expl_pca[order(names(prop_var_expl_pca))]
-```
-
-The five axis of the rotated PCA explained respectively
-`r paste0(prop_var_expl_pca, "%", collapse = ", ")` of the variance.
-Please see the main text for the interpretation of the axis.
-
-```{r }
-rc2 <- tibble(
-  station = pca_pressure$station,
-  alt = pca_pressure$alt,
-  temperature_med = pca_pressure$temperature_med,
-  value = pca_rotated$rotated$scores[,"RC2"]
-)
-
-rc2_sf <- station_analysis %>%
-  select(station = id) %>%
-  filter(station %in% rc2$station) %>%
-  left_join(rc2, by = "station")
-
-caption_rc2_map <- paste0(
-  "Map of the station values for the second axis of the rotated PCA."
-)
-```
-
-```{r rc2-map, eval = FALSE, fig.cap = caption_rc2_map}
-p +
-  geom_sf(data = rc2_sf, aes(color = log(value + abs(min(value)) + 1 ))) +
-  viridis::scale_color_viridis() +
-  labs(title = "RC2 (Log)") +
-  theme(legend.title = element_blank())
-```
-
-```{r pca-two-axis, eval = FALSE}
-two_axis <- compute_rotated_pca(.data = pca_pressure, naxis = 2)
-two_axis$rotated$Vaccounted
-
-cor(two_axis$rotated$score[,c("RC1", "RC2")],
-  pca_rotated$rotated$score[,c("RC1", "RC2")])
-```
-
-```{=latex}
-\pagebreak
-```
-
-# Statistical analysis
-
-```{r}
-sem_variable_table <- tibble(
-  variable = c(paste0("PCA axis", seq(1, 2)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
-  unit = c(rep("unitless", 2), "# by square meter", rep("unitless", 4), "gram by square meter"
-    ),
-  transformation = c(rep("Log base 10", 2), "Log base 10", rep("No", 2), rep("Log base 10", 3)),
-  interpretation = c("linked to stream size",
-    "linked to average temperature",
-    "Total species richness over the temporal series",
-    "Median of annual link density", "Median of annual average trophic level", "", "",
-    "Median of annual total biomass")) %>%
-kable(
-  format = "latex",
-  booktabs = T,
-  caption = "Variable description and transformation"
-  ) %>%
-kable_styling(latex_options = c("striped"))
-sem_variable_table
-```
-
-### SEM hypothesis
-
-We linked environmental variables both to community structure and stability
-components. Rooted in assembly theory, environment filters species that can
-establish in a community and thus affect community structure. (+ add specific
-hypothesis about physical and climate). (1) We hypothesized that enrichment
-(characterized by DBO) and mean annual temperature will increase species turnover
-[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
-decrease biomass stability directly without going by community structure. First,
-instability of habitat and environmental factors may in turn drive biomass
-instability [@hansen_climate_2013]. Secondly, average environmental conditions
-such as enrichment can increase directly CV by increasing species biomass
-fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
-to decrease stability through starvation resulting from high metabolic activity
-[@tabi_warming_2019].
-
----
-# Species richness to community attributes 
----
-
-To reveal the mechanisms behind the relationship between species richness and
-biomass stability, causal links were set from species richness to other
-community attributes. In particular, species richness decreased connectance
-following results from @thebault_stability_2010; @winemiller_must_1989. But
-theoretically, some ecological networks can show the inverse relationship
-[@winemiller_must_1989]. (6) We hypothesized also that species richness will
-modulate average weighted trophic level because of food web assembly processes.
-A community with more fish species can support higher trophic level. Finally, we
-set up causal relationships from community attributes to stability components.
-
----
-#  Community attributes to stability
----
-We hypothesized that (7) species richness decreased synchrony between species
-[@loreau_species_2008] and increased $\overline{CV_{sp}}$
-[@tilman_biodiversity_2006]. (8a) We expected that average trophic level had a
-positive or negative relationship with synchrony, bottom-up effects should
-result in positive whereas top-down in negative relationships. We expected a (8b)
-negative relationship between average trophic level and $\overline{CV_{sp}}$ if
-predators stabilised prey fluctuations or if the increasing part of
-biomass in the predators decreased $\overline{CV_{sp}}$ because of their higher
-body mass (if mean increase faster than variance). (9a) Connectance was expected
-to decrease or increase $\overline{CV_{sp}}$ and (9b) synchrony because of top
-down effects or bottom up effects.
-
-```{r}
-hist_var_caption <- paste0(
-  "Distribution of the variables used in the Structural Equation Modeling. The
-  biomass stability, the CV of species (CVsp), PCA1, PCA2, species richness,
-  synchrony and total biomass were logged."
-)
-```
-
-```{r hist-sem-data, fig.cap = hist_var_caption}
-sem_data %>%
-  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct) %>%
-  gather(variable, value) %>%
-  mutate(variable = str_replace_all(variable, get_sem_var_name_replacement())) %>%
-  ggplot(aes(x = value)) +
-  geom_histogram() +
-  facet_wrap(~variable, scales = "free")
-```
-
-```{r}
-colin_sem_cap <- paste0(
-  "Variance Inflation Factor for each individual linear model of the structural
-  equation models."
-) 
-```
-
-```{r s-colin-sem, fig.cap = ""}
-mod_stab_list <-
-  list(
-    nlme::lme(log_rich_tot_std ~ log_RC1 + log_RC2,  random = ~ 1 | basin, data = sem_data),
-    nlme::lme(ct ~ log_RC1 + log_RC2 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
-    nlme::lme(log_sync ~ log_rich_tot_std + ct + t_lvl + log_RC1 + log_RC2,
-      random = ~ 1 | basin, data = sem_data),
-    nlme::lme(log_cv_sp ~ log_rich_tot_std  + ct + t_lvl
-      + log_RC1 + log_RC2, random = ~ 1 | basin, data = sem_data),
-    lm(log_stab_std ~ log_cv_sp + log_sync, data = sem_data),
-    nlme::lme(log_bm_std ~ log_rich_tot_std  + ct + t_lvl
-      + log_RC1 + log_RC2, random = ~ 1 | basin, data = sem_data)
-  )
-names(mod_stab_list) <- c(
-  "Species richness",
-  "Connectance",
-  "Avg trophic level",
-  "Synchrony",
-  "CVsp",
-  "Biomass stability",
-  "Total biomass"
-)
-
-colin_stab_sem <- map(mod_stab_list, car::vif)
-
-tmp <- map(colin_stab_sem, enframe)
-
-# colinearity table
-colin_stab_sem <- tibble(vif = tmp, mod = names(mod_stab_list)) %>%
-  unnest(vif) %>%
-  rename(`Response variable` = mod) %>%
-  mutate(
-    value = round(value, 1),
-    name = str_replace_all(name, get_sem_var_name_replacement())
-    ) %>%
-  spread(name, value)
-
-kable(colin_stab_sem,
-  format = "latex",
-  booktabs = T,
-  caption = "Variance Inflation Factor for the linear models used in structural
-  equation modeling"
-  ) %>%
-kable_styling(latex_options = c("striped", "scale_down"))
-```
-
-```{r}
-caption_mod_res <- paste0(
-  "Residuals versus fitted values of the linear models used in the structural
-  equation models."
-) 
-```
-
-```{r mod-res, fig.height = 8, fig.cap = caption_mod_res}
-library(nlme)
-plot_residuals <- function (x, y = "Diagnostic") {
-  plot.lme(x, main = y, xlab = "Fitted values", ylab = "Residuals")
-}
-p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
-plot_grid(plotlist = p_resid_stab_sem, ncol = 2)
-```
-
-```{r}
-format_coef_table <- function (sem = NULL) {
-
-  params <- sem$coefficients
-  colnames(params)[length(colnames(params))] <- "Stars"
-
-  replace_wo_n <- str_replace_all(get_sem_var_name_replacement(), "\n", "")
-  names(replace_wo_n) <- names(get_sem_var_name_replacement())
-
-  params %<>%
-    mutate_at(c("Response", "Predictor"),
-      ~str_replace_all(., replace_wo_n))
-
-  params
-}
-```
-
-```{r}
-est_stab_sem_caption <- paste0(
-  "Estimate of the effects for the temporal stability of annual biomass of the structural equation
-  model."
-
-)
-
-kable(format_coef_table(stab_sem_rich),
-  format = "latex",
-  booktabs = T,
-  caption = est_stab_sem_caption
-  ) %>%
-collapse_rows(columns = 1, valign = "top") %>%
-kable_styling(latex_options = c("striped", "scale_down"))
-```
-
-```{r}
-est_bm_sem_caption <- paste0(
-  "Estimate of the effects for the structural equation
-  model of the median of annual total biomass."
-)
-
-kable(format_coef_table(bm_sem_rich),
-  format = "latex",
-  booktabs = T,
-  caption = est_bm_sem_caption
-  ) %>%
-collapse_rows(columns = 1, valign = "top") %>%
-kable_styling(latex_options = c("striped", "scale_down"))
-```
-
-```{r rsq-model}
-rm_n <- str_remove_all(get_sem_var_name_replacement(), pattern = "\n")
-names(rm_n) <- names(get_sem_var_name_replacement()) 
-rsq_table <- map_dfr(mod_stab_list, piecewiseSEM::rsquared, method = "nagelkerke") %>%
-  mutate_at(vars(Conditional, Marginal), ~round(., 2)) %>%
-  mutate(Response = str_replace_all(Response, rm_n)) %>%
-  dplyr::select(Response, Marginal, Conditional, R.squared)
-rsq_table_caption <- paste0(
-  "R squared of the linear models used in the structural equation modeling."
-)
-```
-
-```{r tab-coeff-bm, fig.cap = "Coefficient"}
-# Replacement rules for term
-rp_est <- c(
-  "(Intercept)" =     "intercept",
-  "sd\\_\\(intercept\\)\\.basin" = "sd intercept basin",
-  "log_rich" =     "Median richness (log base 10)",
-  "troph_group3" =     "high trophic group",
-  "log_rich:troph_group3" =     "Median richness (log10) : high trophic group",
-  "sig01.basin" =     "sd intercept basin",
-  "sd_Observation.Residual" =     "residuals",
-  "sigma" = "residuals"
-)
-# Replacement rules for group
-rp_group <- c(
-  "fixed" = "Fixed",
-  "basin" = "Random"
-)
-```
-
-```{r}
-mask_drop_lm <- names(mod_stab_list) %in% "Biomass stability"
-random_coeff_sem <- map(mod_stab_list[!mask_drop_lm], random.effects)
-test <- getVarCov(mod_stab_list[!mask_drop_lm][[2]])
-
-# get random effect 
-get_intercept_variance <- function (mod) {
-  vc <- VarCorr(mod)
-  suppressWarnings(storage.mode(vc) <- "numeric")
-  enframe(vc[1,])
-}
-random_coeff_sem <- map(mod_stab_list[!mask_drop_lm],
-  get_intercept_variance) %>%
-  enframe(name = "variable") %>%
-  unnest(value) %>%
-  pivot_wider(names_from = "name", values_from = "value")
-#check
-#all.equal(random_coeff_sem[[2]],(random_coeff_sem[[3]])^2)
-#good
-
-# get intercept 
-get_intercept <- function (mod) {
-  mod[["coefficients"]]$fixed["(Intercept)"]
-}
-intercept_sem <- map_dbl(
-  mod_stab_list[!mask_drop_lm], get_intercept) %>%
-  enframe(name = "variable", value = "Intercept")
-
-formated_random_effects <- intercept_sem %>% 
-  left_join(random_coeff_sem, by = "variable") %>%
-  rename(`Response variable` = variable)
-caption_random_effect <- paste0(
-  "Estimated variance and standard deviation on the intercept due to the hydrographic basins."
-)
-
-kable(formated_random_effects,
-  format = "latex",
-  booktabs = T,
-  caption = caption_random_effect
-  ) %>%
-kable_styling(latex_options = c("striped"))
-```
-
-```{r sensitivity, message = FALSE, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
-library(furrr)
-
-myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
-myload(biomass_ts_sax, dir = mypath("data"))
-op_analysis_bbb <- filter(op_analysis, station %in%
-  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
-op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
-  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
-
-myload(network_metrics, dir = mypath("data", "classes"))
-sem_sensivity_data <- list(full = op_analysis, bbb = op_analysis_bbb,
-  without_holes = op_analysis_wo_holes, bbb_without_holes = op_analysis_wo_holes_bbb)
-
-sem_stab_l_data <- 
-  furrr::future_map(sem_sensivity_data,
-    ~build_dataset_get_sem_coefficient(
-      .op = .x,
-      sem_fun = compute_stab_sem_rich
-    )
-  )
-
-nb_station <- map_int(sem_sensivity_data, ~length(unique(.x$station)))
-
-sem_stab_results <- map(sem_stab_l_data,
-  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
-  enframe() %>%
-  rename(dataset = name) %>%
-  unnest(value)
-
-# Reformat
-colnames(sem_stab_results) <- str_to_lower(colnames(sem_stab_results))
-mysave(sem_stab_results, dir = mypath("data"), overwrite = TRUE)
-```
-
-```{r sem-sens-bm, fig.cap = "Sensivity analysis for Biomass"}
-sem_bm_l_data <- furrr::future_map(sem_sensivity_data,
-  ~build_dataset_get_sem_coefficient(
-    .op = .x,
-    sem_fun = compute_prod_sem_rich)
-)
-sem_bm_results <- map(sem_bm_l_data,
-  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
-  enframe() %>%
-  rename(dataset = name) %>%
-  unnest(value)
-
-# Reformat
-colnames(sem_bm_results) <- str_to_lower(colnames(sem_bm_results))
-mysave(sem_bm_results, dir = mypath("data"), overwrite = TRUE)
-```
-
-```{r}
-sens_cap <- paste0(
-  "Sensivity analysis of the Structural Equation models for total biomass
-  and its temporal stability."," The Constant dataset is the one kepting only the
-  sites that had not a significant temporal trend in biomass; ", "Constant/
-    without holes dataset kept only the constant sites plus the ones that had not
-  holes in their sampling period; ", "Complete is the dataset containing all the
-  site that have been followed ten years or more, as the other dataset;", "Without holes dataset is
-  the dataset containing only the sites that had no holes in the their sampling period."
-)
-```
-
-```{r, fig.height = 8, fig.cap = sens_cap}
-p_sens_bm <- plot_sensivity_analysis(
-  .data = sem_bm_results,
-  inverse_label_order = TRUE) +
-  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
-
-p_sens_stab <- plot_sensivity_analysis(.data = sem_stab_results,
-  inverse_label_order = TRUE) +
-  guides(color = guide_legend(direction = "horizontal", nrow = 2))
-legend_b <- get_legend(p_sens_stab)
-p_sens_stab %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm"))
-p <- plot_grid(
-  p_sens_bm, p_sens_stab, legend_b, nrow = 3,
-  rel_heights = c(1, 1, .1),
-  labels = c("Total biomass", "Biomass stability")
-)
-p
-```
-
-```{=latex}
-\pagebreak
-```
-
-# References

### 2020-12-01 manuscript/bef_stability/appendixB.Rmd
Extract environmental data for fish dynamics

@@
   ) %>%
-kable_styling(latex_options = c("striped"))
+kable_styling(latex_options = c("striped", "scale_down"))
 sem_variable_table

### 2020-12-01 manuscript/bef_stability/manuscript.Rmd
Extract environmental data for fish dynamics

@@
   "The species names corresponding to the three digit codes are found in Table
-  SXX." ,
+  S1." ,
   "Yearly temporal series of networks of two stations having respectively a low
@@
 in total biomass were selected (detailed in supplementary methods). However, the
-results were robust to the relaxation of this hypothesis (Table SXX). These
+results were robust to the relaxation of this hypothesis (Figure S7). These
 selection steps resulted in 99 stations distributed over seven hydrographic
@@
 which a piscivorous species begin to feed on fishes. The ontogenic fish diet
-database was filled according to fishbase and literature [REF WILLEM]. Each
+database was filled according to fishbase and literature (Table S2). Each
 fish species had two or three life stages which are delimited by a body size
@@
 were logged to fulfill model assumptions (see residual plots and data
-transformation in supplementary informations, Table SXX). We set the seven
+transformation in supplementary informations, Figure S5 and S6, Table S5). We set the seven
 hydrographic basins as a random effect on the intercept of the linear models to
 account for their heterogeneity. We checked for the absence of multicollinearity 
-with Variance Inflation Factor (VIF, Table SXX). The slopes reported
+with Variance Inflation Factor (VIF, Table S6). The slopes reported
 in the main text were standardized in order to compare their magnitude ($r_\delta
@@
 slope had a $P$ value inferior to $0.05$ were reported in the main text, all the
-path values are presented in Table SXX and SXX).
+path values are presented in Table S7 and S8).
 
@@
 
-```{r sem-plot, fig.height = 6, fig.cap = sem_caption}
+```{r sem-plot, out.width="\\maxwidth", fig.cap = sem_caption, results = "fig.show", cache = FALSE}
+#out.height="120%",
 #https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
@@
 
-plot_grid(
-  meta_bm_sem_rich, p_bm_sem_rich,
-  meta_stab_sem_rich, p_stab_sem_rich,
-  labels = LETTERS[1:4], nrow = 2,
-  rel_widths = c(1, 1)
-)
+#plot_grid(
+  #meta_bm_sem_rich, p_bm_sem_rich,
+  #meta_stab_sem_rich, p_stab_sem_rich,
+  #labels = LETTERS[1:4], nrow = 2,
+  #rel_widths = c(1, 1)
+#)
+# Put the panel of Colin
+arrow_dir <- mypath("manuscript", "bef_stability","fleches", "figure_sem2")
+filename <- list.files(arrow_dir, full.names = TRUE)
+mask <- str_match(filename, "\\.svg")[, 1] %>% is.na %>% !.
+#filename[mask]
+type <- c("bm", "meta_bm", "meta_stab", "stab")
+sem_list <- map(filename[mask], function (x) {
+  w <- 2400
+  img <- magick::image_read_svg(
+    path = x, width = w, height=w*1.618)#, density = 600
+  p_sem <- cowplot::ggdraw() +
+    cowplot::draw_image(img)#, scale = 1.0
+  return(p_sem)
+})
+sem_list %<>% map(., ~.x + theme(plot.margin = unit(x = rep(0, 4), units = "pt")))
+names(sem_list) <- type
+sem_plot <- plot_grid(
+  plotlist = sem_list[c("meta_bm", "bm", "meta_stab", "stab")],
+  labels = "AUTO" 
+  )
+save_plot(
+  filename = mypath("manuscript", "bef_stability", "figs",
+    "sem_colin.pdf"),
+  plot = sem_plot, ncol = 2, nrow = 2,
+  base_width = 2.71, base_asp = 1.2 
+)
+#sem_plot
+knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "sem_mano.pdf"))
 ```
@@
 collapse_rows(columns = 1, valign = "top")
-write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
+#write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
 ```

### 2020-12-01 manuscript/bef_stability/temporal_biomass.R

@@ -113,8 +113,9 @@ comb %<>%
 
 debugonce(plot_temporal_biomass)
 plot_temporal_biomass(bm_data = comb,
-  biomass_var = "mv_win", com = sem_data,
-  net_metrics = NULL, .log = FALSE)
+  biomass_var = "mv_win",
+  com = filter(sem_data, station == 1755),
+  .log = FALSE)
 
 # Get biomass by sp node:
 net_sp_troph <- select(network_analysis, opcod, composition) %>%

### 2020-12-07 manuscript/bef_stability/manuscript.Rmd
Add new references: fish biomass, stability

@@
 running from 1995 to 2018. We inferred trophic interactions from
-body size recorded and diet literature. We reveal that species richness and average
+individual body size and diet literature. We reveal that species richness and average
 trophic level had a positive relationship with annual biomass of fish
@@
 natural communities such as forests [@szwagrzyk_above-ground_2007;
-@jacob_productivity_2010; @seidel_relationship_2013]. Some authors suggest that
-the lack of resource complementarity or environmental harshness might be
-responsible for negligible, or negative effects of species richness
-[@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015].
+@jacob_productivity_2010; @seidel_relationship_2013] and marine fishes [@maureaud_biodiversityecosystem_2019]. Some authors suggest that
+the lack of resource complementarity, environmental harshness or past human
+pressures might be responsible for negligible, or negative effects of species
+richness [@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015;
+@maureaud_biodiversityecosystem_2019].
 
@@
 @grace_integrative_2016]. Environment affects organism performance directly, and
-thereby, species abundances, total biomass [@grace_integrative_2016] and temporal
+thereby, species abundances, total biomass [@grace_integrative_2016; @woods_testing_2020] and temporal
 stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
@@
 grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
-@wu_relationship_2015; @li_relationship_2018]. The positive effect of species
+@wu_relationship_2015; @li_relationship_2018] as well as in streams
+[@woods_testing_2020]. The positive effect of species
 richness on total biomass might be due to resource use complementarity
@@
 @dossena_warming_2012; @edeline_ecological_2013; @emmrich_geographical_2014;
-@hattab_forecasting_2016]. Contrasting with a previous study in experimental
-plant communities [@grace_integrative_2016] and in fish communities
-[@yvondurocher_warming_2011; @dossena_warming_2012], we found that environmental
-drivers overall affect total biomass indirectly rather than directly.
+@hattab_forecasting_2016; @woods_testing_2020]. Contrasting with previous studies in experimental
+plant communities [@grace_integrative_2016], aquatic mesocosms [@yvondurocher_warming_2011; @dossena_warming_2012] and marine fish communities [@maureaud_biodiversityecosystem_2019]
+, we found that environmental drivers overall affect total biomass indirectly
+rather than directly [@woods_testing_2020].
 

### 2020-12-07 manuscript/bef_stability/manuscript.Rmd
Introduction reviewed according to elisa comments

@@
 
-Current biodiversity losses and further global change has the potential to affect
-ecosystems in complex ways [@loreau_biodiversity_2001; @tilman_biodiversity_2014]. Biodiversity has a
-tremendous effect on ecosystem properties because it largely determines both the
-amount and the distribution of matter and energy fluxes
-within and among ecosystems [@loreau_meta-ecosystems:_2003]. Biodiversity thus affects biomass
-production [@tilman_productivity_1996; @cardinale_species_2002;
-@grace_integrative_2016], distribution [@thebault_relationship_2006] and
-stability [@thebault_trophic_2005; @thebault_relationship_2006;
-@tilman_biodiversity_2006]. The relationship between biodiversity and
-ecosystem properties is a central topic in ecology [@hector_plant_1999;
-@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
-@duffy_why_2009; @isbell_forest_quantifying_2018] and our understanding of it is 
-crucial to better anticipate the impacts of global change.
+Current biodiversity losses and further global change have the potential to
+affect ecosystems in complex ways [@loreau_biodiversity_2001;
+@tilman_biodiversity_2014]. Biodiversity has indeed a tremendous effect on
+ecosystem functions and their stability in response to perturbations
+[@hector_plant_1999; @loreau_biodiversity_2001; @hooper_effects_2005;
+@dunne_network_2006; @duffy_why_2009], because it largely determines both the
+amount and the distribution of matter and energy fluxes within and among
+ecosystems [@loreau_meta-ecosystems:_2003]. Understanding the relationship
+between biodiversity and ecosystem properties is thus crucial to better
+anticipate the impacts of global change.
 
@@
 
-Species richness promotes higher biomass production in a variety of ecosystems
-and taxons. Indeed species richness generally increases primary productivity and
+Biodiversity affects biomass production [@tilman_productivity_1996;
+@cardinale_species_2002; @grace_integrative_2016], distribution
+[@thebault_relationship_2006] and stability [@thebault_trophic_2005;
+@thebault_relationship_2006; @tilman_biodiversity_2006].
+Species richness has been shown to promote higher biomass production and  
+higher temporal stability of total biomass in a variety of ecosystems
+and taxa. 
+Indeed species richness generally increases primary productivity and
 total biomass in experimental plant communities [@tilman_productivity_1996;
@@
 [@mulder_physical_2001], stream feeders, [@cardinale_species_2002] and aquatic
-bacterial consumers [@pennekamp_biodiversity_2018]. Despite the diversity of
-ecosystems and taxons studied, the relationship between diversity and ecosystem
-functioning remains traditionally focused on single trophic levels, ignoring the
-effects of foodweb structure. Theoretical models have recently moved from
-single trophic [@tilman_plant_1997;
-@loreau_biodiversity_2001] to multitrophic communities [@thebault_food-web_2003;
-@poisot_dissimilarity_2012; @schneider_animal_2016; @wang_biodiversity_2018]. 
-These models show that both complementarity in the use of resources and selection effects,
-the two main mechanisms previously highlighted in single-trophic studies, are
-also important to understand diversity effects in foodwebs
-[@thebault_food-web_2003; @poisot_dissimilarity_2012; @schneider_animal_2016].
-However, they also reveal new mechanisms such as positive effects of 
-the number of trophic levels, i.e. associated with higher trophic levels, on ecosystem
-functioning [@wang_biodiversity_2018]. Theoretical studies also showed that food
-web properties, such as interaction distribution and strength, affect the
-distribution of biomass among adjacent trophic levels
-[@thebault_relationship_2006; @schneider_animal_2016; @barbier_pyramids_2019].
-Despite these theoretical evidence that structure affects biomass, we are
-lacking empirical studies that assess jointly how foodweb structure and species
-diversity affect total biomass and its production.
-
----
-#### Single and multitrophic communities
----
-
-Further than biomass production, many studies showed that species richness
-increases temporal stability of communities, i.e. variation through time, often
-quantified by the temporal CV of biomass.  Such positive relationship between
+bacterial consumers [@pennekamp_biodiversity_2018]. 
+In parallel, such positive relationship between
 species richness and temporal stability of biomass has been reported in
@@
 settings, such as stream fish communities [@franssen_annual_2011], bird and
-butterfly communities [@olivier_urbanization_2020]. However, this relationship
-has been mostly explored in single trophic level systems or without accounting
-for foodweb structure, even more so than the relationship between diversity and
-biomass production.
-
-Several theoretical studies considering a single trophic level have
-clarified which mechanisms generate this positive relationship between species
-richness and temporal
-stability [@loreau_species_2008; @thibaut_understanding_2013], (1) species
-synchrony and (2) species variability. Species synchrony captures to what extent
-the fluctuations of abundances or biomasses through time are correlated among
-species. A low synchrony in species fluctuations, i.e. asynchrony, is
-synonymous of compensatory dynamic, where the decrease in abundance of a species
-is compensated by the increase of an other. Asynchrony is generally the main
-mechanism which species richness has a stabilizing effect on temporal
-stability [@tilman_biodiversity_2006; @olivier_urbanization_2020]. Asynchrony is
-expected to increase with the variability of species responses to perturbations. Though most
-often positive, the relationship between species diversity and asynchrony has
-also been evidenced to be neutral or negative in natural settings
-[@tilman_biodiversity_2006; @thibaut_understanding_2013;
-@olivier_urbanization_2020; @valencia_synchrony_2020].
-
-In addition to diversity,
-foodweb structure is expected to strongly affect the stability of communities
-and ecosystems, as outlined by the large body of theoretical studies on this
-topic [@may_will_1972; @dunne_network_2006; @neutel_reconciling_2007;
-@duffy_why_2009; @stouffer_compartmentalization_2011]. In particular, predation
-has cascading effects on both species variability and synchrony
-[@teng_dynamics_2004; @shanafelt_stability_2018] and it also affects
-synchrony between species.
-
----
-#### Problematic
----
-
-Overall, the evidence suggests that both species richness and network structure
-should modulate total biomass and stability of communities. The effects of
-species richness and network structure, such as connectance and average trophic
-level, are potentially conflicting or synergistic in such a way that they need
-to be addressed jointly. Despite the long-standing interest for the links
-between foodweb complexity and stability in ecology, we still have very few
-evidence of the relationship between network structure and the temporal
-stability of multitrophic communities in natural settings.
-Although the relationships between diversity, total biomass and its stability
-found in experimental and in natural settings can be similar
-[e.g., @wu_relationship_2015; @li_relationship_2018], negative or non
-significant effects of species richness on total biomass have been found in some
-natural communities such as forests [@szwagrzyk_above-ground_2007;
-@jacob_productivity_2010; @seidel_relationship_2013] and marine fishes [@maureaud_biodiversityecosystem_2019]. Some authors suggest that
-the lack of resource complementarity, environmental harshness or past human
-pressures might be responsible for negligible, or negative effects of species
-richness [@loreau_biodiversity_2001; @he_global_2013; @wu_relationship_2015;
-@maureaud_biodiversityecosystem_2019].
-
----
-#### Environment can mitigate community structure and ecosystem properties 
----
-
-When analyzing data from natural communities, the relationships among species
-richness, total biomass and species richness might also arise from effects of
-the environment on both diversity and ecosystem functions
-[@loreau_biodiversity_2001; @he_global_2013;
-@grace_integrative_2016]. Environment affects organism performance directly, and
-thereby, species abundances, total biomass [@grace_integrative_2016; @woods_testing_2020] and temporal
-stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
-@oliver_heterogeneous_2010; @franssen_annual_2011; @friedpetersen_drivers_2020].
-For example, larger ecosystem might increase the number of available
-resources and thus total biomass [@post_ecosystem_2000; @doi_resource_2009].
+butterfly communities [@olivier_urbanization_2020].
+Despite the diversity of
+ecosystems and taxa studied, the relationship between diversity and ecosystem
+functioning in experimental and empirical studies remains mostly focused
+on single trophic levels, ignoring the effects of foodweb structure. 
+This gap is even more striking for the relationship between diversity and
+temporal stability of ecosystem functioning, in spite of long-standing interest
+for the links between food web complexity and stability in theoretical ecology
+[e.g. @may_will_1972; @dunne_network_2006; @neutel_reconciling_2007;
+@duffy_why_2009; @stouffer_compartmentalization_2011].
+
+Overall, the evidence from theoretical models suggests that both species
+richness and foodweb structure should modulate ecosystem propertiestotal
+biomass and their stability of communities. Complementarity in the use of
+resources, a main mechanism previously highlighted in single-trophic studies, is
+important to understand the effects of species richness in food webs [@thebault_food-web_2003;
+@poisot_trophic_2013; @schneider_animal_2016], but in that case it also depends
+on food web connectance [@thebault_food-web_2003; @poisot_trophic_2013].
+
+As classically found in studies considering a single trophic level,
+[@tilman_biodiversity_2006; @loreau_species_2008; olivier_urbanization_2020],
+asynchrony in species temporal variations is also explaining a significant part
+of the stabilizing effects of species richness on total biomass in food webs
+[@thebault_trophic_2005]. Indeed, a low synchrony in species fluctuations,
+i.e. asynchrony, is synonymous of compensatory dynamics, where the decrease in
+abundance of a species is compensated by the increase of an other. However,
+higher connectance can in some cases reverse the positive effects of species
+richness on temporal stability of total biomass, by leading to a negative
+relationship between species richness and species temporal variability
+[@thebault_trophic_2005]. In addition, recent models revealed new mechanisms by
+which food web structure affects total ecosystem biomass and its temporal
+variability. In particular, the number of trophic levels in food webs, which is
+associated with the presence of species at higher trophic levels, increases
+total primary production [@wang_biodiversity_2018]. The addition of predators has
+also cascading effects on both species variability and synchrony at lower
+trophic levels [@teng_dynamics_2004; @shanafelt_stability_2018].
+Overall, these theoretical studies show that the effects of species richness and
+network structure, such as connectance and average trophic level, are
+potentially conflicting or synergistic in such a way that they need to be
+addressed jointly.
+
+The gap in studies that consider jointly effects of diversity and food web
+structure on ecosystem functions can be explained by the challenges associated
+with manipulating both species richness and food web complexity in an
+experimental context [e.g. @sander_ecological_2017] and by the fact that describing
+trophic interactions between species is highly labour intensive. These
+challenges are even more acute for the study of the stability of ecosystem
+properties, which additionally requires time-series data and longer-term
+analyses. In this context, recent developments to predict species trophic
+interactions [@gravel_inferring_2013], combined with observational long-term surveys
+of ecological communities, can offer an opportunity to investigate the links
+between diversity, food web structure and the stability of total community
+biomass in natural settings.
+
+Such approach based on data from natural communities can in addition give
+insights on the effects of environmental variables on ecosystem properties and
+their stability. Environment affects organism performance directly, and thereby,
+species abundances, total biomass [@grace_integrative_2016; @woods_testing_2020]
+and its temporal stability [@de_boeck_patterns_2017; @hansen_climate_2013;
+@bluthgen_land_2016; @oliver_heterogeneous_2010; @franssen_annual_2011;
+@friedpetersen_drivers_2020]. For example, larger ecosystem might increase the
+number of available resources and thus total biomass [@post_ecosystem_2000;
+@doi_resource_2009] while temperature affects ecosystem respiration and biomass
+distribution [@yvondurocher_warming_2011; @schwarz_warming_2017]. Environment also
+directly affect species richness and food web structure. For instance, larger
+ecosystems host food webs with higher diversity and trophic levels
+[@mchugh_dual_2010] while temperature can affect food web diversity and
+structure in contrasted ways depending on the ecosystem studied
+[@ogorman_unexpected_2017; @gauzens_biodiversity_2020]. When analyzing data
+from natural communities, the relationships among species richness, total
+biomass and its temporal stability might also arise from effects of the
+environment on both diversity and ecosystem functions
+[@loreau_biodiversity_2001; @he_global_2013; @grace_integrative_2016].
 @li_relationship_2018 have notably shown that climate moisture has a positive

### 2020-12-07 manuscript/bef_stability/manuscript.Rmd
Discussion reviewed according to Elisa

@@
 
-Overall, its study is unique by its level of integration, from environmental
+Overall, this study is unique by its level of integration, from environmental
 effects to total biomass and stability, going through species richness and
-network structure. It is the first direct assessment of a possible joint effect
+foodweb structure. It is the first direct assessment of a possible joint effect
 of species richness and network structure on both total biomass and its temporal
@@
 that the effect of species richness and mean trophic level on total biomass and
-its temporal stability were not independant as species richness had a negative
+its temporal stability were not independent as species richness had a negative
 effect on mean trophic level. Furthermore, we found that connectance had no
@@
 
-We found that species richness increased total biomass as found in salt marshes,
+We found that species richness increased total biomass as already found in salt marshes,
 grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
@@
 probability of getting high biomass species with higher species richness
-[@loreau_biodiversity_2001].
+[@loreau_biodiversity_2001]. Our result is also in agreement with a recent
+study predicting a positive relationship between animal diversity and total
+consumer biomass in size-structured food web models [@schneider_animal_2016].
 
@@
 species richness. Overall, it contrasts with experimental studies in grasslands
-[@tilman_biodiversity_2006; @valencia_synchrony_2020]; mesocosms (Pennekamp et al. 2018), in 
-natural communities of butterflies [@olivier_urbanization_2020] or even in lotic
-fish communities [@franssen_annual_2011] where positive relationships were found
-between temporal stability and species richness. However, other studies found an
-opposite relationship in natural grassland [@yang_effects_2011] and a marginal
-one in natural forests [@declerck_species_2006].
+[@tilman_biodiversity_2006; @valencia_synchrony_2020], mesocosms
+[@pennekamp_biodiversity_2018] with studies on natural communities such as
+butterflies  or lotic fishes [@olivier_urbanization_2020; @franssen_annual_2011;
+@houlalan__2018], where positive relationships were found between temporal
+stability and species richness. However, some other studies also found a
+negative relationship, for instance in natural grasslands [@yang_effects_2011]
+or in natural forests as a marginal trend [@declerck_species_2006].
 
@@
 $\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
-positive effect of species richness on $\overline{CV_{sp}}$ was reported in
-experimental grasslands and natural bird communities [@tilman_biodiversity_2006;
-@olivier_urbanization_2020], negative and neutral relationships have been found
-in butterfly and bat communities. Our results contrast with a previous
-meta-analysis which concludes that species richness had a positive effect on
-population stability in multi-trophic aquatic microcosms
-[@jiang_different_2009]. In foodwebs, the relationship between temporal
+studies focusing on single-trophic communities have reported mixed effects of
+species richness on $\overline{CV_{sp}}$, with destabilising effects of species
+richness at population level in grasslands [@jiang_different_2009;
+@gross__2014], a previous meta-analysis suggested that species richness had
+often a positive effect on population stability in multi-trophic communities
+[@jiang_different_2009].
+In foodwebs, the relationship between temporal
 stability of populations and species richness depends on interaction strength
 and its distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
-@brose_allometric_2006], high interaction strength inducing a negative
-relationship. Therefore, it is possible that our results are due to a high
-degree of omnivory in foodwebs, which combined with strong trophic interactions
-lead to more fluctuations in population biomass.
+@brose_allometric_2006 DOWNING à la place de BROSE?], high interaction strength inducing a negative
+relationship whereas the presence of weak interactions at high species richness is
+expected to promote stability. Therefore, it is possible that our results are
+due to a high degree of omnivory in foodwebs, which combined with strong trophic
+interactions lead to more fluctuations in population biomass.
 
@@
 
-## Average trophic level increased total biomass and its temporal stability
-
-The average trophic level was positively linked to total biomass.
-Experimental and theoretical work suggested that a higher trophic level can be the
-result of a stronger top-down effect, meaning higher predation rates and biomass
-fluxes to higher trophic levels [@kratina_warming_2012], hence leading to an
-increase in total biomass with trophic length. Furthermore,
-@wang_biodiversity_2016 have shown that total nutrient uptake might increase
-with the length of trophic chains and so results in higher total biomass.
-
+## Average trophic level increased total biomass and its temporal stability while connectance had no effect
+
+The average trophic level was positively linked to total biomass.  Furthermore,
+@wang_biodiversity_2018 have shown that total nutrient uptake might increase
+with the length of trophic chains and so results in higher total biomass.  While
+the predictions of @wang_biodiversity_2018 were restricted to food chains, and
+thus might not hold in more complex food webs with omnivorous species, our
+results are in agreement with their model predictions and highlight the
+importance of food chain length as a determinant of total biomass in foodwebs.
+In addition, mean trophic level had a positive effect on biomass stability by
+its negative effect on $\overline{CV_{sp}}$, thereby increasing average species
+stability. It might result from a higher stability of higher trophic level as
+predicted by food chain models in the presence of strong top-down control
+[@barbier_pyramids_2019; @shanafelt_stability_2018]. An alternative
+explanation is that higher mean trophic level leads to a stronger top-down
+control and resource complementarity and thus reduce biomass fluctuations in
+lower trophic levels [REF?].
 In contrast, connectance had no effect on total biomass. One might have expected
 that an increase in connectance may translate in a higher total nutrient uptake
-and so results in higher total biomass in the fish compartment. A reason for
+and so results in higher total biomass in the fish compartment. 
+However, a few studies suggest that greater connectance should decrease
+complementarity in resource use between species, which is expected to lead to
+lower total biomass [@thebault_food-web_2003; @poisot_trophic_2013].
+A reason for
 such an absence of an effect might be explained by the fact that our data lack
@@
 
-Mean trophic level had a positive effect on biomass stability by its negative
-effect on $\overline{CV_{sp}}$, thereby increasing average species stability. It
-might result from a higher stability of higher trophic level as predicted by
-food chain models in the presence of strong top-down control
-[@barbier_pyramids_2019; @shanafelt_stability_2018]. But it
-might not hold when considering omnivorous species
-[@wang_biodiversity_2016]. An alternative explanation is that higher mean
-trophic level leads to a stronger top-down control and resource complementarity
-and thus reduce biomass fluctuations in lower trophic levels
-[@rooney_structural_2006].
-
-We found that connectance had no effect on temporal stability. This result
-contradicts previous precedent theoretical studies on the relationship between
-stability and network structure [@angelis_stability_1975; @may_will_1972;
+Regarding temporal stability, our results
+contradicts numerous previous theoretical studies on the relationship between
+connectance and stability [e.g., @angelis_stability_1975; @may_will_1972;
 @thebault_stability_2010; but see @neutel_reconciling_2007], although they
 considered different stability concepts and metrics [@arnoldi_resilience_2016].
-However, our measure of connectance does not include the variability of the
-lower compartments of the foodweb and further research should examine the effect
-of connectance on temporal stability in more complete empirical foodwebs.
+The lack of effect of connectance on the temporal stability of total biomass
+might be related to the fact that our measure of connectance does not take into
+account the distribution of interaction strengths in the food webs. Indeed, food
+web connectance is expected to have different consequences on the temporal
+stability of total biomass depending on the strength of trophic interactions
+[@thebault_trophic_2005]. However, our measure of connectance does not fully
+account for the whole foodweb structure, and further research should examine the
+effects of connectance on total biomass and its temporal stability in more
+complete empirical foodwebs.
 
@@
 [@mccann_reevaluating_1997]. How both strengths and the relative contribution of
-synchrony and population variaribility to overall stability vary between
+synchrony and population variability to overall stability vary between
 foodwebs and single trophic communities is still an open question.
@@
 We found that the total effect of environmental drivers on total biomass and its
-stability was indirect and of the same magnitude order than the effect of
+stability was mainly indirect and of the same magnitude order than the effect of
 species richness and average trophic level, highlighting that environmental
-changes may result in signicant ecosystem responses, through alteration of
+changes may result in significant ecosystem responses, through alteration of
 both species richness and network structure.
 
-Consistent with research showing that foodwebs in wider streams support more
-species and biomass [@allan_stream_2007], we found that the PCA axis related to
-stream size had a positive effect on total
-biomass through a positive effect on mean trophic level. Greater ecosystem size
-might provide a greater diversity of resources through habitat heterogeneity,
-and so higher species richness and total biomass by surface unit, through
-resource complementarity. Greater diversity of resources can also maintain
-more biomass at high trophic level [@post_ecosystem_2000; @doi_resource_2009].
-Furthermore, the positive effect of the PCA axis related to temperature on total
-biomass was of the magnitude of effects of network structure and species
-richness, in line with the mounting body of work reporting important effects of
-temperature on the structure and biomass of aquatic system [e.g.
-@dossena_warming_2012; @edeline_ecological_2013; @emmrich_geographical_2014;
-@hattab_forecasting_2016; @woods_testing_2020]. Contrasting with previous studies in experimental
-plant communities [@grace_integrative_2016], aquatic mesocosms [@yvondurocher_warming_2011; @dossena_warming_2012] and marine fish communities [@maureaud_biodiversityecosystem_2019]
-, we found that environmental drivers overall affect total biomass indirectly
-rather than directly [@woods_testing_2020].
+Contrasting with previous studies in experimental plant communities
+[@grace_integrative_2016], aquatic mesocosms [@yvondurocher_warming_2011;
+@dossena_warming_2012] and marine fish communities
+[@maureaud_biodiversityecosystem_2019], we found that environmental drivers
+overall affect total biomass indirectly rather than directly
+[@woods_testing_2020]. First, consistent with research showing that foodwebs in
+wider streams support more species and biomass [@allan_stream_2007], we found
+that the PCA axis related to stream size had a positive effect on total biomass
+through a positive effect on mean trophic level and species richness. Greater
+ecosystem size might provide a greater diversity of resources through habitat
+heterogeneity, and so higher species richness and total biomass by surface unit,
+through resource complementarity. Greater diversity of resources can also
+maintain more biomass at high trophic level [@post_ecosystem_2000;
+@doi_resource_2009].  Second, the positive effect of the PCA axis related to
+temperature on total biomass was of the magnitude of the effects of network
+structure and species richness, in line with the mounting body of work reporting
+important effects of temperature on the structure and biomass of aquatic systems
+[e.g.  @dossena_warming_2012; @edeline_ecological_2013;
+@emmrich_geographical_2014; @hattab_forecasting_2016; @woods_testing_2020].  We
+found that streams with higher average temperature supported higher diversity as
+well as higher average trophic level and total biomass, which is in agreement
+with recent findings on streams where the positive effects of temperature were
+related to larger nutrient supply [@ogorman_unexpected_2017].
+
+While the PCA axis related with stream size had only a very weak effect on the
+temporal stability of total biomass, the PCA axis related to temperature had a
+clear negative effect on the temporal stability through a direct destabilizing
+effect on populations and through indirect effects. Temperature can have both
+stabilizing and destabilizing effects in resource-consumer models depending on
+the temperature optima of species growth rates and consumption rates and on how
+nutrient supply varies with temperature (Uszko et al. 2017). In our case, the
+observed increased variability of populations might also relate with factors
+covarying with temperature such as the average Biological Organic Demand which
+is linked to enrichment.
 

### 2020-12-14 manuscript/bef_stability/appendixB.Rmd
Last edits before submission

--- 2020-11-17 manuscript/bef_stability/appendixB.Rmd
@@
 ---
-title: Appendix of Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
+title: Appendix B of Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
 author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
@@
 the small streams (depth < 0.7m across the entire width), the complete protocol
-is used. It consists in placing anodes every X meters across the width of the
-river. The fishermen made from one to three row
+is used. It consists in placing anodes across the width of the
+stream. The fishermen made from one to three row
 of fishing. We kept only the first row for analysis to homogenize the sampling
@@
 types of partial protocols takes place: partial over bank and partial by points.
-The former is continuous while the latter is discrete. Furthermore, in partial
-by point protocol the channel can be sampled as well. We kept only the partial
-by point fish sampling which all the sampling point were done over the bank to
-homogenize the sampling. Then, we merged partial over bank and partial over
-point protocols. Some sampling stations had mix characteristics in which mix of
-partial and complete protocols were applied depending of the depth of the river
-at the time of sampling.
+The former is continuous while the latter is discrete. Furthermore, in the "partial
+by point" protocol, the channel can be sampled as well. We kept only the "partial
+by point" sampling in which all the sampling points were done over the bank to
+homogenize the sampling. Then, we merged partial over bank and partial by 
+point protocols. Some sampled stations had mixed characteristics in which mix of
+partial and complete protocols were applied depending of the depth of the stream 
+at the time of sampling. In this case, we kept only the protocol that was the
+most used.
 
@@
 heterogeneity in sampling time, only one sampling per year was retained if there
-was two in a given year, the one with with the most species and then individual
+was two in a given year, the one with the most species and then individual
 collected. Finally, most of the fish sampling occurred in September (Median:
 mid-August) and the median standard deviation of the sampling month was inferior
-to one (0.7) within station. Additionally, we removed sampling events, in a
-given station, which the sampled length along the stream was outside the median
+to one (0.7) within stations. Additionally, we removed sampling events, in a
+given station, in which the sampled length along the stream was outside the median
 length sampled more or less 30%. Finally, we standardized the biomass record
@@
 
-During the electric fishing, and before that fish body size are measured, they
-are regrouped by batches. Each batches contains one species but there can be
-several batches by species. Body size assessment are different according to the
-batches. There are four types of batches: N, I, S/L and G. The batches N and
-I contains the biggest individuals, there are normally less numerous and then
-the body size of the individuals of those batches is recorded. The batches S/L
+During the electric fishing, and before that fish body size are measured, the
+fishes are regrouped by batches. Each batch contains one species but there can
+be several batches by species. Body size assessment are different according to
+the batches. There are four types of batches: N, I, S/L and G. The batches N and
+I contains the biggest individuals which are normally less numerous. Then
+the body size of all the individuals in the N and I batches is recorded. The batches S/L
 contains fishes of intermediate sizes. Inside each S/L batches, the operator
-tries to make batches as homogeneous as possible in body size. Then, the body
-size of a subsample of X individuals are recorded. The G batches contain
-individuals of low body size, with care that body size is as homogeneous as
-possible in the batches. Then body size of the shortest and the longest
-individuals are recorded.
+tries to make batches as homogeneous as possible in terms of body size. Then, the body
+size of a subsample of at least 20 individuals is recorded. The G batches
+contain individuals of small body size, with care that body size is as
+homogeneous as possible in a given batches. Then body size of the shortest and the
+longest individuals are recorded.
 
@@
 
-```{r}
+```{r, cache = FALSE}
 body_size_caption <- paste0(
@@
   batches, S/L, the body size of a subsample of the individuals was recorded.
-  Finally, only the body size of the littlest and of the tallest individual was
+  Finally, only the body size of the smallest and of the largest individual were
   recorded in the G batches. ",
   "Then, (3) we inferred the body size distribution in the S/L and G batches by
-  assuming that it followed a normal distribution. The mean and the standard
+  assuming a normal distribution. The mean and the standard
   deviation were estimated with the measured subsample."
@@
 
-```{r p-body-size, fig.cap=body_size_caption}
+```{r p-body-size, cache = FALSE, fig.cap=body_size_caption}
 knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "length_inference.pdf"))
@@
 the fishes in the community. No inference were needed for the N and I batches
-because the body size of the individuals were recorded. The body size ($l$) of the
-fishes in the S/L and G were inferred under the assumption that its distribution
+because the body size of all individuals was recorded. The body size ($l$) of the
+fishes in the S/L and G was inferred under the assumption that its distribution
 followed a normal law ($l ~ N(\mu , \sigma)$).
@@
 We removed batches that did not satisfied the following conditions. First, we
-removed batches which the total number of individuals was not recorded. In lot
-"G", we removed batches were  $l_{min} \geq l_{max}$ or if at least one of the
+removed batches in which the total number of individuals was not recorded. In lot
+"G", we removed batches where $l_{min} \geq l_{max}$ or if at least one of the
 measurement was missing. Additionally, G batches were removed when number of
 individuals fell below five, as G batches normally contained more individuals.
-In the S/L lot, we removed batches were the number of individuals in the
+In the S/L lot, we removed batches in which the number of individuals in the
 recorded individuals fell below 10. In sum, those sanity check allowed to
@@
 species. In total, we removed `r nrow(removed_ind)` over 
-`r nrow(length_sem_analysis)` individuals and `r length(removed_sp)`.
+`r nrow(length_sem_analysis)` individuals and `r length(removed_sp)` species.
 
@@
 belong to the same species based on fecundation criteria.  We merged those
-morphotype species into one species. There was `r
-length(unique(names(sp_to_replace())))` to merge which belonged to `r
-length(unique(sp_to_replace()))` species.
+morphotype species into one species. There was 
+`r length(unique(names(sp_to_replace())))` species to merge which belonged to 
+`r length(unique(sp_to_replace()))` species.
 
@@
 
-Diet information were obtained from fishbase.org and literature (Appendix A, Table S2). The
+Diet information were obtained from fishbase.org and literature (Appendix a, Table S2). The
 diet information contained from two to three life stages by species, the life
 stages being defined by the body size of the fishes. Over the 57 fish species,
-only seven had a piscivorous life stage and only three had as strict piscivorous
-life stage. Fish species were largely omnivorous.
+only seven had a piscivorous life stage and only three had a strict piscivorous
+life stage. Fish species were then largely omnivorous.
 
@@
 interactions with the resource nodes of its life stage. Interactions between
-resource nodes were determined by literature. For example, phytobenthos fed on
-detritus, while zooplankton fed on zooplankton and phytoplankton. Fish-fish
 trophic interactions between a predator and a prey were determined by body size
@@
 @schneider_body_2012].  For a given trophic species, we first determined if its
-size class end up in a life stage containing piscivorous diet, i.e. if there was
-an overlap between them. We were more liberal for piscivory determination to not
-miss potential fish-fish trophic interactions which were the main interactions
+size class ends up in a life stage containing piscivorous diet, i.e. if there was
+an overlap between them. We were more liberal for piscivory determination to
+avoid 
+missing potential fish-fish trophic interactions which were the main interactions
 in our community. If the trophic species was piscivorous, we determined its prey
@@
 (hourly, daily and monthly for temperature, flow and BOD resp.). For each
-recording station, we applied a moving window averaging (more details in
-supplementary material) to get rid of seasonal effects. For temperature, the
-moving was performed on daily average temperature. Then we took the annual
-average of each year and each variable (i.e. one value by year and by station).
+recording station, we applied a moving window averaging to get rid of seasonal
+effects. For temperature, the moving was performed on daily average temperature.
+Then we took the annual average of each year and each variable (i.e. one value
+by year and by station).
 
@@
 be not related or a only a few. For those reason, we used stream spatial network
-methods to interpolate temperature, flow and BOD.
-
-We reconstructed the stream network and the connection between sites with the
+methods to interpolate water temperature, flow and BOD.
+
+We reconstructed the stream network and the connection between stations with the
 `openSTARS` R package [@kattwinkel_preparing_2020]. The reconstruction was done with a raster of digital
@@
 and the level of dataset splitting. We then merge some hydrographic basin to end
-up with four region of interpolation: West, East, South and North. (XXX ADD 
-basins merged)
+up with four region of interpolation: West, East, South and North.
 
@@
 were done with the `SSN` R package 
-[@isaak_applications_2014, @hoef_ssn:_2014].
+[@isaak_applications_2014; @hoef_ssn:_2014].
 
@@
 The performance of the interpolation was evaluated with leave one out
-cross-validation (already implemented in the SSN package). The value of the
+cross-validation (already implemented in the SSN package), i.e. the value of the
 interpolated variable of each station was predicted after removing it from the
@@
 
-The CV of biomass over can cover multiple dynamics, including increases,
+## Temporal series classification
+
+The CV of biomass over time can cover multiple dynamics, including increases,
 stable, decreases and a mix of them. Theoretically, however, the CV computed to
@@
 series shapes. The classification necessitates three steps. First, the time
-series are normalized (i.e. Substituting the mean and divide by the standard
+series are normalized (i.e. substituting the mean and divide by the standard
 deviation). The second step is to reduce the dimensionality of the time series
@@
 
+## PCA over environmental variables
+
 ```{r eig-plot}
@@
 
-```{r}
+```{r, cache = FALSE}
 prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
@@
   paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
-  "(A) Axis 1 was positively related to the river size, axis 2 was related to
-  average temperature and negatively related to the river slope and altitude.
-  (B) Axis 3 was negatively related to the CV of stream size.
-  Axis 4 was related to the CV of enrichment.
-  Finally, axis 5 was related to the CV of flow and average enrichment.")
-```
-
-```{r pca-rotated, fig.cap = pca_caption}
+  "(A) Axis 1 was positively related to the stream size, axis 2 was related to
+  the stream slope and altitude and negatively related to average water temperature and
+  BOD. (B) Eigenvalues distribution, we kept the first two axis for the data analysis. ",
+  "Please note that we took the inverse of the second axis in the data analysis,
+  to make the axis more easily interpretable, i.e. positively related de average
+  water temperature."
+
+  )
+```
+
+```{r pca-rotated, cache = FALSE, fig.cap = pca_caption}
 p1 <- my_pca_plot(xaxis = "RC1", yaxis = "RC2", ctb_thld = .4)
@@
 
-The five axis of the rotated PCA explained respectively
-`r paste0(prop_var_expl_pca, "%", collapse = ", ")` of the variance.
-Please see the main text for the interpretation of the axis.
-
 ```{r }
@@
     ),
-  transformation = c(rep("Log base 10", 2), "Log base 10", rep("No", 2), rep("Log base 10", 3)),
+  transformation = c("Log base 10", "Log base 10 and inversion", "Log base 10", rep("No", 2), rep("Log base 10", 3)),
   interpretation = c("linked to stream size",
-    "linked to average temperature",
+    "linked to average temperature and BOD",
     "Total species richness over the temporal series",
@@
 
-### SEM hypothesis
-
-We linked environmental variables both to community structure and stability
-components. Rooted in assembly theory, environment filters species that can
-establish in a community and thus affect community structure. (+ add specific
-hypothesis about physical and climate). (1) We hypothesized that enrichment
-(characterized by DBO) and mean annual temperature will increase species turnover
-[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
-decrease biomass stability directly without going by community structure. First,
-instability of habitat and environmental factors may in turn drive biomass
-instability [@hansen_climate_2013]. Secondly, average environmental conditions
-such as enrichment can increase directly CV by increasing species biomass
-fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
-to decrease stability through starvation resulting from high metabolic activity
-[@tabi_warming_2019].
-
 ---
-# Species richness to community attributes 
+#### SEM hypothesis
+#
+#We linked environmental variables both to community structure and stability
+#components. Rooted in assembly theory, environment filters species that can
+#establish in a community and thus affect community structure. (+ add specific
+#hypothesis about physical and climate). (1) We hypothesized that enrichment
+#(characterized by DBO) and mean annual temperature will increase species turnover
+#[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
+#decrease biomass stability directly without going by community structure. First,
+#instability of habitat and environmental factors may in turn drive biomass
+#instability [@hansen_climate_2013]. Secondly, average environmental conditions
+#such as enrichment can increase directly CV by increasing species biomass
+#fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
+#to decrease stability through starvation resulting from high metabolic activity
+#[@tabi_warming_2019].
+#
+#---
+## Species richness to community attributes 
+#---
+#
+#To reveal the mechanisms behind the relationship between species richness and
+#biomass stability, causal links were set from species richness to other
+#community attributes. In particular, species richness decreased connectance
+#following results from @thebault_stability_2010; @winemiller_must_1989. But
+#theoretically, some ecological networks can show the inverse relationship
+#[@winemiller_must_1989]. (6) We hypothesized also that species richness will
+#modulate average weighted trophic level because of food web assembly processes.
+#A community with more fish species can support higher trophic level. Finally, we
+#set up causal relationships from community attributes to stability components. 
+#
+#---
+##  Community attributes to stability
+#---
+#We hypothesized that (7) species richness decreased synchrony between species
+#[@loreau_species_2008] and increased $\overline{CV_{sp}}$
+#[@tilman_biodiversity_2006]. (8a) We expected that average trophic level had a
+#positive or negative relationship with synchrony, bottom-up effects should
+#result in positive whereas top-down in negative relationships. We expected a (8b)
+#negative relationship between average trophic level and $\overline{CV_{sp}}$ if
+#predators stabilised prey fluctuations or if the increasing part of
+#biomass in the predators decreased $\overline{CV_{sp}}$ because of their higher
+#body mass (if mean increase faster than variance). (9a) Connectance was expected
+#to decrease or increase $\overline{CV_{sp}}$ and (9b) synchrony because of top
+#down effects or bottom up effects.
 ---
-
-To reveal the mechanisms behind the relationship between species richness and
-biomass stability, causal links were set from species richness to other
-community attributes. In particular, species richness decreased connectance
-following results from @thebault_stability_2010; @winemiller_must_1989. But
-theoretically, some ecological networks can show the inverse relationship
-[@winemiller_must_1989]. (6) We hypothesized also that species richness will
-modulate average weighted trophic level because of food web assembly processes.
-A community with more fish species can support higher trophic level. Finally, we
-set up causal relationships from community attributes to stability components.
-
----
-#  Community attributes to stability
----
-We hypothesized that (7) species richness decreased synchrony between species
-[@loreau_species_2008] and increased $\overline{CV_{sp}}$
-[@tilman_biodiversity_2006]. (8a) We expected that average trophic level had a
-positive or negative relationship with synchrony, bottom-up effects should
-result in positive whereas top-down in negative relationships. We expected a (8b)
-negative relationship between average trophic level and $\overline{CV_{sp}}$ if
-predators stabilised prey fluctuations or if the increasing part of
-biomass in the predators decreased $\overline{CV_{sp}}$ because of their higher
-body mass (if mean increase faster than variance). (9a) Connectance was expected
-to decrease or increase $\overline{CV_{sp}}$ and (9b) synchrony because of top
-down effects or bottom up effects.
 
@@
 
-```{r sensitivity, message = FALSE, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
+```{r sensitivity, cache = TRUE, message = FALSE, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
 library(furrr)

### 2020-12-14 manuscript/bef_stability/manuscript.Rmd
Last edits before submission

@@
 
+- Running title: Foodweb structure, biomass and stability
+
 - Number of words:
-  - Abstract: 172
-  - Main text: 5383
-
-- Number of references: 87 
+  - Abstract: 151
+  - Main text: 5535
+
+- Number of references: 92
 - Number of figures: 2
@@
 
-Both biodiversity-ecosystem functioning (BEF) and foodweb complexity-stability
-relationships have received considerable attention during the last decades.
-Still, the BEF relationship remains rarely investigated in the context of food
-webs, especially in empirical studies explicitly considering foodweb structures.
-Foodweb stability-complexity relationship has been mainly the focus of
-theoretical studies with very little empirical testing. To fill this gap, we linked
-species richness, foodweb structure, annual biomass and its temporal
-stability using a standardized monitoring of fish communities in French streams
-running from 1995 to 2018. We inferred trophic interactions from
-individual body size and diet literature. We reveal that species richness and average
-trophic level had a positive relationship with annual biomass of fish
-communities while they had respectively a negative and positive effect on its
-temporal stability. We also found that the effects of stream size and
-temperature on annual biomass and stability are mediated by their effects on
-diversity and foodweb structure. Overall, our study opens fruitful perspectives
-on the link among species richness, network structure, community biomass and its
-temporal stability.
+Biodiversity-ecosystem functioning (BEF) and foodweb complexity-stability
+relationships are central to ecology. However, they remain largely untested in a
+foodweb context in natural settings. Here we study the links among
+environmental conditions, richness, foodweb structure, annual biomass and its
+temporal stability using a standardized monitoring of 99 stream fish communities
+spanning from 1995 to 2018. We first reveal that both richness and average
+trophic level are positively related to annual biomass, with effects of similar
+strength. Second, we show that network structure affects community stability,
+with a positive effect of mean trophic level, and contrary to general
+expectation, we find that richness destabilizes fish communities. Finally, we
+find that environmental conditions affect both biomass and its stability via
+effects on richness and network structure. Strikingly, effects on stability are
+mediated by changes in species stability rather than synchrony, which contrasts
+with results from single-trophic communities and might be characteristic of
+multi-trophic communities.
 
@@
 [@thebault_relationship_2006] and stability [@thebault_trophic_2005;
-@thebault_relationship_2006; @tilman_biodiversity_2006].
-Species richness has been shown to promote higher biomass production and  
-higher temporal stability of total biomass in a variety of ecosystems
-and taxa. 
-Indeed species richness generally increases primary productivity and
-total biomass in experimental plant communities [@tilman_productivity_1996;
-@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
-@grace_integrative_2016], but also in briophyte communities
-[@mulder_physical_2001], stream feeders, [@cardinale_species_2002] and aquatic
-bacterial consumers [@pennekamp_biodiversity_2018]. 
-In parallel, such positive relationship between
+@thebault_relationship_2006; @tilman_biodiversity_2006].  Species richness has
+been shown to promote higher biomass production and  higher temporal stability
+of total biomass in a variety of ecosystems and taxa.  Indeed species richness
+generally increases primary productivity and total biomass in experimental plant
+communities [@tilman_productivity_1996; @grace_integrative_2016;
+@hector_plant_1999; @tilman_biodiversity_2014; @grace_integrative_2016], but
+also in briophyte communities [@mulder_physical_2001], stream feeders,
+[@cardinale_species_2002] and aquatic bacterial consumers
+[@pennekamp_biodiversity_2018].  In parallel, such positive relationship between
 species richness and temporal stability of biomass has been reported in
@@
 settings, such as stream fish communities [@franssen_annual_2011], bird and
-butterfly communities [@olivier_urbanization_2020].
-Despite the diversity of
+butterfly communities [@olivier_urbanization_2020].  Despite the diversity of
 ecosystems and taxa studied, the relationship between diversity and ecosystem
-functioning in experimental and empirical studies remains mostly focused
-on single trophic levels, ignoring the effects of foodweb structure. 
-This gap is even more striking for the relationship between diversity and
-temporal stability of ecosystem functioning, in spite of long-standing interest
-for the links between food web complexity and stability in theoretical ecology
-[e.g. @may_will_1972; @dunne_network_2006; @neutel_reconciling_2007;
-@duffy_why_2009; @stouffer_compartmentalization_2011].
+functioning in experimental and empirical studies remains mostly focused on
+single trophic levels, ignoring the effects of foodweb structure.  This gap is
+even more striking for the relationship between diversity and temporal stability
+of ecosystem functioning, in spite of long-standing interest for the links
+between foodweb complexity and stability in theoretical ecology [e.g.
+@may_will_1972; @dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
+@stouffer_compartmentalization_2011].
 
 Overall, the evidence from theoretical models suggests that both species
-richness and foodweb structure should modulate ecosystem propertiestotal
-biomass and their stability of communities. Complementarity in the use of
+richness and foodweb structure should modulate ecosystem properties such as
+total biomass and its stability. Complementarity in the use of
 resources, a main mechanism previously highlighted in single-trophic studies, is
-important to understand the effects of species richness in food webs [@thebault_food-web_2003;
+important to understand the effects of species richness in foodwebs [@thebault_food-web_2003;
 @poisot_trophic_2013; @schneider_animal_2016], but in that case it also depends
-on food web connectance [@thebault_food-web_2003; @poisot_trophic_2013].
+on foodweb connectance [@thebault_food-web_2003; @poisot_trophic_2013].
 
 As classically found in studies considering a single trophic level,
-[@tilman_biodiversity_2006; @loreau_species_2008; olivier_urbanization_2020],
+[@tilman_biodiversity_2006; @loreau_species_2008; @olivier_urbanization_2020],
 asynchrony in species temporal variations is also explaining a significant part
-of the stabilizing effects of species richness on total biomass in food webs
+of the stabilizing effects of species richness on total biomass in foodwebs
 [@thebault_trophic_2005]. Indeed, a low synchrony in species fluctuations,
@@
 [@thebault_trophic_2005]. In addition, recent models revealed new mechanisms by
-which food web structure affects total ecosystem biomass and its temporal
-variability. In particular, the number of trophic levels in food webs, which is
+which foodweb structure affects total ecosystem biomass and its temporal
+variability. In particular, the number of trophic levels in foodwebs, which is
 associated with the presence of species at higher trophic levels, increases
@@
 
-The gap in studies that consider jointly effects of diversity and food web
+The gap in studies that consider jointly effects of diversity and foodweb
 structure on ecosystem functions can be explained by the challenges associated
-with manipulating both species richness and food web complexity in an
+with manipulating both species richness and foodweb complexity in an
 experimental context [e.g. @sander_ecological_2017] and by the fact that describing
@@
 of ecological communities, can offer an opportunity to investigate the links
-between diversity, food web structure and the stability of total community
+between diversity, foodweb structure and the stability of total community
 biomass in natural settings.
 
-Such approach based on data from natural communities can in addition give
+Such approach based on data from natural communities can, in addition, give
 insights on the effects of environmental variables on ecosystem properties and
@@
 species abundances, total biomass [@grace_integrative_2016; @woods_testing_2020]
-and its temporal stability [@de_boeck_patterns_2017; @hansen_climate_2013;
-@bluthgen_land_2016; @oliver_heterogeneous_2010; @franssen_annual_2011;
+and its temporal stability [@oliver_heterogeneous_2010; @franssen_annual_2011;
+@hansen_climate_2013; @bluthgen_land_2016; @de_boeck_patterns_2017;
 @friedpetersen_drivers_2020]. For example, larger ecosystem might increase the
@@
 @doi_resource_2009] while temperature affects ecosystem respiration and biomass
-distribution [@yvondurocher_warming_2011; @schwarz_warming_2017]. Environment also
-directly affect species richness and food web structure. For instance, larger
-ecosystems host food webs with higher diversity and trophic levels
-[@mchugh_dual_2010] while temperature can affect food web diversity and
-structure in contrasted ways depending on the ecosystem studied
-[@ogorman_unexpected_2017; @gauzens_biodiversity_2020]. When analyzing data
-from natural communities, the relationships among species richness, total
+distribution [@yvondurocher_warming_2011; @schwarz_warming_2017;
+@tabi_warming_2019]. Environment also directly affect species richness and
+foodweb structure. For instance, larger ecosystems host foodwebs with higher
+diversity and trophic levels [@mchugh_dual_2010] while temperature can affect
+foodweb diversity and structure in contrasted ways depending on the ecosystem
+studied [@ogorman_unexpected_2017; @gauzens_biodiversity_2020]. When analyzing
+data from natural communities, the relationships among species richness, total
 biomass and its temporal stability might also arise from effects of the
@@
 direct effect on total biomass, but also indirect through a positive effect on
-species richness. Accounting for environment also allow for an overall
+species richness. Accounting for environment also allows for an overall
 comparison of the strength of the effects of environment and community structure
@@
 constitute a good model to study the effects of network structure on total
-biomass and its temporal stability. Despite that fish trophic
-interactions are difficult to measure in natural conditions, a substantial body
-of literature supports that they can be inferred through body size and diet
-informations [@gravel_inferring_2013; @jennings_weak_2001;
-@brose_predator_2019]. Especially in stream communities, including fishes,
-@brose_predator_2019 found that the prediction of predator prey trophic
-interactions based on body size ratio was far better in stream ecosystems than
-in other aquatic and terrestrial ecosystems. Lastly, most of the
-diversity-biomass and diversity-stability relationships, have been assessed in
-terrestrial ecosystems while there is a evident need to test such relationships
-in a variety of ecosystem types.
-
-Our aim is to document the relationships among species richness, foodweb structure, 
-total biomass and its temporal stability in natural communities. To do so, we
-used the ONEMA dataset consisting in standardized sampling of fish communities
-in French streams [@edeline_ecological_2013]. We selected 99 sites that were sampled for more than 10
-years spanning on the 1995-2018 period. We inferred 1496 interaction networks,
-based on body size and diet. We question whether species richness, connectance
-and average trophic level increase, decrease or are not related to
-total biomass and its temporal stability. We further question whether the
-species richness, connectance, and average trophic level have antagonistic or
-mutual effect on total biomass and its temporal stability. Finally, we
-question if ecosystem size and average temperature increase total biomass and
-its temporal stability.
+biomass and its temporal stability. Despite that fish trophic interactions are
+difficult to measure in natural conditions, a substantial body of literature
+supports that they can be inferred through body size and diet informations
+[@jennings_weak_2001; @gravel_inferring_2013; @brose_predator_2019]. Especially
+in stream communities, including fishes, @brose_predator_2019 found that the
+prediction of predator-prey trophic interactions based on body size ratio was
+far better in stream ecosystems than in other aquatic and terrestrial
+ecosystems. Lastly, most of the diversity-biomass and diversity-stability
+relationships, have been assessed in terrestrial ecosystems while there is a
+evident need to test such relationships in a variety of ecosystem types.
+
+Our aim is to document the relationships among species richness, foodweb
+structure, total biomass and its temporal stability in natural communities. To
+do so, we used the ONEMA dataset consisting in a standardized sampling of fish
+communities in French streams [@edeline_ecological_2013]. We selected 99 sites
+that have been sampled for more than 10 years spanning on the 1995-2018 period. We
+inferred 1496 interaction networks, based on body size and diet. We question
+whether species richness, connectance and average trophic level increase,
+decrease or are unrelated to total biomass and its temporal stability. We
+further question whether the species richness, connectance, and average trophic
+level have antagonistic or mutual effect on total biomass and its temporal
+stability. Finally, we question if ecosystem size and average temperature
+increase total biomass and its temporal stability.
 
@@
 
-```{r}
+```{r, cache = FALSE}
 myload(qt_station, dir = mypath("data"))
@@
   and each
-  color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
+  color represents a species (S = 45). Resource nodes (7) are drawn in grey. ",
   "The species names corresponding to the three digit codes are found in Table
@@
   round(qt_station$bm_std_stab[2],
-    2), ". Point size are proportional to the biomass of the trophic species.")
-
-```
-
-```{r matmet, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
+    2), ". Point size is proportional to the biomass of the trophic species.")
+
+```
+
+```{r matmet, cache = FALSE, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
 library(knitr)
@@
 electric fishing. Two different standardized protocols were used for small and
-large streams (detailed in Supplementary material, part 1.1). For streams
+large streams (detailed in appendix B, part 1.1). For streams
 shallower than 0.7m across the entire width, the sampling took place over the
@@
 0.7m, the sampling was done over the bank by foot or by boat. The sampling
-season spanned from late spring to autumn. One sampling event correspond to a
+season spanned from late spring to autumn. One sampling event corresponds to a
 sampling a given year in a given sampling station. During sampling, all the
-fishes caught were identified. For each species, either the body size of all
-fish was measured, or a representative sample when the number of fish was high
-(Figure S1, supplementary information). The fishes were released at the end of
-the sampling. Additionally, the physical characteristics of the stream were 
+fishes caught were identified. The fishes were released at the end of
+the sampling. Additionally, the width and the depth of the stream were 
 recorded during sampling event as well as the sampling effort, quantified as the
@@
 characterize in natural communities, only stations with no temporal trends
-in total biomass were selected (detailed in supplementary methods). However, the
+in total biomass were selected (detailed in appendix B, part 2). However, the
 results were robust to the relaxation of this hypothesis (Figure S7). These
@@
 
-## Variable computation
+## Total biomass and its temporal stability
 
@@
 The body size of all fish individuals was not recorded when they were too
-numerous. The body size of the unmeasured individuals was inferred under the
-assumption that species body size followed a normal distribution whose mean and
-standard deviation were quantified from the recorded individuals of the sampling
-(See supplementary methods, Figure S1). The body mass of each individual was
-then estimated using an allometric law $B_i = 0.01 \times l_i^{3.03}$, $B$
-with the body mass in grams, $l$ the body size in millimeters, $i$ the
-individual and where the coefficients $0.01$ and $3.03$ comes from two
-meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006]. Species
-biomass and total biomass at each sampling event was then calculated by summing
-individual body masses. To account for the variation in sampling effort among
-sites, species biomass and total biomass have been related to the surface
-sampled, i.e. $gm^{-2}$. In the analysis, the total biomass of a
-station has been defined as the median of the total biomass across sampling
-events.
+numerous (Figure S1, appendix B, part 1.1). The body size of the unmeasured
+individuals was inferred under the assumption that species body size followed a
+normal distribution whose mean and standard deviation were quantified from the
+recorded individuals of the sampling (Figure S1, appendix B, part 1.2). The body
+mass of each individual was then estimated following the results of two
+meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006], using an
+allometric law $B_i = 0.01 \times l_i^{3.03}$, with $B$ the body mass in grams,
+$l$ the body size in millimeters, $i$ the individual and where the coefficients
+$0.01$ and $3.03$.  Species biomass and total biomass at each sampling event
+were then calculated by summing individual body masses. To account for the
+variation in sampling effort among sites, species biomass and total biomass were
+corrected by the surface sampled, and expressed in grams by square meter ($gm^{-2}$). In the analysis,
+the temporal average of the annual total biomass of a station has been defined
+as the median of the total biomass across sampling years.
 
@@
 station $i$, $\overline{CV_{sp, i}}$ the average coefficient of variation of
-species in the station $i$ weighted by the biomass of the species, $B_{k,i}$.
+species in the station $i$ weighted by the relative biomass of the species, $B_{k,i}$.
 Synchrony of the station $i$, $\phi_i$, is the ratio between the variance of
@@
 $$
-\phi_i = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sqrt{\sigma^2_{x_{k,i}}}})^2}
+\phi_i = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sqrt{\sigma^2_{x_{k,i}}}})^2} = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sigma_{x_{k,i}}})^2}
 $$
 
+## Species richness and foodweb structure
+
 ### Species richness
@@
 Species richness was computed as the total number of species present across
-sampling events 
-in a given station. As for biomass, we controlled species richness for sampling
-effort by dividing the total number of species by the total surface sampled in
-the given station. Species richness was then expressed in number of species per 
-square meter sampled.
+all the sampling events in a given station. As for biomass, we controlled
+species richness for sampling effort by dividing the total number of species by
+the total surface sampled in the given station. Species richness was then
+expressed in number of species per square meter sampled.
 
@@
 
-The trophic interaction network was inferred from body size and ontogenic diet shift
-following previous studies [@gravel_inferring_2013; @brose_predator_2019;
-@poisot_structure_2016]. The diet of stream fishes, as for many organisms, shifts
-throughout an individual's life, and thereby with body size. For example, alvins
-feed on plankton while adults may feed on algae and fishes, with bigger individuals
-eating bigger
-fishes. Each fish species was hence divided in nine body size classes, each
-corresponding to a trophic species (Figure S2). Additionally to the fish trophic
-species, we added seven resource nodes present in the ontogenic food diet database:
-detritus, biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and
-zoobenthos (grey nodes in Figure \@ref(fig:matmet) B, C & D). The fish trophic
-species and the resources constituted the 412 nodes of the metaweb, 45 fish
-species divided into nine body size classes plus seven resource nodes. The inference
-of trophic interactions was shown to be more accurate when considering body size
-classes, i.e. trophic species, than species [@jennings_weak_2001].
+The trophic interaction network was inferred from body size and ontogenic diet
+shift following previous studies [@edeline_ecological_2013;
+@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019]. The diet
+of stream fishes, as for many organisms, shifts throughout an individual's life,
+and thereby with body size. For example, alvins feed on plankton while adults
+may feed on algae and fishes, with bigger individuals eating bigger fishes. Each
+fish species was hence divided in nine body size classes, each corresponding to
+a trophic species (Figure S2). Additionally to the trophic species, we added
+seven resource nodes present in the ontogenic food diet database: detritus,
+biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos
+(grey nodes in Figure \@ref(fig:matmet) B, C & D). The trophic species and the
+resources constituted the 412 nodes of the metaweb, i.e. 45 fish species divided
+into nine body size classes plus seven resource nodes. The inference of trophic
+interactions was shown to be more accurate when considering body size classes,
+i.e. trophic species, than species [@jennings_weak_2001].
 
@@
 which a piscivorous species begin to feed on fishes. The ontogenic fish diet
-database was filled according to fishbase and literature (Table S2). Each
+database was filled according to fishbase and literature (appendix A, Table S2). Each
 fish species had two or three life stages which are delimited by a body size
@@
 
-For a piscivorous trophic species, the fish-fish
-trophic links was defined in two steps and based on the body size ratio between
-predators and prey. First of all, the predation window of a piscivorous trophic specie was
-defined as 3% to 45% of its midpoint [@mittelbach_ontogeny_1998;
-@claessen_impact_2002; @hart_handbook_2008]. Then, a trophic link was set
-between the piscivorous trophic species and every trophic species whose midpoint
-was included in the predation window (Figure S2). The fish-resource trophic
-links were set between the trophic species and the resources nodes according the
-food diet of their size class, for both the piscivorous and non piscivorous
-trophic species. Lastly, the trophic links among resource nodes were set
-according to the literature [@allan_stream_2007; @hart_handbook_2008].
+For a piscivorous trophic species, the fish-fish trophic links were defined in
+two steps and based on the body size ratio between predators and prey. First of
+all, the predation window of a piscivorous trophic specie was defined as 3% to
+45% of its midpoint [@mittelbach_ontogeny_1998; @claessen_impact_2002;
+@hart_handbook_2008]. Then, a trophic link was set between the piscivorous
+trophic species and every trophic species whose midpoint was included in the
+predation window (Figure S2). The fish-resource trophic links were set between
+the trophic species and the resources nodes according the food diet of their
+size class, for both the piscivorous and non piscivorous trophic species.
+Lastly, the trophic links among resource nodes were set according to the
+literature [@allan_stream_2007; @hart_handbook_2008].
 
@@
 (excluding resource nodes for which we had no biomass information), so
-$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and
+$\overline{T} = \sum_i^N{B_iT_i \times (\sum_i^N{B_i})^{-1}}$, with $T_i$ and
 $B_i$ being respectively the trophic level and the biomass of the node $i$. The
@@
 not collected on the same site as our fish sampling sites, we performed an
-interpolation with spatial stream networks [@isaak_applications_2014;
-@hoef_ssn:_2014]. The interpolation procedure is detailed in supplementary (part
-1.2).
+interpolation of the water temperature and flow based on the spatial stream
+network [@isaak_applications_2014; @hoef_ssn:_2014]. The interpolation procedure
+is detailed in appendix B (part 1.4).
 
@@
 for water temperature for which the record began in 2006. Then, we computed the
-average and CV values of for water temperature, flow, BOD, river width and
+average and CV values of water temperature, flow, Biological Oxygen Demand (BOD), river width and
 depth. As habitat and environmental variables are often collinear, a principal
@@
 the analysis the two first principal components based on the elbow method, on
-the eigen values distribution (Figure S4). The two first principal components
+the eigenvalues distribution (Figure S4). The two first principal components
 explained `r tot_var_expl_pca`% of the variance (Figure S4). A varimax axis rotation was
-performed to maximize the representation of the variables by the principal
+performed to maximize the representation of the environmental variables by the principal
 components [@kaiser_varimax_1958; @revelle_psych_2019]. The first axis
 represented a gradient from small to big streams, characterized by their width
-and depth, but also a gradient from stream close to far from the source. The
-second axis represented a gradient of increasing average water temperature and
-decreasing altitude and slope. Further description of the variables are provided
-in supplementary information (part 1.3).
+and depth, but also a gradient from stream close to far from the source. We
+reversed the values of the second axis, such as it represented a gradient of
+increasing average water temperature, DBO and decreasing altitude and slope.
+Further description of the variables are provided in appendix B (part 1.4).
 
@@
 
-Structural Equation Modeling enables us to assess multivariate relationships
+Structural Equation Modeling enables to assess multivariate relationships
 between variables. It is a promising way to go beyond bivariate relationships
-and to investigate complex relationships, direct and
-indirect, between variables [@grace_structural_2008; @grace_causal_2014;
-@lefcheck_piecewisesem_2016; @grace_integrative_2016]. The structural equation
-model explaining the annual total biomass allowed the environment
-to affect directly species richness and network structure, as well as annual total
-biomass (Figure \@ref(fig:sem-plot) A). We assumed that both species richness
-and network structure directly affect total biomass (Figure \@ref(fig:sem-plot)
-A) and that species richness affected foodweb structure
-[@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010].
+and to investigate complex relationships, direct and indirect, between variables
+[@grace_structural_2008; @grace_causal_2014; @lefcheck_piecewisesem_2016;
+@grace_integrative_2016]. We defined a structural equation model explaining the
+average annual total biomass as a function of the two synthetic environmental
+variables, species richness and foodweb structure as measured by connectance and
+average trophic level [@maureaud_biodiversityecosystem_2019;
+@woods_testing_2020]. We assumed that both species richness and network
+structure directly affect total biomass (Figure
+\@ref(fig:sem-plot) A)
+and that species richness affected foodweb structure [@winemiller_must_1989;
+@dunne_network_2006; @thebault_stability_2010].
 
@@
 
-The structural equation models were based on Gaussian linear models, all variables
+The structural equation models were based on Gaussian linear models. All variables
 except the connectance and average trophic level
 were logged to fulfill model assumptions (see residual plots and data
-transformation in supplementary informations, Figure S5 and S6, Table S5). We set the seven
+transformation in Figure S5 and S6, Table S5). We set the seven
 hydrographic basins as a random effect on the intercept of the linear models to
@@
 [@pinheiro_nlme_2020; @lefcheck_piecewisesem_2016]. The code used for the
-analysis and the manuscript are accessible on github. The analysis were
+analysis and the manuscript are accessible on github (alaindanet/fishcom). The analyses were
 performed with R version 3.6.3 [@r_core_team_r_2020].
@@
 
-#ctrl <- lmeControl(opt='optim')
+#ctrl <- lmeControl(opt='optim' relative)
 ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
@@
 
-```{r}
+```{r, cache = FALSE}
 sem_caption <- paste0(
@@
   "Results of the Structural Equation Models for
-  (B) the determinants of the median of annual total biomass and (D) its temporal stability. Red and green
+  (B) the median of annual total biomass and (D) its temporal stability. Red and black
   arrows represent respectively negative and positive path coefficients. The
@@
   Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
-  second axis of the PCA performed on environmental variables (cf methods)."
+  second axis of the PCA performed on environmental variables (see methods)."
 )
@@
 rich_on_tlvl <- get_clean_sem_coef(sem = bm_sem_coef, resp = "t_lvl", pred = "log_rich_tot_std")
+rich_on_ct <- get_clean_sem_coef(sem = bm_sem_coef, resp = "ct", pred = "log_rich_tot_std")
 tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
@@
 The structural equation models explained a large part of the variation
-of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
-.45$, $.47$, $.49$ and $.38$) but less so for mean trophic level ($R^2 =
-.18$, Figure \@ref(fig:sem-plot) B and D). We found that species richness had a
+of species richness, connectance, synchrony, $\overline{CV_{sp}}$ and total
+biomass (resp. $R^2 = .43$, $.38$, $.46$, $.47$ and $.32$) but less so for mean
+trophic level ($R^2 =
+.11$, Figure \@ref(fig:sem-plot) B and D). We found that species richness had a
 significant negative effect on mean trophic level ($r_\delta = 
-`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_stab$total`$, Figure
+`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_ct`$, Figure
 \@ref(fig:sem-plot) B and D), meaning that a part of the effects of species richness went 
@@
 $r_\delta = `r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) B, Table
-\@ref(tab:indir-sem)),
-while connectance had no direct effect on total biomass (Figure
-\@ref(fig:sem-plot) B).
-
-The two PCA axis capturing environmental variables had no significant direct effects on total biomass
-, but indirect (Table \@ref(tab:indir-sem)). The first axis, PCA1,
-related to the stream size was positively linked to total biomass ($r_\delta = 
-`r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
+\@ref(tab:indir-sem)), while connectance had no direct effect on total biomass
+(Figure \@ref(fig:sem-plot) B).
+
+The two PCA axes capturing environmental variables had no significant direct
+effects on total biomass, but indirect (Table \@ref(tab:indir-sem)). The first
+axis, PCA1, related to the stream size was positively linked to total biomass
+($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
 through both species richness and mean trophic level ($r_\delta = 
@@
 \@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
-`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The effect
-of PCA2 on total biomass was of the same magnitude than the effects on species
-richness and mean trophic level.
+`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The total effect
+of PCA1 and PCA2 on total biomass was of the same magnitude than the total effects of species
+richness on total biomass.
 
@@
 PCA2 had an indirect positive effect on temporal stability through a
-direct positive effect on mean trophic level ($r_\delta = `r
-env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)). However, PCA2
+direct positive effect on mean trophic level ($r_\delta = 
+`r env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)). However, PCA2
 had a negative effect on temporal stability through a direct positive effect on 
@@
 Table \@ref(tab:indir-sem)). This was also true for the PCA1, related to stream
-size, but effects were weaker than for PCA2.
-
-```{r indir-stab}
-caption_sem <- paste0(
+size, with a resulting very slight positive effect of PCA1 on temporal stability
+($r_\delta = `r env_on_stab$total["log_RC1"]`$, Table \@ref(tab:indir-sem)).
+
+```{r, cache = FALSE}
+cap_sem <- paste0(
   "Direct, indirect and total effects of environment, species richness,
@@
   and its temporal stability. Indirect effects are computed by multiplying the
-  path coefficients from the variable predictor to the response variable, here
-  biomass stability. Indirect effects are considered as one step from the target
-  variable. For exemple, the indirect effect of species richness on
+  path coefficients from the variable predictor to the response variable.
+  Indirect effects are considered as one step from the target variable. For
+  exemple, the indirect effect of species richness on
   biomass stability via its effect on CVsp is $-0.62$. Only the
@@
   into account the direct effect of species richness as well as the effect of
-  species richness through connectance and average trophic level.",
+  species richness through connectance and average trophic level. ",
  "NA values indicate that the corresponding paths do not exist in the
- specified Structural Equation Model (SEM)."
-)
+ specified Structural Equation Model (SEM). ", "NS: statistically non-significant."
+)
+```
+
+```{r indir-stab, cache = FALSE}
 
@@
 
+full_table %<>%
+  mutate(Direct = ifelse(Direct == 0, "NS", Direct)) %>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)
+
 library(kableExtra)
@@
   label = paste0("indir-sem"),
-  caption = caption_sem
+  caption = cap_sem
   ) %>%
@@
 
-Overall, this study is unique by its level of integration, from environmental
-effects to total biomass and stability, going through species richness and
+This study is unique by its level of integration, from environmental
+effects to total biomass and its stability, going through species richness and
 foodweb structure. It is the first direct assessment of a possible joint effect
@@
 effect on mean trophic level. Furthermore, we found that connectance had no
-significant effect on both total biomass and its temporal stability. Finally, we
-found that the magnitude of the effects of average temperature and altitude was
-equal or superior to the effects of species richness and mean trophic level.
+significant effect on both total biomass and its temporal stability. The results
+shows that temporal stability was mediated by changes in species variability 
+rather than synchrony. Finally, we found that the magnitude of the effects of
+average temperature and altitude was equal or superior to the effects of species
+richness and mean trophic level.
 
@@
 
-We found that species richness increased total biomass as already found in salt marshes,
-grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
+We found that species richness increased total biomass as already found in salt
+marshes, grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
 @wu_relationship_2015; @li_relationship_2018] as well as in streams
-[@woods_testing_2020]. The positive effect of species
-richness on total biomass might be due to resource use complementarity
-[@carey_determining_2011], which is held by niche differentiation
-[@loreau_biodiversity_1998; @loreau_partitioning_2001] or to the higher
-probability of getting high biomass species with higher species richness
-[@loreau_biodiversity_2001]. Our result is also in agreement with a recent
-study predicting a positive relationship between animal diversity and total
-consumer biomass in size-structured food web models [@schneider_animal_2016].
+[@woods_testing_2020]. The positive effect of species richness on total biomass
+might be due to resource use complementarity [@carey_determining_2011], which is
+held by niche differentiation [@loreau_biodiversity_1998;
+@loreau_partitioning_2001] or to the higher probability of getting high biomass
+species with higher species richness [@loreau_biodiversity_2001]. Our result is
+also in agreement with a recent study predicting a positive relationship between
+animal diversity and total consumer biomass in size-structured foodweb models
+[@schneider_animal_2016].
 
@@
 butterflies  or lotic fishes [@olivier_urbanization_2020; @franssen_annual_2011;
-@houlalan__2018], where positive relationships were found between temporal
+@houlahan_priority_2017], where positive relationships were found between temporal
 stability and species richness. However, some other studies also found a
@@
 settings. Species richness can reduce synchrony when (i) a given increase in species
-richness leads to a decrease of population sizes which increases the impacts of
-demographic stochasticity, when (ii) species have different
+richness raises demographic stochasticity by decreasing population
+sizes, or when (ii) species have different
 responses to environmental variation [@loreau_species_2008].
@@
 richness at population level in grasslands [@jiang_different_2009;
-@gross__2014], a previous meta-analysis suggested that species richness had
+@gross_species_2014], a previous meta-analysis suggested that species richness had
 often a positive effect on population stability in multi-trophic communities
 [@jiang_different_2009].
-In foodwebs, the relationship between temporal
+In foodwebs, theoretical models predict that the relationship between temporal
 stability of populations and species richness depends on interaction strength
 and its distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
-@brose_allometric_2006 DOWNING à la place de BROSE?], high interaction strength inducing a negative
+@downing_temporal_2020], high interaction strength inducing a negative
 relationship whereas the presence of weak interactions at high species richness is
 expected to promote stability. Therefore, it is possible that our results are
-due to a high degree of omnivory in foodwebs, which combined with strong trophic
+due to a high degree of omnivory in foodwebs which combined with strong trophic
 interactions lead to more fluctuations in population biomass.
@@
 the predictions of @wang_biodiversity_2018 were restricted to food chains, and
-thus might not hold in more complex food webs with omnivorous species, our
+thus might not hold in more complex foodwebs with omnivorous species, our
 results are in agreement with their model predictions and highlight the
@@
 predicted by food chain models in the presence of strong top-down control
-[@barbier_pyramids_2019; @shanafelt_stability_2018]. An alternative
-explanation is that higher mean trophic level leads to a stronger top-down
-control and resource complementarity and thus reduce biomass fluctuations in
-lower trophic levels [REF?].
+[@shanafelt_stability_2018; @barbier_pyramids_2019]. An alternative
+explanation is that higher mean trophic level leads complexify biomass pathways
+through the foodwebs, which might reduce biomass fluctuations in lower trophic
+levels [@mccann_diversitystability_2000].
+
 In contrast, connectance had no effect on total biomass. One might have expected
@@
 and so results in higher total biomass in the fish compartment. 
-However, a few studies suggest that greater connectance should decrease
-complementarity in resource use between species, which is expected to lead to
+However, some studies suggest that a greater connectance should decrease
+complementarity in resource use between species, which is expected to
 lower total biomass [@thebault_food-web_2003; @poisot_trophic_2013].
-A reason for
-such an absence of an effect might be explained by the fact that our data lack
-information about the lower compartments of the community, i.e., the primary
-producers, zooplankton and zoobenthos.
+A reason for such an absence of an effect might be explained by the fact that
+our data lack information about the lower compartments of the community, i.e.
+the primary producers, zooplankton and zoobenthos.
 
 Regarding temporal stability, our results
-contradicts numerous previous theoretical studies on the relationship between
+contrast with numerous previous theoretical studies on the relationship between
 connectance and stability [e.g., @angelis_stability_1975; @may_will_1972;
@@
 might be related to the fact that our measure of connectance does not take into
-account the distribution of interaction strengths in the food webs. Indeed, food
-web connectance is expected to have different consequences on the temporal
+account the distribution of interaction strengths in the foodwebs. Indeed,
+foodweb connectance is expected to have different consequences on the temporal
 stability of total biomass depending on the strength of trophic interactions
@@
 complete empirical foodwebs.
+
+One limitation of our study is indeed the use of inferred networks, i.e. not
+observed interactions, and the lack of of information on the other compartments
+of the foodweb (e.g. primary producers, decomposers, the benthic part of the
+foodweb). However, this approach is a promising way to explore how the
+architecture of ecological networks vary along environmental gradients across
+time. It constitutes an interesting complement to the real assessment of
+ecological interactions. The use of inferred networks also allow to extract most
+of the information contained from already available long term datasets.
 
@@
 
-## Environment had an high effect on total biomass and its temporal stability
+## Environment had an strong effect on total biomass and its temporal stability
 
@@
 
-Contrasting with previous studies in experimental plant communities
+Contrasting with previous studies on experimental plant communities
 [@grace_integrative_2016], aquatic mesocosms [@yvondurocher_warming_2011;
@@
 stabilizing and destabilizing effects in resource-consumer models depending on
-the temperature optima of species growth rates and consumption rates and on how
-nutrient supply varies with temperature (Uszko et al. 2017). In our case, the
-observed increased variability of populations might also relate with factors
-covarying with temperature such as the average Biological Organic Demand which
-is linked to enrichment.
-
-Interestingly, the two PCA axis related to environmental conditions had indirect
+the thermal niche of the species and on how nutrient supply varies with
+temperature [@uszko_effects_2017]. In our case, the observed increased
+variability of populations might also relate with ecosystem enrichment
+[@ogorman_unexpected_2017] because average Biological Oxygen Demand covaries
+with temperature in our study. It has been suggested that enrichment can increase CV by
+increasing species biomass fluctuations while higher temperature might decrease
+decrease stability through starvation resulting from high metabolic activity
+[@tabi_warming_2019].
+
+Interestingly, the two PCA axes related to environmental conditions had indirect
 effects on stability through two conflicting pathways, either stabilising, via
@@
 
-# Conclusion and perspectives
-
-While theoretical ecology has focused on the effects of network structure on
-stability, empirical ecology has focused on species richness but often did not
-consider network structure. Furthermore, both fields have largely used
-different stability metrics. Our work is hence contributing to bridging the gap
-between theoretical and empirical ecology.
-
-Our study extends the assessment of the effect of species richness on total
-annual biomass and its temporal stability in natural settings to the case of
-foodwebs, while including network structure. Species richness had a direct
-positive effect on total biomass and a negative effect on biomass stability.
-Mean trophic level had a positive effect on both total biomass and its temporal
-stability. Furthermore, we found that species richness had antagonistic effects
-on total biomass, through its effect on mean trophic level. Our study thus
-highlights the importance of considering both species richness, network
-structure and their dependence, though the mechanisms remain to be elucidated.
-Finally, we found that environmental gradient related to temperature and
-ecosystem size have antagonistic effects on biomass and its temporal stability,
-positive through mean trophic level and negative through species richness.
-Further research is needed to find the mechanisms behind those pathways, and
-crucial in the context of global change.
-
-One limitation of our study is the use of inferred networks, i.e. not
-observed interactions, and the lack of information about the foodwebs outside
-fishes. But this approach is a promising way to explore how the architecture of
-ecological networks vary along environmental gradients across time. It
-constitutes an interesting complement to the real assessment of ecological
-interactions. The use of inferred networks also allow to maximise the
-information contained from already available long term datasets.
-
-We look forward to seeing our findings and their interpretation tested by future
-experimental and theoretical studies, allowing to unravel the ecological
-mechanisms driving the complex relationships among environment, the structure of
-ecological networks and ecosystem properties such as productivity and temporal
-stability.
+# Conclusion
+
+Our work contributes to bridging the gap between theoretical, experimental and
+empirical findings on the functioning and stability of communities. Our study
+extends the assessment of the effect of species richness on total biomass and
+its temporal stability to the case of food-webs in natural settings and
+highlights the need to consider species richness, network structure and their
+dependence to understand both functioning and stability of communities. Further,
+we found that the effects of environmental gradient related to temperature and
+ecosystem size are largely mediated by their impact on richness and average
+trophic level. Finally, our results highlight species variability as key in
+transmitting effects of richness, network structure and environmental gradients
+on community stability. This contrast with previous results found in single
+trophic communities, mostly plants, that mainly focus on synchrony and, although
+further confirmation are needed, might be characteristic of animal and/or
+multi-trophic communities.
 

### 2020-12-17 manuscript/bef_stability/manuscript.Rmd
Decrease number of words lower than 4980

@@
 abundance of a species is compensated by the increase of an other. However,
-higher connectance can in some cases reverse the positive effects of species
+higher connectance can reverse the positive effects of species
 richness on temporal stability of total biomass, by leading to a negative
 relationship between species richness and species temporal variability
-[@thebault_trophic_2005]. In addition, recent models revealed new mechanisms by
-which foodweb structure affects total ecosystem biomass and its temporal
-variability. In particular, the number of trophic levels in foodwebs, which is
-associated with the presence of species at higher trophic levels, increases
-total primary production [@wang_biodiversity_2018]. The addition of predators has
-also cascading effects on both species variability and synchrony at lower
-trophic levels [@teng_dynamics_2004; @shanafelt_stability_2018].
-Overall, these theoretical studies show that the effects of species richness and
-network structure, such as connectance and average trophic level, are
-potentially conflicting or synergistic in such a way that they need to be
-addressed jointly.
+[@thebault_trophic_2005]. In addition, the presence of species at higher trophic
+levels increases total primary production [@wang_biodiversity_2018]. The
+addition of predators has also cascading effects on both species variability and
+synchrony at lower trophic levels [@teng_dynamics_2004;
+@shanafelt_stability_2018]. Overall, these theoretical studies show that the
+effects of species richness and network structure, such as connectance and
+average trophic level, are potentially conflicting or synergistic in such a way
+that they need to be addressed jointly.
 
@@
 direct effect on total biomass, but also indirect through a positive effect on
-species richness. Accounting for environment also allows for an overall
-comparison of the strength of the effects of environment and community structure
-on total biomass and its stability.
+species richness.
 
@@
 
-```{r matmet, cache = FALSE, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
-library(knitr)
-include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"))
-```
-
 ```{r}
@@
 electric fishing. Two different standardized protocols were used for small and
-large streams (detailed in appendix B, part 1.1). For streams
-shallower than 0.7m across the entire width, the sampling took place over the
-whole width of the streams and was done by foot whereas in streams deeper than
-0.7m, the sampling was done over the bank by foot or by boat. The sampling
-season spanned from late spring to autumn. One sampling event corresponds to a
-sampling a given year in a given sampling station. During sampling, all the
-fishes caught were identified. The fishes were released at the end of
-the sampling. Additionally, the width and the depth of the stream were 
-recorded during sampling event as well as the sampling effort, quantified as the
-surface sampled (range `r range_surface[1]`-`r range_surface[2]` square metres).
-
-The stations where the stream was of intermediate size could be sampled
-alternatively with one of the two sampling protocols. In this case, we
-kept only the most frequently used sampling protocol. Then, we selected the
-stations that had been sampled ten years or more. There was low heterogeneity of
-the sampling month within stations, with the median sampled month being
-mid-August while the median of the standard deviation of the sampled month
-within station was $0.7$. As the concept of community variability referred to
-variability around an equilibrium, which is rarely observed or difficult to
-characterize in natural communities, only stations with no temporal trends
-in total biomass were selected (detailed in appendix B, part 2). However, the
-results were robust to the relaxation of this hypothesis (Figure S7). These
-selection steps resulted in 99 stations distributed over seven hydrographic
-basins (Figure \@ref(fig:matmet) A).
+large streams (detailed in appendix B, part 1.1). The stations where the stream
+was of intermediate size could be sampled alternatively with one of the two
+sampling protocols. In this case, we kept only the most frequently used sampling
+protocol. The sampling season spanned from late spring to autumn. There was low
+heterogeneity of the sampling month within stations, with the median sampled
+month being mid-August while the median of the standard deviation of the sampled
+month within station was $0.7$.
+
+We selected the stations that had been sampled ten years or more. As the concept
+of community variability referred to variability around an equilibrium, which is
+rarely observed or difficult to characterize in natural communities, only
+stations with no temporal trends in total biomass were selected (detailed in
+appendix B, part 2). However, the results were robust to the relaxation of this
+hypothesis (Fig. S7). These selection steps resulted in 99 stations distributed
+over seven hydrographic basins (Fig. \@ref(fig:matmet) A).
 
@@
 The body size of all fish individuals was not recorded when they were too
-numerous (Figure S1, appendix B, part 1.1). The body size of the unmeasured
+numerous (Fig. S1, appendix B, part 1.1). The body size of the unmeasured
 individuals was inferred under the assumption that species body size followed a
-normal distribution whose mean and standard deviation were quantified from the
-recorded individuals of the sampling (Figure S1, appendix B, part 1.2). The body
-mass of each individual was then estimated following the results of two
-meta-analyses on fishes [@lleonart_removing_2000; @froese_cube_2006], using an
-allometric law $B_i = 0.01 \times l_i^{3.03}$, with $B$ the body mass in grams,
-$l$ the body size in millimeters, $i$ the individual and where the coefficients
-$0.01$ and $3.03$.  Species biomass and total biomass at each sampling event
-were then calculated by summing individual body masses. To account for the
-variation in sampling effort among sites, species biomass and total biomass were
-corrected by the surface sampled, and expressed in grams by square meter ($gm^{-2}$). In the analysis,
-the temporal average of the annual total biomass of a station has been defined
-as the median of the total biomass across sampling years.
+normal distribution (Fig. S1, appendix B, part 1.2). The body mass of each
+individual was then estimated following the results of two meta-analyses on
+fishes [@lleonart_removing_2000; @froese_cube_2006], using an allometric law
+$B_i = 0.01 \times l_i^{3.03}$, with $B$ the body mass in grams, $l$ the body
+size in millimeters and $i$ the individual. Species biomass and total biomass at
+each sampling event were then calculated by summing individual body masses. To
+account for the variation in sampling effort among sites, species biomass and
+total biomass were corrected by the surface sampled (range `r range_surface[1]`-
+`r range_surface[2]` square metres), and expressed in grams by square meter
+($gm^{-2}$). In the analysis, the total biomass of a site has been defined as
+the median of the total biomass across sampling years.
 
@@
 
-Species richness was computed as the total number of species present across
-all the sampling events in a given station. As for biomass, we controlled
-species richness for sampling effort by dividing the total number of species by
-the total surface sampled in the given station. Species richness was then
-expressed in number of species per square meter sampled.
+Species richness in a given station has been defined as the total number of species present across
+all the sampling events. We controlled species richness for sampling effort by
+dividing the total number of species by the total surface sampled in the given
+station. Species richness was then expressed in number of species per square
+meter sampled.
 
@@
 We determined the network structure in two steps: (1) build a metaweb describing the
-trophic interactions between all trophic species and the resources (Figure
+trophic interactions between all trophic species and the resources (Fig.
 \@ref(fig:matmet) B), then (2) determine network of a given community by
 extracting the metaweb according to the trophic species present at a given
-site and sampling event (Figure \@ref(fig:matmet) C and D).
+site and sampling event (Fig. \@ref(fig:matmet) C and D).
 
@@
 fish species was hence divided in nine body size classes, each corresponding to
-a trophic species (Figure S2). Additionally to the trophic species, we added
+a trophic species (Fig. S2). Additionally to the trophic species, we added
 seven resource nodes present in the ontogenic food diet database: detritus,
 biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos
-(grey nodes in Figure \@ref(fig:matmet) B, C & D). The trophic species and the
+(grey nodes in Fig. \@ref(fig:matmet) B, C & D). The trophic species and the
 resources constituted the 412 nodes of the metaweb, i.e. 45 fish species divided
@@
 fish species had two or three life stages which are delimited by a body size
-range (Figure S2). The life stage of a fish trophic species was determined with
-the center of its body size range, hereafter midpoint (Figure S2).
+range (Fig. S2). The life stage of a fish trophic species was determined with
+the center of its body size range, hereafter midpoint (Fig. S2).
 
@@
 trophic species and every trophic species whose midpoint was included in the
-predation window (Figure S2). The fish-resource trophic links were set between
+predation window (Fig. S2). The fish-resource trophic links were set between
 the trophic species and the resources nodes according the food diet of their
@@
 the analysis the two first principal components based on the elbow method, on
-the eigenvalues distribution (Figure S4). The two first principal components
-explained `r tot_var_expl_pca`% of the variance (Figure S4). A varimax axis rotation was
+the eigenvalues distribution (Fig. S4). The two first principal components
+explained `r tot_var_expl_pca`% of the variance (Fig. S4). A varimax axis rotation was
 performed to maximize the representation of the environmental variables by the principal
@@
 @woods_testing_2020]. We assumed that both species richness and network
-structure directly affect total biomass (Figure
+structure directly affect total biomass (Fig.
 \@ref(fig:sem-plot) A)
@@
 
-We used the same model structure for temporal stability of biomass (Figure
+We used the same model structure for temporal stability of biomass (Fig.
 \@ref(fig:sem-plot) C). Instead of the annual total biomass, we modelled the
 synchrony and population variability which in turn determined the temporal
-stability of biomass. The structural equation models used for annual total
-biomass and its temporal stability contained respectively 4 and 6 response
-variables, 35 and 26 direct paths.
+stability of biomass.
 
@@
 were logged to fulfill model assumptions (see residual plots and data
-transformation in Figure S5 and S6, Table S5). We set the seven
+transformation in Fig. S5 and S6, Table S5). We set the seven
 hydrographic basins as a random effect on the intercept of the linear models to
@@
 )
+```
+
+```{r get-bm-sem-single-effect}
+bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)
+
+rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_rich_tot_std")
+rich_on_tlvl <- get_clean_sem_coef(sem = bm_sem_coef, resp = "t_lvl", pred = "log_rich_tot_std")
+rich_on_ct <- get_clean_sem_coef(sem = bm_sem_coef, resp = "ct", pred = "log_rich_tot_std")
+tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
+ct_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "ct")
+RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC1")
+RC2_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC2")
+```
+
+```{r get-bm-tot-effect-env}
+bm_all_params <- get_coefficient_piecewisesem(sem = bm_sem_rich, p_val_thl = NULL)
+
+# effect of env on bm 
+env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05,
+  type = "std")
+# rich on bm 
+rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
+  p_val_thl = 0.05, type = "std")
+# direct
+ct_on_bm_trick <- list(direct = c(ct = ct_on_bm), total = c(ct = ct_on_bm))
+tlvl_on_bm_trick <- list(direct = c(t_lvl = tlvl_on_bm), total = c(t_lvl = tlvl_on_bm))
+
+tmp_bm_indir_table <- map(list(env_on_bm, rich_on_bm, ct_on_bm_trick,
+    tlvl_on_bm_trick),
+  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
+  ) %>%
+bind_rows()
+```
+
+```{r}
+stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
+# effect of env on stab
+env_on_stab <- get_env_on_stab(fit = stab_all_params, p_val_thl = 0.05,
+  type = "std")
+rich_on_stab <- get_rich_on_stab(fit = stab_all_params,
+  p_val_thl = 0.05, type = "std")
+ct_on_stab <- get_ct_on_stab(fit = stab_all_params,
+  p_val_thl = 0.05, type = "std")
+tlvl_on_stab <- get_tlvl_on_stab(fit = stab_all_params,
+  p_val_thl = 0.05, type = "std")
+
+tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, ct_on_stab, tlvl_on_stab),
+  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
+  ) %>%
+bind_rows()
+```
+```{r get-sem-single-effect}
+stab_sem_coef <- filter(coef_stab_sem, P.Value < 0.05)
+
+sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_sync")
+cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_cv_sp")
+RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
+tlvl_on_cv_sp <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_cv_sp", pred = "t_lvl")
+```
+
+```{r get-sem-tot-effect-env}
+# effect of env on sync and cv_sp
+env_on_sync <- get_env_on_stab_comp(fit = stab_all_params,
+  p_val_thl = 0.05,
+  stab_comp = "log_sync", type = "std")
+env_on_cv_sp <- get_env_on_stab_comp(fit = stab_all_params,
+  p_val_thl = 0.05,
+  stab_comp = "log_cv_sp", type = "std")
+# env on stab via network 
+env_on_t_lvl <- get_env_on_com(fit = stab_all_params,
+  p_val_thl = 0.05,
+  com = "t_lvl", type = "std")
+env_on_ct <- get_env_on_com(fit = stab_all_params,
+  p_val_thl = 0.05,
+  com = "ct", type = "std")
+env_on_richness <- get_env_on_rich(fit = stab_all_params,
+  p_val_thl = 0.05, type = "std")
+```
+
+# Results
+
+The structural equation models explained a large part of the variation
+of species richness, connectance, synchrony, $\overline{CV_{sp}}$ and total
+biomass (resp. $R^2 = .43$, $.38$, $.46$, $.47$ and $.32$) but less so for mean
+trophic level ($R^2 =
+.11$, Fig. \@ref(fig:sem-plot) B and D). We found that species richness had a
+significant negative effect on mean trophic level ($r_\delta = 
+`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_ct`$, Fig.
+\@ref(fig:sem-plot) B and D), meaning that a part of the effects of species richness went 
+through network structure.
+
+## Species richness and average trophic level are positively correlated with total biomass
+
+```{r get-sem-tot-effect-rich}
+rich_on_sync <- get_rich_on_stab_comp(fit = stab_all_params,
+  p_val_thl = 0.05,
+  stab_comp = "log_sync", type = "std")
+rich_on_cv_sp <- get_rich_on_stab_comp(fit = stab_all_params,
+  p_val_thl = 0.05,
+  stab_comp = "log_cv_sp", type = "std")
+```
+
+Species richness and mean trophic level had a significant positive direct effect
+on total biomass ($r_\delta = `r rich_on_bm$direct`$ and 
+$r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-plot) B, Table
+\@ref(tab:indir-sem)), while connectance had no direct effect on total biomass
+(Fig. \@ref(fig:sem-plot) B).
+
+The two PCA axes capturing environmental variables had no significant direct
+effects on total biomass, but indirect (Table \@ref(tab:indir-sem)). The first
+axis, PCA1, related to the stream size was positively linked to total biomass
+($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
+through both species richness and mean trophic level ($r_\delta = 
+`r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_tlvl["log_RC1"]`$
+resp., Table \@ref(tab:indir-sem)). The second axis, PCA2, related to the average
+annual temperature and inversely to altitude of the sites was positively related
+to total biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
+\@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
+`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The total effect
+of PCA1 and PCA2 on total biomass was of the same magnitude than the total effects of species
+richness on total biomass.
+
+## Temporal stability of annual biomass
+
+By its effects on synchrony and $\overline{CV_{sp}}$, species richness had a
+negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
+Table \@ref(tab:indir-sem)). This effect resulted from two opposite effects. On
+the one hand, species richness had a direct negative effect on synchrony
+($r_\delta = `r rich_on_sync$direct`$), thereby
+increasing stability ($r_\delta = `r rich_on_stab$via_sync`$). On the other
+hand, species richness had a positive direct effect on $\overline{CV_{sp}}$
+($r_\delta = `r rich_on_cv_sp$direct`$),
+thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
+\@ref(tab:indir-sem)). The negative effect of $\overline{CV_{sp}}$ on temporal
+stability was twice higher than the negative effect of synchrony (resp.
+$r_\delta = `r cv_sp_on_stab`$ and $r_\delta = `r sync_on_stab`$, Fig.
+\@ref(fig:sem-plot) D).
+
+The total effect of mean trophic level on temporal stability of biomass was of
+the same magnitude than the one of species richness (resp.
+$`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
+\@ref(tab:indir-sem)).
+The mean trophic level had only a direct negative effect on
+$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
+Fig. \@ref(fig:sem-plot) D) and thereby had a total positive
+effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$,
+Table \@ref(tab:indir-sem)). Connectance had no significant direct effect on either
+$\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
+(Fig. \@ref(fig:sem-plot) D, Table \@ref(tab:indir-sem)).
+
+The total effect of PCA2, related to average annual temperature and inversely to
+altitude, on temporal stability was of higher magnitude than the effects of
+species richness and mean trophic level (Table
+\@ref(tab:indir-sem)).
+The PCA2 had a total negative effect on temporal stability, meaning that higher
+temperature results in lower stability
+($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
+PCA2 had an indirect positive effect on temporal stability through a
+direct positive effect on mean trophic level ($r_\delta = 
+`r env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)). However, PCA2
+had a negative effect on temporal stability through a direct positive effect on 
+$\overline{CV_{sp}}$ and species richness (resp.  $r_\delta = 
+`r env_on_cv_sp$direct["log_RC2"]`$ and $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$,
+Table \@ref(tab:indir-sem)). This was also true for the PCA1, related to stream
+size, with a resulting very slight positive effect of PCA1 on temporal stability
+($r_\delta = `r env_on_stab$total["log_RC1"]`$, Table \@ref(tab:indir-sem)).
+
+```{r, cache = FALSE}
+cap_sem <- paste0(
+  "Direct, indirect and total effects of environment, species richness,
+  connectance and mean trophic level on total biomass
+  and its temporal stability. Indirect effects are computed by multiplying the
+  path coefficients from the variable predictor to the response variable.
+  Indirect effects are considered as one step from the target variable. For
+  exemple, the indirect effect of species richness on
+  biomass stability via its effect on CVsp is $-0.62$. Only the
+  significant direct effects were retained for the computation of indirect
+  effects. ", "As an example, the indirect effect via species richness takes
+  into account the direct effect of species richness as well as the effect of
+  species richness through connectance and average trophic level. ",
+ "NA values indicate that the corresponding paths do not exist in the
+ specified Structural Equation Model (SEM). ", "NS: statistically non-significant."
+)
+```
+
+```{r indir-stab, cache = FALSE}
+
+full_table <- bind_rows(
+  tmp_bm_indir_table,
+  tmp_stab_indir_table
+) %>%
+mutate(`SEM type` = c(rep("Total annual biomass", 5), rep("Temporal Stability of annual biomass", 5))) %>%
+select(`SEM type`, variable, direct, via_richness, via_ct, via_tlvl, via_cv_sp, via_sync, total) %>%
+format_table() %>%
+select(`SEM type`, everything())
+
+full_table %<>%
+  mutate(Direct = ifelse(Direct == 0, "NS", Direct)) %>%
+  mutate_if(is.numeric, format, digits = 2, nsmall = 2)
+
+library(kableExtra)
+mytable <- kable(full_table,
+  format = "latex",
+  booktabs = T,
+  label = paste0("indir-sem"),
+  caption = cap_sem
+  ) %>%
+kable_styling(latex_options =c("scale_down")) %>%
+add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
+column_spec(1:2, width = "3cm") %>%
+collapse_rows(columns = 1, valign = "top")
+#write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
+```
+
+# Discussion
+
+---
+#This study is unique by its level of integration, from environmental
+#effects to total biomass and its stability, going through species richness and
+#foodweb structure. It is the first direct assessment of a possible joint effect
+#of species richness and network structure on both total biomass and its temporal
+#stability. We found that species richness and mean trophic level had a positive
+#effect on total biomass. In contrast, species richness had a negative effect on
+#temporal stability whereas mean trophic level covaried positively. We also found
+#that the effect of species richness and mean trophic level on total biomass and
+#its temporal stability were not independent as species richness had a negative
+#effect on mean trophic level. Furthermore, we found that connectance had no
+#significant effect on both total biomass and its temporal stability. The results
+#shows that temporal stability was mediated by changes in species variability 
+#rather than synchrony. Finally, we found that the magnitude of the effects of
+#average temperature and altitude was equal or superior to the effects of species
+#richness and mean trophic level. 
+---
+
+## Species richness increased total biomass but decreased its temporal stability
+
+We found that species richness increased total biomass as already found in salt
+marshes, grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
+@wu_relationship_2015; @li_relationship_2018] as well as in streams
+[@woods_testing_2020]. The positive effect of species richness on total biomass
+might be due to resource use complementarity [@carey_determining_2011], which is
+held by niche differentiation [@loreau_biodiversity_1998;
+@loreau_partitioning_2001] or to the higher probability of getting high biomass
+species with higher species richness [@loreau_biodiversity_2001]. Our result is
+also in agreement with a recent study predicting a positive relationship between
+animal diversity and total consumer biomass in size-structured foodweb models
+[@schneider_animal_2016].
+
+Surprisingly, we found a negative relationship between temporal stability and
+species richness. Overall, it contrasts with experimental studies in grasslands
+[@tilman_biodiversity_2006; @valencia_synchrony_2020], mesocosms
+[@pennekamp_biodiversity_2018] with studies on natural communities such as
+butterflies  or lotic fishes [@olivier_urbanization_2020; @franssen_annual_2011;
+@houlahan_priority_2017], where positive relationships were found between temporal
+stability and species richness. However, some other studies also found a
+negative relationship, for instance in natural grasslands [@yang_effects_2011]
+or in natural forests as a marginal trend [@declerck_species_2006].
+
+The first step to identify the mechanisms behind those contrasting patterns is to
+look at the effects of species richness on synchrony and $\overline{CV_{sp}}$.
+As most studies on experimental grasslands
+[@isbell_biodiversity_2009; @roscher_identifying_2011] and natural communities
+of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
+@olivier_urbanization_2020], we found that species richness decreases synchrony,
+thereby increasing stability [but see @declerck_species_2006;
+@valencia_synchrony_2020]. Our study thus extends the evidence that species
+richness decreases synchrony to the case of trophic communities in natural
+settings. Species richness can reduce synchrony when (i) a given increase in species
+richness raises demographic stochasticity by decreasing population
+sizes, or when (ii) species have different responses to environmental variation
+[@loreau_species_2008].
+
+The positive effect of species richness on
+$\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
+studies focusing on single-trophic communities have reported mixed effects of
+species richness on $\overline{CV_{sp}}$, with destabilising effects of species
+richness at population level in grasslands [@jiang_different_2009;
+@gross_species_2014], a previous meta-analysis suggested that species richness had
+often a positive effect on population stability in multi-trophic communities
+[@jiang_different_2009].
+In foodwebs, theoretical models predict that the relationship between temporal
+stability of populations and species richness depends on interaction strength
+and its distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
+@downing_temporal_2020], high interaction strength inducing a negative
+relationship whereas the presence of weak interactions at high species richness is
+expected to promote stability. Therefore, it is possible that our results are
+due to a high degree of omnivory in foodwebs which combined with strong trophic
+interactions lead to more fluctuations in population biomass.
+
+---
+#@thibaut_understanding_2013 proposed that a
+#strongly uneven biomass distribution across populations and that the biomass
+#variance of population increases much faster than its mean can generate a
+#positive effect of species richness on population ($\overline{CV_{sp}}$)
+#stability.
+---
+
+## Average trophic level increased total biomass and its temporal stability while connectance had no effect
+
+The average trophic level was positively linked to total biomass. Furthermore,
+@wang_biodiversity_2018 have shown that total nutrient uptake might increase
+with the length of trophic chains and so results in higher total biomass.  While
+the predictions of @wang_biodiversity_2018 were restricted to food chains, and
+thus might not hold in more complex foodwebs with omnivorous species, our
+results are in agreement with their model predictions and highlight the
+importance of food chain length as a determinant of total biomass in foodwebs.
+In addition, mean trophic level had a positive effect on biomass stability by
+its negative effect on $\overline{CV_{sp}}$, thereby increasing average species
+stability. It might result from a higher stability of higher trophic level as
+predicted by food chain models in the presence of strong top-down control
+[@shanafelt_stability_2018; @barbier_pyramids_2019]. An alternative
+explanation is that higher mean trophic level leads complexify biomass pathways
+through the foodwebs, which might reduce biomass fluctuations in lower trophic
+levels [@mccann_diversitystability_2000].
+
+In contrast, connectance had no effect on total biomass. One might have expected
+that an increase in connectance may translate in a higher total nutrient uptake
+and so results in higher total biomass in the fish compartment. 
+However, some studies suggest that a greater connectance should decrease
+complementarity in resource use between species, which is expected to
+lower total biomass [@thebault_food-web_2003; @poisot_trophic_2013].
+A reason for such an absence of an effect might be explained by the fact that
+our data lack information about the lower compartments of the community, i.e.
+the primary producers, zooplankton and zoobenthos.
+
+Regarding temporal stability, our results
+contrast with numerous previous theoretical studies on the relationship between
+connectance and stability [e.g., @angelis_stability_1975; @may_will_1972;
+@thebault_stability_2010; but see @neutel_reconciling_2007], although they
+considered different stability concepts and metrics [@arnoldi_resilience_2016].
+The lack of effect of connectance on the temporal stability of total biomass
+might be related to the fact that our measure of connectance does not take into
+account the distribution of interaction strengths in the foodwebs. Indeed,
+foodweb connectance is expected to have different consequences on the temporal
+stability of total biomass depending on the strength of trophic interactions
+[@thebault_trophic_2005]. However, our measure of connectance does not fully
+account for the whole foodweb structure, and further research should examine the
+effects of connectance on total biomass and its temporal stability in more
+complete empirical foodwebs.
+
+One limitation of our study is indeed the use of inferred networks, i.e. not
+observed interactions, and the lack of of information on the other compartments
+of the foodweb (e.g. primary producers, decomposers, the benthic part of the
+foodweb). However, this approach is a promising way to explore how the
+architecture of ecological networks vary along environmental gradients across
+time. It constitutes an interesting complement to the real assessment of
+ecological interactions. The use of inferred networks also allow to extract most
+of the information contained from already available long term datasets.
+
+## Population stability was the main driver of temporal stability
+
+In contrast with previous studies, we found that the average population
+variability ($\overline{CV_{sp}}$) had a stronger negative effect on biomass
+stability than synchrony [@tilman_biodiversity_2006;
+@olivier_urbanization_2020]. It explains why we observe a negative effect of
+species richness on temporal stability of biomass. The lower effect of synchrony
+might be explained by the presence of generalist predators in stream
+communities, that raise synchrony between prey species that share the
+same predator and thus reduces compensatory
+population dynamics [@raimondo_interspecific_2004]. Alternatively, it is
+possible that, in aquatic foodwebs, the occurrence of large oscillatory dynamics
+ leads to a higher contribution of population
+variability rather than synchrony to community stability
+[@mccann_reevaluating_1997]. How both strengths and the relative contribution of
+synchrony and population variability to overall stability vary between
+foodwebs and single trophic communities is still an open question.
+
+---
+#Rough average synchrony in Théophile study: exp(-0.75) = .47 or exp(-0.6) = .54
+#This study: sync avg = .69
+---
+
+## Environment had an strong effect on total biomass and its temporal stability
+
+We found that the total effect of environmental drivers on total biomass and its
+stability was mainly indirect and of the same magnitude order than the effect of
+species richness and average trophic level, highlighting that environmental
+changes may result in significant ecosystem responses, through alteration of
+both species richness and network structure.
+
+We found that environmental drivers overall affect total biomass indirectly
+[@woods_testing_2020] rather than directly , contrasting with previous studies
+[@yvondurocher_warming_2011; @dossena_warming_2012; @grace_integrative_2016;
+@maureaud_biodiversityecosystem_2019]. First, consistent with research showing
+that foodwebs in wider streams support more species and biomass
+[@allan_stream_2007], we found that the PCA axis related to stream size had a
+positive effect on total biomass through a positive effect on mean trophic level
+and species richness. Greater ecosystem size might provide a greater diversity
+of resources through habitat heterogeneity, and so higher species richness and
+total biomass by surface unit, through resource complementarity. Greater
+diversity of resources can also maintain more biomass at high trophic level
+[@post_ecosystem_2000; @doi_resource_2009]. Second, the positive effect of the
+PCA axis related to temperature on total biomass was of the magnitude of the
+effects of network structure and species richness, in line with the mounting
+body of work reporting important effects of temperature on the structure and
+biomass of aquatic systems [e.g.  @dossena_warming_2012;
+@edeline_ecological_2013; @emmrich_geographical_2014; @hattab_forecasting_2016;
+@woods_testing_2020]. We found that warmer streams
+supported higher diversity as well as higher average trophic level and total
+biomass, which is in agreement with recent findings on streams where the
+positive effects of temperature were related to larger nutrient supply
+[@ogorman_unexpected_2017].
+
+While the PCA axis related with stream size had only a very weak effect on the
+temporal stability of total biomass, the PCA axis related to temperature had a
+negative effect on the temporal stability through a direct destabilizing
+effect on populations and through indirect effects. Temperature can have both
+stabilizing and destabilizing effects in resource-consumer models depending on
+the thermal niche of the species and on how nutrient supply varies with
+temperature [@uszko_effects_2017]. In our case, the observed increased
+variability of populations might also relate with ecosystem enrichment
+[@ogorman_unexpected_2017] because average Biological Oxygen Demand covaries
+with temperature in our study. Enrichment can increase CV by
+increasing species biomass fluctuations while higher temperature might decrease
+ stability through starvation resulting from high metabolic activity
+[@tabi_warming_2019].
+
+---
+#Interestingly, the two PCA axes related to environmental conditions had indirect
+#effects on stability through two conflicting pathways, either stabilising, via
+#network structure, or destabilising, via species richness. The first pathway
+#consists in a positive effect of temperature and stream size on mean
+#trophic level, in line with the idea that wider streams and warmer conditions
+#are favourable to mesotrophic predators [@allan_stream_2007;
+#@emmrich_geographical_2014], which in turn stabilises biomass fluctuations,
+#possibly due to increased top-down regulation. The second pathway consists in a
+#positive effect of temperature and stream size on species richness, which itself
+#has a destabilising effect. This result is interesting in that both
+#pathways had not been evidenced to jointly play, to the best of our knowledge.
+#Furthermore, it is unclear which pathway is dominating, and under which circumstances,
+#opening an interesting avenue for further investigations.
+---
+
+---
+## Final thoughts about empirical foodwebs
+
+#It was unexpected that the average population $\overline{CV_{sp}}$
+#had a stronger negative effect on biomass stability than synchrony
+#[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
+#negative effect of species on temporal stability of biomass. The lower effect of
+#synchrony can be explained by the  presence of generalist predators in stream
+#communities, which can raise synchrony between prey species which shares the
+#same predator [@raimondo_interspecific_2004]. Uneven population biomass within
+#communities also raise synchrony between species [@thibaut_understanding_2013].
+
+#As found in other studies, we found that species richness was negatively related
+#to mean trophic level and connectance [@winemiller_must_1989;
+#@dunne_network_2006; @thebault_stability_2010]. Species richness had thus a
+#consistent destabilising effect on temporal stability of biomass directly and
+#through average trophic level, but it has a direct positive effect on total annual
+#biomass directly but a negative one through the decrease of average trophic
+#level. It highlights the importance to consider several aspects of
+#network structure to order to improve our understanding of the drivers of
+#community structure and stability.
+---
+
+# Conclusion
+
+Our work contributes to bridging the gap between theoretical, experimental and
+empirical findings on the functioning and stability of communities. Our study
+extends the assessment of the effect of species richness on total biomass and
+its temporal stability to the case of food-webs in natural settings and
+highlights the need to consider species richness, network structure and their
+dependence to understand both functioning and stability of communities. Further,
+we found that the effects of environmental gradient related to temperature and
+ecosystem size are largely mediated by their impact on richness and average
+trophic level. Finally, our results highlight species variability as key in
+transmitting effects of richness, network structure and environmental gradients
+on community stability. This contrast with previous results found in single
+trophic communities, mostly plants, that mainly focus on synchrony and, although
+further confirmation are needed, might be characteristic of animal and/or
+multi-trophic communities.
+
+```{r}
+save.image(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
+```
+
+# References {-}
+
+<div id="refs"></div>
+
+\clearpage
+
+# Figures and Table {-}
+
+```{=latex}
+\input{table.tex}
+```
+
+```{r matmet, cache = FALSE, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
+library(knitr)
+include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"))
 ```
@@
 ```
-
-```{r get-bm-sem-single-effect}
-bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)
-
-rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_rich_tot_std")
-rich_on_tlvl <- get_clean_sem_coef(sem = bm_sem_coef, resp = "t_lvl", pred = "log_rich_tot_std")
-rich_on_ct <- get_clean_sem_coef(sem = bm_sem_coef, resp = "ct", pred = "log_rich_tot_std")
-tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
-ct_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "ct")
-RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC1")
-RC2_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC2")
-```
-
-```{r get-bm-tot-effect-env}
-bm_all_params <- get_coefficient_piecewisesem(sem = bm_sem_rich, p_val_thl = NULL)
-
-# effect of env on bm 
-env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05,
-  type = "std")
-# rich on bm 
-rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
-  p_val_thl = 0.05, type = "std")
-# direct
-ct_on_bm_trick <- list(direct = c(ct = ct_on_bm), total = c(ct = ct_on_bm))
-tlvl_on_bm_trick <- list(direct = c(t_lvl = tlvl_on_bm), total = c(t_lvl = tlvl_on_bm))
-
-tmp_bm_indir_table <- map(list(env_on_bm, rich_on_bm, ct_on_bm_trick,
-    tlvl_on_bm_trick),
-  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
-  ) %>%
-bind_rows()
-```
-
-```{r}
-stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
-# effect of env on stab
-env_on_stab <- get_env_on_stab(fit = stab_all_params, p_val_thl = 0.05,
-  type = "std")
-rich_on_stab <- get_rich_on_stab(fit = stab_all_params,
-  p_val_thl = 0.05, type = "std")
-ct_on_stab <- get_ct_on_stab(fit = stab_all_params,
-  p_val_thl = 0.05, type = "std")
-tlvl_on_stab <- get_tlvl_on_stab(fit = stab_all_params,
-  p_val_thl = 0.05, type = "std")
-
-tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, ct_on_stab, tlvl_on_stab),
-  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
-  ) %>%
-bind_rows()
-```
-```{r get-sem-single-effect}
-stab_sem_coef <- filter(coef_stab_sem, P.Value < 0.05)
-
-sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_sync")
-cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_cv_sp")
-RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
-tlvl_on_cv_sp <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_cv_sp", pred = "t_lvl")
-```
-
-```{r get-sem-tot-effect-env}
-# effect of env on sync and cv_sp
-env_on_sync <- get_env_on_stab_comp(fit = stab_all_params,
-  p_val_thl = 0.05,
-  stab_comp = "log_sync", type = "std")
-env_on_cv_sp <- get_env_on_stab_comp(fit = stab_all_params,
-  p_val_thl = 0.05,
-  stab_comp = "log_cv_sp", type = "std")
-# env on stab via network 
-env_on_t_lvl <- get_env_on_com(fit = stab_all_params,
-  p_val_thl = 0.05,
-  com = "t_lvl", type = "std")
-env_on_ct <- get_env_on_com(fit = stab_all_params,
-  p_val_thl = 0.05,
-  com = "ct", type = "std")
-env_on_richness <- get_env_on_rich(fit = stab_all_params,
-  p_val_thl = 0.05, type = "std")
-```
-
-# Results
-
-The structural equation models explained a large part of the variation
-of species richness, connectance, synchrony, $\overline{CV_{sp}}$ and total
-biomass (resp. $R^2 = .43$, $.38$, $.46$, $.47$ and $.32$) but less so for mean
-trophic level ($R^2 =
-.11$, Figure \@ref(fig:sem-plot) B and D). We found that species richness had a
-significant negative effect on mean trophic level ($r_\delta = 
-`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_ct`$, Figure
-\@ref(fig:sem-plot) B and D), meaning that a part of the effects of species richness went 
-through network structure.
-
-## Species richness and average trophic level are positively correlated with total biomass
-
-```{r get-sem-tot-effect-rich}
-rich_on_sync <- get_rich_on_stab_comp(fit = stab_all_params,
-  p_val_thl = 0.05,
-  stab_comp = "log_sync", type = "std")
-rich_on_cv_sp <- get_rich_on_stab_comp(fit = stab_all_params,
-  p_val_thl = 0.05,
-  stab_comp = "log_cv_sp", type = "std")
-```
-
-Species richness and mean trophic level had a significant positive direct effect
-on total biomass ($r_\delta = `r rich_on_bm$direct`$ and 
-$r_\delta = `r tlvl_on_bm`$ resp., Figure \@ref(fig:sem-plot) B, Table
-\@ref(tab:indir-sem)), while connectance had no direct effect on total biomass
-(Figure \@ref(fig:sem-plot) B).
-
-The two PCA axes capturing environmental variables had no significant direct
-effects on total biomass, but indirect (Table \@ref(tab:indir-sem)). The first
-axis, PCA1, related to the stream size was positively linked to total biomass
-($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
-through both species richness and mean trophic level ($r_\delta = 
-`r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_tlvl["log_RC1"]`$
-resp., Table \@ref(tab:indir-sem)). The second axis, PCA2, related to the average
-annual temperature and inversely to altitude of the sites was positively related
-to total biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
-\@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
-`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The total effect
-of PCA1 and PCA2 on total biomass was of the same magnitude than the total effects of species
-richness on total biomass.
-
-## Temporal stability of annual biomass
-
-By its effects on synchrony and $\overline{CV_{sp}}$, species richness had a
-negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
-Table \@ref(tab:indir-sem)). This effect resulted from two opposite effects. On
-the one hand, species richness had a direct negative effect on synchrony
-($r_\delta = `r rich_on_sync$direct`$), thereby
-increasing stability ($r_\delta = `r rich_on_stab$via_sync`$). On the other
-hand, species richness had a positive direct effect on $\overline{CV_{sp}}$
-($r_\delta = `r rich_on_cv_sp$direct`$),
-thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
-\@ref(tab:indir-sem)). The negative effect of $\overline{CV_{sp}}$ on temporal
-stability was twice higher than the negative effect of synchrony (resp.
-$r_\delta = `r cv_sp_on_stab`$ and $r_\delta = `r sync_on_stab`$, Figure
-\@ref(fig:sem-plot) D).
-
-The total effect of mean trophic level on temporal stability of biomass was of
-the same magnitude than the one of species richness (resp.
-$`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
-\@ref(tab:indir-sem)).
-The mean trophic level had only a direct negative effect on
-$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
-Figure \@ref(fig:sem-plot) D) and thereby had a total positive
-effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$,
-Table \@ref(tab:indir-sem)). Connectance had no significant direct effect on either
-$\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
-(Figure \@ref(fig:sem-plot) D, Table \@ref(tab:indir-sem)).
-
-The total effect of PCA2, related to average annual temperature and inversely to
-altitude, on temporal stability was of higher magnitude than the effects of
-species richness and mean trophic level (Table
-\@ref(tab:indir-sem)).
-The PCA2 had a total negative effect on temporal stability, meaning that higher
-temperature results in lower stability
-($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
-PCA2 had an indirect positive effect on temporal stability through a
-direct positive effect on mean trophic level ($r_\delta = 
-`r env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)). However, PCA2
-had a negative effect on temporal stability through a direct positive effect on 
-$\overline{CV_{sp}}$ and species richness (resp.  $r_\delta = 
-`r env_on_cv_sp$direct["log_RC2"]`$ and $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$,
-Table \@ref(tab:indir-sem)). This was also true for the PCA1, related to stream
-size, with a resulting very slight positive effect of PCA1 on temporal stability
-($r_\delta = `r env_on_stab$total["log_RC1"]`$, Table \@ref(tab:indir-sem)).
-
-```{r, cache = FALSE}
-cap_sem <- paste0(
-  "Direct, indirect and total effects of environment, species richness,
-  connectance and mean trophic level on total biomass
-  and its temporal stability. Indirect effects are computed by multiplying the
-  path coefficients from the variable predictor to the response variable.
-  Indirect effects are considered as one step from the target variable. For
-  exemple, the indirect effect of species richness on
-  biomass stability via its effect on CVsp is $-0.62$. Only the
-  significant direct effects were retained for the computation of indirect
-  effects. ", "As an example, the indirect effect via species richness takes
-  into account the direct effect of species richness as well as the effect of
-  species richness through connectance and average trophic level. ",
- "NA values indicate that the corresponding paths do not exist in the
- specified Structural Equation Model (SEM). ", "NS: statistically non-significant."
-)
-```
-
-```{r indir-stab, cache = FALSE}
-
-full_table <- bind_rows(
-  tmp_bm_indir_table,
-  tmp_stab_indir_table
-) %>%
-mutate(`SEM type` = c(rep("Total annual biomass", 5), rep("Temporal Stability of annual biomass", 5))) %>%
-select(`SEM type`, variable, direct, via_richness, via_ct, via_tlvl, via_cv_sp, via_sync, total) %>%
-format_table() %>%
-select(`SEM type`, everything())
-
-full_table %<>%
-  mutate(Direct = ifelse(Direct == 0, "NS", Direct)) %>%
-  mutate_if(is.numeric, format, digits = 2, nsmall = 2)
-
-library(kableExtra)
-mytable <- kable(full_table,
-  format = "latex",
-  booktabs = T,
-  label = paste0("indir-sem"),
-  caption = cap_sem
-  ) %>%
-kable_styling(latex_options =c("scale_down")) %>%
-add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
-column_spec(1:2, width = "3cm") %>%
-collapse_rows(columns = 1, valign = "top")
-#write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
-```
-
-```{=latex}
-\input{table.tex}
-```
-
-# Discussion
-
-This study is unique by its level of integration, from environmental
-effects to total biomass and its stability, going through species richness and
-foodweb structure. It is the first direct assessment of a possible joint effect
-of species richness and network structure on both total biomass and its temporal
-stability. We found that species richness and mean trophic level had a positive
-effect on total biomass. In contrast, species richness had a negative effect on
-temporal stability whereas mean trophic level covaried positively. We also found
-that the effect of species richness and mean trophic level on total biomass and
-its temporal stability were not independent as species richness had a negative
-effect on mean trophic level. Furthermore, we found that connectance had no
-significant effect on both total biomass and its temporal stability. The results
-shows that temporal stability was mediated by changes in species variability 
-rather than synchrony. Finally, we found that the magnitude of the effects of
-average temperature and altitude was equal or superior to the effects of species
-richness and mean trophic level.
-
-## Species richness increased total biomass but decreased its temporal stability
-
-We found that species richness increased total biomass as already found in salt
-marshes, grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
-@wu_relationship_2015; @li_relationship_2018] as well as in streams
-[@woods_testing_2020]. The positive effect of species richness on total biomass
-might be due to resource use complementarity [@carey_determining_2011], which is
-held by niche differentiation [@loreau_biodiversity_1998;
-@loreau_partitioning_2001] or to the higher probability of getting high biomass
-species with higher species richness [@loreau_biodiversity_2001]. Our result is
-also in agreement with a recent study predicting a positive relationship between
-animal diversity and total consumer biomass in size-structured foodweb models
-[@schneider_animal_2016].
-
-Surprisingly, we found a negative relationship between temporal stability and
-species richness. Overall, it contrasts with experimental studies in grasslands
-[@tilman_biodiversity_2006; @valencia_synchrony_2020], mesocosms
-[@pennekamp_biodiversity_2018] with studies on natural communities such as
-butterflies  or lotic fishes [@olivier_urbanization_2020; @franssen_annual_2011;
-@houlahan_priority_2017], where positive relationships were found between temporal
-stability and species richness. However, some other studies also found a
-negative relationship, for instance in natural grasslands [@yang_effects_2011]
-or in natural forests as a marginal trend [@declerck_species_2006].
-
-The first step to identify the mechanisms behind those contrasting patterns is to
-look at the effects of species richness on synchrony and $\overline{CV_{sp}}$.
-As most studies on experimental grasslands
-[@isbell_biodiversity_2009; @roscher_identifying_2011] and natural communities
-of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
-@olivier_urbanization_2020], we found that species richness decreases synchrony,
-thereby increasing stability [but see @declerck_species_2006;
-@valencia_synchrony_2020]. Our study thus extends the evidence that species
-richness decreases synchrony to the case of trophic communities in natural
-settings. Species richness can reduce synchrony when (i) a given increase in species
-richness raises demographic stochasticity by decreasing population
-sizes, or when (ii) species have different
-responses to environmental variation [@loreau_species_2008].
-
-The positive effect of species richness on
-$\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
-studies focusing on single-trophic communities have reported mixed effects of
-species richness on $\overline{CV_{sp}}$, with destabilising effects of species
-richness at population level in grasslands [@jiang_different_2009;
-@gross_species_2014], a previous meta-analysis suggested that species richness had
-often a positive effect on population stability in multi-trophic communities
-[@jiang_different_2009].
-In foodwebs, theoretical models predict that the relationship between temporal
-stability of populations and species richness depends on interaction strength
-and its distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
-@downing_temporal_2020], high interaction strength inducing a negative
-relationship whereas the presence of weak interactions at high species richness is
-expected to promote stability. Therefore, it is possible that our results are
-due to a high degree of omnivory in foodwebs which combined with strong trophic
-interactions lead to more fluctuations in population biomass.
-
----
-#@thibaut_understanding_2013 proposed that a
-#strongly uneven biomass distribution across populations and that the biomass
-#variance of population increases much faster than its mean can generate a
-#positive effect of species richness on population ($\overline{CV_{sp}}$)
-#stability.
----
-
-## Average trophic level increased total biomass and its temporal stability while connectance had no effect
-
-The average trophic level was positively linked to total biomass. Furthermore,
-@wang_biodiversity_2018 have shown that total nutrient uptake might increase
-with the length of trophic chains and so results in higher total biomass.  While
-the predictions of @wang_biodiversity_2018 were restricted to food chains, and
-thus might not hold in more complex foodwebs with omnivorous species, our
-results are in agreement with their model predictions and highlight the
-importance of food chain length as a determinant of total biomass in foodwebs.
-In addition, mean trophic level had a positive effect on biomass stability by
-its negative effect on $\overline{CV_{sp}}$, thereby increasing average species
-stability. It might result from a higher stability of higher trophic level as
-predicted by food chain models in the presence of strong top-down control
-[@shanafelt_stability_2018; @barbier_pyramids_2019]. An alternative
-explanation is that higher mean trophic level leads complexify biomass pathways
-through the foodwebs, which might reduce biomass fluctuations in lower trophic
-levels [@mccann_diversitystability_2000].
-
-In contrast, connectance had no effect on total biomass. One might have expected
-that an increase in connectance may translate in a higher total nutrient uptake
-and so results in higher total biomass in the fish compartment. 
-However, some studies suggest that a greater connectance should decrease
-complementarity in resource use between species, which is expected to
-lower total biomass [@thebault_food-web_2003; @poisot_trophic_2013].
-A reason for such an absence of an effect might be explained by the fact that
-our data lack information about the lower compartments of the community, i.e.
-the primary producers, zooplankton and zoobenthos.
-
-Regarding temporal stability, our results
-contrast with numerous previous theoretical studies on the relationship between
-connectance and stability [e.g., @angelis_stability_1975; @may_will_1972;
-@thebault_stability_2010; but see @neutel_reconciling_2007], although they
-considered different stability concepts and metrics [@arnoldi_resilience_2016].
-The lack of effect of connectance on the temporal stability of total biomass
-might be related to the fact that our measure of connectance does not take into
-account the distribution of interaction strengths in the foodwebs. Indeed,
-foodweb connectance is expected to have different consequences on the temporal
-stability of total biomass depending on the strength of trophic interactions
-[@thebault_trophic_2005]. However, our measure of connectance does not fully
-account for the whole foodweb structure, and further research should examine the
-effects of connectance on total biomass and its temporal stability in more
-complete empirical foodwebs.
-
-One limitation of our study is indeed the use of inferred networks, i.e. not
-observed interactions, and the lack of of information on the other compartments
-of the foodweb (e.g. primary producers, decomposers, the benthic part of the
-foodweb). However, this approach is a promising way to explore how the
-architecture of ecological networks vary along environmental gradients across
-time. It constitutes an interesting complement to the real assessment of
-ecological interactions. The use of inferred networks also allow to extract most
-of the information contained from already available long term datasets.
-
-## Population stability was the main driver of temporal stability
-
-In contrast with previous studies, we found that the average population
-variability ($\overline{CV_{sp}}$) had a stronger negative effect on biomass
-stability than synchrony [@tilman_biodiversity_2006;
-@olivier_urbanization_2020]. It explains why we observe a negative effect of
-species richness on temporal stability of biomass. The lower effect of synchrony
-might be explained by the presence of generalist predators in stream
-communities, that raise synchrony between prey species that share the
-same predator and thus reduces compensatory
-population dynamics [@raimondo_interspecific_2004]. Alternatively, it is
-possible that, in aquatic foodwebs, the occurrence of large oscillatory dynamics
- leads to a higher contribution of population
-variability rather than synchrony to community stability
-[@mccann_reevaluating_1997]. How both strengths and the relative contribution of
-synchrony and population variability to overall stability vary between
-foodwebs and single trophic communities is still an open question.
-
----
-#Rough average synchrony in Théophile study: exp(-0.75) = .47 or exp(-0.6) = .54
-#This study: sync avg = .69
----
-
-## Environment had an strong effect on total biomass and its temporal stability
-
-We found that the total effect of environmental drivers on total biomass and its
-stability was mainly indirect and of the same magnitude order than the effect of
-species richness and average trophic level, highlighting that environmental
-changes may result in significant ecosystem responses, through alteration of
-both species richness and network structure.
-
-Contrasting with previous studies on experimental plant communities
-[@grace_integrative_2016], aquatic mesocosms [@yvondurocher_warming_2011;
-@dossena_warming_2012] and marine fish communities
-[@maureaud_biodiversityecosystem_2019], we found that environmental drivers
-overall affect total biomass indirectly rather than directly
-[@woods_testing_2020]. First, consistent with research showing that foodwebs in
-wider streams support more species and biomass [@allan_stream_2007], we found
-that the PCA axis related to stream size had a positive effect on total biomass
-through a positive effect on mean trophic level and species richness. Greater
-ecosystem size might provide a greater diversity of resources through habitat
-heterogeneity, and so higher species richness and total biomass by surface unit,
-through resource complementarity. Greater diversity of resources can also
-maintain more biomass at high trophic level [@post_ecosystem_2000;
-@doi_resource_2009]. Second, the positive effect of the PCA axis related to
-temperature on total biomass was of the magnitude of the effects of network
-structure and species richness, in line with the mounting body of work reporting
-important effects of temperature on the structure and biomass of aquatic systems
-[e.g.  @dossena_warming_2012; @edeline_ecological_2013;
-@emmrich_geographical_2014; @hattab_forecasting_2016; @woods_testing_2020]. We
-found that streams with higher average temperature supported higher diversity as
-well as higher average trophic level and total biomass, which is in agreement
-with recent findings on streams where the positive effects of temperature were
-related to larger nutrient supply [@ogorman_unexpected_2017].
-
-While the PCA axis related with stream size had only a very weak effect on the
-temporal stability of total biomass, the PCA axis related to temperature had a
-clear negative effect on the temporal stability through a direct destabilizing
-effect on populations and through indirect effects. Temperature can have both
-stabilizing and destabilizing effects in resource-consumer models depending on
-the thermal niche of the species and on how nutrient supply varies with
-temperature [@uszko_effects_2017]. In our case, the observed increased
-variability of populations might also relate with ecosystem enrichment
-[@ogorman_unexpected_2017] because average Biological Oxygen Demand covaries
-with temperature in our study. It has been suggested that enrichment can increase CV by
-increasing species biomass fluctuations while higher temperature might decrease
-decrease stability through starvation resulting from high metabolic activity
-[@tabi_warming_2019].
-
-Interestingly, the two PCA axes related to environmental conditions had indirect
-effects on stability through two conflicting pathways, either stabilising, via
-network structure, or destabilising, via species richness. The first pathway
-consists in a positive effect of temperature and stream size on mean
-trophic level, in line with the idea that wider streams and warmer conditions
-are favourable to mesotrophic predators [@allan_stream_2007;
-@emmrich_geographical_2014], which in turn stabilises biomass fluctuations,
-possibly due to increased top-down regulation. The second pathway consists in a
-positive effect of temperature and stream size on species richness, which itself
-has a destabilising effect. This result is interesting in that both
-pathways had not been evidenced to jointly play, to the best of our knowledge.
-Furthermore, it is unclear which pathway is dominating, and under which circumstances,
-opening an interesting avenue for further investigations.
-
----
-## Final thoughts about empirical foodwebs
-
-#It was unexpected that the average population $\overline{CV_{sp}}$
-#had a stronger negative effect on biomass stability than synchrony
-#[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
-#negative effect of species on temporal stability of biomass. The lower effect of
-#synchrony can be explained by the  presence of generalist predators in stream
-#communities, which can raise synchrony between prey species which shares the
-#same predator [@raimondo_interspecific_2004]. Uneven population biomass within
-#communities also raise synchrony between species [@thibaut_understanding_2013].
-
-#As found in other studies, we found that species richness was negatively related
-#to mean trophic level and connectance [@winemiller_must_1989;
-#@dunne_network_2006; @thebault_stability_2010]. Species richness had thus a
-#consistent destabilising effect on temporal stability of biomass directly and
-#through average trophic level, but it has a direct positive effect on total annual
-#biomass directly but a negative one through the decrease of average trophic
-#level. It highlights the importance to consider several aspects of
-#network structure to order to improve our understanding of the drivers of
-#community structure and stability.
----
-
-# Conclusion
-
-Our work contributes to bridging the gap between theoretical, experimental and
-empirical findings on the functioning and stability of communities. Our study
-extends the assessment of the effect of species richness on total biomass and
-its temporal stability to the case of food-webs in natural settings and
-highlights the need to consider species richness, network structure and their
-dependence to understand both functioning and stability of communities. Further,
-we found that the effects of environmental gradient related to temperature and
-ecosystem size are largely mediated by their impact on richness and average
-trophic level. Finally, our results highlight species variability as key in
-transmitting effects of richness, network structure and environmental gradients
-on community stability. This contrast with previous results found in single
-trophic communities, mostly plants, that mainly focus on synchrony and, although
-further confirmation are needed, might be characteristic of animal and/or
-multi-trophic communities.
-
-```{r}
-save.image(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
-```
-
-# References

### 2020-12-17 manuscript/bef_stability/manuscript.Rmd
Decrease to 5000 words:
8391 - 21 - 237 - 2730 - 251 - 151

@@
   - Abstract: 151
-  - Main text: 5535
+  - Main text: 4980
 
@@
 supports that they can be inferred through body size and diet informations
-[@jennings_weak_2001; @gravel_inferring_2013; @brose_predator_2019]. Especially
-in stream communities, including fishes, @brose_predator_2019 found that the
-prediction of predator-prey trophic interactions based on body size ratio was
-far better in stream ecosystems than in other aquatic and terrestrial
-ecosystems. Lastly, most of the diversity-biomass and diversity-stability
-relationships, have been assessed in terrestrial ecosystems while there is a
-evident need to test such relationships in a variety of ecosystem types.
+[@jennings_weak_2001; @gravel_inferring_2013], especially
+in stream communities including fishes [@brose_predator_2019]. Lastly, most of
+the diversity-biomass and diversity-stability relationships, have been assessed
+in terrestrial ecosystems while there is a evident need to test such
+relationships in a variety of ecosystem types.
 
@@
 inferred 1496 interaction networks, based on body size and diet. We question
-whether species richness, connectance and average trophic level increase,
-decrease or are unrelated to total biomass and its temporal stability. We
-further question whether the species richness, connectance, and average trophic
-level have antagonistic or mutual effect on total biomass and its temporal
-stability. Finally, we question if ecosystem size and average temperature
-increase total biomass and its temporal stability.
+whether species richness, connectance and average trophic level are related or
+not to total biomass and its temporal stability. We further question whether
+species richnes and foodweb structure have antagonistic or mutual effect on
+total biomass and its temporal stability. Finally, we question how ecosystem size
+and average temperature are related to total biomass and its temporal stability.
 
@@
 The feeding interactions of a fish node, i.e. a trophic species, were determined
-by both its species identity and its body size. Species identity allowed to
-differentiate between piscivorous and non piscivorous species, to know which
-resources the trophic species are feeding on and to know the minimum size at
-which a piscivorous species begin to feed on fishes. The ontogenic fish diet
+by both its species identity and its body size. The ontogenic fish diet
 database was filled according to fishbase and literature (appendix A, Table S2). Each
@@
 transformation in Fig. S5 and S6, Table S5). We set the seven
-hydrographic basins as a random effect on the intercept of the linear models to
+hydrographic basins as a random effect on the intercept to
 account for their heterogeneity. We checked for the absence of multicollinearity 
@@
 slope had a $P$ value inferior to $0.05$ were reported in the main text, all the
-path values are presented in Table S7 and S8).
+path values are presented in Table S7 and S8.
 
@@
 r_{BC}$. Only significant direct slopes were entered in the calculation of
-indirect effects. Finally total effects were computed as the sum
+indirect effects. Total effects were computed as the sum
 of direct and indirect effects.
@@
 trophic level ($R^2 =
-.11$, Fig. \@ref(fig:sem-plot) B and D). We found that species richness had a
+.11$, Fig. \@ref(fig:sem-plot) B and D). Species richness had a
 significant negative effect on mean trophic level ($r_\delta = 
 `r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_ct`$, Fig.
-\@ref(fig:sem-plot) B and D), meaning that a part of the effects of species richness went 
-through network structure.
+\@ref(fig:sem-plot) B and D), meaning that a part of the effects of species
+richness went through network structure.
 

### 2020-12-18 manuscript/bef_stability/manuscript.Rmd
Decrease manuscript length to 4930

@@
 
-- Data accessibility statement: the ONEMA database is available upon request to 
-  eddy.cosson@afbiodiversite.fr and thierry.point@afbiodiversite.fr. The code
-  used for the analysis and to generate the manuscript is available on github:
-  (alaindanet/fishcom.git)
+- Data accessibility statement: Upon acceptance of the paper, we confirmed that
+  the data supporting the results will be archived in an appropriate public
+  repository and that the data DOI will be included at the
+  end of the article. The code used for the analysis and to generate the
+  manuscript is available on github: (alaindanet/fishcom.git). The raw fish
+  database is public and available upon request to eddy.cosson@afbiodiversite.fr and
+  thierry.point@afbiodiversite.fr. The raw data of water temperature, flow and
+  Biological Oxygen Demand are available on http://www.naiades.eaufrance.fr/.
 
@@
 - Number of words:
-  - Abstract: 151
-  - Main text: 4980
+  - Abstract: 149
+  - Main text: 4930
 
@@
 Biodiversity-ecosystem functioning (BEF) and foodweb complexity-stability
-relationships are central to ecology. However, they remain largely untested in a
-foodweb context in natural settings. Here we study the links among
+relationships are central to ecology. However, they remain largely untested for 
+foodweb in natural context. Here we study the links among
 environmental conditions, richness, foodweb structure, annual biomass and its
@@
 [@thebault_relationship_2006] and stability [@thebault_trophic_2005;
-@thebault_relationship_2006; @tilman_biodiversity_2006].  Species richness has
-been shown to promote higher biomass production and  higher temporal stability
-of total biomass in a variety of ecosystems and taxa.  Indeed species richness
+@thebault_relationship_2006; @tilman_biodiversity_2006]. Indeed species richness
 generally increases primary productivity and total biomass in experimental plant
 communities [@tilman_productivity_1996; @grace_integrative_2016;
-@hector_plant_1999; @tilman_biodiversity_2014; @grace_integrative_2016], but
-also in briophyte communities [@mulder_physical_2001], stream feeders,
-[@cardinale_species_2002] and aquatic bacterial consumers
+@hector_plant_1999; @tilman_biodiversity_2014; @grace_integrative_2016], stream
+feeders, [@cardinale_species_2002] and aquatic bacterial consumers
 [@pennekamp_biodiversity_2018]. In parallel, such positive relationship between
@@
 ecosystems and taxa studied, the relationship between diversity and ecosystem
-functioning in experimental and empirical studies remains mostly focused on
+functioning remains mostly focused on
 single trophic levels, ignoring the effects of foodweb structure. This gap is
 even more striking for the relationship between diversity and temporal stability
-of ecosystem functioning, in spite of long-standing interest for the links
+, in spite of long-standing interest for the links
 between foodweb complexity and stability in theoretical ecology [e.g.
@@
 foodweb diversity and structure in contrasted ways depending on the ecosystem
-studied [@ogorman_unexpected_2017; @gauzens_biodiversity_2020]. When analyzing
-data from natural communities, the relationships among species richness, total
-biomass and its temporal stability might also arise from effects of the
-environment on both diversity and ecosystem functions
-[@loreau_biodiversity_2001; @he_global_2013; @grace_integrative_2016].
-@li_relationship_2018 have notably shown that climate moisture has a positive
-direct effect on total biomass, but also indirect through a positive effect on
-species richness.
+studied [@ogorman_unexpected_2017; @gauzens_biodiversity_2020]. In natural
+communities, the relationships among species richness, total biomass and its
+temporal stability might also arise from effects of the environment on both
+diversity and ecosystem functions [@loreau_biodiversity_2001; @he_global_2013;
+@grace_integrative_2016].
 
@@
 constitute a good model to study the effects of network structure on total
-biomass and its temporal stability. Despite that fish trophic interactions are
-difficult to measure in natural conditions, a substantial body of literature
-supports that they can be inferred through body size and diet informations
-[@jennings_weak_2001; @gravel_inferring_2013], especially
-in stream communities including fishes [@brose_predator_2019]. Lastly, most of
-the diversity-biomass and diversity-stability relationships, have been assessed
-in terrestrial ecosystems while there is a evident need to test such
-relationships in a variety of ecosystem types.
+biomass and its temporal stability. A substantial body of literature
+supports that trophic interactions can be inferred through body size and diet
+informations [@jennings_weak_2001; @gravel_inferring_2013], especially in stream
+communities including fishes [@brose_predator_2019].
 
@@
 structure, total biomass and its temporal stability in natural communities. To
-do so, we used the ONEMA dataset consisting in a standardized sampling of fish
+do so, we used a standardized sampling of fish
 communities in French streams [@edeline_ecological_2013]. We selected 99 sites
-that have been sampled for more than 10 years spanning on the 1995-2018 period. We
-inferred 1496 interaction networks, based on body size and diet. We question
-whether species richness, connectance and average trophic level are related or
-not to total biomass and its temporal stability. We further question whether
-species richnes and foodweb structure have antagonistic or mutual effect on
-total biomass and its temporal stability. Finally, we question how ecosystem size
-and average temperature are related to total biomass and its temporal stability.
+that have been sampled for more than 10 years. We inferred 1496 interaction
+networks, based on body size and diet. We question whether species richness,
+connectance and average trophic level are related to total biomass and its
+temporal stability. We further question how ecosystem size and temperature are
+related to total biomass and its temporal stability.
 
@@
 1995-2018 by the French Office of Water and Aquatic Ecosystems (ONEMA) using
-electric fishing. Two different standardized protocols were used for small and
-large streams (detailed in appendix B, part 1.1). The stations where the stream
-was of intermediate size could be sampled alternatively with one of the two
-sampling protocols. In this case, we kept only the most frequently used sampling
-protocol. The sampling season spanned from late spring to autumn. There was low
-heterogeneity of the sampling month within stations, with the median sampled
-month being mid-August while the median of the standard deviation of the sampled
-month within station was $0.7$.
+electrofishing. Two different standardized protocols were used for small and
+large streams (detailed in appendix B, part 1.1). In the case where a stream was
+sampled alternatively with one of the two sampling protocols, we kept only the
+most frequently used. The sampling season spanned from late spring to autumn.
+There was low heterogeneity of the sampling month within stations, with the
+median sampled month being mid-August while the median of the standard deviation
+of the sampled month within station was $0.7$.
 
@@
 hypothesis (Fig. S7). These selection steps resulted in 99 stations distributed
-over seven hydrographic basins (Fig. \@ref(fig:matmet) A).
+over seven hydrographic basins (Fig. \@ref(fig:matmet)A).
 
@@
 account for the variation in sampling effort among sites, species biomass and
-total biomass were corrected by the surface sampled (range `r range_surface[1]`-
-`r range_surface[2]` square metres), and expressed in grams by square meter
+total biomass were corrected by the surface sampled (range `r range_surface[1]` -
+`r range_surface[2]` square metres), and expressed in grams per square meter
 ($gm^{-2}$). In the analysis, the total biomass of a site has been defined as
@@
 
-We described the mechanisms driving the temporal stability of biomass, by
+We described the mechanisms driving the temporal stability of biomass,
 decomposing the $CV$ of total biomass ($CV_{com}$) into a synchrony ($\phi$) and
@@
 
-with $CV_{com, i}$ being the Coefficient of Variation of the biomass in the
-station $i$, $\overline{CV_{sp, i}}$ the average coefficient of variation of
+with $CV_{com, i}$ being the CV of the biomass in the
+station $i$, $\overline{CV_{sp, i}}$ the average CV of
 species in the station $i$ weighted by the relative biomass of the species, $B_{k,i}$.
@@
 
-Species richness in a given station has been defined as the total number of species present across
+Species richness in a given site was defined as the total number of species present across
 all the sampling events. We controlled species richness for sampling effort by
@@
 trophic interactions between all trophic species and the resources (Fig.
-\@ref(fig:matmet) B), then (2) determine network of a given community by
+\@ref(fig:matmet)B), then (2) determine network of a given community by
 extracting the metaweb according to the trophic species present at a given
-site and sampling event (Fig. \@ref(fig:matmet) C and D).
+site and sampling event (Fig. \@ref(fig:matmet)C and D).
 
@@
 biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos
-(grey nodes in Fig. \@ref(fig:matmet) B, C & D). The trophic species and the
+(grey nodes in Fig. \@ref(fig:matmet)B, C & D). The trophic species and the
 resources constituted the 412 nodes of the metaweb, i.e. 45 fish species divided
@@
 two steps and based on the body size ratio between predators and prey. First of
-all, the predation window of a piscivorous trophic specie was defined as 3% to
+all, the predation window of a piscivorous trophic species was defined as 3% to
 45% of its midpoint [@mittelbach_ontogeny_1998; @claessen_impact_2002;
@@
 the trophic species and the resources nodes according the food diet of their
-size class, for both the piscivorous and non piscivorous trophic species.
-Lastly, the trophic links among resource nodes were set according to the
-literature [@allan_stream_2007; @hart_handbook_2008].
+size class.  Lastly, the trophic links among resource nodes were set according
+to the literature [@allan_stream_2007; @hart_handbook_2008].
 
@@
 For each trophic network, corresponding to a particular site and year, we
-computed two of the most commonly used network metrics to characterize food
-webs, namely the connectance and mean trophic level. Connectance describes the
+computed the connectance and mean trophic level. Connectance describes the
 level of generalism in the network and is calculated as the actual number of
-interactions divided by the maximum number of interactions if all species interact
-together ($C = L / N^2$, L and N being resp. the number of links and of trophic
-species plus resource nodes). The mean trophic level $\overline{T}$ was computed
-as the mean trophic level weighted by the biomass of each trophic species
-(excluding resource nodes for which we had no biomass information), so
-$\overline{T} = \sum_i^N{B_iT_i \times (\sum_i^N{B_i})^{-1}}$, with $T_i$ and
-$B_i$ being respectively the trophic level and the biomass of the node $i$. The
-trophic level of the nodes was computed as one added to the average trophic
-level of its food item. For each site, the median of connectance and average
-trophic level over time was used in subsequent analysis.
+interactions divided by the number of interactions if all species interact
+together ($C = L / N^2$, L and N being resp. the number of links and of nodes).
+The trophic level of the nodes was computed as one added to the average trophic
+level of its food item. The mean trophic level $\overline{T}$ was 
+weighted by the biomass of each trophic species (excluding resource nodes for
+which we had no biomass information), so $\overline{T} = \sum_i^N{B_iT_i \times
+(\sum_i^N{B_i})^{-1}}$, with $T_i$ and $B_i$ being respectively the trophic
+level and the biomass of the node $i$. For each site, the median of connectance
+and average trophic level over time was used in subsequent analysis.
 
@@
 source, stream width and depth and its strahler order, i.e. its position in the
-stream network. From the naiades database
-[(www.naiades.eaufrance.fr)](http://www.naiades.eaufrance.fr/), we also
-got data on water temperature and flow. As data from the naiades database are
+stream network. We obtained data on water temperature and flow from the naiades
+database
+[(www.naiades.eaufrance.fr)](http://www.naiades.eaufrance.fr/). As data from naiades are
 not collected on the same site as our fish sampling sites, we performed an
@@
 reversed the values of the second axis, such as it represented a gradient of
-increasing average water temperature, DBO and decreasing altitude and slope.
+increasing average water temperature, BOD and decreasing altitude and slope.
 Further description of the variables are provided in appendix B (part 1.4).
@@
 average annual total biomass as a function of the two synthetic environmental
-variables, species richness and foodweb structure as measured by connectance and
-average trophic level [@maureaud_biodiversityecosystem_2019;
+variables, species richness and foodweb structure [@maureaud_biodiversityecosystem_2019;
 @woods_testing_2020]. We assumed that both species richness and network
-structure directly affect total biomass (Fig.
-\@ref(fig:sem-plot) A)
+structure directly affect total biomass (Fig. \@ref(fig:sem-plot)A)
 and that species richness affected foodweb structure [@winemiller_must_1989;
@@
 We used the same model structure for temporal stability of biomass (Fig.
-\@ref(fig:sem-plot) C). Instead of the annual total biomass, we modelled the
-synchrony and population variability which in turn determined the temporal
+\@ref(fig:sem-plot)C). Instead of the annual total biomass, we modelled the
+synchrony and $\overline{CV_{sp}}$ which in turn determined the temporal
 stability of biomass.
@@
 Indirect effects on total biomass and its temporal stability
-were computed by multiplying slopes along the path. As an example, if we consider
-$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times
-r_{BC}$. Only significant direct slopes were entered in the calculation of
-indirect effects. Total effects were computed as the sum
-of direct and indirect effects.
+were computed by multiplying slopes along the path. Only significant direct
+slopes were entered in the calculation of indirect effects. Total effects were
+computed as the sum of direct and indirect effects.
 
@@
 [@pinheiro_nlme_2020; @lefcheck_piecewisesem_2016]. The code used for the
-analysis and the manuscript are accessible on github (alaindanet/fishcom). The analyses were
-performed with R version 3.6.3 [@r_core_team_r_2020].
+analysis and to generate the manuscript are accessible on github
+(alaindanet/fishcom). The analyses were performed with R version 3.6.3
+[@r_core_team_r_2020].
 
@@
 trophic level ($R^2 =
-.11$, Fig. \@ref(fig:sem-plot) B and D). Species richness had a
+.11$, Fig. \@ref(fig:sem-plot)B and D). Species richness had a
 significant negative effect on mean trophic level ($r_\delta = 
 `r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_ct`$, Fig.
-\@ref(fig:sem-plot) B and D), meaning that a part of the effects of species
+\@ref(fig:sem-plot)B and D), meaning that a part of the effects of species
 richness went through network structure.
@@
 on total biomass ($r_\delta = `r rich_on_bm$direct`$ and 
-$r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-plot) B, Table
-\@ref(tab:indir-sem)), while connectance had no direct effect on total biomass
-(Fig. \@ref(fig:sem-plot) B).
+$r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-plot)B, Table
+\@ref(tab:indir-sem)), while connectance had no direct effect.
 
@@
 effects on total biomass, but indirect (Table \@ref(tab:indir-sem)). The first
-axis, PCA1, related to the stream size was positively linked to total biomass
+axis, related to the stream size, was positively linked to total biomass
 ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
@@
 `r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_tlvl["log_RC1"]`$
-resp., Table \@ref(tab:indir-sem)). The second axis, PCA2, related to the average
-annual temperature and inversely to altitude of the sites was positively related
+resp., Table \@ref(tab:indir-sem)). The second axis, related to the average
+annual temperature was positively related
 to total biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
@@
 `r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The total effect
-of PCA1 and PCA2 on total biomass was of the same magnitude than the total effects of species
-richness on total biomass.
+of PCA1, PCA2 and species richness on total biomass were of the same magnitude.
 
@@
 $r_\delta = `r cv_sp_on_stab`$ and $r_\delta = `r sync_on_stab`$, Fig.
-\@ref(fig:sem-plot) D).
-
-The total effect of mean trophic level on temporal stability of biomass was of
-the same magnitude than the one of species richness (resp.
+\@ref(fig:sem-plot)D).
+
+The total effect of mean trophic level and species richness on temporal
+stability of biomass were of the same magnitude (resp.
 $`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
@@
 $\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
-Fig. \@ref(fig:sem-plot) D) and thereby had a total positive
+Fig. \@ref(fig:sem-plot)D) and thereby had a total positive
 effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$,
@@
 $\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
-(Fig. \@ref(fig:sem-plot) D, Table \@ref(tab:indir-sem)).
-
-The total effect of PCA2, related to average annual temperature and inversely to
-altitude, on temporal stability was of higher magnitude than the effects of
-species richness and mean trophic level (Table
-\@ref(tab:indir-sem)).
+(Fig. \@ref(fig:sem-plot)D, Table \@ref(tab:indir-sem)).
+
+The total effect of PCA2, related to average annual temperature, on temporal
+stability was of higher magnitude than the effects of species richness and mean
+trophic level (Table \@ref(tab:indir-sem)).
 The PCA2 had a total negative effect on temporal stability, meaning that higher
@@
 @loreau_partitioning_2001] or to the higher probability of getting high biomass
-species with higher species richness [@loreau_biodiversity_2001]. Our result is
-also in agreement with a recent study predicting a positive relationship between
-animal diversity and total consumer biomass in size-structured foodweb models
+species with higher species richness [@loreau_biodiversity_2001]. Our results are 
+also in agreement with a model predicting a positive relationship between animal
+diversity and total consumer biomass in size-structured foodweb
 [@schneider_animal_2016].
@@
 Surprisingly, we found a negative relationship between temporal stability and
-species richness. Overall, it contrasts with experimental studies in grasslands
+species richness. It contrasts with experimental studies in grasslands
 [@tilman_biodiversity_2006; @valencia_synchrony_2020], mesocosms
@@
 
-The first step to identify the mechanisms behind those contrasting patterns is to
-look at the effects of species richness on synchrony and $\overline{CV_{sp}}$.
-As most studies on experimental grasslands
-[@isbell_biodiversity_2009; @roscher_identifying_2011] and natural communities
-of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
-@olivier_urbanization_2020], we found that species richness decreases synchrony,
-thereby increasing stability [but see @declerck_species_2006;
-@valencia_synchrony_2020]. Our study thus extends the evidence that species
-richness decreases synchrony to the case of trophic communities in natural
-settings. Species richness can reduce synchrony when (i) a given increase in species
+As most studies on experimental grasslands [@isbell_biodiversity_2009;
+@roscher_identifying_2011] and natural communities of birds, grasslands, bats
+and butterflies [@bluthgen_land_2016; @olivier_urbanization_2020], we found that
+species richness decreases synchrony, thereby increasing stability [but see
+@declerck_species_2006; @valencia_synchrony_2020]. Our study thus extends the
+evidence that species richness decreases synchrony to the case of multi-trophic
+communities. Species richness can reduce synchrony when (i) a given increase in species
 richness raises demographic stochasticity by decreasing population
@@
 @downing_temporal_2020], high interaction strength inducing a negative
-relationship whereas the presence of weak interactions at high species richness is
-expected to promote stability. Therefore, it is possible that our results are
-due to a high degree of omnivory in foodwebs which combined with strong trophic
-interactions lead to more fluctuations in population biomass.
+relationship. Therefore, it is possible that our results are due to strong
+trophic interactions, leading to more fluctuations in population biomass.
 
@@
 
-The average trophic level was positively linked to total biomass. Furthermore,
+The average trophic level was positively linked to total biomass.
 @wang_biodiversity_2018 have shown that total nutrient uptake might increase
@@
 the predictions of @wang_biodiversity_2018 were restricted to food chains, and
-thus might not hold in more complex foodwebs with omnivorous species, our
+thus might not hold in more complex foodwebs with omnivory, our
 results are in agreement with their model predictions and highlight the
@@
 [@shanafelt_stability_2018; @barbier_pyramids_2019]. An alternative
-explanation is that higher mean trophic level leads complexify biomass pathways
+explanation is that higher mean trophic level complexify the biomass pathways
 through the foodwebs, which might reduce biomass fluctuations in lower trophic
@@
 lower total biomass [@thebault_food-web_2003; @poisot_trophic_2013].
-A reason for such an absence of an effect might be explained by the fact that
-our data lack information about the lower compartments of the community, i.e.
-the primary producers, zooplankton and zoobenthos.
-
-Regarding temporal stability, our results
-contrast with numerous previous theoretical studies on the relationship between
+
+Regarding temporal stability, our results contrast with numerous previous
+theoretical studies on the relationship between
 connectance and stability [e.g., @angelis_stability_1975; @may_will_1972;
@@
 stability of total biomass depending on the strength of trophic interactions
-[@thebault_trophic_2005]. However, our measure of connectance does not fully
-account for the whole foodweb structure, and further research should examine the
-effects of connectance on total biomass and its temporal stability in more
-complete empirical foodwebs.
+[@thebault_trophic_2005]. However, our foodwebs lack information about the lower
+compartments of the community, i.e. primary producers, decomposers and the benthic
+part of the foodweb. Further research should examine the effects of connectance
+on total biomass and its temporal stability in more complete empirical foodwebs.
 
 One limitation of our study is indeed the use of inferred networks, i.e. not
-observed interactions, and the lack of of information on the other compartments
-of the foodweb (e.g. primary producers, decomposers, the benthic part of the
-foodweb). However, this approach is a promising way to explore how the
-architecture of ecological networks vary along environmental gradients across
+observed interactions. However, this approach is a promising way to explore how the
+architecture of ecological networks vary along environmental gradients and across
 time. It constitutes an interesting complement to the real assessment of
-ecological interactions. The use of inferred networks also allow to extract most
+ecological interactions because it allows to extract most
 of the information contained from already available long term datasets.
@@
 
-We found that the total effect of environmental drivers on total biomass and its
-stability was mainly indirect and of the same magnitude order than the effect of
-species richness and average trophic level, highlighting that environmental
-changes may result in significant ecosystem responses, through alteration of
-both species richness and network structure.
-
-We found that environmental drivers overall affect total biomass indirectly
-[@woods_testing_2020] rather than directly , contrasting with previous studies
+We found that environmental drivers affect total biomass mostly indirectly
+[@woods_testing_2020] rather than directly, contrasting with previous studies
 [@yvondurocher_warming_2011; @dossena_warming_2012; @grace_integrative_2016;
@@
 supported higher diversity as well as higher average trophic level and total
-biomass, which is in agreement with recent findings on streams where the
-positive effects of temperature were related to larger nutrient supply
-[@ogorman_unexpected_2017].
-
-While the PCA axis related with stream size had only a very weak effect on the
+biomass, which is in agreement with recent findings on streams.
+
+While the PCA axis related to stream size had only a weak effect on the
 temporal stability of total biomass, the PCA axis related to temperature had a
-negative effect on the temporal stability through a direct destabilizing
+negative effect on temporal stability through a direct destabilizing
 effect on populations and through indirect effects. Temperature can have both
@@
 the thermal niche of the species and on how nutrient supply varies with
-temperature [@uszko_effects_2017]. In our case, the observed increased
+temperature [@uszko_effects_2017]. The observed increased
 variability of populations might also relate with ecosystem enrichment
@@
 extends the assessment of the effect of species richness on total biomass and
-its temporal stability to the case of food-webs in natural settings and
+its temporal stability to the case of foodwebs in natural settings and
 highlights the need to consider species richness, network structure and their

### 2021-02-09 manuscript/bef_stability/fig1_biomass_network.Rmd
Test for new fig1

---
title: "New first figure"
---

```{r}
library(tidyverse)
library(magrittr)
library(cowplot)

mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "local_network_build.R"))
theme_set(theme_cowplot())
```

```{r}
myload(community_metrics, op_analysis, sem_data, dir = mypath("data"))
community_metrics %<>%
    left_join(select(op_analysis, station, opcod, year))

```

```{r}
get_bm_dyn_year <- function (com = NULL, station = NULL) {

  test <- com %>%
    filter(station == 1755)

  test %<>%
    mutate(sp_tibble = map(sp_vector, ~tibble(species = names(.x), biomass_sp = .x))) %>%
    unnest(sp_tibble) %>%
    mutate(bm_std_sp = biomass_sp / surface) %>%
    select(station, year, species, bm_std_sp)

  test %<>% 
    pivot_wider(names_from = species, values_from = "bm_std_sp")%>%
    mutate_at(vars(matches("[A-Z]{3}", ignore.case = FALSE)), ~ifelse(is.na(.), 0, .)) %>%
    pivot_longer(cols = matches("[A-Z]{3}", ignore.case = FALSE), names_to = "species", values_to = "bm_std_sp")

  return(test)
}
get_network_summary <- function (com = NULL, station = NULL) {

  st <- station
  tmp <- com %>%
    filter(station == st) %>%
    mutate_if(is.double, ~round(., 2))

  label <- paste(
    "S =", tmp$bm_std_stab, ", ",
    "sync =", tmp$sync, ", ",
    "CVsp =", tmp$cv_sp, ", ",
    "\n",
    "R =", tmp$rich_tot_std, ", ",
    "C =", tmp$ct, ", ",
    "Tlvl= ", tmp$t_lvl
  )

  return(label)

}

plot_dyn_web  <- function (com = NULL, sem_df = NULL, station = NULL, stacked =
  FALSE, .log = FALSE) {

  # get bm dynamic 
  com <- get_bm_dyn_year(com = com, station = station)

  # get total biomass 
    total_bm <- com %>%
	  group_by(year) %>%
	  summarise(bm_std_sp = sum(bm_std_sp)) %>%
	  mutate(species = "Total")

  p <- com %>%
    ggplot(aes(x = year, y = bm_std_sp, color = species))

  if (stacked) {
    p <- p + 
      geom_area(aes(fill = species))
  } else {
    p <- p + 
      geom_line() +
      geom_line(data = total_bm, color = "black")
  }

  # Make it professional:
  p <- p +
    labs(y = "Biomass density (g by square meter)", x = "Year")

  if (!is.null(sem_df)) {

    label <- get_network_summary(com = sem_df, station = station) 
    p <- p +
    annotate("text", x = median(total_bm$year),
      y = max(total_bm$bm_std_sp) + max(total_bm$bm_std_sp) * 5/100, label = label)
  }

  if (.log) {
    p <- p + scale_y_log10()
  }

  return(p)

}
```

```{r}
plot_dyn_web(com = community_metrics, station = 1755, stacked = TRUE, sem_df = sem_data)
plot_dyn_web(com = community_metrics, sem_df = sem_data, station = 1755)
```

# Network

```{r}
source(mypath("R", "codeWeb.R"))
myload(toy_metaweb, dir = mypath("data"))

TL <- NetIndices::TrophInd(toy_metaweb$metaweb)$TL
PlotWeb(
  TL = TL,
  webTL = toy_metaweb$metaweb,
  colnode = rep("red", length(TL)),
  abund = rnorm(length(TL), 100, 10),
  collink="grey70",
  scale_abun = .2
) 
```

```{r}
get_adj_net_station <- function (net = NULL, station = NULL) {

  st <- station

  net <- net %>%
    filter(station %in% st) %>%
    dplyr::select(station, year, network) %>%
    unnest(cols = c(network))

  ## Compute metrics:
  net %>%
    dplyr::select(year, from, to) %>%
    arrange(year) %>%
    group_by(year) %>%
    nest(network = c(from, to)) %>%
    mutate(
      igraph_obj = map(network, igraph::graph_from_data_frame,
	directed = TRUE),
      adj_mat = map(igraph_obj, igraph::as_adjacency_matrix,
	sparse = FALSE),
      troph = map(adj_mat, ~NetIndices::TrophInd(.x)),
      obs_troph_level_vector = map(troph, function (x) {
	TL <- x$TL
	names(TL) <- rownames(x) 
	return(TL)
	})
    )
}

get_net_biomass <- function (net = NULL, station = NULL) {

  st <- station

  # Get bm
  net <- net %>%
    filter(station %in% st) %>%
    dplyr::select(year, composition) %>%
    unnest(cols = c(composition))  %>%
    select(year, sp_class, bm_std)

   # Make list
    net %<>%
      arrange(year) %>%
      group_by(year) %>%
      nest(bm = c(sp_class, bm_std)) %>%
      mutate(bm = map(bm, deframe))
  net
}

set_color_nodes <- function (
  node_list = NULL,
  color_species_resources = NULL
  ) {

  node_list_sp <- stringr::str_replace_all(node_list, "_\\d", "")

  colour <- color_species_resources[node_list_sp]
  names(colour) <- node_list
  return(colour)
}

set_node_resources_abun <- function (
  node_list = NULL,
  node_abun = NULL, resource_abun = NULL) {

  abun <- vector("numeric", length(node_list))  
  names(abun) <- node_list

  if (is.null(resource_abun)) {
    resource_abun <- mean(node_abun)
  }

  abun[names(node_abun)] <- node_abun 
  abun[abun == 0] <- resource_abun 
  return(abun)

}
```

```{r}
myload(network_analysis, dir = mypath("data", "classes"))
network_analysis %<>%
  left_join(dplyr::select(op_analysis, opcod, station, year))

net <- get_adj_net_station(net = network_analysis, station = 1755)
net$obs_troph_level_vector[[1]]
net$adj_mat[[1]]
bm <- get_net_biomass(net = network_analysis, station = 1755)
bm$bm[[1]]

meta_node_color <- set_color_species(node_list = unique(names(unlist(net$obs_troph_level_vector))), species_list = NULL, resource_list = NULL, col_resource = NULL)

PlotWeb(
  TL = net$obs_troph_level_vector[[1]],
  webTL = net$adj_mat[[1]],
  colnode = set_color_nodes(
    node_list = names(net$obs_troph_level_vector[[1]]),
    color_species_resources = meta_node_color),
  abund = set_node_resources_abun(node_list = names(net$obs_troph_level_vector[[1]]), node_abun = bm$bm[[1]]),
  collink="grey70",
  scale_abun = .2
) 
```

## Temporal network

```{r, warning = FALSE, fig.height = 14, fig.width = 14}
par(mfrow = c(2,2))
for (i in seq_along(net$adj_mat)) {
PlotWeb(
  TL = net$obs_troph_level_vector[[i]],
  webTL = net$adj_mat[[i]],
  colnode = set_color_nodes(
    node_list = names(net$obs_troph_level_vector[[i]]),
    color_species_resources = meta_node_color),
  abund = set_node_resources_abun(node_list = names(net$obs_troph_level_vector[[i]]), node_abun = bm$bm[[i]]),
  collink="grey70",
  scale_abun = .2
) 
title(paste0(net$year[[i]]))
}

```

# Test fig plot

```{r, warning = FALSE}
list_p <- list()

nb <- seq.int(from = 1, to = length(net$adj_mat), length.out = 4)

p <- ~{ 
par(
  mfrow = c(2,2),
  mar = c(0, 0, 1, 0), 
  mgp = c(2, 1, 0)
)
for (i in nb) {
PlotWeb(
  TL = net$obs_troph_level_vector[[i]],
  webTL = net$adj_mat[[i]],
  colnode = set_color_nodes(
    node_list = names(net$obs_troph_level_vector[[i]]),
    color_species_resources = meta_node_color),
  abund = set_node_resources_abun(node_list = names(net$obs_troph_level_vector[[i]]), node_abun = bm$bm[[i]]),
  collink="grey70",
  scale_abun = .6
)
title(paste0(net$year[[i]]))
p <- recordPlot()
list_p <- c(list_p, p)

}
}

```

```{r, fig.width = 10, warning = FALSE}
plot_grid(
  plot_dyn_web(com = community_metrics, sem_df = sem_data, station = 1755) +
    theme(legend.position = "bottom"),
  ggdraw(p)
)
```

### 2021-02-10 manuscript/bef_stability/fig1_biomass_network.Rmd
plot_temporal_network properly

@@
 theme_set(theme_cowplot())
+.pardefault <- par()
 ```
@@
 
+  st <- station
   test <- com %>%
-    filter(station == 1755)
+    filter(station == st)
 
@@
 plot_dyn_web  <- function (com = NULL, sem_df = NULL, station = NULL, stacked =
-  FALSE, .log = FALSE) {
+  FALSE, .log = FALSE, color_species = NULL) {
 
@@
     p <- p + scale_y_log10()
+  }
+
+  if (!is.null(color_species)) {
+    p %<>%
+      scale_fill_manual(values = meta_node_color) +
+      scale_color_manual(values = meta_node_color)
   }
@@
 }
+
+get_network_temporal_plot <- function (
+  net_list = NULL,
+  station = NULL,
+  selected_years = NULL,
+  node_color = NULL,
+  scale_node_size = 0.01,
+  par_options = par(mar = c(0,0,4,0)),
+  add_title = FALSE
+  ) {
+
+  net <- get_adj_net_station(net = net_list, station = station)
+  bm <- get_net_biomass(net = net_list, station = station)
+
+  if (!is.null(selected_years)) {
+    net %<>% filter(year %in% selected_years) 
+    bm %<>% filter(year %in% selected_years) 
+  }
+
+  if (is.null(node_color)) {
+    node_color <- set_color_species(
+      node_list = unique(names(unlist(net$obs_troph_level_vector))),
+      species_list = NULL, resource_list = NULL, col_resource = NULL)
+  }
+
+  list_p <- list()
+  index <- seq_along(net$year)
+
+  for (i in index) {
+    if(!is.null(par_options)) {
+      par_options
+    }
+    plot.new()
+    PlotWeb(
+      TL = net$obs_troph_level_vector[[index[i]]],
+      webTL = net$adj_mat[[index[i]]],
+      colnode = set_color_nodes(
+	node_list = names(net$obs_troph_level_vector[[index[i]]]),
+	color_species_resources = node_color),
+      abund = set_node_resources_abun(
+	node_list = names(net$obs_troph_level_vector[[index[i]]]),
+	node_abun = bm$bm[[index[i]]],
+	resource_abun = 1
+	),
+      collink="grey70",
+      scale_abun = scale_node_size,
+      rel_abun = FALSE
+
+    )
+    if (add_title) {
+     title(main = paste0(net$year[[index[i]]]))
+    }
+
+    p <- recordPlot()
+
+    list_p[[i]] <- p 
+  }
+
+  gg <- map(list_p, ggdraw)
+  gg
+}
 ```
@@
 network_analysis %<>%
-  left_join(dplyr::select(op_analysis, opcod, station, year))
+  left_join(dplyr::select(op_analysis, opcod, station, year)) %>%
+  filter(!is.na(opcod))
 
 net <- get_adj_net_station(net = network_analysis, station = 1755)
-net$obs_troph_level_vector[[1]]
-net$adj_mat[[1]]
 bm <- get_net_biomass(net = network_analysis, station = 1755)
-bm$bm[[1]]
 
@@
 
-## Temporal network
+# Test fig plot
 
-```{r, warning = FALSE, fig.height = 14, fig.width = 14}
-par(mfrow = c(2,2))
-for (i in seq_along(net$adj_mat)) {
+```{r, warning = FALSE}
+nb <- seq.int(from = 1, to = length(net$adj_mat), length.out = 4)
+```
+
+```{r, fig.width = 10}
+list_p <- list()
+for (i in seq_along(nb)) {
+#  par(mar = c(0,0,0,0))
+  plot.new()
   PlotWeb(
-  TL = net$obs_troph_level_vector[[i]],
-  webTL = net$adj_mat[[i]],
+    TL = net$obs_troph_level_vector[[nb[i]]],
+    webTL = net$adj_mat[[nb[i]]],
     colnode = set_color_nodes(
-    node_list = names(net$obs_troph_level_vector[[i]]),
+      node_list = names(net$obs_troph_level_vector[[nb[i]]]),
       color_species_resources = meta_node_color),
-  abund = set_node_resources_abun(node_list = names(net$obs_troph_level_vector[[i]]), node_abun = bm$bm[[i]]),
+    abund = set_node_resources_abun(
+      node_list = names(net$obs_troph_level_vector[[nb[i]]]),
+      node_abun = bm$bm[[nb[i]]],
+      resource_abun = 1
+      ),
     collink="grey70",
-  scale_abun = .2
+    scale_abun = .01,
+    rel_abun = FALSE
+
   )
-title(paste0(net$year[[i]]))
+#  title(paste0(net$year[[nb[i]]]))
+
+  p <- recordPlot()
+
+  list_p[[i]] <- p 
 }
+
+gg <- map(list_p, ggdraw)
+plot_grid(plotlist = gg, nrow = 2)
+```
+
+```{r}
+meta_node_color <- set_color_species(node_list = unique(names(unlist(net$obs_troph_level_vector))), species_list = NULL, resource_list = NULL, col_resource = NULL)
+
+p <- get_network_temporal_plot(net_list = network_analysis, station = 1755,
+  selected_years = c(1997, 2010, 2018),
+  node_color = meta_node_color, scale_node_size = 0.05, par_options = par(mar = c(1,0,1,0)))
+```
+
+```{r, fig.width = 10, fig.height = 12, warning = FALSE}
+#par(.pardefault)
+#par(.pardefault)
+test_p <- plot_grid(
+  nrow = 2,
+  plot_dyn_web(com = community_metrics, sem_df = sem_data, stacked = TRUE, station = 1755) +
+    scale_fill_manual(values = meta_node_color) +
+    scale_color_manual(values = meta_node_color)
+    ,
+  plot_grid(plotlist = p, nrow = 1),
+  rel_heights = c(1, 1),
+  align = "v"
+)
+
+test_p
+save_plot(
+  "figs/test_temporal_plot.png", test_p,
+  nrow = 2, 
+  ncol = 1,
+  base_height = 4,
+  base_width = 8)
+```
+
+```{r, eval = FALSE}
+test2 <- ggdraw(
+  plot_dyn_web(com = community_metrics, sem_df = sem_data, stacked = TRUE, station = 1755)) +
+   draw_plot(gg[[1]], .45, .45, .5, .5)
+
+save_plot("figs/test_temporal_plot.png", test2)
+```
+
+```{r}
+sem_data %>%
+  arrange(richness_med, desc(biomass_stab)) %>%
+  filter(richness_med >= 3)
 
@@
 
-# Test fig plot
+```{r}
+st <- 21604
+te <- plot_dyn_web(com = community_metrics, sem_df = sem_data, station = st, stacked = TRUE)
+ti <- get_adj_net_station(net = network_analysis, station = st)
 
-```{r, warning = FALSE}
-list_p <- list()
+meta_node_color <- set_color_species(
+  node_list = unique(names(unlist(ti$obs_troph_level_vector))), 
+  species_list = NULL,
+  resource_list = NULL,
+  col_resource = NULL)
 
-nb <- seq.int(from = 1, to = length(net$adj_mat), length.out = 4)
+p <- get_network_temporal_plot(net_list = network_analysis, station = st,
+  selected_years = c(2007, 2010, 2016),
+  node_color = meta_node_color, scale_node_size = 0.02, par_options = par(mar = c(0,0,0,0)))
+plot_grid(plotlist = p)
 
-p <- ~{ 
-par(
-  mfrow = c(2,2),
-  mar = c(0, 0, 1, 0), 
-  mgp = c(2, 1, 0)
-)
-for (i in nb) {
-PlotWeb(
-  TL = net$obs_troph_level_vector[[i]],
-  webTL = net$adj_mat[[i]],
-  colnode = set_color_nodes(
-    node_list = names(net$obs_troph_level_vector[[i]]),
-    color_species_resources = meta_node_color),
-  abund = set_node_resources_abun(node_list = names(net$obs_troph_level_vector[[i]]), node_abun = bm$bm[[i]]),
-  collink="grey70",
-  scale_abun = .6
-)
-title(paste0(net$year[[i]]))
-p <- recordPlot()
-list_p <- c(list_p, p)
-
+for (i in seq_along(p)) {
+  save_plot(paste0("figs/test_net", i, ".png"), p[[i]], base_height = 4, base_width = 4)
 }
-}
-
 ```
 
-```{r, fig.width = 10, warning = FALSE}
-plot_grid(
-  plot_dyn_web(com = community_metrics, sem_df = sem_data, station = 1755) +
-    theme(legend.position = "bottom"),
-  ggdraw(p)
-)
+```{r}
+test_inc <- ggdraw(te + theme(plot.margin = margin(0, 0, 3, 0, "cm"))) +
+  draw_plot(p[[1]], .15, -.01, .2, .2)
+
+  save_plot(paste0("figs/test_net_inc", ".png"), test_inc, base_height = 4)
 ```

### 2021-02-17 manuscript/bef_stability/appendixB.Rmd
Advance review

@@
 bibliography: references.bib
+number_sections: true
 ---
@@
 
-Diet information were obtained from fishbase.org and literature (Appendix a, Table S2). The
+Diet information were obtained from fishbase.org and literature (Appendix A, Table S2). The
 diet information contained from two to three life stages by species, the life
@@
 removed_sp_metaweb <- unique(removed_ind_metaweb$species)
+```
+
+```{r}
+metaweb_caption <- paste0(
+  "The metaweb which describes the interarctions between all the 412 trophic species, each is
+  represented by a node and each color represents a species (S = 45). The seven
+  resource nodes (7) are drawn in grey. The species names corresponding to the
+  three digit codes are found in Table S1."
+)
+```
+
+```{r metaweb, fig.cap=metaweb_caption}
+knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "metaweb.png"))
 ```

### 2021-02-17 manuscript/bef_stability/fig1_biomass_network.Rmd
Advance review

@@
 source(mypath("R", "misc.R"))
-source(mypath("R", "plot_methods.R"))
-source(mypath("R", "geo_methods.R"))
-source(mypath("R", "press_methods.R"))
-source(mypath("R", "synchrony.R"))
-source(mypath("R", "community_methods.R"))
-source(mypath("R", "community_analysis.R"))
-source(mypath("R", "statistical_analysis.R"))
-source(mypath("R", "local_network_build.R"))
+source_dir(mypath("R"))
 theme_set(theme_cowplot())
@@
 community_metrics %<>%
-    left_join(select(op_analysis, station, opcod, year))
-
+    left_join(dplyr::select(op_analysis, station, opcod, year))
 ```
@@
     mutate(bm_std_sp = biomass_sp / surface) %>%
-    select(station, year, species, bm_std_sp)
+    dplyr::select(station, year, species, bm_std_sp)
 
@@
 }
-get_network_summary <- function (com = NULL, station = NULL) {
+get_network_summary <- function (com = NULL, station = NULL, stab = TRUE, com_avg = TRUE) {
 
@@
 
-  label <- paste(
-    "S =", tmp$bm_std_stab, ", ",
-    "sync =", tmp$sync, ", ",
-    "CVsp =", tmp$cv_sp, ", ",
-    "\n",
-    "R =", tmp$rich_tot_std, ", ",
-    "C =", tmp$ct, ", ",
-    "Tlvl= ", tmp$t_lvl
+  label_stab <- c(
+    "Stability" = tmp$bm_std_stab,
+    "Synchrony" = tmp$sync, 
+    "CVsp" = tmp$cv_sp,
+    "Median total biomass" = tmp$prod_std #"' * (g/m^2) * '"
     )
+  label_com <- c(
+    "Median species richness" = tmp$richness_med,
+    "Median connectance" = tmp$ct,
+    "Median avg trophic level" = tmp$t_lvl
+  )
+  label <- NULL
+
+  if (stab) {
+    label <- c(label, label_stab)
+
+  }
+
+  if (com_avg) {
+
+    label <- c(label, label_com)
+
+  }
 
@@
 
-plot_dyn_web  <- function (com = NULL, sem_df = NULL, station = NULL, stacked =
-  FALSE, .log = FALSE, color_species = NULL) {
+plot_dyn_web  <- function (
+  com = NULL, sem_df = NULL, station = NULL,
+  stacked = FALSE, .log = FALSE, color_species = NULL, label = NULL,
+  label_parsed = FALSE, label_size = 4.5, y_label = NULL, my_ylim = NULL) {
 
@@
 
+  if ( !is.null(my_ylim) ) 
+  {
+    p <- p +
+      ylim(my_ylim)
+  }
+
   # Make it professional:
   p <- p +
-    labs(y = "Biomass density (g by square meter)", x = "Year")
+    labs(y = expression(Biomass~density~(g/m^2)), x = "Year")
 
@@
     label <- get_network_summary(com = sem_df, station = station) 
+  }
+
+  if (!is.null(label)) {
+
+    if (is.null(y_label)) {
+      y_label <- max(total_bm$bm_std_sp) + max(total_bm$bm_std_sp) * 5/100
+    }
+
     p <- p +
     annotate("text", x = median(total_bm$year),
-      y = max(total_bm$bm_std_sp) + max(total_bm$bm_std_sp) * 5/100, label = label)
+      y = y_label,
+      label = label, parse = label_parsed, size = label_size)
   }
@@
   if (!is.null(color_species)) {
-    p %<>%
-      scale_fill_manual(values = meta_node_color) +
-      scale_color_manual(values = meta_node_color)
+    p <- p + 
+      scale_fill_manual(values = color_species) +
+      scale_color_manual(values = color_species)
   }
@@
 }
+
+get_label_from_named_vector <- function ( label = NULL, collapse = "\n") {
+  paste0(names(label), " = ", label, collapse = collapse)
+} 
 ```
@@
 ```{r}
-plot_dyn_web(com = community_metrics, station = 1755, stacked = TRUE, sem_df = sem_data)
-plot_dyn_web(com = community_metrics, sem_df = sem_data, station = 1755)
+label <- get_network_summary(com = sem_data, station = 1755)
+lab <- get_label_from_named_vector(label = label[1:4])
+plot_dyn_web(com = community_metrics, station = 1755, stacked = TRUE, label =
+ lab, label_size = 4.5 )
+plot_dyn_web(com = community_metrics, station = 1755, label = lab)
 ```
@@
     unnest(cols = c(composition))  %>%
-    select(year, sp_class, bm_std)
+    dplyr::select(year, sp_class, bm_std)
 
@@
   par_options = par(mar = c(0,0,4,0)),
-  add_title = FALSE
+  add_title = FALSE,
+  rel_abun = FALSE,
+  log_abun = FALSE
   ) {
@@
       scale_abun = scale_node_size,
-      rel_abun = FALSE
-
+      rel_abun = rel_abun,
+      log_abun = log_abun
     )
@@
 ```{r}
+```
+
+```{r, fig.width = 10, fig.height = 5, warning = FALSE}
+#par(.pardefault)
+#par(.pardefault)
+
 meta_node_color <- set_color_species(node_list = unique(names(unlist(net$obs_troph_level_vector))), species_list = NULL, resource_list = NULL, col_resource = NULL)
@@
   selected_years = c(1997, 2010, 2018),
-  node_color = meta_node_color, scale_node_size = 0.05, par_options = par(mar = c(1,0,1,0)))
-```
-
-```{r, fig.width = 10, fig.height = 12, warning = FALSE}
-#par(.pardefault)
-#par(.pardefault)
+  node_color = meta_node_color, scale_node_size = 0.04, par_options = par(mar = c(0,0,0,0)))
+#low <- plot_grid(plot_grid(plotlist = gg, nrow = 1), NULL, rel_width= c(1, .1))
+low <- plot_grid(plotlist = p, nrow = 1)
 test_p <- plot_grid(
@@
     ,
-  plot_grid(plotlist = p, nrow = 1),
-  rel_heights = c(1, 1),
-  align = "v"
+  low,
+  rel_heights = c(1, .6),
+  align = "h"
 )
-
 test_p
@@
   base_height = 4,
-  base_width = 8)
-```
-
-```{r, eval = FALSE}
-test2 <- ggdraw(
-  plot_dyn_web(com = community_metrics, sem_df = sem_data, stacked = TRUE, station = 1755)) +
-   draw_plot(gg[[1]], .45, .45, .5, .5)
-
-save_plot("figs/test_temporal_plot.png", test2)
+  base_width = 7)
 ```
@@
 ```{r}
-sem_data %>%
-  arrange(richness_med, desc(biomass_stab)) %>%
-  filter(richness_med >= 3)
+first_st <- sem_data %>%
+  arrange(richness_tot, desc(biomass_stab)) %>%
+  filter(richness_tot >= 2)
 
+tes <- map(first_st$station[1:12], ~plot_dyn_web(
+    com = community_metrics,
+    sem_df = sem_data,
+    station = .x,
+    stacked = TRUE))
+plot_grid(plotlist = tes)
 ```
@@
 ```{r}
-st <- 21604
-te <- plot_dyn_web(com = community_metrics, sem_df = sem_data, station = st, stacked = TRUE)
+first_st$station[5]
+#11432 my choice
+```
+
+```{r}
+last_st <- sem_data %>%
+  arrange(desc(prod), biomass_stab ) %>%
+  filter(richness_tot < 15)
+
+tes <- map(last_st$station[1:12], ~plot_dyn_web(
+    com = community_metrics,
+    sem_df = sem_data,
+    station = .x,
+    stacked = TRUE))
+plot_grid(plotlist = tes)
+```
+```{r}
+last_st$station[5]
+#6268 my choice
+```
+
+```{r pca}
+myload(habitat_press, dir = mypath("data"))
+library(sf)
+library(ggspatial)
+# map
+myload(p_st, dir = mypath("manuscript", "bef_stability", "figs"))
+# Station
+myload(biomass_ts_sax, op_analysis, dir = mypath("data"))
+op_analysis_bbb <- filter(op_analysis, station %in%
+  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
+station <- get_basin_station(sf_obj = TRUE)
+station %<>%
+  filter(station %in% unique(op_analysis$station))
+## Get bbb
+station %<>%
+  mutate(type = ifelse(
+      station %in% unique(op_analysis_bbb$station),
+      "stable", "unstable"),
+    st_temporal = ifelse(station %in% qt_station$station, TRUE, FALSE)
+  )
+
+habitat_press %<>% na.omit()
+mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())
+
+qt_station <- sem_data %>%
+  filter(station %in% c(first_st$station[5], last_st$station[5])) %>%
+  dplyr::select(station, bm_std_stab)
+mysave(qt_station, dir = mypath("data"), overwrite = TRUE)
+
+p_st <- p_st + 
+  theme_void() +
+  theme(plot.margin = theme_get()$plot.margin, legend.position = "none")
+
+p_st2 <- p_st +
+  geom_sf(data = filter(station, type == "stable"), color = "black") +
+  geom_sf(data = filter(station, station %in% qt_station$station),
+    color = "red", size = 3) +
+  geom_sf_text(data = filter(
+      station, station %in% qt_station$station
+      ), 
+    aes(label = c("C", "D")),
+    #color = "red",
+    fontface = 2,
+    size = 5,
+    nudge_x = c(-30000, 30000),
+    nudge_y = c(30000, -30000)
+    ) +
+  coord_sf(
+    xlim = c(60000, 1100000),
+    ylim = c(6100000, 7122216),
+    datum = sf::st_crs(2154),
+    crs = 2154,
+    expand = FALSE
+  )
+
+pca_rotated <- compute_rotated_pca(
+  .data = habitat_press[, mask],
+  naxis = 2
+)
+p1 <- my_pca_plot(.data = pca_rotated$rotated,
+  xaxis = "RC1", yaxis = "RC2", ctb_thld = .4, 
+  label_size = 4, force_pull = 0.01, force = 10,
+  seed = 1
+)
+
+cow_p1 <- plot_grid(NULL, p1, NULL, ncol = 1, rel_heights = c(.02, 1, .02))
+fig1ab <- plot_grid(p_st2, cow_p1, ncol = 2, 
+  labels = c("A", "B")
+)
+save_plot(mypath("manuscript", "bef_stability", "figs/fig1ab.png"), fig1ab,
+  nrow = 1, 
+  ncol = 2,
+  base_height = 4,
+  base_width = 4
+)
+``` 
+```{r set-up}
+st <- c(first_st$station[5], last_st$station[5]) 
+library(viridis)
+library(ggsci)
+library(RColorBrewer)
+display.brewer.pal(n = 8, name = 'Dark2')
+display.brewer.pal(n = 8, name = 'Set2')
+
+brew_col <- c(brewer.pal(n = 8, name = "Dark2"), brewer.pal(n = 8, name = "Set2"))
+
 ti <- get_adj_net_station(net = network_analysis, station = st)
+node_list <- unique(names(unlist(ti$obs_troph_level_vector)))
 
+# Color
 meta_node_color <- set_color_species(
-  node_list = unique(names(unlist(ti$obs_troph_level_vector))), 
+  node_list = node_list, 
   species_list = NULL,
@@
   col_resource = NULL)
+fish_node_mask <- str_detect(names(meta_node_color), "[A-Z]{3}")
+meta_node_color[fish_node_mask] <- brew_col[1:sum(fish_node_mask)]
+meta_node_color <- c(meta_node_color, PHX = brew_col[length(brew_col)])
 
-p <- get_network_temporal_plot(net_list = network_analysis, station = st,
-  selected_years = c(2007, 2010, 2016),
-  node_color = meta_node_color, scale_node_size = 0.02, par_options = par(mar = c(0,0,0,0)))
-plot_grid(plotlist = p)
+#y max:
+ymax <- community_metrics %>%
+  filter(station %in% st) %>%
+  summarise(bm = max(bm_std)) %>%
+  deframe 
+ymax <- round(ymax * .1) * 10
+my_y_label <- ymax - 7 
+my_label_size <- 4
 
-for (i in seq_along(p)) {
-  save_plot(paste0("figs/test_net", i, ".png"), p[[i]], base_height = 4, base_width = 4)
-}
+```
+```{r low-rich-high-stab}
+
+# Label
+label <- get_network_summary(com = sem_data, station = st[1])
+lab <- get_label_from_named_vector(label = label[1:5])
+
+te <- plot_dyn_web(
+  com = community_metrics,
+  label = lab,
+  y_label = my_y_label,
+  label_size = my_label_size,
+  my_ylim = c(0, ymax),
+  station = st[1],
+  stacked = TRUE,
+  color = meta_node_color)
+p <- get_network_temporal_plot(net_list = network_analysis, station = st[1],
+  selected_years = c(1997, 1999, 2002),
+  node_color = meta_node_color, scale_node_size = 0.06,
+  par_options = par(mar = c(0,0,0,0)),
+  log_abun = TRUE
+)
+#g <- map(p, ggdraw)
+#g <- plot_grid(g[[1]], NULL, g[[2]], NULL, g[[3]], nrow = 1, rel_width = c(1, -.2, 1, -.2, 1))
+g <- plot_grid(plotlist = map(p, ggdraw), nrow = 1)
+
+cow_te  <- te +
+  theme(legend.position = "none")
+fig1c <- plot_grid(
+  cow_te,
+  g,
+  nrow = 2,
+  align = "h",
+  rel_heights = c(1, .6)
+
+)
+fig1c
+save_plot("figs/fig1c_low_rich.png", fig1c,
+  nrow = 2, 
+  ncol = 1,
+  base_height = 4,
+  base_width = 7
+)
 ```
@@
 ```{r}
-test_inc <- ggdraw(te + theme(plot.margin = margin(0, 0, 3, 0, "cm"))) +
-  draw_plot(p[[1]], .15, -.01, .2, .2)
+# Label
+label2 <- get_network_summary(com = sem_data, station = st[2])
+lab2 <- get_label_from_named_vector(label = label2[1:5])
 
-  save_plot(paste0("figs/test_net_inc", ".png"), test_inc, base_height = 4)
+te2 <- plot_dyn_web(
+  com = mutate(community_metrics, year = as.integer(year)),
+  label = lab2,
+  y_label = my_y_label,
+  label_size = my_label_size,
+  my_ylim = c(0, ymax),
+  station = st[2],
+  stacked = TRUE,
+  color = meta_node_color) +
+scale_x_continuous(breaks = c(1995, 1998, 2001, 2004))
+p2 <- get_network_temporal_plot(net_list = network_analysis, station = st[2],
+  selected_years = c(1997, 1999, 2002),
+  node_color = meta_node_color, scale_node_size = 0.05,
+  par_options = par(mar = c(0,0,0,0)),
+  log_abun = TRUE
+)
+#g <- map(p, ggdraw)
+#g <- plot_grid(g[[1]], NULL, g[[2]], NULL, g[[3]], nrow = 1, rel_width = c(1, -.2, 1, -.2, 1))
+g2 <- plot_grid(plotlist = map(p2, ggdraw), nrow = 1)
+
+# get legend
+cow_te2 <- te2 + theme(legend.position = "bottom") +
+  guides(
+    fill = guide_legend(nrow = 2, title = "Species"),
+    color = guide_legend(nrow = 3, title = "Species")
+  )
+leg_species <- get_legend(cow_te2)
+cow_te2 <- te2 + theme(legend.position = "none")
+
+fig1d <- plot_grid(
+  cow_te2,
+  g2,
+  nrow = 2,
+  align = "h",
+  rel_heights = c(1, .60)
+
+)
+save_plot("figs/fig1d_high_rich.png", fig1d,
+  nrow = 2, 
+  ncol = 1,
+  base_height = 4,
+  base_width = 7
+)
 ```
+
+```{r}
+cow_fig1ab <- plot_grid(
+  p_st2 + theme(panel.background = element_rect(fill = "white")),
+  p1, NULL,
+  rel_widths = c(.5, .5, .07),
+  ncol = 3,
+  labels = c("A", "B", ""))
+fig1cd <- plot_grid(fig1c, fig1d, ncol = 2, labels = c("C", "D"))
+cow_leg_species <- plot_grid(NULL, leg_species, NULL, nrow = 1, rel_widths = c(.25, .5, .25))
+fig1 <- plot_grid(cow_fig1ab, fig1cd, cow_leg_species,
+  nrow = 3,
+  rel_heights = c(.35, .60,.05),
+  align = "h"
+)
+# ele: single column (82 mm), two-thirds page width (110 mm) or full page width (173 mm)
+dev.new(width = 8.2, height = 11.0, units = "cm")
+# i3: mod + shift + space
+
+# Draw connectance and average trophic level:
+lab_net <- get_label_from_named_vector(label = label[6:7])
+lab2_net <- get_label_from_named_vector(label = label2[6:7])
+fig1_draw <- ggdraw(fig1) +
+  draw_label(lab_net, x = .25, y = .075, size = 11) +
+  draw_line(
+    x = c(0.01, 0.01, 0.49, .49),
+    y = c(.11, 0.1, 0.1, .11),
+    color = "black", size = 1
+  ) + 
+  draw_label(lab2_net, x = .75, y = .075, size = 11) +
+  draw_line(
+    x = c(0.52, 0.52, 0.98, .98),
+    y = c(.11, 0.1, 0.1, .11),
+    color = "black", size = 1
+  )
+
+test <- ggdraw(fig1)
+for(i in seq(0,1, .02)) {
+  test <- test +
+  draw_line(x = c(0, 1), y = c(i , i), color = "black", size = .5) +
+  draw_line(x = c(i, i), y = c(0 , 1), color = "black", size = .5)
+}
+for(i in seq(0,1, .1)) {
+  test <- test +
+  draw_line(x = c(0, 1), y = c(i , i), color = "red", size = 1) +
+  draw_line(x = c(i, i), y = c(0 , 1), color = "red", size = 1)
+}
+
+fig1_draw_test <- fig1_draw +
+  draw_line(
+    x = c(0.1, 0.16),
+    y = c(0.26, 0.325),
+    color = "black", size = 1
+  ) +
+  draw_line(
+    x = c(0.26, 0.24),
+    y = c(0.26, 0.325),
+    color = "black", size = 1
+  ) +
+  draw_line(
+    x = c(0.43, 0.34),
+    y = c(0.26, 0.325),
+    color = "black", size = 1
+  ) +
+  draw_line(
+    x = c(0.59, 0.69),
+    y = c(0.26, 0.325),
+    color = "black", size = 1
+  ) +
+  draw_line(
+    x = c(0.76, 0.77),
+    y = c(0.26, 0.325),
+    color = "black", size = 1
+  ) +
+  draw_line(
+    x = c(0.93, 0.89),
+    y = c(0.26, 0.325),
+    color = "black", size = 1
+  )
+
+save_plot(mypath("manuscript", "bef_stability", "figs/fig1.png"), fig1_draw_test,
+nrow = 3, 
+  ncol = 1,
+  base_height = 4,
+  base_width = 10 
+)
+```

### 2021-02-17 manuscript/bef_stability/manuscript.Rmd
Advance review

@@
 ---
-title: Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
+title: Species richness and food-web structure jointly drive community biomass and its temporal stability in fish communities
 author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault, Colin Fontaine
@@
 
-- Running title: Foodweb structure, biomass and stability
+- Running title: food-web structure, biomass and stability
 
@@
 
-Biodiversity-ecosystem functioning (BEF) and foodweb complexity-stability
-relationships are central to ecology. However, they remain largely untested for 
-foodweb in natural context. Here we study the links among
-environmental conditions, richness, foodweb structure, annual biomass and its
-temporal stability using a standardized monitoring of 99 stream fish communities
+Biodiversity-ecosystem functioning (BEF) and food-web complexity-stability
+relationships are central to ecology. However, they remain largely untested in natural context. Here we study the links among
+environmental conditions, richness, food-web structure, annual biomass and its
+temporal stability using a standardized monitoring dataset of 99 stream fish communities
 spanning from 1995 to 2018. We first reveal that both richness and average
 trophic level are positively related to annual biomass, with effects of similar
-strength. Second, we show that network structure affects community stability,
-with a positive effect of mean trophic level, and contrary to general
-expectation, we find that richness destabilizes fish communities. Finally, we
+strength. Second, we show that food-web structure affects community stability,
+with a positive effect of mean trophic level, and contrary to
+expectation, a destabilizing effect of species richness. Finally, we
 find that environmental conditions affect both biomass and its stability via
 effects on richness and network structure. Strikingly, effects on stability are
-mediated by changes in species stability rather than synchrony, which contrasts
+mediated by changes in population stability rather than synchrony, which contrasts
 with results from single-trophic communities and might be characteristic of
@@
 affect ecosystems in complex ways [@loreau_biodiversity_2001;
-@tilman_biodiversity_2014]. Biodiversity has indeed a tremendous effect on
+@tilman_biodiversity_2014]. Biodiversity has indeed a major effect on
 ecosystem functions and their stability in response to perturbations
 [@hector_plant_1999; @loreau_biodiversity_2001; @hooper_effects_2005;
-@dunne_network_2006; @duffy_why_2009], because it largely determines both the
+@dunne_network_2006; @duffy_why_2009], because it largely determines the
 amount and the distribution of matter and energy fluxes within and among
@@
 settings, such as stream fish communities [@franssen_annual_2011], bird and
-butterfly communities [@olivier_urbanization_2020]. Despite the diversity of
-ecosystems and taxa studied, the relationship between diversity and ecosystem
-functioning remains mostly focused on
-single trophic levels, ignoring the effects of foodweb structure. This gap is
-even more striking for the relationship between diversity and temporal stability
-, in spite of long-standing interest for the links
-between foodweb complexity and stability in theoretical ecology [e.g.
-@may_will_1972; @dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
-@stouffer_compartmentalization_2011].
+butterfly communities [@houlahan_negative_2017; @olivier_urbanization_2020].
+Despite the diversity of ecosystems and taxa studied, the relationship between
+diversity and ecosystem functioning remains mostly focused on single trophic
+levels, ignoring the effects of food-web structure. This gap is even more
+striking for the relationship between diversity and temporal stability , in
+spite of long-standing interest for the links between food-web complexity and
+stability in theoretical ecology [e.g.  @may_will_1972; @dunne_network_2006;
+@neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011].
 
 Overall, the evidence from theoretical models suggests that both species
-richness and foodweb structure should modulate ecosystem properties such as
-total biomass and its stability. Complementarity in the use of
-resources, a main mechanism previously highlighted in single-trophic studies, is
-important to understand the effects of species richness in foodwebs [@thebault_food-web_2003;
-@poisot_trophic_2013; @schneider_animal_2016], but in that case it also depends
-on foodweb connectance [@thebault_food-web_2003; @poisot_trophic_2013].
+richness and food-web structure should modulate ecosystem properties such as
+community biomass and its stability. Complementarity in the use of
+resources is important to understand the effects of species richness in food-webs
+[@thebault_food-web_2003; @poisot_trophic_2013; @schneider_animal_2016], but it
+also depends on food-webs connectance, i.e. its level of generalism
+[@thebault_food-web_2003; @poisot_trophic_2013].
 
@@
 [@tilman_biodiversity_2006; @loreau_species_2008; @olivier_urbanization_2020],
-asynchrony in species temporal variations is also explaining a significant part
-of the stabilizing effects of species richness on total biomass in foodwebs
-[@thebault_trophic_2005]. Indeed, a low synchrony in species fluctuations,
+asynchrony in population temporal variations also explains a significant part
+of the stabilizing effects of species richness on community biomass in food-webs
+[@thebault_trophic_2005]. Indeed, a low synchrony in population fluctuations,
 i.e. asynchrony, is synonymous of compensatory dynamics, where the decrease in
-abundance of a species is compensated by the increase of an other. However,
-higher connectance can reverse the positive effects of species
-richness on temporal stability of total biomass, by leading to a negative
-relationship between species richness and species temporal variability
+abundance of a population is compensated by the increase of another. However,
+higher connectance can counterbalance the positive effects of species
+richness on temporal stability of community biomass, by leading to a negative
+relationship between species richness and population temporal variability
 [@thebault_trophic_2005]. In addition, the presence of species at higher trophic
-levels increases total primary production [@wang_biodiversity_2018]. The
-addition of predators has also cascading effects on both species variability and
+levels increases total primary production, through stronger top-down effects
+associated with higher nutrient uptake [@wang_biodiversity_2018]. The addition of predators has
+also cascading effects on both population variability and
 synchrony at lower trophic levels [@teng_dynamics_2004;
 @shanafelt_stability_2018]. Overall, these theoretical studies show that the
-effects of species richness and network structure, such as connectance and
+effects of species richness and food-web structure, such as connectance and
 average trophic level, are potentially conflicting or synergistic in such a way
@@
 
-The gap in studies that consider jointly effects of diversity and foodweb
+The lack of studies that consider jointly effects of diversity and food-web
 structure on ecosystem functions can be explained by the challenges associated
-with manipulating both species richness and foodweb complexity in an
-experimental context [e.g. @sander_ecological_2017] and by the fact that describing
-trophic interactions between species is highly labour intensive. These
-challenges are even more acute for the study of the stability of ecosystem
-properties, which additionally requires time-series data and longer-term
-analyses. In this context, recent developments to predict species trophic
-interactions [@gravel_inferring_2013], combined with observational long-term surveys
-of ecological communities, can offer an opportunity to investigate the links
-between diversity, foodweb structure and the stability of total community
+with manipulating both species richness and food-web complexity in an
+experimental context [e.g. @sander_ecological_2017] and by the fact that
+describing trophic interactions between species is highly labour intensive.
+These challenges are even more acute for the study of the stability of ecosystem
+properties, which additionally requires longer-term
+perspectives. In this context, recent developments to predict species trophic
+interactions [@beckerman_foraging_2006; @gravel_inferring_2013; @portalier_foraging_2019], combined with observational long-term
+surveys of ecological communities, can offer the opportunity to investigate the
+links between diversity, food-web structure and the stability of total community
 biomass in natural settings.
@@
 their stability. Environment affects organism performance directly, and thereby,
-species abundances, total biomass [@grace_integrative_2016; @woods_testing_2020]
+population abundances, community biomass [@grace_integrative_2016; @woods_testing_2020]
 and its temporal stability [@oliver_heterogeneous_2010; @franssen_annual_2011;
@@
 @friedpetersen_drivers_2020]. For example, larger ecosystem might increase the
-number of available resources and thus total biomass [@post_ecosystem_2000;
+number of available resources and thus community biomass [@post_ecosystem_2000;
 @doi_resource_2009] while temperature affects ecosystem respiration and biomass
@@
 @tabi_warming_2019]. Environment also directly affect species richness and
-foodweb structure. For instance, larger ecosystems host foodwebs with higher
-diversity and trophic levels [@mchugh_dual_2010] while temperature can affect
-foodweb diversity and structure in contrasted ways depending on the ecosystem
+food-web structure, as larger ecosystems host food-webs with higher
+diversity and trophic levels [@mchugh_dual_2010] whereas temperature can affect
+food-web diversity and structure in contrasted ways depending on the ecosystem
 studied [@ogorman_unexpected_2017; @gauzens_biodiversity_2020]. In natural
-communities, the relationships among species richness, total biomass and its
+communities, the relationships among species richness, community biomass and its
 temporal stability might also arise from effects of the environment on both
@@
 supports that trophic interactions can be inferred through body size and diet
-informations [@jennings_weak_2001; @gravel_inferring_2013], especially in stream
-communities including fishes [@brose_predator_2019].
-
-Our aim is to document the relationships among species richness, foodweb
-structure, total biomass and its temporal stability in natural communities. To
+informations [@jennings_weak_2001; @beckerman_foraging_2006;
+@gravel_inferring_2013; @brose_predator_2019; @portalier_foraging_2019].
+
+Our aim is to document the relationships among species richness, food-web
+structure, community biomass and its temporal stability in natural communities. To
 do so, we used a standardized sampling of fish
@@
 networks, based on body size and diet. We question whether species richness,
-connectance and average trophic level are related to total biomass and its
-temporal stability. We further question how ecosystem size and temperature are
-related to total biomass and its temporal stability.
+food-web connectance and average trophic level are related to community biomass and its
+temporal stability. We further assess how ecosystem size and temperature
+mediated this relationship.
 
@@
 
+```{r, fig.show = "hide"}
+myload(
+  hab_analysis,
+  temporal_station_desc,
+  temporal_press_polluants,
+  geo_station,
+  dir = mypath("data")
+)
+habitat_press <- build_habitat_pressure_dataset(
+  .habitat_analysis = hab_analysis,
+  .tmp_press = temporal_press_polluants,
+  .tmp_st_desc = temporal_station_desc,
+  .geo_st = geo_station 
+)
+
+# Make PCA 
+habitat_press %<>% na.omit()
+mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())
+
+pca_rotated <- compute_rotated_pca(
+  .data = habitat_press[, mask],
+  naxis = 2
+)
+habitat_pressure <- 
+  cbind(habitat_press[, c("station", "temperature_med", "alt")], pca_rotated$rotated$score) %>%
+  as_tibble
+
+mysave(habitat_press, habitat_pressure, dir = mypath("data"), overwrite = TRUE)
+```
+
+```{r}
+prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
+  map_dbl(., ~round(.x * 100))
+tot_var_expl_pca <- sum(prop_var_expl_pca) 
+```
+
 ```{r, cache = FALSE}
-myload(qt_station, dir = mypath("data"))
+pca_caption <- paste0(
+  "(B) Rotated axis of PCA on environmental variables. The five components
+  explained,", tot_var_expl_pca, "% of the variance (",
+  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
+  " Axis 1 was positively related to the stream size, axis 2 was related to
+  the stream slope and altitude and negatively related to average water temperature and
+  BOD."
+  )
+
 matmet_cap <- paste0( 
@@
   on the period 1995-2018. The red dots show the location of (C) and (D) sites.
-  ", " Inner borders draw the limits of the hydrographic basins. ", "(B) The
-  metaweb of the study. Each trophic species (N = 412) is represented by a node
-  and each
-  color represents a species (S = 45). Resource nodes (7) are drawn in grey. ",
+  ", " Inner borders draw the limits of the hydrographic basins. ", pca_caption,
+  " (C) and (D) The temporal dynamic of population biomass with three networks
+  of years 1997, 1999 and 2002. Each trophic species is represented
+  by a node and each color represents a species. The node size are proportional to
+  the biomass of the trophic species. The seven resource nodes are drawn in grey. ",
   "The species names corresponding to the three digit codes are found in Table
-  S1." ,
-  "Yearly temporal series of networks of two stations having respectively a low
-  (C) and high (D) temporal stability of biomass. C and D stations have
-  respectively biomass stability the closest to the first and third quartile of
-  the distribution of the temporal stability of biomass in the dataset,
-  respectively ", round(qt_station$bm_std_stab[1],2), " and ",
-  round(qt_station$bm_std_stab[2],
-    2), ". Point size is proportional to the biomass of the trophic species.")
+  S1.")
 
@@
 large streams (detailed in appendix B, part 1.1). In the case where a stream was
-sampled alternatively with one of the two sampling protocols, we kept only the
-most frequently used. The sampling season spanned from late spring to autumn.
-There was low heterogeneity of the sampling month within stations, with the
-median sampled month being mid-August while the median of the standard deviation
-of the sampled month within station was $0.7$.
+sampled alternatively with one of the two sampling protocols, we only included
+data derived from the most frequently used sampling method. The sampling season
+spanned from late spring to autumn.  There was low heterogeneity of the sampling
+month within stations, with the median sampling month being mid-August where the
+median standard deviation of the sampling month was $0.7$ month, i.e. three weeks.
 
@@
 rarely observed or difficult to characterize in natural communities, only
-stations with no temporal trends in total biomass were selected (detailed in
+stations with no temporal trends in community biomass were selected (detailed in
 appendix B, part 2). However, the results were robust to the relaxation of this
@@
 
-## Total biomass and its temporal stability
+## Community biomass and its temporal stability
 
@@
 $B_i = 0.01 \times l_i^{3.03}$, with $B$ the body mass in grams, $l$ the body
-size in millimeters and $i$ the individual. Species biomass and total biomass at
+size in millimeters and $i$ the individual. Population biomass and community biomass at
 each sampling event were then calculated by summing individual body masses. To
-account for the variation in sampling effort among sites, species biomass and
-total biomass were corrected by the surface sampled (range `r range_surface[1]` -
+account for the variation in sampling effort among sites, population biomass and
+community biomass were corrected by the surface sampled (range `r range_surface[1]` -
 `r range_surface[2]` square metres), and expressed in grams per square meter
-($gm^{-2}$). In the analysis, the total biomass of a site has been defined as
-the median of the total biomass across sampling years.
+($gm^{-2}$). In the analysis, the community biomass of a site was defined as
+the median of the community biomass across sampling years.
 
@@
 We described the mechanisms driving the temporal stability of biomass,
-decomposing the $CV$ of total biomass ($CV_{com}$) into a synchrony ($\phi$) and
-a weighted average species $CV$ ($\overline{CV_{sp}}$) components according to
-@thibaut_understanding_2013:
+decomposing the $CV$ of the community biomass ($CV_{com}$) into a
+synchrony ($\phi$) component and a weighted average species $CV$ ($\overline{CV_{sp}}$)
+component according to @thibaut_understanding_2013:
 
@@
 
-with $CV_{com, i}$ being the CV of the biomass in the
-station $i$, $\overline{CV_{sp, i}}$ the average CV of
-species in the station $i$ weighted by the relative biomass of the species, $B_{k,i}$.
+with $CV_{com, i}$ being the CV of the community biomass in the
+station $i$, $\overline{CV_{sp, i}}$ the average CV at the species-level in the station $i$, weighted by the relative biomass of the species, $B_{k,i}$.
 Synchrony of the station $i$, $\phi_i$, is the ratio between the variance of
-total biomass over time ($\sigma^2_{x_{T,i}}$) and the sum of the variance of
-population biomass over time ($\sigma_{x_k}$), $i$ being the station $i$ and $k$
+community biomass over time ($\sigma^2_{x_{T,i}}$) and the sum of the variance of
+population biomass over time ($\sigma_{x_{k,i}}$), $i$ being the station $i$ and $k$
 the species $k$ [@loreau_species_2008].
@@
 
-## Species richness and foodweb structure
+## Species richness and food-web structure
 
@@
 We determined the network structure in two steps: (1) build a metaweb describing the
-trophic interactions between all trophic species and the resources (Fig.
+trophic interactions between all fishes and the resources (Fig.
 \@ref(fig:matmet)B), then (2) determine network of a given community by
-extracting the metaweb according to the trophic species present at a given
+extracting the metaweb according to the fishes present at a given
 site and sampling event (Fig. \@ref(fig:matmet)C and D).
@@
 of stream fishes, as for many organisms, shifts throughout an individual's life,
-and thereby with body size. For example, alvins feed on plankton while adults
+and thereby with body size. For example, larvae and small juveniles feed on plankton while adults
 may feed on algae and fishes, with bigger individuals eating bigger fishes. Each
 fish species was hence divided in nine body size classes, each corresponding to
-a trophic species (Fig. S2). Additionally to the trophic species, we added
+a trophic species (appendix B, Fig. S2). Additionally to the trophic species, we added
 seven resource nodes present in the ontogenic food diet database: detritus,
@@
 database was filled according to fishbase and literature (appendix A, Table S2). Each
-fish species had two or three life stages which are delimited by a body size
-range (Fig. S2). The life stage of a fish trophic species was determined with
-the center of its body size range, hereafter midpoint (Fig. S2).
+fish species had two or three life stages which are delimited by its body size
+range (appendix B, Fig. S2). The life stage of a fish trophic species was determined by 
+the center of its body size range, hereafter midpoint (appendix B, Fig. S2).
 
@@
 @hart_handbook_2008]. Then, a trophic link was set between the piscivorous
-trophic species and every trophic species whose midpoint was included in the
-predation window (Fig. S2). The fish-resource trophic links were set between
-the trophic species and the resources nodes according the food diet of their
-size class.  Lastly, the trophic links among resource nodes were set according
-to the literature [@allan_stream_2007; @hart_handbook_2008].
+trophic species and every trophic species whose midpoint in bodysize range was
+included in the predation window (appendix B, Fig. S2). The fish-resource trophic links were
+set between the trophic species and the resources nodes according the food items
+of their size class.  Lastly, the trophic links among resource nodes were set
+according to the literature [@allan_stream_2007; @hart_handbook_2008].
 
@@
 interactions divided by the number of interactions if all species interact
-together ($C = L / N^2$, L and N being resp. the number of links and of nodes).
+($C = L / N^2$, L and N being resp. the number of links and of nodes).
 The trophic level of the nodes was computed as one added to the average trophic
@@
 and average trophic level over time was used in subsequent analysis.
-
-```{r, fig.show = "hide"}
-myload(
-  hab_analysis,
-  temporal_station_desc,
-  temporal_press_polluants,
-  geo_station,
-  dir = mypath("data")
-)
-habitat_press <- build_habitat_pressure_dataset(
-  .habitat_analysis = hab_analysis,
-  .tmp_press = temporal_press_polluants,
-  .tmp_st_desc = temporal_station_desc,
-  .geo_st = geo_station 
-)
-
-# Make PCA 
-habitat_press %<>% na.omit()
-mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())
-
-pca_rotated <- compute_rotated_pca(
-  .data = habitat_press[, mask],
-  naxis = 2
-)
-habitat_pressure <- 
-  cbind(habitat_press[, c("station", "temperature_med", "alt")], pca_rotated$rotated$score) %>%
-  as_tibble
-ggplot(habitat_pressure, aes(x = RC2, y = temperature_med)) +
-  geom_point()
-
-ggplot(
-  pivot_longer(habitat_pressure, cols = c("RC1", "RC2"),
-    names_to = "variable", values_to = "value"
-  )
-  , aes(x = value)) +
-geom_histogram() +
-facet_grid(cols = vars(variable))
-
-mysave(habitat_press, habitat_pressure, dir = mypath("data"), overwrite = TRUE)
-
-```
-
-```{r}
-prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
-  map_dbl(., ~round(.x * 100))
-tot_var_expl_pca <- sum(prop_var_expl_pca) 
-```
 
@@
 We characterised the sites by their altitude, slope, distance from
-source, stream width and depth and its strahler order, i.e. its position in the
-stream network. We obtained data on water temperature and flow from the naiades
+source, stream width, depth and strahler order, i.e. its position in the
+stream network hierarchy. We obtained data on water temperature, flow and Biological Oxygen
+Demand (BOD) from the naiades
 database
@@
 interpolation of the water temperature and flow based on the spatial stream
-network [@isaak_applications_2014; @hoef_ssn:_2014]. The interpolation procedure
+network models [@isaak_applications_2014; @hoef_ssn:_2014]. The interpolation procedure
 is detailed in appendix B (part 1.4).
@@
 for water temperature for which the record began in 2006. Then, we computed the
-average and CV values of water temperature, flow, Biological Oxygen Demand (BOD), river width and
+average and temporal CV values of water temperature, flow, BOD, river width and
 depth. As habitat and environmental variables are often collinear, a principal
@@
 the analysis the two first principal components based on the elbow method, on
-the eigenvalues distribution (Fig. S4). The two first principal components
-explained `r tot_var_expl_pca`% of the variance (Fig. S4). A varimax axis rotation was
+the eigenvalues distribution (appendix B, Fig. S4). The two first principal components
+explained `r tot_var_expl_pca`% of the variance (appendix B, Fig. S4). A varimax axis rotation was
 performed to maximize the representation of the environmental variables by the principal
@@
 reversed the values of the second axis, such as it represented a gradient of
-increasing average water temperature, BOD and decreasing altitude and slope.
+increasing average water temperature, average BOD and decreasing altitude and slope.
 Further description of the variables are provided in appendix B (part 1.4).
@@
 
-Structural Equation Modeling enables to assess multivariate relationships
-between variables. It is a promising way to go beyond bivariate relationships
-and to investigate complex relationships, direct and indirect, between variables
-[@grace_structural_2008; @grace_causal_2014; @lefcheck_piecewisesem_2016;
-@grace_integrative_2016]. We defined a structural equation model explaining the
-average annual total biomass as a function of the two synthetic environmental
-variables, species richness and foodweb structure [@maureaud_biodiversityecosystem_2019;
-@woods_testing_2020]. We assumed that both species richness and network
-structure directly affect total biomass (Fig. \@ref(fig:sem-plot)A)
-and that species richness affected foodweb structure [@winemiller_must_1989;
+We analyzed the relationships among environment, species richness, food-web
+structure, community biomass and its temporal stability with structural equation
+models as they enable the assessment of potential indirect and direct causal
+relationships among multiple variables [@grace_structural_2008;
+@grace_causal_2014; @lefcheck_piecewisesem_2016; @grace_integrative_2016].  We
+defined a structural equation model explaining the median annual community
+biomass as a function of the two synthetic environmental variables, species
+richness and food-web structure [@maureaud_biodiversityecosystem_2019;
+@woods_testing_2020]. We assumed that both species richness and food-web
+structure directly affect community biomass (Fig. \@ref(fig:sem-plot)A) and that
+species richness affected food-web structure [@winemiller_must_1989;
 @dunne_network_2006; @thebault_stability_2010].
 
-We used the same model structure for temporal stability of biomass (Fig.
-\@ref(fig:sem-plot)C). Instead of the annual total biomass, we modelled the
-synchrony and $\overline{CV_{sp}}$ which in turn determined the temporal
-stability of biomass.
-
-The structural equation models were based on Gaussian linear models. All variables
+We used the same model structure to assess the drivers of temporal stability
+of community biomass (Fig.  \@ref(fig:sem-plot)C). Instead of the
+annual community biomass, we modelled the synchrony and $\overline{CV_{sp}}$ which
+in turn determined the temporal stability of community biomass.
+
+The structural equation models were based on Gaussian linear mixed-effects models. All variables
 except the connectance and average trophic level
-were logged to fulfill model assumptions (see residual plots and data
-transformation in Fig. S5 and S6, Table S5). We set the seven
+were log-transformed to fulfill model assumptions (see residual plots and data
+transformation in Fig. S5 and S6, Table S5, appendix B). We set the seven
 hydrographic basins as a random effect on the intercept to
 account for their heterogeneity. We checked for the absence of multicollinearity 
-with Variance Inflation Factor (VIF, Table S6). The slopes reported
+with Variance Inflation Factor (VIF, Table S6, appendix B). The slopes reported
 in the main text were standardized in order to compare their magnitude ($r_\delta
@@
 predictive variable $x$ and of the response variable $y$). The paths whose
-slope had a $P$ value inferior to $0.05$ were reported in the main text, all the
+slope had a $P$ value inferior or equal to $0.05$ were reported in the main text, all the
 path values are presented in Table S7 and S8.
 
-Indirect effects on total biomass and its temporal stability
+Indirect effects on community biomass and its temporal stability
 were computed by multiplying slopes along the path. Only significant direct
-slopes were entered in the calculation of indirect effects. Total effects were
+slopes were included in the calculation of indirect effects. Total effects were
 computed as the sum of direct and indirect effects.
@@
   select(- 9) %>%
-  filter(P.Value < 0.05)
+  filter(P.Value <= 0.05)
 
@@
   select(- 9) %>%
-  filter(P.Value < 0.05)
+  filter(P.Value <= 0.05)
 ```
@@
   "Metamodel of the Structural Equation Models for the (A) median of annual
-  total biomass (in grams by square meter) and (C) its temporal stability.",
+  community biomass (in grams by square meter) and (C) its temporal stability.",
   "Results of the Structural Equation Models for
-  (B) the median of annual total biomass and (D) its temporal stability. Red and black
+  (B) the median of annual community biomass and (D) its temporal stability. Red and black
   arrows represent respectively negative and positive path coefficients. The
   path coefficients are standardized. For convenience, only significant
-  paths (i.e. $P < 0.05$) are shown. Rsq: Ajusted $R^2$; Avg:
+  paths (i.e. $P < 0.05$) are shown. Rsq: Adjusted $R^2$; Avg:
   Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
@@
 biomass (resp. $R^2 = .43$, $.38$, $.46$, $.47$ and $.32$) but less so for mean
-trophic level ($R^2 =
-.11$, Fig. \@ref(fig:sem-plot)B and D). Species richness had a
-significant negative effect on mean trophic level ($r_\delta = 
-`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_ct`$, Fig.
-\@ref(fig:sem-plot)B and D), meaning that a part of the effects of species
-richness went through network structure.
-
-## Species richness and average trophic level are positively correlated with total biomass
+trophic level ($R^2 = .11$, Fig. \@ref(fig:sem-plot)B and D). We found a
+negative relationship between species richness and mean trophic level ($r_\delta
+= `r rich_on_tlvl`$, $r_\delta$ meaning standardized slope) and connectance
+($r_\delta = `r rich_on_ct`$, Fig.  \@ref(fig:sem-plot)B and D), meaning that a
+part of the effects of species richness on community biomass and its temporal
+stability went through food-web structure.
+
+## Species richness and average trophic level are positively correlated with community biomass
 
@@
 Species richness and mean trophic level had a significant positive direct effect
-on total biomass ($r_\delta = `r rich_on_bm$direct`$ and 
+on community biomass ($r_\delta = `r rich_on_bm$direct`$ and 
 $r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-plot)B, Table
@@
 
-The two PCA axes capturing environmental variables had no significant direct
-effects on total biomass, but indirect (Table \@ref(tab:indir-sem)). The first
-axis, related to the stream size, was positively linked to total biomass
+The two PCA axes synthesising environmental variables had no significant direct
+effects on community biomass, but indirect (Table \@ref(tab:indir-sem)). The first
+axis, related to the stream size, was positively linked to community biomass
 ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
@@
 annual temperature was positively related
-to total biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
+to community biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
 \@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
 `r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The total effect
-of PCA1, PCA2 and species richness on total biomass were of the same magnitude.
-
-## Temporal stability of annual biomass
-
-By its effects on synchrony and $\overline{CV_{sp}}$, species richness had a
+of PCA1, PCA2 and species richness on community biomass were of the same magnitude.
+
+## Temporal stability of annual community biomass
+
+By its effects on synchrony and $\overline{CV_{sp}}$, which respectively
+measures the level of compensatory dynamics among population and the average
+population variability, species richness had a
 negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
@@
   "Direct, indirect and total effects of environment, species richness,
-  connectance and mean trophic level on total biomass
+  connectance and mean trophic level on community biomass
   and its temporal stability. Indirect effects are computed by multiplying the
@@
 #effects to total biomass and its stability, going through species richness and
-#foodweb structure. It is the first direct assessment of a possible joint effect
+#food-web structure. It is the first direct assessment of a possible joint effect
 #of species richness and network structure on both total biomass and its temporal
@@
 
-## Species richness increased total biomass but decreased its temporal stability
-
-We found that species richness increased total biomass as already found in salt
-marshes, grasslands and forests [@hector_plant_1999; @tilman_biodiversity_2014;
-@wu_relationship_2015; @li_relationship_2018] as well as in streams
-[@woods_testing_2020]. The positive effect of species richness on total biomass
+## Species richness increased community biomass but decreased its temporal stability
+
+We found that species richness increased community biomass as already
+found in plant and tree communities [@hector_plant_1999;
+@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018] as well
+as in fish communities [@maureaud_biodiversityecosystem_2019;
+@woods_testing_2020]. The positive effect of species richness on community biomass
 might be due to resource use complementarity [@carey_determining_2011], which is
-held by niche differentiation [@loreau_biodiversity_1998;
-@loreau_partitioning_2001] or to the higher probability of getting high biomass
-species with higher species richness [@loreau_biodiversity_2001]. Our results are 
-also in agreement with a model predicting a positive relationship between animal
-diversity and total consumer biomass in size-structured foodweb
+driven by niche differentiation [@loreau_biodiversity_1998;
+@loreau_partitioning_2001] or to the higher probability to include high biomass
+species with higher species richness [@loreau_biodiversity_2001]. Our results
+are also in agreement with a model predicting a positive relationship between
+animal diversity and total consumer biomass in size-structured food-web
 [@schneider_animal_2016].
@@
 [@pennekamp_biodiversity_2018] with studies on natural communities such as
-butterflies  or lotic fishes [@olivier_urbanization_2020; @franssen_annual_2011;
-@houlahan_priority_2017], where positive relationships were found between temporal
+butterflies  or lotic fishes [@olivier_urbanization_2020; @franssen_annual_2011
+], where positive relationships were found between temporal community
 stability and species richness. However, some other studies also found a
 negative relationship, for instance in natural grasslands [@yang_effects_2011]
-or in natural forests as a marginal trend [@declerck_species_2006].
+or a marginal relationship in natural forests [@declerck_species_2006].
 
@@
 [@jiang_different_2009].
-In foodwebs, theoretical models predict that the relationship between temporal
+In food-webs, theoretical models predict that the relationship between temporal
 stability of populations and species richness depends on interaction strength
 and its distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
-@downing_temporal_2020], high interaction strength inducing a negative
-relationship. Therefore, it is possible that our results are due to strong
-trophic interactions, leading to more fluctuations in population biomass.
+@downing_temporal_2020], with stronger interactions promoting a negative
+relationship between species richness and stability. Therefore, it is possible
+that our results are due to strong trophic interactions, leading to more
+fluctuations in population biomass, but this hypothese was not testable with the
+available dataset.
 
@@
 
-## Average trophic level increased total biomass and its temporal stability while connectance had no effect
-
-The average trophic level was positively linked to total biomass.
+## Average trophic level increased community biomass and its temporal stability while connectance had no effect
+
+The average trophic level was positively linked to community biomass.
 @wang_biodiversity_2018 have shown that total nutrient uptake might increase
-with the length of trophic chains and so results in higher total biomass. While
+with the length of trophic chains and so results in higher community biomass. While
 the predictions of @wang_biodiversity_2018 were restricted to food chains, and
-thus might not hold in more complex foodwebs with omnivory, our
+thus might not hold in more complex food-webs with omnivory, our
 results are in agreement with their model predictions and highlight the
-importance of food chain length as a determinant of total biomass in foodwebs.
+importance of food chain length as a determinant of community biomass in food-webs.
 In addition, mean trophic level had a positive effect on biomass stability by
-its negative effect on $\overline{CV_{sp}}$, thereby increasing average species
-stability. It might result from a higher stability of higher trophic level as
-predicted by food chain models in the presence of strong top-down control
-[@shanafelt_stability_2018; @barbier_pyramids_2019]. An alternative
-explanation is that higher mean trophic level complexify the biomass pathways
-through the foodwebs, which might reduce biomass fluctuations in lower trophic
-levels [@mccann_diversitystability_2000].
-
-In contrast, connectance had no effect on total biomass. One might have expected
+its negative effect on $\overline{CV_{sp}}$, thereby increasing average
+population 
+stability. This effect might result from a higher stability of population of higher
+trophic level as predicted by food chain models in the presence of strong
+top-down control [@shanafelt_stability_2018; @barbier_pyramids_2019]. An
+alternative explanation is that higher mean trophic level complexify the biomass
+fluxes through the food-webs, which might reduce biomass fluctuations in lower
+trophic levels [@mccann_diversitystability_2000].
+
+In contrast, connectance had no effect on community biomass. One might have expected
 that an increase in connectance may translate in a higher total nutrient uptake
-and so results in higher total biomass in the fish compartment. 
+and so results in higher community biomass in the fish compartment. 
 However, some studies suggest that a greater connectance should decrease
 complementarity in resource use between species, which is expected to
-lower total biomass [@thebault_food-web_2003; @poisot_trophic_2013].
+lower community biomass [@thebault_food-web_2003; @poisot_trophic_2013].
 
@@
 considered different stability concepts and metrics [@arnoldi_resilience_2016].
-The lack of effect of connectance on the temporal stability of total biomass
+The lack of effect of connectance on the temporal stability of community biomass
 might be related to the fact that our measure of connectance does not take into
-account the distribution of interaction strengths in the foodwebs. Indeed,
-foodweb connectance is expected to have different consequences on the temporal
-stability of total biomass depending on the strength of trophic interactions
-[@thebault_trophic_2005]. However, our foodwebs lack information about the lower
+account the distribution of interaction strengths in the food-webs. Indeed,
+food-web connectance is expected to have different consequences on the temporal
+stability of community biomass depending on the strength of trophic interactions
+[@thebault_trophic_2005]. However, our food-webs lack information about the lower
 compartments of the community, i.e. primary producers, decomposers and the benthic
-part of the foodweb. Further research should examine the effects of connectance
-on total biomass and its temporal stability in more complete empirical foodwebs.
+part of the food-web. Further research should examine the effects of connectance
+on community biomass and its temporal stability in more complete empirical food-webs.
 
@@
 
-## Population stability was the main driver of temporal stability
+## Population stability was the main driver of community temporal stability
 
 In contrast with previous studies, we found that the average population
-variability ($\overline{CV_{sp}}$) had a stronger negative effect on biomass
+variability ($\overline{CV_{sp}}$) had a stronger negative effect on community biomass
 stability than synchrony [@tilman_biodiversity_2006;
 @olivier_urbanization_2020]. It explains why we observe a negative effect of
-species richness on temporal stability of biomass. The lower effect of synchrony
+species richness on temporal stability of community biomass. The weaker effect of synchrony
 might be explained by the presence of generalist predators in stream
-communities, that raise synchrony between prey species that share the
+communities, which can promote synchrony between prey species that share the
 same predator and thus reduces compensatory
 population dynamics [@raimondo_interspecific_2004]. Alternatively, it is
-possible that, in aquatic foodwebs, the occurrence of large oscillatory dynamics
+possible that, in aquatic food-webs, the occurrence of large oscillatory dynamics
  leads to a higher contribution of population
 variability rather than synchrony to community stability
-[@mccann_reevaluating_1997]. How both strengths and the relative contribution of
-synchrony and population variability to overall stability vary between
-foodwebs and single trophic communities is still an open question.
+[@mccann_reevaluating_1997]. How both strengths of interactions and the relative
+contribution of synchrony and population variability to overall stability vary
+between food-webs and single trophic communities is still an open question.
 
@@
 
-## Environment had an strong effect on total biomass and its temporal stability
-
-We found that environmental drivers affect total biomass mostly indirectly
+## Environment had an strong effect on community biomass and its temporal stability
+
+We found that environmental drivers affect community biomass mostly indirectly
 [@woods_testing_2020] rather than directly, contrasting with previous studies
@@
 @maureaud_biodiversityecosystem_2019]. First, consistent with research showing
-that foodwebs in wider streams support more species and biomass
+that food-webs in wider streams support more species and biomass
 [@allan_stream_2007], we found that the PCA axis related to stream size had a
-positive effect on total biomass through a positive effect on mean trophic level
-and species richness. Greater ecosystem size might provide a greater diversity
+positive effect on community biomass through a positive effect on mean trophic level
+and species richness. Greater ecosystem size might provide a higher diversity
 of resources through habitat heterogeneity, and so higher species richness and
-total biomass by surface unit, through resource complementarity. Greater
+community biomass by surface unit, through complementarity in resource use. Greater
 diversity of resources can also maintain more biomass at high trophic level
 [@post_ecosystem_2000; @doi_resource_2009]. Second, the positive effect of the
-PCA axis related to temperature on total biomass was of the magnitude of the
-effects of network structure and species richness, in line with the mounting
+PCA axis related to temperature on community biomass was of the magnitude of the
+effects of food-web structure and species richness, in line with the mounting
 body of work reporting important effects of temperature on the structure and
@@
 While the PCA axis related to stream size had only a weak effect on the
-temporal stability of total biomass, the PCA axis related to temperature had a
+temporal stability of community biomass, the PCA axis related to temperature had a
 negative effect on temporal stability through a direct destabilizing
@@
 with temperature in our study. Enrichment can increase CV by
-increasing species biomass fluctuations while higher temperature might decrease
+increasing population biomass fluctuations while higher temperature might decrease
  stability through starvation resulting from high metabolic activity
@@
 ---
-## Final thoughts about empirical foodwebs
+## Final thoughts about empirical food-webs
 
@@
 empirical findings on the functioning and stability of communities. Our study
-extends the assessment of the effect of species richness on total biomass and
-its temporal stability to the case of foodwebs in natural settings and
-highlights the need to consider species richness, network structure and their
+extends the assessment of the effect of species richness on community biomass and
+its temporal stability to the case of food-webs in natural settings and
+highlights the need to consider species richness, food-web structure and their
 dependence to understand both functioning and stability of communities. Further,
@@
 ecosystem size are largely mediated by their impact on richness and average
-trophic level. Finally, our results highlight species variability as key in
+trophic level. Finally, our results highlight population variability as key in
 transmitting effects of richness, network structure and environmental gradients
@@
 further confirmation are needed, might be characteristic of animal and/or
-multi-trophic communities.
+multi-trophic communities. Food-web reconstruction methods enable to confront
+theory and experiment to empirical data. With the increasing availability of
+long-term empirical data, we believe that those methods have a great potential
+to increase our understanding of the role of food-web structure on ecosystem
+functioning.
 
@@
 library(knitr)
-include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.pdf"))
+include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.png"))
 ```

### 2021-02-17 R/plot_methods.R

@@ -1179,7 +1179,12 @@ make_troph_plot <- function (
 ##############
 #  PCA plot  #
 ##############
-my_pca_plot <- function (.data = pca_rotated$rotated, xaxis = NULL, yaxis = NULL, ctb_thld = .4) {
+my_pca_plot <- function (.data = pca_rotated$rotated,
+  xaxis = NULL, yaxis = NULL,
+  ctb_thld = .4, label_size = 2, 
+  force = 10,  force_pull = 1,
+  seed = NA
+  ) {
 
   pca_data <- .data$loadings[1:nrow(.data$loadings),]
   pca_data %<>%
@@ -1217,7 +1222,9 @@ ggplot() +
   ) +
   ggrepel::geom_label_repel(data = pca_label,
     aes_string(x = xaxis, y = yaxis, label = "variable"),
-    size = 2, force = 10, box.padding = .1, label.padding = .1
+    size = label_size,
+    force = force, force_pull = force_pull, seed = seed,
+    box.padding = .1, label.padding = .1
   )
 }
 
@@ -1303,12 +1310,12 @@ get_pca_var_name_replacement <- function () {
   out <- c(
     "slope" = "Slope",
     "alt" = "Altitude",
-    "d_source" = "Distance from source",
+    "d_source" = "Spring dist",
     "strahler" = "Strahler order",
-    "width_river_mean" = "Avg stream width",
-    "avg_depth_station_mean" = "Avg stream depth",
-    "width_river_cv" = "CV stream width",
-    "avg_depth_station_cv" = "CV stream depth",
+    "width_river_mean" = "Avg width",
+    "avg_depth_station_mean" = "Avg depth",
+    "width_river_cv" = "CV width",
+    "avg_depth_station_cv" = "CV depth",
     "DBO_med" = "Avg BOD",
     "flow_med" = "Avg flow",
     "temperature_med" = "Avg temperature",

### 2021-02-17 map.R

@@ -3,10 +3,10 @@
 #################
 
 
+library(raster)
 library(tidyverse)
 library(magrittr)
 library(sf)
-library(raster)
 mypath <- rprojroot::find_package_root_file
 source(mypath("R", "plot_methods.R"))
 source(mypath("R", "misc.R"))
@@ -106,7 +106,7 @@ country_points[country_points$name == "Spain", c("X", "Y")] <- c(300000, 6150000
 country_points[country_points$name == "Italy", c("X", "Y")] <- c(1300000, 6450000) 
 
 ocean <- data.frame(X = 200000, Y = 6500000, name = "atlantic \n ocean")
-sea <- data.frame(X = c(450000, 900000), Y = c(7025000, 6180000), name = c("Manche \n sea", "Mediterranean \n sea"))
+sea <- data.frame(X = c(450000, 900000), Y = c(7025000, 6180000), name = c("English \n sea", "Mediterranean \n sea"))
 
 basin_inner <- basin %>% 
         rmapshaper::ms_innerlines() %>% 
@@ -114,37 +114,36 @@ basin_inner <- basin %>%
         st_as_sf()
   #
 # Font size
-font_size <- 10 
-    
+font_size <- 10
+size_label <- 3.5
+   
 p <- ggplot() +
   geom_sf(data = st_geometry(world)) +
   # Coutry
   geom_text(data= country_points,aes(x=X, y=Y, label=toupper(name)),
-    color = "black", fontface = "bold", size = 2, check_overlap = FALSE) +
+    color = "black", fontface = "bold", size = size_label, check_overlap = FALSE) +
   # Ocean + sea
   geom_text(data= ocean,aes(x=X, y=Y, label=toupper(name)),
-    color = "darkblue", fontface = "bold", check_overlap = FALSE, size = 2) +
+    color = "darkblue", fontface = "bold", check_overlap = FALSE, size = size_label) +
   geom_text(data= sea,aes(x=X, y=Y, label=name),
-    color = "darkblue", fontface = "bold", check_overlap = FALSE, size = 2) +
+    color = "darkblue", fontface = "bold", check_overlap = FALSE, size = size_label) +
   #theme_map() +
-    # Plot basin
-    geom_sf(data = basin_inner) +
-    # raster comes as the first layer, municipalities on top
-    #geom_raster(data = hillshade,
-      #aes(x = x, y = y, alpha = value)) +
[…]

### 2021-02-17 manuscript/bef_stability/sem_relationship.Rmd
Produce sem indiv plot

---
title: test
---

```{r}
library(tidyverse)
library(magrittr)
library(cowplot)
library(nlme)
library(ggeffects)

mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "local_network_build.R"))
theme_set(theme_cowplot())
```

# Prepare data

```{r}
myload(sem_data, community_metrics, op_analysis, dir = mypath("data"))
community_metrics %<>%
    left_join(select(op_analysis, station, opcod, year))

stab_sem_rich <- compute_stab_sem_rich(.data = as.data.frame(sem_data),
  random_effect = as.formula("~1|basin"), get_sem = TRUE)

bm_sem_rich <- compute_prod_sem_rich(.data = as.data.frame(sem_data),
  random_effect = as.formula("~1|basin"), get_sem = TRUE)
```

# Make function

```{r}
get_y_x_comb_from_model <- function(mod = NULL) {

  x_terms <- labels(terms(mod))
  all_terms <- dimnames(attr(terms(mod), "factors"))[[1]]

  y_term <- all_terms[! all_terms %in% x_terms]

  tibble(
    y = y_term, 
    x = x_terms 
  )
}

get_predict_from_model_x <- function (mod = NULL, term = NULL) {
  ggpredict(mod, terms = c(term)) %>%
    as.tibble()
}

get_predict_plot_from_model_x <- function (mod = NULL, x = NULL) {

  stopifnot(is.character(x))

  pred <- get_predict_from_model_x(mod = mod, term = x)

  y <- unique(get_y_x_comb_from_model(mod = mod)$y)

  dataset <- mod$data

  # In case of classic lm model:
  if (is.null(dataset)) {
    dataset <- mod$model
  }

  p <- dataset %>%
    ggplot(aes_string(y = y, x = x)) +
    geom_point()

  p <- p +
    geom_line(data = pred, aes(y = predicted, x = x))

  # Axis label
  label_tmp <- get_sem_var_name_replacement()
  label <- str_replace_all(label_tmp, "\n", "") 
  names(label) <- names(label_tmp)
  p +
    labs(
      x = label[x],
      y = label[y]
    )
}
```

## Test function

```{r}
test <- get_y_x_comb_from_model(stab_sem_rich[[1]])

map(test$x, ~get_predict_from_model_x(stab_sem_rich[[1]], .x))

get_predict_plot_from_model_x(stab_sem_rich[[1]], x = "log_RC1")
```

# Produce plot

```{r}
class(stab_sem_rich) <- "list"
# drop data element from the list
stab_sem_rich[[length(stab_sem_rich)]] <- NULL

ti <- tibble(model = stab_sem_rich,
  comb_term = map(model, ~try(get_y_x_comb_from_model(.x)))) %>%
  unnest(comb_term)
stab_plot <- 
  ti %>%
  mutate(
    gg = map2(x, model, ~try(get_predict_plot_from_model_x(mod = .y, x = .x)))
  )
plot_grid(plotlist = stab_plot$gg)

# Write plots:
map(stab_plot$gg,
  ~save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      paste0(
	"stab_",
	names(.x$labels$y),
	"_",
	names(.x$labels$x),
	".png"
      )
      ), .x) 
)

mysave(stab_plot, mypath("manuscript", "bef_stability", "result"), overwrite = TRUE)
```

```{r}
class(bm_sem_rich) <- "list"
# drop data element from the list
bm_sem_rich[[length(bm_sem_rich)]] <- NULL

bm_mod <- tibble(model = bm_sem_rich,
  comb_term = map(model, ~try(get_y_x_comb_from_model(.x)))) %>%
  unnest(comb_term)
bm_plot <- 
  bm_mod %>%
  mutate(
    gg = map2(x, model, ~try(get_predict_plot_from_model_x(mod = .y, x = .x)))
  )
plot_grid(plotlist = bm_plot$gg)

# Write plots:
map(bm_plot$gg,
  ~save_plot(file = mypath(
      "manuscript", "bef_stability", "result", 
      paste0(
	"bm_",
	names(.x$labels$y),
	"_",
	names(.x$labels$x),
	".png"
      )
      ), .x) 
)
mysave(bm_plot, mypath("manuscript", "bef_stability", "result"), overwrite = TRUE)
```

### 2021-02-18 manuscript/bef_stability/appendixB.Rmd
Sensivity analysis for referee two and three

@@
 
-  params <- sem$coefficients
-  colnames(params)[length(colnames(params))] <- "Stars"
+  params <- sem$coefficients[, -length(colnames(sem$coefficients))]
+  #colnames(params)[length(colnames(params))] <- "Stars"
 
@@
 
-kable(format_coef_table(stab_sem_rich),
+format_coef_table(stab_sem_rich) %>%
+  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
+  kable(
     format = "latex",
@@
 
-kable(format_coef_table(bm_sem_rich),
+format_coef_table(bm_sem_rich) %>%
+  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
+kable(
   format = "latex",

### 2021-02-18 manuscript/bef_stability/fig2.Rmd
Sensivity analysis for referee two and three

---
title: "Figure 2"
---

```{r}
library(tidyverse)
library(magrittr)
library(cowplot)

mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

source(mypath("R", "misc.R"))
source_dir(mypath("R"))
```

```{r}
load(mypath("manuscript", "bef_stability", "result", "workspace.rda"))
ti <- stab_sem_rich$coefficients[,-9] %>%
  filter(P.Value <= 0.05) %>%
  mutate(
    std_est = round(Std.Estimate, 2),
    abs_std_est = abs(std_est)
  )
ti %>%
  mutate(width_arrow = abs_std_est * 0.3 / min(abs_std_est)) %>%
  select(Response, Predictor, Estimate, Std.Estimate:width_arrow)
```
```{r}
ti <- bm_sem_rich$coefficients[,-9] %>%
  filter(P.Value <= 0.05) %>%
  mutate(
    std_est = round(Std.Estimate, 2),
    abs_std_est = abs(std_est)
  )
ti %>%
  mutate(width_arrow = abs_std_est * 0.3 / min(abs_std_est)) %>%
  select(Response, Predictor, Estimate, Std.Estimate:width_arrow)
```

### 2021-02-18 manuscript/bef_stability/review_analysis.Rmd
Sensivity analysis for referee two and three

---
title: "Analyse from review"
output: bookdown::html_document2
---

```{r, message = FALSE, results = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  comment = "#>",
  cache = TRUE,
  echo = FALSE,
  warning = FALSE,
  warnings = FALSE
)
#knitr::opts_chunk$get()
```

```{r}
mypath <- rprojroot::find_package_root_file

library(tidyverse)
library(cowplot)
library(magrittr)

source(mypath("R", "misc.R"))
source_dir(mypath("R"))

theme_set(theme_alain())

myload(sem_data, synchrony, dir = mypath("data"))
```

# Response to the comment R1-5

We check that $CV_{com, i} = \overline{CV_{sp, i}} \times \sqrt{\phi_i}$

```{r}
synchrony %>%
  ggplot(aes(y = cv_sp * sqrt(synchrony), x = cv_classic)) +
  geom_point() +
  labs(y = "CVsp * sqrt(synchrony)", x = "CV of biomass")
```

# Response to the comment R3-1

```{r}

mod <- lm(log_stab_std ~ 0 + log_cv_sp + log_sync, data = sem_data)

#summary(mod)
coefs <- broom::tidy(mod) %>%
  select(term,estimate)

coefs %<>%
  mutate(
    sd = map_dbl(term, ~sd(sem_data[[.x]])),
    coef_std = (estimate * sd) / sd(sem_data$log_stab_std)
  )

# SD de la variable de Olivier et al. (2020):  
sd(log(1 / sem_data$sync))
sd(log(1 / sem_data$cv_sp))
```

# Response to the comment R3-L231

```{r}
myload(op_analysis, dir = mypath("data"))

# station used in sem_data
op <- op_analysis %>%
  filter(station %in% sem_data$station)

## Combien de station par année
op %>%
  group_by(year) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x = year, y = n)) +
  geom_bar(stat = "identity")
```

```{r, fig.cap=""}
match_op_temp_data <- op %>%
  group_by(station) %>%
  summarise(
    year_temp = length(which(year %in% seq(2006, 2018))),
    year_temp_percent = length(which(year %in% seq(2006, 2018))) / n()
  )

match_op_temp_data %>%
  ggplot(aes(x = year_temp)) +
  geom_histogram() +
  labs(y = "Frequency", x = "Nb year of overlap between sampling and temperature time series")

match_op_temp_data %>%
  ggplot(aes(x = year_temp_percent)) +
  geom_histogram() +
  labs(y = "Frequency", x = "Percent of sampling years which overlaps with temperature time series")
```

```{r}
library(nlme)

myload(biomass_ts_sax, habitat_pressure, dir = mypath("data"))
myload(network_metrics, dir = mypath("data", "classes"))

# Get op only from 2006: 
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
op_analysis_bbb_start_2006 <- op_analysis_bbb %>%
  filter(year >= 2006) 
# Select station followed 10 years or more
op_analysis_bbb_start_2006 %<>%
  group_by(station) %>%
  filter(n() >= 10) %>%
  ungroup()

st_basin <- get_basin_station()

sem_data_2006 <- compute_sem_dataset_from_op(
  .op = op_analysis_bbb_start_2006,
  habitat_pressure = habitat_pressure,
  st_basin = st_basin
)

stab_sem_rich_2006 <- compute_stab_sem_rich(
  .data = sem_data_2006,
  random_effect = as.formula("~1|basin")
)
stab_sem_rich <- compute_stab_sem_rich(
  .data = sem_data,
  random_effect = as.formula("~1|basin")
)
data_sensivity_2006 <- list(
  full = sem_data,
  from_2006 = sem_data_2006 
)

nb_station <- map_int(data_sensivity_2006, ~length(unique(.x$station)))
```

```{r stab}
stab_sensivity_2006 <- 
  map(data_sensivity_2006,
    ~compute_stab_sem_rich(
      .data = .x,
      random_effect = as.formula("~1|basin")
    )
  )

sem_stab_results_2006 <- map(stab_sensivity_2006,
  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
  enframe() %>%
  rename(dataset = name) %>%
  unnest(value)

# Reformat
colnames(sem_stab_results_2006) <- str_to_lower(colnames(sem_stab_results_2006))

p_sens_stab <- plot_sensivity_analysis(
  .data = sem_stab_results_2006,
  inverse_label_order = TRUE, 
  y_lim = c(-1.5, .75)
  ) +
scale_color_manual(
  values = c("full" = "red", "from_2006" = "blue"),
  labels = c("Full dataset", "Dataset from 2006"),
  breaks = c("full", "from_2006") 
  ) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
```

```{r}
bm_sensivity_2006 <- 
  map(data_sensivity_2006,
    ~compute_prod_sem_rich(
      .data = .x,
      random_effect = as.formula("~1|basin")
    )
  )
sem_bm_results_2006 <- map(bm_sensivity_2006,
  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
  enframe() %>%
  rename(dataset = name) %>%
  unnest(value)

# Reformat
colnames(sem_bm_results_2006) <- str_to_lower(colnames(sem_bm_results_2006))

p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results_2006,
  inverse_label_order = TRUE,
  y_lim = c(-1.5, .75)
  ) +
scale_color_manual(
  values = c("full" = "red", "from_2006" = "blue")
  ) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
```

```{r start-sens, fig.dim = c(14, 10), fig.cap="Sensivity of standardized estimate to the station starting date."}
legend_b <- get_legend(p_sens_stab)

p <- plot_grid(
  p_sens_bm %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  p_sens_stab %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  legend_b, nrow = 3,
  rel_heights = c(1, 1, .1),
  labels = c("Total biomass", "Biomass stability")
)
p
```

## L180-182

```{r}
library(nlme)

compute_bm_sem_rich_var <- function(.data, rich_var = "log_rich_tot_std", random_effect = "~ 1 | basin", get_sem = FALSE) {

  formula_list <- list(
    rich = paste0(rich_var, " ~ log_RC1 + log_RC2"),
    ct = paste0("ct ~ log_RC1 + log_RC2 + ", rich_var),
    t_lvl = paste0("t_lvl ~ log_RC1 + log_RC2 + ", rich_var),
    bm = paste0("log_bm_std ~ ", rich_var," + ct + t_lvl + log_RC1 + log_RC2")
  )
  model_list <- map(formula_list, function(x)  {
    temp_model <- nlme::lme(as.formula(x), random = ~ 1 | basin, data = .data)
    temp_model$call$fixed <- as.formula(x)
    return(temp_model)
  }
    )

  corsem <- piecewiseSEM::as.psem(model_list)

  if (get_sem) {
    return(corsem)
  }
  output <- summary(corsem, .progressBar = F)

  return(output)
}
compute_stab_sem_rich_var <- function(.data, rich_var = "log_rich_tot_std", random_effect = "~ 1 | basin", get_sem = FALSE) {

  formula_list <- list(
    rich = paste0(rich_var, " ~ log_RC1 + log_RC2"),
    ct = paste0("ct ~ log_RC1 + log_RC2 + ", rich_var),
    t_lvl = paste0("t_lvl ~ log_RC1 + log_RC2 + ", rich_var),
    sync = paste0("log_sync ~ ", rich_var, " + ct + t_lvl + log_RC1 + log_RC2"),
    cvsp = paste0("log_cv_sp ~ ", rich_var," + ct + t_lvl + log_RC1 + log_RC2") 
    )

  model_list <- map(formula_list, function(x)  {
    temp_model <- nlme::lme(as.formula(x), random = ~ 1 | basin, data = .data)
    temp_model$call$fixed <- as.formula(x)
    return(temp_model)
  }
    )

  ## Add linear model
  model_list <- c(
    model_list,
    stab = list(lm(log_stab_std ~ log_cv_sp + log_sync, data = .data))
  )

  corsem <- piecewiseSEM::as.psem(model_list)

  if (get_sem) {
    return(corsem)
  }
  output <- summary(corsem, .progressBar = F)

  return(output)
}
sem_data %<>%
  mutate(log_rich_std = log(rich_std_med))
```

```{r}
rich <- names(sem_data)[str_detect(names(sem_data), "log_rich")]
```

```{r}
bm_sens_rich <- map(rich, 
  ~compute_bm_sem_rich_var(
    .data = sem_data,
    rich_var = .x, random_effect = "~ 1 | basin",
    get_sem = FALSE)
)
names(bm_sens_rich) <- rich

sem_bm_results_rich <- map(bm_sens_rich,
  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
  enframe() %>%
  rename(dataset = name) %>%
  unnest(value) %>%
  mutate_at(c("Response", "Predictor"), ~ifelse(str_detect(., "rich"), "richness", .))

colnames(sem_bm_results_rich) <- str_to_lower(colnames(sem_bm_results_rich))

cols_rich <- c(
  "log_rich" = "red",
  "log_rich_std" = "blue",
  "log_rich_tot_std" = "darkgreen",
  "log_rich_tot" = "orange"
)
label_rich <- c(
  "log_rich" = "Log median richness",
  "log_rich_std" = "Log median of standardized richness",
  "log_rich_tot_std" = "Log standardized total richness",
  "log_rich_tot" = "Log total richness"
)

p_sens_bm_rich <- plot_sensivity_analysis(
  .data = sem_bm_results_rich,
  inverse_label_order = TRUE, scale_color = FALSE,
  y_lim = c(-1.5, .75)
  ) +
scale_color_manual(
  values =  cols_rich,
  labels = label_rich,
  breaks = names(label_rich)) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
```

```{r}
stab_sens_rich <- map(rich, 
  ~compute_stab_sem_rich_var(
    .data = sem_data,
    rich_var = .x, random_effect = "~ 1 | basin",
    get_sem = FALSE)
)
names(stab_sens_rich) <- rich

sem_stab_results_rich <- map(stab_sens_rich,
  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
  enframe() %>%
  rename(dataset = name) %>%
  unnest(value) %>%
  mutate_at(c("Response", "Predictor"), ~ifelse(str_detect(., "rich"), "richness", .))

colnames(sem_stab_results_rich) <- str_to_lower(colnames(sem_stab_results_rich))

cols_rich <- c(
  "log_rich" = "red",
  "log_rich_std" = "blue",
  "log_rich_tot_std" = "darkgreen",
  "log_rich_tot" = "orange"
)
label_rich <- c(
  "log_rich" = "Log median richness",
  "log_rich_std" = "Log median of species richness density",
  "log_rich_tot_std" = "Log species richness density",
  "log_rich_tot" = "Log total richness"
)

p_sens_stab_rich <- plot_sensivity_analysis(
  .data = sem_stab_results_rich,
  inverse_label_order = TRUE,
  scale_color = FALSE, y_lim = c(-1.4, .75)) +
scale_color_manual(
  values =  cols_rich,
  labels = label_rich,
  breaks = names(label_rich)) +
  guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
```

```{r rich-sens, fig.dim = c(14, 10), fig.cap="Sensivity of the standardized estimates to species richeness specification for the two structural equation model."}
legend_b <- get_legend(p_sens_stab_rich)
p <- plot_grid(
  p_sens_bm_rich %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  p_sens_stab_rich %<>% + theme(legend.position = "none", plot.margin = unit(c(0,0,0,27), units = "mm")),
  legend_b, nrow = 3,
  rel_heights = c(1, 1, .1),
  labels = c("Total biomass", "Biomass stability")
)
p
```

The choice of richness variable would

# Response to comment R3-Section 5.3

```{r}

```

### 2021-02-18 manuscript/bef_stability/sem_relationship.Rmd
Sensivity analysis for referee two and three

@@
   ggpredict(mod, terms = c(term)) %>%
-    as.tibble()
+    as_tibble()
 }
@@
 map(stab_plot$gg,
-  ~save_plot(file = mypath(
+  ~save_plot(
+    file = mypath(
       "manuscript", "bef_stability", "result", 
@@
       )
-      ), .x) 
+      ),
+    plot = .x,
+    base_height = 2.5, base_asp = 1.2#1.618 
+  ) 
 )
@@
       )
-      ), .x) 
+      ),
+    plot = .x,
+    base_height = 2.5, base_asp = 1.2#1.618 
+    ) 
 )

### 2021-02-19 manuscript/bef_stability/manuscript.Rmd
Minor edits

@@
 Biodiversity-ecosystem functioning (BEF) and food-web complexity-stability
-relationships are central to ecology. However, they remain largely untested in natural context. Here we study the links among
-environmental conditions, richness, food-web structure, annual biomass and its
-temporal stability using a standardized monitoring dataset of 99 stream fish communities
-spanning from 1995 to 2018. We first reveal that both richness and average
-trophic level are positively related to annual biomass, with effects of similar
-strength. Second, we show that food-web structure affects community stability,
-with a positive effect of mean trophic level, and contrary to
-expectation, a destabilizing effect of species richness. Finally, we
-find that environmental conditions affect both biomass and its stability via
-effects on richness and network structure. Strikingly, effects on stability are
-mediated by changes in population stability rather than synchrony, which contrasts
-with results from single-trophic communities and might be characteristic of
-multi-trophic communities.
+relationships are central to ecology. However, they remain largely untested in
+natural context. Here we study the links among environmental conditions,
+richness, food-web structure, annual biomass and its temporal stability using a
+standardized monitoring dataset of 99 stream fish communities spanning from 1995
+to 2018. We first reveal that both richness and average trophic level are
+positively related to annual biomass, with effects of similar strength. Second,
+we show that food-web structure affects community stability, with a positive
+effect of mean trophic level, and contrary to expectation, a destabilizing
+effect of species richness. Finally, we find that environmental conditions
+affect both biomass and its stability via effects on richness and network
+structure. Strikingly, effects on stability are mediated by changes in
+population stability rather than synchrony, which contrasts with results from
+single-trophic communities and might be characteristic of multi-trophic
+communities.
 
@@
 abundance of a population is compensated by the increase of another. However,
-higher connectance can counterbalance the positive effects of species
-richness on temporal stability of community biomass, by leading to a negative
-relationship between species richness and population temporal variability
+higher food-web connectance can counterbalance the positive effects of species
+richness on temporal stability of community biomass, because it may increase
+competition between consumers and then leads to a positive relationship between
+species richness and population temporal variability
 [@thebault_trophic_2005]. In addition, the presence of species at higher trophic
@@
 These challenges are even more acute for the study of the stability of ecosystem
-properties, which additionally requires longer-term
-perspectives. In this context, recent developments to predict species trophic
-interactions [@beckerman_foraging_2006; @gravel_inferring_2013; @portalier_foraging_2019], combined with observational long-term
-surveys of ecological communities, can offer the opportunity to investigate the
-links between diversity, food-web structure and the stability of total community
-biomass in natural settings.
+properties, which additionally requires longer-term perspectives. In this
+context, recent developments to predict species trophic interactions
+[@beckerman_foraging_2006; @gravel_inferring_2013; @portalier_foraging_2019],
+combined with observational long-term surveys of ecological communities, can
+offer the opportunity to investigate the links between diversity, food-web
+structure and the stability of total community biomass in natural settings.
 

### 2021-02-19 manuscript/bef_stability/table/hypothesis_sem.tex
Minor edits

\begin{tabular}{| m{7cm}| m{2cm}| m{4cm}|}
    \hline
    Link & hypothesis & reference\\
    \hline
    PCA1 Avg stream size $\to$ Species richness & (+) &
    \citet{post_ecosystem_2000, doi_resource_2009, mchugh_dual_2010} \\
    \hline
    PCA2 Avg temperature $\to$ Species richness & (+/-) & \citet{ogorman_unexpected_2017,gauzens_biodiversity_2020} \\
    \hline
    PCA1 Avg stream size $\to$ Connectance & ? & NA\\
    \hline
    PCA2 Avg temperature $\to$ Connectance & ? & NA\\
    \hline
    Species richness $\to$ Connectance & (-) & \citet{dunne_network_2006} \\
    \hline
    PCA1 Avg stream size $\to$ Avg trophic level & (+) & \citet{mchugh_dual_2010}\\
    \hline
    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & \citet{ogorman_unexpected_2017}\\
    \hline
    Species richness $\to$ Avg trophic level & ? & NA\\
    \hline
    Species richness $\to$ Synchrony & (-) & \citet{thebault_trophic_2005, loreau_species_2008, thibaut_understanding_2013} \\
    \hline
    Connectance $\to$ Synchrony & (+) & \citet{teng_dynamics_2004}\\
    \hline
    Avg trophic level $\to$ Synchrony & (+) & \citet{raimondo_interspecific_2004}\\
    \hline
    PCA1 Avg stream size $\to$ Synchrony & (-) & NA\\
    \hline
    PCA2 Avg temperature $\to$ Synchrony & (+) & \citet{loreau_species_2008}\\
    \hline
    Species richness $\to$ CVsp & (+) & \citep{tilman_biodiversity_1996} \\
    \hline
    Connectance $\to$ CVsp & NA & NA\\
    \hline
    Avg trophic level $\to$ CVsp & (-) & \citet{shanafelt_stability_2018}\\
    \hline
    PCA1 Avg stream size $\to$ CVsp & (-) & NA\\
    \hline
    PCA2 Avg temperature $\to$ CVsp & (+) & \citep{ogorman_unexpected_2017;tabi_warming_2019}\\
    \hline
    CVsp $\to$ Biomass stability & (-) & \citet{thibaut_understanding_2013}\\
    \hline
    Synchrony $\to$ Biomass stability & (-) & \citet{thibaut_understanding_2013}\\
    \hline
    Species richness $\to$ Total biomass & (+) & \citet{schneider_animal_2016}\\
    \hline
    Connectance $\to$ Total biomass & NA & \citet{wang_biodiversity_2018}\\
    \hline
    Avg trophic level $\to$ Total biomass & (+) & \citet{wang_biodiversity_2018}\\
    \hline
    PCA1 Avg stream size $\to$ Total biomass & (+) & \citet{post_ecosystem_2000, doi_resource_2009, @allan_stream_2007}\\
    \hline
    PCA2 Avg temperature $\to$ Total biomass & (+/-) & \citep{ogorman_unexpected_2017}\\
    \hline
\end{tabular}

### 2021-02-19 manuscript/bef_stability/table/hypothesis_table.Rmd
Minor edits

---
title: "Make a table for hypothesis"
output: 
  bookdown::pdf_document2:
    citation_package: natbib
biliography: references.bib
---

```{r, message = FALSE, results = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  comment = "#>",
  cache = TRUE,
  echo = FALSE,
  warning = FALSE,
  warnings = FALSE
)
#knitr::opts_chunk$get()
```

```{r}
mypath <- rprojroot::find_package_root_file

library(tidyverse)
library(cowplot)
library(magrittr)
library(kableExtra)

source(mypath("R", "misc.R"))
source_dir(mypath("R"))

```

```{r}
sem_hyp <- tibble(
  link = "Species richness \\to connectance",
  pred = "Connectance is negatively linked to species richness",
  ref = "\\citep{dunne_network_2006}"
)
sem_hyp <- tibble(
  link = "Species richness \\to connectance",
  pred = "Connectance is negatively linked to species richness",
  ref = "@dunne_network_2006"
)

sem_hyp %>%
  kable(format = "latex")

```
(ref:studies-table-ref1) Bogaert *et al.* (2011) [@dunne_network_2006]

```{r}
sem_hyp <- tibble(
  link = "Species richness to connectance",
  pred = "Connectance is negatively linked to species richness",
  ref = ""
)
library(nlme)
myload(sem_data, dir = mypath("data"))
stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))
bm_sem_rich <- compute_prod_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))
resp_pred <- map_dfr(list(stab_sem_rich, bm_sem_rich), ~.x$coefficients) %>% 
  distinct(Predictor, Response) %>%
  select(pred = Predictor, resp = Response)

var_replacement <- str_replace_all(get_sem_var_name_replacement(),
  c("\n" = "", "\\s{2}" = " "))
names(var_replacement) <- names(get_sem_var_name_replacement())

ta <- resp_pred %>%
  mutate_all(~str_replace_all(., var_replacement)) %>%
  unite(Link, pred:resp, sep = " xto ") %>%
  mutate(hypothesis = NA, reference = NA)

ti <- ta %>%
  kable(format = "latex")

test <- str_replace_all(ti, "xto", "$\to$")
class(test) <- class(ti) 
attr(test, "format") <- attr(ti, "format")

write(ti, file = mypath("manuscript", "bef_stability", "hypothesis_sem_empty.tex"))
```

### 2021-02-20 manuscript/bef_stability/fig1_biomass_network.Rmd
Finalize figures

@@
 myload(p_st, dir = mypath("manuscript", "bef_stability", "figs"))
+qt_station <- sem_data %>%
+  filter(station %in% c(first_st$station[5], last_st$station[5])) %>%
+  dplyr::select(station, bm_std_stab)
+mysave(qt_station, dir = mypath("data"), overwrite = TRUE)
 # Station
 myload(biomass_ts_sax, op_analysis, dir = mypath("data"))
+
 op_analysis_bbb <- filter(op_analysis, station %in%
@@
 mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())
-
-qt_station <- sem_data %>%
-  filter(station %in% c(first_st$station[5], last_st$station[5])) %>%
-  dplyr::select(station, bm_std_stab)
-mysave(qt_station, dir = mypath("data"), overwrite = TRUE)
-
-p_st <- p_st + 
-  theme_void() +
-  theme(plot.margin = theme_get()$plot.margin, legend.position = "none")
 
@@
     expand = FALSE
-  )
+  ) +
+  theme_void() +
+  theme(plot.margin = theme_get()$plot.margin, legend.position = "none")
 
@@
 fig1c
-save_plot("figs/fig1c_low_rich.png", fig1c,
+save_plot("figs/fig1c_low_rich.pdf", fig1c,
   nrow = 2, 
@@
 )
-save_plot("figs/fig1d_high_rich.png", fig1d,
+save_plot("figs/fig1d_high_rich.pdf", fig1d,
   nrow = 2, 
@@
 
-save_plot(mypath("manuscript", "bef_stability", "figs/fig1.png"), fig1_draw_test,
+save_plot(mypath("manuscript", "bef_stability", "figs/fig1.pdf"), fig1_draw_test,
 nrow = 3, 

### 2021-02-20 manuscript/bef_stability/manuscript.Rmd
Finalize figures

@@
 respectively the standard deviation and the temporal average of the annual total
-biomass of the station $i$). Then, temporal stability was equal to $CV^{-1} =
+biomass of the station $i$). Then, temporal stability ($S_i$) was equal to $CV^{-1} =
 \mu \sigma^{-1}$.
@@
 
-$$
+\begin{equation} 
   CV_{com, i} = \overline{CV_{sp, i}} \times \sqrt{\phi_i}
-$$
+  (\#eq:cvcom)
+\end{equation}
 
@@
 
-$$
+\begin{equation} 
 \overline{CV_{sp, i}} = \sum_k{\frac{B_{k,i} {CV}_{k, i}}{\sum_k{B_{k,i}}}}
-$$
-
-$$
+(\#eq:cvsp)
+\end{equation}
+
+\begin{equation} 
 \phi_i = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sqrt{\sigma^2_{x_{k,i}}}})^2} = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sigma_{x_{k,i}}})^2}
-$$
+(\#eq:phi)
+\end{equation}
+
+In further analysis, we linearized the mathematical relationship linking
+temporal stability to $\overline{CV_{sp, i}}$ and $\phi$ by taking the log of
+temporal stability:
+
+\begin{equation} 
+  \begin{aligned}
+    S_i &= (\overline{CV_{sp, i}} * \phi_i^\frac{1}{2})^{-1} \\
+    \log S_i &= - \log (\overline{CV_{sp, i}} * \phi_i^\frac{1}{2}) \\
+    \log S_i &= - \log (\overline{CV_{sp, i}} - \log \phi_i^\frac{1}{2} \\
+    \log S_i &= - \log \overline{CV_{sp, i}} - \frac{1}{2} \log \phi_i \\
+  \end{aligned}
+  (\#eq:stab)
+\end{equation}
 
@@
 $\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
-predictive variable $x$ and of the response variable $y$). The paths whose
-slope had a $P$ value inferior or equal to $0.05$ were reported in the main text, all the
-path values are presented in Table S7 and S8.
-
-Indirect effects on community biomass and its temporal stability
-were computed by multiplying slopes along the path. Only significant direct
-slopes were included in the calculation of indirect effects. Total effects were
-computed as the sum of direct and indirect effects.
+predictive variable $x$ and of the response variable $y$). Therefore, the
+standardized coefficients expressed the variation of $x$ and $y$ in standard
+deviation units. According to the equation (\@ref(eq:stab)), the unstandardized
+coefficients of synchrony and $\overline{CV_{sp}}$ determining temporal
+stability of biomass are respectively $-0.5$ and $1.0$. When standardized, a 
+comparaison of those coefficients comes down to a comparaison of the standard
+deviation of these two variables. The paths whose slope had a $P$ value inferior
+or equal to $0.05$ were reported in the main text, all the path values are
+presented in Table S7 and S8.
+
+Indirect effects on community biomass and its temporal stability were computed
+by multiplying slopes along the path. Only significant direct slopes were
+included in the calculation of indirect effects. Total effects were computed as
+the sum of direct and indirect effects.
 
@@
 fluctuations in population biomass, but this hypothese was not testable with the
-available dataset.
+available dataset.  Alternatively, our results might be explain by the effect of
+increasing species richness which can increase demographic stochasticity.
 
@@
 
-In contrast with previous studies, we found that the average population
-variability ($\overline{CV_{sp}}$) had a stronger negative effect on community biomass
-stability than synchrony [@tilman_biodiversity_2006;
-@olivier_urbanization_2020]. It explains why we observe a negative effect of
-species richness on temporal stability of community biomass. The weaker effect of synchrony
-might be explained by the presence of generalist predators in stream
-communities, which can promote synchrony between prey species that share the
-same predator and thus reduces compensatory
-population dynamics [@raimondo_interspecific_2004]. Alternatively, it is
-possible that, in aquatic food-webs, the occurrence of large oscillatory dynamics
- leads to a higher contribution of population
-variability rather than synchrony to community stability
-[@mccann_reevaluating_1997]. How both strengths of interactions and the relative
-contribution of synchrony and population variability to overall stability vary
-between food-webs and single trophic communities is still an open question.
+The population variability and synchrony are mathematically linked to the
+stability of community biomass (see Methods), so the comparaison of their effect
+reflected that the the comparaison of their variability. In contrast with
+previous studies, we found that the average population variability
+($\overline{CV_{sp}}$) had a stronger negative effect on the stability of
+community biomass than synchrony [@olivier_urbanization_2020], meaning that the
+variability of synchrony was equivalent the one of population variability. It
+explains why we observe a negative effect of species richness on temporal
+stability of community biomass whereas species richness had a strong negative
+effect of synchrony. The lower variability of synchrony might be explained by
+the presence of generalist predators in stream communities, which can promote
+synchrony between prey species that share the same predator and thus reduces
+compensatory population dynamics [@raimondo_interspecific_2004]. Alternatively,
+it is possible that, in aquatic food-webs, the occurrence of large oscillatory
+dynamics leads to a higher variability of population variability rather than
+synchrony to community stability [@mccann_reevaluating_1997]. How both strengths
+of interactions and the relative contribution of synchrony and population
+variability to overall stability vary between food-webs and single trophic
+communities is still an open question.
+
+Our results raise the question of the fundamental differences between single and
+multi-trophic communities. Some mechanisms are transferable from the first to
+the second such higher connectance which might translate in higher competition
+between consumers and thus destabilise populations [@thebault_trophic_2005].
+However, the existence of top-down and bottom-up effects are obviously typical
+to multi-trophic communities. The population at the top of a food-web are
+limited by the growth of its prey (bottom-up effects) while the lower trophic
+levels are limited by both their predators (top-down effect) and their preys
+(bottom-up effects). We can conjecture that the stability of food-webs mainly
+controlled by bottom-up effects will display higher synchrony while  mainly
+controlled by the food-webs mainly controlled by top-down effects will display
+higher population variability.
 

### 2021-02-20 manuscript/bef_stability/review_analysis.Rmd
Finalize figures

@@
 
-# SD de la variable de Olivier et al. (2020):  
+# Standard deviation according to Olivier et al. (2020):
 sd(log(1 / sem_data$sync))
 sd(log(1 / sem_data$cv_sp))
+mod_olivier <- lm(I(-log(bm_std_stab)) ~ 0 + I(-log(cv_sp)) + I(-log(sync)), data = sem_data)
+broom::tidy(mod_olivier)
+
 ```

### 2021-02-20 map.R

@@ -106,7 +106,7 @@ country_points[country_points$name == "Spain", c("X", "Y")] <- c(300000, 6150000
 country_points[country_points$name == "Italy", c("X", "Y")] <- c(1300000, 6450000) 
 
 ocean <- data.frame(X = 200000, Y = 6500000, name = "atlantic \n ocean")
-sea <- data.frame(X = c(450000, 900000), Y = c(7025000, 6180000), name = c("English \n sea", "Mediterranean \n sea"))
+sea <- data.frame(X = c(450000, 900000), Y = c(7025000, 6180000), name = c("English \n channel", "Mediterranean \n sea"))
 
 basin_inner <- basin %>% 
         rmapshaper::ms_innerlines() %>% 
@@ -168,3 +168,4 @@ save_plot(
   base_height = 7 / 2.54,
   base_width = 7 / 2.54
 )
+

### 2021-03-06 manuscript/bef_stability/manuscript.Rmd
Reviewed according to Elisa's comments

@@
 ---
-title: Species richness and food-web structure jointly drive community biomass and its temporal stability in fish communities
+title: Species richness and food-web structure jointly drive community biomass and its temporal stability in fish assemblages 
 author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault, Colin Fontaine
@@
 bibliography: references.bib
+csl: ecology-letters.csl
 ---
@@
 affect both biomass and its stability via effects on richness and network
-structure. Strikingly, effects on stability are mediated by changes in
-population stability rather than synchrony, which contrasts with results from
-single-trophic communities and might be characteristic of multi-trophic
-communities.
+structure. Strikingly, effects on stability are mediated by population stability
+rather than synchrony, which contrasts with results from single-trophic
+communities and might be characteristic of multi-trophic communities.
 
@@
 
-Biodiversity affects biomass production [@tilman_productivity_1996;
-@cardinale_species_2002; @grace_integrative_2016], distribution
-[@thebault_relationship_2006] and stability [@thebault_trophic_2005;
-@thebault_relationship_2006; @tilman_biodiversity_2006]. Indeed species richness
-generally increases primary productivity and total biomass in experimental plant
-communities [@tilman_productivity_1996; @grace_integrative_2016;
-@hector_plant_1999; @tilman_biodiversity_2014; @grace_integrative_2016], stream
-feeders, [@cardinale_species_2002] and aquatic bacterial consumers
-[@pennekamp_biodiversity_2018]. In parallel, such positive relationship between
-species richness and temporal stability of biomass has been reported in
-experimental grasslands and aquatic bacterial systems
-[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018] as well as in natural
-settings, such as stream fish communities [@franssen_annual_2011], bird and
-butterfly communities [@houlahan_negative_2017; @olivier_urbanization_2020].
-Despite the diversity of ecosystems and taxa studied, the relationship between
+Species richness has been found to increase primary productivity, community biomass
+and its temporal stability in a diversity of ecosystems and taxa both
+empirically and experimentally [@tilman_productivity_1996;
+@cardinale_species_2002; @tilman_biodiversity_2006; @franssen_annual_2011;
+@grace_integrative_2016; @pennekamp_biodiversity_2018; @houlahan_negative_2018;
+@olivier_urbanization_2020]. However, the relationship between
 diversity and ecosystem functioning remains mostly focused on single trophic
-levels, ignoring the effects of food-web structure. This gap is even more
-striking for the relationship between diversity and temporal stability , in
-spite of long-standing interest for the links between food-web complexity and
-stability in theoretical ecology [e.g.  @may_will_1972; @dunne_network_2006;
-@neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011].
+levels, generally the primary producers, ignoring the effects of food-web
+structure. This gap is even more striking for the relationship between diversity
+and temporal stability, in spite of long-standing interest for the links between
+food-web complexity and stability in theoretical ecology [e.g.  @may_will_1972;
+@dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
+@stouffer_compartmentalization_2011].
 
@@
 community biomass and its stability. Complementarity in the use of
-resources is important to understand the effects of species richness in food-webs
-[@thebault_food-web_2003; @poisot_trophic_2013; @schneider_animal_2016], but it
-also depends on food-webs connectance, i.e. its level of generalism
-[@thebault_food-web_2003; @poisot_trophic_2013].
+resources is important to understand the effects of species richness on
+productivity in food-webs [@thebault_food-web_2003; @poisot_trophic_2013;
+@schneider_animal_2016], but it also depends on food-webs connectance, i.e. its
+level of generalism [@thebault_food-web_2003; @thebault_cascading_2007]. In
+addition, the presence of species at higher trophic levels may increase total
+primary production, through possibly through the selection of primary producers
+which are larger and more complementary [@wang_biodiversity_2018].
 
@@
 species richness and population temporal variability
-[@thebault_trophic_2005]. In addition, the presence of species at higher trophic
-levels increases total primary production, through stronger top-down effects
-associated with higher nutrient uptake [@wang_biodiversity_2018]. The addition of predators has
+[@thebault_trophic_2005]. The addition of predators has
 also cascading effects on both population variability and
@@
 context, recent developments to predict species trophic interactions
-[@beckerman_foraging_2006; @gravel_inferring_2013; @portalier_foraging_2019],
+[@beckerman_foraging_2006; @gravel_inferring_2013; @portalier_mechanics_2019],
 combined with observational long-term surveys of ecological communities, can
@@
 
-Such approach based on data from natural communities can, in addition, give
-insights on the effects of environmental variables on ecosystem properties and
-their stability. Environment affects organism performance directly, and thereby,
-population abundances, community biomass [@grace_integrative_2016; @woods_testing_2020]
-and its temporal stability [@oliver_heterogeneous_2010; @franssen_annual_2011;
+The joint study of the effects of diversity and food web structure on total
+biomass and its stability is even more important in the context of environmental
+changes. Recent studies on natural communities have shown that environment may
+alter community biomass [@grace_integrative_2016; @woods_testing_2020] and its
+temporal stability [@oliver_heterogeneous_2010; @franssen_annual_2011;
 @hansen_climate_2013; @bluthgen_land_2016; @de_boeck_patterns_2017;
@@
 @tabi_warming_2019]. Environment also directly affect species richness and
-food-web structure, as larger ecosystems host food-webs with higher
-diversity and trophic levels [@mchugh_dual_2010] whereas temperature can affect
-food-web diversity and structure in contrasted ways depending on the ecosystem
-studied [@ogorman_unexpected_2017; @gauzens_biodiversity_2020]. In natural
-communities, the relationships among species richness, community biomass and its
-temporal stability might also arise from effects of the environment on both
-diversity and ecosystem functions [@loreau_biodiversity_2001; @he_global_2013;
-@grace_integrative_2016].
+food-web structure, as larger ecosystems host food-webs with higher diversity
+and trophic levels [@mchugh_dual_2010] whereas temperature can affect food-web
+diversity and structure in contrasted ways depending on the ecosystem studied
+[@ogorman_unexpected_2017; @gauzens_biodiversity_2020]. In natural communities,
+the relationships among species richness, community biomass and its temporal
+stability might also arise from effects of the environment on both diversity and
+ecosystem functions [@loreau_biodiversity_2001; @he_global_2013;
+@grace_integrative_2016]. Thus, the effect of environment on ecosystem
+functioning might arise from direct effects or indirectly through effects on
+species richness or food-web structure.
 
@@
 informations [@jennings_weak_2001; @beckerman_foraging_2006;
-@gravel_inferring_2013; @brose_predator_2019; @portalier_foraging_2019].
+@gravel_inferring_2013; @brose_predator_2019; @portalier_mechanics_2019].
 
@@
 tot_var_expl_pca <- sum(prop_var_expl_pca) 
-```
-
-```{r, cache = FALSE}
-pca_caption <- paste0(
-  "(B) Rotated axis of PCA on environmental variables. The five components
-  explained,", tot_var_expl_pca, "% of the variance (",
-  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
-  " Axis 1 was positively related to the stream size, axis 2 was related to
-  the stream slope and altitude and negatively related to average water temperature and
-  BOD."
-  )
-
-matmet_cap <- paste0( 
-  "(A) Observation sites (black dots) were located across France and monitored
-  on the period 1995-2018. The red dots show the location of (C) and (D) sites.
-  ", " Inner borders draw the limits of the hydrographic basins. ", pca_caption,
-  " (C) and (D) The temporal dynamic of population biomass with three networks
-  of years 1997, 1999 and 2002. Each trophic species is represented
-  by a node and each color represents a species. The node size are proportional to
-  the biomass of the trophic species. The seven resource nodes are drawn in grey. ",
-  "The species names corresponding to the three digit codes are found in Table
-  S1.")
-
 ```
@@
 We selected the stations that had been sampled ten years or more. As the concept
-of community variability referred to variability around an equilibrium, which is
-rarely observed or difficult to characterize in natural communities, only
-stations with no temporal trends in community biomass were selected (detailed in
-appendix B, part 2). However, the results were robust to the relaxation of this
-hypothesis (Fig. S7). These selection steps resulted in 99 stations distributed
-over seven hydrographic basins (Fig. \@ref(fig:matmet)A).
+of community stability often refersred to the variability around an equilibrium
+point [@donohue_navigating_2016], which is rarely observed or difficult to
+characterize in natural communities. Then, we selected the stations that did not
+show temporal trends in community biomass (detailed in appendix B, part 2).
+However, the results were robust to the relaxation of this hypothesis (Fig. S7).
+We selected the stations that had been sampled ten years or more. As the concept
+of community stability referred to variability around an equilibrium, which is
+rarely observed or difficult to characterize in natural communities, only those
+stations that did not show temporal trends in community biomass were selected
+(detailed in appendix B, part 2). However, the results were robust to the
+relaxation of this hypothesis (Fig. S7). These selection steps resulted in 99
+stations distributed over seven hydrographic basins (Fig. \@ref(fig:matmet)A).
 
@@
 
-The body size of all fish individuals was not recorded when they were too
+The body size of all fish individuals from a given species was not recorded when they were too
 numerous (Fig. S1, appendix B, part 1.1). The body size of the unmeasured
@@
 Temporal biomass stability was defined as the inverse of biomass variability.
-Variability was computed as Coefficient of Variation (CV) of the biomass over
+Variability was computed as Coefficient of Variation (CV) of the community biomass over
 time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being
-respectively the standard deviation and the temporal average of the annual total
-biomass of the station $i$). Then, temporal stability ($S_i$) was equal to $CV^{-1} =
-\mu \sigma^{-1}$.
-
-We described the mechanisms driving the temporal stability of biomass,
-decomposing the $CV$ of the community biomass ($CV_{com}$) into a
-synchrony ($\phi$) component and a weighted average species $CV$ ($\overline{CV_{sp}}$)
-component according to @thibaut_understanding_2013:
+respectively the standard deviation and the temporal average of the annual
+community biomass of the station $i$). Then, temporal stability ($S_i$) was
+equal to $CV_i^{-1} = \mu_i \sigma_i^{-1}$.
+
+The variability of community biomass ($CV_{com, i}$) can be decomposed 
+into a
+synchrony ($\phi$) component and a weighted average population variability
+($\overline{CV_{sp, i}}$) component according to @thibaut_understanding_2013:
 
@@
 
-with $CV_{com, i}$ being the CV of the community biomass in the
-station $i$, $\overline{CV_{sp, i}}$ the average CV at the species-level in the station $i$, weighted by the relative biomass of the species, $B_{k,i}$.
+To assess the mechanisms driving stability of community biomass, we thus in addition measure
+the synchrony and the weighted average population variability $\overline{CV_{sp,
+i}}$, the average CV at the species-level in the station $i$, weighted by the
+relative biomass of the species, $B_{k,i}$.
+
 Synchrony of the station $i$, $\phi_i$, is the ratio between the variance of
@@
 (\#eq:phi)
-\end{equation}
-
-In further analysis, we linearized the mathematical relationship linking
-temporal stability to $\overline{CV_{sp, i}}$ and $\phi$ by taking the log of
-temporal stability:
-
-\begin{equation} 
-  \begin{aligned}
-    S_i &= (\overline{CV_{sp, i}} * \phi_i^\frac{1}{2})^{-1} \\
-    \log S_i &= - \log (\overline{CV_{sp, i}} * \phi_i^\frac{1}{2}) \\
-    \log S_i &= - \log (\overline{CV_{sp, i}} - \log \phi_i^\frac{1}{2} \\
-    \log S_i &= - \log \overline{CV_{sp, i}} - \frac{1}{2} \log \phi_i \\
-  \end{aligned}
-  (\#eq:stab)
 \end{equation}
@@
 trophic interactions between all fishes and the resources (Fig.
-\@ref(fig:matmet)B), then (2) determine network of a given community by
+SXX), then (2) determine network of a given community by
 extracting the metaweb according to the fishes present at a given
@@
 biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos
-(grey nodes in Fig. \@ref(fig:matmet)B, C & D). The trophic species and the
+(grey nodes in Fig. \@ref(fig:matmet)C & D). The trophic species and the
 resources constituted the 412 nodes of the metaweb, i.e. 45 fish species divided
@@
 
-For each trophic network, corresponding to a particular site and year, we
-computed the connectance and mean trophic level. Connectance describes the
-level of generalism in the network and is calculated as the actual number of
-interactions divided by the number of interactions if all species interact
-($C = L / N^2$, L and N being resp. the number of links and of nodes).
-The trophic level of the nodes was computed as one added to the average trophic
-level of its food item. The mean trophic level $\overline{T}$ was 
-weighted by the biomass of each trophic species (excluding resource nodes for
-which we had no biomass information), so $\overline{T} = \sum_i^N{B_iT_i \times
-(\sum_i^N{B_i})^{-1}}$, with $T_i$ and $B_i$ being respectively the trophic
-level and the biomass of the node $i$. For each site, the median of connectance
-and average trophic level over time was used in subsequent analysis.
+For each food-web, corresponding to a particular site and year, we computed the
+connectance and mean trophic level. Connectance describes the level of
+generalism in the network and is calculated as the actual number of interactions
+divided by the number of interactions if all species interact ($C = L / N^2$, L
+and N being resp. the number of links and of nodes).  The trophic level of the
+nodes was computed as one added to the average trophic level of its food item.
+The average trophic level $\overline{T}$ was computed as the average trophic
+level of the trophic species weighted by their biomass (excluding resource nodes
+for which we had no biomass information), so $\overline{T} = \sum_i^N{B_iT_i
+\times (\sum_i^N{B_i})^{-1}}$, with $T_i$ and $B_i$ being respectively the
+trophic level and the biomass of the node $i$. For each site, the median of
+connectance and average trophic level over time was used in subsequent analysis
+(Fig. \@ref(fig:matmet)C & D).
 
@@
 the analysis the two first principal components based on the elbow method, on
-the eigenvalues distribution (appendix B, Fig. S4). The two first principal components
-explained `r tot_var_expl_pca`% of the variance (appendix B, Fig. S4). A varimax axis rotation was
+the eigenvalues distribution (appendix B, Fig. SXX). The two first principal components
+explained `r tot_var_expl_pca`% of the variance (Fig. \@ref(fig:matmet)B). A varimax axis rotation was
 performed to maximize the representation of the environmental variables by the principal
@@
 @woods_testing_2020]. We assumed that both species richness and food-web
-structure directly affect community biomass (Fig. \@ref(fig:sem-plot)A) and that
+structure directly affect community biomass (Fig. \@ref(fig:sem-bm)A) and that
 species richness affected food-web structure [@winemiller_must_1989;
@@
 We used the same model structure to assess the drivers of temporal stability
-of community biomass (Fig.  \@ref(fig:sem-plot)C). Instead of the
+of community biomass (Fig.  \@ref(fig:sem-stab)A). Instead of the
 annual community biomass, we modelled the synchrony and $\overline{CV_{sp}}$ which
-in turn determined the temporal stability of community biomass.
+in turn determined the temporal stability of community biomass. We linearized
+the mathematical relationship linking temporal stability to $\overline{CV_{sp,
+i}}$ and $\phi$ by taking the log of
+temporal stability such as
+
+\begin{equation} 
+    \log S_i = - \log \overline{CV_{sp, i}} - \frac{1}{2} \log \phi_i
+  (\#eq:stab)
+\end{equation}
 
@@
 biomass (resp. $R^2 = .43$, $.38$, $.46$, $.47$ and $.32$) but less so for mean
-trophic level ($R^2 = .11$, Fig. \@ref(fig:sem-plot)B and D). We found a
+trophic level ($R^2 = .11$, Fig. \@ref(fig:sem-bm)A and \@ref(fig:sem-stab)A). We found a
 negative relationship between species richness and mean trophic level ($r_\delta
 = `r rich_on_tlvl`$, $r_\delta$ meaning standardized slope) and connectance
-($r_\delta = `r rich_on_ct`$, Fig.  \@ref(fig:sem-plot)B and D), meaning that a
+($r_\delta = `r rich_on_ct`$, Fig.  \@ref(fig:sem-bm)A and \@ref(fig:sem-stab)A), meaning that a
 part of the effects of species richness on community biomass and its temporal
@@
 on community biomass ($r_\delta = `r rich_on_bm$direct`$ and 
-$r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-plot)B, Table
+$r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-bm)A, Table
 \@ref(tab:indir-sem)), while connectance had no direct effect.
@@
 \@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
-`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). The total effect
-of PCA1, PCA2 and species richness on community biomass were of the same magnitude.
+`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). Streams
+with higher temperature and BOD contained more species, indirectly increasing
+community biomass. The total effect of PCA1, PCA2 and species richness on
+community biomass were of the same magnitude.
 
@@
 
-By its effects on synchrony and $\overline{CV_{sp}}$, which respectively
-measures the level of compensatory dynamics among population and the average
-population variability, species richness had a
+By its effects on synchrony and population variability ($\overline{CV_{sp}}$), species richness had a
 negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
@@
 thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
-\@ref(tab:indir-sem)). The negative effect of $\overline{CV_{sp}}$ on temporal
-stability was twice higher than the negative effect of synchrony (resp.
+\@ref(tab:indir-sem)), which outweighted the decreasing effect of species
+richness on synchrony. The
+negative effect of $\overline{CV_{sp}}$ on temporal stability was twice higher
+than the negative effect of synchrony (resp.
 $r_\delta = `r cv_sp_on_stab`$ and $r_\delta = `r sync_on_stab`$, Fig.
-\@ref(fig:sem-plot)D).
+\@ref(fig:sem-stab)A).
 
@@
 $\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
-Fig. \@ref(fig:sem-plot)D) and thereby had a total positive
+Fig. \@ref(fig:sem-stab)A) and thereby had a total positive
 effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$,
-Table \@ref(tab:indir-sem)). Connectance had no significant direct effect on either
+Table \@ref(tab:indir-sem)). Food webs in which community biomass is located on
+average at higher trophic levels thus tend to have higher population and
+community stability. Connectance had no significant direct effect on either
 $\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
-(Fig. \@ref(fig:sem-plot)D, Table \@ref(tab:indir-sem)).
-
-The total effect of PCA2, related to average annual temperature, on temporal
+(Fig. \@ref(fig:sem-stab)A, Table \@ref(tab:indir-sem)).
+
+The total effect of PCA2, related to average annual temperature and BOD, on temporal
 stability was of higher magnitude than the effects of species richness and mean
@@
 The PCA2 had a total negative effect on temporal stability, meaning that higher
-temperature results in lower stability
+temperature and BOD results in lower stability
 ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
@@
 ($r_\delta = `r env_on_stab$total["log_RC1"]`$, Table \@ref(tab:indir-sem)).
+Warmer and larger streams thus tend to have more species and more variability in
+population biomass, then have a lower stability of community biomass.
 
@@
 (bottom-up effects). We can conjecture that the stability of food-webs mainly
-controlled by bottom-up effects will display higher synchrony while  mainly
-controlled by the food-webs mainly controlled by top-down effects will display
-higher population variability.
+controlled by bottom-up effects will display higher synchrony while the
+food-webs mainly controlled by top-down effects will display higher population
+variability. In sum, average synchrony and population variability might be
+characteristic of communities more or less controlled by top-down or bottom-up
+effects.
 
@@
 
-While the PCA axis related to stream size had only a weak effect on the
-temporal stability of community biomass, the PCA axis related to temperature had a
-negative effect on temporal stability through a direct destabilizing
-effect on populations and through indirect effects. Temperature can have both
-stabilizing and destabilizing effects in resource-consumer models depending on
-the thermal niche of the species and on how nutrient supply varies with
-temperature [@uszko_effects_2017]. The observed increased
-variability of populations might also relate with ecosystem enrichment
-[@ogorman_unexpected_2017] because average Biological Oxygen Demand covaries
-with temperature in our study. Enrichment can increase CV by
-increasing population biomass fluctuations while higher temperature might decrease
+While the PCA axis related to stream size had only a weak effect on the temporal
+stability of community biomass, the PCA axis related to temperature had a
+negative effect on temporal stability through a direct destabilizing effect on
+populations and through indirect effects. Temperature can have both stabilizing
+and destabilizing effects in resource-consumer models depending on the thermal
+niche of the species and on how nutrient supply varies with temperature
+[@uszko_effects_2017]. The observed increased variability of populations might
+also relate with ecosystem enrichment [@ogorman_unexpected_2017] because average
+Biological Oxygen Demand covaries with the PCA axis related to average
+temperature (Fig. \ref{fig:matmet}B). Enrichment can increase CV by increasing
+population biomass fluctuations while higher temperature might decrease
 stability through starvation resulting from high metabolic activity
@@
 
+\clearpage
+
+```{r, cache = FALSE}
+pca_caption <- paste0(
+  "(B) Rotated axis of PCA on environmental variables. The five components
+  explained, ", tot_var_expl_pca, "% of the variance (",
+  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
+  " Axis 1 was positively related to the stream size, axis 2 was related to
+  the stream slope and altitude and negatively related to average water temperature and
+  BOD. For simplicity, we reversed the second axis of the PCA in the structural equation
+  models, so that the second axis covaries with average water temperature and
+  BOD."
+  )
+
+matmet_cap <- paste0( 
+  "(A) Observation sites (black dots) were located across France and monitored
+  on the period 1995-2018. The red dots show the location of (C) and (D) sites.
+  ", " Inner borders draw the limits of the hydrographic basins. ", pca_caption,
+  " (C) and (D) The temporal dynamic of population biomass with three networks
+  of years 1997, 1999 and 2002. Each trophic species is represented
+  by a node and each color represents a species. The node size are proportional to
+  the biomass of the trophic species. The seven resource nodes are drawn in grey. ",
+  "The species names corresponding to the three digit codes are found in Table
+  S1.")
+
+```
+
 ```{r matmet, cache = FALSE, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
 library(knitr)
-include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1.png"))
-```
-
-```{r sem-plot, out.width="\\maxwidth", fig.cap = sem_caption, results = "fig.show", cache = FALSE}
+include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1_modif.pdf"))
+```
+
+\clearpage
+
+```{r, cache = FALSE}
+sem_caption <- paste0(
+  "Structural Equation Models for the median of annual
+  community biomass (in grams by square meter) and (C) its temporal stability.",
+  " Results of the Structural Equation Models for
+  (B) the median of annual community biomass and (D) its temporal stability. Red and black
+  arrows represent respectively negative and positive path coefficients. The
+  path coefficients are standardized. For convenience, only significant
+  paths (i.e. $P < 0.05$) are shown. Rsq: Adjusted $R^2$; Avg:
+  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
+  second axis of the PCA performed on environmental variables (see methods)."
+)
+```
+
+```{r}
+
+sem_bm_caption <- paste0( "Species richness and average trophic level are
+  positively linked to community biomass. (A) Structural Equation Model for the
+  median of annual community biomass (in grams by square meter). Dotted and
+  solid arrows represent respectively negative and positive path coefficients.
+  Non significant paths are shown in grey. The path coefficients are
+  standardized. The $R^2$ are the adjusted $R^2$; Avg: Average, CVsp: weighted
+  temporal CV of the population biomass; PCA1 and PCA2: respectively the first
+  and second axis of the PCA performed on environmental variables (see methods).
+  (B) to (G): significant bivariate relationships between variables of the
+  structural equation model. The solid lines show the predictions of the
+  statiscal model.")
+
+```
+
+```{r sem-bm, out.width="\\maxwidth", fig.cap = sem_bm_caption, results = "fig.show", cache = FALSE}
 #out.height="120%",
@@
 #sem_plot
-knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "sem_mano.pdf"))
-```
+knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "fig2.pdf"))
+```
+
+\clearpage
+
+```{r}
+
+sem_stab_caption <- paste0("Relationships among environment, species richness,
+  food-web structure, stability decomposition and the temporal stability of community biomass. (A)
+    Structural Equation Model for the temporal stability of community biomass.
+  Dotted and solid arrows represent respectively
+  negative and positive path coefficients. Non significant paths are shown in
+  grey. The path coefficients are standardized. The $R^2$ are the adjusted
+  $R^2$; Avg: Average, CVsp: weighted temporal CV of the population biomass;
+  PCA1 and PCA2: respectively the first and second axis of the PCA performed on
+  environmental variables (see methods). (B) to (I): significant bivariate
+  relationships between variables of the structural equation model. The solid
+  lines show the predictions of the statistical model.")
+```
+
+```{r sem-stab, out.width="\\maxwidth", fig.cap = sem_stab_caption, results = "fig.show", cache = FALSE}
+knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "fig3.pdf"))
+```

### 2021-04-26 manuscript/bef_stability/appendixB.Rmd
Minor edits
Updates

--- 2020-12-14 manuscript/bef_stability/appendixB.Rmd
@@
 ---
-title: Appendix B of Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
+title: Appendix B of Species richness and food-web structure jointly drive community biomass and its temporal stability in fish assemblages 
 author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
@@
 output:
-  pdf_document:
+  bookdown::pdf_document2:
     fig_caption: true 
@@
 header-includes:
+   - \usepackage{natbib}
    - \newcommand{\beginsupplement}{\setcounter{table}{2}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
+   - \usepackage{float}
    - \usepackage{booktabs}
    - \usepackage{makecell}
-   - \usepackage{float}
    - \usepackage{setspace}
@@
 bibliography: references.bib
+number_sections: true
+nocite: |
+    @post_ecosystem_2000| @doi_resource_2009| @mchugh_dual_2010|
+    @ogorman_unexpected_2017| @gauzens_biodiversity_2020| @dunne_network_2006|
+    @mchugh_dual_2010| @doi_resource_2009| @allan_stream_2009|
+    @petchey_predicting_2010| @winemiller_must_1989
+csl: ecology-letters.csl
 ---
@@
 
-The fish community sampling took place in a variety of stream size, shape and
-depth. This diversity constraints the type of protocol that can take place.  For
-the small streams (depth < 0.7m across the entire width), the complete protocol
-is used. It consists in placing anodes across the width of the
-stream. The fishermen made from one to three row
-of fishing. We kept only the first row for analysis to homogenize the sampling
-effort. For deeper and wider streams, the sampling was partial over the bank and
-the channel and performed by boat and by foot (along the bank). We kept only
-sampling done over the bank because channel sampling was not always done. Two
-types of partial protocols takes place: partial over bank and partial by points.
-The former is continuous while the latter is discrete. Furthermore, in the "partial
-by point" protocol, the channel can be sampled as well. We kept only the "partial
-by point" sampling in which all the sampling points were done over the bank to
-homogenize the sampling. Then, we merged partial over bank and partial by 
-point protocols. Some sampled stations had mixed characteristics in which mix of
-partial and complete protocols were applied depending of the depth of the stream 
-at the time of sampling. In this case, we kept only the protocol that was the
-most used.
-
-Heterogeneity in the sampling period may introduce variability that is not related
+The monitoring of the fish communities occurs in a variety of stream size, shape
+and depth. The stream characteristics constrain the type of protocol that can be
+applied. Small streams (depth < 0.7m across the entire width) are sampled with
+the complete protocol. The protocol consists of placing anodes across the entire
+width of the stream. The fishermen made from one to three rows of electric
+fishing. We selected only the data from the first row to homogenize the sampling
+effort. In deeper and wider streams (depth >= 0.7m), the sampling was partial
+over the bank and the channel and performed by boat and by foot (along the
+bank). We selected only the sampling done over the bank because the channel was
+not systematically sampled. Two types of partial protocols takes place: partial
+over bank and partial by points, which are respectively continuous and discrete.
+Furthermore, in the "partial by point" protocol, the channel was sometimes
+sampled as well. We selected only the "partial by point" sampling in which all
+the sampling points were done over the bank to homogenize the sampling. Then, we
+merged partial over bank and partial by point protocols. Some sampled stations
+were located in stream with intermediate characteristics where both protocols
+were alternatively used depending on the state of the stream at the time of
+sampling. For these sites, we only kept the samples that had been carried out
+with the most used protocol.
+
+Heterogeneity in the sampling date may introduce variability that is not related
 to ecological processes such as the presence of juveniles. In order to reduce
-heterogeneity in sampling time, only one sampling per year was retained if there
-was two in a given year, the one with the most species and then individual
-collected. Finally, most of the fish sampling occurred in September (Median:
-mid-August) and the median standard deviation of the sampling month was inferior
-to one (0.7) within stations. Additionally, we removed sampling events, in a
-given station, in which the sampled length along the stream was outside the median
-length sampled more or less 30%. Finally, we standardized the biomass record
-and species richness by the sampled surface to get rid of sampling effort
-effects.
+heterogeneity in the sampling date, only one sampling per year was retained if
+there was more in a given year, the one with that had the most species and then
+the most individuals. Finally, most of the fish sampling occurred in September
+(Median: mid-August) and the median standard deviation of the sampling month was
+inferior to one (0.7) within stations, i.e. 3 weeks. To further reduce sampling
+heterogeneity, we only kept the sampling in which the length of stream sampled
+along the stream was inside the median length sampled more or less 30%.
 
@@
 
-During the electric fishing, and before that fish body size are measured, the
-fishes are regrouped by batches. Each batch contains one species but there can
-be several batches by species. Body size assessment are different according to
-the batches. There are four types of batches: N, I, S/L and G. The batches N and
-I contains the biggest individuals which are normally less numerous. Then
-the body size of all the individuals in the N and I batches is recorded. The batches S/L
-contains fishes of intermediate sizes. Inside each S/L batches, the operator
-tries to make batches as homogeneous as possible in terms of body size. Then, the body
+Once the fishes have been caught, they are divided into different batches (Fig.
+\@ref(fig:p-body-size)). Each batch contains only one species but there may be
+several batches for one species. The body size of the fishes is measured
+differently for each type of batch.  There are four types of batches: N, I, S/L
+and G. The batches N and I contain the biggest individuals. In the N and I
+batches, the body size of all the individuals is recorded. The batches S/L
+contain fishes of intermediate sizes.  Inside each S/L batch, the operator tries
+to make batches as homogeneous as possible in terms of body size. Then, the body
 size of a subsample of at least 20 individuals is recorded. The G batches
 contain individuals of small body size, with care that body size is as
-homogeneous as possible in a given batches. Then body size of the shortest and the
-longest individuals are recorded.
+homogeneous as possible in a given batches.  Then body size of the shortest and
+the longest individuals are recorded.
 
@@
 
-With the information contained in the batch record, we inferred the body size of
-the fishes in the community. No inference were needed for the N and I batches
-because the body size of all individuals was recorded. The body size ($l$) of the
-fishes in the S/L and G was inferred under the assumption that its distribution
-followed a normal law ($l ~ N(\mu , \sigma)$).
-For a S/L batch, the mean $\mu$ and the standard deviation $\sigma$ were simply
-the average and the standard deviation of the body size of the subsample
-recorded. For a G batch, the average was approximated by 
-$\hat{\mu} = (l_{min} + l_{max}) 2^{-1}$ and the standard deviation by
-$\hat{\sigma} = (l_{min} + l_{max}) 4^{-1}$. Together with the estimations of
-the mean and the standard deviation, the number of individuals in a batch and
-assumption of a normal distribution, we simulated the body size distribution in
-S/L and G batches. To avoid simulation of unrealistic body size, we used a
-truncated normal distribution bounded at [0.05; .95] for the density of
-probability of the S/L batches, and bounded at [$l_{min}$; $l_{max}$] for the G
-batches. Body size distribution were generated using the R function
-`truncdist::rtrunc`.
-
-We removed batches that did not satisfied the following conditions. First, we
-removed batches in which the total number of individuals was not recorded. In lot
-"G", we removed batches where $l_{min} \geq l_{max}$ or if at least one of the
-measurement was missing. Additionally, G batches were removed when number of
-individuals fell below five, as G batches normally contained more individuals.
-In the S/L lot, we removed batches in which the number of individuals in the
-recorded individuals fell below 10. In sum, those sanity check allowed to
-exclude potentially problematic batches. Finally, in the dataset used in the
-analysis, `r na_length` individuals had missing length over 
+We inferred the body size of all the unmeasured individuals using the batch
+records. There was no need for inference for the N and I batches since the body
+size of all individuals was recorded (Fig. \@ref(fig:p-body-size)). The body
+size ($l$) of the fishes in the S/L and G was inferred under the assumption that
+body size distribution follows a normal law ($l ~ N(\mu, \sigma)$).  For an S/L
+batch, the mean $\mu$ and the standard deviation $\sigma$ were simply the
+average and the standard deviation of the body size of the subsample recorded.
+For a G batch, the average was approximated by $\hat{\mu} = (l_{min} + l_{max})
+2^{-1}$ and the standard deviation by $\hat{\sigma} = (l_{min} + l_{max})
+4^{-1}$. With the estimations of the mean and the standard deviation, the number
+of individuals in a batch and the assumption of normal distribution, we
+simulated the body size distribution in S/L and G batches. To avoid simulation
+of unrealistic body size, we used a truncated normal distribution bounded at
+[0.05; .95] for the density of probability of the S/L batches, and bounded at
+[$l_{min}$; $l_{max}$] for the G batches. Body size distribution were generated
+using the R function `truncdist::rtrunc`.
+
+Batches that did not meet certain conditions were excluded. First, we also
+excluded batches for which the total number of individuals was not recorded. We
+also excluded G batches for which $l_{min} \geq l_{max}$ or if
+at least one of the measurement was missing. Additionally, a given G batch was
+excluded when the number of individuals fell below five, as G batches normally
+contained more individuals. We finally excluded S/L batches for which the
+number of measured individuals was inferior to 10. Finally, in the dataset used
+in the analysis, `r na_length` individuals had missing length over 
 `r nrow_fish_length` individuals.
-
-```{=latex}
-\pagebreak
-```
 
@@
 
-We removed rare fish species, species from lake, crayfish species, and migratory
-species. In total, we removed `r nrow(removed_ind)` over 
+The rare fish species, species from lake, crayfish species, and migratory
+species were excluded. In total, we removed `r nrow(removed_ind)` over 
 `r nrow(length_sem_analysis)` individuals and `r length(removed_sp)` species.
 
-During fish sampling, some species are identified based on morphotype but they
+Some species were identified based on their morphotype, but they
 belong to the same species based on fecundation criteria. We merged those
@@
 
-```{r}
-trophic_building_caption <- paste0(
-  "Trophic species"
-) 
-```
-
-```{r p-net-inf, fig.cap=trophic_building_caption}
+```{r, cache = FALSE}
+
+trophic_building_caption <- paste0( "Building of the metaweb. (1) Each
+  species are divided in nine body size classes. We gathered information about
+  the food diet of each fish species and how food diet varies according to
+  ontogeny. (2) The life stage of a trophic species was determined with the
+  median of the body size class. A trophic link was set between the trophic
+  species and the resources associated to this life stage. (3) For a piscivorous
+  trophic species, the trophic links between fishes were defined according to
+  the predators/prey body size ratio. The predation window of the trophic
+  species ranged from 3% to 45% of the median of the body size range. A trophic
+  link between the predator trophic species and every trophic species whose
+  midpoint of bodysize range was included in the predation window.")
+
+```
+
+```{r p-net-inf, cache = FALSE, fig.cap=trophic_building_caption}
 knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "network_inference.pdf"))
@@
 
-The metaweb described the potential trophic interactions between the
+```{r, cache = FALSE}
+metaweb_caption <- paste0(
+  "The metaweb describes the trophic interactions between all the 412 trophic species, each is
+  represented by a node and each color represents a species (S = 45). The seven
+  resource nodes (7) are drawn in grey. The species names corresponding to the
+  three digit codes are found in Table S1."
+)
+```
+
+```{r metaweb, cache = FALSE, fig.cap=metaweb_caption}
+knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "metaweb.png"))
+```
+
+The metaweb describes the potential trophic interactions between the
 ($`r ncol(metaweb_analysis$metaweb) - length(metaweb_analysis$resource)`$) trophic species.
-We had seven resource nodes which were present in the diet of the trophic
+The metaweb also included seven resource nodes which were present in the diet of the trophic
 species namely detritus, biofilm, phytoplankton, zooplankton, macrophages,
-phytobenthos and zoobenthos.
-
-The metaweb building was based on trait matching, so it necessitates to have
-information about their diet. `r length(removed_sp_metaweb)` species were
-removed because information about their diet was missing. It represented  
-`r nrow(removed_ind_metaweb)` individuals over `r nrow(length_sem_analysis)` 
-individuals.
-
-A trophic species belonged to a life stage if the median of its body size range
-fell in the range of the life stage. In turn, this trophic species has feeding
-interactions with the resource nodes of its life stage. Interactions between
-trophic interactions between a predator and a prey were determined by body size
-ratio as in many studies [@brose_predator_2019; @poisot_structure_2016;
-@schneider_body_2012].  For a given trophic species, we first determined if its
-size class ends up in a life stage containing piscivorous diet, i.e. if there was
-an overlap between them. We were more liberal for piscivory determination to
-avoid 
-missing potential fish-fish trophic interactions which were the main interactions
-in our community. If the trophic species was piscivorous, we determined its prey
-size range from 3% to 45% of the median of its size range. A trophic interaction
-was set for each trophic species whose median of its size class fell into the
-prey range of the predator trophic species. To sum up, the metaweb was obtained
-with allometric feeding interactions (1) between trophic species, (2) between
-trophic species and resource nodes and (3) between resource nodes.
+phytobenthos and zoobenthos (Fig. \@ref(fig:metaweb)).
+
+Trophic interactions between the nodes of the metaweb were determined according to
+the diet and the body size of the trophic species. `r length(removed_sp_metaweb)` 
+species were removed because information about their diet was missing. It
+represented  `r nrow(removed_ind_metaweb)` individuals over
+`r nrow(length_sem_analysis)` individuals.
+
+The life stage to which a trophic species belongs was determined by the median of
+the body size range of the trophic species, each life stage being delimited by a body
+size range. In turn, this trophic species has trophic interactions with the
+resource nodes of its life stage. The trophic interactions between a
+predator and a prey were determined by predator-prey body size ratio
+[@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012]. For a
+given trophic species, we first determined if its body size range overlap
+with a piscivorous life stage (Fig. \@ref(fig:p-net-inf)). We were then more
+liberal for piscivory determination than for fish-resource interactions, to
+avoid missing potential interactions which were the main interactions in our
+community. If the trophic species was piscivorous, we determined its prey size
+range from 3% to 45% of the median of its size range. A trophic interaction was
+set for each trophic species whose median of its size class fell into the prey
+range of the predator trophic species. To sum up, the metaweb contains feeding
+interactions (1) between trophic species, (2) between trophic species and
+resource nodes and (3) between resource nodes.
 
@@
 
-The local trophic network (i.e. one network for each fish community
-sampling) was obtained by determining the trophic species of each fish
-individual in the community and interactions were set according to the metaweb.
+The local trophic networks (i.e. one network by
+sampling) were obtained by determining the trophic species of each fish
+individual in the community. According to the trophic species present in a given
+community, we set the trophic interactions between them according to the metaweb. 
 All the resource nodes were assumed to be present in each local network.
 Finally, the structure of the local networks varied according the presence of
-the trophic species. The inferred interactions represent potential interactions
-(i.e. not measured interactions) and are binary (i.e. presence or absence of
-feeding interactions).
+the trophic species.
 
@@
 
-The procedure to obtain altitude, slope, width depth of the streams are fully
+The procedure to obtain altitude, slope, width and depth of the streams are fully
 explained in main text. Because those measurements were collected during the
 fishing protocol, they were easier to manage in the analysis. Then, we detailed
-in the following sections how water temperature, flow and BOD were obtained.
+in the following sections how water temperature, water flow and Biological
+Oxygen Demand (BOD) variables were obtained. The goal was to obtain an annual
+mean for each variable, to match the yearly resolution of the fish monitoring.
+Furthermore, those variables are measured at different locations than the fish
+monitoring.
 
@@
 
-Water temperature, flow and BOD (Biological Oxygen Demand) were obtained from the
-[naiades database](http://www.naiades.eaufrance.fr/).
-Water temperature, flow and BOD were respectively collected at a hourly, daily
-and monthly frequency. Water temperature and flow are recorded by automated
-sensors while BOD is collected manually because it necessitates analysis in a
-laboratory. BOD data collection is coordinated by the Agence de l'eau which
-realized the analysis itself or order it to a company.
-It is crucial to make clear that those variables are collected at different
-places than the fish samplings.
-
-```{r}
+Water temperature, water flow and BOD variables were obtained from the [naiades
+database](http://www.naiades.eaufrance.fr/) and were respectively collected at
+an
+hourly, daily and monthly frequency. Water temperature and flow are recorded by
+automated sensors while BOD is collected manually because its measurement
+requires laboratory analysis. BOD data collection is coordinated by the Agence
+de l'eau which realized the analysis itself or order it to a company.
+
+```{r, cache = FALSE}
 pressure_cap <- paste0(
-  "Map of environmental variables obtained for the 99 sites used in the analysis."
-)
-```
-
-```{r, fig.height = 20/2.54, fig.cap = pressure_cap}
+  "Map of the environmental variables obtained for the 99 sites used in the
+  analysis. Slope is expressed in degree, altitude in meter, distance from
+  source in kilometer, Strahler order has no units, average stream width and
+  depth are expressed in meter, Biological Oxygen Demand (BOD) is expressed in
+  mg of dissolved oxygen, water flow is expressed in cube meter per second and
+  water temperature is expressed in Celsius degree.")
+```
+
+```{r, cache = FALSE, fig.height = 20/2.54, fig.cap = pressure_cap}
 pca_pressure <- habitat_press
@@
 
-The time resolution was heterogeneous according to the variable considered
-(hourly, daily and monthly for temperature, flow and BOD resp.). For each
-recording station, we applied a moving window averaging to get rid of seasonal
-effects. For temperature, the moving was performed on daily average temperature.
-Then we took the annual average of each year and each variable (i.e. one value
-by year and by station).
+To get rid of seasonal effects of temperature, we applied a moving window
+averaging to each time series. The moving window was applied on daily average
+temperature. Then we took the annual mean of each year and each variable
+(i.e. one value by year and by station).
 
@@
 than along terrestrial surface. Interpolations in terrestrial areas are roughly
-based on euclidean distance. Euclidean distance is more complicated to consider
-in streams because it had the follow the path of the streams. Furthermore, two
-streams can be close by but not connected and the value of their variables could
-be not related or a only a few. For those reason, we used stream spatial network
-methods to interpolate water temperature, flow and BOD.
+based on euclidean distance while euclidean distance is complicated to consider
+in streams because it had to follow the path of the streams. Furthermore, two
+streams can be close by but not connected and thus the value of their variables might 
+not be related or only a few. For those reason, we used stream spatial network
+methods to interpolate water temperature, water flow and BOD.
 
@@
 
-The procedure was done by hydrographic basin because of convergence problem
-when the interpolation was done at the France scale. We had to make a trade-off
-between the number of data (to keep enough high to perform the interpolation)
-and the level of dataset splitting. We then merge some hydrographic basin to end
-up with four region of interpolation: West, East, South and North.
-
-Then we modeled each variable as dependant only on the covariation between sites
-and taking in account stream network. To model the autocovariance between sites,
-we used the linear-sill and mariah functions for taildown and tailup
-autocovariance, according to their prediction performance. The interpolations
-were done with the `SSN` R package 
-[@isaak_applications_2014; @hoef_ssn:_2014].
+The interpolations were carried out by hydrographic basin due to convergence
+issues when the interpolation was carried out at the scale of the whole
+France. We had to find a trade-off between the number of data (to keep enough
+high to perform the interpolation) and the level of dataset splitting. We then
+merged some hydrographic basin to end up with four regions of interpolation:
+West, East, South and North.
+
+Then we modelled each variable as dependant only on the covariation between
+sites and taking in account stream network. To model the autocovariance between
+sites, we used the linear-sill and mariah functions for taildown and tailup
+autocovariance, according to their predictive performance. The interpolations
+were done with the `SSN` R package [@isaak_applications_2014; @hoef_ssn:_2014].
 
@@
 
-```{r eval = TRUE}
+```{r, cache = FALSE}
+cv_bias_caption <- paste0(
+  "Bias of the interpolation from Leave-One-Out Cross Validation (LOOCV). "
+)
+```
+
+```{r, eval = TRUE}
 myload(cv_press_interp_mv_avg,
@@
 
+```
+```{r, cache = FALSE}
+
 cv_dbo_temp_flow %>%
@@
     caption = paste0("Results of the cross-validation for the interpolation of
-      BOD, temperature and flow. Average over 4 interpolations are shown.") 
-      ) %>%
+      BOD, temperature and flow. Average over 4 interpolations are shown. The
+      cross-validation were performed with the SSN R package. bias: average
+      predicted error, std.biais: bias standardized, RMSPE: Root Mean-Squared
+      Prediction Error, std.MSPE: standardized Mean-Squared Prediction Error.") ) %>%
     collapse_rows(columns = c(1, 2), valign = "top") %>%
@@
 
-```{r}
-cv_bias_caption <- paste0(
-  "Bias of the interpolation from Leave-One-Out Cross Validation (LOOCV). "
-)
-```
-
-The performance of the interpolation was evaluated with leave one out
+The performance of the interpolations was evaluated with leave one out
 cross-validation (already implemented in the SSN package), i.e. the value of the
@@
 predicted value by respectively the minimum and the maximum value found in the
-dataset. We ran the interpolation four times and we kept the predicted value
+dataset. We ran the interpolation four times, and we kept the predicted value
 which had the least standard deviation.
 
-```{=latex}
-\pagebreak
-```
-
 # Data analysis
@@
 
-The CV of biomass over time can cover multiple dynamics, including increases,
-stable, decreases and a mix of them. Theoretically, however, the CV computed to
-quantify stability is often represented with the assumption that the overall
-dynamic of the biomass varies around an equilibrium. In order to approach this
-condition, we kept only the stations that have met this criteria. To qualify the
-biomass trajectories over time, we used the symbolic aggregated approximation
-method (SAX) which is commonly used in time series analysis and implemented in
-the `jmotif` R package. This method classifies time series rather than
-quantifies trends and so is generic enough to encompass the diversity of time
-series shapes. The classification necessitates three steps. First, the time
+The CV of biomass over time can cover multiple temporal dynamics, including
+increases, stable, decreases and a mix of them. Theoretically, however, the CV
+computed to quantify stability is often represented with the assumption that the
+overall dynamic of the biomass varies around an equilibrium
+[@kefi_advancing_2019]. In order to approach the condition of equilibrium, we kept only the
+stations that have met this criteria. To characterise the biomass temporal
+dynamics, we used the symbolic aggregated approximation method (SAX), which is
+commonly used in time series analysis and implemented in the `jmotif` R package
+[@senin_grammarviz_2018].  This method classifies time series rather than
+quantifies trends and so is generic enough to encompass a diversity of temporal
+trajectories. The classification necessitates three steps. First, the time
 series are normalized (i.e. substituting the mean and divide by the standard
 deviation). The second step is to reduce the dimensionality of the time series
-by Piecewise Aggregation Approximation (PAA) method. Each time series is divided
-in $N$ frames of equal size that allows to the reduce the dimensionality of the
-time series. For each frame, we simply kept the mean value of the time series.
-The last step is to qualify each frame into string. Because values of
+by a Piecewise Aggregation Approximation (PAA) method. Each time series is
+divided in $N$ frames of equal size that allows to reduce the dimensionality
+of the time series. For each frame, we simply kept the mean value of the time
+series. The last step is to qualify each frame into string. Because values of
 normalized time series typically follows a normal distribution ($N(0,1)$), a
-breakpoints can be computed by dividing the area under the normal distribution
-in equal parts. The algorithm attributes a alphabetic letter to each part from
+breakpoint can be computed by dividing the area under the normal distribution
+in equal parts. The algorithm attributes an alphabetic letter to each part from
 the lowest to the highest ($a$, $b$, $c$, ...). We set three breakpoints, so
@@
 a combination of $a$, $b$, $c$ letters. $abc$ and $cba$ time series represent
-respectively monotonic increasing and decreasing trajectories. For data analysis,
-we kept only the $bbb$ which represent time series that showed no temporal
-tendencies, with respect to our methodology.
+respectively monotonic increasing and decreasing trajectories. For data
+analysis, we kept only the $bbb$ which represent time series that showed no
+temporal tendencies, with respect to our methodology.
 
@@
 
-```{r contrib-pca}
+```{r contrib-pca, cache = FALSE}
 #https://stats.stackexchange.com/a/143949
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, cache = FALSE}
 corr_pca_caption <- paste0(
@@
 pca_caption <- paste0(
-  "Rotated axis of PCA on environmental variables. The five components
-  explained,", tot_var_expl_pca, "% of the variance (",
-  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
-  "(A) Axis 1 was positively related to the stream size, axis 2 was related to
-  the stream slope and altitude and negatively related to average water temperature and
-  BOD. (B) Eigenvalues distribution, we kept the first two axis for the data analysis. ",
-  "Please note that we took the inverse of the second axis in the data analysis,
-  to make the axis more easily interpretable, i.e. positively related de average
-  water temperature."
-
+  "Eigenvalues distribution, we kept the first two axis for the data analysis." 
   )
@@
 
-pca_plot <- plot_grid(p1, eigen_rotated_plot, nrow = 1)
+pca_plot <- plot_grid(eigen_rotated_plot, nrow = 1)
 save_plot(
@@
 
-```{r}
+```{r, cache = FALSE}
 sem_variable_table <- tibble(
@@
   transformation = c("Log base 10", "Log base 10 and inversion", "Log base 10", rep("No", 2), rep("Log base 10", 3)),
-  interpretation = c("linked to stream size",
+  description = c("linked to stream size",
     "linked to average temperature and BOD",
     "Total species richness over the temporal series",
-    "Median of annual link density", "Median of annual average trophic level", "", "",
-    "Median of annual total biomass")) %>%
+    "Median of annual link density", "Median of annual average trophic level",
+    "Temporal synchrony in the dynamics of population biomass", "Average
+    variability of population biomass", "Median of annual total biomass")) %>%
 kable(
@@
   booktabs = T,
-  caption = "Variable description and transformation"
+  caption = "The description of the variables used in the structural equation models."
   ) %>%
@@
 ```
+
+\begin{table}
+\caption{\label{tab:hyp-sem} Presentation of the links 
+of the Structural Equation Models associated with the references supporting the links.}
+\begin{center}
+\begin{tabular}{ m{7cm}| m{1cm}| m{6cm}}
+    \hline
+    Link & sign & reference\\
+    \hline
+    PCA1 Avg stream size $\to$ Species richness & (+) & Post et al. (2000); Doi et al. (2009); McHugh et al. (2010) \\
+    \hline
+    PCA2 Avg temperature $\to$ Species richness & (+/-) & O’Gorman et al. (2017); Gauzens et al. (2020) \\
+    \hline
+    PCA1 Avg stream size $\to$ Connectance & (?) & \\
+    \hline
+    PCA2 Avg temperature $\to$ Connectance & (+/-) & Petchey et al. (2010) \\
+    \hline
+    Species richness $\to$ Connectance & (-) & Winemiller (1989); Dunne (2006) \\
+    \hline
+    PCA1 Avg stream size $\to$ Avg trophic level & (+) & Post et al. (2000); Doi et al. (2009); McHugh et al. (2010) \\
+    \hline
+    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & O’Gorman et al. (2017)\\
+    \hline
+    Species richness $\to$ Avg trophic level & (+) & Schneider et al. (2016)\\
+    \hline
+    Species richness $\to$ Synchrony & (-) & Thébault and Loreau (2005); Loreau and de Mazancourt (2008); Thibaut and Connolly (2013) \\
+    \hline
+    Connectance $\to$ Synchrony & (+) & Teng and McCann (2004)\\
+    \hline
+    Avg trophic level $\to$ Synchrony & (+) & Raimondo et al. (2004)\\
+    \hline
+    PCA1 Avg stream size $\to$ Synchrony & (?) & \\
+    \hline
+    PCA2 Avg temperature $\to$ Synchrony & (+) & Loreau and de Mazancourt (2008)\\
+    \hline
+    Species richness $\to$ CVsp & (+) & Tilman (1996) \\
+    \hline
+    Connectance $\to$ CVsp & (+) & Thébault and Loreau (2005)\\
+    \hline
+    Avg trophic level $\to$ CVsp & (-) & McCann and Rooney (2009); Shanafelt and Loreau (2018)\\
+    \hline
+    PCA1 Avg stream size $\to$ CVsp & (?) & \\
+    \hline
+    PCA2 Avg temperature $\to$ CVsp & (+) & O’Gorman et al. (2017); Tabi et al. (2019)\\
+    \hline
+    CVsp $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
+    \hline
+    Synchrony $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
+    \hline
+    Species richness $\to$ Total biomass & (+) & Schneider et al. (2016)\\
+    \hline
+    Connectance $\to$ Total biomass & NA & Wang and Brose (2018)\\
+    \hline
+    Avg trophic level $\to$ Total biomass & (+) & Wang and Brose (2018)\\
+    \hline
+    PCA1 Avg stream size $\to$ Total biomass & (+) & Post et al. (2000); Allan and Ibanez Castillo (2009); Doi et al. (2009)\\
+    \hline
+    PCA2 Avg temperature $\to$ Total biomass & (+/-) & O’Gorman et al. (2017)\\
+    \hline
+    \end{tabular}
+\end{center}
+\end{table}
 
@@
 
-```{r}
+```{r, cache = FALSE}
 hist_var_caption <- paste0(
-  "Distribution of the variables used in the Structural Equation Modeling. The
+  "Distribution of the variables included Structural Equation Models The
   biomass stability, the CV of species (CVsp), PCA1, PCA2, species richness,
@@
 
-```{r hist-sem-data, fig.cap = hist_var_caption}
+```{r hist-sem-data, cache = FALSE, fig.cap = hist_var_caption}
 sem_data %>%
@@
 
-```{r}
+```{r, cache = FALSE}
 colin_sem_cap <- paste0(
@@
 
+```
+
+```{r, cache = FALSE}
 kable(colin_stab_sem,
@@
   booktabs = T,
-  caption = "Variance Inflation Factor for the linear models used in structural
-  equation modeling"
+  caption = "Variance Inflation Factor for the linear models used in the structural
+  equation models. NA values indicate that the term in column was not included
+  in the modeling of the response variable in row."
   ) %>%
@@
 
-```{r}
+```{r, cache = FALSE}
 caption_mod_res <- paste0(
-  "Residuals versus fitted values of the linear models used in the structural
+  "Residuals versus fitted values of the linear models included in the structural
   equation models."
@@
 
-```{r mod-res, fig.height = 8, fig.cap = caption_mod_res}
+```{r mod-res, fig.width = 7, fig.asp = 2, fig.cap = caption_mod_res, cache = FALSE}
 library(nlme)
@@
 
-kable(format_coef_table(stab_sem_rich),
+format_coef_table(stab_sem_rich) %>%
+  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F), format = "latex", escape = F)) %>%
+  kable(
     format = "latex",
     booktabs = T,
-  caption = est_stab_sem_caption
+    caption = est_stab_sem_caption,
+    escape = F 
     ) %>%
@@
 
-kable(format_coef_table(bm_sem_rich),
+format_coef_table(bm_sem_rich) %>%
+  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
+kable(
   format = "latex",
   booktabs = T,
-  caption = est_bm_sem_caption
+  caption = est_bm_sem_caption,
+  escape = F 
   ) %>%
@@
   holes in their sampling period; ", "Complete is the dataset containing all the
-  site that have been followed ten years or more, as the other dataset;", "Without holes dataset is
+  site that have been followed ten years or more, as the other dataset;", " Without holes dataset is
   the dataset containing only the sites that had no holes in the their sampling period."

### 2021-04-26 manuscript/bef_stability/fig1_biomass_network.Rmd
Updates

@@
 
+```{r}
+sp_color <- set_color_species(
+  node_list = colnames(metaweb_analysis$metaweb),
+  resource_list = metaweb_analysis$resource
+)
+node_sp <- str_extract(colnames(metaweb_analysis$metaweb), "[A-Z|a-z]*")
+sp_color[node_sp]
+
+myload(metaweb_analysis,  dir = mypath("data"))
+TL <- NetIndices::TrophInd(metaweb_analysis$metaweb)$TL
+PlotWeb(
+  TL = TL,
+  webTL = metaweb_analysis$metaweb,
+  colnode = sp_color[node_sp],
+  abund = 1,
+  collink="grey70",
+  scale_abun = .005
+) 
+```
+
+```{r}
+```
+
 ```{r, warning = FALSE}
@@
 plot_grid(plotlist = gg, nrow = 2)
-```
-
-```{r}
 ```
@@
 )
+pca_rotated$rotated$loadings[, 2] <- pca_rotated$rotated$loadings[, 2] * (-1) 
 p1 <- my_pca_plot(.data = pca_rotated$rotated,
@@
   seed = 1
+)
+save_plot(file = mypath("manuscript", "bef_stability", "figs", 
+	"my_sweet_rotated_pca_reversed_axis2.pdf"),
+    plot = p1,
+    base_height = 4.5, base_asp = 1.2#1.618 
     )
@@
 )
+
 ``` 
@@
 # i3: mod + shift + space 
+png(file = “C://R//SAVEHERE//myplot.jpeg”)
+plot(x,y)
+dev.off()
 

### 2021-04-26 manuscript/bef_stability/manuscript.Rmd
Updates

@@
     keep_tex: true
+  word_document:
 fontsize: 12pt
@@
 - Number of references: 92
-- Number of figures: 2
+- Number of figures: 3
 - Number of tables: 1
@@
 relationships are central to ecology. However, they remain largely untested in
-natural context. Here we study the links among environmental conditions,
+natural context. Here we quantify the links among environmental conditions,
 richness, food-web structure, annual biomass and its temporal stability using a
@@
 positively related to annual biomass, with effects of similar strength. Second,
-we show that food-web structure affects community stability, with a positive
-effect of mean trophic level, and contrary to expectation, a destabilizing
+we show that mean trophic level decrease population variability thereby
+increasing community stability, and contrary to expectation, a destabilizing
 effect of species richness. Finally, we find that environmental conditions
 affect both biomass and its stability via effects on richness and network
-structure. Strikingly, effects on stability are mediated by population stability
-rather than synchrony, which contrasts with results from single-trophic
-communities and might be characteristic of multi-trophic communities.
+structure. Strikingly, the variation of stability are mediated by population
+stability rather than synchrony, which contrasts with results from
+single-trophic communities and might be characteristic of multi-trophic
+communities.
 
@@
 [@hector_plant_1999; @loreau_biodiversity_2001; @hooper_effects_2005;
-@dunne_network_2006; @duffy_why_2009], because it largely determines the
-amount and the distribution of matter and energy fluxes within and among
-ecosystems [@loreau_meta-ecosystems:_2003]. Understanding the relationship
+@dunne_network_2006; @duffy_why_2009]. Understanding the relationship
 between biodiversity and ecosystem properties is thus crucial to better
@@
 
-Species richness has been found to increase primary productivity, community biomass
-and its temporal stability in a diversity of ecosystems and taxa both
+Species richness has been found to increase primary productivity, community
+biomass and its temporal stability in a diversity of ecosystems and taxa both
 empirically and experimentally [@tilman_productivity_1996;
@@
 @grace_integrative_2016; @pennekamp_biodiversity_2018; @houlahan_negative_2018;
-@olivier_urbanization_2020]. However, the relationship between
-diversity and ecosystem functioning remains mostly focused on single trophic
-levels, generally the primary producers, ignoring the effects of food-web
-structure. This gap is even more striking for the relationship between diversity
-and temporal stability, in spite of long-standing interest for the links between
-food-web complexity and stability in theoretical ecology [e.g.  @may_will_1972;
+@olivier_urbanization_2020].  However, these studies mainly focused on
+communities composed of a single trophic level, generally primary producers,
+thereby ignoring potential effects of food-web structure [but see
+@scherber_bottom-up_2010]. Conversely, theoretical works suggest that both
+species richness and food-web structure affect ecosystem properties such as
+productivity, total biomass and its stability. For example, the presence of
+species at higher trophic levels may increase total primary production, through
+the selection of primary producers which are larger and more complementary
+[@wang_biodiversity_2018]. In communities including producers and consumers, the
+connectance which measures the degree of consumer generalism is predicted to
+modulate the diversity-productivity relationship [@thebault_food-web_2003;
+@thebault_cascading_2007]. Similarly, theoretical studies generally show strong
+links between food-web structure and stability [e.g.  @may_will_1972;
 @dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
-@stouffer_compartmentalization_2011].
-
-Overall, the evidence from theoretical models suggests that both species
-richness and food-web structure should modulate ecosystem properties such as
-community biomass and its stability. Complementarity in the use of
-resources is important to understand the effects of species richness on
-productivity in food-webs [@thebault_food-web_2003; @poisot_trophic_2013;
-@schneider_animal_2016], but it also depends on food-webs connectance, i.e. its
-level of generalism [@thebault_food-web_2003; @thebault_cascading_2007]. In
-addition, the presence of species at higher trophic levels may increase total
-primary production, through possibly through the selection of primary producers
-which are larger and more complementary [@wang_biodiversity_2018].
-
-As classically found in studies considering a single trophic level,
-[@tilman_biodiversity_2006; @loreau_species_2008; @olivier_urbanization_2020],
-asynchrony in population temporal variations also explains a significant part
-of the stabilizing effects of species richness on community biomass in food-webs
-[@thebault_trophic_2005]. Indeed, a low synchrony in population fluctuations,
-i.e. asynchrony, is synonymous of compensatory dynamics, where the decrease in
-abundance of a population is compensated by the increase of another. However,
-higher food-web connectance can counterbalance the positive effects of species
-richness on temporal stability of community biomass, because it may increase
-competition between consumers and then leads to a positive relationship between
-species richness and population temporal variability
-[@thebault_trophic_2005]. The addition of predators has
-also cascading effects on both population variability and
-synchrony at lower trophic levels [@teng_dynamics_2004;
-@shanafelt_stability_2018]. Overall, these theoretical studies show that the
-effects of species richness and food-web structure, such as connectance and
-average trophic level, are potentially conflicting or synergistic in such a way
-that they need to be addressed jointly.
-
-The lack of studies that consider jointly effects of diversity and food-web
-structure on ecosystem functions can be explained by the challenges associated
-with manipulating both species richness and food-web complexity in an
-experimental context [e.g. @sander_ecological_2017] and by the fact that
-describing trophic interactions between species is highly labour intensive.
-These challenges are even more acute for the study of the stability of ecosystem
-properties, which additionally requires longer-term perspectives. In this
-context, recent developments to predict species trophic interactions
-[@beckerman_foraging_2006; @gravel_inferring_2013; @portalier_mechanics_2019],
-combined with observational long-term surveys of ecological communities, can
-offer the opportunity to investigate the links between diversity, food-web
-structure and the stability of total community biomass in natural settings.
-
-The joint study of the effects of diversity and food web structure on total
+@stouffer_compartmentalization_2011].  Overall, the evidences from theoretical
+model suggests that both species richness and food-web structure should affect
+community biomass and stability, but empirical evidences of the effects of
+network structure on community biomass and stability are lacking.
+
+While community stability can be measured in many ways in theoretical studies,
+most empirical studies measure community stability as the inverse of the
+coefficient of variation of community productivity, biomass or abundance, also
+called temporal stability [@kefi_advancing_2019]. This stability metric is also
+well grounded in theory [e.g. @thebault_trophic_2005; @loreau_species_2008;
+@thibaut_understanding_2013] and can be decomposed into two components:
+population stability and synchrony [@thibaut_understanding_2013].  Studies
+considering a single trophic level [@yachi_biodiversity_1999;
+@tilman_biodiversity_2006; @loreau_species_2008; @olivier_urbanization_2020] as
+well as theoretical prediction for multitrophic communities
+[@thebault_trophic_2005] tend to highlight that asynchrony in population
+dynamics as key for the stabilizing effects of species richness on community
+biomass. Theory also predicts that higher food-web connectance can
+counterbalance the positive effect of species richness on the temporal stability
+of community biomass, because it may increase interaction strength and
+thereby increases population variability, leading to a negative relationship
+between species richness and the temporal stability of populations
+[@thebault_trophic_2005]. Predators can also have cascading effects on both
+population variability and synchrony at lower trophic levels
+[@teng_dynamics_2004; @shanafelt_stability_2018]. Overall, these theoretical
+studies show that the effects of species richness and food-web structure, such
+as connectance and average trophic level, are potentially conflicting or
+synergistic in such a way that they need to be addressed jointly.
+
+The joint study of the effects of species richness and food-web structure on total
 biomass and its stability is even more important in the context of environmental
-changes. Recent studies on natural communities have shown that environment may
-alter community biomass [@grace_integrative_2016; @woods_testing_2020] and its
-temporal stability [@oliver_heterogeneous_2010; @franssen_annual_2011;
-@hansen_climate_2013; @bluthgen_land_2016; @de_boeck_patterns_2017;
-@friedpetersen_drivers_2020]. For example, larger ecosystem might increase the
-number of available resources and thus community biomass [@post_ecosystem_2000;
-@doi_resource_2009] while temperature affects ecosystem respiration and biomass
-distribution [@yvondurocher_warming_2011; @schwarz_warming_2017;
-@tabi_warming_2019]. Environment also directly affect species richness and
-food-web structure, as larger ecosystems host food-webs with higher diversity
-and trophic levels [@mchugh_dual_2010] whereas temperature can affect food-web
-diversity and structure in contrasted ways depending on the ecosystem studied
-[@ogorman_unexpected_2017; @gauzens_biodiversity_2020]. In natural communities,
-the relationships among species richness, community biomass and its temporal
-stability might also arise from effects of the environment on both diversity and
-ecosystem functions [@loreau_biodiversity_2001; @he_global_2013;
-@grace_integrative_2016]. Thus, the effect of environment on ecosystem
-functioning might arise from direct effects or indirectly through effects on
-species richness or food-web structure.
+changes. Recent studies comparing natural communities have shown that
+environmental characteristics determine in part community biomass
+[@grace_integrative_2016; @woods_testing_2020] and its temporal stability
+[@franssen_annual_2011; @hansen_climate_2013; @bluthgen_land_2016;
+@de_boeck_patterns_2017; @friedpetersen_drivers_2020]. The environment can
+affect ecosystem function or stability directly. For example, larger freshwater ecosystems
+tend to have more available resources and thus community biomass
+[@post_ecosystem_2000; @doi_resource_2009] while agricultural intensification
+destabilizes bird communities by decreasing population stability
+[@olivier_urbanization_2020]. The effects of environment can also go through
+effects on species richness and food-web structure, as larger ecosystems host
+food-webs with higher diversity and trophic levels [@mchugh_dual_2010] whereas
+temperature can affect food-web diversity and structure in contrasted ways
+depending on the ecosystem studied [@ogorman_unexpected_2017;
+@gauzens_biodiversity_2020]. Environmental characteristics have thus to be
+accounted for if we are to tease apart the effects of species richness and
+foodweb structure on community biomass and its temporal stability.
 
@@
 
-Because their trophic interactions are well known, stream fish communities
-constitute a good model to study the effects of network structure on total
-biomass and its temporal stability. A substantial body of literature
-supports that trophic interactions can be inferred through body size and diet
-informations [@jennings_weak_2001; @beckerman_foraging_2006;
-@gravel_inferring_2013; @brose_predator_2019; @portalier_mechanics_2019].
-
-Our aim is to document the relationships among species richness, food-web
-structure, community biomass and its temporal stability in natural communities. To
-do so, we used a standardized sampling of fish
-communities in French streams [@edeline_ecological_2013]. We selected 99 sites
-that have been sampled for more than 10 years. We inferred 1496 interaction
-networks, based on body size and diet. We question whether species richness,
-food-web connectance and average trophic level are related to community biomass and its
-temporal stability. We further assess how ecosystem size and temperature
-mediated this relationship.
+Stream fish communities constitute a good model to study the effects of network
+structure on total biomass and its temporal stability because their trophic
+interactions are well known,. A substantial body of literature supports that
+trophic interactions can be inferred through body size and diet informations
+[@jennings_weak_2001; @beckerman_foraging_2006; @gravel_inferring_2013;
+@brose_predator_2019; @portalier_mechanics_2019]. Using long-term monitoring of
+stream fish communities [@edeline_ecological_2013], we propose one of the first
+attempts to test empirically the theoretical expectations on the
+diversity-stability relationships according for community, trophic complexity
+and environmental characteristics.
 
@@
 We determined the network structure in two steps: (1) build a metaweb describing the
-trophic interactions between all fishes and the resources (Fig.
+trophic interactions between fishes and the resources (Fig.
 SXX), then (2) determine network of a given community by
@@
 of stream fishes, as for many organisms, shifts throughout an individual's life,
-and thereby with body size. For example, larvae and small juveniles feed on plankton while adults
-may feed on algae and fishes, with bigger individuals eating bigger fishes. Each
-fish species was hence divided in nine body size classes, each corresponding to
-a trophic species (appendix B, Fig. S2). Additionally to the trophic species, we added
-seven resource nodes present in the ontogenic food diet database: detritus,
-biofilm, phytoplankton, zooplankton, macrophages, phytobenthos and zoobenthos
-(grey nodes in Fig. \@ref(fig:matmet)C & D). The trophic species and the
-resources constituted the 412 nodes of the metaweb, i.e. 45 fish species divided
-into nine body size classes plus seven resource nodes. The inference of trophic
-interactions was shown to be more accurate when considering body size classes,
-i.e. trophic species, than species [@jennings_weak_2001].
+and thereby with body size. For example, larvae and small juveniles feed on
+plankton while adults may feed on algae and fishes, with bigger individuals
+eating bigger fishes. Each fish species was divided in nine body size
+classes, each corresponding to a trophic species (appendix B, Fig. S2). A
+trophic species constitutes a group of individuals from the same species and
+size class, which are expected to share the same sets of prey and predators.
+Additionally to the trophic species, we added seven resource nodes present in
+the ontogenic food diet database: detritus, biofilm, phytoplankton, zooplankton,
+macrophages, phytobenthos and zoobenthos (grey nodes in Fig. \@ref(fig:matmet)C
+& D). The trophic species and the resources constituted the 412 nodes of the
+metaweb, i.e. 45 fish species divided into nine body size classes plus seven
+resource nodes. The inference of trophic interactions was shown to be more
+accurate when considering body size classes, i.e. trophic species, than species
+[@jennings_weak_2001].
 
@@
 on community biomass ($r_\delta = `r rich_on_bm$direct`$ and 
-$r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-bm)A, Table
+$r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-bm)A, B, C, Table
 \@ref(tab:indir-sem)), while connectance had no direct effect.
@@
 `r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_tlvl["log_RC1"]`$
-resp., Table \@ref(tab:indir-sem)). The second axis, related to the average
+resp., Fig. \@ref(fig:sem-bm) F, G, Table \@ref(tab:indir-sem)). The second axis, related to the average
 annual temperature was positively related
@@
 \@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
-`r env_on_bm$via_richness["log_RC2"]`$, Table \@ref(tab:indir-sem)). Streams
+`r env_on_bm$via_richness["log_RC2"]`$, Fig. \@ref(fig:sem-bm) G, Table \@ref(tab:indir-sem)). Streams
 with higher temperature and BOD contained more species, indirectly increasing
@@
 
-By its effects on synchrony and population variability ($\overline{CV_{sp}}$), species richness had a
-negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
-Table \@ref(tab:indir-sem)). This effect resulted from two opposite effects. On
-the one hand, species richness had a direct negative effect on synchrony
-($r_\delta = `r rich_on_sync$direct`$), thereby
-increasing stability ($r_\delta = `r rich_on_stab$via_sync`$). On the other
-hand, species richness had a positive direct effect on $\overline{CV_{sp}}$
-($r_\delta = `r rich_on_cv_sp$direct`$),
-thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
-\@ref(tab:indir-sem)), which outweighted the decreasing effect of species
-richness on synchrony. The
-negative effect of $\overline{CV_{sp}}$ on temporal stability was twice higher
-than the negative effect of synchrony (resp.
-$r_\delta = `r cv_sp_on_stab`$ and $r_\delta = `r sync_on_stab`$, Fig.
-\@ref(fig:sem-stab)A).
+By its effects on synchrony and population variability ($\overline{CV_{sp}}$),
+species richness had a negative total effect on biomass stability ($r_\delta =
+`r rich_on_stab$total`$, Table \@ref(tab:indir-sem)). This effect resulted from
+two opposite effects. On the one hand, species richness had a direct negative
+effect on synchrony ($r_\delta = `r rich_on_sync$direct`$, Fig.
+\@ref(fig:sem-stab) A, B), thereby increasing stability ($r_\delta = 
+`r rich_on_stab$via_sync`$). On the other hand, species richness had a positive
+direct effect on $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$,
+Fig. \@ref(fig:sem-stab) A, C), thereby decreasing biomass stability ($r_\delta
+= `r rich_on_stab$via_cv_sp`$, Table \@ref(tab:indir-sem)), which outweighted
+the decreasing effect of species richness on synchrony. The negative effect of
+$\overline{CV_{sp}}$ on temporal stability was twice higher than the negative
+effect of synchrony (resp.  $r_\delta = `r cv_sp_on_stab`$ and $r_\delta = 
+`r sync_on_stab`$, Fig.  \@ref(fig:sem-stab)A). Population variability and
+synchrony constitute a mathematical decompositon of the stability, contributing
+respectively to 1 and 0.5 respectively (Eq. \@ref{eq:stab}), meaning that their
+$r_\delta$ difference to temporal stability is due to their standard deviation,
+and so that the standard deviation of $\overline{CV_{sp}}$ is of the same
+magnitude than the one of synchrony.
 
@@
 $`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
-\@ref(tab:indir-sem)).
-The mean trophic level had only a direct negative effect on
-$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
-Fig. \@ref(fig:sem-stab)A) and thereby had a total positive
-effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$,
-Table \@ref(tab:indir-sem)). Food webs in which community biomass is located on
+\@ref(tab:indir-sem)).  The mean trophic level had only a direct negative effect
+on $\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$, Fig.
+\@ref(fig:sem-stab)A, F) and thereby had a total positive effect on temporal
+stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$, Table
+\@ref(tab:indir-sem)). Food webs in which community biomass is located on
 average at higher trophic levels thus tend to have higher population and
@@
 
-The total effect of PCA2, related to average annual temperature and BOD, on temporal
-stability was of higher magnitude than the effects of species richness and mean
-trophic level (Table \@ref(tab:indir-sem)).
-The PCA2 had a total negative effect on temporal stability, meaning that higher
-temperature and BOD results in lower stability
-($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). 
-PCA2 had an indirect positive effect on temporal stability through a
-direct positive effect on mean trophic level ($r_\delta = 
-`r env_on_stab$via_tlvl["log_RC2"]`$, Table \@ref(tab:indir-sem)). However, PCA2
-had a negative effect on temporal stability through a direct positive effect on 
-$\overline{CV_{sp}}$ and species richness (resp.  $r_\delta = 
-`r env_on_cv_sp$direct["log_RC2"]`$ and $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$,
-Table \@ref(tab:indir-sem)). This was also true for the PCA1, related to stream
-size, with a resulting very slight positive effect of PCA1 on temporal stability
-($r_\delta = `r env_on_stab$total["log_RC1"]`$, Table \@ref(tab:indir-sem)).
-Warmer and larger streams thus tend to have more species and more variability in
-population biomass, then have a lower stability of community biomass.
+The total effect of PCA2, related to average annual temperature and BOD, on
+temporal stability was of higher magnitude than the effects of species richness
+and mean trophic level (Table \@ref(tab:indir-sem)).  The PCA2 had a total
+negative effect on temporal stability, meaning that higher temperature and BOD
+results in lower stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table
+\@ref(tab:indir-sem)).  PCA2 had an indirect positive effect on temporal
+stability through a direct positive effect on mean trophic level ($r_\delta = 
+`r env_on_stab$via_tlvl["log_RC2"]`$, Fig. \@ref(fig:sem-stab) I, Table
+\@ref(tab:indir-sem)). However, PCA2 had a negative effect on temporal stability
+through a direct positive effect on $\overline{CV_{sp}}$ and species richness
+(resp.  $r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$ and $r_\delta = 
+`r env_on_stab$via_richness["log_RC2"]`$, Fig. \@ref(fig:sem-stab)G, Fig.
+\@ref(fig:sem-bm)G, Table \@ref(tab:indir-sem)). This was
+also true for the PCA1, related to stream size, with a resulting very slight
+positive effect of PCA1 on temporal stability ($r_\delta = 
+`r env_on_stab$total["log_RC1"]`$, Table \@ref(tab:indir-sem)).  Warmer and
+larger streams thus tend to have more species and more variability in population
+biomass, then have a lower stability of community biomass.
 
@@
 
-We found that species richness increased community biomass as already
-found in plant and tree communities [@hector_plant_1999;
+We found that species richness increased community biomass in line with the
+results on plants and tree communities [@hector_plant_1999;
 @tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018] as well
-as in fish communities [@maureaud_biodiversityecosystem_2019;
-@woods_testing_2020]. The positive effect of species richness on community biomass
-might be due to resource use complementarity [@carey_determining_2011], which is
-driven by niche differentiation [@loreau_biodiversity_1998;
-@loreau_partitioning_2001] or to the higher probability to include high biomass
-species with higher species richness [@loreau_biodiversity_2001]. Our results
-are also in agreement with a model predicting a positive relationship between
-animal diversity and total consumer biomass in size-structured food-web
-[@schneider_animal_2016].
-
-Surprisingly, we found a negative relationship between temporal stability and
-species richness. It contrasts with experimental studies in grasslands
-[@tilman_biodiversity_2006; @valencia_synchrony_2020], mesocosms
-[@pennekamp_biodiversity_2018] with studies on natural communities such as
-butterflies  or lotic fishes [@olivier_urbanization_2020; @franssen_annual_2011
-], where positive relationships were found between temporal community
-stability and species richness. However, some other studies also found a
-negative relationship, for instance in natural grasslands [@yang_effects_2011]
-or a marginal relationship in natural forests [@declerck_species_2006].
-
-As most studies on experimental grasslands [@isbell_biodiversity_2009;
-@roscher_identifying_2011] and natural communities of birds, grasslands, bats
-and butterflies [@bluthgen_land_2016; @olivier_urbanization_2020], we found that
-species richness decreases synchrony, thereby increasing stability [but see
-@declerck_species_2006; @valencia_synchrony_2020]. Our study thus extends the
-evidence that species richness decreases synchrony to the case of multi-trophic
-communities. Species richness can reduce synchrony when (i) a given increase in species
-richness raises demographic stochasticity by decreasing population
-sizes, or when (ii) species have different responses to environmental variation
-[@loreau_species_2008].
-
-The positive effect of species richness on
-$\overline{CV_{sp}}$, thereby decreasing stability, is more intriguing. While
-studies focusing on single-trophic communities have reported mixed effects of
-species richness on $\overline{CV_{sp}}$, with destabilising effects of species
-richness at population level in grasslands [@jiang_different_2009;
-@gross_species_2014], a previous meta-analysis suggested that species richness had
-often a positive effect on population stability in multi-trophic communities
-[@jiang_different_2009].
-In food-webs, theoretical models predict that the relationship between temporal
-stability of populations and species richness depends on interaction strength
-and its distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
-@downing_temporal_2020], with stronger interactions promoting a negative
-relationship between species richness and stability. Therefore, it is possible
-that our results are due to strong trophic interactions, leading to more
-fluctuations in population biomass, but this hypothese was not testable with the
-available dataset.  Alternatively, our results might be explain by the effect of
-increasing species richness which can increase demographic stochasticity.
+as those found for fish communities [@maureaud_biodiversityecosystem_2019;
+@woods_testing_2020] and for theoretical food-web models
+[@schneider_animal_2016]. Theory suggests that the positive effect of species
+richness on community biomass might be held by resource use complementarity
+[@carey_determining_2011], which is driven by niche differentiation
+[@loreau_biodiversity_1998; @loreau_partitioning_2001] or by positive selection
+effect, which is driven by the dominance of the most productive species
+[@loreau_biodiversity_2001]. Recent findings suggest that dominance, a positive
+selection effect [@loreau_partitioning_2001], is the main driver of the observed
+positive relationship between biomass and species richnes in fish communities
+[@maureaud_biodiversityecosystem_2019; @woods_testing_2020].
+
+We found that species richness decreases synchrony, threby increasing stability.
+This is in accordance with most studies on experimental grasslands
+[@isbell_biodiversity_2009; @roscher_identifying_2011] and natural communities
+of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
+@olivier_urbanization_2020]. It is thought that it is the main effect by which
+species richness increases stability [but see @declerck_species_2006;
+@valencia_synchrony_2020].  Our result thus extend that species richness
+decreases synchrony also in multi-trophic communities.  However, theory does not
+clearly state what would be the effect of food-web structure on the relationship
+between species richness and synchrony [@raimondo_interspecific_2004;
+@korpimaki_predatorinduced_2005; @mccann_more_2009].
+
+The positive effect of species richness on population variability, thereby
+decreasing stability, is more intriguing. A previous meta-analysis has indeed
+reported that species richness had often a negative effect on population
+variability in multi-trophic communities while a positive effect is often found
+in single-trophic communities [@jiang_different_2009]. In food-webs, theoretical
+models predict that the relationship between the temporal stability of populations
+and species richness depends on interaction strength and its distribution
+[@mccann_reevaluating_1997; @thebault_trophic_2005; @downing_temporal_2020],
+with stronger interactions promoting a negative relationship between species
+richness and stability. Therefore, it is possible that our results are due to
+strong trophic interactions, leading to more fluctuations in population biomass,
+but this hypothese was not testable with the available dataset. Alternatively,
+other authors suggest that this effect might be due to an increase of
+demographic stochasticity with an increase of species richness [@loreau_species_2008].
+
+A major finding of the study is that we found a negative relationship between
+species richess and temporal stability, contrast with most experimental and
+empirical studies to date [@franssen_annual_2011; @tilman_biodiversity_2006;
+@valencia_synchrony_2020; @pennekamp_biodiversity_2018;
+@olivier_urbanization_2020], but coincide with a few empirical ones
+[@declerck_species_2006]. This finding means that the destabilising effect of
+species richness through population variability was superior its stabilising
+effect through synchrony. It can happen either because of the relative strength
+of the effect species richness on both population variability and synchrony or
+because of the overall variability of synchrony and population variability in
+the our study system.
+
+We found indeed that the population variability had a standardized effect
+on the stability of community biomass twice stronger than synchrony, meaning that the
+variability of synchrony was equivalent the one of population variability, in
+contrast with a previous study which found that the variability of synchrony was
+twice higher than the variability of population variability
+[@olivier_urbanization_2020]. Therefore, the low variability of synchrony in our
+system might be a cause for the observed negative effect of species richness on
+temporal stability of community biomass despite the strong negative effect of species
+richness on synchrony. Could the lower variability of synchrony be a
+characteristic of multitrophic communities? Theoretical models suggest that
+generalist predator can either synchronise or desynchronize the dynamics its
+prey, depending on the distribution of interaction strength and competition
+between preys [@raimondo_interspecific_2004; @korpimaki_predatorinduced_2005;
+@mccann_more_2009]. Alternatively, it is possible that, in aquatic food-webs,
+the occurrence of large oscillatory dynamics typical of predator-prey dynamics
+leads to a larger variability of population variability than the one of synchrony
+[@mccann_reevaluating_1997]. Another hypothese is that food-webs are
+characterized by highly uneveness biomass distribution, which can decrease the
+variability of synchrony, i.e. decrease the strength of the porfolio effect
+[@doak_statistical_1998; @thibaut_understanding_2013].
+
+All together, the destabilising effect of species richness on temporal stability
+raises more questions than it solves and then highlight the need for more
+investigations about the difference between single and multitrophic
+communities in natural communities.
 
@@
 
-The average trophic level was positively linked to community biomass.
-@wang_biodiversity_2018 have shown that total nutrient uptake might increase
-with the length of trophic chains and so results in higher community biomass. While
-the predictions of @wang_biodiversity_2018 were restricted to food chains, and
-thus might not hold in more complex food-webs with omnivory, our
-results are in agreement with their model predictions and highlight the
-importance of food chain length as a determinant of community biomass in food-webs.
-In addition, mean trophic level had a positive effect on biomass stability by
-its negative effect on $\overline{CV_{sp}}$, thereby increasing average
-population 
-stability. This effect might result from a higher stability of population of higher
-trophic level as predicted by food chain models in the presence of strong
-top-down control [@shanafelt_stability_2018; @barbier_pyramids_2019]. An
-alternative explanation is that higher mean trophic level complexify the biomass
-fluxes through the food-webs, which might reduce biomass fluctuations in lower
-trophic levels [@mccann_diversitystability_2000].
-
-In contrast, connectance had no effect on community biomass. One might have expected
-that an increase in connectance may translate in a higher total nutrient uptake
-and so results in higher community biomass in the fish compartment. 
-However, some studies suggest that a greater connectance should decrease
-complementarity in resource use between species, which is expected to
+Our analysis further indicates that network structure, and in particular average
+trophic level was strongly related to community biomass, as higher total
+biomass was found in communities with an higher average trophic level. These results are
+in accordance with the predictions of theoretical models [@schneider_animal_2016;
+@wang_biodiversity_2018]. @wang_biodiversity_2018 proposed that this effect is driven
+by predators selecting primary producers with higher resource use efficiency and predators
+enhancing complementarity between primary producers, a mechanism which
+drive the positive effect of horizontal diversity on productivity
+[@loreau_biodiversity_2001].
+
+In addition, our results show that communities with an higher average trophic
+level had a lower population variability, and thereby were more stable. This
+result is in accordance with theoretical models [@shanafelt_stability_2018;
+@barbier_pyramids_2019; @mccann_diversitystability_2000] and might result from a
+higher stability of populations of higher trophic levels
+[@shanafelt_stability_2018; @barbier_pyramids_2019] or a damping effect of
+higher trophic levels on the variability of lower trophic level populations
+[@mccann_diversitystability_2000].
+
+In contrast, we found that connectance was not related to community biomass,
+which contradicts theoretical models which suggest that a greater connectance should
+decrease complementarity in resource use between species, which is expected to
 lower community biomass [@thebault_food-web_2003; @poisot_trophic_2013].
-
-Regarding temporal stability, our results contrast with numerous previous
-theoretical studies on the relationship between
-connectance and stability [e.g., @angelis_stability_1975; @may_will_1972;
-@thebault_stability_2010; but see @neutel_reconciling_2007], although they
-considered different stability concepts and metrics [@arnoldi_resilience_2016].
-The lack of effect of connectance on the temporal stability of community biomass
-might be related to the fact that our measure of connectance does not take into
-account the distribution of interaction strengths in the food-webs. Indeed,
-food-web connectance is expected to have different consequences on the temporal
-stability of community biomass depending on the strength of trophic interactions
-[@thebault_trophic_2005]. However, our food-webs lack information about the lower
-compartments of the community, i.e. primary producers, decomposers and the benthic
-part of the food-web. Further research should examine the effects of connectance
-on community biomass and its temporal stability in more complete empirical food-webs.
-
-One limitation of our study is indeed the use of inferred networks, i.e. not
-observed interactions. However, this approach is a promising way to explore how the
-architecture of ecological networks vary along environmental gradients and across
-time. It constitutes an interesting complement to the real assessment of
-ecological interactions because it allows to extract most
-of the information contained from already available long term datasets.
-
-## Population stability was the main driver of community temporal stability
-
-The population variability and synchrony are mathematically linked to the
-stability of community biomass (see Methods), so the comparaison of their effect
-reflected that the the comparaison of their variability. In contrast with
-previous studies, we found that the average population variability
-($\overline{CV_{sp}}$) had a stronger negative effect on the stability of
-community biomass than synchrony [@olivier_urbanization_2020], meaning that the
-variability of synchrony was equivalent the one of population variability. It
-explains why we observe a negative effect of species richness on temporal
-stability of community biomass whereas species richness had a strong negative
-effect of synchrony. The lower variability of synchrony might be explained by
-the presence of generalist predators in stream communities, which can promote
-synchrony between prey species that share the same predator and thus reduces
-compensatory population dynamics [@raimondo_interspecific_2004]. Alternatively,
-it is possible that, in aquatic food-webs, the occurrence of large oscillatory
-dynamics leads to a higher variability of population variability rather than
-synchrony to community stability [@mccann_reevaluating_1997]. How both strengths
-of interactions and the relative contribution of synchrony and population
-variability to overall stability vary between food-webs and single trophic
-communities is still an open question.
-
-Our results raise the question of the fundamental differences between single and
-multi-trophic communities. Some mechanisms are transferable from the first to
-the second such higher connectance which might translate in higher competition
-between consumers and thus destabilise populations [@thebault_trophic_2005].
-However, the existence of top-down and bottom-up effects are obviously typical
-to multi-trophic communities. The population at the top of a food-web are
-limited by the growth of its prey (bottom-up effects) while the lower trophic
-levels are limited by both their predators (top-down effect) and their preys
-(bottom-up effects). We can conjecture that the stability of food-webs mainly
-controlled by bottom-up effects will display higher synchrony while the
-food-webs mainly controlled by top-down effects will display higher population
-variability. In sum, average synchrony and population variability might be
-characteristic of communities more or less controlled by top-down or bottom-up
-effects.
-
----
-#Rough average synchrony in Théophile study: exp(-0.75) = .47 or exp(-0.6) = .54
-#This study: sync avg = .69
----
+However, the effect of connectance on productivity has been poorly investigated.
+
+One of the most surprising result is that we found no relationship between
+connectance and stability. It contrasts with the central role that connectance
+plays in the studies of the food-web complexity-stability relationship [e.g.,
+@angelis_stability_1975; @may_will_1972; @thebault_stability_2010; but see
+@neutel_reconciling_2007], although theoretical ecology generally considers
+different stability concepts and metrics [@arnoldi_resilience_2016]. The lack of
+effect of connectance on the temporal stability of community biomass might be
+related to the fact that our measure of connectance does not take into account
+the distribution of interaction strengths in the food-webs. Indeed, food-web
+connectance is expected to have different consequences on the temporal stability
+of community biomass depending on the strength of trophic interactions
+[@thebault_trophic_2005], which we could not test due to the scarcity of
+information on the lower compartments of the community, i.e. primary producers,
+decomposers and the benthic species.
 
@@
 
-We found that environmental drivers affect community biomass mostly indirectly
-[@woods_testing_2020] rather than directly, contrasting with previous studies
-[@yvondurocher_warming_2011; @dossena_warming_2012; @grace_integrative_2016;
-@maureaud_biodiversityecosystem_2019]. First, consistent with research showing
-that food-webs in wider streams support more species and biomass
-[@allan_stream_2007], we found that the PCA axis related to stream size had a
-positive effect on community biomass through a positive effect on mean trophic level
-and species richness. Greater ecosystem size might provide a higher diversity
-of resources through habitat heterogeneity, and so higher species richness and
-community biomass by surface unit, through complementarity in resource use. Greater
-diversity of resources can also maintain more biomass at high trophic level
-[@post_ecosystem_2000; @doi_resource_2009]. Second, the positive effect of the
-PCA axis related to temperature on community biomass was of the magnitude of the
-effects of food-web structure and species richness, in line with the mounting
+We found that the larger, warmer and more enriched streams had higher total biomass
+through higher average trophic level and species richness, in line with mounting
 body of work reporting important effects of temperature on the structure and
-biomass of aquatic systems [e.g.  @dossena_warming_2012;
-@edeline_ecological_2013; @emmrich_geographical_2014; @hattab_forecasting_2016;
-@woods_testing_2020]. We found that warmer streams
-supported higher diversity as well as higher average trophic level and total
-biomass, which is in agreement with recent findings on streams.
-
-While the PCA axis related to stream size had only a weak effect on the temporal
-stability of community biomass, the PCA axis related to temperature had a
-negative effect on temporal stability through a direct destabilizing effect on
-populations and through indirect effects. Temperature can have both stabilizing
-and destabilizing effects in resource-consumer models depending on the thermal
-niche of the species and on how nutrient supply varies with temperature
-[@uszko_effects_2017]. The observed increased variability of populations might
-also relate with ecosystem enrichment [@ogorman_unexpected_2017] because average
-Biological Oxygen Demand covaries with the PCA axis related to average
-temperature (Fig. \ref{fig:matmet}B). Enrichment can increase CV by increasing
-population biomass fluctuations while higher temperature might decrease
-stability through starvation resulting from high metabolic activity
-[@tabi_warming_2019].
+biomass of aquatic systems [@allan_stream_2007; @edeline_ecological_2013;
+@emmrich_geographical_2014; @hattab_forecasting_2016; @woods_testing_2020].
+Larger ecosystem in freshwater systems might provide a higher diversity
+of resources through habitat heterogeneity and then result in higher species
+richness and community biomass by surface unit, through complementarity in
+resource use. Our result suggest that warming and enrichment might result in
+higher total biomass but previous studies find contradictory results
+[@yvondurocher_warming_2011; @dossena_warming_2012;
+@maureaud_biodiversityecosystem_2019; @tabi_warming_2019]. One of the reason
+might be that temperature has non monotonic effects on biological processes and
+that temperature and enrichment can have antagonistic effects 
+[@oconnor_warming_2009; @uszko_effects_2017; @tabi_warming_2019].
+
+Our analysis revealed that stream size had only a weak effect on the temporal
+stability of community biomass, while warmer and enriched streams had an higher
+average population variability, thereby a lower temporal stability. Our results
+are in line with previous experiments showing that warming decreases temporal
+stability, however enrichment is predicted to counter the destabilising effect
+of warming [@binzer_dynamics_2012; @tabi_warming_2019].  However, enrichment alone 
+is predicted to increase population variability while warmer 
+temperature is predicted to decrease stability through starvation resulting from high
+metabolic activity [@tabi_warming_2019] but again it depends on the species thermal
+niche and of the shape of the response of biological processes to warming
+[@uszko_effects_2017].
 
@@
 
+## Network reconstruction: limits and perspectives
+
+The lack of experimental or empirical studies considering the effects of both
+species richness and food-web structure on ecosystem functions can be explained
+by the challenges associated with manipulating both species richness and
+food-web structure  experimentally [e.g. @sander_ecological_2017] and by the
+fact that describing trophic interactions between species is highly labour
+intensive. These challenges are even more acute when studying the temporal
+stability of ecosystem properties, which requires time series. In this context,
+recent developments to predict trophic interactions among species
+[@beckerman_foraging_2006; @gravel_inferring_2013; @portalier_mechanics_2019],
+combined with observational long-term monitoring of ecological communities,
+offer an promising opportunity. They thus offer a way to maximise the  amount of
+information that we can extract from already collected empirical data, but at
+the cost of their precision. Build on the ratio of body-size between predator
+and prey [@gravel_inferring_2013], those methods are however in general blind to
+the modulation of species interactions according to the realized niche of
+species such as temperature and prey preferences. Although, the development of
+more mechanistic methods incorporating predator behaviour
+[@portalier_mechanics_2019] or more statistically flexible framework such as
+machine learning [@pichler_machine_2020] will certainly increase the accuracy of
+species interaction predictions. With the increasing availability of long-term
+empirical data, we believe that methods of food-web reconstruction have a great
+potential to increase our understanding of the role of network structure on
+ecosystem functioning in natural settings.
+
 # Conclusion
@@
 empirical findings on the functioning and stability of communities. Our study
-extends the assessment of the effect of species richness on community biomass and
-its temporal stability to the case of food-webs in natural settings and
-highlights the need to consider species richness, food-web structure and their
-dependence to understand both functioning and stability of communities. Further,
-we found that the effects of environmental gradient related to temperature and
-ecosystem size are largely mediated by their impact on richness and average
-trophic level. Finally, our results highlight population variability as key in
-transmitting effects of richness, network structure and environmental gradients
-on community stability. This contrast with previous results found in single
-trophic communities, mostly plants, that mainly focus on synchrony and, although
-further confirmation are needed, might be characteristic of animal and/or
-multi-trophic communities. Food-web reconstruction methods enable to confront
-theory and experiment to empirical data. With the increasing availability of
-long-term empirical data, we believe that those methods have a great potential
-to increase our understanding of the role of food-web structure on ecosystem
-functioning.
+extends the assessment of the effect of species richness on community biomass
+and its temporal stability to the case of food-webs in natural settings,
+providing the evidence that species richness decreases synchrony also in
+multi-trophic communities. Our results highlight population variability as key
+in transmitting effects of species richness, network structure and environmental
+gradients on community stability. This contrast with previous results found in
+single trophic communities, mostly plants, that mainly focus on synchrony and,
+although further confirmation are needed, might be characteristic of animal
+and/or multi-trophic communities. Further, we found that the effects of
+environmental gradient related to temperature, enrichment and ecosystem size are
+largely mediated by their impact on richness and average trophic level. Finally,
+our study open stimulating questions about how the food-web structure and
+species richness drives synchrony and population variability.
 

### 2021-04-26 manuscript/bef_stability/review_analysis.Rmd
Updates

@@
 
-theme_set(theme_alain())
+theme_set(theme_cowplot())
 
@@
 ```{r}
-synchrony %>%
+p_sync <- synchrony %>%
   ggplot(aes(y = cv_sp * sqrt(synchrony), x = cv_classic)) +
@@
 
-```{r}
-
+```{r, echo = TRUE}
 mod <- lm(log_stab_std ~ 0 + log_cv_sp + log_sync, data = sem_data)
@@
 coefs <- broom::tidy(mod) %>%
-  select(term,estimate)
+  select(term, estimate)
 
@@
 
+```
+
+# Response to the comment
+
+```{r}
+source(mypath("R", "synchrony.R"))
+
+myload(community_analysis, op_analysis, synchrony, dir = mypath("data"))
+
+myload(network_metrics, network_analysis, dir = mypath("data", "classes"))
+```
+
+```{r}
+compute_pair_synchrony <- function (com_mat = NULL) {
+  sp_names <- colnames(com_mat)
+  ti <- combn(sp_names, 2,
+    FUN = function (x) {
+      covar <- cov(x = com_mat[, x[1:2]])
+      #  vars <- var(c(mat[, x[1]], mat[, x[2]])) 
+      sync <- compute_synchrony(covar)
+      names(sync) <- paste(x[1], x[2], sep = "-")
+      return(sync)
+    }, simplify = FALSE
+  )
+  unlist(ti)
+}
+```
+
+```{r}
+
+net <- left_join(network_metrics, op_analysis, by = "opcod") %>%
+  ungroup() %>%
+  filter(!is.na(station))
+
+prep_troph_sp_biomass <- net %>%
+  select(opcod, station, year, composition, surface) %>%
+  unnest(composition) %>%
+  mutate(bm_std = biomass/ surface)
+
+troph_sp_biomass <- prep_troph_sp_biomass %>%
+  select(station, year, sp_class, bm_std) %>%
+  group_by(station) %>%
+  nest() %>%
+  mutate(
+    com_mat = map(data, function(x) {
+      ti <- x %>%
+	pivot_wider(names_from = sp_class, values_from = bm_std) %>%
+	mutate_at(vars(matches("[A-Z]{3}", ignore.case = FALSE)),
+	  ~ifelse(is.na(.), 0, .))
+    return(as.matrix(select(ti, -year)))
+}
+    )
+  )
+
+library(furrr)
+library(parallel)
+plan(multisession, workers = 3)
+
+sync_troph_sp <- troph_sp_biomass %>%
+  ungroup() %>% # For furrr to works
+  mutate(sync = future_map(com_mat, ~compute_pair_synchrony(.x)))
+
+```
+
+```{r}
+get_if_fish_pair_interact <- function (net = NULL) {
+
+  te <- net[
+    str_detect(colnames(net), "[A-Z]{3}"),
+    str_detect(colnames(net), "[A-Z]{3}")
+    ]
+
+  sp_names <- colnames(te)
+  ti <- combn(sp_names, 2,
+    FUN = function (x) {
+      int <- as.logical(te[x[2], x[1]])
+      names(int) <- paste(x[1], x[2], sep = "-")
+      return(int)
+    }, simplify = FALSE
+  )
+  unlist(ti)
+}
+```
+
+```{r}
+myload(metaweb_analysis, dir = mypath("data"))
+metaweb <- metaweb_analysis$metaweb
+
+```
+
+```{r}
+
+pair_int <- get_if_fish_pair_interact(metaweb)
+metaweb["ANG_2", "TRF_8"]
+
+```
+
+```{r}
+get_sync_int <- function(sync = NULL, pair_int = NULL) {
+
+  # compute inv prey-pred names to have symetric name combination   
+  pair_site <- names(sync)
+  inv_pair_site <- str_split(pair_site, "-") %>% map_chr(., ~paste0(.x[2], "-",.x[1]))
+
+  tmp <- pair_int[c(pair_site, inv_pair_site)]
+  pair_int_com <- tmp[!is.na(tmp)]
+
+  replace_pair_inv_pair <-  pair_site
+  names(replace_pair_inv_pair) <- inv_pair_site 
+  names(pair_int_com) <- str_replace_all(names(pair_int_com), replace_pair_inv_pair)
+
+  df_pair <- enframe(pair_int_com, name = "pair", value = "interact")
+  df_sync <- enframe(sync, name = "pair", value = "sync")
+
+  df_sync %<>%
+    left_join(df_pair, by = "pair")
+
+  return(df_sync)
+}
+```
+
+```{r}
+
+pair_site <- names(sync_troph_sp$sync[[1]])
+inv_pair_site <-str_split(pair_site, "-") %>% map_chr(., ~paste0(.x[2], "-",.x[1]))
+tmp <- pair_int[c(pair_site, inv_pair_site)]
+pair_int_com <- tmp[!is.na(tmp)]
+
+get_sync_int(sync_troph_sp$sync[[1]], pair_int = pair_int)
+
+```
+
+```{r, eval=FALSE}
+sync_troph_sp %<>%
+  mutate(sync_int = future_map(sync, get_sync_int, pair_int = pair_int))
+
+sync_pair_int <- sync_troph_sp %>%
+  select(station, sync_int) %>%
+  unnest(sync_int)
+
+mysave(sync_pair_int, dir = mypath("data"), overwrite = TRUE)
+```
+
+```{r}
+myload(sync_pair_int, dir = mypath("data"))
+sync_pair_int2 <- sync_pair_int %>%
+  separate(pair, c("sp1", "sp2"), "-") %>%
+  mutate_at(c("sp1", "sp2"), ~str_extract(., "[A-Z]{3}")) %>%
+  mutate(cannibalism = map2_lgl(sp1, sp2, ~ifelse(.x == .y, TRUE, FALSE)))
+```
+
+There is no cannibalism case!
+
+```{r}
+sync_pred <- sync_pair_int2 %>%
+  ggplot(aes(y = sync, x = as.factor(interact)), fill = as.factor(cannibalism)) +
+  geom_boxplot() +
+  facet_grid(~cannibalism) +
+  labs(y = "Synchrony", x = "Species in interaction", fill = "Cannibalism")
+```
+
+```{r}
+sync_pred <- sync_pair_int2 %>%
+  ggplot(aes(y = sync, x = as.factor(interact))) +
+  geom_boxplot() +
+  labs(y = "Synchrony", x = "Species pairs in interaction", fill = "Cannibalism")
+```
+
+```{r}
+save_plot(file = mypath(
+      "manuscript", "bef_stability", "result", 
+      "synchrony_species_pairs.png"),
+    plot = sync_pred,
+    base_height = 2.5, base_asp = 1.2#1.618 
+    )
 ```
@@
   inverse_label_order = TRUE, 
-  y_lim = c(-1.5, .75)
+  y_lim = c(-1.5, .75), pval = TRUE
   ) +
@@
   guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
-  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
+  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))+
+  labs(shape = "P <= 0.05")
+```
+
+```{r}
+save_plot(file = mypath(
+      "manuscript", "bef_stability", "result", 
+      "sensivity_stab_2006.png"),
+    plot = p_sens_stab,
+    base_height = 9, base_asp = 1.2#1.618 
+    )
 ```
@@
   inverse_label_order = TRUE,
-  y_lim = c(-1.5, .75)
+  y_lim = c(-1.5, .75), pval = TRUE
   ) +
@@
   guides(color = guide_legend(direction = "horizontal", nrow = 1)) +
-  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
+  theme(legend.position = "bottom", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))+
+  labs(shape = "P <= 0.05")
 ```
 
-```{r start-sens, fig.dim = c(14, 10), fig.cap="Sensivity of standardized estimate to the station starting date."}
+```{r}
+save_plot(file = mypath(
+      "manuscript", "bef_stability", "result", 
+      "sensivity_bm_2006.png"),
+    plot = p_sens_bm,
+    base_height = 9, base_asp = 1.2#1.618 
+    )
+```
+
+```{r start-sens, fig.dim = c(10, 14), fig.cap="Sensivity of standardized estimate to the station starting date."}
 legend_b <- get_legend(p_sens_stab)
@@
 p
+save_plot(
+  file = mypath( "manuscript", "bef_stability", "result", 
+      "sensivity_2006.png"),
+    plot = p,
+    nrow = 2,
+    base_height = 9, base_asp = 1.6#1.618 
+)
+```
+
+# Second answer
+
+- get air temperature data 
+- match them with water temperature (raw or interpolated?)
+
+```{r}
+#devtools::install_github("RetoSchmucki/climateExtract")
+library(climateExtract)
+library(ncdf4)
+
+fr_border <- sf::st_as_sf(raster::getData("GADM", country = "FRA", level = 0))
+debug(extract_nc_value)
+climate_data = extract_nc_value(first_year = 1995, 
+                                last_year = 2018,
+                                local_file = FALSE,
+                                file_path = NULL,
+                                sml_chunk = "2011-2020",
+                                spatial_extent = fr_border,
+                                clim_variable = "mean temp",
+                                statistic = "mean",
+                                grid_size = 0.25,
+                                ecad_v = NULL,
+                                write_raster = TRUE,
+                                out = "raster_mean_temp.grd",
+                                return_data = TRUE)
+# Get annual mean for each point 
+annual_avg_temp_pnts = temporal_aggregate(x = rbk,
+                                          y = sf_point,
+                                          agg_function = "mean",
+                                          variable_name = "average temp",
+                                          time_step = "annual")
+```
+
+```{r}
+library(reprex)
+library(climateExtract)
+climate_data = extract_nc_value(first_year = 2012, 
+                                last_year = 2015,
+                                local_file = FALSE,
+                                file_path = NULL,
+                                sml_chunk = "2011-2020",
+                                spatial_extent = fr_border,
+                                clim_variable = "mean temp",
+                                statistic = "mean",
+                                grid_size = 0.25,
+                                ecad_v = NULL,
+                                write_raster = TRUE,
+                                out = "raster_mean_temp.grd",
+                                return_data = TRUE)
+```
+
+```{r}
+library(climate)
+
+po <- nearest_stations_ogimet(country = "France",
+  date = Sys.Date(),
+  add_map = TRUE,
+  no_of_stations = 500 
+)
+
+o = meteo_ogimet(date = c("1995-01-01", "2018-12-31"), 
+                 interval = "daily",
+                 coords = FALSE, 
+                 station = "07005")
+```
+
+```{r}
+library(ncdf4)
+library(raster)
+library(sf)
+cru_file <- list.files(mypath("data-raw", "cru"))[!str_detect(list.files(mypath("data-raw", "cru")), "gz")]
+nc.pre <- nc_open(mypath("data-raw", "cru", "cru_ts4.03.2011.2018.tmp.dat.nc"))
+
+l <- map(cru_file, function (x) {
+  pre <- raster::brick(mypath("data-raw", "cru", x), varname="tmp")
+  extract(pre, st_wgs)
+		 }
+)
+
+tmean <- do.call(cbind, l)
+rownames(tmean) <- st_wgs$station
+colnames(tmean) <- paste0(rep(c(paste0(0, seq(1,9)), seq(10, 12)), 2018 - 1991), "_", rep(seq(1991, 2018), each = 12))
+
+# Correlation mean air temperature / water temperature
+air_mean_temp <-
+  rowMeans(tmean[, which(colnames(tmean) == "01_1995"):which(colnames(tmean) == "12_2018")]) 
+air_temp <- enframe(air_mean_temp, name = "station", value = "air_95_18") %>%
+  mutate(
+    station = as.integer(station),
+    air_06_18 = rowMeans(
+      tmean[, which(colnames(tmean) == "01_2006"):which(colnames(tmean) == "12_2018")]
+    )
+  )
+
+myload(habitat_press, sem_data, dir = mypath("data"))
+temp_avg_comp <- habitat_press %>%
+  dplyr::select(station, temperature_med) %>%
+  left_join(air_temp, by = "station") %>%
+  rename(water_06_2018 = temperature_med) %>%
+  filter(station %in% sem_data$station)
+
+dev.new(width = 6, height = 6, units = "cm")
+# i3: mod + shift + space 
+png(
+  file = mypath("manuscript", "bef_stability", "figs",
+    "pairs_temperature_plot.png")
+)
+pairs(
+  temp_avg_comp[, 2:4], pch = 19 
+)
+dev.off()
+
+mat <- round(cor(temp_avg_comp[, 2:4]), 3)
+write.table(mat,
+  file = mypath("manuscript", "bef_stability", "result", "cor_mat_temp.txt"),
+  sep = ",",
+  quote = FALSE,
+  row.names = T)
+
+# Test with monthly data
+myload(yearly_temp_press_interp_mv_avg, dir = mypath("data-raw", "temp"))
+temp <- yearly_temp_press_interp_mv_avg %>%
+  group_by(id, year) %>%
+  arrange(value.predSE) %>%
+  slice(1) %>%
+  select(station = id, year, temp = value_corrected) %>%
+  mutate(temp = ifelse(temp > 45, NA, temp)) %>%
+  ungroup()
+
+#plot(pre[[1]])
+#
+#uk.area <- extent(-12, 4, 48, 64)
+#uk <- crop(pre, uk.area)
+#plot(uk)
+#st <- get_basin_station(sf =TRUE)
+#st_wgs <- st_transform(st, crs = 4326)
+#
+#test <- extract(pre, st_wgs)
 ```
@@
 ## L180-182
+
+```{r}
+myload(community_metrics, community_analysis,
+  sem_data , dir = mypath("data"))
+ti <- get_sync_cv_mat(com_analysis = community_analysis,
+    op_analysis = op_analysis, presence_threshold = NA)
+
+test <- ti %>%
+  mutate(
+    richness_tot = map_dbl(com_mat, ~ncol(.x)),
+  ) %>%
+select(station, richness_tot)
+surf <- op_analysis %>%
+  filter(station %in% sem_data$station) %>%
+  group_by(station) %>%
+  summarise(tot_surface = sum(surface), avg_surface = mean(surface))
+
+surf_rich_tot <- surf %>%
+  left_join(test, by = "station")
+
+p_linear <- surf_rich_tot %>%
+  ggplot(aes(x = tot_surface, y = (richness_tot))) +
+  geom_point() +
+  labs(y = "Total species richness", x = "Total surface (m^2)") +
+  geom_smooth(method = "lm")
+```
+
+```{r}
+test <- glm(richness_tot ~ tot_surface + I(tot_surface^2), family=quasipoisson, surf_rich_tot)
+broom::tidy(test) %>%
+  knitr::kable(, format = "rst")
+
+```
+
+```{r}
+save_plot(file = mypath(
+      "manuscript", "bef_stability", "result", 
+      "richness_surface.png"),
+    plot = p_linear,
+    base_height = 9, base_asp = 1.2#1.618 
+)
+```
 
@@
   ) +
+geom_point(aes(colour = "pink", size = 4)) +
 scale_color_manual(
@@
 
-```{r rich-sens, fig.dim = c(14, 10), fig.cap="Sensivity of the standardized estimates to species richeness specification for the two structural equation model."}
+```{r rich-sens, fig.dim = c(10, 14), fig.cap="Sensivity of the standardized estimates to species richeness specification for the two structural equation model."}
 legend_b <- get_legend(p_sens_stab_rich)
@@
 ```
-
-The choice of richness variable would
-
-# Response to comment R3-Section 5.3
-
-```{r}
-
-```

### 2021-04-26 manuscript/bef_stability/table/hypothesis_sem.tex
Updates

@@
     \hline
-    PCA1 Avg stream size $\to$ Species richness & (+) &
-    \citet{post_ecosystem_2000, doi_resource_2009, mchugh_dual_2010} \\
+    PCA1 Avg stream size $\to$ Species richness & (+) & \citet{post_ecosystem_2000,doi_resource_2009,mchugh_dual_2010} \\
     \hline
@@
     \hline
-    PCA1 Avg stream size $\to$ Connectance & ? & NA\\
+    PCA1 Avg stream size $\to$ Connectance & (?) & \\
     \hline
-    PCA2 Avg temperature $\to$ Connectance & ? & NA\\
+    PCA2 Avg temperature $\to$ Connectance & (+/-) & \citet{petchey_predicting_2010} \\
     \hline
-    Species richness $\to$ Connectance & (-) & \citet{dunne_network_2006} \\
+    Species richness $\to$ Connectance & (-) & \citet{winemiller_must_1989, dunne_network_2006} \\
     \hline
-    PCA1 Avg stream size $\to$ Avg trophic level & (+) & \citet{mchugh_dual_2010}\\
+    PCA1 Avg stream size $\to$ Avg trophic level & (+) &
+    \citet{mchugh_dual_2010, doi_resource_2009, post_ecosystem_2000}\\
     \hline
@@
     \hline
-    Species richness $\to$ Avg trophic level & ? & NA\\
+    Species richness $\to$ Avg trophic level & (+) & \citet{schneider_animal_2016}\\
     \hline
@@
     \hline
-    PCA1 Avg stream size $\to$ Synchrony & (-) & NA\\
+    PCA1 Avg stream size $\to$ Synchrony & (?) & \\
     \hline
@@
     \hline
-    Connectance $\to$ CVsp & NA & NA\\
+    Connectance $\to$ CVsp & (+) & \citep{thebault_trophic_2005}\\
     \hline
-    Avg trophic level $\to$ CVsp & (-) & \citet{shanafelt_stability_2018}\\
+    Avg trophic level $\to$ CVsp & (-) & \citet{mccann_more_2009, shanafelt_stability_2018}\\
     \hline
-    PCA1 Avg stream size $\to$ CVsp & (-) & NA\\
+    PCA1 Avg stream size $\to$ CVsp & (?) & \\
     \hline
-    PCA2 Avg temperature $\to$ CVsp & (+) & \citep{ogorman_unexpected_2017;tabi_warming_2019}\\
+    PCA2 Avg temperature $\to$ CVsp & (+) & \citep{ogorman_unexpected_2017, tabi_warming_2019}\\
     \hline

### 2021-04-26 R/plot_methods.R

@@ -1359,7 +1359,7 @@ format_table <- function (x = tmp_stab_indir_table) {
   x
 }
 
-plot_sensivity_analysis <- function (.data = NULL, y_lim = c(-1.26, .75), inverse_label_order = FALSE, scale_color = TRUE) {
+plot_sensivity_analysis <- function (.data = NULL, y_lim = c(-1.26, .75), inverse_label_order = FALSE, scale_color = TRUE, pval = FALSE, size_point = NULL) {
   .data %<>%
     mutate(
       r_p = str_c(response, predictor, sep = " ~ "),
@@ -1383,9 +1383,21 @@ plot_sensivity_analysis <- function (.data = NULL, y_lim = c(-1.26, .75), invers
   p <- p +
     labs(x = "Terms of the linear models",
       y = "Standardized estimate", color = "Dataset type") +
-    ylim(y_lim) +
-    geom_point(aes(color = dataset)) 
+    ylim(y_lim) 
   
+  if (is.null(size_point)) {
+    size_point <- 3 
+  }
+
+  if (pval) {
+    p <- p +
+      geom_point(aes(color = dataset, shape = ifelse(p.value <= 0.05, TRUE,
+	    FALSE)), size = size_point) 
+  } else {
+    p <- p +
+      geom_point(aes(color = dataset), size = size_point)
+  }
+
   if (scale_color) {
     
   p <- p +

### 2021-04-30 manuscript/bef_stability/fig1_biomass_network.Rmd
Generate figures for talk

@@
 ```{r}
+myload(metaweb_analysis,  dir = mypath("data"))
 sp_color <- set_color_species(
@@
 
-myload(metaweb_analysis,  dir = mypath("data"))
 TL <- NetIndices::TrophInd(metaweb_analysis$metaweb)$TL
@@
 ) 
-```
-
-```{r}
 ```
@@
 
+map_alone <- p_st + 
+  geom_sf(data = filter(station, type == "stable"), color = "black") +
+  coord_sf(
+    xlim = c(60000, 1100000),
+    ylim = c(6100000, 7122216),
+    datum = sf::st_crs(2154),
+    crs = 2154,
+    expand = FALSE
+    ) +
+  theme_void() +
+  theme(plot.margin = theme_get()$plot.margin, legend.position = "none")
+save_plot(mypath("manuscript", "bef_stability", "figs/map_station.png"), map_alone,
+  nrow = 1,
+  ncol = 1,
+  base_height = 4,
+  base_width = 4,
+  bg = "transparent"
+)
+ggdraw(map_alone)
+
 p_st2 <- p_st +
@@
 ```
+
 ```{r set-up}
@@
 ```
+
+## Get a temporal network
+
+```{r}
+temporal_network_plot <- get_network_temporal_plot(net_list = network_analysis, station = st[2],
+  selected_years = NULL,
+  node_color = meta_node_color, scale_node_size = 0.05,
+  par_options = par(mar = c(0,0,0,0)),
+  log_abun = TRUE
+)
+temporal_network_plot <- map(temporal_network_plot,
+  ~.x + theme(rect = element_rect(fill = "transparent")))
+p_temporal_network <- plot_grid(plotlist = temporal_network_plot)
+
+save_plot(mypath("manuscript", "bef_stability", "figs/temporal_network.png"),
+  p_temporal_network,
+  nrow = 3, 
+  ncol = 4,
+  base_height = 4,
+  base_width = 4,
+  bg = "transparent"
+)
+```

### 2021-04-30 manuscript/bef_stability/review_analysis.Rmd
Generate figures for talk

@@
 debug(extract_nc_value)
+options(timeout=120)
 climate_data = extract_nc_value(first_year = 1995, 

### 2021-05-05 manuscript/bef_stability/appendixB.Rmd
Update appendix following Elisa's review

@@
 ---
-title: Appendix B of Species richness and food-web structure jointly drive community biomass and its temporal stability in fish assemblages 
+title: Appendix B
+subtitle: Species richness and food-web structure jointly drive community biomass and its temporal stability in fish assemblages 
 author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
@@
     @mchugh_dual_2010| @doi_resource_2009| @allan_stream_2009|
-    @petchey_predicting_2010| @winemiller_must_1989
+    @petchey_predicting_2010| @winemiller_must_1989 | @galiana_spatial_2018 | @ogorman_simple_2019| @oksanen_exploitation_1981| @thebault_trophic_2005| @mccann_more_2009| @jiang_different_2009| @fussmann_ecological_2014| kratina_warming_2012
 csl: ecology-letters.csl
@@
 
-The monitoring of the fish communities occurs in a variety of stream size, shape
+The monitoring of the fish communities occurs in streams varying in size, shape
 and depth. The stream characteristics constrain the type of protocol that can be
 applied. Small streams (depth < 0.7m across the entire width) are sampled with
-the complete protocol. The protocol consists of placing anodes across the entire
-width of the stream. The fishermen made from one to three rows of electric
-fishing. We selected only the data from the first row to homogenize the sampling
-effort. In deeper and wider streams (depth >= 0.7m), the sampling was partial
-over the bank and the channel and performed by boat and by foot (along the
-bank). We selected only the sampling done over the bank because the channel was
-not systematically sampled. Two types of partial protocols takes place: partial
-over bank and partial by points, which are respectively continuous and discrete.
-Furthermore, in the "partial by point" protocol, the channel was sometimes
-sampled as well. We selected only the "partial by point" sampling in which all
-the sampling points were done over the bank to homogenize the sampling. Then, we
-merged partial over bank and partial by point protocols. Some sampled stations
-were located in stream with intermediate characteristics where both protocols
-were alternatively used depending on the state of the stream at the time of
-sampling. For these sites, we only kept the samples that had been carried out
-with the most used protocol.
-
-Heterogeneity in the sampling date may introduce variability that is not related
-to ecological processes such as the presence of juveniles. In order to reduce
-heterogeneity in the sampling date, only one sampling per year was retained if
-there was more in a given year, the one with that had the most species and then
-the most individuals. Finally, most of the fish sampling occurred in September
-(Median: mid-August) and the median standard deviation of the sampling month was
-inferior to one (0.7) within stations, i.e. 3 weeks. To further reduce sampling
+the "complete" protocol. This protocol consists of placing anodes across the
+entire width of the stream. As the fishermen made from one to three rows of
+electric fishing, we selected only the data from the first row to homogenize the
+sampling effort. In deeper and wider streams (depth >= 0.7m), the sampling is
+partial over the bank and the channel and it is performed by boat and by foot
+(along the bank). We selected only the sampling done over the bank because the
+channel was not systematically sampled. Two types of partial protocols takes
+place: "partial over bank" and "partial by points", which are respectively
+continuous and discrete samplings. We considered both types of partial protocols
+in our analysis. In the "partial by point" protocol, the channel was sometimes
+sampled as well, so we selected only the "partial by point" sampling in which
+all the sampling points were done over the bank to homogenize the sampling. Some
+sampled stations were located in streams with intermediate characteristics where
+both "complete" and "partial" protocols were alternatively used depending on the
+state of the stream at the time of sampling. For these sites, we only kept the
+samples that had been carried out with the most used protocol.
+
+Heterogeneity in the sampling date may introduce variability in the fish
+communities such as the presence of juveniles. In order to reduce heterogeneity
+in the sampling date, only one sampling per year was retained if there were more
+in a given year, the one that had the most species and then the most
+individuals. Finally, most of the fish sampling occurred in September (Median:
+mid-August) and the median standard deviation of the sampling month was inferior
+to one (0.7) within stations, i.e. 3 weeks. To further reduce sampling
 heterogeneity, we only kept the sampling in which the length of stream sampled
@@
 
-The instructions for body size inference were guided by the recommendations of
+Body size inference was guided by the recommendations of
 the OFB agency, which has defined the sampling protocols, supervised the data
-collection and performed analysis for multiple purpose including stream
+collection and performed analyses on the dataset for multiple purpose including stream
 management.
@@
 size ($l$) of the fishes in the S/L and G was inferred under the assumption that
-body size distribution follows a normal law ($l ~ N(\mu, \sigma)$).  For an S/L
+body size distribution follows a normal law ($l \sim N(\mu, \sigma)$).  For an S/L
 batch, the mean $\mu$ and the standard deviation $\sigma$ were simply the
-average and the standard deviation of the body size of the subsample recorded.
-For a G batch, the average was approximated by $\hat{\mu} = (l_{min} + l_{max})
-2^{-1}$ and the standard deviation by $\hat{\sigma} = (l_{min} + l_{max})
-4^{-1}$. With the estimations of the mean and the standard deviation, the number
+average and the standard deviation of the body sizes of the subsample recorded.
+For a G batch, the average was approximated by $\hat{\mu} = (l_{min} +
+l_{max}) / 2$ and the standard deviation by $\hat{\sigma} = (l_{min} + l_{max})
+/ 4$. With the estimations of the mean and the standard deviation, the number
 of individuals in a batch and the assumption of normal distribution, we
@@
 [0.05; .95] for the density of probability of the S/L batches, and bounded at
-[$l_{min}$; $l_{max}$] for the G batches. Body size distribution were generated
+[$l_{min}$; $l_{max}$] for the G batches. Body size distributions were generated
 using the R function `truncdist::rtrunc`.
@@
 excluded batches for which the total number of individuals was not recorded. We
-also excluded G batches for which $l_{min} \geq l_{max}$ or if
-at least one of the measurement was missing. Additionally, a given G batch was
-excluded when the number of individuals fell below five, as G batches normally
-contained more individuals. We finally excluded S/L batches for which the
-number of measured individuals was inferior to 10. Finally, in the dataset used
-in the analysis, `r na_length` individuals had missing length over 
-`r nrow_fish_length` individuals.
+also excluded G batches for which $l_{min} \geq l_{max}$ or if at least one of
+the measurement was missing. Additionally, a given G batch was excluded when the
+number of individuals felt below five, as G batches normally contained more
+individuals. We finally excluded S/L batches for which the number of measured
+individuals was inferior to 10, because it indicates a potential problem in the
+batch. Finally, in the dataset used in the analysis, `r na_length` individuals
+had missing length over `r nrow_fish_length` individuals, and body size was
+inferred for these individuals.
 
@@
 
-Some species were identified based on their morphotype, but they
+Some species were identified to subspecies, based on their morphotype, but they
 belong to the same species based on fecundation criteria. We merged those
-morphotype species into one species. There was
+subspecies into one species. There was
 `r length(unique(names(sp_to_replace())))` species to merge which belonged to 
@@
 
-Diet information were obtained from fishbase.org and literature (Appendix A, Table S2). The
+Diet information was obtained from fishbase.org and literature (Appendix A, Table S2). The
 diet information contained from two to three life stages by species, the life
@@
 
-#### Define trophic interactions
+#### Definition of trophic interactions
 
@@
 trophic_building_caption <- paste0( "Building of the metaweb. (1) Each
-  species are divided in nine body size classes. We gathered information about
+  species is divided into nine body size classes. We gathered information about
   the food diet of each fish species and how food diet varies according to
-  ontogeny. (2) The life stage of a trophic species was determined with the
-  median of the body size class. A trophic link was set between the trophic
-  species and the resources associated to this life stage. (3) For a piscivorous
-  trophic species, the trophic links between fishes were defined according to
-  the predators/prey body size ratio. The predation window of the trophic
-  species ranged from 3% to 45% of the median of the body size range. A trophic
-  link between the predator trophic species and every trophic species whose
-  midpoint of bodysize range was included in the predation window.")
+  ontogeny. (2) The life stage of a trophic species is determined by the
+  median of the body size class, hereafter midpoint. A trophic link is set between the trophic
+  species and the resources associated to this life stage. (3) For piscivorous
+  trophic species, the trophic links among fishes are defined according to
+  the predator/prey body size ratio. The predation window of a trophic
+  species ranges from 3% to 45% of its midpoint. A trophic
+  link is set between the predator trophic species and every trophic species whose
+  midpoint of body size class range was included in the predation window.")
 
@@
 metaweb_caption <- paste0(
-  "The metaweb describes the trophic interactions between all the 412 trophic species, each is
+  "The metaweb describes the trophic interactions between all the 412 trophic species. Each trophic species is
   represented by a node and each color represents a species (S = 45). The seven
-  resource nodes (7) are drawn in grey. The species names corresponding to the
+  resource nodes are drawn in grey. The species names corresponding to the
   three digit codes are found in Table S1."
@@
 
-The life stage to which a trophic species belongs was determined by the median of
-the body size range of the trophic species, each life stage being delimited by a body
-size range. In turn, this trophic species has trophic interactions with the
-resource nodes of its life stage. The trophic interactions between a
-predator and a prey were determined by predator-prey body size ratio
+The life stage to which a trophic species belongs was determined by the median
+of the body size range of the trophic species, each life stage being delimited
+by a body size range. In turn, this trophic species has trophic interactions
+with the resource nodes of its life stage. The trophic interactions between a
+predator and a prey were determined by the predator-prey body size ratio
 [@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012]. For a
-given trophic species, we first determined if its body size range overlap
-with a piscivorous life stage (Fig. \@ref(fig:p-net-inf)). We were then more
-liberal for piscivory determination than for fish-resource interactions, to
-avoid missing potential interactions which were the main interactions in our
-community. If the trophic species was piscivorous, we determined its prey size
-range from 3% to 45% of the median of its size range. A trophic interaction was
-set for each trophic species whose median of its size class fell into the prey
-range of the predator trophic species. To sum up, the metaweb contains feeding
-interactions (1) between trophic species, (2) between trophic species and
-resource nodes and (3) between resource nodes.
-
-#### Local trophic network
-
-The local trophic networks (i.e. one network by
+given trophic species, we first determined if its body size range overlapped
+with a piscivorous life stage (Fig. \@ref(fig:p-net-inf)). If the trophic
+species was piscivorous, we determined its prey size range from 3% to 45% of the
+median of its size range. A trophic interaction was set for each trophic species
+whose corresponding size class median felt into the prey range of the predator trophic
+species (Fig. \@ref(fig:p-net-inf)). To sum up, the metaweb contains feeding interactions (1) between
+trophic species, (2) between trophic species and resource nodes and (3) between
+resource nodes.
+
+#### Local food-webs
+
+The local food-webs (i.e. one network by
 sampling) were obtained by determining the trophic species of each fish
 individual in the community. According to the trophic species present in a given
-community, we set the trophic interactions between them according to the metaweb. 
+community, we set the trophic interactions between them as defined in the metaweb. 
 All the resource nodes were assumed to be present in each local network.
-Finally, the structure of the local networks varied according the presence of
+Thus, the structure of the local food-webs varied according to the presence of
 the trophic species.
@@
 
-The procedure to obtain altitude, slope, width and depth of the streams are fully
+The procedures to obtain altitude, slope, width and depth of the streams are fully
 explained in main text. Because those measurements were collected during the
-fishing protocol, they were easier to manage in the analysis. Then, we detailed
+fishing protocol, they were easier to manage in the analysis. Then, we detail
 in the following sections how water temperature, water flow and Biological
@@
 mean for each variable, to match the yearly resolution of the fish monitoring.
-Furthermore, those variables are measured at different locations than the fish
-monitoring.
+Furthermore, the available data for these variables were measured at different
+locations than the fish monitoring and then necessitates a step of spatial
+interpolation.
 
@@
 database](http://www.naiades.eaufrance.fr/) and were respectively collected at
-an
-hourly, daily and monthly frequency. Water temperature and flow are recorded by
-automated sensors while BOD is collected manually because its measurement
+an hourly, daily and monthly frequency. Water temperature and flow are recorded
+by automated sensors while BOD is collected manually because its measurement
 requires laboratory analysis. BOD data collection is coordinated by the Agence
-de l'eau which realized the analysis itself or order it to a company.
+de l'eau (i.e. French national water agency).
 
@@
   "Map of the environmental variables obtained for the 99 sites used in the
-  analysis. Slope is expressed in degree, altitude in meter, distance from
+  analysis. The inner borders delimit the hydrographic basins. Slope is expressed in degree, altitude in meter, distance from
   source in kilometer, Strahler order has no units, average stream width and
   depth are expressed in meter, Biological Oxygen Demand (BOD) is expressed in
-  mg of dissolved oxygen, water flow is expressed in cube meter per second and
+  mg of dissolved oxygen, water flow is expressed in cubic meter per second and
   water temperature is expressed in Celsius degree.")
@@
 
-To get rid of seasonal effects of temperature, we applied a moving window
-averaging to each time series. The moving window was applied on daily average
-temperature. Then we took the annual mean of each year and each variable
-(i.e. one value by year and by station).
-
-Several characteristics of the streams make the interpolation more complicated
-than along terrestrial surface. Interpolations in terrestrial areas are roughly
-based on euclidean distance while euclidean distance is complicated to consider
-in streams because it had to follow the path of the streams. Furthermore, two
-streams can be close by but not connected and thus the value of their variables might 
-not be related or only a few. For those reason, we used stream spatial network
-methods to interpolate water temperature, water flow and BOD.
+To smooth out the seasonal patterns of temperature variation across year and
+keep the general trends, we applied a moving window averaging to each time
+series. The moving window was applied on daily average temperature. Then we took
+the annual mean of each year and each variable (i.e. one value by year and by
+station).
+
+We used stream spatial network methods to interpolate water temperature, water
+flow and BOD. Indeed, stream characteristics make interpolation more
+complicated than in terrestrial areas. Interpolations in terrestrial areas are
+often based on euclidean distance, which is not possible for streams as two
+streams can be close but disconnected. For those reason, we used stream spatial
+network methods to interpolate water temperature, water flow and BOD.
 
@@
 `openSTARS` R package [@kattwinkel_preparing_2020]. The reconstruction was done with a raster of digital
-elevation model at a resolution of 250 meters [(IGN)](https://wxs.ign.fr/jvam1hsjm11u8voorw81v2xb/telechargement/prepackage/BDALTI-75M_PACK_FXX_2018-01-24%24BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15/file/BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15.7z)
-and a theoretical hydrologic network [@pella_reseau_2012].
+elevation model at a resolution of 250 meters [(link to the raster)](https://wxs.ign.fr/jvam1hsjm11u8voorw81v2xb/telechargement/prepackage/BDALTI-75M_PACK_FXX_2018-01-24%24BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15/file/BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15.7z)
+and a theoretical hydrologic network, which is more convenient to use than the observed one [@pella_reseau_2012].
 
@@
 issues when the interpolation was carried out at the scale of the whole
-France. We had to find a trade-off between the number of data (to keep enough
-high to perform the interpolation) and the level of dataset splitting. We then
-merged some hydrographic basin to end up with four regions of interpolation:
+France. We had to find a trade-off between the number of data (to keep 
+high enough to perform the interpolation) and the level of dataset splitting. We then
+merged some hydrographic basins to end up with four regions of interpolation:
 West, East, South and North.
 
-Then we modelled each variable as dependant only on the covariation between
-sites and taking in account stream network. To model the autocovariance between
+We modelled each variable, i.e. water temperature, water flow and BOD, as dependant only on the covariation between
+sites taking in account the stream network. To model the autocovariance between
 sites, we used the linear-sill and mariah functions for taildown and tailup
@@
     caption = paste0("Results of the cross-validation for the interpolation of
-      BOD, temperature and flow. Average over 4 interpolations are shown. The
+      BOD, temperature and flow. The averages over 4 interpolations are shown. The
       cross-validation were performed with the SSN R package. bias: average
@@
 dataset. We ran the interpolation four times, and we kept the predicted value
-which had the least standard deviation.
+which had the smaller standard deviation.
 
@@
 overall dynamic of the biomass varies around an equilibrium
-[@kefi_advancing_2019]. In order to approach the condition of equilibrium, we kept only the
-stations that have met this criteria. To characterise the biomass temporal
-dynamics, we used the symbolic aggregated approximation method (SAX), which is
-commonly used in time series analysis and implemented in the `jmotif` R package
-[@senin_grammarviz_2018].  This method classifies time series rather than
-quantifies trends and so is generic enough to encompass a diversity of temporal
-trajectories. The classification necessitates three steps. First, the time
-series are normalized (i.e. substituting the mean and divide by the standard
-deviation). The second step is to reduce the dimensionality of the time series
-by a Piecewise Aggregation Approximation (PAA) method. Each time series is
-divided in $N$ frames of equal size that allows to reduce the dimensionality
-of the time series. For each frame, we simply kept the mean value of the time
-series. The last step is to qualify each frame into string. Because values of
-normalized time series typically follows a normal distribution ($N(0,1)$), a
-breakpoint can be computed by dividing the area under the normal distribution
-in equal parts. The algorithm attributes an alphabetic letter to each part from
-the lowest to the highest ($a$, $b$, $c$, ...). We set three breakpoints, so
-$a$, $b$ and $c$.  Finally, the trajectory of each time series is classified as
-a combination of $a$, $b$, $c$ letters. $abc$ and $cba$ time series represent
-respectively monotonic increasing and decreasing trajectories. For data
-analysis, we kept only the $bbb$ which represent time series that showed no
-temporal tendencies, with respect to our methodology.
+[@kefi_advancing_2019]. In order to approach the condition of equilibrium, we
+kept only the stations that show no clear temporal trends. To characterise the
+biomass temporal dynamics according to their trajectories, we used the symbolic
+aggregated approximation method (SAX), which is commonly used in time series
+analysis and implemented in the `jmotif` R package [@senin_grammarviz_2018].
+This method classifies time series rather than quantifies trends and so is
+generic enough to encompass a diversity of temporal trajectories. The
+classification necessitates three steps. The time series are first normalized. Then, we reduced the dimensionality of the time series by a Piecewise
+Aggregation Approximation (PAA) method. Each time series is divided into $N$
+frames of equal size that allows to reduce the dimensionality of the time
+series. For each frame, we simply kept the mean value of the time series. The
+last step is to qualify each frame into string. Because values of normalized
+time series typically follows a normal distribution ($N(0,1)$), a breakpoint can
+be computed by dividing the area under the normal distribution in equal parts.
+The algorithm attributes an alphabetic letter to each part from the lowest to
+the highest ($a$, $b$, $c$, ...). We set three breakpoints, so $a$, $b$ and $c$.
+Finally, the trajectory of each time series is classified as a combination of
+$a$, $b$, $c$ letters. $abc$ and $cba$ time series represent respectively
+monotonic increasing and decreasing trajectories. For data analysis, we kept
+only the $bbb$ which represent time series that showed no temporal tendencies,
+with respect to our methodology.
 
@@
   scale_fill_discrete(name = "Status") +
-  labs(x = "Rotated component", y = "Eigen values") +
+  labs(x = "Rotated component", y = "Eigenvalues") +
   theme(legend.position = "none",
@@
   "Loadings of variable to rotated components of the PCA.
-  Loadings are the coefficients which determine the components of the PCA as
-  linear combinations of the variables.
+  Loadings are the coordinates of the variables in the space of the PCA
+  components.
   "
@@
 
-```{r, cache = FALSE}
+```{r, cache = FALSE, fig.pos = "!H", out.extra = ""}
 sem_variable_table <- tibble(
@@
     \hline
-    PCA1 Avg stream size $\to$ Species richness & (+) & Post et al. (2000); Doi et al. (2009); McHugh et al. (2010) \\
-    \hline
-    PCA2 Avg temperature $\to$ Species richness & (+/-) & O’Gorman et al. (2017); Gauzens et al. (2020) \\
-    \hline
-    PCA1 Avg stream size $\to$ Connectance & (?) & \\
-    \hline
-    PCA2 Avg temperature $\to$ Connectance & (+/-) & Petchey et al. (2010) \\
+    PCA1 Avg stream size $\to$ Species richness & (+) & Galiana et al. (2018) \\
+    \hline
+    PCA2 Avg temperature $\to$ Species richness & (+/-) & Woods et al. (2020); Gauzens et al. (2020) \\
+    \hline
+    PCA1 Avg stream size $\to$ Connectance & (-) & Galiana et al. (2018) \\
+    \hline
+    PCA2 Avg temperature $\to$ Connectance & (+/-) & O’Gorman et al. (2019);
+    Oksanen et al. (1981)\\
     \hline
@@
     \hline
-    Connectance $\to$ Synchrony & (+) & Teng and McCann (2004)\\
-    \hline
-    Avg trophic level $\to$ Synchrony & (+) & Raimondo et al. (2004)\\
-    \hline
-    PCA1 Avg stream size $\to$ Synchrony & (?) & \\
-    \hline
-    PCA2 Avg temperature $\to$ Synchrony & (+) & Loreau and de Mazancourt (2008)\\
-    \hline
-    Species richness $\to$ CVsp & (+) & Tilman (1996) \\
+    Connectance $\to$ Synchrony & (+) & Thébault and Loreau (2005)\\
+    \hline
+    Avg trophic level $\to$ Synchrony & (+) & Raimondo et al. (2004); McCann and Rooney (2009) \\
+    \hline
+    PCA1 Avg stream size $\to$ Synchrony & (-) & Wang et al. (2019)\\
+    \hline
+    PCA2 Avg temperature $\to$ Synchrony & (?) & \\
+    \hline
+    Species richness $\to$ CVsp & (+) & Jiang et al. (2009)\\
     \hline
@@
     \hline
-    PCA2 Avg temperature $\to$ CVsp & (+) & O’Gorman et al. (2017); Tabi et al. (2019)\\
+    PCA2 Avg temperature $\to$ CVsp & (+) & Kratina et al. (2012); Fussmann et al. (2014)\\
     \hline
@@
     \hline
-    Connectance $\to$ Total biomass & NA & Wang and Brose (2018)\\
+    Connectance $\to$ Total biomass & (+/-) & Thébault & Loreau (2003); Poisot
+    et al. (2013)\\
     \hline
@@
     \hline
-    PCA2 Avg temperature $\to$ Total biomass & (+/-) & O’Gorman et al. (2017)\\
+    PCA2 Avg temperature $\to$ Total biomass & (+/-) & Kratina et al. (2012);
+    Tabi et al. (2019)\\
     \hline
@@
 hist_var_caption <- paste0(
-  "Distribution of the variables included Structural Equation Models The
+  "Distribution of the variables included in the Structural Equation Models. The
   biomass stability, the CV of species (CVsp), PCA1, PCA2, species richness,
@@
 est_stab_sem_caption <- paste0(
-  "Estimate of the effects for the temporal stability of annual biomass of the structural equation
-  model."
+  "Estimates of the effects of the studied variables as predicted by the
+  structural equation model on the temporal stability of annual community
+  biomass."
 
@@
 est_bm_sem_caption <- paste0(
-  "Estimate of the effects for the structural equation
-  model of the median of annual total biomass."
+    "Estimates of the effects of the studied variables as predicted by the
+  structural equation model on the median of annual community
+  biomass."
 )
@@
 caption_random_effect <- paste0(
-  "Estimated variance and standard deviation on the intercept due to the hydrographic basins."
-)
+  "Random effect estimation from the linear models. This was set as a random
+  effect of the hydrographic basins on the intercept.")
 
@@
   "Sensivity analysis of the Structural Equation models for total biomass
-  and its temporal stability."," The Constant dataset is the one kepting only the
-  sites that had not a significant temporal trend in biomass; ", "Constant/
-    without holes dataset kept only the constant sites plus the ones that had not
+  and its temporal stability."," The Constant dataset is the one keeping only the
+  sites that does not show a clear temporal trend of community biomass; ", "Constant/
+    without holes dataset kept only the constant sites plus the ones that had no
   holes in their sampling period; ", "Complete is the dataset containing all the
-  site that have been followed ten years or more, as the other dataset;", " Without holes dataset is
-  the dataset containing only the sites that had no holes in the their sampling period."
+  sites that have been followed ten years or more", " Without holes dataset is
+  the complete dataset but containing only the sites that had no holes in their sampling period."
 )

### 2021-05-06 manuscript/bef_stability/appendixB.Rmd
Reviewed according to Maud's comments

@@
    - \usepackage{float}
+   - \usepackage[table]{xcolor}
+   - \usepackage{multirow}
    - \usepackage{booktabs}
@@
 The monitoring of the fish communities occurs in streams varying in size, shape
-and depth. The stream characteristics constrain the type of protocol that can be
+and depth. Stream characteristics constrain the type of protocol
 applied. Small streams (depth < 0.7m across the entire width) are sampled with
-the "complete" protocol. This protocol consists of placing anodes across the
-entire width of the stream. As the fishermen made from one to three rows of
-electric fishing, we selected only the data from the first row to homogenize the
-sampling effort. In deeper and wider streams (depth >= 0.7m), the sampling is
+the "complete" protocol. Anodes are distributed across the width of the river
+then one to three electric fidhing events are performed. We selected only the
+data from the first event to homogenize the sampling effort. In deeper and wider
+streams (depth >= 0.7m), the sampling is
 partial over the bank and the channel and it is performed by boat and by foot
@@
 state of the stream at the time of sampling. For these sites, we only kept the
-samples that had been carried out with the most used protocol.
-
-Heterogeneity in the sampling date may introduce variability in the fish
-communities such as the presence of juveniles. In order to reduce heterogeneity
-in the sampling date, only one sampling per year was retained if there were more
-in a given year, the one that had the most species and then the most
-individuals. Finally, most of the fish sampling occurred in September (Median:
-mid-August) and the median standard deviation of the sampling month was inferior
-to one (0.7) within stations, i.e. 3 weeks. To further reduce sampling
-heterogeneity, we only kept the sampling in which the length of stream sampled
-along the stream was inside the median length sampled more or less 30%.
+samples that had been carried out with the most frequently used protocol.
+
+Heterogeneity in the sampling date may introduce variability due to different
+climatic or environmental conditions but also to the life cycle of the species.
+For instance, early surveys may precede the egg hatching and youngs-of-the-year.
+In order to reduce heterogeneity in the sampling date, only one sampling per
+year was retained if there were more in a given year, the one that had the most
+species and then the most individuals. Finally, most of the fish sampling
+occurred in September (Median: mid-August). There was low heterogeneity of the
+sampling month within stations, with the median sampling month being mid-August
+where the median standard deviation of the sampling month was  month, i.e. three
+weeks. To further reduce sampling heterogeneity, we only kept the sampling in
+which the length of stream sampled along the stream was inside the median length
+sampled more or less 30%.
 
@@
 Once the fishes have been caught, they are divided into different batches (Fig.
-\@ref(fig:p-body-size)). Each batch contains only one species but there may be
-several batches for one species. The body size of the fishes is measured
-differently for each type of batch.  There are four types of batches: N, I, S/L
-and G. The batches N and I contain the biggest individuals. In the N and I
-batches, the body size of all the individuals is recorded. The batches S/L
-contain fishes of intermediate sizes.  Inside each S/L batch, the operator tries
-to make batches as homogeneous as possible in terms of body size. Then, the body
-size of a subsample of at least 20 individuals is recorded. The G batches
-contain individuals of small body size, with care that body size is as
-homogeneous as possible in a given batches.  Then body size of the shortest and
-the longest individuals are recorded.
+\@ref(fig:p-body-size)). Each batch contains only one species but individuals of
+one species can be distributed in several batches. The body size of the fishes
+is measured differently for each type of batch.  There are four types of
+batches: N, I, S/L and G. The batches N and I contain the largest individuals.
+In the N and I batches, the body size of all the individuals is recorded. The
+batches S/L contain fishes of intermediate sizes. Inside each S/L batch, the
+operator tries to make batches as homogeneous as possible in terms of body size.
+Then, the body size of a subsample of at least 20 individuals is recorded. The G
+batches contain individuals of small body size. In G batches, the body size of
+the shortest and the largest individuals are recorded.
 
@@
 collection and performed analyses on the dataset for multiple purpose including stream
-management.
+management. The database was obtained from the OFB agency.
 
@@
 
-Batches that did not meet certain conditions were excluded. First, we also
-excluded batches for which the total number of individuals was not recorded. We
-also excluded G batches for which $l_{min} \geq l_{max}$ or if at least one of
-the measurement was missing. Additionally, a given G batch was excluded when the
-number of individuals felt below five, as G batches normally contained more
-individuals. We finally excluded S/L batches for which the number of measured
-individuals was inferior to 10, because it indicates a potential problem in the
-batch. Finally, in the dataset used in the analysis, `r na_length` individuals
-had missing length over `r nrow_fish_length` individuals, and body size was
-inferred for these individuals.
+Batches that did not meet conditions regarding the number of individuals were
+excluded.  We excluded batches for which the total number of individuals was not
+recorded. We also excluded G batches for which $l_{min} \geq l_{max}$ or if at
+least one of the measurement was missing. Additionally, a given G batch was
+excluded when the number of individuals felt below 5, as G batches normally
+contained more individuals. We excluded S/L batches for which the number of
+measured individuals was inferior to 10, because it indicates a potential
+problem in the batch. Finally, in the dataset used in the analysis, `r
+na_length` individuals had missing length over `r nrow_fish_length` individuals,
+and body size was inferred for these individuals.
 
@@
 belong to the same species based on fecundation criteria. We merged those
-subspecies into one species. There was
-`r length(unique(names(sp_to_replace())))` species to merge which belonged to 
+subspecies into one species. We merged 
+`r length(unique(names(sp_to_replace())))` morphotypes into
 `r length(unique(sp_to_replace()))` species.
@@
 
-Diet information was obtained from fishbase.org and literature (Appendix A, Table S2). The
-diet information contained from two to three life stages by species, the life
-stages being defined by the body size of the fishes. Over the 57 fish species,
-only seven had a piscivorous life stage and only three had a strict piscivorous
-life stage. Fish species were then largely omnivorous.
+Diet information was obtained from fishbase.org and literature (Appendix A,
+Table S2). The diet information contained from two to three life stages by
+species, the life stages being defined by the body size of the fishes. Over the
+57 fish species, only 7 had a piscivorous life stage and only three had a strict
+piscivorous life stage. Fish species were then largely omnivorous.
 
@@
 
-trophic_building_caption <- paste0( "Building of the metaweb. (1) Each
-  species is divided into nine body size classes. We gathered information about
+trophic_building_caption <- paste0( "Define trophic species and trophic
+  interactions. (1) Each
+  species is divided into 9 body size classes. We gathered data about
   the food diet of each fish species and how food diet varies according to
@@
 metaweb_caption <- paste0(
-  "The metaweb describes the trophic interactions between all the 412 trophic species. Each trophic species is
-  represented by a node and each color represents a species (S = 45). The seven
+  "The metaweb describing the trophic interactions between all the 412 trophic species. Each trophic species is
+  represented by a node and each color represents a species (S = 45). The 7 
   resource nodes are drawn in grey. The species names corresponding to the
@@
 ```{r metaweb, cache = FALSE, fig.cap=metaweb_caption}
-knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "metaweb.png"))
+knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "metaweb2.png"))
 ```
@@
 Trophic interactions between the nodes of the metaweb were determined according to
-the diet and the body size of the trophic species. `r length(removed_sp_metaweb)` 
-species were removed because information about their diet was missing. It
+the diet and the body size of the trophic species. We removed 
+`r length(removed_sp_metaweb)` species because data about their diet was missing. It
 represented  `r nrow(removed_ind_metaweb)` individuals over
@@
 of the body size range of the trophic species, each life stage being delimited
-by a body size range. In turn, this trophic species has trophic interactions
+by a body size range. In return, this trophic species has trophic interactions
 with the resource nodes of its life stage. The trophic interactions between a
@@
 median of its size range. A trophic interaction was set for each trophic species
-whose corresponding size class median felt into the prey range of the predator trophic
-species (Fig. \@ref(fig:p-net-inf)). To sum up, the metaweb contains feeding interactions (1) between
-trophic species, (2) between trophic species and resource nodes and (3) between
-resource nodes.
+whose corresponding size class median felt into the prey range of the predator
+trophic species (Fig. \@ref(fig:p-net-inf)). To sum up, the metaweb contains
+feeding interactions (1) between trophic species, (2) between trophic species
+and resource nodes and (3) between resource nodes.
 
@@
 explained in main text. Because those measurements were collected during the
-fishing protocol, they were easier to manage in the analysis. Then, we detail
+fishing protocol, they were easier to manage in the analyses. Then, we detail
 in the following sections how water temperature, water flow and Biological
-Oxygen Demand (BOD) variables were obtained. The goal was to obtain an annual
-mean for each variable, to match the yearly resolution of the fish monitoring.
-Furthermore, the available data for these variables were measured at different
-locations than the fish monitoring and then necessitates a step of spatial
-interpolation.
+Oxygen Demand (BOD) variables were obtained. In the following section, we will
+present how we averaged each variable to match the annual fish monitoring
+events. We also detailed how we interpolated these variables to match the
+spatial location of the fish samplings.
 
@@
 We modelled each variable, i.e. water temperature, water flow and BOD, as dependant only on the covariation between
-sites taking in account the stream network. To model the autocovariance between
-sites, we used the linear-sill and mariah functions for taildown and tailup
+sites taking in account the stream network. The autocovariance between
+sites was modelled with the linear-sill and mariah functions for taildown and tailup
 autocovariance, according to their predictive performance. The interpolations
@@
 analysis and implemented in the `jmotif` R package [@senin_grammarviz_2018].
-This method classifies time series rather than quantifies trends and so is
-generic enough to encompass a diversity of temporal trajectories. The
-classification necessitates three steps. The time series are first normalized. Then, we reduced the dimensionality of the time series by a Piecewise
+This method classifies time series rather than quantifies trends. Therefore, it
+is enough generic to encompass a diversity of temporal trajectories. The
+classification necessitates three steps. The time series are first normalized.
+Then, we reduced the dimensionality of the time series by a Piecewise
 Aggregation Approximation (PAA) method. Each time series is divided into $N$
@@
 series. For each frame, we simply kept the mean value of the time series.  The
-last step is to qualify each frame into string. Because values of normalized
+final stage is to qualify each frame into string. Because values of normalized
 time series typically follows a normal distribution ($N(0,1)$), a breakpoint can
@@
 sem_variable_table <- tibble(
-  variable = c(paste0("PCA axis", seq(1, 2)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
-  unit = c(rep("unitless", 2), "# by square meter", rep("unitless", 4), "gram by square meter"
+  Variable = c(paste0("PCA axis", seq(1, 2)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
+  Unit = c(rep("unitless", 2), "number by square meter", rep("unitless", 4), "gram by square meter"
     ),
-  transformation = c("Log base 10", "Log base 10 and inversion", "Log base 10", rep("No", 2), rep("Log base 10", 3)),
-  description = c("linked to stream size",
+  Transformation = c("Log base 10", "Log base 10 and inversion", "Log base 10", rep("No", 2), rep("Log base 10", 3)),
+  Description = c("linked to stream size",
     "linked to average temperature and BOD",
@@
     \hline
-    Connectance $\to$ Total biomass & (+/-) & Thébault & Loreau (2003); Poisot
+    Connectance $\to$ Total biomass & (+/-) & Thébault and Loreau (2003); Poisot
     et al. (2013)\\
@@
   biomass stability, the CV of species (CVsp), PCA1, PCA2, species richness,
-  synchrony and total biomass were logged."
+  synchrony and total biomass were logged. See Table S5 for the units."
 )
@@
   ggplot(aes(x = value)) +
+  labs(y = "Values", x = "Frequency") +
   geom_histogram() +
@@
 library(nlme)
-plot_residuals <- function (x, y = "Diagnostic") {
-  plot.lme(x, main = y, xlab = "Fitted values", ylab = "Residuals")
+plot_lme_residuals <- function (x = NULL, main = NULL) {
+  if (is.matrix(x$residuals)) {
+    tb <- tibble(
+      resid = x$residuals[, "fixed"], 
+      fitted = x$fitted[, "fixed"]
+    )
+  } else {
+    tb <- tibble(
+      resid = x$residuals, 
+      fitted = x$fitted
+    )
   }
-p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
+
+  ggplot(tb, aes(y = resid, x = fitted)) +
+    geom_point() +
+    labs(x = "Fitted values", y = "Residuals", title = main)
+
+}
+p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_lme_residuals)
 plot_grid(plotlist = p_resid_stab_sem, ncol = 2)
@@
 
-```{r}
+```{r, cache = FALSE}
 est_stab_sem_caption <- paste0(
@@
   structural equation model on the temporal stability of annual community
-  biomass."
-
-)
-
+  biomass. Avg: Average, Sdt.Error: Standard Error, DF: Degree of Freedom,
+  P.Value: P-value, Std.Estimate: Standardised
+  estimate. Significant standardised estimates are in bold."
+
+)
 format_coef_table(stab_sem_rich) %>%
-  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F), format = "latex", escape = F)) %>%
+  select(-Crit.Value) %>%
+  mutate_if(is.numeric, round, digits = 2) %>%
+  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05,
+	T, F), format = "latex", escape = F)
+    ) %>%
 kable(
@@
   caption = est_stab_sem_caption,
-    escape = F 
+  escape = F,
+  digits = 2
   ) %>%
@@
 
-```{r}
+```{r, cache = FALSE}
 est_bm_sem_caption <- paste0(
@@
   structural equation model on the median of annual community
-  biomass."
+  biomass. Avg: Average, Sdt.Error: Standard Error, DF: Degree of Freedom,
+  P.Value: P-value, Std.Estimate: Standardised
+  estimate. Significant standardised estimates are in bold."
 )
@@
 format_coef_table(bm_sem_rich) %>%
+  select(-Crit.Value) %>%
+  mutate_if(is.numeric, round, digits = 2) %>%
   mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
@@
   caption = est_bm_sem_caption,
-  escape = F 
+  escape = F, 
+  digits = 2
   ) %>%
@@
   booktabs = T,
+  digits = 2,
   caption = caption_random_effect
@@
   holes in their sampling period; ", "Complete is the dataset containing all the
-  sites that have been followed ten years or more", " Without holes dataset is
+  sites that have been followed ten years or more;", " Without holes dataset is
   the complete dataset but containing only the sites that had no holes in their sampling period."
@@
   inverse_label_order = TRUE) +
+  labs(x = "", title = "Median of annual community biomass") +
   theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
@@
   inverse_label_order = TRUE) +
+  labs(title = "Temporal stability of annual community biomass") +
   guides(color = guide_legend(direction = "horizontal", nrow = 2))
@@
   p_sens_bm, p_sens_stab, legend_b, nrow = 3,
-  rel_heights = c(1, 1, .1),
-  labels = c("Total biomass", "Biomass stability")
+  rel_heights = c(1, 1, .1)
+  #,
+  #labels = c("Total biomass", "Biomass stability")
 )

### 2021-05-06 manuscript/bef_stability/fig1_biomass_network.Rmd
Reviewed according to Maud's comments

@@
 sp_color[node_sp]
+names(sp_color)[names(sp_color) %in% meta$resource] <- 
+  c("detritivore", "biofilm", "phytobenthos", "macrophage", "phytoplankton", "zooplankton", "zoobenthos")
 
 TL <- NetIndices::TrophInd(metaweb_analysis$metaweb)$TL
+
+dev.new(width = 5, height = 7, units = "in")
+# i3: mod + shift + space
+
+png(
+  filename = mypath("manuscript/bef_stability/figs",
+    "metaweb2.png"), 
+  units = "in",
+  width = 5,
+  height = 7,
+  pointsize = 12*96/72,
+  res = 200 
+)
+org_par <- par(
+  mar = c(4, 0, 0, 0) + 0,
+  oma = c(0, 0, 0, 0),
+  xpd = NA 
+)
 PlotWeb(
@@
   colnode = sp_color[node_sp],
-  abund = 1,
-  collink="grey70",
-  scale_abun = .005
+  abund = 6,
+  collink="grey90",
+  scale_abun = .01
 )
+
+legend(
+#  x      = 0.031,
+#  y      = 4,
+  x      = "bottom",
+  inset = -.15,
+  legend = names(sp_color),
+  pch    = 21,
+  col    = "#777777",
+  pt.bg  = sp_color,
+  pt.cex = 0.7,
+  cex    = .5,
+  bty    = "n",
+  x.intersp = 1,
+  text.width = .1, 
+  ncol   = 6
+
+)
+
+dev.off()
+par(org_par)
 ```

### 2021-05-11 manuscript/bef_stability/appendixB.Rmd
Add trophic synchrony figure

@@
     \hline
-    Link & sign & reference\\
+    Link & Sign & References\\
     \hline
@@
   ggplot(aes(x = value)) +
-  labs(y = "Values", x = "Frequency") +
+  labs(y = "Frequency", x = "Values") +
   geom_histogram() +
@@
 
-```{r sensitivity, cache = TRUE, message = FALSE, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
+```{r sensitivity, cache = TRUE, message = FALSE, fig.dim = c(10.5, 7), fig.cap = "Sensivity analysis with different dataset"}
 library(furrr)
@@
 sens_cap <- paste0(
-  "Sensivity analysis of the Structural Equation models for total biomass
+  "Sensivity analysis of the structural equation models for total biomass
   and its temporal stability."," The Constant dataset is the one keeping only the
@@
 
-```{r, fig.height = 8, fig.cap = sens_cap}
+```{r, fig.height = 7, fig.cap = sens_cap}
 p_sens_bm <- plot_sensivity_analysis(
@@
   labs(x = "", title = "Median of annual community biomass") +
-  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))
+  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 28), units = "mm"))
 
@@
 
+```{r}
+sync_cap <- paste0(
+  "Synchrony between trophic species pairs that are trophically linked or not.
+  There is one point by trophic species pair and by site. The figure shows that
+  the trophic species pairs that are trophically linked are more synchronous
+  than the ones that are not trophically linked. Please see the definition of
+  synchrony in the methods of the main text.") 
+```
+
+```{r, fig.cap=sync_cap}
+knitr::include_graphics(mypath("manuscript", "bef_stability", "result", "synchrony_species_pairs.png"))
+```
+
 ```{=latex}

### 2021-05-11 manuscript/bef_stability/review_analysis.Rmd
Add trophic synchrony figure

@@
 sync_pred <- sync_pair_int2 %>%
+  mutate(interact = ifelse(interact, "Trophically linked", "Non trophically
+      linked")) %>%
   ggplot(aes(y = sync, x = as.factor(interact))) +
   geom_boxplot() +
-  labs(y = "Synchrony", x = "Species pairs in interaction", fill = "Cannibalism")
+  labs(y = "Synchrony", x = " Trophic interactions betweem trophic species pairs", fill = "Cannibalism")
 ```
@@
     plot = sync_pred,
-    base_height = 2.5, base_asp = 1.2#1.618 
+    base_height = 4.2, base_asp = 1.2#1.618 
     )

### 2021-05-12 manuscript/bef_stability/appendixB.Rmd
Reviewed according to willem comments

@@
 the "complete" protocol. Anodes are distributed across the width of the river
-then one to three electric fidhing events are performed. We selected only the
+then one to three electric fishing events are performed. We selected only the
 data from the first event to homogenize the sampling effort. In deeper and wider
-streams (depth >= 0.7m), the sampling is
-partial over the bank and the channel and it is performed by boat and by foot
-(along the bank). We selected only the sampling done over the bank because the
-channel was not systematically sampled. Two types of partial protocols takes
+streams (depth >= 0.7m), this protocol is partial and is carried out along the
+banks and the channel and it is performed by boat and by foot (along the bank).
+We selected only the sampling done over the bank because the
+channel was not systematically sampled. Two types of partial protocols take
 place: "partial over bank" and "partial by points", which are respectively
-continuous and discrete samplings. We considered both types of partial protocols
+a continuous and discrete fishing events. We considered both types of partial protocols
 in our analysis. In the "partial by point" protocol, the channel was sometimes
@@
 
-Heterogeneity in the sampling date may introduce variability due to different
+Heterogeneity in the fishing date may introduce variability due to different
 climatic or environmental conditions but also to the life cycle of the species.
@@
 in the following sections how water temperature, water flow and Biological
-Oxygen Demand (BOD) variables were obtained. In the following section, we will
+Oxygen Demand (BOD) variables were obtained. In the following section, we 
 present how we averaged each variable to match the annual fish monitoring
-events. We also detailed how we interpolated these variables to match the
+events. We also detail how we interpolated these variables to match the
 spatial location of the fish samplings.
@@
 issues when the interpolation was carried out at the scale of the whole
-France. We had to find a trade-off between the number of data (to keep 
+country. We had to find a trade-off between the number of data (to keep 
 high enough to perform the interpolation) and the level of dataset splitting. We then
@@
 dataset. We ran the interpolation four times, and we kept the predicted value
-which had the smaller standard deviation.
+which had the smallest standard deviation.
 
@@
 The CV of biomass over time can cover multiple temporal dynamics, including
-increases, stable, decreases and a mix of them. Theoretically, however, the CV
+increases, decreases, no trends or and a mixture of the above. Theoretically, however, the CV
 computed to quantify stability is often represented with the assumption that the
@@
 This method classifies time series rather than quantifies trends. Therefore, it
-is enough generic to encompass a diversity of temporal trajectories. The
+is generic enough to encompass a diversity of temporal trajectories. The
 classification necessitates three steps. The time series are first normalized.
-Then, we reduced the dimensionality of the time series by a Piecewise
+Then, the dimensionality of the time series is reduced by a Piecewise
 Aggregation Approximation (PAA) method. Each time series is divided into $N$
@@
 final stage is to qualify each frame into string. Because values of normalized
-time series typically follows a normal distribution ($N(0,1)$), a breakpoint can
+time series typically follow a normal distribution ($N(0,1)$), a breakpoint can
 be computed by dividing the area under the normal distribution in equal parts.
@@
 caption_mod_res <- paste0(
-  "Residuals versus fitted values of the linear models included in the structural
+  "Residuals versus fitted values from the linear models included in the structural
   equation models."
@@
 
-```{r, fig.height = 7, fig.cap = sens_cap}
+```{r, fig.height = 7.5, fig.cap = sens_cap}
 p_sens_bm <- plot_sensivity_analysis(
@@
   p_sens_bm, p_sens_stab, legend_b, nrow = 3,
-  rel_heights = c(1, 1, .1)
+  rel_heights = c(1, 1, .12)
   #,

### 2021-05-12 manuscript/bef_stability/fig1_biomass_network.Rmd
Reviewed according to willem comments

@@
 sp_color[node_sp]
-names(sp_color)[names(sp_color) %in% meta$resource] <- 
+names(sp_color)[names(sp_color) %in% metaweb_analysis$resource] <- 
   c("detritivore", "biofilm", "phytobenthos", "macrophage", "phytoplankton", "zooplankton", "zoobenthos")

### 2021-05-17 manuscript/bef_stability/review_analysis.Rmd
Add BOD to SEM figures + change correlation in review

@@
 library(sf)
+myload(habitat_press, sem_data, dir = mypath("data"))
+st_wgs <- station_analysis %>%
+  filter(id %in% sem_data$station)
+
 cru_file <- list.files(mypath("data-raw", "cru"))[!str_detect(list.files(mypath("data-raw", "cru")), "gz")]
@@
   extract(pre, st_wgs)
-		 }
-)
+		 })
 
 tmean <- do.call(cbind, l)
-rownames(tmean) <- st_wgs$station
+rownames(tmean) <- st_wgs$id
 colnames(tmean) <- paste0(rep(c(paste0(0, seq(1,9)), seq(10, 12)), 2018 - 1991), "_", rep(seq(1991, 2018), each = 12))
@@
       tmean[, which(colnames(tmean) == "01_2006"):which(colnames(tmean) == "12_2018")]
+    ),
+  air_95_05 = rowMeans(
+      tmean[, which(colnames(tmean) == "01_1995"):which(colnames(tmean) == "12_2005")]
     )
@@
 
-myload(habitat_press, sem_data, dir = mypath("data"))
 temp_avg_comp <- habitat_press %>%
@@
 pairs(
-  temp_avg_comp[, 2:4], pch = 19 
+  temp_avg_comp[, c(2, 4, 5)], pch = 19 
 )
@@
 
-mat <- round(cor(temp_avg_comp[, 2:4]), 3)
+mat <- round(cor(temp_avg_comp[, c(2, 4, 5)]), 3)
 write.table(mat,
@@
   row.names = T)
-
-# Test with monthly data
-myload(yearly_temp_press_interp_mv_avg, dir = mypath("data-raw", "temp"))
-temp <- yearly_temp_press_interp_mv_avg %>%
-  group_by(id, year) %>%
-  arrange(value.predSE) %>%
-  slice(1) %>%
-  select(station = id, year, temp = value_corrected) %>%
-  mutate(temp = ifelse(temp > 45, NA, temp)) %>%
-  ungroup()
-
-#plot(pre[[1]])
-#
-#uk.area <- extent(-12, 4, 48, 64)
-#uk <- crop(pre, uk.area)
-#plot(uk)
-#st <- get_basin_station(sf =TRUE)
-#st_wgs <- st_transform(st, crs = 4326)
-#
-#test <- extract(pre, st_wgs)
 ```

### 2021-05-17 manuscript/bef_stability/appendixB.Rmd
Update metaweb figures

@@
   #fig.dim = c(7, 7),
+  fig.align = "center",
   fig.fullwidth = TRUE,
@@
 sampling month within stations, with the median sampling month being mid-August
-where the median standard deviation of the sampling month was  month, i.e. three
+where the median standard deviation of the sampling month was 0.7 month, i.e. three
 weeks. To further reduce sampling heterogeneity, we only kept the sampling in
@@
 measured individuals was inferior to 10, because it indicates a potential
-problem in the batch. Finally, in the dataset used in the analysis, `r
-na_length` individuals had missing length over `r nrow_fish_length` individuals,
-and body size was inferred for these individuals.
+problem in the batch. Finally, in the dataset used in the analysis, 
+`r na_length` individuals had missing length over `r nrow_fish_length`
+individuals, and body size was inferred for these individuals.
 
@@
 Diet information was obtained from fishbase.org and literature (Appendix A,
-Table S2). The diet information contained from two to three life stages by
+Table S2). The diet information described two to three life stages by
 species, the life stages being defined by the body size of the fishes. Over the
@@
 
-trophic_building_caption <- paste0( "Define trophic species and trophic
+trophic_building_caption <- paste0( "Definition of trophic species and trophic
   interactions. (1) Each
@@
 trophic species (Fig. \@ref(fig:p-net-inf)). To sum up, the metaweb contains
-feeding interactions (1) between trophic species, (2) between trophic species
-and resource nodes and (3) between resource nodes.
+feeding interactions (1) among trophic species, (2) among trophic species
+and resource nodes and (3) among resource nodes.
 
@@
 
-The local food-webs (i.e. one network by
-sampling) were obtained by determining the trophic species of each fish
-individual in the community. According to the trophic species present in a given
-community, we set the trophic interactions between them as defined in the metaweb. 
-All the resource nodes were assumed to be present in each local network.
-Thus, the structure of the local food-webs varied according to the presence of
-the trophic species.
+The local food-webs (i.e. networks at each sampling event) were obtained by
+determining the trophic species of each fish individual in the community.
+According to the trophic species present in a given community, we set the
+trophic interactions between them as defined in the metaweb.  All the resource
+nodes were assumed to be present in each local network.  Thus, the structure of
+the local food-webs varied according to the presence of the trophic species.
 
@@
 We used stream spatial network methods to interpolate water temperature, water
-flow and BOD. Indeed, stream characteristics make interpolation more
+flow and BOD at the sampling sites. Indeed, stream characteristics make interpolation more
 complicated than in terrestrial areas. Interpolations in terrestrial areas are
@@
 interpolated variable of each station was predicted after removing it from the
-dataset.
+dataset (Table S3).
 
@@
 is generic enough to encompass a diversity of temporal trajectories. The
-classification necessitates three steps. The time series are first normalized.
+classification necessitates three steps. The time series are first centred such
+as the mean value is equal to 0.
 Then, the dimensionality of the time series is reduced by a Piecewise
@@
 The algorithm attributes an alphabetic letter to each part from the lowest to
-the highest ($a$, $b$, $c$, ...). We set three breakpoints, so $a$, $b$ and $c$.
+the highest ($a$, $b$, $c$, ...). We set two breakpoints, thereby simplifying
+our time series into three periods.
 Finally, the trajectory of each time series is classified as a combination of
@@
 \begin{table}
-\caption{\label{tab:hyp-sem} Presentation of the links 
-of the Structural Equation Models associated with the references supporting the links.}
+\caption{\label{tab:hyp-sem} Presentation of the hypothesis underlying the
+effects included in the Structural Equation Models with supporting references.}
 \begin{center}
@@
   booktabs = T,
+  align = "c",
   caption = est_stab_sem_caption,
@@
   booktabs = T,
+  align = "c",
   caption = est_bm_sem_caption,
@@
   inverse_label_order = TRUE) +
+  geom_hline(yintercept = 0) +
   labs(x = "", title = "Median of annual community biomass") +
@@
   inverse_label_order = TRUE) +
+  geom_hline(yintercept = 0) +
   labs(title = "Temporal stability of annual community biomass") +

### 2021-05-17 manuscript/bef_stability/fig1_biomass_network.Rmd
Add BOD to SEM figures + change correlation in review
Update metaweb figures

@@
 png(
+  filename = mypath("manuscript", "bef_stability", "figs", "metaweb2.png"), 
+  units = "in",
+  width = 5,
+  height = 7,
+  pointsize = 12*96/72,
+  res = 200 
+)
+org_par <- par(
+  mar = c(4, 0, 0, 0) + 0,
+  oma = c(0, 0, 0, 0),
+  xpd = NA 
+)
+PlotWeb(
+  TL = TL,
+  webTL = metaweb_analysis$metaweb,
+  colnode = rgb(t(col2rgb(sp_color[node_sp]))/255,alpha=0.7),
+  abund = 6,
+  collink=rgb(t(col2rgb("grey50"))/255,alpha=0.05),
+  scale_abun = .01
+)
+
+legend(
+#  x      = 0.031,
+#  y      = 4,
+  x      = "bottom",
+  inset = -.15,
+  legend = names(sp_color),
+  pch    = 21,
+  col    = "#777777",
+  pt.bg  = sp_color,
+  pt.cex = 0.7,
+  cex    = .5,
+  bty    = "n",
+  x.intersp = 1,
+  text.width = .1, 
+  ncol   = 6
+
+)
+
+dev.off()
+par(org_par)
+```
+
+```{r}
+myload(metaweb_analysis,  dir = mypath("data"))
+sp_color <- set_color_species(
+  node_list = colnames(metaweb_analysis$metaweb),
+  resource_list = metaweb_analysis$resource
+)
+node_sp <- str_extract(colnames(metaweb_analysis$metaweb), "[A-Z|a-z]*")
+sp_color[node_sp]
+names(sp_color)[names(sp_color) %in% metaweb_analysis$resource] <- 
+  c("detritivore", "biofilm", "phytobenthos", "macrophage", "phytoplankton", "zooplankton", "zoobenthos")
+
+TL <- NetIndices::TrophInd(metaweb_analysis$metaweb)$TL
+
+dev.new(width = 5, height = 7, units = "in")
+# i3: mod + shift + space
+
+png(
   filename = mypath("manuscript/bef_stability/figs",
@@
 par(org_par)
+
 ```

### 2021-07-06 manuscript/bef_stability/manuscript.Rmd
rewiew according to reviewer 1 and 2

@@
 ---
-title: Species richness and food-web structure jointly drive community biomass and its temporal stability in fish assemblages 
+title: Species richness and food-web structure jointly drive community biomass and its temporal stability in fish communities
 author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault, Colin Fontaine
@@
 bibliography: references.bib
+nocite: |
+    @declerck_species_2006
 csl: ecology-letters.csl
@@
 - Number of words:
-  - Abstract: 149
-  - Main text: 4930
-
-- Number of references: 92
+  - Abstract: 148
+  - Main text: 4917
+
+- Number of references: 102
 - Number of figures: 3
@@
 relationships are central to ecology. However, they remain largely untested in
-natural context. Here we quantify the links among environmental conditions,
+natural contexts. Here we estimated the links among environmental conditions,
 richness, food-web structure, annual biomass and its temporal stability using a
-standardized monitoring dataset of 99 stream fish communities spanning from 1995
-to 2018. We first reveal that both richness and average trophic level are
+standardised monitoring dataset of 99 stream fish communities spanning from 1995
+to 2018. We first revealed that both richness and average trophic level are
 positively related to annual biomass, with effects of similar strength. Second,
-we show that mean trophic level decrease population variability thereby
-increasing community stability, and contrary to expectation, a destabilizing
-effect of species richness. Finally, we find that environmental conditions
-affect both biomass and its stability via effects on richness and network
-structure. Strikingly, the variation of stability are mediated by population
-stability rather than synchrony, which contrasts with results from
-single-trophic communities and might be characteristic of multi-trophic
+we found that community stability is fostered by mean trophic level, while
+contrary to expectation, it is decreased by species richness. Finally, we found
+that environmental conditions affect both biomass and its stability mainly via
+effects on richness and network structure. Strikingly,
+community stability was mediated by the variation of population stability rather
+than synchrony, which contrasts with results from single-trophic communities. We
+discuss the hypothesis that it could be a characteristic of multi-trophic
 communities.
@@
 affect ecosystems in complex ways [@loreau_biodiversity_2001;
-@tilman_biodiversity_2014]. Biodiversity has indeed a major effect on
-ecosystem functions and their stability in response to perturbations
-[@hector_plant_1999; @loreau_biodiversity_2001; @hooper_effects_2005;
-@dunne_network_2006; @duffy_why_2009]. Understanding the relationship
-between biodiversity and ecosystem properties is thus crucial to better
-anticipate the impacts of global change.
+@tilman_biodiversity_2014].  Biodiversity has indeed a major effect on ecosystem
+functions and their stability in response to perturbations [@hector_plant_1999;
+@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
+@duffy_why_2009]. Understanding the relationship between biodiversity and
+ecosystem properties is thus crucial to better anticipate the impacts of global
+change.
 
@@
 Species richness has been found to increase primary productivity, community
-biomass and its temporal stability in a diversity of ecosystems and taxa both
-empirically and experimentally [@tilman_productivity_1996;
+biomass and its temporal stability in various ecosystems and taxa both
+experimentally and in natural settings [@tilman_productivity_1996;
 @cardinale_species_2002; @tilman_biodiversity_2006; @franssen_annual_2011;
 @grace_integrative_2016; @pennekamp_biodiversity_2018; @houlahan_negative_2018;
-@olivier_urbanization_2020].  However, these studies mainly focused on
-communities composed of a single trophic level, generally primary producers,
-thereby ignoring potential effects of food-web structure [but see
-@scherber_bottom-up_2010]. Conversely, theoretical works suggest that both
-species richness and food-web structure affect ecosystem properties such as
-productivity, total biomass and its stability. For example, the presence of
-species at higher trophic levels may increase total primary production, through
-the selection of primary producers which are larger and more complementary
-[@wang_biodiversity_2018]. In communities including producers and consumers, the
-connectance which measures the degree of consumer generalism is predicted to
+@olivier_urbanization_2020]. However, these studies mainly focused on communities
+composed of a single trophic level, generally primary producers, thereby
+ignoring potential effects of food-web structure [but see
+@scherber_bottom-up_2010].
+Conversely, theoretical works suggest that both species richness and food-web
+structure affect ecosystem properties such as productivity, total biomass and
+its temporal stability. For example, the presence of species at higher trophic
+levels may increase total primary production through top-down effects, which
+result in the selection of primary producers that are larger and more
+complementary in their use of resources [@wang_biodiversity_2018]. In communities
+including producers and consumers, the food-web connectance is predicted to
 modulate the diversity-productivity relationship [@thebault_food-web_2003;
@@
 @dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
-@stouffer_compartmentalization_2011].  Overall, the evidences from theoretical
-model suggests that both species richness and food-web structure should affect
-community biomass and stability, but empirical evidences of the effects of
-network structure on community biomass and stability are lacking.
-
-While community stability can be measured in many ways in theoretical studies,
-most empirical studies measure community stability as the inverse of the
-coefficient of variation of community productivity, biomass or abundance, also
-called temporal stability [@kefi_advancing_2019]. This stability metric is also
-well grounded in theory [e.g. @thebault_trophic_2005; @loreau_species_2008;
+@stouffer_compartmentalization_2011]. Overall, theoretical
+models suggest that both species richness and food-web structure should affect
+community biomass and its stability, but empirical evidence of such effects are
+lacking.
+
+While community stability is measured in many ways in theoretical studies, most
+empirical studies measure community stability as the inverse of the coefficient
+of variation of community productivity, biomass or abundance, also called
+temporal stability [@kefi_advancing_2019]. This stability metric is also well
+grounded in theory [e.g. @thebault_trophic_2005; @loreau_species_2008;
 @thibaut_understanding_2013] and can be decomposed into two components:
@@
 [@thebault_trophic_2005] tend to highlight that asynchrony in population
-dynamics as key for the stabilizing effects of species richness on community
-biomass. Theory also predicts that higher food-web connectance can
-counterbalance the positive effect of species richness on the temporal stability
-of community biomass, because it may increase interaction strength and
-thereby increases population variability, leading to a negative relationship
-between species richness and the temporal stability of populations
-[@thebault_trophic_2005]. Predators can also have cascading effects on both
-population variability and synchrony at lower trophic levels
-[@teng_dynamics_2004; @shanafelt_stability_2018]. Overall, these theoretical
-studies show that the effects of species richness and food-web structure, such
-as connectance and average trophic level, are potentially conflicting or
-synergistic in such a way that they need to be addressed jointly.
-
-The joint study of the effects of species richness and food-web structure on total
-biomass and its stability is even more important in the context of environmental
-changes. Recent studies comparing natural communities have shown that
-environmental characteristics determine in part community biomass
-[@grace_integrative_2016; @woods_testing_2020] and its temporal stability
-[@franssen_annual_2011; @hansen_climate_2013; @bluthgen_land_2016;
-@de_boeck_patterns_2017; @friedpetersen_drivers_2020]. The environment can
-affect ecosystem function or stability directly. For example, larger freshwater ecosystems
-tend to have more available resources and thus community biomass
-[@post_ecosystem_2000; @doi_resource_2009] while agricultural intensification
-destabilizes bird communities by decreasing population stability
-[@olivier_urbanization_2020]. The effects of environment can also go through
-effects on species richness and food-web structure, as larger ecosystems host
-food-webs with higher diversity and trophic levels [@mchugh_dual_2010] whereas
-temperature can affect food-web diversity and structure in contrasted ways
-depending on the ecosystem studied [@ogorman_unexpected_2017;
-@gauzens_biodiversity_2020]. Environmental characteristics have thus to be
-accounted for if we are to tease apart the effects of species richness and
-foodweb structure on community biomass and its temporal stability.
+dynamics is key for the stabilising effects of species richness on community
+biomass. Theory predicts that higher food-web connectance may increase
+interaction strength and thereby increase population variability,
+counterbalancing the positive effect of species richness on the temporal
+stability of community biomass [@thebault_trophic_2005]. Predators can also have
+cascading effects on both population variability and synchrony at lower trophic
+levels [@teng_dynamics_2004; @shanafelt_stability_2018]. Overall, these
+theoretical studies show that the effects of species richness and food-web
+structure, such as connectance and average trophic level, are potentially
+conflicting or synergistic in such a way that they need to be simultaneously
+assessed.
+
+The joint study of the effects of species richness and food-web structure on
+community biomass and its stability is important in the context of environmental
+changes. Recent studies comparing natural communities showed that environmental
+characteristics determine in part community biomass [@grace_integrative_2016;
+@woods_testing_2020] and its temporal stability [@franssen_annual_2011;
+@hansen_climate_2013; @bluthgen_land_2016; @de_boeck_patterns_2018;
+@friedpetersen_drivers_2020]. The environment can affect ecosystem function or
+stability directly. For instance, larger freshwater ecosystems are expected to
+have more available resources and thus community biomass [@post_ecosystem_2000;
+@doi_resource_2009] while agricultural intensification destabilises bird
+communities by decreasing population stability [@olivier_urbanization_2020]. The
+effects of environment can also be mediated by changes in species richness and
+food-web structure. Larger ecosystems host food-webs with higher diversity and
+trophic levels [e.g., @mchugh_dual_2010] and temperature is also known to affect
+food-web diversity and structure  [e.g., @edeline_ecological_2013;
+@ogorman_unexpected_2017; @gauzens_biodiversity_2020; @bonnaffe_trophic_2021].
+Environmental characteristics have thus to be accounted for if we are to tease
+apart the effects of species richness and food-web structure on community
+biomass and its temporal stability.
+
+Environment can affect functioning and stability directly or through effects on
+resource availability, species richness or food-web
+structure. Agricultural intensification and temperature changes can also...
 
@@
 ---
-
 Stream fish communities constitute a good model to study the effects of network
-structure on total biomass and its temporal stability because their trophic
-interactions are well known,. A substantial body of literature supports that
-trophic interactions can be inferred through body size and diet informations
+structure on community biomass and its temporal stability because their trophic
+interactions are well-known. A substantial body of literature supports that
+trophic interactions can be inferred through body size and diet information
 [@jennings_weak_2001; @beckerman_foraging_2006; @gravel_inferring_2013;
-@brose_predator_2019; @portalier_mechanics_2019]. Using long-term monitoring of
-stream fish communities [@edeline_ecological_2013], we propose one of the first
-attempts to test empirically the theoretical expectations on the
-diversity-stability relationships according for community, trophic complexity
-and environmental characteristics.
+@brose_predator_2019; @portalier_mechanics_2019]. Using long-term monitoring of stream fish
+communities and inference of trophic interactions [@bonnaffe_trophic_2021], we
+provide one of the first empirical tests of the expected relationship between
+BEF and food-web complexity-stability accounting for environmental
+characteristics.
 
@@
 
-Fish communities were monitored across stream sections in France on the period
-1995-2018 by the French Office of Water and Aquatic Ecosystems (ONEMA) using
-electrofishing. Two different standardized protocols were used for small and
-large streams (detailed in appendix B, part 1.1). In the case where a stream was
-sampled alternatively with one of the two sampling protocols, we only included
-data derived from the most frequently used sampling method. The sampling season
-spanned from late spring to autumn.  There was low heterogeneity of the sampling
-month within stations, with the median sampling month being mid-August where the
-median standard deviation of the sampling month was $0.7$ month, i.e. three weeks.
+Fish communities were monitored across stream sections in metropolitan France
+over the period 1995-2018 by the French Office of Water and Aquatic Ecosystems
+(ONEMA) using electrofishing. Two different standardised protocols were used for
+small and large streams (detailed in appendix B, part 1.1). In the case where a
+stream was sampled alternatively with one of the two sampling protocols, we only
+included data derived from the most frequently used sampling method. The
+sampling season spanned from late spring to autumn. There was low heterogeneity
+in the sampling month within stations, with the median sampling month being
+mid-August and the median standard deviation of the sampling month was $0.7$ month,
+i.e. three weeks.
 
 We selected the stations that had been sampled ten years or more. As the concept
-of community stability often refersred to the variability around an equilibrium
-point [@donohue_navigating_2016], which is rarely observed or difficult to
-characterize in natural communities. Then, we selected the stations that did not
-show temporal trends in community biomass (detailed in appendix B, part 2).
-However, the results were robust to the relaxation of this hypothesis (Fig. S7).
-We selected the stations that had been sampled ten years or more. As the concept
-of community stability referred to variability around an equilibrium, which is
-rarely observed or difficult to characterize in natural communities, only those
-stations that did not show temporal trends in community biomass were selected
-(detailed in appendix B, part 2). However, the results were robust to the
-relaxation of this hypothesis (Fig. S7). These selection steps resulted in 99
-stations distributed over seven hydrographic basins (Fig. \@ref(fig:matmet)A).
+of temporal stability often referred to the variability around an equilibrium
+point [@donohue_navigating_2016], we selected the stations that did not show temporal
+trends in community biomass (detailed in appendix B, part 2). However, the
+results were robust to the relaxation of this hypothesis (Fig. S7). These
+selection steps resulted in 99 stations distributed over seven hydrographic
+basins (Fig. \@ref(fig:matmet)A).
 
@@
 
-The body size of all fish individuals from a given species was not recorded when they were too
-numerous (Fig. S1, appendix B, part 1.1). The body size of the unmeasured
-individuals was inferred under the assumption that species body size followed a
-normal distribution (Fig. S1, appendix B, part 1.2). The body mass of each
-individual was then estimated following the results of two meta-analyses on
-fishes [@lleonart_removing_2000; @froese_cube_2006], using an allometric law
-$B_i = 0.01 \times l_i^{3.03}$, with $B$ the body mass in grams, $l$ the body
-size in millimeters and $i$ the individual. Population biomass and community biomass at
-each sampling event were then calculated by summing individual body masses. To
-account for the variation in sampling effort among sites, population biomass and
-community biomass were corrected by the surface sampled (range `r range_surface[1]` -
-`r range_surface[2]` square metres), and expressed in grams per square meter
-($gm^{-2}$). In the analysis, the community biomass of a site was defined as
-the median of the community biomass across sampling years.
+The fishes collected by electrofishing were grouped in batches according to
+their body size class and  species identity (Fig. S1, appendix B, part 1.1).
+When individuals were too numerous in a given batch, the body size of a
+subsample of the individuals was measured. The body size of the unmeasured
+individuals was inferred under the assumption that the  body size of the
+individuals in a batch follows a normal distribution (Fig. S1, appendix B,
+part 1.2). The body mass of each individual was then estimated following the
+results of two meta-analyses on fishes [@lleonart_removing_2000;
+@froese_cube_2006], using an allometric law $B_i = 0.01 \times l_i^{3.03}$, with
+$B$ the body mass in grams, $l$ the body size in millimetres and $i$ the
+individual. Population biomass and community biomass at each sampling event were
+then calculated by summing individual body masses. To account for the variation
+in sampling effort among sites, population biomass and community biomass were
+corrected by the surface sampled (range 
+`r range_surface[1]` - `r range_surface[2]` square metres), and expressed in
+grams per square metre ($gm^{-2}$). In the analysis, the community biomass of a
+site was defined as the median of the community biomass across sampled years.
 
@@
 Temporal biomass stability was defined as the inverse of biomass variability.
-Variability was computed as Coefficient of Variation (CV) of the community biomass over
-time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being
-respectively the standard deviation and the temporal average of the annual
+Variability was computed as Coefficient of Variation (CV) of the community
+biomass over time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and $\mu_i$
+being respectively the standard deviation and the temporal average of the annual
 community biomass of the station $i$). Then, temporal stability ($S_i$) was
-equal to $CV_i^{-1} = \mu_i \sigma_i^{-1}$.
-
-The variability of community biomass ($CV_{com, i}$) can be decomposed 
-into a
-synchrony ($\phi$) component and a weighted average population variability
-($\overline{CV_{sp, i}}$) component according to @thibaut_understanding_2013:
+equal to $CV_i^{-1} = \mu_i \sigma_i^{-1}$. The variability of community
+biomass ($CV_{com, i}$) can be decomposed into a synchrony ($\phi$) component
+and a weighted average population variability ($\overline{CV_{sp, i}}$)
+component according to @thibaut_understanding_2013:
 
@@
 
-To assess the mechanisms driving stability of community biomass, we thus in addition measure
+To assess the mechanisms driving stability of community biomass, we thus in addition measured
 the synchrony and the weighted average population variability $\overline{CV_{sp,
-i}}$, the average CV at the species-level in the station $i$, weighted by the
-relative biomass of the species, $B_{k,i}$.
+i}}$, the average CV at the population-level in the station $i$, weighted by the
+relative biomass of the species populations, $B_{k,i}$.
 
 Synchrony of the station $i$, $\phi_i$, is the ratio between the variance of
-community biomass over time ($\sigma^2_{x_{T,i}}$) and the sum of the variance of
-population biomass over time ($\sigma_{x_{k,i}}$), $i$ being the station $i$ and $k$
-the species $k$ [@loreau_species_2008].
+community biomass over time ($\sigma^2_{x_{T,i}}$) and the squared sum of the
+standard deviation of population biomass over time ($\sigma_{x_{k,i}}$), $i$
+being the station $i$ and $k$ the species $k$ [@loreau_species_2008]. Synchrony
+varies from 0 to 1; 0 indicating complete asynchrony and 1 perfect synchrony.
+Consequently, the lower is synchrony, the higher are the compensatory dynamics.
 
@@
 
-Species richness in a given site was defined as the total number of species present across
-all the sampling events. We controlled species richness for sampling effort by
-dividing the total number of species by the total surface sampled in the given
-station. Species richness was then expressed in number of species per square
-meter sampled.
-
-### Network inference
+Species richness in a given site was defined as the total number of species
+present across all the sampling events. We controlled species richness for
+sampling effort by dividing the total number of species by the total surface
+sampled in the given station. Species richness was then expressed in number of
+species per square metre sampled.
+
+### Food-web inference
 
@@
 
-We determined the network structure in two steps: (1) build a metaweb describing the
-trophic interactions between fishes and the resources (Fig.
-SXX), then (2) determine network of a given community by
-extracting the metaweb according to the fishes present at a given
-site and sampling event (Fig. \@ref(fig:matmet)C and D).
-
-The trophic interaction network was inferred from body size and ontogenic diet
-shift following previous studies [@edeline_ecological_2013;
-@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019]. The diet
-of stream fishes, as for many organisms, shifts throughout an individual's life,
-and thereby with body size. For example, larvae and small juveniles feed on
-plankton while adults may feed on algae and fishes, with bigger individuals
-eating bigger fishes. Each fish species was divided in nine body size
-classes, each corresponding to a trophic species (appendix B, Fig. S2). A
-trophic species constitutes a group of individuals from the same species and
-size class, which are expected to share the same sets of prey and predators.
-Additionally to the trophic species, we added seven resource nodes present in
-the ontogenic food diet database: detritus, biofilm, phytoplankton, zooplankton,
-macrophages, phytobenthos and zoobenthos (grey nodes in Fig. \@ref(fig:matmet)C
-& D). The trophic species and the resources constituted the 412 nodes of the
-metaweb, i.e. 45 fish species divided into nine body size classes plus seven
-resource nodes. The inference of trophic interactions was shown to be more
-accurate when considering body size classes, i.e. trophic species, than species
-[@jennings_weak_2001].
-
-The feeding interactions of a fish node, i.e. a trophic species, were determined
-by both its species identity and its body size. The ontogenic fish diet
-database was filled according to fishbase and literature (appendix A, Table S2). Each
-fish species had two or three life stages which are delimited by its body size
-range (appendix B, Fig. S2). The life stage of a fish trophic species was determined by 
-the center of its body size range, hereafter midpoint (appendix B, Fig. S2).
+We determined the food-web structure in two steps [@bonnaffe_trophic_2021]: (1) we
+built a metaweb describing the trophic interactions among all possible fish size
+classes and species as well as with non-fish resource classes (Fig. S2), then
+(2) we determined the food-web corresponding to each sampling event by
+extracting from the metaweb the subset of fish species and size classes present
+at a given site and sampling event (Fig. \@ref(fig:matmet)C and D).
+
+The food-web was inferred from body size and ontogenic diet shift following
+previous studies [@gravel_inferring_2013; @poisot_structure_2016;
+@brose_predator_2019; @bonnaffe_trophic_2021]. The diet of stream fishes, as for
+many organisms, shifts throughout an individual’s life, and thereby with body
+size. For example, larvae and small juveniles feed on plankton while adults may
+feed on algae and fishes, with bigger individuals eating bigger fishes. Each
+fish species was divided into nine body size classes, each corresponding to a
+trophic species (appendix B, Fig. S2). A trophic species constitutes a group of
+individuals from the same species and size class, which are expected to share
+the same sets of prey and predators. Additionally, we added seven resource nodes
+present in the ontogenic food diet database: detritus, biofilm, phytoplankton,
+zooplankton, macrophages, phytobenthos and zoobenthos (grey nodes in Fig.
+\@ref(fig:matmet)C & D). The trophic species and the resources constituted the
+412 nodes of the metaweb, i.e. 45 fish species divided into nine body size
+classes plus seven resource nodes. The inference of trophic interactions was
+shown to be more accurate when considering body size classes, i.e. trophic
+species, than species [@jennings_weak_2001].
+
+The feeding interactions of a trophic species were determined by both its
+species identity and its body size. The ontogenic fish diet database was filled
+according to fishbase [@froese_fishbase_2021] and literature (appendix A, Table
+S2). Each fish species had two or three life stages which are delimited by its
+body size range (appendix B, Fig. S2). The life stage of a fish trophic species
+was determined by the centre of its body size range, hereafter midpoint
+(appendix B, Fig. S2).
 
@@
 45% of its midpoint [@mittelbach_ontogeny_1998; @claessen_impact_2002;
-@hart_handbook_2008]. Then, a trophic link was set between the piscivorous
-trophic species and every trophic species whose midpoint in bodysize range was
-included in the predation window (appendix B, Fig. S2). The fish-resource trophic links were
-set between the trophic species and the resources nodes according the food items
-of their size class.  Lastly, the trophic links among resource nodes were set
-according to the literature [@allan_stream_2007; @hart_handbook_2008].
-
-### Network structure
+@hart_handbook_2008]. Then, a trophic link was set between the piscivorous trophic
+species and every trophic species whose midpoint in body size range was included
+in the predation window (appendix B, Fig. S2). The fish-resource trophic links
+were set between the trophic species and the resources nodes according to the
+food items of their size class. Lastly, the trophic links among resource nodes
+were set according to the literature [@allan_stream_2007; @hart_handbook_2008].
+
+### Food-web structure
 
 For each food-web, corresponding to a particular site and year, we computed the
-connectance and mean trophic level. Connectance describes the level of
+connectance and mean trophic level. Food-web connectance describes the level of
 generalism in the network and is calculated as the actual number of interactions
@@
 and N being resp. the number of links and of nodes). The trophic level of the
-nodes was computed as one added to the average trophic level of its food item.
+nodes was computed as one added to the average trophic level of its food items.
 The average trophic level $\overline{T}$ was computed as the average trophic
@@
 
-We characterised the sites by their altitude, slope, distance from
-source, stream width, depth and strahler order, i.e. its position in the
-stream network hierarchy. We obtained data on water temperature, flow and Biological Oxygen
-Demand (BOD) from the naiades
-database
-[(www.naiades.eaufrance.fr)](http://www.naiades.eaufrance.fr/). As data from naiades are
-not collected on the same site as our fish sampling sites, we performed an
-interpolation of the water temperature and flow based on the spatial stream
-network models [@isaak_applications_2014; @hoef_ssn:_2014]. The interpolation procedure
-is detailed in appendix B (part 1.4).
-
-We had one environmental variable value for each sampling event, except
-for water temperature for which the record began in 2006. Then, we computed the
-average and temporal CV values of water temperature, flow, BOD, river width and
-depth. As habitat and environmental variables are often collinear, a principal
+We characterised the sites by their altitude, slope, distance from source,
+stream width, depth and strahler order, i.e. its position in the stream network
+hierarchy. We obtained data on Biological Oxygen Demand (BOD), which is often
+related to enrichment and eutrophication in aquatic systems
+[@mallin_factors_2006], water temperature, flow and from the naiades database
+[(www.naiades.eaufrance.fr)](http://www.naiades.eaufrance.fr/). As data from naiades are not collected on the same
+site as our fish sampling sites, we performed an interpolation of the water
+temperature and flow based on the spatial stream network models
+[@isaak_applications_2014; @hoef_ssn:_2014]. The interpolation procedure is
+detailed in appendix B (part 1.4).
+
+We had one environmental variable value for each sampling event, except for
+water temperature for which records began in 2006. Then, we computed the average
+and temporal CV values of water temperature, flow, BOD, river width and depth.
+As habitat and environmental variables are often collinear, a principal
 component analysis (PCA) was performed on the 14 scaled variables. We kept in
-the analysis the two first principal components based on the elbow method, on
-the eigenvalues distribution (appendix B, Fig. SXX). The two first principal components
-explained `r tot_var_expl_pca`% of the variance (Fig. \@ref(fig:matmet)B). A varimax axis rotation was
-performed to maximize the representation of the environmental variables by the principal
-components [@kaiser_varimax_1958; @revelle_psych_2019]. The first axis
-represented a gradient from small to big streams, characterized by their width
-and depth, but also a gradient from stream close to far from the source. We
-reversed the values of the second axis, such as it represented a gradient of
-increasing average water temperature, average BOD and decreasing altitude and slope.
-Further description of the variables are provided in appendix B (part 1.4).
+the analysis the two first principal components based on the elbow method on the
+eigenvalues distribution (appendix B, Fig. S5). The two first principal
+components explained `r tot_var_expl_pca`% of the variance (Fig.
+\@ref(fig:matmet)B). A varimax axis rotation was performed to maximise the
+representation of the environmental variables by the principal components
+[@kaiser_varimax_1958; @revelle_psych_2019]. The first axis represented a
+gradient from small to big streams, characterised by their width and depth, but
+also a gradient of distance from source. We reversed the values
+of the second axis, so that is represented a gradient of increasing average
+water temperature, average BOD and decreasing altitude and slope. Further
+description of the variables are provided in appendix B (part 1.4).
 
@@
 
-We analyzed the relationships among environment, species richness, food-web
+We analysed the relationships among environment, species richness, food-web
 structure, community biomass and its temporal stability with structural equation
-models as they enable the assessment of potential indirect and direct causal
+models as they enable the assessment of potential direct and indirect
 relationships among multiple variables [@grace_structural_2008;
-@grace_causal_2014; @lefcheck_piecewisesem_2016; @grace_integrative_2016].  We
-defined a structural equation model explaining the median annual community
-biomass as a function of the two synthetic environmental variables, species
-richness and food-web structure [@maureaud_biodiversityecosystem_2019;
-@woods_testing_2020]. We assumed that both species richness and food-web
-structure directly affect community biomass (Fig. \@ref(fig:sem-bm)A) and that
-species richness affected food-web structure [@winemiller_must_1989;
-@dunne_network_2006; @thebault_stability_2010].
-
-We used the same model structure to assess the drivers of temporal stability
-of community biomass (Fig.  \@ref(fig:sem-stab)A). Instead of the
-annual community biomass, we modelled the synchrony and $\overline{CV_{sp}}$ which
-in turn determined the temporal stability of community biomass. We linearized
-the mathematical relationship linking temporal stability to $\overline{CV_{sp,
-i}}$ and $\phi$ by taking the log of
-temporal stability such as
+@grace_causal_2014; @lefcheck_piecewisesem_2016; @grace_integrative_2016]. The
+structural equation model explains the median annual community biomass as a
+function of the environment, species richness and food-web structure
+[@maureaud_biodiversityecosystem_2019; @woods_testing_2020]. We assumed that the
+environment, species richness and food-web structure directly affect community
+biomass (Fig. \@ref(fig:sem-bm)A), that species richness affects food-web
+structure [@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010]
+and that environment affects species richness and food-web structure.
+
+We used the same model structure to assess the drivers of temporal stability of
+community biomass (Fig. \@ref(fig:sem-stab)A). Instead of the annual community
+biomass, we modelled the synchrony and population variability which in turn
+fully determined the temporal stability of community biomass. We linearized the
+mathematical relationship linking temporal stability of community biomass $S_i$
+to $\overline{CV_{sp, i}}$ and $\phi$ by taking the log of temporal stability
+such as
 
@@
 
-The structural equation models were based on Gaussian linear mixed-effects models. All variables
-except the connectance and average trophic level
-were log-transformed to fulfill model assumptions (see residual plots and data
+The structural equation models were based on Gaussian linear mixed-effects
+models. All variables except the connectance and average trophic level were
+log-transformed to fulfil model requirements (see residual plots and data
 transformation in Fig. S5 and S6, Table S5, appendix B). We set the seven
-hydrographic basins as a random effect on the intercept to
-account for their heterogeneity. We checked for the absence of multicollinearity 
-with Variance Inflation Factor (VIF, Table S6, appendix B). The slopes reported
-in the main text were standardized in order to compare their magnitude ($r_\delta
-= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
-$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
-predictive variable $x$ and of the response variable $y$). Therefore, the
-standardized coefficients expressed the variation of $x$ and $y$ in standard
-deviation units. According to the equation (\@ref(eq:stab)), the unstandardized
-coefficients of synchrony and $\overline{CV_{sp}}$ determining temporal
-stability of biomass are respectively $-0.5$ and $1.0$. When standardized, a 
-comparaison of those coefficients comes down to a comparaison of the standard
-deviation of these two variables. The paths whose slope had a $P$ value inferior
-or equal to $0.05$ were reported in the main text, all the path values are
-presented in Table S7 and S8.
-
-Indirect effects on community biomass and its temporal stability were computed
-by multiplying slopes along the path. Only significant direct slopes were
-included in the calculation of indirect effects. Total effects were computed as
-the sum of direct and indirect effects.
-
-Environmental variables were interpolated with the `openStars` and `SSN`
-R packages [@kattwinkel_openstars_2018; @hoef_ssn:_2014]. Linear models and SEMs
-were computed with respectively the `nlme` and `piecewieseSEM` R packages
+hydrographic basins as a random effect on the intercept to account for their
+heterogeneity. We checked for the absence of multicollinearity with Variance
+Inflation Factor (VIF, Table S6, appendix B). The slopes estimated by the
+structural equation models and reported in the main text were standardised in
+order to compare their magnitude ($r_\delta = \beta \frac{\sigma_x}{\sigma_y}$,
+$\beta$ being the unstandardised slope, $\sigma_x$ and $\sigma_y$ being
+respectively the standard deviation of the predictor variable $x$ and of the
+response variable $y$). Therefore, the standardised coefficients expressed the
+variation of $x$ and $y$ in standard deviation units. According to the equation
+\@ref(eq:stab), the unstandardised coefficients of synchrony and population
+variability determining
+temporal stability of community biomass are respectively -0.5 and -1.0. When
+standardised, the relative comparison of those coefficients comes down to a
+comparison of the standard deviation of these two variables. The deviation from
+unstandardised effect values (i.e. -0.5 and -1.0) indicates that one component of community stability
+displays more variations than the other, and that the determinants of
+the more variable component will be those affecting community
+stability the most. The paths whose slope had a $P$ value inferior or equal to $0.05$
+were reported in the main text, all the path values are presented in Table S7
+and S8. Indirect effects on community biomass and its temporal stability were
+computed by multiplying slopes along the path. Only significant direct slopes
+were included in the calculation of indirect effects. Total effects were
+computed as the sum of direct and indirect effects.
+
+Environmental variables were interpolated with the `openStars` and `SSN` R
+packages [@kattwinkel_openstars_2018; @hoef_ssn:_2014]. Linear models and SEMs
+were computed with respectively the nlme and piecewieseSEM R packages
 [@pinheiro_nlme_2020; @lefcheck_piecewisesem_2016]. The code used for the
@@
   filter(P.Value <= 0.05)
-```
-
-```{r, cache = FALSE}
-sem_caption <- paste0(
-  "Metamodel of the Structural Equation Models for the (A) median of annual
-  community biomass (in grams by square meter) and (C) its temporal stability.",
-  "Results of the Structural Equation Models for
-  (B) the median of annual community biomass and (D) its temporal stability. Red and black
-  arrows represent respectively negative and positive path coefficients. The
-  path coefficients are standardized. For convenience, only significant
-  paths (i.e. $P < 0.05$) are shown. Rsq: Adjusted $R^2$; Avg:
-  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
-  second axis of the PCA performed on environmental variables (see methods)."
-)
 ```
@@
 
-The structural equation models explained a large part of the variation
-of species richness, connectance, synchrony, $\overline{CV_{sp}}$ and total
+The structural equation models explained a large part of the variation of
+species richness, connectance, synchrony, $\overline{CV_{sp}}$ and community
 biomass (resp. $R^2 = .43$, $.38$, $.46$, $.47$ and $.32$) but less so for mean
-trophic level ($R^2 = .11$, Fig. \@ref(fig:sem-bm)A and \@ref(fig:sem-stab)A). We found a
-negative relationship between species richness and mean trophic level ($r_\delta
-= `r rich_on_tlvl`$, $r_\delta$ meaning standardized slope) and connectance
-($r_\delta = `r rich_on_ct`$, Fig.  \@ref(fig:sem-bm)A and \@ref(fig:sem-stab)A), meaning that a
-part of the effects of species richness on community biomass and its temporal
-stability went through food-web structure.
+trophic level ($R^2 = .11$, Fig. \@ref(fig:sem-bm)A and \@ref(fig:sem-stab)A).
+We found a negative relationship between species richness and mean trophic level
+($r_\delta = `r rich_on_tlvl`$, $r_\delta$ meaning standardised slope) and
+connectance ($r_\delta = `r rich_on_ct`$, Fig. \@ref(fig:sem-bm)A and
+\@ref(fig:sem-stab)A), meaning that a part of the effects of species richness on
+community biomass and its temporal stability went through food-web structure.
 
@@
 Species richness and mean trophic level had a significant positive direct effect
-on community biomass ($r_\delta = `r rich_on_bm$direct`$ and 
-$r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-bm)A, B, C, Table
-\@ref(tab:indir-sem)), while connectance had no direct effect.
-
-The two PCA axes synthesising environmental variables had no significant direct
-effects on community biomass, but indirect (Table \@ref(tab:indir-sem)). The first
-axis, related to the stream size, was positively linked to community biomass
-($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
-through both species richness and mean trophic level ($r_\delta = 
-`r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_tlvl["log_RC1"]`$
-resp., Fig. \@ref(fig:sem-bm) F, G, Table \@ref(tab:indir-sem)). The second axis, related to the average
-annual temperature was positively related
+on community biomass ($r_\delta = `r rich_on_bm$direct`$ and $r_\delta = 
+`r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-bm)A, B, C, Table
+\@ref(tab:indir-sem)),
+while connectance had no direct effect.  The two PCA axes synthesising
+environmental variables had no significant direct effects on community biomass,
+but indirect ones (Table \@ref(tab:indir-sem)).  The first axis, related to the
+stream size, was positively linked to community biomass ($r_\delta = 
+`r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)), through both
+species
+richness and mean trophic level 
+($r_\delta = `r env_on_bm$via_richness["log_RC1"]`$ and 
+$`r env_on_bm$via_tlvl["log_RC1"]`$
+resp., Fig. \@ref(fig:sem-bm) F, G, Table \@ref(tab:indir-sem)). The second
+axis, related to the average annual temperature and BOD was positively related
 to community biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
-\@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
-`r env_on_bm$via_richness["log_RC2"]`$, Fig. \@ref(fig:sem-bm) G, Table \@ref(tab:indir-sem)). Streams
-with higher temperature and BOD contained more species, indirectly increasing
-community biomass. The total effect of PCA1, PCA2 and species richness on
-community biomass were of the same magnitude.
+\@ref(tab:indir-sem)) mainly through species richness ($r_\delta = 
+`r env_on_bm$via_richness["log_RC2"]`$, Fig. \@ref(fig:sem-bm) G, Table
+\@ref(tab:indir-sem)). Warmer and enriched, i.e.  with higher BOD, streams
+contained more species, and thus indirectly increased the biomass of the
+communities. The total effect of PCA1, PCA2 and species richness on community
+biomass were of the same magnitude.
 
@@
 effect on synchrony ($r_\delta = `r rich_on_sync$direct`$, Fig.
-\@ref(fig:sem-stab) A, B), thereby increasing stability ($r_\delta = 
+\@ref(fig:sem-stab)A, B), thereby increasing stability ($r_\delta = 
 `r rich_on_stab$via_sync`$).  On the other hand, species richness had a positive
 direct effect on $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$,
-Fig. \@ref(fig:sem-stab) A, C), thereby decreasing biomass stability ($r_\delta
-= `r rich_on_stab$via_cv_sp`$, Table \@ref(tab:indir-sem)), which outweighted
-the decreasing effect of species richness on synchrony. The negative effect of
-$\overline{CV_{sp}}$ on temporal stability was twice higher than the negative
-effect of synchrony (resp.  $r_\delta = `r cv_sp_on_stab`$ and $r_\delta = 
-`r sync_on_stab`$, Fig.  \@ref(fig:sem-stab)A). Population variability and
-synchrony constitute a mathematical decompositon of the stability, contributing
-respectively to 1 and 0.5 respectively (Eq. \@ref{eq:stab}), meaning that their
-$r_\delta$ difference to temporal stability is due to their standard deviation,
-and so that the standard deviation of $\overline{CV_{sp}}$ is of the same
-magnitude than the one of synchrony.
+Fig. \@ref(fig:sem-stab)A, C), thereby decreasing biomass stability ($r_\delta =
+`r rich_on_stab$via_cv_sp`$, Table \@ref(tab:indir-sem)), which outweighed the
+stabilising effect of species richness via decreased synchrony. The negative
+effect of $\overline{CV_{sp}}$ on temporal stability was twice higher than the negative effect of
+synchrony (resp.  $r_\delta = `r cv_sp_on_stab`$ and $r_\delta = 
+`r sync_on_stab`$, Fig.  \@ref(fig:sem-stab)A), which is as expected from the mathematical
+decomposition of the stability of community biomass. Population variability and
+synchrony indeed contribute respectively to -1 and -0.5 when the coefficients
+are not standardised (Eq. 4). Our result thus also means that the standard
+deviation of $\overline{CV_{sp}}$ is of roughly the same magnitude as the one of
+synchrony in this case.
 
 The total effect of mean trophic level and species richness on temporal
-stability of biomass were of the same magnitude (resp.  
-$`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
+stability of community biomass were of the same magnitude (resp. $`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
 \@ref(tab:indir-sem)). The mean trophic level had only a direct negative effect
-on $\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$, Fig.
-\@ref(fig:sem-stab)A, F) and thereby had a total positive effect on temporal
-stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$, Table
-\@ref(tab:indir-sem)). Food webs in which community biomass is located on
-average at higher trophic levels thus tend to have higher population and
-community stability. Connectance had no significant direct effect on either
-$\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
-(Fig. \@ref(fig:sem-stab)A, Table \@ref(tab:indir-sem)).
+on $\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$, Fig.  \@ref(fig:sem-stab)A, F) and thereby
+had a total positive effect on temporal stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$, Table \@ref(tab:indir-sem)). Food-webs in
+which community biomass is located on average at higher trophic levels thus tend
+to have higher stability of population and community biomass. Connectance had
+no significant direct effect on either $\overline{CV_{sp}}$ nor synchrony and
+thus no effect on temporal stability of community biomass (Fig.
+\@ref(fig:sem-stab)A, Table \@ref(tab:indir-sem)).
 
@@
 and mean trophic level (Table \@ref(tab:indir-sem)). The PCA2 had a total
-negative effect on temporal stability, meaning that higher temperature and BOD
-results in lower stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table
-\@ref(tab:indir-sem)).  PCA2 had an indirect positive effect on temporal
-stability through a direct positive effect on mean trophic level ($r_\delta = 
-`r env_on_stab$via_tlvl["log_RC2"]`$, Fig. \@ref(fig:sem-stab) I, Table
-\@ref(tab:indir-sem)). However, PCA2 had a negative effect on temporal stability
-through a direct positive effect on $\overline{CV_{sp}}$ and species richness
-(resp.  $r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$ and $r_\delta = 
+negative effect on the temporal stability of communities, meaning that higher
+temperature and BOD results in lower stability ($r_\delta = 
+`r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-sem)). PCA2 had an
+indirect positive effect on temporal stability through a direct positive effect
+on mean trophic level ($r_\delta = `r env_on_stab$via_tlvl["log_RC2"]`$, Fig.
+\@ref(fig:sem-stab) I, Table \@ref(tab:indir-sem)). However, PCA2 had a negative
+effect on stability of community biomass through a direct positive effect on
+$\overline{CV_{sp}}$ and species richness (resp.  $r_\delta = 
+`r env_on_stab$via_cv_sp["log_RC2"]`$ and $r_\delta = 
 `r env_on_stab$via_richness["log_RC2"]`$, Fig. \@ref(fig:sem-stab)G, Fig.
-\@ref(fig:sem-bm)G, Table \@ref(tab:indir-sem)). This was
-also true for the PCA1, related to stream size, with a resulting very slight
-positive effect of PCA1 on temporal stability ($r_\delta = 
-`r env_on_stab$total["log_RC1"]`$, Table \@ref(tab:indir-sem)).  Warmer and
-larger streams thus tend to have more species and more variability in population
-biomass, then have a lower stability of community biomass.
+\@ref(fig:sem-bm)G, Table \@ref(tab:indir-sem)). PCA1, related to stream size,
+had in contrast a very slight positive effect on stability of community biomass
+($r_\delta = `r env_on_stab$total["log_RC1"]`$, Table \@ref(tab:indir-sem)).
+Warmer and larger streams tend to have more species, but the variability of
+their population biomass is respectively higher and lower, resulting in
+respectively lower and higher temporal stability of community biomass.
 
@@
 We found that species richness increased community biomass in line with the
-results on plants and tree communities [@hector_plant_1999;
+results in the plants and tree communities [@hector_plant_1999;
 @tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018] as well
@@
 [@schneider_animal_2016]. Theory suggests that the positive effect of species
-richness on community biomass might be held by resource use complementarity
+richness on community biomass might be induced by resource use complementarity
 [@carey_determining_2011], which is driven by niche differentiation
-[@loreau_biodiversity_1998; @loreau_partitioning_2001] or by positive selection
-effect, which is driven by the dominance of the most productive species
-[@loreau_biodiversity_2001]. Recent findings suggest that dominance, a positive
-selection effect [@loreau_partitioning_2001], is the main driver of the observed
-positive relationship between biomass and species richnes in fish communities
+[@loreau_biodiversity_1998; @loreau_partitioning_2001] or driven by the
+dominance of a highly productive species [i.e. positive selection effect,
+@loreau_biodiversity_2001]. Recent findings suggest that such positive selection
+effect [@loreau_partitioning_2001] is the main driver of the observed positive
+relationship between biomass and species richness in fish communities
 [@maureaud_biodiversityecosystem_2019; @woods_testing_2020].
 
-We found that species richness decreases synchrony, threby increasing stability.
-This is in accordance with most studies on experimental grasslands
-[@isbell_biodiversity_2009; @roscher_identifying_2011] and natural communities
-of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
-@olivier_urbanization_2020]. It is thought that it is the main effect by which
-species richness increases stability [but see @declerck_species_2006;
-@valencia_synchrony_2020].  Our result thus extend that species richness
-decreases synchrony also in multi-trophic communities.  However, theory does not
-clearly state what would be the effect of food-web structure on the relationship
-between species richness and synchrony [@raimondo_interspecific_2004;
-@korpimaki_predatorinduced_2005; @mccann_more_2009].
-
-The positive effect of species richness on population variability, thereby
-decreasing stability, is more intriguing. A previous meta-analysis has indeed
-reported that species richness had often a negative effect on population
-variability in multi-trophic communities while a positive effect is often found
-in single-trophic communities [@jiang_different_2009]. In food-webs, theoretical
-models predict that the relationship between the temporal stability of populations
-and species richness depends on interaction strength and its distribution
-[@mccann_reevaluating_1997; @thebault_trophic_2005; @downing_temporal_2020],
-with stronger interactions promoting a negative relationship between species
-richness and stability. Therefore, it is possible that our results are due to
-strong trophic interactions, leading to more fluctuations in population biomass,
-but this hypothese was not testable with the available dataset. Alternatively,
-other authors suggest that this effect might be due to an increase of
-demographic stochasticity with an increase of species richness [@loreau_species_2008].
-
-A major finding of the study is that we found a negative relationship between
-species richess and temporal stability, contrast with most experimental and
-empirical studies to date [@franssen_annual_2011; @tilman_biodiversity_2006;
-@valencia_synchrony_2020; @pennekamp_biodiversity_2018;
-@olivier_urbanization_2020], but coincide with a few empirical ones
-[@declerck_species_2006]. This finding means that the destabilising effect of
-species richness through population variability was superior its stabilising
-effect through synchrony. It can happen either because of the relative strength
-of the effect species richness on both population variability and synchrony or
-because of the overall variability of synchrony and population variability in
-the our study system.
-
-We found indeed that the population variability had a standardized effect
-on the stability of community biomass twice stronger than synchrony, meaning that the
-variability of synchrony was equivalent the one of population variability, in
-contrast with a previous study which found that the variability of synchrony was
-twice higher than the variability of population variability
-[@olivier_urbanization_2020]. Therefore, the low variability of synchrony in our
-system might be a cause for the observed negative effect of species richness on
-temporal stability of community biomass despite the strong negative effect of species
-richness on synchrony. Could the lower variability of synchrony be a
-characteristic of multitrophic communities? Theoretical models suggest that
-generalist predator can either synchronise or desynchronize the dynamics its
-prey, depending on the distribution of interaction strength and competition
-between preys [@raimondo_interspecific_2004; @korpimaki_predatorinduced_2005;
-@mccann_more_2009]. Alternatively, it is possible that, in aquatic food-webs,
-the occurrence of large oscillatory dynamics typical of predator-prey dynamics
-leads to a larger variability of population variability than the one of synchrony
-[@mccann_reevaluating_1997]. Another hypothese is that food-webs are
-characterized by highly uneveness biomass distribution, which can decrease the
-variability of synchrony, i.e. decrease the strength of the porfolio effect
-[@doak_statistical_1998; @thibaut_understanding_2013].
-
-All together, the destabilising effect of species richness on temporal stability
-raises more questions than it solves and then highlight the need for more
-investigations about the difference between single and multitrophic
-communities in natural communities.
+Contrary to most experimental and empirical results [@tilman_biodiversity_2006;
+@franssen_annual_2011; @pennekamp_biodiversity_2018; @olivier_urbanization_2020;
+@valencia_synchrony_2020, but see, Declerck *et al.* 2006], we found a negative
+relationship between species richness and stability of community biomass. This
+effect resulted from a combination of two effects, one on population synchrony
+and one on population variability, both of which contribute to the stability of
+community biomass. The negative effect of species richness on population
+synchrony we found, thereby increasing stability of community biomass, is in
+accordance with most studies on experimental grasslands
+[@isbell_biodiversity_2009; @roscher_identifying_2011] as well as natural
+communities such as birds, grasses, bats or butterflies [@bluthgen_land_2016;
+@olivier_urbanization_2020, but see, Declerck *et al.* 2006;
+@valencia_synchrony_2020]. Our result thus extend this relationship to
+multi-trophic communities.
+
+The positive effect of species richness on population variability that we found,
+thereby destabilising communities, is more intriguing and does not fit the
+findings of a meta-analysis reporting more frequent negative effects of richness
+on population variability in multi-trophic communities [@jiang_different_2009].
+Food-web theory predicts that the relationship between the temporal stability of
+populations and species richness depends on the strength of interactions and its
+distribution [@mccann_reevaluating_1997; @thebault_trophic_2005;
+@downing_temporal_2020], with stronger interactions promoting a negative
+relationship between species richness and stability. This might be the case in
+our study system but this hypothesis remains to be directly tested.
+Alternatively, a positive richness-population variability relationship can come
+from an increased demographic stochasticity with increasing species richness
+[@loreau_species_2008].
+
+In our study system, the destabilising effect of species richness via increased
+population variability was stronger than the stabilising effect via decreased
+synchrony. The balance between both effects is governed by the balance in the
+variation in population variability and synchrony among communities, this
+because we used standardised coefficients (see methods). Such an effect of
+population variability on community stability twice as strong as the one of
+synchrony is expected from the mathematical relation between these three
+variables. This indicates that the variability of population variability and
+synchrony among the studied communities are equivalent (Eq. \@ref(eq:stab)).
+This result contrasts with previous findings on terrestrial animal communities
+showing a variability in population synchrony twice as strong as the one of
+population variability [@olivier_urbanization_2020]. Such difference in the
+relative variability of population stability and synchrony between studies might
+be related to the multitrophic structure of the dataset as theory predicts
+potential synchronising effect of generalist predators, such as piscivorous
+fishes, on prey dynamics [@raimondo_interspecific_2004; @huber_role_2006].
+Trophic interactions might also raise synchrony between predators and preys and
+thereby increase the overall synchrony of trophic communities [Fig. S9,
+@bulmer_phase_1975]. However, generalist predators can also generate
+asynchronous dynamics among preys depending on the distribution of interaction
+strengths [@huber_role_2006; @mccann_more_2009]. The difference between our
+results and those of @olivier_urbanization_2020 might also relate to the type of
+ecosystems considered. Aquatic ecosystems have been suggested to show greater
+population variability than terrestrial ecosystems [@rip_cross-ecosystem_2011],
+which could also translate in greater variation range of population variability
+among aquatic communities than among terrestrial ones. Another hypothesis
+relates to the evenness of the biomass distribution among species, with low
+evenness decreasing the range of variation in synchrony among communities and thereby
+the strength of the portfolio effect [@doak_statistical_1998;
+@thibaut_understanding_2013]. Whether the biomass distribution in stream fish
+assemblages is particularly uneven when compared to the terrestrial communities
+studied by @olivier_urbanization_2020 remains however to be tested. In any case,
+more studies are needed to understand how the relative importance of synchrony
+and population variability for community stability varies among ecosystems.
 
@@
 Our analysis further indicates that network structure, and in particular average
-trophic level was strongly related to community biomass, as higher total
-biomass was found in communities with an higher average trophic level. These results are
-in accordance with the predictions of theoretical models [@schneider_animal_2016;
-@wang_biodiversity_2018]. @wang_biodiversity_2018 proposed that this effect is driven
-by predators selecting primary producers with higher resource use efficiency and predators
-enhancing complementarity between primary producers, a mechanism which
-drive the positive effect of horizontal diversity on productivity
-[@loreau_biodiversity_2001].
-
-In addition, our results show that communities with an higher average trophic
-level had a lower population variability, and thereby were more stable. This
-result is in accordance with theoretical models [@shanafelt_stability_2018;
-@barbier_pyramids_2019; @mccann_diversitystability_2000] and might result from a
-higher stability of populations of higher trophic levels
-[@shanafelt_stability_2018; @barbier_pyramids_2019] or a damping effect of
-higher trophic levels on the variability of lower trophic level populations
+trophic level was strongly related to community biomass, as higher community
+biomass was found in communities with higher average trophic level. These
+results are in accordance with the theoretical predictions [@schneider_animal_2016;
+@wang_biodiversity_2018], proposing that predation selects for primary producers with
+higher resource use efficiency and enhance complementarity between primary
+producers [@wang_biodiversity_2018].
+
+Further, our results show that communities with higher average trophic level had
+a lower population variability, and were thereby more stable. This result is
+also in accordance with theoretical models predicting a higher stability of
+populations of higher trophic levels [@shanafelt_stability_2018;
+@barbier_pyramids_2019] or a damping effect of higher trophic levels on the
+variability of lower trophic level populations
 [@mccann_diversitystability_2000].
 
-In contrast, we found that connectance was not related to community biomass,
-which contradicts theoretical models which suggest that a greater connectance should
-decrease complementarity in resource use between species, which is expected to
-lower community biomass [@thebault_food-web_2003; @poisot_trophic_2013].
-However, the effect of connectance on productivity has been poorly investigated.
-
-One of the most surprising result is that we found no relationship between
-connectance and stability. It contrasts with the central role that connectance
-plays in the studies of the food-web complexity-stability relationship [e.g.,
+In contrast, we found that food-web connectance was not related to community
+biomass, which contradicts theoretical models suggesting that higher connectance
+is expected to lower community biomass by decreasing complementarity in resource
+use among species [@thebault_food-web_2003; @poisot_trophic_2013]. However, the
+effect of connectance on productivity remains poorly investigated.
+
+Unexpectedly, we found no relationship between food-web connectance and
+stability of community biomass which contrasts with many theoretical results
+highlighting a food-web complexity-stability relationships [e.g.,
 @angelis_stability_1975; @may_will_1972; @thebault_stability_2010; but see
-@neutel_reconciling_2007], although theoretical ecology generally considers
-different stability concepts and metrics [@arnoldi_resilience_2016]. The lack of
-effect of connectance on the temporal stability of community biomass might be
-related to the fact that our measure of connectance does not take into account
-the distribution of interaction strengths in the food-webs. Indeed, food-web
-connectance is expected to have different consequences on the temporal stability
-of community biomass depending on the strength of trophic interactions
-[@thebault_trophic_2005], which we could not test due to the scarcity of
-information on the lower compartments of the community, i.e. primary producers,
-decomposers and the benthic species.
+@neutel_reconciling_2007], although they generally consider different stability
+concepts and metrics [@arnoldi_resilience_2016]. The lack of connectance effect
+on the temporal stability of community biomass might be related to the
+connectance metric we used, in particular the fact that it did not account for
+interaction strengths. Indeed, connectance stability relationship is expected to
+vary depending on the strength of trophic interactions [@thebault_trophic_2005].
+Further, in our dataset, resource nodes, i.e. primary producers, decomposers and
+the benthic species, were highly aggregated which might blur potential
+connectance differences among communities.
 
@@
 
-We found that the larger, warmer and more enriched streams had higher total biomass
-through higher average trophic level and species richness, in line with mounting
-body of work reporting important effects of temperature on the structure and
-biomass of aquatic systems [@allan_stream_2007; @edeline_ecological_2013;
-@emmrich_geographical_2014; @hattab_forecasting_2016; @woods_testing_2020].
-Larger ecosystem in freshwater systems might provide a higher diversity
-of resources through habitat heterogeneity and then result in higher species
-richness and community biomass by surface unit, through complementarity in
-resource use. Our result suggest that warming and enrichment might result in
-higher total biomass but previous studies find contradictory results
-[@yvondurocher_warming_2011; @dossena_warming_2012;
-@maureaud_biodiversityecosystem_2019; @tabi_warming_2019]. One of the reason
-might be that temperature has non monotonic effects on biological processes and
-that temperature and enrichment can have antagonistic effects 
-[@oconnor_warming_2009; @uszko_effects_2017; @tabi_warming_2019].
-
-Our analysis revealed that stream size had only a weak effect on the temporal
-stability of community biomass, while warmer and enriched streams had an higher
-average population variability, thereby a lower temporal stability. Our results
-are in line with previous experiments showing that warming decreases temporal
-stability, however enrichment is predicted to counter the destabilising effect
-of warming [@binzer_dynamics_2012; @tabi_warming_2019].  However, enrichment alone 
-is predicted to increase population variability while warmer 
-temperature is predicted to decrease stability through starvation resulting from high
-metabolic activity [@tabi_warming_2019] but again it depends on the species thermal
-niche and of the shape of the response of biological processes to warming
-[@uszko_effects_2017].
-
----
-#Interestingly, the two PCA axes related to environmental conditions had indirect
-#effects on stability through two conflicting pathways, either stabilising, via
-#network structure, or destabilising, via species richness. The first pathway
-#consists in a positive effect of temperature and stream size on mean
-#trophic level, in line with the idea that wider streams and warmer conditions
-#are favourable to mesotrophic predators [@allan_stream_2007;
-#@emmrich_geographical_2014], which in turn stabilises biomass fluctuations,
-#possibly due to increased top-down regulation. The second pathway consists in a
-#positive effect of temperature and stream size on species richness, which itself
-#has a destabilising effect. This result is interesting in that both
-#pathways had not been evidenced to jointly play, to the best of our knowledge.
-#Furthermore, it is unclear which pathway is dominating, and under which circumstances,
-#opening an interesting avenue for further investigations.
----
-
----
-## Final thoughts about empirical food-webs
-
-#It was unexpected that the average population $\overline{CV_{sp}}$
-#had a stronger negative effect on biomass stability than synchrony
-#[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
-#negative effect of species on temporal stability of biomass. The lower effect of
-#synchrony can be explained by the  presence of generalist predators in stream
-#communities, which can raise synchrony between prey species which shares the
-#same predator [@raimondo_interspecific_2004]. Uneven population biomass within
-#communities also raise synchrony between species [@thibaut_understanding_2013].
-
-#As found in other studies, we found that species richness was negatively related
-#to mean trophic level and connectance [@winemiller_must_1989;
-#@dunne_network_2006; @thebault_stability_2010]. Species richness had thus a
-#consistent destabilising effect on temporal stability of biomass directly and
-#through average trophic level, but it has a direct positive effect on total annual
-#biomass directly but a negative one through the decrease of average trophic
-#level. It highlights the importance to consider several aspects of
-#network structure to order to improve our understanding of the drivers of
-#community structure and stability.
----
+We found that the larger as well as warmer and more enriched streams had higher
+community biomass, and that this was mediated by higher species richness and
+average trophic level. Regarding the effect of ecosystem size, our results thus
+support a classical theory of food-web ecology [@post_ecosystem_2000;
+@doi_resource_2009]. Larger freshwater ecosystems provide higher diversity of
+resources through habitat heterogeneity and then result in higher species
+richness and mean trophic level per surface unit, through complementarity in
+resource use [@post_ecosystem_2000; @doi_resource_2009; @mchugh_dual_2010].
+Regarding temperature and enrichment effect, our study joins the mounting body
+of works reporting effect on the structure and biomass of aquatic systems
+[@allan_stream_2007; @edeline_ecological_2013; @emmrich_geographical_2014;
+@hattab_forecasting_2016; @woods_testing_2020; @bonnaffe_trophic_2021]. However,
+current results do not show consensus [@yvondurocher_warming_2011;
+@dossena_warming_2012; @maureaud_biodiversityecosystem_2019;
+@tabi_warming_2019], with potential antagonistic effects of temperature and
+enrichment as well as non-monotonic effects [@oconnor_warming_2009;
+@uszko_effects_2017; @tabi_warming_2019]. Although we could not tease apart the
+respective effects of temperature and enrichment, our results indicates that in
+the range of observed covariation in temperature and enrichment, their joint
+effects result in a positive relationship with community biomass.
+
+Our analysis further revealed that stream size had only a weak effect on the
+temporal stability of community biomass, while warmer and enriched streams
+exhibit less stable community biomass mainly via an increase in population
+variability. These results are in line with previous experiments showing that
+warming or enrichment decrease the temporal stability of communities
+[@kratina_warming_2012; @tabi_warming_2019]. However, several studies have
+highlighted that the effects of temperature on stability can be complex, and
+interact with those of enrichment [@binzer_dynamics_2012; @uszko_effects_2017].
 
@@
 by the challenges associated with manipulating both species richness and
-food-web structure  experimentally [e.g. @sander_ecological_2017] and by the
-fact that describing trophic interactions between species is highly labour
-intensive. These challenges are even more acute when studying the temporal
-stability of ecosystem properties, which requires time series. In this context,
-recent developments to predict trophic interactions among species
+food-web structure experimentally [e.g. @sander_ecological_2017] and by the fact
+that describing trophic interactions between species is highly labour-intensive.
+These challenges are even more acute when studying the temporal stability of
+ecosystem properties, which requires time series. In this context, recent
+developments to predict trophic interactions among species
 [@beckerman_foraging_2006; @gravel_inferring_2013; @portalier_mechanics_2019],
 combined with observational long-term monitoring of ecological communities,
-offer an promising opportunity. They thus offer a way to maximise the  amount of
-information that we can extract from already collected empirical data, but at
-the cost of their precision. Build on the ratio of body-size between predator
-and prey [@gravel_inferring_2013], those methods are however in general blind to
-the modulation of species interactions according to the realized niche of
-species such as temperature and prey preferences. Although, the development of
-more mechanistic methods incorporating predator behaviour
-[@portalier_mechanics_2019] or more statistically flexible framework such as
-machine learning [@pichler_machine_2020] will certainly increase the accuracy of
-species interaction predictions. With the increasing availability of long-term
-empirical data, we believe that methods of food-web reconstruction have a great
-potential to increase our understanding of the role of network structure on
-ecosystem functioning in natural settings.
+offer a promising opportunity.  They offer a way to maximise the amount of
+information that can be extracted from already collected empirical data, but at
+the cost of their precision. Here, we built binary interaction networks based on
+the ratio of body-size between predator and prey ignoring modulation of
+interactions strength depending on preferences or environmental factors.
+Refining the construction of interaction networks by, for example, integrating
+predator behaviour [@portalier_mechanics_2019] or developing more statistically
+flexible framework such as machine learning [@pichler_machine_2020] will
+certainly increase the accuracy of species interaction predictions. Although
+challenging, methods of food-web reconstruction have a great potential to
+increase our understanding of network structure effects on ecosystem function
+and dynamic in natural settings using available long-term empirical data.
 
@@
 extends the assessment of the effect of species richness on community biomass
-and its temporal stability to the case of food-webs in natural settings,
-providing the evidence that species richness decreases synchrony also in
-multi-trophic communities. Our results highlight population variability as key
-in transmitting effects of species richness, network structure and environmental
-gradients on community stability. This contrast with previous results found in
-single trophic communities, mostly plants, that mainly focus on synchrony and,
-although further confirmation are needed, might be characteristic of animal
-and/or multi-trophic communities. Further, we found that the effects of
-environmental gradient related to temperature, enrichment and ecosystem size are
-largely mediated by their impact on richness and average trophic level. Finally,
-our study open stimulating questions about how the food-web structure and
-species richness drives synchrony and population variability.
+and its temporal stability to the case of freshwater food-webs in natural
+settings. While our results are in accordance with numbers of studies showing a
+positive effect of richness on community biomass, they provide a contrasting
+example of negative relationship between richness and stability of community
+biomass. Our results highlight population variability as key in transmitting
+effects of species richness, network structure and environmental gradients on
+community stability, opening stimulating questions about how the food-web
+structure and species richness drive population synchrony and variability.
 
@@
   on the period 1995-2018. The red dots show the location of (C) and (D) sites.
-  ", " Inner borders draw the limits of the hydrographic basins. ", pca_caption,
-  " (C) and (D) The temporal dynamic of population biomass with three networks
-  of years 1997, 1999 and 2002. Each trophic species is represented
-  by a node and each color represents a species. The node size are proportional to
-  the biomass of the trophic species. The seven resource nodes are drawn in grey. ",
-  "The species names corresponding to the three digit codes are found in Table
-  S1.")
+  Inner borders draw the limits of the hydrographic basins. (B) Principal
+  Component Analysis performed on environmental variables.  The first axis was
+  positively related to the stream size, the second axis was related to the
+  stream slope and altitude and negatively related to average water temperature
+  and Biological Oxygen Demand (BOD). (C) and (D) Temporal dynamic of
+  communities with examples of networks corresponding to the years 1997, 1999
+  and 2002. Each trophic species is represented by a node and each color
+  represents a species (see method). Node size is proportional to the biomass of
+  the trophic species. The seven resource nodes are coloured in grey. Species
+  names corresponding to the three digit codes are found in Table S1.")
 
@@
 
-```{r, cache = FALSE}
-sem_caption <- paste0(
-  "Structural Equation Models for the median of annual
-  community biomass (in grams by square meter) and (C) its temporal stability.",
-  " Results of the Structural Equation Models for
-  (B) the median of annual community biomass and (D) its temporal stability. Red and black
-  arrows represent respectively negative and positive path coefficients. The
-  path coefficients are standardized. For convenience, only significant
-  paths (i.e. $P < 0.05$) are shown. Rsq: Adjusted $R^2$; Avg:
-  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
-  second axis of the PCA performed on environmental variables (see methods)."
-)
-```
-
 ```{r}
 
-sem_bm_caption <- paste0( "Species richness and average trophic level are
-  positively linked to community biomass. (A) Structural Equation Model for the
-  median of annual community biomass (in grams by square meter). Dotted and
-  solid arrows represent respectively negative and positive path coefficients.
-  Non significant paths are shown in grey. The path coefficients are
-  standardized. The $R^2$ are the adjusted $R^2$; Avg: Average, CVsp: weighted
-  temporal CV of the population biomass; PCA1 and PCA2: respectively the first
-  and second axis of the PCA performed on environmental variables (see methods).
-  (B) to (G): significant bivariate relationships between variables of the
-  structural equation model. The solid lines show the predictions of the
-  statiscal model.")
+sem_bm_caption <- paste0( 
+  "Relationships among the predictors of community biomass. (A) Structural
+  Equation Model for the median of annual community biomass (in grams by square
+    metre). Dotted and solid arrows represent, respectively, negative and
+  positive path coefficients. Non significant paths are coloured in grey. The
+  path coefficients are standardised. $R^2$: adjusted $R^2$; Avg: Average, CVsp: weighted
+  temporal coefficient of variation of the population biomass; PCA1 and PCA2:
+  respectively the first and second axis of the principal component analysis
+  performed on environmental variables (see methods). (B) to (G): significant
+  bivariate relationships between variables of the structural equation model.
+  Solid lines depict the predictions of the statistical model. A sensibility
+  analysis is displayed in supplementary information (Fig.
+    S8).")
 
@@
 
-sem_stab_caption <- paste0("Relationships among environment, species richness,
-  food-web structure, stability decomposition and the temporal stability of community biomass. (A)
-    Structural Equation Model for the temporal stability of community biomass.
-  Dotted and solid arrows represent respectively
-  negative and positive path coefficients. Non significant paths are shown in
-  grey. The path coefficients are standardized. The $R^2$ are the adjusted
-  $R^2$; Avg: Average, CVsp: weighted temporal CV of the population biomass;
-  PCA1 and PCA2: respectively the first and second axis of the PCA performed on
-  environmental variables (see methods). (B) to (I): significant bivariate
-  relationships between variables of the structural equation model. The solid
-  lines show the predictions of the statistical model.")
+sem_stab_caption <- paste0(
+  "Relationships among the predictors of the temporal stability of community
+  biomass. (A) Structural Equation Model for the temporal stability of community
+  biomass. Dotted and solid arrows represent, respectively, negative and positive
+  path coefficients. Non significant paths are coloured in grey. The path
+  coefficients are standardised. $R^2$: adjusted $R^2$; Avg: Average, CVsp: weighted
+  temporal coefficient of variation of the population biomass; PCA1 and PCA2:
+  respectively the first and second axis of the principal component analysis
+  performed on environmental variables (see methods). The $R^2$ for the temporal
+  stability of community biomass is exactly one because the relation is
+  determistic (see Eq. 4). (B) to (I): significant
+  bivariate relationships between variables of the structural equation model.
+  Solid lines depict the predictions of the statistical model. A sensibility
+  analysis is displayed in supplementary information (Fig.
+    S8)."
+  )
 ```

### 2021-07-06 manuscript/bef_stability/manuscript.Rmd
A proposition for reviewer 3

@@
 population variability was stronger than the stabilising effect via decreased
-synchrony. The balance between both effects is governed by the balance in the
-variation in population variability and synchrony among communities, this
-because we used standardised coefficients (see methods). Such an effect of
-population variability on community stability twice as strong as the one of
-synchrony is expected from the mathematical relation between these three
-variables. This indicates that the variability of population variability and
-synchrony among the studied communities are equivalent (Eq. \@ref(eq:stab)).
-This result contrasts with previous findings on terrestrial animal communities
-showing a variability in population synchrony twice as strong as the one of
-population variability [@olivier_urbanization_2020]. Such difference in the
-relative variability of population stability and synchrony between studies might
-be related to the multitrophic structure of the dataset as theory predicts
+synchrony.  This contrasts with the previous study of Olivier et al. (2021) on
+animal communities in terrestrial ecosystems. The difference of the effect of
+species richness on population stability and synchrony between studies might be
+related to the multitrophic structure of the dataset as theory predicts
 potential synchronising effect of generalist predators, such as piscivorous
@@
 relates to the evenness of the biomass distribution among species, with low
-evenness decreasing the range of variation in synchrony among communities and thereby
-the strength of the portfolio effect [@doak_statistical_1998;
+evenness decreasing the range of variation in synchrony among communities and
+thereby the strength of the portfolio effect [@doak_statistical_1998;
 @thibaut_understanding_2013]. Whether the biomass distribution in stream fish
@@
 studied by @olivier_urbanization_2020 remains however to be tested. In any case,
-more studies are needed to understand how the relative importance of synchrony
-and population variability for community stability varies among ecosystems.
+more studies are needed to understand how the relative importance of the effect
+of species richness on synchrony and population variability varies among
+ecosystems.
 

### 2021-07-12 manuscript/bef_stability/manuscript.Rmd
According to comments of coauthors

@@
 effects on richness and network structure. Strikingly,
-community stability was mediated by the variation of population stability rather
+the effect of species richness on community stability was mediated by population stability rather
 than synchrony, which contrasts with results from single-trophic communities. We
@@
 
-Environment can affect functioning and stability directly or through effects on
-resource availability, species richness or food-web
-structure. Agricultural intensification and temperature changes can also...
-
 ---
@@
 \@ref(eq:stab), the unstandardised coefficients of synchrony and population
-variability determining
-temporal stability of community biomass are respectively -0.5 and -1.0. When
-standardised, the relative comparison of those coefficients comes down to a
-comparison of the standard deviation of these two variables. The deviation from
-unstandardised effect values (i.e. -0.5 and -1.0) indicates that one component of community stability
-displays more variations than the other, and that the determinants of
-the more variable component will be those affecting community
-stability the most. The paths whose slope had a $P$ value inferior or equal to $0.05$
-were reported in the main text, all the path values are presented in Table S7
-and S8. Indirect effects on community biomass and its temporal stability were
-computed by multiplying slopes along the path. Only significant direct slopes
-were included in the calculation of indirect effects. Total effects were
-computed as the sum of direct and indirect effects.
+variability determining temporal stability of community biomass are respectively
+-0.5 and -1.0. When standardised, the relative comparison of those coefficients
+comes down to a comparison of the standard deviation of these two variables. The
+deviation from unstandardised effect values (i.e. -0.5 and -1.0) indicates that
+one component of community stability displays more variations than the other,
+and that the determinants of the more variable component will be those affecting
+community stability the most. The paths whose slope had a $P$ value inferior or
+equal to $0.05$ were reported in the main text, all the path values are
+presented in Table S7 and S8. Indirect effects on community biomass and its
+temporal stability were computed by multiplying slopes along the path. Only
+significant direct slopes were included in the calculation of indirect effects.
+Total effects were computed as the sum of direct and indirect effects.
 
@@
 community biomass and its temporal stability went through food-web structure.
+The relationships resulting from the SEM are robust to different station
+selection criteria in the analysis, with different selections ranging in 65 to
+403 stations (see sensitivity analysis, Fig. S8).
 
@@
 $`r env_on_bm$via_tlvl["log_RC1"]`$
-resp., Fig. \@ref(fig:sem-bm) F, G, Table \@ref(tab:indir-sem)). The second
+resp., Fig. \@ref(fig:sem-bm)F, G, Table \@ref(tab:indir-sem)). The second
 axis, related to the average annual temperature and BOD was positively related
@@
 population variability was stronger than the stabilising effect via decreased
-synchrony.  This contrasts with the previous study of Olivier et al. (2021) on
-animal communities in terrestrial ecosystems. The difference of the effect of
-species richness on population stability and synchrony between studies might be
-related to the multitrophic structure of the dataset as theory predicts
-potential synchronising effect of generalist predators, such as piscivorous
-fishes, on prey dynamics [@raimondo_interspecific_2004; @huber_role_2006].
-Trophic interactions might also raise synchrony between predators and preys and
-thereby increase the overall synchrony of trophic communities [Fig. S9,
-@bulmer_phase_1975]. However, generalist predators can also generate
-asynchronous dynamics among preys depending on the distribution of interaction
-strengths [@huber_role_2006; @mccann_more_2009]. The difference between our
-results and those of @olivier_urbanization_2020 might also relate to the type of
-ecosystems considered. Aquatic ecosystems have been suggested to show greater
-population variability than terrestrial ecosystems [@rip_cross-ecosystem_2011],
-which could also translate in greater variation range of population variability
-among aquatic communities than among terrestrial ones. Another hypothesis
-relates to the evenness of the biomass distribution among species, with low
-evenness decreasing the range of variation in synchrony among communities and
-thereby the strength of the portfolio effect [@doak_statistical_1998;
-@thibaut_understanding_2013]. Whether the biomass distribution in stream fish
-assemblages is particularly uneven when compared to the terrestrial communities
-studied by @olivier_urbanization_2020 remains however to be tested. In any case,
-more studies are needed to understand how the relative importance of the effect
-of species richness on synchrony and population variability varies among
-ecosystems.
+synchrony. Further, as the effects of species richness on population variability
+and synchrony we found here were of similar amplitude, the balance between both
+pathways is governed by the relative standard deviation of population
+variability and synchrony, this because we used standardized coefficients (see
+methods). The fish communities studied here therefor present similar level of
+variation in population variability and synchrony, again contrasting with
+results on terrestrial animal communities that exhibited twice as much variation
+in population synchrony than in population variability
+[@olivier_urbanization_2020]. This opens intriguing questions as to potential
+mechanisms constraining the variation range of population variability and
+synchrony among communities. Lower variation in population synchrony among the
+fish communities studied here might relates to their trophic structure as theory
+predicts potential synchronising effect of generalist predators, such as
+piscivorous fishes, on prey dynamics [@raimondo_interspecific_2004;
+@huber_role_2006]. Trophic interactions might also raise synchrony between
+predators and preys, [Fig. S9, @bulmer_phase_1975], although predictions can
+vary depending on the distribution of interaction strengths [@huber_role_2006;
+@mccann_more_2009]. Restricted variations in population synchrony among
+communities can also be fostered by low biomass evenness and thereby low
+portfolio effect [@doak_statistical_1998; @thibaut_understanding_2013], but
+whether biomass eveness of stream fish communities is particularly low remains
+to be tested. Alternatively, aquatic ecosystems have been suggested to show
+greater population variability than terrestrial ones
+[@rip_cross-ecosystem_2011], which could translate in greater variation range of
+population variability among aquatic communities than among terrestrial ones.
+In any case, more studies are needed to understand how the type of ecosystems
+and trophic interactions constrain synchrony and population variability.
 
@@
   bivariate relationships between variables of the structural equation model.
-  Solid lines depict the predictions of the statistical model. A sensibility
-  analysis is displayed in supplementary information (Fig.
-    S8).")
+  Solid lines depict the predictions of the statistical model. See Fig. S8
+  for a sensitivity analysis according to different station selection
+  criteria.")
 
@@
   bivariate relationships between variables of the structural equation model.
-  Solid lines depict the predictions of the statistical model. A sensibility
-  analysis is displayed in supplementary information (Fig.
-    S8)."
+  Solid lines depict the predictions of the statistical model. See Fig. S8
+  for a sensitivity analysis according to different station selection
+  criteria."
   )
